### 2016-08-02 Documents/Euler/dgEulerCurvilinear.tex
Adding tex document describing hydro.

\documentclass[10pt,preprint]{aastex}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{yhmath}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{../definitions}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

\newcommand{\ee}[1]{{\color{red} #1}}
\newcommand{\dx}{\Delta x}
\newcommand{\pbK}{\partial\mathbf{K}}
\newcommand{\UDG}{\bU_{\mbox{\tiny DG}}}
\newcommand{\sumx}{\sum_{i=1}^{d}}

\begin{document}

\title{Nodal Discontinuous Galerkin Method for the Euler Equations with Curvilinear Coordinates and Nuclear Equation of State for Astrophysics Simulations}
\author{Eirik Endeve\altaffilmark{1}}
\altaffiltext{1}{Department of Computational and Applied Mathematics, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}

\begin{abstract}
We explore the use of the nodal Discontinuous Galerkin (DG) method in astrophysical hydrodynamics.  
We focus on issues related to core-collapse supernova dynamics, which include the use of curvilinear coordinates and a nuclear equation of state.  
\end{abstract}

\section{Introduction}

\section{Euler Equations of Gas Dynamics in Curvilinear Coordinates}

$\vect{r}(\vect{x})\in\mathbb{R}^{3}$, so that the displacement vector is $d\vect{r}=dx^{i}\,\vect{e}_{i}$, where the coordinate basis vectors are
\begin{equation}
  \vect{e}_{i}=\pderiv{\vect{r}}{x^{i}}
\end{equation}
$ds_{\vect{x}}^{2}=d\vect{r}\cdot d\vect{r}$
\begin{equation}
  ds_{\vect{x}}^{2}=\gamma_{ij}\,dx^{i}\,dx^{j},
\end{equation}
where the coordinate basis metric tensor is defined as $\gamma_{ij}=\vect{e}_{i}\cdot\vect{e}_{j}$.

For general curvilinear spatial coordinates, the Euler equations for gas dynamics are \citep{landauLifshitz_1959}
\begin{equation}
  \pderiv{\rho}{t}
  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\rho\,v^{i}\,\Big)=0,
\end{equation}
\begin{equation}
  \pderiv{M_{j}}{t}
  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,P^{i}_{~j}\,\Big)=\f{1}{2}\,P^{ik}\,\pderiv{\gamma_{ik}}{x^{j}},
\end{equation}
\begin{equation}
  \pderiv{E}{t}
  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\big(E+p\big)\,v^{i}\,\Big)=0,
\end{equation}
\begin{equation}
  \pderiv{n_{e}}{t}
  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,n_{e}\,v^{i}\,\Big)=0,
\end{equation}
where $\rho$ is the (baryon) mass density, $M^{i}=\rho\,v^{i}$ is the momentum density, $P^{ij}=\rho\,v^{i}\,v^{j}+p\,\gamma^{ij}$ the stress tensor, $E=e+\f{1}{2}\,\rho\,v_{i}\,v^{i}$ the total (internal plus kinetic) energy density, and $n_{e}$ the electron density.  
The pressure is related to the density, internal energy density, and electron density by an equation of state (EoS); i.e., $p=p(\rho,e,n_{e})$.  
(We also define the specific internal energy by $\epsilon=e/\rho$.)

We assume the following diagonal form of the spatial metric tensor
\begin{equation}
  \gamma_{ij}=\mbox{diag}\big[\,1,a(x^{1})^{2},\,b(x^{1})^{2}c(x^{2})^{2}\,\big], 
\end{equation}
which is sufficiently general to accommodate Cartesian, cylindrical, and spherical polar coordinates (see Table~\ref{tab:metricFunctions} and Appendix~\ref{app:CurvilinearEuler}).  
$\sqrt{\gamma}=abc$.  $w^{i}=e^{i}_{~j}\,\bar{w}^{j}$.  
With $e^{i}_{~j}=\mbox{diag}\big[\,1,a(x^{1})^{-1},\,b(x^{1})^{-1}c(x^{2})^{-1}\,\big]$, we have $\{w^{i}\}_{i=1}^{3}=\{\bar{w}^{1},\,a^{-1}\,\bar{w}^{2},\,b^{-1}c^{-1}\,\bar{w}^{3}\}$.  
\begin{table}
  \begin{center}
  \caption{Metric functions for Cartesian, Cylindrical, and Spherical coordinate systems.\label{tab:metricFunctions}}
  \begin{tabular}{cccccccccccccc}
    \midrule
    Coordinates & $x^{1}$ & $x^{2}$ & $x^{3}$ & $\bar{w}^{1}$ & $\bar{w}^{2}$ & $\bar{w}^{3}$ & $a$ & $b$ & $c$ & $\sqrt{\gamma}$
    & $\pderiv{a}{x^{1}}$ & $\pderiv{b}{x^{1}}$ & $\pderiv{c}{x^{2}}$ \\
    \midrule
    \midrule
    Cartesian & $x$ & $y$ & $z$ & $w_{x}$ & $w_{y}$ & $w_{z}$ & 1 & 1 & 1 & 1 & 0 & 0 & 0 \\
    Cylindrical & $R$ & $z$ & $\phi$ & $w_{R}$ & $w_{z}$ & $w_{\phi}$ & 1 & $R$ & 1 & $R$ & 0 & 1 & 0 \\
    Spherical & $r$ & $\theta$ & $\phi$ & $w_{r}$ & $w_{\theta}$ & $w_{\phi}$ & $r$ & $r$ & $\sin\theta$ & $r^{2}\sin\theta$ & 1 & 1 & $\cos\theta$ \\
    \midrule
    \midrule
  \end{tabular}
  \end{center}
\end{table}

The mass conservation equation
\begin{equation}
  \pderiv{\rho}{t}
  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,\rho\,\bar{v}^{1}\,\Big)
  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,\rho\,\bar{v}^{2}\,\Big)
  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\rho\,\bar{v}^{3}\,\Big)=0
\end{equation}
Components of the momentum equation
\begin{equation}
  \pderiv{\bar{M}^{i}}{t}
  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,\bar{P}^{1i}\,\Big)
  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,\bar{P}^{2i}\,\Big)
  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\bar{P}^{3i}\,\Big)
  =\bar{S}^{i},
\end{equation}
where the ``geometry sources'' are given by
\small
\begin{equation}
  \bar{S}^{1}
  =\bar{P}^{22}\f{1}{a}\pderiv{a}{x^{1}}+\bar{P}^{33}\f{1}{b}\pderiv{b}{x^{1}}, \quad
  \bar{S}^{2}
  =\bar{P}^{33}\f{1}{ac}\pderiv{c}{x^{2}}-\bar{P}^{12}\f{1}{a}\pderiv{a}{x^{1}}, \quad
  \bar{S}^{3}
  =-\bar{P}^{13}\f{1}{b}\pderiv{b}{x^{1}}-\bar{P}^{23}\f{1}{ac}\pderiv{c}{x^{2}}.  
\end{equation}
\normalsize
Energy equation
\begin{equation}
  \pderiv{E}{t}
  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,\big(E+p\big)\,\bar{v}^{1}\,\Big)
  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,\big(E+p\big)\,\bar{v}^{2}\,\Big)
  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\big(E+p\big)\,\bar{v}^{3}\,\Big)=0.  
\end{equation}
The electron conservation equation
\begin{equation}
  \pderiv{n_{e}}{t}
  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,n_{e}\,\bar{v}^{1}\,\Big)
  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,n_{e}\,\bar{v}^{2}\,\Big)
  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,n_{e}\,\bar{v}^{3}\,\Big)=0
\end{equation}
By defining $\bU=\big(\,\rho,\,\rho\,\bar{v}^{1},\,\rho\,\bar{v}^{2},\,\rho\,\bar{v}^{3},\,E,\,n_{e}\,\big)^{T}$, $\vect{S}(\bU)=\big(\,0,\,\bar{S}^{1},\,\bar{S}^{2},\,\bar{S}^{3}\,,0,\,0\,\big)^{T}$, and
\begin{equation}
  \vect{F}^{i}(\bU)
  =\big(\,\rho\,\bar{v}^{i},\,\rho\,\bar{v}^{1}\,\bar{v}^{i}+p\,\delta^{1i},\,\rho\,\bar{v}^{2}\,\bar{v}^{i}+p\,\delta^{2i},\,\rho\,\bar{v}^{3}\,\bar{v}^{i}+p\,\delta^{3i},\,(E+p)\,\bar{v}^{i},\,n_{e}\,\bar{v}^{i}\,\big)^{T},
\end{equation}
we can write the system of equations in compact form
\begin{equation}
  \pderiv{\bU}{t}
  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,\vect{F}^{1}(\bU)\,\Big)
  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,\vect{F}^{2}(\bU)\,\Big)
  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\vect{F}^{3}(\bU)\,\Big)
  =\vect{S}(\bU).
  \label{eq:extendedEulerCompact}
\end{equation}

\section{Discontinuous Galerkin Discretization}

We divide the computational domain $D$ into a disjoint union $\mathcal{T}$ of open elements $\bK$, so that $D = \cup_{\bK \in \mathcal{T}}\bK$.  
We require that each element is a box in the logical coordinates; i.e.,
\begin{equation}
  \bK=\{\vect{x} : x^{i} \in K^{i} := (\xL^{i},\xH^{i})\}, 
\end{equation}
with the surface elements denoted $\pbK^{i}=\otimes_{j\ne i}K^{j}$.  
We use $V_{\bK}$ to denote the proper volume of the element
\begin{equation}
  V_{\bK} = \int_{\bK}dV, \quad\text{where}\quad dV = \sqrt{\gamma}\,\prod_{i=1}^{d}dx^{i}.  
\end{equation}
We also define $\bx=\{\tilde{\bx}^{i},x^{i}\}$ and $\dx^{i}=\xH^{i}-\xL^{i}$.  
Here we let the approximation space for the DG method, $\mathbb{V}^{k}$, to be constructed from tensor products of one-dimensional polynomials of maximal degree $k$.  
Note that functions in $\mathbb{V}^{k}$ can be discontinuous across element interfaces.

The semi-discrete DG problem is to find $\UDG\in\mathbb{V}^{k}$ (which approximates $\bU$) such that
\begin{align}
  &\partial_{t}\int_{\bK}\UDG\,v\,dV
  +\sumx\int_{\pbK^{i}}\big(\,v\,\widehat{\vect{F}}^{i}(\UDG)\,dA^{i}\big|_{\xH^{i}}-v\,\widehat{\vect{F}}^{i}(\UDG)\,dA^{i}\big|_{\xL^{i}}\,\big) \nonumber \\
  &\hspace{24pt}
  -\sumx\int_{\bK}\vect{F}^{i}(\UDG)\,\nabla_{i}v\,dV
  =\int_{\bK}\vect{S}(\UDG)\,v\,dV
  \label{eq:semidiscreteDG}
\end{align}
for all $v\in\mathbb{V}^{k}$ and all $\bK\in\mathcal{T}$.  
Here, $dV=abc\,dx^{1}\,dx^{2}\,dx^{3}$, the area elements are given by
\begin{equation}
  dA^{1}=abc\,dx^{2}\,dx^{3}=\tau^{1}\,dx^{2}\,dx^{3}, \quad
  dA^{2}=bc\,dx^{1}\,dx^{3}=\tau^{2}\,dx^{1}\,dx^{3}, \quad
  dA^{3}=a\,dx^{1}\,dx^{2}=\tau^{3}\,dx^{1}\,dx^{2}, 
\end{equation}
and the gradient operator is $\nabla_{i}=e^{j}_{~i}\pderiv{}{x^{j}}$.

\ee{Write more about Riemann solvers here.}
In \eqref{eq:semidiscreteDG}, $\vect{\widehat{F}}^{i}(\UDG)$ is a numerical flux approximating the flux on the $i$th surface of $\bK$.  
We also define the numerical flux function $\vect{\mathcal{F}}^{i}$, which for any $v\in\mathbb{V}^{k}$ is written as
\begin{equation}
  \vect{\widehat{F}}^{i}(v)=\vect{\mathcal{F}}^{i}(v(x^{i,-},\tilde{\bx}^{i}),v(x^{i,+},\tilde{\bx}^{i})),
\end{equation}
where superscripts $-/+$, e.g., in the arguments of $v(x^{i,-/+},\tilde{\bx}^{i})$, indicate that the function is evaluated to the immediate left/right of $x^{i}$.

The approximation space $\mathbb{V}^{k}$ contains the constant functions, and the choice $v=1$ in \eqref{eq:semidiscreteDG} gives
\begin{equation}
  \partial_{t}\bU_{\bK}
  +\f{1}{V_{\bK}}\sumx\int_{\pbK^{i}}\big(\,\widehat{\vect{F}}^{i}(\UDG)\,dA^{i}\big|_{\xH^{i}}-\widehat{\vect{F}}^{i}(\UDG)\,dA^{i}\big|_{\xL^{i}}\,\big)
  =\bS_{\bK},
\end{equation}
where we have defined the volume averages
\begin{equation}
  \bU_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\UDG\,dV \quad\text{and}\quad
  \bS_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\vect{S}(\UDG)\,dV.  
\end{equation}
Here we use explicit, SSP-RK time integrators, which are convex combinations of forward Euler time steps \citep{gottlieb_etal_2001}.  
Thus, without loss of generality, we consider here only a forward Euler time step for $\bU_{\bK}$; i.e., 
\begin{equation}
  \bU_{\bK}^{n+1}=\bU_{\bK}^{n}
  =-\f{\dt}{V_{\bK}}\sumx\int_{\pbK^{i}}\big(\,\widehat{\vect{F}}^{i}(\UDG^{n})\,dA^{i}\big|_{\xH^{i}}-\widehat{\vect{F}}^{i}(\UDG^{n})\,dA^{i}\big|_{\xL^{i}}\,\big)
  +\vect{S}_{\bK}^{n},
\end{equation}
where $\dt=t^{n+1}-t^{n}$ is the time step.

\subsection{Further Details on the DG Discretization of the Euler Equations}

In each element $\bK$, we use a nodal representation in the conserved variables $\bU$; i.e.,
\begin{equation}
  \bU(\bx,t)\approx
  \bU_{\DG}(\bx,t)=\sum_{\bi=\vect{1}}^{\bN}\bU_{\bi}(t)\,\ell_{\bi}(\bx),
  \label{eq:conservedNodalExpansion}
\end{equation}
where $\ell_{\bi}(\bx)\in\bbQ^{k}$ are basis functions.  
(Specifically, we use Lagrange polynomials $\ell_{i}(x)$ to construct the multidimensional representation.)  
Moreover $\bi=\{i_{1},\ldots,i_{d}\}$ is a multi-index, and $\ell_{\bi}(\bx)=\prod_{k=1}^{d}\ell_{i_{k}}(x^{k})$.  
From the property $\ell_{i}(x_{j})=\delta_{ij}$ we have the corresponding multidimensional version $\ell_{\bi}(\bx_{\bj})=\delta_{\bi\bj}$, so that $\bU_{\DG}(\bx_{\bi},t)=\bU_{\bi}(t)$; i.e., the expansion coefficients in Equation \eqref{eq:conservedNodalExpansion} represent the conserved variables defined in the nodes $\bx_{\bi}$.  
To evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}, we introduce numerical quadratures.  
First we define the one-dimensional $N$-point quadrature $Q_{N}^{i}:C^{0}(I^{i})\to\bbR$ with abscissas $\{\eta_{q}\}_{q=1}^{N}$ and weights $\{w_{q}\}_{q=1}^{N}$, normalized such that $\sum_{q=1}^{N}w_{q}=1$.  
(For example, the $N$-point Legendre-Gauss quadrature, which we will use, integrates polynomials of degree $\le 2N-1$ exactly.)
If $P(x)$ is such a polynomial, we have
\begin{equation}
  \f{1}{\Delta x}\int_{K}P(x)\,dx=\int_{I}P(\eta)\,d\eta=Q_{N}\big[P\big]\equiv\sum_{q=1}^{N}w_{q}\,P(\eta_{q}).  
\end{equation}

Multi-dimensional integrals are evaluated by tensorization of one-dimensional quadratures.  
For volume integrals, we define $\bQ_{N}:C^{0}(\bI)\to\bbR$ as the tensor product of one-dimensional $N$-point Legendre-Gauss quadrature rules $\bQ_{N}=\otimes_{i=1}^{d}Q_{N}^{i}$ with abscissas $\{\vect{\eta}_{\bq}\}_{\bq=\vect{1}}^{\bN}$ and weights $\{w_{\bq}\}_{\bq=\vect{1}}^{\bN}$.  
Here, $\bq=\{q_{i}\}_{i=1}^{d}\in\bbN^{d}$, $\vect{\eta}_{\bq}=\{\eta_{q_{1}}^{1},\ldots,\eta_{q_{d}}^{d}\}$, and $w_{\bq}=w_{q_{1}}\ldots w_{q_{d}}$, so that the multi-dimensional volume integral is evaluated as
\begin{equation}
  \f{1}{|\bK|}\int_{\bK}P(\bx)\,d\bx
  =\int_{\bI}P(\vect{\eta})\,d\vect{\eta}
  =\bQ_{N}\big[P\big]
  \equiv\sum_{\bq=\vect{1}}^{\bN}w_{\bq}\,P(\vect{\eta}_{\bq}),
\end{equation}
where $P:\bbR^{d}\to\bbR$.  
Similarly, for surface integrals, we define $\tilde{\bQ}_{N}^{i}:C^{0}(\tilde{\bI}^{i})\to\bbR$ as the tensor product $\tilde{\bQ}_{N}^{i}=\otimes_{j\ne i}Q_{N}^{j}$ and denote the abscissas with $\{\tilde{\vect{\eta}}_{\tilde{\bq}_{i}}^{i}\}_{\tilde{\bq}_{i}=\vect{1}}^{\bN}$ and the weights with $\{w_{\tilde{\bq}_{i}}\}_{\tilde{\bq}_{i}=\vect{1}}^{\bN}$, respectively.  
Here, the multi-index is $\tilde{\bq}_{i}=\{q_{j}\}_{j\ne i}\in\bbN^{d-1}$, $\tilde{\vect{\eta}}_{\tilde{\bq}_{i}}^{i}=\{\eta_{q_{j}}^{j}\}_{j\ne i}$, and $w_{\tilde{\bq}_{i}}=\prod_{j\ne i}w_{q_{j}}$.  
Surface integrals are then evaluated as
\begin{equation}
  \f{1}{|\tilde{\bK}^{i}|}\int_{\tilde{\bK}^{i}}P(x^{i},\tilde{\bx}^{i})\,d\tilde{\bx}^{i}
  =\int_{\tilde{\bI}^{i}}P(x^{i},\tilde{\vect{\eta}}^{i})\,d\tilde{\vect{\eta}}^{i}
  =\tilde{\bQ}_{N}^{i}\big[P\big]
  \equiv\sum_{\tilde{\bq}_{i}=\vect{1}}^{\bN}w_{\tilde{\bq}_{i}}\,P(x^{i},\tilde{\vect{\eta}}_{\tilde{\bq_{i}}}^{i}).  
\end{equation}

Inserting \eqref{eq:conservedNodalExpansion} into \eqref{eq:semidiscreteDG}, with $v(\bx)=\ell_{\bk}(\bx)$ and the quadratures defined above, we obtain
\begin{align}
  \pd{}{t}\int_{\bK}\bU_{\DG}\,v\,dV
  &\approx w_{\bk}\,\sqrt{\gamma}_{\bk}\,|\bK|\,\pd{}{t}\bU_{\bk} \nonumber \\
  &\hspace{12pt}
  =w_{\bk}\,a(x_{k_{1}}^{1})\,b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{1}\,\dx^{2}\,\dx^{3}\,\pd{}{t}\bU_{\bk}
\end{align}
for the time derivative term, and
\begin{align}
  \int_{\bK}\bS(\bU_{\DG})\,v\,dV
  &\approx w_{\bk}\,\sqrt{\gamma}_{\bk}\,|\bK|\,\bS(\bU_{\bk}) \nonumber \\
  &\hspace{12pt}
  =w_{\bk}\,a(x_{k_{1}}^{1})\,b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{1}\,\dx^{2}\,\dx^{3}\,\bS(\bU_{\bk})
\end{align}
for the source term.  
For the surface integrals, we obtain, e.g., 
\begin{align}
  %
  \int_{\tilde{\bK}^{1}}v\,\widehat{\bF}^{1}|_{x_{\Hgh}^{1}}\,dA^{1}
  &\approx w_{\tilde{\bk}_{1}}\,\ell_{k_{1}}(+1)\,\widehat{\bF}^{1}(x_{\Hgh}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,
  \tau^{1}(x_{\Hgh}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,|\tilde{\bK}^{1}| \nonumber \\
  &\hspace{12pt}
  =w_{\tilde{\bk}_{1}}\,\ell_{k_{1}}(+1)\,\widehat{\bF}^{1}(x_{\Hgh}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,
  a(x_{\Hgh}^{1})\,b(x_{\Hgh}^{1})\,c(x_{k_{2}}^{2})\,\dx^{2}\,\dx^{3}, \\
  %
  \int_{\tilde{\bK}^{2}}v\,\widehat{\bF}^{2}|_{x_{\Hgh}^{2}}\,dA^{2}
  &\approx w_{\tilde{\bk}_{2}}\,\ell_{k_{2}}(+1)\,\widehat{\bF}^{2}(x_{\Hgh}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,
  \tau^{2}(x_{\Hgh}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,|\tilde{\bK}^{2}| \nonumber \\
  &\hspace{12pt}
  =w_{\tilde{\bk}_{2}}\,\ell_{k_{2}}(+1)\,\widehat{\bF}^{2}(x_{\Hgh}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,
  b(x_{k_{1}}^{1})\,c(x_{\Hgh}^{2})\,\dx^{1}\,\dx^{3}, \\
  %
  \int_{\tilde{\bK}^{3}}v\,\widehat{\bF}^{3}|_{x_{\Hgh}^{3}}\,dA^{3}
  &\approx w_{\tilde{\bk}_{3}}\,\ell_{k_{3}}(+1)\,\widehat{\bF}^{3}(x_{\Hgh}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,
  \tau^{3}(x_{\Hgh}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,|\tilde{\bK}^{3}| \nonumber \\
  &\hspace{12pt}
  =w_{\tilde{\bk}_{3}}\,\ell_{k_{3}}(+1)\,\widehat{\bF}^{3}(x_{\Hgh}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,
  a(x_{k_{1}}^{1})\,\dx^{1}\,\dx^{2}.  
\end{align}
Finally, the `volume terms' become
\begin{align}
  %
  \int_{\bK}\bF^{1}\,\pderiv{v}{x^{1}}\,dV
  &\approx w_{\tilde{\bk}_{1}}\sum_{q_{1}=1}^{N}w_{q_{1}}\,\bF^{1}(x_{q_{1}}^{1},\tilde{\bx}_{\tilde{\bk}_{1}}^{1})\,
  \pderiv{\ell_{k_{1}}}{\eta^{1}}(\eta_{q_{1}}^{1})\,\sqrt{\gamma}(x_{q_{1}}^{1},\tilde{\bx}_{\tilde{\bk}_{1}}^{1})\,|\tilde{\bK}^{1}| \nonumber \\
  &\hspace{12pt}
  =w_{\tilde{\bk}_{1}}\,c(x_{k_{2}}^{2})\,\dx^{2}\,\dx^{3}
  \sum_{q_{1}=1}^{N}w_{q_{1}}\,\bF^{1}(x_{q_{1}}^{1},\tilde{\bx}_{\tilde{\bk}_{1}}^{1})\,
  \pderiv{\ell_{k_{1}}}{\eta^{1}}(\eta_{q_{1}}^{1})\,a(x_{q_{1}}^{1})\,b(x_{q_{1}}^{1}), \\
  %
  \int_{\bK}\bF^{2}\,\f{1}{a}\pderiv{v}{x^{2}}\,dV
  &\approx w_{\tilde{\bk}_{2}}\sum_{q_{2}=1}^{N}w_{q_{2}}\,\bF^{2}(x_{q_{2}}^{2},\tilde{\bx}_{\tilde{\bk}_{2}}^{2})\,
  \f{1}{a(x_{k_{1}}^{1})}\pderiv{\ell_{k_{2}}}{\eta^{2}}(\eta_{q_{2}}^{2})\,\sqrt{\gamma}(x_{q_{2}}^{2},\tilde{\bx}_{\tilde{\bk}_{2}}^{2})\,|\tilde{\bK}^{2}| \\
  &\hspace{12pt}
  =w_{\tilde{\bk}_{2}}\,b(x_{k_{1}}^{1})\,\dx^{1}\,\dx^{3}\sum_{q_{2}=1}^{N}w_{q_{2}}\,\bF^{2}(x_{q_{2}}^{2},\tilde{\bx}_{\tilde{\bk}_{2}}^{2})\,
  \pderiv{\ell_{k_{2}}}{\eta^{2}}(\eta_{q_{2}}^{2})\,c(x_{q_{2}}^{2}), \\
  %
  \int_{\bK}\bF^{3}\,\f{1}{bc}\pderiv{v}{x^{3}}\,dV
  &\approx w_{\tilde{\bk}_{3}}\sum_{q_{3}=1}^{N}w_{q_{3}}\,\bF^{3}(x_{q_{3}}^{3},\tilde{\bx}_{\tilde{\bk}_{3}}^{3})\,
  \f{1}{b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})}\pderiv{\ell_{k_{3}}}{\eta^{3}}(\eta_{q_{3}}^{3})\,\sqrt{\gamma}(x_{q_{3}}^{3},\tilde{\bx}_{\tilde{\bk}_{3}}^{3})\,|\tilde{\bK}^{3}| \nonumber \\
  &\hspace{12pt}
  =w_{\tilde{\bk}_{3}}\,a(x_{k_{1}}^{1})\,\dx^{1}\,\dx^{2}\sum_{q_{3}=1}^{N}w_{q_{3}}\,\bF^{3}(x_{q_{3}}^{3},\tilde{\bx}_{\tilde{\bk}_{3}}^{3})\,
  \pderiv{\ell_{k_{3}}}{\eta^{3}}(\eta_{q_{3}}^{3}).  
\end{align}

Combining the terms above with forward Euler time integration, we obtain
\begin{align}
  \bU_{\bk}^{n+1}
  &=\bU_{\bk}^{n} \nonumber \\
  &\hspace{12pt}
  -\f{\dt}{w_{k_{1}}\,a(x_{k_{1}}^{1})\,b(x_{k_{1}}^{1})\,\dx^{1}}
  \Big(\,
    a(x_{\Hgh}^{1})\,b(x_{\Hgh}^{1})\,\widehat{\bF}^{1,n}(x_{\Hgh}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,\ell_{k_{1}}(+1) \nonumber \\
    &\hspace{128pt}
    -a(x_{\Low}^{1})\,b(x_{\Low}^{1})\,\widehat{\bF}^{1,n}(x_{\Low}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,\ell_{k_{1}}(-1)
  \,\Big) \nonumber \\
  &\hspace{12pt}
  +\f{\dt}{w_{k_{1}}\,a(x_{k_{1}}^{1})\,b(x_{k_{1}}^{1})\,\dx^{1}}
  \sum_{q_{1}=1}^{N}w_{q_{1}}\,a(x_{q_{1}}^{1})\,b(x_{q_{1}}^{1})\,\bF^{1,n}(x_{q_{1}}^{1},\tilde{\bx}_{\tilde{\bk}_{1}}^{1})\,
  \pderiv{\ell_{k_{1}}}{\eta^{1}}(\eta_{q_{1}}^{1}) \nonumber \\
  &\hspace{12pt}
  -\f{\dt}{w_{k_{2}}\,a(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{2}}
  \Big(\,
    c(x_{\Hgh}^{2})\,\widehat{\bF}^{2,n}(x_{\Hgh}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,\ell_{k_{2}}(+1) \nonumber \\
    &\hspace{128pt}
    -c(x_{\Low}^{2})\,\widehat{\bF}^{2,n}(x_{\Low}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,\ell_{k_{2}}(-1)
  \,\Big) \nonumber \\
  &\hspace{12pt}
  +\f{\dt}{w_{k_{2}}\,a(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{2}}
  \sum_{q_{2}=1}^{N}w_{q_{2}}\,\bF^{2}(x_{q_{2}}^{2},\tilde{\bx}_{\tilde{\bk}_{2}}^{2})\,\pderiv{\ell_{k_{2}}}{\eta^{2}}(\eta_{q_{2}}^{2})\,c(x_{q_{2}}^{2}) \nonumber \\
  &\hspace{12pt}
  -\f{\dt}{w_{k_{3}}\,b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{3}}
  \Big(\,
    \widehat{\bF}^{3,n}(x_{\Hgh}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,\ell_{k_{3}}(+1)
    -\widehat{\bF}^{3,n}(x_{\Low}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,\ell_{k_{3}}(-1)
  \,\Big) \nonumber \\
  &\hspace{12pt}
  +\f{\dt}{w_{k_{3}}\,b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{3}}
  \sum_{q_{3}=1}^{N}w_{q_{3}}\,\bF^{3}(x_{q_{3}}^{3},\tilde{\bx}_{\tilde{\bk}_{3}}^{3})\,
  \pderiv{\ell_{k_{3}}}{\eta^{3}}(\eta_{q_{3}}^{3})
  +\dt\,\bS(\bU_{\bk}^{n}).  
\end{align}

\bibliography{./references/references.bib}

\appendix

\section{Euler Equations in Commonly Used Curvilinear Coordinates}
\label{app:CurvilinearEuler}

\subsection{Cylindrical Coordinates}

\begin{equation}
  \pderiv{\rho}{t}
  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{R}\Big)
  +\pderiv{}{z}\Big(\rho\,v_{z}\Big)
  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\Big)=0,
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{R}\big)}{t}
  +\f{1}{R}\pderiv{}{R}\Big(R\,\big(\rho\,v_{R}\,v_{R}+p\big)\Big)
  +\pderiv{}{z}\Big(\rho\,v_{R}\,v_{z}\Big)
  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{R}\,v_{\phi}\Big)
  =\f{\big(\rho\,v_{\phi}^{2}+p\big)}{R},
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{z}\big)}{t}
  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{z}\,v_{R}\Big)
  +\pderiv{}{z}\Big(\big(\rho\,v_{z}\,v_{z}+p\big)\Big)
  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{z}\,v_{\phi}\Big)=0,
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{\phi}\big)}{t}
  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{\phi}\,v_{R}\Big)
  +\pderiv{}{z}\Big(\rho\,v_{\phi}\,v_{z}\Big)
  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\,v_{\phi}+p\Big)
  =-\f{\rho\,v_{\phi}\,v_{R}}{R},
\end{equation}
\begin{equation}
  \pderiv{E}{t}+\f{1}{R}\pderiv{}{R}\Big(\,R\,\big(E+p\big)\,v_{R}\,\Big)+\pderiv{}{z}\Big(\,\big(E+p\big)\,v_{z}\,\Big)+\f{1}{R}\pderiv{}{\phi}\Big(\,\big(E+p\big)\,v_{\phi}\,\Big)=0.
\end{equation}
\begin{equation}
  \pderiv{n_{e}}{t}
  +\f{1}{R}\pderiv{}{R}\Big(R\,n_{e}\,v_{R}\Big)
  +\pderiv{}{z}\Big(n_{e}\,v_{z}\Big)
  +\f{1}{R}\pderiv{}{\phi}\Big(n_{e}\,v_{\phi}\Big)=0,
\end{equation}

\subsection{Spherical Coordinates}

\begin{equation}
  \pderiv{\rho}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v_{r}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{\theta}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\Big)=0,
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{r}\big)}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\big(\rho\,v_{r}\,v_{r}+p\big)\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{r}\,v_{\theta}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{r}\,v_{\phi}\Big)
  =\rho\,\f{\big(v_{\theta}^{2}+v_{\phi}^{2}\big)}{r}+\f{2\,p}{r},
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{\theta}\big)}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v_{\theta}\,v_{r}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\big(\rho\,v_{\theta}\,v_{\theta}+p\big)\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\theta}\,v_{\phi}\Big)
  =\cot\theta\,\f{\big(\rho\,v_{\phi}^{2}+p\big)}{r}-\rho\,\f{v_{r}\,v_{\theta}}{r},
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{\phi}\big)}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(\,r^{2}\,\rho\,v_{\phi}\,v_{r}\,\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{\phi}\,v_{\theta}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\,v_{\phi}+p\Big)
  =-\rho\,v_{\phi}\,\f{\big(v_{r}+v_{\theta}\,\cot\theta\big)}{r},
\end{equation}
\begin{equation}
  \pderiv{E}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\big(E+p\big)\,v_{r}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\big(E+p\big)\,v_{\theta}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\big(E+p\big)\,v_{\phi}\Big)=0.
\end{equation}

\begin{equation}
  \pderiv{n_{e}}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,n_{e}\,v_{r}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,n_{e}\,v_{\theta}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(n_{e}\,v_{\phi}\Big)=0,
\end{equation}

\section{Characteristic Decomposition}
\label{app:Characteristic}

Here we list eigenvalues and eigenvectors of the extended Euler equations in Eq.~\eqref{eq:extendedEulerCompact}.  
Let $\bU=(\rho,u,v,w,E,n)^{T}$ and 
\begin{align}
  \bF^{1}(\bU)
  &=\big(\,u,\,u^{2}/\rho+p,\,u\,v/\rho,\,u\,w/\rho,\,(E+p)\,u/\rho,\,n\,u/\rho\,\big)^{T}, \\
  \bF^{2}(\bU)
  &=, \\
  \bF^{3}(\bU)
  &=.
\end{align}
The flux Jacobian matrices are given by
\begin{align}
  \pderiv{\bF^{1}(\bU)}{\bU}
  =
  \left(
  \begin{array}{cccccc}
  0 & 1 & 0 & 0 & 0 & 0 \\
  -(u/\rho)^{2}+c_{s}^{2} & 2\,u/\rho & 0 & 0 & p_{E} & p_{n} \\
  - u\,v/\rho^{2} & v/\rho & u/\rho & 0 & 0 & 0 \\
  - u\,w/\rho^{2} & w/\rho & 0 & u/\rho & 0 & 0 \\
  (c_{s}^{2}-h)\,u/\rho & h & 0 & 0 & (1+p_{E})\,u/\rho & p_{n}\,u/\rho \\
  -n\,u/\rho^{2} & n/\rho & 0 & 0 & 0 & u/\rho
  \end{array}
  \right),
\end{align}
where we have defined $c_{s}^{2}=\Gamma\,p/\rho$, $\Gamma=(\partial\ln p/\partial\ln \rho)$, $h=(E+p)/\rho$, $p_{E}=(\partial p/\partial E)$, and $p_{n}=(\partial p/\partial n)$

\end{document}

### 2016-08-03 Documents/Euler/dgEulerCurvilinear.tex
Starting to add gravitational sources to equations

@@
 \usepackage{natbib}
-\bibliographystyle{apj}
 \usepackage{../definitions}
@@
 
-$\vect{r}(\vect{x})\in\mathbb{R}^{3}$, so that the displacement vector is $d\vect{r}=dx^{i}\,\vect{e}_{i}$, where the coordinate basis vectors are
+We consider evolution in three-dimensional position space and denote the position vector with for a point with coordinates $\bx=\{x^{1},x^{2},x^{3}\}$ with $\vect{r}(\vect{x})\in\mathbb{R}^{3}$, so that the displacement vector is $d\vect{r}=dx^{i}\,\vect{e}_{i}$ and the coordinate basis vectors are
 \begin{equation}
-  \vect{e}_{i}=\pderiv{\vect{r}}{x^{i}}
+  \vect{e}_{i}=\pderiv{\vect{r}}{x^{i}}.  
 \end{equation}
-$ds_{\vect{x}}^{2}=d\vect{r}\cdot d\vect{r}$
+The squared infinitesimal line-element is
 \begin{equation}
-  ds_{\vect{x}}^{2}=\gamma_{ij}\,dx^{i}\,dx^{j},
+  ds_{\vect{x}}^{2}=d\vect{r}\cdot d\vect{r}=\gamma_{ij}\,dx^{i}\,dx^{j},
 \end{equation}
@@
 
-For general curvilinear spatial coordinates, the Euler equations for gas dynamics are \citep{landauLifshitz_1959}
+For general curvilinear spatial coordinates, the Euler equations for gas dynamics are \citep{leveque_2002}
 \begin{equation}
@@
   \pderiv{M_{j}}{t}
-  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,P^{i}_{~j}\,\Big)=\f{1}{2}\,P^{ik}\,\pderiv{\gamma_{ik}}{x^{j}},
+  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,P^{i}_{~j}\,\Big)
+  =\f{1}{2}\,P^{ik}\,\pderiv{\gamma_{ik}}{x^{j}}-\rho\,\pderiv{\Phi}{x^{j}},
 \end{equation}
@@
   \pderiv{E}{t}
-  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\big(E+p\big)\,v^{i}\,\Big)=0,
+  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\big(E+p\big)\,v^{i}\,\Big)
+  =-M^{i}\,\pderiv{\Phi}{x^{i}},
 \end{equation}
@@
   +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\bar{P}^{3i}\,\Big)
-  =\bar{S}^{i},
+  =\bar{S}^{i}+\bar{G}^{i},
 \end{equation}
@@
   \bar{S}^{3}
-  =-\bar{P}^{13}\f{1}{b}\pderiv{b}{x^{1}}-\bar{P}^{23}\f{1}{ac}\pderiv{c}{x^{2}}.  
+  =-\bar{P}^{13}\f{1}{b}\pderiv{b}{x^{1}}-\bar{P}^{23}\f{1}{ac}\pderiv{c}{x^{2}},
 \end{equation}
 \normalsize
-Energy equation
+and the gravitational sources are
+\begin{equation}
+  \bar{G}^{1}
+  =-\rho\,\pderiv{\Phi}{x^{1}}, \quad
+  \bar{G}^{2}
+  =-\rho\,\f{1}{a}\pderiv{\Phi}{x^{2}}, \quad
+  \bar{G}^{3}
+  =-\rho\,\f{1}{bc}\pderiv{\Phi}{x^{3}}.
+\end{equation}
+The energy equation is given by
 \begin{equation}
@@
   +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,\big(E+p\big)\,\bar{v}^{2}\,\Big)
-  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\big(E+p\big)\,\bar{v}^{3}\,\Big)=0.  
+  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\big(E+p\big)\,\bar{v}^{3}\,\Big)=Q,  
 \end{equation}
-The electron conservation equation
+where the gravitational energy source is
+\begin{equation}
+  Q=-\Big(\,\bar{M}^{1}\pderiv{\Phi}{x^{1}}+\bar{M}^{2}\f{1}{a}\pderiv{\Phi}{x^{2}}+\bar{M}^{3}\f{1}{bc}\pderiv{\Phi}{x^{3}}\,\Big).
+\end{equation}
+Finally, the electron conservation equation
 \begin{equation}
@@
 \end{equation}
-By defining $\bU=\big(\,\rho,\,\rho\,\bar{v}^{1},\,\rho\,\bar{v}^{2},\,\rho\,\bar{v}^{3},\,E,\,n_{e}\,\big)^{T}$, $\vect{S}(\bU)=\big(\,0,\,\bar{S}^{1},\,\bar{S}^{2},\,\bar{S}^{3}\,,0,\,0\,\big)^{T}$, and
+By defining the vector of evolved variables $\bU=\big(\,\rho,\,\rho\,\bar{v}^{1},\,\rho\,\bar{v}^{2},\,\rho\,\bar{v}^{3},\,E,\,n_{e}\,\big)^{T}$, the vector of geometry sources $\vect{S}(\bU)=\big(\,0,\,\bar{S}^{1},\,\bar{S}^{2},\,\bar{S}^{3}\,,0,\,0\,\big)^{T}$, the vector of gravitational sources $\bG(\bU,\Phi)=\big(\,0,\bar{G}^{1},\bar{G}^{2},\bar{G}^{3},Q,0\,\big)^{T}$, and the vectors of flux vector components
 \begin{equation}
@@
   +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\vect{F}^{3}(\bU)\,\Big)
-  =\vect{S}(\bU).
+  =\vect{S}(\bU)+\bG(\bU,\Phi).
   \label{eq:extendedEulerCompact}
@@
 
-\bibliography{./references/references.bib}
+\bibliographystyle{apj}
+\bibliography{../References/references.bib}
 

### 2016-08-25 Documents/Euler/dgEulerCurvilinear.tex
Reworked flux jacobian for nuclear equation of state.

@@
 Here we list eigenvalues and eigenvectors of the extended Euler equations in Eq.~\eqref{eq:extendedEulerCompact}.  
-Let $\bU=(\rho,u,v,w,E,n)^{T}$ and 
+Let the vector of conserved variables be $\bU=(\rho,m_{1},m_{2},m_{3},E,n)^{T}$ and the flux vectors
 \begin{align}
   \bF^{1}(\bU)
-  &=\big(\,u,\,u^{2}/\rho+p,\,u\,v/\rho,\,u\,w/\rho,\,(E+p)\,u/\rho,\,n\,u/\rho\,\big)^{T}, \\
+  &=\big(\,m_{1},\,m_{1}^{2}/\rho+p,\,m_{1}m_{2}/\rho,\,m_{1}\,m_{3}/\rho,\,(E+p)\,m_{1}/\rho,\,n\,m_{1}/\rho\,\big)^{T}, \\
   \bF^{2}(\bU)
@@
 \end{align}
+The vector of primitive variables is $\bP=(\rho,v_{1},v_{2},v_{3},e,n)^{T}$.  
+We have $v_{i}=m_{i}/\rho$ ($i=1,2,3$) and $e=E-\f{m^{2}}{2\,\rho}$, where $m^{2}=m_{1}^{2}+m_{2}^{2}+m_{3}^{2}$.  
+The pressure is a function of the primitive variables $\rho$, $e$, and $n$; $p=p(\rho,e,n)$
+
 The flux Jacobian matrices are given by
@@
   0 & 1 & 0 & 0 & 0 & 0 \\
-  -(u/\rho)^{2}+c_{s}^{2} & 2\,u/\rho & 0 & 0 & p_{E} & p_{n} \\
-  - u\,v/\rho^{2} & v/\rho & u/\rho & 0 & 0 & 0 \\
-  - u\,w/\rho^{2} & w/\rho & 0 & u/\rho & 0 & 0 \\
-  (c_{s}^{2}-h)\,u/\rho & h & 0 & 0 & (1+p_{E})\,u/\rho & p_{n}\,u/\rho \\
-  -n\,u/\rho^{2} & n/\rho & 0 & 0 & 0 & u/\rho
+  \big(\,p_{\rho}+\f{1}{2}p_{e}v^{2}\,\big)-v_{1}^{2} & \big(\,2-p_{e}\,\big)\,v_{1} & -p_{e}\,v_{2} & -p_{e}\,v_{3} & p_{e} & p_{n} \\
+  - v_{1}v_{2} & v_{2} & v_{3} & 0 & 0 & 0 \\
+  - v_{1}v_{3} & v_{3} & 0 & v_{1} & 0 & 0 \\
+  \big[\big(p_{\rho}+\f{1}{2}p_{e}v^{2}\big)-H\big]\,v_{1} & H-p_{e}v_{1}^{2} & -p_{e}v_{1}v_{2} & -p_{e}v_{1}v_{3} & (1+p_{e})\,v_{1} & p_{n}\,v_{1} \\
+  -n\,v_{1}/\rho & n/\rho & 0 & 0 & 0 & v_{1}
   \end{array}
@@
 \end{align}
-where we have defined $c_{s}^{2}=\Gamma\,p/\rho$, $\Gamma=(\partial\ln p/\partial\ln \rho)$, $h=(E+p)/\rho$, $p_{E}=(\partial p/\partial E)$, and $p_{n}=(\partial p/\partial n)$
+where $v^{2}=v_{1}^{2}+v_{2}^{2}+v_{3}^{2}$, $H=(E+p)/\rho$, $p_{\rho}=(\partial p/\partial \rho)$, $p_{e}=(\partial p/\partial e)$, and $p_{n}=(\partial p/\partial n)$.
 

### 2016-09-01 Applications/TransportProblems/ReadRadiationFields1D.m
Adding transport application

@@ -1,0 +1,49 @@
+function...
+  [ Time, E, X, uCR_N, uCR_G1, uPR_D, uPR_I1 ]...
+    = ReadRadiationFields1D( AppName, FileNumber, Directory )
+
+  if( exist( 'Directory', 'var' ) )
+    DirName = Directory;
+  else
+    DirName = './Output';
+  end
+
+  FileName = [ DirName '/' AppName '_RadiationFields_'...
+                 sprintf( '%06d', FileNumber ) '.dat' ];
+
+  RF = load( FileName )';
+
+  Time = RF(1);
+  nE   = RF(2);
+  E    = RF(3:nE+2);
+  nX   = RF(nE+3:nE+3);
+  X    = RF(nE+4:nE+4+nX-1);
+  
+  iO = nE + nX + 3;
+  
+  uCR_N  = zeros( nE, nX );
+  uCR_G1 = zeros( nE, nX );
+  uCR_G2 = zeros( nE, nX );
+  uCR_G3 = zeros( nE, nX );
+  uPR_D  = zeros( nE, nX );
+  uPR_I1 = zeros( nE, nX );
+  uPR_I2 = zeros( nE, nX );
+  uPR_I3 = zeros( nE, nX );
+  
+  for i = 1 : nX
+      
+    uCR_N (:,i) = RF(iO+0*nE*nX+(i-1)*nE+1:iO+0*nE*nX+i*nE);
+    uCR_G1(:,i) = RF(iO+1*nE*nX+(i-1)*nE+1:iO+1*nE*nX+i*nE);
+    uCR_G2(:,i) = RF(iO+2*nE*nX+(i-1)*nE+1:iO+2*nE*nX+i*nE);
+    uCR_G3(:,i) = RF(iO+3*nE*nX+(i-1)*nE+1:iO+3*nE*nX+i*nE);
+    uPR_D (:,i) = RF(iO+4*nE*nX+(i-1)*nE+1:iO+4*nE*nX+i*nE);
+    uPR_I1(:,i) = RF(iO+5*nE*nX+(i-1)*nE+1:iO+5*nE*nX+i*nE);
+    uPR_I2(:,i) = RF(iO+6*nE*nX+(i-1)*nE+1:iO+6*nE*nX+i*nE);
+    uPR_I3(:,i) = RF(iO+7*nE*nX+(i-1)*nE+1:iO+7*nE*nX+i*nE);
+
+  end
+  
+%  keyboard
+
+end
+

### 2016-09-01 Applications/TransportProblems/TransportProblemsInitializationModule.f90

@@ -1,0 +1,272 @@
+MODULE TransportProblemsInitializationModule
+
+  USE KindModule, ONLY: &
+    DP, Pi
+  USE UnitsModule, ONLY: &
+    Centimeter, &
+    Gram, &
+    Kelvin, &
+    Kilometer, &
+    BoltzmannConstant
+  USE ProgramHeaderModule, ONLY: &
+    ProgramName, &
+    nX, nNodesX, &
+    nE, nNodesE
+  USE UtilitiesModule, ONLY: &
+    Locate, &
+    NodeNumberX, &
+    NodeNumber, &
+    Interpolate1D_Linear
+  USE MeshModule, ONLY: &
+    MeshX, &
+    MeshE, &
+    NodeCoordinate
+  USE FluidFieldsModule, ONLY: &
+    uPF, iPF_D, iPF_E, iPF_Ne, &
+    uAF, iAF_T, iAF_E, iAF_Ye, iAF_Me, iAF_Mp, iAF_Mn
+  USE RadiationFieldsModule, ONLY: &
+    uPR, nPR, iPR_D, iPR_I1, iPR_I2, iPR_I3, &
+    uCR, nCR, iCR_N, iCR_G1, iCR_G2, iCR_G3
+  USE EquationOfStateModule, ONLY: &
+    ApplyEquationOfState, &
+    ComputeThermodynamicStates_Primitive
+  USE MomentEquationsUtilitiesModule, ONLY: &
+    Conserved
+
+  IMPLICIT NONE
+  PRIVATE
+
+  TYPE ProfileType
+    INTEGER                             :: nPoints
+    REAL(DP), DIMENSION(:), ALLOCATABLE :: Radius
+    REAL(DP), DIMENSION(:), ALLOCATABLE :: MassDensity
+    REAL(DP), DIMENSION(:), ALLOCATABLE :: Temperature
+    REAL(DP), DIMENSION(:), ALLOCATABLE :: ElectronFraction
+  END TYPE ProfileType
+
+  PUBLIC :: InitializeCoolingProblem1D
+
+CONTAINS
+
+
+  SUBROUTINE InitializeCoolingProblem1D( ProfileName )
+
+    CHARACTER(LEN=*), INTENT(in) :: ProfileName
+
+    INTEGER           :: iX1, iX2, iX3, iR, iE
+    INTEGER           :: iNodeX1, iNodeX2, iNodeX3, iNodeE
[…]

### 2016-10-24 Documents/Euler/Benchmarks1D/draft.tex
adding benchmark document

\documentclass[letterpaper,12pt]{article}
\usepackage{graphicx}
%\extrafloats{100}%
\graphicspath{ {figures/} }
\author{Juliana Pulsinelli}
\title{Benchmarking of the Non-Relativistic Hydrodynamics Alogorithms in thornado}
\begin{document}
\maketitle
\begin{abstract}

The thornado project is astrophysical code based on the Euler equations for fluid dynamics. In this project, the algorithms were benchmarked for accuracy. A group of one-dimensional Riemann problems with known exact solutions were run, and the thornado results were graphed and compared to the exact solutions.

\end{abstract}
\section{Introduction}
Astrophysical fluid dynamics models the movement of fluids in space. It yields very different solutions from terrestrial fluid dynamics, as the effect of gravity is reduced or removed. 
Fluid dynamics play a major role in the formation of stars and neutron stars, as well as the movement of galaxies and numerous other astrophysical topics.

In this project, algorithms solving the Euler equations for fluid dynamics were tested using a variety of tests. The Euler equations for fluid dynamics are \cite{ZhangShu2010}:

\begin{equation}
	\frac{\partial \rho}{\partial t}  
	+ \frac{\partial}{\partial x} \Big(\rho u\Big) = 0
\end{equation}

\begin{equation}
	\frac{\partial}{\partial t} \Big(\rho u\Big)
	+ \frac{\partial}{\partial x} \Big(\rho u^2 + p\Big) = 0
\end{equation}

\begin{equation}
	\frac{\partial E}{\partial t}
	+ \frac{\partial}{\partial x} \Big((E + p) u\Big) = 0
\end{equation}

\begin{equation}
	p = (\gamma - 1)
	\Big(E - \frac{1}{2} \rho u^2 \Big)
\end{equation}

where $\rho$ represents mass density, u represents fluid velocity, p represents pressure of the fluid, and E represents energy. 
Equation 1 represents conservation of mass, equation 2 represents conservation of momentum, and equation 3 represents conservation of energy. Equation 4 is the equation of state, which links the other three equations.

The code was tested using Riemann problems. The Riemann problem models a fluid in an area of one-dimensional space. The initial data features one jump discontinuity, and is constant on either side of this discontinuity. The computational domain is divided into space and time cells. The conditions of each cell are advanced forward for all space cells, one time step at a time, according to the Euler equations for fluid dynamics. \cite{Leveque2002}

%models an area with two fluids, each of which has different characteristics, which are separated from one another by a barrier. When the barrier is removed, the Riemann problem solver code models how the fluids mix, determining how different properties of the fluid change at various spatial locations over time. The fields are evolved forward over time based on the Euler equations.

\section{Numerical Experiments}
Several tests were used to assess the accuracy of the integration method \cite{LiskaWendroff2003}. 
\begin{table}
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & T \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^-6$ & 1 & -1 & $10^-6$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & ? \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & ? \\
 \hline
\end{tabular}
  \caption{table of tests}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. The computational domain is 0.0 to 1.0 in tests 1--8, 0.1 to 0.6 in test 9 \cite{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \cite{Leveque2002}.

Test 12 is an interacting blast waves test, computed on 0.0 to 1.0, with discontinuities at 0.1 and 0.9. At all positions, initial density is 1 and initial velocity is 0. Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right \cite{LiskaWendroff2003}.

\subsection{Test 1: Sod's Shock Tube}

First, the tests were run with values computed at different intervals; the method of integration is the same in each test. Between the two endpoints, 128, 256, 512, and 1024 points were computed for on each respective test. Figures~\ref{fig:dencellcomp_20}--\ref{fig:velcellcomp_20} show results of these tests:
\begin{figure}
  \begin{center}
    \includegraphics[width=.95\textwidth]{dencellcomp_20}
  \end{center}
  \caption{density}
  \label{fig:dencellcomp_20}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prscellcomp_20} &
	  \includegraphics[width=.425\textwidth]{velcellcomp_20}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}
%\newpage

%\clearpage
%\begin{figure}
 % \begin{center}

 % \end{center}
 % \caption{velocity}
 % \label{fig:velcellcomp_20}
%\end{figure}
%\clearpage
Next, several tests were run of different integration methods; the number of points was held constant at 128 each time. Higher numbers in the key correspond to higher-order, more exact methods of integration.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.78\textwidth]{den128comp_20}
  \end{center}
  \caption{density}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs128comp_20} &
	  \includegraphics[width=.425\textwidth]{vel128comp_20}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

These graphs show that the combination of both the lowest order integration method and 128 points yields significant error; however, improving either the method of integration or the number of points gives a solution much closer to the exact solution.

\clearpage

\subsection{Test 2}
For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
The graphs for the second test show a result common throughout many of the different tests: The first order integration method is considerably far from the exact solution; the second and third order integration methods yield nearly identical results which are near, but not exactly equal to, the exact solution. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T2.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T2.png} &
	  \includegraphics[width=.425\textwidth]{vel_T2.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

\clearpage

\subsection{Test 3}
Test 3 shows results similar to Test 2. The deviation of experimental results from exact is especially noticeable in velocity. Near the initial point of discontinuity, the exact results appear completely horizontal. Method 1 almost completely ignores this horizontal part, while Methods 2 and 3 smooth it out considerably. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T3.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T3.png} &
	  \includegraphics[width=.425\textwidth]{vel_T3.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

\clearpage

\subsection{Test 4}

This test obviously displays some difference from the exact solution in density. A depression appears in the center of the graph which is not part of the exact solution. This depression is most severe when method 1 is used, but it also appears with methods 2 and 3.

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T4.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T4.png} &
	  \includegraphics[width=.425\textwidth]{vel_T4.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

\clearpage

\subsection{Test 5}
This test has interesting features in velocity. The first integration method underestimates the velocity at positions between about 0.2 and 0.5. The second and third order methods find a bump in density at around 0.4, which is not present in the exact solution.

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T5.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T5.png} &
	  \includegraphics[width=.425\textwidth]{vel_T5.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}
\clearpage

\subsection{Test 6}
For this test's pressures and velocity, all three integration methods give values very close to exact. However, method 1 proves to be quite bad--worse than usual--at computing the density for this test.

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T6.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T6.png} &
	  \includegraphics[width=.425\textwidth]{vel_T6.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

\clearpage

\subsection{Test 7}
This test features an unusual situation--method 1 calculates the velocity exactly, while method 2 introduces more error and method 3 introduces the most. However, this graph only appears extreme because the intervals on its axis are so small. The numbers are always very close to zero, but very slight errors occur in some of the computations.

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T7.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T7.png} &
	  \includegraphics[width=.425\textwidth]{vel_T7.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

\clearpage

\subsection{Test 8}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T8.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T8.png} &
	  \includegraphics[width=.425\textwidth]{vel_T8.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

\clearpage

\subsection{Test 9}
When finding density, method 1 falls considerably short of the maximum. On the pressure graph, method 3 features both a jump above and a dip below the graph between positions 0.1 and 0.2. Velocity shows a similar (but considerably larger) dip, followed by jump, in the vertical section of the graph between 0.1 and 0.2. Method 1 also overestimates the maximum velocity and is above both exact and method 3 in the middle horizontal section.

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T9.png} &
	  \includegraphics[width=.4\textwidth]{denT9zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T9.png} &	
      \includegraphics[width=.4\textwidth]{vel_T9.png}\\
	\end{tabular}	
  \end{center}
  \caption{}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T9.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T9.png}	
  \end{center}
  \caption{pressure}
\end{figure}

\begin{figure}
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T9.png}	
  \end{center}
  \caption{velocity}
\end{figure}
\clearpage

\subsection{Test 10}

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T10.png} &
	  \includegraphics[width=.4\textwidth]{den10zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T10.png} &	
	  \includegraphics[width=.4\textwidth]{prs10zoom.png} \\
      \includegraphics[width=.4\textwidth]{vel_T10.png} &	
      \includegraphics[width=.4\textwidth]{vel10zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{}
\end{figure}

\clearpage

\subsection{Test 11}

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T11.png} &
	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T11.png} &	
	  \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
      \includegraphics[width=.4\textwidth]{vel_T11.png} &	
      \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{}
\end{figure}

\clearpage

\subsection{Test 12: Interacting Blast Waves}
This test was run for all three integration methods with both 400 cells and 2000 cells. Since it has no exact solution, the 2000 cell, third order test is compared to all three 400 cell tests and labeled as ``exact.''

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T12_400.png}	
  \end{center}
  \caption{density (400 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T12_2000.png}	
  \end{center}
  \caption{density (2000 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T12_400.png}	
  \end{center}
  \caption{pressure (400 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T12_2000.png}	
  \end{center}
  \caption{pressure (2000 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T12_400.png}	
  \end{center}
  \caption{velocity (400 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T12_2000.png}	
  \end{center}
  \caption{velocity (2000 cells)}
\end{figure}

\bibliographystyle{siam}
\bibliography{references.bib}

\end{document}

### 2016-12-03 Documents/M1/dgM1Curvilinear.tex
Working document describing the transport

\documentclass[10pt,preprint]{aastex}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{yhmath}
\usepackage{natbib}
\usepackage{../definitions}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

\newcommand{\ee}[1]{{\color{red} #1}}
\newcommand{\dx}{\Delta x}
\newcommand{\pbK}{\partial\mathbf{K}}
\newcommand{\UDG}{\bU_{\mbox{\tiny DG}}}
\newcommand{\sumx}{\sum_{i=1}^{d}}

\begin{document}

\title{Nodal Discontinuous Galerkin Method for the Two-Moment Model of Neutrino Transport}
\author{Eirik Endeve\altaffilmark{1}, et al.}
\altaffiltext{1}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}

\begin{abstract}
We present a nodal Discontinuous Galerkin (DG) method for solving the non-relativistic two-moment model for neutrino transport.  
The method --- ultimately targeted for simulations of core-collapse supernovae --- includes the use of curvilinear coordinates and non-ideal microphysics (nuclear equation of state and weak interactions) for neutrino-matter interactions.  
\end{abstract}

\tableofcontents

\section{Introduction}

We will use inits in which the speed of light is unity ($c=1$).

\section{Two-Moment Model for Neutrino Transport}

\subsection{Basic Mathematical Model}

For general curvilinear spatial coordinates $\{x^{i}\}$, the two-moment model for radiation transport takes the form \citep[see, e.g.,][for fully general relativistic treatments]{shibata_etal_2011,cardall_etal_2013a}
\begin{equation}
  \f{1}{\sqrt{\gamma}}\pderiv{}{t}\Big(\,\sqrt{\gamma}\,\cJ\,\Big)
  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\cH^{i}\,\Big)=\chi\,\big(\cJ_{0}-\cJ\big),
  \label{eq:momentEquationEnergy}
\end{equation}
\begin{equation}
  \f{1}{\sqrt{\gamma}}\pderiv{}{t}\Big(\,\sqrt{\gamma}\,\cH_{j}\,\Big)
  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\cK^{i}_{~j}\,\Big)
  =\f{1}{2}\,\cK^{ik}\,\pderiv{\gamma_{ik}}{x^{j}}-\kappa\,\cH_{j},
  \label{eq:momentEquationMomentum}
\end{equation}
where $\cJ$, $\cH^{i}$, and $\cK^{ij}$ are defined as angular moments of a positive neutrino distribution function $f(\omegaNu,\epsilonNu,\bx,t)$
\begin{equation}
  \big\{\,\cJ,\,\cH^{i},\,\cK^{ij}\,\big\}(\epsilonNu,\bx,t)
  =\int_{\bbS^{2}}f(\omegaNu,\epsilonNu,\bx,t)\,\big\{1,l^{i},l^{i}\,l^{j}\}\,d\omegaNu.  
  \label{eq:angularMoments}
\end{equation}
Here, $\{l^{i}\}$ are components of a unit three-vector proportional to the neutrino three-momentum $\bp=\epsilonNu\,\bl$.  
(We adopt the Einstein summation convention and let repeated Latin indices run from $1$ to $3$.)
In a kinetic description, neutrinos are described by the phase space distribution function $f$, and the momentum space coordinates used here are the neutrino energy $\epsilonNu$, and the angles $\thetaNu$ and $\phiNu$ (describing the neutrino propagation direction relative to a local orthonormal basis).  
In forming the angular moments in Eq.~\eqref{eq:angularMoments}, the integrals extend over the unit sphere
\begin{equation}
  \bbS^{2}=\big\{\,(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi),\,\phiNu\in[0,2\pi)\,\big\}.  
\end{equation}
The angular moments are related to the neutrino energy density, momentum density, and stress ($\cJ$, $\cH^{i}$, and $\cK^{ij}$, respectively).  
They are functions of the neutrino energy $\epsilonNu$, spatial position $\{x^{i}\}$, and time $t$.

To model neutrino matter interactions, we include emission and absorption, and isotropic, elastic scattering on nucleons and nuclei.  
On the right-hand sides of Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}, $\chi(\epsilonNu,\bU)$ and $\kappa(\epsilonNu,\bU)=\chi(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$ are absorption and total (absorption plus scattering) opacities, respectively.  
The opacities depend on the neutrino energy and the local thermodynamic state of the fluid $\bU=(\rho,T,Y_{e})^{T}$, where $\rho$ is the (baryon) mass density, $T$ the temperature, and $Y_{e}$ the electron fraction.  
We use the opacities given by \citet{bruenn_1985}.  
In Eq.~\eqref{eq:momentEquationEnergy}, the equilibrium density $\cJ_{0}=4\pi\,f_{0}(\epsilonNu,\bU)$ is computed from the angular moment of the isotropic Fermi-Dirac distribution
\begin{equation}
  f_{0}(\epsilonNu,\bU)=\f{1}{e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T}+1},
\end{equation}
where $k_{\mbox{\tiny B}}$ is Boltzmann's constant, and $\mu_{\nu}$ is the neutrino chemical potential.

The model given by Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum} is non-relativistic (i.e., it does not include effects due to strong gravitational fields or interactions with a moving fluid), but is expressed in terms of curvilinear coordinates through the spatial metric tensor $\gamma_{ij}$, which gives squared infinitesimal line-element
\begin{equation}
  ds_{\vect{x}}^{2}=\gamma_{ij}\,dx^{i}\,dx^{j},
\end{equation}
where $\gamma_{ij}$ are the spatial components of the coordinate basis metric tensor.  
We will make two simplifying assumptions: the metric tensor is (1) diagonal and (2) time-independent.  
Specifically we assume the following diagonal form
\begin{equation}
  \gamma_{ij}
  =\mbox{diag}\big[\,\gamma_{11},\,\gamma_{22}(x^{1}),\,\gamma_{33}(x^{1},x^{2})\,\big]
  =\mbox{diag}\big[\,1,\,a(x^{1})^{2},\,b(x^{1})^{2}c(x^{2})^{2}\,\big], 
  \label{eq:threeMetric}
\end{equation}
which is sufficiently general to accommodate Cartesian, cylindrical, and spherical polar coordinates (see Table~\ref{tab:metricFunctions} and Appendix~\ref{app:CurvilinearEuler}).  
Moreover, $\gamma$ is the determinant of the metric tensor, and $\sqrt{\gamma}=abc$.  
The inverse of the spatial metric is denoted $\gamma^{ij}$, so that $\gamma^{ik}\gamma_{kj}=\delta^{i}_{~j}$.  
We can use the spatial metric to raise and lower indices on spatial vectors and tensors; e.g., $\cH_{j}=\gamma_{jk}\,\cH^{k}$.

The two-moment system contains the higher order moments $\cK^{ij}$ --- the symmetric stress tensor.  
In order to form a closed system of equations, the components of the stress tensor must be related to the lower order moments through a closure procedure.  
Following \citet{levermore_1984}, we write
\begin{equation}
  \cK^{ij}
  =\f{1}{2}\,\Big[\,(1-\psi)\,\gamma^{ij}+(3\,\psi-1)\,h^{i}\,h^{j}\,\Big]\,\cJ,
\end{equation}
where $\psi$ is the Eddington factor, $h^{i}=\cH^{i}/\cH$, and $\cH=\sqrt{\cH_{i}\cH^{i}}$.  
We also define the flux factor $h=\cH/\cJ$, and use the analytic expression for the Eddington factor \citep{minerbo_1978} given by 
\begin{equation}
  \psi(h)=\f{1}{3}+\f{2}{3}\,\Big(\,h^{2}\,\big(\,3-h+3h^{2}\,\big)/5\,\Big),
\end{equation}
which approximates the low occupancy limit of the maximum entropy closure for Fermi-Dirac particles given by \citet{cernohorskyBludman_1994}.  
Specifically, we have $\psi(0)=1/3$ (diffusion limit) and $\psi(1)=1$ (streaming limit).

\subsection{Two-Moment Model as a System of Conservation Laws with Sources}

\begin{table}
  \begin{center}
  \caption{Metric functions for Cartesian, Cylindrical, and Spherical coordinate systems.\label{tab:metricFunctions}}
  \begin{tabular}{ccccccccccc}
    \midrule
    Coordinates & $x^{1}$ & $x^{2}$ & $x^{3}$ & $a$ & $b$ & $c$ & $\sqrt{\gamma}$
    & $\pderiv{a}{x^{1}}$ & $\pderiv{b}{x^{1}}$ & $\pderiv{c}{x^{2}}$ \\
    \midrule
    \midrule
    Cartesian & $x$ & $y$ & $z$ & 1 & 1 & 1 & 1 & 0 & 0 & 0 \\
    Cylindrical & $R$ & $z$ & $\phi$ & 1 & $R$ & 1 & $R$ & 0 & 1 & 0 \\
    Spherical & $r$ & $\theta$ & $\phi$ & $r$ & $r$ & $\sin\theta$ & $r^{2}\sin\theta$ & 1 & 1 & $\cos\theta$ \\
    \midrule
    \midrule
  \end{tabular}
  \end{center}
\end{table}

We define the geometry sources in Eq.~\eqref{eq:momentEquationMomentum} by
\begin{equation}
  \cG_{j}
  =\f{1}{2}\,\cK^{ik}\,\pderiv{\gamma_{ik}}{x^{j}}.  
\end{equation}
Specifically, using the time-independent metric tensor in Eq.~\eqref{eq:threeMetric}, the components are
\begin{equation}
  \cG_{1}
  =\f{1}{2}\,\Big(\,\cK^{22}\,\pderiv{\gamma_{22}}{x^{1}}+\cK^{33}\,\pderiv{\gamma_{33}}{x^{1}}\,\Big), \quad
  \cG_{2}
  =\f{1}{2}\,\cK^{33}\,\pderiv{\gamma_{33}}{x^{2}}, \quad\text{and}\quad
  \cG_{3}
  =0.
\end{equation}
Then, by defining the vector of evolved moments $\bcM=\big(\,\cJ,\,\cH_{1},\,\cH_{2},\,\cH_{3}\,\big)^{T}$, the vector of geometry sources $\bcG(\bcM)=\big(\,0,\,\cG_{1},\,\cG_{2},\,\cG_{3}\,\big)^{T}$, the vector of collision sources $\bcC(\bcM)=\big(\,\chi\,(\cJ_{0}-\cJ),\,-\kappa\,\cH_{1},\,-\kappa\,\cH_{2},\,-\kappa\,\cH_{3}\,\big)^{T}$, and the flux vectors $\bcF^{i}(\bcM)=\big(\,\cH^{i},\,\cK_{~1}^{i},\,\cK_{~2}^{i},\,\cK_{~3}^{i}\,\big)^{T}$, we write the system of equations in compact form
\begin{equation}
  \f{1}{\sqrt{\gamma}}\pderiv{}{t}\Big(\,\sqrt{\gamma}\,\bcM\,\Big)
  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\bcF^{i}(\bcM)\,\Big)
  =\bcG(\bcM)+\bcC(\bcM).
  \label{eq:momentEquationsCompact}
\end{equation}
Eq.~\eqref{eq:momentEquationsCompact} forms the basis for developing DG methods for neutrino transport.

\clearpage

\section{Discontinuous Galerkin Discretization}

In the DG method, the moments are approximated by a local expansion of the form
\begin{equation}
  \bcM_{\DG}(\epsilonNu,\bx,t)
  =\sum_{\bi=\vect{1}}^{\bN}\bcM_{\bi}(\epsilonNu,t)\,\ell_{\bi}(\bx), 
\end{equation}
where basis functions $\ell_{\bi}(\bx)$, which we will take to be polynomials, belong to a function space denoted $\bbV^{k}$ and have local support in a computational cell or element denoted by $\bK$.  
Here we do not consider relativistic effects, which would lead to energy advection terms in the moment equations \citep[cf.][]{cardall_etal_2013a}.  
Thus, we treat the neutrino energy simply as a parameter, and do not introduce an expansion in the energy dimension.

Several books and review articles on the DG method are available now available \citep[see, e.g.,][]{cockburnShu_2001,hesthavenWarburton_2008}, and we will not go into too much detail here.  
However, we review some key concepts to introduce notation, and, since multiple `flavors' of the DG method has emerged, we emphasize specific choices in our implementation.

\subsection{Basic Principles of the DG Method}

We divide the computational domain $D$ into a disjoint union $\mathcal{T}$ of open elements $\bK$, so that $D = \cup_{\bK \in \mathcal{T}}\bK$.  
We require that each element is a $d$-dimensional box in the logical coordinates; i.e.,
\begin{equation}
  \bK=\{\,\vect{x} : x^{i} \in K^{i} := (\xL^{i},\xH^{i}),~|~i=1,\ldots,d\,\}, 
\end{equation}
with the surface elements denoted $\tilde{\bK}^{i}=\otimes_{j\ne i}K^{j}$.  
We use $V_{\bK}$ to denote the proper volume of the element
\begin{equation}
  V_{\bK} = \int_{\bK}dV, \quad\text{where}\quad dV = \sqrt{\gamma}\,\prod_{i=1}^{d}dx^{i}.  
\end{equation}
We also define $\bx=\{\tilde{\bx}^{i},x^{i}\}$ and $\dx^{i}=\xH^{i}-\xL^{i}$.

We let the approximation space for the DG method, $\mathbb{V}^{k}$, to be constructed from the tensor product of one-dimensional polynomials of maximal degree $k$.  
Note that functions in $\mathbb{V}^{k}$ can be discontinuous across element interfaces.  
The semi-discrete DG problem is to find $\bcM_{\DG}\in\mathbb{V}^{k}$ (which approximates $\bcM$ in Eq.~\eqref{eq:momentEquationsCompact}) such that \citep[cf.][]{cockburnShu_2001}
\begin{align}
  &\partial_{t}\int_{\bK}\bcM_{\DG}\,v\,dV
  +\sumx\int_{\tilde{\bK}^{i}}
  \big(\,
    \sqrt{\gamma}\,\widehat{\bcF}^{i}(\bcM_{\DG})\,v\big|_{\xH^{i}}
    -\sqrt{\gamma}\,\widehat{\bcF}^{i}(\bcM_{\DG})\,v\big|_{\xL^{i}}\,\big)\,d\tilde{\bx}^{i} \nonumber \\
  &\hspace{24pt}
  -\sumx\int_{\bK}\bcF^{i}(\bcM_{\DG})\,\pderiv{v}{x^{i}}\,dV
  =\int_{\bK}\bcG(\bcM_{\DG})\,v\,dV+\int_{\bK}\bcC(\bcM_{\DG})\,v\,dV,
  \label{eq:semidiscreteDG}
\end{align}
for all $v\in\mathbb{V}^{k}$ and all $\bK\in\mathcal{T}$.

To connect the elements in Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\bcF}^{i}(\bcM_{\DG})$ is a numerical flux approximating the flux on the $i$th surface of $\bK$.  
For this purpose we define the numerical flux function $\vect{f}^{i}$, which evaluates the numerical flux given values from both sides of an element interface; i.e.,
\begin{equation}
  \widehat{\bcF}^{i}(\bcM_{\DG})=\vect{f}^{i}(\bcM_{\DG}(x^{i,-},\tilde{\bx}^{i}),\bcM_{\DG}(x^{i,+},\tilde{\bx}^{i})),
\end{equation}
where superscripts $-/+$, e.g., in the arguments of $\bcM_{\DG}(x^{i,-/+},\tilde{\bx}^{i})$, indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
For example, the simple Lax-Friedrichs flux, which we use in this paper, is given by
\begin{equation}
  \vect{f}^{i}(\bcM^{-},\bcM^{+})
  =\f{1}{2}\,\big(\,\bcF^{i}(\bcM^{-})+\bcF^{i}(\bcM^{+})-\alpha^{i}\,(\,\bcM^{+}-\bcM^{-}\,)\,\big),
\end{equation}
where $\alpha^{i}=||\mbox{eig}\big(\partial\bcF^{i}/\partial\bcM\big)||_{\infty}$ is the largest eigenvalue of the flux jacobian.  
For classical neutrinos, which propagate at the speed of light, we take $\alpha^{i}=1$.

The approximation space $\mathbb{V}^{k}$ contains the constant functions, and the choice $v=1$ in Eq.~\eqref{eq:semidiscreteDG} gives
\begin{equation}
  \partial_{t}\bcM_{\bK}
  +\f{1}{V_{\bK}}\sumx\int_{\tilde{\bK}^{i}}
  \big(\,\sqrt{\gamma}\,\widehat{\bcF}^{i}(\bcM_{\DG})\big|_{\xH^{i}}-\sqrt{\gamma}\,\widehat{\bcF}^{i}(\bcM_{\DG})\big|_{\xL^{i}}\,\big)\,d\tilde{\bx}^{i}
  =\bcG_{\bK}+\bcC_{\bK},
\end{equation}
where we have defined the volume averages
\begin{equation}
  \bcM_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\bcM_{\DG}\,dV, \quad
  \bcG_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\bcG(\bcM_{\DG})\,dV  \quad\text{and}\quad
  \bcC_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\bcC(\bcM_{\DG})\,dV.
\end{equation}
This illustrates how the DG method evolves the cell average (similar to finite volume methods).

\subsection{Further Details on the DG Discretization of the Moment Equations}

Here we provide further details on the DG method in order to arrive at the equations that are actually implemented in our code.  
We start by introducing some notation, defining the polynomial expansion for $\bcM_{\DG}$, and the quadrature rules used to evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}.  
Then, using these rules, we provide explicit expressions for each of the terms in Equation~\eqref{eq:semidiscreteDG}.

\subsubsection{Notation and Definitions}

In each element $\bK$, we use a nodal representation in the conserved variables $\bcM$; i.e.,
\begin{equation}
  \bcM(\epsilonNu,\bx,t)\approx
  \bcM_{\DG}(\epsilonNu,\bx,t)=\sum_{\bi=\vect{1}}^{\bN}\bcM_{\bi}(\epsilonNu,t)\,\ell_{\bi}(\bx),
  \label{eq:conservedNodalExpansion}
\end{equation}
where $\ell_{\bi}(\bx)\in\bbV^{k}$ are basis functions.  
(In the following, to simplify the notation, we will suppress the dependence on $\epsilonNu$ of the moments.)
Specifically, we use one-dimensional Lagrange polynomials $\ell_{i}(x)$ to construct the multidimensional representation, where
\begin{equation}
  \ell_{i}(\eta)=
  \prod_{\substack{j=1\\j\ne i}}^{N}\f{\eta-\eta_{j}}{\eta_{i}-\eta_{j}}.  
\end{equation}
The basis polynomials are defined on the local reference element with coordinates $\eta\in I=[\eta_{\Low},\eta_{\Hgh}]=[-1/2,1/2]$.  
The global coordinates are then given by $x(\eta)=x_{c}+\eta\,\Delta x$, where the center value is given by the arithmetic mean $x_{c}=(x_{\Low}+x_{\Hgh})/2$.  
In \eqref{eq:semidiscreteDG}, we also need to evaluate derivatives of the basis functions.  
For Lagrange polynomials, these are given by
\begin{equation}
  \pderiv{\ell_{i}}{\eta}(\eta)
  =\sum_{\substack{k = 1 \\ k \ne i}}^{N}\f{1}{\eta_{i}-\eta_{k}}
  \prod_{\substack{j=1 \\ j \ne k}}^{N}\f{\eta-\eta_{j}}{\eta_{i}-\eta_{j}}.  
\end{equation}

To simplify expressions, we have introduced compact notation.  
Let $\bi=\{i_{1},\ldots,i_{d}\}$ be a multi-index, and define the multidimensional polynomial as $\ell_{\bi}(\bx)=\prod_{k=1}^{d}\ell_{i_{k}}(x^{k})$.  
From the property $\ell_{i}(x_{j})=\delta_{ij}$ we have the corresponding multidimensional version $\ell_{\bi}(\bx_{\bj})=\delta_{\bi\bj}$, so that $\bcM_{\DG}(\bx_{\bi},t)=\bcM_{\bi}(t)$; i.e., the expansion coefficients in Equation \eqref{eq:conservedNodalExpansion} represent the conserved variables defined in the nodes $\bx_{\bi}$.  
We then have
\begin{equation}
  \sum_{\bi=\vect{1}}^{\bN}\bcM_{\bi}(t)\,\ell_{\bi}(\bx)
  =\sum_{i_{1}=1}^{N}\ldots\sum_{i_{d}=1}^{N}\bcM_{i_{1}\ldots i_{d}}(t)\,\ell_{i_{1}}(x^{1})\ldots\ell_{i_{d}}(x^{d}).  
\end{equation}

To evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}, we introduce numerical quadratures.  
First we define the one-dimensional $N$-point quadrature $Q_{N}^{i}:C^{0}(I^{i})\to\bbR$ with abscissas $\{\eta_{q}\}_{q=1}^{N}$ and weights $\{w_{q}\}_{q=1}^{N}$, normalized such that $\sum_{q=1}^{N}w_{q}=1$.  
(For example, the $N$-point Legendre-Gauss quadrature, which we will use, integrates polynomials of degree $\le 2N-1$ exactly.)
If $P(x)$ is such a polynomial, we have
\begin{equation}
  \f{1}{\Delta x}\int_{K}P(x)\,dx=\int_{I}P(\eta)\,d\eta=Q_{N}\big[P\big]\equiv\sum_{q=1}^{N}w_{q}\,P(\eta_{q}).  
\end{equation}

Multi-dimensional integrals are evaluated by tensorization of one-dimensional quadratures.  
For volume integrals, we define $\bQ_{N}:C^{0}(\bI)\to\bbR$ as the tensor product of one-dimensional $N$-point Legendre-Gauss quadrature rules $\bQ_{N}=\otimes_{i=1}^{d}Q_{N}^{i}$ with abscissas $\{\vect{\eta}_{\bq}\}_{\bq=\vect{1}}^{\bN}$ and weights $\{w_{\bq}\}_{\bq=\vect{1}}^{\bN}$.  
Here, $\bq=\{q_{i}\}_{i=1}^{d}\in\bbN^{d}$, $\vect{\eta}_{\bq}=\{\eta_{q_{1}}^{1},\ldots,\eta_{q_{d}}^{d}\}$, and $w_{\bq}=w_{q_{1}}\ldots w_{q_{d}}$, so that the multi-dimensional volume integral is evaluated as
\begin{equation}
  \f{1}{|\bK|}\int_{\bK}P(\bx)\,d\bx
  =\int_{\bI}P(\vect{\eta})\,d\vect{\eta}
  =\bQ_{N}\big[P\big]
  \equiv\sum_{\bq=\vect{1}}^{\bN}w_{\bq}\,P(\vect{\eta}_{\bq}),
\end{equation}
where $P:\bbR^{d}\to\bbR$.  
Similarly, for surface integrals, we define $\tilde{\bQ}_{N}^{i}:C^{0}(\tilde{\bI}^{i})\to\bbR$ as the tensor product $\tilde{\bQ}_{N}^{i}=\otimes_{j\ne i}Q_{N}^{j}$ and denote the abscissas with $\{\tilde{\vect{\eta}}_{\tilde{\bq}_{i}}^{i}\}_{\tilde{\bq}_{i}=\vect{1}}^{\bN}$ and the weights with $\{w_{\tilde{\bq}_{i}}\}_{\tilde{\bq}_{i}=\vect{1}}^{\bN}$, respectively.  
Here, the multi-index is $\tilde{\bq}_{i}=\{q_{j}\}_{j\ne i}\in\bbN^{d-1}$, $\tilde{\vect{\eta}}_{\tilde{\bq}_{i}}^{i}=\{\eta_{q_{j}}^{j}\}_{j\ne i}$, and $w_{\tilde{\bq}_{i}}=\prod_{j\ne i}w_{q_{j}}$.  
Surface integrals are then evaluated as
\begin{equation}
  \f{1}{|\tilde{\bK}^{i}|}\int_{\tilde{\bK}^{i}}P(x^{i},\tilde{\bx}^{i})\,d\tilde{\bx}^{i}
  =\int_{\tilde{\bI}^{i}}P(x^{i},\tilde{\vect{\eta}}^{i})\,d\tilde{\vect{\eta}}^{i}
  =\tilde{\bQ}_{N}^{i}\big[P\big]
  \equiv\sum_{\tilde{\bq}_{i}=\vect{1}}^{\bN}w_{\tilde{\bq}_{i}}\,P(x^{i},\tilde{\vect{\eta}}_{\tilde{\bq_{i}}}^{i}).  
\end{equation}

We now use these definitions to furnish explicit expressions for the discretized moment equations.

\subsubsection{Explicit Expressions}

Inserting \eqref{eq:conservedNodalExpansion} into \eqref{eq:semidiscreteDG}, with $v(\bx)=\ell_{\bk}(\bx)$ and the quadratures defined above, we obtain
\begin{equation}
  \pd{}{t}\int_{\bK}\bcM_{\DG}\,v\,dV
  \approx w_{\bk}\,\sqrt{\gamma}_{\bk}\,\pd{}{t}\bcM_{\bk}\,|\bK|
\end{equation}
for the time derivative term, where $|\bK|=\prod_{i=1}^{d}\Delta x^{i}$.  
Note that the integration is approximate since we use the Legendre-Gauss quadrature rule with the nodal points given by the expansion in Eq.~\eqref{eq:conservedNodalExpansion}.  
This leads to a diagonal mass matrix, and simplifies the implementation.  
Similarly, we obtain
\begin{equation}
  \int_{\bK}\bcG(\bcM_{\DG})\,v\,dV
  \approx w_{\bk}\,\sqrt{\gamma}_{\bk}\,\bcG(\bcM_{\bk})\,|\bK| \quad\text{and}\quad
  \int_{\bK}\bcC(\bcM_{\DG})\,v\,dV
  \approx w_{\bk}\,\sqrt{\gamma}_{\bk}\,\bcC(\bcM_{\bk})\,|\bK|
\end{equation}
for the source terms.  
For the surface integrals, we obtain, e.g., 
\begin{equation}
  \int_{\tilde{\bK}^{i}}\sqrt{\gamma}\,\widehat{\bcF}^{i}\,v|_{x_{\Hgh}^{i}}\,d\tilde{\bx}^{i}
  \approx w_{\tilde{\bk}_{i}}\,\sqrt{\gamma}(x_{\Hgh}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})\,
  \widehat{\bcF}^{i}(x_{\Hgh}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})\,\ell_{k_{i}}(\eta_{\Hgh})\,|\tilde{\bK}^{i}|,
\end{equation}
where $|\tilde{\bK}^{i}|=\prod_{i\ne j}\Delta x^{j}$.  
(Note that we do not use the Einstein summation convention in the numerical expressions presented in this section.  
Summation over indices will be explicitly indicated.)  
Finally, the `volume terms' become
\begin{equation}
  \int_{\bK}\bcF^{i}\,\pderiv{v}{x^{i}}\,dV
  \approx w_{\tilde{\bk}_{i}}\sum_{q_{i}=1}^{N}w_{q_{i}}\,\sqrt{\gamma}(x_{q_{i}}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,
  \bcF^{i}(x_{q_{i}}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\pderiv{\ell_{k_{i}}}{\eta^{i}}(\eta_{q_{i}}^{i})\,|\tilde{\bK}^{i}|.  
\end{equation}
Combining the terms and dividing through by $w_{\bk}\,\sqrt{\gamma}_{\bk}\,|\bK|$ we obtain the semi-discrete form of the moment equations
\begin{align}
  \pd{\bcM_{\bk}}{t}
  &=
  -\f{1}{\sqrt{\gamma}_{\bk}}\sum_{i=1}^{d} 
  \f{1}{w_{k_{i}}\Delta x^{i}}\,
  \Big(\,
    \sqrt{\gamma}(x_{\Hgh}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})\,\widehat{\bcF}^{i}(x_{\Hgh}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})\,\ell_{k_{i}}(\eta_{\Hgh})
    -\sqrt{\gamma}(x_{\Low}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})\,\widehat{\bcF}^{i}(x_{\Low}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})\,\ell_{k_{i}}(\eta_{\Low})
  \,\Big)
  \nonumber \\
  &\hspace{12pt}
  +\f{1}{\sqrt{\gamma}_{\bk}}\sum_{i=1}^{d}\f{1}{w_{k_{i}}\Delta x^{i}}
  \sum_{q_{i}=1}^{N}w_{q_{i}}\,\sqrt{\gamma}(x_{q_{i}}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,
  \bcF^{i}(x_{q_{i}}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\pderiv{\ell_{k_{i}}}{\eta^{i}}(\eta_{q_{i}}^{i})
  +\bcG(\bcM_{\bk})+\bcC(\bcM_{\bk}).
  \label{eq:semidiscreteDiscretized}
\end{align}
Equation~\eqref{eq:semidiscreteDiscretized} provides the basis for implementation in our code.

By defining the cell average
\begin{equation}
  \bcM_{\bK}=\f{|\bK|}{V_{\bK}}\sum_{\bk=\vect{1}}^{\bN}w_{\bk}\,\sqrt{\gamma}_{\bk}\,\bcM_{\bk},
\end{equation}
we obtain the discrete equation for the cell average by multiplying Eq.~\eqref{eq:semidiscreteDiscretized} with $w_{\bk}\,\sqrt{\gamma}_{\bk}$ and summing over all $\bk$
\begin{equation}
  \pd{\bcM_{\bK}}{t}
  =-\f{1}{V_{\bK}}\sum_{i=1}^{d}\sum_{\tilde{\bk}_{i}=\vect{1}}^{\bN}w_{\tilde{\bk}_{i}}
  \Big(\,
    \sqrt{\gamma}(x_{\Hgh}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})\,\widehat{\bcF}^{i}(x_{\Hgh}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})
    -\sqrt{\gamma}(x_{\Low}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})\,\widehat{\bcF}^{i}(x_{\Low}^{i},\tilde{x}_{\tilde{\bk}_{i}}^{i})
  \,\Big)\,|\tilde{\bK}^{i}|
  +\bcG_{\bK}+\bcC_{\bK},
  \label{eq:semidiscreteDiscretizedCellAverage}
\end{equation}
where we have used $\sum_{i=1}^{N}\ell_{i}(\eta)=1$ and $\sum_{i=1}^{N}\partial\ell_{i}/\partial\eta=0$.  
In the absence of sources, Eq.~\eqref{eq:semidiscreteDiscretizedCellAverage} is conservative.

We have now defined the spatial discretization of the moment equations.

\clearpage

\section{Semi-Implicit Time Integration}

\section{Slope Limiters}

\subsection{TVD and TVB Limiters}

For slope limiting, we introduce the modal expansion
\begin{equation}
  (\sqrt{\gamma}\bcM)_{\DG}=\sum_{\bi=\vect{1}}^{\bN}(\widetilde{\sqrt{\gamma}\bcM})_{\bi}\,\phi_{\bi}(\bx),
\end{equation}
where $\{\phi_{\bi}\}_{\bi=\vect{1}}^{\bN}$ are elements of an orthogonal basis and $(\widetilde{\sqrt{\gamma}\bcM})_{\bi}$ are the corresponding expansion coefficients.  
(Here, we let the orthogonal basis be given by normalized Legendre polynomials; $\{\phi_{k}(\eta)\}_{k=1}^{4}=\{\,1,\,\eta,\,\eta^{2}-1/12,\,\eta\,(\eta^{2}-3/20)\,\}$.)  
By orthogonality of the basis functions, we have
\begin{equation}
  (\widetilde{\sqrt{\gamma}\bcM})_{\bi}
  =\cT_{\bi}^{-1}\int_{\bK}(\sqrt{\gamma}\bcM)_{\DG}\,\phi_{\bi}(\bx)\,d\bx,
\end{equation}
where
\begin{equation}
  \cT_{\bi}=\int_{\bK}\phi_{\bi}(\bx)\,\phi_{\bi}(\bx)\,d\bx,
\end{equation}
and $\{\cT_{i}^{-1}\}_{i=1}^{4}=\{\,1,\,12,\,180,\,2800\,\}$.  
\begin{equation}
  (\widetilde{\sqrt{\gamma}\bcM})_{|\vect{1}|}
  \to\text{minmodB}
  \big(\,
    (\widetilde{\sqrt{\gamma}\bcM})_{|\vect{1}|},\,
    \beta\,((\widetilde{\sqrt{\gamma}\bcM})_{|\vect{0}|}-(\widetilde{\sqrt{\gamma}\bcM})_{|\vect{0}|}^{-}),\,
    \beta\,((\widetilde{\sqrt{\gamma}\bcM})_{|\vect{0}|}^{+}-(\widetilde{\sqrt{\gamma}\bcM})_{|\vect{0}|})
  \,\big),
\end{equation}
where $\beta\in[1,2]$.

\citet{cockburnShu_2001}
\begin{equation}
  \mbox{minmodB}(a,b,c)
  =\left\{\begin{array}{ll}
  a \quad\text{if}\quad |a|\le M\,\Delta x^{2} \\
  \mbox{minmod}(a,b,c) \quad \text{otherwise}
  \end{array}\right.,
\end{equation}
where the minmod function is given by
\begin{equation}
  \mbox{minmod}(a,b,c)
  =\left\{\begin{array}{ll}
  s\,\min[\,|a|,|b|,|c|\,] \quad\text{if}\quad $s=\mbox{sign}(a)=\mbox{sign}(b)=\mbox{sign}(c)$ \\
  0 \quad \text{otherwise}.
  \end{array}\right..
\end{equation}

\subsection{Positivity Limiters}

\section{Benchmark Problems}

We benchmark the DG implementation against a series of test problems.  
We will vary the degree $k$ of the polynomial representation used in DG method from 0 to 3, which we then denote DG($k$).  
First we consider test problems in the streaming limit.  
In this case we use the explicit SSP-RK time integrators.  
The 2-stage and 3-stage methods are denoted SSP-RK2 and SSP-RK3, respectively.  
As an example, an expected third-order accurate method (for problems with smooth solutions), using DG(2) and SSP-RK3, will then be denoted DG(2)+RK3.

\subsection{Streaming Sine Wave}

To measure the accuracy of the implementation using Cartesian coordinates, and to gauge the performance of the DG scheme using different limiter parameters, we advect a sine wave across the one-dimensional, periodic domain $D=\{x:x\in[0,1]\}$ ten times, until $t=10$.  
We let the initial condition be given by
\begin{equation}
  \cJ(x,t=0)=\cH_{x}(x,t=0)=1+\sin\big(2\pi\,x\big).  
\end{equation}
Results are shown in Figure~\ref{fig:streamingSineWave} and Table~\ref{tab:streamingSineWave}.

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.38]{./Figures/StreamingSineWave1D}
  \end{center}
  \caption{Energy density versus position after ten grid crossings ($t=10$) for the streaming sine wave problem computed with the DG(2)+RK3 scheme using 16 elements.  We compare results obtained using various limiter parameters (see text for details) with the analytic solution (dotted line).}
  \label{fig:streamingSineWave}
\end{figure}

\begin{table}
  \begin{center}
  \caption{$L^{\infty}$ error and convergence rates for the streaming sine wave problem.}
  \label{tab:streamingSineWave}
  \begin{tabular}{ccccccccc}
    & \multicolumn{4}{c}{SSP-RK2} & \multicolumn{4}{c}{SSP-RK3} \\
    \cmidrule(r){2-5} \cmidrule(r){6-9}
    $N$ & DG(1) & Rate & DG(2) & Rate & DG(2) & Rate & DG(3) & Rate \\
    \midrule \midrule
    8     & $3.493\times10^{-1}$ & ---  & $9.082\times10^{-3}$ & ---  & $3.310\times10^{-3}$ & ---  & $1.151\times10^{-4}$  & --- \\
    16   & $5.793\times10^{-2}$ &2.59& $2.310\times10^{-3}$ &1.98& $2.652\times10^{-4}$ &3.64& $8.929\times10^{-6}$ &3.69 \\
    32   & $8.423\times10^{-3}$ &2.78& $6.117\times10^{-4}$ &1.92& $3.170\times10^{-5}$ &3.06& $7.911\times10^{-7}$ &3.50 \\
    64   & $1.314\times10^{-3}$ &2.68& $1.574\times10^{-4}$ &1.96& $3.949\times10^{-6}$ &3.00& $7.843\times10^{-8}$ &3.33 \\
    128 & $2.336\times10^{-4}$ &2.49& $3.987\times10^{-5}$ &1.98& $4.934\times10^{-7}$ &3.00& $8.524\times10^{-9}$ &3.20 \\
    256 & $4.736\times10^{-5}$ &2.30& $1.003\times10^{-5}$ &1.99& $6.162\times10^{-8}$ &3.00& $9.997\times10^{-10}$ &3.09 \\
    \midrule \midrule
  \end{tabular}
  \end{center}
\end{table}

\subsection{Spherical Wave}

This problem is taken from \citet{pons_etal_2000}

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.38]{./Figures/GaussianSphericalWave1D}
  \end{center}
  \caption{Energy density versus radius at various times for the spherical wave problem computed with the DG(2)+RK3 scheme using 32 elements.  The numerical solution (open circles) is compared to the analytical solution (dotted lines).  }
  \label{fig:sphericalWave}
\end{figure}

\begin{table}
  \begin{center}
  \caption{$L^{\infty}$ error and convergence rates for the spherical wave problem.}
  \begin{tabular}{ccccccccc}
    & \multicolumn{4}{c}{SSP-RK2} & \multicolumn{4}{c}{SSP-RK3} \\
    \cmidrule(r){2-5} \cmidrule(r){6-9}
    $N$ & DG(1) & Rate & DG(2) & Rate & DG(2) & Rate & DG(3) & Rate \\
    \midrule \midrule
    32   & $4.648\times10^{-4}$ & ---  & $5.540\times10^{-5}$ & ---   & $4.803\times10^{-5}$ & ---  & $1.707\times10^{-5}$ & --- \\
    64   & $9.506\times10^{-5}$ &2.29& $1.088\times10^{-5}$ &2.35& $1.373\times10^{-5}$ &1.81& $7.812\times10^{-7}$ &4.45 \\
    128 & $1.996\times10^{-5}$ &2.25& $1.502\times10^{-6}$ &2.86& $1.836\times10^{-6}$ &2.90& $1.150\times10^{-7}$ &2.76 \\
    256 & $5.783\times10^{-6}$ &1.79& $2.529\times10^{-7}$ &2.57& $1.895\times10^{-7}$ &3.28& $6.268\times10^{-9}$ &4.20 \\
    \midrule \midrule
  \end{tabular}
  \end{center}
\end{table}

\subsection{Line Source}

\subsection{Diffusion Problem}

This problem is adapted from \citet{abdikamalov_etal_2012} \citep[see also][]{pons_etal_2000,sumiyoshiYamada_2012}.

\begin{equation}
  \cJ(r,t)=\Big(\f{t_{0}}{t_{0}+t}\Big)^{3/2}\,\exp\Big\{\,-\f{3\,\sigma\,r^{2}}{4\,(t_{0}+t)}\,\Big\}
\end{equation}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[scale=0.38]{./Figures/GaussianSphericalDiffusion_Kappa_1e-5_Density} &
      \includegraphics[scale=0.38]{./Figures/GaussianSphericalDiffusion_Kappa_1e-5_Flux}
    \end{tabular}
  \end{center}
  \caption{Results from the one-dimensional diffusion problem in spherical symmetry with $\sigma=10^{-5}$~cm$^{-1}$, obtained with the DG(2)+SIRK2 method using $24$ elements.  
  The number density $\cJ$ (left panel) and the number flux density $\cH_{r}$ (right panel) are plotted for $t=0,0.3,1.0$~ms (red, blue, and black curves, respectively).  
  Solid lines represent the analytical solution while open circles represent the element center value of the numerical solution.}
  \label{fig:diffusionProblem1e-5}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[scale=0.38]{./Figures/GaussianSphericalDiffusion_Kappa_1e-1_Density} &
      \includegraphics[scale=0.38]{./Figures/GaussianSphericalDiffusion_Kappa_1e-1_Flux}
    \end{tabular}
  \end{center}
  \caption{Results similar to those displayed in Figure~\ref{fig:diffusionProblem1e-5}, but with $\sigma=10^{-1}$~cm$^{-1}$.}
  \label{fig:diffusionProblem1e-1}
\end{figure}

\subsection{Homogeneous Sphere}

\bibliographystyle{apj}
\bibliography{../References/references.bib}

\appendix

\section{Moment Equations in Commonly Used Coordinate Systems}
\label{app:CurvilinearEuler}

\subsection{Cylindrical Coordinates}

\begin{equation}
  \pderiv{\cJ}{t}
  +\f{1}{R}\pderiv{}{R}\Big(R\,\cH_{R}\Big)
  +\pderiv{}{z}\Big(\cH_{z}\Big)
  +\f{1}{R}\pderiv{}{\phi}\Big(\cH_{\phi}\Big)=0,
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{R}\big)}{t}
  +\f{1}{R}\pderiv{}{R}\Big(R\,\big(\rho\,v_{R}\,v_{R}+p\big)\Big)
  +\pderiv{}{z}\Big(\rho\,v_{R}\,v_{z}\Big)
  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{R}\,v_{\phi}\Big)
  =\f{\big(\rho\,v_{\phi}^{2}+p\big)}{R},
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{z}\big)}{t}
  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{z}\,v_{R}\Big)
  +\pderiv{}{z}\Big(\big(\rho\,v_{z}\,v_{z}+p\big)\Big)
  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{z}\,v_{\phi}\Big)=0,
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{\phi}\big)}{t}
  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{\phi}\,v_{R}\Big)
  +\pderiv{}{z}\Big(\rho\,v_{\phi}\,v_{z}\Big)
  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\,v_{\phi}+p\Big)
  =-\f{\rho\,v_{\phi}\,v_{R}}{R},
\end{equation}

\subsection{Spherical Coordinates}

\begin{equation}
  \pderiv{\rho}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v_{r}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{\theta}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\Big)=0,
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{r}\big)}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\big(\rho\,v_{r}\,v_{r}+p\big)\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{r}\,v_{\theta}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{r}\,v_{\phi}\Big)
  =\rho\,\f{\big(v_{\theta}^{2}+v_{\phi}^{2}\big)}{r}+\f{2\,p}{r},
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{\theta}\big)}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v_{\theta}\,v_{r}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\big(\rho\,v_{\theta}\,v_{\theta}+p\big)\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\theta}\,v_{\phi}\Big)
  =\cot\theta\,\f{\big(\rho\,v_{\phi}^{2}+p\big)}{r}-\rho\,\f{v_{r}\,v_{\theta}}{r},
\end{equation}
\begin{equation}
  \pderiv{\big(\rho\,v_{\phi}\big)}{t}
  +\f{1}{r^{2}}\pderiv{}{r}\Big(\,r^{2}\,\rho\,v_{\phi}\,v_{r}\,\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{\phi}\,v_{\theta}\Big)
  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\,v_{\phi}+p\Big)
  =-\rho\,v_{\phi}\,\f{\big(v_{r}+v_{\theta}\,\cot\theta\big)}{r},
\end{equation}

\end{document}

### 2017-01-04 Documents/M1/dgM1Curvilinear.tex
Added description of slope limiter and smaller edits to section 2

@@
   \gamma_{ij}
-  =\mbox{diag}\big[\,\gamma_{11},\,\gamma_{22}(x^{1}),\,\gamma_{33}(x^{1},x^{2})\,\big]
-  =\mbox{diag}\big[\,1,\,a(x^{1})^{2},\,b(x^{1})^{2}c(x^{2})^{2}\,\big], 
+  =\mbox{diag}\big[\,\gamma_{11},\,\gamma_{22}(x^{1}),\,\gamma_{33}(x^{1},x^{2})\,\big], 
   \label{eq:threeMetric}
@@
 which is sufficiently general to accommodate Cartesian, cylindrical, and spherical polar coordinates (see Table~\ref{tab:metricFunctions} and Appendix~\ref{app:CurvilinearEuler}).  
-Moreover, $\gamma$ is the determinant of the metric tensor, and $\sqrt{\gamma}=abc$.  
+Moreover, $\gamma$ is the determinant of the metric tensor, and $\sqrt{\gamma}=\sqrt{\gamma_{11}\gamma_{22}\gamma_{33}}$.  
 The inverse of the spatial metric is denoted $\gamma^{ij}$, so that $\gamma^{ik}\gamma_{kj}=\delta^{i}_{~j}$.  
@@
 \begin{equation}
-  \cK^{ij}
-  =\f{1}{2}\,\Big[\,(1-\psi)\,\gamma^{ij}+(3\,\psi-1)\,h^{i}\,h^{j}\,\Big]\,\cJ,
+  \cK^{i}_{~j}
+  =\f{1}{2}\,\Big[\,(1-\psi)\,\delta^{i}_{~j}+(3\,\psi-1)\,h^{i}\,h_{j}\,\Big]\,\cJ,
 \end{equation}
@@
   \begin{center}
-  \caption{Metric functions for Cartesian, Cylindrical, and Spherical coordinate systems.\label{tab:metricFunctions}}
+  \caption{Relevant metric functions for Cartesian, Cylindrical, and Spherical coordinate systems.\label{tab:metricFunctions}}
   \begin{tabular}{ccccccccccc}
     \midrule
-    Coordinates & $x^{1}$ & $x^{2}$ & $x^{3}$ & $a$ & $b$ & $c$ & $\sqrt{\gamma}$
-    & $\pderiv{a}{x^{1}}$ & $\pderiv{b}{x^{1}}$ & $\pderiv{c}{x^{2}}$ \\
+    Coordinates & $x^{1}$ & $x^{2}$ & $x^{3}$ & $\gamma_{11}$ & $\gamma_{22}$ & $\gamma_{33}$ & $\sqrt{\gamma}$
+    & $\f{1}{\gamma_{22}}\pderiv{\gamma_{22}}{x^{1}}$ & $\f{1}{\gamma_{33}}\pderiv{\gamma_{33}}{x^{1}}$ & $\f{1}{\gamma_{33}}\pderiv{\gamma_{33}}{x^{2}}$ \\
     \midrule
@@
     Cartesian & $x$ & $y$ & $z$ & 1 & 1 & 1 & 1 & 0 & 0 & 0 \\
-    Cylindrical & $R$ & $z$ & $\phi$ & 1 & $R$ & 1 & $R$ & 0 & 1 & 0 \\
-    Spherical & $r$ & $\theta$ & $\phi$ & $r$ & $r$ & $\sin\theta$ & $r^{2}\sin\theta$ & 1 & 1 & $\cos\theta$ \\
+    Cylindrical & $R$ & $z$ & $\phi$ & 1 & 1 & $R^{2}$ & $R$ & 0 & $2/R$ & 0 \\
+    Spherical & $r$ & $\theta$ & $\phi$ & 1 & $r^{2}$ & $r^{2}\sin^{2}\theta$ & $r^{2}\sin\theta$ & $2/r$ & $2/r$ & $2\cot\theta$ \\
     \midrule
@@
 \end{equation}
-Specifically, using the time-independent metric tensor in Eq.~\eqref{eq:threeMetric}, the components are
+Specifically, using the time-independent metric tensor in Eq.~\eqref{eq:threeMetric} and writing in terms of $\cK^{i}_{~j}$, the components are
 \begin{equation}
   \cG_{1}
-  =\f{1}{2}\,\Big(\,\cK^{22}\,\pderiv{\gamma_{22}}{x^{1}}+\cK^{33}\,\pderiv{\gamma_{33}}{x^{1}}\,\Big), \quad
+  =\f{1}{2}\,\Big(\,\cK^{2}_{~2}\,\f{1}{\gamma_{22}}\pderiv{\gamma_{22}}{x^{1}}+\cK^{3}_{~3}\,\f{1}{\gamma_{33}}\pderiv{\gamma_{33}}{x^{1}}\,\Big), \quad
   \cG_{2}
-  =\f{1}{2}\,\cK^{33}\,\pderiv{\gamma_{33}}{x^{2}}, \quad\text{and}\quad
+  =\f{1}{2}\,\cK^{3}_{~3}\,\f{1}{\gamma_{33}}\pderiv{\gamma_{33}}{x^{2}}, \quad\text{and}\quad
   \cG_{3}
@@
 
-Several books and review articles on the DG method are available now available \citep[see, e.g.,][]{cockburnShu_2001,hesthavenWarburton_2008}, and we will not go into too much detail here.  
+Several books and review articles on the DG method are now available \citep[see, e.g.,][]{cockburnShu_2001,hesthavenWarburton_2008}, and we will not go into too much detail here.  
 However, we review some key concepts to introduce notation, and, since multiple `flavors' of the DG method has emerged, we emphasize specific choices in our implementation.
@@
   \bcM_{\bK}=\f{|\bK|}{V_{\bK}}\sum_{\bk=\vect{1}}^{\bN}w_{\bk}\,\sqrt{\gamma}_{\bk}\,\bcM_{\bk},
+  \label{eq:conservedCellAverage}
 \end{equation}
@@
 
-We have now defined the spatial discretization of the moment equations.
+This defines the spatial discretization of the moment equations.
 
@@
 
-\section{Slope Limiters}
+\clearpage
 
-\subsection{TVD and TVB Limiters}
+\section{Polynomial Limiting}
+
+During time integration we apply limiters that modify the polynomial representation in elements so as to prevent development and growth of nonphysical oscillations (slope limiters; Sec.~\ref{sec:slopeLimiters}) or nonphysical states (positivity limiters; Sec.~\ref{sec:positivityLimiters}).
+
+\subsection{Slope Limiters}
+\label{sec:slopeLimiters}
 
@@
 \begin{equation}
-  (\sqrt{\gamma}\bcM)_{\DG}=\sum_{\bi=\vect{1}}^{\bN}(\widetilde{\sqrt{\gamma}\bcM})_{\bi}\,\phi_{\bi}(\bx),
+  \bcM_{\DG}(\bx)=\sum_{\bi=\vect{1}}^{\bN}\bcC_{\bi}\,\phi_{\bi}(\bx),
+  \label{eq:conservedModalExpansion}
 \end{equation}
-where $\{\phi_{\bi}\}_{\bi=\vect{1}}^{\bN}$ are elements of an orthogonal basis and $(\widetilde{\sqrt{\gamma}\bcM})_{\bi}$ are the corresponding expansion coefficients.  
-(Here, we let the orthogonal basis be given by normalized Legendre polynomials; $\{\phi_{k}(\eta)\}_{k=1}^{4}=\{\,1,\,\eta,\,\eta^{2}-1/12,\,\eta\,(\eta^{2}-3/20)\,\}$.)  
-By orthogonality of the basis functions, we have
+where $\{\phi_{\bi}\}_{\bi=\vect{1}}^{\bN}$ are elements of an orthogonal basis and $\bcC_{\bi}$ are the corresponding expansion coefficients (not to be confused with the collision term in Eq.~\eqref{eq:momentEquationsCompact}).
+Here, we let the orthogonal basis be constructed from the tensor product of one-dimensional, normalized Legendre polynomials up to degree 3; i.e., $\{\phi_{k}(\eta)\}_{k=1}^{4}=\{\,1,\,\eta,\,\eta^{2}-1/12,\,\eta\,(\eta^{2}-3/20)\,\}$.
+By orthogonality of the basis functions, the expansion coefficients are easily obtained by projection of the nodal representation in Eq.~\eqref{eq:conservedNodalExpansion} onto the modal basis in Eq.~\eqref{eq:conservedModalExpansion}; i.e.,
 \begin{equation}
-  (\widetilde{\sqrt{\gamma}\bcM})_{\bi}
-  =\cT_{\bi}^{-1}\int_{\bK}(\sqrt{\gamma}\bcM)_{\DG}\,\phi_{\bi}(\bx)\,d\bx,
+  \bcC_{\bi}
+  =\langle\,\phi_{\bi},\,\phi_{\bi}\,\rangle_{\bK}^{-1}\sum_{\bj=\vect{1}}^{\bN}\langle\,\phi_{\bi},\,\ell_{\bj}\,\rangle_{\bK}\,\bcM_{\bj}
 \end{equation}
@@
 \begin{equation}
-  \cT_{\bi}=\int_{\bK}\phi_{\bi}(\bx)\,\phi_{\bi}(\bx)\,d\bx,
+  \langle\phi_{\bi},\phi_{\bi}\rangle_{\bK}=\int_{\bK}\phi_{\bi}(\bx)\,\phi_{\bi}(\bx)\,d\bx
+  \quad\text{and}\quad
+  \langle\phi_{\bi},\ell_{\bj}\rangle_{\bK}=\int_{\bK}\phi_{\bi}(\bx)\,\ell_{\bj}(\bx)\,d\bx.
+  \label{eq:projectionIntegrals}
 \end{equation}
-and $\{\cT_{i}^{-1}\}_{i=1}^{4}=\{\,1,\,12,\,180,\,2800\,\}$.  
+The integrals in Eq.~\eqref{eq:projectionIntegrals} can be computed exactly with a sufficiently accurate quadrature rule.  
+The projection is a linear transformation, and the projection matrix integrals can be computed once and stored at program initialization.  
+Also note that the projection matrix does not depend on the metric function, and is therefore the same for all elements, which limits storage requirements.
+
+The elements of the multidimensional modal basis are ordered by increasing polynomial degree; i.e., 
 \begin{equation}
-  (\widetilde{\sqrt{\gamma}\bcM})_{|\vect{1}|}
-  \to\text{minmodB}
+  \{\phi_{1}(\eta^{1})\phi_{1}(\eta^{2})\ldots\phi_{1}(\eta^{d}),\,\phi_{2}(\eta^{1})\phi_{1}(\eta^{2})\ldots\phi_{1}(\eta^{d}),\,\phi_{1}(\eta^{1})\phi_{2}(\eta^{2})\ldots\phi_{1}(\eta^{d}),\ldots\},
+\end{equation}
+so that the first expansion coefficient represents the average value of $\bcM$ in $\bK$, $\bcC_{|\vect{0}|}=\langle\bcM\rangle_{\bK}$ (the coefficient of the basis polynomial with total degree $0$).  
+The second expansion coefficient, $\bcC_{|\vect{1}|}^{1}$ (coefficient of the basis function with total degree $1$ varying in the first dimension), represents the first derivative of $\bcM$ in the first dimension, and so on.
+
+The limiting procedure first computes, for each dimension $i=1,\ldots,d$, the limited slopes $\widetilde{\bcC}_{|\vect{1}|}^{i}$ by comparing the variation within $\bK$, $\bcC_{|\vect{1}|}^{i}$, with the variation in the cell average by considering the neighboring elements
+\begin{equation}
+  \widetilde{\bcC}_{|\vect{1}|}^{i}
+  =\text{minmodB}
   \big(\,
-    (\widetilde{\sqrt{\gamma}\bcM})_{|\vect{1}|},\,
-    \beta\,((\widetilde{\sqrt{\gamma}\bcM})_{|\vect{0}|}-(\widetilde{\sqrt{\gamma}\bcM})_{|\vect{0}|}^{-}),\,
-    \beta\,((\widetilde{\sqrt{\gamma}\bcM})_{|\vect{0}|}^{+}-(\widetilde{\sqrt{\gamma}\bcM})_{|\vect{0}|})
+    \bcC_{|\vect{1}|}^{i},\,
+    \beta\,(\langle\bcM\rangle_{\bK}-\langle\bcM\rangle_{\bK}^{i,-}),\,
+    \beta\,(\langle\bcM\rangle_{\bK}^{i,+}-\langle\bcM\rangle_{\bK})
   \,\big),
+  \label{eq:limitedSlopes}
 \end{equation}
-where $\beta\in[1,2]$.
-
-\citet{cockburnShu_2001}
+where the limiter parameter $\beta\in[1,2]$ controls how aggressive limiting is applied.  
+($\beta=2$ is the least aggressive, and, in many cases, leads to the most accurate results.)  
+The $\text{minmodB}$ function is given by \citet{cockburnShu_2001} as
 \begin{equation}
@@
   a \quad\text{if}\quad |a|\le M\,\Delta x^{2} \\
-  \mbox{minmod}(a,b,c) \quad \text{otherwise}
-  \end{array}\right.,
+  \mbox{minmod}(a,b,c) \quad \text{otherwise},
+  \end{array}\right.
+  \label{eq:minmodB}
 \end{equation}
-where the minmod function is given by
+and the usual minmod function is given by
 \begin{equation}
@@
   =\left\{\begin{array}{ll}
-  s\,\min[\,|a|,|b|,|c|\,] \quad\text{if}\quad $s=\mbox{sign}(a)=\mbox{sign}(b)=\mbox{sign}(c)$ \\
+  s\,\min[\,|a|,|b|,|c|\,] \quad\text{if}\quad s=\mbox{sign}(a)=\mbox{sign}(b)=\mbox{sign}(c) \\
   0 \quad \text{otherwise}.
-  \end{array}\right..
+  \end{array}\right.
+  \label{eq:minmod}
 \end{equation}
+In Eq.~\eqref{eq:minmodB}, the parameter $M>0$ is proportional to the second derivative, and can be adjusted to prevent clipping at smooth extrema.  
+For $M=0$, the $\text{minmodB}$ functions reduces to the usual minmod function in Eq.~\eqref{eq:minmod}.  
+In Eq.~\eqref{eq:limitedSlopes}, $\langle\bcM\rangle_{\bK}^{i,-/+}$ is the cell average in the element to the left/right in the $i$-th dimension of the element under consideration.
+
+After computing the limited slopes in Eq.~\eqref{eq:limitedSlopes}, they are compared with the original slopes.  
+Then, if
+\begin{equation}
+  |\widetilde{\bcC}_{|\vect{1}|}^{i}-\bcC_{|\vect{1}|}^{i}|/\max\big(|\widetilde{\bcC}_{|\vect{1}|}^{i}|,|\bcC_{|\vect{1}|}^{i}|\big)>\text{tol},
+\end{equation}
+where we set $\text{tol}=10^{-2}$, we replace the modal expansion in Eq.~\eqref{eq:conservedModalExpansion} with the limited polynomial
+\begin{equation}
+  \bcM_{\DG}(\bx)
+  \to\widetilde{\bcM}_{\DG}(\bx)
+  =\langle\bcM\rangle_{\bK}+\sum_{i=1}^{d}\widetilde{\bcC}_{|\vect{1}|}^{i}\,\phi_{|\vect{1}|}^{i}(\bx).  
+  \label{eq:conservedModalExpansionLimited}
+\end{equation}
+We limit all the fields in $\bcM$ if the difference in any of the coefficients exceeds the tolerance.  
+This limiting procedure locally destroys the high-order accuracy of the DG method, but leads to non-oscillatory evolution when sharp features are present in the solution.
+
+The limiting procedure described here operates on the coefficients of the modal expansion of $\bcM$, not that of $\sqrt{\gamma}\bcM$.  
+As a consequence, the average $\langle\bcM\rangle_{\bK}$ is preserved in the limiting process, and not the average given in Eq.~\eqref{eq:conservedCellAverage}, which defines the conserved quantities governed by the two-moment model in curvilinear coordinates.
+(We have found that limiting a polynomial expansion of $\sqrt{\gamma}\bcM$ leads to inaccurate results, especially near coordinate singularities.)  
+To enforce conservation, we therefore introduce a correction step, similar in spirit to that discussed by \citet{radiceRezzolla_2011}.  
+To this end we define $\widetilde{\bcC}=\big(\bcC_{|\vect{0}|},\,\widetilde{\bcC}_{|\vect{1}|}^{1},\ldots,\,\widetilde{\bcC}_{|\vect{1}|}^{d}\big)^{T}$ and $\widehat{\bcC}=\big(\widehat{\bcC}_{|\vect{0}|},\,\widehat{\bcC}_{|\vect{1}|}^{1},\ldots,\,\widehat{\bcC}_{|\vect{1}|}^{d}\big)^{T}$, and find $\widehat{\bcC}$ by solving
+\begin{equation}
+  \min_{\widehat{\bcC}}\f{1}{2}||\widetilde{\bcC}-\widehat{\bcC}||^{2}
+\end{equation}
+subject to the constraint
+\begin{equation}
+  \widehat{\bcM}_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\widehat{\bcM}_{\DG}\,\sqrt{\gamma}\,d\bx\equiv\bcM_{\bK}.  
+\end{equation}
+This linear equality-constrained least squares problem can be solved, e.g., using LAPACK's DGGLSE subroutine.
 
 \subsection{Positivity Limiters}
+\label{sec:positivityLimiters}
+
+\clearpage
 

### 2017-01-09 Documents/Euler/dgEulerCurvilinear.tex
Adding transport application
Updates to hydro document

@@
 
-\title{Nodal Discontinuous Galerkin Method for the Euler Equations with Curvilinear Coordinates and Nuclear Equation of State for Astrophysics Simulations}
-\author{Eirik Endeve\altaffilmark{1}}
-\altaffiltext{1}{Department of Computational and Applied Mathematics, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
+\title{Nodal Discontinuous Galerkin Method for the Euler Equations of Fluid Dynamics}
+\author{Eirik Endeve\altaffilmark{1}, et al.}
+\altaffiltext{1}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
 
 \begin{abstract}
-We explore the use of the nodal Discontinuous Galerkin (DG) method in astrophysical hydrodynamics.  
-We focus on issues related to core-collapse supernova dynamics, which include the use of curvilinear coordinates and a nuclear equation of state.  
+We present a nodal Discontinuous Galerkin (DG) method for the Euler equations with an eye towards astrophysical hydrodynamics.  
+We focus on issues related to core-collapse supernova dynamics, which include the use of curvilinear coordinates and a non-ideal (nuclear) equation of state.  
 \end{abstract}
+
+\tableofcontents
 
@@
 
-We consider evolution in three-dimensional position space and denote the position vector with for a point with coordinates $\bx=\{x^{1},x^{2},x^{3}\}$ with $\vect{r}(\vect{x})\in\mathbb{R}^{3}$, so that the displacement vector is $d\vect{r}=dx^{i}\,\vect{e}_{i}$ and the coordinate basis vectors are
-\begin{equation}
-  \vect{e}_{i}=\pderiv{\vect{r}}{x^{i}}.  
-\end{equation}
-The squared infinitesimal line-element is
-\begin{equation}
-  ds_{\vect{x}}^{2}=d\vect{r}\cdot d\vect{r}=\gamma_{ij}\,dx^{i}\,dx^{j},
-\end{equation}
-where the coordinate basis metric tensor is defined as $\gamma_{ij}=\vect{e}_{i}\cdot\vect{e}_{j}$.
+\subsection{Basic Mathematical Model}
 
-For general curvilinear spatial coordinates, the Euler equations for gas dynamics are \citep{leveque_2002}
+For general curvilinear spatial coordinates, the non-relativistic Euler equations for gas dynamics are \citep[][see, e.g., \citet{} and references therein for a fully general relativistic treatment]{leveque_2002}
 \begin{equation}
@@
   +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\rho\,v^{i}\,\Big)=0,
+  \label{eq:massConservation}
 \end{equation}
 \begin{equation}
-  \pderiv{M_{j}}{t}
+  \pderiv{S_{j}}{t}
   +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,P^{i}_{~j}\,\Big)
   =\f{1}{2}\,P^{ik}\,\pderiv{\gamma_{ik}}{x^{j}}-\rho\,\pderiv{\Phi}{x^{j}},
+  \label{eq:momentumConservation}
 \end{equation}
@@
   +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\big(E+p\big)\,v^{i}\,\Big)
-  =-M^{i}\,\pderiv{\Phi}{x^{i}},
+  =-S^{i}\,\pderiv{\Phi}{x^{i}},
+  \label{eq:energyConservation}
 \end{equation}
@@
   +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,n_{e}\,v^{i}\,\Big)=0,
+  \label{eq:electronConservation}
 \end{equation}
-where $\rho$ is the (baryon) mass density, $M^{i}=\rho\,v^{i}$ is the momentum density, $P^{ij}=\rho\,v^{i}\,v^{j}+p\,\gamma^{ij}$ the stress tensor, $E=e+\f{1}{2}\,\rho\,v_{i}\,v^{i}$ the total (internal plus kinetic) energy density, and $n_{e}$ the electron density.
+where $\rho$ is the (baryon) mass density, $S^{i}=\rho\,v^{i}$ is the momentum density, $P^{ij}=\rho\,v^{i}\,v^{j}+p\,\gamma^{ij}$ the stress tensor, $E=e+\f{1}{2}\,\rho\,v_{i}\,v^{i}$ the total (internal plus kinetic) energy density, and $n_{e}$ the electron density.
 The pressure is related to the density, internal energy density, and electron density by an equation of state (EoS); i.e., $p=p(\rho,e,n_{e})$.  
 (We also define the specific internal energy by $\epsilon=e/\rho$.)
+The Newtonian gravitation potential, $\Phi$, is obtained from solving
+\begin{equation}
+  \f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\gamma^{ij}\pderiv{\Phi}{x^{j}}\,\Big)=4\pi\,\rho.  
+  \label{eq:poisson}
+\end{equation}
 
-We assume the following diagonal form of the spatial metric tensor
+The model given by Eqs.~\eqref{eq:massConservation} - \eqref{eq:electronConservation} is non-relativistic (i.e., it does not include effects due to strong gravitational fields or relativistic fluid velocities), but is expressed in terms of curvilinear coordinates through the spatial metric tensor $\gamma_{ij}$, which gives squared infinitesimal line-element
 \begin{equation}
-  \gamma_{ij}=\mbox{diag}\big[\,1,a(x^{1})^{2},\,b(x^{1})^{2}c(x^{2})^{2}\,\big], 
+  ds_{\vect{x}}^{2}=\gamma_{ij}\,dx^{i}\,dx^{j},
+\end{equation}
+where $\gamma_{ij}$ are the spatial components of the coordinate basis metric tensor.  
+We will make two simplifying assumptions: the metric tensor is (1) diagonal and (2) time-independent.  
+Specifically we assume the following diagonal form
+\begin{equation}
+  \gamma_{ij}
+  =\mbox{diag}\big[\,\gamma_{11},\,\gamma_{22}(x^{1}),\,\gamma_{33}(x^{1},x^{2})\,\big]
+  =\mbox{diag}\big[\,1,\,a(x^{1})^{2},\,b(x^{1})^{2}c(x^{2})^{2}\,\big], 
+  \label{eq:threeMetric}
 \end{equation}
 which is sufficiently general to accommodate Cartesian, cylindrical, and spherical polar coordinates (see Table~\ref{tab:metricFunctions} and Appendix~\ref{app:CurvilinearEuler}).  
-$\sqrt{\gamma}=abc$.  $w^{i}=e^{i}_{~j}\,\bar{w}^{j}$.  
-With $e^{i}_{~j}=\mbox{diag}\big[\,1,a(x^{1})^{-1},\,b(x^{1})^{-1}c(x^{2})^{-1}\,\big]$, we have $\{w^{i}\}_{i=1}^{3}=\{\bar{w}^{1},\,a^{-1}\,\bar{w}^{2},\,b^{-1}c^{-1}\,\bar{w}^{3}\}$.  
+Moreover, $\gamma$ is the determinant of the metric tensor, and $\sqrt{\gamma}=abc$.  
+The inverse of the spatial metric is denoted $\gamma^{ij}$, so that $\gamma^{ik}\gamma_{kj}=\delta^{i}_{~j}$.  
+We can use the spatial metric to raise and lower indices on spatial vectors and tensors; e.g., $S_{j}=\gamma_{jk}\,S^{k}$.
+
 \begin{table}
@@
 
-The mass conservation equation
+\subsection{Euler Equations as a System of Conservation Laws with Sources}
+
+We define the geometry sources (fictitious plus gravitational sources) in Eq.~\eqref{eq:momentumConservation} by
 \begin{equation}
-  \pderiv{\rho}{t}
-  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,\rho\,\bar{v}^{1}\,\Big)
-  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,\rho\,\bar{v}^{2}\,\Big)
-  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\rho\,\bar{v}^{3}\,\Big)=0
+  G_{j}
+  =\f{1}{2}\,P^{ik}\,\pderiv{\gamma_{ik}}{x^{j}}-\rho\,\pderiv{\Phi}{x^{j}}.  
 \end{equation}
-Components of the momentum equation
+Specifically, using the time-independent metric tensor in Eq.~\eqref{eq:threeMetric}, the components are
 \begin{equation}
-  \pderiv{\bar{M}^{i}}{t}
-  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,\bar{P}^{1i}\,\Big)
-  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,\bar{P}^{2i}\,\Big)
-  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\bar{P}^{3i}\,\Big)
-  =\bar{S}^{i}+\bar{G}^{i},
+  G_{1}
+  =\f{1}{2}\,\Big(\,P^{22}\,\pderiv{\gamma_{22}}{x^{1}}+P^{33}\,\pderiv{\gamma_{33}}{x^{1}}\,\Big)-\rho\,\pderiv{\Phi}{x^{1}}, \quad
+  G_{2}
+  =\f{1}{2}\,P^{33}\,\pderiv{\gamma_{33}}{x^{2}}-\rho\,\pderiv{\Phi}{x^{2}}, \quad\text{and}\quad
+  G_{3}
+  =-\rho\,\pderiv{\Phi}{x^{3}}.
 \end{equation}
-where the ``geometry sources'' are given by
-\small
-\begin{equation}
-  \bar{S}^{1}
-  =\bar{P}^{22}\f{1}{a}\pderiv{a}{x^{1}}+\bar{P}^{33}\f{1}{b}\pderiv{b}{x^{1}}, \quad
-  \bar{S}^{2}
-  =\bar{P}^{33}\f{1}{ac}\pderiv{c}{x^{2}}-\bar{P}^{12}\f{1}{a}\pderiv{a}{x^{1}}, \quad
-  \bar{S}^{3}
-  =-\bar{P}^{13}\f{1}{b}\pderiv{b}{x^{1}}-\bar{P}^{23}\f{1}{ac}\pderiv{c}{x^{2}},
-\end{equation}
-\normalsize
-and the gravitational sources are
-\begin{equation}
-  \bar{G}^{1}
-  =-\rho\,\pderiv{\Phi}{x^{1}}, \quad
-  \bar{G}^{2}
-  =-\rho\,\f{1}{a}\pderiv{\Phi}{x^{2}}, \quad
-  \bar{G}^{3}
-  =-\rho\,\f{1}{bc}\pderiv{\Phi}{x^{3}}.
-\end{equation}
-The energy equation is given by
-\begin{equation}
-  \pderiv{E}{t}
-  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,\big(E+p\big)\,\bar{v}^{1}\,\Big)
-  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,\big(E+p\big)\,\bar{v}^{2}\,\Big)
-  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\big(E+p\big)\,\bar{v}^{3}\,\Big)=Q,  
-\end{equation}
-where the gravitational energy source is
-\begin{equation}
-  Q=-\Big(\,\bar{M}^{1}\pderiv{\Phi}{x^{1}}+\bar{M}^{2}\f{1}{a}\pderiv{\Phi}{x^{2}}+\bar{M}^{3}\f{1}{bc}\pderiv{\Phi}{x^{3}}\,\Big).
-\end{equation}
-Finally, the electron conservation equation
-\begin{equation}
-  \pderiv{n_{e}}{t}
-  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,n_{e}\,\bar{v}^{1}\,\Big)
-  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,n_{e}\,\bar{v}^{2}\,\Big)
-  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,n_{e}\,\bar{v}^{3}\,\Big)=0
-\end{equation}
-By defining the vector of evolved variables $\bU=\big(\,\rho,\,\rho\,\bar{v}^{1},\,\rho\,\bar{v}^{2},\,\rho\,\bar{v}^{3},\,E,\,n_{e}\,\big)^{T}$, the vector of geometry sources $\vect{S}(\bU)=\big(\,0,\,\bar{S}^{1},\,\bar{S}^{2},\,\bar{S}^{3}\,,0,\,0\,\big)^{T}$, the vector of gravitational sources $\bG(\bU,\Phi)=\big(\,0,\bar{G}^{1},\bar{G}^{2},\bar{G}^{3},Q,0\,\big)^{T}$, and the vectors of flux vector components
+The gravitational energy source term in Eq.~\eqref{eq:energyConservation} is denoted with $G_{E}=-S^{i}\,\pd{\Phi}{x^{i}}$.
+
+Then, by defining the vector of evolved variables $\bU=\big(\,\rho,\,S_{1},\,S_{2},\,S_{3},\,E,\,n_{e}\,\big)^{T}$, the vector of geometry sources $\bG(\bU)=\big(\,0,\,G_{1},\,G_{2},\,G_{3},\,G_{E},\,0\,\big)^{T}$, and the flux vector components
 \begin{equation}
   \vect{F}^{i}(\bU)
-  =\big(\,\rho\,\bar{v}^{i},\,\rho\,\bar{v}^{1}\,\bar{v}^{i}+p\,\delta^{1i},\,\rho\,\bar{v}^{2}\,\bar{v}^{i}+p\,\delta^{2i},\,\rho\,\bar{v}^{3}\,\bar{v}^{i}+p\,\delta^{3i},\,(E+p)\,\bar{v}^{i},\,n_{e}\,\bar{v}^{i}\,\big)^{T},
+  =\big(\,\rho\,v^{i},\,P_{~1}^{i},\,P_{~2}^{i},\,P_{~3}^{i},\,(E+p)\,\bar{v}^{i},\,n_{e}\,\bar{v}^{i}\,\big)^{T},
 \end{equation}
-we can write the system of equations in compact form
+we write the system of equations in the usual compact form
 \begin{equation}
-  \pderiv{\bU}{t}
-  +\f{1}{ab}\pderiv{}{x^{1}}\Big(\,ab\,\vect{F}^{1}(\bU)\,\Big)
-  +\f{1}{ac}\pderiv{}{x^{2}}\Big(\,c\,\vect{F}^{2}(\bU)\,\Big)
-  +\f{1}{bc}\pderiv{}{x^{3}}\Big(\,\vect{F}^{3}(\bU)\,\Big)
-  =\vect{S}(\bU)+\bG(\bU,\Phi).
+  \pd{\bU}{t}
+  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\vect{F}^{i}(\bU)\,\Big)
+  =\bG(\bU).
   \label{eq:extendedEulerCompact}
 \end{equation}
+Eq.~\eqref{eq:extendedEulerCompact} forms the basis for developing DG methods for the Euler equations.
 
 \section{Discontinuous Galerkin Discretization}
+
+\subsection{Basic Principles of the DG Method}
 
@@
   \pd{}{t}\int_{\bK}\bU_{\DG}\,v\,dV
-  &\approx w_{\bk}\,\sqrt{\gamma}_{\bk}\,|\bK|\,\pd{}{t}\bU_{\bk} \nonumber \\
-  &\hspace{12pt}
-  =w_{\bk}\,a(x_{k_{1}}^{1})\,b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{1}\,\dx^{2}\,\dx^{3}\,\pd{}{t}\bU_{\bk}
+  &\approx w_{\bk}\,\sqrt{\gamma}_{\bk}\,\pd{}{t}\bU_{\bk}\,|\bK|
 \end{align}
@@
 \begin{align}
-  \int_{\bK}\bS(\bU_{\DG})\,v\,dV
-  &\approx w_{\bk}\,\sqrt{\gamma}_{\bk}\,|\bK|\,\bS(\bU_{\bk}) \nonumber \\
-  &\hspace{12pt}
-  =w_{\bk}\,a(x_{k_{1}}^{1})\,b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{1}\,\dx^{2}\,\dx^{3}\,\bS(\bU_{\bk})
+  \int_{\bK}\bG(\bU_{\DG})\,v\,dV
+  &\approx w_{\bk}\,\sqrt{\gamma}_{\bk}\,\bG(\bU_{\bk})\,|\bK|.
 \end{align}
 for the source term.  
+The gravitational source terms contain the derivative to the potential, which warrants some additional exposition.  
+We choose a local representation of the potential (obtained by evaluating the potential in the nodes in $\bK$ using the FEM solution); i.e.,
+\begin{equation}
+  \Phi(\bx)=\sum_{\bi=\vect{1}}^{\bN}\Phi_{\bi}\,\ell_{\bi}(\bx).  
+\end{equation}
+Differentiating with respect to $x^{j}$ gives
+\begin{equation}
+  \pderiv{\Phi}{x^{j}}\Big|_{\bx_{\bk}}
+  =\f{1}{|K^{j}|}\sum_{\bi=\vect{1}}^{\bN}\pderiv{\ell_{\bi}}{\eta^{j}}(\eta_{\bk})\,\Phi_{\bi}
+  =\f{1}{|K^{j}|}\sum_{i_{j}=1}^{N}\pderiv{\ell_{i_{j}}}{\eta^{j}}(\eta_{k_{j}}^{j})\,\Phi(x_{i_{j}}^{j},\tilde{\bx}_{\tilde{\bk}_{j}}^{j}).  
+\end{equation}
+This expression is used to evaluate the gravitational sources in the momentum and energy equations.
+
 For the surface integrals, we obtain, e.g., 
@@
 \end{align}
+
+\section{Time Integration}
+
+\section{Slope Limiters}
 
@@
 where $v^{2}=v_{1}^{2}+v_{2}^{2}+v_{3}^{2}$, $H=(E+p)/\rho$, $p_{\rho}=(\partial p/\partial \rho)$, $p_{e}=(\partial p/\partial e)$, and $p_{n}=(\partial p/\partial n)$.  
+(For the ideal gas law, $p=p(e)=(\gamma-1)\,e$, we have $p_{\rho}=(\gamma-1)\f{1}{2}v^{2}$, $p_{e}=(\gamma-1)$, and $p_{n}=0$.)
 

### 2017-01-09 Documents/M1/dgM1Curvilinear.tex
Adding Riemann problem for M1, description of eigenstructure, and updated equations in appendix

@@
   =\f{1}{2}\,\Big[\,(1-\psi)\,\delta^{i}_{~j}+(3\,\psi-1)\,h^{i}\,h_{j}\,\Big]\,\cJ,
+  \label{eq:stressTensor}
 \end{equation}
@@
   \psi(h)=\f{1}{3}+\f{2}{3}\,\Big(\,h^{2}\,\big(\,3-h+3h^{2}\,\big)/5\,\Big),
+  \label{eq:eddingtonFactor}
 \end{equation}
@@
 
+\subsection{Riemann Problem}
+
+To test the ability of the DG method to capture discontinuities, we solve the Riemann problem presented by \citet{OHF2012}.  
+To compare with their results, we use the Eddington factor due to Levermore \citep{levermore_1984}
+\begin{equation}
+  \psi(h)=\f{1}{3}\big(\,5-2\,\sqrt{4-3\,h^{2}}\,\big).  
+\end{equation}
+The computational domain extends from $x=-0.05$ to $x=0.1$, and a discontinuity is located at $x_{\mbox{\tiny d}}=0.0$.  
+The initial condition is given by
+\begin{equation}
+  \bcM(x,t=0)=
+  \left\{
+  \begin{array}{l}
+  \bcM_{\mbox{\tiny L}}=\big(1,0.9999,0,0\big)^{T} \quad\text{if}\quad x\le x_{\mbox{\tiny d}} \\
+  \bcM_{\mbox{\tiny R}}=\big(0.5,0,0,0\big)^{T} \quad\text{otherwise}.
+  \end{array}
+  \right.
+\end{equation}
+
 \subsection{Diffusion Problem}
@@
 
+\clearpage
+
+\section{Eigenvalues and Eigenvectors for the Two-Moment Model}
+\label{sec:eigenstructure}
+
+Here we list eigenvalues and eigenvectors for the flux Jacobian associated with the hyperbolic system in Eq.~\eqref{eq:momentEquationsCompact}.  
+To this end, we define the Eddington tensor
+\begin{equation}
+  k^{i}_{~j}=\cK^{i}_{~j}/\cJ,
+\end{equation}
+where $\cK^{i}_{~j}$ is given by Eq.~\eqref{eq:stressTensor}.
+
+The flux Jacobian is given by
+\begin{equation}
+  \pderiv{\bcF^{i}(\bcM)}{\bcM}
+  =\left[
+  \begin{array}{cccc}
+    0 & \gamma^{i1} & \gamma^{i2} & \gamma^{i3} \\
+    k^{i}_{~1}+\cJ\,\pderiv{k^{i}_{~1}}{\cJ} & \cJ\,\pderiv{k^{i}_{~1}}{\cH_{1}} & \cJ\,\pderiv{k^{i}_{~1}}{\cH_{2}} & \cJ\,\pderiv{k^{i}_{~1}}{\cH_{3}} \\
+    k^{i}_{~2}+\cJ\,\pderiv{k^{i}_{~2}}{\cJ} & \cJ\,\pderiv{k^{i}_{~2}}{\cH_{1}} & \cJ\,\pderiv{k^{i}_{~2}}{\cH_{2}} & \cJ\,\pderiv{k^{i}_{~2}}{\cH_{3}} \\
+    k^{i}_{~3}+\cJ\,\pderiv{k^{i}_{~3}}{\cJ} & \cJ\,\pderiv{k^{i}_{~3}}{\cH_{1}} & \cJ\,\pderiv{k^{i}_{~3}}{\cH_{2}} & \cJ\,\pderiv{k^{i}_{~3}}{\cH_{3}}
+  \end{array}
+  \right].  
+\end{equation}
+We will need the derivatives
+\begin{equation}
+  \pderiv{\psi}{\cJ}=-\f{\cH}{\cJ^{2}}\pderiv{\psi}{h},
+  \quad
+  \pderiv{\psi}{\cH_{k}}=\f{h^{k}}{\cJ}\pderiv{\psi}{h},
+  \quad
+  \pderiv{h^{i}}{\cH_{k}}
+  =\f{1}{\cH}\big(\,\gamma^{ik}-h^{i}\,h^{k}\,\big),
+  \quad\text{and}\quad
+  \pderiv{h_{j}}{\cH_{k}}
+  =\f{1}{\cH}\big(\,\delta^{k}_{~j}-h^{k}\,h_{j}\,\big).
+\end{equation}
+Then, we have
+\begin{equation}
+  \cJ\,\pderiv{k^{i}_{~j}}{\cJ}
+  =\f{1}{2}\,\big[\,\delta^{i}_{~j}-3\,h^{i}\,h_{j}\,\big]\,h\,\pderiv{\psi}{h},
+\end{equation}
+and
+\begin{equation}
+  \cJ\,\pderiv{k^{i}_{~j}}{\cH_{k}}
+  =-\f{1}{2}\,\big[\,\delta^{i}_{~j}-3\,h^{i}\,h_{j}\,\big]\,h^{k}\,\pderiv{\psi}{h}
+  +\f{1}{2}(3\psi-1)\,\big[\,\big(\gamma^{ik}\,h_{j}+h^{i}\,\delta^{k}_{~j}\big)-2\,h^{i}\,h^{k}\,h_{j}\,\big]\,\f{1}{h}.  
+\end{equation}
+
+Computing the flux Jacobian in the $1$-dimension, using the metric tensor in Eq.~\eqref{eq:threeMetric} and simplifying by setting $h^{2},h^{3}=0$ so that $h^{1}h_{1}=1$, gives
+\begin{equation}
+  \pderiv{\bcF^{1}(\bcM)}{\bcM}
+  =\left[
+  \begin{array}{cccc}
+    0 & 1 & 0 & 0 \\
+    \psi-h\,\psi' & h^{1}\,\psi' & 0 & 0 \\
+    0 & 0 & \f{(3\,\psi-1)\,h^{1}}{2\,h} & 0 \\
+    0 & 0 & 0 & \f{(3\,\psi-1)\,h^{1}}{2\,h}
+  \end{array}
+  \right],
+\end{equation}
+where $\psi'=\partial\psi/\partial h$.  
+The characteristic polynomial is
+\begin{equation}
+  p(\lambda)=\Big[\,\lambda^{2}-h^{1}\,\psi'\,\lambda-\big(\,\psi-h\,\psi\,\big)\Big]\,\Big[\,\f{(3\,\psi-1)\,h^{1}}{2\,h}-\lambda\,\Big]^{2}
+\end{equation}
+so that the eigenvalues are
+\begin{equation}
+  \vect{\lambda}
+  =\{\,\lambda_{1},\,\lambda_{2},\,\lambda_{3},\,\lambda_{4}\,\}
+  =\big\{\,\f{1}{2}\,\big(h^{1}\,\psi'+\sqrt{\Delta}\big),\,\f{1}{2}\,\big(h^{1}\,\psi'-\sqrt{\Delta}\big),\,\f{(3\,\psi-1)\,h^{1}}{2\,h},\,\f{(3\,\psi-1)\,h^{1}}{2\,h}\,\big\},
+\end{equation}
+where $\Delta=(\psi'-2\,h)^{2}+4(\psi-h^{2})$ \citep[cf.][]{pons_etal_2000}.  
+With the Eddington factor in Eq.~\eqref{eq:eddingtonFactor}, we have
+\begin{equation}
+  \psi'(h)=2\,h\,\big(\,2-h+4\,h^{2}\,\big)/5.  
+\end{equation}
+We then have, as expected, $\vect{\lambda}(h=0)=\{\,\sqrt{1/3},\,-\sqrt{1/3},\,0,\,0\,\}$ (diffusion limit) and $\vect{\lambda}(h=1)=\{\,h^{1},\,h^{1},\,h^{1},\,h^{1}\,\}$ (streaming limit).
+
+The corresponding right and left eigenvectors are given by the columns and rows, respectively of the matrices
+\begin{equation}
+  \cR^{1}
+  =\left[
+  \begin{array}{cccc}
+    1 & 1 & 0 & 0 \\
+    \lambda_{1} & \lambda_{2} & 0 & 0 \\
+    0 & 0 & 1 & 0 \\
+    0 & 0 & 0 & 1
+  \end{array}
+  \right]
+  \quad\text{and}\quad
+  \cL^{1}=(\cR^{1})^{-1}
+  =\left[
+  \begin{array}{cccc}
+  \lambda_{2}/(\lambda_{2}-\lambda_{1}) & 1/(\lambda_{1}-\lambda_{2}) & 0 & 0 \\
+  \lambda_{1}/(\lambda_{1}-\lambda_{2}) & 1/(\lambda_{2}-\lambda_{1}) & 0 & 0 \\
+  0 & 0 & 1 & 0 \\
+  0 & 0 & 0 & 1
+  \end{array}
+  \right].  
+\end{equation}
+
+\clearpage
+
 \section{Moment Equations in Commonly Used Coordinate Systems}
@@
 
+Number conservation equation
 \begin{equation}
   \pderiv{\cJ}{t}
-  +\f{1}{R}\pderiv{}{R}\Big(R\,\cH_{R}\Big)
-  +\pderiv{}{z}\Big(\cH_{z}\Big)
-  +\f{1}{R}\pderiv{}{\phi}\Big(\cH_{\phi}\Big)=0,
+  +\f{1}{R}\pderiv{}{R}\Big(R\,\cH^{1}\Big)
+  +\pderiv{\cH^{2}}{z}
+  +\pderiv{\cH^{3}}{\phi}=0,
 \end{equation}
+number flux equation ($R$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{R}\big)}{t}
-  +\f{1}{R}\pderiv{}{R}\Big(R\,\big(\rho\,v_{R}\,v_{R}+p\big)\Big)
-  +\pderiv{}{z}\Big(\rho\,v_{R}\,v_{z}\Big)
-  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{R}\,v_{\phi}\Big)
-  =\f{\big(\rho\,v_{\phi}^{2}+p\big)}{R},
+  \pderiv{\cH_{1}}{t}
+  +\f{1}{R}\pderiv{}{R}\Big(R\,\cK^{1}_{~1}\Big)
+  +\pderiv{\cK^{2}_{~1}}{z}
+  +\pderiv{\bcK^{3}_{~1}}{\phi}
+  =\f{\cK^{3}_{~3}}{R},
 \end{equation}
+number flux equation ($z$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{z}\big)}{t}
-  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{z}\,v_{R}\Big)
-  +\pderiv{}{z}\Big(\big(\rho\,v_{z}\,v_{z}+p\big)\Big)
-  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{z}\,v_{\phi}\Big)=0,
+  \pderiv{\cH_{2}}{t}
+  +\f{1}{R}\pderiv{}{R}\Big(R\,\cK^{1}_{~2}\Big)
+  +\pderiv{\cK^{2}_{~2}}{z}
+  +\pderiv{\cK^{3}_{~3}}{\phi}=0,
 \end{equation}
+and the number flux equation ($\phi$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{\phi}\big)}{t}
-  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{\phi}\,v_{R}\Big)
-  +\pderiv{}{z}\Big(\rho\,v_{\phi}\,v_{z}\Big)
-  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\,v_{\phi}+p\Big)
-  =-\f{\rho\,v_{\phi}\,v_{R}}{R},
+  \pderiv{\cH_{3}}{t}
+  +\f{1}{R}\pderiv{}{R}\Big(R\,\cK^{1}_{~3}\Big)
+  +\pderiv{\cK^{2}_{~2}}{z}
+  +\pderiv{\cK^{3}_{3}}{\phi}=0.
 \end{equation}
@@
 
+Number conservation equation
 \begin{equation}
-  \pderiv{\rho}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v_{r}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{\theta}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\Big)=0,
+  \pderiv{\cJ}{t}
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\cH^{1}\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\cH^{2}\Big)
+  +\pderiv{}{\phi}\Big(\cH^{3}\Big)=0,
 \end{equation}
+number flux equation ($r$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{r}\big)}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\big(\rho\,v_{r}\,v_{r}+p\big)\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{r}\,v_{\theta}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{r}\,v_{\phi}\Big)
-  =\rho\,\f{\big(v_{\theta}^{2}+v_{\phi}^{2}\big)}{r}+\f{2\,p}{r},
+  \pderiv{\cH_{1}}{t}
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\cK^{1}_{~1}\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\cK^{2}_{~1}\Big)
+  +\pderiv{\cK^{3}_{~1}}{\phi}
+  =\big(\cK^{2}_{~2}+\cK^{3}_{~3}\big)\f{1}{r},
 \end{equation}
+number flux equation ($\theta$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{\theta}\big)}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v_{\theta}\,v_{r}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\big(\rho\,v_{\theta}\,v_{\theta}+p\big)\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\theta}\,v_{\phi}\Big)
-  =\cot\theta\,\f{\big(\rho\,v_{\phi}^{2}+p\big)}{r}-\rho\,\f{v_{r}\,v_{\theta}}{r},
+  \pderiv{\cH_{2}}{t}
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\cK^{1}_{~2}\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\cK^{2}_{~2}\Big)
+  +\pderiv{\cK^{3}_{~2}}{\phi}
+  =\cK^{3}_{~3}\cot\theta,
 \end{equation}
+number flux equation ($\phi$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{\phi}\big)}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(\,r^{2}\,\rho\,v_{\phi}\,v_{r}\,\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{\phi}\,v_{\theta}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\,v_{\phi}+p\Big)
-  =-\rho\,v_{\phi}\,\f{\big(v_{r}+v_{\theta}\,\cot\theta\big)}{r},
+  \pderiv{\cH_{3}}{t}
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(\,r^{2}\,\cK^{1}_{~3}\,\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\cK^{2}_{~3}\,\Big)
+  +\pderiv{\cK^{3}_{~3}}{\phi}=0.
 \end{equation}

### 2017-01-09 Documents/Euler/dgEulerCurvilinear.tex
Updates to discretization document for Euler

@@
 \newcommand{\pbK}{\partial\mathbf{K}}
-\newcommand{\UDG}{\bU_{\mbox{\tiny DG}}}
 \newcommand{\sumx}{\sum_{i=1}^{d}}
@@
 which is sufficiently general to accommodate Cartesian, cylindrical, and spherical polar coordinates (see Table~\ref{tab:metricFunctions} and Appendix~\ref{app:CurvilinearEuler}).  
-Moreover, $\gamma$ is the determinant of the metric tensor, and $\sqrt{\gamma}=abc$.  
+Moreover, $\gamma$ is the determinant of the metric tensor; $\sqrt{\gamma}=\sqrt{\gamma_{11}\gamma_{22}\gamma_{33}}$.  
 The inverse of the spatial metric is denoted $\gamma^{ij}$, so that $\gamma^{ik}\gamma_{kj}=\delta^{i}_{~j}$.  
@@
   \begin{center}
-  \caption{Metric functions for Cartesian, Cylindrical, and Spherical coordinate systems.\label{tab:metricFunctions}}
-  \begin{tabular}{cccccccccccccc}
+  \caption{Relevant metric functions for Cartesian, Cylindrical, and Spherical coordinate systems.\label{tab:metricFunctions}}
+  \begin{tabular}{ccccccccccc}
     \midrule
-    Coordinates & $x^{1}$ & $x^{2}$ & $x^{3}$ & $\bar{w}^{1}$ & $\bar{w}^{2}$ & $\bar{w}^{3}$ & $a$ & $b$ & $c$ & $\sqrt{\gamma}$
-    & $\pderiv{a}{x^{1}}$ & $\pderiv{b}{x^{1}}$ & $\pderiv{c}{x^{2}}$ \\
+    Coordinates & $x^{1}$ & $x^{2}$ & $x^{3}$ & $\gamma_{11}$ & $\gamma_{22}$ & $\gamma_{33}$ & $\sqrt{\gamma}$
+    & $\f{1}{\gamma_{22}}\pderiv{\gamma_{22}}{x^{1}}$ & $\f{1}{\gamma_{33}}\pderiv{\gamma_{33}}{x^{1}}$ & $\f{1}{\gamma_{33}}\pderiv{\gamma_{33}}{x^{2}}$ \\
     \midrule
     \midrule
-    Cartesian & $x$ & $y$ & $z$ & $w_{x}$ & $w_{y}$ & $w_{z}$ & 1 & 1 & 1 & 1 & 0 & 0 & 0 \\
-    Cylindrical & $R$ & $z$ & $\phi$ & $w_{R}$ & $w_{z}$ & $w_{\phi}$ & 1 & $R$ & 1 & $R$ & 0 & 1 & 0 \\
-    Spherical & $r$ & $\theta$ & $\phi$ & $w_{r}$ & $w_{\theta}$ & $w_{\phi}$ & $r$ & $r$ & $\sin\theta$ & $r^{2}\sin\theta$ & 1 & 1 & $\cos\theta$ \\
+    Cartesian  & $x$ & $y$ & $z$ & 1 & 1 & 1 & 1 & 0 & 0 & 0 \\
+    Cylindrical & $R$ & $z$ & $\phi$ & 1 & 1 & $R^{2}$ & $R$ & 0 & $2/R$ & 0 \\
+    Spherical   & $r$ & $\theta$ & $\phi$ & 1 & $r^{2}$ & $r^{2}\sin^{2}\theta$ & $r^{2}\sin\theta$ & $2/r$ & $2/r$ & $2\cot\theta$ \\
     \midrule
@@
 
-We define the geometry sources (fictitious plus gravitational sources) in Eq.~\eqref{eq:momentumConservation} by
+We define the geometry sources in Eq.~\eqref{eq:momentumConservation} by
 \begin{equation}
@@
 \end{equation}
-Specifically, using the time-independent metric tensor in Eq.~\eqref{eq:threeMetric}, the components are
+Specifically, using the time-independent metric tensor in Eq.~\eqref{eq:threeMetric} and writing in terms of $P^{i}_{~j}$, the components are
 \begin{equation}
   G_{1}
-  =\f{1}{2}\,\Big(\,P^{22}\,\pderiv{\gamma_{22}}{x^{1}}+P^{33}\,\pderiv{\gamma_{33}}{x^{1}}\,\Big)-\rho\,\pderiv{\Phi}{x^{1}}, \quad
+  =\f{1}{2}\,\Big(\,P^{2}_{~2}\,\f{1}{\gamma_{22}}\pderiv{\gamma_{22}}{x^{1}}+P^{3}_{~3}\,\f{1}{\gamma_{33}}\pderiv{\gamma_{33}}{x^{1}}\,\Big)-\rho\,\pderiv{\Phi}{x^{1}}, \quad
   G_{2}
-  =\f{1}{2}\,P^{33}\,\pderiv{\gamma_{33}}{x^{2}}-\rho\,\pderiv{\Phi}{x^{2}}, \quad\text{and}\quad
+  =\f{1}{2}\,P^{3}_{~3}\,\f{1}{\gamma_{33}}\pderiv{\gamma_{33}}{x^{2}}-\rho\,\pderiv{\Phi}{x^{2}}, \quad\text{and}\quad
   G_{3}
@@
   \vect{F}^{i}(\bU)
-  =\big(\,\rho\,v^{i},\,P_{~1}^{i},\,P_{~2}^{i},\,P_{~3}^{i},\,(E+p)\,\bar{v}^{i},\,n_{e}\,\bar{v}^{i}\,\big)^{T},
+  =\big(\,\rho\,v^{i},\,P_{~1}^{i},\,P_{~2}^{i},\,P_{~3}^{i},\,(E+p)\,v^{i},\,n_{e}\,v^{i}\,\big)^{T},
 \end{equation}
@@
 
+In the DG method, the conserved quantities are approximated by a local expansion of the form
+\begin{equation}
+  \bU_{\DG}(\bx,t)
+  =\sum_{\bi=\vect{1}}^{\bN}\bU_{\bi}(t)\,\ell_{\bi}(\bx), 
+\end{equation}
+where basis functions $\ell_{\bi}(\bx)$, which we will take to be polynomials, belong to a function space denoted $\bbV^{k}$ and have local support in a computational cell or element denoted by $\bK$.
+
+Several books and review articles on the DG method are now available \citep[see, e.g.,][]{cockburnShu_2001,hesthavenWarburton_2008}, and we will not go into too much detail here.  
+However, we review some key concepts to introduce notation, and emphasize specific choices in our implementation.
+
 \subsection{Basic Principles of the DG Method}
 
-We divide the computational domain $D$ into a disjoint union $\mathcal{T}$ of open elements $\bK$, so that $D = \cup_{\bK \in \mathcal{T}}\bK$.  
+We divide the computational domain $D$ into a disjoint union $\mathcal{T}$ of open elements $\bK$, so that $D = \cup_{\bK \in \cT}\bK$.  
 We require that each element is a box in the logical coordinates; i.e.,
@@
 We also define $\bx=\{\tilde{\bx}^{i},x^{i}\}$ and $\dx^{i}=\xH^{i}-\xL^{i}$.
-Here we let the approximation space for the DG method, $\mathbb{V}^{k}$, to be constructed from tensor products of one-dimensional polynomials of maximal degree $k$.  
+
+We let the approximation space for the DG method, $\mathbb{V}^{k}$, to be constructed from the tensor product of one-dimensional polynomials of maximal degree $k$.  
 Note that functions in $\mathbb{V}^{k}$ can be discontinuous across element interfaces.  
-
-The semi-discrete DG problem is to find $\UDG\in\mathbb{V}^{k}$ (which approximates $\bU$) such that
+The semi-discrete DG problem is to find $\bU_{\DG}\in\mathbb{V}^{k}$ (which approximates $\bU$) such that
 \begin{align}
-  &\partial_{t}\int_{\bK}\UDG\,v\,dV
-  +\sumx\int_{\pbK^{i}}\big(\,v\,\widehat{\vect{F}}^{i}(\UDG)\,dA^{i}\big|_{\xH^{i}}-v\,\widehat{\vect{F}}^{i}(\UDG)\,dA^{i}\big|_{\xL^{i}}\,\big) \nonumber \\
+  &\partial_{t}\int_{\bK}\bU_{\DG}\,v\,dV
+  +\sumx\int_{\pbK^{i}}\big(\,\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\bU_{\DG})\,v\big|_{\xH^{i}}-\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\bU_{\DG})\,v\big|_{\xL^{i}}\,\big)\,\tilde{\bx}^{i} \nonumber \\
   &\hspace{24pt}
-  -\sumx\int_{\bK}\vect{F}^{i}(\UDG)\,\nabla_{i}v\,dV
-  =\int_{\bK}\vect{S}(\UDG)\,v\,dV
+  -\sumx\int_{\bK}\vect{F}^{i}(\bU_{\DG})\,\pderiv{v}{x^{i}}\,dV
+  =\int_{\bK}\bG(\bU_{\DG})\,v\,dV
   \label{eq:semidiscreteDG}
@@
 for all $v\in\mathbb{V}^{k}$ and all $\bK\in\mathcal{T}$.
-Here, $dV=abc\,dx^{1}\,dx^{2}\,dx^{3}$, the area elements are given by
+
+To connect the elements in Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\bF}^{i}(\bU_{\DG})$ is a numerical flux approximating the flux on the $i$th surface of $\bK$.  
+For this purpose we define the numerical flux function $\vect{f}^{i}$, which evaluates the numerical flux given values from both sides of an element interface; i.e.,
 \begin{equation}
-  dA^{1}=abc\,dx^{2}\,dx^{3}=\tau^{1}\,dx^{2}\,dx^{3}, \quad
-  dA^{2}=bc\,dx^{1}\,dx^{3}=\tau^{2}\,dx^{1}\,dx^{3}, \quad
-  dA^{3}=a\,dx^{1}\,dx^{2}=\tau^{3}\,dx^{1}\,dx^{2}, 
+  \widehat{\bF}^{i}(\bU_{\DG})=\vect{f}^{i}(\bU_{\DG}(x^{i,-},\tilde{\bx}^{i}),\bU_{\DG}(x^{i,+},\tilde{\bx}^{i})),
 \end{equation}
-and the gradient operator is $\nabla_{i}=e^{j}_{~i}\pderiv{}{x^{j}}$.
+where superscripts $-/+$, e.g., in the arguments of $\bU_{\DG}(x^{i,-/+},\tilde{\bx}^{i})$, indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
+For example, the simple Lax-Friedrichs flux is given by
+\begin{equation}
+  \vect{f}^{i}(\bU^{-},\bU^{+})
+  =\f{1}{2}\,\big(\,\bF^{i}(\bU^{-})+\bF^{i}(\bU^{+})-\alpha^{i}\,(\,\bU^{+}-\bU^{-}\,)\,\big),
+\end{equation}
+where $\alpha^{i}=||\mbox{eig}\big(\partial\bF^{i}/\partial\bU\big)||_{\infty}$ is the largest eigenvalue of the flux jacobian.
 
-\ee{Write more about Riemann solvers here.}
-In \eqref{eq:semidiscreteDG}, $\vect{\widehat{F}}^{i}(\UDG)$ is a numerical flux approximating the flux on the $i$th surface of $\bK$.  
-We also define the numerical flux function $\vect{\mathcal{F}}^{i}$, which for any $v\in\mathbb{V}^{k}$ is written as
-\begin{equation}
-  \vect{\widehat{F}}^{i}(v)=\vect{\mathcal{F}}^{i}(v(x^{i,-},\tilde{\bx}^{i}),v(x^{i,+},\tilde{\bx}^{i})),
-\end{equation}
-where superscripts $-/+$, e.g., in the arguments of $v(x^{i,-/+},\tilde{\bx}^{i})$, indicate that the function is evaluated to the immediate left/right of $x^{i}$.
-
-The approximation space $\mathbb{V}^{k}$ contains the constant functions, and the choice $v=1$ in \eqref{eq:semidiscreteDG} gives
+The approximation space $\mathbb{V}^{k}$ contains the constant functions, and the choice $v=1$ in Eq.~\eqref{eq:semidiscreteDG} gives
 \begin{equation}
   \partial_{t}\bU_{\bK}
-  +\f{1}{V_{\bK}}\sumx\int_{\pbK^{i}}\big(\,\widehat{\vect{F}}^{i}(\UDG)\,dA^{i}\big|_{\xH^{i}}-\widehat{\vect{F}}^{i}(\UDG)\,dA^{i}\big|_{\xL^{i}}\,\big)
-  =\bS_{\bK},
+  +\f{1}{V_{\bK}}\sumx\int_{\pbK^{i}}\big(\,\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\bU_{\DG})\big|_{\xH^{i}}-\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\bU_{\DG})\big|_{\xL^{i}}\,\big)\,d\tilde{\bx}^{i}
+  =\bG_{\bK},
 \end{equation}
@@
 \begin{equation}
-  \bU_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\UDG\,dV \quad\text{and}\quad
-  \bS_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\vect{S}(\UDG)\,dV.  
+  \bU_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\bU_{\DG}\,dV \quad\text{and}\quad
+  \bG_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\bG(\bU_{\DG})\,dV.  
 \end{equation}
-Here we use explicit, SSP-RK time integrators, which are convex combinations of forward Euler time steps \citep{gottlieb_etal_2001}.  
-Thus, without loss of generality, we consider here only a forward Euler time step for $\bU_{\bK}$; i.e., 
-\begin{equation}
-  \bU_{\bK}^{n+1}=\bU_{\bK}^{n}
-  =-\f{\dt}{V_{\bK}}\sumx\int_{\pbK^{i}}\big(\,\widehat{\vect{F}}^{i}(\UDG^{n})\,dA^{i}\big|_{\xH^{i}}-\widehat{\vect{F}}^{i}(\UDG^{n})\,dA^{i}\big|_{\xL^{i}}\,\big)
-  +\vect{S}_{\bK}^{n},
-\end{equation}
-where $\dt=t^{n+1}-t^{n}$ is the time step.
+This illustrates how the cell average (similar to finite volume methods) is evolved in the DG method.
 
 \subsection{Further Details on the DG Discretization of the Euler Equations}
+
+Here we provide further details on the DG method in order to arrive at the equations that are actually implemented in our code.  
+We start by introducing some notation, defining the polynomial expansion for $\bcM_{\DG}$, and the quadrature rules used to evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}.  
+Then, using these rules, we provide explicit expressions for each of the terms in Equation~\eqref{eq:semidiscreteDG}.
 
@@
 where $\ell_{\bi}(\bx)\in\bbQ^{k}$ are basis functions.  
-(Specifically, we use Lagrange polynomials $\ell_{i}(x)$ to construct the multidimensional representation.)  
+Specifically, we use one-dimensional Lagrange polynomials $\ell_{i}(x)$ to construct the multidimensional representation, where
+\begin{equation}
+  \ell_{i}(\eta)=
+  \prod_{\substack{j=1\\j\ne i}}^{N}\f{\eta-\eta_{j}}{\eta_{i}-\eta_{j}}.  
+\end{equation}
 Moreover $\bi=\{i_{1},\ldots,i_{d}\}$ is a multi-index, and $\ell_{\bi}(\bx)=\prod_{k=1}^{d}\ell_{i_{k}}(x^{k})$.  
@@
 
-\section{Euler Equations in Commonly Used Curvilinear Coordinates}
+\section{Euler Equations in Commonly Used Coordinate Systems}
 \label{app:CurvilinearEuler}
@@
 
+Mass conservation equation
 \begin{equation}
   \pderiv{\rho}{t}
-  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{R}\Big)
-  +\pderiv{}{z}\Big(\rho\,v_{z}\Big)
-  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\Big)=0,
+  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v^{1}\Big)
+  +\pderiv{}{z}\Big(\rho\,v^{2}\Big)
+  +\pderiv{}{\phi}\Big(\rho\,v^{3}\Big)=0,
 \end{equation}
+momentum conservation equation ($R$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{R}\big)}{t}
-  +\f{1}{R}\pderiv{}{R}\Big(R\,\big(\rho\,v_{R}\,v_{R}+p\big)\Big)
-  +\pderiv{}{z}\Big(\rho\,v_{R}\,v_{z}\Big)
-  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{R}\,v_{\phi}\Big)
-  =\f{\big(\rho\,v_{\phi}^{2}+p\big)}{R},
+  \pderiv{\big(\rho\,v_{1}\big)}{t}
+  +\f{1}{R}\pderiv{}{R}\Big(R\,\big(\rho\,v_{1}\,v^{1}+p\big)\Big)
+  +\pderiv{}{z}\Big(\rho\,v_{1}\,v^{2}\Big)
+  +\pderiv{}{\phi}\Big(\rho\,v_{1}\,v^{3}\Big)
+  =\f{\big(\rho\,v_{3}\,v^{3}+p\big)}{R}-\rho\pderiv{\Phi}{R},
 \end{equation}
+momentum conservation equation ($z$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{z}\big)}{t}
-  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{z}\,v_{R}\Big)
-  +\pderiv{}{z}\Big(\big(\rho\,v_{z}\,v_{z}+p\big)\Big)
-  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{z}\,v_{\phi}\Big)=0,
+  \pderiv{\big(\rho\,v_{2}\big)}{t}
+  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{2}\,v^{1}\Big)
+  +\pderiv{}{z}\Big(\rho\,v_{2}\,v^{2}+p\Big)
+  +\pderiv{}{\phi}\Big(\rho\,v_{2}\,v^{3}\Big)=-\rho\pderiv{\Phi}{z},
 \end{equation}
+momentum conservation equation ($\phi$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{\phi}\big)}{t}
-  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{\phi}\,v_{R}\Big)
-  +\pderiv{}{z}\Big(\rho\,v_{\phi}\,v_{z}\Big)
-  +\f{1}{R}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\,v_{\phi}+p\Big)
-  =-\f{\rho\,v_{\phi}\,v_{R}}{R},
+  \pderiv{\big(\rho\,v_{3}\big)}{t}
+  +\f{1}{R}\pderiv{}{R}\Big(R\,\rho\,v_{3}\,v^{1}\Big)
+  +\pderiv{}{z}\Big(\rho\,v_{3}\,v^{2}\Big)
+  +\pderiv{}{\phi}\Big(\rho\,v_{3}\,v^{3}+p\Big)
+  =-\rho\pderiv{\Phi}{\phi},
 \end{equation}
+energy equation
 \begin{equation}
-  \pderiv{E}{t}+\f{1}{R}\pderiv{}{R}\Big(\,R\,\big(E+p\big)\,v_{R}\,\Big)+\pderiv{}{z}\Big(\,\big(E+p\big)\,v_{z}\,\Big)+\f{1}{R}\pderiv{}{\phi}\Big(\,\big(E+p\big)\,v_{\phi}\,\Big)=0.
+  \pderiv{E}{t}+\f{1}{R}\pderiv{}{R}\Big(\,R\,\big(E+p\big)\,v^{1}\,\Big)+\pderiv{}{z}\Big(\,\big(E+p\big)\,v^{2}\,\Big)+\pderiv{}{\phi}\Big(\,\big(E+p\big)\,v^{3}\,\Big)=-\rho\,v^{i}\pderiv{\Phi}{x^{i}},
 \end{equation}
+electron conservation equation
 \begin{equation}
   \pderiv{n_{e}}{t}
-  +\f{1}{R}\pderiv{}{R}\Big(R\,n_{e}\,v_{R}\Big)
-  +\pderiv{}{z}\Big(n_{e}\,v_{z}\Big)
-  +\f{1}{R}\pderiv{}{\phi}\Big(n_{e}\,v_{\phi}\Big)=0,
+  +\f{1}{R}\pderiv{}{R}\Big(R\,n_{e}\,v^{1}\Big)
+  +\pderiv{}{z}\Big(n_{e}\,v^{2}\Big)
+  +\pderiv{}{\phi}\Big(n_{e}\,v^{3}\Big)=0.  
 \end{equation}
@@
 
+Mass conservation equation
 \begin{equation}
   \pderiv{\rho}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v_{r}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{\theta}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\Big)=0,
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v^{1}\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v^{2}\Big)
+  +\pderiv{}{\phi}\Big(\rho\,v^{3}\Big)=0,
 \end{equation}
+momentum conservation equation ($r$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{r}\big)}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\big(\rho\,v_{r}\,v_{r}+p\big)\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{r}\,v_{\theta}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{r}\,v_{\phi}\Big)
-  =\rho\,\f{\big(v_{\theta}^{2}+v_{\phi}^{2}\big)}{r}+\f{2\,p}{r},
+  \pderiv{\big(\rho\,v_{1}\big)}{t}
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\big(\rho\,v_{1}\,v^{1}+p\big)\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{1}\,v^{2}\Big)
+  +\pderiv{}{\phi}\Big(\rho\,v_{1}\,v^{3}\Big)
+  =\f{\rho(v_{2}v^{2}+v_{3}v^{3})+2p}{r}-\rho\pderiv{\Phi}{r},
 \end{equation}
+momentum conservation equation ($\theta$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{\theta}\big)}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v_{\theta}\,v_{r}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\big(\rho\,v_{\theta}\,v_{\theta}+p\big)\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\theta}\,v_{\phi}\Big)
-  =\cot\theta\,\f{\big(\rho\,v_{\phi}^{2}+p\big)}{r}-\rho\,\f{v_{r}\,v_{\theta}}{r},
+  \pderiv{\big(\rho\,v_{2}\big)}{t}
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\rho\,v_{2}\,v^{1}\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\big(\rho\,v_{2}\,v^{2}+p\big)\Big)
+  +\pderiv{}{\phi}\Big(\rho\,v_{2}\,v^{3}\Big)
+  =\big(\rho\,v_{3}v^{3}+p\big)\cot\theta-\rho\pderiv{\Phi}{\theta},
 \end{equation}
+momentum conservation equation ($\phi$-component)
 \begin{equation}
-  \pderiv{\big(\rho\,v_{\phi}\big)}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(\,r^{2}\,\rho\,v_{\phi}\,v_{r}\,\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{\phi}\,v_{\theta}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\rho\,v_{\phi}\,v_{\phi}+p\Big)
-  =-\rho\,v_{\phi}\,\f{\big(v_{r}+v_{\theta}\,\cot\theta\big)}{r},
+  \pderiv{\big(\rho\,v_{3}\big)}{t}
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(\,r^{2}\,\rho\,v_{3}\,v^{1}\,\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\rho\,v_{3}\,v^{2}\Big)
+  +\pderiv{}{\phi}\Big(\rho\,v_{3}\,v^{3}+p\Big)
+  =-\rho\pderiv{\Phi}{\phi},
 \end{equation}
+energy equation
 \begin{equation}
   \pderiv{E}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\big(E+p\big)\,v_{r}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\big(E+p\big)\,v_{\theta}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(\big(E+p\big)\,v_{\phi}\Big)=0.
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,\big(E+p\big)\,v^{1}\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,\big(E+p\big)\,v^{2}\Big)
+  +\pderiv{}{\phi}\Big(\big(E+p\big)\,v^{3}\Big)=-\rho\,v^{i}\pderiv{\Phi}{x^{i}},
 \end{equation}
-
+electron conservation equation
 \begin{equation}
   \pderiv{n_{e}}{t}
-  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,n_{e}\,v_{r}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,n_{e}\,v_{\theta}\Big)
-  +\f{1}{r\sin\theta}\pderiv{}{\phi}\Big(n_{e}\,v_{\phi}\Big)=0,
+  +\f{1}{r^{2}}\pderiv{}{r}\Big(r^{2}\,n_{e}\,v^{1}\Big)
+  +\f{1}{\sin\theta}\pderiv{}{\theta}\Big(\sin\theta\,n_{e}\,v^{2}\Big)
+  +\pderiv{}{\phi}\Big(n_{e}\,v^{3}\Big)=0.  
 \end{equation}

### 2017-01-27 Documents/M1/dgM1Curvilinear.tex
Additions to the text.  Figures for Homogeneous sphere and Riemann problem

@@
 
+For time integration we employ the method lines.  
+Having specified the spatial discretization for the advection terms, we consider the discretized moment equations in Eq.~\eqref{eq:semidiscreteDiscretized} as a system of ordinary differential equations (ODEs) to evolve forward in time, and write
+\begin{equation}
+  d_{t}\bcM_{\bk}
+  =\bcF_{\bx}(\bcM)_{\bk}+\bcC(\bcM)_{\bk},
+  \label{eq:momentEquationsODEs}
+\end{equation}
+where the operator $\bcF_{\bx}:\bbR^{d+1}\to\bbR^{d+1}$ represents the discretization of the spatial divergence operator.
+
 \clearpage
@@
 
+When solving the moment equations, we need to prevent non-physical states from developing.  
+In particular, from the definition of the moments in Eq.~\eqref{eq:angularMoments}, it is easy to show that a positive distribution function implies a positive density $\cJ>0$ and a limited flux density $\cJ-|\bcH|>0$.
+Failure in maintaining these bounds can lead to an ill-posed closure problem and loss of hyperbolicity for the moment equations.
+
+\section{Neutrino Opacities}
+
 \clearpage
@@
   \psi(h)=\f{1}{3}\big(\,5-2\,\sqrt{4-3\,h^{2}}\,\big).  
+  \label{eq:eddingtonFactorLevermore}
 \end{equation}
@@
   \right.
+  \label{eq:riemannProblem}
 \end{equation}
+Results for $t=0.1$ are shown in Figure~\ref{fig:riemannProblem}.  
+The discontinuities remain sharp, and oscillations around the discontinuities are controlled (in part due to limiting of characteristic variables; cf. Section~\ref{sec:slopeLimiters}).
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[scale=0.5]{./Figures/RiemannProblem1D}
+  \end{center}
+  \caption{Results from the one-dimensional Riemann problem in Eq.~\eqref{eq:riemannProblem}, obtained with the DG(2)+RK3 method using $240$ elements, the HLL Riemann solver, and the Eddington factor in Eq.~\eqref{eq:eddingtonFactorLevermore}.
+  The number density $\cJ$ (black) and the number flux density $\cH_{r}$ (red) are plotted for $t=0.1$.}
+  \label{fig:riemannProblem}
+\end{figure}
 
@@
 \subsection{Homogeneous Sphere}
+
+The homogeneous sphere test \citep[cf.][]{smit_etal_1997} considers of a sphere with radius $R$.  
+Inside the sphere ($r<R$), the absorption opacity and equilibrium distribution function are set to constant values $\chi=\chi_{0}$ and $f_{0}=1$, respectively.  
+Outside the sphere, the absorption opacity is zero.  
+The steady state solution, obtained by solving the transport equation in spherical symetry, is given by
+\begin{equation}
+  f_{\mbox{\tiny A}}(r,\mu)=f_{0}\,\big(1-e^{-\chi_{0}\,s(r,\mu)}\big),
+  \label{distributionHomogeneousSphere}
+\end{equation}
+where
+\begin{equation}
+  s(r,\mu)
+  =\left\{
+  \begin{array}{lll}
+    r\,\mu+R\,g(r,\mu) & \mbox{if}\quad r<R, & \mu\in[-1,+1], \\
+    2\,R\,g(r,\mu) & \mbox{if}\quad r \ge R, & \mu\in[(1-(R/r)^{2})^{1/2},+1], \\
+    0 & \mbox{otherwise},
+  \end{array}
+  \right.
+\end{equation}
+and $g(r,\mu)=[1-(r/R)^{2}(1-\mu^{2})]^{1/2}$.
+
+Similar to \citet{oConnor_2015}, we solve two versions of this test.  
+One where the absorption opacity is set to $\chi_{0}=10^{-4}$~cm$^{-1}$ (thick; similar to the electron capture opacity encountered in the center of a collapsed stellar core), and one where the absorption opacity is set to $\chi_{0}=10^{-6}$~cm$^{-1}$ (thin).
+Both simulations are run with a computational domain with $r\in[0,500]$~km using 100 uniform elements $\Delta r=5$~km.  
+Thus, in the thick case, the Knudsen number is small, $\mbox{Kn}=(\chi_{0}\,\Delta r)^{-1}=0.02$, while it exceeds unity in the thin case, $\mbox{Kn}=2$.  
+The radius of the sphere is set to $R=100$~km.
+
+Results are plotted in Figure~\ref{fig:homogeneousSphere1D}.
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-4_Density} &
+      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-6_Density} \\
+      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-4_FluxFactor} &
+      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-6_FluxFactor} \\
+      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-4_EddingtonFactor} &
+      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-6_EddingtonFactor}
+    \end{tabular}
+  \end{center}
+  \caption{Results from solving the Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ elements.  
+  In the left panels, the absorption opacity is set to $\chi_{0}=10^{-4}$~cm$^{-1}$, while in the right panels it is set to $\chi_{0}=10^{-6}$~cm$^{-1}$.  
+  The numerical results (dashed lines) are compared to the analytical solution (solid lines).}
+  \label{fig:homogeneousSphere1D}
+\end{figure}
+
+\subsection{Milne's Problem}
+
+\section{Mini-app: Transport Problems with Tabulated Neutrino Opacities}
 

### 2017-01-30 Documents/Euler/Benchmarks1D/draft.tex
updated document

@@
 Several tests were used to assess the accuracy of the integration method \cite{LiskaWendroff2003}. 
-\begin{table}
+\begin{table}[h!]
 \begin{center}
@@
  9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
-10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & ? \\
-11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & ? \\
+10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
+11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
  \hline
@@
 Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right \cite{LiskaWendroff2003}.
-
+%\clearpage
 \subsection{Test 1: Sod's Shock Tube}
@@
 Between the two endpoints, 128, 256, 512, and 1024 points were computed for on each respective test.
-Figures~\ref{fig:dencellcomp_20}--\ref{fig:velcellcomp_20} show results of these tests:
-\begin{figure}
+Figures~\ref{fig:dencellcomp_20}--\ref{fig:pvcellcomp} show results of these tests:
+\begin{figure}[h!]
   \begin{center}
@@
   \caption{pressure and velocity}
+  \label{fig:pvcellcomp}
 \end{figure}
@@
 
-\begin{figure}[h]
-  \begin{center}
-	\begin{tabular}{cc}
-      \includegraphics[width=.4\textwidth]{den_T9.png} &
-	  \includegraphics[width=.4\textwidth]{denT9zoom.png} \\
-	  \includegraphics[width=.4\textwidth]{prs_T9.png} &	
-      \includegraphics[width=.4\textwidth]{vel_T9.png}\\
-	\end{tabular}	
-  \end{center}
-  \caption{}
-\end{figure}
+%\begin{figure}[h]
+ % \begin{center}
+	%\begin{tabular}{cc}
+     % \includegraphics[width=.4\textwidth]{den_T9.png} &
+	  %\includegraphics[width=.4\textwidth]{denT9zoom.png} \\
+	  %\includegraphics[width=.4\textwidth]{prs_T9.png} &	
+      %\includegraphics[width=.4\textwidth]{vel_T9.png}\\
+	%\end{tabular}	
+  %\end{center}
+ % \caption{}
+%\end{figure}
 
@@
   \end{center}
-  \caption{}
+  \caption{density, pressure, and velocity}
 \end{figure}
@@
 
+\clearpage
+
+\subsection{Test 13: Shock Entropy Waves}
+
+This test was first run with 1000 cells to see the solution with high resolution.
+Subsequent tests all had 200 cells, with various values of the beta parameter.
+Again, the 3rd order, 1000 cell solution is called ``exact.''
+
+\begin{figure}[h]
+  \begin{center}
+     \includegraphics[width=.78\textwidth]{1000.png}	
+  \end{center}
+  \caption{density, 1000 cells}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+	\begin{tabular}{cc}
+      \includegraphics[width=.425\textwidth]{10.png} &
+	  \includegraphics[width=.425\textwidth]{10zoom.png}
+	\end{tabular}
+  \end{center}
+  \caption{density, beta=10}
+  \label{fig:pvcellcomp}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+	\begin{tabular}{cc}
+      \includegraphics[width=.425\textwidth]{50.png} &
+	  \includegraphics[width=.425\textwidth]{50zoom.png}
+	\end{tabular}
+  \end{center}
+  \caption{density, beta=50}
+  \label{fig:pvcellcomp}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+	\begin{tabular}{cc}
+      \includegraphics[width=.425\textwidth]{300.png} &
+	  \includegraphics[width=.425\textwidth]{300zoom.png}
+	\end{tabular}
+  \end{center}
+  \caption{density, beta=300}
+  \label{fig:pvcellcomp}
+\end{figure}
+
 \bibliographystyle{siam}

### 2017-01-30 Documents/Euler/Benchmarks1D/draft.tex
New style file for document + text in the introduction.

@@
-\documentclass[letterpaper,12pt]{article}
+\documentclass[10pt,preprint]{aastex}
+
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{booktabs}
+\usepackage{mathrsfs}
+\usepackage{cite}
+\usepackage{times}
+\usepackage{url}
+\usepackage{hyperref}
+\usepackage{lineno}
+\usepackage{yhmath}
+\usepackage{natbib}
+\hypersetup{
+  bookmarksnumbered = true,
+  bookmarksopen=false,
+  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
+  pdffitwindow=true,      % window fit to page when opened
+  pdfnewwindow=true, % links in new window
+  colorlinks=true,           % false: boxed links; true: colored links
+  linkcolor=blue,            % color of internal links
+  citecolor=magenta,    % color of links to bibliography
+  filecolor=magenta,     % color of file links
+  urlcolor=cyan              % color of external links
+}
 \usepackage{graphicx}
-%\extrafloats{100}%
 \graphicspath{ {figures/} }
-\author{Juliana Pulsinelli}
-\title{Benchmarking of the Non-Relativistic Hydrodynamics Alogorithms in thornado}
+
+\newcommand{\thornado}{\texttt{thornado}}
+
 \begin{document}
-\maketitle
+
+\title{Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado}
+\author{Juliana Pulsinelli\altaffilmark{1} and Eirik Endeve\altaffilmark{2}}
+
+\altaffiltext{1}{Insert Juliana's affiliation and email}
+\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
+
 \begin{abstract}
+\thornado\ is a new astrophysical code for radiation-hydrodynamics based on high-order Runge-Kutta Discontinuous Galerkin (RKDG) methods.  
+It currently solves the Euler equations for fluid dynamics and the two-moment ($M_{1}$) approximation of the radiative transfer equation. 
+In this document, we benchmark the algorithms for solving the Euler equations.  
+An extensive set of one-dimensional Riemann problems with known exact solutions were run, and the \thornado\ results were graphed and compared to exact solutions in cases where they exist. 
+\end{abstract}
 
-The thornado project is astrophysical code based on the Euler equations for fluid dynamics.
-In this project, the algorithms were benchmarked for accuracy.
-A group of one-dimensional Riemann problems with known exact solutions were run, and the thornado results were graphed and compared to the exact solutions.
+\tableofcontents
 
-\end{abstract}
 \section{Introduction}
+
 Astrophysical fluid dynamics models the movement of fluids in space. It yields very different solutions from terrestrial fluid dynamics, as the effect of gravity is reduced or removed. 
@@
 
-In this project, algorithms solving the Euler equations for fluid dynamics were tested using a variety of tests. The Euler equations for fluid dynamics are \cite{ZhangShu2010}:
+\section{Equations and Numerical Method}
 
+In this project, numerical algorithms for solving the Euler equations of fluid dynamics are tested against an extensive suite of standard problems taken from the literature.  
+In the following subsections we briefly describe the equations and the numerical methods used.
+
+\subsection{Euler Equations of Gas Dynamics}
+
+The Euler equations for fluid dynamics \citep[see, e.g.,][for details]{Leveque2002} consists of the mass equation
 \begin{equation}
   \frac{\partial \rho}{\partial t}  
-	+ \frac{\partial}{\partial x} \Big(\rho u\Big) = 0
+  + \frac{\partial}{\partial x} \Big(\rho u\Big) = 0,
+  \label{eq:massConservation}
 \end{equation}
-
+the momentum equation
 \begin{equation}
   \frac{\partial}{\partial t} \Big(\rho u\Big)
-	+ \frac{\partial}{\partial x} \Big(\rho u^2 + p\Big) = 0
+  + \frac{\partial}{\partial x} \Big(\rho u^2 + p\Big) = 0,
+  \label{eq:momentumConservation}
 \end{equation}
-
+and the energy equation
 \begin{equation}
   \frac{\partial E}{\partial t}
-	+ \frac{\partial}{\partial x} \Big((E + p) u\Big) = 0
+  + \frac{\partial}{\partial x} \Big((E + p) u\Big) = 0.  
+  \label{eq:energyConservation}
 \end{equation}
-
+where $\rho$ represents mass density, $u$ the fluid velocity, $p$ the pressure of the fluid, and $E$ the energy.  
+Equation~\eqref{eq:massConservation} describes conservation of mass, Equation~\eqref{eq:momentumConservation} describes conservation of momentum, and equation \eqref{eq:energyConservation} describes conservation of energy.
+The equation of state
 \begin{equation}
@@
   \Big(E - \frac{1}{2} \rho u^2 \Big)
+  \label{eq:eos}
+\end{equation}
+closes the system of equations, and links the pressure to the quantities evolved in Equations \eqref{eq:massConservation}-\eqref{eq:energyConservation}. 
+The ratio of specific heats, $\gamma$, is taken to be a constant.
+
+By defining the vector of conserved variables $\boldsymbol{U}=(\rho,\rho u,E)^{T}$ and the vector of fluxes $\boldsymbol{F}(\boldsymbol{U})=(\rho u,\rho u^{2}+p,(E+p)u)^{T}$ we write the Euler equations as system of conservation laws
+\begin{equation}
+  \partial_{t}\boldsymbol{U}
+  +\partial_{x}\boldsymbol{F}(\boldsymbol{U})
+  =0.
 \end{equation}
 
-where $\rho$ represents mass density, u represents fluid velocity, p represents pressure of the fluid, and E represents energy. 
-Equation 1 represents conservation of mass, equation 2 represents conservation of momentum, and equation 3 represents conservation of energy.
-Equation 4 is the equation of state, which links the other three equations.
+\subsection{Runge-Kutta Discontinuous Galerkin Methods}
+
+In the Runge-Kutta Discontinuous Galerkin \citep[RKDG;][]{cockburnShu_2001} method the solution to the Euler equations is approximated by a polynomial expansion of the form
+\begin{equation}
+  \boldsymbol{U}(x,t)
+  \approx\boldsymbol{U}_{h}(x,t)=\sum_{j=0}^{k}\boldsymbol{C}_{j}(t)\,\phi_{j}(x),
+\end{equation}
+where $\{\phi_{j}(x)\}_{j=0}^{k}$ are polynomials of degree at most $k$ and .
+
+\section{Numerical Experiments}
 
@@
 The conditions of each cell are advanced forward for all space cells, one time step at a time, according to the Euler equations for fluid dynamics.
-\cite{Leveque2002}
+\citep{Leveque2002}
 
@@
 
-\section{Numerical Experiments}
-Several tests were used to assess the accuracy of the integration method \cite{LiskaWendroff2003}. 
+Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
 \begin{table}[h!]
@@
  3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
- 4 & 1 & 1 & $10^-6$ & 1 & -1 & $10^-6$ & 0.5 & 1 \\
+ 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
  5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
@@
 $x_0$ refers to the position of the barrier.
-The computational domain is 0.0 to 1.0 in tests 1--8, 0.1 to 0.6 in test 9 \cite{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \cite{Leveque2002}.
+The computational domain is 0.0 to 1.0 in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2002}.
 
@@
 At all positions, initial density is 1 and initial velocity is 0.
-Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right \cite{LiskaWendroff2003}.
+Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right \citep{LiskaWendroff2003}.
 %\clearpage
@@
 
-\bibliographystyle{siam}
+\bibliographystyle{apj}
 \bibliography{references.bib}

### 2017-01-30 Documents/Euler/Benchmarks1D/draft.tex
Captions for Sod figures.

@@
   \end{center}
-  \caption{density}
+  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with the first-order method using different number of elements: 128 (solid red), 256 (dashed green), 512 (dotted blue), and 1024 (dash-dot pink).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted cyan line.}
   \label{fig:dencellcomp_20}
@@
     \begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{prscellcomp_20} &
-	  \includegraphics[width=.425\textwidth]{velcellcomp_20}
+      \includegraphics[width=.475\textwidth]{velcellcomp_20} &
+      \includegraphics[width=.475\textwidth]{prscellcomp_20}
     \end{tabular}
   \end{center}
-  \caption{pressure and velocity}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:dencellcomp_20}:
+  velocity (left panel) and pressure (right panel).}
   \label{fig:pvcellcomp}

### 2017-01-31 Documents/Euler/Benchmarks1D/draft.tex
Added some text on DG

@@
 
-In the Runge-Kutta Discontinuous Galerkin \citep[RKDG;][]{cockburnShu_2001} method the solution to the Euler equations is approximated by a polynomial expansion of the form
+In the Runge-Kutta Discontinuous Galerkin \citep[RKDG; cf.][]{cockburnShu_2001} method the solution to the Euler equations is approximated by a local polynomial expansion of the form
 \begin{equation}
@@
 \end{equation}
-where $\{\phi_{j}(x)\}_{j=0}^{k}$ are polynomials of degree at most $k$ and .
+where $\{\phi_{j}(x)\}_{j=0}^{k}$ are polynomials of degree at most $k$ and $\boldsymbol{C}_{j}$ are expansion the coefficients to be solved for.  
+In \thornado, $\phi_{j}(x)$ are given by Lagrange polynomials.
+
+The computational domain $D=\{x:x\in[x_{\mbox{\tiny L}},x_{\mbox{\tiny R}}]\}$ is subdivided into $N$ elements $I_{i}=\{x:x\in(x_{i-1/2},x_{i+1/2})\}$.  
+The width of element $I_{i}$ is then $\Delta x_{i}=x_{i+1/2}-x_{i-1/2}$.  
+The semi-discrete DG method is then to find $\boldsymbol{U}_{h}$ such that
+\begin{equation}
+  \partial_{t}\int_{I_{i}}\boldsymbol{U}_{h}\,\phi_{j}\,dx
+  +\big(\widehat{\boldsymbol{F}}\,\phi_{j}|_{i+1/2}-\widehat{\boldsymbol{F}}\,\phi_{j}|_{i-1/2}\big)
+  -\int_{I_{i}}\boldsymbol{F}(\boldsymbol{U}_{h})\,\partial_{x}\phi_{j}\,dx=0
+  \label{eq:semidiscreteDG}
+\end{equation}
+for all $\phi_{j}$ and all $I_{i}\in D$.  
+In Equation~\eqref{eq:semidiscreteDG}, $\widehat{\boldsymbol{F}}_{i\pm1/2}$ is a numerical flux approximating the flux across the interfaces connecting neighboring elements.  
+In \thornado, we have implemented the Local Lax-Friedrichs (LLF), the Harten-Lax-van Leer (HLL), and the HLLC Riemann solvers, but in the numerical experiments presented here, we only use the HLLC solver.
+To complete the spatial discretization, we use Gaussian quadratures to evaluate the integrals in Eq.~\eqref{eq:semidiscreteDG}.  
+During time-integration, we apply limiters to the polynomial representation.  
+We use the TVB limiter of \citet{} to prevent oscillations near discontinuities and the positivity limiter of \citet{ZhangShu2010} to ensure that the density and pressure remain positive.
 

### 2017-02-06 Documents/Euler/Benchmarks1D/draft.tex
zoomed density for test 9
captions 2-8

@@
 
-\altaffiltext{1}{Insert Juliana's affiliation and email}
+\altaffiltext{1}{Bearden High School, Knoxville, TN 37919-5449, USA}
 \altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
@@
   \end{center}
-  \caption{density}
+  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with 128 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den128comp}
 \end{figure}
@@
   \end{center}
-  \caption{pressure and velocity}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:den128comp}:
+  velocity (left panel) and pressure (right panel).}
 \end{figure}
@@
   \end{center}
-  \caption{density}
+  \caption{Results showing the density for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T2}
 \end{figure}
@@
   \end{center}
-  \caption{pressure and velocity}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T2}:
+  velocity (left panel) and pressure (right panel).}
 \end{figure}
@@
   \end{center}
-  \caption{density}
+  \caption{Results showing the density for test 3 at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T3}
 \end{figure}
@@
   \end{center}
-  \caption{pressure and velocity}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T3}:
+  velocity (left panel) and pressure (right panel).}
 \end{figure}
@@
   \end{center}
-  \caption{density}
+  \caption{Results showing the density for test 4 at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T4}
 \end{figure}
@@
   \end{center}
-  \caption{pressure and velocity}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T4}:
+  velocity (left panel) and pressure (right panel).}
 \end{figure}
@@
   \end{center}
-  \caption{density}
+  \caption{Results showing the density for test 5 at $t=0.012$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T5}
 \end{figure}
@@
   \end{center}
-  \caption{pressure and velocity}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T5}:
+  velocity (left panel) and pressure (right panel).}
 \end{figure}
@@
   \end{center}
-  \caption{density}
+  \caption{Results showing the density for test 6 at $t=0.035$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T6}
 \end{figure}
@@
   \end{center}
-  \caption{pressure and velocity}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T6}:
+  velocity (left panel) and pressure (right panel).}
 \end{figure}
@@
   \end{center}
-  \caption{density}
+  \caption{Results showing the density for test 7 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T7}
 \end{figure}
@@
   \end{center}
-  \caption{pressure and velocity}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T7}:
+  velocity (left panel) and pressure (right panel).}
 \end{figure}
@@
   \end{center}
-  \caption{density}
+  \caption{Results showing the density for test 8 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T8}
 \end{figure}
@@
   \end{center}
-  \caption{pressure and velocity}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
+  velocity (left panel) and pressure (right panel).}}
 \end{figure}
@@
 
-%\begin{figure}[h]
- % \begin{center}
-	%\begin{tabular}{cc}
-     % \includegraphics[width=.4\textwidth]{den_T9.png} &
-	  %\includegraphics[width=.4\textwidth]{denT9zoom.png} \\
-	  %\includegraphics[width=.4\textwidth]{prs_T9.png} &	
-      %\includegraphics[width=.4\textwidth]{vel_T9.png}\\
-	%\end{tabular}	
-  %\end{center}
- % \caption{}
-%\end{figure}
-
 \begin{figure}[h]
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T9.png}	
+	\begin{tabular}{cc}
+      \includegraphics[width=.4\textwidth]{den_T9.png} &
+	  \includegraphics[width=.4\textwidth]{denT9zoom.png} \\
+	  \includegraphics[width=.4\textwidth]{prs_T9.png} &	
+      \includegraphics[width=.4\textwidth]{vel_T9.png}\\
+	\end{tabular}	
   \end{center}
-  \caption{density}
+  \caption{}
 \end{figure}
 
-\begin{figure}
-  \begin{center}
-     \includegraphics[width=.78\textwidth]{prs_T9.png}	
-  \end{center}
-  \caption{pressure}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-     \includegraphics[width=.78\textwidth]{vel_T9.png}	
-  \end{center}
-  \caption{velocity}
-\end{figure}
 \clearpage

### 2017-02-06 Documents/Euler/Benchmarks1D/draft.tex
more captions

@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{prs128comp_20} &
-	  \includegraphics[width=.425\textwidth]{vel128comp_20}
+      \includegraphics[width=.425\textwidth]{vel128comp_20} &
+	  \includegraphics[width=.425\textwidth]{prs128comp_20}
 	\end{tabular}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{prs_T2.png} &
-	  \includegraphics[width=.425\textwidth]{vel_T2.png}
+      \includegraphics[width=.425\textwidth]{vel_T2.png} &
+	  \includegraphics[width=.425\textwidth]{prs_T2.png}
 	\end{tabular}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{prs_T3.png} &
-	  \includegraphics[width=.425\textwidth]{vel_T3.png}
+      \includegraphics[width=.425\textwidth]{vel_T3.png} &
+	  \includegraphics[width=.425\textwidth]{prs_T3.png}
 	\end{tabular}
@@
   \end{center}
-  \caption{Results showing the density for test 4 at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+  \caption{Results showing the density for the Noh problem at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
 The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{prs_T4.png} &
-	  \includegraphics[width=.425\textwidth]{vel_T4.png}
+      \includegraphics[width=.425\textwidth]{vel_T4.png} &
+	  \includegraphics[width=.425\textwidth]{prs_T4.png}
 	\end{tabular}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{prs_T5.png} &
-	  \includegraphics[width=.425\textwidth]{vel_T5.png}
+      \includegraphics[width=.425\textwidth]{vel_T5.png} &
+	  \includegraphics[width=.425\textwidth]{prs_T5.png}
 	\end{tabular}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{prs_T6.png} &
-	  \includegraphics[width=.425\textwidth]{vel_T6.png}
+      \includegraphics[width=.425\textwidth]{vel_T6.png} &
+	  \includegraphics[width=.425\textwidth]{prs_T6.png}
 	\end{tabular}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{prs_T7.png} &
-	  \includegraphics[width=.425\textwidth]{vel_T7.png}
+      \includegraphics[width=.425\textwidth]{vel_T7.png} &
+	  \includegraphics[width=.425\textwidth]{prs_T7.png}
 	\end{tabular}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{prs_T8.png} &
-	  \includegraphics[width=.425\textwidth]{vel_T8.png}
+      \includegraphics[width=.425\textwidth]{vel_T8.png} &
+	  \includegraphics[width=.425\textwidth]{prs_T8.png}
 	\end{tabular}
@@
 	  \includegraphics[width=.4\textwidth]{denT9zoom.png} \\
-	  \includegraphics[width=.4\textwidth]{prs_T9.png} &	
-      \includegraphics[width=.4\textwidth]{vel_T9.png}\\
+	  \includegraphics[width=.4\textwidth]{vel_T9.png} &	
+      \includegraphics[width=.4\textwidth]{prs_T9.png}\\
 	\end{tabular}	
   \end{center}
-  \caption{}
+  \caption{Results for the peak problem at $t=0.0039$, computed with 800 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.
+Density is shown in the top two panels at two different zoom levels.
+The bottom left panel shows velocity, and the bottom right panel shows pressure.}
 \end{figure}
@@
 	  \includegraphics[width=.4\textwidth]{den10zoom.png} \\
+	  \includegraphics[width=.4\textwidth]{vel_T10.png} &	
+	  \includegraphics[width=.4\textwidth]{vel10zoom.png} \\
       \includegraphics[width=.4\textwidth]{prs_T10.png} &	
       \includegraphics[width=.4\textwidth]{prs10zoom.png} \\
-      \includegraphics[width=.4\textwidth]{vel_T10.png} &	
-      \includegraphics[width=.4\textwidth]{vel10zoom.png} \\
 	\end{tabular}	
   \end{center}
-  \caption{density, pressure, and velocity}
+  \caption{Results for test 10 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.
+Each pair of side-by-side panels shows the same results at different zoom levels.
+The top panels show density, the middle show velocity, and the bottom show pressure.}
 \end{figure}
@@
 	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
+	  \includegraphics[width=.4\textwidth]{vel_T11.png} &	
+	  \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
       \includegraphics[width=.4\textwidth]{prs_T11.png} &	
       \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
-      \includegraphics[width=.4\textwidth]{vel_T11.png} &	
-      \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
 	\end{tabular}	
   \end{center}
-  \caption{density, pressure, and velocity}
+  \caption{Results for test 11 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.
+Each pair of side-by-side panels shows the same results at different zoom levels.
+The top panels show density, the middle show velocity, and the bottom show pressure.}
 \end{figure}
@@
   \end{center}
-  \caption{density (400 cells)}
+  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
+  \label{fig:den_T12_400}
 \end{figure}
@@
   \end{center}
-  \caption{density (2000 cells)}
+  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
+\end{figure}
+
+\begin{figure}[h]
+  \begin{center}
+     \includegraphics[width=.78\textwidth]{vel_T12_400.png}	
+  \end{center}
+  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
+\end{figure}
+
+\begin{figure}[h]
+  \begin{center}
+     \includegraphics[width=.78\textwidth]{vel_T12_2000.png}	
+  \end{center}
+  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
 \end{figure}
@@
   \end{center}
-  \caption{pressure (400 cells)}
+  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
 \end{figure}
@@
   \end{center}
-  \caption{pressure (2000 cells)}
-\end{figure}
-
-\begin{figure}[h]
-  \begin{center}
-     \includegraphics[width=.78\textwidth]{vel_T12_400.png}	
-  \end{center}
-  \caption{velocity (400 cells)}
-\end{figure}
-
-\begin{figure}[h]
-  \begin{center}
-     \includegraphics[width=.78\textwidth]{vel_T12_2000.png}	
-  \end{center}
-  \caption{velocity (2000 cells)}
+  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
 \end{figure}

### 2017-02-06 Documents/Euler/Benchmarks1D/draft.tex
Reverting to article style

@@
-\documentclass[10pt,preprint]{aastex}
+\documentclass[10pt]{article}
 
@@
 \title{Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado}
-\author{Juliana Pulsinelli\altaffilmark{1} and Eirik Endeve\altaffilmark{2}}
+%\author{Juliana Pulsinelli\altaffilmark{1} and Eirik Endeve\altaffilmark{2}}
 
-\altaffiltext{1}{Bearden High School, Knoxville, TN 37919-5449, USA}
-\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
+%\altaffiltext{1}{Bearden High School, Knoxville, TN 37919-5449, USA}
+%\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
+
+\maketitle
 
@@
   \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
-  velocity (left panel) and pressure (right panel).}}
+  velocity (left panel) and pressure (right panel).}
 \end{figure}

### 2017-02-06 Documents/Euler/Benchmarks1D/draft.tex
Removed a few packages
fixes for compilation

@@
 \usepackage{cite}
-\usepackage{times}
+%\usepackage{times}
 \usepackage{url}
-\usepackage{hyperref}
-\usepackage{lineno}
-\usepackage{yhmath}
+%\usepackage{hyperref}
 \usepackage{natbib}
-\hypersetup{
-  bookmarksnumbered = true,
-  bookmarksopen=false,
-  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
-  pdffitwindow=true,      % window fit to page when opened
-  pdfnewwindow=true, % links in new window
-  colorlinks=true,           % false: boxed links; true: colored links
-  linkcolor=blue,            % color of internal links
-  citecolor=magenta,    % color of links to bibliography
-  filecolor=magenta,     % color of file links
-  urlcolor=cyan              % color of external links
-}
+%\hypersetup{
+ % bookmarksnumbered = true,
+  %bookmarksopen=false,
+  %pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
+  %pdffitwindow=true,      % window fit to page when opened
+  %pdfnewwindow=true, % links in new window
+  %colorlinks=true,           % false: boxed links; true: colored links
+  %linkcolor=blue,            % color of internal links
+  %citecolor=magenta,    % color of links to bibliography
+  %filecolor=magenta,     % color of file links
+  %urlcolor=cyan              % color of external links
+%}
 \usepackage{graphicx}

### 2017-02-10 Documents/Euler/Benchmarks1D/draft.tex
edited captions and increased image size

@@
   \begin{center}
-    \includegraphics[width=.78\textwidth]{den128comp_20}
+    \includegraphics[width=.95\textwidth]{den128comp_20}
   \end{center}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{vel128comp_20} &
-	  \includegraphics[width=.425\textwidth]{prs128comp_20}
+      \includegraphics[width=.475\textwidth]{vel128comp_20} &
+	  \includegraphics[width=.475\textwidth]{prs128comp_20}
 	\end{tabular}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T2.png}	
+     \includegraphics[width=.95\textwidth]{den_T2.png}	
   \end{center}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{vel_T2.png} &
-	  \includegraphics[width=.425\textwidth]{prs_T2.png}
+      \includegraphics[width=.475\textwidth]{vel_T2.png} &
+	  \includegraphics[width=.475\textwidth]{prs_T2.png}
 	\end{tabular}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T3.png}	
+     \includegraphics[width=.95\textwidth]{den_T3.png}	
   \end{center}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{vel_T3.png} &
-	  \includegraphics[width=.425\textwidth]{prs_T3.png}
+      \includegraphics[width=.475\textwidth]{vel_T3.png} &
+	  \includegraphics[width=.475\textwidth]{prs_T3.png}
 	\end{tabular}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T4.png}	
+     \includegraphics[width=.95\textwidth]{den_T4.png}	
   \end{center}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{vel_T4.png} &
-	  \includegraphics[width=.425\textwidth]{prs_T4.png}
+      \includegraphics[width=.475\textwidth]{vel_T4.png} &
+	  \includegraphics[width=.475\textwidth]{prs_T4.png}
 	\end{tabular}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T5.png}	
+     \includegraphics[width=.95\textwidth]{den_T5.png}	
   \end{center}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{vel_T5.png} &
-	  \includegraphics[width=.425\textwidth]{prs_T5.png}
+      \includegraphics[width=.475\textwidth]{vel_T5.png} &
+	  \includegraphics[width=.475\textwidth]{prs_T5.png}
 	\end{tabular}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T6.png}	
+     \includegraphics[width=.95\textwidth]{den_T6.png}	
   \end{center}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{vel_T6.png} &
-	  \includegraphics[width=.425\textwidth]{prs_T6.png}
+      \includegraphics[width=.475\textwidth]{vel_T6.png} &
+	  \includegraphics[width=.475\textwidth]{prs_T6.png}
 	\end{tabular}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T7.png}	
+     \includegraphics[width=.95\textwidth]{den_T7.png}	
   \end{center}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{vel_T7.png} &
-	  \includegraphics[width=.425\textwidth]{prs_T7.png}
+      \includegraphics[width=.475\textwidth]{vel_T7.png} &
+	  \includegraphics[width=.475\textwidth]{prs_T7.png}
 	\end{tabular}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T8.png}	
+     \includegraphics[width=.95\textwidth]{den_T8.png}	
   \end{center}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{vel_T8.png} &
-	  \includegraphics[width=.425\textwidth]{prs_T8.png}
+      \includegraphics[width=.475\textwidth]{vel_T8.png} &
+	  \includegraphics[width=.475\textwidth]{prs_T8.png}
 	\end{tabular}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T12_400.png}	
+     \includegraphics[width=.95\textwidth]{den_T12_400.png}	
   \end{center}
-  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=0.038$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
 The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{den_T12_2000.png}	
+     \includegraphics[width=.95\textwidth]{den_T12_2000.png}	
   \end{center}
-  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
+  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 2000 cells}
 \end{figure}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{vel_T12_400.png}	
+     \includegraphics[width=.95\textwidth]{vel_T12_400.png}	
   \end{center}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{vel_T12_2000.png}	
+     \includegraphics[width=.95\textwidth]{vel_T12_2000.png}	
   \end{center}
-  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
+  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 2000 cells}
 \end{figure}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{prs_T12_400.png}	
+     \includegraphics[width=.95\textwidth]{prs_T12_400.png}	
   \end{center}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{prs_T12_2000.png}	
+     \includegraphics[width=.95\textwidth]{prs_T12_2000.png}	
   \end{center}
-  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
+  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 2000 cells}
 \end{figure}
@@
   \begin{center}
-     \includegraphics[width=.78\textwidth]{1000.png}	
+     \includegraphics[width=.95\textwidth]{1000.png}	
   \end{center}
-  \caption{density, 1000 cells}
+  \caption{Results showing the density for the Shock Entropy Wave problem at $t=1.8$, computed with 1000 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).}
+  \label{fig:shock}
 \end{figure}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{10.png} &
-	  \includegraphics[width=.425\textwidth]{10zoom.png}
+      \includegraphics[width=.475\textwidth]{10.png} &
+	  \includegraphics[width=.475\textwidth]{10zoom.png}
 	\end{tabular}
   \end{center}
-  \caption{density, beta=10}
-  \label{fig:pvcellcomp}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:shock}~at two different zoom levels, computed with 200 cells and beta set to 10.
+The solution labelled ``exact' and given by the dotted blue line is the results of the problem when computed using the third-order integration method with 2000 cells.}
 \end{figure}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{50.png} &
-	  \includegraphics[width=.425\textwidth]{50zoom.png}
+      \includegraphics[width=.475\textwidth]{50.png} &
+	  \includegraphics[width=.475\textwidth]{50zoom.png}
 	\end{tabular}
   \end{center}
-  \caption{density, beta=50}
-  \label{fig:pvcellcomp}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:shock}~at two different zoom levels, computed with 200 cells and beta set to 50.}
 \end{figure}
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=.425\textwidth]{300.png} &
-	  \includegraphics[width=.425\textwidth]{300zoom.png}
+      \includegraphics[width=.475\textwidth]{300.png} &
+	  \includegraphics[width=.475\textwidth]{300zoom.png}
 	\end{tabular}
   \end{center}
-  \caption{density, beta=300}
-  \label{fig:pvcellcomp}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:shock}~at two different zoom levels, computed with 200 cells and beta set to 300.}
 \end{figure}

### 2017-02-13 Documents/Euler/Benchmarks1D/draft.tex
moved blast figures, updated text

@@
 $x_0$ refers to the position of the barrier.
-The computational domain is 0.0 to 1.0 in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2002}.
+The computational domain is 0.0 to 1.0 in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2003}.
 
-Test 12 is an interacting blast waves test, computed on 0.0 to 1.0, with discontinuities at 0.1 and 0.9.
+Test 12 is the Woodward-Collela blast wave problem, computed on 0.0 to 1.0, with discontinuities at 0.1 and 0.9.
 At all positions, initial density is 1 and initial velocity is 0.
-Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right \citep{LiskaWendroff2003}.
+Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right, and the test is advanced to 0.038 seconds.
+\citep{LiskaWendroff2003}.
+Test 13 shows Shock Entropy Wave interactions, advanced to 1.8 seconds.
 %\clearpage
@@
 This depression is most severe when method 1 is used, but it also appears with methods 2 and 3.
+Additionally, all three solutions show many small oscillations along horizontal lines.
 
@@
 \subsection{Test 8}
-
+In density, this test shows a small blip around $x=0.7$ that is unique to the second order method. Velocity and pressure are both constant throughout. 
 \begin{figure}[h]
@@
 \subsection{Test 10}
-
+Density, pressure, and velocity all show significant oscillations that follow the shock wave.
+These oscillations are not part of the exact solution, and appear to a different extend based on the integration method used.
+First order gives a few wide oscillations; higher order methods give more, taller, and thinner oscillations, with the third order giving the most.
 \begin{figure}[h]
@@
 \subsection{Test 11}
-
+This test, like the previous one, shows significant oscilltions following the shock wave, particularly with higher order methods.
+However, these oscillations in the second and third order results appear to be more periodic than those in the previous test.
 \begin{figure}[h]
@@
   \begin{center}
+     \includegraphics[width=.95\textwidth]{den_T12_2000.png}	
+  \end{center}
+  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=0.038$, computed with 2000 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).}
+  \label{fig:den_T12_2000}
+\end{figure}
+
+\begin{figure}[h]
+  \begin{center}
      \includegraphics[width=.95\textwidth]{den_T12_400.png}	
   \end{center}
-  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=0.038$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 400 cells.
 The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
@@
   \begin{center}
-     \includegraphics[width=.95\textwidth]{den_T12_2000.png}	
+	\begin{tabular}{cc}
+     \includegraphics[width=.475\textwidth]{vel_T12_2000.png}
+     \includegraphics[width=.475\textwidth]{vel_T12_400.png}	
+    \end{tabular}
   \end{center}
-  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 2000 cells}
+  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_2000} and Figure~\ref{fig:den_T12_400}, computed with 2000 cells (left) and 400 cells (right).}
 \end{figure}
@@
   \begin{center}
-     \includegraphics[width=.95\textwidth]{vel_T12_400.png}	
+	\begin{tabular}{cc}
+     \includegraphics[width=.475\textwidth]{prs_T12_2000.png}
+     \includegraphics[width=.475\textwidth]{prs_T12_400.png}
+    \end{tabular}	
   \end{center}
-  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
-\end{figure}
-
-\begin{figure}[h]
-  \begin{center}
-     \includegraphics[width=.95\textwidth]{vel_T12_2000.png}	
-  \end{center}
-  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 2000 cells}
-\end{figure}
-
-\begin{figure}[h]
-  \begin{center}
-     \includegraphics[width=.95\textwidth]{prs_T12_400.png}	
-  \end{center}
-  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
-\end{figure}
-
-\begin{figure}[h]
-  \begin{center}
-     \includegraphics[width=.95\textwidth]{prs_T12_2000.png}	
-  \end{center}
-  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 2000 cells}
+  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_2000} and Figure~\ref{fig:den_T12_400}, computed with 2000 cells (left) and 400 cells (right).}
 \end{figure}
@@
 Again, the 3rd order, 1000 cell solution is called ``exact.''
+
+This test features many oscillations that are part of the real solution.
+In the higher-resolution runs, at least the second order integration method was needed to show these oscillations.
+In the lower-resolutions, when beta was set to 10, 2nd and 3rd order yielded similar results, both greatly smoothing out the oscillations.
+When beta was 50, 3rd order outperformed 2nd, but both were still insufficient to model the oscillations.
+Beta set to 300 yielded the most accurate results, and the 3rd order results were especially accurate.
 

### 2017-02-13 Documents/Euler/Benchmarks1D/draft.tex
Added description of time stepping

@@
 \usepackage{booktabs}
-\usepackage{mathrsfs}
+%\usepackage{mathrsfs}
 \usepackage{cite}
@@
 \usepackage{natbib}
+\usepackage{color}
 %\hypersetup{
@@
 \newcommand{\thornado}{\texttt{thornado}}
+\newcommand{\ee}[1]{{\color{blue} #1}}
 
@@
 
+We apply the method of lines approach to temporal discretization.  
+With the spatial discretization specified, the DG problem in Eq.~\eqref{eq:semidiscreteDG} can be viewed as a system of ordinary differential equations (ODEs) for the expansion coefficients $\boldsymbol{C}=\{\boldsymbol{C}_{j}\}_{j=0}^{k}$, i.e.,
+\begin{equation}
+  d_{t}\boldsymbol{C}
+  =\boldsymbol{L}(\boldsymbol{C}),
+\end{equation}
+which can be discretized in time.  
+To this end, we apply the strong stability-preserving Runge-Kutta (SSP-RK) methods of order 1 to 3 \citep{gottlieb_etal_2001}.  
+The 1st order method (SSP-RK1) is simply the forward Euler method, while the 2nd and 3rd order methods (SSP-RK2 and SSP-RK3, respectively) can be expressed as convex combinations of forward Euler steps.
+A general $m$-stage Runge-Kutta method is given by
+\begin{align}
+  \boldsymbol{C}^{(0)}
+  &=\boldsymbol{C}^{n} \\
+  \boldsymbol{C}^{(i)}
+  &=\sum_{l=1}^{i-1}\alpha_{il}\,\big(\,\boldsymbol{C}^{(l)}+\beta_{il}\,\Delta t\,\boldsymbol{L}(\boldsymbol{C}^{(l)})\,\big)
+  \quad i=1,\ldots,m \\
+  \boldsymbol{C}^{n+1}
+  &=\boldsymbol{C}^{(m)},
+\end{align}
+where $\alpha_{il},\beta_{il}\ge0$ are given by Butcher tables.  
+During time integration, we apply slope and positivity limiters after each stage as a post-processing step.
+
+In the numerical experiments presented below, we will vary the spatial and temporal order of the method.  
+The 1st order method (DG(0)+RK1) uses polynomials of degree $0$ in each element and the forward Euler time integration method, the second-order method (DG(1)+RK2) uses polynomials of degree $1$ combined SSP-RK2 time integration, while the 3rd order method (DG(2)+RK3) uses polynomials of degree $2$ combined SSP-RK3 time integration.
+
 \section{Numerical Experiments}
@@
 \end{tabular}
-  \caption{table of tests}
+  \caption{table of tests \ee{Add more descriptive caption}}
   \label{tab:testtable}
@@
 $x_0$ refers to the position of the barrier. 
-The computational domain is 0.0 to 1.0 in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2003}.
+The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2002}.
+\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}
 

### 2017-02-14 Documents/Euler/Benchmarks1D/draft.tex
Named test 2

@@
 \begin{abstract}
-\thornado\ is a new astrophysical code for radiation-hydrodynamics based on high-order Runge-Kutta Discontinuous Galerkin (RKDG) methods.  
+The toolkit for high-order neutrino-radiation hydrodynamics (\thornado) is a code for astrophysical radiation-hydrodynamics based on high-order Runge-Kutta Discontinuous Galerkin (RKDG) methods.  
 It currently solves the Euler equations for fluid dynamics and the two-moment ($M_{1}$) approximation of the radiative transfer equation. 
@@
  \hline
- Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & T \\
+ Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & $T$ \\
  \hline
@@
 
-\subsection{Test 2}
+\subsection{Test 2: Toro's Riemann Problem}
+
+This test is the same as Sod's shock tube from the previous section, except that there is a non-zero velocity to the left of the initial discontinuity.  
+As a result, a sonic point develops in the rarefaction wave.  
 For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
@@
 
-\subsection{Test 13: Shock Entropy Waves}
+\subsection{Test 13: Shock-Entropy Wave Interaction}
 

### 2017-02-18 Documents/Euler/Benchmarks1D/draft.tex
test names and some wave types

@@
 \subsection{Test 1: Sod's Shock Tube} 
+The Sod's Shock tube test features examples of threee different types of waves.
+A shock wave appears around $x=0.85$.
+A contact discontinuity appears around $x=0.68$.
+A rarefaction wave appears between about $x=0.3$ and $x=0.5$.
 
@@
 
-\subsection{Test 3}
-Test 3 shows results similar to Test 2.
+\subsection{Test 3: Double Rarefaction}
+This test features two rarefaction waves. They are moving in opposite directions, away from the initial discontinuity in the center.
+
+This test shows results similar to Toro's Riemann Problem.
 The deviation of experimental results from exact is especially noticeable in velocity.
@@
   \end{center}
-  \caption{Results showing the density for test 3 at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+  \caption{Results showing the density for the double rarefaction problem at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
 The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
@@
 
-\subsection{Test 4}
-
+\subsection{Test 4: Noh}
+The Noh problem features two shock waves. One is located near $x=0.28$, while the other is near $x=.82$.
 This test obviously displays some difference from the exact solution in density.
@@
 \subsection{Test 5}
+This test features three different types of waves. A shock wave appears around $x=0.85$. A contact discontinuity appears at $x=0.8$. A rarefaction wave appears between $x=0.1$ and $x=0.4$.
+
 This test has interesting features in velocity.
@@
 \subsection{Test 6}
+This test features two shock waves, one around $x=0.85$ and the other around $x=0.42$. It also features a contact discontinutiy at $x=0.7$.
 For this test's pressures and velocity, all three integration methods give values very close to exact.
@@
 
-\subsection{Test 7}
+\subsection{Test 7: Stationary Contact Discontinuity}
+This test features a contact discontinuity at $x=0.5$.
 This test features an unusual situation--method 1 calculates the velocity exactly, while method 2 introduces more error and method 3 introduces the most.
@@
   \end{center}
-  \caption{Results showing the density for test 7 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+  \caption{Results showing the density for the stationary contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
 The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
@@
 
-\subsection{Test 8}
-In density, this test shows a small blip around $x=0.7$ that is unique to the second order method. Velocity and pressure are both constant throughout. 
+\subsection{Test 8: Moving Contact Discontinuity}
+This test features a contact discontinuity at $x=0.7$.
+In density, this test shows a small blip around $x=0.7$ that is unique to the second order method.
+Velocity and pressure are both constant throughout.
 \begin{figure}[h]
@@
   \end{center}
-  \caption{Results showing the density for test 8 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+  \caption{Results showing the density the moving contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
 The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
@@
 
-\subsection{Test 9}
+\subsection{Test 9: Peak}
 When finding density, method 1 falls considerably short of the maximum.

### 2017-02-20 Documents/Euler/Benchmarks1D/draft.tex
Two more test names

@@
 
-\subsection{Test 10}
+\subsection{Test 10: Start-up Errors}
+
 Density, pressure, and velocity all show significant oscillations that follow the shock wave.
@@
 
-\subsection{Test 11}
+\subsection{Test 11: Slow-moving Shock}
 This test, like the previous one, shows significant oscilltions following the shock wave, particularly with higher order methods.

### 2017-02-20 Documents/Euler/Benchmarks1D/draft.tex
more wave types

@@
 \subsection{Test 9: Peak}
+The peak problem features a shock wave at $x=0.554$, as well as a contact discontinuity at $x=0.546$.
+A rarefaction wave is also present between about $x=0.16$ and $x=0.2$.
 When finding density, method 1 falls considerably short of the maximum.
@@
 
+In this problem, a shock wave is present at about $x=11$.
 Density, pressure, and velocity all show significant oscillations that follow the shock wave.
@@
 \subsection{Test 11: Slow-moving Shock}
-This test, like the previous one, shows significant oscilltions following the shock wave, particularly with higher order methods.
+In this problem, a shock wave is present at about $x=0.5$.This test, like the previous one, shows significant oscilltions following the shock wave, particularly with higher order methods.
 However, these oscillations in the second and third order results appear to be more periodic than those in the previous test.

### 2017-02-27 Documents/Euler/Benchmarks1D/draft.tex
changes to test 12 and experiments intro

@@
 \end{tabular}
-  \caption{table of tests \ee{Add more descriptive caption}}
+  \caption{Initial parameters for most of the tests described in this paper, from \citep{LiskaWendroff2003}~and \citep{Leveque2002}.
+The table shows initial density ($\rho$), velocity ($u$), and pressure ($p$) on both sides of a discontinuity located at $x_0$.
+These initial conditions are then advanced to time $T$.}
   \label{tab:testtable}
@@
 $x_0$ refers to the position of the barrier. 
-The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2002}.
+The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, $x_{\mbox{\tiny L}}=0.1$ and $x_{\mbox{\tiny R}}=0.6$ in test 9 \citep{LiskaWendroff2003}, $x_{\mbox{\tiny L}}=-5$ and $x_{\mbox{\tiny R}}=15$ in test 10, and $x_{\mbox{\tiny L}}=-15$ and $x_{\mbox{\tiny R}}=5$ in test 11 \citep{Leveque2002}.
 \ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}
@@
   \begin{center}
+	\begin{tabular}{cc}
+     \includegraphics[width=.475\textwidth]{vel_T12_2000.png}
+     \includegraphics[width=.475\textwidth]{prs_T12_2000.png}	
+    \end{tabular}
+  \end{center}
+ \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T12_2000}:
+  velocity (left panel) and pressure (right panel).}
+\end{figure}
+
+\begin{figure}[h]
+  \begin{center}
      \includegraphics[width=.95\textwidth]{den_T12_400.png}	
   \end{center}
-  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 400 cells.
+  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_2000}~computed with 400 cells.
 The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
@@
 	\begin{tabular}{cc}
-     \includegraphics[width=.475\textwidth]{vel_T12_2000.png}
      \includegraphics[width=.475\textwidth]{vel_T12_400.png}
-    \end{tabular}
-  \end{center}
-  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_2000} and Figure~\ref{fig:den_T12_400}, computed with 2000 cells (left) and 400 cells (right).}
-\end{figure}
-
-\begin{figure}[h]
-  \begin{center}
-	\begin{tabular}{cc}
-     \includegraphics[width=.475\textwidth]{prs_T12_2000.png}
      \includegraphics[width=.475\textwidth]{prs_T12_400.png}	
@@
   \end{center}
-  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_2000} and Figure~\ref{fig:den_T12_400}, computed with 2000 cells (left) and 400 cells (right).}
+  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T12_400}:
+  velocity (left panel) and pressure (right panel)}
 \end{figure}
@@
 
+\section{Conclusion}
+
 \bibliographystyle{apj}

### 2017-03-19 Documents/Euler/Benchmarks1D/draft.tex
Merged figures
combined figures and shrank margins

@@
 \graphicspath{ {figures/} }
+
+\addtolength{\oddsidemargin}{-.875in}
+\addtolength{\evensidemargin}{-.875in}
+\addtolength{\textwidth}{1.75in}
+
+\addtolength{\topmargin}{-.875in}
+\addtolength{\textheight}{1.75in}
 
@@
 10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
-11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
+11 & 5.6698 & -1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
  \hline
@@
 Between the two endpoints, 128, 256, 512, and 1024 points were computed for on each respective test.
-Figures~\ref{fig:dencellcomp_20}--\ref{fig:pvcellcomp} show results of these tests:
+Figure~\ref{fig:dencellcomp_20} shows results of these tests:
 \begin{figure}[h!]
@@
     \includegraphics[width=.95\textwidth]{dencellcomp_20}
-  \end{center}
-  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with the first-order method using different number of elements: 128 (solid red), 256 (dashed green), 512 (dotted blue), and 1024 (dash-dot pink).
-The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted cyan line.}
-  \label{fig:dencellcomp_20}
-\end{figure}
-%\newpage
-
-\begin{figure}
-  \begin{center}
     \begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:dencellcomp_20}:
-  velocity (left panel) and pressure (right panel).}
-  \label{fig:pvcellcomp}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for Sod's shock tube at $t=0.2$, computed with the first-order method using different number of elements: 128 (solid red), 256 (dashed green), 512 (dotted blue), and 1024 (dash-dot pink).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted cyan line.}
+  \label{fig:dencellcomp_20}
 \end{figure}
-%\newpage
 
-%\clearpage
-%\begin{figure}
- % \begin{center}
-
- % \end{center}
- % \caption{velocity}
- % \label{fig:velcellcomp_20}
-%\end{figure}
-%\clearpage
 Next, several tests were run of different integration methods; the number of points was held constant at 128 each time.
@@
   \begin{center}
-    \includegraphics[width=.95\textwidth]{den128comp_20}
-  \end{center}
-  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with 128 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
-The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
-  \label{fig:den128comp}
-\end{figure}
-%\newpage
-
-\begin{figure}
-  \begin{center}
+    \includegraphics[width=.975\textwidth]{den128comp_20}
     \begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:den128comp}:
-  velocity (left panel) and pressure (right panel).}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for Sod's shock tube at $t=0.2$, computed with 128 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den128comp}
 \end{figure}
@@
      \includegraphics[width=.95\textwidth]{den_T2.png}
-  \end{center}
-  \caption{Results showing the density for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
-The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
-  \label{fig:den_T2}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
 	 \begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T2}:
-  velocity (left panel) and pressure (right panel).}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T2}
 \end{figure}
@@
      \includegraphics[width=.95\textwidth]{den_T3.png}	
-  \end{center}
-  \caption{Results showing the density for the double rarefaction problem at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
-The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
-  \label{fig:den_T3}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
 	\begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T3}:
-  velocity (left panel) and pressure (right panel).}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the double rarefaction problem at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T3}
 \end{figure}
@@
      \includegraphics[width=.95\textwidth]{den_T4.png}	
-  \end{center}
-  \caption{Results showing the density for the Noh problem at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
-The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
-  \label{fig:den_T4}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
 	\begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T4}:
-  velocity (left panel) and pressure (right panel).}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the Noh problem at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T4}
 \end{figure}
@@
      \includegraphics[width=.95\textwidth]{den_T5.png}
-  \end{center}
-  \caption{Results showing the density for test 5 at $t=0.012$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
-The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
-  \label{fig:den_T5}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
 	\begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T5}:
-  velocity (left panel) and pressure (right panel).}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for test 5 at $t=0.012$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T5}
 \end{figure}
-\clearpage
 
@@
      \includegraphics[width=.95\textwidth]{den_T6.png}	
-  \end{center}
-  \caption{Results showing the density for test 6 at $t=0.035$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
-The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
-  \label{fig:den_T6}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
 	\begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T6}:
-  velocity (left panel) and pressure (right panel).}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for test 6 at $t=0.035$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T6}
 \end{figure}
@@
      \includegraphics[width=.95\textwidth]{den_T7.png}	
-  \end{center}
-  \caption{Results showing the density for the stationary contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
-The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
-  \label{fig:den_T7}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
 	\begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T7}:
-  velocity (left panel) and pressure (right panel).}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the stationary contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T7}
 \end{figure}
@@
      \includegraphics[width=.95\textwidth]{den_T8.png}
-  \end{center}
-  \caption{Results showing the density the moving contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
-The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
-  \label{fig:den_T8}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
 	\begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
-  velocity (left panel) and pressure (right panel).}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the moving contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).
+The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
+  \label{fig:den_T8}
 \end{figure}
@@
      \includegraphics[width=.95\textwidth]{den_T12_2000.png}
+	\begin{tabular}{cc}
+     \includegraphics[width=.475\textwidth]{vel_T12_2000.png}
+     \includegraphics[width=.475\textwidth]{prs_T12_2000.png}	
+    \end{tabular}	
   \end{center}
-  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=0.038$, computed with 2000 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the Woodward-Collela blast wave problem at $t=0.038$, computed with 2000 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).}
   \label{fig:den_T12_2000}
@@
   \begin{center}
-	\begin{tabular}{cc}
-     \includegraphics[width=.475\textwidth]{vel_T12_2000.png}
-     \includegraphics[width=.475\textwidth]{prs_T12_2000.png}	
-    \end{tabular}
-  \end{center}
- \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T12_2000}:
-  velocity (left panel) and pressure (right panel).}
-\end{figure}
-
-\begin{figure}[h]
-  \begin{center}
      \includegraphics[width=.95\textwidth]{den_T12_400.png}	
-  \end{center}
-  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_2000}~computed with 400 cells.
-The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
-  \label{fig:den_T12_400}
-\end{figure}
-
-\begin{figure}[h]
-  \begin{center}
 	\begin{tabular}{cc}
@@
   \end{center}
-  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T12_400}:
-  velocity (left panel) and pressure (right panel)}
+  \caption{Results for the density (top), velocity (bottom left), and pressure (bottom right) from the same experiments as shown in Figure~\ref{fig:den_T12_2000}~computed with 400 cells.
+The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
+  \label{fig:den_T12_400}
 \end{figure}

### 2017-03-21 Documents/Euler/Benchmarks1D/draft.tex
draft of conclusion

@@
 \section{Conclusion}
+The thornado code was benchmarked using a large suite of Riemann problem tests.
+In all of these tests, the code was able to capture the structure of the problem well.
+In general, using a second order integration method instead of a first order integration method greatly increased the accuracy of the solution.
+For tests in which constant states were separated by a discontinuity, changing from second to third order brought little improvement.
+However, the difference between these methods was significant in the Shock Entropy Waves test—third order showed a much greater ability to follow oscillations when beta was set to 300.
+With smaller values of beta, the ability of the third order method to capture these oscillations was diminished, as was the difference between the second and third order methods.
+The tunable parameter beta is problematic because its optimal value is dependent on the features of the problem; it is impossible to choose a correct value of beta that can be used generally, in all situations.
 

### 2017-03-21 Documents/Euler/dgEulerCurvilinear.tex
Updates to documents

@@
   &\partial_{t}\int_{\bK}\bU_{\DG}\,v\,dV
-  +\sumx\int_{\pbK^{i}}\big(\,\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\bU_{\DG})\,v\big|_{\xH^{i}}-\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\bU_{\DG})\,v\big|_{\xL^{i}}\,\big)\,\tilde{\bx}^{i} \nonumber \\
+  +\sumx\int_{\pbK^{i}}\big(\,\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\bU_{\DG})\,v\big|_{\xH^{i}}-\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\bU_{\DG})\,v\big|_{\xL^{i}}\,\big)\,d\tilde{\bx}^{i} \nonumber \\
   &\hspace{24pt}
@@
 Then, using these rules, we provide explicit expressions for each of the terms in Equation~\eqref{eq:semidiscreteDG}.
+
+\subsubsection{Notation and Definitions}
 
@@
 
+\subsubsection{Explicit Expressions}
+
 Inserting \eqref{eq:conservedNodalExpansion} into \eqref{eq:semidiscreteDG}, with $v(\bx)=\ell_{\bk}(\bx)$ and the quadratures defined above, we obtain
@@
 \end{align}
-for the time derivative term, and
+for the time derivative term, where $|\bK|=\prod_{i=1}^{d}\Delta x^{i}$.  
+The integration is approximate since we use the Legendre-Gauss quadrature rule with the nodal points given by the expansion in Eq.~\eqref{eq:conservedNodalExpansion}.  
+This leads to a diagonal mass matrix, and simplifies the implementation.  
+Similarly, we obtain
 \begin{align}
@@
 for the source term.  
-The gravitational source terms contain the derivative to the potential, which warrants some additional exposition.  
-We choose a local representation of the potential (obtained by evaluating the potential in the nodes in $\bK$ using the FEM solution); i.e.,
-\begin{equation}
-  \Phi(\bx)=\sum_{\bi=\vect{1}}^{\bN}\Phi_{\bi}\,\ell_{\bi}(\bx).  
-\end{equation}
-Differentiating with respect to $x^{j}$ gives
-\begin{equation}
-  \pderiv{\Phi}{x^{j}}\Big|_{\bx_{\bk}}
-  =\f{1}{|K^{j}|}\sum_{\bi=\vect{1}}^{\bN}\pderiv{\ell_{\bi}}{\eta^{j}}(\eta_{\bk})\,\Phi_{\bi}
-  =\f{1}{|K^{j}|}\sum_{i_{j}=1}^{N}\pderiv{\ell_{i_{j}}}{\eta^{j}}(\eta_{k_{j}}^{j})\,\Phi(x_{i_{j}}^{j},\tilde{\bx}_{\tilde{\bk}_{j}}^{j}).  
-\end{equation}
-This expression is used to evaluate the gravitational sources in the momentum and energy equations.
+The gravitational source terms warrants some additional exposition, which we defer to Section~\ref{sec:sourceTerms}.
 
 For the surface integrals, we obtain, e.g., 
+\begin{equation}
+  \int_{\pbK^{i}}\sqrt{\gamma}\,\widehat{\vect{F}}^{i}\,v\big|_{\xH^{i}}\,d\tilde{\bx}^{i}
+  \approx w_{\tilde{\bk}_{i}}\,\sqrt{\gamma}(x_{\Hgh}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\widehat{\bF}^{i}(x_{\Hgh}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\ell_{k_{i}}(\eta_{\Hgh}^{i})\,|\tilde{\bK}^{i}|,
+\end{equation}
+where $|\tilde{\bK}^{i}|=\prod_{j\ne i}\Delta x^{j}$.  
+(Note: we do not use Einstein's summation convention in the numerical expressions presented in this section.  
+Summation over indices will be explicitly indicated.)  
+Finally, the volume term becomes
+\begin{equation}
+  \int_{\bK}\bF^{i}\,\pderiv{v}{x^{i}}\,dV
+  \approx w_{\tilde{\bk}_{i}}\sum_{q_{i}=1}^{N}
+  w_{q_{i}}\,\sqrt{\gamma}(x_{q_{i}}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\bF^{i}(x_{q_{i}}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\pderiv{\ell_{k_{i}}}{\eta^{i}}(\eta_{q_{i}}^{i})\,|\tilde{\bK}^{i}|.
+\end{equation}
+Combining the terms and dividing though by $w_{\bk}\,\sqrt{\gamma}_{\bk}\,|\bK|$, we obtain the semi-discrete for of the Euler equations
 \begin{align}
-  %
-  \int_{\tilde{\bK}^{1}}v\,\widehat{\bF}^{1}|_{x_{\Hgh}^{1}}\,dA^{1}
-  &\approx w_{\tilde{\bk}_{1}}\,\ell_{k_{1}}(+1)\,\widehat{\bF}^{1}(x_{\Hgh}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,
-  \tau^{1}(x_{\Hgh}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,|\tilde{\bK}^{1}| \nonumber \\
+  \pd{}{t}\bU_{\bk}
+  &=
+  -\f{1}{\sqrt{\gamma}_{\bk}}
+  \sum_{i=1}^{d}\f{1}{w_{k_{i}}\,\Delta x^{i}}\,
+  \Big(\,
+    \sqrt{\gamma}(x_{\Hgh}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\widehat{\bF}^{i}(x_{\Hgh}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\ell_{k_{i}}(\eta_{\Hgh}^{i})
+    -\sqrt{\gamma}(x_{\Low}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\widehat{\bF}^{i}(x_{\Low}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\ell_{k_{i}}(\eta_{\Low}^{i})
+  \,\Big) \nonumber \\
   &\hspace{12pt}
-  =w_{\tilde{\bk}_{1}}\,\ell_{k_{1}}(+1)\,\widehat{\bF}^{1}(x_{\Hgh}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,
-  a(x_{\Hgh}^{1})\,b(x_{\Hgh}^{1})\,c(x_{k_{2}}^{2})\,\dx^{2}\,\dx^{3}, \\
-  %
-  \int_{\tilde{\bK}^{2}}v\,\widehat{\bF}^{2}|_{x_{\Hgh}^{2}}\,dA^{2}
-  &\approx w_{\tilde{\bk}_{2}}\,\ell_{k_{2}}(+1)\,\widehat{\bF}^{2}(x_{\Hgh}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,
-  \tau^{2}(x_{\Hgh}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,|\tilde{\bK}^{2}| \nonumber \\
-  &\hspace{12pt}
-  =w_{\tilde{\bk}_{2}}\,\ell_{k_{2}}(+1)\,\widehat{\bF}^{2}(x_{\Hgh}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,
-  b(x_{k_{1}}^{1})\,c(x_{\Hgh}^{2})\,\dx^{1}\,\dx^{3}, \\
-  %
-  \int_{\tilde{\bK}^{3}}v\,\widehat{\bF}^{3}|_{x_{\Hgh}^{3}}\,dA^{3}
-  &\approx w_{\tilde{\bk}_{3}}\,\ell_{k_{3}}(+1)\,\widehat{\bF}^{3}(x_{\Hgh}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,
-  \tau^{3}(x_{\Hgh}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,|\tilde{\bK}^{3}| \nonumber \\
-  &\hspace{12pt}
-  =w_{\tilde{\bk}_{3}}\,\ell_{k_{3}}(+1)\,\widehat{\bF}^{3}(x_{\Hgh}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,
-  a(x_{k_{1}}^{1})\,\dx^{1}\,\dx^{2}.  
+  +\f{1}{\sqrt{\gamma}_{\bk}}
+  \sum_{i=1}^{d}\f{1}{w_{k_{i}}\,\Delta x^{i}}\sum_{q_{i}=1}^{N}w_{q_{i}}\,\sqrt{\gamma}(x_{q_{i}}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\bF^{i}(x_{q_{i}}^{i},\tilde{\bx}_{\tilde{\bk}_{i}}^{i})\,\pderiv{\ell_{k_{i}}}{\eta^{i}}(\eta_{q_{i}}^{i})
+  +\bG(\bU_{\bk})
+  \label{eq:semidiscreteDiscretized}
 \end{align}
-Finally, the `volume terms' become
+Equation~\eqref{eq:semidiscreteDiscretized} provides the basis for implementation in our code.
+
+\subsubsection{Reconstruction to Element interfaces}
+
+\begin{equation}
+  \bU_{\DG}(\eta_{\Low}^{i},\tilde{\vect{\eta}}_{\tilde{\bq}_{i}}^{i})
+  =\sum_{\bk=\vect{1}}^{\bN}\bU_{\bk}\,\ell_{\bk}(\eta_{\Low}^{i},\tilde{\vect{\eta}}_{\tilde{\bq}_{i}}^{i})
+  =\sum_{k_{i}=1}^{N}\sum_{\tilde{\bk}_{i}=\vect{1}}^{\bN}\bU_{(k_{i},\tilde{\bk}_{i})}\,\ell_{k_{i}}(\eta_{\Low}^{i})\,\ell_{\tilde{\bk}_{i}}(\tilde{\vect{\eta}}_{\tilde{\bq}_{i}}^{i})
+\end{equation}
+
+\subsubsection{The One-Dimensional Case}
+
+Here we simplify the DG discretization in Eq.~\eqref{eq:semidiscreteDiscretized} to the one-dimensional ($d=1$) case to make the notation more transparent.  
+With $d=1$, we substitute $\bk\to k_{d}\to k$, $x^{d}\to x$, $q_{i}\to q$, etc., so that Eq.~\eqref{eq:semidiscreteDiscretized} reduces to
 \begin{align}
-  %
-  \int_{\bK}\bF^{1}\,\pderiv{v}{x^{1}}\,dV
-  &\approx w_{\tilde{\bk}_{1}}\sum_{q_{1}=1}^{N}w_{q_{1}}\,\bF^{1}(x_{q_{1}}^{1},\tilde{\bx}_{\tilde{\bk}_{1}}^{1})\,
-  \pderiv{\ell_{k_{1}}}{\eta^{1}}(\eta_{q_{1}}^{1})\,\sqrt{\gamma}(x_{q_{1}}^{1},\tilde{\bx}_{\tilde{\bk}_{1}}^{1})\,|\tilde{\bK}^{1}| \nonumber \\
-  &\hspace{12pt}
-  =w_{\tilde{\bk}_{1}}\,c(x_{k_{2}}^{2})\,\dx^{2}\,\dx^{3}
-  \sum_{q_{1}=1}^{N}w_{q_{1}}\,\bF^{1}(x_{q_{1}}^{1},\tilde{\bx}_{\tilde{\bk}_{1}}^{1})\,
-  \pderiv{\ell_{k_{1}}}{\eta^{1}}(\eta_{q_{1}}^{1})\,a(x_{q_{1}}^{1})\,b(x_{q_{1}}^{1}), \\
-  %
-  \int_{\bK}\bF^{2}\,\f{1}{a}\pderiv{v}{x^{2}}\,dV
-  &\approx w_{\tilde{\bk}_{2}}\sum_{q_{2}=1}^{N}w_{q_{2}}\,\bF^{2}(x_{q_{2}}^{2},\tilde{\bx}_{\tilde{\bk}_{2}}^{2})\,
-  \f{1}{a(x_{k_{1}}^{1})}\pderiv{\ell_{k_{2}}}{\eta^{2}}(\eta_{q_{2}}^{2})\,\sqrt{\gamma}(x_{q_{2}}^{2},\tilde{\bx}_{\tilde{\bk}_{2}}^{2})\,|\tilde{\bK}^{2}| \\
-  &\hspace{12pt}
-  =w_{\tilde{\bk}_{2}}\,b(x_{k_{1}}^{1})\,\dx^{1}\,\dx^{3}\sum_{q_{2}=1}^{N}w_{q_{2}}\,\bF^{2}(x_{q_{2}}^{2},\tilde{\bx}_{\tilde{\bk}_{2}}^{2})\,
-  \pderiv{\ell_{k_{2}}}{\eta^{2}}(\eta_{q_{2}}^{2})\,c(x_{q_{2}}^{2}), \\
-  %
-  \int_{\bK}\bF^{3}\,\f{1}{bc}\pderiv{v}{x^{3}}\,dV
-  &\approx w_{\tilde{\bk}_{3}}\sum_{q_{3}=1}^{N}w_{q_{3}}\,\bF^{3}(x_{q_{3}}^{3},\tilde{\bx}_{\tilde{\bk}_{3}}^{3})\,
-  \f{1}{b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})}\pderiv{\ell_{k_{3}}}{\eta^{3}}(\eta_{q_{3}}^{3})\,\sqrt{\gamma}(x_{q_{3}}^{3},\tilde{\bx}_{\tilde{\bk}_{3}}^{3})\,|\tilde{\bK}^{3}| \nonumber \\
-  &\hspace{12pt}
-  =w_{\tilde{\bk}_{3}}\,a(x_{k_{1}}^{1})\,\dx^{1}\,\dx^{2}\sum_{q_{3}=1}^{N}w_{q_{3}}\,\bF^{3}(x_{q_{3}}^{3},\tilde{\bx}_{\tilde{\bk}_{3}}^{3})\,
-  \pderiv{\ell_{k_{3}}}{\eta^{3}}(\eta_{q_{3}}^{3}).  
+  \pd{}{t}\bU_{k}
+  &=-\f{1}{\sqrt{\gamma}_{k}}
+  \f{1}{w_{k}\,\Delta x}\,
+  \Big(\,
+    \sqrt{\gamma}(x_{\Hgh})\,\widehat{\bF}(x_{\Hgh})\,\ell_{k}(\eta_{\Hgh})
+    -\sqrt{\gamma}(x_{\Low})\,\widehat{\bF}(x_{\Low})\,\ell_{k}(\eta_{\Low})
+  \,\Big) \nonumber \\
+  & \hspace{12pt}
+  +\f{1}{\sqrt{\gamma}_{k}}
+  \f{1}{w_{k}\,\Delta x}\sum_{q=1}^{N}w_{q}\,\sqrt{\gamma}(x_{q})\,\bF(x_{q})\,\pderiv{\ell_{k}}{\eta}(\eta_{q})
+  +\bG(\bU_{k}).
+  \label{eq:semidiscreteDiscretized1D}
 \end{align}
 
-Combining the terms above with forward Euler time integration, we obtain
-\begin{align}
-  \bU_{\bk}^{n+1}
-  &=\bU_{\bk}^{n} \nonumber \\
-  &\hspace{12pt}
-  -\f{\dt}{w_{k_{1}}\,a(x_{k_{1}}^{1})\,b(x_{k_{1}}^{1})\,\dx^{1}}
-  \Big(\,
-    a(x_{\Hgh}^{1})\,b(x_{\Hgh}^{1})\,\widehat{\bF}^{1,n}(x_{\Hgh}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,\ell_{k_{1}}(+1) \nonumber \\
-    &\hspace{128pt}
-    -a(x_{\Low}^{1})\,b(x_{\Low}^{1})\,\widehat{\bF}^{1,n}(x_{\Low}^{1},\tilde{x}_{\tilde{\bk}_{1}}^{1})\,\ell_{k_{1}}(-1)
-  \,\Big) \nonumber \\
-  &\hspace{12pt}
-  +\f{\dt}{w_{k_{1}}\,a(x_{k_{1}}^{1})\,b(x_{k_{1}}^{1})\,\dx^{1}}
-  \sum_{q_{1}=1}^{N}w_{q_{1}}\,a(x_{q_{1}}^{1})\,b(x_{q_{1}}^{1})\,\bF^{1,n}(x_{q_{1}}^{1},\tilde{\bx}_{\tilde{\bk}_{1}}^{1})\,
-  \pderiv{\ell_{k_{1}}}{\eta^{1}}(\eta_{q_{1}}^{1}) \nonumber \\
-  &\hspace{12pt}
-  -\f{\dt}{w_{k_{2}}\,a(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{2}}
-  \Big(\,
-    c(x_{\Hgh}^{2})\,\widehat{\bF}^{2,n}(x_{\Hgh}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,\ell_{k_{2}}(+1) \nonumber \\
-    &\hspace{128pt}
-    -c(x_{\Low}^{2})\,\widehat{\bF}^{2,n}(x_{\Low}^{2},\tilde{x}_{\tilde{\bk}_{2}}^{2})\,\ell_{k_{2}}(-1)
-  \,\Big) \nonumber \\
-  &\hspace{12pt}
-  +\f{\dt}{w_{k_{2}}\,a(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{2}}
-  \sum_{q_{2}=1}^{N}w_{q_{2}}\,\bF^{2}(x_{q_{2}}^{2},\tilde{\bx}_{\tilde{\bk}_{2}}^{2})\,\pderiv{\ell_{k_{2}}}{\eta^{2}}(\eta_{q_{2}}^{2})\,c(x_{q_{2}}^{2}) \nonumber \\
-  &\hspace{12pt}
-  -\f{\dt}{w_{k_{3}}\,b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{3}}
-  \Big(\,
-    \widehat{\bF}^{3,n}(x_{\Hgh}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,\ell_{k_{3}}(+1)
-    -\widehat{\bF}^{3,n}(x_{\Low}^{3},\tilde{x}_{\tilde{\bk}_{3}}^{3})\,\ell_{k_{3}}(-1)
-  \,\Big) \nonumber \\
-  &\hspace{12pt}
-  +\f{\dt}{w_{k_{3}}\,b(x_{k_{1}}^{1})\,c(x_{k_{2}}^{2})\,\dx^{3}}
-  \sum_{q_{3}=1}^{N}w_{q_{3}}\,\bF^{3}(x_{q_{3}}^{3},\tilde{\bx}_{\tilde{\bk}_{3}}^{3})\,
-  \pderiv{\ell_{k_{3}}}{\eta^{3}}(\eta_{q_{3}}^{3})
-  +\dt\,\bS(\bU_{\bk}^{n}).  
-\end{align}
+\subsection{Source Terms}
+\label{sec:sourceTerms}
 
@@
 
-\section{Slope Limiters}
+\section{Polynomial Limiting}
+
+\subsection{Slope Limiters}
+
+\subsection{Positivity Limiters}
+
+\section{Equation of State (EoS)}
+
+\section{Gravity Solver: Finite Element Method}
+
+To solve Poisson's equation given by Eq.~\eqref{eq:poisson}, we use the finite element method (FEM).  
+\ee{Nick fills in here}.
+
+\section{Benchmark Problems}
+
+\subsection{Smooth Problem: Linear Waves}
+
+\subsection{Riemann Problems}
+
+\subsubsection{Interacting Blast Waves}
+
+\subsubsection{Shock-Entropy Wave Interaction}
+
+\subsubsection{Sedov Blast Wave}
+
+\subsubsection{Riemann Problem with Tabulated Nuclear EoS}
+
+\subsection{Gravity Problems}
+
+\subsubsection{Homogeneous Sphere}
+
+\subsubsection{Hydrostatic Polytrope}
+
+\subsubsection{Evrard's Collapse Test}
+
+\subsubsection{Stationary Accretion Shock}
+
+\section{Miniapp: Adiabatic Collapse of Stellar Iron Core}
 

### 2017-03-21 Documents/M1/dgM1Curvilinear.tex
Updates to documents

@@
 where superscripts $-/+$, e.g., in the arguments of $\bcM_{\DG}(x^{i,-/+},\tilde{\bx}^{i})$, indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
-For example, the simple Lax-Friedrichs flux, which we use in this paper, is given by
+For example, the simple Lax-Friedrichs (LF) flux, which we have implemented, is given by
 \begin{equation}
-  \vect{f}^{i}(\bcM^{-},\bcM^{+})
+  \vect{f}^{\mbox{\tiny LF},i}(\bcM^{-},\bcM^{+})
   =\f{1}{2}\,\big(\,\bcF^{i}(\bcM^{-})+\bcF^{i}(\bcM^{+})-\alpha^{i}\,(\,\bcM^{+}-\bcM^{-}\,)\,\big),
@@
 where $\alpha^{i}=||\mbox{eig}\big(\partial\bcF^{i}/\partial\bcM\big)||_{\infty}$ is the largest eigenvalue of the flux jacobian.  
-For classical neutrinos, which propagate at the speed of light, we take $\alpha^{i}=1$.
+For classical neutrinos, which propagate at the speed of light, we take $\alpha^{i}=1$ (i.e., the global LF flux).  
+We have also implemented the Harten-Lax-van Leer (HLL) flux
+\begin{equation}
+  \vect{f}^{\mbox{\tiny HLL},i}(\bcM^{-},\bcM^{+})
+  =
+\end{equation}
 
@@
 
-\section{Semi-Implicit Time Integration}
+\section{Time Integration}
 
 For time integration we employ the method lines.  
-Having specified the spatial discretization for the advection terms, we consider the discretized moment equations in Eq.~\eqref{eq:semidiscreteDiscretized} as a system of ordinary differential equations (ODEs) to evolve forward in time, and write
+Having specified the spatial discretization for the advection terms and the representation of the collision terms, we consider the discretized moment equations in Eq.~\eqref{eq:semidiscreteDiscretized} as a system of ordinary differential equations (ODEs) to evolve forward in time, and write
 \begin{equation}
   d_{t}\bcM_{\bk}
-  =\bcF_{\bx}(\bcM)_{\bk}+\bcC(\bcM)_{\bk},
+  =\bcF_{\bx}(\bcM)_{\bk}+\bcC(\bcM)_{\bk}
+  \equiv\bcL(\bcM)_{\bk},
   \label{eq:momentEquationsODEs}
 \end{equation}
-where the operator $\bcF_{\bx}:\bbR^{d+1}\to\bbR^{d+1}$ represents the discretization of the spatial divergence operator.
+where the operator $\bcF_{\bx},\bcC:\bbR^{d+1}\to\bbR^{d+1}$ represents the discretization of the spatial divergence operator and the collision operator modeling neutrino-matter interactions, respectively.
+(In the following, to simplify notation, we drop the spatial subscript $\bk$, but note that a system of ODEs is to solved for each spatial point.)
+
+\subsection{Explicit Integration Scheme: SSP-RK Methods}
+\label{sec:explicitTime}
+
+For non-stiff problems, we employ the strong stability-preserving Runge-Kutta (SSP-RK) methods \citep[e.g.,][]{gottlieb_etal_2001}, which, for evolving the moments from $t^{n}$ to $t^{n+1}=t^{n}+\dt$ ($\bcM^{n}\to\bcM^{n+1}$), take the general form
+\begin{align}
+  \bcM^{(0)}
+  &=\bcM^{n}, \\
+  \bcM^{(i)}
+  &=\sum_{k=1}^{i-1}\alpha_{ik}\,\big[\,\bcM^{(k)}+\beta_{ik}\,\dt\,\bcL(\bcM^{(k)})\,\big], \quad i=1,\ldots,m 
+  \label{eq:ssprkStages} \\
+  \bcM^{n+1}
+  &=\bcM^{(m)}.  
+\end{align}
+For second- and third-order temporal accuracy (denoted SSP-RK2 and SSP-RK3, respectively), the coefficient matrices $\alpha_{ik}$ and $\beta_{ik}$ are given in Table~\ref{tab:ssprkCoefficients}.  
+Note that $\alpha_{ik},\beta_{ik}\ge0$ and $\sum_{k}\alpha_{ik}=1~\forall i$, so that the RK stages in Eq.~\eqref{eq:ssprkStages} are simply convex combinations of forward Euler steps with time step $\beta_{ik}\,\dt$ \citep{shuOsher_1988}.
+
+\begin{table}
+  \begin{center}
+  \caption{Optimal coefficients for SSP-RK Methods \citep{shuOsher_1988} \label{tab:ssprkCoefficients}}
+  \begin{tabular}{cccccccccccccccccc}
+    \midrule
+     SSP-RK2 & $\alpha_{ik}$ & & & & $\beta_{ik}$ & & & SSP-RK3 & $\alpha_{ik}$ & & & & $\beta_{ik}$ \\
+    \midrule
+    \midrule
+      & $1$ & & & & 1 & & & & 1 & & & & 1 \\  
+      & $1/2$ & $1/2$ & & & $0$ & $1$ & & & $3/4$ & $1/4$ & & & 0 & 1  \\
+      & & & & & & & & & $1/3$ & 0 & $2/3$ & & 0 & 0 & 1 \\ 
+    \midrule
+    \midrule
+  \end{tabular}
+  \end{center}
+\end{table}
+
+\subsection{Semi-Implicit Runge-Kutta Methods}
+\label{sec:semiImplicitTime}
+
+For stiff problems, the explicit methods in Section~\ref{sec:explicitTime} impose a severe restriction on the time step for numerical stability.  
+In essence, the time step must be chosen small enough to resolve the collision time (the time between subsequent neutrino-matter interactions), which is much shorter than the streaming time (induced by $\bcF_{\bx}$) in regions of dense nuclear matter in a proto-neutron star.
+
+To overcome this time step restriction, we integrate the collision term with implicit methods.  
+Following \citet{chertock_etal_2015}, we define the forward Euler stages in Eq.~\eqref{eq:ssprkStages}
+\begin{equation}
+  \bcM_{ik}^{\mbox{\tiny FE}}
+  =\bcM^{(k)}+\beta_{ik}\,\dt\,\big(\,\bcF_{\bx}(\bcM^{(k)})+\bcC(\bcM^{(k)})\,\big).  
+\end{equation}
+The semi-implicit Runge-Kutta (SIRK) method is obtained by substituting $\bcM_{ik}^{\mbox{\tiny FE}}\to\bcM_{ik}^{\mbox{\tiny SI}}$, where $\bcM_{ik}^{\mbox{\tiny SI}}$ is obtained by solving the implicit equation
+\begin{equation}
+  \bcM_{ik}^{\mbox{\tiny SI}}
+  =\bcM^{(k)}+\beta_{ik}\,\dt\,\big(\,\bcF_{\bx}(\bcM^{(k)})+\bcC(\bcM_{ik}^{\mbox{\tiny SI}})\,\big).  
+\end{equation}
+As discussed by \citet{chertock_etal_2015}, the time-integration method using Eq.~\eqref{eq:ssprkStages}, with $\bcM_{ik}^{\mbox{\tiny FE}}$ replaced by $\bcM_{ik}^{\mbox{\tiny SI}}$, is at most first-order accurate in time.
+To increase the temporal accuracy to second order, \citet{chertock_etal_2015} propose a correction step to be applied after the last stage.  
+We defer the development of the correction step, and use the first-order accurate time integrator for stiff problems.  
+We note that the SIRK method reduces to the SSP-RK methods in Section~\ref{sec:explicitTime} when $\bcC=0$.
 
@@
 First we consider test problems in the streaming limit.  
-In this case we use the explicit SSP-RK time integrators.  
+In this case we use the explicit SSP-RK time integrators in Section~\ref{sec:explicitTime}.  
 The 2-stage and 3-stage methods are denoted SSP-RK2 and SSP-RK3, respectively.  
@@
 
-This problem is taken from \citet{pons_etal_2000}
+This problem in spherical symmetry is taken from \citet{pons_etal_2000}, and consists of a gaussian-shaped wave propagating in the radial direction.  
+The computational domain is given by $D=\{r:r\in[0.2,10.2]\}$.  
+The analytical solution is given by
+\begin{equation}
+  \cJ(r,t)=\cH_{r}(r,t)
+  =\exp\big[-\big(r-t\big)^{2}\big]/r^{2}.  
+\end{equation}
+We let the boundary conditions be given by the analytical solution, and integrate in time from $t=0$ to $t=7$.
+
+Snapshots of the solution ($\cJ$ versus $r$), obtained with the DG(2)+RK3 scheme, are shown in Figure~\ref{fig:sphericalWave} for $t=\{2.5,3.5,5.0,7.0\}$ (open circles).  
+For comparison, the analytical solution is plotted with dotted lines.
 
@@
   \begin{center}
-    \includegraphics[scale=0.5]{./Figures/RiemannProblem1D}
+    \begin{tabular}{cc}
+      \includegraphics[scale=0.4]{./Figures/RiemannProblem1D} &
+      \includegraphics[scale=0.4]{./Figures/RiemannProblem1D_Limiters}
+    \end{tabular}
   \end{center}
@@
     \begin{tabular}{cc}
-      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-4_Density} &
-      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-6_Density} \\
-      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-4_FluxFactor} &
-      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-6_FluxFactor} \\
-      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-4_EddingtonFactor} &
-      \includegraphics[scale=0.32]{./Figures/HomogeneousSphere1D_Chi_1e-6_EddingtonFactor}
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere1D_Chi_1e-4_Density} &
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere1D_Chi_1e-6_Density} \\
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere1D_Chi_1e-4_FluxFactor} &
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere1D_Chi_1e-6_FluxFactor} \\
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere1D_Chi_1e-4_EddingtonFactor} &
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere1D_Chi_1e-6_EddingtonFactor}
     \end{tabular}
@@
 \section{Mini-app: Transport Problems with Tabulated Neutrino Opacities}
+
+\subsection{Homogeneous Sphere}
+
+\begin{table}
+  \caption{Parameters for homogeneous sphere problem with tabulated opacities.}
+  \begin{tabular}{ccccc}
+    Model & $\rho$ [g~cm$^{-3}$] & $T$ [MeV] & $Y_{e}$ & $\mu_{\nu}$ [MeV] \\
+    \midrule \midrule
+    A & $1.0\times10^{14}$ & 21.0  & 0.25 &   90.65 \\
+    B & $1.0\times10^{13}$ & 16.0 & 0.14 &     4.80 \\
+    C & $1.0\times10^{12}$ &   8.0 & 0.12 & -   0.57 \\
+    D & $1.0\times10^{11}$ &   8.0 & 0.15 & - 10.87 \\
+    \midrule \midrule
+  \end{tabular}
+\end{table}
+
+\subsection{Diffuse Scattering}
+
+\subsection{Deleptonization}
 

### 2017-04-03 Documents/Euler/Benchmarks1D/draft.tex
new figures for 11
changes to section 11 in document

@@
 \end{figure}
-
+Subsequent runs of this test varied the values of $beta_TVB$ and $beta_TVD$, while maintaining the third order method.
+Lower values of $beta_TVB$ give more accurate results, with fewer, smaller oscillations appearing.
+Variations in $beta_TVD$ have some effect, but not a great one.
+A few of the oscillations appear larger with $beta_TVD$ set to 1.0, but the difference is not especially large.
+\begin{figure}[h]
+  \begin{center}
+     \includegraphics[width=.95\textwidth]{11_300zoom.png}	
+	\begin{tabular}{cc}
+     \includegraphics[width=.475\textwidth]{11_1zoom.png}
+     \includegraphics[width=.475\textwidth]{11_2zoom.png}	
+    \end{tabular}
+  \end{center}
+  \caption{Zoomed results for test 11 at $t=1$, computed with 400 cells and the third order method.
+The top panel shows results when $beta_TVB$ is set to 300, with varying values of $beta_TVD$: 1.0 (dotted blue), 1.5 (dashed green) and 2.0 (solid red).
+The bottom two panels show results when $beta_TVD$ is held constant, with varying values of $beta_TVB$: 0 (solid red), 10 (dashed green), 50 (dotted blue), and 300 (dash-dotted pink).
+$beta_TVD$ is set to 1.0 in the right panel and 2.0 in the left panel.}
+\end{figure}
 \clearpage

### 2017-04-03 Documents/M1/dgM1Curvilinear.tex
Adding figures for transport problems

@@
 
+\ee{Ran write about tabulated B85 absorption and scattering opacities.}
+
 \clearpage
@@
 
-\subsection{Homogeneous Sphere}
-
 \begin{table}
-  \caption{Parameters for homogeneous sphere problem with tabulated opacities.}
+  \caption{Parameters used for problems with tabulated opacities. \label{tab:tabulatedModels}}
   \begin{tabular}{ccccc}
@@
 
+\subsection{Homogeneous Sphere}
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_Opacities} &
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_BaseSpectra} \\
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_B} &
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_D}
+    \end{tabular}
+  \end{center}
+  \caption{Results from solving the multi-group Homogeneous sphere problem with the DG(1)+SIRK2 method using $100$ elements.
+    In the upper left panel we plot the absorption opacity versus energy $\epsilonNu$ using the values for $\rho$, $T$, and $Y_{e}$ listed in Table~\ref{tab:tabulatedModels}.
+In the upper right panel, we plot the spectral number density versus energy at the end of the computations for a radius of $52.5$~km solid lines.
+The corresponding Fermi-Dirac spectrum is also plotted (dashed lines).
+}
+  \label{fig:homogeneousSphere1D_weaklib}
+\end{figure}
+
 \subsection{Diffuse Scattering}
@@
 \subsection{Deleptonization}
+
+We conclude with a problem mimicking the deleptonization of a collapsed stellar core.  
+To this end, we adopt an analytic density profile
+\begin{equation}
+  \rho(r)=\big[\,1-\Theta(r)\,\big]\,\rho_{1}(r)+\Theta(r)\,\rho_{2}(r)
+  \label{eq:densityProfile}
+\end{equation}
+where the function $\Theta(r)=0.5\times\big[\,1.0+\tanh\big(\,(r-r_{0})/R_{0}\,\big)\,\big]$ transitions smoothly between two density profiles, given by a Gaussian in the central region and a polynomial at larger radii; i.e.,
+\begin{align}
+  \rho_{1}(r)
+  &=\rho_{1,0}\times\exp\big[-(r/R_{1})^{2}\big]
+  \label{eq:densityProfile1} \\
+  \rho_{2}(r)
+  &=\rho_{2,0}\times\big(r/R_{2}\big)^{\alpha},
+  \label{eq:densityProfile2}
+\end{align}
+where $\rho_{1,0}>\rho_{2,0}$ and $\alpha<0$.  
+We set $\rho_{1,0}=4.5\times10^{14}$, $\rho_{1,0}=1.0\times10^{13}$, $\alpha=-4$, and $R_{1}=10$~km.  
+Then, by imposing $\rho_{1}(R_{2})=\rho_{2}(R_{2})$, we find $R_{2}=R_{1}\sqrt{\ln(\rho_{1,0}/\rho_{2,0})}\approx19.5$~km.  
+We also set $r_{0}=R_{2}$ and $R_{0}=1$~km.  
+With these parameters, the density profile given by Eqs~\eqref{eq:densityProfile}, \eqref{eq:densityProfile1}, and \eqref{eq:densityProfile2} provides a reasonable approximation to the density profile in the post-bounce phase of a supernova realistic model (cf.
+Figure~\ref{fig:analyticDensityProfile}).
+
+\begin{figure}
+  \begin{center}
+      \includegraphics[scale=0.5]{./Figures/AnalyticDensityProfile}
+  \end{center}
+  \caption{Density profile used in the deleptonization problem (solid black line; cf. Eq.~\eqref{eq:densityProfile}).  
+  It is composed of a Gaussian profile for radii $\lesssim20$~km (dashed black line), and a power law, with $\rho\propto r^{-4}$, for larger radii (dotted black line).  
+  The density profile from a full physics core-collapse supernova simulation at $100$~ms after core bounce is also plotted (solid red line).  }
+  \label{fig:analyticDensityProfile}
+\end{figure}
 

### 2017-04-03 Documents/Euler/Benchmarks1D/draft.tex
formatting fixes on test 11

--- 2017-03-21 Documents/Euler/Benchmarks1D/draft.tex
@@
 
+Subsequent runs of this test varied the values of $\beta_{\mbox{\tiny TVB}}$ and $\beta_{\mbox{\tiny TVD}}$, while maintaining the third order method.
+Lower values of $\beta_{\mbox{\tiny TVB}}$ give more accurate results, with fewer, smaller oscillations appearing.
+Variations in $\beta_{\mbox{\tiny TVD}}$ have some effect, but not a great one.
+A few of the oscillations appear larger with $\beta_{\mbox{\tiny TVD}}$ set to 1.0, but the difference is not especially large.
+
+\begin{figure}[h]
+  \begin{center}
+     \includegraphics[width=.95\textwidth]{11_300zoom.png}	
+	\begin{tabular}{cc}
+     \includegraphics[width=.475\textwidth]{11_1zoom.png}
+     \includegraphics[width=.475\textwidth]{11_2zoom.png}	
+    \end{tabular}
+  \end{center}
+  \caption{Zoomed results for test 11 at $t=1$, computed with 400 cells and the third order method.
+The top panel shows results when $\beta_{\mbox{\tiny TVB}}$ is set to 300, with varying values of $\beta_{\mbox{\tiny TVD}}$: 1.0 (dotted blue), 1.5 (dashed green) and 2.0 (solid red).
+The bottom two panels show results when $\beta_{\mbox{\tiny TVD}}$ is held constant, with varying values of $\beta_{\mbox{\tiny TVB}}$: 0 (solid red), 10 (dashed green), 50 (dotted blue), and 300 (dash-dotted pink).
+$\beta_{\mbox{\tiny TVD}}$ is set to 1.0 in the right panel and 2.0 in the left panel.}
+\end{figure}
 \clearpage

### 2017-04-14 Documents/M1/dgM1Curvilinear.tex
Committed as a sample of neutrino opacity section.

@@
 
-\ee{Ran write about tabulated B85 absorption and scattering opacities.}
+%\ee{Ran write about tabulated B85 absorption and scattering opacities.}
+
+Given by \citet{bruenn_1985}, the absorption opacity of neutrino $\chi$ 
+\begin{equation}
+  \chi(\epsilonNu,\bU) = \dfrac{1}{\lambda(\epsilonNu,\bU)} + j(\epsilonNu,\bU), 
+\end{equation}
+where $j(\epsilonNu,\bU) $ is the neutrino emissivity
+\begin{equation}
+j = j_{nucleon} + j_{nuclear},
+\end{equation}  
+and $\lambda(\epsilonNu,\bU)$ is the neutrino absorption mean free path.
+They have the following relation:
+\begin{equation}
+\dfrac{1}{\lambda(\epsilonNu,\bU)} = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T} j(\epsilonNu,\bU) .
+\end{equation}
+Therefore,
+\begin{equation}
+\dfrac{1}{\lambda} = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T} (j_{nucleon} + j_{nuclear} ) = (\dfrac{1}{\lambda})_{nucleon} + (\dfrac{1}{\lambda})_{nuclear}.
+\end{equation}
+The two terms of electron-neutrino absorption on nucleons are
+ \begin{align}
+    (\dfrac{1}{\lambda})_{nucleon}(\epsilonNu,\bU) & = \dfrac{G^2}{\pi} \eta_{np}(g_V^2+3g_A^2)[1-F_e(\varepsilon+Q)](\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2},\\
+    j_{nucleon}(\epsilonNu,\bU) &= \dfrac{G^2}{\pi}\eta_{pn}(g_V^2+3g_A^2)F_e(\varepsilon+Q)(\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2}.
+\end{align}
+And the two terms of electron-neutrino absorption on nuclear are
+\begin{align}
+    (\dfrac{1}{\lambda})_{nuclear}(\epsilonNu,\bU) & = \dfrac{G^2}{\pi} n_A e^{\beta (\mu_n -\mu_p -Q')} g^2_A \dfrac{2}{7} N_p(Z) N_n(N)[1-F_e(\varepsilon+Q')](\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} ,\\
+    j_{nuclear}(\epsilonNu,\bU) &=\dfrac{G^2}{\pi} n_A g^2_A \dfrac{2}{7} N_p(Z) N_n(N)F_e(\varepsilon+Q')(\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} .
+\end{align}
+
+The total opacity $\kappa(\epsilonNu,\bU)=\chi(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$, and $\sigma(\epsilonNu,\bU)$ is the scattering opacities.
 

### 2017-04-24 Documents/Euler/Benchmarks1D/draft.tex
edits to beginning

@@
 The toolkit for high-order neutrino-radiation hydrodynamics (\thornado) is a code for astrophysical radiation-hydrodynamics based on high-order Runge-Kutta Discontinuous Galerkin (RKDG) methods.  
-It currently solves the Euler equations for fluid dynamics and the two-moment ($M_{1}$) approximation of the radiative transfer equation. 
-In this document, we benchmark the algorithms for solving the Euler equations.  
-An extensive set of one-dimensional Riemann problems with known exact solutions were run, and the \thornado\ results were graphed and compared to exact solutions in cases where they exist. 
+It currently solves the Euler equations for fluid dynamics and the two-moment ($M_{1}$) approximation of the radiative transfer equation, both in the non-relativistic limits. 
+In this document, we benchmark the algorithms for solving the non-relativistic Euler equations.  
+Results from an extensive set of one-dimensional Riemann problems are compared to exact solutions in cases where they exist.
+We also show results for th interacting blast wave problem of Colella and Woodward and the shock entropy wave problem of Shu and Oster.
 \end{abstract}
@@
 
-The Euler equations for fluid dynamics \citep[see, e.g.,][for details]{Leveque2002} consists of the mass equation
+The Euler equations for fluid dynamics \citep[see, e.g.,][for details]{Leveque2002} consists of the mass conservation equation
 \begin{equation}
@@
 \end{equation}
-the momentum equation
+the momentum conservation equation
 \begin{equation}
@@
 \end{equation}
-and the energy equation
+and the energy conservation equation
 \begin{equation}
@@
 \end{equation}
-where $\rho$ represents mass density, $u$ the fluid velocity, $p$ the pressure of the fluid, and $E$ the energy.  
-Equation~\eqref{eq:massConservation} describes conservation of mass, Equation~\eqref{eq:momentumConservation} describes conservation of momentum, and equation \eqref{eq:energyConservation} describes conservation of energy.
+where $\rho$ represents mass density, $u$ the fluid velocity, $p$ the fluid pressure, and $E=e+\frac{1}{2}\rho u^2$ the total energy (internal plus kinetic).  
+Equation~\eqref{eq:massConservation} expresses conservation of mass, Equation~\eqref{eq:momentumConservation} expresses conservation of momentum, and equation \eqref{eq:energyConservation} expresses conservation of energy.
 The equation of state
@@
 \end{equation}
-closes the system of equations, and links the pressure to the quantities evolved in Equations \eqref{eq:massConservation}-\eqref{eq:energyConservation}. 
+closes the system of equations, and links the pressure to the quantities evolved by Equations \eqref{eq:massConservation}-\eqref{eq:energyConservation}. 
 The ratio of specific heats, $\gamma$, is taken to be a constant.
@@
 
-The computational domain $D=\{x:x\in[x_{\mbox{\tiny L}},x_{\mbox{\tiny R}}]\}$ is subdivided into $N$ elements $I_{i}=\{x:x\in(x_{i-1/2},x_{i+1/2})\}$.  
+The computational domain $D=\{x:x\in[x_{\mbox{\tiny L}},x_{\mbox{\tiny R}}]\}$ is subdivided into $N$ elements $I_{i}=\{x:x\in(x_{i-1/2},x_{i+1/2})\}$ for $i=1,\ldots,N$.  
 The width of element $I_{i}$ is then $\Delta x_{i}=x_{i+1/2}-x_{i-1/2}$.  
@@
 To complete the spatial discretization, we use Gaussian quadratures to evaluate the integrals in Eq.~\eqref{eq:semidiscreteDG}.
-During time-integration, we apply limiters to the polynomial representation.  
-We use the TVB limiter of \citet{} to prevent oscillations near discontinuities and the positivity limiter of \citet{ZhangShu2010} to ensure that the density and pressure remain positive.
 
@@
 \end{align}
-where $\alpha_{il},\beta_{il}\ge0$ are given by Butcher tables.  
-During time integration, we apply slope and positivity limiters after each stage as a post-processing step.
+where $\alpha_{il},\beta_{il}\ge0$ are given by Butcher tables. During time-integration, we apply limiters to the polynomial representation after each stage as a post-processing step.  
+We use the TVB limiter of \citet{} to prevent oscillations near discontinuities and the positivity limiter of \citet{ZhangShu2010} to ensure that the density and pressure remain positive.
 
@@
 
-The code was tested using Riemann problems.
+The code was tested against a series of one-dimensional Riemann problems.
 The Riemann problem models a fluid in an area of one-dimensional space.
@@
 
-Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
+Several tests were used to assess the accuracy of the RKDG method implemented in thornado \citep{LiskaWendroff2003}. 
 \begin{table}[h!]
@@
 \end{table}
-$x_0$ refers to the position of the barrier. 
+TAble 1 dispplays the initial data for the Riemann problems.
+($\rho_L$, $u_L$ , $p_L$) denote the mass density, velocity, and pressure to the left of the interface at $x=x_0$;($\rho_R$, $u_R$,  $p_R$) refer to these same quantities to the right of the interface.
+The problem is advanced to time T.
 The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, $x_{\mbox{\tiny L}}=0.1$ and $x_{\mbox{\tiny R}}=0.6$ in test 9 \citep{LiskaWendroff2003}, $x_{\mbox{\tiny L}}=-5$ and $x_{\mbox{\tiny R}}=15$ in test 10, and $x_{\mbox{\tiny L}}=-15$ and $x_{\mbox{\tiny R}}=5$ in test 11 \citep{Leveque2002}.
-\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}
+%\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}
 

### 2017-05-11 Documents/M1/dgM1Curvilinear.tex
Completed Ab/Em part in chapter 6. Isoenergetic scattering needs to be added.

--- 2017-04-03 Documents/M1/dgM1Curvilinear.tex
@@
 
-\ee{Ran write about tabulated B85 absorption and scattering opacities.}
-
+%\ee{Ran write about tabulated B85 absorption and scattering opacities.}
+
+Given by \citet{bruenn_1985}, the absorption opacity of neutrino $\chi$ 
+\begin{equation}
+  \tilde{\chi}(\epsilonNu,\bU) = \chi(\epsilonNu,\bU) + \eta(\epsilonNu,\bU), 
+\end{equation}
+where $\eta(\epsilonNu,\bU) $ is the neutrino emissivity
+\begin{equation}
+\eta = \eta_{nucleon} + \eta_{nuclear},
+\end{equation}  
+and $ \chi(\epsilonNu,\bU)$ is the neutrino absorptivity, which is the inverse of neutrino absorption mean free path.
+They have the following relation:
+\begin{equation}
+\chi(\epsilonNu,\bU) = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T} \eta(\epsilonNu,\bU). 
+\end{equation}
+
+Therefore,
+\begin{equation}
+\chi = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T} (\eta_{nucleon} + \eta_{nuclear} ) = \chi_{nucleon} + \chi_{nuclear}.
+\end{equation}
+The two terms of electron-neutrino absorption on nucleons are
+ \begin{align}
+    \chi_{nucleon}(\epsilonNu,\bU) & = \dfrac{G^2}{\pi} \eta_{np}(g_V^2+3g_A^2)[1-F_e(\varepsilon+Q)](\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2} \label{eq:nucleonabsorption} ,\\
+    \eta_{nucleon}(\epsilonNu,\bU) &= \dfrac{G^2}{\pi}\eta_{pn}(g_V^2+3g_A^2)F_e(\varepsilon+Q)(\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2} \label{eq:nucleonemissivity} ,
+\end{align}
+and the two terms of electron-neutrino absorption on nuclear are
+\begin{align}
+    \chi_{nuclear}(\epsilonNu,\bU) & = \dfrac{G^2}{\pi} n_A e^{(\mu_n -\mu_p -Q')/k_B T} g^2_A \dfrac{2}{7} N_p(Z) N_h(N)[1-F_e(\varepsilon+Q')](\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} \label{eq:nuclearabsorption} ,\\
+    \eta_{nuclear}(\epsilonNu,\bU) &=\dfrac{G^2}{\pi} n_A g^2_A \dfrac{2}{7} N_p(Z) N_h(N)F_e(\varepsilon+Q')(\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} \label{eq:nuclearemissivity},
+\end{align} 
+where $g_V = 1$ and $g_A =1.23$ are form factors resulting from virtual strong-interaction processes, $M_e = 0.511$ MeV is the electron rest energy, $Q = 1.2935$ MeV is the difference between the neutron and proton rest energies, $\mu_n$ and $\mu_p$ are the neutron and proton chemical potential, respectively.
+And $Q'$ is defined by $Q' = \mu_n -\mu_p + \Delta$, where $\Delta=3$MeV is the energy of the $1f_{5/2}$ level above the ground state.
+
+In Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity}, $F_e(E)$ is the Fermi-Dirac distribution function:
+\begin{align}
+F_e(E) = \dfrac{1}{e^{(E-\mu_e)/k_B T} + 1},
+\end{align}
+where $\mu_e$ is the electron chemical potential.
+
+In Eq.~\eqref{eq:nucleonabsorption} and ~\eqref{eq:nucleonemissivity}, $\eta_{np}$ and $\eta_{pn}$ take into account the nucleon final-state blocking and equal to $n_n$ and $n_p$, the nucleon number density, when the nucleons are nondegenerate, respectively.
+\begin{align}
+n_p & =  \dfrac{X_p \rho}{m_p} \\
+n_n & =  \dfrac{X_n \rho}{m_n},
+\end{align}
+where $X_p$ and $X_n$ are the proton and neutron fractions, respectively.
+
+In Eq.~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity}, $n_A$ is the nuclei number density and $n_A = \dfrac{\rho X_H}{m_B A}$.
+The function $N_p$ is the number of protons in the single-particle $1f_{7/2}$ level and $N_h$ is the number of neutron holes in the single-particle $1f_{5/2}$ level.
+As a crude estimate of $N_p$ and $N_h$, a zero-order shell model predicts that
+\[   
+N_p(Z) = 
+     \begin{cases}
+       0, &\quad Z<20\\
+       Z-20, &\quad 20<Z<28 \\
+       8, &\quad Z>28,\\
+     \end{cases}
+\]
+and
+\[   
+N_h(N) = 
+     \begin{cases}
+       6, &\quad N<34\\
+       40-N, &\quad 34<N<40 \\
+       0, &\quad N>40.\\
+     \end{cases}
+\]
+
+The factor $G^2$ in Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity} is the Fermi constant [$G=(1.015\pm 0.03)\time 10^5 M_p^{-2}$] with the value
+\begin{equation}
+	G^2 = \left[ \dfrac{1}{(\hbar c)^4} \right] G^2 = 5.18 \times 10^{-44} MeV^{-2}cm^2, 
+\end{equation}
+giving $\chi$ and $\eta$ the required units of $cm^{-1}$.
+
+The sum of Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity} gives the explicit expression of the absorption opacity of neutrino $\chi$ .
+
+The total opacity $\kappa(\epsilonNu,\bU)=\chi(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$, and $\sigma(\epsilonNu,\bU)$ is the scattering opacities.
+The scattering opacities $\sigma(\epsilonNu,\bU)$ contains isoenergetic scattering opacities and have a integral form in the Boltzmann equation: if we include emission, absorption, and isoenergetic scattering of neutrino by nucleons and nuclei, the simplified Boltzmann equation is
+\begin{align}
+\dfrac{\partial f(\epsilonNu,\bU)}{\partial t} = \eta(\epsilonNu,\bU) - \tilde{\chi}(\epsilonNu,\bU)f(\epsilonNu,\bU) & + \dfrac{1}{h^3} \epsilonNu^2 \int d\mu^\prime_0 R_{IS}( \mu^\prime_0, \mu_0,\epsilonNu, \bU) f(\mu^\prime_0, \epsilonNu,\bU) \nonumber \\
+	& - \dfrac{1}{h^3} \epsilonNu^2 f(\epsilonNu,\bU)\int d\mu^\prime_0 R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) .
+\end{align}
+
+The last two terms are contributions from isoenergetic scattering of neutrino by nucleons and nuclei.
+The isoenergetic scattering kernel $R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
+\begin{align}
+R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) & = R_{IS}^{nucleons}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) +  R_{IS}^{nuclei}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)\\
+& = \int_{0}^{2\pi}d
+\end{align}
 \clearpage

### 2017-06-01 Documents/M1/dgM1Curvilinear.tex
Updates to manuscript.

@@
 \newcommand{\sumx}{\sum_{i=1}^{d}}
+\newcommand{\NES}{\mbox{\tiny NES}}
 
@@
 For general curvilinear spatial coordinates $\{x^{i}\}$, the two-moment model for radiation transport takes the form \citep[see, e.g.,][for fully general relativistic treatments]{shibata_etal_2011,cardall_etal_2013a}
-\begin{equation}
-  \f{1}{\sqrt{\gamma}}\pderiv{}{t}\Big(\,\sqrt{\gamma}\,\cJ\,\Big)
-  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\cH^{i}\,\Big)=\chi\,\big(\cJ_{0}-\cJ\big),
+\begin{align}
+  &\f{1}{\sqrt{\gamma}}\pderiv{}{t}\Big(\,\sqrt{\gamma}\,\cJ\,\Big)
+  +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\cH^{i}\,\Big)
+  =\tilde{\chi}\,\big(\cJ_{0}-\cJ\big) \nonumber \\
+  &\hspace{12pt}
+  +\big(4\pi-\cJ\big)\int_{\bbR^{+}}R^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')\,dV_{\epsilonNu'}
+  -\cJ\int_{\bbR^{+}}R^{\Out}(\epsilonNu,\epsilonNu')\,\big(4\pi-\cJ(\epsilonNu')\big)\,dV_{\epsilonNu'},
   \label{eq:momentEquationEnergy}
-\end{equation}
-\begin{equation}
-  \f{1}{\sqrt{\gamma}}\pderiv{}{t}\Big(\,\sqrt{\gamma}\,\cH_{j}\,\Big)
+\end{align}
+\begin{align}
+  &\f{1}{\sqrt{\gamma}}\pderiv{}{t}\Big(\,\sqrt{\gamma}\,\cH_{j}\,\Big)
   +\f{1}{\sqrt{\gamma}}\pderiv{}{x^{i}}\Big(\,\sqrt{\gamma}\,\cK^{i}_{~j}\,\Big)
-  =\f{1}{2}\,\cK^{ik}\,\pderiv{\gamma_{ik}}{x^{j}}-\kappa\,\cH_{j},
+  =\f{1}{2}\,\cK^{ik}\,\pderiv{\gamma_{ik}}{x^{j}}-\kappa\,\cH_{j} \nonumber \\
+  &\hspace{12pt}
+  -\cH_{j}\int_{\bbR^{+}}\big[\,R^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')+R^{\Out}(\epsilonNu,\epsilonNu')\big(4\pi-\cJ(\epsilonNu')\big)\,\big]\,dV_{\epsilonNu'},
   \label{eq:momentEquationMomentum}
-\end{equation}
+\end{align}
 where $\cJ$, $\cH^{i}$, and $\cK^{ij}$ are defined as angular moments of a positive neutrino distribution function $f(\omegaNu,\epsilonNu,\bx,t)$
@@
 
-To model neutrino matter interactions, we include emission and absorption, and isotropic, elastic scattering on nucleons and nuclei.  
-On the right-hand sides of Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}, $\chi(\epsilonNu,\bU)$ and $\kappa(\epsilonNu,\bU)=\chi(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$ are absorption and total (absorption plus scattering) opacities, respectively.
+To model neutrino matter interactions, we include emission and absorption, (isotropic) elastic scattering on nucleons and nuclei, and neutrino-electron scattering (NES).  
+On the right-hand sides of Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}, $\tilde{\chi}(\epsilonNu,\bU)$ and $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$ are absorption and total (absorption plus scattering) opacities, respectively.
+The absorption opacity $\tilde{\chi}$ is corrected for stimulated absorption \citep[cf.][]{mezzacappaBruenn_1993a}.  
+The NES rates $R^{\In}$ and $R^{\Out}$ are obtained by expanding the full kernels in a Legendre series, retaining only the isotropic part \citep[see, e.g.,][]{cernohorsky_1994}, and the integrals extend over all energies $\bbR^{+}=\{\epsilonNu~|~\epsilonNu\in[0,\infty)\}$.
+The energy volume element is $dV_{\epsilonNu}=\epsilonNu^{2}d\epsilonNu$.  
 The opacities depend on the neutrino energy and the local thermodynamic state of the fluid $\bU=(\rho,T,Y_{e})^{T}$, where $\rho$ is the (baryon) mass density, $T$ the temperature, and $Y_{e}$ the electron fraction.
-We use the opacities given by \citet{bruenn_1985}.  
+For simplicity we consider a single neutrino species (electron neutrinos), and we use opacities given by \citet{bruenn_1985}; see Section~\ref{sec:opacities} for further details.  
 In Eq.~\eqref{eq:momentEquationEnergy}, the equilibrium density $\cJ_{0}=4\pi\,f_{0}(\epsilonNu,\bU)$ is computed from the angular moment of the isotropic Fermi-Dirac distribution
@@
 \end{equation}
-where $k_{\mbox{\tiny B}}$ is Boltzmann's constant, and $\mu_{\nu}$ is the neutrino chemical potential.
+where $k_{\mbox{\tiny B}}$ is Boltzmann's constant, and $\mu_{\nu}=\mu_{p}-\mu_{n}+\mu_{e}$ is the neutrino chemical potential.  
+(The chemical potentials of protons, neutrons, and electrons are denoted by $\mu_{p}$, $\mu_{n}$, and $\mu_{e}$, respectively.)
 
@@
 
-We define the geometry sources in Eq.~\eqref{eq:momentEquationMomentum} by
+For the forthcoming description it is useful to write the moment equations in a more compact form.  
+To this end, we define the geometry sources in Eq.~\eqref{eq:momentEquationMomentum} by
 \begin{equation}
@@
 \end{equation}
-Then, by defining the vector of evolved moments $\bcM=\big(\,\cJ,\,\cH_{1},\,\cH_{2},\,\cH_{3}\,\big)^{T}$, the vector of geometry sources $\bcG(\bcM)=\big(\,0,\,\cG_{1},\,\cG_{2},\,\cG_{3}\,\big)^{T}$, the vector of collision sources $\bcC(\bcM)=\big(\,\chi\,(\cJ_{0}-\cJ),\,-\kappa\,\cH_{1},\,-\kappa\,\cH_{2},\,-\kappa\,\cH_{3}\,\big)^{T}$, and the flux vectors $\bcF^{i}(\bcM)=\big(\,\cH^{i},\,\cK_{~1}^{i},\,\cK_{~2}^{i},\,\cK_{~3}^{i}\,\big)^{T}$, we write the system of equations in compact form
+(Explicit expressions for metric functions appearing in the geometry sources are listed in Table~\ref{tab:metricFunctions}.)  
+Then, by defining the vector of evolved moments $\bcM=\big(\,\cJ,\,\bcH\,\big)^{T}$, the vector of geometry sources $\bcG(\bcM)=\big(\,0,\,\cG_{1},\,\cG_{2},\,\cG_{3}\,\big)^{T}$, the vector of collision sources $\bcC(\bcM)=\big(\,\chi\,(\cJ_{0}-\cJ)+\cL_{\NES},\,-(\kappa+\kappa_{\NES})\,\bcH\,\big)^{T}$, and the flux vectors $\bcF^{i}(\bcM)=\big(\,\cH^{i},\,\cK_{~1}^{i},\,\cK_{~2}^{i},\,\cK_{~3}^{i}\,\big)^{T}$, we write the system of equations in compact form
 \begin{equation}
@@
 \end{equation}
+Here, $\cL_{\NES}$ and $\kappa_{\NES}$ represent the integral operators appearing in Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}, respectively.  
 Eq.~\eqref{eq:momentEquationsCompact} forms the basis for developing DG methods for neutrino transport.
-
-\clearpage
 
@@
 This defines the spatial discretization of the moment equations.
-
-\clearpage
 
@@
 
-\clearpage
-
 \section{Polynomial Limiting}
@@
 \section{Neutrino Opacities}
+\label{sec:opacities}
 
@@
 \end{align}
-\clearpage
 
@@
 Results are shown in Figure~\ref{fig:streamingSineWave} and Table~\ref{tab:streamingSineWave}.  
+In Figure~\ref{fig:streamingSineWave}, results obtained using the TVD limiter (cf. Eq.~\eqref{eq:minmodB} with $M=0$) with various $\beta$ values are shown.  
+With this limiter, the accuracy of the scheme is severely compromised.  
+The accuracy can be significantly improved with the TVB limiter ($M>0$), but the proper value for $M$ is problem dependent, and difficult to set a priori.  
+Instead, we have implemented the discontinuity detector based on Harten's subcell resolution method as a ``troubled-cell'' indicator \citep{harten_1989,qiuShu_2005}, which prevents limiting in smooth regions.
+Results using the detector (black open circles) show a significant improvement.  
+In Table~\ref{tab:streamingSineWave} we list convergence results for this latter method, which demonstrates high-order accuracy (i.e., better than second-order) when expected.  
+Unless otherwise noted, we continue to use the discontinuity detector in the remaining numerical experiments.
 
@@
   \begin{center}
-    \includegraphics[scale=0.38]{./Figures/StreamingSineWave1D}
+    \includegraphics[scale=0.78]{./Figures/StreamingSineWave1D}
   \end{center}
-  \caption{Energy density versus position after ten grid crossings ($t=10$) for the streaming sine wave problem computed with the DG(2)+RK3 scheme using 16 elements.
-We compare results obtained using various limiter parameters (see text for details) with the analytic solution (dotted line).}
+  \caption{Particle density versus position after ten grid crossings ($t=10$) for the streaming sine wave problem computed with the DG(2)+RK3 scheme using 16 elements.  
+  We compare results obtained using various limiter parameters (open circles; see text for details) with the analytic solution (dotted line).  
+  Results obtained using the discontinuity detector (D) is denoted with black open circles.}
   \label{fig:streamingSineWave}
@@
 For comparison, the analytical solution is plotted with dotted lines.  
+There is good agreement between the numerical and analytical solutions.  
+In Table~\ref{tab:sphericalWave} we list convergence results obtained with the various schemes.  
+High-order accuracy is achieved with the DG(2)+RK3 and DG(3)+RK3 schemes.
 
@@
   \begin{center}
-    \includegraphics[scale=0.38]{./Figures/GaussianSphericalWave1D}
+    \includegraphics[scale=0.78]{./Figures/GaussianSphericalWave1D}
   \end{center}
@@
   \caption{$L^{\infty}$ error and convergence rates for the spherical wave problem.}
+  \label{tab:sphericalWave}
   \begin{tabular}{ccccccccc}
@@
 
-To test the ability of the DG method to capture discontinuities, we solve the Riemann problem presented by \citet{OHF2012}.  
-To compare with their results, we use the Eddington factor due to Levermore \citep{levermore_1984}
+To test the ability of the DG method to capture discontinuities without spurious oscillations, we solve the Riemann problem presented by \citet{OHF2012}.  
+This problem is also challenging because the condition $\cJ-|\bcH|>0$ can be violated.  
+To compare with the results of \citet{OHF2012}, we use the Eddington factor due to Levermore \citep{levermore_1984}
 \begin{equation}
@@
 Results for $t=0.1$ are shown in Figure~\ref{fig:riemannProblem}.  
+In the left panel we plot the number density and flux, obtained with the third-order method (DG(2)+RK3).  
 The discontinuities remain sharp, and oscillations around the discontinuities are controlled (in part due to limiting of characteristic variables; cf. Section~\ref{sec:slopeLimiters}).  
+In the right panel we plot the number density for three computations: limiting triggered everywhere (blue), no slope limiting (positivity limiting only; red), and limiting triggered by the discontinuity detector (black).
+In the plot we have zoomed in on the discontinuity around $x=0.075$.  
+Without limiting, significant oscillations are present in the solution.  
+With the slope limiter, the oscillations are essentially removed, while using the discontinuity detector to trigger limiting maintains a sharper discontinuity than when limiting is permitted everywhere.
 
@@
   \caption{Results from the one-dimensional Riemann problem in Eq.~\eqref{eq:riemannProblem}, obtained with the DG(2)+RK3 method using $240$ elements, the HLL Riemann solver, and the Eddington factor in Eq.~\eqref{eq:eddingtonFactorLevermore}.
-  The number density $\cJ$ (black) and the number flux density $\cH_{r}$ (red) are plotted for $t=0.1$.}
+  The number density $\cJ$ (black) and the number flux density $\cH_{1}$ (red) are plotted for $t=0.1$.}
   \label{fig:riemannProblem}
@@
 
-\subsection{Diffusion Problem}
-
+\subsection{Spherical Diffusion}
+
+Next, we consider a diffusion problem in spherical symmetry, which involves a constant scattering opacity $\sigma$.  
 This problem is adapted from \citet{abdikamalov_etal_2012} \citep[see also][]{pons_etal_2000,sumiyoshiYamada_2012}.  
-
-\begin{equation}
-  \cJ(r,t)=\Big(\f{t_{0}}{t_{0}+t}\Big)^{3/2}\,\exp\Big\{\,-\f{3\,\sigma\,r^{2}}{4\,(t_{0}+t)}\,\Big\}
-\end{equation}
+For sufficiently high scattering opacity, the moment equations limit to a diffusion equation for the radiation number density.  
+With a Gaussian initial distribution for the energy density $\cJ_{0}(x)=\exp(-3\,\sigma\,r^{2}/(4\,t_{0}))$, the analytical solution to the limiting diffusion equation is given by
+\begin{equation}
+  \cJ(r,t)=\Big(\f{t_{0}}{t_{0}+t}\Big)^{3/2}\,\exp\Big\{\,-\f{3\,\sigma\,r^{2}}{4\,(t_{0}+t)}\,\Big\},
+\end{equation}
+while the number flux is obtained from $\cH_{r}=-\pd{\cJ}{r}/(3\,\sigma)$.
+
+We present two versions of this test:  one with $\sigma=10^{-5}$~cm$^{-1}$ (thin test), and one with $\sigma=10^{-1}$~cm$^{-1}$ (thick test).  
+In the thin test, the computational domain extends over $r\in[0,100]$~km, $t_{0}=0.3$~ms, and is run until $t=1$~ms.  
+In the thick test, the computational domain extends over $r\in[0,50]$~km and $t_{0}=0.3$~s, and is run until $t=1$~s.  
+In both tests we use 32 elements and the DG(2)+SIRK2 scheme.  
+With the mean-free path defined as $\lambda=1/\sigma$, the ratio of the mean-free path to the cell width $\Delta r$ is $0.32$ in the thin test, and $6.4\times10^{-5}$ in the thick test.
+
+Results are plotted in Figure~\ref{fig:diffusionProblem}.  
+There is good agreement between the numerical and analytical solutions, for both the thin and thick cases.
 
@@
       \includegraphics[scale=0.38]{./Figures/GaussianSphericalDiffusion_Kappa_1e-5_Density} &
-      \includegraphics[scale=0.38]{./Figures/GaussianSphericalDiffusion_Kappa_1e-5_Flux}
-    \end{tabular}
-  \end{center}
-  \caption{Results from the one-dimensional diffusion problem in spherical symmetry with $\sigma=10^{-5}$~cm$^{-1}$, obtained with the DG(2)+SIRK2 method using $24$ elements.  
-  The number density $\cJ$ (left panel) and the number flux density $\cH_{r}$ (right panel) are plotted for $t=0,0.3,1.0$~ms (red, blue, and black curves, respectively).  
-  Solid lines represent the analytical solution while open circles represent the element center value of the numerical solution.}
-  \label{fig:diffusionProblem1e-5}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{cc}
+      \includegraphics[scale=0.38]{./Figures/GaussianSphericalDiffusion_Kappa_1e-5_Flux} \\
       \includegraphics[scale=0.38]{./Figures/GaussianSphericalDiffusion_Kappa_1e-1_Density} &
@@
   \end{center}
-  \caption{Results similar to those displayed in Figure~\ref{fig:diffusionProblem1e-5}, but with $\sigma=10^{-1}$~cm$^{-1}$.}
-  \label{fig:diffusionProblem1e-1}
+  \caption{Results from the one-dimensional diffusion problem in spherical symmetry, obtained with the DG(2)+SIRK2 method using $32$ elements.  
+  The number density $\cJ$ (left panel) and the number flux density $\cH_{r}$ (right panel) are plotted.  
+  In the upper panels $\sigma=10^{-5}$~cm$^{-1}$, with results plotted for $t=0,0.3,1.0$~ms (red, blue, and black curves, respectively).  
+  In the lower panels $\sigma=10^{-1}$~cm$^{-1}$, with results plotted for $t=0,0.4,1.0$~s (red, blue, and black curves, respectively).  
+  Solid lines represent the analytical solution while open circles represent the element center value of the numerical solution.}
+  \label{fig:diffusionProblem}
 \end{figure}
@@
 
+For the tests in this section we employ the tabulated opacities described in Section~\ref{sec:opacities}.  
+We present two tests from the previous section (the homogeneous sphere and spherical diffusion problems), where the background is kept fixed.  
+Then we present a relaxation problem involving neutrino-electron scattering (NES) with a homogeneous background.  
+Finally, we present a deleptonization problem where the background density mimics that of a collapsed stellar core.  
+The first deleptonization problem (Em/Ab) involves emission and absorption only, while the second deleptonization problem (Full) involves the full set of opacities described in Section~\ref{sec:opacities}.
+
+When coupling neutrinos to the background fluid, the gain/loss terms involve integrals of the right-hand sides in Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum} over energy space.
+To simulate multi-group neutrino transport and compute the lepton and energy exchange with the fluid, the infinite energy domain $\bbR^{+}$ is replaced with a finite domain $D^{\epsilonNu}=\{\epsilonNu~|~\epsilonNu\in[0,\epsilonNu_{\mbox{\tiny max}}]\}$.
+The domain $D^{\epsilonNu}$ is then split up into $N_{\epsilonNu}$ energy bins $K_{i}^{\epsilonNu}=\{\epsilonNu~|~\epsilonNu\in[\epsilonNu_{i-1/2},\epsilonNu_{i+1/2}]\}$, where the width of the $i$th bin is $|K_{i}^{\epsilonNu}|=(\epsilonNu_{i+1/2}-\epsilonNu_{i-1/2})$.
+Within each bin, we employ a polynomial representation of the radiation fields and solve for nodal values collocated in Gaussian quadrature points.  
+The number of quadrature points $N$ then increases with the degree $k$ of the polynomial representation ($N=k+1$).  
+Integrals of radiation quantities over energy space are then evaluated as
+\begin{equation}
+  \int_{\bbR^{+}}g(\epsilonNu)\,d\epsilonNu
+  \approx\int_{D^{\epsilonNu}}g(\epsilonNu)\,d\epsilonNu
+  =\sum_{i=1}^{N^{\epsilonNu}}\int_{K_{i}^{\epsilonNu}}g(\epsilonNu)\,d\epsilonNu
+  \approx\sum_{i=1}^{N^{\epsilonNu}}|K_{i}^{\epsilonNu}|\sum_{q=1}^{N}w_{q}\,g_{q}=\sum_{j=1}^{M^{\epsilonNu}} W_{j}\,g_{j}=\vect{W}\cdot\vect{g},
+\end{equation}
+where $w_{q}$ are Gaussian quadrature weights (normalized such that $\sum_{q=1}^{N}w_{q}=1$) and $M^{\epsilonNu}=N^{\epsilonNu}\times N$.  
+In constructing the vectors $\vect{W},\vect{g}\in\bbR^{M^{\epsilonNu}}$, the elements are sorted with monotonically increasing energy; e.g., $W_{j}=|K_{i}^{\epsilonNu}|\,w_{q}$, where $j=(i-1)\times N+q$, ($i=1,\ldots,N^{\epsilonNu}$, $q=1,\ldots,N$).
+
+\subsection{Fluid-Radiation Coupling}
+
+\subsubsection{Emission and Absorption}
+
+Electron capture on nucleons and nuclei results in changes to the electron fraction and internal energy of the fluid given by
+\begin{align}
+  d_{t}Y_{e}
+  &=-\f{m_{\mbox{\tiny B}}}{\rho}\int_{\bbR^{+}}\tilde{\chi}\,\big(\cJ_{0}-\cJ\big)\,dV_{\epsilonNu}, \label{eq:electronFractionEmAb} \\
+  d_{t}\epsilon
+  &=-\f{1}{\rho}\int_{\bbR^{+}}\tilde{\chi}\,\big(\cJ_{0}-\cJ\big)\,\epsilonNu\,dV_{\epsilonNu}, \label{eq:internalEnergyEmAb}
+\end{align}
+where $m_{\mbox{\tiny B}}$ is the baryon mass and $\epsilon$ is the specific internal energy.  
+In each implicit step in the SIRK2 scheme discussed in Section~\ref{sec:semiImplicitTime} we solve Eqs.~\eqref{eq:electronFractionEmAb}-\eqref{eq:internalEnergyEmAb} coupled to the collision part of the moment equations.
+\begin{align}
+  Y_{e}^{n+1}-Y_{e}^{n}
+  &=-\f{m_{\mbox{\tiny B}}}{\rho}\sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(2)}\,\gamma_{j}^{n}\,\big(\cJ_{0,j}^{n+1}-\cJ_{j}^{n+1}\big), \label{eq:electronFractionEmAbDiscrete0} \\
+  \epsilon^{n+1}-\epsilon^{n}
+  &=-\f{1}{\rho}\sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\,\gamma_{j}^{n}\,\big(\cJ_{0,j}^{n+1}-\cJ_{j}^{n+1}\big), \label{eq:internalEnergyEmAbDiscrete0}
+\end{align}
+where $W_{j}^{(2,3)}=w_{q}\,\epsilonNu_{i,q}^{2,3}\,\Delta\epsilonNu_{i}$ and $\gamma_{j}^{n}=\dt\,\tilde{\chi}_{j}^{n}$.  
+Note that the absorption opacity is defined at the known time level $t^{n}$, which avoids computation of derivatives with respect to temperature and electron fraction.  
+The radiation energy density is updated from
+\begin{equation}
+  \cJ_{j}^{n+1}=\f{\cJ_{j}^{n}+\gamma_{j}^{n}\,\cJ_{0,j}^{n+1}}{1+\gamma_{j}^{n}}, 
+  \label{eq:momentEquationEnergyEmAbDiscrete}
+\end{equation}
+which, when inserted into Eqs.~\eqref{eq:electronFractionEmAbDiscrete0}-\eqref{eq:internalEnergyEmAbDiscrete0}, results in a nonlinear system for the unknowns $Y^{n+1}$ and $\epsilonNu^{n+1}$
+\begin{align}
+  Y_{e}^{n+1}-Y_{e}^{n}
+  &=-\f{m_{\mbox{\tiny B}}}{\rho}\sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(2)}\,\tilde{\gamma}_{j}^{n}\,\big(\cJ_{0,j}^{n+1}-\cJ_{j}^{n}\big), \label{eq:electronFractionEmAbDiscrete} \\
+  \epsilon^{n+1}-\epsilon^{n}
+  &=-\f{1}{\rho}\sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\,\tilde{\gamma}_{j}^{n}\,\big(\cJ_{0,j}^{n+1}-\cJ_{j}^{n}\big), \label{eq:internalEnergyEmAbDiscrete}
+\end{align}
+where $\tilde{\gamma}_{j}^{n}=\gamma_{j}^{n}/(1+\gamma_{j}^{n})$.  
+Since the equilibrium density $\cJ_{0,j}$ is a nonlinear function of $Y_{e}$ and $\epsilon$, Eqs.~\label{eq:electronFractionEmAbDiscrete}-\label{eq:internalEnergyEmAbDiscrete} are solved using Newton's method.
+Once $Y_{e}^{n+1}$ and $\epsilon^{n+1}$ are obtained, the radiation density is obtained from Eq.~\eqref{eq:momentEquationEnergyEmAbDiscrete}, while the flux is given by
+\begin{equation}
+  \bcH_{j}^{n+1}=\bcH_{j}^{n}/(1+\gamma_{j}^{n}).  
+  \label{eq:momentEquationMomentumEmAbDiscrete}
+\end{equation}
+
+\subsubsection{Neutrino-Electron Scattering}
+
+\subsubsection{Full Interaction Set}
+
 \begin{table}
@@
 
+\subsection{Relaxation}
+
 \subsection{Deleptonization}
@@
 We also set $r_{0}=R_{2}$ and $R_{0}=1$~km.  
-With these parameters, the density profile given by Eqs~\eqref{eq:densityProfile}, \eqref{eq:densityProfile1}, and \eqref{eq:densityProfile2} provides a reasonable approximation to the density profile in the post-bounce phase of a supernova realistic model (cf.
+With these parameters, the density profile given by Eqs~\eqref{eq:densityProfile}, \eqref{eq:densityProfile1}, and \eqref{eq:densityProfile2} provides a reasonable approximation to the density profile in the post-bounce phase of a realistic supernova model (cf.
 Figure~\ref{fig:analyticDensityProfile}).
@@
   \begin{center}
-      \includegraphics[scale=0.5]{./Figures/AnalyticDensityProfile}
+      \includegraphics[scale=0.78]{./Figures/AnalyticDensityProfile}
   \end{center}

### 2017-06-01 Documents/M1/dgM1Curvilinear.tex
minor modifications to text

@@
 where $w_{q}$ are Gaussian quadrature weights (normalized such that $\sum_{q=1}^{N}w_{q}=1$) and $M^{\epsilonNu}=N^{\epsilonNu}\times N$.  
-In constructing the vectors $\vect{W},\vect{g}\in\bbR^{M^{\epsilonNu}}$, the elements are sorted with monotonically increasing energy; e.g., $W_{j}=|K_{i}^{\epsilonNu}|\,w_{q}$, where $j=(i-1)\times N+q$, ($i=1,\ldots,N^{\epsilonNu}$, $q=1,\ldots,N$).
+In constructing the vectors $\vect{W},\vect{g}\in\bbR^{M^{\epsilonNu}}$, their elements are sorted with energy monotonically increasing with $j$; e.g., $\epsilonNu_{j}=\epsilonNu_{i-1/2}+|K_{i}|\times(1/2+\eta_{q}^{\epsilonNu})$ and $W_{j}=|K_{i}^{\epsilonNu}|\,w_{q}$, where $\eta_{q}^{\epsilonNu}$ is the Gaussian quadrature point on the local reference element ($\eta^{\epsilonNu}\in[-1/2,1/2]$), and $j=(i-1)\times N+q$, ($i=1,\ldots,N^{\epsilonNu}$, $q=1,\ldots,N$).
 
@@
 \end{equation}
-which, when inserted into Eqs.~\eqref{eq:electronFractionEmAbDiscrete0}-\eqref{eq:internalEnergyEmAbDiscrete0}, results in a nonlinear system for the unknowns $Y^{n+1}$ and $\epsilonNu^{n+1}$
+which, when inserted into Eqs.~\eqref{eq:electronFractionEmAbDiscrete0}-\eqref{eq:internalEnergyEmAbDiscrete0}, results in a nonlinear system for the unknowns $Y^{n+1}$ and $\epsilon^{n+1}$
 \begin{align}
@@
 where $\tilde{\gamma}_{j}^{n}=\gamma_{j}^{n}/(1+\gamma_{j}^{n})$.  
-Since the equilibrium density $\cJ_{0,j}$ is a nonlinear function of $Y_{e}$ and $\epsilon$, Eqs.~\label{eq:electronFractionEmAbDiscrete}-\label{eq:internalEnergyEmAbDiscrete} are solved using Newton's method.
+Since the equilibrium density $\cJ_{0,j}$ is a nonlinear function of $Y_{e}$ and $\epsilon$, Eqs.~\eqref{eq:electronFractionEmAbDiscrete}-\eqref{eq:internalEnergyEmAbDiscrete} are solved using Newton's method.
 Once $Y_{e}^{n+1}$ and $\epsilon^{n+1}$ are obtained, the radiation density is obtained from Eq.~\eqref{eq:momentEquationEnergyEmAbDiscrete}, while the flux is given by

### 2017-06-02 Documents/M1/dgM1Curvilinear.tex
Modification backup for chapter 6.

@@
 %\ee{Ran write about tabulated B85 absorption and scattering opacities.}
-
-Given by \citet{bruenn_1985}, the absorption opacity of neutrino $\chi$ 
+In this section, we bring the speed of light $c$ back.
+
+The total opacity $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$, where $\tilde{\chi}(\epsilonNu,\bU)$ is the absorption opacity of neutrino and  $\sigma(\epsilonNu,\bU)$ is the scattering opacities.
+The absorption opacity of neutrino $\tilde{\chi}(\epsilonNu,\bU)$ 
+\begin{equation}
+  \tilde{\chi}(\epsilonNu,\bU) = \chi(\epsilonNu,\bU) + \eta(\epsilonNu,\bU), 
+\end{equation}
+ is the sum of the neutrino emissivity $\eta(\epsilonNu,\bU) $ and the neutrino absorptivity  $ \chi(\epsilonNu,\bU)$.
+The scattering opacities $\sigma(\epsilonNu,\bU)$ contains isoenergetic scattering opacities, neutrino-electron scattering opacities and have a integral form in the Boltzmann equation: if we include emission, absorption, isoenergetic scattering of neutrino by nucleons and nuclei, and neutrino electron scattering, the simplified Boltzmann equation is
+\begin{align}
+\dfrac{1}{c}\dfrac{\partial f(\epsilonNu,\bU)}{\partial t} = 
+&  \eta(\epsilonNu,\bU) - \tilde{\chi}(\epsilonNu,\bU)f(\epsilonNu,\bU) \nonumber \\
+& + \dfrac{1}{c(hc)^3} \epsilonNu^2 \int d\mu^\prime_0 R_{IS}( \mu^\prime_0, \mu_0,\epsilonNu, \bU) f(\mu^\prime_0, \epsilonNu,\bU) \nonumber \\
+& - \dfrac{1}{c(hc)^3} \epsilonNu^2 f(\epsilonNu,\bU)\int d\mu^\prime_0 R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) \nonumber \\
+& + \dfrac{1}{c(hc)^3} [1- f(\epsilonNu,\bU)] \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime_0 R^{in}_{NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} )f(\mu^\prime_0,\epsilonNu^{\prime} ) \nonumber \\
+& - \dfrac{1}{c(hc)^3} f(\epsilonNu,\bU) \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime R^{out}_{NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} ) [1-f(\mu^\prime_0,\epsilonNu^{\prime} )] .
+\end{align}
+
+The third and fourth terms are contributions from isoenergetic scattering of neutrino by nucleons and nuclei. The last two terms are contributions from neutrino-electron scattering.
+
+\subsection{The neutrino absorptivity}
+
+Given by \citet{bruenn_1985}, the absorption opacity of neutrino $\tilde{\chi}(\epsilonNu,\bU)$ 
 \begin{equation}
@@
 \end{equation}
+
 The two terms of electron-neutrino absorption on nucleons are
@@
 
-The sum of Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity} gives the explicit expression of the absorption opacity of neutrino $\chi$ .
-
-The total opacity $\kappa(\epsilonNu,\bU)=\chi(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$, and $\sigma(\epsilonNu,\bU)$ is the scattering opacities.
-The scattering opacities $\sigma(\epsilonNu,\bU)$ contains isoenergetic scattering opacities and have a integral form in the Boltzmann equation: if we include emission, absorption, and isoenergetic scattering of neutrino by nucleons and nuclei, the simplified Boltzmann equation is
-\begin{align}
-\dfrac{\partial f(\epsilonNu,\bU)}{\partial t} = \eta(\epsilonNu,\bU) - \tilde{\chi}(\epsilonNu,\bU)f(\epsilonNu,\bU) & + \dfrac{1}{h^3} \epsilonNu^2 \int d\mu^\prime_0 R_{IS}( \mu^\prime_0, \mu_0,\epsilonNu, \bU) f(\mu^\prime_0, \epsilonNu,\bU) \nonumber \\
-	& - \dfrac{1}{h^3} \epsilonNu^2 f(\epsilonNu,\bU)\int d\mu^\prime_0 R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) .
-\end{align}
-
-The last two terms are contributions from isoenergetic scattering of neutrino by nucleons and nuclei.
+The sum of Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity} gives the explicit expression of the absorption opacity of neutrino $\chi(\epsilonNu,\bU)$ .
+
+\subsection{The isoenergetic scattering kernel}
 The isoenergetic scattering kernel $R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
 \begin{align}
-R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) & = R_{IS}^{nucleons}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) +  R_{IS}^{nuclei}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)\\
-& = \int_{0}^{2\pi}d
+R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) & = R_{IS}^{nucleons}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) +  R_{IS}^{nuclei}(\mu_0, \mu^\prime_0, \epsilonNu,\bU),
+\end{align}
+where
+\begin{align}
+\cos\theta = \mu_0\mu^\prime_0 + [(1-\mu_0^2)(1-\mu_0^{\prime 2})]^{1/2}\cos\theta,
+\end{align}
+and
+\begin{align}
+R_{IS}(\cos\theta, \epsilonNu, \bU) = R^{nucleons}(\cos\theta,\epsilonNu, \bU) + R^{nuclei}_{IS}(\cos\theta, \epsilonNu, \bU)
+\end{align}
+where
+\begin{align}
+& R^{nucleons}_{IS} (\cos\theta,\epsilonNu, \bU) = \dfrac{(2\pi)^2 G_F^2}{h} \nonumber \\
+& \cdot \left\lbrace  \eta_{nn}\left[ (h^n_V)^2 + 3(h^n_A)^2\right] + \eta_{pp} \left[ (h^p_V)^2 + 3(h^p_A)^2\right] +\eta_{nn}\left[ (h^n_V)^2 - (h^n_A)^2\right]\cos\theta + \eta_{pp}\left[ (h^p_V)^2 - (h^p_A)^2\right]\cos\theta \right\rbrace
+\end{align}
+and
+\begin{align}
+R^{nuclei}_{IS}(\cos\theta,\epsilonNu,\bU)  = \dfrac{(2\pi)^2 G_F^2}{h}\dfrac{\rho X_H}{m_B}A\left(  C_{V0} - \dfrac{1}{2}\dfrac{N-Z}{A} C_{V1}\right)^2(1+\cos\theta)e^{-4b\epsilonNu^2(1-\cos\theta)}.
+\end{align}
+$h^p_V$, $h^n_V$, $h^p_A$ and $h^n_A$, are the nucleon neutral current form factors arising from virtual strong-interaction processes: $h_V^p = \dfrac{1}{2} - 2 \sin^2\theta_W$, $h^n_V = - \dfrac{1}{2}$, $h_A^p = \dfrac{1}{2}g_A$, and $h^n_A = - \dfrac{1}{2} g_A$, where $\theta_W$ is the Weinberg angle.
+The constants, $C_{V0}$ and $C_{V1}$, are defined in terms of $h_V^p$ and $h_V^n$: $C_{V0} = \dfrac{1}{2}(h_V^p + h_V^n)$ and $C_{V1} = h_V^p - h_V^n$.
+The quantity $b$ is given by $b = 4.8 \times 10^{-6} A^{2/3}$.
+
+For nondegenerate, nonrelativistic nucleons, $\eta_{pp}$ and $\eta_{nn}$ are given by
+\begin{align}
+&\eta_{pp} = n_p \\
+&\eta_{nn} = n_n.
 \end{align}

### 2017-06-02 Documents/M1/dgM1Curvilinear.tex
Modification backup for chapter 6.

@@
 
+Expanding the isoenergetic scattering kernel in the first two terms of a Legendre series yields
+\begin{align}
+R^{0}_{IS}(\omega, \omega, \cos\theta) \approx \dfrac{1}{2} \Phi_{0,IS}(\omega) + \dfrac{3}{2}\Phi_{1,IS}(\omega)\cos\theta
+\end{align}
+
+\subsection{The neutrino-electron scattering kernel}
+Given by \citet{bruenn_1985}, for $\epsilonNu \neq \epsilonNu^\prime$, the neutrino-electron scattering kernels are written as
+\begin{align}
+    R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime,\omega, \bU) = & R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime,\mu_0,\mu^\prime_0,\phi_0, \bU) \nonumber \\
+     = &\dfrac{1}{2}\dfrac{1}{(2\pi)^3}\dfrac{\pi \sigma_0 c}{(m_e c^2)^2}\dfrac{1}{\epsilonNu, \epsilonNu^\prime} [ \beta_1I_1(\epsilonNu,\epsilonNu^\prime,\omega,\bU) + \beta_2I_2(\epsilonNu,\epsilonNu^\prime,\omega, \bU) \nonumber \\
+    & +  \beta_3I_3(\epsilonNu,\epsilonNu^\prime,\omega, \bU)] 
+\end{align}
+where $\beta_1 = (C_V + C_A)^2$, $\beta_2 = (C_V -C_A)^2$, $\beta_3 = C_A^2 - C_V^2$, $\sigma_0 = 1.746 \times 10^{-44} cm^{-2}$, and
+\begin{align}
+\omega = \mu_0 \mu_0^\prime + [(1-\mu_0^2)(1-\mu_0^{\prime 2})]^{1/2}\cos\phi_0
+\end{align}
+and where the function $I_{1,2,3}(\epsilonNu,\epsilonNu^\prime,\omega, \bU)$ are defined by 
+\begin{align}
+I_1(\epsilonNu, \epsilonNu^\prime, \omega, \bU) = & \dfrac{2\pi T \epsilonNu^2 \epsilonNu^{\prime 2}(1-\omega)^2}{\Delta^5} f_\gamma(\epsilonNu^\prime - \epsilonNu) \cdot \\
+& \left\lbrace  A T^2 [G_2(y_0)+2y_0G_1(y_0)+y_0^2G_0(y_0)] \right.\nonumber\\
+& + \left. BT[G_1(y_0)+y_0G_0(y_0)] + CG_0(y_0)\right\rbrace,
+\end{align}
+\begin{align}
+I_2(\epsilonNu, \epsilonNu^\prime, \omega, \bU)  = I_1(\epsilonNu \rightarrow -\epsilonNu^\prime, \epsilonNu^\prime\rightarrow -\epsilonNu, \omega, \bU) 
+\end{align}
+\begin{align}
+I_3(\epsilonNu, \epsilonNu^\prime, \omega, \bU)  = \dfrac{2\pi T \epsilonNu \epsilonNu^{\prime}(1-\omega)(m_ec^2)^2}{\Delta} f_\gamma(\epsilonNu^\prime - \epsilonNu) G_0(y_0)
+\end{align}
+with
+\begin{align}
+\Delta = (\epsilonNu^2 + \epsilonNu^{\prime 2} - 2\epsilonNu \epsilonNu^\prime
+\omega)^{1/2}
+\end{align}
+\begin{align}
+y_0 = \dfrac{1}{T}\left\lbrace - \dfrac{\epsilonNu -\epsilonNu^\prime}{2} + \dfrac{\Delta}{2} \left[1+\dfrac{2(m_e c^2)^2}{\epsilonNu \epsilonNu^\prime (1-\omega)}\right]^{1/2} \right\rbrace 
+\end{align}
+\begin{align}
+A &= \epsilonNu^2 + \epsilonNu^{\prime 2} + \epsilonNu \epsilonNu^\prime(3+\omega),\\
+B &= \epsilonNu \left[ 2\epsilonNu^2 + \epsilonNu \epsilonNu^\prime(3-\omega) - E^{\prime 2}_0(1+3\omega) \right] \\
+C &= \epsilonNu^2\left[ (\epsilonNu -\epsilonNu^\prime \omega)^2 - \dfrac{E^{\prime 2}_0 (1-\omega^2)}{2} - \dfrac{(1+\omega)(m_e c^2)^2 \Delta^2}{2(1-\omega)\epsilonNu^2} \right] 
+\end{align}
+\begin{align}
+f_{\gamma}(x) = \dfrac{1}{e^{x/T} - 1}
+\end{align}
+and the function $G_n(y)$ are defined in terms of Fermi integrals:
+\begin{align}
+G_n(y) = F_n(\eta^\prime - y) - F_n(\eta - y)
+\end{align}
+where
+\begin{align}
+\eta &= \dfrac{\mu_e}{T} \\
+\eta^\prime &= \eta - \dfrac{\epsilonNu - \epsilonNu^\prime}{T} \\
+F_n(\eta) &= \int_{0}^{\infty} \dfrac{x^n dx}{e^{x-\eta}+1}
+\end{align}
+
+For $\epsilonNu = \epsilonNu^\prime$, the functions
+\begin{align}
+I_1(\epsilonNu, \epsilonNu^\prime, \omega, \bU) = I_1(\epsilonNu, \omega, \bU) &= \dfrac{2\pi T \epsilonNu^4 (1-\omega)^2}{\Delta^5}\cdot \\
+& \left\lbrace  A T^2 [2F_1(\eta -y_0)+2y_0F_0(\eta-y_0)+y_0^2F_{-1}(\eta-y_0)] \right.\nonumber\\
+& + \left. BT[F_0(\eta-y_0)+y_0F_{-1}(\eta-y_0)] + CF_{-1}(\eta-y_0)\right\rbrace,
+\end{align}
+\begin{align}
+I_2(\epsilonNu, \epsilonNu^\prime, \omega, \bU)  = I_2(\epsilonNu, \omega, \bU)&=I_1(\epsilonNu, \omega, \bU) 
+\end{align}
+\begin{align}
+I_3(\epsilonNu, \epsilonNu^\prime, \omega,\bU)  = I_3(\epsilonNu, \omega, \bU)=\dfrac{2\pi T \epsilonNu^2(1-\omega)(m_ec^2)^2}{\Delta}F_{-1}(\eta - y_0)
+\end{align}
+with
+\begin{align}
+\Delta = (\epsilonNu^2 + \epsilonNu^{\prime 2} - 2\epsilonNu \epsilonNu^\prime
+\omega)^{1/2} = \epsilonNu(2 - 2\omega)^{1/2}
+\end{align}
+\begin{align}
+y_0 = \dfrac{1}{T}\left\lbrace \dfrac{\Delta}{2} \left[1+\dfrac{2(m_e c^2)^2}{\epsilonNu^2 (1-\omega)}\right]^{1/2} \right\rbrace 
+\end{align}
+\begin{align}
+A &= \epsilonNu ^2(5+\omega),\\
+B &= \epsilonNu^3 (4-4\omega),\\
+C &= \epsilonNu^2\left[\dfrac{E^{2}_0 (1-\omega^2)}{2} - \dfrac{(1+\omega)(m_e c^2)^2 \Delta^2}{2(1-\omega)\epsilonNu^2} \right] 
+\end{align}
+\begin{align}
+F_{-1} (\eta) &= \dfrac{1}{e^{-\eta} + 1} 
+\end{align}
+
+Therefore, $R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime, \omega)$ is known.
+
+Expand the scattering kernel in a Legendre series:
+\begin{align}
+R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU) = \sum_{l=0}^{\infty} \dfrac{2l+1}{2} R^{out}_{{NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) P_l(\omega),
+\end{align}
+where the Legendre coefficients $R^{out}_{{NES}, l}(\epsilonNu,\epsilonNu^\prime)$ are given by
+\begin{align}
+R^{out}_{{NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) = \int_{-1}^{1} d\omega P_l(\omega) R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU).
+\end{align}
+
+Expanding the neutrino-electron scattering kernels in the first two terms of Legendre series yields
+\begin{align}
+R^{in/out}_{NES}(\omega, \omega^{\prime}, \cos\theta, \bU) & = \dfrac{1}{2} \sum_{l} (2l+1)\Phi^{in/out}_{l,NES}(\omega,\omega^{\prime},\bU)P_l(\cos\theta) \\
+& \approx \dfrac{1}{2}\Phi_{0,NES}^{in/out}(\omega,\omega^{\prime}, \bU) + \dfrac{3}{2}\Phi^{in/out}_{1,NES}(\omega,\omega^{\prime}, \bU)\cos\theta
+\end{align}
+
 \section{Benchmark Problems}

### 2017-06-29 Documents/Euler/Benchmarks1D/draft.tex
Linear Waves

@@
 \end{table}
-TAble 1 dispplays the initial data for the Riemann problems.
+Table 1 dispplays the initial data for the Riemann problems.
 ($\rho_L$, $u_L$ , $p_L$) denote the mass density, velocity, and pressure to the left of the interface at $x=x_0$;($\rho_R$, $u_R$,  $p_R$) refer to these same quantities to the right of the interface.
@@
 %\clearpage
+\subsection{Linear Waves Tests}
+
+\begin{figure}
+  \begin{center}
+	\includegraphics[width=.975\textwidth]{lw1den.png}
+	\begin{tabular}{cc}
+	  \includegraphics[width=.475\textwidth]{lw1vel.png} &
+	  \includegraphics[width=.475\textwidth]{lw1prs.png}
+	\end{tabular}
+  \end{center}
+  \caption{Results from linear waves tests, showing density (top), velocity (bottom left) and pressure (bottom right) computed at various times after a disturbance.}
+  \label{fig:lw1}
+\end{figure}
+\clearpage
+
+\begin{figure}
+  \begin{center}
+	\includegraphics[width=.975\textwidth]{lw2den.png}
+	\begin{tabular}{cc}
+	  \includegraphics[width=.475\textwidth]{lw2vel.png} &
+	  \includegraphics[width=.475\textwidth]{lw2prs.png}
+	\end{tabular}
+  \end{center}
+  \caption{Results from linear waves tests, showing density (top), velocity (bottom left) and pressure (bottom right) computed using different integration methods and compared with an initial condition.}
+  \label{fig:lw2}
+\end{figure}
+\clearpage
+
 \subsection{Test 1: Sod's Shock Tube} 
-The Sod's Shock tube test features examples of threee different types of waves.
+The Sod's Shock tube test features examples of three different types of waves.
 A shock wave appears around $x=0.85$.

### 2017-06-30 Documents/Euler/dgEulerCurvilinear.tex
Some text on positivity limiter

@@
 
+\clearpage
+
 \section{Euler Equations of Gas Dynamics in Curvilinear Coordinates}
@@
 
-For general curvilinear spatial coordinates, the non-relativistic Euler equations for gas dynamics are \citep[][see, e.g., \citet{} and references therein for a fully general relativistic treatment]{leveque_2002}
+For general curvilinear spatial coordinates, the non-relativistic Euler equations for gas dynamics are %\citep[][see, e.g., \citet{} and references therein for a fully general relativistic treatment]{leveque_2002}
 \begin{equation}
@@
 
+\section{Equation of State (EoS)}
+
 \section{Polynomial Limiting}
@@
 
-\section{Equation of State (EoS)}
+In the case of the nuclear EoS, the thermodynamic quantities (e.g, pressure) are tabulated in terms of mass density $\rho$, temperature $T$, and electron fraction $Y_{e}$.  
+Obviously, the tables are of finite extent in these independent variables; i.e., $\rho\in[\rho_{0},\rho_{1}]$, $T\in[T_{0},T_{1}]$, and $Y_{e}\in[Y_{e,0},Y_{e,1}]$.  
+During stellar core-collapse, the internal energy density has a dominant contribution from degenerate electrons, which is independent of the temperature.  
+During core bounce and shock formation, we have found that the numerical scheme (e.g., during reconstruction of element interfaces) can lead to internal energy densities that fall below the lower boundary of the tabulated data and failure to obtain a temperature, which is needed to evaluate the pressure.
+(Extending the table to lower values of temperature does not help since the internal energy density is practically independent of the temperature.)
+
+For the solution to the Euler equations, we define the set of physically admissible states as
+\begin{equation}
+  \cG=\big\{\,\bU~|~\rho\ge\rho_{0}, e\ge e_{0}(\rho,T_{0},n_{e}),n_{e}\ge n_{e,0}(\rho,Y_{e,0})\,\big\}
+\end{equation}
 

### 2017-07-11 Documents/Euler/dgEulerCurvilinear.tex
added figures to paper

@@
 }
+
+\usepackage{graphicx}
+\graphicspath{ {Figures/} }
 
@@
 
+\begin{figure}[h]
+  \begin{center}
+     \includegraphics[width=.95\textwidth]{RiemannProblem_d5.png}
+	\begin{tabular}{cc}
+      \includegraphics[width=.475\textwidth]{RiemannProblem_v5.png} &
+	  \includegraphics[width=.475\textwidth]{RiemannProblem_p5.png}
+	\end{tabular}	
+  \end{center}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the Riemann Problem at $t=0.012$, computed with 200 cells and the third order integration method (black), and the exact solution, obtained with Toro's Riemann solver (red).}
+  \label{fig:Riemann}
+\end{figure}
+
 \subsubsection{Interacting Blast Waves}
 
+\begin{figure}[h]
+  \begin{center}
+     \includegraphics[width=.95\textwidth]{BlastD.png}	
+	\begin{tabular}{cc}
+     \includegraphics[width=.475\textwidth]{BlastV.png}
+     \includegraphics[width=.475\textwidth]{BlastP.png}	
+    \end{tabular}
+  \end{center}
+  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the Woodward-Collela blast wave problem at $t=0.038$, computed with the 400 cells (black) and 2000 cells (red).}
+  \label{fig:Blast}
+\end{figure}
+\clearpage
 \subsubsection{Shock-Entropy Wave Interaction}
+
+\begin{figure}[h]
+  \begin{center}
+	\begin{tabular}{cc}
+      \includegraphics[width=.475\textwidth]{den.png} &
+	  \includegraphics[width=.475\textwidth]{denzoom.png}
+	\end{tabular}
+  \end{center}
+  \caption{Results showing the density for the Shock Entropy Wave problem at $t=1.8$, computed with 200 cells (green) and 1000 cells (black).}
+  \label{fig:shock}
+\end{figure}
 

### 2017-07-14 Documents/M1/dgM1Curvilinear.tex
Keep updates.

@@
 \begin{align}
-\chi_{nucleon}(\epsilonNu,\bU) & = \dfrac{G^2}{\pi} \eta_{np}(g_V^2+3g_A^2)[1-F_e(\varepsilon+Q)](\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2} \label{eq:nucleonabsorption} ,\\
-\eta_{nucleon}(\epsilonNu,\bU) &= \dfrac{G^2}{\pi}\eta_{pn}(g_V^2+3g_A^2)F_e(\varepsilon+Q)(\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2} \label{eq:nucleonemissivity} ,
+\chi_{nucleon}(\epsilonNu,\bU) & = \dfrac{G^2_F}{\pi} \eta_{np}(g_V^2+3g_A^2)[1-F_e(\varepsilon+Q)](\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2} \label{eq:nucleonabsorption} ,\\
+\eta_{nucleon}(\epsilonNu,\bU) &= \dfrac{G^2_F}{\pi}\eta_{pn}(g_V^2+3g_A^2)F_e(\varepsilon+Q)(\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2} \label{eq:nucleonemissivity} ,
 \end{align}
@@
 \begin{align}
-\chi_{nuclear}(\epsilonNu,\bU) & = \dfrac{G^2}{\pi} n_A e^{(\mu_n -\mu_p -Q')/k_B T} g^2_A \dfrac{2}{7} N_p(Z) N_h(N)[1-F_e(\varepsilon+Q')](\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} \label{eq:nuclearabsorption} ,\\
-\eta_{nuclear}(\epsilonNu,\bU) &=\dfrac{G^2}{\pi} n_A g^2_A \dfrac{2}{7} N_p(Z) N_h(N)F_e(\varepsilon+Q')(\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} \label{eq:nuclearemissivity},
+\chi_{nuclear}(\epsilonNu,\bU) & = \dfrac{G^2_F}{\pi} n_A e^{(\mu_n -\mu_p -Q')/k_B T} g^2_A \dfrac{2}{7} N_p(Z) N_h(N)[1-F_e(\varepsilon+Q')](\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} \label{eq:nuclearabsorption} ,\\
+\eta_{nuclear}(\epsilonNu,\bU) &=\dfrac{G^2_F}{\pi} n_A g^2_A \dfrac{2}{7} N_p(Z) N_h(N)F_e(\varepsilon+Q')(\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} \label{eq:nuclearemissivity},
 \end{align} 
@@
 
+The factor $G^2_F$ in Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity} is the Fermi constant [$G=(1.015\pm 0.03)\time 10^5 M_p^{-2}$] with the value
+\begin{equation}
+G^2_F = \left[ \dfrac{1}{(\hbar c)^4} \right] G^2 = 5.18 \times 10^{-44} MeV^{-2}cm^2, 
+\end{equation}
+giving $\chi$ and $\eta$ the required units of $cm^{-1}$.
+
 In Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity}, $F_e(E)$ is the Fermi-Dirac distribution function:
@@
 
-In Eq.~\eqref{eq:nucleonabsorption} and ~\eqref{eq:nucleonemissivity}, $\eta_{np}$ and $\eta_{pn}$ take into account the nucleon final-state blocking and equal to $n_n$ and $n_p$, the nucleon number density, when the nucleons are nondegenerate, respectively.
+In Eq.~\eqref{eq:nucleonabsorption} and ~\eqref{eq:nucleonemissivity}, $\eta_{np}$ and $\eta_{pn}$ take into account the nucleon final-state blocking. 
+\begin{align}
+\eta_{pn} = \dfrac{2}{h^3 c^3} \int d^3 p F_p (E)[1-F_n(E)] = (n_n - n_p) \dfrac{1}{e^{(\mu_n^0 - \mu_p^0)/k_bT}-1},\\
+\eta_{np} = \dfrac{2}{h^3 c^3} \int d^3 p F_n (E)[1-F_p(E)] = (n_p - n_n) \dfrac{1}{e^{(\mu_p^0 - \mu_n^0)/k_bT}-1}.
+\end{align}
+
+The factors $\eta_{np}$ and $\eta_{pn}$ equal to $n_n$ and $n_p$, the nucleon number density, when the nucleons are non-degenerate, respectively.
 \begin{align}
@@
 
-The factor $G^2$ in Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity} is the Fermi constant [$G=(1.015\pm 0.03)\time 10^5 M_p^{-2}$] with the value
-\begin{equation}
-G^2 = \left[ \dfrac{1}{(\hbar c)^4} \right] G^2 = 5.18 \times 10^{-44} MeV^{-2}cm^2, 
-\end{equation}
-giving $\chi$ and $\eta$ the required units of $cm^{-1}$.
-
 The sum of Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity} gives the explicit expression of the absorption opacity of neutrino $\chi(\epsilonNu,\bU)$ .
@@
 
+The factors $\eta_{pp}$ and $\eta_{nn}$ account for the nucleon final-state blocking,
+\begin{align}
+\eta_{pp} = T \dfrac{\partial n_p}{\partial \mu_p} = n_p \dfrac{3T/2\epsilon^p_F}{[1+(3T/2\epsilon^p_F)^2]^{1/2}}, \\
+\eta_{nn} = T \dfrac{\partial n_n}{\partial \mu_n}=n_n \dfrac{3T/2\epsilon^n_F}{[1+(3T/2\epsilon^n_F)^2]^{1/2}},
+\end{align}
+where $\epsilon^p_F$ and $\epsilon^n_F$ are the proton and neutron Fermi energies, respectively,
+\begin{align}
+\epsilon^p_F = \dfrac{h^2}{8 \pi^2 m_B}(3\pi^2n_p)^{2/3},\\
+\epsilon^n_F = \dfrac{h^2}{8\pi^2m_B}(3\pi^2n_n)^{2/3}.
+\end{align}
 For nondegenerate, nonrelativistic nucleons, $\eta_{pp}$ and $\eta_{nn}$ are given by
@@
 \begin{align}
-R^{0}_{IS}(\omega, \omega, \cos\theta) \approx \dfrac{1}{2} \Phi_{0,IS}(\omega) + \dfrac{3}{2}\Phi_{1,IS}(\omega)\cos\theta
+R_{IS}(\omega, \omega, \cos\theta) \approx \dfrac{1}{2} \Phi_{0,IS}(\omega) + \dfrac{3}{2}\Phi_{1,IS}(\omega)\cos\theta
 \end{align}
@@
 \begin{align}
-R^{in/out}_{NES}(\omega, \omega^{\prime}, \cos\theta, \bU) & = \dfrac{1}{2} \sum_{l} (2l+1)\Phi^{in/out}_{l,NES}(\omega,\omega^{\prime},\bU)P_l(\cos\theta) \\
+R^{in/out}_{NES}(\omega, \omega^{\prime}, \cos\theta, \bU) & = \sum_{l=0}^{1} \dfrac{ 2l+1}{2}\Phi^{in/out}_{l,NES}(\omega,\omega^{\prime},\bU)P_l(\cos\theta) \\
 & \approx \dfrac{1}{2}\Phi_{0,NES}^{in/out}(\omega,\omega^{\prime}, \bU) + \dfrac{3}{2}\Phi^{in/out}_{1,NES}(\omega,\omega^{\prime}, \bU)\cos\theta

### 2017-07-17 Documents/M1/dgM1Curvilinear.tex
Adding results from test problems.  Text for the Milne problem

@@
 To model neutrino matter interactions, we include emission and absorption, (isotropic) elastic scattering on nucleons and nuclei, and neutrino-electron scattering (NES).  
-On the right-hand sides of Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}, $\tilde{\chi}(\epsilonNu,\bU)$ and $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$ are absorption and total (absorption plus scattering) opacities, respectively.
+On the right-hand sides of Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}, $\tilde{\chi}(\epsilonNu,\bU)$ and $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$ are absorption and transport (absorption plus elastic scattering) opacities, respectively.
 The absorption opacity $\tilde{\chi}$ is corrected for stimulated absorption \citep[cf.][]{mezzacappaBruenn_1993a}.  
@@
 (Explicit expressions for metric functions appearing in the geometry sources are listed in Table~\ref{tab:metricFunctions}.)  
-Then, by defining the vector of evolved moments $\bcM=\big(\,\cJ,\,\bcH\,\big)^{T}$, the vector of geometry sources $\bcG(\bcM)=\big(\,0,\,\cG_{1},\,\cG_{2},\,\cG_{3}\,\big)^{T}$, the vector of collision sources $\bcC(\bcM)=\big(\,\chi\,(\cJ_{0}-\cJ)+\cL_{\NES},\,-(\kappa+\kappa_{\NES})\,\bcH\,\big)^{T}$, and the flux vectors $\bcF^{i}(\bcM)=\big(\,\cH^{i},\,\cK_{~1}^{i},\,\cK_{~2}^{i},\,\cK_{~3}^{i}\,\big)^{T}$, we write the system of equations in compact form
+Then, by defining the vector of evolved moments $\bcM=\big(\,\cJ,\,\bcH\,\big)^{T}$, the vector of geometry sources $\bcG(\bcM)=\big(\,0,\,\cG_{1},\,\cG_{2},\,\cG_{3}\,\big)^{T}$, the vector of collision sources $\bcC(\bcM)=\big(\,\tilde{\chi}\,(\cJ_{0}-\cJ)+\cL_{\NES},\,-(\kappa+\kappa_{\NES})\,\bcH\,\big)^{T}$, and the flux vectors $\bcF^{i}(\bcM)=\big(\,\cH^{i},\,\cK_{~1}^{i},\,\cK_{~2}^{i},\,\cK_{~3}^{i}\,\big)^{T}$, we write the system of equations in compact form
 \begin{equation}
@@
 
-For non-stiff problems, we employ the strong stability-preserving Runge-Kutta (SSP-RK) methods \citep[e.g.,][]{gottlieb_etal_2001}, which, for evolving the moments from $t^{n}$ to $t^{n+1}=t^{n}+\dt$ ($\bcM^{n}\to\bcM^{n+1}$), take the general form
+For non-stiff problems, we employ the strong stability-preserving Runge-Kutta (SSP-RK) methods \citep[e.g.,][]{gottlieb_etal_2001}, which, for evolving the moments from $t^{n}$ to $t^{n+1}=t^{n}+\dt$ ($\bcM^{n}\to\bcM^{n+1}$) using $m$ stages, take the general form
 \begin{align}
@@
   \bcM^{(i)}
-  &=\sum_{k=1}^{i-1}\alpha_{ik}\,\big[\,\bcM^{(k)}+\beta_{ik}\,\dt\,\bcL(\bcM^{(k)})\,\big], \quad i=1,\ldots,m 
+  &=\sum_{k=0}^{i-1}\alpha_{ik}\,\big[\,\bcM^{(k)}+\beta_{ik}\,\dt\,\bcL(\bcM^{(k)})\,\big], \quad i=1,\ldots,m 
   \label{eq:ssprkStages} \\
@@
 To increase the temporal accuracy to second order, \citet{chertock_etal_2015} propose a correction step to be applied after the last stage.  
-We defer the development of the correction step, and use the first-order accurate time integrator for stiff problems.  
+We defer the development of the correction step \citep[see, e.g.][]{endeveHauck_2017}, and use the first-order accurate time integrator for stiff problems.  
 We note that the SIRK method reduces to the SSP-RK methods in Section~\ref{sec:explicitTime} when $\bcC=0$.
@@
 
-During time integration we apply limiters that modify the polynomial representation in elements so as to prevent development and growth of nonphysical oscillations (slope limiters; Sec.~\ref{sec:slopeLimiters}) or nonphysical states (positivity limiters; Sec.~\ref{sec:positivityLimiters}).
+During time integration we apply limiters that modify the polynomial representation in elements in order to prevent development and growth of nonphysical oscillations (slope limiters; Sec.~\ref{sec:slopeLimiters}), or nonphysical states (positivity limiters; Sec.~\ref{sec:positivityLimiters}).
 
@@
 This limiting procedure locally destroys the high-order accuracy of the DG method, but leads to non-oscillatory evolution when sharp features are present in the solution.  
+(In our implementation we apply the limiting to characteristic variables, using the eigenvectors given in Appendix~\ref{sec:eigenstructure}, which gives somewhat better results near discontinuities.)
 
@@
 
+\ee{Discuss discontinuity detection using Harten's sub-cell resolution method.}
+
 \subsection{Positivity Limiters}
@@
 Failure in maintaining these bounds can lead to an ill-posed closure problem and loss of hyperbolicity for the moment equations.  
+In order to maintain these bounds we adopt the framework of \citet{ZS2010b}, developed for the Euler equations of gas dynamics \citep[see also][]{ZS2010a,ZS2011,OHF2012}.  
+The full details of the application of this framework to the multi-dimensional two-moment method for radiation transfer will be presented elsewhere \citep{endeveHauck_2017}.  
+We give only a brief description here.  
+The bound-preserving methodology introduces the realizable set
+\begin{equation}
+  \cR=\big\{\bcM=\big(\cJ,\bcH\big)^{\mbox{\tiny T}}~|~\cJ\ge\epsilon\quad\text{and}\quad\gamma(\bcM)=\cJ-|\bcH|\ge\epsilon\big\},
+  \label{eq:realizableSet}
+\end{equation}
+where $\epsilon$ is an arbitrarily small positive parameter.  
+The realizable set in Eq.~\eqref{eq:realizableSet} is a convex cone \citep{OHF2012}.  
+Key to the \emph{realizability-preserving} (RP) scheme is to express the updated cell-averages of the moments as positive combinations of elements in $\cR$.  
+Realizability of the cell-average of the updated moments is then guaranteed by convexity arguments.  
+Sufficient conditions include: (i) the polynomial representation of the moments are realizable in a finite set of quadrature points in each element $\bK$, and (ii) the timestep $\dt$ is restricted by a CFL-like condition, which is somewhat stricter than that required for stability.
+
+Since the RP scheme only guarantees realizability of the cell-averages, polynomial limiting is needed after each timestep (and after each stage in the Runge-Kutta method) to enforce realizability in the quadrature points.
+This limiting procedure is similar to that described by \citet{ZS2010a} for the Euler equations \citep[see also][]{liuOsher_1996}, and consists of two steps.  
+First, if $\cJ<\epsilon$ for any of the quadrature points, we replace $\cJ_{\DG}\to\widehat{\cJ}_{\DG}$, where the new polynomial representation is given by
+\begin{equation}
+  \widehat{\cJ}_{\DG}=\theta_{1}\,\cJ_{\DG}+(1-\theta_{1})\,\cJ_{\bK},
+\end{equation}
+where
+\begin{equation}
+  \theta_{1}=\min\Big\{1,\f{\cJ_{\bK}-\epsilon}{\cJ_{\bK}-\cJ_{\mbox{\tiny min}}}\Big\},
+\end{equation}
+and $\cJ_{\mbox{\tiny min}}$ is the minimum density in all the quadrature points.  
+(Note that the limiting procedure is conservative, since it leaves the cell average unchanged.)  
+In the second step, we let $\widehat{\bcM}_{\DG}=(\widehat{\cJ}_{\DG},\bcH_{\DG})^{\mbox{\tiny T}}$.  
+Then, if $\widehat{\bcM}_{\DG}$ lies outside $\cR$ for any quadrature point (i.e., $\gamma(\widehat{\bcM}_{\DG})<\epsilon$), there exists an intersection point of the straight line connecting $\bcM_{\bK}\in\cR$ and $\widehat{\bcM}_{\DG}$ evaluated in the troubled quadrature point (denoted $\widehat{\bcM}_{q}$), and the surface of $\cR$.
+Any point on this line is given by the convex combination $\bs_{q}(\xi)=(1-\xi)\,\bcM_{\bK}+\xi\,\widehat{\bcM}_{q}$, where $\xi\in[0,1]$, and the intersection point is obtained by solving the equation $\gamma(\bs_{q}(\xi))=\epsilon$ for $\xi$.
+We then replace the polynomial representation $\widehat{\bcM}_{\DG}\to\widetilde{\bcM}_{\DG}$, where
+\begin{equation}
+  \widetilde{\bcM}_{\DG}=\theta_{2}\,\widehat{\bcM}_{\DG}+(1-\theta_{2})\,\bcM_{\DG},
+\end{equation}
+and $\theta_{2}$ is the smallest $\xi$ obtained in the element by considering all the troubled quadrature points.
 
@@
 
-\section{Benchmark Problems}
+\section{Basic Benchmark Problems}
 
@@
 
-\section{Mini-app: Transport Problems with Tabulated Neutrino Opacities}
+The Milne problem \citep[see, e.g.,][for details]{hummerRybicki_1971} considers isotropic radiation emanating from a source with radius $r=R_{\mbox{\tiny min}}$, propagating through a purely (elastic) scattering atmosphere with an outer boundary at $r=R_{\mbox{\tiny max}}$.
+Thus, the absorption opacity is zero $\tilde{\chi}=0$, and the scattering opacity is given by a power law in radius
+\begin{equation}
+  \sigma=r^{-n}.  
+  \label{eq:opacityMilne}
+\end{equation}
+\citet{hummerRybicki_1971} computed steady-state solutions for $n=3/2$, $2$, and $3$, and different values of $R_{\mbox{\tiny max}}$ by solving the radiative transfer equation.  
+Here we compare results obtained with the two-moment model with solutions given by \citet{hummerRybicki_1971}.
+
+With the scattering opacity in Eq.~\eqref{eq:opacityMilne}, the optical depth at radius $r$ is given by
+\begin{equation}
+  \tau(r)=\f{1}{n-1}\big[\,1/r^{n-1}-1/R_{\mbox{\tiny max}}^{n-1}\,\big].
+\end{equation}
+\citet{hummerRybicki_1971} also provide asymptotic solutions for the energy density in the optically thick and thin regimes, which we use to set initial values and boundary conditions when solving the two-moment equations.
+In the optically thick regime (large $\tau$), the asymptotic value for the energy density is
+\begin{equation}
+  \cJ_{\mbox{\tiny thick}}(r)
+  =\f{3}{r^{2}}\,\Big(\,\f{n-1}{n+1}\,\Big)\,[\,\tau+K\,], 
+  \label{eq:MilneThick}
+\end{equation}
+where $K$ is a constant.  
+In the optically thin regime (small $\tau$), the asymptotic value is
+\begin{equation}
+  \cJ_{\mbox{\tiny thin}}(r)
+  =\f{1}{r^{2}}\,[\,1+\tau\,].  
+\end{equation}
+Our initial condition for the energy density is then set as
+\begin{equation}
+  \cJ_{0}(r)
+  =(1-e^{-\tau(r)})\,\cJ_{\mbox{\tiny thick}}(r)+e^{-\tau(r)}\,\cJ_{\mbox{\tiny thin}}(r),
+\end{equation}
+while the initial momentum density is set as $\cH_{r,0}(r)=1/r^{2}$.  
+These expressions are also used to set boundary conditions, which are held fixed during the computations.  
+(We use solutions provided by \citet{hummerRybicki_1971} in the thick regime to determine values for the constant $K$ in Eq.~\eqref{eq:MilneThick}.)
+With the specified initial and boundary conditions, we evolve the moment equations until a steady state is reached.
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[scale=0.4]{./Figures/MilneProblem1D_n20.png} &
+      \includegraphics[scale=0.4]{./Figures/MilneProblem1D_n20_EddingtonFactors.png} \\
+      \includegraphics[scale=0.4]{./Figures/MilneProblem1D_n15.png} &
+      \includegraphics[scale=0.4]{./Figures/MilneProblem1D_n30.png}
+    \end{tabular}
+  \end{center}
+  \caption{Results of the Milne problem obtained with the two-moment model (solid lines), obtained with the DG(2)+SIRK2 scheme, compared with solutions provided by \citep{hummerRybicki_1971} (boxes).
+See text for details.}
+  \label{fig:milneProblem1D}
+\end{figure}
+
+Results for various combinations of $n$ and $R_{\mbox{\tiny max}}$, obtained with the DG2+SIRK2 scheme, are plotted in Figure~\ref{fig:milneProblem1D}.  
+The radius of the inner boundary is $R_{\mbox{\tiny min}}=0.01$ in all the models.  
+We use 64 elements for the models with $R_{\mbox{\tiny max}}=0.1$, and 128 elements for the models with $R_{\mbox{\tiny max}}=10$, $30$, and $100$.  
+The size of the innermost (smallest) element is $\Delta r=10^{-3}$, which increases geometrically with radius.
+
+In the upper left panel in Figure~\ref{fig:milneProblem1D}, we plot $\cJ\times r^{2}$ versus radius for $n=2$, where $R_{\mbox{\tiny max}}=0.1$ (solid black lines) and $R_{\mbox{\tiny max}}=30$ (solid blue lines).
+These results are compared with solutions given by \citet{hummerRybicki_1971} (black and blue boxes).  
+We also plot the asymptotic values in the thick regime (dashed lines), while the radius where $\tau=1$ is indicated with dotted vertical lines.  
+The the two lower panels show similar results using different values of $n$ and $R_{\mbox{\tiny max}}$.  
+In the lower left panel we plot results for $n=3/2$, with $R_{\mbox{\tiny max}}=0.1$ (black lines) and $R_{\mbox{\tiny max}}=100$.  
+In the lower right panel we plot results for $n=3$, with $R_{\mbox{\tiny max}}=0.1$ (black lines) and $R_{\mbox{\tiny max}}=10$.  
+In the upper right panel we plot flux factors ($\cH_{r}/\cJ$, black lines) and Eddington factors ($\psi$, blue lines) for a model with $n=2$ and $R_{\mbox{\tiny max}}=10$, and compare with results given \citet{hummerRybicki_1971} (their Table~I; boxes).
+For this model, we computed results with the Minerbo closure (cf. Eq.~\eqref{eq:eddingtonFactor}; solid lines) and the Levermore closure (cf. Eq.~\eqref{eq:eddingtonFactorLevermore}; dashed lines).  
+As can be seen, there is very little difference between the closure methods, but the results obtained with the Levermore closure are somewhat closer to the results given by \citet{hummerRybicki_1971}.
+
+Overall, there is quite good agreement between the results obtained with the two-moment model and the transport solutions of \citet{hummerRybicki_1971} when $R_{\mbox{\tiny max}}/R_{\mbox{\tiny min}}=10$.
+For larger values of this ratio, the agreement is worse, but seems to improve with increasing value of the index $n$ (cf. the blue lines in the lower two panels in Figure~\ref{fig:milneProblem1D}).
+
+\section{Transport Problems with Tabulated Neutrino Opacities}
 
@@
 
-\subsubsection{Neutrino-Electron Scattering}
+\subsubsection{Neutrino-Electron Scattering (NES)}
+
+When NES is included the internal energy of the fluid evolves according to
+\begin{align}
+  \rho\,d_{t}\epsilon
+  &=-\int_{\bbR^{+}}\int_{\bbR^{+}}\big(4\pi-\cJ(\epsilonNu)\big)R^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu} \\
+  &\hspace{12pt}
+  +\int_{\bbR^{+}}\int_{\bbR^{+}}\cJ(\epsilonNu)\,R^{\Out}(\epsilonNu,\epsilonNu')\,\big(4\pi-\cJ(\epsilonNu)\big)\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu}.  
+\end{align}
+With the semi-implicit approximation (evaluating the NES scattering rates using fluid properties at $t^{n}$), the neutrino number density can be solved for without iterative coupling to the thermodynamic state of the fluid.
+We first define the solution vector $\bcJ=(\cJ_{1},\ldots,\cJ_{M^{\epsilonNu}})^{\mbox{\tiny T}}$, and solve the nonlinear system of equations
+\begin{equation}
+  \bF(\bcJ^{n+1})=0
+  \label{eq:NonlinearSystemNES}
+\end{equation}
+using Newton's method.  
+Here, the $j$th component of the nonlinear system of equations is given by
+\begin{equation}
+  F_{j}(\bcJ^{n+1})
+  =\big(\cJ_{j}^{n+1}-\cJ_{j}^{n}\big)
+  -\dt\,\Big\{\,
+    \big(4\pi-\cJ_{j}^{n+1}\big)\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1}
+    -\cJ_{j}^{n+1}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)\,\Big\},
+\end{equation}
+and the Jacobian matrix is
+\begin{align}
+  \pderiv{\bF}{\bcJ}
+  =\pderiv{F_{j}}{\cJ_{k}}
+  &=\delta_{jk}\,\Big(1+\dt\,\Big\{\sum_{l=1}^{M^{\epsilonNu}}W_{l}^{(2)}\,R_{jl}^{\In,n}\,\cJ_{l}
+  +\sum_{l=1}^{M^{\epsilonNu}}W_{l}^{(2)}\,R_{jl}^{\Out,n}\,\big(4\pi-\cJ_{l}\big)\Big\}\Big) \nonumber \\
+  &\hspace{12pt}
+  -\dt\,\Big\{\big(4\pi-\cJ_{j}\big)\,W_{k}^{(2)}\,R_{jk}^{\In,n}+\cJ_{j}\,W_{k}^{(2)}\,R_{jk}^{\Out,n}\Big\}.
+\end{align}
+When Eq.~\eqref{eq:NonlinearSystemNES} is converged to give $\bcJ^{n+1}$, the fluid energy density is updated as
+\begin{align}
+  \epsilon^{n+1}
+  &=\epsilon^{n}-\f{\dt}{\rho}
+  \Big\{\,
+    \sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\big(4\pi-\cJ_{j}^{n+1}\big)
+    \sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1} \nonumber \\
+    &\hspace{56pt}
+    -\sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\,\cJ_{j}^{n+1}
+    \sum_{k=1}^{M^{\epsilonNu}}W^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)
+  \,\Big\}.
+\end{align}
 
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.75\textwidth]{./Figures/RelaxationEmissionAbsorption_Spectra_ModelA}
+  \end{center}
+  \caption{Results from solving an emission/absorption relaxation problem with initial material properties given by Model A in Table~\ref{tab:tabulatedModels}.  
+  The neutrino energy spectrum is plotted for various times as the radiation field approaches equilibrium.}
+  \label{fig:RelaxationEmissionAbsorption}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.85\textwidth]{./Figures/RelaxationNES_Spectra.png}
+    \begin{tabular}{cc}
+      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_DensitiesVsTime.png} &
+      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_EnergiesVsTime.png}
+    \end{tabular}
+  \end{center}
+  \caption{Results from solving an NES relaxation problem with initial material properties given by Model C in Table~\ref{tab:tabulatedModels}.}
+  \label{fig:RelaxationNES}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_DensitiesVsTime_Timestep.png} &
+      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_EnergiesVsTime_Timestep.png}
+    \end{tabular}
+  \end{center}
+  \caption{Results from the NES relaxation problem with initial material properties given by Model C in Table~\ref{tab:tabulatedModels}, where the timestep $\dt$ has been set to $10^{-5}$~ms (solid lines), $10^{-4}$~ms (dashed lines), and $10^{-3}$~ms (dotted lines).
+In the left panel we plot the occupation density versus time for $\epsilonNu=11.2$~MeV (red lines) and $\epsilonNu=97.5$~MeV (blue lines).
+In the right panel we plot the fluid energy versus time.}
+  \label{fig:RelaxationNES_Timestep}
+\end{figure}
+
 \subsection{Deleptonization}
@@
 \end{figure}
+
+\begin{figure}
+  \begin{center}
+	\includegraphics[width=.85\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction.png}
+	\begin{tabular}{cc}
+	  \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_Temperature.png} &
+	  \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_EntropyPerBaryon.png}
+	\end{tabular}
+  \end{center}
+  \caption{Fluid quantities from the deleptonization problem.  Plotted versus radius for various times are electron fraction (top), temperature (bottom left), and entropy per baryon (bottom right).}
+  \label{fig:}
+\end{figure}
+
+\begin{equation}
+  J=\int_{\bbR^{+}}\cJ\,dV_{\epsilonNu}
+\end{equation}
+
+\begin{equation}
+  f_{r}=\f{1}{J}\int_{\bbR^{+}}\cH_{r}\,dV_{\epsilonNu}
+\end{equation}
+
+\begin{equation}
+  \bar{\epsilonNu}=\f{1}{J}\int_{\bbR^{+}}\cJ\,\epsilonNu\,dV_{\epsilonNu}
+\end{equation}
+
+\begin{equation}
+  L_{r}=4\pi\,r^{2}\,\int_{\bbR^{+}}\cH_{r}\,\epsilonNu\,dV_{\epsilonNu}
+\end{equation}
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_NumberDensity.png} &
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_FluxFactor.png} \\
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MeanEnergy.png} &
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_Luminosity.png}
+    \end{tabular}
+  \end{center}
+  \caption{Radiation quantities from the deleptonization problem.
+Plotted versus radius for various times are neutrino number density (top left), flux factor (top right), mean energy (bottom left), and luminosity (bottom right).}
+  \label{fig:}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+      \includegraphics[scale=0.78]{./Figures/DeleptonizationProblem1D_Spectra.png}
+  \end{center}
+  \caption{Neutrino energy spectra at various radii for $t=100$~ms (solid lines).  The dashed lines represent equilibrium spectra, computed using local thermodynamic conditions.}
+  \label{fig:}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction_SpatialResolution.png} &
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MeanEnergy_SpatialResolution.png} \\
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction_SpectralResolution.png} &
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MeanEnergy_SpectralResolution.png}
+    \end{tabular}
+  \end{center}
+  \caption{Results for the deleptonization problem where the spatial and spectral resolution has been varied: the electron fraction (left panels) and mean energy (right panel) are plotted versus radius for $t=100$~ms.}
+  \label{fig:}
+\end{figure}
+
+\section{Miniapp: Collapse of Stellar Iron Core}
 

### 2017-07-18 Documents/Euler/dgEulerCurvilinear.tex
Added skeleton convergence table

@@
 
+\subsubsection{Entropy Waves (Accuracy Test)}
+
+\begin{table}
+  \begin{center}
+  \caption{$L^{\infty}$ error and convergence rates for the entropy wave problem.}
+  \label{tab:streamingSineWave}
+  \begin{tabular}{ccccccccc}
+    & \multicolumn{4}{c}{SSP-RK2} & \multicolumn{4}{c}{SSP-RK3} \\
+    \cmidrule(r){2-5} \cmidrule(r){6-9}
+    $N$ & DG(1) & Rate & DG(2) & Rate & DG(2) & Rate & DG(3) & Rate \\
+    \midrule \midrule
+    8     & $x.xxx\times10^{-x}$ & ---  & $x.xxx\times10^{-x}$ & ---  & $x.xxx\times10^{-x}$ & ---  & $x.xxx\times10^{-x}$  & --- \\
+    16   & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
+    32   & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
+    64   & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
+    128 & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
+    256 & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
+    \midrule \midrule
+  \end{tabular}
+  \end{center}
+\end{table}
+
+\subsubsection{Sound Waves}
+
 \subsection{Riemann Problems}
+
+\subsubsection{Shock Tube}
 
@@
 \subsubsection{Hydrostatic Polytrope}
+
+\subsubsection{Homologous Collapse}
 

### 2017-07-19 Documents/M1/dgM1Curvilinear.tex
Keep updates.

@@
 The scattering opacities $\sigma(\epsilonNu,\bU)$ contains isoenergetic scattering opacities, neutrino-electron scattering opacities and have a integral form in the Boltzmann equation: if we include emission, absorption, isoenergetic scattering of neutrino by nucleons and nuclei, and neutrino electron scattering, the simplified Boltzmann equation is
-\begin{align}
-\dfrac{1}{c}\dfrac{\partial f(\epsilonNu,\bU)}{\partial t} = 
+
+\begin{align}
+\dfrac{1}{c}\dfrac{\partial f(\omegaNu,\epsilonNu,\bx,t)}{\partial t} = 
 &  \eta(\epsilonNu,\bU) - \tilde{\chi}(\epsilonNu,\bU)f(\epsilonNu,\bU) \nonumber \\
-& + \dfrac{1}{c(hc)^3} \epsilonNu^2 \int d\mu^\prime_0 R_{IS}( \mu^\prime_0, \mu_0,\epsilonNu, \bU) f(\mu^\prime_0, \epsilonNu,\bU) \nonumber \\
-& - \dfrac{1}{c(hc)^3} \epsilonNu^2 f(\epsilonNu,\bU)\int d\mu^\prime_0 R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) \nonumber \\
-& + \dfrac{1}{c(hc)^3} [1- f(\epsilonNu,\bU)] \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime_0 R^{in}_{NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} )f(\mu^\prime_0,\epsilonNu^{\prime} ) \nonumber \\
-& - \dfrac{1}{c(hc)^3} f(\epsilonNu,\bU) \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime R^{out}_{NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} ) [1-f(\mu^\prime_0,\epsilonNu^{\prime} )] .
+& + \dfrac{1}{c(hc)^3} \epsilonNu^2 \int d\mu^\prime_0 R_{\IS}( \mu^\prime_0, \mu_0,\epsilonNu, \bU) f(\mu^\prime_0, \epsilonNu,\bU) \nonumber \\
+& - \dfrac{1}{c(hc)^3} \epsilonNu^2 f(\omegaNu,\epsilonNu,\bx,t)\int d\mu^\prime_0 R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) \nonumber \\
+& + \dfrac{1}{c(hc)^3} [1- f(\omegaNu,\epsilonNu,\bx,t)] \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime_0 R^{\In}_{\NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} )f(\mu^\prime_0,\epsilonNu^{\prime} ) \nonumber \\
+& - \dfrac{1}{c(hc)^3} f(\omegaNu,\epsilonNu,\bx,t) \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime R^{\Out}_{\NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} ) [1-f(\mu^\prime_0,\epsilonNu^{\prime} )].
 \end{align}
@@
 
-The two terms of electron-neutrino absorption on nucleons are
-\begin{align}
-\chi_{nucleon}(\epsilonNu,\bU) & = \dfrac{G^2_F}{\pi} \eta_{np}(g_V^2+3g_A^2)[1-F_e(\varepsilon+Q)](\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2} \label{eq:nucleonabsorption} ,\\
-\eta_{nucleon}(\epsilonNu,\bU) &= \dfrac{G^2_F}{\pi}\eta_{pn}(g_V^2+3g_A^2)F_e(\varepsilon+Q)(\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2} \label{eq:nucleonemissivity} ,
-\end{align}
-and the two terms of electron-neutrino absorption on nuclear are
-\begin{align}
-\chi_{nuclear}(\epsilonNu,\bU) & = \dfrac{G^2_F}{\pi} n_A e^{(\mu_n -\mu_p -Q')/k_B T} g^2_A \dfrac{2}{7} N_p(Z) N_h(N)[1-F_e(\varepsilon+Q')](\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} \label{eq:nuclearabsorption} ,\\
-\eta_{nuclear}(\epsilonNu,\bU) &=\dfrac{G^2_F}{\pi} n_A g^2_A \dfrac{2}{7} N_p(Z) N_h(N)F_e(\varepsilon+Q')(\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} \label{eq:nuclearemissivity},
-\end{align} 
-where $g_V = 1$ and $g_A =1.23$ are form factors resulting from virtual strong-interaction processes, $M_e = 0.511$ MeV is the electron rest energy, $Q = 1.2935$ MeV is the difference between the neutron and proton rest energies, $\mu_n$ and $\mu_p$ are the neutron and proton chemical potential, respectively.
-And $Q'$ is defined by $Q' = \mu_n -\mu_p + \Delta$, where $\Delta=3$MeV is the energy of the $1f_{5/2}$ level above the ground state.
-
-The factor $G^2_F$ in Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity} is the Fermi constant [$G=(1.015\pm 0.03)\time 10^5 M_p^{-2}$] with the value
-\begin{equation}
-G^2_F = \left[ \dfrac{1}{(\hbar c)^4} \right] G^2 = 5.18 \times 10^{-44} MeV^{-2}cm^2, 
-\end{equation}
-giving $\chi$ and $\eta$ the required units of $cm^{-1}$.
-
-In Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity}, $F_e(E)$ is the Fermi-Dirac distribution function:
-\begin{align}
-F_e(E) = \dfrac{1}{e^{(E-\mu_e)/k_B T} + 1},
-\end{align}
-where $\mu_e$ is the electron chemical potential.
-
-In Eq.~\eqref{eq:nucleonabsorption} and ~\eqref{eq:nucleonemissivity}, $\eta_{np}$ and $\eta_{pn}$ take into account the nucleon final-state blocking. 
-\begin{align}
-\eta_{pn} = \dfrac{2}{h^3 c^3} \int d^3 p F_p (E)[1-F_n(E)] = (n_n - n_p) \dfrac{1}{e^{(\mu_n^0 - \mu_p^0)/k_bT}-1},\\
-\eta_{np} = \dfrac{2}{h^3 c^3} \int d^3 p F_n (E)[1-F_p(E)] = (n_p - n_n) \dfrac{1}{e^{(\mu_p^0 - \mu_n^0)/k_bT}-1}.
-\end{align}
-
-The factors $\eta_{np}$ and $\eta_{pn}$ equal to $n_n$ and $n_p$, the nucleon number density, when the nucleons are non-degenerate, respectively.
-\begin{align}
-n_p & =  \dfrac{X_p \rho}{m_p} \\
-n_n & =  \dfrac{X_n \rho}{m_n},
-\end{align}
-where $X_p$ and $X_n$ are the proton and neutron fractions, respectively.
-
-In Eq.~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity}, $n_A$ is the nuclei number density and $n_A = \dfrac{\rho X_H}{m_B A}$.
-The function $N_p$ is the number of protons in the single-particle $1f_{7/2}$ level and $N_h$ is the number of neutron holes in the single-particle $1f_{5/2}$ level.
-As a crude estimate of $N_p$ and $N_h$, a zero-order shell model predicts that
-\[   
-N_p(Z) = 
-     \begin{cases}
-       0, &\quad Z<20\\
-       Z-20, &\quad 20<Z<28 \\
-       8, &\quad Z>28,\\
-     \end{cases}
-\]
+The two terms of electron-neutrino absorption on nucleons $\chi_{nucleon}(\epsilonNu,\bU)$ and $\eta_{nucleon}(\epsilonNu,\bU)$ are given by Eq.
+(C13) and Eq.
+(C15) in \citet{bruenn_1985}  and the two terms of electron-neutrino absorption $\chi_{nuclear}(\epsilonNu,\bU)$ and $\eta_{nuclear}(\epsilonNu,\bU)$ on nuclear are given by Eq.
+(C29) and Eq.
+(C27) in \citet{bruenn_1985}.
+They all have units of $cm^{-1}$.
+
+\subsection{The isoenergetic scattering kernel}
+The isoenergetic scattering kernel $R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
+\begin{align}
+R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) & = R_{\IS}^{nucleons}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) +  R_{\IS}^{nuclei}(\mu_0, \mu^\prime_0, \epsilonNu,\bU),
+\end{align}
+where
+\begin{align}
+\cos\theta = \mu_0\mu^\prime_0 + [(1-\mu_0^2)(1-\mu_0^{\prime 2})]^{1/2}\cos\theta,
+\end{align}
 and
-\[   
-N_h(N) = 
-     \begin{cases}
-       6, &\quad N<34\\
-       40-N, &\quad 34<N<40 \\
-       0, &\quad N>40.\\
-     \end{cases}
-\]
-
-The sum of Eq.~\eqref{eq:nucleonabsorption}, ~\eqref{eq:nucleonemissivity}, ~\eqref{eq:nuclearabsorption} and ~\eqref{eq:nuclearemissivity} gives the explicit expression of the absorption opacity of neutrino $\chi(\epsilonNu,\bU)$ .
-
-\subsection{The isoenergetic scattering kernel}
-The isoenergetic scattering kernel $R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
-\begin{align}
-R_{IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) & = R_{IS}^{nucleons}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) +  R_{IS}^{nuclei}(\mu_0, \mu^\prime_0, \epsilonNu,\bU),
-\end{align}
-where
-\begin{align}
-\cos\theta = \mu_0\mu^\prime_0 + [(1-\mu_0^2)(1-\mu_0^{\prime 2})]^{1/2}\cos\theta,
-\end{align}
-and
-\begin{align}
-R_{IS}(\cos\theta, \epsilonNu, \bU) = R^{nucleons}(\cos\theta,\epsilonNu, \bU) + R^{nuclei}_{IS}(\cos\theta, \epsilonNu, \bU)
-\end{align}
-where
-\begin{align}
-& R^{nucleons}_{IS} (\cos\theta,\epsilonNu, \bU) = \dfrac{(2\pi)^2 G_F^2}{h} \nonumber \\
-& \cdot \left\lbrace  \eta_{nn}\left[ (h^n_V)^2 + 3(h^n_A)^2\right] + \eta_{pp} \left[ (h^p_V)^2 + 3(h^p_A)^2\right] +\eta_{nn}\left[ (h^n_V)^2 - (h^n_A)^2\right]\cos\theta + \eta_{pp}\left[ (h^p_V)^2 - (h^p_A)^2\right]\cos\theta \right\rbrace
-\end{align}
-and
-\begin{align}
-R^{nuclei}_{IS}(\cos\theta,\epsilonNu,\bU)  = \dfrac{(2\pi)^2 G_F^2}{h}\dfrac{\rho X_H}{m_B}A\left(  C_{V0} - \dfrac{1}{2}\dfrac{N-Z}{A} C_{V1}\right)^2(1+\cos\theta)e^{-4b\epsilonNu^2(1-\cos\theta)}.
-\end{align}
-$h^p_V$, $h^n_V$, $h^p_A$ and $h^n_A$, are the nucleon neutral current form factors arising from virtual strong-interaction processes: $h_V^p = \dfrac{1}{2} - 2 \sin^2\theta_W$, $h^n_V = - \dfrac{1}{2}$, $h_A^p = \dfrac{1}{2}g_A$, and $h^n_A = - \dfrac{1}{2} g_A$, where $\theta_W$ is the Weinberg angle.
-The constants, $C_{V0}$ and $C_{V1}$, are defined in terms of $h_V^p$ and $h_V^n$: $C_{V0} = \dfrac{1}{2}(h_V^p + h_V^n)$ and $C_{V1} = h_V^p - h_V^n$.
-The quantity $b$ is given by $b = 4.8 \times 10^{-6} A^{2/3}$.
-
-The factors $\eta_{pp}$ and $\eta_{nn}$ account for the nucleon final-state blocking,
-\begin{align}
-\eta_{pp} = T \dfrac{\partial n_p}{\partial \mu_p} = n_p \dfrac{3T/2\epsilon^p_F}{[1+(3T/2\epsilon^p_F)^2]^{1/2}}, \\
-\eta_{nn} = T \dfrac{\partial n_n}{\partial \mu_n}=n_n \dfrac{3T/2\epsilon^n_F}{[1+(3T/2\epsilon^n_F)^2]^{1/2}},
-\end{align}
-where $\epsilon^p_F$ and $\epsilon^n_F$ are the proton and neutron Fermi energies, respectively,
-\begin{align}
-\epsilon^p_F = \dfrac{h^2}{8 \pi^2 m_B}(3\pi^2n_p)^{2/3},\\
-\epsilon^n_F = \dfrac{h^2}{8\pi^2m_B}(3\pi^2n_n)^{2/3}.
-\end{align}
-For nondegenerate, nonrelativistic nucleons, $\eta_{pp}$ and $\eta_{nn}$ are given by
-\begin{align}
-&\eta_{pp} = n_p \\
-&\eta_{nn} = n_n.
-\end{align}
+\begin{align}
+R_{\IS}(\cos\theta, \epsilonNu, \bU) = R^{nucleons}(\cos\theta,\epsilonNu, \bU) + R^{nuclei}_{\IS}(\cos\theta, \epsilonNu, \bU)
+\end{align}
+where $R^{nucleons}_{\IS} (\cos\theta,\epsilonNu, \bU)$ and $R^{nuclei}_{\IS}(\cos\theta,\epsilonNu,\bU)$ are given by Eq. (35) and Eq. (36) in \citet{mezzacappaBruenn_1993a}.
 
@@
 \begin{align}
-R_{IS}(\omega, \omega, \cos\theta) \approx \dfrac{1}{2} \Phi_{0,IS}(\omega) + \dfrac{3}{2}\Phi_{1,IS}(\omega)\cos\theta
+R_{\IS}(\omega, \omega, \cos\theta) \approx \dfrac{1}{2} \Phi_{0,\IS}(\omega) + \dfrac{3}{2}\Phi_{1,\IS}(\omega)\cos\theta
 \end{align}
@@
 \subsection{The neutrino-electron scattering kernel}
-Given by \citet{bruenn_1985}, for $\epsilonNu \neq \epsilonNu^\prime$, the neutrino-electron scattering kernels are written as
-\begin{align}
-    R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime,\omega, \bU) = & R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime,\mu_0,\mu^\prime_0,\phi_0, \bU) \nonumber \\
-     = &\dfrac{1}{2}\dfrac{1}{(2\pi)^3}\dfrac{\pi \sigma_0 c}{(m_e c^2)^2}\dfrac{1}{\epsilonNu, \epsilonNu^\prime} [ \beta_1I_1(\epsilonNu,\epsilonNu^\prime,\omega,\bU) + \beta_2I_2(\epsilonNu,\epsilonNu^\prime,\omega, \bU) \nonumber \\
-    & +  \beta_3I_3(\epsilonNu,\epsilonNu^\prime,\omega, \bU)] 
-\end{align}
-where $\beta_1 = (C_V + C_A)^2$, $\beta_2 = (C_V -C_A)^2$, $\beta_3 = C_A^2 - C_V^2$, $\sigma_0 = 1.746 \times 10^{-44} cm^{-2}$, and
-\begin{align}
-\omega = \mu_0 \mu_0^\prime + [(1-\mu_0^2)(1-\mu_0^{\prime 2})]^{1/2}\cos\phi_0
-\end{align}
-and where the function $I_{1,2,3}(\epsilonNu,\epsilonNu^\prime,\omega, \bU)$ are defined by 
-\begin{align}
-I_1(\epsilonNu, \epsilonNu^\prime, \omega, \bU) = & \dfrac{2\pi T \epsilonNu^2 \epsilonNu^{\prime 2}(1-\omega)^2}{\Delta^5} f_\gamma(\epsilonNu^\prime - \epsilonNu) \cdot \\
-& \left\lbrace  A T^2 [G_2(y_0)+2y_0G_1(y_0)+y_0^2G_0(y_0)] \right.\nonumber\\
-& + \left. BT[G_1(y_0)+y_0G_0(y_0)] + CG_0(y_0)\right\rbrace,
-\end{align}
-\begin{align}
-I_2(\epsilonNu, \epsilonNu^\prime, \omega, \bU)  = I_1(\epsilonNu \rightarrow -\epsilonNu^\prime, \epsilonNu^\prime\rightarrow -\epsilonNu, \omega, \bU) 
-\end{align}
-\begin{align}
-I_3(\epsilonNu, \epsilonNu^\prime, \omega, \bU)  = \dfrac{2\pi T \epsilonNu \epsilonNu^{\prime}(1-\omega)(m_ec^2)^2}{\Delta} f_\gamma(\epsilonNu^\prime - \epsilonNu) G_0(y_0)
-\end{align}
-with
-\begin{align}
-\Delta = (\epsilonNu^2 + \epsilonNu^{\prime 2} - 2\epsilonNu \epsilonNu^\prime
-\omega)^{1/2}
-\end{align}
-\begin{align}
-y_0 = \dfrac{1}{T}\left\lbrace - \dfrac{\epsilonNu -\epsilonNu^\prime}{2} + \dfrac{\Delta}{2} \left[1+\dfrac{2(m_e c^2)^2}{\epsilonNu \epsilonNu^\prime (1-\omega)}\right]^{1/2} \right\rbrace 
-\end{align}
-\begin{align}
-A &= \epsilonNu^2 + \epsilonNu^{\prime 2} + \epsilonNu \epsilonNu^\prime(3+\omega),\\
-B &= \epsilonNu \left[ 2\epsilonNu^2 + \epsilonNu \epsilonNu^\prime(3-\omega) - E^{\prime 2}_0(1+3\omega) \right] \\
-C &= \epsilonNu^2\left[ (\epsilonNu -\epsilonNu^\prime \omega)^2 - \dfrac{E^{\prime 2}_0 (1-\omega^2)}{2} - \dfrac{(1+\omega)(m_e c^2)^2 \Delta^2}{2(1-\omega)\epsilonNu^2} \right] 
-\end{align}
-\begin{align}
-f_{\gamma}(x) = \dfrac{1}{e^{x/T} - 1}
-\end{align}
-and the function $G_n(y)$ are defined in terms of Fermi integrals:
-\begin{align}
-G_n(y) = F_n(\eta^\prime - y) - F_n(\eta - y)
-\end{align}
-where
-\begin{align}
-\eta &= \dfrac{\mu_e}{T} \\
-\eta^\prime &= \eta - \dfrac{\epsilonNu - \epsilonNu^\prime}{T} \\
-F_n(\eta) &= \int_{0}^{\infty} \dfrac{x^n dx}{e^{x-\eta}+1}
-\end{align}
-
-For $\epsilonNu = \epsilonNu^\prime$, the functions
-\begin{align}
-I_1(\epsilonNu, \epsilonNu^\prime, \omega, \bU) = I_1(\epsilonNu, \omega, \bU) &= \dfrac{2\pi T \epsilonNu^4 (1-\omega)^2}{\Delta^5}\cdot \\
-& \left\lbrace  A T^2 [2F_1(\eta -y_0)+2y_0F_0(\eta-y_0)+y_0^2F_{-1}(\eta-y_0)] \right.\nonumber\\
-& + \left. BT[F_0(\eta-y_0)+y_0F_{-1}(\eta-y_0)] + CF_{-1}(\eta-y_0)\right\rbrace,
-\end{align}
-\begin{align}
-I_2(\epsilonNu, \epsilonNu^\prime, \omega, \bU)  = I_2(\epsilonNu, \omega, \bU)&=I_1(\epsilonNu, \omega, \bU) 
-\end{align}
-\begin{align}
-I_3(\epsilonNu, \epsilonNu^\prime, \omega,\bU)  = I_3(\epsilonNu, \omega, \bU)=\dfrac{2\pi T \epsilonNu^2(1-\omega)(m_ec^2)^2}{\Delta}F_{-1}(\eta - y_0)
-\end{align}
-with
-\begin{align}
-\Delta = (\epsilonNu^2 + \epsilonNu^{\prime 2} - 2\epsilonNu \epsilonNu^\prime
-\omega)^{1/2} = \epsilonNu(2 - 2\omega)^{1/2}
-\end{align}
-\begin{align}
-y_0 = \dfrac{1}{T}\left\lbrace \dfrac{\Delta}{2} \left[1+\dfrac{2(m_e c^2)^2}{\epsilonNu^2 (1-\omega)}\right]^{1/2} \right\rbrace 
-\end{align}
-\begin{align}
-A &= \epsilonNu ^2(5+\omega),\\
-B &= \epsilonNu^3 (4-4\omega),\\
-C &= \epsilonNu^2\left[\dfrac{E^{2}_0 (1-\omega^2)}{2} - \dfrac{(1+\omega)(m_e c^2)^2 \Delta^2}{2(1-\omega)\epsilonNu^2} \right] 
-\end{align}
-\begin{align}
-F_{-1} (\eta) &= \dfrac{1}{e^{-\eta} + 1} 
-\end{align}
-
-Therefore, $R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime, \omega)$ is known.
+The neutrino-electron scattering kernels are given by Eq.(9) and Eq.(28) in \citet{mezzacappaBruenn_1993c}.
+
+Therefore, $R^{\Out}_{\NES}(\epsilonNu,\epsilonNu^\prime, \omega)$ is known.
 
@@
 \begin{align}
-R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU) = \sum_{l=0}^{\infty} \dfrac{2l+1}{2} R^{out}_{{NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) P_l(\omega),
-\end{align}
-where the Legendre coefficients $R^{out}_{{NES}, l}(\epsilonNu,\epsilonNu^\prime)$ are given by
-\begin{align}
-R^{out}_{{NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) = \int_{-1}^{1} d\omega P_l(\omega) R^{out}_{NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU).
+R^{\Out}_{\NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU) = \sum_{l=0}^{\infty} \dfrac{2l+1}{2} R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) P_l(\omega),
+\end{align}
+where the Legendre coefficients $R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu^\prime)$ are given by
+\begin{align}
+R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) = \int_{-1}^{1} d\omega P_l(\omega) R^{\Out}_{\NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU).
 \end{align}
@@
 \begin{align}
-R^{in/out}_{NES}(\omega, \omega^{\prime}, \cos\theta, \bU) & = \sum_{l=0}^{1} \dfrac{ 2l+1}{2}\Phi^{in/out}_{l,NES}(\omega,\omega^{\prime},\bU)P_l(\cos\theta) \\
-& \approx \dfrac{1}{2}\Phi_{0,NES}^{in/out}(\omega,\omega^{\prime}, \bU) + \dfrac{3}{2}\Phi^{in/out}_{1,NES}(\omega,\omega^{\prime}, \bU)\cos\theta
+R^{\In/\Out}_{\NES}(\omega, \omega^{\prime}, \cos\theta, \bU) & = \sum_{l=0}^{1} \dfrac{ 2l+1}{2}\Phi^{\In/\Out}_{l,\NES}(\omega,\omega^{\prime},\bU)P_l(\cos\theta) \\
+& \approx \dfrac{1}{2}\Phi_{0,\NES}^{\In/\Out}(\omega,\omega^{\prime}, \bU) + \dfrac{3}{2}\Phi^{\In/\Out}_{1,\NES}(\omega,\omega^{\prime}, \bU)\cos\theta
 \end{align}

### 2017-07-20 Documents/M1/dgM1Curvilinear.tex
Keep updates.

@@
 \section{Two-Moment Model for Neutrino Transport}
+\label{sec:twoMomentModel}
 
@@
 
-%\ee{Ran write about tabulated B85 absorption and scattering opacities.}
 In this section, we bring the speed of light $c$ back.
 
-The total opacity $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$, where $\tilde{\chi}(\epsilonNu,\bU)$ is the absorption opacity of neutrino and  $\sigma(\epsilonNu,\bU)$ is the scattering opacities.
-The absorption opacity of neutrino $\tilde{\chi}(\epsilonNu,\bU)$ 
-\begin{equation}
-  \tilde{\chi}(\epsilonNu,\bU) = \chi(\epsilonNu,\bU) + \eta(\epsilonNu,\bU), 
-\end{equation}
- is the sum of the neutrino emissivity $\eta(\epsilonNu,\bU) $ and the neutrino absorptivity  $ \chi(\epsilonNu,\bU)$.
-The scattering opacities $\sigma(\epsilonNu,\bU)$ contains isoenergetic scattering opacities, neutrino-electron scattering opacities and have a integral form in the Boltzmann equation: if we include emission, absorption, isoenergetic scattering of neutrino by nucleons and nuclei, and neutrino electron scattering, the simplified Boltzmann equation is
+As we mentioned in Section~\ref{sec:twoMomentModel}, the total opacity $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$.
+The absorption opacity of neutrino $\tilde{\chi}(\epsilonNu,\bU)$ is the sum of the neutrino emissivity $\eta(\epsilonNu,\bU) $ and the neutrino absorptivity  $ \chi(\epsilonNu,\bU)$:
+\begin{equation}
+  \tilde{\chi}(\epsilonNu,\bU) = \eta(\epsilonNu,\bU) + \chi(\epsilonNu,\bU). 
+\end{equation}
+ The scattering opacities $\sigma(\epsilonNu,\bU)$ contains (isotropic) elastic scattering opacities, neutrino-electron scattering opacities and have a integral form in the Boltzmann equation: the simplified Boltzmann equation is
 
@@
 
-The third and fourth terms are contributions from isoenergetic scattering of neutrino by nucleons and nuclei. The last two terms are contributions from neutrino-electron scattering.
+The third and fourth terms are contributions from (isotropic) elastic scattering of neutrino by nucleons and nuclei. The last two terms are contributions from neutrino-electron scattering.
 
@@
 
-\subsection{The isoenergetic scattering kernel}
-The isoenergetic scattering kernel $R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
+\subsection{The isotropic elastic scattering kernel}
+The isotropic elastic scattering kernel $R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
 \begin{align}
@@
 
-Expanding the isoenergetic scattering kernel in the first two terms of a Legendre series yields
+Expanding the isotropic elastic scattering kernel in the first two terms of a Legendre series yields
 \begin{align}
@@
 \end{align}
+
+The isotropic term $\dfrac{1}{2}\Phi_{0,\NES}^{\In/\Out}(\omega,\omega^{\prime}, \bU)$ is the $R^{\In}$ and $R^{\Out}$  in Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}.
 

### 2017-07-21 Documents/M1/dgM1Curvilinear.tex
Keep updated.

@@
 \dfrac{1}{c}\dfrac{\partial f(\omegaNu,\epsilonNu,\bx,t)}{\partial t} = 
-&  \eta(\epsilonNu,\bU) - \tilde{\chi}(\epsilonNu,\bU)f(\epsilonNu,\bU) \nonumber \\
-& + \dfrac{1}{c(hc)^3} \epsilonNu^2 \int d\mu^\prime_0 R_{\IS}( \mu^\prime_0, \mu_0,\epsilonNu, \bU) f(\mu^\prime_0, \epsilonNu,\bU) \nonumber \\
-& - \dfrac{1}{c(hc)^3} \epsilonNu^2 f(\omegaNu,\epsilonNu,\bx,t)\int d\mu^\prime_0 R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) \nonumber \\
-& + \dfrac{1}{c(hc)^3} [1- f(\omegaNu,\epsilonNu,\bx,t)] \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime_0 R^{\In}_{\NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} )f(\mu^\prime_0,\epsilonNu^{\prime} ) \nonumber \\
-& - \dfrac{1}{c(hc)^3} f(\omegaNu,\epsilonNu,\bx,t) \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime R^{\Out}_{\NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} ) [1-f(\mu^\prime_0,\epsilonNu^{\prime} )].
+&  \eta(\epsilonNu,\bU) - \tilde{\chi}(\epsilonNu,\bU)f(\omegaNu,\epsilonNu,\bx,t) \nonumber \\
+& + \dfrac{1}{c(hc)^3} \epsilonNu^2 \int d\mu'_0 R_{\IS}( \omega', \omega,\epsilonNu, \bU) f(\omega', \epsilonNu,\bx,t) \nonumber \\
+& - \dfrac{1}{c(hc)^3} \epsilonNu^2 f(\omegaNu,\epsilonNu,\bx,t)\int d\omega' R_{\IS}(\omega, \omega', \epsilonNu,\bU) \nonumber \\
+& + \dfrac{1}{c(hc)^3} [1- f(\omegaNu,\epsilonNu,\bx,t)] \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\omega' R^{\In}_{\NES} (\omega,\omega',\epsilonNu,\epsilonNu^{\prime},\bU)f(\omega',\epsilonNu^{\prime},\bx,t ) \nonumber \\
+& - \dfrac{1}{c(hc)^3} f(\omegaNu,\epsilonNu,\bx,t) \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu' R^{\Out}_{\NES} (\omega,\omega',\epsilonNu,\epsilonNu^{\prime},\bU) [1-f(\omega',\epsilonNu^{\prime},\bx,t )].
 \end{align}
@@
 \subsection{The isotropic elastic scattering kernel}
-The isotropic elastic scattering kernel $R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
-\begin{align}
-R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) & = R_{\IS}^{nucleons}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) +  R_{\IS}^{nuclei}(\mu_0, \mu^\prime_0, \epsilonNu,\bU),
+The isotropic elastic scattering kernel $R_{\IS}(\omega, \omega', \epsilonNu,\bU)$ has the following relation:
+\begin{align}
+R_{\IS}(\omega, \omega', \epsilonNu,\bU) & = R_{\IS}^{nucleons}(\omega, \omega', \epsilonNu,\bU) +  R_{\IS}^{nuclei}(\omega, \omega', \epsilonNu,\bU),
 \end{align}
@@
 \begin{align}
-\cos\theta = \mu_0\mu^\prime_0 + [(1-\mu_0^2)(1-\mu_0^{\prime 2})]^{1/2}\cos\theta,
+\cos\theta = \omega\omega' + [(1-\omega^2)(1-\omega^{\prime 2})]^{1/2}\cos\theta,
 \end{align}
@@
 \end{align}
-where $R^{nucleons}_{\IS} (\cos\theta,\epsilonNu, \bU)$ and $R^{nuclei}_{\IS}(\cos\theta,\epsilonNu,\bU)$ are given by Eq. (35) and Eq. (36) in \citet{mezzacappaBruenn_1993a}.
+where $R^{nucleons}_{\IS} (\cos\theta,\epsilonNu, \bU)$ and $R^{nuclei}_{\IS}(\cos\theta,\epsilonNu,\bU)$ are given by Eq. (35) and Eq. (36) in \citet{mezzacappaBruenn_1993a}, respectively.
 
@@
 \begin{align}
-R_{\IS}(\omega, \omega, \cos\theta) \approx \dfrac{1}{2} \Phi_{0,\IS}(\omega) + \dfrac{3}{2}\Phi_{1,\IS}(\omega)\cos\theta
+R_{\IS}(\cos\theta,\epsilonNu) \approx \dfrac{1}{2} \Phi_{0,\IS}(\epsilonNu) + \dfrac{3}{2}\Phi_{1,\IS}(\epsilonNu)\cos\theta
 \end{align}
@@
 
-Therefore, $R^{\Out}_{\NES}(\epsilonNu,\epsilonNu^\prime, \omega)$ is known.
-
-Expand the scattering kernel in a Legendre series:
-\begin{align}
-R^{\Out}_{\NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU) = \sum_{l=0}^{\infty} \dfrac{2l+1}{2} R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) P_l(\omega),
-\end{align}
-where the Legendre coefficients $R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu^\prime)$ are given by
-\begin{align}
-R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) = \int_{-1}^{1} d\omega P_l(\omega) R^{\Out}_{\NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU).
+Expand the neutrino-electron out scattering kernel $R^{\Out}_{\NES}(\epsilonNu,\epsilonNu', \omega)$ in a Legendre series:
+\begin{align}
+R^{\Out}_{\NES}(\epsilonNu,\epsilonNu', \omega, \bU) = \sum_{l=0}^{\infty} \dfrac{2l+1}{2} R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu', \bU) P_l(\omega),
+\end{align}
+where the Legendre coefficients $R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu')$ are given by
+\begin{align}
+R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu', \bU) = \int_{-1}^{1} d\omega P_l(\omega) R^{\Out}_{\NES}(\epsilonNu,\epsilonNu', \omega, \bU).
 \end{align}
@@
 \begin{align}
-R^{\In/\Out}_{\NES}(\omega, \omega^{\prime}, \cos\theta, \bU) & = \sum_{l=0}^{1} \dfrac{ 2l+1}{2}\Phi^{\In/\Out}_{l,\NES}(\omega,\omega^{\prime},\bU)P_l(\cos\theta) \\
-& \approx \dfrac{1}{2}\Phi_{0,\NES}^{\In/\Out}(\omega,\omega^{\prime}, \bU) + \dfrac{3}{2}\Phi^{\In/\Out}_{1,\NES}(\omega,\omega^{\prime}, \bU)\cos\theta
-\end{align}
-
-The isotropic term $\dfrac{1}{2}\Phi_{0,\NES}^{\In/\Out}(\omega,\omega^{\prime}, \bU)$ is the $R^{\In}$ and $R^{\Out}$  in Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}.
+R^{\In/\Out}_{\NES}(\epsilonNu, \epsilonNu^{\prime}, \cos\theta, \bU) & = \sum_{l=0}^{1} \dfrac{ 2l+1}{2}\Phi^{\In/\Out}_{l,\NES}(\epsilonNu,\epsilonNu^{\prime},\bU)P_l(\cos\theta) \\
+& \approx \dfrac{1}{2}\Phi_{0,\NES}^{\In/\Out}(\epsilonNu,\epsilonNu^{\prime}, \bU) + \dfrac{3}{2}\Phi^{\In/\Out}_{1,\NES}(\epsilonNu,\epsilonNu^{\prime}, \bU)\cos\theta
+\end{align}
+
+The isotropic term $\dfrac{1}{2}\Phi_{0,\NES}^{\In/\Out}(\epsilonNu,\epsilonNu^{\prime}, \bU)$ is the $R^{\In}(\epsilonNu,\epsilonNu')$ and $R^{\Out}(\epsilonNu,\epsilonNu')$  in Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}.
 

### 2017-07-22 Documents/M1/dgM1Curvilinear.tex
Reworked the opacity section.  Added figures for tabulated homogeneous sphere

--- 2017-07-20 Documents/M1/dgM1Curvilinear.tex
@@
 
-In this section, we bring the speed of light $c$ back.
-
-As we mentioned in Section~\ref{sec:twoMomentModel}, the total opacity $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$.
-The absorption opacity of neutrino $\tilde{\chi}(\epsilonNu,\bU)$ is the sum of the neutrino emissivity $\eta(\epsilonNu,\bU) $ and the neutrino absorptivity  $ \chi(\epsilonNu,\bU)$:
+To model neutrino-matter interactions, we have tabulated a basic --- but important --- set of neutrino opacities for inclusion in simulations presented in Section~\ref{sec:numericalTableOpacities}.  
+We consider a single neutrino specie (electron-type neutrinos), and include the relevant rates due to electron capture on nucleons and nuclei, iso-energetic (elastic) scattering on nucleons and nuclei, and elastic neutrino-electron scattering (NES).
+For completeness, we provide sufficient detail to arrive at the tabulates opacities relevant for the two-moment model.  
+For further details on the specific opacities we use, see \citet{bruenn_1985}, \citet{mezzacappaBruenn_1993a}, and \citet{mezzacappaBruenn_1993c}.
+
+As we mentioned in Section~\ref{sec:twoMomentModel} when discussing Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}, the total opacity (excluding NES) is $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$, where the absorption opacity $\tilde{\chi}(\epsilonNu,\bU)$, corrected for stimulated absorption, is given by the sum of the neutrino emissivity $\eta(\epsilonNu,\bU)$ and the neutrino absorptivity $\chi(\epsilonNu,\bU)$
 \begin{equation}
@@
 \end{equation}
- The scattering opacities $\sigma(\epsilonNu,\bU)$ contains (isotropic) elastic scattering opacities, neutrino-electron scattering opacities and have a integral form in the Boltzmann equation: the simplified Boltzmann equation is
-
+The scattering opacity $\sigma(\epsilonNu,\bU)$ is due to (isotropic) elastic scattering.   
+Neutrino-electron scattering gives rise to the integral operators involving the rates $R^{\In}(\epsilonNu,\epsilonNu',\bU)$ and $R^{\In}(\epsilonNu,\epsilonNu',\bU)$.  
+(In the following, to simplify the notation, we will drop the explicit spatial dependence and dependence on material properties $\bU$.)  
+To arrive at the collision terms for the two-moment model, we consider the space-homogeneous Boltzmann equation \citep[e.g., Eq.~(7) in][]{mezzacappaBruenn_1993c}
 \begin{align}
-\dfrac{1}{c}\dfrac{\partial f(\omegaNu,\epsilonNu,\bx,t)}{\partial t} = 
-&  \eta(\epsilonNu,\bU) - \tilde{\chi}(\epsilonNu,\bU)f(\epsilonNu,\bU) \nonumber \\
-& + \dfrac{1}{c(hc)^3} \epsilonNu^2 \int d\mu^\prime_0 R_{\IS}( \mu^\prime_0, \mu_0,\epsilonNu, \bU) f(\mu^\prime_0, \epsilonNu,\bU) \nonumber \\
-& - \dfrac{1}{c(hc)^3} \epsilonNu^2 f(\omegaNu,\epsilonNu,\bx,t)\int d\mu^\prime_0 R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) \nonumber \\
-& + \dfrac{1}{c(hc)^3} [1- f(\omegaNu,\epsilonNu,\bx,t)] \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime_0 R^{\In}_{\NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} )f(\mu^\prime_0,\epsilonNu^{\prime} ) \nonumber \\
-& - \dfrac{1}{c(hc)^3} f(\omegaNu,\epsilonNu,\bx,t) \int d\epsilonNu^{\prime} \epsilonNu^{\prime 2} \int d\mu^\prime R^{\Out}_{\NES} (\mu_0,\mu^\prime_0,\epsilonNu,\epsilonNu^{\prime} ) [1-f(\mu^\prime_0,\epsilonNu^{\prime} )].
+  \f{1}{c}\deriv{f}{t}(\omegaNu,\epsilonNu,t)
+  & = \eta(\epsilonNu) - \tilde{\chi}(\epsilonNu)\,f(\omegaNu,\epsilonNu,t) \nonumber \\
+  & \hspace{12pt}
+  + \frac{\epsilonNu^2}{c\,(hc)^3} \int_{\bbS^{2}} R_{\IS}(\bl'\cdot\bl,\epsilonNu)\,f(\omega', \epsilonNu,t)\,d\omegaNu'
+  - \frac{\epsilonNu^2}{c\,(hc)^3} f(\omegaNu,\epsilonNu,t) \int_{\bbS^{2}} R_{\IS}(\bl'\cdot\bl,\epsilonNu)\,d\omega' \nonumber \\
+  & \hspace{12pt} 
+  + \frac{1}{c\,(hc)^3}\big(1- f(\omegaNu,\epsilonNu)\big) \, 
+  \int_{\bbR^{+}} \int_{\bbS^{2}}  R^{\In}_{\NES} (\bl'\cdot\bl,\epsilonNu,\epsilonNu')\,f(\omega',\epsilonNu',t)\,d\epsilonNu' \epsilonNu'^{2}\,d\omega' \nonumber \\
+  & \hspace{12pt} 
+  - \frac{1}{c\,(hc)^3} f(\omegaNu,\epsilonNu,t) \int_{\bbR^{+}} 
+  \int_{\bbS^{2}}  R^{\Out}_{\NES} (\bl'\cdot\bl,\epsilonNu,\epsilonNu^{\prime})\,\big(1-f(\omegaNu',\epsilonNu',t )\big)\,d\epsilonNu' \epsilonNu'^{2}\,d\omegaNu',
+  \label{eq:homogeneousBoltzmann}
 \end{align}
-
-The third and fourth terms are contributions from (isotropic) elastic scattering of neutrino by nucleons and nuclei. The last two terms are contributions from neutrino-electron scattering.
-
-\subsection{The neutrino absorptivity}
-
-Given by \citet{bruenn_1985}, the absorption opacity of neutrino $\tilde{\chi}(\epsilonNu,\bU)$ 
-\begin{equation}
-\tilde{\chi}(\epsilonNu,\bU) = \chi(\epsilonNu,\bU) + \eta(\epsilonNu,\bU), 
-\end{equation}
-where $\eta(\epsilonNu,\bU) $ is the neutrino emissivity
-\begin{equation}
-\eta = \eta_{nucleon} + \eta_{nuclear},
-\end{equation}  
-and $ \chi(\epsilonNu,\bU)$ is the neutrino absorptivity, which is the inverse of neutrino absorption mean free path.
-They have the following relation:
-\begin{equation}
-\chi(\epsilonNu,\bU) = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T} \eta(\epsilonNu,\bU). 
-\end{equation}
-
+where we have brought back physical constants; i.e., the speed of light $c$ and the Planck constant $h$.  
+In the scattering kernels, $\bl(\omegaNu)=(\cos\vartheta,\sin\vartheta\cos\varphi,\sin\vartheta\sin\varphi)^{\mbox{\tiny T}}$, so that
+\begin{equation}
+ \bl'\cdot\bl  = \mu\mu' + [(1-\mu^2)(1-\mu'^{2})]^{1/2}\cos(\phiNu-\phiNu')
+ \equiv \cos\alpha,
+ \quad(\mu=\cos\thetaNu)
+\end{equation}
+is the cosine of the angle between incoming and outgoing neutrino is the scattering process.  
+In Eq.~\eqref{eq:homogeneousBoltzmann}, the first two terms are due to emission and absorption, the third and fourth terms are due to elastic (isoenergetic) neutrino scattering on nucleons and nuclei, and the last two terms are due to inelastic (non-isoenergetic) neutrino-electron scattering.
+In the following subsections we separately give the collision terms for the two-moment model by taking angular moments of Eq.~\eqref{eq:homogeneousBoltzmann}.  
+The total collision term in the two-moment model is then given by the sum of the separate terms.
+
+\subsection{Emission and Absorption}
+
+Electron capture on nucleons and nuclei ($p+e^{-}\rightleftharpoons n+\nu_{e}$) is governed by the corrected absorption opacity $\tilde{\chi}(\epsilonNu)$ 
+\begin{equation}
+  \tilde{\chi}(\epsilonNu) = \chi(\epsilonNu) + \eta(\epsilonNu), 
+\end{equation}
+where $\eta(\epsilonNu)$ is the emissivity (taken as the sum of contributions from nucleons and nuclei)
+\begin{equation}
+  \eta = \eta_{\mbox{\tiny nucleon}} + \eta_{\mbox{\tiny nuclei}},
+\end{equation}
+and $ \chi(\epsilonNu)$ is the absorption opacity.  
+They are related by equilibrium condition
+\begin{equation}
+  \chi(\epsilonNu) = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T}\,\eta(\epsilonNu). 
+\end{equation}
 Therefore,
 \begin{equation}
-\chi = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T} (\eta_{nucleon} + \eta_{nuclear} ) = \chi_{nucleon} + \chi_{nuclear}.
-\end{equation}
-
-The two terms of electron-neutrino absorption on nucleons $\chi_{nucleon}(\epsilonNu,\bU)$ and $\eta_{nucleon}(\epsilonNu,\bU)$ are given by Eq.
-(C13) and Eq.
-(C15) in \citet{bruenn_1985}  and the two terms of electron-neutrino absorption $\chi_{nuclear}(\epsilonNu,\bU)$ and $\eta_{nuclear}(\epsilonNu,\bU)$ on nuclear are given by Eq.
-(C29) and Eq.
-(C27) in \citet{bruenn_1985}.
-They all have units of $cm^{-1}$.
-
-\subsection{The isotropic elastic scattering kernel}
-The isotropic elastic scattering kernel $R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
+  \chi = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T}\,(\eta_{\mbox{\tiny nucleon}} + \eta_{\mbox{\tiny nuclei}}) 
+  \equiv \chi_{\mbox{\tiny nucleon}} + \chi_{\mbox{\tiny nuclei}},
+\end{equation}
+and
+\begin{equation}
+  \eta-\tilde{\chi}\,f=\tilde{\chi}\,\big(\,\eta/\tilde{\chi}-f\,\big)=\tilde{\chi}\,\big(\,f_{0}-f\,\big).  
+\end{equation}
+Thus, the corresponding moment equations are
+\begin{equation}
+  \f{1}{c}\deriv{\cJ}{t}=\tilde{\chi}\,\big(\,\cJ_{0}-\cJ\,\big)
+  \quad\text{and}\quad
+  \f{1}{c}\deriv{\bcH}{t}=-\tilde{\chi}\,\bcH.  
+\end{equation}
+We use the electron-neutrino nucleon absorption opacity $\chi_{\mbox{\tiny nucleon}}$ and emissivity $\eta_{\mbox{\tiny nucleon}}$ as given by Eq.~(C13) and Eq.~(C15), respectively, in \citet{bruenn_1985}, and the electron-neutrino nuclei absorption opacity $\chi_{\mbox{\tiny nuclei}}$ and emissivity $\eta_{\mbox{\tiny nuclei}}$ as given by Eq.~(C29) and Eq.~(C27), respectively, in \citet{bruenn_1985}.
+We only tabulate the corrected absorption opacity $\tilde{\chi}$, which has units cm$^{-1}$.
+
+\subsection{Elastic Scattering}
+
+The isoenergetic scattering kernel $R_{\IS}(\bl'\cdot\bl,\epsilonNu)$ is taken as the sum of contributions from scattering on nucleons and nuclei
+\begin{equation}
+  R_{\IS}(\bl'\cdot\bl,\epsilonNu,\epsilonNu) = R_{\IS}^{\mbox{\tiny nucleon}}(\bl'\cdot\bl,\epsilonNu) + R_{\IS}^{\mbox{\tiny nuclei}}(\bl'\cdot\bl,\epsilonNu),
+\end{equation}
+where $R_{\IS}^{\mbox{\tiny nucleon}}$ and $R_{\IS}^{\mbox{\tiny nuclei}}$ are given by Eq. (35) and Eq. (36), respectively, in \citet{mezzacappaBruenn_1993a}.  
+For inclusion in the two-moment model, these kernels are approximated by a two-term Legendre series
 \begin{align}
-R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) & = R_{\IS}^{nucleons}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) +  R_{\IS}^{nuclei}(\mu_0, \mu^\prime_0, \epsilonNu,\bU),
+  R_{\IS}(\cos\alpha,\epsilonNu) \approx \f{1}{2} \Phi_{\IS,0}(\epsilonNu) + \f{3}{2}\Phi_{\IS,1}(\epsilonNu)\,\cos\alpha.
 \end{align}
+By orthogonality of the Legendre polynomials ($P_{0}(x)=1,P_{1}(x)=x$), the expansion coefficients are given by
+\begin{equation}
+  \Phi_{\IS,\ell}(\epsilonNu)
+  =\int_{-1}^{+1}R_{\IS}(\cos\alpha,\epsilonNu)\,P_{\ell}(\cos\alpha)\,d\cos\alpha \quad (\ell=0,1).  
+\end{equation}
+Inserting the Legendre expansion into Eq.~\eqref{eq:homogeneousBoltzmann} and taking the angular moments gives no contribution to the equation for $\cJ$ (energy conservation), while the contribution to the equation for $\bcH$ is
+\begin{equation}
+  \f{1}{c}\deriv{\bcH}{t}
+  =-\big(\,\sigma_{\IS,0}-\sigma_{\IS,1}\big)\,\bcH,
+\end{equation}
+where we have defined
+\begin{equation}
+  \sigma_{\IS,\ell}(\epsilonNu)
+  =\f{2\pi\,\epsilonNu^{2}}{c\,(hc)^{3}}\,\Phi_{\IS,\ell}(\epsilonNu) \quad (\ell=0,1).  
+\end{equation}
+We tabulate the scattering opacities $\sigma_{\IS,0}$ and $\sigma_{\IS,1}$, which have units cm$^{-1}$, but use only $\sigma_{\IS,0}$ in the numerical experiments in Section~\ref{sec:numericalTableOpacities}, where $\sigma=\sigma_{\IS,0}$ in Equation~\eqref{eq:momentEquationMomentum}.
+
+\subsection{Neutrino-Electron Scattering}
+
+The NES scattering kernel $R_{\NES}^{\Out}(\cos\alpha,\epsilonNu,\epsilonNu')$ is given by Eq.~(9) in \citet{mezzacappaBruenn_1993c}.  
+As we did in the isoenergetic scattering case, we approximate the angular dependence of the scattering kernels by a two-term Legendre expansion; e.g.,
+\begin{equation}
+  R^{\Out}_{\NES}(\cos\alpha,\epsilonNu,\epsilonNu') 
+  \approx \f{1}{2} \Phi_{\NES,0}^{\Out}(\epsilonNu,\epsilonNu') + \f{3}{2}\Phi^{\Out}_{\NES,1}(\epsilonNu,\epsilonNu')\,\cos\alpha,
+\end{equation}
 where
+\begin{equation}
+  \Phi_{\NES,\ell}^{\Out}(\epsilonNu,\epsilonNu')
+  =\int_{-1}^{+1}R_{\NES}^{\Out}(\cos\alpha,\epsilonNu,\epsilonNu')\,P_{\ell}(\cos\alpha)\,d\cos\alpha \quad (\ell=0,1).  
+\end{equation}
+The in-scattering kernels $\Phi_{\NES,\ell}^{\In}(\epsilonNu,\epsilonNu')$ are obtained from symmetry properties \citep{cernohorsky_1994}
+\begin{equation}
+  \Phi_{\NES,\ell}^{\In}(\epsilonNu,\epsilonNu')=\Phi_{\NES,\ell}^{\Out}(\epsilonNu',\epsilonNu)
+  \quad\text{and}\quad
+  \Phi_{\NES,\ell}^{\Out}(\epsilonNu',\epsilonNu)
+  =e^{-(\epsilonNu-\epsilonNu')/k_{\mbox{\tiny B}}T}\,\Phi_{\NES,\ell}^{\Out}(\epsilonNu,\epsilonNu').
+  \label{eq:symmetryNES}
+\end{equation}
+Inserting the Legendre expansion into Eq.~\eqref{eq:homogeneousBoltzmann}, and taking the zeroth moment (number equation), gives
 \begin{align}
-\cos\theta = \mu_0\mu^\prime_0 + [(1-\mu_0^2)(1-\mu_0^{\prime 2})]^{1/2}\cos\theta,
+  \f{1}{c}\deriv{\cJ}{t}
+  &=\big(\,4\pi-\cJ(\epsilonNu)\,\big)\int_{\bbR^{+}}R_{\NES,0}^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')\,dV_{\epsilonNu'}
+  -\bcH(\epsilonNu)\cdot\int_{\bbR^{+}}R_{\NES,1}^{\In}(\epsilonNu,\epsilonNu')\,\bcH(\epsilonNu')\,dV_{\epsilonNu'} \nonumber \\
+  & \hspace{12pt}
+  -\cJ(\epsilonNu)\int_{\bbR^{+}}R_{\NES,0}^{\Out}(\epsilonNu,\epsilonNu')\,\big(\,4\pi-\cJ(\epsilonNu')\,\big)\,dV_{\epsilonNu'}
+  +\bcH(\epsilonNu)\cdot\int_{\bbR^{+}}R_{\NES,1}^{\Out}(\epsilonNu,\epsilonNu')\,\bcH(\epsilonNu')\,dV_{\epsilonNu'}.  
 \end{align}
-and
+Similarly, taking the first moment (number flux) of Eq.~\eqref{eq:homogeneousBoltzmann} results in
 \begin{align}
-R_{\IS}(\cos\theta, \epsilonNu, \bU) = R^{nucleons}(\cos\theta,\epsilonNu, \bU) + R^{nuclei}_{\IS}(\cos\theta, \epsilonNu, \bU)
+  \f{1}{c}\deriv{\bcH}{t}
+  &=-\bcH(\epsilonNu)\int_{\bbR^{+}}R_{\NES,0}^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')\,dV_{\epsilonNu'}
+  +\big(\,(4\pi/3)\,\bI-\bcK\,\big)\cdot\int_{\bbR^{+}}R_{\NES,1}^{\In}(\epsilonNu,\epsilonNu')\,\bcH(\epsilonNu')\,dV_{\epsilonNu'} \nonumber \\
+  & \hspace{12pt}
+  -\bcH\int_{\bbR^{+}}R_{\NES,0}^{\Out}(\epsilonNu,\epsilonNu')\,\big(\,4\pi-\cJ(\epsilonNu')\,\big)\,dV_{\epsilonNu'}
+  +\bcK\cdot\int_{\bbR^{+}}R_{\NES,1}^{\Out}(\epsilonNu,\epsilonNu')\,\bcH(\epsilonNu')\,dV_{\epsilonNu'},
 \end{align}
-where $R^{nucleons}_{\IS} (\cos\theta,\epsilonNu, \bU)$ and $R^{nuclei}_{\IS}(\cos\theta,\epsilonNu,\bU)$ are given by Eq. (35) and Eq. (36) in \citet{mezzacappaBruenn_1993a}.
-
-Expanding the isotropic elastic scattering kernel in the first two terms of a Legendre series yields
-\begin{align}
-R_{\IS}(\omega, \omega, \cos\theta) \approx \dfrac{1}{2} \Phi_{0,\IS}(\omega) + \dfrac{3}{2}\Phi_{1,\IS}(\omega)\cos\theta
-\end{align}
-
-\subsection{The neutrino-electron scattering kernel}
-The neutrino-electron scattering kernels are given by Eq.(9) and Eq.(28) in \citet{mezzacappaBruenn_1993c}.
-
-Therefore, $R^{\Out}_{\NES}(\epsilonNu,\epsilonNu^\prime, \omega)$ is known.
-
-Expand the scattering kernel in a Legendre series:
-\begin{align}
-R^{\Out}_{\NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU) = \sum_{l=0}^{\infty} \dfrac{2l+1}{2} R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) P_l(\omega),
-\end{align}
-where the Legendre coefficients $R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu^\prime)$ are given by
-\begin{align}
-R^{\Out}_{{\NES}, l}(\epsilonNu,\epsilonNu^\prime, \bU) = \int_{-1}^{1} d\omega P_l(\omega) R^{\Out}_{\NES}(\epsilonNu,\epsilonNu^\prime, \omega, \bU).
-\end{align}
-
-Expanding the neutrino-electron scattering kernels in the first two terms of Legendre series yields
-\begin{align}
-R^{\In/\Out}_{\NES}(\omega, \omega^{\prime}, \cos\theta, \bU) & = \sum_{l=0}^{1} \dfrac{ 2l+1}{2}\Phi^{\In/\Out}_{l,\NES}(\omega,\omega^{\prime},\bU)P_l(\cos\theta) \\
-& \approx \dfrac{1}{2}\Phi_{0,\NES}^{\In/\Out}(\omega,\omega^{\prime}, \bU) + \dfrac{3}{2}\Phi^{\In/\Out}_{1,\NES}(\omega,\omega^{\prime}, \bU)\cos\theta
-\end{align}
-
-The isotropic term $\dfrac{1}{2}\Phi_{0,\NES}^{\In/\Out}(\omega,\omega^{\prime}, \bU)$ is the $R^{\In}$ and $R^{\Out}$  in Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}.
+where we have defined
+\begin{equation}
+  R_{\NES,0}^{\In/\Out}
+  =\f{1}{c\,(hc)^{3}}\,\f{1}{2}\,\Phi_{\NES,0}^{\In/\Out}(\epsilonNu,\epsilonNu')
+  \quad\text{and}\quad
+  R_{\NES,1}^{\In/\Out}
+  =\f{1}{c\,(hc)^{3}}\,\f{3}{2}\,\Phi_{\NES,1}^{\In/\Out}(\epsilonNu,\epsilonNu').  
+\end{equation}
+We tabulate the scattering kernels $R_{\NES,0}^{\Out}$ and $R_{\NES,1}^{\Out}$, which have units MeV$^{-3}$ cm$^{-1}$, and obtain the in-scattering rates from the symmetry properties in Eq.~\eqref{eq:symmetryNES}.
+We only use $R_{\NES,0}^{\In/\Out}$ in the numerical experiments in Section~\ref{sec:numericalTableOpacities}, so that $R^{\In/\Out}=R_{\NES,0}^{\In/\Out}$ in Eqs~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}.
 
 \section{Basic Benchmark Problems}
+\label{sec:numericalBasic}
 
@@
 \section{Transport Problems with Tabulated Neutrino Opacities}
+\label{sec:numericalTableOpacities}
 
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics[scale=0.8]{./Figures/HomogeneousSphere_Opacities}
+  \end{center}
+  \caption{Absorption opacityies versus energy $\epsilonNu$ using values for $\rho$, $T$, and $Y_{e}$ listed in Table~\ref{tab:tabulatedModels}.}
+  \label{fig:absorptionOpacities_weaklib}
+\end{figure}
+
 \subsection{Homogeneous Sphere}
@@
     \begin{tabular}{cc}
-      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_Opacities} &
-      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_BaseSpectra} \\
-      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_B} &
-      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_D}
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphereTable_B_Density} &
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphereTable_B_EddingtonFactor} \\
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphereTable_B_FluxFactor} &
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphereTable_B_MeanEnergy}
     \end{tabular}
   \end{center}
-  \caption{Results from solving the multi-group Homogeneous sphere problem with the DG(1)+SIRK2 method using $100$ elements.
-    In the upper left panel we plot the absorption opacity versus energy $\epsilonNu$ using the values for $\rho$, $T$, and $Y_{e}$ listed in Table~\ref{tab:tabulatedModels}.
+  \caption{Results from solving the multi-group Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ spatial elements and $24$ energy groups, and using material properties from Model~D in Table~\ref{tab:tabulatedModels} to compute the neutrino absorption opacities.
+    We plot the energy-averaged neutrino density (upper left), flux factor (lower left), Eddington factor (upper right), and mean neutrino energy (lower right) versus radius.  
+    The analytical solution is represented by the solid lines, while the numerical solution is given by the dashed lines.}
+  \label{fig:homogeneousSphere1D_weaklib_B}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphereTable_D_Density} &
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphereTable_D_EddingtonFactor} \\
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphereTable_D_FluxFactor} &
+      \includegraphics[scale=0.4]{./Figures/HomogeneousSphereTable_D_MeanEnergy}
+    \end{tabular}
+  \end{center}
+  \caption{Same as in Figure~\ref{fig:homogeneousSphere1D_weaklib_B}, but using material properties from Model~D in Table~\ref{tab:tabulatedModels} to compute the neutrino absorption opacities.}
+  \label{fig:homogeneousSphere1D_weaklib_D}
+\end{figure}
+
+%\begin{figure}
+%  \begin{center}
+%    \begin{tabular}{cc}
+%      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_Opacities} &
+%      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_BaseSpectra} \\
+%      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_B} &
+%      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_D}
+%    \end{tabular}
+%  \end{center}
+%  \caption{Results from solving the multi-group Homogeneous sphere problem with the DG(1)+SIRK2 method using $100$ elements.
+%    In the upper left panel we plot the absorption opacity versus energy $\epsilonNu$ using the values for $\rho$, $T$, and $Y_{e}$ listed in Table~\ref{tab:tabulatedModels}.
 In the upper right panel, we plot the spectral number density versus energy at the end of the computations for a radius of $52.5$~km solid lines.
@@
 }
-  \label{fig:homogeneousSphere1D_weaklib}
-\end{figure}
+%  \label{fig:homogeneousSphere1D_weaklib}
+%\end{figure}
 

### 2017-07-22 Documents/M1/dgM1Curvilinear.tex
Minor updates.

@@
 In Eq.~\eqref{eq:homogeneousBoltzmann}, the first two terms are due to emission and absorption, the third and fourth terms are due to elastic (isoenergetic) neutrino scattering on nucleons and nuclei, and the last two terms are due to inelastic (non-isoenergetic) neutrino-electron scattering.
+
 In the following subsections we separately give the collision terms for the two-moment model by taking angular moments of Eq.~\eqref{eq:homogeneousBoltzmann}.  
-The total collision term in the two-moment model is then given by the sum of the separate terms.
+(The total collision term in the two-moment model is then given by the sum of the separate terms.)  
+The opacities are computed using the SFHo equation of state \citep{steiner_etal_2013}, and tabulated for densities $\rho\in[1.66\times10^{4},3.16\times10^{15}]$~g~cm$^{-3}$, temperatures $T\in[1.16\times10^{9},1.84\times10^{12}]$~K, and electron fractions $Y_{e}\in[0.01,0.6]$.
+The neutrino energies are in the range $\epsilonNu\in[0.1,300]$~MeV.  
+We use logarithmic grids to cover the range in density $N_{\rho}=308$, temperature ($N_{T}=129$), and the neutrino energy ($N_{\epsilonNu}=40$), and a linear grid to cover the range in electron fraction ($N_{Y_{e}}=60$).
+The neutrino electron scattering rates are tabulated in terms of neutrino energies ($\epsilonNu$ and $\epsilonNu'$), temperature, and $\eta=\mu_{\nu}/(k_{\mbox{\tiny B}}T)$.  
+Here we use a logarithmic grid in $\eta\in[1.0\times10^{-8},2.5\times10^{3}]$~MeV, using $N_{\eta}=100$ points.
 
@@
 \end{equation}
-Thus, the corresponding moment equations are
+Thus, the corresponding terms in the moment equations are
 \begin{equation}
@@
 \end{equation}
-We use the electron-neutrino nucleon absorption opacity $\chi_{\mbox{\tiny nucleon}}$ and emissivity $\eta_{\mbox{\tiny nucleon}}$ as given by Eq.~(C13) and Eq.~(C15), respectively, in \citet{bruenn_1985}, and the electron-neutrino nuclei absorption opacity $\chi_{\mbox{\tiny nuclei}}$ and emissivity $\eta_{\mbox{\tiny nuclei}}$ as given by Eq.~(C29) and Eq.~(C27), respectively, in \citet{bruenn_1985}.
+We use the electron neutrino nucleon absorption opacity $\chi_{\mbox{\tiny nucleon}}$ and emissivity $\eta_{\mbox{\tiny nucleon}}$ as given by Eq.~(C13) and Eq.~(C15), respectively, in \citet{bruenn_1985}, and the electron-neutrino nuclei absorption opacity $\chi_{\mbox{\tiny nuclei}}$ and emissivity $\eta_{\mbox{\tiny nuclei}}$ as given by Eq.~(C29) and Eq.~(C27), respectively, in \citet{bruenn_1985}.
 We only tabulate the corrected absorption opacity $\tilde{\chi}$, which has units cm$^{-1}$.
@@
 \end{equation}
+These integrals are performed numerically using a ??-point Gauss-Legendre quadrature rule.  (\ee{Ran: Fill in the number of quadrature points}.)
 Inserting the Legendre expansion into Eq.~\eqref{eq:homogeneousBoltzmann} and taking the angular moments gives no contribution to the equation for $\cJ$ (energy conservation), while the contribution to the equation for $\bcH$ is
@@
 \end{equation}
+(Again, these integrals are computed numerically using a ??-point Gauss-Legendre quadrature.  (\ee{Ran: Fill in the number of quadrature points}.))
 The in-scattering kernels $\Phi_{\NES,\ell}^{\In}(\epsilonNu,\epsilonNu')$ are obtained from symmetry properties \citep{cernohorsky_1994}

### 2017-07-25 Documents/M1/dgM1Curvilinear.tex
Minor updates.
Added figures and text for the line source problem.  Also some text on the discontinuity detector.

@@
 \end{equation}
-and the usual minmod function is given by
+and the usual $\text{minmod}$ function is given by
 \begin{equation}
@@
 
-\ee{Discuss discontinuity detection using Harten's sub-cell resolution method.}
+Unfortunately, the $\text{minmod}$ function in Eq.~\eqref{eq:minmod} can result in excessive dissipation around smooth extrema and destroy high-order accuracy.  
+The $\text{minmodB}$ in Eq.~\eqref{eq:minmodB} prevents this excessive dissipation, but introduces the parameter $M$, which we have found to be difficult to adjust in order to obtain uniformly acceptable results across all the numerical experiments presented later.
+To alleviate this dependence on the parameter $M$, we have implemented a discontinuity detector based on the subcell resolution idea of \citet{harten_1989}, following the description in \citet{qiuShu_2005}.
 
@@
 The scattering opacity $\sigma(\epsilonNu,\bU)$ is due to (isotropic) elastic scattering.   
-Neutrino-electron scattering gives rise to the integral operators involving the rates $R^{\In}(\epsilonNu,\epsilonNu',\bU)$ and $R^{\In}(\epsilonNu,\epsilonNu',\bU)$.  
+Neutrino-electron scattering gives rise to the integral operators involving the rates $R^{\In}(\epsilonNu,\epsilonNu',\bU)$ and $R^{\Out}(\epsilonNu,\epsilonNu',\bU)$.  
 (In the following, to simplify the notation, we will drop the explicit spatial dependence and dependence on material properties $\bU$.)  
@@
 \begin{equation}
-  R_{\NES,0}^{\In/\Out}
+  R_{\NES,0}^{\In/\Out}(\epsilonNu,\epsilonNu')
   =\f{1}{c\,(hc)^{3}}\,\f{1}{2}\,\Phi_{\NES,0}^{\In/\Out}(\epsilonNu,\epsilonNu')
   \quad\text{and}\quad
-  R_{\NES,1}^{\In/\Out}
+  R_{\NES,1}^{\In/\Out}(\epsilonNu,\epsilonNu')
   =\f{1}{c\,(hc)^{3}}\,\f{3}{2}\,\Phi_{\NES,1}^{\In/\Out}(\epsilonNu,\epsilonNu').  
@@
 \subsection{Line Source}
+
+The line source benchmark \citep[cf.][]{brunner_2002,garrettHauck_2013} is a challenging test for approximate transport algorithms.  
+In cylindrical coordinates, it consists of an initial delta function particle distribution in radius; i.e., $f_{0}=\delta(R)/4\,\pi$.  
+For $t>0$, a cylindrical radiation front propagates radially.  
+Apart from capturing details of the exact transport solution, maintaining realizability ($\bcM\in\cR$ cf. Eq.~\eqref{eq:realizableSet}) of the two-moment solution is challenging.
+
+This test is computed using cylindrical coordinates on a one-dimensional domain with $R\in[0,1.5]$.  
+To avoid initiating the radiation field with the delta function, we follow the procedure in \citet{garrettHauck_2013}, and approximate the initial condition with an isotropic Gaussian distribution function
+\begin{equation}
+  f_{\mbox{\tiny G},0}
+  =\max\Big[\,\f{1}{8\,\pi\,\sigma_{\mbox{\tiny G}}^{2}}\,e^{-R^{2}/(2\,\sigma_{\mbox{\tiny G}}^{2})},10^{-4}\,\Big],
+\end{equation}
+where we use $\sigma_{\mbox{\tiny G}}=0.03$.  
+We run this test to a final time $t=1.0$.
+
+In Figure~\ref{fig:lineSource} we plot the density $\cJ$ (left panel) and flux factor $h=|\cH_{1}|/\cJ$ (right panel) for various times during the evolution: $t=0.0$ (red), $t=0.35$ (green), $t=0.65$ (blue), and $t=1.0$ (black).
+The solid lines are for a high-resolution reference solution obtained with the DG(1)+RK2 scheme using 2048 elements, while the open circles are for a low resolution run using the DG(2)+RK3 scheme and 64 elements.
+There is good agreement between the two solutions.  
+When comparing the density $\cJ$ with the transport solutions in \citet{garrettHauck_2013}, we observe that the peak of the radiation front reaches the correct location, but otherwise, the two-moment model is not accurate for this problem.
+This is expected since a high number of angular moments is needed to capture the transport solution.  
+Despite the shortcomings of the two-moment approximation, our implementation maintains $\cJ\ge0$ and $h\in[0,1]$.
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[scale=0.4]{./Figures/LineSource1D_Density.png} &
+      \includegraphics[scale=0.4]{./Figures/LineSource1D_FluxFactor.png}
+    \end{tabular}
+  \end{center}
+  \caption{Results from the line source problem with the two-moment model for various times.
+In the left panel we plot the radiation density $\cJ$.
+In the right panel we plot the flux factor $h=|\cH_{1}|/\cJ$.
+Solid lines represent a high resolution (2048 elements) reference solution using the DG(1)+RK2 scheme, while circles are results obtained with the DG(2)+RK3 scheme using 64 elements.
+Both solutions maintain the bounds $\cJ>0$ and $h\in[0,1]$.}
+  \label{fig:lineSource}
+\end{figure}
 

### 2017-07-26 Documents/M1/dgM1Curvilinear.tex
Added discussion of full interaction solver.  Added HLL flux expression.

@@
 where $\alpha^{i}=||\mbox{eig}\big(\partial\bcF^{i}/\partial\bcM\big)||_{\infty}$ is the largest eigenvalue of the flux jacobian.  
-For classical neutrinos, which propagate at the speed of light, we take $\alpha^{i}=1$ (i.e., the global LF flux).  
-We have also implemented the Harten-Lax-van Leer (HLL) flux
+For classical neutrinos, which propagate at the speed of light, we can take $\alpha^{i}=1$ (i.e., the global LF flux).  
+We have also implemented the Harten-Lax-van Leer (HLL) flux \citep{harten_etal_1983}
 \begin{equation}
   \vect{f}^{\mbox{\tiny HLL},i}(\bcM^{-},\bcM^{+})
-  =
-\end{equation}
+  =\f{\alpha^{+,i}\,\bcF^{i}(\bcM^{-})+\alpha^{-,i}\,\bcF^{i}(\bcM^{+})-\alpha^{-,i}\alpha^{+,i}(\,\bcM^{+}-\bcM^{-}\,)}{\alpha^{-,i}+\alpha^{+,i}},
+\end{equation}
+where $\alpha^{-,i}$ and $\alpha^{+,i}$ are estimates for the largest (in absolute value) wave speed for left-moving and right-moving waves, respectively.
 
@@
 The neutrino energies are in the range $\epsilonNu\in[0.1,300]$~MeV.  
-We use logarithmic grids to cover the range in density $N_{\rho}=308$, temperature ($N_{T}=129$), and the neutrino energy ($N_{\epsilonNu}=40$), and a linear grid to cover the range in electron fraction ($N_{Y_{e}}=60$).
+We use logarithmic grids to cover the range in density $N_{\rho}=308$, temperature ($N_{T}=161$), and the neutrino energy ($N_{\epsilonNu}=40$), and a linear grid to cover the range in electron fraction ($N_{Y_{e}}=60$).
 The neutrino electron scattering rates are tabulated in terms of neutrino energies ($\epsilonNu$ and $\epsilonNu'$), temperature, and $\eta=\mu_{\nu}/(k_{\mbox{\tiny B}}T)$.  
@@
   \end{center}
-  \caption{Results of the Milne problem obtained with the two-moment model (solid lines), obtained with the DG(2)+SIRK2 scheme, compared with solutions provided by \citep{hummerRybicki_1971} (boxes).
+  \caption{Results of the Milne problem obtained with the two-moment model (solid lines), using the DG(2)+SIRK2 scheme, compared with solutions provided by \citep{hummerRybicki_1971} (boxes).
 See text for details.}
@@
 \end{equation}
+When elastic scattering is included, the above description remains unchanged, except for $\gamma_{j}^{n}\to\dt\big(\tilde{\chi}_{j}^{n}+\sigma_{j}^{n}\big)$ in Eq.~\eqref{eq:momentEquationMomentumEmAbDiscrete}.
 
@@
 \subsubsection{Full Interaction Set}
+
+With the complete interaction set considered in this paper (i.e., emission and absorption, elastic scattering, and NES), the electron fraction and fluid internal energy evolve according to
+\begin{align}
+  d_{t}Y_{e}
+  &=-\f{m_{\mbox{\tiny B}}}{\rho}\int_{\bbR^{+}}\tilde{\chi}\,\big(\cJ_{0}-\cJ\big)\,dV_{\epsilonNu}, \\
+  \rho\,d_{t}\epsilon
+  &=-\int_{\bbR^{+}}\tilde{\chi}\,\big(\cJ_{0}-\cJ\big)\,\epsilonNu\,dV_{\epsilonNu} \nonumber \\
+  &\hspace{12pt}
+  -\int_{\bbR^{+}}\int_{\bbR^{+}}\big(4\pi-\cJ(\epsilonNu)\big)R^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu} \nonumber \\
+  &\hspace{12pt}
+  +\int_{\bbR^{+}}\int_{\bbR^{+}}\cJ(\epsilonNu)\,R^{\Out}(\epsilonNu,\epsilonNu')\,\big(4\pi-\cJ(\epsilonNu)\big)\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu},
+\end{align}
+and the conserved quantities are the total lepton number
+\begin{equation}
+  d_{t}\big(\,\f{\rho}{m_{\mbox{\tiny B}}}Y_{e}+\int_{\bbR^{+}}\cJ\,dV_{\epsilonNu}\,\big)=0,
+  \label{eq:leptonConservationFull}
+\end{equation}
+and the total (fluid plus radiation) energy
+\begin{equation}
+  d_{t}\big(\,\rho\,\epsilon+\int_{\bbR^{+}}\cJ\,\epsilonNu\,dV_{\epsilonNu}\,\big)=0.  
+  \label{eq:energyConservationFull}
+\end{equation}
+
+In the solution to the coupled system, we use Eqs.~\eqref{eq:leptonConservationFull} and \eqref{eq:energyConservationFull} together with the equation for the neutrino number density to form a system of nonlinear equations for the solution vector $\bU=(\bcJ,Y_{e},\epsilon)^{\mbox{\tiny T}}$, i.e.,
+\begin{equation}
+  \bF(\bU^{n+1})=0,
+  \label{eq:nonlinearSystemFull}
+\end{equation}
+where, for $j=1,\ldots,M^{\epsilonNu}$,
+\begin{align}
+  F_{j}(\bU^{n+1})
+  &=\big(\cJ_{j}^{n+1}-\cJ_{j}^{n}\big)-\dt\,\tilde{\chi}_{j}^{n}\big(\,\cJ_{0,j}^{n+1}-\cJ_{j}^{n+1}\,\big) \nonumber \\
+  &\hspace{12pt}
+  -\dt\,\Big\{\,
+    \big(4\pi-\cJ_{j}^{n+1}\big)\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1}
+    -\cJ_{j}^{n+1}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)\,\Big\}.
+\end{align}
+The electron fraction is constrained by
+\begin{equation}
+  F_{M^{\epsilonNu}+1}(\bU^{n+1})
+  =Y_{e}^{n+1}-Y_{e}^{n}+\f{m_{\mbox{\tiny B}}}{\rho}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\big(\,\cJ_{k}^{n+1}-\cJ_{k}^{n}\,\big),
+\end{equation}
+while the internal energy is constrained by
+\begin{equation}
+  F_{M^{\epsilonNu}+2}(\bU^{n+1})
+  =\epsilon^{n+1}-\epsilon^{n}+\f{1}{\rho}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(3)}\big(\,\cJ_{k}^{n+1}-\cJ_{k}^{n}\,\big).  
+\end{equation}
+The system given by Eq.~\eqref{eq:nonlinearSystemFull} is solved using Newton's method, where $\bU^{n}$ is taken as an initial guess.  
+The dense Jacobian matrix is computed analytically, except for derivatives of the equilibrium density $\cJ_{0}$, which are computed numerically by taking derivatives of table interpolation functions.
+The radiation flux is subsequently obtained from
+\begin{equation}
+  \bcH_{j}^{n+1}-\bcH_{j}^{n}
+  =-\dt\,\big(\,\tilde{\chi}_{j}^{n}+\sigma_{j}^{n}+\sigma_{\NES,j}^{n}\,\big)\,\bcH_{j}^{n+1},
+\end{equation}
+where
+\begin{equation}
+  \sigma_{\NES,j}^{n}
+  =\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\big[\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1}+R_{jk}^{\Out,n}\big(4\pi-\cJ_{k}^{n+1}\big)\,\big].
+\end{equation}
 

### 2017-07-28 Documents/Euler/dgEulerCurvilinear.tex
updated entropy wave error chart

--- 2017-07-11 Documents/Euler/dgEulerCurvilinear.tex
@@
 
+\subsubsection{Entropy Waves (Accuracy Test)}
+
+\begin{table}
+  \begin{center}
+  \caption{$L^{\infty}$ error and convergence rates for the entropy wave problem.}
+  \label{tab:streamingSineWave}
+  \begin{tabular}{ccccccccc}
+    & \multicolumn{4}{c}{SSP-RK2} & \multicolumn{4}{c}{SSP-RK3} \\
+    \cmidrule(r){2-5} \cmidrule(r){6-9}
+    $N$ & DG(1) & Rate & DG(2) & Rate & DG(2) & Rate & DG(3) & Rate \\
+    \midrule \midrule
+    8     & $1.766\times10^{-1}$ & ---  & $2.371\times10^{-3}$ & ---  & $1.700\times10^{-3}$ & ---  & $4.958\times10^{-5}$  & --- \\
+    16   & $2.893\times10^{-2}$ &x.xx& $3.236\times10^{-4}$ &x.xx& $1.300\times10^{-4}$ &x.xx& $3.044\times10^{-6}$ &x.xx \\
+    32   & $4.203\times10^{-3}$ &x.xx& $6.800\times10^{-5}$ &x.xx& $1.580\times10^{-5}$ &x.xx& $1.983\times10^{-7}$ &x.xx \\
+    64   & $6.455\times10^{-4}$ &x.xx& $1.542\times10^{-5}$ &x.xx& $1.971\times10^{-6}$ &x.xx& $1.343\times10^{-8}$ &x.xx \\
+    128 & $1.101\times10^{-4}$ &x.xx& $3.659\times10^{-6}$ &x.xx& $2.464\times10^{-7}$ &x.xx& $9.737\times10^{-10}$ &x.xx \\
+    256 & $2.109\times10^{-5}$ &x.xx& $8.904\times10^{-7}$ &x.xx& $3.081\times10^{-8}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
+    \midrule \midrule
+  \end{tabular}
+  \end{center}
+\end{table}
+
+\subsubsection{Sound Waves}
+
 \subsection{Riemann Problems}
+
+\subsubsection{Shock Tube}
 

### 2017-12-06 Documents/Euler/dgEulerCurvilinearSupplement.tex
Various duscretization documents

\documentclass[10pt,preprint]{aastex}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{yhmath}
\usepackage{natbib}
\usepackage{../definitions}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

\usepackage{graphicx}
\newtheorem*{remark}{Remark}
\graphicspath{{Figures/}}

\begin{document}

\title{Nodal Discontinuous Galerkin Method for the Euler Equations of Fluid Dynamics}
\author{Eirik Endeve\altaffilmark{1}, et al.}
\altaffiltext{1}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}

%\begin{abstract}
%We present a nodal Discontinuous Galerkin (DG) method for the Euler equations with an eye towards astrophysical hydrodynamics.  
%We focus on issues related to core-collapse supernova dynamics, which include the use of curvilinear coordinates and a non-ideal (nuclear) equation of state.  
%\end{abstract}

\tableofcontents

\section{Discontinuous Galerkin Scheme}
\label{sec:dgMethod}

We consider the system of conservation laws with sources
\begin{equation}
  \pd{}{t}\big(\sqrt{\gamma}\,\bU\big)+\sum_{i=1}^{d}\pd{}{x^{i}}\big(\sqrt{\gamma}\,\bF^{i}(\bU)\big)=\sqrt{\gamma}\,\big(\bG(\bU)+\bQ(\bU,\bM)\big),
  \label{eq:conservationLaws}
\end{equation}
where we have split the source term into two contributions; $\bG$ is due to gravity and the use of curvilinear spatial coordinates, while $\bQ$ is due to coupling with an external field $\bM$ (e.g., radiation).

The semi-discrete DG scheme is given by (letting the test function be given by $\ell_{j}$)
\begin{align}
  &\pd{}{t}\int_{\bK}\sqrt{\gamma}\,\bU_{\DG}\,\ell_{j}\,d\bx
  +\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
  \big(\,
    \sqrt{\gamma}\,\widehat{\bF}^{i}\,\ell_{j}\big|_{x_{\Hgh}^{i}}
    -\sqrt{\gamma}\,\widehat{\bF}^{i}\,\ell_{j}\big|_{x_{\Low}^{i}}
  \,\big)\,d\tilde{\bx}^{i} \nonumber \\
  &\hspace{12pt}
  -\sum_{i=1}^{d}\int_{\bK}\sqrt{\gamma}\,\bF^{i}\,(\pd{\ell_{j}}{x^{i}})\,d\bx
  =\int_{\bK}\sqrt{\gamma}\,\big(\bG+\bQ\big)\,\ell_{j}\,d\bx,
  \label{eq:dgSemiDiscrete}
\end{align}
where $\widehat{\bF}^{i}$ are numerical fluxes; computed by solving Riemann problems on element interfaces.  
In each element, the DG solution is given by the polynomial expansion
\begin{equation}
  \bU_{\DG}(\bx,t)=\sum_{k=1}^{N}\bU_{k}(t)\,\ell_{k}(\bx), 
\end{equation}
where the basis $\big\{\ell_{k}\big\}_{k=1}^{N}$ is constructed from a tensor product of one-dimensional Lagrange polynomials based on a set of interpolation points $S=\{\bx_{k}\}_{k=1}^{N}$.  
We may use Gaussian points, but leave room for flexibility in the specification of these points.  
We use a polynomial representation of the metric functions as well; e.g.,
\begin{equation}
  \sqrt{\gamma}(\bx)=\sum_{k=1}^{N}\widehat{\sqrt{\gamma}}_{k}\,\hat{\ell}_{k}(\bx),
\end{equation}
where the basis $\big\{\hat{\ell}_{k}\big\}_{k=1}^{N}$ is also constructed from a tensor product of one-dimensional Lagrange polynomials, but is based on the Lobatto points $\hat{S}=\{\hat{\bx}_{k}\}_{k=1}^{N}$.  
(The use of Lobatto points will ensure continuity of the metric functions across element interfaces.)  
We assume that the metric functions are time-independent.  
Then, once the metric functions are computed analytically in the Lobatto points $\hat{\bx}_{k}\in\hat{S}$, they can be interpolated to the points $\bx_{i}\in S$; e.g.,
\begin{equation}
  \sqrt{\gamma}_{i}=\sqrt{\gamma}(\bx_{i})
  =\sum_{k=1}^{N}\hat{\ell}_{k}(\bx_{i})\,\widehat{\sqrt{\gamma}}_{k}.  
  \label{eq:l2g}
\end{equation}
An example of the interpolation matrix (using Gaussian points in $S$), $L_{ik}^{\mbox{\tiny L2G}}=\hat{\ell}_{k}(\bx_{i})\in\bbR^{N\times N}$, is shown in Figure~\ref{fig:LL2G}.

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{L_L2G.png}
  \end{center}
  \caption{}
  \label{fig:LL2G}
\end{figure}

We proceed by using the polynomial representation
\begin{equation}
  \sqrt{\gamma}(\bx)=\sum_{i=1}^{N}\sqrt{\gamma}_{i}\,\ell_{i}(\bx)
\end{equation}
for the metric functions as well, where the basis functions are constructed from points in $S$, and $\sqrt{\gamma}_{i}$ given by Eq.~\eqref{eq:l2g}.  
Note that these representations are equivalent, and
\begin{equation}
  \sqrt{\gamma}(\hat{\bx}_{q})=\sum_{i=1}^{N}\sqrt{\gamma}_{i}\,\ell_{i}(\hat{\bx}_{q})
  =\sum_{k=1}^{N}\Big(\sum_{i=1}^{N}\hat{\ell}_{k}(\bx_{i})\ell_{i}(\hat{\bx}_{q})\Big)\,\widehat{\sqrt{\gamma}}_{k}
  =\widehat{\sqrt{\gamma}}_{q}.  
\end{equation}

Inserting the polynomial representations, we can write the time-derivative term in Eq.~\eqref{eq:dgSemiDiscrete} as
\begin{equation}
  \pd{}{t}\int_{\bK}\sqrt{\gamma}\,\bU_{\DG}\,\ell_{j}\,d\bx
  =\sum_{k=1}^{N}M_{jk}^{(0)}\,\deriv{\bU_{k}}{t},
\end{equation}
where the volume mass matrix is given by
\begin{equation}
  M_{jk}^{(0)}=\sum_{m=1}^{N}\int_{\bK}\ell_{m}(\bx)\,\ell_{j}(\bx)\,\ell_{k}(\bx)\,d\bx\,\sqrt{\gamma}_{m}.  
\end{equation}
For the flux terms, we define a polynomial representation on the surface $\tilde{\bK}^{i}$
\begin{equation}
  [\sqrt{\gamma}\widehat{\bF}^{i}](x^{i},\tilde{\bx}^{i})
  =\sum_{k=1}^{\tilde{N}^{i}}[\sqrt{\gamma}\widehat{\bF}^{i}]_{k}(x^{i})\,\tilde{\ell}_{k}(\tilde{\bx}^{i}),
\end{equation}
where the basis functions are based on a set of interpolation points $\tilde{S}^{i}=\{\tilde{\bx}_{k}^{i}\}_{k=1}^{\tilde{N}^{i}}$ on the element surface $\tilde{\bK}^{i}$.  
Then, the surface integrals are evaluated as
\begin{equation}
  \int_{\tilde{\bK}^{i}}\sqrt{\gamma}\,\widehat{\bF}^{i}\,\ell_{j}\big|_{x^{i}}\,d\tilde{\bx}^{i}
  =\sum_{k=1}^{\tilde{N}^{i}}\widetilde{M}_{jk}^{i}(x^{i})\,[\sqrt{\gamma}\widehat{\bF}^{i}]_{k}(x^{i}),
\end{equation}
where the surface mass matrices $\widetilde{M}_{jk}^{i}\in\bbR^{N\times\tilde{N}^{i}}$ are given by
\begin{equation}
  \widetilde{M}_{jk}^{i}(x^{i})
  =\int_{\tilde{\bK}^{i}}\ell_{j}(x^{i},\tilde{\bx}^{i})\,\tilde{\ell}_{k}(\tilde{\bx}^{i})\,d\tilde{\bx}^{i}, 
\end{equation}
and plotted in Figure~\ref{fig:SurfMassMats}.

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=1.0\textwidth]{IntegrationMatrices.png}
  \end{center}
  \caption{}
  \label{fig:SurfMassMats}
\end{figure}

In order to compute numerical fluxes, the evolved quantities and metric functions are interpolated to the relevant surface.  
For example, to interpolate to $x_{\Low}^{i,+}=\lim_{\delta\to0}x_{\Low}^{i}+\delta$ ($\delta>0$) we evaluate
\begin{equation}
  \bU_{k}(x_{\Low}^{i,+})
  =\bU_{\DG}(x_{\Low}^{i,+},\tilde{\bx}_{k}^{i})
  =\sum_{l=1}^{N}L_{kl}^{i}(x_{\Low}^{i})\,\bU_{l},
\end{equation}
where we have defined the interpolation matrix $L_{kl}^{i}(x_{\Low}^{i})=\ell_{l}(x_{\Low}^{i},\tilde{\bx}_{k}^{i})\in\bbR^{\tilde{N}^{i}\times N}$.  
Interpolation matrices are shown in Figure~\ref{fig:IntMatsDims}.  
The metric functions are interpolated similarly.

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=1.0\textwidth]{InterpolationMatricesDims.png}
  \end{center}
  \caption{}
  \label{fig:IntMatsDims}
\end{figure}

For the volume term and source terms due to gravity and curvilinear coordinates we use the expansions
\begin{equation}
  \sqrt{\gamma}\bF^{i}=\sum_{k=1}^{N}[\sqrt{\gamma}\,\bF^{i}]_{k}\,\ell_{k}(\bx)
  \quad\text{and}\quad
  \sqrt{\gamma}\bG=\sum_{k=1}^{N}[\sqrt{\gamma}\,\bG]_{k}\,\ell_{k}(\bx)
\end{equation}
where the basis functions are based on the points $S$.  
Then, 
\begin{equation}
  \int_{\bK}\sqrt{\gamma}\,\bF^{i}\,(\pd{\ell_{j}}{x^{i}})\,d\bx
  =\sum_{k=1}^{N}S_{jk}^{i}\,[\sqrt{\gamma}\,\bF^{i}]_{k}
  \quad\text{and}\quad
  \int_{\bK}\sqrt{\gamma}\,\bG\,\ell_{j}\,d\bx
  =\sum_{k=1}^{N}M_{jk}\,[\sqrt{\gamma}\,\bG]_{k},
\end{equation}
where
\begin{equation}
  S_{jk}^{i}=\int_{\bK}\pderiv{\ell_{j}}{x^{i}}(\bx)\,\ell_{k}(\bx)\,d\bx
  \quad\text{and}\quad
  M_{jk}
  =\int_{\bK}\ell_{j}(\bx)\,\ell_{k}(\bx)\,d\bx.
\end{equation}
These matrices are displayed on Figure~\ref{fig:MassStiffMats}.  
Note again the sparsity patterns.

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=1.0\textwidth]{MassAndStiffnessMatrices.png}
  \end{center}
  \caption{}
  \label{fig:MassStiffMats}
\end{figure}

For the source terms due to coupling with the external field, we write
\begin{equation}
  \bQ=\sum_{k=1}^{N}\bQ_{k}\,\ell_{k}(\bx),
\end{equation}
where the basis is constructed from the points in $S$.  
Then
\begin{equation}
  \int_{\bK}\sqrt{\gamma}\,\bQ\,\ell_{j}(\bx)\,d\bx
  =\sum_{k=1}^{N}M_{jk}^{(0)}\,\bQ_{k}.  
\end{equation}

We can then write the DG scheme in the compact form
\begin{equation}
  M^{(0)}\deriv{\bU}{t}
  =-\sum_{i=1}^{d}
  \Big(\,
    \widetilde{M}^{i}(x_{\Hgh}^{i,-})\,[\sqrt{\gamma}\widehat{\bF}^{i}](x_{\Hgh}^{i})
    -\widetilde{M}^{i}(x_{\Low}^{i,+})\,[\sqrt{\gamma}\widehat{\bF}^{i}](x_{\Low}^{i})
    -S^{i}\,[\sqrt{\gamma}\bF^{i}]    
  \,\Big)
  +M\,[\sqrt{\gamma}\,\bG]
  +M^{(0)}\bQ,
  \label{eq:dgCompact}
\end{equation}
where $M^{(0)},M,S^{i}\in\bbR^{N\times N}$ and $\widetilde{M}^{i}\in\bbR^{N\times\tilde{N}^{i}}$.  
In Eq~\eqref{eq:dgCompact}, $\bU=(\bU_{1},\ldots,\bU_{N})^{\mbox{\tiny T}}$, $[\sqrt{\gamma}\bF^{i}]=([\sqrt{\gamma}\bF^{i}]_{1},\ldots,[\sqrt{\gamma}\bF^{i}]_{N})^{\mbox{\tiny T}}$, $[\sqrt{\gamma}\bG]=([\sqrt{\gamma}\bG]_{1},\ldots,[\sqrt{\gamma}\bG]_{N})^{\mbox{\tiny T}}$, $\bQ=(\bQ_{1},\ldots,\bQ_{N})^{\mbox{\tiny T}}$, and $[\sqrt{\gamma}\widehat{\bF}]^{i}=([\sqrt{\gamma}\widehat{\bF}^{i}]_{1},\ldots,[\sqrt{\gamma}\widehat{\bF}^{i}]_{\tilde{N}^{i}})^{\mbox{\tiny T}}$; i.e., point values within $\bK$ or on the element faces $\tilde{\bK}^{i}$ --- not to be confused with the continuous fields in Eq.~\eqref{eq:conservationLaws}.

In multi-dimensional problems, the evaluation of $d_{t}\bU$ in Eq.~\eqref{eq:dgCompact} can become costly for several reasons.  
Assume $d=3$, and that the basis functions are constructed from polynomials of degree $p=3$.  
Then, $N=(p+1)^{d}=64$.  
If we use the same polynomial degree to construct the numerical flux on the element interfaces we have $\tilde{N}^{i}=(p+1)^{d-1}=16$.  
The matrices involve the metric function $\sqrt{\gamma}$, which depends on spatial coordinate $\bx$.  
We can precompute matrices of the form
\begin{equation}
  \int_{\bK}\ell_{m}(\bx)\,\ell_{j}(\bx)\,\ell_{k}(\bx)\,d\bx,
\end{equation}
which contains $1024$ entries, and contract with $\sqrt{\gamma}_{m}$ in each element to avoid storing matrices for each element.  
The contraction operation involves $N^{3}$ operations.  
Additional (similar) cost is incurred by inverting the mass matrix.  
We achieve significant computational savings from lumping the mass matrix; i.e., when computing the mass matrix, we use a quadrature where the quadrature points coincide with the interpolation points $S$.  
Then, the mass matrix takes the following simple (diagonal) form
\begin{equation}
  M_{jk}^{(0)}
  \approx\sum_{m=1}^{N}\sum_{q=1}^{N}w_{q}\,\ell_{m}(\bx_{q})\,\ell_{j}(\bx_{q})\,\ell_{k}(\bx_{q})\,\sqrt{\gamma}_{m}
  =\delta_{jk}\,w_{k}\,\sqrt{\gamma}_{k},
\end{equation}
where $\sqrt{\gamma}_{k}=\sum_{m=1}^{N}\widehat{\sqrt{\gamma}}_{m}\,\hat{\ell}_{m}(\bx_{k})$.  
In our example with $p=3$ we are using $4$ points to integrate a polynomial of degree $3\times p=9$, while a $4$-point Gaussian quadrature only integrates polynomials of degree $\le 2\times N-1=7$ exactly.

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{cc}
     \includegraphics[width=0.5\textwidth]{MassMatrix0_G4.png}
     \includegraphics[width=0.5\textwidth]{MassMatrix0_G5.png}
    \end{tabular}
  \end{center}
  \caption{}
  \label{fig:MassMats}
\end{figure}

\section{Cell Averages and Conservation}

The DG method evolves a high-order approximation the solution $\bU$.  
Each element contains $N$ degrees of freedom $\{\bU_{i}\}_{i=1}^{N}$.  
Let the cell-average in element $\bK$ be given by
\begin{equation}
  \bU_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\bU_{\DG}\,\sqrt{\gamma}\,d\bx,
  \quad\text{where}\quad
  V_{\bK}=\int_{\bK}\sqrt{\gamma}\,d\bx.  
\end{equation}
The cell volume is computed as
\begin{equation}
  V_{\bK}=\sum_{k=1}^{N}w_{k}\sqrt{\gamma}_{k},
  \quad\text{where}\quad
  w_{k}=\int_{\bK}\ell_{k}(\bx)\,d\bx, 
\end{equation}
while the cell average becomes
\begin{equation}
  \bU_{\bK}=\f{1}{V_{\bK}}\sum_{j=1}^{N}\sum_{k=1}^{N}M_{jk}\,\sqrt{\gamma}_{j}\,\bU_{k}.  
\end{equation}
Note that $M_{jk}$ is diagonal (cf. Figure~\ref{fig:MassStiffMats}), which simplifies the computation of $\bU_{\bK}$.

Define the vector of ones $\be^{\mbox{\tiny T}}=(1,\ldots,1)$.  
Then we see that
\begin{equation}
  \be^{\mbox{\tiny T}}\,M^{(0)}\deriv{\bU}{t}=V_{\bK}\deriv{\bU_{\bK}}{t},
\end{equation}
since $\sum_{j=1}^{N}\ell_{j}(\bx)=1$.  
The evolution equation for the cell average is then given by
\begin{equation}
  \deriv{\bU_{\bK}}{t}
  =-\f{1}{V_{\bK}}\Big[\sum_{i=1}^{d}
  \Big(\,
    (\tilde{w}^{i})^{\mbox{\tiny T}}[\sqrt{\gamma}\widehat{\bF}^{i}](x^{i}_{\Hgh})
    -(\tilde{w}^{i})^{\mbox{\tiny T}}[\sqrt{\gamma}\widehat{\bF}^{i}](x^{i}_{\Low})
  \,\Big)-w^{\mbox{\tiny T}}[\sqrt{\gamma}\bG]\Big]+\bQ_{\bK},
  \label{eq:dgCellAverage}
\end{equation}
where we have defined the surface integral weights
\begin{equation}
  \tilde{w}_{k}^{i}=\int_{\tilde{\bK}^{i}}\tilde{\ell}_{k}(\tilde{\bx}^{i})\,d\tilde{\bx}^{i}.  
\end{equation}
Equation~\eqref{eq:dgCellAverage} is familiar from the literature on finite volume methods for hyperbolic conservation laws.  
In the absence of sources, it expresses exact conservation of the cell average quantities $\bU_{\bK}$.

\section{Source Terms from Geometry Fields}

The source terms from geometry fields (i.e., gravity and curvilinear coordinates) involve spatial derivatives.  
One could use the polynomial expansions of these fields and simply take derivatives.  
This approach reduces the order of accuracy in the representation of these fields, and leads to vanishing source terms in the case with polynomial degree $p=0$.  
To avoid this, we define expansions of derivatives of the geometry fields.  
To this end, let $f$ represent a geometry field (e.g., $f=\sqrt{\gamma}$) and define $g^{i}=\pderiv{f}{x^{i}}$.  
Then
\begin{equation}
  g_{i}(\bx)=\sum_{k=1}^{N}(g_{i})_{k}\,\ell_{k}(\bx),
\end{equation}
where the basis is constructed from points $\bx_{k}\in S$, and
\begin{align}
  (g_{i})_{j}
  &=M_{jj}^{-1}\int_{\bK}g_{i}\,\ell_{j}\,d\bx \nonumber \\
  &=M_{jj}^{-1}
  \Big\{\,
    \int_{\tilde{\bK}^{i}}\big[\,\hat{f}\,\ell_{j}\big|_{x_{\Hgh}^{i}}-\hat{f}\,\ell_{j}\big|_{x_{\Low}^{i}}\,\big]\,d\tilde{\bx}^{i}
    -\int_{\bK}f\,\pderiv{\ell_{j}}{x^{i}}\,d\bx
  \,\Big\}.  
\end{align}
(Note that $M_{jk}=M_{jj}\delta_{jk}$.)
By construction, the geometry fields are continuous across element interfaces.  
(In the $p=0$ case, the geometry fields on the faces are computed by averaging values from elements abutting the face.)  
Introducing the expansions
\begin{equation}
  \hat{f}(x^{i},\tilde{\bx}^{i})=\sum_{k=1}^{\tilde{N}^{i}}\hat{f}_{k}(x^{i})\,\tilde{\ell}_{k}(\tilde{\bx}^{i})
  \quad\text{and}\quad
  f(\bx)=\sum_{k=1}^{N}f_{k}\,\ell_{k}(\bx)
\end{equation}
on the faces and the interior of $\bK$, we have
\begin{equation}
  (g_{i})_{j}=M_{jj}^{-1}
  \Big\{\,
    \sum_{k=1}^{\tilde{N}^{i}}
    \Big(
      \widetilde{M}_{jk}^{i}(x_{\Hgh}^{i,-})\,\hat{f}_{k}(x_{\Hgh}^{i})
      -\widetilde{M}_{jk}^{i}(x_{\Low}^{i,+})\,\hat{f}_{k}(x_{\Low}^{i})
    \Big)
    -\sum_{k=1}^{N}S_{jk}^{i}\,f_{k}
  \,\Big\}.  
  \label{eq:geometryDerivative}
\end{equation}
Writing this in matrix form, letting $g_{i}=\big((g_{i})_{1},\ldots,(g_{i})_{N}\big)^{\mbox{\tiny T}}$, $f=\big(f_{1},\ldots,f_{N}\big)^{\mbox{\tiny T}}$, and $\hat{f}=\big(\hat{f}_{1},\ldots,\hat{f}_{\tilde{N}^{i}}\big)^{\mbox{\tiny T}}$, we have
\begin{equation}
  g_{i}=M^{-1}\Big\{\widetilde{M}^{i}(x_{\Hgh}^{i,-})\,\hat{f}(x_{\Hgh}^{i})-\widetilde{M}^{i}(x_{\Low}^{i,+})\,\hat{f}(x_{\Low}^{i})-S^{i}f\Big\}.  
\end{equation}

For a continuous field approximated by $f(\bx)=\sum_{i=1}^{N}f_{k}\,\ell_{k}(\bx)$, these representations are equivalent in the sense that
\begin{equation}
  M_{jj}^{-1}\int_{\bK}\big(g_{i}-\pderiv{f}{x^{i}}\big)\,\ell_{j}=0.  
\end{equation}
We approximate metric factors $\sqrt{\gamma}$, $\sqrt{\gamma_{11}}$, $\sqrt{\gamma_{22}}$, and $\sqrt{\gamma_{33}}$, and the gravitational potential $\Phi$ with polynomial representations that are continuous across element interfaces, as discussed for $\sqrt{\gamma}$ in Section~\ref{sec:dgMethod}.

\section{Source Terms from Curvilinear Coordinates}

In the absence of gravity ($\Phi=0$), the geometry sources are purely due to curvilinear coordinates and contribute only to the right-hand side of the momentum equation.  
We consider the case where $\gamma_{ij}$ is diagonal, and write
\begin{equation}
  \f{1}{2}\,P^{ik}\pderiv{\gamma_{ik}}{x^{j}}
  =\sum_{i=1}^{d}P_{~i}^{i}\f{1}{\sqrt{\gamma_{ii}}}\pderiv{\sqrt{\gamma_{ii}}}{x^{j}}.
\end{equation}

Next we investigate the balance between the curvilinear sources and the geometry terms in the spatial divergence of the momentum equation.  
For a fluid associated with an isotropic and spatially homogeneous stress tensor, i.e., $P_{~k}^{i}=P\,\delta_{~k}^{i}$, the balance should be exact so as to not induce artificial flows.  
The cell average of the $j$-th component of the momentum equation is denoted $(S_{j})_{\bK}$.  
Under the stated conditions, the evolution equation is given by
\begin{equation}
  \deriv{(S_{j})_{\bK}}{t}
  =-\f{1}{V_{\bK}}
  \Big[\,
  \Big(\,
    (\tilde{w}^{j})^{\mbox{\tiny T}}[\sqrt{\gamma}](x^{j}_{\Hgh})
    -(\tilde{w}^{j})^{\mbox{\tiny T}}[\sqrt{\gamma}](x^{j}_{\Low})
  \,\Big)
  -\sum_{i=1}^{d}w^{\mbox{\tiny T}}
  \big[\f{\sqrt{\gamma}}{\sqrt{\gamma_{ii}}}\pderiv{\sqrt{\gamma_{ii}}}{x^{j}}\big]
  \,\Big],
  \label{eq:MomentumUniformP}
\end{equation}
where, without loss of generality, we have set $P=1$.  
In Cartesian coordinates, the balance is trivial.  
Next, we consider the balance for the case of spherical polar and cylindrical coordinates.

\subsection{Spherical Polar Coordinates}

In spherical polar coordinates, we have $\sqrt{\gamma_{11}}=1$, $\sqrt{\gamma_{22}}=r$, $\sqrt{\gamma_{33}}=r\sin\theta$, and $\sqrt{\gamma}=r^{2}\sin\theta$.

For $j=1$ (the radial component of the momentum equation), we have
\begin{equation}
  \sum_{i=1}^{d}w^{\mbox{\tiny T}}
  \big[\f{\sqrt{\gamma}}{\sqrt{\gamma_{ii}}}\pderiv{\sqrt{\gamma_{ii}}}{x^{j}}\big]
  =w^{\mbox{\tiny T}}\big[2\,r\,\sin\theta\big]
  =(\tilde{w}^{1})^{\mbox{\tiny T}}[r_{\Hgh}^{2}\sin\theta]-(\tilde{w}^{1})^{\mbox{\tiny T}}[r_{\Low}^{2}\sin\theta]
  =(\tilde{w}^{1})^{\mbox{\tiny T}}[\sqrt{\gamma}](r_{\Hgh})-(\tilde{w}^{1})^{\mbox{\tiny T}}[\sqrt{\gamma}](r_{\Low}).  
\end{equation}
Hence the balance is exact for a quadrature that integrates polynomials of degree $1$ in the radial direction.

For $j=2$ (the latitudinal component of the momentum equation), we have
\begin{equation}
  \sum_{i=1}^{d}w^{\mbox{\tiny T}}
  \big[\f{\sqrt{\gamma}}{\sqrt{\gamma_{ii}}}\pderiv{\sqrt{\gamma_{ii}}}{x^{j}}\big]
  =w^{\mbox{\tiny T}}\big[\sqrt{\gamma_{22}}\,\pderiv{\sqrt{\gamma_{33}}}{x^{2}}\big].  
\end{equation}
Since $\sqrt{\gamma_{22}}$ and $\sqrt{\gamma_{33}}$ are approximated by polynomials of degree $1$ in the radial direction and $\sqrt{\gamma_{33}}$ is approximated by a degree $p$ polynomial in the latitudinal direction, the balance is exact if the quadrature exactly integrates polynomials of degree $2$ in the radial direction and degree $p-1$ in the latitudinal direction (e.g., the Gaussian quadrature with $N=2$).  
By using the approximation in Eq.~\eqref{eq:geometryDerivative}, we also achieve exact balance in the case with $p=0$ polynomials.

The balance is trivial for $j=3$ (the azimuthal component of the momentum equation).

\subsection{Cylindrical Coordinates}

In spherical polar coordinates, we have $\sqrt{\gamma_{11}}=1$, $\sqrt{\gamma_{22}}=1$, $\sqrt{\gamma_{33}}=R$, and $\sqrt{\gamma}=R$.

\section{Source Terms from Gravitational Fields}

For the source terms due to gravitational fields, we investigate conservation of energy.

\subsection{Time-Independent Gravitational Fields}

Multiplying the mass conservation equation with a time-independent gravitational field $\Phi=\Phi(\bx)$, we obtain
\begin{equation}
  \pd{}{t}\big(\sqrt{\gamma}\,\rho\,\Phi\big)
  +\sum_{i=1}^{d}\pd{}{i}\big(\sqrt{\gamma}\,(\rho\,\Phi\,v^{i})\big)
  =\sqrt{\gamma}\sum_{i=1}^{d}\rho\,v^{i}\,\pd{\Phi}{i}.
\end{equation}
Adding this equation to the fluid energy equation 
\begin{equation}
  \pd{}{t}\big(\sqrt{\gamma}\,E\big)
  +\sum_{i=1}^{d}\pd{}{i}\big(\sqrt{\gamma}\,(E+p)\,v^{i}\big)
  =-\sqrt{\gamma}\sum_{i=1}^{d}\rho\,v^{i}\,\pd{\Phi}{i},
\end{equation}
where we ignore the sources $\bQ$ due to energy exchange with the external field $\bM$, gives the conservation law
\begin{equation}
  \pd{}{t}\big(\sqrt{\gamma}\,(E+\rho\,\Phi)\big)
  +\sum_{i=1}^{d}\big(\sqrt{\gamma}\,(E+p+\rho\,\Phi)\,v^{i}\big)
  =0.  
\end{equation}

In the semi-discrete DG representation, the approximation to the mass density $\rho_{\DG}$ satisfies
\begin{equation}
  \pd{}{t}\int_{\bK}\sqrt{\gamma}\,\rho_{\DG}\,\ell_{j}\,d\bx
  +\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
  \Big(
    \sqrt{\gamma}\,\widehat{\rho v^{i}}\,\ell_{j}\big|_{x_{\Hgh}^{i}}
    -\sqrt{\gamma}\,\widehat{\rho v^{i}}\,\ell_{j}\big|_{x_{\Low}^{i}}
  \Big)
  =\sum_{i=1}^{d}\int_{\bK}\sqrt{\gamma}\,(\rho\,v^{i})\,\pd{\ell_{j}}{i}.  
\end{equation}
Contracting this with $\Phi_{j}$, noting that $\Phi(\bx)=\sum_{j=1}^{N}\Phi_{j}\,\ell_{j}(\bx)$, gives
\begin{equation}
  \pd{}{t}\big(\rho\Phi\big)_{\bK}
  +\f{1}{V_{\bK}}\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
  \Big(
    \sqrt{\gamma}\,\widehat{F}_{g}^{i}\big|_{x_{\Hgh}^{i}}
    -\sqrt{\gamma}\,\widehat{F}_{g}^{i}\big|_{x_{\Low}^{i}}
  \Big)
  =\f{1}{V_{\bK}}\sum_{i=1}^{d}\int_{\bK}\sqrt{\gamma}\,(\rho\,v^{i})\,\pd{\Phi}{i},
\end{equation}
where the cell-averaged gravitational energy density is
\begin{equation}
  \big(\rho\Phi\big)_{\bK}
  =\f{1}{V_{\bK}}\int_{\bK}\rho_{\DG}\,\Phi\,\sqrt{\gamma}\,d\bx,
\end{equation}
and $\widehat{F}_{g}^{i}=\widehat{\rho \Phi v^{i}}=\widehat{\rho v^{i}}\,\Phi$.

\begin{remark}
  The requirement that $\Phi$ is continuous across element interfaces is needed for conservation.
\end{remark}

The cell-averaged energy density satisfies
\begin{equation}
  \pd{E_{\bK}}{t}
  +\f{1}{V_{\bK}}\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
  \Big(
    \sqrt{\gamma}\,\widehat{F}_{E}^{i}\big|_{x_{\Hgh}^{i}}
    -\sqrt{\gamma}\,\widehat{F}_{E}^{i}\big|_{x_{\Low}^{i}}
  \Big)
  =-\f{1}{V_{\bK}}\sum_{i=1}^{d}\int_{\bK}\sqrt{\gamma}\,(\rho\,v^{i})\,\pd{\Phi}{i}.  
\end{equation}
Thus, adding the equation for the cell-averaged gravitational energy density and the equation for the total fluid energy density results in an exact conservation law for the total (gravitational plus fluid) energy.  
(Complications may arise when limiters are invoked.)

\bibliographystyle{apj}
\bibliography{../References/references.bib}

\end{document}

### 2017-12-06 Documents/Euler/dgEulerGR.tex
Various duscretization documents

--- 2017-12-06 Documents/Euler/dgEulerCurvilinearSupplement.tex
@@
 
-\title{Nodal Discontinuous Galerkin Method for the Euler Equations of Fluid Dynamics}
-\author{Eirik Endeve\altaffilmark{1}, et al.}
-\altaffiltext{1}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
-
-%\begin{abstract}
-%We present a nodal Discontinuous Galerkin (DG) method for the Euler equations with an eye towards astrophysical hydrodynamics.  
-%We focus on issues related to core-collapse supernova dynamics, which include the use of curvilinear coordinates and a non-ideal (nuclear) equation of state.  
-%\end{abstract}
+\title{Nodal Discontinuous Galerkin Method for the Euler Equations in GR}
+\author{Sam Dunham\altaffilmark{1}, Eirik Endeve\altaffilmark{2}, et al.}
+\altaffiltext{2}{Vanderbilt}
+\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
 
@@
 
-We consider the system of conservation laws with sources
+We assume a spacetime metric
 \begin{equation}
-  \pd{}{t}\big(\sqrt{\gamma}\,\bU\big)+\sum_{i=1}^{d}\pd{}{x^{i}}\big(\sqrt{\gamma}\,\bF^{i}(\bU)\big)=\sqrt{\gamma}\,\big(\bG(\bU)+\bQ(\bU,\bM)\big),
+  ds^{2}=-\alpha^{2}\,dt^{2}+\gamma_{ij}\,dx^{i}\,dx^{j},
+\end{equation}
+and consider the system of conservation laws with sources
+\begin{equation}
+  \pd{}{t}\big(\sqrt{\gamma}\,\bU\big)+\sum_{i=1}^{d}\pd{}{i}\big(\alpha\,\sqrt{\gamma}\,\bF^{i}(\bU)\big)=\alpha\,\sqrt{\gamma}\,\bG(\bU),
   \label{eq:conservationLaws}
 \end{equation}
-where we have split the source term into two contributions; $\bG$ is due to gravity and the use of curvilinear spatial coordinates, while $\bQ$ is due to coupling with an external field $\bM$ (e.g., radiation).
-
-The semi-discrete DG scheme is given by (letting the test function be given by $\ell_{j}$)
+where
 \begin{align}
-  &\pd{}{t}\int_{\bK}\sqrt{\gamma}\,\bU_{\DG}\,\ell_{j}\,d\bx
-  +\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
-  \big(\,
-    \sqrt{\gamma}\,\widehat{\bF}^{i}\,\ell_{j}\big|_{x_{\Hgh}^{i}}
-    -\sqrt{\gamma}\,\widehat{\bF}^{i}\,\ell_{j}\big|_{x_{\Low}^{i}}
-  \,\big)\,d\tilde{\bx}^{i} \nonumber \\
-  &\hspace{12pt}
-  -\sum_{i=1}^{d}\int_{\bK}\sqrt{\gamma}\,\bF^{i}\,(\pd{\ell_{j}}{x^{i}})\,d\bx
-  =\int_{\bK}\sqrt{\gamma}\,\big(\bG+\bQ\big)\,\ell_{j}\,d\bx,
-  \label{eq:dgSemiDiscrete}
+  \bU
+  &=\big(D,\,S_{j},\,\tau\big)^{\mbox{\tiny T}}
+  =\big(\rho\,W,\,\rho\,h\,W^{2}\,v_{j},\,\rho\,h\,W^{2}-p-D\big)^{\mbox{\tiny T}}, \\
+  \bF^{i}(\bU)
+  &=\big(D\,v^{i},\,\big)^{\mbox{\tiny T}}
 \end{align}
-where $\widehat{\bF}^{i}$ are numerical fluxes; computed by solving Riemann problems on element interfaces.  
-In each element, the DG solution is given by the polynomial expansion
-\begin{equation}
-  \bU_{\DG}(\bx,t)=\sum_{k=1}^{N}\bU_{k}(t)\,\ell_{k}(\bx), 
-\end{equation}
-where the basis $\big\{\ell_{k}\big\}_{k=1}^{N}$ is constructed from a tensor product of one-dimensional Lagrange polynomials based on a set of interpolation points $S=\{\bx_{k}\}_{k=1}^{N}$.  
-We may use Gaussian points, but leave room for flexibility in the specification of these points.  
-We use a polynomial representation of the metric functions as well; e.g.,
-\begin{equation}
-  \sqrt{\gamma}(\bx)=\sum_{k=1}^{N}\widehat{\sqrt{\gamma}}_{k}\,\hat{\ell}_{k}(\bx),
-\end{equation}
-where the basis $\big\{\hat{\ell}_{k}\big\}_{k=1}^{N}$ is also constructed from a tensor product of one-dimensional Lagrange polynomials, but is based on the Lobatto points $\hat{S}=\{\hat{\bx}_{k}\}_{k=1}^{N}$.
-(The use of Lobatto points will ensure continuity of the metric functions across element interfaces.)  
-We assume that the metric functions are time-independent.  
-Then, once the metric functions are computed analytically in the Lobatto points $\hat{\bx}_{k}\in\hat{S}$, they can be interpolated to the points $\bx_{i}\in S$; e.g.,
-\begin{equation}
-  \sqrt{\gamma}_{i}=\sqrt{\gamma}(\bx_{i})
-  =\sum_{k=1}^{N}\hat{\ell}_{k}(\bx_{i})\,\widehat{\sqrt{\gamma}}_{k}.  
-  \label{eq:l2g}
-\end{equation}
-An example of the interpolation matrix (using Gaussian points in $S$), $L_{ik}^{\mbox{\tiny L2G}}=\hat{\ell}_{k}(\bx_{i})\in\bbR^{N\times N}$, is shown in Figure~\ref{fig:LL2G}.
-
-\begin{figure}[h]
-  \begin{center}
-     \includegraphics[width=.95\textwidth]{L_L2G.png}
-  \end{center}
-  \caption{}
-  \label{fig:LL2G}
-\end{figure}
-
-We proceed by using the polynomial representation
-\begin{equation}
-  \sqrt{\gamma}(\bx)=\sum_{i=1}^{N}\sqrt{\gamma}_{i}\,\ell_{i}(\bx)
-\end{equation}
-for the metric functions as well, where the basis functions are constructed from points in $S$, and $\sqrt{\gamma}_{i}$ given by Eq.~\eqref{eq:l2g}.  
-Note that these representations are equivalent, and
-\begin{equation}
-  \sqrt{\gamma}(\hat{\bx}_{q})=\sum_{i=1}^{N}\sqrt{\gamma}_{i}\,\ell_{i}(\hat{\bx}_{q})
-  =\sum_{k=1}^{N}\Big(\sum_{i=1}^{N}\hat{\ell}_{k}(\bx_{i})\ell_{i}(\hat{\bx}_{q})\Big)\,\widehat{\sqrt{\gamma}}_{k}
-  =\widehat{\sqrt{\gamma}}_{q}.  
-\end{equation}
-
-Inserting the polynomial representations, we can write the time-derivative term in Eq.~\eqref{eq:dgSemiDiscrete} as
-\begin{equation}
-  \pd{}{t}\int_{\bK}\sqrt{\gamma}\,\bU_{\DG}\,\ell_{j}\,d\bx
-  =\sum_{k=1}^{N}M_{jk}^{(0)}\,\deriv{\bU_{k}}{t},
-\end{equation}
-where the volume mass matrix is given by
-\begin{equation}
-  M_{jk}^{(0)}=\sum_{m=1}^{N}\int_{\bK}\ell_{m}(\bx)\,\ell_{j}(\bx)\,\ell_{k}(\bx)\,d\bx\,\sqrt{\gamma}_{m}.  
-\end{equation}
-For the flux terms, we define a polynomial representation on the surface $\tilde{\bK}^{i}$
-\begin{equation}
-  [\sqrt{\gamma}\widehat{\bF}^{i}](x^{i},\tilde{\bx}^{i})
-  =\sum_{k=1}^{\tilde{N}^{i}}[\sqrt{\gamma}\widehat{\bF}^{i}]_{k}(x^{i})\,\tilde{\ell}_{k}(\tilde{\bx}^{i}),
-\end{equation}
-where the basis functions are based on a set of interpolation points $\tilde{S}^{i}=\{\tilde{\bx}_{k}^{i}\}_{k=1}^{\tilde{N}^{i}}$ on the element surface $\tilde{\bK}^{i}$.  
-Then, the surface integrals are evaluated as
-\begin{equation}
-  \int_{\tilde{\bK}^{i}}\sqrt{\gamma}\,\widehat{\bF}^{i}\,\ell_{j}\big|_{x^{i}}\,d\tilde{\bx}^{i}
-  =\sum_{k=1}^{\tilde{N}^{i}}\widetilde{M}_{jk}^{i}(x^{i})\,[\sqrt{\gamma}\widehat{\bF}^{i}]_{k}(x^{i}),
-\end{equation}
-where the surface mass matrices $\widetilde{M}_{jk}^{i}\in\bbR^{N\times\tilde{N}^{i}}$ are given by
-\begin{equation}
-  \widetilde{M}_{jk}^{i}(x^{i})
-  =\int_{\tilde{\bK}^{i}}\ell_{j}(x^{i},\tilde{\bx}^{i})\,\tilde{\ell}_{k}(\tilde{\bx}^{i})\,d\tilde{\bx}^{i}, 
-\end{equation}
-and plotted in Figure~\ref{fig:SurfMassMats}.
-
-\begin{figure}[h]
-  \begin{center}
-     \includegraphics[width=1.0\textwidth]{IntegrationMatrices.png}
-  \end{center}
-  \caption{}
-  \label{fig:SurfMassMats}
-\end{figure}
-
-In order to compute numerical fluxes, the evolved quantities and metric functions are interpolated to the relevant surface.  
-For example, to interpolate to $x_{\Low}^{i,+}=\lim_{\delta\to0}x_{\Low}^{i}+\delta$ ($\delta>0$) we evaluate
-\begin{equation}
-  \bU_{k}(x_{\Low}^{i,+})
-  =\bU_{\DG}(x_{\Low}^{i,+},\tilde{\bx}_{k}^{i})
-  =\sum_{l=1}^{N}L_{kl}^{i}(x_{\Low}^{i})\,\bU_{l},
-\end{equation}
-where we have defined the interpolation matrix $L_{kl}^{i}(x_{\Low}^{i})=\ell_{l}(x_{\Low}^{i},\tilde{\bx}_{k}^{i})\in\bbR^{\tilde{N}^{i}\times N}$.  
-Interpolation matrices are shown in Figure~\ref{fig:IntMatsDims}.  
-The metric functions are interpolated similarly.
-
-\begin{figure}[h]
-  \begin{center}
-     \includegraphics[width=1.0\textwidth]{InterpolationMatricesDims.png}
-  \end{center}
-  \caption{}
-  \label{fig:IntMatsDims}
-\end{figure}
-
-For the volume term and source terms due to gravity and curvilinear coordinates we use the expansions
-\begin{equation}
-  \sqrt{\gamma}\bF^{i}=\sum_{k=1}^{N}[\sqrt{\gamma}\,\bF^{i}]_{k}\,\ell_{k}(\bx)
-  \quad\text{and}\quad
-  \sqrt{\gamma}\bG=\sum_{k=1}^{N}[\sqrt{\gamma}\,\bG]_{k}\,\ell_{k}(\bx)
-\end{equation}
-where the basis functions are based on the points $S$.  
-Then, 
-\begin{equation}
-  \int_{\bK}\sqrt{\gamma}\,\bF^{i}\,(\pd{\ell_{j}}{x^{i}})\,d\bx
-  =\sum_{k=1}^{N}S_{jk}^{i}\,[\sqrt{\gamma}\,\bF^{i}]_{k}
-  \quad\text{and}\quad
-  \int_{\bK}\sqrt{\gamma}\,\bG\,\ell_{j}\,d\bx
-  =\sum_{k=1}^{N}M_{jk}\,[\sqrt{\gamma}\,\bG]_{k},
-\end{equation}
-where
-\begin{equation}
-  S_{jk}^{i}=\int_{\bK}\pderiv{\ell_{j}}{x^{i}}(\bx)\,\ell_{k}(\bx)\,d\bx
-  \quad\text{and}\quad
-  M_{jk}
-  =\int_{\bK}\ell_{j}(\bx)\,\ell_{k}(\bx)\,d\bx.
-\end{equation}
-These matrices are displayed on Figure~\ref{fig:MassStiffMats}.  
-Note again the sparsity patterns.
-
-\begin{figure}[h]
-  \begin{center}
-     \includegraphics[width=1.0\textwidth]{MassAndStiffnessMatrices.png}
-  \end{center}
-  \caption{}
-  \label{fig:MassStiffMats}
-\end{figure}
-
-For the source terms due to coupling with the external field, we write
-\begin{equation}
-  \bQ=\sum_{k=1}^{N}\bQ_{k}\,\ell_{k}(\bx),
-\end{equation}
-where the basis is constructed from the points in $S$.  
-Then
-\begin{equation}
-  \int_{\bK}\sqrt{\gamma}\,\bQ\,\ell_{j}(\bx)\,d\bx
-  =\sum_{k=1}^{N}M_{jk}^{(0)}\,\bQ_{k}.  
-\end{equation}
-
-We can then write the DG scheme in the compact form
-\begin{equation}
-  M^{(0)}\deriv{\bU}{t}
-  =-\sum_{i=1}^{d}
-  \Big(\,
-    \widetilde{M}^{i}(x_{\Hgh}^{i,-})\,[\sqrt{\gamma}\widehat{\bF}^{i}](x_{\Hgh}^{i})
-    -\widetilde{M}^{i}(x_{\Low}^{i,+})\,[\sqrt{\gamma}\widehat{\bF}^{i}](x_{\Low}^{i})
-    -S^{i}\,[\sqrt{\gamma}\bF^{i}]    
-  \,\Big)
-  +M\,[\sqrt{\gamma}\,\bG]
-  +M^{(0)}\bQ,
-  \label{eq:dgCompact}
-\end{equation}
-where $M^{(0)},M,S^{i}\in\bbR^{N\times N}$ and $\widetilde{M}^{i}\in\bbR^{N\times\tilde{N}^{i}}$.  
-In Eq~\eqref{eq:dgCompact}, $\bU=(\bU_{1},\ldots,\bU_{N})^{\mbox{\tiny T}}$, $[\sqrt{\gamma}\bF^{i}]=([\sqrt{\gamma}\bF^{i}]_{1},\ldots,[\sqrt{\gamma}\bF^{i}]_{N})^{\mbox{\tiny T}}$, $[\sqrt{\gamma}\bG]=([\sqrt{\gamma}\bG]_{1},\ldots,[\sqrt{\gamma}\bG]_{N})^{\mbox{\tiny T}}$, $\bQ=(\bQ_{1},\ldots,\bQ_{N})^{\mbox{\tiny T}}$, and $[\sqrt{\gamma}\widehat{\bF}]^{i}=([\sqrt{\gamma}\widehat{\bF}^{i}]_{1},\ldots,[\sqrt{\gamma}\widehat{\bF}^{i}]_{\tilde{N}^{i}})^{\mbox{\tiny T}}$; i.e., point values within $\bK$ or on the element faces $\tilde{\bK}^{i}$ --- not to be confused with the continuous fields in Eq.~\eqref{eq:conservationLaws}.
-
-In multi-dimensional problems, the evaluation of $d_{t}\bU$ in Eq.~\eqref{eq:dgCompact} can become costly for several reasons.  
-Assume $d=3$, and that the basis functions are constructed from polynomials of degree $p=3$.  
-Then, $N=(p+1)^{d}=64$.  
-If we use the same polynomial degree to construct the numerical flux on the element interfaces we have $\tilde{N}^{i}=(p+1)^{d-1}=16$.  
-The matrices involve the metric function $\sqrt{\gamma}$, which depends on spatial coordinate $\bx$.  
-We can precompute matrices of the form
-\begin{equation}
-  \int_{\bK}\ell_{m}(\bx)\,\ell_{j}(\bx)\,\ell_{k}(\bx)\,d\bx,
-\end{equation}
-which contains $1024$ entries, and contract with $\sqrt{\gamma}_{m}$ in each element to avoid storing matrices for each element.  
-The contraction operation involves $N^{3}$ operations.  
-Additional (similar) cost is incurred by inverting the mass matrix.  
-We achieve significant computational savings from lumping the mass matrix; i.e., when computing the mass matrix, we use a quadrature where the quadrature points coincide with the interpolation points $S$.
-Then, the mass matrix takes the following simple (diagonal) form
-\begin{equation}
-  M_{jk}^{(0)}
-  \approx\sum_{m=1}^{N}\sum_{q=1}^{N}w_{q}\,\ell_{m}(\bx_{q})\,\ell_{j}(\bx_{q})\,\ell_{k}(\bx_{q})\,\sqrt{\gamma}_{m}
-  =\delta_{jk}\,w_{k}\,\sqrt{\gamma}_{k},
-\end{equation}
-where $\sqrt{\gamma}_{k}=\sum_{m=1}^{N}\widehat{\sqrt{\gamma}}_{m}\,\hat{\ell}_{m}(\bx_{k})$.  
-In our example with $p=3$ we are using $4$ points to integrate a polynomial of degree $3\times p=9$, while a $4$-point Gaussian quadrature only integrates polynomials of degree $\le 2\times N-1=7$ exactly.
-
-\begin{figure}[h]
-  \begin{center}
-    \begin{tabular}{cc}
-     \includegraphics[width=0.5\textwidth]{MassMatrix0_G4.png}
-     \includegraphics[width=0.5\textwidth]{MassMatrix0_G5.png}
-    \end{tabular}
-  \end{center}
-  \caption{}
-  \label{fig:MassMats}
-\end{figure}
-
-\section{Cell Averages and Conservation}
-
-The DG method evolves a high-order approximation the solution $\bU$.  
-Each element contains $N$ degrees of freedom $\{\bU_{i}\}_{i=1}^{N}$.  
-Let the cell-average in element $\bK$ be given by
-\begin{equation}
-  \bU_{\bK}=\f{1}{V_{\bK}}\int_{\bK}\bU_{\DG}\,\sqrt{\gamma}\,d\bx,
-  \quad\text{where}\quad
-  V_{\bK}=\int_{\bK}\sqrt{\gamma}\,d\bx.  
-\end{equation}
-The cell volume is computed as
-\begin{equation}
-  V_{\bK}=\sum_{k=1}^{N}w_{k}\sqrt{\gamma}_{k},
-  \quad\text{where}\quad
-  w_{k}=\int_{\bK}\ell_{k}(\bx)\,d\bx, 
-\end{equation}
-while the cell average becomes
-\begin{equation}
-  \bU_{\bK}=\f{1}{V_{\bK}}\sum_{j=1}^{N}\sum_{k=1}^{N}M_{jk}\,\sqrt{\gamma}_{j}\,\bU_{k}.  
-\end{equation}
-Note that $M_{jk}$ is diagonal (cf. Figure~\ref{fig:MassStiffMats}), which simplifies the computation of $\bU_{\bK}$.
-
-Define the vector of ones $\be^{\mbox{\tiny T}}=(1,\ldots,1)$.  
-Then we see that
-\begin{equation}
-  \be^{\mbox{\tiny T}}\,M^{(0)}\deriv{\bU}{t}=V_{\bK}\deriv{\bU_{\bK}}{t},
-\end{equation}
-since $\sum_{j=1}^{N}\ell_{j}(\bx)=1$.  
-The evolution equation for the cell average is then given by
-\begin{equation}
-  \deriv{\bU_{\bK}}{t}
-  =-\f{1}{V_{\bK}}\Big[\sum_{i=1}^{d}
-  \Big(\,
-    (\tilde{w}^{i})^{\mbox{\tiny T}}[\sqrt{\gamma}\widehat{\bF}^{i}](x^{i}_{\Hgh})
-    -(\tilde{w}^{i})^{\mbox{\tiny T}}[\sqrt{\gamma}\widehat{\bF}^{i}](x^{i}_{\Low})
-  \,\Big)-w^{\mbox{\tiny T}}[\sqrt{\gamma}\bG]\Big]+\bQ_{\bK},
-  \label{eq:dgCellAverage}
-\end{equation}
-where we have defined the surface integral weights
-\begin{equation}
-  \tilde{w}_{k}^{i}=\int_{\tilde{\bK}^{i}}\tilde{\ell}_{k}(\tilde{\bx}^{i})\,d\tilde{\bx}^{i}.  
-\end{equation}
-Equation~\eqref{eq:dgCellAverage} is familiar from the literature on finite volume methods for hyperbolic conservation laws.  
-In the absence of sources, it expresses exact conservation of the cell average quantities $\bU_{\bK}$.
-
-\section{Source Terms from Geometry Fields}
-
-The source terms from geometry fields (i.e., gravity and curvilinear coordinates) involve spatial derivatives.  
-One could use the polynomial expansions of these fields and simply take derivatives.  
-This approach reduces the order of accuracy in the representation of these fields, and leads to vanishing source terms in the case with polynomial degree $p=0$.  
-To avoid this, we define expansions of derivatives of the geometry fields.  
-To this end, let $f$ represent a geometry field (e.g., $f=\sqrt{\gamma}$) and define $g^{i}=\pderiv{f}{x^{i}}$.  
-Then
-\begin{equation}
-  g_{i}(\bx)=\sum_{k=1}^{N}(g_{i})_{k}\,\ell_{k}(\bx),
-\end{equation}
-where the basis is constructed from points $\bx_{k}\in S$, and
-\begin{align}
-  (g_{i})_{j}
-  &=M_{jj}^{-1}\int_{\bK}g_{i}\,\ell_{j}\,d\bx \nonumber \\
-  &=M_{jj}^{-1}
-  \Big\{\,
-    \int_{\tilde{\bK}^{i}}\big[\,\hat{f}\,\ell_{j}\big|_{x_{\Hgh}^{i}}-\hat{f}\,\ell_{j}\big|_{x_{\Low}^{i}}\,\big]\,d\tilde{\bx}^{i}
-    -\int_{\bK}f\,\pderiv{\ell_{j}}{x^{i}}\,d\bx
-  \,\Big\}.  
-\end{align}
-(Note that $M_{jk}=M_{jj}\delta_{jk}$.)
-By construction, the geometry fields are continuous across element interfaces.  
-(In the $p=0$ case, the geometry fields on the faces are computed by averaging values from elements abutting the face.)  
-Introducing the expansions
-\begin{equation}
-  \hat{f}(x^{i},\tilde{\bx}^{i})=\sum_{k=1}^{\tilde{N}^{i}}\hat{f}_{k}(x^{i})\,\tilde{\ell}_{k}(\tilde{\bx}^{i})
-  \quad\text{and}\quad
-  f(\bx)=\sum_{k=1}^{N}f_{k}\,\ell_{k}(\bx)
-\end{equation}
-on the faces and the interior of $\bK$, we have
-\begin{equation}
-  (g_{i})_{j}=M_{jj}^{-1}
-  \Big\{\,
-    \sum_{k=1}^{\tilde{N}^{i}}
-    \Big(
-      \widetilde{M}_{jk}^{i}(x_{\Hgh}^{i,-})\,\hat{f}_{k}(x_{\Hgh}^{i})
-      -\widetilde{M}_{jk}^{i}(x_{\Low}^{i,+})\,\hat{f}_{k}(x_{\Low}^{i})
-    \Big)
-    -\sum_{k=1}^{N}S_{jk}^{i}\,f_{k}
-  \,\Big\}.  
-  \label{eq:geometryDerivative}
-\end{equation}
-Writing this in matrix form, letting $g_{i}=\big((g_{i})_{1},\ldots,(g_{i})_{N}\big)^{\mbox{\tiny T}}$, $f=\big(f_{1},\ldots,f_{N}\big)^{\mbox{\tiny T}}$, and $\hat{f}=\big(\hat{f}_{1},\ldots,\hat{f}_{\tilde{N}^{i}}\big)^{\mbox{\tiny T}}$, we have
-\begin{equation}
-  g_{i}=M^{-1}\Big\{\widetilde{M}^{i}(x_{\Hgh}^{i,-})\,\hat{f}(x_{\Hgh}^{i})-\widetilde{M}^{i}(x_{\Low}^{i,+})\,\hat{f}(x_{\Low}^{i})-S^{i}f\Big\}.  
-\end{equation}
-
-For a continuous field approximated by $f(\bx)=\sum_{i=1}^{N}f_{k}\,\ell_{k}(\bx)$, these representations are equivalent in the sense that
-\begin{equation}
-  M_{jj}^{-1}\int_{\bK}\big(g_{i}-\pderiv{f}{x^{i}}\big)\,\ell_{j}=0.  
-\end{equation}
-We approximate metric factors $\sqrt{\gamma}$, $\sqrt{\gamma_{11}}$, $\sqrt{\gamma_{22}}$, and $\sqrt{\gamma_{33}}$, and the gravitational potential $\Phi$ with polynomial representations that are continuous across element interfaces, as discussed for $\sqrt{\gamma}$ in Section~\ref{sec:dgMethod}.
-
-\section{Source Terms from Curvilinear Coordinates}
-
-In the absence of gravity ($\Phi=0$), the geometry sources are purely due to curvilinear coordinates and contribute only to the right-hand side of the momentum equation.  
-We consider the case where $\gamma_{ij}$ is diagonal, and write
-\begin{equation}
-  \f{1}{2}\,P^{ik}\pderiv{\gamma_{ik}}{x^{j}}
-  =\sum_{i=1}^{d}P_{~i}^{i}\f{1}{\sqrt{\gamma_{ii}}}\pderiv{\sqrt{\gamma_{ii}}}{x^{j}}.
-\end{equation}
-
-Next we investigate the balance between the curvilinear sources and the geometry terms in the spatial divergence of the momentum equation.  
-For a fluid associated with an isotropic and spatially homogeneous stress tensor, i.e., $P_{~k}^{i}=P\,\delta_{~k}^{i}$, the balance should be exact so as to not induce artificial flows.  
-The cell average of the $j$-th component of the momentum equation is denoted $(S_{j})_{\bK}$.  
-Under the stated conditions, the evolution equation is given by
-\begin{equation}
-  \deriv{(S_{j})_{\bK}}{t}
-  =-\f{1}{V_{\bK}}
-  \Big[\,
-  \Big(\,
-    (\tilde{w}^{j})^{\mbox{\tiny T}}[\sqrt{\gamma}](x^{j}_{\Hgh})
-    -(\tilde{w}^{j})^{\mbox{\tiny T}}[\sqrt{\gamma}](x^{j}_{\Low})
-  \,\Big)
-  -\sum_{i=1}^{d}w^{\mbox{\tiny T}}
-  \big[\f{\sqrt{\gamma}}{\sqrt{\gamma_{ii}}}\pderiv{\sqrt{\gamma_{ii}}}{x^{j}}\big]
-  \,\Big],
-  \label{eq:MomentumUniformP}
-\end{equation}
-where, without loss of generality, we have set $P=1$.  
-In Cartesian coordinates, the balance is trivial.  
-Next, we consider the balance for the case of spherical polar and cylindrical coordinates.
-
-\subsection{Spherical Polar Coordinates}
-
-In spherical polar coordinates, we have $\sqrt{\gamma_{11}}=1$, $\sqrt{\gamma_{22}}=r$, $\sqrt{\gamma_{33}}=r\sin\theta$, and $\sqrt{\gamma}=r^{2}\sin\theta$.
-
-For $j=1$ (the radial component of the momentum equation), we have
-\begin{equation}
-  \sum_{i=1}^{d}w^{\mbox{\tiny T}}
-  \big[\f{\sqrt{\gamma}}{\sqrt{\gamma_{ii}}}\pderiv{\sqrt{\gamma_{ii}}}{x^{j}}\big]
-  =w^{\mbox{\tiny T}}\big[2\,r\,\sin\theta\big]
-  =(\tilde{w}^{1})^{\mbox{\tiny T}}[r_{\Hgh}^{2}\sin\theta]-(\tilde{w}^{1})^{\mbox{\tiny T}}[r_{\Low}^{2}\sin\theta]
-  =(\tilde{w}^{1})^{\mbox{\tiny T}}[\sqrt{\gamma}](r_{\Hgh})-(\tilde{w}^{1})^{\mbox{\tiny T}}[\sqrt{\gamma}](r_{\Low}).  
-\end{equation}
-Hence the balance is exact for a quadrature that integrates polynomials of degree $1$ in the radial direction.
-
-For $j=2$ (the latitudinal component of the momentum equation), we have
-\begin{equation}
-  \sum_{i=1}^{d}w^{\mbox{\tiny T}}
-  \big[\f{\sqrt{\gamma}}{\sqrt{\gamma_{ii}}}\pderiv{\sqrt{\gamma_{ii}}}{x^{j}}\big]
-  =w^{\mbox{\tiny T}}\big[\sqrt{\gamma_{22}}\,\pderiv{\sqrt{\gamma_{33}}}{x^{2}}\big].  
-\end{equation}
-Since $\sqrt{\gamma_{22}}$ and $\sqrt{\gamma_{33}}$ are approximated by polynomials of degree $1$ in the radial direction and $\sqrt{\gamma_{33}}$ is approximated by a degree $p$ polynomial in the latitudinal direction, the balance is exact if the quadrature exactly integrates polynomials of degree $2$ in the radial direction and degree $p-1$ in the latitudinal direction (e.g., the Gaussian quadrature with $N=2$).
-By using the approximation in Eq.~\eqref{eq:geometryDerivative}, we also achieve exact balance in the case with $p=0$ polynomials.
-
-The balance is trivial for $j=3$ (the azimuthal component of the momentum equation).
-
-\subsection{Cylindrical Coordinates}
-
-In spherical polar coordinates, we have $\sqrt{\gamma_{11}}=1$, $\sqrt{\gamma_{22}}=1$, $\sqrt{\gamma_{33}}=R$, and $\sqrt{\gamma}=R$.
-
-\section{Source Terms from Gravitational Fields}
-
-For the source terms due to gravitational fields, we investigate conservation of energy.
-
-\subsection{Time-Independent Gravitational Fields}
-
-Multiplying the mass conservation equation with a time-independent gravitational field $\Phi=\Phi(\bx)$, we obtain
-\begin{equation}
-  \pd{}{t}\big(\sqrt{\gamma}\,\rho\,\Phi\big)
-  +\sum_{i=1}^{d}\pd{}{i}\big(\sqrt{\gamma}\,(\rho\,\Phi\,v^{i})\big)
-  =\sqrt{\gamma}\sum_{i=1}^{d}\rho\,v^{i}\,\pd{\Phi}{i}.
-\end{equation}
-Adding this equation to the fluid energy equation 
-\begin{equation}
-  \pd{}{t}\big(\sqrt{\gamma}\,E\big)
-  +\sum_{i=1}^{d}\pd{}{i}\big(\sqrt{\gamma}\,(E+p)\,v^{i}\big)
-  =-\sqrt{\gamma}\sum_{i=1}^{d}\rho\,v^{i}\,\pd{\Phi}{i},
-\end{equation}
-where we ignore the sources $\bQ$ due to energy exchange with the external field $\bM$, gives the conservation law
-\begin{equation}
-  \pd{}{t}\big(\sqrt{\gamma}\,(E+\rho\,\Phi)\big)
-  +\sum_{i=1}^{d}\big(\sqrt{\gamma}\,(E+p+\rho\,\Phi)\,v^{i}\big)
-  =0.  
-\end{equation}
-
-In the semi-discrete DG representation, the approximation to the mass density $\rho_{\DG}$ satisfies
-\begin{equation}
-  \pd{}{t}\int_{\bK}\sqrt{\gamma}\,\rho_{\DG}\,\ell_{j}\,d\bx
-  +\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
-  \Big(
-    \sqrt{\gamma}\,\widehat{\rho v^{i}}\,\ell_{j}\big|_{x_{\Hgh}^{i}}
-    -\sqrt{\gamma}\,\widehat{\rho v^{i}}\,\ell_{j}\big|_{x_{\Low}^{i}}
-  \Big)
-  =\sum_{i=1}^{d}\int_{\bK}\sqrt{\gamma}\,(\rho\,v^{i})\,\pd{\ell_{j}}{i}.  
-\end{equation}
-Contracting this with $\Phi_{j}$, noting that $\Phi(\bx)=\sum_{j=1}^{N}\Phi_{j}\,\ell_{j}(\bx)$, gives
-\begin{equation}
-  \pd{}{t}\big(\rho\Phi\big)_{\bK}
-  +\f{1}{V_{\bK}}\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
-  \Big(
-    \sqrt{\gamma}\,\widehat{F}_{g}^{i}\big|_{x_{\Hgh}^{i}}
-    -\sqrt{\gamma}\,\widehat{F}_{g}^{i}\big|_{x_{\Low}^{i}}
-  \Big)
-  =\f{1}{V_{\bK}}\sum_{i=1}^{d}\int_{\bK}\sqrt{\gamma}\,(\rho\,v^{i})\,\pd{\Phi}{i},
-\end{equation}
-where the cell-averaged gravitational energy density is
-\begin{equation}
-  \big(\rho\Phi\big)_{\bK}
-  =\f{1}{V_{\bK}}\int_{\bK}\rho_{\DG}\,\Phi\,\sqrt{\gamma}\,d\bx,
-\end{equation}
-and $\widehat{F}_{g}^{i}=\widehat{\rho \Phi v^{i}}=\widehat{\rho v^{i}}\,\Phi$.
-
-\begin{remark}
-  The requirement that $\Phi$ is continuous across element interfaces is needed for conservation.
-\end{remark}
-
-The cell-averaged energy density satisfies
-\begin{equation}
-  \pd{E_{\bK}}{t}
-  +\f{1}{V_{\bK}}\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
-  \Big(
-    \sqrt{\gamma}\,\widehat{F}_{E}^{i}\big|_{x_{\Hgh}^{i}}
-    -\sqrt{\gamma}\,\widehat{F}_{E}^{i}\big|_{x_{\Low}^{i}}
-  \Big)
-  =-\f{1}{V_{\bK}}\sum_{i=1}^{d}\int_{\bK}\sqrt{\gamma}\,(\rho\,v^{i})\,\pd{\Phi}{i}.  
-\end{equation}
-Thus, adding the equation for the cell-averaged gravitational energy density and the equation for the total fluid energy density results in an exact conservation law for the total (gravitational plus fluid) energy.
-(Complications may arise when limiters are invoked.)
 

### 2018-01-22 Documents/M1/realizableFermionicM1/realizableM1_fermionPaper.tex
Created tex files for the realiazableM1 paper.

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Journal of Computational Physics }

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Realizability-Preserving Two-Moment DG Method for Fermionic Transport \tnoteref{ldrd-support}}
\tnotetext[ldrd-support]{This research is sponsored by ...}

%% Group authors per affiliation:
\author[ornl,utk-phys]{Eirik Endeve\corref{cor}}
\ead{endevee@ornl.gov}

\author[utk-phys]{Ran Chu}
\ead{rchu@vols.utk.edu}

\author[utk-phys]{Anthony Mezzacappa}
\ead{mezz@utk.edu}

\cortext[cor]{Corresponding author. Tel.:+1 865 576 6349; fax:+1 865 241 0381}

\address[ornl]{Computational and Applied Mathematics Group,
Oak Ridge National Laboratory,
Oak Ridge, TN 37831 USA }

\address[utk-phys]{Department of Physics and Astronomy,
University of Tennessee
Knoxville, TN 37996-1200}

\begin{abstract}
This paper ...
\end{abstract}

\begin{keyword}
Boltzmann equation, 
Radiation transport, 
Hyperbolic conservation laws, 
Discontinuous Galerkin, 
Realizability
\end{keyword}

\end{frontmatter}

\linenumbers

\input{sections/intro}
\input{sections/model}
\input{sections/MomentsRealizability}
\input{sections/IMEX}
\input{sections/DGmethod}
\input{sections/DGIMEXscheme}
\input{sections/limiter}
\input{sections/numerical}
\input{sections/conclusion}
%\input{sections/appendix}
\clearpage

\section*{References}

\bibliography{./refs/dgCurv.bib}
\end{document}

### 2018-01-22 Documents/M1/realizableFermionicM1/sections/model.tex
Created tex files for the realiazableM1 paper.

\section{Mathematical Model}

  - Boltzmann Equation with emission and absorption, and isotropic scattering

  - Angular moments and moment equations

### 2018-01-22 Documents/M1/realizableFermionicM1/realizableM1_fermionPaper.tex
Made some additions to model section

@@
 \usepackage{lineno,hyperref}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
 \modulolinenumbers[5]
+\hypersetup{
+  bookmarksnumbered = true,
+  bookmarksopen=false,
+  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
+  pdffitwindow=true,      % window fit to page when opened
+  pdfnewwindow=true, % links in new window
+  colorlinks=true,           % false: boxed links; true: colored links
+  linkcolor=blue,            % color of internal links
+  citecolor=magenta,    % color of links to bibliography
+  filecolor=magenta,     % color of file links
+  urlcolor=cyan              % color of external links
+}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{./definitions}
 
@@
 Discontinuous Galerkin, 
-Realizability
+Moment Realizability
 \end{keyword}
@@
 
-\bibliography{./refs/dgCurv.bib}
+\bibliography{./references/references.bib}
 \end{document}

### 2018-01-22 Documents/M1/realizableFermionicM1/sections/model.tex
Made some additions to model section

@@
 
-  - Boltzmann Equation with emission and absorption, and isotropic scattering
+\subsection{Boltzmann Equation}
 
-  - Angular moments and moment equations
+In this paper, we consider approximate solutions to the Boltzmann equation for radiation transport
+\begin{equation}
+  \pd{f}{t}+\vect{\ell}\cdot\nabla f
+  =\sigma_{\Ab}\,\big(\,f_{0}-f\,\big)
+  +\sigma_{\Scatt}\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omegaNu-f\,\big),
+  \label{eq:boltzmann}
+\end{equation}
+where the distribution function $f(\omegaNu,\epsilonNu,x,t):\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in direction $\omegaNu\in\bbS^{2}:=\{\,\omegaNu=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\epsilonNu\in\bbR^{+}$, at position $x\in\bbR^{3}$ and time $t\in\bbR^{+}$.
+The unit vector $\vect{\ell}(\omegaNu)\in\bbR^{3}$ is parallel to the particle three-momentum.  
+On the right-hand side of Eq.~\eqref{eq:boltzmann}, $\sigma_{\Ab}(\epsilonNu,x)$ and $\sigma_{\Scatt}(\epsilonNu,x)$ are the absorption and scattering opacities, respectively, and $f_{0}(\epsilonNu,x)$ is the equilibrium distribution distribution function.
+
+\subsection{Angular Moment Equations}
+
+The boltzmann equation is often too expensive to solve directly.  
+Instead, equations for angular moments of the distribution function are solved instead.  
+\begin{equation}
+  \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(z,t)=\f{1}{4\pi}\int_{\bbS}f(\omegaNu,z,t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omegaNu
+\end{equation}

### 2018-01-23 Documents/M1/realizableFermionicM1/sections/model.tex
Further description of the model.

--- 2018-01-22 Documents/M1/realizableFermionicM1/sections/model.tex
@@
 
-  - Boltzmann Equation with emission and absorption, and isotropic scattering
+In this section we give a brief summary of the mathematical model.
 
-  - Angular moments and moment equations
+\subsection{Boltzmann Equation}
+
+In this paper, we consider approximate solutions to the Boltzmann equation for radiation transport in slab geometry
+\begin{equation}
+  \pd{f}{t}+\vect{\ell}\cdot\nabla f
+  =\sigma_{\Ab}\,\big(\,f_{0}-f\,\big)
+  +\sigma_{\Scatt}\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omegaNu-f\,\big),
+  \label{eq:boltzmann}
+\end{equation}
+where the distribution function $f(\omegaNu,\epsilonNu,\vect{x},t):\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in direction $\omegaNu\in\bbS^{2}:=\{\,\omegaNu=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\epsilonNu\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
+Thus, we use spherical momentum space coordinates $(\omegaNu,\epsilonNu)$.  
+We also define the energy-position coordinates $\vect{z}:=\{\epsilonNu,\vect{x}\}\in\bbR^{+}\times\bbR^{3}$.  
+The unit vector $\vect{\ell}(\omegaNu)\in\bbR^{3}$ (independent of $\vect{z}$) is parallel to the particle three-momentum.  
+On the right-hand side of Eq.~\eqref{eq:boltzmann}, $\sigma_{\Ab}(\vect{z})\ge0$ and $\sigma_{\Scatt}(\vect{z})\ge0$ are the absorption and scattering opacities due to interactions with a background, respectively, and $f_{0}(\vect{z})$ is the equilibrium distribution distribution function.
+Here, we consider transport of Fermions (e.g., neutrinos), so that the equilibrium distribution function takes the form
+\begin{equation}
+  f_{0}(\vect{z})=\f{1}{e^{(\epsilonNu-\mu(\vect{x}))/T(\vect{x})}+1},  
+\end{equation}
+where temperature $T$ and the chemical potential $\mu$ are properties of the background.
+
+\subsection{Angular Moment Equations}
+
+The Boltzmann equation is often too expensive to solve directly.  
+Instead, equations for angular moments of the distribution function can be solved for.  
+To this end, we define the angular moments of the distribution function
+\begin{equation}
+  \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
+  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omegaNu,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omegaNu,
+  \label{eq:angularMoments}
+\end{equation}
+where $\cJ$ (zeroth moment) is the density, $\vect{\cH}$ (first moment) the flux, and $\vect{\cK}$ (second moment) is the stress tensor.  
+Note that the moments defined in Eq.~\ref{eq:angularMoments} are \emph{spectral moments} (depending on the energy $\epsilonNu$).  
+The \emph{grey moments} are obtained by integration over energy
+\begin{equation}
+  \big\{\,J,\vect{H},\vect{K}\,\big\}(\vect{x},t)
+  =\int_{\bbR^{+}}\big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\epsilonNu,\vect{x},t)\,\epsilonNu^{2}d\epsilonNu.  
+\end{equation}
+
+Taking the zeroth and first moments of Eq.~\eqref{eq:boltzmann} gives the two-moment model, comprising of a system of conservation laws with sources
+\begin{equation}
+  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}(\vect{\cM})=\vect{\cC}(\vect{\cM}),
+  \label{eq:momentEquations}
+\end{equation}
+where $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, the components of the flux vector $\vect{\cF}$ are $\vect{\cF}^{i}=\vect{e}_{i}\cdot\vect{\cF}=(\vect{e}_{i}\cdot\vect{\cH},\vect{e}_{i}\cdot\vect{\cK})^{T}$, where $\vect{e}_{i}$ is the unit vector in the $i$th coordinate direction, and $\vect{\cC}=\vect{\cQ}-\vect{\cD}\,\vect{\cM}$.
+Here we have also defined $\vect{\cQ}=(\sigma_{\Ab}\cJ_{0},\vect{0})^{T}$, where $\cJ_{0}=f_{0}$, and $\vect{\cD}=\mbox{diag}(\sigma_{\Ab},\vect{I}\sigma_{\Tot})$, where $\sigma_{\Tot}=\sigma_{\Ab}+\sigma_{\Scatt}$, and $\vect{I}$ is the identity matrix.
+In order to close the system of equations, the stress tensor $\vect{\cK}$ must be related to the lower moments by a closure procedure.  
+To this end, Levermove \cite{levermore_1984} defines $\vect{k}=\vect{\cK}/\cJ$, assumes that the radiation field is symmetric about a preferred direction $\vect{h}=\vect{\cH}/|\vect{\cH}|$, and writes
+\begin{equation}
+  \vect{k}=\f{1}{2}\big[\,\big(1-\chi\big)\,\vect{I}+\big(3\,\chi-1\big)\,\vect{h}\otimes\vect{h}\,\big],
+\end{equation}
+where $\chi=\chi(\cJ,|\vect{\cH}|)$ is the Eddington factor.  
+We will return to the issue of determining the Eddington factor in Section~\ref{sec:realizability}.
+
+This concludes the initial description of our model.

### 2018-01-24 Documents/M1/realizableFermionicM1/sections/model.tex
Updates to paper

@@
 
-In this section we give a brief summary of the mathematical model.
+In this section we give a summary of the mathematical model we employ.
 
@@
   f_{0}(\vect{z})=\f{1}{e^{(\epsilonNu-\mu(\vect{x}))/T(\vect{x})}+1},  
+  \label{eq:fermiDirac}
 \end{equation}
-where temperature $T$ and the chemical potential $\mu$ are properties of the background.
+where the temperature $T$ and the chemical potential $\mu$ are properties of the background.
 
@@
 In order to close the system of equations, the stress tensor $\vect{\cK}$ must be related to the lower moments by a closure procedure.  
-To this end, Levermove \cite{levermore_1984} defines $\vect{k}=\vect{\cK}/\cJ$, assumes that the radiation field is symmetric about a preferred direction $\vect{h}=\vect{\cH}/|\vect{\cH}|$, and writes
+To this end, Levermore \cite{levermore_1984} defines the Eddington tensor $\vect{k}=\vect{\cK}/\cJ$, assumes that the radiation field is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, and writes
 \begin{equation}
-  \vect{k}=\f{1}{2}\big[\,\big(1-\chi\big)\,\vect{I}+\big(3\,\chi-1\big)\,\vect{h}\otimes\vect{h}\,\big],
+  \vect{k}=\f{1}{2}\big[\,\big(1-\chi\big)\,\vect{I}+\big(3\,\chi-1\big)\,\widehat{\vect{h}}\otimes\widehat{\vect{h}}\,\big],
 \end{equation}

### 2018-01-24 Documents/M1/realizableFermionicM1/sections/realizability.tex
Updates to paper

\section{Moment Realizability and Closures for Fermion}
\label{sec:realizability}

Our goal is to design a numerical method for solving the system of equations given by Eq.~\eqref{eq:momentEquations}, which approximates Eq.~\eqref{eq:boltzmann}.  
To this end, we want to obtain solutions that preserve features of the original problem.

\subsection{Moment Realizability}

\begin{define}
  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they are consistent with a distribution function satisfying $0\le f \le 1$.
\end{define}
\begin{lemma}
  Let the distribution function $f$ be bounded by $0\le f \le1$.  
  Then $0\le\cJ\le1$ and $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$
\end{lemma}
\begin{proof}
  Prove this
\end{proof}

We now define the realizable set $\cR$
\begin{equation}
  \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in[0,1]~\text{and}~(1-\cJ)\cJ-|\vect{\cH}|\ge0\,\big\}
  \label{eq:realizableSet}
\end{equation}

\begin{lemma}
  The set $\cR$, defined in Eq.~\eqref{eq:realizableSet}, is convex.  
\end{lemma}
\begin{proof}
  Prove this
\end{proof}

Include figure to illustrate the convex set.

\begin{lemma}
  Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ be defined as in Eq.~\eqref{eq:angularMoments} with distribution function $f_{a}\in[0,1]$.  
  Similarly, $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments of a distribution function $f_{b}\in[0,1]$.  
  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector.  
  Then
  \begin{equation}
    \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
  \end{equation}
\end{lemma}
\begin{proof}
  Prove this.
\end{proof}

\subsection{Moment Closures}

\subsubsection{Maximum Entropy Closure}
Basic principles
Chernohorsky \& Bludman
Banach \& Larecki

\subsubsection{Kershaw Closure}
Basic principles
Banach \& Larecki

### 2018-01-25 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
Added some text on DG and IMEX methods

\section{Realizability-Preserving DG-IMEX Scheme}
\label{sec:realizableDGIMEX}

### 2018-01-25 Documents/M1/realizableFermionicM1/sections/dg.tex
Added some text on DG and IMEX methods

\section{Discontinuous Galerkin Method}
\label{sec:dg}

Here we briefly outline the DG method for the moment equations.  
We do not include any physics that couple the energy dimension.  
Thus, the particle energy $\epsilonNu$ is simply treated as a parameter.  
For notational convenience, we will suppress explicit energy dependence of the moments.  
Employing Cartesian coordinates, we write the moment equations in $d$ spatial dimensions as
\begin{equation}
  \pd{\vect{\cM}}{t}+\sum_{i=1}^{d}\pderiv{}{x^{i}}\big(\,\vect{\cF}^{i}(\vect{\cM})\,\big)=\vect{\cC}(\vect{\cM}).  
  \label{eq:angularMomentsCartesian}
\end{equation}
We divide the spatial domain $D$ into a disjoint union $\cT$ of open elements $\bK$, so that $D = \cup_{\bK \in \cT}\bK$.  
We require that each element is a $d$-dimensional box in the logical coordinates; i.e.,
\begin{equation}
  \bK=\{\,\vect{x} : x^{i} \in K^{i} := (\xL^{i},\xH^{i}),~|~i=1,\ldots,d\,\}, 
\end{equation}
with surface elements denoted $\tilde{\bK}^{i}=\otimes_{j\ne i}K^{j}$.  
We let $|\bK|$ denote the volume of an element
\begin{equation}
  |\bK| = \int_{\bK}d\vect{x}, \quad\text{where}\quad d\vect{x} = \prod_{i=1}^{d}dx^{i}.  
\end{equation}
We also define the coordinates orthogonal to the $i$th dimension, $\tilde{\vect{x}}^{i}$, so that $\vect{x}=\{\tilde{\vect{x}}^{i},x^{i}\}$.  
The with of an element in the $i$th dimension is $|K^{i}|=\xH^{i}-\xL^{i}$.

We let the approximation space for the DG method, $\mathbb{V}^{k}$, to be constructed from the tensor product of one-dimensional polynomials of maximal degree $k$.  
Note that functions in $\mathbb{V}^{k}$ can be discontinuous across element interfaces.  
The semi-discrete DG problem is to find $\bcM_{h}\in\mathbb{V}^{k}$ (which approximates $\bcM$ in Eq.~\eqref{eq:angularMomentsCartesian}) such that
\begin{align}
  &\pd{}{t}\int_{\bK}\bcM_{h}\,v\,d\vect{x}
  +\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
  \big(\,
    \widehat{\bcF}^{i}(\bcM_{h})\,v\big|_{\xH^{i}}
    -\widehat{\bcF}^{i}(\bcM_{h})\,v\big|_{\xL^{i}}
  \,\big)\,d\tilde{\bx}^{i} \nonumber \\
  &\hspace{24pt}
  -\sum_{i=1}^{d}\int_{\bK}\bcF^{i}(\bcM_{h})\,\pderiv{v}{x^{i}}\,d\vect{x}
  =\int_{\bK}\bcC(\bcM_{h})\,v\,d\vect{x},
  \label{eq:semidiscreteDG}
\end{align}
for all $v\in\mathbb{V}^{k}$ and all $\bK\in\cT$.

In Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\bcF}^{i}(\bcM_{h})$ is a numerical flux, approximating the flux on the $i$th surface of $\bK$, and is evaluated with a flux function $\widehat{\mathfrak{F}}^{i}$ using the DG approximation from both sides of the element interface; i.e.,
\begin{equation}
  \widehat{\bcF}^{i}(\bcM_{h})\big|_{x^{i}}=\vect{\mathfrak{F}}^{i}(\bcM_{h}(x^{i,-},\tilde{\bx}^{i}),\bcM_{h}(x^{i,+},\tilde{\bx}^{i})),
\end{equation}
where superscripts $-/+$ in the arguments of $\bcM_{h}(x^{i,-/+},\tilde{\bx}^{i})$ indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
In this paper we use the simple Lax-Friedrichs (LF) flux given by
\begin{equation}
  \vect{\mathfrak{F}}_{\mbox{\tiny LF}}^{i}(\bcA,\bcB)
  =\f{1}{2}\,\big(\,\bcF^{i}(\bcA)+\bcF^{i}(\bcB)-\alpha^{i}\,(\,\bcA-\bcB\,)\,\big),
\end{equation}
where $\alpha^{i}=||\mbox{eig}\big(\partial\bcF^{i}/\partial\bcM\big)||_{\infty}$ is the largest eigenvalue of the flux Jacobian.  
For particles propagating at the speed of light, we can simply take $\alpha^{i}=1$ (i.e., the global LF flux).

For simplicity, we will approximate the opacities $\sigma_{\Ab}$ and $\sigma_{\Scatt}$ appearing in the collision term on the right-hand side of Eq.~\eqref{eq:angularMomentsCartesian} with constants in each element; i.e., $\sigma_{\Ab},\sigma_{\Scatt}\in\bbV^{0}$.

### 2018-01-25 Documents/M1/realizableFermionicM1/sections/imex.tex
Added some text on DG and IMEX methods

\section{Positivity-Preserving IMEX Schemes}
\label{sec:imex}

The semi-discretization of the moment equations with the DG method given in Eq.~\eqref{eq:semidiscreteDG} results in a system of ordinary differential equations (ODEs) in each element of the form
\begin{equation}
  \dot{\vect{u}}
  =\vect{\cT}(\vect{u})+\f{1}{\tau}\,\vect{\cQ}(\vect{u}),
\end{equation}
where $\vect{u}$ are the degrees of freedom evolved with the DG method (e.g., expansion coefficients resulting from a modal expansion).  
The transport term $\vect{\cT}$ is due to the second and third term in the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision term $\vect{\cQ}$ is due to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.

In the application of interest to us, the collision term is stiff ($\tau\ll1$) and must be treated with implicit methods, while we can resolve the time scales induced by the transport term, which we will treat with explicit methods; i.e., we will use IMEX methods \cite{pareschiRusso_2005}.  
Until recently, high-order (second or higher order temporal accuracy) positivity-preserving IMEX methods with time step restrictions solely due to the transport operator were not known.  
Chertock et al. \cite{chertock_etal_2015} presented second order accurate IMEX schemes with a correction step.  
The correction step includes the transport operator, and positivity is subject to a time step restriction that scales with $1/\sqrt{\tau}$.  
More recently, Hu et al. \cite{hu_etal_2017}, presented new IMEX schemes for a class of BGK-type collision operators with a correction step that does not include the transport operator.  
In this case, positivity is only subject to time step restrictions stemming from the transport operator.  
These IMEX schemes take the following form \cite{hu_etal_2017}
\begin{align}
  \vect{u}^{(i)}
  &=\vect{u}^{n}
  +\dt\sum_{i=1}^{j-1}\tilde{\alpha}_{ij}\,\vect{\cT}(\vect{u}^{(j)})
  +\dt\sum_{i=1}^{j}\alpha_{ij}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(j)}),
  \quad i=1,\ldots,s, \\
  \tilde{\vect{u}}^{n+1}
  &=\vect{u}^{n}
  +\dt\sum_{i=1}^{s}\tilde{w}_{i}\,\vect{\cT}(\vect{u}^{(i)})
  +\dt\sum_{i=1}^{s}w_{i}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}), \\
  \vect{u}^{n+1}
  &=\tilde{\vect{u}}^{n+1}-\alpha\,\dt^{2}\,\f{1}{\tau^{2}}\,\vect{\cQ}'(\vect{u}^{*})\,\vect{\cQ}(\vect{u}^{n+1}), 
\end{align}

### 2018-01-26 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added proof of Lemma 1 in 1-dimension.

@@
 \begin{proof}
-  Prove this
+  Since this lemma is independent from $\vect{z}$ and t, we can drop them from the expression for convenience.
+  Let's proof $0\le\cJ\le1$.
+
+  Since $f$ is positive, we have
+    \begin{equation}
+      \cJ=\f{1}{4\pi}\int_{\bbS^{2}}f(\omegaNu)\,d\omegaNu\ge0.
+    \end{equation}
+
+  Since $1-f$ is positive, we have
+    \begin{equation}
+      1-\cJ=\f{1}{4\pi}\int_{\bbS^{2}}(1-f(\omegaNu))\,d\omegaNu\ge0.
+    \end{equation}
+    Therefore, $0\le\cJ\le1$.
+
+    For $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$, we can proof it's valid with 1-dimension $\vect{\cH}$ first.
+    In 1-dimension, $\vect{\ell}(\omegaNu) = \omegaNu$ and
+    \begin{equation}
+    \vect{\cH}
+      =\f{1}{4\pi}\int_{\bbS^{2}}f(\omegaNu) \omegaNu d\omegaNu = \f{1}{2}\int_{-1}^{1}f(\omegaNu) \omegaNu d\omegaNu.
+    \end{equation}
+    Following Banach \& Larecki \cite{banachLarecki_2017}, we can rewrite it to be
+    \begin{align}
+    \vect{\cH}
+        &=(1-\cJ)\,\cJ \nonumber \\
+        &-\Big\{\,
+          \f{1}{2}\int_{-1}^{1-2\cJ}(1-2\cJ-\omegaNu)f(\omegaNu)\,d\omegaNu
+          +\f{1}{2}\int_{1-2\cJ}^{1}(2\cJ-1+\omegaNu)[1-f(\omegaNu)]\,d\omegaNu
+        \,\Big\}.
+        \label{eq:momentumRewrite1}
+    \end{align}
+    Since $(1-2\cJ-\omegaNu)f(\omegaNu)$ is positive when $-1\leq\omegaNu\leq1-2\cJ$ and $(2\cJ-1+\omegaNu)[1-f(\omegaNu)]$ is positive when $1-2\cJ\leq\omegaNu\leq1$,
+    \begin{align}
+    \vect{\cH} \leq (1-\cJ)\,\cJ.
+    \label{eq:HupBry1D}
+    \end{align}
+    Similarly, we can also rewrite $\vect{\cH}$ as
+    \begin{align}
+     \vect{\cH}
+        &=-(1-\cJ)\,\cJ \nonumber \\
+        &-\Big\{\,
+          \f{1}{2}\int_{-1}^{2\cJ-1}(1-2\cJ+\omegaNu)[1-f(\omegaNu)]\,d\omegaNu
+          +\f{1}{2}\int_{2\cJ-1}^{1}(2\cJ-1-\omegaNu)f(\omegaNu)\,d\omegaNu
+        \,\Big\}.
+        \label{eq:momentumRewrite2}
+    \end{align}
+    Since $(1-2\cJ+\omegaNu)[1-f(\omegaNu)]$ is negative when $-1\leq\omegaNu\leq2\cJ-1$ and $(2\cJ-1-\omegaNu)f(\omegaNu)$ is negative when $2\cJ-1\leq\omegaNu\leq1$,
+    \begin{align}
+    \vect{\cH} \geq -(1-\cJ)\,\cJ.
+     \label{eq:HlowBry1D}
+    \end{align}
+    Combining Eq.~\eqref{eq:HupBry1D} and ~\eqref{eq:HlowBry1D} gives $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$ in 1-dimension.
 \end{proof}

### 2018-01-26 Documents/M1/realizableFermionicM1/sections/realizability.tex
Finished the proof of Lemma 1.

@@
 \begin{proof}
-  Since this lemma is independent from $\vect{z}$ and t, we can drop them from the expression for convenience.
-  Let's proof $0\le\cJ\le1$.
+  Since this lemma is independent from $\vect{z}$ and t, we can drop $\vect{z}$ and t from the expressions for this proof.
+  Let's prove $0\le\cJ\le1$.
 
@@
 
-    For $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$, we can proof it's valid with 1-dimension $\vect{\cH}$ first.
+    For $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$, we can prove it's valid with 1-dimension $\vect{\cH}$ first.
     In 1-dimension, $\vect{\ell}(\omegaNu) = \omegaNu$ and
@@
     Combining Eq.~\eqref{eq:HupBry1D} and ~\eqref{eq:HlowBry1D} gives $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$ in 1-dimension.
+
+    To prove $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$ for 3-dimensional $\vect{\cH}$, let's introduce a unit vector $\bn$ with a arbitrary direction.
+    Then 
+    \begin{equation}
+    \vect{\cH} \cdot \bn = |\vect{\cH}| \cos\alpha,
+    \end{equation}
+    with $\alpha$ be the angle between $\vect{\cH}$ and $\bn$. 
+    We know that $-|\vect{\cH}|\leq\vect{\cH} \cdot \bn\leq|\vect{\cH}|$ since $-1\leq\cos\alpha\leq1$.
+    While given by definition,
+    \begin{align}
+    \vect{\cH} \cdot \bn & = \f{1}{4\pi}\int_{\bbS^{2}}f(\omegaNu)\ \bl(\omegaNu) d\omegaNu \cdot \bn \nonumber \\
+     &= \f{1}{4\pi}\int_{\bbS^{2}}f(\omegaNu)\ \bl(\omegaNu) \cdot \bn d\omegaNu \nonumber \\
+     &= \f{1}{4\pi}\int_{0}^{\pi}\int_{0}^{2\pi}f(\theta,\phi)\ \cos \theta \sin\theta d\theta d\phi
+    \end{align}
+    while $\theta$ is the angle between $\bl$ and $\bn$, and the coordinate are rotated so that the $\theta$ from $\omegaNu(\theta,\phi)$ is the same with the angle between $\bl$ and $\bn$.
+    Note the above expression can also be rewritten by changing variables as
+    \begin{align}
+    \vect{\cH} \cdot \bn & = \f{1}{2}\int_{0}^{\pi} \f{1}{2\pi}\int_{0}^{2\pi}f(\theta,\phi)\ d\phi \cdot \cos \theta \sin\theta d\theta  \\
+    & =  \f{1}{2}\int_{-1}^{1} \f{1}{2\pi}\int_{0}^{2\pi}f(\mu,\phi)\ d\phi \mu d\mu.
+    \end{align}
+    Besides,
+    \begin{align}
+    \cJ = \f{1}{4\pi}\int_{\bbS^{2}}f(\omegaNu)\,d\omegaNu = \f{1}{2}\int_{-1}^{1} \f{1}{2\pi}\int_{0}^{2\pi}f(\mu,\phi)\ d\phi d\mu.
+    \end{align}
+    If we define $f(\mu) =  \f{1}{2\pi}\int_{0}^{2\pi}f(\mu,\phi)\ d\phi$, then
+    \begin{align}
+    \cJ &= \f{1}{2}\int_{-1}^{1} f(\mu) d\mu, \\
+    \vect{\cH} \cdot \bn  &= \f{1}{2}\int_{-1}^{1} f(\mu) \mu d\mu.
+    \end{align}
+    We know $0\leq\,f(\mu)\leq1$.
+    Recall the proof we gave for 1-dimension $\vect{\cH}$, we have
+    \begin{equation}
+     \big(1-\cJ\big)\cJ-\vect{\cH} \cdot \bn\ge0.
+    \end{equation}
+    Note this inequality is valid for all the possible $\bn$ which includes the special case with $\cos\alpha=1$ and
+    \begin{equation}
+    \big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0.
+    \end{equation} 
 \end{proof}

### 2018-01-26 Documents/M1/realizableFermionicM1/sections/realizability.tex
Halfway on Lemma 2.

@@
     We know $0\leq\,f(\mu)\leq1$.
-    Recall the proof we gave for 1-dimension $\vect{\cH}$, we have
+    Recall the proof we gave for 1-dimensional $\vect{\cH}$, we have
     \begin{equation}
@@
 \begin{proof}
-  Prove this
+  A convex set $Q$ is a set has the following property: 
+  \begin{align}
+  \theta a + (1-\theta)b \in Q, \text{\space} \text{for } \forall a, b \in Q \text{ and } 0\leq\,\theta\,\leq1. 
+  \end{align} 
+  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements of $\cR$.
+  If $\cR$ is convex, we will have $\vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} = \theta \vect{\cM}_{a} + (1-\theta)\vect{\cM}_{b}$ in $\cR$ with $0\leq\theta\leq1$.
+  Let's prove it is true.
+
+  For the first component
+  \begin{align}
+  \cJ_{ab} = \theta \cJ_{a} + (1-\theta)\cJ_{b},
+  \end{align}
+  since $\theta$, $\cJ_{a}$, $1-\theta$ and $\cJ_{b}$ are all nonnegative, $\cJ_{ab}$ is also nonnegative ($\cJ_{ab}\geq0$).
+  Meanwhile, since $\cJ_{a}\leq1$ and $\cJ_{b}\leq1$, 
+  \begin{align}
+  \cJ_{ab} \leq \theta \cdot 1 + (1-\theta) \cdot 1 = 1.
+  \end{align}
+  Therefore, $\cJ_{ab} \in [0,1]$.
+
+  For the second component,
+  \begin{align}
+  \vect{\cH}_{ab} 
+  & = \theta \vect{\cH}_{a} + (1-\theta)\vect{\cH}_{b} \nonumber\\
+  & = \f{1}{4\pi}\int_{\bbS^{2}} \left[ \theta\,f_{a}(\omegaNu) + (1-\theta) f_{b}(\omegaNu) \right] \bl(\omegaNu) d\omegaNu. 
+  \end{align}
+  Since $\theta\,f_{a}(\omegaNu) + (1-\theta) f_{b}(\omegaNu) \in [0,1]$, we can define $\tilde{f} = \theta\,f_{a}(\omegaNu) + (1-\theta) f_{b}(\omegaNu)$.
+  $\tilde{f} \ in [0,1]$ and 
+  \begin{align}
+  \cJ_{ab} = \f{1}{4\pi}\int_{\bbS^{2}} \tilde{f} d\omegaNu \\
+  \vect{\cH}_{ab} = 
+  \end{align}
 \end{proof}

### 2018-01-26 Documents/M1/realizableFermionicM1/sections/dg.tex
modifications to Lemma 1.  Minor edits to DG discretization.

@@
 \end{equation}
-We divide the spatial domain $D$ into a disjoint union $\cT$ of open elements $\bK$, so that $D = \cup_{\bK \in \cT}\bK$.  
+We divide the spatial domain $D$ into a disjoint union $\mathscr{T}$ of open elements $\bK$, so that $D = \cup_{\bK \in \mathscr{T}}\bK$.  
 We require that each element is a $d$-dimensional box in the logical coordinates; i.e.,
@@
 
-We let the approximation space for the DG method, $\mathbb{V}^{k}$, to be constructed from the tensor product of one-dimensional polynomials of maximal degree $k$.  
+We let the approximation space for the DG method, $\mathbb{V}^{k}$, be constructed from the tensor product of one-dimensional polynomials of maximal degree $k$.  
 Note that functions in $\mathbb{V}^{k}$ can be discontinuous across element interfaces.  
@@
 \end{align}
-for all $v\in\mathbb{V}^{k}$ and all $\bK\in\cT$.
+for all $v\in\mathbb{V}^{k}$ and all $\bK\in\mathscr{T}$.
 
-In Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\bcF}^{i}(\bcM_{h})$ is a numerical flux, approximating the flux on the $i$th surface of $\bK$, and is evaluated with a flux function $\widehat{\mathfrak{F}}^{i}$ using the DG approximation from both sides of the element interface; i.e.,
+In Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\bcF}^{i}(\bcM_{h})$ is a numerical flux, approximating the flux on the surface of $\bK$ with unit normal along the $i$th coordinate direction, and is evaluated with a flux function $\vect{\mathscr{F}}^{i}$ using the DG approximation from both sides of the element interface; i.e.,
 \begin{equation}
-  \widehat{\bcF}^{i}(\bcM_{h})\big|_{x^{i}}=\vect{\mathfrak{F}}^{i}(\bcM_{h}(x^{i,-},\tilde{\bx}^{i}),\bcM_{h}(x^{i,+},\tilde{\bx}^{i})),
+  \widehat{\bcF}^{i}(\bcM_{h})\big|_{x^{i}}=\vect{\mathscr{F}}^{i}(\bcM_{h}(x^{i,-},\tilde{\bx}^{i}),\bcM_{h}(x^{i,+},\tilde{\bx}^{i})),
 \end{equation}
@@
 \begin{equation}
-  \vect{\mathfrak{F}}_{\mbox{\tiny LF}}^{i}(\bcA,\bcB)
+  \vect{\mathscr{F}}_{\mbox{\tiny LF}}^{i}(\bcA,\bcB)
   =\f{1}{2}\,\big(\,\bcF^{i}(\bcA)+\bcF^{i}(\bcB)-\alpha^{i}\,(\,\bcA-\bcB\,)\,\big),

### 2018-01-26 Documents/M1/realizableFermionicM1/sections/realizability.tex
modifications to Lemma 1.  Minor edits to DG discretization.

--- 2018-01-26 Documents/M1/realizableFermionicM1/sections/realizability.tex
@@
 
+Since we only consider the angular dependence of the distribution function in this section, we simplify the notation by suppressing the $\vect{z}$ and $t$ dependence, and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.
+
 \subsection{Moment Realizability}
@@
 \begin{define}
-  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they are consistent with a distribution function satisfying $0\le f \le 1$.
+  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they are consistent with a distribution function satisfying $0\le f(\omegaNu) \le 1$.
 \end{define}
+
+We begin by stating the bounds on the moments by restating results from Theorem~7.1 in \cite{banachLarecki_2017} in the following Lemma.  
 \begin{lemma}
-  Let the distribution function $f$ be bounded by $0\le f \le1$.  
-  Then $0\le\cJ\le1$ and $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$
+  Let the distribution function be bounded by $0\le f(\omegaNu) \le1$ for all $\omegaNu\in\bbS^{2}$.  
+  Then $0\le\cJ\le1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}|\ge0$.  
 \end{lemma}
 \begin{proof}
-  Since this lemma is independent from $\vect{z}$ and t, we can drop them from the expression for convenience.
-  Let's proof $0\le\cJ\le1$.
-
-  Since $f$ is positive, we have
+  First, let $\mu=\cos\thetaNu$ and write
   \begin{equation}
-      \cJ=\f{1}{4\pi}\int_{\bbS^{2}}f(\omegaNu)\,d\omegaNu\ge0.
+    \cJ=\f{1}{2}\int_{\bbS^{1}}\mathfrak{f}(\mu)\,d\mu,
+    \quad\text{where}\quad
+    \mathfrak{f}(\mu)=\f{1}{2\pi}\int_{0}^{2\pi}f(\mu,\phiNu)\,d\phiNu.  
   \end{equation}  
-
-  Since $1-f$ is positive, we have
+  Since $f(\omegaNu)\in[0,1]$, we have $\mathfrak{f}(\mu)\in[0,1]$, which implies $\cJ\in[0,1]$.  
+  Next we need to show that $|\vect{\cH}|\le(1-\cJ)\,\cJ$.  
+  Let $\widehat{\vect{n}}\in\bbR^{3}$ (independent of $\omegaNu$) be an arbitrary unit vector, and write
   \begin{equation}
-      1-\cJ=\f{1}{4\pi}\int_{\bbS^{2}}(1-f(\omegaNu))\,d\omegaNu\ge0.
+    \widehat{\vect{n}}\cdot\vect{\cH}
+    =\int_{\bbS^{1}}\mathfrak{f}(\mu)\,\mu\,d\mu,
+    \label{eq:NdotH}
   \end{equation}
-    Therefore, $0\le\cJ\le1$.
-
-    For $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$, we can proof it's valid with 1-dimension $\vect{\cH}$ first.
-    In 1-dimension, $\vect{\ell}(\omegaNu) = \omegaNu$ and
-    \begin{equation}
-    \vect{\cH}
-      =\f{1}{4\pi}\int_{\bbS^{2}}f(\omegaNu) \omegaNu d\omegaNu = \f{1}{2}\int_{-1}^{1}f(\omegaNu) \omegaNu d\omegaNu.
-    \end{equation}
-    Following Banach \& Larecki \cite{banachLarecki_2017}, we can rewrite it to be
-    \begin{align}
-    \vect{\cH}
-        &=(1-\cJ)\,\cJ \nonumber \\
-        &-\Big\{\,
-          \f{1}{2}\int_{-1}^{1-2\cJ}(1-2\cJ-\omegaNu)f(\omegaNu)\,d\omegaNu
-          +\f{1}{2}\int_{1-2\cJ}^{1}(2\cJ-1+\omegaNu)[1-f(\omegaNu)]\,d\omegaNu
-        \,\Big\}.
-        \label{eq:momentumRewrite1}
-    \end{align}
-    Since $(1-2\cJ-\omegaNu)f(\omegaNu)$ is positive when $-1\leq\omegaNu\leq1-2\cJ$ and $(2\cJ-1+\omegaNu)[1-f(\omegaNu)]$ is positive when $1-2\cJ\leq\omegaNu\leq1$,
-    \begin{align}
-    \vect{\cH} \leq (1-\cJ)\,\cJ.
-    \label{eq:HupBry1D}
-    \end{align}
-    Similarly, we can also rewrite $\vect{\cH}$ as
-    \begin{align}
-     \vect{\cH}
-        &=-(1-\cJ)\,\cJ \nonumber \\
-        &-\Big\{\,
-          \f{1}{2}\int_{-1}^{2\cJ-1}(1-2\cJ+\omegaNu)[1-f(\omegaNu)]\,d\omegaNu
-          +\f{1}{2}\int_{2\cJ-1}^{1}(2\cJ-1-\omegaNu)f(\omegaNu)\,d\omegaNu
-        \,\Big\}.
-        \label{eq:momentumRewrite2}
-    \end{align}
-    Since $(1-2\cJ+\omegaNu)[1-f(\omegaNu)]$ is negative when $-1\leq\omegaNu\leq2\cJ-1$ and $(2\cJ-1-\omegaNu)f(\omegaNu)$ is negative when $2\cJ-1\leq\omegaNu\leq1$,
-    \begin{align}
-    \vect{\cH} \geq -(1-\cJ)\,\cJ.
-     \label{eq:HlowBry1D}
-    \end{align}
-    Combining Eq.~\eqref{eq:HupBry1D} and ~\eqref{eq:HlowBry1D} gives $\big(1-\cJ\big)\cJ-|\vect{\cH}|\ge0$ in 1-dimension.
+  where we have aligned the polar axis of the spherical momentum space coordinate system with $\widehat{\vect{n}}$; i.e., $\widehat{\vect{n}}\cdot\vect{\ell}(\omega)=\mu$.  
+  First, following \cite{banachLarecki_2017}, we can write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
+  \begin{equation*}
+    (1-\cJ)\cJ - \f{1}{2}\int_{-1}^{1-2\cJ}(1-2\cJ-\mu)\,\mathfrak{f}(\mu)\,d\mu
+    -\f{1}{2}\int_{1-2\cJ}^{1}(2\cJ-1+\mu)\,[1-\mathfrak{f}(\mu)]\,d\mu.  
+  \end{equation*}
+  Since $\mathfrak{f}\in[0,1]$, $(1-2\cJ-\mu)$ is nonnegative on the interval $\mu\in[-1,1-2\cJ]$, and $(2\cJ-1+\mu)$ is nonnegative on the interval $\mu\in[1-2\cJ,1]$, we have $\widehat{\vect{n}}\cdot\vect{\cH}\le(1-\cJ)\,\cJ$.
+  In a similar manner, we can also write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
+  \begin{equation*}
+    -(1-\cJ)\cJ-\f{1}{2}\int_{-1}^{2\cJ-1}(1-2\cJ+\mu)\,[1-\mathfrak{f}(\mu)]\,d\mu
+    -\f{1}{2}\int_{2\cJ-1}^{1}(2\cJ-1-\mu)\,\mathfrak{f}(\mu)\,d\mu.  
+  \end{equation*}
+  Then, since $\mathfrak{f}\in[0,1]$, $(1-2\cJ+\mu)$ is nonpositive on the interval $\mu\in[-1,2\cJ-1]$, and $(2\cJ-1-\mu)$ is nonpositive on the interval $\mu\in[2\cJ-1,1]$, we have $\widehat{\vect{n}}\cdot\vect{\cH}\ge-(1-\cJ)\,\cJ$.
+  We therefore have $-(1-\cJ)\,\cJ\le\widehat{\vect{n}}\cdot\vect{\cH}\le(1-\cJ)\,\cJ$.  
+  Since this holds for any unit vector $\widehat{\vect{n}}\in\bbR^{3}$, we must have $|\vect{\cH}|\le(1-\cJ)\,\cJ$.  
 \end{proof}
@@
 \begin{equation}
-  \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in[0,1]~\text{and}~(1-\cJ)\cJ-|\vect{\cH}|\ge0\,\big\}
+  \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in[0,1]~\text{and}~\gamma(\vect{\cM})\equiv(1-\cJ)\cJ-|\vect{\cH}|\ge0\,\big\}
   \label{eq:realizableSet}

### 2018-01-27 Documents/M1/realizableFermionicM1/sections/realizability.tex
Some expressions for moment closures

@@
 
+Flux factor $h=|\vect{\cH}|/\cJ$
+\begin{equation}
+  \chi(\cJ,h)=\f{1}{3}+\f{2\,(1-\cJ)\,(1-2\cJ)}{3}\,\Theta\Big(\f{h}{1-\cJ}\Big)
+\end{equation}
+
 \subsubsection{Maximum Entropy Closure}
 Basic principles
-Chernohorsky \& Bludman
+Chernohorsky \& Bludman \cite{cernohorskyBludman_1994}
+\begin{equation}
+  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny CB}}(x)
+  =x^{2}\,\big(\,3-x+3\,x^{2}\,\big)
+\end{equation}
 Banach \& Larecki
+\begin{equation}
+  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny BL}}(x)
+  =\f{1}{8}\,\big(\,9\,x^{2}-5+\sqrt{33\,x^{4}-42\,x^{2}+25}\,\big)
+\end{equation}
 
@@
 Basic principles
-Banach \& Larecki
+Banach \& Larecki \cite{banachLarecki_2017}
+\begin{equation}
+  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
+\end{equation}
+
+\subsubsection{Low Occupancy Limit}

### 2018-01-28 Documents/M1/realizableFermionicM1/sections/realizability.tex
Proved Lemma 2.

@@
   A convex set $Q$ is a set has the following property: 
-  \begin{align}
-  \theta a + (1-\theta)b \in Q, \text{\space} \text{for } \forall a, b \in Q \text{ and } 0\leq\,\theta\,\leq1. 
-  \end{align} 
+  \begin{equation*}
+  \theta a + (1-\theta)b \in Q,~\text{for}~\forall a, b \in Q~\text{and}~0\leq\,\theta\,\leq1. 
+  \end{equation*} 
   Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements of $\cR$.
   If $\cR$ is convex, we will have $\vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} = \theta \vect{\cM}_{a} + (1-\theta)\vect{\cM}_{b}$ in $\cR$ with $0\leq\theta\leq1$.
-  Let's prove it is true.
-
-  For the first component
-  \begin{align}
-  \cJ_{ab} = \theta \cJ_{a} + (1-\theta)\cJ_{b},
-  \end{align}
-  since $\theta$, $\cJ_{a}$, $1-\theta$ and $\cJ_{b}$ are all nonnegative, $\cJ_{ab}$ is also nonnegative ($\cJ_{ab}\geq0$).
-  Meanwhile, since $\cJ_{a}\leq1$ and $\cJ_{b}\leq1$, 
-  \begin{align}
-  \cJ_{ab} \leq \theta \cdot 1 + (1-\theta) \cdot 1 = 1.
-  \end{align}
-  Therefore, $\cJ_{ab} \in [0,1]$.
-
-  For the second component,
-  \begin{align}
+  The first component of $\vect{\cM}_{ab}$ is
+  \begin{equation*}
+  \cJ_{ab} = \theta \cJ_{a} + (1-\theta)\cJ_{b}.
+  \end{equation*}
+  Since $\theta$, $\cJ_{a}$, $1-\theta$ and $\cJ_{b}$ are all nonnegative, $\cJ_{ab}$ is also nonnegative.
+  Meanwhile, since $\cJ_{a}\leq1$ and $\cJ_{b}\leq1$, $\cJ_{ab}\leq1$.
+  That's $\cJ_{ab} \in [0,1]$.
+  The second component is
+  \begin{equation*}
   \vect{\cH}_{ab} 
-  & = \theta \vect{\cH}_{a} + (1-\theta)\vect{\cH}_{b} \nonumber\\
-  & = \f{1}{4\pi}\int_{\bbS^{2}} \left[ \theta\,f_{a}(\omegaNu) + (1-\theta) f_{b}(\omegaNu) \right] \bl(\omegaNu) d\omegaNu. 
-  \end{align}
-  Since $\theta\,f_{a}(\omegaNu) + (1-\theta) f_{b}(\omegaNu) \in [0,1]$, we can define $\tilde{f} = \theta\,f_{a}(\omegaNu) + (1-\theta) f_{b}(\omegaNu)$.
-  $\tilde{f} \ in [0,1]$ and 
-  \begin{align}
-  \cJ_{ab} = \f{1}{4\pi}\int_{\bbS^{2}} \tilde{f} d\omegaNu \\
-  \vect{\cH}_{ab} = 
-  \end{align}
+  = \theta \vect{\cH}_{a} + (1-\theta)\vect{\cH}_{b}.
+  \end{equation*}
+  Using Jensen's inequality,
+  \begin{equation*}
+  \gamma(\vect{\cM_{ab}}) \leq \theta\gamma(\vect{\cM_{a}}) + (1-\theta)\gamma(\vect{\cM_{b}}) \leq 0.
+  \end{equation*}
 \end{proof}

### 2018-01-29 Documents/M1/realizableFermionicM1/sections/realizability.tex
Proved Lemma 3.

@@
   Then $0\le\cJ\le1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}|\ge0$. 
+  \label{lem: MomentRealizable} 
 \end{lemma}
@@
 \end{proof}
-
-Include figure to illustrate the convex set.
+The Fig.~\ref{fig:RealizableSetFermionic} illustrates how the convex realizable set $\cR$ looks like in $|\vect{\cH}| - \cJ$ coordinates.  
+\begin{figure}
+\centering
+\includegraphics[width=0.7\linewidth]{figures/RealizableSetFermionic}
+\caption[Numerical plot of the convex realizable set $\cR$.]{
+Numerical plot of the convex realizable set $\cR$.
+The blue line are the boundary given by $\gamma(\vect{\cM}) = 0$.
+The red line are the boundary given by $|\vect{\cH}| = \cJ$.
+Every black dot represents a sample whose distribution function $\mathfrak{f}(\mu)$ is an arbitrary Fermi-Dirac function.
+Total 1000,000 $\mathfrak{f}(\mu)$ were sampled for this diagram.}
+\label{fig:RealizableSetFermionic}
+\end{figure}
 
@@
 \begin{proof}
-  Prove this.
+  The first component of $\Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})$ is
+  \begin{equation*} 
+    \f{1}{2}\big(\vect{\cJ_{a}} + \widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cJ_{a}})+\vect{\cJ_{b}} - \widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cJ_{b}})\big) = \f{1}{2}\big(\vect{\cJ_{a}} + \widehat{\vect{e}}\cdot\vect{\cH_{a}}+\vect{\cJ_{b}} - \widehat{\vect{e}}\cdot\vect{\cH_{b}}\big).
+  \end{equation*}
+  Using the same treatment we made in proof of Lemma~\ref{lem: MomentRealizable}, we can rewrite the first component as
+  \begin{align*}
+  &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right] \,d\mu \right\rbrace \\
+  \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,d\mu \\
+  \text{where}&~\mathfrak{f}_{ab}(\mu) \equiv \f{1}{2}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right].
+  \end{align*}
+  We know that $\f{1}{2}(1\pm\mu)\in[0,1]$, $\mathfrak{f}_{a}(\mu)\in[0,1]$ and $\mathfrak{f}_{b}(\mu)\in[0,1]$, therefore $\mathfrak{f}_{ab}(\mu)\in[0,1]$ and the first component is also in $[0,1]$.
+  The second component
+  \begin{equation*} 
+    \f{1}{2}\big(\vect{\cH_{a}} + \widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cH_{a}})+\vect{\cH_{b}} - \widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cH_{b}})\big) = \f{1}{2}\big(\vect{\cH_{a}} + \widehat{\vect{e}}\cdot\vect{\cK_{a}}+\vect{\cH_{b}} - \widehat{\vect{e}}\cdot\vect{\cK_{b}}\big)
+  \end{equation*}  
+  has three subcomponents and each of them can also be rewritten as
+  \begin{align*}
+    \f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]\mu \,d\mu \right\rbrace
+     \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,\mu d\mu. 
+  \end{align*}
+  Therefore, using Lemma~\ref{lem: MomentRealizable} we know that $\Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR$.
 \end{proof}

### 2018-01-29 Documents/M1/realizableFermionicM1/figures/ConvexSetGenerator.m

@@ -43,7 +43,7 @@ for iPt = 1 : nPts
 end
 toc
 
-clf
+fig = figure;
 plot( H_FD, J_FD, '.k', 'MarkerSize', 6 );hold on
 yy = linspace(0.0,1.0,1024)';
 xxP_FD = + yy.*(1.0-yy);
@@ -56,6 +56,7 @@ plot( xxP_FD, yy, '-b', 'linewidth', 3 )
 plot( xxM_FD, yy, '-b', 'linewidth', 3 )
 hold off
 axis([-0.5 0.5 0.0 1.0]);
-xlabel('Angular Moment H');
+xlabel('Angular Moment |H|');
 ylabel('Angular Moment J');
 title('Realizble Set R');
+saveas(fig,'RealizableSetFermionic.png');

### 2018-01-29 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added title for the plot of the realizable set R.

@@
 \end{proof}
+
 The Fig.~\ref{fig:RealizableSetFermionic} illustrates how the convex realizable set $\cR$ looks like in $|\vect{\cH}| - \cJ$ coordinates.  
@@
 \caption[Numerical plot of the convex realizable set $\cR$.]{
-Numerical plot of the convex realizable set $\cR$.
+A numerical plot of the convex realizable set $\cR$.
 The blue line are the boundary given by $\gamma(\vect{\cM}) = 0$. 
 The red line are the boundary given by $|\vect{\cH}| = \cJ$.
-Every black dot represents a sample whose distribution function $\mathfrak{f}(\mu)$ is an arbitrary Fermi-Dirac function.
-Total 1000,000 $\mathfrak{f}(\mu)$ were sampled for this diagram.}
+Every black dot represents a sample whose distribution function $\mathfrak{f}(\mu)$ is an arbitrary Fermi-Dirac function and its angular moments were given by integrals using Trapezoid rule.
+Total 1000,000 $\mathfrak{f}(\mu)$ were sampled for making this plot.}
 \label{fig:RealizableSetFermionic}

### 2018-01-29 Documents/M1/realizableFermionicM1/sections/realizability.tex
Modified the plot of convex set R.

@@
   That's $\cJ_{ab} \in [0,1]$.
-  The second component is
+  Since the second derivative of $\gamma(\vect{\cM})$ is $-2$ which is always negative, $\gamma(\vect{\cM})$ is a concave function.
+  Using Jensen's inequality, we have
   \begin{equation*}
-  \vect{\cH}_{ab} 
-  = \theta \vect{\cH}_{a} + (1-\theta)\vect{\cH}_{b}.
-  \end{equation*}
-  Using Jensen's inequality,
-  \begin{equation*}
-  \gamma(\vect{\cM_{ab}}) \leq \theta\gamma(\vect{\cM_{a}}) + (1-\theta)\gamma(\vect{\cM_{b}}) \leq 0.
+  \gamma(\vect{\cM_{ab}}) \geq \theta\gamma(\vect{\cM_{a}}) + (1-\theta)\gamma(\vect{\cM_{b}}) \ge0.
   \end{equation*}
@@
 The Fig.~\ref{fig:RealizableSetFermionic} illustrates how the convex realizable set $\cR$ looks like in $|\vect{\cH}| - \cJ$ coordinates.
+Total 1000,000 distribution functions having form $\mathfrak{f}(\mu;a,b) = \dfrac{1}{e^{a+b\mu}+1}$ were evaluated.
+The parameters, $a$ and $b$, were chosen from $[-100,100]$ independently.
+The variable $\mu$ ranges from $-1$ to $1$ with $d\mu=\f{1}{128}$.
+And the integrals in angular moment expressions are calculated using Trapezoid rule.
 \begin{figure}
 \centering
-\includegraphics[width=0.7\linewidth]{figures/RealizableSetFermionic}
+\includegraphics[width=1.0\linewidth]{figures/RealizableSetFermionic}
 \caption[Numerical plot of the convex realizable set $\cR$.]{
 A numerical plot of the convex realizable set $\cR$.
-The blue line are the boundary given by $\gamma(\vect{\cM}) = 0$. 
+The black line are the boundary given by $\gamma(\vect{\cM}) = 0$. 
 The red line are the boundary given by $|\vect{\cH}| = \cJ$.
-Every black dot represents a sample whose distribution function $\mathfrak{f}(\mu)$ is an arbitrary Fermi-Dirac function and its angular moments were given by integrals using Trapezoid rule.
+Every light-blue dot represents a sample whose distribution function $\mathfrak{f}(\mu)$ is an arbitrary Fermi-Dirac function and its angular moments were given by integrals using Trapezoid rule.
 Total 1000,000 $\mathfrak{f}(\mu)$ were sampled for making this plot.}

### 2018-01-29 Documents/M1/realizableFermionicM1/sections/realizability.tex
Modified the proof of Lemma 3.

@@
   Similarly, $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments of a distribution function $f_{b}\in[0,1]$.  
-  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector.  
+  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector and $\vect{\cF}(\vect{\cM})=\big(\vect{\cH},\vect{\cK}\big)^{T}$.
   Then
   \begin{equation}
-    \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
+    \vect{\cM}_{ab} \equiv \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
   \end{equation}
@@
 \begin{proof}
-  The first component of $\Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})$ is
-  \begin{equation*} 
-    \f{1}{2}\big(\vect{\cJ_{a}} + \widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cJ_{a}})+\vect{\cJ_{b}} - \widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cJ_{b}})\big) = \f{1}{2}\big(\vect{\cJ_{a}} + \widehat{\vect{e}}\cdot\vect{\cH_{a}}+\vect{\cJ_{b}} - \widehat{\vect{e}}\cdot\vect{\cH_{b}}\big).
-  \end{equation*}
-  Using the same treatment we made in proof of Lemma~\ref{lem: MomentRealizable}, we can rewrite the first component as
+  Using the same treatment we made in proof of Lemma~\ref{lem: MomentRealizable}, we can rewrite the first component of $\vect{\cM}_{ab}$ as
   \begin{align*}
-  &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right] \,d\mu \right\rbrace \\
-  \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,d\mu \\
-  \text{where}&~\mathfrak{f}_{ab}(\mu) \equiv \f{1}{2}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right].
+  \f{1}{2}\big(\vect{\cJ_{a}} + \widehat{\vect{e}}\cdot\vect{\cH_{a}}+\vect{\cJ_{b}} - \widehat{\vect{e}}\cdot\vect{\cH_{b}}\big) = &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right] \,d\mu \right\rbrace \\
+  \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,d\mu
   \end{align*}
-  We know that $\f{1}{2}(1\pm\mu)\in[0,1]$, $\mathfrak{f}_{a}(\mu)\in[0,1]$ and $\mathfrak{f}_{b}(\mu)\in[0,1]$, therefore $\mathfrak{f}_{ab}(\mu)\in[0,1]$ and the first component is also in $[0,1]$.
-  The second component
-  \begin{equation*} 
-    \f{1}{2}\big(\vect{\cH_{a}} + \widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cH_{a}})+\vect{\cH_{b}} - \widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cH_{b}})\big) = \f{1}{2}\big(\vect{\cH_{a}} + \widehat{\vect{e}}\cdot\vect{\cK_{a}}+\vect{\cH_{b}} - \widehat{\vect{e}}\cdot\vect{\cK_{b}}\big)
-  \end{equation*}  
-  has three subcomponents and each of them can also be rewritten as
+  where $\mathfrak{f}_{ab}(\mu) \equiv \f{1}{2}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]$ and $\mathfrak{f}_{ab}(\mu)\in[0,1]$.
+  And the second component is
   \begin{align*} 
-    \f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]\mu \,d\mu \right\rbrace
+   \f{1}{2}\big(\vect{\cH_{a}} + \widehat{\vect{e}}\cdot\vect{\cK_{a}}+\vect{\cH_{b}} - \widehat{\vect{e}}\cdot\vect{\cK_{b}}\big) =
+   &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]\mu \,d\mu \right\rbrace \\
    \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,\mu d\mu. 
   \end{align*}
-  Therefore, using Lemma~\ref{lem: MomentRealizable} we know that $\Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR$.
+  Applying Lemma~\ref{lem: MomentRealizable}, we know that $\vect{\cM}_{ab}\in\cR$.
 \end{proof}

### 2018-01-31 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added the plots of Mab.

@@
   \end{align*}
-  Applying Lemma~\ref{lem: MomentRealizable}, we know that $\vect{\cM}_{ab}\in\cR$.
+  Using Lemma~\ref{lem: MomentRealizable}, we know that $\vect{\cM}_{ab}\in\cR$ and can be written as $\vect{\cM}_{ab}(\cJ_{ab},\vect{\cH}_{ab})$.
 \end{proof}
@@
 \subsubsection{Low Occupancy Limit}
+
+\begin{figure}[h!]
+  \begin{subfigure}[b]{0.5\textwidth}
+    \includegraphics[width=\textwidth]{figures/MabWithMI}
+    \caption{$\vect{\cM}_{ab}$ with Minerbo closure.}
+  \end{subfigure}
+  %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \includegraphics[width=\textwidth]{figures/MabWithBLKS}
+    \caption{$\vect{\cM}_{ab}$ with Kershaw closure.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.5\textwidth}
+    \includegraphics[width=\textwidth]{figures/MabWithCBME}
+    \caption{$\vect{\cM}_{ab}$ with Chernohorsky \& Bludman maximum entropy closure.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.5\textwidth}
+    \includegraphics[width=\textwidth]{figures/MabWithBLME}
+    \caption{$\vect{\cM}_{ab}$ with Banach \& Larecki maximum entropy closure.}
+  \end{subfigure}
+  \label{fig:MabWithDifferentClosure}
+\end{figure}

### 2018-02-01 Documents/M1/realizableFermionicM1/sections/model.tex
Added some text on DG and IMEX methods
Reworked the model section

@@
 
-In this paper, we consider approximate solutions to the Boltzmann equation for radiation transport in slab geometry
+In this paper we consider approximate solutions to the Boltzmann equation for radiation transport in slab geometry, which after scaling to dimensionless units can be written as
 \begin{equation}
   \pd{f}{t}+\vect{\ell}\cdot\nabla f
-  =\sigma_{\Ab}\,\big(\,f_{0}-f\,\big)
-  +\sigma_{\Scatt}\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omegaNu-f\,\big),
+  =\f{1}{\tau}\,\cC(f),
   \label{eq:boltzmann}
 \end{equation}
-where the distribution function $f(\omegaNu,\epsilonNu,\vect{x},t):\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in direction $\omegaNu\in\bbS^{2}:=\{\,\omegaNu=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\epsilonNu\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
-Thus, we use spherical momentum space coordinates $(\omegaNu,\epsilonNu)$.  
+where the distribution function $f(\omegaNu,\epsilonNu,\vect{x},t):\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in direction $\omegaNu\in\bbS^{2}:=\{\,\omegaNu=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\epsilonNu\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$; i.e., we use spherical momentum space coordinates $(\omegaNu,\epsilonNu)$.
 We also define the energy-position coordinates $\vect{z}:=\{\epsilonNu,\vect{x}\}\in\bbR^{+}\times\bbR^{3}$.  
 The unit vector $\vect{\ell}(\omegaNu)\in\bbR^{3}$ (independent of $\vect{z}$) is parallel to the particle three-momentum.  
-On the right-hand side of Eq.~\eqref{eq:boltzmann}, $\sigma_{\Ab}(\vect{z})\ge0$ and $\sigma_{\Scatt}(\vect{z})\ge0$ are the absorption and scattering opacities due to interactions with a background, respectively, and $f_{0}(\vect{z})$ is the equilibrium distribution distribution function.
+On the right-hand side of Eq.~\eqref{eq:boltzmann}, $\tau$ is the ratio of the particle mean-free path (due to interactions with a background) to some characteristic length scale of the problem; in opaque regions, $\tau\ll1$, while for free streaming radiation, $\tau\gg1$.
+The collision term is given by
+\begin{equation}
+  \cC(f)=\xi\,\big(\,f_{0}-f\,\big)
+  +(1-\xi)\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omegaNu-f\,\big),
+  \label{eq:collisionTerm}
+\end{equation}
+where $\xi\in[0,1]$ is the ratio of the absorption opacity $\sigma_{\Ab}\,(\ge0)$ to the total opacity $\sigma_{\Tot}=\sigma_{\Ab}+\sigma_{\Scatt}$, and $\sigma_{\Scatt}\,(\ge0)$ is the scattering opacity.
+Then, $\xi=1$ models pure emission and absorption, while $\xi=0$ models pure scattering.  
+In general, $\sigma_{\Ab}(\vect{z})$ and $\sigma_{\Scatt}$ (and $\tau$ and $\xi$) depend on $\vect{z}$.  
+The equilibrium distribution function is denoted $f_{0}(\vect{z})$.  
 Here, we consider transport of Fermions (e.g., neutrinos), so that the equilibrium distribution function takes the form
@@
 \end{equation}
-where $\cJ$ (zeroth moment) is the density, $\vect{\cH}$ (first moment) the flux, and $\vect{\cK}$ (second moment) is the stress tensor.  
-Note that the moments defined in Eq.~\ref{eq:angularMoments} are \emph{spectral moments} (depending on the energy $\epsilonNu$).  
-The \emph{grey moments} are obtained by integration over energy
+where we will refer to $\cJ$ (zeroth moment) as the particle density, $\vect{\cH}$ (first moment) as the particle flux, and $\vect{\cK}$ (second moment) as the stress tensor.  
+Note that the moments defined in Eq.~\eqref{eq:angularMoments} are \emph{spectral moments} (depending on energy, position, and time).  
+The \emph{grey moments} (depending only on position and time) are obtained by integration over energy as
 \begin{equation}
@@
 \begin{equation}
-  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}(\vect{\cM})=\vect{\cC}(\vect{\cM}),
+  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}(\vect{\cM})=\f{1}{\tau}\,\vect{\cC}(\vect{\cM}),
   \label{eq:momentEquations}
 \end{equation}
-where $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, the components of the flux vector $\vect{\cF}$ are $\vect{\cF}^{i}=\vect{e}_{i}\cdot\vect{\cF}=(\vect{e}_{i}\cdot\vect{\cH},\vect{e}_{i}\cdot\vect{\cK})^{T}$, where $\vect{e}_{i}$ is the unit vector in the $i$th coordinate direction, and $\vect{\cC}=\vect{\cQ}-\vect{\cD}\,\vect{\cM}$.
-Here we have also defined $\vect{\cQ}=(\sigma_{\Ab}\cJ_{0},\vect{0})^{T}$, where $\cJ_{0}=f_{0}$, and $\vect{\cD}=\mbox{diag}(\sigma_{\Ab},\vect{I}\sigma_{\Tot})$, where $\sigma_{\Tot}=\sigma_{\Ab}+\sigma_{\Scatt}$, and $\vect{I}$ is the identity matrix.
-In order to close the system of equations, the stress tensor $\vect{\cK}$ must be related to the lower moments by a closure procedure.  
+where $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, the components of the flux vector $\vect{\cF}$ are $\vect{\cF}^{i}=\vect{e}_{i}\cdot\vect{\cF}=(\vect{e}_{i}\cdot\vect{\cH},\vect{e}_{i}\cdot\vect{\cK})^{T}$, where $\vect{e}_{i}$ is the unit vector in the $i$th coordinate direction.
+On the right-hand side of Eq.~\eqref{eq:momentEquations}, the collision term becomes
+\begin{equation}
+  \vect{\cC}(\vect{\cM})=\vect{\eta}-\vect{\cD}\,\vect{\cM}, 
+  \label{eq:collisionTermMoments}
+\end{equation}
+where we have defined $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$ and $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$, where $\vect{I}$ is the identity matrix.  
+In order to close the system of equations, the components of the stress tensor $\vect{\cK}$ must be related to the lower moments through a closure procedure.  
 To this end, Levermore \cite{levermore_1984} defines the Eddington tensor $\vect{k}=\vect{\cK}/\cJ$, assumes that the radiation field is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, and writes
@@
 where $\chi=\chi(\cJ,|\vect{\cH}|)$ is the Eddington factor.  
+The two-moment model is then closed once the Eddington factor is determined from $\cJ$ and $\vect{\cH}$.  
 We will return to the issue of determining the Eddington factor in Section~\ref{sec:realizability}.

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Reworked the model section
Reworking of section 3: realizability

--- 2018-01-29 Documents/M1/realizableFermionicM1/sections/realizability.tex
@@
-\section{Moment Realizability and Closures for Fermion}
+\section{Moment Realizability and Algebraic Closures for the Fermionic Two-Moment Model}
 \label{sec:realizability}
 
-Our goal is to design a numerical method for solving the system of equations given by Eq.~\eqref{eq:momentEquations}, which approximates Eq.~\eqref{eq:boltzmann}.  
-To this end, we want to obtain solutions that preserve features of the original problem.
-
-Since we only consider the angular dependence of the distribution function in this section, we simplify the notation by suppressing the $\vect{z}$ and $t$ dependence, and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.
+Our goal is to simulate a gas of massless fermions (i.e., classical neutrinos) and study their interactions with matter.  
+The principal objective is to obtain the fermionic distribution function $f$ (or moments of $f$ as in the two-moment model employed here).  
+The Pauli exclusion principle requires the distribution function to satisfy the condition $0 \le f \le 1$, which puts restrictions on the admissible values for the moments of $f$.  
+In this paper, we seek to design a numerical method for solving the system of moment equations given by Eq.~\eqref{eq:momentEquations}, which preserves realizability of the moments; i.e., the moments evolve within the set of admissible values as dictated by Pauli's exclusion principle.
+(Since are concerned with the angular dependence of $f$ in this section, we simplify notation by suppressing the $\vect{z}$ and $t$ dependence and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.)
 
@@
 
+We begin with the following definition of moment realizability.  
 \begin{define}
-  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they are consistent with a distribution function satisfying $0\le f(\omegaNu) \le 1$.
+  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they can be obtained from a distribution function satisfying $0\le f(\omegaNu) \le 1~\forall~\omegaNu\in\bbS^{2}$.
 \end{define}
 
-We begin by stating the bounds on the moments by restating results from Theorem~7.1 in \cite{banachLarecki_2017} in the following Lemma.  
+Obviously, realizable moments must satisfy the bounds imposed by $f$.  
+We proceed by stating the bounds on the moments by restating (with slightly modified proof) results from Theorem~7.1 in \cite{banachLarecki_2017} in the following Lemma.  
 \begin{lemma}
-  Let the distribution function be bounded by $0\le f(\omegaNu) \le1$ for all $\omegaNu\in\bbS^{2}$.  
-  Then $0\le\cJ\le1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}|\ge0$. 
-  \label{lem: MomentRealizable} 
+  Let the distribution function be bounded by $0\le f(\omegaNu) \le1~\forall~\omegaNu\in\bbS^{2}$.  
+  Then the moments $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, defined as in Eq.~\eqref{eq:angularMoments}, satisfy $0\le\cJ\le1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}|\ge0$. 
+  \label{lem:MomentRealizable} 
 \end{lemma}
 \begin{proof}
-  First, let $\mu=\cos\thetaNu$ and write
+  First, let $\mu=\cos\thetaNu$ and $\bbS^{1}:=\{\,\mu\,|\,\mu\in[-1,1]\,\}$, and write
   \begin{equation}
@@
 \begin{proof}
-  A convex set $Q$ is a set has the following property: 
-  \begin{equation*}
-  \theta a + (1-\theta)b \in Q,~\text{for}~\forall a, b \in Q~\text{and}~0\leq\,\theta\,\leq1. 
-  \end{equation*} 
-  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements of $\cR$.
-  If $\cR$ is convex, we will have $\vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} = \theta \vect{\cM}_{a} + (1-\theta)\vect{\cM}_{b}$ in $\cR$ with $0\leq\theta\leq1$.
+  In order to prove that $\cR$ is convex, we must show that a convex combination of elements in $\cR$ also belongs to $\cR$.  
+  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements in $\cR$.  
+  Let $\vect{\cM}_{ab} = \theta\,\vect{\cM}_{a} + (1-\theta)\,\vect{\cM}_{b}$, with $0\leq\theta\leq1$.
   The first component of $\vect{\cM}_{ab}$ is
   \begin{equation*}
-  \cJ_{ab} = \theta \cJ_{a} + (1-\theta)\cJ_{b}.
+    \cJ_{ab} = \theta\,\cJ_{a} + (1-\theta)\,\cJ_{b}.
   \end{equation*}
-  Since $\theta$, $\cJ_{a}$, $1-\theta$ and $\cJ_{b}$ are all nonnegative, $\cJ_{ab}$ is also nonnegative.
-  Meanwhile, since $\cJ_{a}\leq1$ and $\cJ_{b}\leq1$, $\cJ_{ab}\leq1$.
-  That's $\cJ_{ab} \in [0,1]$.
-  Since the second derivative of $\gamma(\vect{\cM})$ is $-2$ which is always negative, $\gamma(\vect{\cM})$ is a concave function.
-  Using Jensen's inequality, we have
+  Since $\theta,\cJ_{a},\cJ_{b}\in[0,1]$, we have $\cJ_{ab} \in [0,1]$.  
+  It is straightforward to verify that $\gamma(\vect{\cM})$ is a concave function of $\bcM$ if $\cJ\in[0,1]$.
+  Jensen's inequality implies
   \begin{equation*}
-  \gamma(\vect{\cM_{ab}}) \geq \theta\gamma(\vect{\cM_{a}}) + (1-\theta)\gamma(\vect{\cM_{b}}) \ge0.
+  \gamma(\vect{\cM}_{ab}) \geq \theta\,\gamma(\vect{\cM}_{a}) + (1-\theta)\,\gamma(\vect{\cM}_{b}) \ge0.
   \end{equation*}
@@
 
-The Fig.~\ref{fig:RealizableSetFermionic} illustrates how the convex realizable set $\cR$ looks like in $|\vect{\cH}| - \cJ$ coordinates.
-Total 1000,000 distribution functions having form $\mathfrak{f}(\mu;a,b) = \dfrac{1}{e^{a+b\mu}+1}$ were evaluated.
-The parameters, $a$ and $b$, were chosen from $[-100,100]$ independently.
-The variable $\mu$ ranges from $-1$ to $1$ with $d\mu=\f{1}{128}$.
-And the integrals in angular moment expressions are calculated using Trapezoid rule.
+Figure~\ref{fig:RealizableSetFermionic} illustrates the geometry of the convex set $\cR$ in $|\vect{\cH}| - \cJ$ coordinates (light blue region).
+To make this plot, a total of $10^{6}$ distribution functions of the form $\mathfrak{f}(\mu;a,b) = \dfrac{1}{e^{a+b\mu}+1}$ ($\mu\in[-1,1]$) were generated, where the parameters $a$ and $b$ were chosen randomly and independently in the range $a,b\in[-10^{2},10^{2}]$.
+A uniform $\mu$-grid with $\Delta\mu=1/128$, was used to represent the distribution functions, and the angular moments were calculated using the trapezoid rule.  
 \begin{figure}
@@
   \includegraphics[width=1.0\linewidth]{figures/RealizableSetFermionic}
-\caption[Numerical plot of the convex realizable set $\cR$.]{
-A numerical plot of the convex realizable set $\cR$.
-The black line are the boundary given by $\gamma(\vect{\cM}) = 0$. 
-The red line are the boundary given by $|\vect{\cH}| = \cJ$.
-Every light-blue dot represents a sample whose distribution function $\mathfrak{f}(\mu)$ is an arbitrary Fermi-Dirac function and its angular moments were given by integrals using Trapezoid rule.
-Total 1000,000 $\mathfrak{f}(\mu)$ were sampled for making this plot.}
+  \caption{Illustration of the realizable set $\cR$ defined in Eq.~\eqref{eq:realizableSet}.  
+  Each of the $10^{6}$ light-blue points in the figure represents a set of moments $\vect{\cM}=(\cJ,\vect{\cH})$, computed from a random Fermi-Dirac distribution (see text for details).  
+  Black lines define the boundary of $\cR$; $\gamma(\vect{\cM}) = 0$.}
   \label{fig:RealizableSetFermionic}
@@
 
+For the realizability-preserving scheme, we state some additional results.  
 \begin{lemma}
-  Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ be defined as in Eq.~\eqref{eq:angularMoments} with distribution function $f_{a}\in[0,1]$.  
-  Similarly, $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments of a distribution function $f_{b}\in[0,1]$.  
-  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector and $\vect{\cF}(\vect{\cM})=\big(\vect{\cH},\vect{\cK}\big)^{T}$.
+  Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ be defined as in Eq.~\eqref{eq:angularMoments} with distribution function $f_{a}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$.  
+  Similarly, let $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments of a distribution function $f_{b}\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$.  
+  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector, and $\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})=\big(\widehat{\vect{e}}\cdot\vect{\cH},\widehat{\vect{e}}\cdot\vect{\cK}\big)^{T}$.
   Then
-  \begin{equation}
-    \vect{\cM}_{ab} \equiv \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
-  \end{equation}
+  \begin{equation*}
+    \vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} \equiv \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
+  \end{equation*}
 \end{lemma}
 \begin{proof}
-  Using the same treatment we made in proof of Lemma~\ref{lem: MomentRealizable}, we can rewrite the first component of $\vect{\cM}_{ab}$ as
-  \begin{align*}
-  \f{1}{2}\big(\vect{\cJ_{a}} + \widehat{\vect{e}}\cdot\vect{\cH_{a}}+\vect{\cJ_{b}} - \widehat{\vect{e}}\cdot\vect{\cH_{b}}\big) = &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right] \,d\mu \right\rbrace \\
-  \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,d\mu
-  \end{align*}
-  where $\mathfrak{f}_{ab}(\mu) \equiv \f{1}{2}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]$ and $\mathfrak{f}_{ab}(\mu)\in[0,1]$.
-  And the second component is
-  \begin{align*} 
-   \f{1}{2}\big(\vect{\cH_{a}} + \widehat{\vect{e}}\cdot\vect{\cK_{a}}+\vect{\cH_{b}} - \widehat{\vect{e}}\cdot\vect{\cK_{b}}\big) =
-   &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]\mu \,d\mu \right\rbrace \\
-   \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,\mu d\mu. 
-  \end{align*}
-  Applying Lemma~\ref{lem: MomentRealizable}, we know that $\vect{\cM}_{ab}\in\cR$.
+  It is straightforward to rewrite the components of $\vect{\cM}_{ab}$ as
+  \begin{equation*}
+    \cJ_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omegaNu)\,d\omegaNu
+    \quad\text{and}\quad
+    \vect{\cH}_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omegaNu)\,\vect{\ell}(\omegaNu)\,d\omegaNu,
+  \end{equation*}
+  where $f_{ab}(\omegaNu)=\theta\,f_{a}+(1-\theta)\,f_{b}$ and $\theta(\omegaNu)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omegaNu))/2\in[0,1]$.  
+  Then, since $f_{ab}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
 \end{proof}
 
-\subsection{Moment Closures}
+\subsection{Algebraic Moment Closures}
 
@@
 \subsubsection{Low Occupancy Limit}
+
+\begin{figure}
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{figures/MabWithBLME}
+    \includegraphics[width=0.5\textwidth]{figures/MabWithCBME} \\
+    \includegraphics[width=0.5\textwidth]{figures/MabWithBLKS}
+    \includegraphics[width=0.5\textwidth]{figures/MabWithMI}
+  \end{tabular}
+  \caption{}
+  \label{fig:MabWithDifferentClosure}
+\end{figure}
+
+%\begin{figure}[h!]
+%  \begin{subfigure}[b]{0.5\textwidth}
+%    \includegraphics[width=\textwidth]{figures/MabWithMI}
+%    \caption{$\vect{\cM}_{ab}$ with Minerbo closure.}
+%  \end{subfigure}
+%  %
+%  \begin{subfigure}[b]{0.5\textwidth}
+%    \includegraphics[width=\textwidth]{figures/MabWithBLKS}
+%    \caption{$\vect{\cM}_{ab}$ with Kershaw closure.}
+%  \end{subfigure}
+%  \begin{subfigure}[b]{0.5\textwidth}
+%    \includegraphics[width=\textwidth]{figures/MabWithCBME}
+%    \caption{$\vect{\cM}_{ab}$ with Chernohorsky \& Bludman maximum entropy closure.}
+%  \end{subfigure}
+%  \begin{subfigure}[b]{0.5\textwidth}
+%    \includegraphics[width=\textwidth]{figures/MabWithBLME}
+%    \caption{$\vect{\cM}_{ab}$ with Banach \& Larecki maximum entropy closure.}
+%  \end{subfigure}
+%  \label{fig:MabWithDifferentClosure}
+%\end{figure}

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Minor text additions to algebraic moment closures

@@
 
-Flux factor $h=|\vect{\cH}|/\cJ$
+Algebraic moment closures for the two-moment model are computationally efficient as they provide the Eddington factor in Eq.~\eqref{eq:eddingtonTensor} in closed form as a function of the density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$.
+The family of algebraic closures we consider in this paper can be written in the form \cite{cernohorskyBludman_1994}
 \begin{equation}
-  \chi(\cJ,h)=\f{1}{3}+\f{2\,(1-\cJ)\,(1-2\cJ)}{3}\,\Theta\Big(\f{h}{1-\cJ}\Big)
+  \chi(\cJ,h)=\f{1}{3}+\f{2\,(1-\cJ)\,(1-2\cJ)}{3}\,\Theta\Big(\f{h}{1-\cJ}\Big),
 \end{equation}
+where the closure function $\Theta(x)$ varies with the specifics of the closure procedure.  
+We will consider two basic closure procedures in more detail below: the maximum entropy (ME) closure and the Kershaw (K) closure.
 
 \subsubsection{Maximum Entropy Closure}
-Basic principles
+Basic principles.  
 Chernohorsky \& Bludman \cite{cernohorskyBludman_1994}
@@
 \subsubsection{Kershaw Closure}
-Basic principles
+Basic principles.  
 Banach \& Larecki \cite{banachLarecki_2017}

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added lemma needed for implicit solves in IMEX scheme.

@@
 \end{proof}
+\begin{lemma}
+  Let $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$.  
+  Let $\vect{\cM}_{b}=(\cJ_{b},\vect{\cH}_{b})^{T}$ satisfy
+  \begin{equation*}
+    \vect{\cM}_{b}=\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b}), 
+  \end{equation*}
+  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.  
+  Then $\vect{\cM}_{b}\in\cR$.  
+\end{lemma}
+\begin{proof}
+  The first component of $\vect{\cM}_{b}$ can be written as
+  \begin{equation}
+    \cJ_{b}=\f{1}{4\pi}\int_{\bbS}f_{b}(\omegaNu)\,d\omegaNu,
+  \end{equation}
+  where $f_{b}(\omegaNu)=\theta\,f_{a}(\omegaNu)+(1-\theta)\,f_{0}$ and $\theta=1/(1+\alpha\,\xi)\in[0,1]$.  
+  Then, since $f_{b}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$, $\cJ_{b}\in[0,1]$.  
+  Similarly, we can write
+  \begin{equation*}
+    \vect{\cH}_{b}=\f{(1+\alpha\,\xi)}{(1+\alpha)}\,\widetilde{\vect{\cH}}_{b},
+    \quad\text{where}\quad
+    \widetilde{\vect{\cH}}_{b}=\f{1}{4\pi}\int_{\bbS^{2}}f_{b}(\omegaNu)\,\vect{\ell}(\omegaNu)\,d\omegaNu.  
+  \end{equation*}
+  It follows from Lemma~\ref{lem:MomentRealizable} that $\widetilde{\vect{\bcM}}_{b}=(\cJ_{b},\widetilde{\vect{\cH}}_{b})^{T}\in\cR$.  
+  Then, since $0\le\xi\le1$, we have $|\vect{\cH}_{b}|\le|\widetilde{\vect{\cH}}_{b}|\le(1-\cJ_{b})\,\cJ_{b}$.  
+\end{proof}
 

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Cosmetic Changes.

@@
 In this paper, we seek to design a numerical method for solving the system of moment equations given by Eq.~\eqref{eq:momentEquations}, which preserves realizability of the moments; i.e., the moments evolve within the set of admissible values as dictated by Pauli's exclusion principle.
-(Since are concerned with the angular dependence of $f$ in this section, we simplify notation by suppressing the $\vect{z}$ and $t$ dependence and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.)
+(Since we only concern with the angular dependence of $f$ in this section, we simplify the notation by suppressing the $\vect{z}$ and $t$ dependence and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.)
 
@@
     \widehat{\vect{n}}\cdot\vect{\cH}
-    =\int_{\bbS^{1}}\mathfrak{f}(\mu)\,\mu\,d\mu,
+    =\f{1}{2} \int_{\bbS^{1}}\mathfrak{f}(\mu)\,\mu\,d\mu,
     \label{eq:NdotH}
@@
 
-We now define the realizable set $\cR$
+We now define the realizable set $\cR$:
 \begin{equation}
-  \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in[0,1]~\text{and}~\gamma(\vect{\cM})\equiv(1-\cJ)\cJ-|\vect{\cH}|\ge0\,\big\}
+  \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in[0,1]~\text{and}~\gamma(\vect{\cM})\equiv(1-\cJ)\cJ-|\vect{\cH}|\ge0\,\big\}.
   \label{eq:realizableSet}
@@
 \begin{lemma}
-  The set $\cR$, defined in Eq.~\eqref{eq:realizableSet}, is convex.  
+  The realizable set $\cR$, defined in Eq.~\eqref{eq:realizableSet}, is convex.  
 \end{lemma}
 \begin{proof}
-  In order to prove that $\cR$ is convex, we must show that a convex combination of elements in $\cR$ also belongs to $\cR$.  
+  In order to prove that $\cR$ is convex, we must show that any convex combination of elements in $\cR$ also belongs to $\cR$.  
   Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements in $\cR$.  
@@
 To make this plot, a total of $10^{6}$ distribution functions of the form $\mathfrak{f}(\mu;a,b) = \dfrac{1}{e^{a+b\mu}+1}$ ($\mu\in[-1,1]$) were generated, where the parameters $a$ and $b$ were chosen randomly and independently in the range $a,b\in[-10^{2},10^{2}]$.
-A uniform $\mu$-grid with $\Delta\mu=1/128$, was used to represent the distribution functions, and the angular moments were calculated using the trapezoid rule.  
-\begin{figure}
+A uniform $\mu$-grid with $\Delta\mu=1/128$ was used to represent the distribution functions. And the angular moments were calculated using the trapezoid rule.  
+\begin{figure}[h]
   \centering
@@
   Each of the $10^{6}$ light-blue points in the figure represents a set of moments $\vect{\cM}=(\cJ,\vect{\cH})$, computed from a random Fermi-Dirac distribution (see text for details).  
-  Black lines define the boundary of $\cR$; $\gamma(\vect{\cM}) = 0$.}
+  Black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
   \label{fig:RealizableSetFermionic}
@@
 \end{lemma}
+
+\begin{lemma}
+  For any $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$,
+  \begin{equation*}
+    \vect{\cM}_{b}\equiv\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b})\in\cR
+  \end{equation*}
+  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.
+\end{lemma}
+
 \begin{proof}

### 2018-02-02 Documents/M1/realizableFermionicM1/manuscript.tex
Updates to paper
modifications to Lemma 1.  Minor edits to DG discretization.
Added the plots of Mab.
Reworked title
Added lemma on correction step

--- 2018-01-22 Documents/M1/realizableFermionicM1/realizableM1_fermionPaper.tex
@@
 \usepackage{amsthm}
+\usepackage{mathrsfs}
+\usepackage{subcaption}
+
 \modulolinenumbers[5]
@@
 
+\newtheorem{define}{Definition}
+\newtheorem{lemma}{Lemma}
+\newtheorem{prop}{Proposition}
+\newtheorem{rem}{Remark}
+\newtheorem{theorem}{Theorem}
+
 \usepackage{./definitions}
@@
 
-\title{Realizability-Preserving Two-Moment DG Method for Fermionic Transport \tnoteref{ldrd-support}}
-\tnotetext[ldrd-support]{This research is sponsored by ...}
+\title{Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}}
+\tnotetext[support]{This research is sponsored by ...}
 
@@
 
+\tableofcontents
+
 \linenumbers
@@
 \input{sections/model}
-\input{sections/MomentsRealizability}
-\input{sections/IMEX}
-\input{sections/DGmethod}
+\input{sections/realizability}
+\input{sections/dg}
+\input{sections/imex}
 \input{sections/DGIMEXscheme}

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added lemma on correction step

@@
   \end{equation*}
-  where $f_{ab}(\omegaNu)=\theta\,f_{a}+(1-\theta)\,f_{b}$ and $\theta(\omegaNu)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omegaNu))/2\in[0,1]$.  
+  where $f_{ab}(\omegaNu)=\theta\,f_{a}(\omegaNu)+(1-\theta)\,f_{b}(\omegaNu)$ and $\theta(\omegaNu)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omegaNu))/2\in[0,1]$.  
   Then, since $f_{ab}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
 \end{proof}
+
 \begin{lemma}
@@
   Then $\vect{\cM}_{b}\in\cR$.  
+  \label{lem:implicitStep}
 \end{lemma}
 
-\begin{lemma}
-  For any $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$,
-  \begin{equation*}
-    \vect{\cM}_{b}\equiv\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b})\in\cR
-  \end{equation*}
-  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.
-\end{lemma}
+%\begin{lemma}
+%  For any $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$,
+%  \begin{equation*}
+%    \vect{\cM}_{b}\equiv\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b})\in\cR
+%  \end{equation*}
+%  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.
+%\end{lemma}
 
@@
   Then, since $0\le\xi\le1$, we have $|\vect{\cH}_{b}|\le|\widetilde{\vect{\cH}}_{b}|\le(1-\cJ_{b})\,\cJ_{b}$.  
+\end{proof}
+
+\begin{lemma}
+  Let $\vect{\cM}_{a}$ and $\alpha$ be given as in Lemma~\ref{lem:implicitStep}, and let $\vect{\cM}_{b}$ satisfy
+  \begin{equation*}
+    \vect{\cM}_{b}=\vect{\cM}_{a}+\alpha\,\vect{\cD}\,\vect{\cC}(\vect{\cM}_{b}),    
+  \end{equation*}
+  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments}.  
+  Then $\vect{\cM}_{b}\in\cR$.  
+  \label{lem:correctionStep}
+\end{lemma}
+
+\begin{proof}
+  The proof follows along the same lines as the proof of Lemma~\ref{lem:implicitStep}.  
 \end{proof}

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added the caption of Figure 2

@@
 
-\begin{figure}
+\begin{figure}[h]
   \centering
@@
   \end{tabular}
-  \caption{}
+   \caption{Illustration of $\vect{\cM}_{ab}$ with four different closures: Banach \& Larecki maximum entropy closure (left top), Chernohorsky \& Bludman maximum entropy closure (right top), Kershaw closure (left bottom), and Minerbo closure (right bottom).
+   Total $10^{6}$ pairs of random Fermi-Dirac distribution were generated.
+   With these pairs, $\vect{\cM}_{ab}$ with different closures were calculated separately and marked with light-blue points.
+   Black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
   \label{fig:MabWithDifferentClosure}
 \end{figure}
-
-%\begin{figure}[h!]
-%  \begin{subfigure}[b]{0.5\textwidth}
-%    \includegraphics[width=\textwidth]{figures/MabWithMI}
-%    \caption{$\vect{\cM}_{ab}$ with Minerbo closure.}
-%  \end{subfigure}
-%  %
-%  \begin{subfigure}[b]{0.5\textwidth}
-%    \includegraphics[width=\textwidth]{figures/MabWithBLKS}
-%    \caption{$\vect{\cM}_{ab}$ with Kershaw closure.}
-%  \end{subfigure}
-%  \begin{subfigure}[b]{0.5\textwidth}
-%    \includegraphics[width=\textwidth]{figures/MabWithCBME}
-%    \caption{$\vect{\cM}_{ab}$ with Chernohorsky \& Bludman maximum entropy closure.}
-%  \end{subfigure}
-%  \begin{subfigure}[b]{0.5\textwidth}
-%    \includegraphics[width=\textwidth]{figures/MabWithBLME}
-%    \caption{$\vect{\cM}_{ab}$ with Banach \& Larecki maximum entropy closure.}
-%  \end{subfigure}
-%  \label{fig:MabWithDifferentClosure}
-%\end{figure}

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added the basic principle behind the maximum entropy closure.

@@
 
-%\begin{lemma}
-%  For any $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$,
-%  \begin{equation*}
-%    \vect{\cM}_{b}\equiv\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b})\in\cR
-%  \end{equation*}
-%  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.
-%\end{lemma}
-
 \begin{proof}
@@
 \subsubsection{Maximum Entropy Closure}
-Basic principles.  
+The basic principle behind the maximum entropy closure is that one can approximate the real fermion distribution with a distribution which having the Fermi-Dirac distribution form 
+\begin{equation}
+f(\omega)=\f{1}{e^{a + b\omega}+1}, 
+\end{equation} 
+meanwhile, maximizing the entropy function
+\begin{equation}
+S[f(\omega)] = (1-f)\log(1-f) + f\log f.
+\end{equation} 
+Given moments $\cJ$ and $\vect{\cH}$, a distribution satisfying the above requirements can be found, hence $\vect{\cK}$.
+
 Chernohorsky \& Bludman \cite{cernohorskyBludman_1994}
@@
 \end{equation}
+
 Banach \& Larecki
@@
 
+Figure~\ref{fig:MabWithDifferentClosure} illustrates the behavior of these four closure.
 \begin{figure}[h]

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Updated the references.

@@
 Obviously, realizable moments must satisfy the bounds imposed by $f$.  
-We proceed by stating the bounds on the moments by restating (with slightly modified proof) results from Theorem~7.1 in \cite{banachLarecki_2017} in the following Lemma.  
+We proceed by stating the bounds on the moments by restating (with slightly modified proof) results from Theorem~7.1 in \cite{banachLarecki_2017a} in the following Lemma.  
 \begin{lemma}
@@
   where we have aligned the polar axis of the spherical momentum space coordinate system with $\widehat{\vect{n}}$; i.e., $\widehat{\vect{n}}\cdot\vect{\ell}(\omega)=\mu$.  
-  First, following \cite{banachLarecki_2017}, we can write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
+  First, following \cite{banachLarecki_2017a}, we can write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
   \begin{equation*}
@@
 \end{equation} 
-Given moments $\cJ$ and $\vect{\cH}$, a distribution satisfying the above requirements can be found, hence $\vect{\cK}$.
+Given moments $\cJ$ and $\vect{\cH}$, a distribution satisfying above requirements can be found. Hence, $\vect{\cK}$.
 
@@
 
-Banach \& Larecki
+Banach \& Larecki \cite{banachLarecki_2017b}
 \begin{equation}
@@
 Basic principles.  
-Banach \& Larecki \cite{banachLarecki_2017}
+Banach \& Larecki \cite{banachLarecki_2017a}
 \begin{equation}

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
Working on DG-IMEX section

@@
 \label{sec:realizableDGIMEX}
+
+The realizability preserving DG scheme is designed to ensure realizability of the cell averages in each element $\bK$, defined as
+\begin{equation}
+  \vect{\cM}_{\bK}
+  =\f{1}{|\bK|}\int_{\bK}\vect{\cM}_{h}\,d\bx.  
+\end{equation}
+Then, with $v=1$ in Eq.~\eqref{eq:semidiscreteDG}, the stage values for the cell average in the IMEX scheme in Eq.~\eqref{eq:imexStagesRewrite} are given by
+\begin{equation}
+  \vect{\cM}_{\bK}^{(i)}
+  =c_{i0}\,\vect{\cM}_{\bK}^{n}
+  +\sum_{j=1}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}
+  +a_{ii}\,\dt\,\f{1}{\tau}\,\big(\,\vect{\eta}-\vect{\cD}\,\vect{\cM}_{\bK}^{(i)}\,\big),
+  \label{eq:imexStagesCellAverage}
+\end{equation}
+where we have defined
+\begin{equation}
+  \vect{\cM}_{\bK}^{(ij)}
+  =\vect{\cM}_{\bK}^{(j)}-\hat{c}_{ij}\,\dt\,\big\langle\,\nabla\cdot\vect{\cF}(\vect{\cM}_{h}^{(j)})\,\big\rangle_{\bK},
+\end{equation}
+and the cell average of the divergence operator is (cf. Section~\ref{sec:dg})
+\begin{equation}
+  \big\langle\,\nabla\cdot\vect{\cF}(\vect{\cM}_{h})\,\big\rangle_{\bK}
+  =\f{1}{|\bK|}\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
+  \big(\,\widehat{\bcF}^{i}(\vect{\cM}_{h})\big|_{\xH^{i}}-\widehat{\bcF}^{i}(\vect{\cM}_{h})\big|_{\xL^{i}}\,\big)\,d\tilde{\vect{x}}^{i}.  
+\end{equation}
+
+\begin{lemma}
+  Let $\vect{\cM}_{\bK}^{(i)}$ satisfy Eq.~\eqref{eq:imexStagesCellAverage}.
+  Assume that $\vect{\cM}_{\bK}^{n}\in\cR$ and $\vect{\cM}_{\bK}^{(ij)}\in\cR\,\forall\,j\le i-1$.  
+  Then, $\vect{\cM}_{\bK}^{(i)}\in\cR$.  
+\end{lemma}
+\begin{proof}
+  The first two terms on the right-hand side of Eq.~\eqref{eq:imexStagesCellAverage} constitute a convex combination of elements in $\cR$; i.e.,
+  \begin{equation*}
+    c_{i0}\,\vect{\cM}_{\bK}^{n}+\sum_{j=1}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}\in\cR.
+  \end{equation*}
+  Since $a_{ii}\,\dt/\tau>0$, it follows from Lemma~\ref{lem:implicitStep} that $\vect{\cM}_{\bK}^{(i)}\in\cR$.  
+\end{proof}
+
+We proceed to establish conditions for which $\vect{\cM}_{\bK}^{(ij)}\in\cR$.  
+To this end, to simplify notation, we consider the moments
+\begin{equation}
+  \vect{\cM}_{\bK}^{*}
+  =\vect{\cM}_{\bK}-\hat{c}\,\dt\,\big\langle\,\nabla\cdot\vect{\cF}(\vect{\cM}_{h})\,\big\rangle_{\bK},
+\end{equation}
+where $\vect{\cM}_{\bK}$ is the cell average of $\vect{\cM}_{h}\in\bbV^{k}$ and $\hat{c}\ge0$.  
+\begin{lemma}
+  Let $\{s_{i}\}_{i=1}^{d}$ be a set of positive constants satisfying $\sum_{i=1}^{d}=1$.  
+  If for each $i\in\{1,\ldots,d\}$, 
+  \begin{equation}
+    \Gamma^{i}\big[\vect{\cM}_{h}\big](\tilde{\vect{x}}^{i})
+    :=\f{1}{|K^{i}|}
+    \Big[\,\int_{K^{i}}\vect{\cM}_{h}\,dx^{i}-\f{\hat{c}\,\dt}{s_{i}}\big(\,\widehat{\bcF}^{i}(\vect{\cM}_{h})\big|_{\xH^{i}}-\widehat{\bcF}^{i}(\vect{\cM}_{h})\big|_{\xL^{i}}\,\big)\,\Big]\in\cR,
+    \label{eq:realizableGamma}
+  \end{equation}
+  then $\vect{\cM}_{\bK}^{*}\in\cR$.  
+\end{lemma}
+\begin{proof}
+  It is easy to show that $\vect{\cM}_{\bK}^{*}$ can be expressed as the convex combination
+  \begin{equation}
+    \sum_{i=1}^{d}s_{i}\,\f{1}{|\tilde{\vect{\bK}}^{i}|}\int_{\tilde{\bK}^{i}}\Gamma^{i}\big[\vect{\cM}_{h}\big]\,d\tilde{\vect{x}}^{i}.  
+    \label{eq:cellAverageInTermsOfGamma}
+  \end{equation}
+  The result follows immediately.  
+\end{proof}
+\begin{rem}
+  If a quadrature rule $\tilde{\vect{Q}}^{i}:C^{0}\to\bbR$, with positive weights, and points defined by the set $\tilde{\vect{S}}^{i}$, is used to approximate the integral over $\tilde{\bK}^{i}$ in \eqref{eq:cellAverageInTermsOfGamma}, it is sufficient for \eqref{eq:realizableGamma} to hold in the quadrature points $\tilde{\vect{S}}^{i}\subset\tilde{\bK}^{i}$.
+\end{rem}

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/dg.tex
Working on DG-IMEX section

@@
 \begin{equation}
-  \pd{\vect{\cM}}{t}+\sum_{i=1}^{d}\pderiv{}{x^{i}}\big(\,\vect{\cF}^{i}(\vect{\cM})\,\big)=\vect{\cC}(\vect{\cM}).  
+  \pd{\vect{\cM}}{t}+\sum_{i=1}^{d}\pderiv{}{x^{i}}\big(\,\vect{\cF}^{i}(\vect{\cM})\,\big)
+  =\frac{1}{\tau}\,\vect{\cC}(\vect{\cM}).  
   \label{eq:angularMomentsCartesian}
@@
 Note that functions in $\mathbb{V}^{k}$ can be discontinuous across element interfaces.  
-The semi-discrete DG problem is to find $\bcM_{h}\in\mathbb{V}^{k}$ (which approximates $\bcM$ in Eq.~\eqref{eq:angularMomentsCartesian}) such that
+The semi-discrete DG problem is to find $\vect{\cM}_{h}\in\mathbb{V}^{k}$ (which approximates $\vect{\cM}$ in Eq.~\eqref{eq:angularMomentsCartesian}) such that
 \begin{align}
-  &\pd{}{t}\int_{\bK}\bcM_{h}\,v\,d\vect{x}
+  &\pd{}{t}\int_{\bK}\vect{\cM}_{h}\,v\,d\vect{x}
   +\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
   \big(\,
-    \widehat{\bcF}^{i}(\bcM_{h})\,v\big|_{\xH^{i}}
-    -\widehat{\bcF}^{i}(\bcM_{h})\,v\big|_{\xL^{i}}
+    \widehat{\bcF}^{i}(\vect{\cM}_{h})\,v\big|_{\xH^{i}}
+    -\widehat{\bcF}^{i}(\vect{\cM}_{h})\,v\big|_{\xL^{i}}
   \,\big)\,d\tilde{\bx}^{i} \nonumber \\
   &\hspace{24pt}
-  -\sum_{i=1}^{d}\int_{\bK}\bcF^{i}(\bcM_{h})\,\pderiv{v}{x^{i}}\,d\vect{x}
-  =\int_{\bK}\bcC(\bcM_{h})\,v\,d\vect{x},
+  -\sum_{i=1}^{d}\int_{\bK}\bcF^{i}(\vect{\cM}_{h})\,\pderiv{v}{x^{i}}\,d\vect{x}
+  =\f{1}{\tau}\int_{\bK}\bcC(\vect{\cM}_{h})\,v\,d\vect{x},
   \label{eq:semidiscreteDG}
@@
 
-In Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\bcF}^{i}(\bcM_{h})$ is a numerical flux, approximating the flux on the surface of $\bK$ with unit normal along the $i$th coordinate direction, and is evaluated with a flux function $\vect{\mathscr{F}}^{i}$ using the DG approximation from both sides of the element interface; i.e.,
+In Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\bcF}^{i}(\vect{\cM}_{h})$ is a numerical flux, approximating the flux on the surface of $\bK$ with unit normal along the $i$th coordinate direction, and is evaluated with a flux function $\vect{\mathscr{F}}^{i}$ using the DG approximation from both sides of the element interface; i.e.,
 \begin{equation}
-  \widehat{\bcF}^{i}(\bcM_{h})\big|_{x^{i}}=\vect{\mathscr{F}}^{i}(\bcM_{h}(x^{i,-},\tilde{\bx}^{i}),\bcM_{h}(x^{i,+},\tilde{\bx}^{i})),
+  \widehat{\bcF}^{i}(\vect{\cM}_{h})\big|_{x^{i}}=\vect{\mathscr{F}}^{i}(\vect{\cM}_{h}(x^{i,-},\tilde{\bx}^{i}),\vect{\cM}_{h}(x^{i,+},\tilde{\bx}^{i})),
 \end{equation}
-where superscripts $-/+$ in the arguments of $\bcM_{h}(x^{i,-/+},\tilde{\bx}^{i})$ indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
+where superscripts $-/+$ in the arguments of $\vect{\cM}_{h}(x^{i,-/+},\tilde{\bx}^{i})$ indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
 In this paper we use the simple Lax-Friedrichs (LF) flux given by
 \begin{equation}
-  \vect{\mathscr{F}}_{\mbox{\tiny LF}}^{i}(\bcA,\bcB)
-  =\f{1}{2}\,\big(\,\bcF^{i}(\bcA)+\bcF^{i}(\bcB)-\alpha^{i}\,(\,\bcA-\bcB\,)\,\big),
+  \vect{\mathscr{F}}_{\mbox{\tiny LF}}^{i}(\vect{\cM}_{a},\vect{\cM}_{b})
+  =\f{1}{2}\,\big(\,\bcF^{i}(\vect{\cM}_{a})+\bcF^{i}(\vect{\cM}_{b})-\alpha^{i}\,(\,\vect{\cM}_{a}-\vect{\cM}_{b}\,)\,\big),
 \end{equation}
-where $\alpha^{i}=||\mbox{eig}\big(\partial\bcF^{i}/\partial\bcM\big)||_{\infty}$ is the largest eigenvalue of the flux Jacobian.  
+where $\alpha^{i}=||\mbox{eig}\big(\partial\bcF^{i}/\partial\vect{\cM}\big)||_{\infty}$ is the largest eigenvalue (in absolute value) of the flux Jacobian.  
 For particles propagating at the speed of light, we can simply take $\alpha^{i}=1$ (i.e., the global LF flux).
 
-For simplicity, we will approximate the opacities $\sigma_{\Ab}$ and $\sigma_{\Scatt}$ appearing in the collision term on the right-hand side of Eq.~\eqref{eq:angularMomentsCartesian} with constants in each element; i.e., $\sigma_{\Ab},\sigma_{\Scatt}\in\bbV^{0}$.
+\begin{rem}
+For simplicity, in Eq.~\eqref{eq:semidiscreteDG}, we have approximated the opacities $\sigma_{\Ab}$ and $\sigma_{\Scatt}$ (and thus $\xi$ and $\tau$) on the right-hand side of Eq.~\eqref{eq:angularMomentsCartesian} with constants in each element; i.e., $\sigma_{\Ab},\sigma_{\Scatt}\in\bbV^{0}$.
+\end{rem}

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/imex.tex
Working on DG-IMEX section

@@
   =\vect{\cT}(\vect{u})+\f{1}{\tau}\,\vect{\cQ}(\vect{u}),
+  \label{eq:ode}
 \end{equation}
-where $\vect{u}$ are the degrees of freedom evolved with the DG method (e.g., expansion coefficients resulting from a modal expansion).  
+where $\vect{u}$ are the degrees of freedom evolved with the DG method; i.e., for a test space spanned by $\{\phi_{i}(\vect{x})\}_{i=1}^{N}\in\bbV^{k}$, we let
+\begin{equation}
+  \vect{u}=\f{1}{|\bK|}\Big(\,\int_{\bK}\vect{\cM}_{h}\,\phi_{1}\,d\vect{x},\int_{\bK}\vect{\cM}_{h}\,\phi_{2}\,d\vect{x},\ldots,\int_{\bK}\vect{\cM}_{h}\,\phi_{N}\,d\vect{x}\,\Big)^{T}.
+\end{equation}
 The transport term $\vect{\cT}$ is due to the second and third term in the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision term $\vect{\cQ}$ is due to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
@@
 Chertock et al. \cite{chertock_etal_2015} presented second order accurate IMEX schemes with a correction step.  
-The correction step includes the transport operator, and positivity is subject to a time step restriction that scales with $1/\sqrt{\tau}$.  
+The correction step includes the transport operator, and positivity is subject to a time step restriction $\dt\propto1/\sqrt{\tau}$.  
 More recently, Hu et al. \cite{hu_etal_2017}, presented new IMEX schemes for a class of BGK-type collision operators with a correction step that does not include the transport operator.  
@@
   +\dt\sum_{i=1}^{j}\alpha_{ij}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(j)}),
-  \quad i=1,\ldots,s, \\
+  \quad i=1,\ldots,s, \label{imexStages} \\
   \tilde{\vect{u}}^{n+1}
@@
   +\dt\sum_{i=1}^{s}\tilde{w}_{i}\,\vect{\cT}(\vect{u}^{(i)})
-  +\dt\sum_{i=1}^{s}w_{i}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}), \\
+  +\dt\sum_{i=1}^{s}w_{i}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}), \label{imexIntermediate} \\
   \vect{u}^{n+1}
-  &=\tilde{\vect{u}}^{n+1}-\alpha\,\dt^{2}\,\f{1}{\tau^{2}}\,\vect{\cQ}'(\vect{u}^{*})\,\vect{\cQ}(\vect{u}^{n+1}), 
+  &=\tilde{\vect{u}}^{n+1}-\alpha\,\dt^{2}\,\f{1}{\tau^{2}}\,\vect{\cQ}'(\vect{u}^{*})\,\vect{\cQ}(\vect{u}^{n+1}), \label{eq:imexCorrection}
 \end{align}
+To prove the positivity-preserving property of the IMEX scheme, Hu et al. \cite{hu_etal_2017} rewrite the stage values in Eq.~\eqref{imexStages} as
+\begin{equation}
+  \vect{u}^{(i)}
+  =c_{i0}\,\vect{u}^{n}+\sum_{j=1}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
+  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{Q}(\vect{u}^{(i)}),
+  \label{eq:imexStagesRewrite}
+\end{equation}
+where $c_{i0}+\sum_{j=1}^{i-1}c_{ij}=1$.
+
+For globally stiffly accurate (GSA) IMEX schemes $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Working on DG-IMEX section
Backup.

@@
   \end{equation*}
-  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.  
+  where $\vect{\cC}(\vect{\cM})=\vect{\eta}-\vect{\cD}\,\vect{\cM}$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.  
   Then $\vect{\cM}_{b}\in\cR$.  
@@
 \subsubsection{Kershaw Closure}
-Basic principles.  
+The basic principles behind Kershaw closure is that since $\cR$ is convex and bounded, every element in $\cR$ can be written as a convex combination of the elements on the realization boundary.
+For fermionic radiation, the boundary is based on the Heaviside step functions.
+
 Banach \& Larecki \cite{banachLarecki_2017a}

### 2018-02-03 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
Additions to imex and dg-imex section

@@
   \begin{equation}
-    \Gamma^{i}\big[\vect{\cM}_{h}\big](\tilde{\vect{x}}^{i})
+    \vect{\Gamma}^{i}\big[\vect{\cM}_{h}\big](\tilde{\vect{x}}^{i})
     :=\f{1}{|K^{i}|}
@@
   \begin{equation}
-    \sum_{i=1}^{d}s_{i}\,\f{1}{|\tilde{\vect{\bK}}^{i}|}\int_{\tilde{\bK}^{i}}\Gamma^{i}\big[\vect{\cM}_{h}\big]\,d\tilde{\vect{x}}^{i}.  
+    \sum_{i=1}^{d}s_{i}\,\f{1}{|\tilde{\vect{\bK}}^{i}|}\int_{\tilde{\bK}^{i}}\vect{\Gamma}^{i}\big[\vect{\cM}_{h}\big]\,d\tilde{\vect{x}}^{i}.  
     \label{eq:cellAverageInTermsOfGamma}
@@
 \end{rem}
+
+Next, we establish conditions for which \eqref{eq:realizableGamma} holds.  
+To simplify the notation, we temporarily drop the dimension index $i$, setting $x^{i}=x$, $K^{i}=K$, $\vect{\Gamma}^{i}=\vect{\Gamma}$, etc.  
+We let $\hat{Q}_{N}$ denote the $N$-point \emph{Gauss-Lobatto} quadrature rule on the interval $K=(x_{\Low},x_{\Hgh})$, with points
+\begin{equation}
+  \hat{S}=\left\{x_{\Low}=\hat{x}_{1},\cdots,\hat{x}_{N}=x_{\Hgh}\right\}, 
+  \label{eq:quadraturePointsGL}
+\end{equation}
+and weights $\hat{w}_{q} \in (0,1]$, normalized so that $\sum_{q=1}^{N} \hat{w}_{q} = 1$.  
+(The hat is used to denote the Gauss-Lobatto rule, which includes the endpoints of the interval $K$.)
+This quadrature integrates polynomials in $x \in \bbR$ with degree $\le2N-3$ exactly.

### 2018-02-03 Documents/M1/realizableFermionicM1/sections/imex.tex
Additions to imex and dg-imex section

@@
 
+In this section we summarize the IMEX scheme used for the realizability-preserving DG-IMEX method for the two-moment model developed in Section~\ref{sec:realizableDGIMEX}.  
 The semi-discretization of the moment equations with the DG method given in Eq.~\eqref{eq:semidiscreteDG} results in a system of ordinary differential equations (ODEs) in each element of the form
@@
 In this case, positivity is only subject to time step restrictions stemming from the transport operator.  
-These IMEX schemes take the following form \cite{hu_etal_2017}
+These $s$-stage IMEX schemes take the following form \cite{hu_etal_2017}
 \begin{align}
@@
 \end{align}
+where, as in standard IMEX schemes, $(\tilde{a}_{ij})$ and $(a_{ij})$, components of $s\times s$ matrices, and the vectors $(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $(w_{1},\ldots,w_{s})^{T}$ must satisfy certain order conditions \cite{pareschiRusso_2005}.
+The coefficient in the correction step is positive, $\alpha>0$.  
+For globally stiffly accurate (GSA) IMEX schemes, $\tilde{w}_{i}=\tilde{a}_{si}$ and $w_{i}=a_{si}$ for $i=\{1,\ldots,s\}$, so that $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$.  
 To prove the positivity-preserving property of the IMEX scheme, Hu et al. \cite{hu_etal_2017} rewrite the stage values in Eq.~\eqref{imexStages} as
@@
 \end{equation}
-where $c_{i0}+\sum_{j=1}^{i-1}c_{ij}=1$.
-
-For globally stiffly accurate (GSA) IMEX schemes $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$
+where $c_{i0}$, $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$ (see \cite{hu_etal_2017} for details).  
+Importantly, $c_{i0}+\sum_{j=1}^{i-1}c_{ij}=1$.  
+The positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$, for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.

### 2018-02-03 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
Additions to DG-IMEX scheme

@@
 To simplify the notation, we temporarily drop the dimension index $i$, setting $x^{i}=x$, $K^{i}=K$, $\vect{\Gamma}^{i}=\vect{\Gamma}$, etc.  
-We let $\hat{Q}_{N}$ denote the $N$-point \emph{Gauss-Lobatto} quadrature rule on the interval $K=(x_{\Low},x_{\Hgh})$, with points
+We let $\hat{Q}_{N}$ denote the $N$-point \emph{Gauss-Lobatto (GL)} quadrature rule on the interval $K=(x_{\Low},x_{\Hgh})$, with points
 \begin{equation}
@@
 and weights $\hat{w}_{q} \in (0,1]$, normalized so that $\sum_{q=1}^{N} \hat{w}_{q} = 1$.  
-(The hat is used to denote the Gauss-Lobatto rule, which includes the endpoints of the interval $K$.)
+(The hat is used to denote the GL rule, which includes the endpoints of the interval $K$.)
 This quadrature integrates polynomials in $x \in \bbR$ with degree $\le2N-3$ exactly.  
+Then, if $\vect{\cM}_{h}$ is represented by such polynomials we have
+\begin{equation}
+  \int_{K} \bcM_{h}\,dx = \hat{Q}_{N}[\bcM_{h}] \equiv
+  |K| \sum_{q=1}^{N} \hat{w}_{q}\,\hat{\bcM}_{q}
+  \label{eq:quadratureRuleGL}
+\end{equation}
+where $\hat{\bcM}_{q} := \bcM_{h}(\hat{x}_q,\tilde{\vect{x}})$.  
+In each element, $\hat{\vect{\cM}}_{1}=\vect{\cM}_{\Low}^{+}$ and $\hat{\vect{\cM}}_{N}=\vect{\cM}_{\Hgh}^{-}$.
+
+With the GL quadrature rule in \eqref{eq:quadratureRuleGL} (note $\hat{w}_{1}=\hat{w}_{N}$), we can write $\vect{\Gamma}$ as the convex combination
+\begin{equation}
+  \vect{\Gamma}\big[\bcM_{h}\big]
+  =\sum_{q=2}^{N-1}\hat{w}_{q}\,\hat{\vect{\cM}}_{q}
+  +2\,\hat{w}_{N}\,\Phi(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+}),
+  \label{eq:realizableGammaConvex}
+\end{equation}
+where we have defined
+\begin{align}
+  &\Phi(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+}) \nonumber \\
+  &\hspace{12pt}
+  =\f{1}{2}\big(\,\vect{\cM}_{\Low}^{+}+\lambda\,\mathscr{F}(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+})\,\big)
+  +\f{1}{2}\big(\,\vect{\cM}_{\Hgh}^{-}-\lambda\,\mathscr{F}(\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+})\,\big),
+\end{align}
+with $\lambda=\hat{c}\,\dt/(s\,\hat{w}_{N}\,|K|)$.  
+The following Lemma establishes sufficient conditions for realizability of $\vect{\Gamma}$, and hence $\vect{\cM}_{\bK}^{*}$.  
+\begin{lemma}
+  Assume that $\hat{\vect{\cM}}_{q}\in\cR$ for all $q=1,\ldots,N$ and all $\bK\in\mathscr{T}$.  
+  Let the time step $\dt$ be chosen so that $\lambda\le1$.  
+  Let the numerical flux be given by the Lax-Friedrichs flux in Eq.~\eqref{eq:fluxFunctionLF} with $\alpha=1$.  
+  Then $\vect{\Gamma}[\bcM_{h}]\in\cR$.  
+\end{lemma}
+\begin{proof}
+  In Eq.~\eqref{eq:realizableGammaConvex}, $\vect{\Gamma}[\vect{\cM}_{h}]$ is expressed as a convex combination.  
+  By assumption, $\hat{\vect{\cM}}_{q}\in\cR$ ($q=2,\ldots,N-1$).  
+  It remains to show $\Phi(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+})\in\cR$.  
+  Using the Lax-Friedrichs flux with $\alpha=1$, it is straightforward to show that
+  \begin{align}
+    &\Phi(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+})
+    =(1-\lambda)\,\f{1}{2}\,\big(\,\vect{\cM}_{\Low}^{+}+\vect{\cM}_{\Hgh}^{-}\,\big) \nonumber \\
+    &\hspace{12pt}
+    +\f{1}{2}\,\lambda\,\big(\,\Phi^{+}(\vect{\cM}_{\Low}^{-})+\Phi^{-}(\vect{\cM}_{\Hgh}^{-})\,\big)
+    +\f{1}{2}\,\lambda\,\big(\,\Phi^{+}(\vect{\cM}_{\Low}^{+})+\Phi^{-}(\vect{\cM}_{\Hgh}^{+})\,\big),
+    \label{eq:phiConvex}
+  \end{align}
+  where $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\,\big(\vect{\cM}\pm\vect{e}\cdot\vect{\cF}(\vect{\cM})\big)$.  
+  Since $\lambda\le1$, $\Phi$ is expressed as a convex combination of three terms.  
+  By assumption, $\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+}\in\cR$, which immediately implies realizability of the first term on the right-hand side of Eq.~\eqref{eq:phiConvex}.
+  Realizability of the second and third terms follows by invoking Lemma~\ref{lem:explicitStep}.  
+  This completes the proof.  
+\end{proof}

### 2018-02-08 Documents/M1/realizableFermionicM1/sections/numerical.tex
Added initial outline of numerical tests

\section{Numerical Tests}
\label{sec:numerical}

\subsection{Problems with Known Smooth Solutions}

\subsubsection{Sine Wave: Streaming}

\subsubsection{Sine Wave: Damping}

\subsubsection{Sine Wave: Diffusion}

\subsection{Line Source}

\subsection{Homogeneous Sphere}

### 2018-02-12 Documents/M1/realizableFermionicM1/sections/numerical.tex
Additions to paper

@@
 \subsection{Homogeneous Sphere}
+
+The homogeneous sphere test (e.g., \cite{smit_etal_1997}) considers of a sphere with radius $R$.  
+Inside the sphere (radius $<R$), the absorption opacity $\sigma_{\Ab}$ and the equilibrium distribution function $f_{0}$ are set to constant values.  
+The scattering opacity $\sigma_{\Scatt}$ is set to zero in this test (i.e., $\xi=1$).  
+%Outside the sphere, the absorption opacity is zero.  
+%The steady state solution, obtained by solving the transport equation in spherical symmetry, is given by
+%\begin{equation}
+%  f_{\mbox{\tiny A}}(r,\mu)=f_{0}\,\big(1-e^{-\chi_{0}\,s(r,\mu)}\big),
+%  \label{distributionHomogeneousSphere}
+%\end{equation}
+%where
+%\begin{equation}
+%  s(r,\mu)
+%  =\left\{
+%  \begin{array}{lll}
+%    r\,\mu+R\,g(r,\mu) & \mbox{if}\quad r<R, & \mu\in[-1,+1], \\
+%    2\,R\,g(r,\mu) & \mbox{if}\quad r \ge R, & \mu\in[(1-(R/r)^{2})^{1/2},+1], \\
+%    0 & \mbox{otherwise},
+%  \end{array}
+%  \right.
+%\end{equation}
+%and $g(r,\mu)=[1-(r/R)^{2}(1-\mu^{2})]^{1/2}$.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Resolution_3}
+  \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_1}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_2}
+  \end{tabular}
+   \caption{Homogeneous sphere problem: 32$^{3}$, 48$^{3}$, and 64$^{3}$}
+  \label{fig:HomogeneousSphere_Resolution}
+\end{figure}

### 2018-02-12 Documents/M1/realizableFermionicM1/sections/realizability.tex
moved low occupancy limit to paragraph
Additions to DG-IMEX scheme
Added introduction to Kershaw closure.
Additions to paper

@@
   \end{equation*}
+  \label{lem:explicitStep}
 \end{lemma}
@@
 \end{lemma}
-
-\begin{proof}
-  The proof follows along the same lines as the proof of Lemma~\ref{lem:implicitStep}.  
-\end{proof}
+The proof follows along the same lines as the proof of Lemma~\ref{lem:implicitStep} and is omitted.
 
@@
   \chi(\cJ,h)=\f{1}{3}+\f{2\,(1-\cJ)\,(1-2\cJ)}{3}\,\Theta\Big(\f{h}{1-\cJ}\Big),
+  \label{eq:eddingtonFactor}
 \end{equation}
@@
 We will consider two basic closure procedures in more detail below: the maximum entropy (ME) closure and the Kershaw (K) closure.
+
+\paragraph{Low Occupancy Limit}
+We note in passing that in the low occupancy limit ($\cJ\ll1$), the Eddington factor in Eq.~\eqref{eq:eddingtonFactor} becomes independent of $\cJ$; i.e.,
+\begin{equation}
+  \chi(\cJ,h)\to\chi_{0}(h)=\f{1}{3}+\f{2}{3}\,\Theta\big(h\big).  
+  \label{eq:eddingtonFactorLow}
+\end{equation}
 
@@
 The basic principles behind Kershaw closure is that since $\cR$ is convex and bounded, every element in $\cR$ can be written as a convex combination of the elements on the realization boundary. 
+In other words, Kershaw closure satisfies realizability inherently.
 For fermionic radiation, the boundary is based on the Heaviside step functions.
@@
 \end{equation}
-
-\subsubsection{Low Occupancy Limit}
 

### 2018-02-12 Documents/M1/realizableFermionicM1/sections/realizability.tex
Cosmetic Changes.

@@
   \end{equation*}
+  Hence, $\vect{\cM}_{ab}\in\cR$.
 \end{proof}
@@
   \end{equation*}
-  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments}.  
-  Then $\vect{\cM}_{b}\in\cR$.  
+  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments},  then $\vect{\cM}_{b}\in\cR$.  
   \label{lem:correctionStep}
@@
 \subsubsection{Maximum Entropy Closure}
-The basic principle behind the maximum entropy closure is that one can approximate the real fermion distribution with a distribution which having the Fermi-Dirac distribution form 
+The basic principle behind the maximum entropy closure is that one can approximate the real fermion distribution with a distribution which have the Fermi-Dirac distribution form 
 \begin{equation}
@@
 \end{equation} 
-meanwhile, maximizing the entropy function
+meanwhile maximize the entropy function
 \begin{equation}
@@
 \end{equation} 
-Given moments $\cJ$ and $\vect{\cH}$, a distribution satisfying above requirements can be found. Hence, $\vect{\cK}$.
+Given moments $\cJ$ and $\vect{\cH}$, a distribution satisfying above requirements can be found. 
+Therefore, the stress tensor $\vect{\cK}$.
 
-Chernohorsky \& Bludman \cite{cernohorskyBludman_1994}
+One ME closure given by Chernohorsky \& Bludman \cite{cernohorskyBludman_1994} is
 \begin{equation}
   \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny CB}}(x)
-  =x^{2}\,\big(\,3-x+3\,x^{2}\,\big)
+  =x^{2}\,\big(\,3-x+3\,x^{2}\,\big).
 \end{equation}
 
-Banach \& Larecki \cite{banachLarecki_2017b}
+Another ME closure given by Banach \& Larecki \cite{banachLarecki_2017b} is
 \begin{equation}
   \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny BL}}(x)
-  =\f{1}{8}\,\big(\,9\,x^{2}-5+\sqrt{33\,x^{4}-42\,x^{2}+25}\,\big)
+  =\f{1}{8}\,\big(\,9\,x^{2}-5+\sqrt{33\,x^{4}-42\,x^{2}+25}\,\big).
 \end{equation}
@@
 \subsubsection{Kershaw Closure}
-The basic principles behind Kershaw closure is that since $\cR$ is convex and bounded, every element in $\cR$ can be written as a convex combination of the elements on the realization boundary. 
-In other words, Kershaw closure satisfies realizability inherently.
+The basic principle behind Kershaw closure is derived from the fact that $\cR$ is convex.
+Due to the convexity, one can write any element in $\cR$ as a convex combination of the elements on the realization boundary. 
+Therefore, Kershaw closure satisfies realizability inherently.
 For fermionic radiation, the boundary is based on the Heaviside step functions.
-
-Banach \& Larecki \cite{banachLarecki_2017a}
+Here we introduce a closure function $\Theta(x)$ given by Banach \& Larecki \cite{banachLarecki_2017a}:
 \begin{equation}
@@
 Figure~\ref{fig:MabWithDifferentClosure} illustrates the behavior of these four closure.
+As it shows, Minerbo closure (right bottom) is the only one among those four closures that does not preserve realizability.
 \begin{figure}[h]

### 2018-02-24 Documents/M1/realizableFermionicM1/sections/numerical.tex
Cosmetic Changes.
Some work on results.  Added figures.

--- 2018-02-08 Documents/M1/realizableFermionicM1/sections/numerical.tex
@@
 
+To compare the accuracy of the IMEX schemes, we present results from smooth problems in streaming, absorption, and scattering dominated regimes in one spatial dimension.  
+In all tests, we employ the maximum entropy closure in the low occupancy limit (i.e., the Minerbo closure).
+
 \subsubsection{Sine Wave: Streaming}
+
+Periodic domain $D=\{x:x\in[0,1]\}$.  
+The initial condition is given by
+\begin{equation}
+  \cJ(x,t=0)=\cH_{x}(x,t=0)=0.5+0.49\times\sin\big(2\pi\,x\big).  
+\end{equation}
 
@@
 
+Periodic domain $D=\{x:x\in[0,1]\}$.
+
 \subsubsection{Sine Wave: Diffusion}
+
+\subsection{Packed Beam}
+
+Next we consider a one-dimensional test with discontinuous initial conditions.  
+The computational domain is $D=\{x:x\in[-1,1]\}$, and the initial condition is obtained from a distribution function given by
+\begin{equation}
+  f(x,\mu)
+  =\left\{
+  \begin{array}{cl}
+    1        & \text{if} ~ x\le x_{\mbox{\tiny D}}, ~ \mu\ge\mu_{\mbox{\tiny D}} \\
+    \delta & \text{if} ~ x\le x_{\mbox{\tiny D}}, ~ \mu<   \mu_{\mbox{\tiny D}} \\
+    \delta & \text{otherwise},
+  \end{array}
+  \right.
+\end{equation}
+so that $\vect{\cM}=\big(0.5\,(1+\delta),0.25\,(1-\delta)\big)^{T}$ for $x\le x_{\mbox{\tiny D}}$, and $\vect{\cM}=\big(\delta,0\big)^{T}$ for $x> x_{\mbox{\tiny D}}$.  
+We let $\delta=10^{-8}$.  
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_ME_CB}
+    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_ME_MI}
+  \end{tabular}
+   \caption{Packed Beam}
+  \label{fig:PackedBeam}
+\end{figure}
 
@@
 
+The line source benchmark \citep[cf.][]{brunner_2002,garrettHauck_2013} is a challenging test for approximate transport algorithms.  
+In cylindrical coordinates, it consists of an initial delta function particle distribution in radius; i.e., $f_{0}=\delta(R)/4\,\pi$.  
+For $t>0$, a cylindrical radiation front propagates radially.  
+Apart from capturing details of the exact transport solution, maintaining realizability ($\bcM\in\cR$ cf. Eq.~\eqref{eq:realizableSet}) of the two-moment solution is challenging.
+
+This test is computed on a two-dimensional domain with $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,1.25], x^{2}\in[0,1.25]\}$.  
+We follow the initialization procedure in \citet{garrettHauck_2013}, and approximate the initial condition with an isotropic Gaussian distribution function
+\begin{equation}
+  f_{\mbox{\tiny G},0}
+  =\max\Big[\,\f{1}{8\,\pi\,\sigma_{\mbox{\tiny G}}^{2}}\,e^{-R^{2}/(2\,\sigma_{\mbox{\tiny G}}^{2})},10^{-4}\,\Big],
+\end{equation}
+where $R=|\vect{x}|$, and we use $\sigma_{\mbox{\tiny G}}=0.03$.  
+We run this test to a final time $t=1.0$.
+
 \subsection{Homogeneous Sphere}
+
+The homogeneous sphere test (e.g., \cite{smit_etal_1997}) considers of a sphere with radius $R$.  
+Inside the sphere (radius $<R$), the absorption opacity $\sigma_{\Ab}$ and the equilibrium distribution function $f_{0}$ are set to constant values.  
+The scattering opacity $\sigma_{\Scatt}$ is set to zero in this test (i.e., $\xi=1$).  
+Outside the sphere, the absorption opacity is zero.  
+The steady state solution, obtained by solving the transport equation in spherical symmetry, is given by
+\begin{equation}
+  f_{\mbox{\tiny A}}(r,\mu)=f_{0}\,\big(1-e^{-\chi_{0}\,s(r,\mu)}\big),
+  \label{eq:distributionHomogeneousSphere}
+\end{equation}
+where
+\begin{equation}
+  s(r,\mu)
+  =\left\{
+  \begin{array}{lll}
+    r\,\mu+R\,g(r,\mu) & \mbox{if}\quad r<R, & \mu\in[-1,+1], \\
+    2\,R\,g(r,\mu) & \mbox{if}\quad r \ge R, & \mu\in[(1-(R/r)^{2})^{1/2},+1], \\
+    0 & \mbox{otherwise},
+  \end{array}
+  \right.
+\end{equation}
+and $g(r,\mu)=[1-(r/R)^{2}(1-\mu^{2})]^{1/2}$.
+
+\begin{figure}[h]
+  \centering
+%  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Resolution_3}
+  \begin{tabular}{cc}
+%    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_1}
+%    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_2}
+  \end{tabular}
+   \caption{Homogeneous sphere problem: 32$^{3}$, 48$^{3}$, and 64$^{3}$}
+  \label{fig:HomogeneousSphere_Resolution}
+\end{figure}

### 2018-02-25 Documents/M1/realizableFermionicM1/sections/limiter.tex
Initial description of limiter.

\section{Realizability-Preserving Limiter}
\label{eq:limiter}

The bound-preserving DG-IMEX method developed in previous sections is designed to preserve realizability of the cell averaged moments, i.e., $\vect{\cM}_{\bK}\in\cR$, provided sufficiently accurate quadratures are used to integrate integrals in the DG method, specific CFL conditions are satisfied, and that the polynomial approximation $\vect{\cM}_{h}$, at time $t^{n}$, is realizable in a set of quadrature points in each element $\bK$.  
We denote this quadrature set by $S\subset\bK$.  
In the DG method, we use the limiter proposed by Zhang \& Shu \cite{zhangShu_2010a} for scalar conservation laws to enforce the bounds on the zeroth moment $\cJ$ (see also \cite{liuOsher_1996}).  
We replace the polynomial $\cJ_{h}^{n}(\vect{z})$ with the limited polynomial
\begin{equation}
  \tilde{\cJ}_{h}^{n}(\vect{z})
  =\vartheta_{1}\,\cJ_{h}^{n}(\vect{z})+(1-\vartheta_{1})\,\cJ_{\bK}^{n},
\end{equation}
where the limiter parameter $\vartheta_{1}$ is given by
\begin{equation}
  \vartheta_{1}
  =\min\Big\{\,\Big|\f{M-\cJ_{\bK}^{n}}{M_{S}-\cJ_{\bK}^{n}}\Big|,\Big|\f{m-\cJ_{\bK}^{n}}{m_{S}-\cJ_{\bK}^{n}}\Big|,1\,\Big\},
\end{equation}
with $m=0$ and $M=1$, and
\begin{equation}
  M_{S}=\max_{\vect{z}\in S}\cJ_{h}^{n}(\vect{z})
  \quad\text{and}\quad
  m_{S}=\min_{\vect{z}\in S}\cJ_{h}^{n}(\vect{z}).  
\end{equation}

In the next step, we ensure realizability of the moments by following the framework of \cite{zhangShu_2010b}, developed to ensure positivity of the pressure when solving the Euler equations of gas dynamics.  
We let $\widetilde{\vect{\cM}}_{h}^{n}=\big(\tilde{\cJ}_{h}^{n},\vect{\cH}_{h}^{n}\big)^{T}$.  
Then, if $\widetilde{\bcM}_{h}^{n}$ lies outside $\cR$ for any quadrature point $\vect{z}_{q}\in S$, i.e., $\gamma(\widetilde{\bcM}_{h}^{n})<0$, there exists an intersection point of the straight line, $\vect{s}_{q}(\xi)$, connecting $\vect{\cM}_{\bK}^{n}\in\cR$ and $\widetilde{\vect{\cM}}_{h}^{n}$ evaluated in the troubled quadrature point $\vect{z}_{q}$, denoted $\widetilde{\vect{\cM}}_{q}^{n}$, and the boundary of $\cR$.  
This line is given by the convex combination 
\begin{equation}
  \vect{s}_{q}(\xi)=\xi\,\widetilde{\vect{\cM}}_{q}^{n}+(1-\xi)\,\bcM_{\bK}^{n},
\end{equation}
where $\xi\in[0,1]$, and the intersection point $\xi_{q}$ is obtained by solving $\gamma(\bs_{q}(\xi))=0$ for $\xi$, using the bisection algorithm.  
We then replace the polynomial representation $\widetilde{\vect{\cM}}_{h}^{n}\to\widehat{\vect{\cM}}_{h}^{n}$, where
\begin{equation}
  \widehat{\vect{\cM}}_{h}^{n}(\vect{z})=\vartheta_{2}\,\widetilde{\vect{\cM}}_{h}^{n}(\vect{z})+(1-\vartheta_{2})\,\vect{\cM}_{\bK}^{n},
\end{equation}
and $\vartheta_{2}=\min_{q}\xi_{q}$ is the smallest $\xi$ obtained in the element by considering all the troubled quadrature points.

We note that the realizability-preserving limiter is conservative; i.e., preserves the cell-average.

### 2018-03-28 Documents/M1/realizableFermionicM1/sections/realizability.tex
Split section 3 in two: Moment Realizability... and Algebraic Moment Closures

--- 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
@@
-\section{Moment Realizability and Algebraic Closures for the Fermionic Two-Moment Model}
+\section{Moment Realizability for the Fermionic Two-Moment Model}
 \label{sec:realizability}
@@
 (Since we only concern with the angular dependence of $f$ in this section, we simplify the notation by suppressing the $\vect{z}$ and $t$ dependence and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.)
-
-\subsection{Moment Realizability}
 
@@
   \end{equation*}
-  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments}.  
-  Then $\vect{\cM}_{b}\in\cR$.  
+  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments},  then $\vect{\cM}_{b}\in\cR$.  
   \label{lem:correctionStep}
 \end{lemma}
-
-\begin{proof}
-  The proof follows along the same lines as the proof of Lemma~\ref{lem:implicitStep}.  
-\end{proof}
-
-\subsection{Algebraic Moment Closures}
-
-Algebraic moment closures for the two-moment model are computationally efficient as they provide the Eddington factor in Eq.~\eqref{eq:eddingtonTensor} in closed form as a function of the density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$.
-The family of algebraic closures we consider in this paper can be written in the form \cite{cernohorskyBludman_1994}
-\begin{equation}
-  \chi(\cJ,h)=\f{1}{3}+\f{2\,(1-\cJ)\,(1-2\cJ)}{3}\,\Theta\Big(\f{h}{1-\cJ}\Big),
-\end{equation}
-where the closure function $\Theta(x)$ varies with the specifics of the closure procedure.  
-We will consider two basic closure procedures in more detail below: the maximum entropy (ME) closure and the Kershaw (K) closure.
-
-\subsubsection{Maximum Entropy Closure}
-The basic principle behind the maximum entropy closure is that one can approximate the real fermion distribution with a distribution which having the Fermi-Dirac distribution form 
-\begin{equation}
-f(\omega)=\f{1}{e^{a + b\omega}+1}, 
-\end{equation} 
-meanwhile, maximizing the entropy function
-\begin{equation}
-S[f(\omega)] = (1-f)\log(1-f) + f\log f.
-\end{equation} 
-Given moments $\cJ$ and $\vect{\cH}$, a distribution satisfying above requirements can be found. Hence, $\vect{\cK}$.
-
-Chernohorsky \& Bludman \cite{cernohorskyBludman_1994}
-\begin{equation}
-  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny CB}}(x)
-  =x^{2}\,\big(\,3-x+3\,x^{2}\,\big)
-\end{equation}
-
-Banach \& Larecki \cite{banachLarecki_2017b}
-\begin{equation}
-  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny BL}}(x)
-  =\f{1}{8}\,\big(\,9\,x^{2}-5+\sqrt{33\,x^{4}-42\,x^{2}+25}\,\big)
-\end{equation}
-
-\subsubsection{Kershaw Closure}
-The basic principles behind Kershaw closure is that since $\cR$ is convex and bounded, every element in $\cR$ can be written as a convex combination of the elements on the realization boundary.
-For fermionic radiation, the boundary is based on the Heaviside step functions.
-
-Banach \& Larecki \cite{banachLarecki_2017a}
-\begin{equation}
-  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
-\end{equation}
-
-\subsubsection{Low Occupancy Limit}
-
-Figure~\ref{fig:MabWithDifferentClosure} illustrates the behavior of these four closure.
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{figures/MabWithBLME}
-    \includegraphics[width=0.5\textwidth]{figures/MabWithCBME} \\
-    \includegraphics[width=0.5\textwidth]{figures/MabWithBLKS}
-    \includegraphics[width=0.5\textwidth]{figures/MabWithMI}
-  \end{tabular}
-   \caption{Illustration of $\vect{\cM}_{ab}$ with four different closures: Banach \& Larecki maximum entropy closure (left top), Chernohorsky \& Bludman maximum entropy closure (right top), Kershaw closure (left bottom), and Minerbo closure (right bottom).
-   Total $10^{6}$ pairs of random Fermi-Dirac distribution were generated.
-   With these pairs, $\vect{\cM}_{ab}$ with different closures were calculated separately and marked with light-blue points.
-   Black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
-  \label{fig:MabWithDifferentClosure}
-\end{figure}
+The proof follows along the same lines as the proof of Lemma~\ref{lem:implicitStep} and is omitted.

### 2018-03-28 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Forgot to add algebraicClosures.tex.  Added appendix with some detail on the IMEX schemes discussed in the paper has been added (not complete)

\section{Algebraic Moment Closures}
\label{sec:algebraicClosure}

Algebraic moment closures for the two-moment model are computationally efficient as they provide the Eddington factor in Eq.~\eqref{eq:eddingtonTensor} in closed form as a function of the density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$.  
The family of algebraic closures we consider in this paper can be written in the form \cite{cernohorskyBludman_1994}
\begin{equation}
  \chi(\cJ,h)=\f{1}{3}+\f{2\,(1-\cJ)\,(1-2\cJ)}{3}\,\Theta\Big(\f{h}{1-\cJ}\Big),
  \label{eq:eddingtonFactor}
\end{equation}
where the closure function $\Theta(x)$ varies with the specifics of the closure procedure.  
We will consider two basic closure procedures in more detail below: the maximum entropy (ME) closure and the Kershaw (K) closure.

\paragraph{Low Occupancy Limit}
We note in passing that in the low occupancy limit ($\cJ\ll1$), the Eddington factor in Eq.~\eqref{eq:eddingtonFactor} becomes independent of $\cJ$; i.e.,
\begin{equation}
  \chi(\cJ,h)\to\chi_{0}(h)=\f{1}{3}+\f{2}{3}\,\Theta\big(h\big).  
  \label{eq:eddingtonFactorLow}
\end{equation}

\subsection{Maximum Entropy Closure}

The basic principle behind the maximum entropy closure is that one can approximate the real fermion distribution with a distribution which have the Fermi-Dirac distribution form 
\begin{equation}
f(\omega)=\f{1}{e^{a + b\omega}+1}, 
\end{equation} 
meanwhile maximize the entropy function
\begin{equation}
S[f(\omega)] = (1-f)\log(1-f) + f\log f.
\end{equation} 
Given moments $\cJ$ and $\vect{\cH}$, a distribution satisfying above requirements can be found. 
Therefore, the stress tensor $\vect{\cK}$.

One ME closure given by Chernohorsky \& Bludman \cite{cernohorskyBludman_1994} is
\begin{equation}
  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny CB}}(x)
  =x^{2}\,\big(\,3-x+3\,x^{2}\,\big).
\end{equation}

Another ME closure given by Banach \& Larecki \cite{banachLarecki_2017b} is
\begin{equation}
  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny BL}}(x)
  =\f{1}{8}\,\big(\,9\,x^{2}-5+\sqrt{33\,x^{4}-42\,x^{2}+25}\,\big).
\end{equation}

\subsection{Kershaw Closure}
The basic principle behind Kershaw closure is derived from the fact that $\cR$ is convex.
Due to the convexity, one can write any element in $\cR$ as a convex combination of the elements on the realization boundary. 
Therefore, Kershaw closure satisfies realizability inherently.
For fermionic radiation, the boundary is based on the Heaviside step functions.
Here we introduce a closure function $\Theta(x)$ given by Banach \& Larecki \cite{banachLarecki_2017a}:
\begin{equation}
  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
\end{equation}

Figure~\ref{fig:MabWithDifferentClosure} illustrates the behavior of these four closure.
As it shows, Minerbo closure (right bottom) is the only one among those four closures that does not preserve realizability.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/MabWithBLME}
    \includegraphics[width=0.5\textwidth]{figures/MabWithCBME} \\
    \includegraphics[width=0.5\textwidth]{figures/MabWithBLKS}
    \includegraphics[width=0.5\textwidth]{figures/MabWithMI}
  \end{tabular}
   \caption{Illustration of $\vect{\cM}_{ab}$ with four different closures: Banach \& Larecki maximum entropy closure (left top), Chernohorsky \& Bludman maximum entropy closure (right top), Kershaw closure (left bottom), and Minerbo closure (right bottom).
   Total $10^{6}$ pairs of random Fermi-Dirac distribution were generated.
   With these pairs, $\vect{\cM}_{ab}$ with different closures were calculated separately and marked with light-blue points.
   Black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
  \label{fig:MabWithDifferentClosure}
\end{figure}

### 2018-03-28 Documents/M1/realizableFermionicM1/sections/appendix.tex
Forgot to add algebraicClosures.tex.  Added appendix with some detail on the IMEX schemes discussed in the paper has been added (not complete)

\appendix

\section{Butcher Tableau for IMEX Schemes}

For easy reference, we include the Butcher tableau for the IMEX schemes considered in this paper, which can be written in the standard double Butcher tableau
\begin{equation}
  \begin{array}{c | c}
    \tilde{\vect{c}} & \tilde{A} \\
    \hline
    & \tilde{\vect{w}}^{T}
  \end{array}
  \qquad
  \begin{array}{c | c}
    \vect{c} & A \\
    \hline
    \alpha & \vect{w}^{T}
  \end{array},
\end{equation}
where the \emph{explicit tableau} (left; components adorned with a tilde) represent the explicit part of the IMEX scheme, and the \emph{implicit tableau} (right; unadorned components) represent the implicit part of the IMEX scheme.  
For $s$ stages, $\tilde{A}=(\tilde{a}_{ij})$, $\tilde{a}_{ij}=0$ for $j\ge i$, and $A=(a_{ij})$, $a_{ij}=0$ for $j>i$, are $s\times s$ matrices, and $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$.  
The vectors $\tilde{\vect{c}}=(\tilde{c}_{1},\ldots,\tilde{c}_{s})^{T}$ and $\vect{c}=(c_{1},\ldots,c_{s})^{T}$, used for non autonomous systems, satisfy $\tilde{c}_{i}=\sum_{j=1}^{i-1}\tilde{a}_{ij}$ and $c_{i}=\sum_{j=1}^{i}a_{ij}$.  
For the implicit tableau, we have included the scalar $\alpha$, used for the correction step in Eq.~\eqref{eq:imexCorrection}.

\paragraph{IMEX PA2}

A second-order accurate, positivity-preserving IMEX scheme of type $A$ (the matrix $A$ is invertible) was given in \cite{hu_etal_2017}.  
We refer to this scheme as IMEX PA2.  
For this scheme, the non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.7369502715, \nonumber \\
  \tilde{a}_{31} &= 0.3215281691, \quad \tilde{a}_{32} = 0.6784718309, \nonumber \\
  a_{11} &= 0.6286351712, \nonumber \\
  a_{21} &= 0.2431004655, \quad a_{22} = 0.1959392570, \nonumber \\
  a_{31} &= 0.4803651051, \quad a_{32} = 0.0746432814, \quad a_{33} = 0.4449916135. \nonumber
\end{align}
The coefficient in the correction step is $\alpha = 0.2797373792$.  
This scheme is globally stiffly accurate (GSA), so that $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.

\paragraph{IMEX PA2+}

\paragraph{IMEX PC2}

\paragraph{IMEX RKCB2}

\paragraph{IMEX SSP2332}

\paragraph{SSPRK2 and SSPRK3}

### 2018-03-28 Documents/M1/realizableFermionicM1/sections/numerical.tex
Some work in numerical.tex

@@
 
-Periodic domain $D=\{x:x\in[0,1]\}$.  
-The initial condition is given by
+The first test involves the streaming part only, and does not include any collisions ($\sigma_{\Ab}=\sigma_{\Scatt}=0$).  
+We consider a periodic domain $D=\{x:x\in[0,1]\}$, and let the initial condition be given by
 \begin{equation}
@@
 \end{equation}
+We evolve until $t=10$, when the sine wave has completed 10 crossings of the computational domain.  
+We use polynomials of degree $k=2$ for the spatial discretization (third-order spatial accuracy), and set the time step as $\Delta t = $.  
+We vary the number of elements from $??$ to $??$ and compute errors for various time stepping schemes.
+
+\ee{Include figure of error versus number of elements for various schemes.}
 
@@
 \end{equation}
-so that $\vect{\cM}=\big(0.5\,(1+\delta),0.25\,(1-\delta)\big)^{T}$ for $x\le x_{\mbox{\tiny D}}$, and $\vect{\cM}=\big(\delta,0\big)^{T}$ for $x> x_{\mbox{\tiny D}}$.  
+so that $\vect{\cM}=\big(0.5\,(1+\delta),0.25\,(1-\delta)\big)^{T}$ for $x\le x_{\mbox{\tiny D}}$, and $\vect{\cM}=\big(\delta,0\big)^{T}$ for $x> x_{\mbox{\tiny D}}$, where $\delta>0$ is a small parameter ($\delta\ll1$).
 We let $\delta=10^{-8}$.  
@@
 
-The line source benchmark \citep[cf.][]{brunner_2002,garrettHauck_2013} is a challenging test for approximate transport algorithms.  
+The line source benchmark (cf. \cite{brunner_2002,garrettHauck_2013}) is a challenging test for approximate transport algorithms.  
 In cylindrical coordinates, it consists of an initial delta function particle distribution in radius; i.e., $f_{0}=\delta(R)/4\,\pi$.  
@@
 This test is computed on a two-dimensional domain with $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,1.25], x^{2}\in[0,1.25]\}$.  
-We follow the initialization procedure in \citet{garrettHauck_2013}, and approximate the initial condition with an isotropic Gaussian distribution function
+We follow the initialization procedure in \cite{garrettHauck_2013}, and approximate the initial condition with an isotropic Gaussian distribution function
 \begin{equation}

### 2018-03-29 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added coeff for IMEXPA2+.

@@
 \end{align}
-The coefficient in the correction step is $\alpha = 0.2797373792$.  
+The coefficient in the correction step is $\alpha = 0.2797373792$ and the CFL constant is $c_{sch} = 0.5247457524$.
 This scheme is globally stiffly accurate (GSA), so that $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.
@@
 
+We here give another second-order accurate, sitivity-preserving IMEX scheme of type $A$, named IMEX PA2+, which has a lager $c_{sch}$ than IMEX PA2.
+It was chosen from $10^{6}$ coefficient groups that satisfy both the second-order accuracy requirement and the positivity-preserving requirement.
+IMEX PA2+ is the one has the largest ($C_{sch} = 0.895041066934$). Its non-zero components of $\tilde{A}$ and $A$ are given by
+\begin{align}
+  \tilde{a}_{21} &= 0.909090909090909, \nonumber \\
+  \tilde{a}_{31} &= 0.450000000000000, \quad \tilde{a}_{32} = 0.550000000000000, \nonumber \\
+  a_{11} &= 0.521932391842510, \nonumber \\
+  a_{21} &= 0.479820781424967, \quad a_{22} = 0.002234534340252, \nonumber \\
+  a_{31} &= 0.499900000000000, \quad a_{32} = 0.001100000000000, \quad a_{33} = 0.499000000000000. \nonumber
+\end{align}
+The coefficient in the correction step is $\alpha = 0.260444263529413$.  
 \paragraph{IMEX PC2}

### 2018-04-02 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added more description for IMEX PA2+.
Added the details of IMEX PC2.

@@
 It was chosen from $10^{6}$ coefficient groups that satisfy both the second-order accuracy requirement and the positivity-preserving requirement.
-IMEX PA2+ is the one has the largest ($C_{sch} = 0.895041066934$). Its non-zero components of $\tilde{A}$ and $A$ are given by
+IMEX PA2+ is the one has the largest ($c_{sch} = 0.895041066934$). 
+Its non-zero components of $\tilde{A}$ and $A$ are given by
 \begin{align}
@@
 The coefficient in the correction step is $\alpha = 0.260444263529413$.  
+This scheme is also a GSA scheme: $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.
+
 \paragraph{IMEX PC2}
+
+A second-order accurate, positivity-preserving, diffusion accurate IMEX scheme was given in \cite{mcclareen_2008}.  
+We refer to this scheme as IMEX PC2.  
+Its non-zero components of $\tilde{A}$ and $A$ are given by
+\begin{align}
+  \tilde{a}_{21} &= 0.5, \nonumber \\
+  \tilde{a}_{32} &= 1, \nonumber \\
+  a_{22} &= 0.5, \nonumber \\
+  a_{33} &= 1.0. \nonumber
+\end{align}
+And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.
+A common choice of this scheme is $c_{sch} = 0.3$.
 

### 2018-04-02 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added the details of IMEX RKCB2.
Added the details of IMEX SSP2332.

@@
 
+A second-order accurate, diffusion accurate, L-stable, strong-stability-preserving IMEX scheme was given in \cite{cavaglieriBewley2015}.  
+We refer to this scheme as IMEX RKCB2.  
+Its non-zero components of $\tilde{A}$ and $A$ are given by
+\begin{align}
+  \tilde{a}_{21} &= 2/5, \nonumber \\
+  \tilde{a}_{32} &= 1, \nonumber \\
+  a_{22} &= 2/5, \nonumber \\
+  a_{32} &= 5/6, \quad a_{33} = 1/6. \nonumber
+\end{align}
+And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
+CFL ...
+
 \paragraph{IMEX SSP2332}
 
+A second-order accurate, diffusion accurate, L-stable, strong-stability-preserving IMEX scheme was given in \cite{pareschiRusso_2005}.  
+We refer to this scheme as IMEX SSP2332.  
+Its non-zero components of $\tilde{A}$ and $A$ are given by
+\begin{align}
+  \tilde{a}_{21} &= 1/2, \nonumber \\
+  \tilde{a}_{31} &= 1/2, \quad \tilde{a}_{32} = 1/2, \nonumber \\
+  a_{11} &= 1/4, \nonumber \\
+  a_{22} &= 1/4, \nonumber \\
+  a_{31} &= 1/3, \quad a_{32} = 1/3, \quad a_{33} = 1/3. \nonumber
+\end{align}
+And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
+CFL ...
+
 \paragraph{SSPRK2 and SSPRK3}

### 2018-04-02 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added the details of SSPRK2 and SSPRK3.
Adjustments to the text on IMEX AP2+

@@
 
-We here give another second-order accurate, sitivity-preserving IMEX scheme of type $A$, named IMEX PA2+, which has a lager $c_{sch}$ than IMEX PA2.
-It was chosen from $10^{6}$ coefficient groups that satisfy both the second-order accuracy requirement and the positivity-preserving requirement.
-IMEX PA2+ is the one has the largest ($c_{sch} = 0.895041066934$). 
-Its non-zero components of $\tilde{A}$ and $A$ are given by
+We have found another second-order accurate, positivity-preserving IMEX scheme of type $A$, which we refer to as IMEX PA2+.  
+This scheme allows for has a larger $c_{sch}$ than IMEX PA2 (i.e., a larger time step for positivity).  
+The scheme chosen by random sampling of the parameter space, and was the scheme with the largest $c_{sch}$ that satisfied both the order conditions for second order accuracy and possessed the positivity-preserving property.
+For IMEX PA2+, ($c_{sch} = 0.895041066934$). 
+The non-zero components of $\tilde{A}$ and $A$ are given by
 \begin{align}
@@
 The coefficient in the correction step is $\alpha = 0.260444263529413$.  
-This scheme is also a GSA scheme: $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.
+This scheme is also GSA; $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.
 
@@
 \paragraph{SSPRK2 and SSPRK3}
+
+A second-order accurate, strong-stability-preserving explicit Runge-Kutta scheme, referred as SSPRK2, has the following non-zero components:
+\begin{align}
+  \tilde{a}_{21} &= 1, \nonumber \\
+  \tilde{w}_{1} &= 1/2, \quad \tilde{w}_{2} = 1/2. \nonumber 
+\end{align}
+A third-order accurate, strong-stability-preserving explicit Runge-Kutta scheme, was referred as SSPRK3.
+It has the following non-zero components:
+\begin{align}
+  \tilde{a}_{21} &= 1, \nonumber \\
+  \tilde{a}_{31} &= 1/4, \quad \tilde{a}_{32} = 1/4, \nonumber \\
+  \tilde{w}_{1} &= 1/6, \quad \tilde{w}_{2} = 1/6, \quad \tilde{w}_{3} =2/3 \nonumber
+\end{align}

### 2018-04-03 Documents/M1/realizableFermionicM1/sections/appendix.tex
Some adjustments to text in appendix

@@
 We have found another second-order accurate, positivity-preserving IMEX scheme of type $A$, which we refer to as IMEX PA2+.  
-This scheme allows for has a larger $c_{sch}$ than IMEX PA2 (i.e., a larger time step for positivity).  
-The scheme chosen by random sampling of the parameter space, and was the scheme with the largest $c_{sch}$ that satisfied both the order conditions for second order accuracy and possessed the positivity-preserving property.
+This scheme allows for has a larger $c_{sch}$ than IMEX PA2 (i.e., a larger time step while still maintaining positivity).  
+The scheme chosen from random sampling of the IMEX parameter space, and was the scheme with the largest $c_{sch}$ that satisfied both the order conditions for second order accuracy and possessed the positivity-preserving property.
 For IMEX PA2+, ($c_{sch} = 0.895041066934$). 
@@
 
-A second-order accurate, positivity-preserving, diffusion accurate IMEX scheme was given in \cite{mcclareen_2008}.  
-We refer to this scheme as IMEX PC2.  
-Its non-zero components of $\tilde{A}$ and $A$ are given by
+Another positivity-preserving IMEX scheme was given in \cite{mcclareen_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclareen_2008}).  
+This scheme can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
+The non-zero components of $\tilde{A}$ and $A$ are given by
 \begin{align}
@@
 
-A second-order accurate, diffusion accurate, L-stable, strong-stability-preserving IMEX scheme was given in \cite{cavaglieriBewley2015}.  
+We compare the performance of the positivity-preserving IMEX schemes with two other, non-positive, schemes.  
+The first one is the second-order accurate IMEX scheme given in \cite{cavaglieriBewley2015}.  
 We refer to this scheme as IMEX RKCB2.  
-Its non-zero components of $\tilde{A}$ and $A$ are given by
+The non-zero components of $\tilde{A}$ and $A$ are given by
 \begin{align}
@@
 
-A second-order accurate, diffusion accurate, L-stable, strong-stability-preserving IMEX scheme was given in \cite{pareschiRusso_2005}.  
+The second scheme we use for comparison is the second-order accurate IMEX scheme given in \cite{pareschiRusso_2005}.  
 We refer to this scheme as IMEX SSP2332.  
-Its non-zero components of $\tilde{A}$ and $A$ are given by
+The non-zero components of $\tilde{A}$ and $A$ are given by
 \begin{align}

### 2018-04-03 Documents/M1/realizableFermionicM1/sections/appendix.tex
Some adjustments to paragraph on SSPRK methods.  Added reference to gottlieb at al.

@@
 
-A second-order accurate, strong-stability-preserving explicit Runge-Kutta scheme, referred as SSPRK2, has the following non-zero components:
+To compare the performance of the IMEX schemes in the streaming limit (no collisions), we also compute results with explicit strong stability-preserving Runge-Kutta methods \cite{gottlieb_etal_2001}.
+(All elements of the implicit Butcher tableau are zero.)  
+The optimal second-order accurate, strong-stability-preserving Runge-Kutta scheme (SSPRK2) has the following non-zero components
 \begin{align}
@@
 \end{align}
-A third-order accurate, strong-stability-preserving explicit Runge-Kutta scheme, was referred as SSPRK3.
-It has the following non-zero components:
+The optimal third-order accurate, strong-stability-preserving Runge-Kutta scheme (SSPRK3) has the following non-zero components
 \begin{align}
@@
   \tilde{a}_{31} &= 1/4, \quad \tilde{a}_{32} = 1/4, \nonumber \\
-  \tilde{w}_{1} &= 1/6, \quad \tilde{w}_{2} = 1/6, \quad \tilde{w}_{3} =2/3 \nonumber
+  \tilde{w}_{1} &= 1/6, \quad \tilde{w}_{2} = 1/6, \quad \tilde{w}_{3} =2/3. \nonumber
 \end{align}

### 2018-04-11 Documents/M1/realizableFermionicM1/sections/imex.tex
Additions to paper
fixed typo in specification of IMEX scheme
Some work on results.  Added figures.
Reverted correction step back to only include collision term.
Working on text discussing IMEX schemes.

--- 2018-02-02 Documents/M1/realizableFermionicM1/sections/imex.tex
@@
 
-The semi-discretization of the moment equations with the DG method given in Eq.~\eqref{eq:semidiscreteDG} results in a system of ordinary differential equations (ODEs) in each element of the form
+In this section we summarize and discuss the class of IMEX schemes we consider for the realizability-preserving DG-IMEX method for the two-moment model developed in Section~\ref{sec:realizableDGIMEX}.
+The semi-discretization of the moment equations with the DG method given by Eq.~\eqref{eq:semidiscreteDG} results in a system of ordinary differential equations (ODEs) in each element of the form
 \begin{equation}
@@
 
-In the application of interest to us, the collision term is stiff ($\tau\ll1$) and must be treated with implicit methods, while we can resolve the time scales induced by the transport term, which we will treat with explicit methods; i.e., we will use IMEX methods \cite{pareschiRusso_2005}.
+In the application of interest to us, the collision term is stiff ($\tau\ll1$) in regions of the computational domain and must be treated with implicit methods, while we can resolve the time scales induced by the transport term, which we will treat with explicit methods; i.e., we will use IMEX methods \cite{pareschiRusso_2005}.
+We would like to employ IMEX schemes that preserve realizability of the moments (subject to a time step governed by the transport term).  
 Until recently, high-order (second or higher order temporal accuracy) positivity-preserving IMEX methods with time step restrictions solely due to the transport operator were not known.  
 Chertock et al. \cite{chertock_etal_2015} presented second order accurate IMEX schemes with a correction step.  
-The correction step includes the transport operator, and positivity is subject to a time step restriction $\dt\propto1/\sqrt{\tau}$.  
-More recently, Hu et al. \cite{hu_etal_2017}, presented new IMEX schemes for a class of BGK-type collision operators with a correction step that does not include the transport operator.  
-In this case, positivity is only subject to time step restrictions stemming from the transport operator.  
-These IMEX schemes take the following form \cite{hu_etal_2017}
+The correction step in \cite{chertock_etal_2015} includes the transport operator, and we have found that realizability is then subject to a time step restriction that scales as $\dt\propto1/\sqrt{\tau}$, which may become too restrictive.
+More recently, Hu et al.
+\cite{hu_etal_2017}, presented similar IMEX schemes for problems involving BGK-type collision operators, but with a correction step that does not include the transport operator.
+In this case, positivity is only subject to time step restrictions stemming from the transport operator, which is more attractive for our target application.  
+These second order accurate, $s$-stage IMEX schemes take the following form \cite{hu_etal_2017}
 \begin{align}
@@
   &=\vect{u}^{n}
-  +\dt\sum_{i=1}^{j-1}\tilde{\alpha}_{ij}\,\vect{\cT}(\vect{u}^{(j)})
-  +\dt\sum_{i=1}^{j}\alpha_{ij}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(j)}),
+  +\dt\sum_{j=1}^{i-1}\tilde{a}_{ij}\,\vect{\cT}(\vect{u}^{(j)})
+  +\dt\sum_{j=1}^{i}a_{ij}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(j)}),
   \quad i=1,\ldots,s, \label{imexStages} \\
@@
 \end{align}
-To prove the positivity-preserving property of the IMEX scheme, Hu et al. \cite{hu_etal_2017} rewrite the stage values in Eq.~\eqref{imexStages} as
+where, as in standard IMEX schemes, $(\tilde{a}_{ij})$ and $(a_{ij})$, components of $s\times s$ matrices $\tilde{A}$ and $A$, respectively, and the vectors $\vect{w}^{T}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ must satisfy certain order conditions \cite{pareschiRusso_2005}.
+The coefficient in the correction step is positive, $\alpha>0$, and $\vect{\cQ}'$ is the Frechet derivative of the collision term, and can be evaluated using any of the stage values ($\vect{u}^{n}$, $\vect{u}^{(i)}$, or $\tilde{\vect{u}}^{n+1}$).
+For second order temporal accuracy, the order conditions are
+\begin{equation}
+  \sum_{i=1}^{s}\tilde{w}_{i}=\sum_{i=1}^{s}w_{i}=1,
+\end{equation}
+and
+\begin{equation}
+  \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}
+  =\sum_{i=1}^{s}\tilde{w}_{i}\,c_{i}
+  =\sum_{i=1}^{s}w_{i}\,\tilde{c}_{i}
+  =\sum_{i=1}^{s}w_{i}\,c_{i}-\alpha=\f{1}{2}, 
+\end{equation}
+where $\tilde{c}_{i}$ and $c_{i}$ are given in \ref{app:butcherTables}.  
+For globally stiffly accurate (GSA) IMEX schemes, $\tilde{w}_{i}=\tilde{a}_{si}$ and $w_{i}=a_{si}$ for $i=\{1,\ldots,s\}$, so that $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$.
+
+To prove the positivity-preserving property of the IMEX scheme, Hu et al. \cite{hu_etal_2017} rewrite the stage values in Eq.~\eqref{imexStages} in the following form
 \begin{equation}
   \vect{u}^{(i)}
-  =c_{i0}\,\vect{u}^{n}+\sum_{j=1}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
-  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{Q}(\vect{u}^{(i)}),
+  =\sum_{j=0}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
+  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{Q}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
   \label{eq:imexStagesRewrite}
 \end{equation}
-where $c_{i0}+\sum_{j=1}^{i-1}c_{ij}=1$.
+where $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$ (see \cite{hu_etal_2017} for details).  
+In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.  
+Two types of IMEX schemes are considered: type A and type ARS.  
+For IMEX schemes of type A, the matrix $A$ is invertible.  
+For IMEX schemes of type ARS, the first column of $A$ is zero and the submatrix consisting of the last $s-1$ rows and columns of $A$ is invertible.  
+For type A schemes, $\tilde{c}_{i0}=0$, and the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.
+For type ARS schemes, $c_{i1}=\tilde{c}_{i1}=0$, and positivity follows from requiring $a_{ii}>0$ and $c_{i0},\tilde{c}_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$ for $i=3,\ldots,s$, $j=2,\ldots,i-1$.
+Such coefficients were given in \cite{hu_etal_2017} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
+Importantly, the coefficients $c_{ij}$ satisfy $\sum_{j=0}^{i-1}c_{ij}=1$, which implies that, if the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} is positive for all $i=2,\ldots,s$, $j=0,\ldots,i-1$, positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
+Thus, if the explicit update with the transport operator is positive for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is positivity preserving for a time step $\dt\le c_{\mbox{\tiny Sch}}\,\dt_{\mbox{\tiny Ex}}$, where
+\begin{equation}
+  c_{\mbox{\tiny Sch}}=\min_{ij}\,\f{1}{\hat{c}_{ij}}.  
+\end{equation}
+(Positivity of $\vect{u}^{(i)}$ requires the implicit solve to preserve positivity.)  
+Hu et al. provide examples of GSA positivity-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
+In \ref{app:butcherTables}, we provide another example of a type A scheme (scheme PA2+), but with a significantly larger $c_{\mbox{\tiny Sch}}$.
 
-For globally stiffly accurate (GSA) IMEX schemes $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$
+Unfortunately, the correction step in Eq.~\eqref{eq:imexCorrection} deteriorates the accuracy of the IMEX scheme when applied to the moment equations in the diffusion limit.  
+This is because in the diffusion limit, to leading order in $\tau$, we have $\vect{\cH}=-\f{1}{3}\,\tau\,\nabla\cJ$, which is due to a balance between the transport term and the collision term in the equation for the particle flux.
+The absence of the transport operator in the correction step, destroys this balance.  
+(We demonstrate the inferior performance of IMEX schemes with the correction step given by Eq.~\eqref{eq:imexCorrection} in the diffusion limit in Section~\ref{sec:smoothProblems}.)
+
+\ee{Can we prove that it is impossible to find a second-order accurate, positivity-preserving IMEX scheme that is accurate in the diffusion limit?}

### 2018-04-11 Documents/M1/realizableFermionicM1/sections/imex.tex
More work in imex

@@
 
-In this section we summarize and discuss the class of IMEX schemes we consider for the realizability-preserving DG-IMEX method for the two-moment model developed in Section~\ref{sec:realizableDGIMEX}.
+In this section we summarize and discuss the class of IMEX schemes we consider for the realizability-preserving DG-IMEX method for the two-moment model developed in Section~\ref{sec:realizableDGIMEX} (see also \ref{app:butcherTables} for additional details).
 The semi-discretization of the moment equations with the DG method given by Eq.~\eqref{eq:semidiscreteDG} results in a system of ordinary differential equations (ODEs) in each element of the form
@@
   \sum_{i=1}^{s}\tilde{w}_{i}=\sum_{i=1}^{s}w_{i}=1,
+  \label{orderConditions1}
 \end{equation}
@@
   =\sum_{i=1}^{s}w_{i}\,c_{i}-\alpha=\f{1}{2}, 
+  \label{orderConditions2}
 \end{equation}
@@
 For IMEX schemes of type A, the matrix $A$ is invertible.  
-For IMEX schemes of type ARS, the first column of $A$ is zero and the submatrix consisting of the last $s-1$ rows and columns of $A$ is invertible.  
+For IMEX schemes of type ARS, the first column of $A$ is zero and the submatrix consisting of the last $s-1$ rows and columns of $A$, $\hat{A}$, is invertible.  
 For type A schemes, $\tilde{c}_{i0}=0$, and the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.
@@
 Such coefficients were given in \cite{hu_etal_2017} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.
-Importantly, the coefficients $c_{ij}$ satisfy $\sum_{j=0}^{i-1}c_{ij}=1$, which implies that, if the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} is positive for all $i=2,\ldots,s$, $j=0,\ldots,i-1$, positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
+
+Importantly, the coefficients $c_{ij}$ in Eq.~\eqref{eq:imexStagesRewrite} satisfy $\sum_{j=0}^{i-1}c_{ij}=1$.  
+This implies that, if the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} is positive for all $i=2,\ldots,s$, $j=0,\ldots,i-1$, positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
 Thus, if the explicit update with the transport operator is positive for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is positivity preserving for a time step $\dt\le c_{\mbox{\tiny Sch}}\,\dt_{\mbox{\tiny Ex}}$, where
@@
   c_{\mbox{\tiny Sch}}=\min_{ij}\,\f{1}{\hat{c}_{ij}}.  
+  \label{eq:imexCFL}
 \end{equation}
+It is desirable to make $c_{\mbox{\tiny Sch}}$ as large (close to $1$) as possible.  
 (Positivity of $\vect{u}^{(i)}$ requires the implicit solve to preserve positivity.)  
-Hu et al. provide examples of GSA positivity-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
-In \ref{app:butcherTables}, we provide another example of a type A scheme (scheme PA2+), but with a significantly larger $c_{\mbox{\tiny Sch}}$.
+In \cite{hu_etal_2017}, Hu et al. provide examples of GSA, positivity-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
+In \ref{app:butcherTables}, we provide another example of a type A scheme (scheme PA2+), with a significantly larger $c_{\mbox{\tiny Sch}}$.
 
-Unfortunately, the correction step in Eq.~\eqref{eq:imexCorrection} deteriorates the accuracy of the IMEX scheme when applied to the moment equations in the diffusion limit.  
-This is because in the diffusion limit, to leading order in $\tau$, we have $\vect{\cH}=-\f{1}{3}\,\tau\,\nabla\cJ$, which is due to a balance between the transport term and the collision term in the equation for the particle flux.
+Unfortunately, the correction step in Eq.~\eqref{eq:imexCorrection} deteriorates the accuracy of the IMEX scheme when applied to the moment equations in the diffusion limit ($\xi=0$, $\tau\ll 1$).  
+In the diffusion limit, to leading order in $\tau$, we have $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$, which is due to a balance between the transport term and the collision term in the equation for the particle flux $\vect{\cH}$.
 The absence of the transport operator in the correction step, destroys this balance.  
-(We demonstrate the inferior performance of IMEX schemes with the correction step given by Eq.~\eqref{eq:imexCorrection} in the diffusion limit in Section~\ref{sec:smoothProblems}.)
+We demonstrate the inferior performance of IMEX schemes with the correction step given by Eq.~\eqref{eq:imexCorrection} in the diffusion limit in Section~\ref{sec:smoothProblems}.  
+We have also implemented one of IMEX schemes in Chertock et al.
+\cite{chertock_etal_2015}, where the transport operator is included in the correction step, and found it to perform very well in the diffusion limit.
+However, we have not been able to prove sufficiently general realizability-preserving properties with this approach, without invoking a too severe time step restriction.
 
-\ee{Can we prove that it is impossible to find a second-order accurate, positivity-preserving IMEX scheme that is accurate in the diffusion limit?}
+We therefore proceed to design positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
+To this end we define the vectors $\vec{\cJ}=(\cJ^{(1)},\ldots,\cJ^{(s)})^{T}$ and $\vec{\vect{\cH}}=(\vect{\cH}^{(1)},\ldots,\vect{\cH}^{(s)})^{T}$.  
+In the context of IMEX schemes, the diffusion limit balance implies that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ must hold for the stage values in Eq.~\eqref{imexStages}.
+For the final stage (i=s), 
+\begin{equation}
+  \vect{\cH}^{(s)}=-\f{1}{3}\,\tau\,\vect{e}_{s}^{T}A^{-1}\tilde{A}\vect{e}\,\nabla\cJ^{n}+\cO(\dt\,\tau),
+\end{equation}
+where $\vect{e}_{s}=(0,\ldots,0,1)^{T}$ and $\vect{e}=(1,\ldots,1)^{T}$.  
+Thus, for $\vect{\cH}^{(s)}$ to be accurate in the diffusion limit, we require the IMEX coefficients to satisfy
+\begin{equation}
+  \vect{e}_{s}^{T}A^{-1}\tilde{A}\vect{e} = 1.
+  \label{eq:diffusionCondition}
+\end{equation}
+Unfortunately, this requirement, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$) and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$ results in too many constraints.
+(\ee{Can we prove that it is impossible to find a second-order accurate, positivity-preserving IMEX scheme that is accurate in the diffusion limit?})
+To reduce the number of constraints, we relax the requirement of overall second order accuracy of the IMEX scheme.  
+Instead, we only require the scheme to be second order accurate in the streaming limit ($\vect{\cQ}=0$).  
+This is similar to the IMEX scheme given in \cite{mcclareen_2008} (see scheme PC2 in \ref{app:butcherTables}).

### 2018-04-12 Documents/M1/realizableFermionicM1/sections/imex.tex
More work on the imex section.

@@
 \end{equation}
-The transport term $\vect{\cT}$ is due to the second and third term in the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision term $\vect{\cQ}$ is due to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
+Thus, for $\phi_{1}=1$, the first components of $\vect{u}$ are the cell averaged moments.  
+In Eq.~\eqref{eq:ode}, the transport term $\vect{\cT}$ is due to the second and third term in the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision term $\vect{\cQ}$ is due to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
 
-In the application of interest to us, the collision term is stiff ($\tau\ll1$) in regions of the computational domain and must be treated with implicit methods, while we can resolve the time scales induced by the transport term, which we will treat with explicit methods; i.e., we will use IMEX methods \cite{pareschiRusso_2005}.
+In the applications of interest to us, the collision term is stiff ($\tau\ll1$) in regions of the computational domain and must be treated with implicit methods, while we can resolve the time scales induced by the transport term, which we will treat with explicit methods; i.e., we will use IMEX methods \cite{pareschiRusso_2005}.
 We would like to employ IMEX schemes that preserve realizability of the moments (subject to a time step governed by the transport term).  
 Until recently, high-order (second or higher order temporal accuracy) positivity-preserving IMEX methods with time step restrictions solely due to the transport operator were not known.  
-Chertock et al. \cite{chertock_etal_2015} presented second order accurate IMEX schemes with a correction step.  
+Chertock et al. \cite{chertock_etal_2015} presented second-order accurate IMEX schemes with a correction step.  
 The correction step in \cite{chertock_etal_2015} includes the transport operator, and we have found that realizability is then subject to a time step restriction that scales as $\dt\propto1/\sqrt{\tau}$, which may become too restrictive.
@@
 In this case, positivity is only subject to time step restrictions stemming from the transport operator, which is more attractive for our target application.  
-These second order accurate, $s$-stage IMEX schemes take the following form \cite{hu_etal_2017}
+These second-order accurate, $s$-stage IMEX schemes take the following form \cite{hu_etal_2017}
 \begin{align}
@@
 where, as in standard IMEX schemes, $(\tilde{a}_{ij})$ and $(a_{ij})$, components of $s\times s$ matrices $\tilde{A}$ and $A$, respectively, and the vectors $\vect{w}^{T}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ must satisfy certain order conditions \cite{pareschiRusso_2005}.
-The coefficient in the correction step is positive, $\alpha>0$, and $\vect{\cQ}'$ is the Frechet derivative of the collision term, and can be evaluated using any of the stage values ($\vect{u}^{n}$, $\vect{u}^{(i)}$, or $\tilde{\vect{u}}^{n+1}$).
-For second order temporal accuracy, the order conditions are
+The coefficient in the correction step is positive, $\alpha>0$, and $\vect{\cQ}'$ is the Fr{\'e}chet derivative of the collision term evaluated at $\vect{u}^{*}$.  
+For second-order accuracy, $\vect{Q}$ can be evaluated using any of the stage values ($\vect{u}^{n}$, $\vect{u}^{(i)}$, or $\tilde{\vect{u}}^{n+1}$).  
+For second-order temporal accuracy, the order conditions are
 \begin{equation}
@@
 where $\tilde{c}_{i}$ and $c_{i}$ are given in \ref{app:butcherTables}.  
-For globally stiffly accurate (GSA) IMEX schemes, $\tilde{w}_{i}=\tilde{a}_{si}$ and $w_{i}=a_{si}$ for $i=\{1,\ldots,s\}$, so that $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$.
+For globally stiffly accurate (GSA) IMEX schemes, $\tilde{w}_{i}=\tilde{a}_{si}$ and $w_{i}=a_{si}$ for $i=1,\ldots,s$, so that $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$.
 
@@
 Such coefficients were given in \cite{hu_etal_2017} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
+It was also proven that $s=3$ and $s=4$ are the necessary number of stages for GSA second-order positivity-preserving IMEX schemes of type A and type ARS, respectively.
 
@@
 In \cite{hu_etal_2017}, Hu et al. provide examples of GSA, positivity-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
-In \ref{app:butcherTables}, we provide another example of a type A scheme (scheme PA2+), with a significantly larger $c_{\mbox{\tiny Sch}}$.
+In \ref{app:butcherTables}, we provide another example of a type A scheme (scheme PA2+), with a significantly larger $c_{\mbox{\tiny Sch}}$ (a factor of about $1.7$).
 
@@
 
-We therefore proceed to design positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
+We therefore proceed to design GSA positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
 To this end we define the vectors $\vec{\cJ}=(\cJ^{(1)},\ldots,\cJ^{(s)})^{T}$ and $\vec{\vect{\cH}}=(\vect{\cH}^{(1)},\ldots,\vect{\cH}^{(s)})^{T}$.  
-In the context of IMEX schemes, the diffusion limit balance implies that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ must hold for the stage values in Eq.~\eqref{imexStages}.
-For the final stage (i=s), 
+In the context of IMEX schemes, the diffusion limit balance implies that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold to relate the stage values in Eq.~\eqref{imexStages}.
+For the final stage ($i=s$), 
 \begin{equation}
@@
 \end{equation}
-Unfortunately, this requirement, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$) and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$ results in too many constraints.
-(\ee{Can we prove that it is impossible to find a second-order accurate, positivity-preserving IMEX scheme that is accurate in the diffusion limit?})
-To reduce the number of constraints, we relax the requirement of overall second order accuracy of the IMEX scheme.  
-Instead, we only require the scheme to be second order accurate in the streaming limit ($\vect{\cQ}=0$).  
-This is similar to the IMEX scheme given in \cite{mcclareen_2008} (see scheme PC2 in \ref{app:butcherTables}).
+Unfortunately, this requirement, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$ results in too many constraints.
+(\ee{Can we prove that it is impossible to find a second-order accurate, positivity-preserving IMEX scheme that is accurate in the diffusion limit?  Does the answer to this depend on $s$?})
+(We are concerned about increasing the number of stages, and implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with a more realistic collision operator.)
+To reduce the number of constraints, and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
+Instead, we only require the scheme to be second-order accurate in the streaming limit ($\vect{\cQ}=0$).  
+This gives the order conditions
+\begin{equation}
+  \sum_{i=1}^{s}\tilde{w}_{i}=1
+  \quad\text{and}\quad
+  \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2}.  
+  \label{eq:orderConditionsEx}
+\end{equation}
+We then seek to design a GSA IMEX scheme with the following properties
+\begin{itemize}
+  \item Second-order in the streaming limit; i.e., satisfies Eq.~\eqref{eq:orderConditionsEx}.
+  \item Well-behaved in the diffusion limit; i.e., satisfies Eq.~\eqref{eq:diffusionCondition}.
+  \item Positivity-preserving (conditions given by \cite{hu_etal_2017}; with $c_{\mbox{\tiny Sch}}$ maximal).
+  \item Few implicit stages.
+\end{itemize}
+Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example of type ARS with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PARSD).  
+This scheme is similar to the scheme given in \cite{mcclareen_2008} (see scheme PC2 in \ref{app:butcherTables}), which is also a GSA IMEX scheme of type ARS with $s=3$.  
+Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclareen_2008,radice_etal_2013}, and satisfies the positivity conditions, but $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).
+In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PARSD is practically identical to the accuracy of scheme PC2.

### 2018-04-12 Documents/M1/realizableFermionicM1/sections/imex.tex
Added comment on PARSD

@@
 Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example of type ARS with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PARSD).  
-This scheme is similar to the scheme given in \cite{mcclareen_2008} (see scheme PC2 in \ref{app:butcherTables}), which is also a GSA IMEX scheme of type ARS with $s=3$.  
+In the streaming limit, this scheme is identical to the optimal second-order accurate strong-stability preserving Runge-Kutta method \cite{gottlieb_etal_2001}.  
+It is also very similar to the scheme given in \cite{mcclareen_2008} (see scheme PC2 in \ref{app:butcherTables}), which is also a GSA IMEX scheme of type ARS with $s=3$.  
 Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclareen_2008,radice_etal_2013}, and satisfies the positivity conditions, but $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).

### 2018-04-18 Documents/M1/realizableFermionicM1/sections/appendix.tex
Removed CFL from PC2, RKCB2 and SSP2332.
Working on text discussing IMEX schemes.
Added 'IMEX PARSD'.

@@
 \section{Butcher Tableau for IMEX Schemes}
+\label{app:butcherTables}
 
@@
 And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.
-A common choice of this scheme is $c_{sch} = 0.3$.
+
+\paragraph{IMEX PARSD}
+
+We have found a second-order accurate in the streaming limit, diffusion accurate, positivity-preserving IMEX scheme of type $ARS$, which we refer to as IMEX PARSD.  
+This scheme allows for has a $c_{sch}= 1 - 2\epsilon$ which can arbitrary close to 1 by setting $\epsilon$ a arbitrary small positive value.
+Here we give an example by setting $\epsilon=0.1$.
+\begin{align}
+  \tilde{a}_{21} & = 1.0, \nonumber \\
+  \tilde{a}_{31} & = 0.5, \quad \tilde{a}_{32} = 0.5, \nonumber \\
+  a_{22} & = 1.0, \nonumber \\
+  a_{32} & = 0.4 \,( = 0.5 - \epsilon\,), \quad a_{33} = 0.6 \,( = 0.5 + \epsilon\,). \nonumber
+\end{align} 
+This scheme is also GSA and needs only two compute for implicit terms each time-step.
 
@@
 And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
-CFL ...
 

### 2018-04-19 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
forgot left-hand side of equation
Cosmetic Changes
Minor adjustments to dg.tex and imex.tex.  Began work on updating DGIMEX.tex

@@
 
-The realizability preserving DG scheme is designed to ensure realizability of the cell averages in each element $\bK$, defined as
+Here we proceed to develop realizability-preserving DG schemes for the two-moment model based on the IMEX schemes discussed in the previous section.  
+The realizability-preserving DG scheme is designed to preserve realizability of cell averages over a time step in each element $\bK$.  
+The cell average of the moments is defined as
 \begin{equation}
@@
   \vect{\cM}_{\bK}^{(i)}
-  =c_{i0}\,\vect{\cM}_{\bK}^{n}
-  +\sum_{j=1}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}
+  =\sum_{j=0}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}
   +a_{ii}\,\dt\,\f{1}{\tau}\,\big(\,\vect{\eta}-\vect{\cD}\,\vect{\cM}_{\bK}^{(i)}\,\big),
@@
 \end{equation}
-and the cell average of the divergence operator is (cf. Section~\ref{sec:dg})
+with $\cM_{\bK}^{(0)}=\cM_{\bK}^{n}$, and the cell average of the divergence operator is (cf. Section~\ref{sec:dg})
 \begin{equation}
@@
 \begin{lemma}
-  Let $\{s_{i}\}_{i=1}^{d}$ be a set of positive constants satisfying $\sum_{i=1}^{d}=1$.  
+  Let $\{s_{i}\}_{i=1}^{d}$ be a set of positive constants satisfying $\sum_{i=1}^{d}s_{i}=1$.  
   If for each $i\in\{1,\ldots,d\}$, 
@@
   \begin{equation}
-    \sum_{i=1}^{d}s_{i}\,\f{1}{|\tilde{\vect{\bK}}^{i}|}\int_{\tilde{\bK}^{i}}\vect{\Gamma}^{i}\big[\vect{\cM}_{h}\big]\,d\tilde{\vect{x}}^{i}.  
+    \vect{\cM}_{\bK}^{*}
+    =\sum_{i=1}^{d}s_{i}\,\f{1}{|\tilde{\vect{\bK}}^{i}|}\int_{\tilde{\bK}^{i}}\vect{\Gamma}^{i}\big[\vect{\cM}_{h}\big]\,d\tilde{\vect{x}}^{i}.  
     \label{eq:cellAverageInTermsOfGamma}
@@
     &\Phi(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+})
-    =(1-\lambda)\,\f{1}{2}\,\big(\,\vect{\cM}_{\Low}^{+}+\vect{\cM}_{\Hgh}^{-}\,\big) \nonumber \\
+    =(1-\lambda)\,\big(\,\f{1}{2}\,\vect{\cM}_{\Low}^{+}+\f{1}{2}\,\vect{\cM}_{\Hgh}^{-}\,\big) \nonumber \\
     &\hspace{12pt}

### 2018-04-19 Documents/M1/realizableFermionicM1/sections/imex.tex
Minor adjustments to dg.tex and imex.tex.  Began work on updating DGIMEX.tex

@@
 Thus, for $\phi_{1}=1$, the first components of $\vect{u}$ are the cell averaged moments.  
-In Eq.~\eqref{eq:ode}, the transport term $\vect{\cT}$ is due to the second and third term in the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision term $\vect{\cQ}$ is due to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
+In Eq.~\eqref{eq:ode}, the transport term $\vect{\cT}$ is due to the second and third term on the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision term $\vect{\cQ}$ is due to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
+
+\subsection{Second-Order Accurate, Positivity-Preserving IMEX Schemes}
 
 In the applications of interest to us, the collision term is stiff ($\tau\ll1$) in regions of the computational domain and must be treated with implicit methods, while we can resolve the time scales induced by the transport term, which we will treat with explicit methods; i.e., we will use IMEX methods \cite{pareschiRusso_2005}.
-We would like to employ IMEX schemes that preserve realizability of the moments (subject to a time step governed by the transport term).  
+Furthermore, we would like to employ IMEX schemes that preserve realizability of the moments (subject only to a time step governed by the explicit transport term).  
 Until recently, high-order (second or higher order temporal accuracy) positivity-preserving IMEX methods with time step restrictions solely due to the transport operator were not known.  
@@
 The coefficient in the correction step is positive, $\alpha>0$, and $\vect{\cQ}'$ is the Fr{\'e}chet derivative of the collision term evaluated at $\vect{u}^{*}$.  
-For second-order accuracy, $\vect{Q}$ can be evaluated using any of the stage values ($\vect{u}^{n}$, $\vect{u}^{(i)}$, or $\tilde{\vect{u}}^{n+1}$).  
-For second-order temporal accuracy, the order conditions are
+For second-order accuracy, $\vect{\cQ}'$ can be evaluated using any of the stage values ($\vect{u}^{n}$, $\vect{u}^{(i)}$, or $\tilde{\vect{u}}^{n+1}$).  
+For second-order temporal accuracy, the order conditions for the IMEX scheme in Eqs.~\eqref{imexStages}-\eqref{eq:imexCorrection} are
 \begin{equation}
@@
 where $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$ (see \cite{hu_etal_2017} for details).  
-In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.  
-Two types of IMEX schemes are considered: type A and type ARS.  
+(In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.)  
+Two types of IMEX schemes are considered: \emph{type A} and \emph{type ARS}.  
 For IMEX schemes of type A, the matrix $A$ is invertible.  
@@
 Such coefficients were given in \cite{hu_etal_2017} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
-It was also proven that $s=3$ and $s=4$ are the necessary number of stages for GSA second-order positivity-preserving IMEX schemes of type A and type ARS, respectively.
+(It was also proven that $s=3$ and $s=4$ are the necessary number of stages needed for GSA second-order positivity-preserving IMEX schemes of type A and type ARS, respectively.)
 
@@
 It is desirable to make $c_{\mbox{\tiny Sch}}$ as large (close to $1$) as possible.  
-(Positivity of $\vect{u}^{(i)}$ requires the implicit solve to preserve positivity.)  
+(Positivity of $\vect{u}^{(i)}$ also requires the implicit solve to preserve positivity.)  
 In \cite{hu_etal_2017}, Hu et al. provide examples of GSA, positivity-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
-In \ref{app:butcherTables}, we provide another example of a type A scheme (scheme PA2+), with a significantly larger $c_{\mbox{\tiny Sch}}$ (a factor of about $1.7$).
+In \ref{app:butcherTables}, we provide another example of a GSA, positivity-preserving IMEX scheme of type A (scheme PA2+), with a significantly larger $c_{\mbox{\tiny Sch}}$ (a factor of about $1.7$ larger).
+
+\subsection{Diffusion Accurate, Positivity-Preserving IMEX Schemes}
 
@@
 \end{equation}
-Unfortunately, this requirement, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$ results in too many constraints.
+Unfortunately, this requirement, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints.
 (\ee{Can we prove that it is impossible to find a second-order accurate, positivity-preserving IMEX scheme that is accurate in the diffusion limit?  Does the answer to this depend on $s$?})
-(We are concerned about increasing the number of stages, and implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with a more realistic collision operator.)
+(We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators.)
 To reduce the number of constraints, and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
@@
 \end{equation}
-We then seek to design a GSA IMEX scheme with the following properties
+We then seek to design GSA IMEX schemes with the following properties
 \begin{itemize}

### 2018-04-19 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
Completed first pass in updating DGIMEXscheme.tex

@@
 
-Here we proceed to develop realizability-preserving DG schemes for the two-moment model based on the IMEX schemes discussed in the previous section.  
-The realizability-preserving DG scheme is designed to preserve realizability of cell averages over a time step in each element $\bK$.  
+We proceed to develop realizability-preserving DG schemes for the two-moment model based on the IMEX schemes discussed in the previous section (cf.
+Eqs.~\eqref{imexStages}-\eqref{eq:imexCorrection}).
+The realizability-preserving DG scheme is designed to preserve realizability of cell averages over a time step $\dt$ in each element $\bK$.  
+Following the framework in \cite{zhangShu_2010b}, for high-order DG schemes, realizability of the cell average is leveraged to limit the polynomial approximation $\vect{\cM}_{h}$, if $\vect{\cM}_{h}$ is not realizable in a finite number of points in $\bK$ (Section~\ref{sec:limiter}).
 The cell average of the moments is defined as
@@
   =\sum_{j=0}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}
-  +a_{ii}\,\dt\,\f{1}{\tau}\,\big(\,\vect{\eta}-\vect{\cD}\,\vect{\cM}_{\bK}^{(i)}\,\big),
+  +a_{ii}\,\dt\,\f{1}{\tau}\,\big(\,\vect{\eta}-\vect{\cD}\,\vect{\cM}_{\bK}^{(i)}\,\big), \quad i=1,\ldots,s,
   \label{eq:imexStagesCellAverage}
 \end{equation}
-where we have defined
+where $c_{ij}\ge0$, $a_{ii}>0$, and $\sum_{j=0}^{i-1}c_{ij}=1$, and we have defined
 \begin{equation}
@@
 \end{equation}
-with $\cM_{\bK}^{(0)}=\cM_{\bK}^{n}$, and the cell average of the divergence operator is (cf. Section~\ref{sec:dg})
+with $\cM_{\bK}^{(0)}=\cM_{\bK}^{n}$.  
+The cell average of the divergence operator is (cf. Section~\ref{sec:dg})
 \begin{equation}
@@
   Let $\vect{\cM}_{\bK}^{(i)}$ satisfy Eq.~\eqref{eq:imexStagesCellAverage}.
-  Assume that $\vect{\cM}_{\bK}^{n}\in\cR$ and $\vect{\cM}_{\bK}^{(ij)}\in\cR\,\forall\,j\le i-1$.  
-  Then, $\vect{\cM}_{\bK}^{(i)}\in\cR$.  
+  Assume that $\vect{\cM}_{\bK}^{(ij)}\in\cR\,\forall\,i=1,\ldots,s,\,j\le i-1$.  
+  Then, $\vect{\cM}_{\bK}^{(i)}\in\cR$, for $i=1,\ldots,s$.  
 \end{lemma}
 \begin{proof}
-  The first two terms on the right-hand side of Eq.~\eqref{eq:imexStagesCellAverage} constitute a convex combination of elements in $\cR$; i.e.,
+  For $i=1,\ldots,s$, the first term on the right-hand side of Eq.~\eqref{eq:imexStagesCellAverage} constitutes a convex combination of elements in $\cR$; i.e.,
   \begin{equation*}
-    c_{i0}\,\vect{\cM}_{\bK}^{n}+\sum_{j=1}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}\in\cR.
+    \sum_{j=0}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}\in\cR.
   \end{equation*}
-  Since $a_{ii}\,\dt/\tau>0$, it follows from Lemma~\ref{lem:implicitStep} that $\vect{\cM}_{\bK}^{(i)}\in\cR$.  
+  Since $a_{ii}\,\dt/\tau>0$, it follows from Lemma~\ref{lem:implicitStep} that $\vect{\cM}_{\bK}^{(i)}\in\cR$, for $i=1,\ldots,s$.  
 \end{proof}
@@
 \begin{rem}
-  If a quadrature rule $\tilde{\vect{Q}}^{i}:C^{0}\to\bbR$, with positive weights, and points defined by the set $\tilde{\vect{S}}^{i}$, is used to approximate the integral over $\tilde{\bK}^{i}$ in \eqref{eq:cellAverageInTermsOfGamma}, it is sufficient for \eqref{eq:realizableGamma} to hold in the quadrature points $\tilde{\vect{S}}^{i}\subset\tilde{\bK}^{i}$.
+  If a quadrature rule $\tilde{\vect{Q}}^{i}:C^{0}\to\bbR$, with positive weights, and points defined by the set $\tilde{\vect{S}}^{i}$, is used to approximate the integral over $\tilde{\bK}^{i}$ in Eq.~\eqref{eq:cellAverageInTermsOfGamma}, it is sufficient for Eq.~\eqref{eq:realizableGamma} to hold in the quadrature points $\tilde{\vect{S}}^{i}\subset\tilde{\bK}^{i}$.
 \end{rem}
 
-Next, we establish conditions for which \eqref{eq:realizableGamma} holds.  
+Next, we establish conditions for which Eq.~\eqref{eq:realizableGamma} holds.  
 To simplify the notation, we temporarily drop the dimension index $i$, setting $x^{i}=x$, $K^{i}=K$, $\vect{\Gamma}^{i}=\vect{\Gamma}$, etc.  
@@
 
-With the GL quadrature rule in \eqref{eq:quadratureRuleGL} (note $\hat{w}_{1}=\hat{w}_{N}$), we can write $\vect{\Gamma}$ as the convex combination
+With the GL quadrature rule in Eq.~\eqref{eq:quadratureRuleGL} (note $\hat{w}_{1}=\hat{w}_{N}$), we can write $\vect{\Gamma}$ as the convex combination
 \begin{equation}

### 2018-04-20 Documents/M1/realizableFermionicM1/sections/imex.tex
Completed first pass in updating DGIMEXscheme.tex
Added more details for coefficients and c_sch.

@@
 \end{equation}
-where $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$ (see \cite{hu_etal_2017} for details).  
+where $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$.
 (In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.)  
@@
 For IMEX schemes of type A, the matrix $A$ is invertible.  
-For IMEX schemes of type ARS, the first column of $A$ is zero and the submatrix consisting of the last $s-1$ rows and columns of $A$, $\hat{A}$, is invertible.  
-For type A schemes, $\tilde{c}_{i0}=0$, and the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.
-For type ARS schemes, $c_{i1}=\tilde{c}_{i1}=0$, and positivity follows from requiring $a_{ii}>0$ and $c_{i0},\tilde{c}_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$ for $i=3,\ldots,s$, $j=2,\ldots,i-1$.
+For IMEX schemes of type ARS, the matrix $A$ can be written as
+\[\left( 
+   \begin{matrix} 
+       0 & 0 \\ 
+       0 & \hat{A}
+   \end{matrix}
+\right)\]
+with $\hat{A}$ be invertible.
+For $i=1,\ldots,s$, the coefficients
+\begin{align*}
+  c_{i0}
+  =&\left\{
+  \begin{array}{cl}
+    1 - \sum_{j=1}^{i-1}c_{ij}  & \text{for type $A$,} \\
+    1 - \sum_{j=2}^{i-1}c_{ij}  & \text{for type $ARS$;}
+  \end{array}
+  \right.\\
+  \tilde{c}_{i0}
+  =&\left\{
+  \begin{array}{cl}
+    0  & \text{for type $A$,} \\
+   \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1}  & \text{for type $ARS$;}
+  \end{array}
+  \right.\\
+  c_{i1}
+    =&\left\{
+    \begin{array}{cl}
+      \sum_{l =1}^{i-1} a_{il}b_{l1} & \text{for type $A$,} \\
+      0  & \text{for type $ARS$;}
+    \end{array}
+    \right.\\
+    \tilde{c}_{i1}
+    =&\left\{
+      \begin{array}{cl}
+       \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1} & \text{for type $A$,} \\
+       0  & \text{for type $ARS$;}
+      \end{array}
+      \right.
+\end{align*}
+and the rest coefficients were defined as in \cite{hu_etal_2017}.
+For type A schemes, the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.  
+For type ARS schemes, the positivity follows from requiring $a_{ii}>0$ and $c_{i0},\tilde{c}_{i0}\ge0$ for $i=2,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$ for $i=3,\ldots,s$, $j=2,\ldots,i-1$.  
 Such coefficients were given in \cite{hu_etal_2017} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
@@
   \item Positivity-preserving (conditions given by \cite{hu_etal_2017}; with $c_{\mbox{\tiny Sch}}$ maximal).
-  \item Few implicit stages.
+  \item Few ($\le3$) implicit stages.
 \end{itemize}

### 2018-04-24 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Updated text on maximum entropy closures

@@
 Algebraic moment closures for the two-moment model are computationally efficient as they provide the Eddington factor in Eq.~\eqref{eq:eddingtonTensor} in closed form as a function of the density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$.
+For this reason they are widely used in applications where radiation transport plays an important role --- including simulation of neutrino transport in core-collapse supernovae \cite{roberts_etal_2016} and compact binary mergers \cite{foucart_etal_2015}.
 The family of algebraic closures we consider in this paper can be written in the form \cite{cernohorskyBludman_1994}
@@
 
-\subsection{Maximum Entropy Closure}
+\subsection{Maximum Entropy (ME) Closure}
 
-The basic principle behind the maximum entropy closure is that one can approximate the real fermion distribution with a distribution which have the Fermi-Dirac distribution form 
+For the two-moment model, the ME closure constructs the least biased distribution function based on the limited information available \cite{cernohorskyBludman_1994} --- namely $\cJ$ and $\vect{\cH}$.
+The ME distribution function $f_{\mbox{\tiny ME}}(\omega)$ is found by maximizing the entropy functional for particles obeying Fermi-Dirac statistics
 \begin{equation}
-f(\omega)=\f{1}{e^{a + b\omega}+1}, 
+  S[f_{\mbox{\tiny ME}}] 
+  = \int_{\bbS^{2}}\big[\,(1-f_{\mbox{\tiny ME}})\log(1-f_{\mbox{\tiny ME}}) + f_{\mbox{\tiny ME}}\log f_{\mbox{\tiny ME}}\,]\,d\omega,
+  \label{eq:entropyFunctional}
 \end{equation} 
-meanwhile maximize the entropy function
+subject to the constraints
 \begin{equation}
-S[f(\omega)] = (1-f)\log(1-f) + f\log f.
+  \f{1}{4\pi}\int_{\bbS^{2}}f_{\mbox{\tiny ME}}(\omega)\,d\omega=\cJ
+  \quad\text{and}\quad
+  \f{1}{4\pi}\int_{\bbS^{2}}f_{\mbox{\tiny ME}}(\omega)\,\vect{\ell}(\omega)\,d\omega=\vect{\cH}.  
+  \label{eq:closureConstraints}
 \end{equation}
-Given moments $\cJ$ and $\vect{\cH}$, a distribution satisfying above requirements can be found. 
-Therefore, the stress tensor $\vect{\cK}$.
+From the variation of the entropy functional in Eq.~\eqref{eq:entropyFunctional} with respect to $f_{\mbox{\tiny ME}}$, and introducing Lagrange multipliers to enforce the constraints in Eq.~\eqref{eq:closureConstraints}, the ME distribution takes the general form
+\begin{equation}
+  f_{\mbox{\tiny ME}}(\omega;a,\vect{b})=\f{1}{e^{a + \vect{b}\cdot\vect{\ell}}+1}, 
+  \label{eq:fME}
+\end{equation}
+which can be further simplified by a change of coordinates so that $a + \vect{b}\cdot\vect{\ell}=a + b\,\mu$ ($b=|\vect{b}|$ and $\mu\in[-1,1]$).  
+The Lagrange multipliers are then implicit functions of $\cJ$ and $|\vect{\cH}|$.  
+The ME distribution function satisfies $0 \le f_{\mbox{\tiny ME}} \le 1$, but $a$ and $b$ are unconstrained.
 
-One ME closure given by Chernohorsky \& Bludman \cite{cernohorskyBludman_1994} is
+Chernohorsky \& Bludman \cite{cernohorskyBludman_1994} postulate (see however \cite{lareckiBanach_2011}) that, as a function of the so-called flux saturation $h/(1-\cJ)$, the closure function $\Theta$ is independent of $\cJ$ and can be written explicitly in terms of the inverse Langevin function.
+They also provide a polynomial fit (accurate to $2\%$) given by
 \begin{equation}
@@
   =x^{2}\,\big(\,3-x+3\,x^{2}\,\big).
+  \label{eq:closureMECB}
 \end{equation}
-
-Another ME closure given by Banach \& Larecki \cite{banachLarecki_2017b} is
+More recently, Larecki \& Banach \cite{lareckiBanach_2011} have shown that the explicit expression given in \cite{cernohorskyBludman_1994} is not exact, and provide another approximate expression
 \begin{equation}
   \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny BL}}(x)
-  =\f{1}{8}\,\big(\,9\,x^{2}-5+\sqrt{33\,x^{4}-42\,x^{2}+25}\,\big).
+  =\f{1}{8}\,\big(\,9\,x^{2}-5+\sqrt{33\,x^{4}-42\,x^{2}+25}\,\big),
+  \label{eq:closureMEBL}
 \end{equation}
+which is accurate to within $0.35\%$.
 
-\subsection{Kershaw Closure}
+\subsection{Kershaw (K) Closure}
+
 The basic principle behind Kershaw closure is derived from the fact that $\cR$ is convex.

### 2018-04-30 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Some adjustments to text on algebraic closures

@@
 
-For the two-moment model, the ME closure constructs the least biased distribution function based on the limited information available \cite{cernohorskyBludman_1994} --- namely $\cJ$ and $\vect{\cH}$.
-The ME distribution function $f_{\mbox{\tiny ME}}(\omega)$ is found by maximizing the entropy functional for particles obeying Fermi-Dirac statistics
+For the two-moment model, the ME closure constructs the least biased angular distribution based on the limited information available (i.e., $\cJ$ and $\vect{\cH}$) \cite{cernohorskyBludman_1994}.  
+The ME distribution $f_{\mbox{\tiny ME}}(\omega)$ is found by maximizing the entropy functional, which for particles obeying Fermi-Dirac statistics is given by
 \begin{equation}
@@
 \end{equation}
-which can be further simplified by a change of coordinates so that $a + \vect{b}\cdot\vect{\ell}=a + b\,\mu$ ($b=|\vect{b}|$ and $\mu\in[-1,1]$).  
-The Lagrange multipliers are then implicit functions of $\cJ$ and $|\vect{\cH}|$.  
+which can be further simplified by a change of coordinates $a + \vect{b}\cdot\vect{\ell}=a + b\,\mu$, where $b=|\vect{b}|$, and $\mu\in[-1,1]$ is the cosine of the angle between $\vect{b}$ and $\vect{\ell}$.
+The Lagrange multipliers are implicit functions of $\cJ$ and $|\vect{\cH}|$.  
 The ME distribution function satisfies $0 \le f_{\mbox{\tiny ME}} \le 1$, but $a$ and $b$ are unconstrained.
 
-Chernohorsky \& Bludman \cite{cernohorskyBludman_1994} postulate (see however \cite{lareckiBanach_2011}) that, as a function of the so-called flux saturation $h/(1-\cJ)$, the closure function $\Theta$ is independent of $\cJ$ and can be written explicitly in terms of the inverse Langevin function.
+Chernohorsky \& Bludman \cite{cernohorskyBludman_1994} postulate (but see \cite{lareckiBanach_2011}) that, as a function of the so-called flux saturation $x=h/(1-\cJ)$, the closure function $\Theta(x)$ is independent of $\cJ$ and can be written explicitly in terms of the inverse Langevin function.
 They also provide a polynomial fit (accurate to $2\%$) given by
@@
 which is accurate to within $0.35\%$.  
+On the interval $x\in[0,1]$, the curves given by Eqs.~\eqref{eq:closureMECB} and \eqref{eq:closureMEBL} lie practically on top of each other.
 

### 2018-05-03 Documents/M1/realizableFermionicM1/sections/numerical.tex
Added SineWave Streaming and Damping plots.
Working on text discussing IMEX schemes.
Added some text on Damping and Diffusion

@@
 \subsection{Problems with Known Smooth Solutions}
+\label{sec:smoothProblems}
 
@@
   \cJ(x,t=0)=\cH_{x}(x,t=0)=0.5+0.49\times\sin\big(2\pi\,x\big).  
+  \label{eq:initialConditionStreaming}
 \end{equation}
@@
 
+\begin{figure}[h]
+  \centering
+    \includegraphics[width=\textwidth]{figures/SineWaveStreaming}
+   \caption{Sine Wave Streaming}
+  \label{fig:SineWaveStreaming}
+\end{figure}
+
 \subsubsection{Sine Wave: Damping}
 
-Periodic domain $D=\{x:x\in[0,1]\}$.
+The next test we consider, adapted from \cite{skinnerOstriker_2013}, consists of a sine wave propagating with unit speed in a purely absorbing medium ($f_{0}=0$, $\sigma_{\Scatt}=0$), which results in exponential damping of the wave amplitude.
+We consider a periodic domain $D=\{x:x\in[0,1]\}$, and let the initial condition ($t=0$) be given as in Eq.~\eqref{eq:initialConditionStreaming}.  
+For a constant absorption opacity $\sigma_{\Ab}$, the analytical solution at $t>0$ is given by
+\begin{equation}
+  \cJ(x,t)=\cJ_{0}(x-t)\times\exp(-\sigma_{\Ab} t)
+  \quad\text{and}\quad
+  \cH_{x}(x,t)=\cJ(x,t),
+\end{equation}
+where $\cJ_{0}(x)=\cJ(x,0)$.
+
+We compute numerical solutions for three values of the absorption opacity ($\sigma_{\Ab}=0.1$, $1$, and $10$), and adjust the end time $t_{\mbox{\tiny end}}$ so that $\sigma_{\Ab}t_{\mbox{\tiny end}}=10$, and the initial condition has been damped by factor $e^{-10}$.
+Thus, for $\sigma_{\Ab}=0.1$ the sine wave crosses the domain 100 times, while for $\sigma_{\Ab}=10$, it crosses the grid once.
+
+Figure~\ref{fig:SineWaveDamping} shows convergence results obtained for the various values of $\sigma_{\Ab}$, using various IMEX schemes.  
+Results for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.
+
+\begin{figure}[h]
+  \centering
+    \includegraphics[width=\textwidth]{figures/SineWaveDamping}
+   \caption{Sine Wave Damping}
+  \label{fig:SineWaveDamping}
+\end{figure}
 
 \subsubsection{Sine Wave: Diffusion}
+
+The final test with known smooth solutions, adopted from \cite{radice_etal_2013}, is diffusion of a sine wave in a purely scattering medium ($f_{0}=0$, $\sigma_{\Ab}=0$).  
+The computational domain $D=\{x:x\in[-3,3]\}$ is periodic, and the initial condition is given by
+\begin{equation}
+  \cJ_{0}(x)=0.5+0.49\times\sin\big(\pi\,x/3\big)
+  \quad\text{and}\quad
+  \cH_{x,0}
+  =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}.  
+\end{equation}
 
@@
   \centering
-%  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Resolution_3}
+  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Resolution_3}
   \begin{tabular}{cc}
-%    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_1}
-%    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_2}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_1}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_2}
   \end{tabular}

### 2018-05-04 Documents/M1/realizableFermionicM1/sections/appendix.tex
Cosmetic Changes.
Work on text describing numerical results.

@@
 
-Another positivity-preserving IMEX scheme was given in \cite{mcclareen_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclareen_2008}).  
+Another positivity-preserving IMEX scheme was given in \cite{mcclarren_etal_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclarren_etal_2008}).  
 This scheme can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
@@
 \begin{align}
-  \tilde{a}_{21} &= 0.5, \nonumber \\
-  \tilde{a}_{32} &= 1, \nonumber \\
-  a_{22} &= 0.5, \nonumber \\
-  a_{33} &= 1.0. \nonumber
+  \tilde{a}_{21} &= 0.5, \quad \tilde{a}_{32} = 1, \nonumber \\
+  a_{22} &= 0.5, \quad a_{33} = 1.0. \nonumber
 \end{align}
@@
 \begin{align}
-  \tilde{a}_{21} &= 2/5, \nonumber \\
-  \tilde{a}_{32} &= 1, \nonumber \\
+  \tilde{a}_{21} &= 2/5, \quad \tilde{a}_{32} = 1, \nonumber \\
   a_{22} &= 2/5, \nonumber \\

### 2018-05-04 Documents/M1/realizableFermionicM1/sections/imex.tex
Generalized the diffusion accurate requirement.
Added the plots for sine wave diffusion test.
Work on text describing numerical results.

@@
   \begin{array}{cl}
-    1 - \sum_{j=1}^{i-1}c_{ij}  & \text{for type $A$,} \\
-    1 - \sum_{j=2}^{i-1}c_{ij}  & \text{for type $ARS$;}
+    1 - \sum_{j=1}^{i-1}c_{ij}  & \qquad \text{for type $A$,} \\
+    1 - \sum_{j=2}^{i-1}c_{ij}  & \qquad \text{for type $ARS$;}
   \end{array}
@@
     \begin{array}{cl}
-      \sum_{l =1}^{i-1} a_{il}b_{l1} & \text{for type $A$,} \\
-      0  & \text{for type $ARS$;}
+      \sum_{l =1}^{i-1} a_{il}b_{l1} & \qquad ~\text{for type $A$,} \\
+      \qquad ~ 0  & \qquad ~\text{for type $ARS$;}
     \end{array}
@@
 In the context of IMEX schemes, the diffusion limit balance implies that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold to relate the stage values in Eq.~\eqref{imexStages}.
+Define
+\begin{align*}
+    \mathcal{A}^{-1}
+    =&\left\{
+      \begin{array}{cl}
+       A^{-1} & \text{for type $A$,} \vspace{4pt} \\ 
+       \left( 
+          \begin{matrix} 
+              0 & 0 \\ 
+              0 & \hat{A}^{-1}
+          \end{matrix}
+       \right)  & \text{for type $ARS$.}
+      \end{array}
+      \right.
+\end{align*}
 For the final stage ($i=s$), 
 \begin{equation}
-  \vect{\cH}^{(s)}=-\f{1}{3}\,\tau\,\vect{e}_{s}^{T}A^{-1}\tilde{A}\vect{e}\,\nabla\cJ^{n}+\cO(\dt\,\tau),
+  \vect{\cH}^{(s)}=-\f{1}{3}\,\tau\,\vect{e}_{s}^{T}\mathcal{A}^{-1}\tilde{A}\vect{e}\,\nabla\cJ^{n}+\cO(\dt\,\tau),
 \end{equation}
@@
 \begin{equation}
-  \vect{e}_{s}^{T}A^{-1}\tilde{A}\vect{e} = 1.
+  \vect{e}_{s}^{T}\mathcal{A}^{-1}\tilde{A}\vect{e} = 1.
   \label{eq:diffusionCondition}
@@
 In the streaming limit, this scheme is identical to the optimal second-order accurate strong-stability preserving Runge-Kutta method \cite{gottlieb_etal_2001}.  
-It is also very similar to the scheme given in \cite{mcclareen_2008} (see scheme PC2 in \ref{app:butcherTables}), which is also a GSA IMEX scheme of type ARS with $s=3$.  
-Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclareen_2008,radice_etal_2013}, and satisfies the positivity conditions, but $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).
+It is also very similar to the scheme given in \cite{mcclarren_etal_2008} (see scheme PC2 in \ref{app:butcherTables}), which is also a GSA IMEX scheme of type ARS with $s=3$.  
+Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclarren_etal_2008,radice_etal_2013}, and satisfies the positivity conditions, but $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).
 In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PARSD is practically identical to the accuracy of scheme PC2.

### 2018-05-04 Documents/M1/realizableFermionicM1/sections/numerical.tex
Added the plots for sine wave diffusion test.
Work on text describing numerical results.

@@
 To compare the accuracy of the IMEX schemes, we present results from smooth problems in streaming, absorption, and scattering dominated regimes in one spatial dimension.  
-In all tests, we employ the maximum entropy closure in the low occupancy limit (i.e., the Minerbo closure).
+In all tests, we use third order accurate spatial discretization (polynomials of degree $k=2$) and we employ the maximum entropy closure in the low occupancy limit (i.e., the Minerbo closure).  
+We compare results obtained using IMEX schemes proposed here (PA2+ and PARSD) with IMEX schemes from Hu et al.
+\cite{hu_etal_2017} (PA2), McClarren et al.
+\cite{mcclarren_etal_2008} (PC2), Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332), and Cavaglieri \& Bewley \cite{cavaglieriBewley2015} (RKCB2).
+In the streaming test, we also include results obtained with second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods \cite{gottlieb_etal_2001} in the comparison (SSPRK2 and SSPRK3, respectively).
+See \ref{app:butcherTables} for further details.  
+The time step is set to $\dt=0.1\times\dx$.
+
+When comparing the numerical results to analytic solutions, errors are computed in the $L^{1}$-error norm.  
+We compare results either in the absolute error ($E_{\mbox{\tiny Abs}}^{1}$) or the relative error ($E_{\mbox{\tiny Rel}}^{1}$), defined for a scalar quantity $u_{h}$ (approximating $u$) as
+\begin{equation}
+  E_{\mbox{\tiny Abs}}^{1}[u_{h}](t)
+  =\f{1}{|D|}\sum_{\bK\in\mathscr{T}}\int_{\bK}|u_{h}(\vect{x},t)-u(\vect{x},t)|\,d\vect{x}
+  \label{eq:errorNormAbsolute}
+\end{equation}
+and
+\begin{equation}
+  E_{\mbox{\tiny Rel}}^{1}[u_{h}](t)
+  =\f{1}{|D|}\sum_{\bK\in\mathscr{T}}\int_{\bK}|u_{h}(\vect{x},t)-u(\vect{x},t)|/|u(\vect{x},t)|\,d\vect{x},
+  \label{eq:errorNormRelative}
+\end{equation}
+respectively.  
+The integrals in Eqs.~\eqref{eq:errorNormAbsolute} and \eqref{eq:errorNormRelative} are computed with a $3$-point Gaussian quadrature.
 
@@
 We evolve until $t=10$, when the sine wave has completed 10 crossings of the computational domain.  
-We use polynomials of degree $k=2$ for the spatial discretization (third-order spatial accuracy), and set the time step as $\Delta t = $.  
-We vary the number of elements from $??$ to $??$ and compute errors for various time stepping schemes.
+We vary the number of elements ($N$) from $8$ to $128$ and compute errors for various time stepping schemes.
 
-\ee{Include figure of error versus number of elements for various schemes.}
-
+In Figure~\ref{fig:SineWaveStreaming}, the absolute error for the number density $E_{\mbox{\tiny Abs}}^{1}[\cJ_{h}](t=10)$ is plotted versus $N$ (see figure caption for details).  
+Errors obtained with SSPRK3 are smallest and decrease as $N^{-3}$ (cf.
+bottom black dash-dot reference line), as expected for a scheme combining third-order accurate time stepping with third-order accurate spatial discretization.
+For all the other schemes, using second-order accurate explicit time stepping, the error decreases as $N^{-2}$.  
+Among the second-order accurate methods, SSP2332 has the smallest error, followed by RKCB2.  
+The error for the remaining schemes (including SSPRK2) are indistinguishable on the plot.  
 \begin{figure}[h]
@@
     \includegraphics[width=\textwidth]{figures/SineWaveStreaming}
-   \caption{Sine Wave Streaming}
+   \caption{Absolute error (cf.
+Eq.~\eqref{eq:errorNormAbsolute}) versus number of elements $N$ for the streaming sine wave test.
+Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), PA2 (red), PA2+ (purple), PC2 (blue), RKCB2 (black), SSP2332 (green), and PARSD (light red circles).
+Black dash-dot reference lines are proportional to $N^{-1}$ (top), $N^{-2}$ (middle), and $N^{-3}$ (bottom), respectively.}
   \label{fig:SineWaveStreaming}
@@
 \end{equation}
+
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionN} &
+    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionG}
+    \end{tabular}
+   \caption{Sine Wave Diffusion}
+  \label{fig:SineWaveDiffusion}
+\end{figure}
 

### 2018-05-04 Documents/M1/realizableFermionicM1/sections/numerical.tex
Text describing Sine wave damping

@@
 Among the second-order accurate methods, SSP2332 has the smallest error, followed by RKCB2.  
-The error for the remaining schemes (including SSPRK2) are indistinguishable on the plot.  
+Errors for the remaining schemes (including SSPRK2) are indistinguishable on the plot.  
 \begin{figure}[h]
@@
 
-Figure~\ref{fig:SineWaveDamping} shows convergence results obtained for the various values of $\sigma_{\Ab}$, using various IMEX schemes.  
-Results for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.
+Figure~\ref{fig:SineWaveDamping} shows convergence results, obtained using different values of $\sigma_{\Ab}$, for various IMEX schemes.  
+Results for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively (see figure caption for further details).  
+All the second-order accurate schemes (PA2, PA2+, RKCB2, and SSP2332) display second-order accurate convergence rates.  
+For $\sigma_{\Ab}=0.1$, SSP2332 is the most accurate among these schemes, while PA2+ is the most accurate for $\sigma_{\Ab}=10$.  
+On the other hand, PC2 and PARSD are indistinguishable and display at most first-order accurate convergence, as expected.  
+(For $\sigma_{\Ab}=0.1$, PC2 and PARSD are the most accurate schemes for $N=8$ and $N=16$.)
 
@@
     \includegraphics[width=\textwidth]{figures/SineWaveDamping}
-   \caption{Sine Wave Damping}
+   \caption{Relative error (cf.
+Eq.~\eqref{eq:errorNormRelative}) versus number of elements for the damping sine wave test.
+Results for different values of the absorption opacity $\sigma_{\Ab}$, employing various IMEX time stepping schemes, are compared.
+Errors for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.
+The IMEX schemes employed are: PA2 (triangles pointing left), PA2+ (triangles pointing right), PC2 (asterisk), RKCB2 ($\times$), SSP2332 ($+$), and PARSD (circles).
+Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
   \label{fig:SineWaveDamping}

### 2018-05-04 Documents/M1/realizableFermionicM1/sections/numerical.tex
Text describing sine wave diffusion results.

@@
 
-Figure~\ref{fig:SineWaveDamping} shows convergence results, obtained using different values of $\sigma_{\Ab}$, for various IMEX schemes.  
+Figure~\ref{fig:SineWaveDamping} shows convergence results, obtained using different values of $\sigma_{\Ab}$, for various IMEX schemes at $t=t_{\mbox{\tiny end}}$.  
 Results for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively (see figure caption for further details).  
@@
   =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}.  
+  \label{eq:initialConditionDiffusion}
 \end{equation}
+For a sufficiently high scattering opacity, the moment equations limit to a diffusion equation for the number density (deviations appear at the $1/\sigma_{\Scatt}^{2}$-level).  
+With the initial conditions in Eq.~\eqref{eq:initialConditionDiffusion}, the analytical solution to the limiting diffusion equation is given by
+\begin{equation}
+  \cJ(x,t)=\cJ_{0}(x)\times\exp\big(-\pi^{2}\,t/(27\,\sigma_{\Scatt})\big),
+\end{equation}
+and $\cH_{x}=(3\,\sigma_{\Scatt})^{-1}\pd{\cJ}{x}$.  
+When computing errors for this test, we compare the numerical results obtained with the two-moment model to the analytical solution to the limiting diffusion equation.  
+We compute numerical solutions using three values of the scattering opacity ($\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$), and adjust the end time so that $t_{\mbox{\tiny end}}/\sigma_{\Scatt}=1$.
+The initial amplitude of the sine wave has then been reduced by a factor $e^{-\pi^{2}/27}$ for all values of $\sigma_{\Scatt}$.
 
@@
     \end{tabular}
-   \caption{Sine Wave Diffusion}
+   \caption{Absolute error (cf.
+Eq.~\eqref{eq:errorNormAbsolute}) versus number of elements for the sine wave diffusion test.
+Results with different values of the scattering opacity $\sigma_{\Scatt}$, employing different IMEX schemes, are compared.
+Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.
+The IMEX schemes employed are: PA2 (triangles pointing left), PA2+ (triangles pointing right), PARSD (asterisk), RKCB2 (circles), and SSP2332 (?).
+Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
   \label{fig:SineWaveDiffusion}
 \end{figure}
+
+In Figure~\ref{fig:SineWaveDiffusion} we plot the absolute error, obtained using different values of $\sigma_{\Ab}$, for various IMEX schemes at $t=t_{\mbox{\tiny end}}$.  
+Results for $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively (see figure caption for further details).  
+(Scheme PC2 has been shown to work well for this test \cite{radice_etal_2013}, and is omitted here.)
+Schemes PARSD, RKCB2, and SSP2332 are accurate for this test, and display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$ in this test.  
+For $\sigma=10^{2}$, the errors do not drop below $10^{-6}$ because of differences between the two-moment model and the diffusion equation used to obtain the analytic solution.  
+For larger values of the scattering opacity, we observe convergence over the entire range of $N$.  
+Schemes PA2 and PA2+ do not perform well on this test (for reasons discussed in Section~\ref{sec:imex}).  
+For $\sigma_{\Scatt}=10^{2}$, errors in $\cJ$ and $\cH_{x}$ decrease with increasing $N$, but for $\sigma_{\Scatt}=10^{4}$, errors remain constant with increasing $N$ over the entire range.
 

### 2018-05-05 Documents/M1/realizableFermionicM1/sections/numerical.tex
Work on text for packed beam problem

@@
 Next we consider a one-dimensional test with discontinuous initial conditions.  
+The purpose of this test is to gauge the accuracy of the two-moment model and robustness of the DG scheme for dynamics close to the boundary of the realizable set $\cR$.  
 The computational domain is $D=\{x:x\in[-1,1]\}$, and the initial condition is obtained from a distribution function given by
@@
 so that $\vect{\cM}=\big(0.5\,(1+\delta),0.25\,(1-\delta)\big)^{T}$ for $x\le x_{\mbox{\tiny D}}$, and $\vect{\cM}=\big(\delta,0\big)^{T}$ for $x> x_{\mbox{\tiny D}}$, where $\delta>0$ is a small parameter ($\delta\ll1$).
-We let $\delta=10^{-8}$.  
+We let $\delta=10^{-8}$, so that the initial conditions are very close to the boundary of the realizable domain (cf. Figure~\ref{fig:RealizableSetFermionic}).  
+The analytical solution can be easily obtained by solving the transport equation for all angles $\mu$ (independent linear advection equations), and taking the angular moments.  
+The numerical results shown in this section were obtained with the third-order scheme (polynomials of degree $k=2$ and the SSPRK3 time stepper) using $400$ elements.  
+The time step is set to $\dt=0.1\times\dx$
+
+Figure~\ref{fig:PackedBeam} shows results for various times obtained with the two-moment model.  
+In the upper panels we plot the number density, while the number flux density is plotted in the lower panels.  
+Numerical solutions are plotted with solid lines, while the analytical solution is plotted with dashed lines.  
+In the left panels, the algebraic maximum entropy closure of Cernohorsky \& Bludman (CB) \cite{cernohorskyBludman_1994} (cf.
+Eqs.~\eqref{eq:eddingtonFactor} and \eqref{eq:closureMECB}) was used, while in the right panels the Minerbo closure (cf.
+Eqs.~\eqref{eq:eddingtonFactorLow} and \eqref{eq:closureMECB}) was used.
+For this test, the use of the realizability-preserving limiter described in Section~\ref{sec:limiter} was essential in order to avoid numerical problems.  
+For the results obtained with the CB closure, the limiter was enacted whenever moments ventured outside the realizable set given by Eq.~\eqref{eq:realizableSet}.  
+For the results obtained with the Minerbo closure, which is not based on Fermi-Dirac statistics, we used a modified limiter, which was enacted when the moments ventured outside the realizable domain of positive distributions (not bounded by $f\le1$; see dashed red line in Figure~\ref{fig:RealizableSetFermionic}).
+
 \begin{figure}[h]
@@
   \end{tabular}
-   \caption{Packed Beam}
+   \caption{Numerical results from the packed beam problem at various times: $t=0$ (cyan), $t=0.2$ (magenta), $t=0.4$ (blue), and $t=0.8$ (black).
+Results obtained with the Cernohorsky \& Bludman closure are displayed in the left panels, while results obtained with the Minerbo closure are displayed in the right panels.
+The analytical solution (dashed lines) is also plotted.}
   \label{fig:PackedBeam}
+\end{figure}
+
+As can be seen in Figure~\ref{fig:PackedBeam}, with the CB closure the numerical solution obtained with the two-moment model tracks the analytic solution well, while with the Minerbo closure the numerical solution deviates substantially, and also evolves outside the realizable domain for Fermi-Dirac statistics (see Figure~\ref{fig:PackedBeam_Realizability}).
+We have also run this test using the algebraic maximum entropy closure of Larecki \& Banach \cite{lareckiBanach_2011} and the simpler Kershaw-type closure in \cite{banachLarecki_2017a}.  
+The numerical solutions obtained with both of these closures follow the analytic solution well, and remain within the realizable set $\cR$.  
+We point out that simply using the realizability-preserving limiter described in Section~\ref{sec:limiter} with the Minerbo closure does not result in a realizability-preserving scheme for Fermi-Dirac statistics because of the properties of this closure discussed in Section~\ref{sec:algebraicClosure}, and plotted in the lower right panel of Figure~\ref{fig:MabWithDifferentClosure}.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{figures/PackedBeam_Realizability}
+   \caption{Plot of $\gamma(\vect{\cM})=(1-\cJ)\,\cJ-|\vect{\cH}|$ for various times in the packed beam problem: $t=0$ (cyan), $t=0.2$ (magenta), $t=0.4$ (blue), and $t=0.8$ (black).
+Results obtained with the CB closure, which remain positive throughout the evolution, are plotted with solid lines, while results obtained with the Minerbo closure are plotted with dashed lines.}
+  \label{fig:PackedBeam_Realizability}
 \end{figure}

### 2018-05-06 Documents/M1/realizableFermionicM1/sections/realizability.tex
Modified the caption of the realizable set diagram

@@
 Figure~\ref{fig:RealizableSetFermionic} illustrates the geometry of the convex set $\cR$ in $|\vect{\cH}| - \cJ$ coordinates (light blue region).
-To make this plot, a total of $10^{6}$ distribution functions of the form $\mathfrak{f}(\mu;a,b) = \dfrac{1}{e^{a+b\mu}+1}$ ($\mu\in[-1,1]$) were generated, where the parameters $a$ and $b$ were chosen randomly and independently in the range $a,b\in[-10^{2},10^{2}]$.
-A uniform $\mu$-grid with $\Delta\mu=1/128$ was used to represent the distribution functions. And the angular moments were calculated using the trapezoid rule.  
+
 \begin{figure}[h]
@@
   \caption{Illustration of the realizable set $\cR$ defined in Eq.~\eqref{eq:realizableSet}.  
-  Each of the $10^{6}$ light-blue points in the figure represents a set of moments $\vect{\cM}=(\cJ,\vect{\cH})$, computed from a random Fermi-Dirac distribution (see text for details).  
-  Black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
+  The black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$ while the dash red lines is the boundary given by the Maxwell's distributions.}
   \label{fig:RealizableSetFermionic}

### 2018-05-06 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Modified Kershaw closure section.

@@
 
-The basic principle behind Kershaw closure is derived from the fact that $\cR$ is convex.
-Due to the convexity, one can write any element in $\cR$ as a convex combination of the elements on the realization boundary. 
-Therefore, Kershaw closure satisfies realizability inherently.
-For fermionic radiation, the boundary is based on the Heaviside step functions.
+The basic principle behind Kershaw closure is derived from the fact that the realizable set defined by $(\cJ, \vect{\cH}, \vect{K})$ is convex.
+Due to the convexity, it's sufficient and necessary for an element in the convex set be expressed as a convex combination of two elements that on the set boundary.
+The Kershaw closure assumes that the convex combination has a constant coefficient which is independent from $(\cJ, \vect{\cH})$.
+Therefore, using the lower occupancy limit, one can determine the coefficient and apply the convex combination as an approximation.
 Here we introduce a closure function $\Theta(x)$ given by Banach \& Larecki \cite{banachLarecki_2017a}:

### 2018-05-07 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Modified Kershaw closure section.

@@
 Due to the convexity, it's sufficient and necessary for an element in the convex set be expressed as a convex combination of two elements that on the set boundary.
-The Kershaw closure assumes that the convex combination has a constant coefficient which is independent from $(\cJ, \vect{\cH})$.
-Therefore, using the lower occupancy limit, one can determine the coefficient and apply the convex combination as an approximation.
+The Kershaw closure assumes that the convex combination has a constant coefficient $\beta$ which is independent from $(\cJ,h)$:
+\begin{align}
+ \chi(\cJ,h) = \beta  \chi_{L}(\cJ,h) + (1-\beta) \chi_{U}(\cJ,h),
+\end{align}
+where $\chi_{L}$ and $\chi_{U}$ are the boundary functions given by the Heaviside function with Fermi-Dirac statistic function.
+Therefore, using the lower occupancy limit,
+\begin{align}
+ \chi(\cJ,0) = \dfrac{1}{3},
+\end{align}
+one can determine the coefficient $\beta$ and apply the convex combination as an approximation.
 Here we introduce a closure function $\Theta(x)$ given by Banach \& Larecki \cite{banachLarecki_2017a}:

### 2018-05-07 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added the construction of PARSD

@@
 \end{align}
+
+\newpage 
+\section{Construction of PARSD}
+
+It can be shown that no 2-stage positivity-preserving IMEX exist \cite{hu_etal_2017}.
+Hence we considered 3-stage IMEX scheme.
+There are two kinds of implicit DIRK scheme, Type A and Type ARS.
+Here we discuss the simpler case, Type ARS, first.
+The Butcher tableau for ARS type IMEX scheme is
+\begin{equation}
+  \begin{array}{c | c c c}
+  	         0           & 0                    & 0                    & 0                    \\
+  	\tilde{c}_{2} & \tilde{a}_{21}       & 0                    & 0                    \\
+  	\tilde{c}_{3} & \tilde{a}_{31}       & \tilde{a}_{32}       & 0                    \\ \hline
+  	                     & \tilde{w}_{1} & \tilde{w}_{2} & \tilde{w}_{3}
+  \end{array}
+  \qquad
+  \begin{array}{c | c c c}
+  	     0       & 0            & 0            & 0            \\
+  	c_{2} & 0            & a_{22}       & 0            \\
+  	c_{3} & 0            & a_{32}       & a_{33}       \\ \hline
+  	             & w_{1} & w_{2} & w_{3}
+  \end{array}.
+\end{equation}
+The properties a desired IMEX scheme should have are: 2nd-order accurate in the streaming, globally stiffly accurate, positivity-preserving, diffusion accurate and an affordable time-step restriction.
+Then the problem that find such a scheme can be rewritten as an optimization problem:\\
+Find $(\tilde{a}_{21}, \tilde{a}_{31}, \tilde{a}_{32}, \tilde{w}_{1}, \tilde{w}_{2}, \tilde{w}_{3}, a_{22}, a_{32}, a_{33}, w_{1}, w_{2}, w_{3})$ such that
+\begin{align*}
+\text{maximize} ~ c_{sch} = &\min \{ \dfrac{c_{20}}{\tilde{c}_{20}}, \dfrac{c_{30}}{\tilde{c}_{30}}, \dfrac{c_{32}}{\tilde{c}_{32}}\}\\
+ \text{under these constraints:} \qquad & \\
+ \text{(GSA)} \qquad\ &\tilde{w}_{i} = \tilde{a}_{3i}, \quad w_{i} = a_{3i},\\
+ \text{(2nd-order accuracy)} \qquad\ &\sum_{i=1}^{3}  \tilde{w}_{i} = 1, \quad \sum_{i=1}^{3}  \tilde{w}_{i}\tilde{c}_{i} = 1/2, \\
+ \text{(positivity-preserving)} \qquad & a_{ii} > 0, c_{i0} \geq 0, \tilde{c}_{i0} \geq 0 ~\text{for} ~ i = 2,3 \\
+ & c_{32} \geq 0, \tilde{c}_{32} \geq 0, \\
+ \text{(diffusion accurate)} \qquad & e^{T}_iA^{-1}\tilde{A}e = 1, ~\text{for} ~ i = 2,3, \\
+ \text{(affordable)} \qquad & c_{sch} > 0.
+\end{align*}
+This problem can be simplified as:
+\begin{equation}
+  \begin{array}{c | c c c}
+  	     0       & 0            & 0 & 0 \\
+  	\frac{1}{2x} & \frac{1}{2x} & 0 & 0 \\
+  	     1       & 1-x          & x & 0 \\ \hline
+  	             & 1-x          & x & 0
+  \end{array}
+  \qquad
+  \begin{array}{c | c c c}
+  	     0       & 0 & 0            & 0 \\
+  	\frac{1}{2x} & 0 & \frac{1}{2x} & 0 \\
+  	     1       & 0 & 1-y          & y \\ \hline
+  	             & 0 & 1-y          & y
+  \end{array}.
+\end{equation}
+Find $(x,y)$ such that
+\begin{align*}
+\text{maximize} ~ c_{sch} = &\min \{ 2x, \dfrac{1-2x(1-y)}{y-x}, 2(1-y)\}\\
+ \text{under these constraints:} \qquad & x > 0, ~ 1 \geq y > 0, \\
+ & x \leq y, ~\dfrac{1}{2x} \geq 1-y.
+\end{align*}
+It can be shown that the solution is $x=\frac{1}{2}$, $y=\frac{1}{2} + \epsilon$ with $\epsilon \rightarrow 0$ and $c_{sch} = 1 - 2\epsilon$.
+And the PARSD scheme follows.

### 2018-05-09 Documents/M1/realizableFermionicM1/sections/numerical.tex
Additional figure for packed beam problem

@@
   \centering
-  \includegraphics[width=\textwidth]{figures/PackedBeam_Realizability}
-   \caption{Plot of $\gamma(\vect{\cM})=(1-\cJ)\,\cJ-|\vect{\cH}|$ for various times in the packed beam problem: $t=0$ (cyan), $t=0.2$ (magenta), $t=0.4$ (blue), and $t=0.8$ (black).
-Results obtained with the CB closure, which remain positive throughout the evolution, are plotted with solid lines, while results obtained with the Minerbo closure are plotted with dashed lines.}
+  \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_Realizability}
+    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_RealizableDomain}
+  \end{tabular}
+   \caption{In the left panel, $\gamma(\vect{\cM})=(1-\cJ)\,\cJ-|\vect{\cH}|$ is plotted versus $x$ for various times in the packed beam problem: $t=0$ (cyan), $t=0.2$ (magenta), $t=0.4$ (blue), and $t=0.8$ (black).
+Results obtained with the CB closure, which remain positive throughout the evolution, are plotted with solid lines, while results obtained with the Minerbo closure are plotted with dashed lines.
+In the right panel, the moments are plotted in $(\cJ,\cH)$-space for the same times as in the left panel.
+Results obtained with the CB and Minerbo closures are plotted in blue and magenta, respectively.
+The solid black and red lines are contour where $(1-\cJ)\,\cJ=\cH$ and $\cJ=\cH$, respectively.}
   \label{fig:PackedBeam_Realizability}

### 2018-05-09 Documents/M1/realizableFermionicM1/sections/appendix.tex
Modified the Construction of PARSD section.

@@
 We have found a second-order accurate in the streaming limit, diffusion accurate, positivity-preserving IMEX scheme of type $ARS$, which we refer to as IMEX PARSD.  
-This scheme allows for has a $c_{sch}= 1 - 2\epsilon$ which can arbitrary close to 1 by setting $\epsilon$ a arbitrary small positive value.
+This scheme allows for has a $c_{sch}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.
 Here we give an example by setting $\epsilon=0.1$.
@@
 \end{align*}
-This problem can be simplified as:
+Imposing those equality constraints (including all the constraints exclude those from the positivity-preserving and affordable requirements), the Butcher tableau can be simplified as:
 \begin{equation}
@@
 \end{equation}
+And the rest inequalities and the problem were left to be: \\
 Find $(x,y)$ such that
@@
 \end{align*}
-It can be shown that the solution is $x=\frac{1}{2}$, $y=\frac{1}{2} + \epsilon$ with $\epsilon \rightarrow 0$ and $c_{sch} = 1 - 2\epsilon$.
-And the PARSD scheme follows.
+A solution family is $x=\frac{1}{2}$, $y=\frac{1}{2} + \epsilon$ with $\epsilon \in [0, \frac{1}{2})$ and $c_{sch} = 1 - 2\epsilon$.
+The PARSD scheme follows.
+It's clear that $\epsilon = 0$ and $c_{sch} = 1$ is the most optimized solution.

### 2018-05-09 Documents/M1/realizableFermionicM1/sections/numerical.tex
Replacing line source benchmark with similar test more suitable for fermionic transport

@@
   \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_ME_CB}
-    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_ME_MI}
+    \includegraphics[width=0.485\textwidth]{figures/PackedBeam_ME_CB} &
+    \includegraphics[width=0.485\textwidth]{figures/PackedBeam_ME_MI}
   \end{tabular}
@@
   \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_Realizability}
-    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_RealizableDomain}
+    \includegraphics[width=0.485\textwidth]{figures/PackedBeam_Realizability} &
+    \includegraphics[width=0.485\textwidth]{figures/PackedBeam_RealizableDomain}
   \end{tabular}
@@
 
-\subsection{Line Source}
+\subsection{Fermion Implosion}
 
-The line source benchmark (cf. \cite{brunner_2002,garrettHauck_2013}) is a challenging test for approximate transport algorithms.  
-In cylindrical coordinates, it consists of an initial delta function particle distribution in radius; i.e., $f_{0}=\delta(R)/4\,\pi$.  
-For $t>0$, a cylindrical radiation front propagates radially.  
-Apart from capturing details of the exact transport solution, maintaining realizability ($\bcM\in\cR$ cf. Eq.~\eqref{eq:realizableSet}) of the two-moment solution is challenging.
+The next test is inspired by line source benchmark (cf. \cite{brunner_2002,garrettHauck_2013}), which is a challenging test for approximate transport algorithms.  
+The original line source test consists of an initial delta function particle distribution in radius $R=|\vect{x}|$; i.e., $f_{0}=\delta(R)/4\,\pi$.  
+For $t>0$, a radiation front propagates in the radial direction, away from the initial source.  
+Apart from capturing details of the exact transport solution, maintaining realizability of the two-moment solution is challenging.
 
-This test is computed on a two-dimensional domain with $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,1.25], x^{2}\in[0,1.25]\}$.  
-We follow the initialization procedure in \cite{garrettHauck_2013}, and approximate the initial condition with an isotropic Gaussian distribution function
+Here, a modified version of the line source --- dubbed \emph{Fermion Implosion},  designed to test the realizability-preserving properties of the two moment model for fermionic transport --- is computed on a two-dimensional domain with $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[-1.28,1.28], x^{2}\in[-1.28,1.28]\}$.
+Instead of initializing with a delta function, we follow the initialization procedure in \cite{garrettHauck_2013}, and approximate the initial condition with an isotropic Gaussian distribution function.
+Morover, the initial distribution function is bounded $f_{\mbox{\tiny G},0}\in(0,1)$ and reaches a minimum in the center of the computational domain (hence implosion)
 \begin{equation}
   f_{\mbox{\tiny G},0}
-  =\max\Big[\,\f{1}{8\,\pi\,\sigma_{\mbox{\tiny G}}^{2}}\,e^{-R^{2}/(2\,\sigma_{\mbox{\tiny G}}^{2})},10^{-4}\,\Big],
+  =1-\max\Big[\,e^{-R^{2}/(2\,\sigma_{\mbox{\tiny G}}^{2})},10^{-8}\,\Big].  
 \end{equation}
-where $R=|\vect{x}|$, and we use $\sigma_{\mbox{\tiny G}}=0.03$.  
-We run this test to a final time $t=1.0$.
+We set $\sigma_{\mbox{\tiny G}}=0.03$, and run this test to a final time of $t=1.0$.  
+We run this test using a grid of $512^{2}$ elements, polynomials of degree $k=1$, and the SSPRK2 time stepping scheme.  
+(There are no collisions in this test; i.e., $\sigma_{\Ab}=\sigma_{\Scatt}=0$.)  
+We present results using both the algebraic closure of Cernohorsky \& Bludman and the Minerbo closure.
+
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.495\textwidth]{figures/Implosion_Image} &
+    \includegraphics[width=0.495\textwidth]{figures/Implosion_Lineout} \\
+    \includegraphics[width=0.495\textwidth]{figures/Implosion_RealizableDomain} &
+    \includegraphics[width=0.495\textwidth]{figures/Implosion_LimiterParameters}
+  \end{tabular}
+   \caption{}
+  \label{fig:Implosion}
+\end{figure}
 

### 2018-05-09 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Modified Kershaw closure section.

--- 2018-05-06 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
@@
 The basic principle behind Kershaw closure is derived from the fact that the realizable set defined by $(\cJ, \vect{\cH}, \vect{K})$ is convex.
-Due to the convexity, it's sufficient and necessary for an element in the convex set be expressed as a convex combination of two elements that on the set boundary.
-The Kershaw closure assumes that the convex combination has a constant coefficient which is independent from $(\cJ, \vect{\cH})$.
-Therefore, using the lower occupancy limit, one can determine the coefficient and apply the convex combination as an approximation.
-Here we introduce a closure function $\Theta(x)$ given by Banach \& Larecki \cite{banachLarecki_2017a}:
+Due to the convexity, any element in the convex set be expressed as a convex combination of two elements that on the set boundary, and vice versa.
+That is,
+\begin{align}
+ \chi(\cJ,h) = \beta  \chi_{L}(\cJ,h) + (1-\beta) \chi_{U}(\cJ,h),
+\end{align}
+with $\chi_{L}$ and $\chi_{U}$ be the boundary elements, and $\beta \in [0,1]$. 
+The Kershaw closure uses a convex combination that determined by the isotropic distribution case to approximate $\chi(\cJ,h)$:
+\begin{align}
+ \chi(\cJ,0)  &= \dfrac{1}{3},\\
+\chi_{L}(\cJ,h) & = \dfrac{1}{3}\cJ^2 + h^2, \\
+\chi_{U}(\cJ,h) & = \left( 1 - \cJ + \dfrac{1}{3}\cJ^2 \right) - \dfrac{h^2 \cJ}{1-\cJ},
+\end{align}
+$\chi_{L}$ and $\chi_{U}$ are given by the Heaviside function with Fermi-Dirac statistic function, and
+\begin{align}
+\beta = \dfrac{2 - \cJ}{3}.
+\end{align}
+Then the Kershaw closure function $\Theta(x)$ reads (Banach \& Larecki \cite{banachLarecki_2017a}):
 \begin{equation}

### 2018-05-10 Documents/M1/realizableFermionicM1/sections/numerical.tex
Modified text due to comments from Ran.  Also updated text on the Packed Beam problem

@@
 To compare the accuracy of the IMEX schemes, we present results from smooth problems in streaming, absorption, and scattering dominated regimes in one spatial dimension.  
-In all tests, we use third order accurate spatial discretization (polynomials of degree $k=2$) and we employ the maximum entropy closure in the low occupancy limit (i.e., the Minerbo closure).  
+For all tests in this subsection, we use third order accurate spatial discretization (polynomials of degree $k=2$) and we employ the maximum entropy closure in the low occupancy limit (i.e., the Minerbo closure).
 We compare results obtained using IMEX schemes proposed here (PA2+ and PARSD) with IMEX schemes from Hu et al.
@@
 Eq.~\eqref{eq:errorNormAbsolute}) versus number of elements $N$ for the streaming sine wave test.
-Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), PA2 (red), PA2+ (purple), PC2 (blue), RKCB2 (black), SSP2332 (green), and PARSD (light red circles).
+Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), PA2 (red), PA2+ (purple), PC2 (blue), RKCB2 (dark green), SSP2332 (green), and PARSD (light red circles).
 Black dash-dot reference lines are proportional to $N^{-1}$ (top), $N^{-2}$ (middle), and $N^{-3}$ (bottom), respectively.}
@@
 Results for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively (see figure caption for further details).  
-All the second-order accurate schemes (PA2, PA2+, RKCB2, and SSP2332) display second-order accurate convergence rates.  
+All the second-order accurate schemes (PA2, PA2+, RKCB2, and SSP2332) display second-order accurate convergence rates (cf. bottom, black dash-dot reference line).  
 For $\sigma_{\Ab}=0.1$, SSP2332 is the most accurate among these schemes, while PA2+ is the most accurate for $\sigma_{\Ab}=10$.  
@@
 We compute numerical solutions using three values of the scattering opacity ($\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$), and adjust the end time so that $t_{\mbox{\tiny end}}/\sigma_{\Scatt}=1$.
-The initial amplitude of the sine wave has then been reduced by a factor $e^{-\pi^{2}/27}$ for all values of $\sigma_{\Scatt}$.
+The initial amplitude of the sine wave has then been reduced by a factor $e^{-\pi^{2}/27}\approx0.694$ for all values of $\sigma_{\Scatt}$.
 
@@
   \centering
-  \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionN} &
-    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionG}
-    \end{tabular}
+  \includegraphics[width=1.0\textwidth]{figures/SineWaveDiffusionN}
    \caption{Absolute error (cf.
-Eq.~\eqref{eq:errorNormAbsolute}) versus number of elements for the sine wave diffusion test.
+Eq.~\eqref{eq:errorNormAbsolute}) for the number density $\cJ$ versus number of elements for the sine wave diffusion test.
 Results with different values of the scattering opacity $\sigma_{\Scatt}$, employing different IMEX schemes, are compared.
 Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.
-The IMEX schemes employed are: PA2 (triangles pointing left), PA2+ (triangles pointing right), PARSD (asterisk), RKCB2 (circles), and SSP2332 (?).
+The IMEX schemes employed are: PA2 (triangle pointing left), PA2+ (triangle pointing right), PC2 (asterisk), RKCB2 (cross), SSP2332 (plus), and PARSD (circle).
 Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
-  \label{fig:SineWaveDiffusion}
+  \label{fig:SineWaveDiffusionJ}
 \end{figure}
 
-In Figure~\ref{fig:SineWaveDiffusion} we plot the absolute error, obtained using different values of $\sigma_{\Ab}$, for various IMEX schemes at $t=t_{\mbox{\tiny end}}$.  
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/SineWaveDiffusionG}
+   \caption{Same as in Figure~\ref{fig:SineWaveDiffusionJ}, but for the number flux $\cH_{x}$.}
+  \label{fig:SineWaveDiffusionH}
+\end{figure}
+
+In Figures~\ref{fig:SineWaveDiffusionJ} and \ref{fig:SineWaveDiffusionJ} we plot the absolute error, obtained using different values of $\sigma_{\Scatt}$, for various IMEX schemes at $t=t_{\mbox{\tiny end}}$.
 Results for $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively (see figure caption for further details).  
-(Scheme PC2 has been shown to work well for this test \cite{radice_etal_2013}, and is omitted here.)
-Schemes PARSD, RKCB2, and SSP2332 are accurate for this test, and display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$ in this test.  
+(Scheme PC2 has been shown to work well for this test \cite{radice_etal_2013}, but is included here for comparison with the other IMEX schemes.)
+Schemes PARSD, RKCB2, and SSP2332 are accurate for this test, and display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$.  
 For $\sigma=10^{2}$, the errors do not drop below $10^{-6}$ because of differences between the two-moment model and the diffusion equation used to obtain the analytic solution.  
-For larger values of the scattering opacity, we observe convergence over the entire range of $N$.  
+For larger values of the scattering opacity, the two-moment model agrees better with the diffusion model, and we observe convergence over the entire range of $N$.  
 Schemes PA2 and PA2+ do not perform well on this test (for reasons discussed in Section~\ref{sec:imex}).  
@@
 Next we consider a one-dimensional test with discontinuous initial conditions.  
-The purpose of this test is to gauge the accuracy of the two-moment model and robustness of the DG scheme for dynamics close to the boundary of the realizable set $\cR$.  
+The purpose of this test is to further gauge the accuracy of the two-moment model and demonstrate the robustness of the DG scheme for dynamics close to the boundary of the realizable set $\cR$.  
 The computational domain is $D=\{x:x\in[-1,1]\}$, and the initial condition is obtained from a distribution function given by
@@
 \end{equation}
-so that $\vect{\cM}=\big(0.5\,(1+\delta),0.25\,(1-\delta)\big)^{T}$ for $x\le x_{\mbox{\tiny D}}$, and $\vect{\cM}=\big(\delta,0\big)^{T}$ for $x> x_{\mbox{\tiny D}}$, where $\delta>0$ is a small parameter ($\delta\ll1$).
+so that, with $\mu_{\mbox{\tiny D}}=0$, $\vect{\cM}\equiv\vect{\cM}_{\mbox{\tiny L}}=\big(0.5\,(1+\delta),0.25\,(1-\delta)\big)^{T}$ for $x\le x_{\mbox{\tiny D}}$, and $\vect{\cM}\equiv\vect{\cM}_{\mbox{\tiny R}}=\big(\delta,0\big)^{T}$ for $x> x_{\mbox{\tiny D}}$, where $\delta>0$ is a small parameter ($\delta\ll1$).
 We let $\delta=10^{-8}$, so that the initial conditions are very close to the boundary of the realizable domain (cf. Figure~\ref{fig:RealizableSetFermionic}).  
@@
 For the results obtained with the CB closure, the limiter was enacted whenever moments ventured outside the realizable set given by Eq.~\eqref{eq:realizableSet}.  
-For the results obtained with the Minerbo closure, which is not based on Fermi-Dirac statistics, we used a modified limiter, which was enacted when the moments ventured outside the realizable domain of positive distributions (not bounded by $f\le1$; see dashed red line in Figure~\ref{fig:RealizableSetFermionic}).
+For the results obtained with the Minerbo closure, which is not based on Fermi-Dirac statistics, we used a modified limiter, which was enacted when the moments ventured outside the realizable domain of positive distributions; i.e., not bounded by $f\le1$, so that $\cJ\ge0$ and $\cJ\ge|\vect{\cH}|$ (e.g., \cite{levermore_1984}; see dashed red line in Figure~\ref{fig:RealizableSetFermionic}).
 
@@
 
-As can be seen in Figure~\ref{fig:PackedBeam}, with the CB closure the numerical solution obtained with the two-moment model tracks the analytic solution well, while with the Minerbo closure the numerical solution deviates substantially, and also evolves outside the realizable domain for Fermi-Dirac statistics (see Figure~\ref{fig:PackedBeam_Realizability}).
+As can be seen in Figure~\ref{fig:PackedBeam}, with the CB closure the numerical solution obtained with the two-moment model tracks the analytic solution well, while with the Minerbo closure the numerical solution deviates substantially from the analytic solution.
+With the Minerbo closure, the solution also evolves outside the realizable domain for Fermi-Dirac statistics.
+
+In the left panel in Figure~\ref{fig:PackedBeam_Realizability} we plot $\gamma(\vect{\cM})=\big(1-\cJ\big)\,\cJ-|\vect{\cH}|$ versus position for various times.  
+With the Minerbo closure, $\gamma(\vect{\cM})$ becomes negative in regions of the computational domain (dashed lines), while $\gamma(\vect{\cM})$ remains positive for all $x$ and $t$ the CB closure.  
+In the right panel of Figure~\ref{fig:PackedBeam_Realizability} we plot the numerical solutions in the $(\cH,\cJ)$-plane.  
+Initially, the moments are located in two points: $\vect{\cM}_{\mbox{\tiny L}}$ and $\vect{\cM}_{\mbox{\tiny R}}$, for $x\le0$ and $x>0$, respectively.  
+For $t>0$, the solutions trace out curves in the $(\cH,\cJ)$-plane, connecting $\vect{\cM}_{\mbox{\tiny L}}$ and $\vect{\cM}_{\mbox{\tiny R}}$.  
+With the CB closure, the solution curve (blue points) follows the boundary of the realizable set $\cR$ defined in Eq.~\eqref{eq:realizableSet} (cf.
+black line in Figure~\ref{fig:PackedBeam_Realizability}).
+With the Minerbo closure (magenta points), the solution follows a different curve --- outside the realizable domain for distribution functions bounded by $f\in[0,1]$, but inside the realizable domain of positive distributions (cf.
+red line in Figure~\ref{fig:PackedBeam_Realizability}).
 We have also run this test using the algebraic maximum entropy closure of Larecki \& Banach \cite{lareckiBanach_2011} and the simpler Kershaw-type closure in \cite{banachLarecki_2017a}.  
@@
 Results obtained with the CB closure, which remain positive throughout the evolution, are plotted with solid lines, while results obtained with the Minerbo closure are plotted with dashed lines.
-In the right panel, the moments are plotted in $(\cJ,\cH)$-space for the same times as in the left panel.
+In the right panel, the moments are plotted in the $(\cH,\cJ)$-plane for the same times as in the left panel.
 Results obtained with the CB and Minerbo closures are plotted in blue and magenta, respectively.
-The solid black and red lines are contour where $(1-\cJ)\,\cJ=\cH$ and $\cJ=\cH$, respectively.}
+The solid black and red lines are contours where $(1-\cJ)\,\cJ=\cH$ and $\cJ=\cH$, respectively.}
   \label{fig:PackedBeam_Realizability}
@@
 We set $\sigma_{\mbox{\tiny G}}=0.03$, and run this test to a final time of $t=1.0$.  
-We run this test using a grid of $512^{2}$ elements, polynomials of degree $k=1$, and the SSPRK2 time stepping scheme.  
+We run this test using a grid of $512^{2}$ elements, polynomials of degree $k=1$, and the SSPRK2 time stepping scheme; a second-order accurate scheme.  
 (There are no collisions in this test; i.e., $\sigma_{\Ab}=\sigma_{\Scatt}=0$.)  

### 2018-05-11 Documents/M1/realizableFermionicM1/sections/numerical.tex
Added text for the Fermion Implosion problem

@@
 The next test is inspired by line source benchmark (cf. \cite{brunner_2002,garrettHauck_2013}), which is a challenging test for approximate transport algorithms.  
-The original line source test consists of an initial delta function particle distribution in radius $R=|\vect{x}|$; i.e., $f_{0}=\delta(R)/4\,\pi$.  
-For $t>0$, a radiation front propagates in the radial direction, away from the initial source.  
+The original line source test consists of an initial delta function particle distribution in radius $R=|\vect{x}|$; i.e., $f_{0}=\delta(R)$.  
+For $t>0$, a radiation front propagates in the radial direction, away from $R=0$.  
 Apart from capturing details of the exact transport solution, maintaining realizability of the two-moment solution is challenging.
 
-Here, a modified version of the line source --- dubbed \emph{Fermion Implosion},  designed to test the realizability-preserving properties of the two moment model for fermionic transport --- is computed on a two-dimensional domain with $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[-1.28,1.28], x^{2}\in[-1.28,1.28]\}$.
-Instead of initializing with a delta function, we follow the initialization procedure in \cite{garrettHauck_2013}, and approximate the initial condition with an isotropic Gaussian distribution function.
-Morover, the initial distribution function is bounded $f_{\mbox{\tiny G},0}\in(0,1)$ and reaches a minimum in the center of the computational domain (hence implosion)
+Here, a modified version of the line source --- dubbed \emph{Fermion Implosion},  designed to test the realizability-preserving properties of the two moment model for fermionic transport --- is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[-1.28,1.28], x^{2}\in[-1.28,1.28]\}$.
+Instead of initializing with a delta function, we follow the initialization procedure in \cite{garrettHauck_2013}, and approximate the initial condition using an isotropic Gaussian distribution function.
+However, different from \cite{garrettHauck_2013}, the initial distribution function is bounded $f_{0}\in(0,1)$, and reaches a minimum in the center of the computational domain (hence implosion)
 \begin{equation}
-  f_{\mbox{\tiny G},0}
-  =1-\max\Big[\,e^{-R^{2}/(2\,\sigma_{\mbox{\tiny G}}^{2})},10^{-8}\,\Big].  
+  f_{0}
+  =1-\max\Big[\,e^{-R^{2}/(2\,\sigma_{0}^{2})},10^{-8}\,\Big].  
 \end{equation}
-We set $\sigma_{\mbox{\tiny G}}=0.03$, and run this test to a final time of $t=1.0$.  
-We run this test using a grid of $512^{2}$ elements, polynomials of degree $k=1$, and the SSPRK2 time stepping scheme; a second-order accurate scheme.  
-(There are no collisions in this test; i.e., $\sigma_{\Ab}=\sigma_{\Scatt}=0$.)  
-We present results using both the algebraic closure of Cernohorsky \& Bludman and the Minerbo closure.
+We set $\sigma_{0}=0.03$, and evolve to a final time of $t=1.0$.  
+We run this test using a grid of $512^{2}$ elements, polynomials of degree $k=1$, and the SSPRK2 time stepping scheme with $\dt=0.1\times\dx^{1}$; a second-order accurate scheme.  
+(There are no collisions included in this test; i.e., $\sigma_{\Ab}=\sigma_{\Scatt}=0$.)  
+For comparison, we present results using the algebraic closures of Cernohorsky \& Bludman (CB) and Minerbo.
 
@@
   \end{tabular}
-   \caption{}
+   \caption{Numerical results for the Fermion Implosion problem, computed both the CB and Minerbo closures.
+Spatial distribution of the number density $\cJ$ (CB closure only) at $t=1$ (upper left panel).
+Number density $\cJ$ versus radius $R=|\vect{x}|$ for various times ($t=0$, $0.1$, $0.2$, and $0.4$) for the CB (blue) and the Minerbo (magenta) closures (upper right panel).
+(The initial condition, same for both models, is plotted with cyan.)  Numerical solutions in the $(\cH_{x},\cJ)$-plane (lower left panel), for the same times as plotted in the upper right panel.
+Limiter parameters $\vartheta_{1}$ (solid) and $\vartheta_{2}$ (dashed) in Section~\ref{sec:limiter} (minimum over the whole computational domain) versus time (lower right panel).}
   \label{fig:Implosion}
 \end{figure}
+
+Numerical results for the Fermion Implosion problem are plotted in Figure~\ref{fig:Implosion}.  
+For $t>0$, the low-density region in the center of the computational domain is quickly filled in, and a cylindrical perturbation propagates radially away from the center.  
+For the model with the CB closure, this perturbation, seen as a depression in the density relative to the ambient medium, has reached $R\approx1$ for $t=1$ (upper left panel in Figure~\ref{fig:Implosion}).
+The right panel in Figure~\ref{fig:Implosion} illustrates the difference in dynamics resulting from the two closures.  
+With the CB closure (blue lines), the central density increases towards the maximum value of unity, and an low-density pulse propagates radially.  
+The amplitude of the pulse decreases with time due to the geometry of the problem.  
+For $t=0.4$, the peak depression in located around $R=0.34$ (with $\cJ\approx0.96$).  
+With the Minerbo closure, the central density continues to increase beyond unity, and reaches a maximum of about $\cJ\approx1.37$ at $t=0.1$.  
+The central density starts to decrease beyond this point in time, and a steepening pulse propagates radially away from the center.  
+(This pulse is trailing the pulse in the model computed with the CB closure.)  
+At $t=0.4$, a discontinuity appears to have formed around $R=0.2$, resulting in numerical oscillations.  
+Except for the positivity limiter (which is not triggered for this model), no limiters are used to prevent numerical oscillations.  
+In the lower left panel in Figure~\ref{fig:Implosion}, the moments are plotted in the $(\cH_{x},\cJ)$-plane for the same times as plotted in the upper left panel.  
+(Each dot represents the moments at a specific spatial point and time.)  
+Initially, $\vect{\cH}=0$, and all the moments lie on on the line connecting $(0,0)$ and $(0,1)$; cyan points.  
+With the CB closure (blue points), the moments are confined to evolve inside the realizable domain $\cR$ (black), while with the Minerbo closure, the moments are not confined to $\cR$, but to the region above the red lines (the realizable domain for moments of positive distribution functions), and this is the reason for the difference in dynamics in the two models.
+For the model with the CB closure, some moments evolve very close to the boundary of the realizable domain, and the positivity limiter is continuously triggered to damp these moments towards the cell average, which is realizable by the design of our numerical scheme.
+In the lower right panel in Figure~\ref{fig:Implosion} we plot the limiter parameters $\vartheta_{1}$ (solid) and $\vartheta_{2}$ (dashed) (cf.
+\eqref{eq:limitDensity} and \eqref{eq:limitMoments}) versus time for the CB closure model (blue) and the Minerbo closure model (magenta); the minimum over the whole computational domain is plotted.
+For the CB closure model, the limiter is triggered to prevent both density overshoots and $\gamma(\cM)<0$.  
+Late in the simulation ($t\gtrsim0.7$), the minimum value of $\vartheta_{2}$ is around $0.1$.  
+For the model using the Minerbo closure, the limiter is not triggered ($\vartheta_{1}=\vartheta_{2}=1$).
 

### 2018-05-16 Documents/M1/realizableFermionicM1/sections/realizability.tex
Some work on Section 3 (removed proof of Lemma 1).  And other minor fixes

@@
 In this paper, we seek to design a numerical method for solving the system of moment equations given by Eq.~\eqref{eq:momentEquations}, which preserves realizability of the moments; i.e., the moments evolve within the set of admissible values as dictated by Pauli's exclusion principle.
-(Since we only concern with the angular dependence of $f$ in this section, we simplify the notation by suppressing the $\vect{z}$ and $t$ dependence and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.)
+(Since we are only concerned with the angular dependence of $f$ in this section, we simplify the notation by suppressing the $\vect{z}$ and $t$ dependence and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.)
 
@@
 
-Obviously, realizable moments must satisfy the bounds imposed by $f$.  
-We proceed by stating the bounds on the moments by restating (with slightly modified proof) results from Theorem~7.1 in \cite{banachLarecki_2017a} in the following Lemma.  
+Realizable moments must satisfy the bounds imposed by $f$.  
+We proceed by stating the bounds on the moments by restating results from Theorem~7.1 in \cite{banachLarecki_2017a} in the following Lemma.  
 \begin{lemma}
@@
 \end{lemma}
-\begin{proof}
-  First, let $\mu=\cos\thetaNu$ and $\bbS^{1}:=\{\,\mu\,|\,\mu\in[-1,1]\,\}$, and write
-  \begin{equation}
-    \cJ=\f{1}{2}\int_{\bbS^{1}}\mathfrak{f}(\mu)\,d\mu,
-    \quad\text{where}\quad
-    \mathfrak{f}(\mu)=\f{1}{2\pi}\int_{0}^{2\pi}f(\mu,\phiNu)\,d\phiNu.  
-  \end{equation}  
-  Since $f(\omegaNu)\in[0,1]$, we have $\mathfrak{f}(\mu)\in[0,1]$, which implies $\cJ\in[0,1]$.  
-  Next we need to show that $|\vect{\cH}|\le(1-\cJ)\,\cJ$.  
-  Let $\widehat{\vect{n}}\in\bbR^{3}$ (independent of $\omegaNu$) be an arbitrary unit vector, and write
-  \begin{equation}
-    \widehat{\vect{n}}\cdot\vect{\cH}
-    =\f{1}{2} \int_{\bbS^{1}}\mathfrak{f}(\mu)\,\mu\,d\mu,
-    \label{eq:NdotH}
-  \end{equation}
-  where we have aligned the polar axis of the spherical momentum space coordinate system with $\widehat{\vect{n}}$; i.e., $\widehat{\vect{n}}\cdot\vect{\ell}(\omega)=\mu$.  
-  First, following \cite{banachLarecki_2017a}, we can write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
-  \begin{equation*}
-    (1-\cJ)\cJ - \f{1}{2}\int_{-1}^{1-2\cJ}(1-2\cJ-\mu)\,\mathfrak{f}(\mu)\,d\mu
-    -\f{1}{2}\int_{1-2\cJ}^{1}(2\cJ-1+\mu)\,[1-\mathfrak{f}(\mu)]\,d\mu.  
-  \end{equation*}
-  Since $\mathfrak{f}\in[0,1]$, $(1-2\cJ-\mu)$ is nonnegative on the interval $\mu\in[-1,1-2\cJ]$, and $(2\cJ-1+\mu)$ is nonnegative on the interval $\mu\in[1-2\cJ,1]$, we have $\widehat{\vect{n}}\cdot\vect{\cH}\le(1-\cJ)\,\cJ$.
-  In a similar manner, we can also write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
-  \begin{equation*}
-    -(1-\cJ)\cJ-\f{1}{2}\int_{-1}^{2\cJ-1}(1-2\cJ+\mu)\,[1-\mathfrak{f}(\mu)]\,d\mu
-    -\f{1}{2}\int_{2\cJ-1}^{1}(2\cJ-1-\mu)\,\mathfrak{f}(\mu)\,d\mu.  
-  \end{equation*}
-  Then, since $\mathfrak{f}\in[0,1]$, $(1-2\cJ+\mu)$ is nonpositive on the interval $\mu\in[-1,2\cJ-1]$, and $(2\cJ-1-\mu)$ is nonpositive on the interval $\mu\in[2\cJ-1,1]$, we have $\widehat{\vect{n}}\cdot\vect{\cH}\ge-(1-\cJ)\,\cJ$.
-  We therefore have $-(1-\cJ)\,\cJ\le\widehat{\vect{n}}\cdot\vect{\cH}\le(1-\cJ)\,\cJ$.  
-  Since this holds for any unit vector $\widehat{\vect{n}}\in\bbR^{3}$, we must have $|\vect{\cH}|\le(1-\cJ)\,\cJ$.  
-\end{proof}
+The proof is given in \cite{banachLarecki_2017a} and is omitted.  
+(See also \cite{lareckiBanach_2011,banachLarecki_2013}.)
+%\begin{proof}
+%  First, let $\mu=\cos\thetaNu$ and $\bbS^{1}:=\{\,\mu\,|\,\mu\in[-1,1]\,\}$, and write
+%  \begin{equation}
+%    \cJ=\f{1}{2}\int_{\bbS^{1}}\mathfrak{f}(\mu)\,d\mu,
+%    \quad\text{where}\quad
+%    \mathfrak{f}(\mu)=\f{1}{2\pi}\int_{0}^{2\pi}f(\mu,\phiNu)\,d\phiNu.  
+%  \end{equation}  
+%  Since $f(\omegaNu)\in[0,1]$, we have $\mathfrak{f}(\mu)\in[0,1]$, which implies $\cJ\in[0,1]$.  
+%  Next we need to show that $|\vect{\cH}|\le(1-\cJ)\,\cJ$.  
+%  Let $\widehat{\vect{n}}\in\bbR^{3}$ (independent of $\omegaNu$) be an arbitrary unit vector, and write
+%  \begin{equation}
+%    \widehat{\vect{n}}\cdot\vect{\cH}
+%    =\f{1}{2} \int_{\bbS^{1}}\mathfrak{f}(\mu)\,\mu\,d\mu,
+%    \label{eq:NdotH}
+%  \end{equation}
+%  where we have aligned the polar axis of the spherical momentum space coordinate system with $\widehat{\vect{n}}$; i.e., $\widehat{\vect{n}}\cdot\vect{\ell}(\omega)=\mu$.  
+%  First, following \cite{banachLarecki_2017a}, we can write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
+%  \begin{equation*}
+%    (1-\cJ)\cJ - \f{1}{2}\int_{-1}^{1-2\cJ}(1-2\cJ-\mu)\,\mathfrak{f}(\mu)\,d\mu
+%    -\f{1}{2}\int_{1-2\cJ}^{1}(2\cJ-1+\mu)\,[1-\mathfrak{f}(\mu)]\,d\mu.  
+%  \end{equation*}
+%  Since $\mathfrak{f}\in[0,1]$, $(1-2\cJ-\mu)$ is nonnegative on the interval $\mu\in[-1,1-2\cJ]$, and $(2\cJ-1+\mu)$ is nonnegative on the interval $\mu\in[1-2\cJ,1]$, we have $\widehat{\vect{n}}\cdot\vect{\cH}\le(1-\cJ)\,\cJ$.
+%  In a similar manner, we can also write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
+%  \begin{equation*}
+%    -(1-\cJ)\cJ-\f{1}{2}\int_{-1}^{2\cJ-1}(1-2\cJ+\mu)\,[1-\mathfrak{f}(\mu)]\,d\mu
+%    -\f{1}{2}\int_{2\cJ-1}^{1}(2\cJ-1-\mu)\,\mathfrak{f}(\mu)\,d\mu.  
+%  \end{equation*}
+%  Then, since $\mathfrak{f}\in[0,1]$, $(1-2\cJ+\mu)$ is nonpositive on the interval $\mu\in[-1,2\cJ-1]$, and $(2\cJ-1-\mu)$ is nonpositive on the interval $\mu\in[2\cJ-1,1]$, we have $\widehat{\vect{n}}\cdot\vect{\cH}\ge-(1-\cJ)\,\cJ$.
+%  We therefore have $-(1-\cJ)\,\cJ\le\widehat{\vect{n}}\cdot\vect{\cH}\le(1-\cJ)\,\cJ$.  
+%  Since this holds for any unit vector $\widehat{\vect{n}}\in\bbR^{3}$, we must have $|\vect{\cH}|\le(1-\cJ)\,\cJ$.  
+%\end{proof}
 
-We now define the realizable set $\cR$:
+Next we define the realizable set $\cR$ for the fermion two-moment model
 \begin{equation}
@@
   Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements in $\cR$.  
-  Let $\vect{\cM}_{ab} = \theta\,\vect{\cM}_{a} + (1-\theta)\,\vect{\cM}_{b}$, with $0\leq\theta\leq1$.
-  The first component of $\vect{\cM}_{ab}$ is
+  Consider the convex combination $\vect{\cM}_{c} = \theta\,\vect{\cM}_{a} + (1-\theta)\,\vect{\cM}_{b}$, with $0\leq\theta\leq1$.
+  The first component of $\vect{\cM}_{c}$ is
   \begin{equation*}
-    \cJ_{ab} = \theta\,\cJ_{a} + (1-\theta)\,\cJ_{b}.
+    \cJ_{c} = \theta\,\cJ_{a} + (1-\theta)\,\cJ_{b}.
   \end{equation*}
-  Since $\theta,\cJ_{a},\cJ_{b}\in[0,1]$, we have $\cJ_{ab} \in [0,1]$.  
+  Since $\theta,\cJ_{a},\cJ_{b}\in[0,1]$, we have $\cJ_{c} \in [0,1]$.  
   It is straightforward to verify that $\gamma(\vect{\cM})$ is a concave function of $\bcM$ if $\cJ\in[0,1]$.
@@
   \begin{equation*}
-  \gamma(\vect{\cM}_{ab}) \geq \theta\,\gamma(\vect{\cM}_{a}) + (1-\theta)\,\gamma(\vect{\cM}_{b}) \ge0.
+  \gamma(\vect{\cM}_{c}) \geq \theta\,\gamma(\vect{\cM}_{a}) + (1-\theta)\,\gamma(\vect{\cM}_{b}) \ge0.
   \end{equation*}
-  Hence, $\vect{\cM}_{ab}\in\cR$.
+  Hence, $\vect{\cM}_{c}\in\cR$.
 \end{proof}
 
-Figure~\ref{fig:RealizableSetFermionic} illustrates the geometry of the convex set $\cR$ in $|\vect{\cH}| - \cJ$ coordinates (light blue region).
+Figure~\ref{fig:RealizableSetFermionic} illustrates the geometry of the convex set $\cR$ in the $(\cH,\cJ)$-plane (light blue region).  
+The boundary of $\cR$, $\partial\cR$ (black curves), is given by $\gamma(\vect{\cM})=0$.  
+The realizable domain of positive distribution functions, $\cR^{+}$ (no upper bound on $f$), a convex cone defined by
+\begin{equation}
+  \cR^{+}:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\ge0~\text{and}~\cJ\ge|\vect{\cH}|\,\big\}, 
+  \label{eq:realizableSetPositive}
+\end{equation}
+is partially shown as the region above the red lines.  
+(A Realizability-preserving method, with respect to $\cR^{+}$, for the two-moment model in one spatial dimension was developed in \cite{olbrant_etal_2012}.)
 
@@
   \caption{Illustration of the realizable set $\cR$ defined in Eq.~\eqref{eq:realizableSet}.  
-  The black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$ while the dash red lines is the boundary given by the Maxwell's distributions.}
+  The black lines define the boundary of $\cR$, $\partial\cR$ ($\gamma(\vect{\cM}) = 0$), while the red lines indicate the boundary of the realizable set of positive distributions with no upper bound; cf.
+Eq.~\eqref{eq:realizableSetPositive}.}
   \label{fig:RealizableSetFermionic}

### 2018-05-17 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Some work on Section 3 (removed proof of Lemma 1).  And other minor fixes
Work on algebraic closure section

@@
 
+The two-moment model given by Eq.~\eqref{eq:angularMoments} is not closed because of the appearance of the second moments $\vect{\cK}$ (the normalized pressure tensor).  
 Algebraic moment closures for the two-moment model are computationally efficient as they provide the Eddington factor in Eq.~\eqref{eq:eddingtonTensor} in closed form as a function of the density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$.
 For this reason they are widely used in applications where radiation transport plays an important role --- including simulation of neutrino transport in core-collapse supernovae \cite{roberts_etal_2016} and compact binary mergers \cite{foucart_etal_2015}.
+Algebraic moment closures in the context of these aforementioned applications have also been discussed elsewhere (e.g., \cite{pons_etal_2000,smit_etal_2000,just_etal_2015,murchikova_etal_2017}).  
 The family of algebraic closures we consider in this paper can be written in the form \cite{cernohorskyBludman_1994}
@@
 \end{equation}
-where the closure function $\Theta(x)$ varies with the specifics of the closure procedure.  
+where the \emph{closure function} $\Theta(x)$ varies with the specifics of the closure procedure.  
 We will consider two basic closure procedures in more detail below: the maximum entropy (ME) closure and the Kershaw (K) closure.
@@
 \paragraph{Low Occupancy Limit}
-We note in passing that in the low occupancy limit ($\cJ\ll1$), the Eddington factor in Eq.~\eqref{eq:eddingtonFactor} becomes independent of $\cJ$; i.e.,
+We note in passing that in the low occupancy limit ($\cJ\ll1$), the Eddington factor in Eq.~\eqref{eq:eddingtonFactor} depends solely on $h$; i.e.,
 \begin{equation}
@@
 \end{equation}
+This is also a form of algebraic moment closure suitable for particle systems obeying Maxwell-Boltzmann statistics.
 
@@
 
-For the two-moment model, the ME closure constructs the least biased angular distribution based on the limited information available (i.e., $\cJ$ and $\vect{\cH}$) \cite{cernohorskyBludman_1994}.  
+For the two-moment model, the ME closure constructs the least biased angular distribution based on the limited information available (i.e., $\cJ$ and $\vect{\cH}$) \cite{cernohorskyBludman_1994,lareckiBanach_2011}.
 The ME distribution $f_{\mbox{\tiny ME}}(\omega)$ is found by maximizing the entropy functional, which for particles obeying Fermi-Dirac statistics is given by
@@
 \end{equation}
-From the variation of the entropy functional in Eq.~\eqref{eq:entropyFunctional} with respect to $f_{\mbox{\tiny ME}}$, and introducing Lagrange multipliers to enforce the constraints in Eq.~\eqref{eq:closureConstraints}, the ME distribution takes the general form
+From the variation of the entropy functional in Eq.~\eqref{eq:entropyFunctional} with respect to $f_{\mbox{\tiny ME}}$, and introducing Lagrange multipliers ($a$ and $\vect{b}$) to enforce the constraints in Eq.~\eqref{eq:closureConstraints}, the ME distribution takes the general form
 \begin{equation}
-  f_{\mbox{\tiny ME}}(\omega;a,\vect{b})=\f{1}{e^{a + \vect{b}\cdot\vect{\ell}}+1}, 
+  f_{\mbox{\tiny ME}}(\omega;a,\vect{b})=\f{1}{e^{a + \vect{b}\cdot\vect{\ell}(\omega)}+1}.  
   \label{eq:fME}
 \end{equation}
-which can be further simplified by a change of coordinates $a + \vect{b}\cdot\vect{\ell}=a + b\,\mu$, where $b=|\vect{b}|$, and $\mu\in[-1,1]$ is the cosine of the angle between $\vect{b}$ and $\vect{\ell}$.
-The Lagrange multipliers are implicit functions of $\cJ$ and $|\vect{\cH}|$.  
-The ME distribution function satisfies $0 \le f_{\mbox{\tiny ME}} \le 1$, but $a$ and $b$ are unconstrained.
+The Lagrange multipliers are implicit functions of $\cJ$ and $\vect{\cH}$.  
+The ME distribution function satisfies $0 \le f_{\mbox{\tiny ME}} \le 1$, but $a$ and $\vect{b}$ are unconstrained.  
+Specification of $a$ and $\vect{b}$ from $\vect{\cM}=(\cJ,\vect{\cH})^{T}$ gives $f_{\mbox{\tiny ME}}$, and any number of moments can in principle be computed.  
+Importantly, we note that for the maximum entropy problem to be soluble, we must have $\vect{\cM}\in\cR$ \cite{lareckiBanach_2011}.
 
-Chernohorsky \& Bludman \cite{cernohorskyBludman_1994} postulate (but see \cite{lareckiBanach_2011}) that, as a function of the so-called flux saturation $x=h/(1-\cJ)$, the closure function $\Theta(x)$ is independent of $\cJ$ and can be written explicitly in terms of the inverse Langevin function.
-They also provide a polynomial fit (accurate to $2\%$) given by
+To arrive at the algebraic form of the ME closure, Chernohorsky \& Bludman \cite{cernohorskyBludman_1994} postulate (but see \cite{lareckiBanach_2011}) that, as a function of the so-called flux saturation $x=h/(1-\cJ)$, the closure function $\Theta(x)$ is independent of $\cJ$ and can be written explicitly in terms of the inverse Langevin function.
+To avoid inverting the Langevin function for $\Theta(x)$, they provide a polynomial fit (accurate to $2\%$) given by
 \begin{equation}
   \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny CB}}(x)
-  =x^{2}\,\big(\,3-x+3\,x^{2}\,\big).
+  =\f{1}{5}\,\big(\,3-x+3\,x^{2}\,\big)\,x^{2}.
   \label{eq:closureMECB}
@@
 On the interval $x\in[0,1]$, the curves given by Eqs.~\eqref{eq:closureMECB} and \eqref{eq:closureMEBL} lie practically on top of each other.  
+The closure functions given by Eqs.~\eqref{eq:closureMECB} and \eqref{eq:closureMEBL}, together with the Eddington factor in Eq.~\eqref{eq:eddingtonFactor} and the pressure tensor in Eq~\eqref{eq:eddingtonTensor}, constitute the algebraic maximum entropy closures for fermionic particle systems considered in this paper.
+We will refer to the ME closures with $\Theta_{\mbox{\tiny ME}}^{\mbox{\tiny CB}}$ and $\Theta_{\mbox{\tiny ME}}^{\mbox{\tiny BL}}$ as the CB (Cernohorsky \& Bludman) and BL (Banach \& Larecki) closures, respectively.
+
+We also note that using the closure function given by Eq.~\eqref{eq:closureMECB} with the low occupancy Eddington factor in Eq~\eqref{eq:eddingtonFactorLow} results in the algebraic maximum entropy closure attributed to Minerbo \cite{minerbo_1978}, which is currently in widespread use in simulation of neutrino (fermion) transport in the aforementioned nuclear astrophysics applications.
+In a recent comparison of algebraic (or analytic) closures for the two-moment model applied to neutrino transport around proto-neutron stars, Murchikova et al.
+\cite{murchikova_etal_2017} obtained nearly identical results when using the closures of CB and Minerbo.
+For these reasons, we include the Minerbo closure in the subsequent discussion and in the numerical tests in Section~\ref{sec:numerical}.
 
@@
 
+\subsection{Realizability of Algebraic Moment Closures}
+
+It is not immediately obvious that all the algebraic moment closures discussed above are suitable for the design of a realizability-preserving method for the two-moment model of fermion transport.  
+In particular, the realizability-preserving scheme developed in this paper is based on the result in Lemma~\ref{lem:explicitStep}, which must hold for the adapted closure.  
+The Kershaw closure is consistent with a bounded distribution, $f_{_{\mbox{\tiny K}}}\in[0,1]$, and should be well suited, but the algebraic ME closures are based on approximations to the closure function, and we must make sure that these approximate closures remain consistent with the assumed bounds on the underlying distribution function.
+To this end, we rely on results due to \cite{levermore_1984,lareckiBanach_2011} (see also \cite{kershaw_1976,shohatTamarkin_1943}):  Realizability of the moment triplet $\{\cJ,\vect{\cH},\vect{\cK}\}$ (i.e., they are consistent with a bounded distribution function $0 \le f<1$), with $\vect{\cM}=(\cJ,\vect{\cH})^{T}\in\cR$ and $\vect{\cK}$ given by Eq.~\eqref{eq:eddingtonTensor} is equivalent to the following requirement for the Eddington factor
+\begin{equation}
+  \chi_{\mbox{\tiny min}}
+  =\max\big(1-\f{2}{3\cJ},h^{2}\big)
+  <\chi<\min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}}.  
+\end{equation}
+(Note that for $\cJ\ll1$ this limits to the bounds for positive distributions given by Levermore \cite{levermore_1984}: $h^{2}\le\chi\le1.$)
+
+In Figure~\ref{}, we plot the Eddington factor $\chi$ versus the flux factor $h$ for the various algebraic closures discussed above for different values of $\cJ\in(0,1)$.
+
 Figure~\ref{fig:MabWithDifferentClosure} illustrates the behavior of these four closure.

### 2018-05-23 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Work on algebraic moment closures.

@@
 For this reason they are widely used in applications where radiation transport plays an important role --- including simulation of neutrino transport in core-collapse supernovae \cite{roberts_etal_2016} and compact binary mergers \cite{foucart_etal_2015}.
-Algebraic moment closures in the context of these aforementioned applications have also been discussed elsewhere (e.g., \cite{pons_etal_2000,smit_etal_2000,just_etal_2015,murchikova_etal_2017}).  
+Algebraic moment closures in the context of these aforementioned applications have also been discussed elsewhere (e.g., \cite{janka_etal_1992,pons_etal_2000,smit_etal_2000,just_etal_2015,murchikova_etal_2017}).
 The family of algebraic closures we consider in this paper can be written in the form \cite{cernohorskyBludman_1994}
@@
 
-The basic principle behind Kershaw closure is derived from the fact that the realizable set defined by $(\cJ, \vect{\cH}, \vect{K})$ is convex.
-Due to the convexity, any element in the convex set be expressed as a convex combination of two elements that on the set boundary, and vice versa.
-That is,
-\begin{align}
- \chi(\cJ,h) = \beta  \chi_{L}(\cJ,h) + (1-\beta) \chi_{U}(\cJ,h),
-\end{align}
-with $\chi_{L}$ and $\chi_{U}$ be the boundary elements, and $\beta \in [0,1]$. 
-The Kershaw closure uses a convex combination that determined by the isotropic distribution case to approximate $\chi(\cJ,h)$:
-\begin{align}
- \chi(\cJ,0)  &= \dfrac{1}{3},\\
-\chi_{L}(\cJ,h) & = \dfrac{1}{3}\cJ^2 + h^2, \\
-\chi_{U}(\cJ,h) & = \left( 1 - \cJ + \dfrac{1}{3}\cJ^2 \right) - \dfrac{h^2 \cJ}{1-\cJ},
-\end{align}
-$\chi_{L}$ and $\chi_{U}$ are given by the Heaviside function with Fermi-Dirac statistic function, and
-\begin{align}
-\beta = \dfrac{2 - \cJ}{3}.
-\end{align}
-Then the Kershaw closure function $\Theta(x)$ reads (Banach \& Larecki \cite{banachLarecki_2017a}):
+Another algebraic closure we consider is a Kershaw-type closure \cite{kershaw_1976}, developed for fermion particle systems in \cite{banachLarecki_2017a}.  
+The basic principle of the Kershaw closure for the two-moment model is derived from the fact that the realizable set generated by the triplet of scalar moments
 \begin{equation}
-  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
+  \{\cJ,\cH,\cK\}=\f{1}{2}\int_{-1}^{1}f(\mu)\,\mu^{\{0,1,2\}}\,d\mu,
+  \label{eq:scalarMoments}
 \end{equation} 
+is convex.  
+For the moments in Eq.~\eqref{eq:scalarMoments}, the realizable set is the set of moments obtained from distribution functions satisfying $0<f(\mu)<1,\,\forall\mu\in[-1,1]$.  
+(The moments in Eq.~\eqref{eq:scalarMoments} are the unique moments obtained from the moments in Eq.~\eqref{eq:angularMoments} under the assumption that the distribution function is isotropic about a preferred direction, and $\mu$ is the cosine of the angle between this preferred direction and the particle propagation direction given by $\vect{\ell}$.)
+
+For a bounded distribution $0<f<1$, it is possible to show that the second moment satisfies
+\begin{equation}
+  \cK_{\mbox{\tiny L}}(\cJ,h) < \cK < \cK_{\mbox{\tiny U}}(\cJ,h),
+\end{equation}
+where $\cK_{\mbox{\tiny L}}=\cJ\,\big(\,\f{1}{3}\,\cJ^{2}+h^{2}\,\big)$, $\cK_{\mbox{\tiny U}}=\cK_{\mbox{\tiny L}} + \cJ\,(1-\cJ)\,(1-x^{2})$, and $x=h/(1-\cJ)$.  
+By convexity, the convex combination
+\begin{equation}
+  \cK(\beta,\cJ,h)=\beta\,\cK_{\mbox{\tiny L}}(\cJ,h)+(1-\beta)\,\cK_{\mbox{\tiny U}}(\cJ,h),
+  \label{eq:kershawAnsatz}
+\end{equation}
+with $\beta\in[0,1]$, is realizable for realizable moments $(\cJ,\cH)^{T}\in\cR$.  
+The Kershaw closure for the two-moment model is then obtained from the ansatz in Eq.~\eqref{eq:kershawAnsatz} with the additional requirement that it be correct in the limit of isotropic distribution functions; i.e., $\cK(\beta,\cJ,0)=\cJ/3$.
+This occurs when $\beta=(2-\cJ)/3$, so that $\cK_{\mbox{\tiny K}}(\cJ,h)=\chi_{\mbox{\tiny K}}(\cJ,h)\,\cJ$, where
+\begin{equation}
+  \chi_{\mbox{\tiny K}}(\cJ,h)=\f{1}{3}+\f{2\,(1-\cJ)\,(1-2\cJ)}{3}\,\Theta_{\mbox{\tiny K}}\Big(\f{h}{1-\cJ}\Big),
+  \label{eq:eddingtonFactorKershaw}
+\end{equation}
+and the Kershaw closure function is given by \cite{banachLarecki_2017a}
+\begin{equation}
+  \Theta_{\mbox{\tiny K}}(x)=x^{2}.  
+\end{equation}
+For multidimensional problems, the Kershaw closure is obtained by using the Eddington factor in Eq.~\eqref{eq:eddingtonFactorKershaw} in Eq.~\eqref{eq:eddingtonTensor}.  
+We point out that for the Kershaw closure (see \cite{banachLarecki_2017a} for details), a distribution function $f_{\mbox{\tiny K}}$, satisfying $0\le f_{\mbox{\tiny K}}(\vect{\ell},\cJ,\vect{\cH})\le1$ and reproducing the moments $\cJ$, $\vect{\cH}$, and $\vect{\cK}$, can be written explicitly in terms of Heaviside functions.
 
@@
 The Kershaw closure is consistent with a bounded distribution, $f_{_{\mbox{\tiny K}}}\in[0,1]$, and should be well suited, but the algebraic ME closures are based on approximations to the closure function, and we must make sure that these approximate closures remain consistent with the assumed bounds on the underlying distribution function.
-To this end, we rely on results due to \cite{levermore_1984,lareckiBanach_2011} (see also \cite{kershaw_1976,shohatTamarkin_1943}):  Realizability of the moment triplet $\{\cJ,\vect{\cH},\vect{\cK}\}$ (i.e., they are consistent with a bounded distribution function $0 \le f<1$), with $\vect{\cM}=(\cJ,\vect{\cH})^{T}\in\cR$ and $\vect{\cK}$ given by Eq.~\eqref{eq:eddingtonTensor} is equivalent to the following requirement for the Eddington factor
+To this end, we rely on results due to \cite{levermore_1984,lareckiBanach_2011} (see also \cite{kershaw_1976,shohatTamarkin_1943}):  Realizability of the moment triplet $\{\cJ,\vect{\cH},\vect{\cK}\}$ (i.e., they are consistent with a bounded distribution function $0 \le f<1$), with $\vect{\cM}=(\cJ,\vect{\cH})^{T}\in\cR$ and $\vect{\cK}$ given by Eq.~\eqref{eq:eddingtonTensor}, is equivalent to the following requirement for the Eddington factor
 \begin{equation}
@@
   <\chi<\min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}}.  
+  \label{eq:eddingtonFactorBounds}
 \end{equation}
-(Note that for $\cJ\ll1$ this limits to the bounds for positive distributions given by Levermore \cite{levermore_1984}: $h^{2}\le\chi\le1.$)
+(Note that for $\cJ\ll1$ this limits to the bounds for positive distributions given by Levermore \cite{levermore_1984}; i.e., $h^{2}\le\chi\le1.$)
 
-In Figure~\ref{}, we plot the Eddington factor $\chi$ versus the flux factor $h$ for the various algebraic closures discussed above for different values of $\cJ\in(0,1)$.
+In Figure~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor $\chi$ versus the flux factor $h\,(\le 1-\cJ)$ for the various algebraic closures discussed above and for different values of $\cJ\in(0,1)$: $0.01$ (upper left panel), $0.4$ (upper right panel), $0.6$ (lower left panel), and $0.99$ (lower right panel).
+The maximum entropy closures of CB and BL are plotted with solid red and dashed orange lines respectively.  
+The Kershaw closure is plotted with dash-dot purple lines, while the Minerbo closure is plotted with solid blue lines.  
+The lower and upper bounds on the Eddington factor for realizable closures for fermion particle systems ($\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$, respectively) are plotted with solid black lines.
+We note that for all the closures, the Eddington factor $\chi\to1/3$ as $h\to0^{+}$.  
+For $\cJ=0.01$, the maximum entropy closures (CB, BL, and Minerbo) are practically indistinguishable, while the Eddington factor of the Kershaw closure is clearly larger than that of the other closures over most of the domain.
+For $\cJ=0.4$, the Eddington factor for the closures based on Fermi-Dirac statistics (CB, BL, and Kershaw) remain close together, while the Eddington factor for the Minerbo closure is clearly above the other closures for $h\gtrsim0.2$.
+All closures remain between $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ for $\cJ=0.01$ and $\cJ=0.4$.  
+For $\cJ=0.6$, the Eddington factor for the closures based on Fermi-Dirac statistics remain close together and within the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.  
+The dependence of the Eddington factor on $h$ of the Minerbo closure is clearly different from the other closures (i.e., increases vs decreases with increasing $h$), and exceeds $\chi_{\mbox{\tiny max}}$ for $h\gtrsim0.34$.
+For $\cJ=0.99$, the Eddington factor of the CB and BL closures (indistinguishable) and the Kershaw closure remain within the bounds given in Eq.~\eqref{eq:eddingtonFactorBounds}.  
+The Eddington factor of the Minerbo closure is nearly flat, and exceeds $\chi_{\mbox{\tiny max}}$ for $h\gtrsim0.006$.  
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{figures/Closures0_01}
+    \includegraphics[width=0.5\textwidth]{figures/Closures0_40} \\
+    \includegraphics[width=0.5\textwidth]{figures/Closures0_60}
+    \includegraphics[width=0.5\textwidth]{figures/Closures0_99}
+  \end{tabular}
+   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.01$ (upper left panel), $\cJ=0.4$ (upper right panel), $\cJ=0.6$ (lower left panel), and $\cJ=0.99$ (lower right panel).
+In each panel we plot the Eddington factors of Kershaw (solid blue lines), Chernohorsky \& Bludman (CB, solid red lines), Banach \& Larecki (BL, dashed orange lines), and Minerbo (dash-dot purple lines).
+We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ (lower and upper solid black lines, respectively).}
+  \label{fig:EddingtonFactorsWithDifferentClosure}
+\end{figure}
+We have also checked that for all the algebraic closures based on Fermi-Dirac statistics (CB, BL, and Kershaw), the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds} holds for all $\vect{\cM}\in\cR$.
+Thus, we conclude that these closures are suited for development of realizability-preserving numerical methods for the two-moment model of fermion transport.
 
-Figure~\ref{fig:MabWithDifferentClosure} illustrates the behavior of these four closure.
-As it shows, Minerbo closure (right bottom) is the only one among those four closures that does not preserve realizability.
+In Figure~\ref{fig:MabWithDifferentClosure}, we further illustrate the properties of the algebraic closures by plotting $\vect{\cM}_{ab}$ as defined in Lemma~\ref{lem:explicitStep}.  
+In each of the four panels, representing the algebraic closures discussed above, we plot $\vect{\cM}_{ab}$ constructed from randomly selected pairs $\vect{\cM}_{a},\vect{\cM}_{b}\in\cR$ (each blue dot represents one realization of $\vect{\cM}_{ab}$).
+Results for the maximum entropy closures of BL and CB are plotted in the upper panels (left and right panel, respectively).  
+Results for the Kershaw closure are plotted in the lower left panel, while results for the Minerbo closure are plotted in the lower right panel.  
+As expected for closures consistent with moments of a Fermi-Dirac distribution function, we find $\vect{\cM}_{ab}\in\cR$ for the CB, BL, and Kershaw closures.  
+For the Minerbo closure (right bottom), which is consistent with positive distributions, $\vect{\cM}_{ab}$ is not confined to $\cR$.
 \begin{figure}[h]
@@
   \end{tabular}
-   \caption{Illustration of $\vect{\cM}_{ab}$ with four different closures: Banach \& Larecki maximum entropy closure (left top), Chernohorsky \& Bludman maximum entropy closure (right top), Kershaw closure (left bottom), and Minerbo closure (right bottom).
-   Total $10^{6}$ pairs of random Fermi-Dirac distribution were generated.
-   With these pairs, $\vect{\cM}_{ab}$ with different closures were calculated separately and marked with light-blue points.
-   Black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
+   \caption{Illustration of $\vect{\cM}_{ab}$, as defined in Lemma~\ref{lem:explicitStep}, computed with different algebraic closures: the maximum entropy closures of Banach \& Larecki (top left) and Chernohorsky \& Bludman (top right), the Kershaw closure (bottom left), and the maximum entropy closure of Minerbo (bottom right).
+In each panel, $\vect{\cM}_{ab}$ was computed using the respective closure, using $10^{6}$ random pairs ($\vect{\cM}_{a},\vect{\cM}_{b}\in\cR$), and plotted as a light-blue point.
+The solid black lines mark the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
   \label{fig:MabWithDifferentClosure}

### 2018-05-23 Documents/M1/realizableFermionicM1/sections/numerical.tex
Some work on Section 3 (removed proof of Lemma 1).  And other minor fixes
Work on algebraic moment closures.

@@
 
+\clearpage
+
 \subsection{Homogeneous Sphere}
@@
 \end{equation}
-where
+where $r=|\vect{x}|$ and
 \begin{equation}
@@
 and $g(r,\mu)=[1-(r/R)^{2}(1-\mu^{2})]^{1/2}$.  
+For $f_{0}\in[0,1]$, the solution remains bounded between $0$ and $1$.
+
+This test is computed on a three-dimensional domain $D=\{\vect{x}\in\bbR^{3}:x^{1}\in[0,2], x^{2}\in[0,2], x^{3}\in[0,2]\}$.  
+Because of the symmetry of the problem, and to save computational resources, we only compute the solution in one octant.  
+On the inner boundaries, we impose reflecting boundary conditions, while we impose homogeneous boundary conditions on the outer boundary in all three coordinate dimensions.  
+Since this test is computed using Cartesian using a relatively low spatial resolution ($64^{3}$), we have found it necessary to smooth out the opacity over a finite radial extent to avoid numerical artifacts due to a discontinuous absorption opacity.
+Specifically, we use an absorption opacity of the following form
+\begin{equation}
+  \sigma_{\Ab}(r)=\f{\sigma_{\Ab,0}}{(r/R_{0})^{p}+1}.  
+\end{equation}
+We set $f_{0}=1$, and compute two versions of this test: one with $\sigma_{\Ab,0}=10$, $R_{0}=1$, and $p=80$ (Test A), and one with $\sigma_{\Ab}=10^{3}$, $R_{0}=0.85$, and $p=40$ (Test B).  
+(These values for $R_{0}$ and $p$ result in similar radius for where the optical depth equals $2/3$ in both tests.)
+We compute until $t=5$, when the system has reached a steady state.  
+The main purpose of this test is to compare the results obtained using the different algebraic closures discussed in Section~\ref{sec:algebraicClosure}.
 
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Resolution_3}
   \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_1}
-    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_2}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_ClosureComparison_Density}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_ClosureComparison_FluxFactor}
   \end{tabular}
-   \caption{Homogeneous sphere problem: 32$^{3}$, 48$^{3}$, and 64$^{3}$}
-  \label{fig:HomogeneousSphere_Resolution}
+   \caption{Homogeneous sphere problem}
+  \label{fig:HomogeneousSphere}
 \end{figure}
+
+\clearpage

### 2018-05-24 Documents/M1/realizableFermionicM1/sections/numerical.tex
First complete draft of text on the homogeneous sphere test

--- 2018-05-11 Documents/M1/realizableFermionicM1/sections/numerical.tex
@@
 and $g(r,\mu)=[1-(r/R)^{2}(1-\mu^{2})]^{1/2}$.  
+For $f_{0}\in[0,1]$, the analytical solution is bounded $f_{\mbox{\tiny A}}\in[0,1]$.
 
+Here, this test is computed on a three-dimensional Cartesian domain $D=\{\vect{x}\in\bbR^{3}:x^{1}\in[0,2], x^{2}\in[0,2], x^{3}\in[0,2]\}$.  
+Because of the symmetry of the problem, and to save computational resources, we only compute the solution in one octant.  
+On the inner boundaries, we impose reflecting boundary conditions, while we impose 'homogeneous' boundary conditions on the outer boundary in all three coordinate dimensions; i.e., values for all moments in a boundary element are set equal to the corresponding values in the nearest element just inside $D$.
+Since this test is computed with Cartesian coordinates using a relatively low spatial resolution ($64^{3}$), we have found it necessary to smooth out the opacity over a finite radial extent to avoid numerical artifacts due to a discontinuous absorption opacity.
+Specifically, we use an absorption opacity of the following form
+\begin{equation}
+  \sigma_{\Ab}(r)=\f{\sigma_{\Ab,0}}{(r/R_{0})^{p}+1}.  
+\end{equation}
+We set $f_{0}=1$, and compute three versions of this test: one with $\sigma_{\Ab,0}=1$, $R_{0}=1$, and $p=80$ (Test~A), one with $\sigma_{\Ab,0}=10$, $R_{0}=1$, and $p=80$ (Test~B), and one with $\sigma_{\Ab}=10^{3}$, $R_{0}=0.85$, and $p=40$ (Test~C).
+(These values for $R_{0}$ and $p$ result in similar radius for where the optical depth equals $2/3$ in Test~B and Test~C.)
+We compute until $t=5$, when the system has reached an approximate steady state.  
+We use the IMEX scheme PARSD in all the tests.  
+The main purpose of this test is to compare the results obtained using the different algebraic closures discussed in Section~\ref{sec:algebraicClosure}.
+
+In Figure~\ref{fig:HomogeneousSphere}, we plot results obtained for all tests at $t=5$: Test~A (top panels), Test~B (middle panels), and Test~C (bottom panels).  
+The particle density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$ are plotted versus radius $r=|\vect{x}|$ (left and right panels, respectively).  
+In each panel, results obtained with the various algebraic closures discussed in Section~\ref{sec:algebraicClosure} are plotted: Minerbo (magenta), CB (blue), BL (green), and Kershaw (cyan).  
+The analytical solution is also plotted (dashed black lines).  
 \begin{figure}[h]
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Resolution_3}
   \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_1}
-    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_2}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_ClosureComparison_Chi_1e0_Density}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_ClosureComparison_Chi_1e0_FluxFactor} \\
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_ClosureComparison_Chi_1e1_Density}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_ClosureComparison_Chi_1e1_FluxFactor} \\
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_ClosureComparison_Chi_1e3_Density}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_ClosureComparison_Chi_1e3_FluxFactor}
   \end{tabular}
-   \caption{Homogeneous sphere problem: 32$^{3}$, 48$^{3}$, and 64$^{3}$}
-  \label{fig:HomogeneousSphere_Resolution}
+   \caption{Results obtained for the homogeneous sphere problem with the two-moment model for different values of the absorption opacity $\sigma_{\Ab,0}$: $1$ (top panels), $10$, (middle panels), and $1000$ (bottom panels).
+The particle density (left panels) and the flux factor (right panels) are plotted versus radius.
+Numerical results obtained with the algebraic closures of Minerbo (magenta), CB (blue), BL (green), and Kershaw (cyan) are compared with the analytic solution (dashed black lines).}
+  \label{fig:HomogeneousSphere}
 \end{figure}
+
+We find good overall agreement between the results obtained with the two-moment model and the analytical solution.  
+Partly due to the smoothing of the absorption opacity around the surface, the numerical and analytical solutions naturally differ around $r=1$.  
+Aside from some differences discussed in more detail below, the numerical and analytical solutions --- for all values of the absorption opacity $\sigma_{\Ab,0}$ and all closures --- agree well as $r$ tends to zero, as well as when $r\gg1$.
+The results obtained with the maximum entropy closures CB and BL are practically indistinguishable on the plots.  
+This is consistent with the similarity of the Eddington factors for these two closures plotted in Figure~\ref{fig:EddingtonFactorsWithDifferentClosure}.  
+We also find that the results obtained with the fermionic Kershaw closure agree well with the maximum entropy closures based on Fermi-Dirac statistics (CB and BL).  
+From the plots of the particle density (left panels in Figure~\ref{fig:HomogeneousSphere}), the results obtained with all the closures, including Minerbo, appear very similar.  
+The particle density obtained with the Minerbo closure deviates the most from the analytic solution inside $r\approx0.75$ for Test~A ($\sigma_{\Ab,0}=1$; upper left panel).  
+From the plots of the flux factor (right panels in Figure~\ref{fig:HomogeneousSphere}), it is evident that the results obtained with the Minerbo closure --- the only closure not based on Fermo-Dirac statistics --- deviates the most from the analytic solution outside $r=1$, where the flux factor is consistently higher than the analytical solution for all values of $\sigma_{\Ab,0}$.
+The fermionic closures (CB, BL, and Kershaw) track the analytic solution better.  
+Similar agreement between the numerical and analytical solutions was reported by Smit et al.
+\cite{smit_etal_1997}, when using the CB maximum entropy closure, with $f_{0}=0.8$ and an unsmoothed absorption opacity $\sigma_{\Ab}=4$.
+We also note that our results are at odds with the results recently reported by Murchikova et al.
+\cite{murchikova_etal_2017}, who compared results obtained with with the two-moment model using a large number of algebraic closures for this same problem (albeit using an unsmoothed and slightly different value for the absorption opacity).
+Murchikova et al.
+do not plot the particle density, but find essentially no difference in the flux factor and the Eddington factor when comparing results obtained with the maximum entropy closures of Minerbo and Cernohorsky \& Bludman (CB).
+
+In Figure~\ref{fig:HomogeneousSphereRealizability}, we further compare the results obtained when using the Minerbo and CB closures by plotting the solutions to the homogeneous sphere problem for Test~C at $t=5$ in the $(\cH_{1},\cJ)$-plane (cf.
+the realizable domain in Figure~\ref{fig:RealizableSetFermionic}):  The numerical solution in each spatial point is represented by a magenta dot in the panels.
+Results obtained using the CB closure are plotted in the upper left panel, while results obtained using the Minerbo closure are plotted in the upper right panel.  
+In the lower two panel we zoom in on the results obtained with the Minerbo closure around the top and lower right regions of the realizable domain (lower left and lower right panel, respectively; cf.
+blue boxes in the upper right panel).
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_CB}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_Minerbo} \\
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_Minerbo_Box1}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_Minerbo_Box2}
+  \end{tabular}
+   \caption{Plots of the numerical solution to the homogeneous sphere problem for Test~C in the $(\cH_{1},\cJ)$-plane.
+Results obtained with the CB and Minerbo closures are plotted in the upper left and upper right panels, respectively.
+Zoom-ins on the solutions obtained with the Minerbo closure are plotted in the lower two panels (cf.
+blue boxes in the upper right panel).
+The boundaries of the realizable domains $\cR$ and $\cR^{+}$ are indicated with solid black and solid red curves, respectively.
+See text for further details.
+}
+  \label{fig:HomogeneousSphereRealizability}
+\end{figure}
+As can be seen in the upper panels in Figure~\ref{fig:HomogeneousSphereRealizability}, the solution to the homogeneous sphere problem covers a large fraction of the right half of the realizable domain $\cR$, whose boundary is indicated by solid black curves in each panel.
+When using the CB closure, the realizability-preserving DG-IMEX scheme developed here maintains solutions within $\cR$.  
+When using the Minerbo closure, the appropriate realizable domain is given by $\cR^{+}$ (cf.
+Eq.~\eqref{eq:realizableSetPositive}), whose boundary is indicated by solid red lines in Figure~\ref{fig:HomogeneousSphereRealizability}, and we find that the numerical solution ventures outside $\cR$.
+Near the surface around $r=1$, the number density slightly exceeds unity (lower left panel), while for larger radii, the computed flux may exceed the value allowed by Fermi-Dirac statistics (lower right panel).

### 2018-05-29 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Modifications due to comments from Ran

@@
 Algebraic moment closures in the context of these aforementioned applications have also been discussed elsewhere (e.g., \cite{janka_etal_1992,pons_etal_2000,smit_etal_2000,just_etal_2015,murchikova_etal_2017}).
-The family of algebraic closures we consider in this paper can be written in the form \cite{cernohorskyBludman_1994}
+Here we focus on properties of the algebraic closures that are critical to the development of numerical methods for the two-moment model of fermion transport.  
+The family of algebraic closures we consider can be written in the form \cite{cernohorskyBludman_1994}
 \begin{equation}
@@
 The Kershaw closure for the two-moment model is then obtained from the ansatz in Eq.~\eqref{eq:kershawAnsatz} with the additional requirement that it be correct in the limit of isotropic distribution functions; i.e., $\cK(\beta,\cJ,0)=\cJ/3$.
-This occurs when $\beta=(2-\cJ)/3$, so that $\cK_{\mbox{\tiny K}}(\cJ,h)=\chi_{\mbox{\tiny K}}(\cJ,h)\,\cJ$, where
+One choice for $\beta$, which leads to a strictly hyperbolic and causal two-moment model (and a particularly simple closure function) \cite{banachLarecki_2017a}, is $\beta=(2-\cJ)/3$, so that $\cK_{\mbox{\tiny K}}(\cJ,h)=\chi_{\mbox{\tiny K}}(\cJ,h)\,\cJ$, where
 \begin{equation}
@@
 \end{equation}
-and the Kershaw closure function is given by \cite{banachLarecki_2017a}
+and the Kershaw closure function is given by
 \begin{equation}
@@
 For multidimensional problems, the Kershaw closure is obtained by using the Eddington factor in Eq.~\eqref{eq:eddingtonFactorKershaw} in Eq.~\eqref{eq:eddingtonTensor}.  
-We point out that for the Kershaw closure (see \cite{banachLarecki_2017a} for details), a distribution function $f_{\mbox{\tiny K}}$, satisfying $0\le f_{\mbox{\tiny K}}(\vect{\ell},\cJ,\vect{\cH})\le1$ and reproducing the moments $\cJ$, $\vect{\cH}$, and $\vect{\cK}$, can be written explicitly in terms of Heaviside functions.
+Finally, we point out that for the two-moment Kershaw closure (see \cite{banachLarecki_2017a} for details), a distribution function $f_{\mbox{\tiny K}}(\vect{\ell},\cJ,\vect{\cH})$, satisfying $0\le f_{\mbox{\tiny K}}\le1$, and reproducing the moments $\cJ$, $\vect{\cH}$, and $\vect{\cK}$, can be written explicitly in terms of Heaviside functions.
 
@@
 
-It is not immediately obvious that all the algebraic moment closures discussed above are suitable for the design of a realizability-preserving method for the two-moment model of fermion transport.  
+It is not immediately obvious that all the algebraic moment closures discussed above are suitable for designing realizability-preserving methods for the two-moment model of fermion transport.  
 In particular, the realizability-preserving scheme developed in this paper is based on the result in Lemma~\ref{lem:explicitStep}, which must hold for the adapted closure.  
-The Kershaw closure is consistent with a bounded distribution, $f_{_{\mbox{\tiny K}}}\in[0,1]$, and should be well suited, but the algebraic ME closures are based on approximations to the closure function, and we must make sure that these approximate closures remain consistent with the assumed bounds on the underlying distribution function.
+The Kershaw closure is consistent with a bounded distribution, $f_{_{\mbox{\tiny K}}}\in[0,1]$, and should be well suited, but the algebraic ME closures are based on approximations to the closure function, and we need to consider if these approximate closures remain consistent with the assumed bounds on the underlying distribution function.
 To this end, we rely on results due to \cite{levermore_1984,lareckiBanach_2011} (see also \cite{kershaw_1976,shohatTamarkin_1943}):  Realizability of the moment triplet $\{\cJ,\vect{\cH},\vect{\cK}\}$ (i.e., they are consistent with a bounded distribution function $0 \le f<1$), with $\vect{\cM}=(\cJ,\vect{\cH})^{T}\in\cR$ and $\vect{\cK}$ given by Eq.~\eqref{eq:eddingtonTensor}, is equivalent to the following requirement for the Eddington factor
@@
 \end{equation}
-(Note that for $\cJ\ll1$ this limits to the bounds for positive distributions given by Levermore \cite{levermore_1984}; i.e., $h^{2}\le\chi\le1.$)
+Fortunately, these bounds are satisfied by the algebraic closures based on Fermi-Dirac statistics.  
+(Note that for $\cJ\ll1$ the bounds in Eq.~\eqref{eq:eddingtonFactorBounds} limit to the bounds for positive distributions given by Levermore \cite{levermore_1984}; i.e., $h^{2}\le\chi\le1.$)
 
@@
 The maximum entropy closures of CB and BL are plotted with solid red and dashed orange lines respectively.  
-The Kershaw closure is plotted with dash-dot purple lines, while the Minerbo closure is plotted with solid blue lines.  
+The Kershaw closure is plotted with solid blue lines, while the Minerbo closure is plotted with dash-dot purple lines.  
 The lower and upper bounds on the Eddington factor for realizable closures for fermion particle systems ($\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$, respectively) are plotted with solid black lines.
@@
 For $\cJ=0.01$, the maximum entropy closures (CB, BL, and Minerbo) are practically indistinguishable, while the Eddington factor of the Kershaw closure is clearly larger than that of the other closures over most of the domain.
-For $\cJ=0.4$, the Eddington factor for the closures based on Fermi-Dirac statistics (CB, BL, and Kershaw) remain close together, while the Eddington factor for the Minerbo closure is clearly above the other closures for $h\gtrsim0.2$.
+For $\cJ=0.4$, the Eddington factor for the closures based on Fermi-Dirac statistics (CB, BL, and Kershaw) remain close together, while the Eddington factor for the Minerbo closure is clearly larger than the other closures for $h\gtrsim0.2$.
 All closures remain between $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ for $\cJ=0.01$ and $\cJ=0.4$.  

### 2018-05-29 Documents/M1/realizableFermionicM1/sections/model.tex
Reworking of section 3: realizability
Minor text additions to algebraic moment closures
Split section 3 in two: Moment Realizability... and Algebraic Moment Closures
Modifications due to comments from Ran

@@
 
-In this paper we consider approximate solutions to the Boltzmann equation for radiation transport in slab geometry, which after scaling to dimensionless units can be written as
+In this paper we consider approximate solutions to the Boltzmann equation for transport of massless particles in slab geometry, which, after scaling to dimensionless units, can be written as
 \begin{equation}
@@
 \end{equation}
-where the distribution function $f(\omegaNu,\epsilonNu,\vect{x},t):\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in direction $\omegaNu\in\bbS^{2}:=\{\,\omegaNu=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\epsilonNu\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$; i.e., we use spherical momentum space coordinates $(\omegaNu,\epsilonNu)$.
-We also define the energy-position coordinates $\vect{z}:=\{\epsilonNu,\vect{x}\}\in\bbR^{+}\times\bbR^{3}$.  
-The unit vector $\vect{\ell}(\omegaNu)\in\bbR^{3}$ (independent of $\vect{z}$) is parallel to the particle three-momentum.  
-On the right-hand side of Eq.~\eqref{eq:boltzmann}, $\tau$ is the ratio of the particle mean-free path (due to interactions with a background) to some characteristic length scale of the problem; in opaque regions, $\tau\ll1$, while for free streaming radiation, $\tau\gg1$.
-The collision term is given by
+where the distribution function $f(\omega,\varepsilon,\vect{x},t):\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in direction $\omega\in\bbS^{2}:=\{\,\omega=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
+Here we use spherical momentum space coordinates $(\varepsilon,\omega)$, and the unit vector $\vect{\ell}(\omega)\in\bbR^{3}$ (independent of $\varepsilon$ and $\vect{x}$) is parallel to the particle three-momentum $\vect{p}=\varepsilon\,\vect{\ell}$.
+We also define the energy-position coordinates $\vect{z}:=\{\varepsilon,\vect{x}\}\in\bbR^{+}\times\bbR^{3}$.  
+On the right-hand side of Eq.~\eqref{eq:boltzmann}, $\tau$ is the ratio of the particle mean-free path (due to interactions with a background) to some characteristic length scale of the problem.  
+In opaque regions, $\tau\ll1$, while for free streaming radiation, $\tau\gg1$.  
+The collision term, due to emission, absorption, and isotropic and elastic scattering, is given by
 \begin{equation}
   \cC(f)=\xi\,\big(\,f_{0}-f\,\big)
-  +(1-\xi)\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omegaNu-f\,\big),
+  +(1-\xi)\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omega-f\,\big),
   \label{eq:collisionTerm}
@@
 Then, $\xi=1$ models pure emission and absorption, while $\xi=0$ models pure scattering.  
-In general, $\sigma_{\Ab}(\vect{z})$ and $\sigma_{\Scatt}$ (and $\tau$ and $\xi$) depend on $\vect{z}$.  
-The equilibrium distribution function is denoted $f_{0}(\vect{z})$.  
-Here, we consider transport of Fermions (e.g., neutrinos), so that the equilibrium distribution function takes the form
+In general, $\sigma_{\Ab}$ and $\sigma_{\Scatt}$ (and $\tau$ and $\xi$) depend on $\vect{z}$.  
+The equilibrium distribution function is denoted by $f_{0}(\vect{z})$.  
+Here, we consider transport of Fermions (e.g., neutrinos), and the equilibrium distribution function takes the form
 \begin{equation}
-  f_{0}(\vect{z})=\f{1}{e^{(\epsilonNu-\mu(\vect{x}))/T(\vect{x})}+1},  
+  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1},  
   \label{eq:fermiDirac}
 \end{equation}
-where the temperature $T$ and the chemical potential $\mu$ are properties of the background.
+where $T$ is the temperature of the background, and the chemical potential $\mu$ also depends on properties of the background.
 
-\subsection{Angular Moment Equations}
+\subsection{Angular Moment Equations: Two-Moment Model}
 
@@
   \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
-  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omegaNu,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omegaNu,
+  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega,
   \label{eq:angularMoments}
@@
   \big\{\,J,\vect{H},\vect{K}\,\big\}(\vect{x},t)
-  =\int_{\bbR^{+}}\big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\epsilonNu,\vect{x},t)\,\epsilonNu^{2}d\epsilonNu.  
+  =\int_{\bbR^{+}}\big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\varepsilon,\vect{x},t)\,\varepsilon^{2}d\varepsilon.  
 \end{equation}
@@
   \vect{k}=\f{1}{2}\big[\,\big(1-\chi\big)\,\vect{I}+\big(3\,\chi-1\big)\,\widehat{\vect{h}}\otimes\widehat{\vect{h}}\,\big],
+  \label{eq:eddingtonTensor}
 \end{equation}
@@
 The two-moment model is then closed once the Eddington factor is determined from $\cJ$ and $\vect{\cH}$.  
-We will return to the issue of determining the Eddington factor in Section~\ref{sec:realizability}.
+We will return to the issue of determining the Eddington factor in Section~\ref{sec:algebraicClosure}.
 

### 2018-05-29 Documents/M1/realizableFermionicM1/sections/numerical.tex
Modifications due to comments from Ran

@@
 We compute until $t=5$, when the system has reached an approximate steady state.  
-We use the IMEX scheme PARSD in all the tests.  
+We use the IMEX scheme PARSD --- the least compute-intensive of the realizability-preserving IMEX schemes presented here --- in all the tests.  
 The main purpose of this test is to compare the results obtained using the different algebraic closures discussed in Section~\ref{sec:algebraicClosure}.
@@
 From the plots of the particle density (left panels in Figure~\ref{fig:HomogeneousSphere}), the results obtained with all the closures, including Minerbo, appear very similar.  
-The particle density obtained with the Minerbo closure deviates the most from the analytic solution inside $r\approx0.75$ for Test~A ($\sigma_{\Ab,0}=1$; upper left panel).  
+(For Test~A, the particle density obtained with the Minerbo closure deviates the most from the analytic solution inside $r\approx0.75$; upper left panel).  
 From the plots of the flux factor (right panels in Figure~\ref{fig:HomogeneousSphere}), it is evident that the results obtained with the Minerbo closure --- the only closure not based on Fermo-Dirac statistics --- deviates the most from the analytic solution outside $r=1$, where the flux factor is consistently higher than the analytical solution for all values of $\sigma_{\Ab,0}$.

### 2018-05-29 Documents/M1/realizableFermionicM1/sections/realizability.tex
Modifications due to comments from Ran

@@
   It is straightforward to verify that $\gamma(\vect{\cM})$ is a concave function of $\bcM$ if $\cJ\in[0,1]$.
-  Jensen's inequality implies
+  Then Jensen's inequality implies
   \begin{equation*}
@@
 \end{equation}
-is partially shown as the region above the red lines.  
+is partially shown as the region above the red lines, which mark the boundary of $\cR^{+}$ (denoted $\partial\cR^{+}$).  
 (A Realizability-preserving method, with respect to $\cR^{+}$, for the two-moment model in one spatial dimension was developed in \cite{olbrant_etal_2012}.)  
+The realizable domains $\cR$ and $\cR^{+}$ overlap for for low particle densities ($\cJ\ll1$), but for larger values of $\cJ$, the realizable domain of particles governed by Fermi-Dirac statistics is much more restricted than that of particles described by positive distribution functions with no upper bound.
 
@@
 
-For the realizability-preserving scheme, we state some additional results.  
+For the realizability-preserving scheme developed in later sections, we state some additional results.  
 \begin{lemma}
@@
 \end{lemma}
-The proof follows along the same lines as the proof of Lemma~\ref{lem:implicitStep} and is omitted.
+The proof of Lemma~\ref{lem:correctionStep} follows along the same lines as the proof of Lemma~\ref{lem:implicitStep} and is omitted.

### 2018-05-29 Documents/M1/realizableFermionicM1/sections/imex.tex
Added 'Absolute Stability' subsectionto IMEX section.

@@
 In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PARSD is practically identical to the accuracy of scheme PC2.
+
+\subsection{Absolute Stability}
+
+The absolute stabilities of the proposed IMEX schemes,  PA2+ and PARSD (given in \ref{app:butcherTables}), are analyzed following form \cite{hu_etal_2017}.
+An IMEX scheme can be written as $\vect{u}^{n+1} =P(z_1,z_2)\vect{u}^{n}$, where $P(z_1,z_2)$ is the amplification factor of the scheme, $z_1 = x +iy$ corresponds to the explicit part of the scheme, and $z_2 < 0$ corresponds to the implicit part.
+The absolute stability requires $|P|\leq 1$. 
+The stability regions of PA2+ and PARSD are plotted in Figure~\ref{fig:AbsoluteStability}.
+As can be seen form the figure, the absolute stability region increase with $|z_2|$ increasing for both schemes.
+Thus, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme, $|z_2| = 0$, fulfill the stability requirement for the whole IMEX scheme, $|z_2| \geq 0$. 
+This conclusion is valid for all PARSD $\epsilon\in [0,0.5)$.
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{figures/AbsoluteStabilityPARSD}
+    \includegraphics[width=0.5\textwidth]{figures/AbsoluteStabilityPA2+}
+  \end{tabular}
+   \caption{Boundary of the absolute stability region for different values of $z_2$. Left: PARSD with $\epsilon = 0.1$. Right: PA2+.}
+  \label{fig:AbsoluteStability}
+\end{figure}

### 2018-05-29 Documents/M1/realizableFermionicM1/sections/imex.tex
Modified absolute stability subsection

@@
 The absolute stabilities of the proposed IMEX schemes,  PA2+ and PARSD (given in \ref{app:butcherTables}), are analyzed following form \cite{hu_etal_2017}.
-An IMEX scheme can be written as $\vect{u}^{n+1} =P(z_1,z_2)\vect{u}^{n}$, where $P(z_1,z_2)$ is the amplification factor of the scheme, $z_1 = x +iy$ corresponds to the explicit part of the scheme, and $z_2 < 0$ corresponds to the implicit part.
-The absolute stability requires $|P|\leq 1$. 
+An IMEX scheme can be written as $\vect{u}^{n+1} =P(z_1,z_2)\vect{u}^{n}$, where $P(z_1,z_2)$ is the amplification factor of the scheme, $z_1 = x +iy$ is the eigenvalue corresponding to the explicit part of the scheme, and $z_2 < 0$ corresponds to that of the implicit part.
+The absolute stability of IMEX scheme requires $|P(z_1,z_2)|\leq 1$. 
 The stability regions of PA2+ and PARSD are plotted in Figure~\ref{fig:AbsoluteStability}.
-As can be seen form the figure, the absolute stability region increase with $|z_2|$ increasing for both schemes.
+As can be seen form the figures, the absolute stability regions of both schemes increase with $|z_2|$.
 Thus, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme, $|z_2| = 0$, fulfill the stability requirement for the whole IMEX scheme, $|z_2| \geq 0$. 

### 2018-05-30 Documents/M1/realizableFermionicM1/sections/imex.tex
Corrected typo.

@@
 The stability regions of PA2+ and PARSD are plotted in Figure~\ref{fig:AbsoluteStability}.
-As can be seen form the figures, the absolute stability regions of both schemes increase with $|z_2|$.
-Thus, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme, $|z_2| = 0$, fulfill the stability requirement for the whole IMEX scheme, $|z_2| \geq 0$. 
+As can be seen from the figures, the absolute stability regions of both schemes increase with $|z_2|$.
+Thus, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme ($|z_2| = 0$) fulfill the stability requirement for the whole IMEX scheme ($|z_2| \geq 0$). 
 This conclusion is valid for all PARSD $\epsilon\in [0,0.5)$.

### 2018-05-30 Documents/M1/realizableFermionicM1/sections/dg.tex
Additions to DG-IMEX scheme
Minor adjustments to dg.tex and imex.tex.  Began work on updating DGIMEX.tex
Minor adjustments to DG section

@@
 Here we briefly outline the DG method for the moment equations.  
-We do not include any physics that couple the energy dimension.  
-Thus, the particle energy $\epsilonNu$ is simply treated as a parameter.  
+Since we do not include any physics that couples the energy dimension, the particle energy $\epsilonNu$ is simply treated as a parameter.  
 For notational convenience, we will suppress explicit energy dependence of the moments.  
@@
   \pd{\vect{\cM}}{t}+\sum_{i=1}^{d}\pderiv{}{x^{i}}\big(\,\vect{\cF}^{i}(\vect{\cM})\,\big)
-  =\frac{1}{\tau}\,\vect{\cC}(\vect{\cM}).  
+  =\frac{1}{\tau}\,\vect{\cC}(\vect{\cM}),
   \label{eq:angularMomentsCartesian}
 \end{equation}
+where $x^{i}$ is the coordinate along the $i$th coordinate dimension.  
 We divide the spatial domain $D$ into a disjoint union $\mathscr{T}$ of open elements $\bK$, so that $D = \cup_{\bK \in \mathscr{T}}\bK$.  
@@
 \end{equation}
-We also define the coordinates orthogonal to the $i$th dimension, $\tilde{\vect{x}}^{i}$, so that $\vect{x}=\{\tilde{\vect{x}}^{i},x^{i}\}$.  
-The with of an element in the $i$th dimension is $|K^{i}|=\xH^{i}-\xL^{i}$.
+We also define $\tilde{\vect{x}}^{i}$ as the coordinates orthogonal to the $i$th dimension, so that $\vect{x}=\{\tilde{\vect{x}}^{i},x^{i}\}$.  
+The width of an element in the $i$th dimension is $|K^{i}|=\xH^{i}-\xL^{i}$.
 
@@
   \vect{\mathscr{F}}_{\mbox{\tiny LF}}^{i}(\vect{\cM}_{a},\vect{\cM}_{b})
-  =\f{1}{2}\,\big(\,\bcF^{i}(\vect{\cM}_{a})+\bcF^{i}(\vect{\cM}_{b})-\alpha^{i}\,(\,\vect{\cM}_{a}-\vect{\cM}_{b}\,)\,\big),
+  =\f{1}{2}\,\big(\,\bcF^{i}(\vect{\cM}_{a})+\bcF^{i}(\vect{\cM}_{b})-\alpha^{i}\,(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big),
+  \label{eq:fluxFunctionLF}
 \end{equation}

### 2018-05-31 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added 'Absolute Stability' subsectionto IMEX section.
Work on imex section.  Replaced all hu_et_al_2017 with hu_etal_2018

@@
 
-A second-order accurate, positivity-preserving IMEX scheme of type $A$ (the matrix $A$ is invertible) was given in \cite{hu_etal_2017}.  
+A second-order accurate, positivity-preserving IMEX scheme of type $A$ (the matrix $A$ is invertible) was given in \cite{hu_etal_2018}.  
 We refer to this scheme as IMEX PA2.  
@@
 \section{Construction of PARSD}
+\label{app:PARSD}
 
-It can be shown that no 2-stage positivity-preserving IMEX exist \cite{hu_etal_2017}.
+It can be shown that no 2-stage positivity-preserving IMEX exist \cite{hu_etal_2018}.
 Hence we considered 3-stage IMEX scheme.
@@
  \text{under these constraints:} \qquad & \\
- \text{(GSA)} \qquad\ &\tilde{w}_{i} = \tilde{a}_{3i}, \quad w_{i} = a_{3i},\\
+ \text{(GSA)} \qquad\ &\tilde{w}_{i} = \tilde{a}_{3i}, \quad w_{i} = a_{3i}, ~\text{for} ~ i = 1,2,3\\
  \text{(2nd-order accuracy)} \qquad\ &\sum_{i=1}^{3}  \tilde{w}_{i} = 1, \quad \sum_{i=1}^{3}  \tilde{w}_{i}\tilde{c}_{i} = 1/2, \\
- \text{(positivity-preserving)} \qquad & a_{ii} > 0, c_{i0} \geq 0, \tilde{c}_{i0} \geq 0 ~\text{for} ~ i = 2,3 \\
+ \text{(positivity-preserving)} \qquad & a_{ii} > 0, c_{i0} \geq 0, \tilde{c}_{i0} \geq 0, ~\text{for} ~ i = 2,3 \\
  & c_{32} \geq 0, \tilde{c}_{32} \geq 0, \\

### 2018-05-31 Documents/M1/realizableFermionicM1/sections/imex.tex
Work on imex section.  Replaced all hu_et_al_2017 with hu_etal_2018

--- 2018-05-29 Documents/M1/realizableFermionicM1/sections/imex.tex
@@
 
-In this section we summarize and discuss the class of IMEX schemes we consider for the realizability-preserving DG-IMEX method for the two-moment model developed in Section~\ref{sec:realizableDGIMEX} (see also \ref{app:butcherTables} for additional details).
+In this section we discuss the class of IMEX schemes we consider for the realizability-preserving DG-IMEX method for the two-moment model developed in Section~\ref{sec:realizableDGIMEX} (see also \ref{app:butcherTables} for additional details).
 The semi-discretization of the moment equations with the DG method given by Eq.~\eqref{eq:semidiscreteDG} results in a system of ordinary differential equations (ODEs) in each element of the form
@@
 Thus, for $\phi_{1}=1$, the first components of $\vect{u}$ are the cell averaged moments.  
-In Eq.~\eqref{eq:ode}, the transport term $\vect{\cT}$ is due to the second and third term on the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision term $\vect{\cQ}$ is due to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
+In Eq.~\eqref{eq:ode}, the transport operator $\vect{\cT}$ is due to the second and third term on the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision operator $\vect{\cQ}$ is due to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
 
@@
 
-In the applications of interest to us, the collision term is stiff ($\tau\ll1$) in regions of the computational domain and must be treated with implicit methods, while we can resolve the time scales induced by the transport term, which we will treat with explicit methods; i.e., we will use IMEX methods \cite{pareschiRusso_2005}.
-Furthermore, we would like to employ IMEX schemes that preserve realizability of the moments (subject only to a time step governed by the explicit transport term).  
+In the applications of interest to us, collisions with a background induce stiffness ($\tau\ll1$) in regions of the computational domain and must be treated with implicit methods, while we can resolve the time scales induced by the transport term, which we then can treat with explicit methods.
+This motivates the use of IMEX methods \cite{ascher_etal_1997,pareschiRusso_2005}.  
+Furthermore, we would like to employ IMEX schemes that preserve realizability of the moments --- subject only to a time step governed by the explicit transport operator, and comparable to the time step required for numerical stability of the explicit scheme.
+(The realizability-preserving and positivity-preserving properties of an IMEX scheme are intimately related, and we use two phrases interchangeably.)  
 Until recently, high-order (second or higher order temporal accuracy) positivity-preserving IMEX methods with time step restrictions solely due to the transport operator were not known.  
 Chertock et al. \cite{chertock_etal_2015} presented second-order accurate IMEX schemes with a correction step.  
-The correction step in \cite{chertock_etal_2015} includes the transport operator, and we have found that realizability is then subject to a time step restriction that scales as $\dt\propto1/\sqrt{\tau}$, which may become too restrictive.
+However, the correction step in \cite{chertock_etal_2015} involves both the transport and collision operators, and we have found that realizability is then subject to a time step restriction that depends on $\tau$, which may become too restrictive for stiff problems.
 More recently, Hu et al.
-\cite{hu_etal_2017}, presented similar IMEX schemes for problems involving BGK-type collision operators, but with a correction step that does not include the transport operator.
+\cite{hu_etal_2018}, presented similar IMEX schemes for problems involving BGK-type collision operators, but with a correction step that does not include the transport operator.
 In this case, positivity is only subject to time step restrictions stemming from the transport operator, which is more attractive for our target application.  
-These second-order accurate, $s$-stage IMEX schemes take the following form \cite{hu_etal_2017}
+These second-order accurate, $s$-stage IMEX schemes take the following form \cite{hu_etal_2018}
 \begin{align}
@@
 \end{align}
-where, as in standard IMEX schemes, $(\tilde{a}_{ij})$ and $(a_{ij})$, components of $s\times s$ matrices $\tilde{A}$ and $A$, respectively, and the vectors $\vect{w}^{T}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ must satisfy certain order conditions \cite{pareschiRusso_2005}.
+where, as in standard IMEX schemes, $(\tilde{a}_{ij})$ and $(a_{ij})$, components of $s\times s$ matrices $\tilde{A}$ and $A$, respectively, and the vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ must satisfy certain order conditions \cite{pareschiRusso_2005}.
 The coefficient in the correction step is positive, $\alpha>0$, and $\vect{\cQ}'$ is the Fr{\'e}chet derivative of the collision term evaluated at $\vect{u}^{*}$.  
@@
 where $\tilde{c}_{i}$ and $c_{i}$ are given in \ref{app:butcherTables}.  
-For globally stiffly accurate (GSA) IMEX schemes, $\tilde{w}_{i}=\tilde{a}_{si}$ and $w_{i}=a_{si}$ for $i=1,\ldots,s$, so that $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$.
+For globally stiffly accurate (GSA) IMEX schemes, $\tilde{w}_{i}=\tilde{a}_{si}$ and $w_{i}=a_{si}$ for $i=1,\ldots,s$, so that $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$ \cite{ascher_etal_1997}.  
+This property is beneficial for very stiff problems, and also simplifies the proof of the realizability-preserving property of the IMEX scheme since it eliminates the assembly step in Eq.~\eqref{imexIntermediate}.
 
-To prove the positivity-preserving property of the IMEX scheme, Hu et al. \cite{hu_etal_2017} rewrite the stage values in Eq.~\eqref{imexStages} in the following form
+To prove the positivity-preserving property of the IMEX scheme, Hu et al. \cite{hu_etal_2018} rewrite the stage values in Eq.~\eqref{imexStages} in the following form
 \begin{equation}
@@
   =\sum_{j=0}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
-  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{Q}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
+  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
   \label{eq:imexStagesRewrite}
@@
 (In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.)  
-Two types of IMEX schemes are considered: \emph{type A} and \emph{type ARS}.  
-For IMEX schemes of type A, the matrix $A$ is invertible.  
-For IMEX schemes of type ARS, the matrix $A$ can be written as
+Two types of IMEX schemes are considered: \emph{type~A} (\ee{Insert reference to the origin of Type~A schemes}) and \emph{type~ARS} \cite{ascher_etal_1997}.  
+For IMEX schemes of type~A, the matrix $A$ is invertible.  
+For IMEX schemes of type~ARS, the matrix $A$ can be written as
 \[\left( 
@@
 \right)\]
-with $\hat{A}$ be invertible.
-For $i=1,\ldots,s$, the coefficients
-\begin{align*}
-  c_{i0}
-  =&\left\{
-  \begin{array}{cl}
-    1 - \sum_{j=1}^{i-1}c_{ij}  & \qquad \text{for type $A$,} \\
-    1 - \sum_{j=2}^{i-1}c_{ij}  & \qquad \text{for type $ARS$;}
-  \end{array}
-  \right.\\
-  \tilde{c}_{i0}
-  =&\left\{
-  \begin{array}{cl}
-    0  & \text{for type $A$,} \\
-   \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1}  & \text{for type $ARS$;}
-  \end{array}
-  \right.\\
-  c_{i1}
-    =&\left\{
-    \begin{array}{cl}
-      \sum_{l =1}^{i-1} a_{il}b_{l1} & \qquad ~\text{for type $A$,} \\
-      \qquad ~ 0  & \qquad ~\text{for type $ARS$;}
-    \end{array}
-    \right.\\
-    \tilde{c}_{i1}
-    =&\left\{
-      \begin{array}{cl}
-       \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1} & \text{for type $A$,} \\
-       0  & \text{for type $ARS$;}
-      \end{array}
-      \right.
-\end{align*}
-and the rest coefficients were defined as in \cite{hu_etal_2017}.
+where $\hat{A}$ is invertible.
+In writing the stages in the IMEX scheme in the general form given by Eq.~\eqref{eq:imexStagesRewrite}, it should be noted that $\tilde{c}_{i0}=0$ for IMEX schemes of Type~A, and $c_{i1}=\tilde{c}_{i1}=0$ for IMEX schemes of Type~ARS \cite{hu_etal_2018}.
+%For $i=1,\ldots,s$, the coefficients
+%\begin{align*}
+%  c_{i0}
+%  =&\left\{
+%  \begin{array}{cl}
+%    1 - \sum_{j=1}^{i-1}c_{ij}  & \qquad \text{for type $A$,} \\
+%    1 - \sum_{j=2}^{i-1}c_{ij}  & \qquad \text{for type $ARS$;}
+%  \end{array}
+%  \right.\\
+%  \tilde{c}_{i0}
+%  =&\left\{
+%  \begin{array}{cl}
+%    0  & \text{for type $A$,} \\
+%   \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1}  & \text{for type $ARS$;}
+%  \end{array}
+%  \right.\\
+%  c_{i1}
+%    =&\left\{
+%    \begin{array}{cl}
+%      \sum_{l =1}^{i-1} a_{il}b_{l1} & \qquad ~\text{for type $A$,} \\
+%      \qquad ~ 0  & \qquad ~\text{for type $ARS$;}
+%    \end{array}
+%    \right.\\
+%    \tilde{c}_{i1}
+%    =&\left\{
+%      \begin{array}{cl}
+%       \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1} & \text{for type $A$,} \\
+%       0  & \text{for type $ARS$;}
+%      \end{array}
+%      \right.
+%\end{align*}
+%and the rest coefficients were defined as in \cite{hu_etal_2018}.
 For type A schemes, the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.  
 For type ARS schemes, the positivity follows from requiring $a_{ii}>0$ and $c_{i0},\tilde{c}_{i0}\ge0$ for $i=2,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$ for $i=3,\ldots,s$, $j=2,\ldots,i-1$.  
-Such coefficients were given in \cite{hu_etal_2017} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
+Such coefficients were given in \cite{hu_etal_2018} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
 (It was also proven that $s=3$ and $s=4$ are the necessary number of stages needed for GSA second-order positivity-preserving IMEX schemes of type A and type ARS, respectively.)
 
-Importantly, the coefficients $c_{ij}$ in Eq.~\eqref{eq:imexStagesRewrite} satisfy $\sum_{j=0}^{i-1}c_{ij}=1$.  
-This implies that, if the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} is positive for all $i=2,\ldots,s$, $j=0,\ldots,i-1$, positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
-Thus, if the explicit update with the transport operator is positive for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is positivity preserving for a time step $\dt\le c_{\mbox{\tiny Sch}}\,\dt_{\mbox{\tiny Ex}}$, where
+Importantly, the coefficients $c_{ij}$ in Eq.~\eqref{eq:imexStagesRewrite} satisfy $\sum_{j=0}^{i-1}c_{ij}=1$, which implies the so-called Shu-Osher form.  
+Thus, if the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} --- which is in the form of a forward Euler update with time step $\hat{c}_{ij}\,\dt$ --- is positive for all $i=1,\ldots,s$, $j=0,\ldots,i-1$, positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
+Thus, if the explicit update with the transport operator is positive for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is positivity-preserving for a time step $\dt\le c_{\mbox{\tiny Sch}}\,\dt_{\mbox{\tiny Ex}}$, where
 \begin{equation}
@@
 (Positivity of $\vect{u}^{(i)}$ also requires the implicit solve to preserve positivity.)  
-In \cite{hu_etal_2017}, Hu et al. provide examples of GSA, positivity-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
+In \cite{hu_etal_2018}, Hu et al. provide examples of GSA, positivity-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
 In \ref{app:butcherTables}, we provide another example of a GSA, positivity-preserving IMEX scheme of type A (scheme PA2+), with a significantly larger $c_{\mbox{\tiny Sch}}$ (a factor of about $1.7$ larger).
@@
 
-Unfortunately, the correction step in Eq.~\eqref{eq:imexCorrection} deteriorates the accuracy of the IMEX scheme when applied to the moment equations in the diffusion limit ($\xi=0$, $\tau\ll 1$).  
-In the diffusion limit, to leading order in $\tau$, we have $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$, which is due to a balance between the transport term and the collision term in the equation for the particle flux $\vect{\cH}$.
+Unfortunately, the correction step in Eq.~\eqref{eq:imexCorrection} deteriorates the accuracy of the IMEX scheme when applied to the moment equations in the diffusion limit ($\xi=0$, $\tau\ll 1$), where $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$.
+In the diffusion limit, to leading order in $\tau$, we then have $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$, which is due to a balance between the transport term and the collision term in the equation for the particle flux $\vect{\cH}$.
 The absence of the transport operator in the correction step, destroys this balance.  
 We demonstrate the inferior performance of IMEX schemes with the correction step given by Eq.~\eqref{eq:imexCorrection} in the diffusion limit in Section~\ref{sec:smoothProblems}.  
-We have also implemented one of IMEX schemes in Chertock et al.
+We have also implemented and tested one of the IMEX schemes in Chertock et al.
 \cite{chertock_etal_2015}, where the transport operator is included in the correction step, and found it to perform very well in the diffusion limit.
 However, we have not been able to prove sufficiently general realizability-preserving properties with this approach, without invoking a too severe time step restriction.  
+We therefore proceed to design positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
+We will limit the scope to IMEX schemes of type~ARS.
 
-We therefore proceed to design GSA positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
-To this end we define the vectors $\vec{\cJ}=(\cJ^{(1)},\ldots,\cJ^{(s)})^{T}$ and $\vec{\vect{\cH}}=(\vect{\cH}^{(1)},\ldots,\vect{\cH}^{(s)})^{T}$.  
+To this end we take a heuristic approach and define the vectors 
+\begin{equation}
+  \vec{\cJ}=(\cJ^{(1)},\ldots,\cJ^{(s)})^{T}
+  \quad\text{and}\quad
+  \vec{\vect{\cH}}=(\vect{\cH}^{(1)},\ldots,\vect{\cH}^{(s)})^{T}.  
+\end{equation}
 In the context of IMEX schemes, the diffusion limit balance implies that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold to relate the stage values in Eq.~\eqref{imexStages}.
-Define
-\begin{align*}
-    \mathcal{A}^{-1}
-    =&\left\{
-      \begin{array}{cl}
-       A^{-1} & \text{for type $A$,} \vspace{4pt} \\ 
-       \left( 
+Define the inverse of the implicit coefficient matrix for IMEX schemes of type~ARS as
+\begin{equation*}
+    A^{-1}
+    =\left(
         \begin{matrix}
@@
         \end{matrix}
-       \right)  & \text{for type $ARS$.}
-      \end{array}
-      \right.
-\end{align*}
-For the final stage ($i=s$), 
+      \right).
+\end{equation*}
+For the stages $i=1,\ldots,s$ we have
 \begin{equation}
-  \vect{\cH}^{(s)}=-\f{1}{3}\,\tau\,\vect{e}_{s}^{T}\mathcal{A}^{-1}\tilde{A}\vect{e}\,\nabla\cJ^{n}+\cO(\dt\,\tau),
+  \vect{\cH}^{(i)}=-\f{1}{3}\,\tau\,\vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e}\,\nabla\cJ^{n}+\cO(\dt\,\tau),
 \end{equation}
-where $\vect{e}_{s}=(0,\ldots,0,1)^{T}$ and $\vect{e}=(1,\ldots,1)^{T}$.  
-Thus, for $\vect{\cH}^{(s)}$ to be accurate in the diffusion limit, we require the IMEX coefficients to satisfy
+where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix and $\vect{e}=(1,\ldots,1)^{T}$.  
+Thus, for $\vect{\cH}^{(i)}$ to be accurate in the diffusion limit, we require the IMEX coefficients to satisfy
 \begin{equation}
-  \vect{e}_{s}^{T}\mathcal{A}^{-1}\tilde{A}\vect{e} = 1.
+  \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s.
   \label{eq:diffusionCondition}
 \end{equation}
-Unfortunately, this requirement, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints.
-(\ee{Can we prove that it is impossible to find a second-order accurate, positivity-preserving IMEX scheme that is accurate in the diffusion limit?  Does the answer to this depend on $s$?})
-(We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators.)
+(The case $i=1$ is trivial and does not place any constraints on the IMEX coefficients.)  
+Then, for the particle number equation we have
+\begin{equation}
+  \f{\cJ^{(s)}-\cJ^{n}}{\dt}
+  =-\tilde{\vect{w}}^{T}(\nabla\cdot\vec{\vect{\cH}})
+  \approx\f{1}{3}\tau\,\nabla^{2}\cJ^{n}, 
+\end{equation}
+which approximates a diffusion equation with the correct diffusion coefficient $\tau/3$.  
+Unfortunately, the ``diffusion limit requirement" in Eq.~\eqref{eq:diffusionCondition}, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints.
+(It was shown in \cite{hu_etal_2018} --- without the diffusion limit requirement --- that the minimum number of stages for positivity-preserving IMEX schemes of type~ARS is four.)  
+We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators (e.g., inelastic scattering).
 To reduce the number of constraints, and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
@@
 \end{equation}
-We then seek to design GSA IMEX schemes with the following properties
+We then seek to design GSA IMEX schemes of Type~ARS with the following properties
 \begin{itemize}
@@
   \item Well-behaved in the diffusion limit; i.e., satisfies Eq.~\eqref{eq:diffusionCondition}.
-  \item Positivity-preserving (conditions given by \cite{hu_etal_2017}; with $c_{\mbox{\tiny Sch}}$ maximal).
+  \item Positivity-preserving (conditions given by \cite{hu_etal_2018}; with $c_{\mbox{\tiny Sch}}$ maximal).
   \item Few ($\le3$) implicit stages.
 \end{itemize}
-Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example of type ARS with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PARSD).  
+Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PARSD; see \ref{app:PARSD} for details).
 In the streaming limit, this scheme is identical to the optimal second-order accurate strong-stability preserving Runge-Kutta method \cite{gottlieb_etal_2001}.  
@@
 Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclarren_etal_2008,radice_etal_2013}, and satisfies the positivity conditions, but $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).
-In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PARSD is practically identical to the accuracy of scheme PC2.
+In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PARSD is comparable to the accuracy of scheme PC2.
 
@@
 
-The absolute stabilities of the proposed IMEX schemes,  PA2+ and PARSD (given in \ref{app:butcherTables}), are analyzed following form \cite{hu_etal_2017}.
-An IMEX scheme can be written as $\vect{u}^{n+1} =P(z_1,z_2)\vect{u}^{n}$, where $P(z_1,z_2)$ is the amplification factor of the scheme, $z_1 = x +iy$ corresponds to the explicit part of the scheme, and $z_2 < 0$ corresponds to the implicit part.
-The absolute stability requires $|P|\leq 1$. 
+Here we analyze the absolute stability of the proposed IMEX schemes, PA2+ and PARSD (given in \ref{app:butcherTables}), following \cite{hu_etal_2018}.  
+As is commonly done, we do this in the context of the linear scalar equation
+\begin{equation}
+  \dot{u}=\lambda_{1}\,u+\lambda_{2}\,u,
+  \label{eq:scalarODE}
+\end{equation}
+where $\lambda_{1}\in\mathbb{C}$ and real $\lambda_{2}\le0$.  
+On the right-hand side of Eq.~\eqref{eq:scalarODE}, the first (oscillatory) term is treated explicitly, while the second (damping) term is treated implicitly.  
+The IMEX schemes can then be written as $u^{n+1} =P(z_{1},z_{2})\,u^{n}$, where $P(z_{1},z_{2})$ is the amplification factor of the scheme, $z_{1}=\dt\,\lambda_{1} = x +iy$, and $z_{2} = \dt\,\lambda_{2} < 0$.
+Stability of the IMEX scheme requires $|P(z_1,z_2)|\leq 1$.  
 The stability regions of PA2+ and PARSD are plotted in Figure~\ref{fig:AbsoluteStability}.  
-As can be seen form the figure, the absolute stability region increase with $|z_2|$ increasing for both schemes.
-Thus, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme, $|z_2| = 0$, fulfill the stability requirement for the whole IMEX scheme, $|z_2| \geq 0$. 
-This conclusion is valid for all PARSD $\epsilon\in [0,0.5)$.
+As can be seen from the figures, the absolute stability region of both schemes increases with increasing $|z_{2}|$.  
+For a given $|z_{2}|>0$, the stability region of PARSD is larger than that for PA2+.  
+In the linear case, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme ($|z_2| = 0$) fulfills the stability requirement for the IMEX scheme as whole ($|z_2| \geq 0$).
+This conclusion is valid for all PARSD schemes with $\epsilon\in [0,0.5)$.
 \begin{figure}[h]
@@
   \end{tabular}
-   \caption{Boundary of the absolute stability region for different values of $z_2$. Left: PARSD with $\epsilon = 0.1$. Right: PA2+.}
+   \caption{Boundary of the absolute stability region for different values of $z_2$ for PARSD with $\epsilon = 0.1$ (left panel) and PA2+ (right panel).}
   \label{fig:AbsoluteStability}

### 2018-05-31 Documents/M1/realizableFermionicM1/sections/model.tex
Updates to Section 2 due to comments from Cory.

@@
 
-In this section we give a summary of the mathematical model we employ.
+In this section we give a summary of the mathematical model.
 
@@
 
-In this paper we consider approximate solutions to the Boltzmann equation for transport of massless particles in slab geometry, which, after scaling to dimensionless units, can be written as
+We consider approximate solutions to the Boltzmann equation for transport of massless particles through a material in Cartesian geometry, which, after scaling to dimensionless units, can be written as
 \begin{equation}
@@
 \end{equation}
-where the distribution function $f(\omega,\varepsilon,\vect{x},t):\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in direction $\omega\in\bbS^{2}:=\{\,\omega=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
+where the distribution function $f\colon(\omega,\varepsilon,\vect{x},t)\in\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in direction $\omega\in\bbS^{2}:=\{\,\omega=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
 Here we use spherical momentum space coordinates $(\varepsilon,\omega)$, and the unit vector $\vect{\ell}(\omega)\in\bbR^{3}$ (independent of $\varepsilon$ and $\vect{x}$) is parallel to the particle three-momentum $\vect{p}=\varepsilon\,\vect{\ell}$.
@@
 \end{equation}
-where $\xi\in[0,1]$ is the ratio of the absorption opacity $\sigma_{\Ab}\,(\ge0)$ to the total opacity $\sigma_{\Tot}=\sigma_{\Ab}+\sigma_{\Scatt}$, and $\sigma_{\Scatt}\,(\ge0)$ is the scattering opacity.
-Then, $\xi=1$ models pure emission and absorption, while $\xi=0$ models pure scattering.  
+where $\xi=\sigma_{\Ab}/\sigma_{\Tot}\in[0,1]$ is the ratio of the absorption opacity $\sigma_{\Ab}\,(\ge0)$ to the total opacity $\sigma_{\Tot}=\sigma_{\Ab}+\sigma_{\Scatt}$, and $\sigma_{\Scatt}\,(\ge0)$ is the scattering opacity.
+In particular, $\xi=1$ models pure emission and absorption, while $\xi=0$ models pure scattering.  
 In general, $\sigma_{\Ab}$ and $\sigma_{\Scatt}$ (and $\tau$ and $\xi$) depend on $\vect{z}$.  
 The equilibrium distribution function is denoted by $f_{0}(\vect{z})$.  
-Here, we consider transport of Fermions (e.g., neutrinos), and the equilibrium distribution function takes the form
+Here, we consider transport of Fermions (e.g., neutrinos), so the equilibrium distribution function takes the form
 \begin{equation}
@@
 \end{equation}
-where $T$ is the temperature of the background, and the chemical potential $\mu$ also depends on properties of the background.
+where the temperature $T$ and the chemical potential $\mu$ depend on properties of the background.
 
@@
 The Boltzmann equation is often too expensive to solve directly.  
-Instead, equations for angular moments of the distribution function can be solved for.  
+Instead, approximate equations for angular moments of the distribution function are solved.  
 To this end, we define the angular moments of the distribution function
@@
   \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
-  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega,
+  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega.  
   \label{eq:angularMoments}
 \end{equation}
-where we will refer to $\cJ$ (zeroth moment) as the particle density, $\vect{\cH}$ (first moment) as the particle flux, and $\vect{\cK}$ (second moment) as the stress tensor.  
-Note that the moments defined in Eq.~\eqref{eq:angularMoments} are \emph{spectral moments} (depending on energy, position, and time).  
-The \emph{grey moments} (depending only on position and time) are obtained by integration over energy as
+We refer to $\cJ$ (zeroth moment) as the particle density, $\vect{\cH}$ (first moment) as the particle flux, and $\vect{\cK}$ (second moment) as the stress tensor.  
+Note that the moments defined in Eq.~\eqref{eq:angularMoments} are \emph{spectral moments} (depending on energy as well as position and time).  
+The \emph{grey moments} (depending only on position and time) are obtained by integration over energy:
 \begin{equation}
@@
 \begin{equation}
-  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}(\vect{\cM})=\f{1}{\tau}\,\vect{\cC}(\vect{\cM}),
+  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}=\f{1}{\tau}\,\vect{\cC}(\vect{\cM}),
   \label{eq:momentEquations}
 \end{equation}
-where $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, the components of the flux vector $\vect{\cF}$ are $\vect{\cF}^{i}=\vect{e}_{i}\cdot\vect{\cF}=(\vect{e}_{i}\cdot\vect{\cH},\vect{e}_{i}\cdot\vect{\cK})^{T}$, where $\vect{e}_{i}$ is the unit vector in the $i$th coordinate direction.
-On the right-hand side of Eq.~\eqref{eq:momentEquations}, the collision term becomes
+where evolved moments are $\vect{\cM}=(\cJ,\vect{\cH})^{T}$ and $\vect{\cF}$ are the fluxes.  
+Components of the fluxes in each coordinate direction are $\vect{\cF}^{i}=\vect{e}_{i}\cdot\vect{\cF}=(\vect{e}_{i}\cdot\vect{\cH},\vect{e}_{i}\cdot\vect{\cK})^{T}$, where $\vect{e}_{i}$ is the unit vector parallel to the $i$th coordinate direction.
+On the right-hand side of Eq.~\eqref{eq:momentEquations}, the source term is
 \begin{equation}
@@
 \end{equation}
-where we have defined $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$ and $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$, where $\vect{I}$ is the identity matrix.  
-In order to close the system of equations, the components of the stress tensor $\vect{\cK}$ must be related to the lower moments through a closure procedure.  
-To this end, Levermore \cite{levermore_1984} defines the Eddington tensor $\vect{k}=\vect{\cK}/\cJ$, assumes that the radiation field is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, and writes
+where $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$ and $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$, with $\vect{I}$ the identity matrix.
+
+In order to close the system given by Eq.~\eqref{eq:momentEquations}, the components of the stress tensor $\vect{\cK}$ must be related to the lower moments through a closure procedure.  
+To this end, Levermore \cite{levermore_1984} defined the Eddington tensor $\vect{k}=\vect{\cK}/\cJ$, assumed that the radiation field is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, so that
 \begin{equation}
@@
 We will return to the issue of determining the Eddington factor in Section~\ref{sec:algebraicClosure}.
-
-This concludes the initial description of our model.

### 2018-06-01 Documents/M1/realizableFermionicM1/sections/imex.tex
Modified c_sch expression.

@@
 (In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.)  
-Two types of IMEX schemes are considered: \emph{type~A} (\ee{Insert reference to the origin of Type~A schemes}) and \emph{type~ARS} \cite{ascher_etal_1997}.  
+Two types of IMEX schemes are considered: \emph{type~A} \cite{pareschiRusso_2005} and \emph{type~ARS} \cite{ascher_etal_1997}.  
 For IMEX schemes of type~A, the matrix $A$ is invertible.  
@@
 In writing the stages in the IMEX scheme in the general form given by Eq.~\eqref{eq:imexStagesRewrite}, it should be noted that $\tilde{c}_{i0}=0$ for IMEX schemes of Type~A, and $c_{i1}=\tilde{c}_{i1}=0$ for IMEX schemes of Type~ARS \cite{hu_etal_2018}.
+%The coefficients are defined as $c_{i0} = 1 - \sum_{j=1}^{i-1}c_{ij} $, 
 %For $i=1,\ldots,s$, the coefficients
 %\begin{align*}
-%  c_{i0}
-%  =&\left\{
-%  \begin{array}{cl}
-%    1 - \sum_{j=1}^{i-1}c_{ij}  & \qquad \text{for type $A$,} \\
-%    1 - \sum_{j=2}^{i-1}c_{ij}  & \qquad \text{for type $ARS$;}
-%  \end{array}
-%  \right.\\
 %  \tilde{c}_{i0}
@@
 %   \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1}  & \text{for type $ARS$;}
-%  \end{array}
-%  \right.\\
-%  c_{i1}
-%    =&\left\{
-%    \begin{array}{cl}
-%      \sum_{l =1}^{i-1} a_{il}b_{l1} & \qquad ~\text{for type $A$,} \\
-%      \qquad ~ 0  & \qquad ~\text{for type $ARS$;}
 %  \end{array}
@@
 \begin{equation}
-  c_{\mbox{\tiny Sch}}=\min_{ij}\,\f{1}{\hat{c}_{ij}}.  
+  c_{\mbox{\tiny Sch}}=\min_{\substack{i = 2,\ldots,s \\ 
+       j = 1,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}} \quad \text{(Type A)}, \quad  c_{\mbox{\tiny Sch}}=\min_{\substack{i = 2,\ldots,s \\ 
+              j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}} \quad \text{(Type ARS)}.
   \label{eq:imexCFL}

### 2018-06-05 Documents/M1/realizableFermionicM1/sections/imex.tex
Added the definitions of IMEX coefficients.
Forgot to commit slight modification to conditions on PARSD

@@
 where $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$.
+Such that, $c_{i0} = 1 - \sum_{j=1}^{i-1}c_{ij}$, $c_{ij} = \sum_{l=j}^{i-1}a_{il}b_{lj}$, $\tilde{c}_{i0} = \tilde{a}_{i1} + \sum_{j=2}^{i-1} a_{ij}\tilde{b}_{j1}$,$\tilde{c}_{ij} = \tilde{a}_{ij} + \sum_{l=j+1}^{i-1} a_{il}\tilde{b}_{lj}$ $b_{ij} = - \frac{1}{a_{ii}} \sum_{l = j}^{i-1}a_{il}b_{lj}$, $b_{ii} = \frac{1}{a_{ii}}$, $\tilde{b}_{ij} = \frac{1}{a_{ii}}\big( -\tilde{a}_{ij} - \sum_{l = j+1}^{i-1}a_{il}\tilde{b}_{lj}\big)$.
 (In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.)  
@@
 In writing the stages in the IMEX scheme in the general form given by Eq.~\eqref{eq:imexStagesRewrite}, it should be noted that $\tilde{c}_{i0}=0$ for IMEX schemes of Type~A, and $c_{i1}=\tilde{c}_{i1}=0$ for IMEX schemes of Type~ARS \cite{hu_etal_2018}.
-%The coefficients are defined as $c_{i0} = 1 - \sum_{j=1}^{i-1}c_{ij} $, 
-%For $i=1,\ldots,s$, the coefficients
-%\begin{align*}
-%  \tilde{c}_{i0}
-%  =&\left\{
-%  \begin{array}{cl}
-%    0  & \text{for type $A$,} \\
-%   \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1}  & \text{for type $ARS$;}
-%  \end{array}
-%  \right.\\
-%    \tilde{c}_{i1}
-%    =&\left\{
-%      \begin{array}{cl}
-%       \tilde{a}_{i1} + \sum_{l=2}^{i-1}a_{il}\tilde{b}_{l1} & \text{for type $A$,} \\
-%       0  & \text{for type $ARS$;}
-%      \end{array}
-%      \right.
-%\end{align*}
-%and the rest coefficients were defined as in \cite{hu_etal_2018}.
 For type A schemes, the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.  
@@
 We therefore proceed to design positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
-We will limit the scope to IMEX schemes of type~ARS.
+We limit the scope to IMEX schemes of type~ARS.  
+(It can be shown that IMEX schemes of type~A satisfying the conditions we list below Eq.~\eqref{eq:orderConditionsEx} do not exist.)
 
@@
   \item Well-behaved in the diffusion limit; i.e., satisfies Eq.~\eqref{eq:diffusionCondition}.
-  \item Positivity-preserving (conditions given by \cite{hu_etal_2018}; with $c_{\mbox{\tiny Sch}}$ maximal).
-  \item Few ($\le3$) implicit stages.
+  \item Positivity-preserving (conditions given by \cite{hu_etal_2018}; with $c_{\mbox{\tiny Sch}}>0$ and maximal).
+  \item Few stages ($s\le3$).
 \end{itemize}

### 2018-06-08 Documents/M1/realizableFermionicM1/sections/model.tex
Minor changes due to comments from Tony

@@
 
-We consider approximate solutions to the Boltzmann equation for transport of massless particles through a material in Cartesian geometry, which, after scaling to dimensionless units, can be written as
+We consider approximate solutions to the Boltzmann equation for transport of massless particles through a static material in Cartesian geometry, which, after scaling to dimensionless units, can be written as
 \begin{equation}
@@
 On the right-hand side of Eq.~\eqref{eq:boltzmann}, $\tau$ is the ratio of the particle mean-free path (due to interactions with a background) to some characteristic length scale of the problem.  
-In opaque regions, $\tau\ll1$, while for free streaming radiation, $\tau\gg1$.  
+In opaque regions, $\tau\ll1$, while for free streaming particles, $\tau\gg1$.  
 The collision term, due to emission, absorption, and isotropic and elastic scattering, is given by
@@
 
-Taking the zeroth and first moments of Eq.~\eqref{eq:boltzmann} gives the two-moment model, comprising of a system of conservation laws with sources
+Taking the zeroth and first moments of Eq.~\eqref{eq:boltzmann} gives the two-moment model, comprising a system of conservation laws with sources
 \begin{equation}

### 2018-06-11 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added the proof of nonexistence s=3 type A IMEX to the appendix.

@@
 It's clear that $\epsilon = 0$ and $c_{sch} = 1$ is the most optimized solution.
+
+\section{Proof of nonexistence of 3-stage Type A ...}
+
+Proof of GSA IMEX schemes of Type~A with 3 stages and the following properties does not exist
+\begin{itemize}
+  \item Second-order in the streaming limit;
+  \item Well-behaved in the diffusion limit;
+  \item Positivity-preserving.
+\end{itemize}
+First of all, the GSA IMEX scheme of Type A with 3 stages have the following form:
+\begin{equation*}
+  \begin{array}{c | c c c}
+  	      0       & 0              & 0              & 0 \\
+  	\tilde{c}_{2} & \tilde{a}_{21} & 0              & 0 \\
+  	\tilde{c}_{3} & \tilde{a}_{31} & \tilde{a}_{32} & 0 \\ \hline
+  	              & \tilde{a}_{31} & \tilde{a}_{32} & 0
+  \end{array}
+  \qquad
+  \begin{array}{c | c c c}
+    c_{1} & a_{11} & 0      & 0      \\
+  	c_{2} & a_{21} & a_{22} & 0      \\
+  	c_{3} & a_{31} & a_{32} & a_{33} \\ \hline
+  	      & a_{31} & a_{32} & a_{33}
+  \end{array}.
+\end{equation*}
+The second-order in the streaming limit requires
+\begin{align*}
+\tilde{a}_{31} + \tilde{a}_{32} = 1, \quad a_{31} + a_{32} + a_{33} = 1, \quad \tilde{a}_{32}\cdot \tilde{a}_{21} =  \frac{1}{2}.
+\end{align*}
+The diffusion accurate Eq.~\eqref{eq:diffusionCondition} requires 
+\begin{align*}
+\tilde{a}_{21} = a_{22}, \quad -\dfrac{a_{32} \tilde{a}_{21}}{a_{22}a_{33}} + \dfrac{1}{a_{33}} =1.
+\end{align*}
+That's 
+\begin{align*}
+\tilde{a}_{21} = a_{22}, \quad a_{31} = 0.
+\end{align*}
+Positivity-preserving requires
+\begin{align*}
+& a_{11} > 0, ~ a_{22} >0, ~ a_{33}>0,\\
+& c_{20} = 1 - \frac{a_{21}}{a_{11}} \geq 0, ~ c_{30} = 1-\frac{a_{31}}{a_{11}} + \frac{a_{32}a_{21}}{a_{22}a_{11}} - \frac{a_{32}}{a_{22}}\geq 0, \\
+& c_{21} = \frac{a_{21}}{a_{11}} \geq 0, ~ c_{31} = \frac{a_{31}}{a_{11}} - \frac{a_{32}a_{21}}{a_{22}a_{11}} \geq 0, ~ c_{32} = \frac{a_{32}}{a_{22}} \geq 0,\\
+& \tilde{c}_{21} = \tilde{a}_{21} \geq 0, \tilde{c}_{31} = \tilde{a}_{31} - \frac{a_{32}\tilde{a}_{21}}{a_{22}} \geq 0, \tilde{c}_{32} = \tilde{a}_{32} \geq 0.
+\end{align*}
+Note that since $a_{31} = 0$, $a_{21} \geq 0$, $a_{32} \geq 0$, $a_{22} > 0$ and $a_{11} >0$, $c_{31} \geq 0$ only holds for $c_{31} = 0$.
+Unfortunately, $c_{31} = 0$ will drag $c_{\mbox{\tiny Sch}} = 0$ since $c_{\mbox{\tiny Sch}} = \min \left\lbrace \dfrac{c_{21}}{\tilde{c}_{21}}, \dfrac{c_{31}}{\tilde{c}_{31}}, \dfrac{c_{32}}{\tilde{c}_{32}}\right\rbrace $.
+Therefore, GSA IMEX schemes of Type~A with 3 stages and the above properties does not exist.

### 2018-06-12 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
Work on realizability-preserving DG-IMEX section.  Also changes due to comments from Tony and Cory.

@@
 Eqs.~\eqref{imexStages}-\eqref{eq:imexCorrection}).
-The realizability-preserving DG scheme is designed to preserve realizability of cell averages over a time step $\dt$ in each element $\bK$.  
-Following the framework in \cite{zhangShu_2010b}, for high-order DG schemes, realizability of the cell average is leveraged to limit the polynomial approximation $\vect{\cM}_{h}$, if $\vect{\cM}_{h}$ is not realizable in a finite number of points in $\bK$ (Section~\ref{sec:limiter}).
+Following the framework in \cite{zhangShu_2010b} for high-order DG schemes, the realizability-preserving DG-IMEX scheme is designed to preserve realizability of cell averages over a time step $\dt$ in each element $\bK$.
+Realizability of the cell average is leveraged to limit the polynomial approximation $\vect{\cM}_{h}$ in the stages of the IMEX scheme.  
+If the polynomial approximation $\vect{\cM}_{h}$ is not realizable in a finite number of points in $\bK$, the high-order components are damped (see Section~\ref{sec:limiter}).  
 The cell average of the moments is defined as
@@
 \begin{equation}
-  \big\langle\,\nabla\cdot\vect{\cF}(\vect{\cM}_{h})\,\big\rangle_{\bK}
-  =\f{1}{|\bK|}\sum_{i=1}^{d}\int_{\tilde{\bK}^{i}}
-  \big(\,\widehat{\bcF}^{i}(\vect{\cM}_{h})\big|_{\xH^{i}}-\widehat{\bcF}^{i}(\vect{\cM}_{h})\big|_{\xL^{i}}\,\big)\,d\tilde{\vect{x}}^{i}.  
+  \big\langle\,\nabla\cdot\vect{\cF}(\vect{\cM}_{h}^{(j)})\,\big\rangle_{\bK}
+  =\f{1}{|\bK|}\sum_{k=1}^{d}\int_{\tilde{\bK}^{k}}
+  \big(\,\widehat{\bcF}^{k}(\vect{\cM}_{h}^{(j)})\big|_{\xH^{k}}-\widehat{\bcF}^{k}(\vect{\cM}_{h}^{(j)})\big|_{\xL^{k}}\,\big)\,d\tilde{\vect{x}}^{k}.  
 \end{equation}
 
+We first establish conditions for realizability of the stage values in Eq.~\eqref{eq:imexStagesCellAverage}.  
 \begin{lemma}
@@
   Then, $\vect{\cM}_{\bK}^{(i)}\in\cR$, for $i=1,\ldots,s$.  
+  \label{lem:imexStagesCellAverage}
 \end{lemma}
@@
 We proceed to establish conditions for which $\vect{\cM}_{\bK}^{(ij)}\in\cR$.  
-To this end, to simplify notation, we consider the moments
-\begin{equation}
-  \vect{\cM}_{\bK}^{*}
-  =\vect{\cM}_{\bK}-\hat{c}\,\dt\,\big\langle\,\nabla\cdot\vect{\cF}(\vect{\cM}_{h})\,\big\rangle_{\bK},
-\end{equation}
-where $\vect{\cM}_{\bK}$ is the cell average of $\vect{\cM}_{h}\in\bbV^{k}$ and $\hat{c}\ge0$.  
 \begin{lemma}
-  Let $\{s_{i}\}_{i=1}^{d}$ be a set of positive constants satisfying $\sum_{i=1}^{d}s_{i}=1$.  
-  If for each $i\in\{1,\ldots,d\}$, 
-  \begin{equation}
-    \vect{\Gamma}^{i}\big[\vect{\cM}_{h}\big](\tilde{\vect{x}}^{i})
-    :=\f{1}{|K^{i}|}
-    \Big[\,\int_{K^{i}}\vect{\cM}_{h}\,dx^{i}-\f{\hat{c}\,\dt}{s_{i}}\big(\,\widehat{\bcF}^{i}(\vect{\cM}_{h})\big|_{\xH^{i}}-\widehat{\bcF}^{i}(\vect{\cM}_{h})\big|_{\xL^{i}}\,\big)\,\Big]\in\cR,
-    \label{eq:realizableGamma}
-  \end{equation}
-  then $\vect{\cM}_{\bK}^{*}\in\cR$.  
+  Let $\{\beta_{k}\}_{k=1}^{d}$ be a set of positive constants satisfying $\sum_{k=1}^{d}\beta_{k}=1$.  
+  If for each $k\in\{1,\ldots,d\}$, 
+  \begin{align}
+    &\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{(j)};\hat{c}_{ij}\big](\tilde{\vect{x}}^{k}) \label{eq:realizableGamma} \\
+    &:=\f{1}{|K^{k}|}
+    \Big[\,\int_{K^{k}}\vect{\cM}_{h}^{(j)}\,dx^{k}-\f{\hat{c}_{ij}\,\dt}{\beta_{k}}\big(\,\widehat{\bcF}^{k}(\vect{\cM}_{h}^{(j)})\big|_{\xH^{k}}-\widehat{\bcF}^{k}(\vect{\cM}_{h}^{(j)})\big|_{\xL^{k}}\,\big)\,\Big]\in\cR, \nonumber
+  \end{align}
+  then $\vect{\cM}_{\bK}^{(ij)}\in\cR$.  
+  \label{lem:realizableMij}
 \end{lemma}
 \begin{proof}
-  It is easy to show that $\vect{\cM}_{\bK}^{*}$ can be expressed as the convex combination
+  It is easy to show that $\vect{\cM}_{\bK}^{(ij)}$ can be expressed as the convex combination
   \begin{equation}
-    \vect{\cM}_{\bK}^{*}
-    =\sum_{i=1}^{d}s_{i}\,\f{1}{|\tilde{\vect{\bK}}^{i}|}\int_{\tilde{\bK}^{i}}\vect{\Gamma}^{i}\big[\vect{\cM}_{h}\big]\,d\tilde{\vect{x}}^{i}.  
+    \vect{\cM}_{\bK}^{(ij)}
+    =\sum_{k=1}^{d}\beta_{k}\,\f{1}{|\tilde{\vect{\bK}}^{k}|}\int_{\tilde{\bK}^{k}}\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{(j)};\hat{c}_{ij}\big]\,d\tilde{\vect{x}}^{k}.  
     \label{eq:cellAverageInTermsOfGamma}
@@
 \begin{rem}
-  If a quadrature rule $\tilde{\vect{Q}}^{i}:C^{0}\to\bbR$, with positive weights, and points defined by the set $\tilde{\vect{S}}^{i}$, is used to approximate the integral over $\tilde{\bK}^{i}$ in Eq.~\eqref{eq:cellAverageInTermsOfGamma}, it is sufficient for Eq.~\eqref{eq:realizableGamma} to hold in the quadrature points $\tilde{\vect{S}}^{i}\subset\tilde{\bK}^{i}$.
+  If a quadrature rule $\tilde{\vect{Q}}^{k}\colon C^{0}(\tilde{\bK}^{k})\to\bbR$, with positive weights, and points defined by the set $\tilde{\vect{S}}^{k}$, is used to approximate the integral over $\tilde{\bK}^{k}$ in Eq.~\eqref{eq:cellAverageInTermsOfGamma}, it is sufficient for Eq.~\eqref{eq:realizableGamma} to hold in the quadrature points $\tilde{\vect{S}}^{k}\subset\tilde{\bK}^{k}$.
 \end{rem}
@@
 Next, we establish conditions for which Eq.~\eqref{eq:realizableGamma} holds.  
-To simplify the notation, we temporarily drop the dimension index $i$, setting $x^{i}=x$, $K^{i}=K$, $\vect{\Gamma}^{i}=\vect{\Gamma}$, etc.  
-We let $\hat{Q}_{N}$ denote the $N$-point \emph{Gauss-Lobatto (GL)} quadrature rule on the interval $K=(x_{\Low},x_{\Hgh})$, with points
+%To simplify the notation, we temporarily drop the dimension index $i$, setting $x^{i}=x$, $K^{i}=K$, $\vect{\Gamma}^{i}=\vect{\Gamma}$, etc.  
+We let $\hat{Q}^{k}\colon C^{0}(K^{k})\to\bbR$ denote the $N$-point \emph{Gauss-Lobatto (GL)} quadrature rule on the interval $K^{k}=(x_{\Low}^{k},x_{\Hgh}^{k})$, with points
 \begin{equation}
-  \hat{S}=\left\{x_{\Low}=\hat{x}_{1},\cdots,\hat{x}_{N}=x_{\Hgh}\right\}, 
+  \hat{S}^{k}=\left\{x_{\Low}^{k}=\hat{x}_{1}^{k},\ldots,\hat{x}_{N}^{k}=x_{\Hgh}^{k}\right\}, 
   \label{eq:quadraturePointsGL}
@@
 and weights $\hat{w}_{q} \in (0,1]$, normalized so that $\sum_{q=1}^{N} \hat{w}_{q} = 1$.  
-(The hat is used to denote the GL rule, which includes the endpoints of the interval $K$.)
-This quadrature integrates polynomials in $x \in \bbR$ with degree $\le2N-3$ exactly.  
-Then, if $\vect{\cM}_{h}$ is represented by such polynomials we have
+(The hat is used to denote the GL rule, which includes the endpoints of the interval $K^{k}$.)
+This quadrature integrates polynomials in $x^{k} \in \bbR$ with degree $\le2N-3$ exactly.  
+Then, if $\vect{\cM}_{h}^{(j)}$ is represented by such polynomials we have
 \begin{equation}
-  \int_{K} \bcM_{h}\,dx = \hat{Q}_{N}[\bcM_{h}] \equiv
-  |K| \sum_{q=1}^{N} \hat{w}_{q}\,\hat{\bcM}_{q}
+  \int_{K^{k}} \bcM_{h}^{(j)}(x^{k})\,dx^{k} = \hat{Q}^{k}[\bcM_{h}^{(j)}] \equiv
+  |K^{k}| \sum_{q=1}^{N} \hat{w}_{q}\,\bcM_{h}^{(j)}(\hat{x}_{q}^{k})
   \label{eq:quadratureRuleGL}
 \end{equation}
-where $\hat{\bcM}_{q} := \bcM_{h}(\hat{x}_q,\tilde{\vect{x}})$.  
-In each element, $\hat{\vect{\cM}}_{1}=\vect{\cM}_{\Low}^{+}$ and $\hat{\vect{\cM}}_{N}=\vect{\cM}_{\Hgh}^{-}$.
+where, for simplicity of notation, we have suppressed the explicit dependence on $\tilde{\vect{x}}^{k}$ to denote $\bcM_{h}^{(j)}(\hat{x}_q^{k},\tilde{\vect{x}}^{k}) = \bcM_{h}^{(j)}(\hat{x}_{q}^{k})$.
+In each element, we also denote $\vect{\cM}_{h}^{(j)}(\hat{x}_{1}^{k})=\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})$ and $\vect{\cM}_{h}^{(j)}(\hat{x}_{N}^{k})=\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})$.  
+Similarly, the solution on $\tilde{\vect{\bK}}^{k}$ to the immediate left of $x_{\Low}^{k}$ is denoted $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})$, and the solution on $\tilde{\vect{\bK}}^{k}$ to the immediate right of $x_{\Hgh}^{k}$ is denoted $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})$.
 
-With the GL quadrature rule in Eq.~\eqref{eq:quadratureRuleGL} (note $\hat{w}_{1}=\hat{w}_{N}$), we can write $\vect{\Gamma}$ as the convex combination
-\begin{equation}
-  \vect{\Gamma}\big[\bcM_{h}\big]
-  =\sum_{q=2}^{N-1}\hat{w}_{q}\,\hat{\vect{\cM}}_{q}
-  +2\,\hat{w}_{N}\,\Phi(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+}),
+With the GL quadrature rule in Eq.~\eqref{eq:quadratureRuleGL} (note $\hat{w}_{1}=\hat{w}_{N}$), we can write $\vect{\Gamma}^{k}$ as the convex combination
+\begin{align}
+  &\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]
+  =\sum_{q=2}^{N-1}\hat{w}_{q}\,\vect{\cM}_{h}^{(j)}(\hat{x}_{q}^{k}) \nonumber \\
+  &\hspace{12pt}
+  +2\,\hat{w}_{N}\,
+  \Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big],
   \label{eq:realizableGammaConvex}
-\end{equation}
-where we have defined
+\end{align}
+where
 \begin{align}
-  &\Phi(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+}) \nonumber \\
+  &\Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big] \nonumber \\
+  &=\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\lambda_{ij}^{k}\,\mathscr{F}\big(\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big)\,\big] \nonumber \\
   &\hspace{12pt}
-  =\f{1}{2}\big(\,\vect{\cM}_{\Low}^{+}+\lambda\,\mathscr{F}(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+})\,\big)
-  +\f{1}{2}\big(\,\vect{\cM}_{\Hgh}^{-}-\lambda\,\mathscr{F}(\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+})\,\big),
+  +\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})-\lambda_{ij}^{k}\,\mathscr{F}\big(\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big)\,\big],
 \end{align}
-with $\lambda=\hat{c}\,\dt/(s\,\hat{w}_{N}\,|K|)$.  
-The following Lemma establishes sufficient conditions for realizability of $\vect{\Gamma}$, and hence $\vect{\cM}_{\bK}^{*}$.  
+with $\lambda_{ij}^{k}=\hat{c}_{ij}\,\dt/(\beta_{k}\,\hat{w}_{N}\,|K^{k}|)$.  
+The following Lemma establishes sufficient conditions for realizability of $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]$, and hence $\vect{\cM}_{\bK}^{(ij)}$.  
 \begin{lemma}
-  Assume that $\hat{\vect{\cM}}_{q}\in\cR$ for all $q=1,\ldots,N$ and all $\bK\in\mathscr{T}$.  
-  Let the time step $\dt$ be chosen so that $\lambda\le1$.  
+  Assume that $\vect{\cM}_{h}^{(j)}(\hat{x}_{q}^{k})\in\cR$ for all $q=1,\ldots,N$ and all $\bK\in\mathscr{T}$.  
+  Let the time step $\dt$ be chosen so that $\lambda_{ij}^{k}\le1$.  
   Let the numerical flux be given by the Lax-Friedrichs flux in Eq.~\eqref{eq:fluxFunctionLF} with $\alpha=1$.  
-  Then $\vect{\Gamma}[\bcM_{h}]\in\cR$.  
+  Then $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]\in\cR$.  
+  \label{lem:realizableGamma}
 \end{lemma}
 \begin{proof}
-  In Eq.~\eqref{eq:realizableGammaConvex}, $\vect{\Gamma}[\vect{\cM}_{h}]$ is expressed as a convex combination.  
-  By assumption, $\hat{\vect{\cM}}_{q}\in\cR$ ($q=2,\ldots,N-1$).  
-  It remains to show $\Phi(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+})\in\cR$.  
+  In Eq.~\eqref{eq:realizableGammaConvex}, $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]$ is expressed as a convex combination.  
+  By assumption, $\vect{\cM}_{h}^{(j)}(\hat{x}_{q}^{k})\in\cR$ ($q=2,\ldots,N-1$).  
+  It remains to show 
+  \begin{equation*}
+    \Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big]\in\cR.  
+  \end{equation*}
   Using the Lax-Friedrichs flux with $\alpha=1$, it is straightforward to show that
   \begin{align}
-    &\Phi(\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+})
-    =(1-\lambda)\,\big(\,\f{1}{2}\,\vect{\cM}_{\Low}^{+}+\f{1}{2}\,\vect{\cM}_{\Hgh}^{-}\,\big) \nonumber \\
+    &\Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big] \nonumber \\
+    &=(1-\lambda_{ij}^{k})\,\big(\,\f{1}{2}\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\f{1}{2}\,\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})\,\big) \nonumber \\
     &\hspace{12pt}
-    +\f{1}{2}\,\lambda\,\big(\,\Phi^{+}(\vect{\cM}_{\Low}^{-})+\Phi^{-}(\vect{\cM}_{\Hgh}^{-})\,\big)
-    +\f{1}{2}\,\lambda\,\big(\,\Phi^{+}(\vect{\cM}_{\Low}^{+})+\Phi^{-}(\vect{\cM}_{\Hgh}^{+})\,\big),
+    +\f{1}{2}\,\lambda_{ij}^{k}\,\big(\,\Phi^{+}\big[\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})\big]\,\big) \nonumber \\
+    &\hspace{12pt}
+    +\f{1}{2}\,\lambda_{ij}^{k}\,\big(\,\Phi^{+}\big[\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big]\,\big),
     \label{eq:phiConvex}
   \end{align}
-  where $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\,\big(\vect{\cM}\pm\vect{e}\cdot\vect{\cF}(\vect{\cM})\big)$.  
-  Since $\lambda\le1$, $\Phi$ is expressed as a convex combination of three terms.  
-  By assumption, $\vect{\cM}_{\Low}^{-},\vect{\cM}_{\Low}^{+},\vect{\cM}_{\Hgh}^{-},\vect{\cM}_{\Hgh}^{+}\in\cR$, which immediately implies realizability of the first term on the right-hand side of Eq.~\eqref{eq:phiConvex}.
+  where $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\,\big(\vect{\cM}\pm\vect{e}_{k}\cdot\vect{\cF}^{k}(\vect{\cM})\big)$.  
+  Since $\lambda_{ij}^{k}\le1$, $\Phi$ is expressed as a convex combination of three terms.  
+  By assumption, $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})$, $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})$, $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})$, $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\in\cR$, which immediately implies realizability of the first term on the right-hand side of Eq.~\eqref{eq:phiConvex}.
   Realizability of the second and third terms follows by invoking Lemma~\ref{lem:explicitStep}.  
@@
 \end{proof}
+
+\begin{rem}
+  Lemma~\eqref{lem:realizableGamma} is proven without specification of $\tilde{\vect{x}}^{k}$.  
+  In the numerical scheme, we need $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]$ to be realizable in the quadrature set $\tilde{\vect{S}}^{k}$ used to approximate the integral over $\tilde{\bK}^{k}$ in Eq.~\eqref{eq:realizableGamma}.
+  We thus require $\vect{\cM}_{h}^{(j)}$ to be realizable in the quadrature set $\hat{\vect{S}}^{k}=\tilde{\vect{S}}^{k}\otimes\hat{S}^{k}\subset\bK$, where $\tilde{\vect{S}}^{k}\subset\tilde{\bK}^{k}$, and $\hat{S}^{k}\subset K^{k}$ are the GL quadrature points.
+\end{rem}
+
+\begin{rem}
+  Lemmas~\ref{lem:imexStagesCellAverage}, \ref{lem:realizableMij}, and \ref{lem:realizableGamma} establish sufficient conditions for realizability of the cell average of each IMEX stage $\vect{\cM}_{\bK}^{(i)}$, for $i=1,\ldots,s$.
+  Within (and after) each IMEX stage, the realizability-preserving limiter discussed in Section~\ref{sec:limiter} is invoked to ensure that the numerical solution is realizable in the quadrature points $\hat{\vect{S}}^{k}$, for $k=1,\ldots,k$.
+  For GSA IMEX schemes, $\tilde{\vect{\cM}}_{\bK}^{n+1}=\vect{\cM}_{\bK}^{(s)}$.  
+\end{rem}
+
+For IMEX schemes incorporating the correction step in Eq.~\eqref{eq:imexCorrection}, the cell average at $t^{n+1}$ is obtained by solving
+\begin{equation}
+  \vect{\cM}_{\bK}^{n+1}=\tilde{\vect{\cM}}_{\bK}^{n+1}+\alpha\,\f{\dt^{2}}{\tau^{2}}\,\vect{\cD}\,\big(\,\vect{\eta}-\vect{\cD}\,\vect{\cM}_{\bK}^{n+1}\,\big),
+  \label{eq:imexCorrectionCellAverage}
+\end{equation}
+where $\vect{\eta}$ and $\vect{\cD}$ are defined in Eq.~\eqref{eq:collisionTermMoments}.  
+For these IMEX schemes, realizability of $\vect{\cM}_{\bK}^{n+1}$ is established by the following lemma.  
+\begin{lemma}
+  Suppose that $\tilde{\vect{\cM}}_{\bK}^{n+1}\in\cR$ and $\vect{\cM}_{\bK}^{n+1}$ is obtained by solving Eq.~\eqref{eq:imexCorrectionCellAverage} with $\beta:=\alpha\,\dt^{2}/\tau^{2}\ge0$.  
+  Then $\vect{\cM}_{\bK}^{n+1}\in\cR$.  
+\end{lemma}
+\begin{proof}
+  With the collision term in Eq.~\eqref{eq:collisionTermMoments}, Eq.~\eqref{eq:imexCorrectionCellAverage} can be rewritten in the form
+  \begin{equation*}
+    \vect{\cM}_{\bK}^{n+1}=\tilde{\vect{\cM}}_{\bK}^{n+1}+\beta\,\vect{\cD}\,\vect{\cC}(\vect{\cM}_{\bK}^{n+1}).  
+  \end{equation*}
+  The proof is completed by invoking Lemma~\ref{lem:correctionStep}.  
+\end{proof}
+
+\begin{rem}
+  For IMEX scheme PARSD (\ref{app:PARSD}), which does not invoke the correction step (i.e., $\alpha=0$), $\vect{\cM}_{\bK}^{n+1}=\vect{\cM}_{\bK}^{(s)}$.  
+\end{rem}
+
+We are now ready to state the main result of this section.  
+\begin{theorem}
+  Let
+\end{theorem}

### 2018-06-12 Documents/M1/realizableFermionicM1/sections/realizability.tex
Work on realizability-preserving DG-IMEX section.  Also changes due to comments from Tony and Cory.

--- 2018-05-16 Documents/M1/realizableFermionicM1/sections/realizability.tex
@@
 
-Our goal is to simulate a gas of massless fermions (i.e., classical neutrinos) and study their interactions with matter.  
+Our goal is to simulate massless fermions (e.g., neutrinos) and study their interactions with matter.  
 The principal objective is to obtain the fermionic distribution function $f$ (or moments of $f$ as in the two-moment model employed here).  
 The Pauli exclusion principle requires the distribution function to satisfy the condition $0 \le f \le 1$, which puts restrictions on the admissible values for the moments of $f$.  
-In this paper, we seek to design a numerical method for solving the system of moment equations given by Eq.~\eqref{eq:momentEquations}, which preserves realizability of the moments; i.e., the moments evolve within the set of admissible values as dictated by Pauli's exclusion principle.
+In this paper, we seek to design a numerical method for solving the system of moment equations given by Eq.~\eqref{eq:momentEquations} that preserves realizability of the moments; i.e., the moments evolve within the set of admissible values as dictated by Pauli's exclusion principle.
 (Since we are only concerned with the angular dependence of $f$ in this section, we simplify the notation by suppressing the $\vect{z}$ and $t$ dependence and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.)
@@
 
-Realizable moments must satisfy the bounds imposed by $f$.  
-We proceed by stating the bounds on the moments by restating results from Theorem~7.1 in \cite{banachLarecki_2017a} in the following Lemma.  
+Realizable moments must satisfy algebraic constraints.  
+We proceed by stating the constraints on the moments by restating results from Theorem~7.1 in \cite{banachLarecki_2017a} in the following Lemma.  
+The proof is given in \cite{banachLarecki_2017a}.  
+(See also \cite{lareckiBanach_2011,banachLarecki_2013}.)
 \begin{lemma}
-  Let the distribution function be bounded by $0\le f(\omegaNu) \le1~\forall~\omegaNu\in\bbS^{2}$.  
+  Suppose that $0\le f(\omegaNu) \le1~\forall~\omegaNu\in\bbS^{2}$.  
   Then the moments $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, defined as in Eq.~\eqref{eq:angularMoments}, satisfy $0\le\cJ\le1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}|\ge0$. 
@@
 \end{lemma}
-The proof is given in \cite{banachLarecki_2017a} and is omitted.  
-(See also \cite{lareckiBanach_2011,banachLarecki_2013}.)
 %\begin{proof}
@@
 
-Next we define the realizable set $\cR$ for the fermion two-moment model
+\begin{define}
+  The realizable set $\cR$ for the fermion two-moment model is given by
   \begin{equation}
@@
   \end{equation}
+\end{define}
 
@@
   In order to prove that $\cR$ is convex, we must show that any convex combination of elements in $\cR$ also belongs to $\cR$.  
-  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements in $\cR$.  
+  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ be two arbitrary elements in $\cR$.  
   Consider the convex combination $\vect{\cM}_{c} = \theta\,\vect{\cM}_{a} + (1-\theta)\,\vect{\cM}_{b}$, with $0\leq\theta\leq1$.
@@
 The boundary of $\cR$, $\partial\cR$ (black curves), is given by $\gamma(\vect{\cM})=0$.  
-The realizable domain of positive distribution functions, $\cR^{+}$ (no upper bound on $f$), a convex cone defined by
+The realizable domain of positive distribution functions, $\cR^{+}$ (no upper bound on $f$), which is a convex cone defined by
 \begin{equation}
@@
 \end{equation}
-is partially shown as the region above the red lines.  
-(A Realizability-preserving method, with respect to $\cR^{+}$, for the two-moment model in one spatial dimension was developed in \cite{olbrant_etal_2012}.)
+is partially shown as the light red region above the red lines, which mark the boundary of $\cR^{+}$ (denoted $\partial\cR^{+}$).  
+(A realizability-preserving method, with respect to $\cR^{+}$, for the two-moment model in one spatial dimension was developed in \cite{olbrant_etal_2012}.)  
+The realizable domains $\cR$ and $\cR^{+}$ overlap for low particle densities ($\cJ\ll1$), but for larger values of $\cJ$, the realizable domain of particles governed by Fermi-Dirac statistics is much more restricted than that of particles described by positive distribution functions with no upper bound.
 
@@
   \includegraphics[width=1.0\linewidth]{figures/RealizableSetFermionic}
-  \caption{Illustration of the realizable set $\cR$ defined in Eq.~\eqref{eq:realizableSet}.  
-  The black lines define the boundary of $\cR$, $\partial\cR$ ($\gamma(\vect{\cM}) = 0$), while the red lines indicate the boundary of the realizable set of positive distributions with no upper bound; cf.
+  \caption{Illustration of the realizable set $\cR$ (light blue region) defined in Eq.~\eqref{eq:realizableSet}.  
+  The black lines define the boundary of $\cR$, $\partial\cR$ ($\gamma(\vect{\cM}) = 0$), while the red lines indicate the boundary of the realizable set of positive distributions with no upper bound (light red region); cf.
 Eq.~\eqref{eq:realizableSetPositive}.}
@@
 
-For the realizability-preserving scheme, we state some additional results.  
+For the realizability-preserving scheme developed in Section~\ref{sec:realizableDGIMEX}, we state some additional results.  
+Lemma~\ref{lem:explicitStep} is used to help prove the realizability-preserving property of explicit steps in the IMEX scheme, while Lemmas~\ref{lem:implicitStep} and \ref{lem:correctionStep} are used to prove realizability-preserving properties of implicit steps.
 \begin{lemma}

### 2018-06-14 Documents/M1/realizableFermionicM1/sections/appendix.tex
Modified the proof of nonexistence of 3-stage Type A.

@@
 The second-order in the streaming limit requires
-\begin{align*}
-\tilde{a}_{31} + \tilde{a}_{32} = 1, \quad a_{31} + a_{32} + a_{33} = 1, \quad \tilde{a}_{32}\cdot \tilde{a}_{21} =  \frac{1}{2}.
-\end{align*}
+\begin{align}
+\tilde{a}_{31} + \tilde{a}_{32} = 1, \quad \tilde{a}_{32}\cdot \tilde{a}_{21} =  \frac{1}{2}.
+\end{align}
+An implicit property, the first-order in general transport condition, requires
+\begin{align}
+ \quad a_{31} + a_{32} + a_{33} = 1.
+ \label{eq:1stOrderGeneral}
+\end{align}
 The diffusion accurate Eq.~\eqref{eq:diffusionCondition} requires 
-\begin{align*}
+\begin{align}
 \tilde{a}_{21} = a_{22}, \quad -\dfrac{a_{32} \tilde{a}_{21}}{a_{22}a_{33}} + \dfrac{1}{a_{33}} =1.
-\end{align*}
-That's 
-\begin{align*}
+\label{eq:diffusionAccurate}
+\end{align}
+Substituting Eq.~\eqref{eq:1stOrderGeneral} into Eq.~\eqref{eq:diffusionAccurate} gives
+\begin{align}
 \tilde{a}_{21} = a_{22}, \quad a_{31} = 0.
-\end{align*}
+\label{eq:a31is0}
+\end{align}
 Positivity-preserving requires

### 2018-06-14 Documents/M1/realizableFermionicM1/sections/imex.tex
Added one more reference for type A IMEX

@@
 (In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.)  
-Two types of IMEX schemes are considered: \emph{type~A} \cite{pareschiRusso_2005} and \emph{type~ARS} \cite{ascher_etal_1997}.  
+Two types of IMEX schemes are considered: \emph{type~A} \cite{pareschiRusso_2005,dimarcoPareschi2013} and \emph{type~ARS} \cite{ascher_etal_1997}.  
 For IMEX schemes of type~A, the matrix $A$ is invertible.  

### 2018-06-14 Documents/M1/realizableFermionicM1/sections/numerical.tex
Work on imex section.  Replaced all hu_et_al_2017 with hu_etal_2018
Added some text for reference transport solution.

@@
 We compare results obtained using IMEX schemes proposed here (PA2+ and PARSD) with IMEX schemes from Hu et al.
-\cite{hu_etal_2017} (PA2), McClarren et al.
+\cite{hu_etal_2018} (PA2), McClarren et al.
 \cite{mcclarren_etal_2008} (PC2), Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332), and Cavaglieri \& Bewley \cite{cavaglieriBewley2015} (RKCB2).
@@
 Spatial distribution of the number density $\cJ$ (CB closure only) at $t=1$ (upper left panel).
-Number density $\cJ$ versus radius $R=|\vect{x}|$ for various times ($t=0$, $0.1$, $0.2$, and $0.4$) for the CB (blue) and the Minerbo (magenta) closures (upper right panel).
-(The initial condition, same for both models, is plotted with cyan.)  Numerical solutions in the $(\cH_{x},\cJ)$-plane (lower left panel), for the same times as plotted in the upper right panel.
+In the upper right panel we plot the number density $\cJ$ versus radius $R=|\vect{x}|$ for various times ($t=0$, $0.1$, $0.2$, and $0.4$) for the CB (blue), the Minerbo (magenta) closures, and the reference transport solution (dashed black lines).
+(The initial condition, which is the same for all models, is plotted with cyan.)  Numerical solutions in the $(\cH_{x},\cJ)$-plane (lower left panel), for the same times as plotted in the upper right panel are plotted for CB and Minerbo.
 Limiter parameters $\vartheta_{1}$ (solid) and $\vartheta_{2}$ (dashed) in Section~\ref{sec:limiter} (minimum over the whole computational domain) versus time (lower right panel).}
@@
 The right panel in Figure~\ref{fig:Implosion} illustrates the difference in dynamics resulting from the two closures.  
+(We also plot a reference transport solution obtained using the filtered spherical harmonics scheme described in \cite{garrettHauck_2013}; dashed black lines.)  
 With the CB closure (blue lines), the central density increases towards the maximum value of unity, and an low-density pulse propagates radially.  
@@
 Except for the positivity limiter (which is not triggered for this model), no limiters are used to prevent numerical oscillations.  
+Although the solutions obtained with the two-moment model differ from the reference transport solution, the results obtained with the CB closure are in closer agreement with the transport solution.  
 In the lower left panel in Figure~\ref{fig:Implosion}, the moments are plotted in the $(\cH_{x},\cJ)$-plane for the same times as plotted in the upper left panel.  

### 2018-06-14 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
First complete draft of this section, including Theorem 1.

@@
 If the polynomial approximation $\vect{\cM}_{h}$ is not realizable in a finite number of points in $\bK$, the high-order components are damped (see Section~\ref{sec:limiter}).  
+The main result of this section is stated in Theorem~\ref{the:realizableDGIMEX}.
+
 The cell average of the moments is defined as
@@
 \end{equation}
-Then, with $v=1$ in Eq.~\eqref{eq:semidiscreteDG}, the stage values for the cell average in the IMEX scheme in Eq.~\eqref{eq:imexStagesRewrite} are given by
+Then, with $v=1$ in Eq.~\eqref{eq:semidiscreteDG}, and invoking the form in Eq.~\eqref{eq:imexStagesRewrite}, the stage values for the cell average in the IMEX scheme are given by
 \begin{equation}
@@
 \end{equation}
-where $c_{ij}\ge0$, $a_{ii}>0$, and $\sum_{j=0}^{i-1}c_{ij}=1$, and we have defined
+where $c_{ij}\ge0$, $\sum_{j=0}^{i-1}c_{ij}=1$, and $a_{ii}>0$, and we have defined
 \begin{equation}
@@
 \end{equation}
-with $\cM_{\bK}^{(0)}=\cM_{\bK}^{n}$.  
+with $\cM_{\bK}^{(0)}=\cM_{\bK}^{n}$, and where $\hat{c}_{ij}\ge0$.  
 The cell average of the divergence operator is (cf. Section~\ref{sec:dg})
@@
 Next, we establish conditions for which Eq.~\eqref{eq:realizableGamma} holds.  
-%To simplify the notation, we temporarily drop the dimension index $i$, setting $x^{i}=x$, $K^{i}=K$, $\vect{\Gamma}^{i}=\vect{\Gamma}$, etc.  
 We let $\hat{Q}^{k}\colon C^{0}(K^{k})\to\bbR$ denote the $N$-point \emph{Gauss-Lobatto (GL)} quadrature rule on the interval $K^{k}=(x_{\Low}^{k},x_{\Hgh}^{k})$, with points
@@
   \end{equation*}
-  Using the Lax-Friedrichs flux with $\alpha=1$, it is straightforward to show that
+  Using the Lax-Friedrichs flux in Eq.~\eqref{eq:fluxFunctionLF}, with $\alpha^{k}=1$ ($k=\{1,\ldots,d\}$), it is straightforward to show that
   \begin{align}
@@
 \begin{rem}
+  For the IMEX scheme to be realizability-preserving it is sufficient to set the time step such that
+  \begin{equation}
+    \dt = c_{\mbox{\tiny Sch}}\,\min_{k} \Big(\, \beta_{k}\,\hat{w}_{N}\,|K^{k}| \,\Big),
+    \label{eq:imexTimeStep}
+  \end{equation}
+  where $c_{\mbox{\tiny Sch}}$ is defined in \eqref{eq:imexCFL}.  
+\end{rem}
+
+\begin{rem}
   Lemma~\eqref{lem:realizableGamma} is proven without specification of $\tilde{\vect{x}}^{k}$.  
-  In the numerical scheme, we need $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]$ to be realizable in the quadrature set $\tilde{\vect{S}}^{k}$ used to approximate the integral over $\tilde{\bK}^{k}$ in Eq.~\eqref{eq:realizableGamma}.
+  In the numerical scheme, we need $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]$ to be realizable in the quadrature set $\tilde{\vect{S}}^{k}$ used to approximate the integral over $\tilde{\bK}^{k}$ in Eq.~\eqref{eq:realizableGamma}; typically the Legendre-Gauss quadrature points.
   We thus require $\vect{\cM}_{h}^{(j)}$ to be realizable in the quadrature set $\hat{\vect{S}}^{k}=\tilde{\vect{S}}^{k}\otimes\hat{S}^{k}\subset\bK$, where $\tilde{\vect{S}}^{k}\subset\tilde{\bK}^{k}$, and $\hat{S}^{k}\subset K^{k}$ are the GL quadrature points.
@@
   Lemmas~\ref{lem:imexStagesCellAverage}, \ref{lem:realizableMij}, and \ref{lem:realizableGamma} establish sufficient conditions for realizability of the cell average of each IMEX stage $\vect{\cM}_{\bK}^{(i)}$, for $i=1,\ldots,s$.
-  Within (and after) each IMEX stage, the realizability-preserving limiter discussed in Section~\ref{sec:limiter} is invoked to ensure that the numerical solution is realizable in the quadrature points $\hat{\vect{S}}^{k}$, for $k=1,\ldots,k$.
-  For GSA IMEX schemes, $\tilde{\vect{\cM}}_{\bK}^{n+1}=\vect{\cM}_{\bK}^{(s)}$.  
+  Within (and after) each IMEX stage, the realizability-enforcing limiter discussed in Section~\ref{sec:limiter} is invoked to ensure that the numerical solution $\vect{\cM}_{h}^{(i)}(\vect{x})$ is realizable in the quadrature points $\hat{\vect{S}}^{k}$, for $k=1,\ldots,d$.
 \end{rem}
 
+For GSA IMEX schemes, $\tilde{\vect{\cM}}_{\bK}^{n+1}=\vect{\cM}_{\bK}^{(s)}$.  
 For IMEX schemes incorporating the correction step in Eq.~\eqref{eq:imexCorrection}, the cell average at $t^{n+1}$ is obtained by solving
@@
 \begin{lemma}
-  Suppose that $\tilde{\vect{\cM}}_{\bK}^{n+1}\in\cR$ and $\vect{\cM}_{\bK}^{n+1}$ is obtained by solving Eq.~\eqref{eq:imexCorrectionCellAverage} with $\beta:=\alpha\,\dt^{2}/\tau^{2}\ge0$.  
+  Suppose that $\tilde{\vect{\cM}}_{\bK}^{n+1}\in\cR$ and $\vect{\cM}_{\bK}^{n+1}$ is obtained by solving Eq.~\eqref{eq:imexCorrectionCellAverage} with $\hat{\alpha}:=\alpha\,\dt^{2}/\tau^{2}\ge0$.  
   Then $\vect{\cM}_{\bK}^{n+1}\in\cR$.  
+  \label{lem:imexCorrectionCellAverage}
 \end{lemma}
@@
   \begin{equation*}
-    \vect{\cM}_{\bK}^{n+1}=\tilde{\vect{\cM}}_{\bK}^{n+1}+\beta\,\vect{\cD}\,\vect{\cC}(\vect{\cM}_{\bK}^{n+1}).  
+    \vect{\cM}_{\bK}^{n+1}=\tilde{\vect{\cM}}_{\bK}^{n+1}+\hat{\alpha}\,\vect{\cD}\,\vect{\cC}(\vect{\cM}_{\bK}^{n+1}).  
   \end{equation*}
@@
 \begin{theorem}
-  Let
+  Suppose that
+  \begin{itemize}
+    \item[1.] For all $k\in\{1,\ldots,d\}$, the Gauss-Lobatto quadrature rule $\hat{Q}^{k}$ is chosen such that Eq.~\eqref{eq:quadratureRuleGL} holds.  
+    \item[2.] For all $k\in\{1,\ldots,d\}$ and all $\vect{x}\in\hat{\vect{S}}^{k}$, $\vect{\cM}_{h}^{n}(\vect{x})\in\cR$.
+    \item[3.] The time step $\dt$ is chosen such that Eq.~\eqref{eq:imexTimeStep} holds.  
+    \item[4.] If $\vect{\cM}_{\bK}^{(i)}\in\cR$, a limiter can be invoked to enforce $\vect{\cM}_{h}^{(i)}(\vect{x})\in\cR$ for all $\vect{x}\in\hat{\vect{S}}^{k}$ and all $k\in\{1,\ldots,d\}$.
+  \end{itemize}
+  Then $\vect{\cM}_{\bK}^{n+1}\in\cR$.  
+  \label{the:realizableDGIMEX}
 \end{theorem}
+\begin{proof}
+  For $i=1$, the cell average $\vect{\cM}_{\bK}^{(1)}$ is obtained by solving (cf. Eq.~\eqref{eq:imexStagesCellAverage})
+  \begin{equation*}
+    \vect{\cM}_{\bK}^{(1)}=c_{10}\,\vect{\cM}_{\bK}^{(10)}+a_{11}\,\f{\dt}{\tau}\big(\,\vect{\eta}-\vect{\cD}\,\vect{\cM}_{\bK}^{(1)}\,\big),
+  \end{equation*}
+  where, after invoking the quadrature rule $\tilde{\vect{Q}}^{k}$ to integrate over $\tilde{\bK}^{k}$ in Eq.~\eqref{eq:cellAverageInTermsOfGamma},
+  \begin{equation*}
+    \vect{\cM}_{\bK}^{(10)}
+    =\sum_{k=1}^{d}\f{\beta_{k}}{|\tilde{\bK}^{k}|}\tilde{\vect{Q}}^{k}\big(\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{n};\hat{c}_{10}\big]\big).  
+  \end{equation*}
+  Since $\vect{\cM}_{h}^{n}\in\cR$ on $\hat{\vect{S}}^{k}$, for each $k\in\{1,\ldots,d\}$, it follows from Lemma~\ref{lem:realizableGamma} that $\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{n};\hat{c}_{10}\big]\in\cR$ on $\tilde{\vect{S}}^{k}$.
+  Then, realizability of $\vect{\cM}_{\bK}^{(10)}$ follows from Lemma~\ref{lem:realizableMij}, while $\vect{\cM}_{\bK}^{(1)}\in\cR$ follows by invoking Lemma~\ref{lem:imexStagesCellAverage}.  
+  By invoking a realizability-enforcing limiter, $\vect{\cM}_{h}^{(1)}(\vect{x})\in\cR$ for all $\vect{x}\in\hat{\vect{S}}^{k}$ and all $k\in\{1,\ldots,d\}$.  
+  Repeated application of these steps give $\vect{\cM}_{\bK}^{(s)}\in\cR$.  
+  Since the IMEX scheme is GSA, it follows that $\tilde{\vect{\cM}}_{\bK}^{n+1}\in\cR$.  
+  The proof is completed by invoking Lemma~\ref{lem:imexCorrectionCellAverage}.  
+\end{proof}

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/appendix.tex
Modified the appendix: modified the consistency requirement and 2nd-order streaming requirement.

@@
  \text{(GSA)} \qquad\ &\tilde{w}_{i} = \tilde{a}_{3i}, \quad w_{i} = a_{3i}, ~\text{for} ~ i = 1,2,3\\
- \text{(2nd-order accuracy)} \qquad\ &\sum_{i=1}^{3}  \tilde{w}_{i} = 1, \quad \sum_{i=1}^{3}  \tilde{w}_{i}\tilde{c}_{i} = 1/2, \\
+ \text{(consistency)} \qquad\ & \sum_{i=1}^{3}  \tilde{w}_{i} = 1, \quad \sum_{i=1}^{3} w_{i} = 1\\ 
+ \text{(2nd-order streaming accuracy)} \qquad\ & \sum_{i=1}^{3}  \tilde{w}_{i}\tilde{c}_{i} = 1/2, \\
  \text{(positivity-preserving)} \qquad & a_{ii} > 0, c_{i0} \geq 0, \tilde{c}_{i0} \geq 0, ~\text{for} ~ i = 2,3 \\
@@
 \end{equation*}
+The consistency of the discrete system to the continuous system requires
+\begin{align}
+ \tilde{a}_{31} + \tilde{a}_{32} = 1, \quad \quad a_{31} + a_{32} + a_{33} = 1.
+ \label{eq:1stOrderGeneral}
+\end{align}
 The second-order in the streaming limit requires
 \begin{align}
-\tilde{a}_{31} + \tilde{a}_{32} = 1, \quad \tilde{a}_{32}\cdot \tilde{a}_{21} =  \frac{1}{2}.
-\end{align}
-An implicit property, the first-order in general transport condition, requires
-\begin{align}
- \quad a_{31} + a_{32} + a_{33} = 1.
- \label{eq:1stOrderGeneral}
+\tilde{a}_{32}\cdot \tilde{a}_{21} =  \frac{1}{2}.
 \end{align}
@@
 \end{align}
-Substituting Eq.~\eqref{eq:1stOrderGeneral} into Eq.~\eqref{eq:diffusionAccurate} gives
+Substituting the second equation in Eq.~\eqref{eq:1stOrderGeneral} into Eq.~\eqref{eq:diffusionAccurate} gives
 \begin{align}

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Changes due to comments from Tony and Cory.  Work on IMEX section

@@
 Algebraic moment closures for the two-moment model are computationally efficient as they provide the Eddington factor in Eq.~\eqref{eq:eddingtonTensor} in closed form as a function of the density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$.
-For this reason they are widely used in applications where radiation transport plays an important role --- including simulation of neutrino transport in core-collapse supernovae \cite{roberts_etal_2016} and compact binary mergers \cite{foucart_etal_2015}.
+For this reason they are used in applications where transport plays an important role, but where limited computational resources precludes the use of higher fidelity models --- including simulation of neutrino transport in core-collapse supernovae \cite{roberts_etal_2016} and compact binary mergers \cite{foucart_etal_2015}.
 Algebraic moment closures in the context of these aforementioned applications have also been discussed elsewhere (e.g., \cite{janka_etal_1992,pons_etal_2000,smit_etal_2000,just_etal_2015,murchikova_etal_2017}).
@@
 \end{equation}
-where the \emph{closure function} $\Theta(x)$ varies with the specifics of the closure procedure.  
+where the \emph{closure function} $\Theta(x)$ depends on the specifics of the closure procedure.  
 We will consider two basic closure procedures in more detail below: the maximum entropy (ME) closure and the Kershaw (K) closure.
 
-\paragraph{Low Occupancy Limit}
-We note in passing that in the low occupancy limit ($\cJ\ll1$), the Eddington factor in Eq.~\eqref{eq:eddingtonFactor} depends solely on $h$; i.e.,
+In the low occupancy limit ($\cJ\ll1$), the Eddington factor in Eq.~\eqref{eq:eddingtonFactor} depends solely on $h$; i.e.,
 \begin{equation}
@@
 
-For the two-moment model, the ME closure constructs the least biased angular distribution based on the limited information available (i.e., $\cJ$ and $\vect{\cH}$) \cite{cernohorskyBludman_1994,lareckiBanach_2011}.
+For the two-moment model, the ME closure attempts to construct the angular distribution based on the limited information available (i.e., $\cJ$ and $\vect{\cH}$) \cite{cernohorskyBludman_1994,lareckiBanach_2011}.
 The ME distribution $f_{\mbox{\tiny ME}}(\omega)$ is found by maximizing the entropy functional, which for particles obeying Fermi-Dirac statistics is given by
@@
 \end{equation}
-From the variation of the entropy functional in Eq.~\eqref{eq:entropyFunctional} with respect to $f_{\mbox{\tiny ME}}$, and introducing Lagrange multipliers ($a$ and $\vect{b}$) to enforce the constraints in Eq.~\eqref{eq:closureConstraints}, the ME distribution takes the general form
+From the variation of the entropy functional in Eq.~\eqref{eq:entropyFunctional} with respect to $f_{\mbox{\tiny ME}}$ and introducing Lagrange multipliers ($a$ and $\vect{b}$) to enforce the constraints in Eq.~\eqref{eq:closureConstraints}, the ME distribution takes the general form \cite{cernohorskyBludman_1994}
 \begin{equation}
@@
 Specification of $a$ and $\vect{b}$ from $\vect{\cM}=(\cJ,\vect{\cH})^{T}$ gives $f_{\mbox{\tiny ME}}$, and any number of moments can in principle be computed.  
-Importantly, we note that for the maximum entropy problem to be soluble, we must have $\vect{\cM}\in\cR$ \cite{lareckiBanach_2011}.
+Importantly, for the maximum entropy problem to be solvable, we must have $\vect{\cM}\in\cR$ \cite{lareckiBanach_2011}.
 
-To arrive at the algebraic form of the ME closure, Chernohorsky \& Bludman \cite{cernohorskyBludman_1994} postulate (but see \cite{lareckiBanach_2011}) that, as a function of the so-called flux saturation $x=h/(1-\cJ)$, the closure function $\Theta(x)$ is independent of $\cJ$ and can be written explicitly in terms of the inverse Langevin function.
+To arrive at an algebraic form of the ME closure, Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} postulate (but see \cite{lareckiBanach_2011}) that, as a function of the flux saturation
+\begin{equation}
+  x := h/(1-\cJ),
+  \label{eq:fluxSaturation}
+\end{equation} 
+the closure function $\Theta(x)$ is independent of $\cJ$ and can be written explicitly in terms of the inverse Langevin function.  
 To avoid inverting the Langevin function for $\Theta(x)$, they provide a polynomial fit (accurate to $2\%$) given by
@@
 
-We also note that using the closure function given by Eq.~\eqref{eq:closureMECB} with the low occupancy Eddington factor in Eq~\eqref{eq:eddingtonFactorLow} results in the algebraic maximum entropy closure attributed to Minerbo \cite{minerbo_1978}, which is currently in widespread use in simulation of neutrino (fermion) transport in the aforementioned nuclear astrophysics applications.
+We also note that using the closure function given by Eq.~\eqref{eq:closureMECB} with the low occupancy Eddington factor in Eq~\eqref{eq:eddingtonFactorLow} results in the algebraic maximum entropy closure attributed to Minerbo \cite{minerbo_1978}, which is currently in use in simulation of neutrino (fermion) transport in the aforementioned nuclear astrophysics applications.
 In a recent comparison of algebraic (or analytic) closures for the two-moment model applied to neutrino transport around proto-neutron stars, Murchikova et al.
@@
    \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.01$ (upper left panel), $\cJ=0.4$ (upper right panel), $\cJ=0.6$ (lower left panel), and $\cJ=0.99$ (lower right panel).
-In each panel we plot the Eddington factors of Kershaw (solid blue lines), Chernohorsky \& Bludman (CB, solid red lines), Banach \& Larecki (BL, dashed orange lines), and Minerbo (dash-dot purple lines).
+In each panel we plot the Eddington factors of Kershaw (solid blue lines), Cernohorsky \& Bludman (CB, solid red lines), Banach \& Larecki (BL, dashed orange lines), and Minerbo (dash-dot purple lines).
 We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ (lower and upper solid black lines, respectively).}
@@
   \end{tabular}
-   \caption{Illustration of $\vect{\cM}_{ab}$, as defined in Lemma~\ref{lem:explicitStep}, computed with different algebraic closures: the maximum entropy closures of Banach \& Larecki (top left) and Chernohorsky \& Bludman (top right), the Kershaw closure (bottom left), and the maximum entropy closure of Minerbo (bottom right).
+   \caption{Illustration of $\vect{\cM}_{ab}$, as defined in Lemma~\ref{lem:explicitStep}, computed with different algebraic closures: the maximum entropy closures of Banach \& Larecki (top left) and Cernohorsky \& Bludman (top right), the Kershaw closure (bottom left), and the maximum entropy closure of Minerbo (bottom right).
 In each panel, $\vect{\cM}_{ab}$ was computed using the respective closure, using $10^{6}$ random pairs ($\vect{\cM}_{a},\vect{\cM}_{b}\in\cR$), and plotted as a light-blue point.

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/appendix.tex
Changes due to comments from Tony and Cory.  Work on IMEX section

@@
 
+For the analysis of positivity-preserving IMEX schemes, additional coefficients are defined \cite{hu_etal_2018} (cf. Eq.~\eqref{eq:imexStagesRewrite}).  
+First, let
+\begin{equation}
+  b_{ii} = \f{1}{a_{ii}}, \quad
+  b_{ij} = -\f{1}{a_{ii}}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad
+  \tilde{b}_{ij} = -\f{1}{a_{ii}}\Big(\tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}\Big).  
+\end{equation}
+Then, for IMEX schemes of Type~A \cite{dimarcoPareschi2013},
+\begin{equation}
+  \begin{aligned}
+    c_{i0} &= 1-\sum_{j=1}^{i-1}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad &
+    c_{ij} &= \sum_{l=j}^{i-1}a_{il}b_{lj}, \\
+    \tilde{c}_{i0} &= 0, \quad &
+    \tilde{c}_{ij} &= \tilde{a}_{ij} + \sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}.
+  \end{aligned}
+\end{equation}
+while for IMEX schemes of Type~ARS \cite{ascher_etal_1997}
+\begin{equation}
+\begin{aligned}
+  c_{i0} &= 1-\sum_{j=2}^{i-1}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad &
+  c_{ij} &= \sum_{l=j}^{i-1}a_{il}b_{lj} \\
+  \tilde{c}_{i0} &= \tilde{a}_{i1}+\sum_{j=2}^{i-1}a_{ij}\tilde{b}_{j1}, \quad &
+  \tilde{c}_{ij} &= \tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}.  
+\end{aligned}
+\end{equation}
+
 \paragraph{IMEX PA2}
@@
 For this scheme, the non-zero components of $\tilde{A}$ and $A$ are given by
-\begin{align}
-  \tilde{a}_{21} &= 0.7369502715, \nonumber \\
-  \tilde{a}_{31} &= 0.3215281691, \quad \tilde{a}_{32} = 0.6784718309, \nonumber \\
-  a_{11} &= 0.6286351712, \nonumber \\
-  a_{21} &= 0.2431004655, \quad a_{22} = 0.1959392570, \nonumber \\
-  a_{31} &= 0.4803651051, \quad a_{32} = 0.0746432814, \quad a_{33} = 0.4449916135. \nonumber
-\end{align}
+\begin{align*}
+  \tilde{a}_{21} &= 0.7369502715, \\
+  \tilde{a}_{31} &= 0.3215281691, \quad \tilde{a}_{32} = 0.6784718309, \\
+  a_{11} &= 0.6286351712, \\
+  a_{21} &= 0.2431004655, \quad a_{22} = 0.1959392570, \\
+  a_{31} &= 0.4803651051, \quad a_{32} = 0.0746432814, \quad a_{33} = 0.4449916135. 
+\end{align*}
 The coefficient in the correction step is $\alpha = 0.2797373792$ and the CFL constant is $c_{sch} = 0.5247457524$.
@@
 We have found another second-order accurate, positivity-preserving IMEX scheme of type $A$, which we refer to as IMEX PA2+.  
-This scheme allows for has a larger $c_{sch}$ than IMEX PA2 (i.e., a larger time step while still maintaining positivity).  
-The scheme chosen from random sampling of the IMEX parameter space, and was the scheme with the largest $c_{sch}$ that satisfied both the order conditions for second order accuracy and possessed the positivity-preserving property.
-For IMEX PA2+, ($c_{sch} = 0.895041066934$). 
+This scheme allows for has a larger $c_{\mbox{\tiny Sch}}$ than IMEX PA2 (i.e., a larger time step while maintaining positivity).  
+The scheme was found by random sampling of the parameter space spanned by the IMEX coefficients, optimizing $c_{\mbox{\tiny Sch}}$.  
+For IMEX PA2+, $c_{\mbox{\tiny Sch}} = 0.895041066934$. 
 The non-zero components of $\tilde{A}$ and $A$ are given by
-\begin{align}
-  \tilde{a}_{21} &= 0.909090909090909, \nonumber \\
-  \tilde{a}_{31} &= 0.450000000000000, \quad \tilde{a}_{32} = 0.550000000000000, \nonumber \\
-  a_{11} &= 0.521932391842510, \nonumber \\
-  a_{21} &= 0.479820781424967, \quad a_{22} = 0.002234534340252, \nonumber \\
-  a_{31} &= 0.499900000000000, \quad a_{32} = 0.001100000000000, \quad a_{33} = 0.499000000000000. \nonumber
-\end{align}
+\begin{align*}
+  \tilde{a}_{21} &= 0.909090909090909, \\
+  \tilde{a}_{31} &= 0.450000000000000, \quad \tilde{a}_{32} = 0.550000000000000, \\
+  a_{11} &= 0.521932391842510, \\
+  a_{21} &= 0.479820781424967, \quad a_{22} = 0.002234534340252, \\
+  a_{31} &= 0.499900000000000, \quad a_{32} = 0.001100000000000, \quad a_{33} = 0.499000000000000.
+\end{align*}
 The coefficient in the correction step is $\alpha = 0.260444263529413$.  
@@
 
+The rest of the IMEX schemes we consider here do not include the correction step in Eq.~\eqref{eq:imexCorrection}; i.e., $\alpha=0$.
+
 \paragraph{IMEX PC2}
 
-Another positivity-preserving IMEX scheme was given in \cite{mcclarren_etal_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclarren_etal_2008}).  
+Another IMEX scheme was given in \cite{mcclarren_etal_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclarren_etal_2008}).  
 This scheme can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
 The non-zero components of $\tilde{A}$ and $A$ are given by
-\begin{align}
-  \tilde{a}_{21} &= 0.5, \quad \tilde{a}_{32} = 1, \nonumber \\
-  a_{22} &= 0.5, \quad a_{33} = 1.0. \nonumber
-\end{align}
-And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.
+\begin{align*}
+  \tilde{a}_{21} &= 0.5, \quad \tilde{a}_{32} = 1, \\
+  a_{22} &= 0.5, \quad a_{33} = 1.0,
+\end{align*}
+$\alpha=0$, and $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.
 
@@
 
-We have found a second-order accurate in the streaming limit, diffusion accurate, positivity-preserving IMEX scheme of type $ARS$, which we refer to as IMEX PARSD.  
-This scheme allows for has a $c_{sch}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.
+We have found diffusion accurate, positivity-preserving IMEX schemes of type ARS that are second-order accurate in the streaming limit, which we refer to as IMEX PARSD; see \ref{app:PARSD}.  
+For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.
 Here we give an example by setting $\epsilon=0.1$.
-\begin{align}
-  \tilde{a}_{21} & = 1.0, \nonumber \\
-  \tilde{a}_{31} & = 0.5, \quad \tilde{a}_{32} = 0.5, \nonumber \\
+\begin{align*}
+  \tilde{a}_{21} & = 1.0, \\
+  \tilde{a}_{31} & = 0.5, \quad \tilde{a}_{32} = 0.5, \\
   a_{22} & = 1.0, \nonumber \\
-  a_{32} & = 0.4 \,( = 0.5 - \epsilon\,), \quad a_{33} = 0.6 \,( = 0.5 + \epsilon\,). \nonumber
-\end{align} 
-This scheme is also GSA and needs only two compute for implicit terms each time-step.
+  a_{32} & = 0.4 \,( = 0.5 - \epsilon\,), \quad a_{33} = 0.6 \,( = 0.5 + \epsilon\,). 
+\end{align*}
+This scheme is GSA, $\alpha=0$, and requires only two implicit solves per time step.
 
@@
 The non-zero components of $\tilde{A}$ and $A$ are given by
-\begin{align}
-  \tilde{a}_{21} &= 2/5, \quad \tilde{a}_{32} = 1, \nonumber \\
+\begin{align*}
+  \tilde{a}_{21} &= 2/5, \quad \tilde{a}_{32} = 1, \\
   a_{22} &= 2/5, \nonumber \\
-  a_{32} &= 5/6, \quad a_{33} = 1/6. \nonumber
-\end{align}
-And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
+  a_{32} &= 5/6, \quad a_{33} = 1/6,
+\end{align*}
+$\alpha=0$, and $w_{i} = a_{3i} = \tilde{w}_{i}$ (stiffly accurate \cite{pareschiRusso_2005}).
 
@@
 
-The second scheme we use for comparison is the second-order accurate IMEX scheme given in \cite{pareschiRusso_2005}.  
+Another scheme we use for comparison is the second-order accurate IMEX scheme given in \cite{pareschiRusso_2005}.  
 We refer to this scheme as IMEX SSP2332.  
 The non-zero components of $\tilde{A}$ and $A$ are given by
-\begin{align}
-  \tilde{a}_{21} &= 1/2, \nonumber \\
-  \tilde{a}_{31} &= 1/2, \quad \tilde{a}_{32} = 1/2, \nonumber \\
-  a_{11} &= 1/4, \nonumber \\
-  a_{22} &= 1/4, \nonumber \\
-  a_{31} &= 1/3, \quad a_{32} = 1/3, \quad a_{33} = 1/3. \nonumber
-\end{align}
-And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
+\begin{align*}
+  \tilde{a}_{21} &= 1/2, \\
+  \tilde{a}_{31} &= 1/2, \quad \tilde{a}_{32} = 1/2, \\
+  a_{11} &= 1/4, \\
+  a_{22} &= 1/4, \\
+  a_{31} &= 1/3, \quad a_{32} = 1/3, \quad a_{33} = 1/3, 
+\end{align*}
+$\alpha=0$, and $w_{i} = a_{3i} = \tilde{w}_{i}$ (stiffly accurate).
 
@@
 \section{Proof of nonexistence of 3-stage Type A ...}
+\label{app:noTypeA}
 

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/imex.tex
Changes due to comments from Tony and Cory.  Work on IMEX section

--- 2018-06-05 Documents/M1/realizableFermionicM1/sections/imex.tex
@@
 Furthermore, we would like to employ IMEX schemes that preserve realizability of the moments --- subject only to a time step governed by the explicit transport operator, and comparable to the time step required for numerical stability of the explicit scheme.
-(The realizability-preserving and positivity-preserving properties of an IMEX scheme are intimately related, and we use two phrases interchangeably.)  
+(The realizability-preserving and positivity-preserving properties of an IMEX scheme are intimately related, and we use the two phrases interchangeably.)  
 Until recently, high-order (second or higher order temporal accuracy) positivity-preserving IMEX methods with time step restrictions solely due to the transport operator were not known.  
@@
 \end{equation}
-where $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$.
-Such that, $c_{i0} = 1 - \sum_{j=1}^{i-1}c_{ij}$, $c_{ij} = \sum_{l=j}^{i-1}a_{il}b_{lj}$, $\tilde{c}_{i0} = \tilde{a}_{i1} + \sum_{j=2}^{i-1} a_{ij}\tilde{b}_{j1}$,$\tilde{c}_{ij} = \tilde{a}_{ij} + \sum_{l=j+1}^{i-1} a_{il}\tilde{b}_{lj}$ $b_{ij} = - \frac{1}{a_{ii}} \sum_{l = j}^{i-1}a_{il}b_{lj}$, $b_{ii} = \frac{1}{a_{ii}}$, $\tilde{b}_{ij} = \frac{1}{a_{ii}}\big( -\tilde{a}_{ij} - \sum_{l = j+1}^{i-1}a_{il}\tilde{b}_{lj}\big)$.
-(In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.)  
-Two types of IMEX schemes are considered: \emph{type~A} \cite{pareschiRusso_2005} and \emph{type~ARS} \cite{ascher_etal_1997}.  
+where $c_{ij}$, and $\hat{c}_{ij}=\tilde{c}_{ij}/c_{ij}$ are computed from $\tilde{a}_{ij}$ and $a_{ij}$ (see \ref{app:butcherTables}).  
+In Eq.~\eqref{eq:imexStagesRewrite}, $\vect{u}^{(0)}=\vect{u}^{n}$.  
+Two types of IMEX schemes are considered: \emph{type~A} \cite{pareschiRusso_2005,dimarcoPareschi2013} and \emph{type~ARS} \cite{ascher_etal_1997}.  
 For IMEX schemes of type~A, the matrix $A$ is invertible.  
@@
 For type A schemes, the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.  
-For type ARS schemes, the positivity follows from requiring $a_{ii}>0$ and $c_{i0},\tilde{c}_{i0}\ge0$ for $i=2,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$ for $i=3,\ldots,s$, $j=2,\ldots,i-1$.  
+For type ARS schemes, positivity follows from requiring $a_{ii}>0$ and $c_{i0},\tilde{c}_{i0}\ge0$ for $i=2,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$ for $i=3,\ldots,s$, $j=2,\ldots,i-1$.  
 Such coefficients were given in \cite{hu_etal_2018} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
@@
 
-Importantly, the coefficients $c_{ij}$ in Eq.~\eqref{eq:imexStagesRewrite} satisfy $\sum_{j=0}^{i-1}c_{ij}=1$, which implies the so-called Shu-Osher form.  
-Thus, if the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} --- which is in the form of a forward Euler update with time step $\hat{c}_{ij}\,\dt$ --- is positive for all $i=1,\ldots,s$, $j=0,\ldots,i-1$, positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
+Importantly, the coefficients $c_{ij}$ in Eq.~\eqref{eq:imexStagesRewrite} satisfy $\sum_{j=0}^{i-1}c_{ij}=1$, which implies the so-called Shu-Osher form of the explicit part \cite{shuOsher_1988}.  
+If the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} --- which is in the form of a forward Euler update with time step $\hat{c}_{ij}\,\dt$ --- is positive for all $i=1,\ldots,s$, $j=0,\ldots,i-1$, positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
 Thus, if the explicit update with the transport operator is positive for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is positivity-preserving for a time step $\dt\le c_{\mbox{\tiny Sch}}\,\dt_{\mbox{\tiny Ex}}$, where
@@
 It is desirable to make $c_{\mbox{\tiny Sch}}$ as large (close to $1$) as possible.  
-(Positivity of $\vect{u}^{(i)}$ also requires the implicit solve to preserve positivity.)  
+Note that positivity of $\vect{u}^{(i)}$ also requires the implicit solve (equivalent to implicit Euler) to preserve positivity.  
 In \cite{hu_etal_2018}, Hu et al. provide examples of GSA, positivity-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
-In \ref{app:butcherTables}, we provide another example of a GSA, positivity-preserving IMEX scheme of type A (scheme PA2+), with a significantly larger $c_{\mbox{\tiny Sch}}$ (a factor of about $1.7$ larger).
+In \ref{app:butcherTables}, we provide another example of a GSA, positivity-preserving IMEX scheme of type A (scheme PA2+), with a larger $c_{\mbox{\tiny Sch}}$ (a factor of about $1.7$ larger).
 
@@
 \cite{chertock_etal_2015}, where the transport operator is included in the correction step, and found it to perform very well in the diffusion limit.
-However, we have not been able to prove sufficiently general realizability-preserving properties with this approach, without invoking a too severe time step restriction.  
+However, we have not been able to prove the realizability-preserving property with this approach without invoking a too severe time step restriction.  
 We therefore proceed to design positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
 We limit the scope to IMEX schemes of type~ARS.  
-(It can be shown that IMEX schemes of type~A satisfying the conditions we list below Eq.~\eqref{eq:orderConditionsEx} do not exist.)
+(It can be shown that IMEX schemes of type~A conforming to Definition~\ref{def:DIMEXP} below do not exist; cf. \ref{app:noTypeA}.)
 
@@
   \quad\text{and}\quad
-  \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2}.  
+  \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2},
   \label{eq:orderConditionsEx}
 \end{equation}
-We then seek to design GSA IMEX schemes of Type~ARS with the following properties
+where the first condition (consistency condition) is required for first-order accuracy.  
+We then seek to design GSA IMEX schemes of Type~ARS conforming to the following definition
+\begin{define}
+  A diffusion accurate, positivity-preserving IMEX scheme satisfies the following properties
   \begin{itemize}
@@
   \end{itemize}
+  \label{def:DIMEXP}
+\end{define}
 Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PARSD; see \ref{app:PARSD} for details).
@@
 As can be seen from the figures, the absolute stability region of both schemes increases with increasing $|z_{2}|$.  
-For a given $|z_{2}|>0$, the stability region of PARSD is larger than that for PA2+.  
+For a given $|z_{2}|>0$, the stability region of PARSD is larger than that of PA2+.  
 In the linear case, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme ($|z_2| = 0$) fulfills the stability requirement for the IMEX scheme as whole ($|z_2| \geq 0$).

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added an additional step
Changes due to comments from Tony and Cory.  Work on IMEX section

@@
 \begin{define}
-  The realizable set $\cR$ for the fermion two-moment model is given by
+  For the fermion two-moment model, the realizable set is
   \begin{equation}
@@
 \begin{proof}
-  In order to prove that $\cR$ is convex, we must show that any convex combination of elements in $\cR$ also belongs to $\cR$.  
+  In order to prove that $\cR$ is convex, it is sufficient to show that any convex combination of elements in $\cR$ also belongs to $\cR$.  
   Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ be two arbitrary elements in $\cR$.  
@@
   \end{equation*}
-  Since $\theta,\cJ_{a},\cJ_{b}\in[0,1]$, we have $\cJ_{c} \in [0,1]$.  
-  It is straightforward to verify that $\gamma(\vect{\cM})$ is a concave function of $\bcM$ if $\cJ\in[0,1]$.
-  Then Jensen's inequality implies
+  Since $\cJ_{a},\cJ_{b}\in[0,1]$, it follows that $\cJ_{c} \in [0,1]$.  
+  Since $\cJ_{a},\cJ_{b}\in[0,1]$, it is straightforward to verify that
   \begin{equation*}
@@
 Figure~\ref{fig:RealizableSetFermionic} illustrates the geometry of the convex set $\cR$ in the $(\cH,\cJ)$-plane (light blue region).  
-The boundary of $\cR$, $\partial\cR$ (black curves), is given by $\gamma(\vect{\cM})=0$.  
+The boundary $\partial\cR$ (black curves) is given by $\gamma(\vect{\cM})=0$.  
 The realizable domain of positive distribution functions, $\cR^{+}$ (no upper bound on $f$), which is a convex cone defined by
@@
   \caption{Illustration of the realizable set $\cR$ (light blue region) defined in Eq.~\eqref{eq:realizableSet}.  
-  The black lines define the boundary of $\cR$, $\partial\cR$ ($\gamma(\vect{\cM}) = 0$), while the red lines indicate the boundary of the realizable set of positive distributions with no upper bound (light red region); cf.
-Eq.~\eqref{eq:realizableSetPositive}.}
+  The black lines define the boundary $\partial\cR$, while the red lines indicate the boundary of the realizable set $\cR^{+}$ (light red region) defined in Eq.~\eqref{eq:realizableSetPositive}.}
   \label{fig:RealizableSetFermionic}
@@
   \end{equation*}
-  where $f_{ab}(\omegaNu)=\theta\,f_{a}(\omegaNu)+(1-\theta)\,f_{b}(\omegaNu)$ and $\theta(\omegaNu)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omegaNu))/2\in[0,1]$.  
+  where $f_{ab}(\omegaNu)=\vartheta\,f_{a}(\omegaNu)+(1-\vartheta)\,f_{b}(\omegaNu)$ and $\vartheta(\omegaNu)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omegaNu))/2\in[0,1]$.  
   Then, since $f_{ab}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
@@
 \end{lemma}
-
 \begin{proof}
+  Solving for $\vect{\cM}_{b}$ gives $\vect{\cM}_{b} = \big(\vect{I}+\alpha\,\vect{\cD}\big)^{-1}\big(\vect{\cM}_{a}+\alpha\,\vect{\eta}\big)$.  
   The first component of $\vect{\cM}_{b}$ can be written as
-  \begin{equation}
+  \begin{equation*}
     \cJ_{b}=\f{1}{4\pi}\int_{\bbS}f_{b}(\omegaNu)\,d\omegaNu,
-  \end{equation}
-  where $f_{b}(\omegaNu)=\theta\,f_{a}(\omegaNu)+(1-\theta)\,f_{0}$ and $\theta=1/(1+\alpha\,\xi)\in[0,1]$.  
+  \end{equation*}
+  where $f_{b}(\omegaNu)=\zeta\,f_{a}(\omegaNu)+(1-\zeta)\,f_{0}$, $\zeta=1/(1+\alpha\,\xi)\in[0,1]$, and $f_{0}$ and $\xi$ are defined in Section~\ref{sec:model}.  
   Then, since $f_{b}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$, $\cJ_{b}\in[0,1]$.  

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/imex.tex
Modifications to definition of PD-IMEX

@@
 
-\subsection{Diffusion Accurate, Positivity-Preserving IMEX Schemes}
+\subsection{Positivity-Preserving, Diffusion Accurate IMEX Schemes}
 
@@
 where the first condition (consistency condition) is required for first-order accuracy.  
-We then seek to design GSA IMEX schemes of Type~ARS conforming to the following definition
+We then seek to design IMEX schemes of Type~ARS conforming to the following working definition
 \begin{define}
-  A diffusion accurate, positivity-preserving IMEX scheme satisfies the following properties
+  Let PD-IMEX be a consistent, positivity-preserving, diffusion accurate, and low-stage GSA IMEX scheme satisfying the following properties
   \begin{itemize}
+    \item Consistency of the implicit coefficients
+    \begin{equation*}
+      \sum_{i=1}^{s}w_{i}=1.
+    \end{equation*}
     \item Second-order in the streaming limit; i.e., satisfies Eq.~\eqref{eq:orderConditionsEx}.
+    \item Positivity-preserving (conditions given by \cite{hu_etal_2018}; with $c_{\mbox{\tiny Sch}}>0$).
     \item Well-behaved in the diffusion limit; i.e., satisfies Eq.~\eqref{eq:diffusionCondition}.
-    \item Positivity-preserving (conditions given by \cite{hu_etal_2018}; with $c_{\mbox{\tiny Sch}}>0$ and maximal).
     \item Few stages ($s\le3$).
+    \item Globally stiffly accurate (GSA)
+    \begin{equation*}
+      a_{si}=w_{i}\quad\text{and}\quad\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s.
+    \end{equation*}
   \end{itemize}

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
PARSD -> PD-ARS

@@
 \begin{rem}
-  For IMEX scheme PARSD (\ref{app:PARSD}), which does not invoke the correction step (i.e., $\alpha=0$), $\vect{\cM}_{\bK}^{n+1}=\vect{\cM}_{\bK}^{(s)}$.  
+  For IMEX scheme PD-ARS (\ref{app:PD-ARS}), which does not invoke the correction step (i.e., $\alpha=0$), $\vect{\cM}_{\bK}^{n+1}=\vect{\cM}_{\bK}^{(s)}$.  
 \end{rem}

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/appendix.tex
PARSD -> PD-ARS

@@
 
-\paragraph{IMEX PARSD}
+\paragraph{IMEX PD-ARS}
 
-We have found diffusion accurate, positivity-preserving IMEX schemes of type ARS that are second-order accurate in the streaming limit, which we refer to as IMEX PARSD; see \ref{app:PARSD}.  
+We have found diffusion accurate, positivity-preserving IMEX schemes of type ARS that are second-order accurate in the streaming limit, which we refer to as IMEX PD-ARS; see \ref{app:PD-ARS}.  
 For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.
@@
 \newpage 
-\section{Construction of PARSD}
-\label{app:PARSD}
+\section{Construction of PD-ARS}
+\label{app:PD-ARS}
 
@@
 A solution family is $x=\frac{1}{2}$, $y=\frac{1}{2} + \epsilon$ with $\epsilon \in [0, \frac{1}{2})$ and $c_{sch} = 1 - 2\epsilon$.
-The PARSD scheme follows.
+The PD-ARS scheme follows.
 It's clear that $\epsilon = 0$ and $c_{sch} = 1$ is the most optimized solution.

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/imex.tex
PARSD -> PD-ARS

@@
 \end{define}
-Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PARSD; see \ref{app:PARSD} for details).
+Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PD-ARS; see \ref{app:PD-ARS} for details).
 In the streaming limit, this scheme is identical to the optimal second-order accurate strong-stability preserving Runge-Kutta method \cite{gottlieb_etal_2001}.  
@@
 Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclarren_etal_2008,radice_etal_2013}, and satisfies the positivity conditions, but $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).
-In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PARSD is comparable to the accuracy of scheme PC2.
+In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PD-ARS is comparable to the accuracy of scheme PC2.
 
@@
 
-Here we analyze the absolute stability of the proposed IMEX schemes, PA2+ and PARSD (given in \ref{app:butcherTables}), following \cite{hu_etal_2018}.  
+Here we analyze the absolute stability of the proposed IMEX schemes, PA2+ and PD-ARS (given in \ref{app:butcherTables}), following \cite{hu_etal_2018}.  
 As is commonly done, we do this in the context of the linear scalar equation
@@
 Stability of the IMEX scheme requires $|P(z_1,z_2)|\leq 1$.  
-The stability regions of PA2+ and PARSD are plotted in Figure~\ref{fig:AbsoluteStability}.  
+The stability regions of PA2+ and PD-ARS are plotted in Figure~\ref{fig:AbsoluteStability}.  
 As can be seen from the figures, the absolute stability region of both schemes increases with increasing $|z_{2}|$.  
-For a given $|z_{2}|>0$, the stability region of PARSD is larger than that of PA2+.  
+For a given $|z_{2}|>0$, the stability region of PD-ARS is larger than that of PA2+.  
 In the linear case, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme ($|z_2| = 0$) fulfills the stability requirement for the IMEX scheme as whole ($|z_2| \geq 0$).
-This conclusion is valid for all PARSD schemes with $\epsilon\in [0,0.5)$.
+This conclusion is valid for all PD-ARS schemes with $\epsilon\in [0,0.5)$.
 \begin{figure}[h]
@@
   \end{tabular}
-   \caption{Boundary of the absolute stability region for different values of $z_2$ for PARSD with $\epsilon = 0.1$ (left panel) and PA2+ (right panel).}
+   \caption{Boundary of the absolute stability region for different values of $z_2$ for PD-ARS with $\epsilon = 0.1$ (left panel) and PA2+ (right panel).}
   \label{fig:AbsoluteStability}

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/numerical.tex
PARSD -> PD-ARS

@@
 For all tests in this subsection, we use third order accurate spatial discretization (polynomials of degree $k=2$) and we employ the maximum entropy closure in the low occupancy limit (i.e., the Minerbo closure).
-We compare results obtained using IMEX schemes proposed here (PA2+ and PARSD) with IMEX schemes from Hu et al.
+We compare results obtained using IMEX schemes proposed here (PA2+ and PD-ARS) with IMEX schemes from Hu et al.
 \cite{hu_etal_2018} (PA2), McClarren et al.
@@
 Eq.~\eqref{eq:errorNormAbsolute}) versus number of elements $N$ for the streaming sine wave test.
-Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), PA2 (red), PA2+ (purple), PC2 (blue), RKCB2 (dark green), SSP2332 (green), and PARSD (light red circles).
+Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), PA2 (red), PA2+ (purple), PC2 (blue), RKCB2 (dark green), SSP2332 (green), and PD-ARS (light red circles).
 Black dash-dot reference lines are proportional to $N^{-1}$ (top), $N^{-2}$ (middle), and $N^{-3}$ (bottom), respectively.}
@@
 For $\sigma_{\Ab}=0.1$, SSP2332 is the most accurate among these schemes, while PA2+ is the most accurate for $\sigma_{\Ab}=10$.  
-On the other hand, PC2 and PARSD are indistinguishable and display at most first-order accurate convergence, as expected.  
-(For $\sigma_{\Ab}=0.1$, PC2 and PARSD are the most accurate schemes for $N=8$ and $N=16$.)
+On the other hand, PC2 and PD-ARS are indistinguishable and display at most first-order accurate convergence, as expected.  
+(For $\sigma_{\Ab}=0.1$, PC2 and PD-ARS are the most accurate schemes for $N=8$ and $N=16$.)
 
@@
 Errors for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.
-The IMEX schemes employed are: PA2 (triangles pointing left), PA2+ (triangles pointing right), PC2 (asterisk), RKCB2 ($\times$), SSP2332 ($+$), and PARSD (circles).
+The IMEX schemes employed are: PA2 (triangles pointing left), PA2+ (triangles pointing right), PC2 (asterisk), RKCB2 ($\times$), SSP2332 ($+$), and PD-ARS (circles).
 Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
@@
 Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.
-The IMEX schemes employed are: PA2 (triangle pointing left), PA2+ (triangle pointing right), PC2 (asterisk), RKCB2 (cross), SSP2332 (plus), and PARSD (circle).
+The IMEX schemes employed are: PA2 (triangle pointing left), PA2+ (triangle pointing right), PC2 (asterisk), RKCB2 (cross), SSP2332 (plus), and PD-ARS (circle).
 Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
@@
 (Scheme PC2 has been shown to work well for this test \cite{radice_etal_2013}, but is included here for comparison with the other IMEX schemes.)
-Schemes PARSD, RKCB2, and SSP2332 are accurate for this test, and display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$.  
+Schemes PD-ARS, RKCB2, and SSP2332 are accurate for this test, and display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$.  
 For $\sigma=10^{2}$, the errors do not drop below $10^{-6}$ because of differences between the two-moment model and the diffusion equation used to obtain the analytic solution.  
@@
 We compute until $t=5$, when the system has reached an approximate steady state.  
-We use the IMEX scheme PARSD --- the least compute-intensive of the realizability-preserving IMEX schemes presented here --- in all the tests.  
+We use the IMEX scheme PD-ARS --- the least compute-intensive of the realizability-preserving IMEX schemes presented here --- in all the tests.  
 The main purpose of this test is to compare the results obtained using the different algebraic closures discussed in Section~\ref{sec:algebraicClosure}.

### 2018-06-22 Documents/M1/realizableFermionicM1/sections/appendix.tex
Reworked Appendix B

@@
   \end{aligned}
+  \label{eq:positivityCoefficientsA}
 \end{equation}
@@
   \end{aligned}
+  \label{eq:positivityCoefficientsARS}
 \end{equation}
@@
 \newpage 
-\section{Construction of PD-ARS}
+\section{Construction of IMEX Scheme PD-ARS}
 \label{app:PD-ARS}
 
-It can be shown that no 2-stage positivity-preserving IMEX exist \cite{hu_etal_2018}.
-Hence we considered 3-stage IMEX scheme.
-There are two kinds of implicit DIRK scheme, Type A and Type ARS.
-Here we discuss the simpler case, Type ARS, first.
-The Butcher tableau for ARS type IMEX scheme is
+Here we construct a three-stage PD-IMEX scheme of Type~ARS, conforming to Definition~\ref{def:PD-IMEX}.  
+We refer to the resulting IMEX scheme as PD-ARS.  
+The double Butcher tableau is
 \begin{equation}
@@
   	\tilde{c}_{3} & \tilde{a}_{31} & \tilde{a}_{32} & 0                    \\ \hline
-  	                     & \tilde{w}_{1} & \tilde{w}_{2} & \tilde{w}_{3}
+  	                   & \tilde{a}_{31} & \tilde{a}_{32} & 0
   \end{array}
@@
   	c_{3} & 0 & a_{32} & a_{33}       \\ \hline
-  	             & w_{1} & w_{2} & w_{3}
-  \end{array}.
+  	         & 0 & a_{32} & a_{33}
+  \end{array}
 \end{equation}
-The properties a desired IMEX scheme should have are: 2nd-order accurate in the streaming, globally stiffly accurate, positivity-preserving, diffusion accurate and an affordable time-step restriction.
-Then the problem that find such a scheme can be rewritten as an optimization problem:\\
-Find $(\tilde{a}_{21}, \tilde{a}_{31}, \tilde{a}_{32}, \tilde{w}_{1}, \tilde{w}_{2}, \tilde{w}_{3}, a_{22}, a_{32}, a_{33}, w_{1}, w_{2}, w_{3})$ such that
-\begin{align*}
-\text{maximize} ~ c_{sch} = &\min \{ \dfrac{c_{20}}{\tilde{c}_{20}}, \dfrac{c_{30}}{\tilde{c}_{30}}, \dfrac{c_{32}}{\tilde{c}_{32}}\}\\
- \text{under these constraints:} \qquad & \\
- \text{(GSA)} \qquad\ &\tilde{w}_{i} = \tilde{a}_{3i}, \quad w_{i} = a_{3i}, ~\text{for} ~ i = 1,2,3\\
- \text{(consistency)} \qquad\ & \sum_{i=1}^{3}  \tilde{w}_{i} = 1, \quad \sum_{i=1}^{3} w_{i} = 1\\ 
- \text{(2nd-order streaming accuracy)} \qquad\ & \sum_{i=1}^{3}  \tilde{w}_{i}\tilde{c}_{i} = 1/2, \\
- \text{(positivity-preserving)} \qquad & a_{ii} > 0, c_{i0} \geq 0, \tilde{c}_{i0} \geq 0, ~\text{for} ~ i = 2,3 \\
- & c_{32} \geq 0, \tilde{c}_{32} \geq 0, \\
- \text{(diffusion accurate)} \qquad & e^{T}_iA^{-1}\tilde{A}e = 1, ~\text{for} ~ i = 2,3, \\
- \text{(affordable)} \qquad & c_{sch} > 0.
-\end{align*}
-Imposing those equality constraints (including all the constraints exclude those from the positivity-preserving and affordable requirements), the Butcher tableau can be simplified as:
+The problem is then to find the coefficients $\{ \tilde{a}_{21}, \tilde{a}_{31}, \tilde{a}_{32}, a_{22}, a_{32}, a_{33} \}$ satisfying the constraints in Definition~\ref{def:PD-IMEX} while maximizing
+\begin{equation}
+  c_{\mbox{\tiny Sch}} = \min \Big\{\, \dfrac{c_{20}}{\tilde{c}_{20}},\, \dfrac{c_{30}}{\tilde{c}_{30}},\, \dfrac{c_{32}}{\tilde{c}_{32}} \,\Big\}.  
+\end{equation}
+%\begin{align*}
+%\text{maximize} ~ c_{sch} = &\min \{ \dfrac{c_{20}}{\tilde{c}_{20}}, \dfrac{c_{30}}{\tilde{c}_{30}}, \dfrac{c_{32}}{\tilde{c}_{32}}\}\\
+% \text{under these constraints:} \qquad & \\
+% \text{(GSA)} \qquad\ &\tilde{w}_{i} = \tilde{a}_{3i}, \quad w_{i} = a_{3i}, ~\text{for} ~ i = 1,2,3\\
+% \text{(consistency)} \qquad\ & \sum_{i=1}^{3}  \tilde{w}_{i} = 1, \quad \sum_{i=1}^{3} w_{i} = 1\\ 
+% \text{(2nd-order streaming accuracy)} \qquad\ & \sum_{i=1}^{3}  \tilde{w}_{i}\tilde{c}_{i} = 1/2, \\
+% \text{(positivity-preserving)} \qquad & a_{ii} > 0, c_{i0} \geq 0, \tilde{c}_{i0} \geq 0, ~\text{for} ~ i = 2,3 \\
+% & c_{32} \geq 0, \tilde{c}_{32} \geq 0, \\
+% \text{(diffusion accurate)} \qquad & e^{T}_iA^{-1}\tilde{A}e = 1, ~\text{for} ~ i = 2,3, \\
+% \text{(affordable)} \qquad & c_{sch} > 0.
+%\end{align*}
+Imposing the equality constraints (i.e., Eqs.~\eqref{eq:implicitConsistency}, \eqref{eq:orderConditionsEx}, and \eqref{eq:diffusionCondition}), the double Butcher tableau can be written in terms of two parameters ($x$ and $y$) as
 \begin{equation}
@@
   	             & 0 & 1-y          & y
-  \end{array}.
+  \end{array}
 \end{equation}
-And the rest inequalities and the problem were left to be: \\
-Find $(x,y)$ such that
-\begin{align*}
-\text{maximize} ~ c_{sch} = &\min \{ 2x, \dfrac{1-2x(1-y)}{y-x}, 2(1-y)\}\\
- \text{under these constraints:} \qquad & x > 0, ~ 1 \geq y > 0, \\
- & x \leq y, ~\dfrac{1}{2x} \geq 1-y.
-\end{align*}
-A solution family is $x=\frac{1}{2}$, $y=\frac{1}{2} + \epsilon$ with $\epsilon \in [0, \frac{1}{2})$ and $c_{sch} = 1 - 2\epsilon$.
-The PD-ARS scheme follows.
-It's clear that $\epsilon = 0$ and $c_{sch} = 1$ is the most optimized solution.
+Computing the relevant coefficients in Eq.~\eqref{eq:positivityCoefficientsARS}, we find $c_{20}=1$, $c_{30}=1-2x(1-y)$, $c_{32}=2x(1-y)$, $\tilde{c}_{20}=\f{1}{2x}$, $\tilde{c}_{30}=(y-x)$, and $\tilde{c}_{32}=(1-y)$, so that
+\begin{equation}
+  c_{\mbox{\tiny Sch}} = \min \Big\{\, 2x,\, \f{1-2x(1-y)}{y-x},\, 2(1-y) \,\Big\}.  
+\end{equation}
+The positivity-preserving property follows from imposing the inequality constraints $a_{22},a_{33}>0$, $c_{20},c_{30},c_{32}\ge0$, and $\tilde{c}_{20},\tilde{c}_{30},\tilde{c}_{32}\ge0$, which imply
+\begin{equation}
+  0 < x \le y
+  \quad\text{and}\quad
+  0 < y \le 1.
+\end{equation}
+We chose $x=\f{1}{2}$, so that the explicit part of the IMEX scheme is equivalent to the optimal second-order SSP-RK scheme in \cite{gottlieb_etal_2001} (SSPRK2 in \ref{app:butcherTables}).  
+Then, $y=\f{1}{2} + \epsilon$, where $\epsilon \in [0, \frac{1}{2})$ and $c_{\mbox{\tiny Sch}} = 1 - 2\epsilon$, results in the PD-ARS IMEX scheme.  
+Setting $\epsilon = 0$ gives the optimal scheme with $c_{\mbox{\tiny Sch}} = 1$.
+
+%It remains to find And the rest inequalities and the problem were left to be: \\
+%Find $(x,y)$ such that
+%\begin{align*}
+%\text{maximize} ~ c_{sch} = &\min \{ 2x, \dfrac{1-2x(1-y)}{y-x}, 2(1-y)\}\\
+% \text{under these constraints:} \qquad & x > 0, ~ 1 \geq y > 0, \\
+% & x \leq y, ~\dfrac{1}{2x} \geq 1-y.
+%\end{align*}
+%A solution family is $x=\frac{1}{2}$, $y=\frac{1}{2} + \epsilon$ with $\epsilon \in [0, \frac{1}{2})$ and $c_{sch} = 1 - 2\epsilon$.
+%The PD-ARS scheme follows.
+%It's clear that $\epsilon = 0$ and $c_{sch} = 1$ is the most optimized solution.
 

### 2018-06-27 Documents/M1/realizableFermionicM1/sections/appendix.tex
Some reworking on Appendix C, and some changes to imex.tex

@@
 
-%It remains to find And the rest inequalities and the problem were left to be: \\
-%Find $(x,y)$ such that
-%\begin{align*}
-%\text{maximize} ~ c_{sch} = &\min \{ 2x, \dfrac{1-2x(1-y)}{y-x}, 2(1-y)\}\\
-% \text{under these constraints:} \qquad & x > 0, ~ 1 \geq y > 0, \\
-% & x \leq y, ~\dfrac{1}{2x} \geq 1-y.
-%\end{align*}
-%A solution family is $x=\frac{1}{2}$, $y=\frac{1}{2} + \epsilon$ with $\epsilon \in [0, \frac{1}{2})$ and $c_{sch} = 1 - 2\epsilon$.
-%The PD-ARS scheme follows.
-%It's clear that $\epsilon = 0$ and $c_{sch} = 1$ is the most optimized solution.
+\clearpage
 
-\section{Proof of nonexistence of 3-stage Type A ...}
+\section{Nonexistence of a three-stage PD-IMEX Scheme of Type~A}
 \label{app:noTypeA}
 
-Proof of GSA IMEX schemes of Type~A with 3 stages and the following properties does not exist
-\begin{itemize}
-  \item Second-order in the streaming limit;
-  \item Well-behaved in the diffusion limit;
-  \item Positivity-preserving.
-\end{itemize}
-First of all, the GSA IMEX scheme of Type A with 3 stages have the following form:
+Here we prove that a PD-IMEX scheme (i.e., conforming to Definition~\ref{def:PD-IMEX}) of type~A does not exist.  
+First, for a three-stage, GSA IMEX scheme of type~A the double Butcher tableau is
 \begin{equation*}
@@
 \end{equation*}
-The consistency of the discrete system to the continuous system requires
+First we consider the equality constraints.  
+Consistency of the implicit coefficients and second-order accuracy in the streaming limit (Eqs.~\eqref{eq:implicitConsistency} and \eqref{eq:orderConditionsEx}, respectively) give
 \begin{align}
- \tilde{a}_{31} + \tilde{a}_{32} = 1, \quad \quad a_{31} + a_{32} + a_{33} = 1.
+  a_{31} + a_{32} + a_{33} = 1, \quad \tilde{a}_{31} + \tilde{a}_{32} = 1, \quad \text{and}\quad \tilde{a}_{32}\,\tilde{a}_{21} =  \f{1}{2}.
   \label{eq:1stOrderGeneral}
 \end{align}
-The second-order in the streaming limit requires
+Accuracy in the diffusion limit (Eq.~\eqref{eq:diffusionCondition}) requires 
 \begin{align}
-\tilde{a}_{32}\cdot \tilde{a}_{21} =  \frac{1}{2}.
-\end{align}
-The diffusion accurate Eq.~\eqref{eq:diffusionCondition} requires 
-\begin{align}
-\tilde{a}_{21} = a_{22}, \quad -\dfrac{a_{32} \tilde{a}_{21}}{a_{22}a_{33}} + \dfrac{1}{a_{33}} =1.
+  \tilde{a}_{21} = a_{22}
+  \quad\text{and}\quad 
+  -\f{a_{32} \tilde{a}_{21}}{a_{22}a_{33}} + \f{1}{a_{33}} =1.
 \label{eq:diffusionAccurate}
 \end{align}
-Substituting the second equation in Eq.~\eqref{eq:1stOrderGeneral} into Eq.~\eqref{eq:diffusionAccurate} gives
+The first constraint in Eq.~\eqref{eq:1stOrderGeneral} together with the constraints in Eq.~\eqref{eq:diffusionAccurate} gives
 \begin{align}
-\tilde{a}_{21} = a_{22}, \quad a_{31} = 0.
+  a_{31} = 0.
   \label{eq:a31is0}
 \end{align}
-Positivity-preserving requires
+The positivity-preserving property requires $a_{11}, a_{22}, a_{33}>0$ and the inequality constraints
 \begin{align*}
-& a_{11} > 0, ~ a_{22} >0, ~ a_{33}>0,\\
-& c_{20} = 1 - \frac{a_{21}}{a_{11}} \geq 0, ~ c_{30} = 1-\frac{a_{31}}{a_{11}} + \frac{a_{32}a_{21}}{a_{22}a_{11}} - \frac{a_{32}}{a_{22}}\geq 0, \\
-& c_{21} = \frac{a_{21}}{a_{11}} \geq 0, ~ c_{31} = \frac{a_{31}}{a_{11}} - \frac{a_{32}a_{21}}{a_{22}a_{11}} \geq 0, ~ c_{32} = \frac{a_{32}}{a_{22}} \geq 0,\\
-& \tilde{c}_{21} = \tilde{a}_{21} \geq 0, \tilde{c}_{31} = \tilde{a}_{31} - \frac{a_{32}\tilde{a}_{21}}{a_{22}} \geq 0, \tilde{c}_{32} = \tilde{a}_{32} \geq 0.
+  & c_{20} = 1 - \frac{a_{21}}{a_{11}} \geq 0, \quad c_{30} = 1-\frac{a_{31}}{a_{11}} + \frac{a_{32}a_{21}}{a_{22}a_{11}} - \frac{a_{32}}{a_{22}}\geq 0, \\
+  & c_{21} = \frac{a_{21}}{a_{11}} \geq 0, \quad c_{31} = \frac{a_{31}}{a_{11}} - \frac{a_{32}a_{21}}{a_{22}a_{11}} \geq 0, \quad c_{32} = \frac{a_{32}}{a_{22}} \geq 0,\\
+  & \tilde{c}_{21} = \tilde{a}_{21} \geq 0, \quad \tilde{c}_{31} = \tilde{a}_{31} - \frac{a_{32}\tilde{a}_{21}}{a_{22}} \geq 0, \quad \tilde{c}_{32} = \tilde{a}_{32} \geq 0.
 \end{align*}
-Note that since $a_{31} = 0$, $a_{21} \geq 0$, $a_{32} \geq 0$, $a_{22} > 0$ and $a_{11} >0$, $c_{31} \geq 0$ only holds for $c_{31} = 0$.
-Unfortunately, $c_{31} = 0$ will drag $c_{\mbox{\tiny Sch}} = 0$ since $c_{\mbox{\tiny Sch}} = \min \left\lbrace \dfrac{c_{21}}{\tilde{c}_{21}}, \dfrac{c_{31}}{\tilde{c}_{31}}, \dfrac{c_{32}}{\tilde{c}_{32}}\right\rbrace $.
-Therefore, GSA IMEX schemes of Type~A with 3 stages and the above properties does not exist.
+Since $a_{31} = 0$, we have
+\begin{equation*}
+  c_{31} = - \frac{a_{32}a_{21}}{a_{22}a_{11}}.  
+\end{equation*}
+Since $a_{21} \geq 0$, $a_{32} \geq 0$, $a_{22} > 0$ and $a_{11} >0$, we have $c_{31} \leq 0$, and the inequality constraints hold only for $c_{31} = 0$.
+Unfortunately, $c_{31} = 0$ gives $c_{\mbox{\tiny Sch}} = \min \Big\{\,\f{c_{21}}{\tilde{c}_{21}}, \f{c_{31}}{\tilde{c}_{31}}, \f{c_{32}}{\tilde{c}_{32}}\Big\} = 0$.
+Therefore, a three-stage PD-IMEX scheme (Definition~\ref{def:PD-IMEX}) of type~A does not exist.

### 2018-06-27 Documents/M1/realizableFermionicM1/sections/imex.tex
Reworked Appendix B
Some reworking on Appendix C, and some changes to imex.tex

@@
 We limit the scope to IMEX schemes of type~ARS.  
-(It can be shown that IMEX schemes of type~A conforming to Definition~\ref{def:DIMEXP} below do not exist; cf. \ref{app:noTypeA}.)
+(It can be shown that IMEX schemes of type~A conforming to Definition~\ref{def:PD-IMEX} below do not exist; cf. \ref{app:noTypeA}.)
 
@@
     \item Consistency of the implicit coefficients
-    \begin{equation*}
+    \begin{equation}
       \sum_{i=1}^{s}w_{i}=1.
-    \end{equation*}
+      \label{eq:implicitConsistency}
+    \end{equation}
     \item Second-order in the streaming limit; i.e., satisfies Eq.~\eqref{eq:orderConditionsEx}.
@@
   \end{itemize}
-  \label{def:DIMEXP}
+  \label{def:PD-IMEX}
 \end{define}
-Fortunately, IMEX schemes satisfying these properties are easy to find, and we provide an example with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PD-ARS; see \ref{app:PD-ARS} for details).
+Fortunately, IMEX schemes of type~ARS satisfying these properties are easy to find, and we provide an example with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PD-ARS; see \ref{app:PD-ARS} for details).
 In the streaming limit, this scheme is identical to the optimal second-order accurate strong-stability preserving Runge-Kutta method \cite{gottlieb_etal_2001}.  

### 2018-06-28 Documents/M1/realizableFermionicM1/sections/appendix.tex
Minor edits

@@
 
-\newpage 
 \section{Construction of IMEX Scheme PD-ARS}
@@
 \end{equation}
-%\begin{align*}
-%\text{maximize} ~ c_{sch} = &\min \{ \dfrac{c_{20}}{\tilde{c}_{20}}, \dfrac{c_{30}}{\tilde{c}_{30}}, \dfrac{c_{32}}{\tilde{c}_{32}}\}\\
-% \text{under these constraints:} \qquad & \\
-% \text{(GSA)} \qquad\ &\tilde{w}_{i} = \tilde{a}_{3i}, \quad w_{i} = a_{3i}, ~\text{for} ~ i = 1,2,3\\
-% \text{(consistency)} \qquad\ & \sum_{i=1}^{3}  \tilde{w}_{i} = 1, \quad \sum_{i=1}^{3} w_{i} = 1\\ 
-% \text{(2nd-order streaming accuracy)} \qquad\ & \sum_{i=1}^{3}  \tilde{w}_{i}\tilde{c}_{i} = 1/2, \\
-% \text{(positivity-preserving)} \qquad & a_{ii} > 0, c_{i0} \geq 0, \tilde{c}_{i0} \geq 0, ~\text{for} ~ i = 2,3 \\
-% & c_{32} \geq 0, \tilde{c}_{32} \geq 0, \\
-% \text{(diffusion accurate)} \qquad & e^{T}_iA^{-1}\tilde{A}e = 1, ~\text{for} ~ i = 2,3, \\
-% \text{(affordable)} \qquad & c_{sch} > 0.
-%\end{align*}
 Imposing the equality constraints (i.e., Eqs.~\eqref{eq:implicitConsistency}, \eqref{eq:orderConditionsEx}, and \eqref{eq:diffusionCondition}), the double Butcher tableau can be written in terms of two parameters ($x$ and $y$) as
@@
 \end{equation}
-Computing the relevant coefficients in Eq.~\eqref{eq:positivityCoefficientsARS}, we find $c_{20}=1$, $c_{30}=1-2x(1-y)$, $c_{32}=2x(1-y)$, $\tilde{c}_{20}=\f{1}{2x}$, $\tilde{c}_{30}=(y-x)$, and $\tilde{c}_{32}=(1-y)$, so that
+Computing the relevant coefficients in Eq.~\eqref{eq:positivityCoefficientsARS}, we find $c_{20}=1$, $c_{30}=1-2x(1-y)$, $c_{32}=2x(1-y)$, $\tilde{c}_{20}=\f{1}{2x}$, $\tilde{c}_{30}=(y-x)$, and $\tilde{c}_{32}=x$, so that
 \begin{equation}
@@
 
-\clearpage
-
-\section{Nonexistence of a three-stage PD-IMEX Scheme of Type~A}
+\section{Nonexistence of Three-Stage PD-IMEX Scheme of Type~A}
 \label{app:noTypeA}
@@
   \quad\text{and}\quad 
-  -\f{a_{32} \tilde{a}_{21}}{a_{22}a_{33}} + \f{1}{a_{33}} =1.
+  -\f{a_{32}\,\tilde{a}_{21}}{a_{22}\,a_{33}} + \f{1}{a_{33}} =1.
 \label{eq:diffusionAccurate}
@@
 \begin{align*}
-  & c_{20} = 1 - \frac{a_{21}}{a_{11}} \geq 0, \quad c_{30} = 1-\frac{a_{31}}{a_{11}} + \frac{a_{32}a_{21}}{a_{22}a_{11}} - \frac{a_{32}}{a_{22}}\geq 0, \\
-  & c_{21} = \frac{a_{21}}{a_{11}} \geq 0, \quad c_{31} = \frac{a_{31}}{a_{11}} - \frac{a_{32}a_{21}}{a_{22}a_{11}} \geq 0, \quad c_{32} = \frac{a_{32}}{a_{22}} \geq 0,\\
-  & \tilde{c}_{21} = \tilde{a}_{21} \geq 0, \quad \tilde{c}_{31} = \tilde{a}_{31} - \frac{a_{32}\tilde{a}_{21}}{a_{22}} \geq 0, \quad \tilde{c}_{32} = \tilde{a}_{32} \geq 0.
+  & c_{20} = 1 - \frac{a_{21}}{a_{11}} \geq 0, \quad c_{30} = 1-\frac{a_{31}}{a_{11}} + \frac{a_{32}\,a_{21}}{a_{22}\,a_{11}} - \frac{a_{32}}{a_{22}}\geq 0, \\
+  & c_{21} = \frac{a_{21}}{a_{11}} \geq 0, \quad c_{31} = \frac{a_{31}}{a_{11}} - \frac{a_{32}\,a_{21}}{a_{22}\,a_{11}} \geq 0, \quad c_{32} = \frac{a_{32}}{a_{22}} \geq 0,\\
+  & \tilde{c}_{21} = \tilde{a}_{21} \geq 0, \quad \tilde{c}_{31} = \tilde{a}_{31} - \frac{a_{32}\,\tilde{a}_{21}}{a_{22}} \geq 0, \quad \tilde{c}_{32} = \tilde{a}_{32} \geq 0.
 \end{align*}

### 2018-07-25 Documents/M1/realizableFermionicM1/sections/dg.tex
Minor correction from Cory

@@
 \end{equation}
-where superscripts $-/+$ in the arguments of $\vect{\cM}_{h}(x^{i,-/+},\tilde{\bx}^{i})$ indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
+where superscripts $-/+$ in the arguments of $\vect{\cM}_{h}$ indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
 In this paper we use the simple Lax-Friedrichs (LF) flux given by
@@
 \end{equation}
-where $\alpha^{i}=||\mbox{eig}\big(\partial\bcF^{i}/\partial\vect{\cM}\big)||_{\infty}$ is the largest eigenvalue (in absolute value) of the flux Jacobian.  
+where $\alpha^{i}$ is the largest eigenvalue (in absolute value) of the flux Jacobian $\partial\bcF^{i}/\partial\vect{\cM}$.  
 For particles propagating at the speed of light, we can simply take $\alpha^{i}=1$ (i.e., the global LF flux).

### 2018-07-25 Documents/M1/realizableFermionicM1/sections/imex.tex
Minor edits
Some corrections due to comments from Cory

@@
 
-In this section we discuss the class of IMEX schemes we consider for the realizability-preserving DG-IMEX method for the two-moment model developed in Section~\ref{sec:realizableDGIMEX} (see also \ref{app:butcherTables} for additional details).
+In this section we discuss the class of IMEX schemes that are used for the realizability-preserving DG-IMEX method developed in Section~\ref{sec:realizableDGIMEX} (see also \ref{app:butcherTables} for additional details).
 The semi-discretization of the moment equations with the DG method given by Eq.~\eqref{eq:semidiscreteDG} results in a system of ordinary differential equations (ODEs) in each element of the form
@@
 Thus, for $\phi_{1}=1$, the first components of $\vect{u}$ are the cell averaged moments.  
-In Eq.~\eqref{eq:ode}, the transport operator $\vect{\cT}$ is due to the second and third term on the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision operator $\vect{\cQ}$ is due to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
+In Eq.~\eqref{eq:ode}, the transport operator $\vect{\cT}$ corresponds to the second and third term on the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision operator $\vect{\cQ}$ corresponds to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
 
@@
 
-In the applications of interest to us, collisions with a background induce stiffness ($\tau\ll1$) in regions of the computational domain and must be treated with implicit methods, while we can resolve the time scales induced by the transport term, which we then can treat with explicit methods.
+In many applications, collisions with a background induce stiffness ($\tau\ll1$) in regions of the computational domain that must be treated with implicit methods.  
+Meanwhile, the time scales induced by the transport term can be treated with explicit methods.  
 This motivates the use of IMEX methods \cite{ascher_etal_1997,pareschiRusso_2005}.  
-Furthermore, we would like to employ IMEX schemes that preserve realizability of the moments --- subject only to a time step governed by the explicit transport operator, and comparable to the time step required for numerical stability of the explicit scheme.
+Our goal is to employ IMEX schemes that preserve realizability of the moments, subject only to a time step governed by the explicit transport operator and comparable to the time step required for numerical stability of the explicit scheme.
 (The realizability-preserving and positivity-preserving properties of an IMEX scheme are intimately related, and we use the two phrases interchangeably.)  
-Until recently, high-order (second or higher order temporal accuracy) positivity-preserving IMEX methods with time step restrictions solely due to the transport operator were not known.  
-Chertock et al. \cite{chertock_etal_2015} presented second-order accurate IMEX schemes with a correction step.  
+Unfortunately, high-order (second or higher order temporal accuracy) positivity-preserving IMEX methods with time step restrictions solely due to the transport operator do not exist (see for example Proposition~6.2 in \cite{gottlieb_etal_2001}, which rules out the existence of strong stability-preserving implicit Runge-Kutta methods of order higher than one).
+To overcome this barrier, Chertock et al. \cite{chertock_etal_2015} presented IMEX schemes with a correction step, which recovers second-order accuracy.  
 However, the correction step in \cite{chertock_etal_2015} involves both the transport and collision operators, and we have found that realizability is then subject to a time step restriction that depends on $\tau$, which may become too restrictive for stiff problems.
@@
 where, as in standard IMEX schemes, $(\tilde{a}_{ij})$ and $(a_{ij})$, components of $s\times s$ matrices $\tilde{A}$ and $A$, respectively, and the vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ must satisfy certain order conditions \cite{pareschiRusso_2005}.
-The coefficient in the correction step is positive, $\alpha>0$, and $\vect{\cQ}'$ is the Fr{\'e}chet derivative of the collision term evaluated at $\vect{u}^{*}$.  
+The coefficient $\alpha$ in the correction step is positive, and $\vect{\cQ}'$ is the Fr{\'e}chet derivative of the collision term evaluated at $\vect{u}^{*}$.  
 For second-order accuracy, $\vect{\cQ}'$ can be evaluated using any of the stage values ($\vect{u}^{n}$, $\vect{u}^{(i)}$, or $\tilde{\vect{u}}^{n+1}$).  
-For second-order temporal accuracy, the order conditions for the IMEX scheme in Eqs.~\eqref{imexStages}-\eqref{eq:imexCorrection} are
+For second-order temporal accuracy, the order conditions for the IMEX scheme in Eqs.~\eqref{imexStages}-\eqref{eq:imexCorrection} are \cite{hu_etal_2018}
 \begin{equation}
@@
 In writing the stages in the IMEX scheme in the general form given by Eq.~\eqref{eq:imexStagesRewrite}, it should be noted that $\tilde{c}_{i0}=0$ for IMEX schemes of Type~A, and $c_{i1}=\tilde{c}_{i1}=0$ for IMEX schemes of Type~ARS \cite{hu_etal_2018}.
-For type A schemes, the positivity-preserving property follows from requiring $a_{ii}>0$ and $c_{i0}\ge0$ for $i=1,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$, for $i=2,\ldots,s$, $j=1,\ldots,s-1$.  
-For type ARS schemes, positivity follows from requiring $a_{ii}>0$ and $c_{i0},\tilde{c}_{i0}\ge0$ for $i=2,\ldots,s$, and $c_{ij},\tilde{c}_{ij}\ge0$ for $i=3,\ldots,s$, $j=2,\ldots,i-1$.  
+For type A schemes, the positivity-preserving property follows from requiring 
+\begin{align}
+  &a_{ii}>0, \quad c_{i0}\ge0, \quad \text{for} \quad i=1,\ldots,s, \nonumber \\
+  &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=2,\ldots,s, \quad\text{and}\quad j=1,\ldots,s-1.  
+  \label{eq:positivityConditionsTypeA}
+\end{align}
+For type ARS schemes, positivity follows from requiring 
+\begin{align}
+  &a_{ii}>0, \quad c_{i0},\tilde{c}_{i0}\ge0, \quad \text{for} \quad i=2,\ldots,s, \nonumber \\
+  &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=3,\ldots,s, \quad\text{and}\quad j=2,\ldots,i-1.  
+  \label{eq:positivityConditionsTypeARS}
+\end{align}
 Such coefficients were given in \cite{hu_etal_2018} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
@@
 Importantly, the coefficients $c_{ij}$ in Eq.~\eqref{eq:imexStagesRewrite} satisfy $\sum_{j=0}^{i-1}c_{ij}=1$, which implies the so-called Shu-Osher form of the explicit part \cite{shuOsher_1988}.  
-If the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} --- which is in the form of a forward Euler update with time step $\hat{c}_{ij}\,\dt$ --- is positive for all $i=1,\ldots,s$, $j=0,\ldots,i-1$, positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
+If the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} --- which is in the form of a forward Euler update with time step $\hat{c}_{ij}\,\dt$ --- is positive for all $i=1,\ldots,s$, and $j=0,\ldots,i-1$, then positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
 Thus, if the explicit update with the transport operator is positive for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is positivity-preserving for a time step $\dt\le c_{\mbox{\tiny Sch}}\,\dt_{\mbox{\tiny Ex}}$, where
@@
 
-\subsection{Positivity-Preserving, Diffusion Accurate IMEX Schemes}
+\subsection{Positivity-Preserving, Diffusion Accurate IMEX (PD-IMEX) Schemes}
 
@@
 Unfortunately, the ``diffusion limit requirement" in Eq.~\eqref{eq:diffusionCondition}, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints.
-(It was shown in \cite{hu_etal_2018} --- without the diffusion limit requirement --- that the minimum number of stages for positivity-preserving IMEX schemes of type~ARS is four.)  
-We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators (e.g., inelastic scattering).
+\footnote{It was shown in \cite{hu_etal_2018} --- without the diffusion limit requirement --- that the minimum number of stages for positivity-preserving IMEX schemes of type~ARS is four.)  
+We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators (e.g., inelastic scattering).}
 To reduce the number of constraints, and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
@@
   Let PD-IMEX be a consistent, positivity-preserving, diffusion accurate, and low-stage GSA IMEX scheme satisfying the following properties
-  \begin{itemize}
+  \begin{enumerate}
     \item Consistency of the implicit coefficients
@@
     \end{equation*}
-  \end{itemize}
+  \end{enumerate}
   \label{def:PD-IMEX}

### 2018-07-25 Documents/M1/realizableFermionicM1/sections/intro.tex
First rough draft of intro.

\section{Introduction}
\label{sec:intro}

In this paper we design numerical methods to solve the two-moment model for transport of particles governed by Fermi-Dirac statistics.  
The numerical method is based on the Discontinuous Galerkin (DG) method for spatial discretization, Implicit-Explicit (IMEX) methods for time integration, and preserves physical constraints of the underlying model.  
The latter property is achieved by considering the spatial and temporal discretization together with the closure procedure for the two-moment model.

In many applications, the particle mean free path exceeds other characteristic length scales in the system under consideration (i.e., the Knudsen number exceeds unity), and non-equilibrium effects become important.  
In these situations, a kinetic description may be required, and the particle distribution function $f(\vect{p},\vect{x},t)$ is solved for.  
The distribution function, a phase space density depending on momentum $\vect{p}$ and position $\vect{x}$, gives at time $t$ the number of particles in the phase space volume element $d\vect{p}\,d\vect{x}$; i.e., $dN=f\,d\vect{p}\,d\vect{x}$.  
The evolution of the distribution function is governed by the Boltzmann equation, which states a balance between phase space advection and collisions.

Solving the Boltzmann equation for $f$ numerically is challenging, in part due to the high dimensionality of phase space.  
To reduce the dimensionality of the problem and make it more computationally tractable, one may instead solve for a finite number of angular moments $\{m^{(k)}\}_{k=0}^{N}$ of the distribution function, defined as
\begin{equation}
  m^{(k)}(\varepsilon,\vect{x},t)=\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\varepsilon,\vect{x},t)\,g^{(k)}(\omega)\,d\omega,
\end{equation}
where $\varepsilon=|\vect{p}|$, $\omega$ is a point on the unit sphere $\bbS^{2}$ indicating the particle propagation direction, and $g^{(k)}$ are momentum space angular weighing functions.  
In problems where collisions are sufficiently frequent, solving this \emph{truncated moment problem} can give significant reductions in the computational cost since only a few moments are needed to represent the solution accurately.  
In problems where collisions do not sufficiently isotropize the angular dependence of the distribution function, more moments are needed to accurately represent the solution.  
In the so-called two-moment model, angular moments representing the particle density and flux vector are solved for.

When solving the truncated moment problem, the equation governing the evolution of the $N$-th order moment $m^{(N)}$ contains higher order moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified to form a closed system of equations.  
For the two-moment model, the symmetric rank-two Eddington tensor (proportional to the pressure tensor) must be specified.  
Solutions to the closure problem include setting $m^{(k)}=0$, for $k>N$, Eddington approximation, Kershaw-type closure, and maximum entropy closure.  
The closure procedure often results in a system of nonlinear hyperbolic conservation laws, which can be solved using suitable numerical methods.  
One challenge in solving the closure problem is constructing a sequence of moments that are consistent with a positive distribution function, which typically implies algebraic constraints on the moments.  
Moments satisfying these constraints are called \emph{realizable moments}.

When solving the Boltzmann equations approximately by a truncated moment model, maintaining realizable moments is necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and entropy dissipation.  
Failure to maintain moment realizability in a numerical model may then require ad hoc post-processing steps with undesirable consequences such as loss of conservation.  
For the two-moment model for particles governed by Maxwell-Boltzmann statistics (``classical'' particles with $f\ge0$), the particle density is nonnegative, the magnitude of the flux vector is bounded by the particle density, and there are further constraints on the components of the Eddington tensor \cite{levermore_1984}.  
Furthermore, the realizable set of moments spanned by the particle density and flux vector constitute a convex cone \cite{olbrant_etal_2012}.

In this paper we consider the two-moment model for particles governed by Fermi-Dirac statistics.  
In this case, there is also an upper bound on the distribution function because of Pauli's exclusion principle, which prevents particles (fermions) from occupying the same microscopic state.  
The fermionic two-moment model was recently studied theoretically in the context of maximum entropy closures \cite{lareckiBanach_2011,banachLarecki_2013,banachLarecki_2017b} and Kershaw-type closures \cite{banachLarecki_2017a}.  
Because of the upper bound on the distribution function, the algebraic constraints on the realizable moments are modified when compared to the classical case with no upper bound, and can lead to significantly different dynamics when the occupancy is high (i.e., when $f$ is close to its upper bound).  
In the fermionic case, the set of realizable moments (particle density and flux vector) is also convex, and resembles a ``pinched'' cone.  
It coincides with the realizable set for the classical case when the occupancy is low, but is much more restricted for high occupancy.

The equations of the two-moment model are discretized in space using high-order Discontinuous Galerkin (DG) methods (e.g., \cite{cockburnShu_2001,hesthavenWarburton_2008}).  
DG methods combine elements from both spectral and finite volume methods, and are an attractive option for solving hyperbolic partial differential equations (PDEs).  
They achieve high-order accuracy on a compact stencil; i.e., data is only communicated with nearest neighbors, regardless of the formal order of accuracy, which can lead to a high computation to communication ratio, and favorable parallel scalability on heterogeneous architectures has been demonstrated \cite{klockner_etal_2009}.  
Furthermore, they can easily be applied to problems involving curvilinear coordinates (e.g., beneficial in numerical relativity \cite{teukolsky_2016}).  
Importantly, DG methods, exhibit favorable properties when collisions with a background are included as they recover the correct asymptotic behavior in the diffusion limit, characterized by frequent collisions (e.g., \cite{larsenMorel_1989,adams_2001,guermondKanschat_2010}).  
The DG method was introduced in the 1970s by Reed \& Hill \cite{reedHill_1973} to solve the neutron transport equation, and has undergone remarkable developments since then (see, e.g., \cite{shu_2016}, and references therein).

In this paper we are concerned with the development and application of DG methods for the fermionic two-moment model that can preserve the aforementioned algebraic constraints and ensure realizable moments.  
The approach is based on the constraint preserving (CP) framework introduced in \cite{zhangShu_2010a}, and later extended to the Euler equations of gas dynamics in \cite{zhangShu_2010b}.  
(See e.g., \cite{endeve_etal_2015}, for extensions and applications to other systems.)  
The main ingredients include (1) a realizability-preserving update for the cell averaged moments based on Euler time stepping, which evaluates the polynomial representation of the DG method in a finite number of quadrature points in the local elements and results in a Courant-Friedrichs-Lewy (CFL) condition on the time step; (2) a limiter to modify the polynomial representation to ensure that the algebraic constraints are satisfied point-wise without changing the cell average of the moments; and (3) a time stepping method that can be expressed as a convex combination of Euler steps, and therefore preserves the algebraic constraints as the Euler methods.

The DG discretization leaves the temporal dimension continuous.  
This semi-discretization leads to a system of ordinary differential equations (ODEs), which can be integrated with standard ODE solvers (i.e., the method of lines approach to solving PDEs).  
We use implicit-explicit (IMEX) Runge-Kutta (RK) methods \cite{ascher_etal_1997,pareschiRusso_2005} to integrate the two-moment model forward in time.  
This approach is motivated by the fact that we can resolve time scales associated with particle streaming terms in the moment equations, which will be integrated with explicit methods, while terms associated with collisional interactions with the background induce fast time scales that we do not wish to resolve, and will be integrated with implicit methods.  
This splitting has some advantages when solving kinetic equations since the collisional interactions may couple across momentum space, but are local in position space, and is easier to parallelize than a fully implicit approach.  
The CP framework of \cite{zhangShu_2010a} achieve high order (i.e., greater than first order) accuracy in time by employing explicit strong stability-preserving Runge-Kutta (SSP-RK) methods \cite{shuOsher_1988,gottlieb_etal_2001}, which can be written as a convex combination of forward Euler steps.  
Unfortunately, this strategy to achieve high order temporal accuracy does not work for standard IMEX Runge-Kutta (IMEX-RK) methods because implicit SSP Runge-Kutta methods with greater than first order accuracy do not exist \cite{gottlieb_etal_2001}.  
To break this ``barrier'', recently proposed IMEX-RK schemes \cite{chertock_etal_2015,hu_etal_2018} have resorted to first order accuracy in favor of the SSP property in the standard IMEX-RK scheme, and recover second-order accuracy with a correction step.  
We consider the application of this approach to the two-moment model.  
With the correction step from \cite{chertock_etal_2015} we are unable to prove the realizability-preserving property without invoking a too restrictive time step.  
With the correction step from \cite{hu_etal_2018} the realizability-preserving property is guaranteed with a time step comparable to that of the forward Euler method, but the resulting scheme performs poorly in the asymptotic diffusion limit.  
Because of these challenges, we resort to first-order accuracy, and propose IMEX-RK schemes that are realizability-preserving with a time step equal to that of forward Euler, perform well in the diffusion limit, and reduce to a second-order SSP-RK scheme in the streaming limit (no collisions with the background material).

The paper is organized as follows.  
In Section~\ref{sec:model} we present the two-moment model.  
In Section~\ref{sec:realizability} we discuss moment realizability for the fermionic two-moment model, while algebraic moment closures are discussed in Section~\ref{sec:algebraicClosure}.  
In Section~\ref{sec:dg} we briefly introduce the DG method for the two-moment model, while the IMEX time stepping methods we use are discussed in Section~\ref{sec:imex}.  
The main results on the realizability-preserving DG-IMEX method for the fermionic two-moment model are worked out in Section~\ref{sec:realizableDGIMEX}.  
In Section~\ref{sec:limiter} we discuss the realizability-preserving limiter.  
Numerical results are presented in Section~\ref{sec:numerical}, and summary and conclusions are given in Section~\ref{sec:conclusions}.

### 2018-08-07 Documents/M1/realizableFermionicM1/manuscript.tex
Additions to paper
Split section 3 in two: Moment Realizability... and Algebraic Moment Closures
Forgot to add algebraicClosures.tex.  Added appendix with some detail on the IMEX schemes discussed in the paper has been added (not complete)
Working on text discussing IMEX schemes.
More work on the imex section.
Minor adjustments to dg.tex and imex.tex.  Began work on updating DGIMEX.tex
Some work on Section 3 (removed proof of Lemma 1).  And other minor fixes
Added abstract

@@
 
+\newcommand{\ee}[1]{{\color{red} #1}}
+\newcommand{\rc}[1]{{\color{blue} #1}}
+
 \usepackage{./definitions}
@@
 \title{Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}}
-\tnotetext[support]{This research is sponsored by ...}
+\tnotetext[support]{
+This research is sponsored, in part, by the Laboratory Directed Research and Development Program of Oak Ridge National Laboratory (ORNL), managed by UT-Battelle, LLC for the U.
+S.
+Department of Energy under Contract No.
+De-AC05-00OR22725.
+This research was supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of the U.S.
+Department of Energy Office of Science and the National Nuclear Security Administration.
+Eirik Endeve was supported in part by NSF under Grant No. 1535130.}
 
@@
 
+\author[ornl,utk-math]{Cory D. Hauck}
+\ead{hauckc@ornl.gov}
+
 \author[utk-phys]{Anthony Mezzacappa}
@@
 
-\address[ornl]{Computational and Applied Mathematics Group,
-Oak Ridge National Laboratory,
-Oak Ridge, TN 37831 USA }
+\address[ornl]{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA }
 
-\address[utk-phys]{Department of Physics and Astronomy,
-University of Tennessee
-Knoxville, TN 37996-1200}
+\address[utk-phys]{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
+
+\address[utk-math]{Department of Mathematics, University of Tennessee Knoxville, TN 37996-1320}
 
 \begin{abstract}
-This paper ...
+Building on the framework of Zhang \& Shu \cite{zhangShu_2010a,zhangShu_2010b}, we develop a realizability-preserving method to simulate transport of particles (fermions) through a background material using the two-moment model of radiation transport, which evolves angular moments of a phase space distribution function $f$.
+The two-moment model is closed using simple algebraic moment closures, e.g., as proposed by Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Banach \& Larecki \cite{banachLarecki_2017a}.  
+Variations of this model have recently been used to simulate neutrino transport in nuclear astrophysics applications --- including core-collapse supernovae and compact binary mergers.  
+We employ the discontinuous Galerkin (DG) method for spatial discretization (in part to capture the asymptotic diffusion limit of the model) combined with implicit-explicit (IMEX) time integration to stably bypass short timescales induced by frequent interactions between particles and the background.
+Appropriate care is taken to ensure the method preserves strict algebraic bounds on the evolved moments (particle density and flux) as dictated by Pauli's exclusion principle, which demands a bounded distribution function (i.e., $f\in[0,1]$).
+This realizability-preserving scheme combines a suitable CFL condition, a realizability-preserving limiter, a closure procedure based on Fermi-Dirac statistics, and an IMEX scheme whose stages can be written as a convex combination of forward Euler steps combined with a backward Euler step.
+The IMEX scheme is formally only first-order accurate, but works well in the diffusion limit and reduces to the optimal second-order strong stability-preserving Runge-Kutta scheme of Shu \& Osher \cite{shuOsher_1988}.
+Numerical results demonstrate the realizability-preserving properties of the scheme.  
+We also demonstrate that the use of algebraic moment closures not based on Fermi-Dirac statistics can lead to unphysical moments in the context of fermion transport.  
 \end{abstract}
@@
 \input{sections/realizability}
+\input{sections/algebraicClosures}
 \input{sections/dg}
@@
 \input{sections/conclusion}
-%\input{sections/appendix}
+\input{sections/appendix}
+
 \clearpage

### 2018-08-07 Documents/M1/realizableFermionicM1/sections/intro.tex
Work on intro

@@
 
-In this paper we design numerical methods to solve the two-moment model for transport of particles governed by Fermi-Dirac statistics.  
-The numerical method is based on the Discontinuous Galerkin (DG) method for spatial discretization, Implicit-Explicit (IMEX) methods for time integration, and preserves physical constraints of the underlying model.
+In this paper we design numerical methods to solve the two-moment model governing transport of particles obeying by Fermi-Dirac statistics (e.g., neutrinos), with the ultimate target being nuclear astrophysics applications (e.g., neutrino transport in core-collapse supernovae and compact binary mergers).
+The numerical method is based on the discontinuous Galerkin (DG) method for spatial discretization, implicit-explicit (IMEX) methods for time integration, and is designed to preserve physical constraints of the underlying model.
 The latter property is achieved by considering the spatial and temporal discretization together with the closure procedure for the two-moment model.
 
-In many applications, the particle mean free path exceeds other characteristic length scales in the system under consideration (i.e., the Knudsen number exceeds unity), and non-equilibrium effects become important.
-In these situations, a kinetic description may be required, and the particle distribution function $f(\vect{p},\vect{x},t)$ is solved for.  
-The distribution function, a phase space density depending on momentum $\vect{p}$ and position $\vect{x}$, gives at time $t$ the number of particles in the phase space volume element $d\vect{p}\,d\vect{x}$; i.e., $dN=f\,d\vect{p}\,d\vect{x}$.
-The evolution of the distribution function is governed by the Boltzmann equation, which states a balance between phase space advection and collisions.
+In many applications, the particle mean free path is comparable to or exceeds other characteristic length scales in the system under consideration (i.e., the Knudsen number exceeds unity), and non-equilibrium effects may become important.
+In these situations, a kinetic description may be required, where particle distribution function $f(\vect{p},\vect{x},t)$ is solved for.  
+The distribution function, a phase space density depending on momentum $\vect{p}$ and position $\vect{x}$, gives at time $t$ the number of particles in the phase space volume element $d\vect{p}\,d\vect{x}$ (i.e., $dN=f\,d\vect{p}\,d\vect{x}$).
+The evolution of the distribution function is governed by the Boltzmann equation, which states a balance between phase space advection and collisions (see, e.g., \cite{braginskii_1965,chapmanCowling_1970,lifshitzPitaevskii_1981}).
 
-Solving the Boltzmann equation for $f$ numerically is challenging, in part due to the high dimensionality of phase space.  
+Solving the Boltzmann equation numerically for $f$ is challenging, in part due to the high dimensionality of phase space.  
 To reduce the dimensionality of the problem and make it more computationally tractable, one may instead solve for a finite number of angular moments $\{m^{(k)}\}_{k=0}^{N}$ of the distribution function, defined as
@@
 \end{equation}
-where $\varepsilon=|\vect{p}|$, $\omega$ is a point on the unit sphere $\bbS^{2}$ indicating the particle propagation direction, and $g^{(k)}$ are momentum space angular weighing functions.  
-In problems where collisions are sufficiently frequent, solving this \emph{truncated moment problem} can give significant reductions in the computational cost since only a few moments are needed to represent the solution accurately.
-In problems where collisions do not sufficiently isotropize the angular dependence of the distribution function, more moments are needed to accurately represent the solution.  
-In the so-called two-moment model, angular moments representing the particle density and flux vector are solved for.
+where $\varepsilon=|\vect{p}|$ is the particle energy, $\omega$ is a point on the unit sphere $\bbS^{2}$ indicating the particle propagation direction, and $g^{(k)}$ are momentum space angular weighing functions.
+In problems where collisions are sufficiently frequent, solving a \emph{truncated moment problem} can provide significant reductions in computational cost since only a few moments are needed to represent the solution accurately.
+On the other hand, in problems where collisions do not sufficiently isotropize the angular dependence of the distribution function, more moments may be needed.  
+In the two-moment model considered here, angular moments representing the particle density and flux (or energy density and momentum) are solved for.  
+Two-moment models for relativistic systems appropriate for nuclear astrophysics applications have been discussed in, e.g., \cite{lindquist_1966,andersonSpiegel_1972,thorne_1981,shibata_etal_2011,cardall_etal_2013a}.
+However, in this paper, for simplicity (and clarity), we consider a non-relativistic model, leaving extensions to relativistic systems for future work.
 
-When solving the truncated moment problem, the equation governing the evolution of the $N$-th order moment $m^{(N)}$ contains higher order moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified to form a closed system of equations.
+When solving a truncated moment problem, the equation governing the evolution of the $N$-th order moment $m^{(N)}$ contains higher order moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified to form a closed system of equations.
 For the two-moment model, the symmetric rank-two Eddington tensor (proportional to the pressure tensor) must be specified.  
@@
 
-When solving the Boltzmann equations approximately by a truncated moment model, maintaining realizable moments is necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and entropy dissipation.
+When solving the Boltzmann equations approximately by a truncated moment model, maintaining realizable moments is necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and (mathematical) entropy dissipation.
 Failure to maintain moment realizability in a numerical model may then require ad hoc post-processing steps with undesirable consequences such as loss of conservation.  

### 2018-08-08 Documents/M1/realizableFermionicM1/sections/intro.tex
Some edits to the intro.

@@
 Solving the Boltzmann equation numerically for $f$ is challenging, in part due to the high dimensionality of phase space.  
-To reduce the dimensionality of the problem and make it more computationally tractable, one may instead solve for a finite number of angular moments $\{m^{(k)}\}_{k=0}^{N}$ of the distribution function, defined as
+To reduce the dimensionality of the problem and make it more computationally tractable, one may instead solve for a finite number of angular moments $\vect{m}_{N}=(m^{(0)},m^{(1)},\ldots,m^{(N)})^{T}$ of the distribution function, defined as
 \begin{equation}
@@
 In problems where collisions are sufficiently frequent, solving a \emph{truncated moment problem} can provide significant reductions in computational cost since only a few moments are needed to represent the solution accurately.
-On the other hand, in problems where collisions do not sufficiently isotropize the angular dependence of the distribution function, more moments may be needed.  
-In the two-moment model considered here, angular moments representing the particle density and flux (or energy density and momentum) are solved for.  
+On the other hand, in problems where collisions do not sufficiently isotropize the distribution function, more moments may be needed.  
+In the two-moment model considered here ($N=1$), angular moments representing the particle density and flux (or energy density and momentum) are solved for.  
 Two-moment models for relativistic systems appropriate for nuclear astrophysics applications have been discussed in, e.g., \cite{lindquist_1966,andersonSpiegel_1972,thorne_1981,shibata_etal_2011,cardall_etal_2013a}.
@@
 
-When solving a truncated moment problem, the equation governing the evolution of the $N$-th order moment $m^{(N)}$ contains higher order moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified to form a closed system of equations.
+In a truncated moment model, the equation governing the evolution of the $N$-th order moment $m^{(N)}$ contains higher order moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified to form a closed system of equations.
 For the two-moment model, the symmetric rank-two Eddington tensor (proportional to the pressure tensor) must be specified.  
-Solutions to the closure problem include setting $m^{(k)}=0$, for $k>N$, Eddington approximation, Kershaw-type closure, and maximum entropy closure.  
-The closure procedure often results in a system of nonlinear hyperbolic conservation laws, which can be solved using suitable numerical methods.  
-One challenge in solving the closure problem is constructing a sequence of moments that are consistent with a positive distribution function, which typically implies algebraic constraints on the moments.
-Moments satisfying these constraints are called \emph{realizable moments}.
+Solutions to the closure problem include setting $m^{(k)}=0$, for $k>N$, Eddington approximation, Kershaw-type closure \cite{kershaw_1976}, and maximum entropy closure \cite{minerbo_1978,cernohorskyBludman_1994}.
+The closure procedure often results in a system of nonlinear hyperbolic conservation laws, which can be solved using suitable numerical methods (e.g., \cite{leveque_1992}).  
+One challenge in solving the closure problem is constructing a sequence of moments that are consistent with a positive distribution function, which typically implies algebraic constraints on the moments \cite{kershaw_1976,levermore_1984}.
+Moments satisfying these constraints are called \emph{realizable moments} (e.g., \cite{levermore_1996}).  
+When evolving a truncated moment model numerically, maintaining realizable moments is necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and (mathematical) entropy dissipation.
+Failure to maintain moment realizability in a numerical model may then require ad hoc post-processing steps with undesirable consequences such as loss of conservation.
 
-When solving the Boltzmann equations approximately by a truncated moment model, maintaining realizable moments is necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and (mathematical) entropy dissipation.
-Failure to maintain moment realizability in a numerical model may then require ad hoc post-processing steps with undesirable consequences such as loss of conservation.  
-For the two-moment model for particles governed by Maxwell-Boltzmann statistics (``classical'' particles with $f\ge0$), the particle density is nonnegative, the magnitude of the flux vector is bounded by the particle density, and there are further constraints on the components of the Eddington tensor \cite{levermore_1984}.
+In this paper we consider a two-moment model for particles governed by Fermi-Dirac statistics.  
+For a two-moment model for particles governed by Maxwell-Boltzmann statistics (``classical'' particles with $f\ge0$), the particle density is nonnegative, the magnitude of the flux vector is bounded by the particle density, and there are further constraints on the components of the Eddington tensor \cite{levermore_1984}.
 Furthermore, the realizable set of moments spanned by the particle density and flux vector constitute a convex cone \cite{olbrant_etal_2012}.  
-
-In this paper we consider the two-moment model for particles governed by Fermi-Dirac statistics.  
-In this case, there is also an upper bound on the distribution function because of Pauli's exclusion principle, which prevents particles (fermions) from occupying the same microscopic state.  
+In the fermionic case, there is also an upper bound on the distribution function because of Pauli's exclusion principle, which prevents particles from occupying the same microscopic state.  
 The fermionic two-moment model was recently studied theoretically in the context of maximum entropy closures \cite{lareckiBanach_2011,banachLarecki_2013,banachLarecki_2017b} and Kershaw-type closures \cite{banachLarecki_2017a}.

### 2018-08-08 Documents/M1/realizableFermionicM1/sections/intro.tex
More edits to the intro

@@
 
-In a truncated moment model, the equation governing the evolution of the $N$-th order moment $m^{(N)}$ contains higher order moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified to form a closed system of equations.
+\clearpage
+
+In a truncated moment model, the equation governing the evolution of the $N$-th moment $m^{(N)}$ contains higher moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified in order to form a closed system of equations.
 For the two-moment model, the symmetric rank-two Eddington tensor (proportional to the pressure tensor) must be specified.  
-Solutions to the closure problem include setting $m^{(k)}=0$, for $k>N$, Eddington approximation, Kershaw-type closure \cite{kershaw_1976}, and maximum entropy closure \cite{minerbo_1978,cernohorskyBludman_1994}.
+Solutions to the closure problem include setting $m^{(k)}=0$, for $k>N$ ($P_N$ approximation \cite{brunnerHolloway_2005}), Eddington approximation \cite{mihalasMihalas_1999}, Kershaw-type closure \cite{kershaw_1976}, and maximum entropy closure \cite{minerbo_1978,cernohorskyBludman_1994}.
 The closure procedure often results in a system of nonlinear hyperbolic conservation laws, which can be solved using suitable numerical methods (e.g., \cite{leveque_1992}).  
@@
 Moments satisfying these constraints are called \emph{realizable moments} (e.g., \cite{levermore_1996}).  
-When evolving a truncated moment model numerically, maintaining realizable moments is necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and (mathematical) entropy dissipation.
-Failure to maintain moment realizability in a numerical model may then require ad hoc post-processing steps with undesirable consequences such as loss of conservation.
+When evolving a truncated moment model numerically, maintaining realizable moments is challenging, but necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and (mathematical) entropy dissipation.
+In addition to putting the validity of the numerical results into question, failure to maintain moment realizability in a numerical model may, in order to continue a simulation, require ad hoc post-processing steps with undesirable consequences such as loss of conservation.
 
 In this paper we consider a two-moment model for particles governed by Fermi-Dirac statistics.  
-For a two-moment model for particles governed by Maxwell-Boltzmann statistics (``classical'' particles with $f\ge0$), the particle density is nonnegative, the magnitude of the flux vector is bounded by the particle density, and there are further constraints on the components of the Eddington tensor \cite{levermore_1984}.
-Furthermore, the realizable set of moments spanned by the particle density and flux vector constitute a convex cone \cite{olbrant_etal_2012}.  
-In the fermionic case, there is also an upper bound on the distribution function because of Pauli's exclusion principle, which prevents particles from occupying the same microscopic state.  
-The fermionic two-moment model was recently studied theoretically in the context of maximum entropy closures \cite{lareckiBanach_2011,banachLarecki_2013,banachLarecki_2017b} and Kershaw-type closures \cite{banachLarecki_2017a}.
-Because of the upper bound on the distribution function, the algebraic constraints on the realizable moments are modified when compared to the classical case with no upper bound, and can lead to significantly different dynamics when the occupancy is high (i.e., when $f$ is close to its upper bound).
-In the fermionic case, the set of realizable moments (particle density and flux vector) is also convex, and resembles a ``pinched'' cone.  
+It is well known from the two-moment model for particles governed by Maxwell-Boltzmann statistics (``classical'' particles with $f\ge0$), that the particle density is nonnegative and the magnitude of the flux vector is bounded by the particle density.
+(There are further constraints on the components of the Eddington tensor \cite{levermore_1984}.)  
+Furthermore, the set of realizable moments generated by the particle density and flux vector constitutes a convex cone \cite{olbrant_etal_2012}.  
+In the fermionic case, there is also an upper bound on the distribution function because Pauli's exclusion principle prevents particles from occupying the same microscopic state.  
+The fermionic two-moment model has recently been studied theoretically in the context of maximum entropy closures \cite{lareckiBanach_2011,banachLarecki_2013,banachLarecki_2017b} and Kershaw-type closures \cite{banachLarecki_2017a}.
+Because of the upper bound on the distribution function, the algebraic constraints on realizable moments differ from the classical case with no upper bound, and can lead to significantly different dynamics when the occupancy is high (i.e., when $f$ is close to its upper bound).
+In the fermionic case, the set of realizable moments generated by the particle density and flux vector is also convex, and resembles a ``pinched'' cone.  
 It coincides with the realizable set for the classical case when the occupancy is low, but is much more restricted for high occupancy.
 
-The equations of the two-moment model are discretized in space using high-order Discontinuous Galerkin (DG) methods (e.g., \cite{cockburnShu_2001,hesthavenWarburton_2008}).  
+The two-moment model is discretized in space using high-order Discontinuous Galerkin (DG) methods (e.g., \cite{cockburnShu_2001,hesthavenWarburton_2008}).  
 DG methods combine elements from both spectral and finite volume methods, and are an attractive option for solving hyperbolic partial differential equations (PDEs).  
@@
 
-In this paper we are concerned with the development and application of DG methods for the fermionic two-moment model that can preserve the aforementioned algebraic constraints and ensure realizable moments.
-The approach is based on the constraint preserving (CP) framework introduced in \cite{zhangShu_2010a}, and later extended to the Euler equations of gas dynamics in \cite{zhangShu_2010b}.  
-(See e.g., \cite{endeve_etal_2015}, for extensions and applications to other systems.)  
+We are concerned with the development and application of DG methods for the fermionic two-moment model that can preserve the aforementioned algebraic constraints and ensure realizable moments, provided the initial condition is realizable.
+Our approach is based on the constraint-preserving (CP) framework introduced in \cite{zhangShu_2010a}, and later extended to the Euler equations of gas dynamics in \cite{zhangShu_2010b}.  
+(See e.g., \cite{xing_etal_2010,zhangShu_2011,olbrant_etal_2012,cheng_etal_2013,zhang_etal_2013,endeve_etal_2015,wuTang_2015}, for extensions and applications to other systems.)  
 The main ingredients include (1) a realizability-preserving update for the cell averaged moments based on Euler time stepping, which evaluates the polynomial representation of the DG method in a finite number of quadrature points in the local elements and results in a Courant-Friedrichs-Lewy (CFL) condition on the time step; (2) a limiter to modify the polynomial representation to ensure that the algebraic constraints are satisfied point-wise without changing the cell average of the moments; and (3) a time stepping method that can be expressed as a convex combination of Euler steps, and therefore preserves the algebraic constraints as the Euler methods.
@@
 Numerical results are presented in Section~\ref{sec:numerical}, and summary and conclusions are given in Section~\ref{sec:conclusions}.
+
+\clearpage

### 2018-08-14 Documents/M1/realizableFermionicM1/sections/conclusion.tex
Added the conclusion sectrion draft

\section{Conclusions}
\label{sec:conclusions}

We develop a realizability-preserving scheme which includes a suitable CFL condition, a realizability-preserving limiter, a realizability-preserving closure procedure and a realizability-preserving IMEX time integrator.
Thanks for the meaningful result domain being a convex set, the realizability-preservation of the limiter and the IMEX time integrator can be ensured by requiring they have convex combination forms.
And a realizability-preserving closure procedure can be obtained by any closure procedure building on Fermi-Dirac statistics.
In the physics which we interested, the transport system introduces a stiff problem: the collision term has much larger eigenvalues than that the advection term has.
Therefore, requiring the scheme be streaming accurate and diffusion accurate is an essential and achievable goal than being overall accurate.
We purpose our PD-ARS scheme. It is 2nd-order accurate and strong stability preserving in the streaming limit and works well in the diffusion limit. Numerical examples are provided to demonstrate those properties.

It's widely known that a realizability-preserving scheme is required for solving the approximating transport problems with conservation law, including the two-moment model.
However, few people are aware of the significance of realizability-preserving closure procedure: the Minerbo closure, which is not built on Fermi-Dirac distribution, is widely used.
We highly recommend the CB closure other than the Minerbo closure because the CB closure not only preserves the realizability but also requires no more calculation than the Minerbo closure.

The realizability-preservation of our IMEX scheme is universal: it can be implemented to any problems where the physical constraints confine its meaningful result to a convex set and the diffusion limit is important.

To build this work, we assume an easy collision term and no relativistic term on the left-hand side of the transport equation.
Hence, to solve a more realistic problem, a complex collision term and some relativistic terms should be taken into consideration.
Besides, a higher order accurate method is always desired.
Moreover, there is no reason to restrict the time integrator to be IMEX.
They all bring the remained open problems which require the future contribution.

### 2018-08-17 Documents/M1/realizableFermionicM1/sections/conclusion.tex
Modified the conclusion section.

@@
 
-We develop a realizability-preserving scheme which includes a suitable CFL condition, a realizability-preserving limiter, a realizability-preserving closure procedure and a realizability-preserving IMEX time integrator.
-Thanks for the meaningful result domain being a convex set, the realizability-preservation of the limiter and the IMEX time integrator can be ensured by requiring they have convex combination forms.
-And a realizability-preserving closure procedure can be obtained by any closure procedure building on Fermi-Dirac statistics.
-In the physics which we interested, the transport system introduces a stiff problem: the collision term has much larger eigenvalues than that the advection term has.
-Therefore, requiring the scheme be streaming accurate and diffusion accurate is an essential and achievable goal than being overall accurate.
-We purpose our PD-ARS scheme.
-It is 2nd-order accurate and strong stability preserving in the streaming limit and works well in the diffusion limit.
+We have developed a realizability-preserving DG-IMEX scheme for the two-moment method of fermion transport.
+The scheme includes a suitable CFL condition, a realizability-preserving limiter, a realizable closure procedure and a realizability-preserving IMEX time integrator.
+Its suitable CFL condition is limited by the phase space advection term only and can be as large as the CFL condition of the forward Euler time stepping scheme. 
+The limiter enforces the spacial space discretization be constraint preserving for DG scheme.
+The closure provides a realizable moment approximation.
+And the IMEX time integrator, which can be written as a combination of forward Euler method and a backward Euler method, enforces each time step and each stage inside a time step be realizable.
+Since the realizable domain is a convex set, the realizability-preserving property of the limiter and the IMEX time integrator can be ensured by requiring they have convex combination forms.
+And a realizable closure procedure can be a closure procedure based on Fermi-Dirac statistics.
+
+The collision term is stiff on time scale of interest: in a small domain, the transport is dominate by the diffusion; other than that, the streaming governed.
+We tried first to build a formally second order IMEX scheme.
+However, a correction step is needed which result a restricted CFL condition.
+As an alternation, we separate the accuracy properties and require the scheme be second order in the streaming limit and first order in the diffusion limit.
+This is an essential and more achievable goal.
+Here we purpose our PD-ARS scheme. 
+It is formally first order accurate but reduces to the optimal second-order strong-stability-preserving Runge-Kutta scheme in the streaming limit and works well in the diffusion limit. 
 Numerical examples are provided to demonstrate those properties.
 
-It's widely known that a realizability-preserving scheme is required for solving the approximating transport problems with conservation law, including the two-moment model.
-However, few people are aware of the significance of realizability-preserving closure procedure: the Minerbo closure, which is not built on Fermi-Dirac distribution, is widely used.
-We highly recommend the CB closure other than the Minerbo closure because the CB closure not only preserves the realizability but also requires no more calculation than the Minerbo closure.
+The constraint-preserving property of PD-ARS scheme is applicable to a wide class of problems where the physical constraints confine its meaningful result to a convex set and the diffusion limit is important.
 
-The realizability-preservation of our IMEX scheme is universal: it can be implemented to any problems where the physical constraints confine its meaningful result to a convex set and the diffusion limit is important.
+It's known that a realizability-preserving scheme is required for solving the approximating transport problems with conservation law, including the two-moment model.
+A break of the constraint-preserving property, such as implementing a non-realizable closure, the Minerbo closure for example, puts the conservation law in danger.
+Among the simple realizable algebraic closures we discussed(CB, BL and Kershaw closure), we recommend the CB closure (reason ... ).
 
-To build this work, we assume an easy collision term and no relativistic term on the left-hand side of the transport equation.
-Hence, to solve a more realistic problem, a complex collision term and some relativistic terms should be taken into consideration.
+In this work, we adapted a relatively simple model. 
+We assume a linear collision term with fixed background, only elastic scattering exists, and no relativistic term on the left-hand side of the transport equation.
+Hence, to solve a more scientific problem, a complex collision term and some relativistic terms should be taken into consideration.
 Besides, a higher order accurate method is always desired.
 Moreover, there is no reason to restrict the time integrator to be IMEX.
-They all bring the remained open problems which require the future contribution.
+In the context of constraint-preserving schemes, these extension provide additional challenge suitable for future investigations.

### 2018-08-21 Documents/M1/realizableFermionicM1/sections/conclusion.tex
Work on the conclusions section

--- 2018-08-14 Documents/M1/realizableFermionicM1/sections/conclusion.tex
@@
-\section{Conclusions}
+\section{Summary and Conclusions}
 \label{sec:conclusions}
 
-We develop a realizability-preserving scheme which includes a suitable CFL condition, a realizability-preserving limiter, a realizability-preserving closure procedure and a realizability-preserving IMEX time integrator.
-Thanks for the meaningful result domain being a convex set, the realizability-preservation of the limiter and the IMEX time integrator can be ensured by requiring they have convex combination forms.
-And a realizability-preserving closure procedure can be obtained by any closure procedure building on Fermi-Dirac statistics.
-In the physics which we interested, the transport system introduces a stiff problem: the collision term has much larger eigenvalues than that the advection term has.
-Therefore, requiring the scheme be streaming accurate and diffusion accurate is an essential and achievable goal than being overall accurate.
-We purpose our PD-ARS scheme.
-It is 2nd-order accurate and strong stability preserving in the streaming limit and works well in the diffusion limit.
-Numerical examples are provided to demonstrate those properties.
+We have developed a realizability-preserving DG-IMEX scheme for a two-moment model for fermion transport.  
+The scheme employs simple algebraic two-moment closures rooted in Fermi-Dirac statistics, and combines a CFL condition, a realizability-enforcing limiter, and a constraint-preserving time integrator to maintain point-wise realizability of the moments.
+Since the realizable domain is a convex set, the realizability-preserving property is obtained from convexity arguments, building on the framework in \cite{zhangShu_2010a}.
 
-It's widely known that a realizability-preserving scheme is required for solving the approximating transport problems with conservation law, including the two-moment model.
-However, few people are aware of the significance of realizability-preserving closure procedure: the Minerbo closure, which is not built on Fermi-Dirac distribution, is widely used.
-We highly recommend the CB closure other than the Minerbo closure because the CB closure not only preserves the realizability but also requires no more calculation than the Minerbo closure.
+In the applications motivating this work, the collision term is stiff in regions of the computational domain, and we have considered IMEX schemes to avoid solving the transport operator implicitly.  
+We considered recently proposed second-order accurate, constraint-preserving IMEX schemes (cf.
+\cite{chertock_etal_2015,hu_etal_2018}), which restore second-order accuracy with an implicit correction step.
+However, we are unable to prove realizability (without invoking a very small time step) with the approach in \cite{chertock_etal_2015}, and we have demonstrated that the approach in \cite{hu_etal_2018} does not perform well in the diffusion limit.
+For these reasons, and the general nonexistence of high-order, implicit SSP-RK schemes \cite{gottlieb_etal_2001}, we have resorted to develop first-order, constraint-preserving IMEX schemes.  
+While the proposed scheme (dubbed PD-ARS) is formally only first-order accurate, it works well in the diffusion limit, is constraint-preserving with a reasonable time step, and reduces to the optimal second-order accurate SSP-RK scheme in the streaming limit.
 
-The realizability-preservation of our IMEX scheme is universal: it can be implemented to any problems where the physical constraints confine its meaningful result to a convex set and the diffusion limit is important.
+For each stage of the IMEX scheme, the cell-averaged moments can be written as a convex combination of forward Euler steps (implying the Shu-Osher form for the explicit part), followed by a backward Euler step.
+Realizability of the explicit part requires the DG solution to be realizable in a finite number of quadrature points in each element and the time step to satisfy a CFL condition.  
+For the backward Euler step, realizability of the cell-averages follows easily from the simple form of the collision operator (which includes emission, absorption, and isotropic elastic scattering), and is independent of the time step.
+The CFL condition is then solely due to the transport operator, and the time step can be as large as that of the forward Euler scheme applied to the explicit part.  
+After each update, the limiter enforces realizability point-wise by damping towards the realizable cell average.  
+Numerical experiments are presented to demonstrate the accuracy and realizability-preserving property of the scheme.  
+The applicability of the PD-ARS scheme is not restricted to the fermionic two-moment model.  
+It may therefore be a useful option in other applications of kinetic theory where physical constraints confine solutions to a convex set and capturing the diffusion limit is important.
 
-To build this work, we assume an easy collision term and no relativistic term on the left-hand side of the transport equation.
-Hence, to solve a more realistic problem, a complex collision term and some relativistic terms should be taken into consideration.
-Besides, a higher order accurate method is always desired.
-Moreover, there is no reason to restrict the time integrator to be IMEX.
-They all bring the remained open problems which require the future contribution.
+Realizability of the fermionic two-moment model depends sensitively on the closure procedure.  
+For the simple algebraic closures adapted in this work, realizability of the scheme demands that lower and upper bounds on the Eddington factor are satisfied \cite{levermore_1984,lareckiBanach_2011}.
+The Eddington factors deriving from the maximum entropy closures of Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Larecki \& Banach \cite{lareckiBanach_2011}, and the Kershaw-type closure of Larecki \& Banach \cite{banachLarecki_2017a} satisfy these bounds, and are suitable for the fermionic two-moment model.
+Further approximations of the closure procedure, e.g., employing the low occupancy limit, which results in the Minerbo closure \cite{minerbo_1978} when starting with the maximum entropy closure of \cite{cernohorskyBludman_1994}), is not compatible with realizability of the fermionic two-moment model, and we caution against this approach to modeling particle systems governed by Fermi-Dirac statistics; particularly if the low occupancy approximation is unlikely to hold (e.g., when modeling neutrino transport in core-collapse supernovae).
+
+In this work, we considered a relatively simple model.  
+In particular, we adopted Cartesian coordinates, assumed a linear collision operator and a fixed material background, isotropic elastic scattering, and relativistic effects due to interactions with a moving background or the presence of a strong gravitational field were not included.
+To solve more realistic problems of higher scientific interest, some or all of these physical effects must be included.  
+In the context of constraint-preserving schemes, these extension provide significant challenges suitable for future investigations, and for which the scheme presented here may serve as a foundation.

### 2018-08-22 Documents/M1/realizableFermionicM1/sections/intro.tex
Work on the introduction

@@
 In this paper we design numerical methods to solve the two-moment model governing transport of particles obeying by Fermi-Dirac statistics (e.g., neutrinos), with the ultimate target being nuclear astrophysics applications (e.g., neutrino transport in core-collapse supernovae and compact binary mergers).
-The numerical method is based on the discontinuous Galerkin (DG) method for spatial discretization, implicit-explicit (IMEX) methods for time integration, and is designed to preserve physical constraints of the underlying model.
+The numerical method is based on the discontinuous Galerkin (DG) method for spatial discretization, implicit-explicit (IMEX) methods for time integration, and is designed to preserve certain physical constraints of the underlying model.
 The latter property is achieved by considering the spatial and temporal discretization together with the closure procedure for the two-moment model.
@@
 
-\clearpage
-
 In a truncated moment model, the equation governing the evolution of the $N$-th moment $m^{(N)}$ contains higher moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified in order to form a closed system of equations.
 For the two-moment model, the symmetric rank-two Eddington tensor (proportional to the pressure tensor) must be specified.  
-Solutions to the closure problem include setting $m^{(k)}=0$, for $k>N$ ($P_N$ approximation \cite{brunnerHolloway_2005}), Eddington approximation \cite{mihalasMihalas_1999}, Kershaw-type closure \cite{kershaw_1976}, and maximum entropy closure \cite{minerbo_1978,cernohorskyBludman_1994}.
+Approaches to this \emph{closure problem} include setting $m^{(k)}=0$, for $k>N$ ($P_N$ approximation \cite{brunnerHolloway_2005}), Eddington approximation \cite{mihalasMihalas_1999}, Kershaw-type closure \cite{kershaw_1976}, and maximum entropy closure \cite{minerbo_1978,cernohorskyBludman_1994}.
 The closure procedure often results in a system of nonlinear hyperbolic conservation laws, which can be solved using suitable numerical methods (e.g., \cite{leveque_1992}).
+
 One challenge in solving the closure problem is constructing a sequence of moments that are consistent with a positive distribution function, which typically implies algebraic constraints on the moments \cite{kershaw_1976,levermore_1984}.
 Moments satisfying these constraints are called \emph{realizable moments} (e.g., \cite{levermore_1996}).  
-When evolving a truncated moment model numerically, maintaining realizable moments is challenging, but necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and (mathematical) entropy dissipation.
+When evolving a truncated moment model numerically, maintaining realizable moments is challenging, but necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and (mathematical) entropy dissipation (\ee{Need citations here}).
 In addition to putting the validity of the numerical results into question, failure to maintain moment realizability in a numerical model may, in order to continue a simulation, require ad hoc post-processing steps with undesirable consequences such as loss of conservation.
@@
 Furthermore, the set of realizable moments generated by the particle density and flux vector constitutes a convex cone \cite{olbrant_etal_2012}.  
-In the fermionic case, there is also an upper bound on the distribution function because Pauli's exclusion principle prevents particles from occupying the same microscopic state.  
+In the fermionic case, there is also an upper bound on the distribution function because Pauli's exclusion principle prevents particles from occupying the same microscopic state (e.g., $f\le1$).  
 The fermionic two-moment model has recently been studied theoretically in the context of maximum entropy closures \cite{lareckiBanach_2011,banachLarecki_2013,banachLarecki_2017b} and Kershaw-type closures \cite{banachLarecki_2017a}.
@@
 This splitting has some advantages when solving kinetic equations since the collisional interactions may couple across momentum space, but are local in position space, and is easier to parallelize than a fully implicit approach.
+
 The CP framework of \cite{zhangShu_2010a} achieve high order (i.e., greater than first order) accuracy in time by employing explicit strong stability-preserving Runge-Kutta (SSP-RK) methods \cite{shuOsher_1988,gottlieb_etal_2001}, which can be written as a convex combination of forward Euler steps.
-Unfortunately, this strategy to achieve high order temporal accuracy does not work for standard IMEX Runge-Kutta (IMEX-RK) methods because implicit SSP Runge-Kutta methods with greater than first order accuracy do not exist \cite{gottlieb_etal_2001}.
+Unfortunately, this strategy to achieve high order temporal accuracy does not work as straightforwardly for standard IMEX Runge-Kutta (IMEX-RK) methods because implicit SSP Runge-Kutta methods with greater than first order accuracy do not exist \cite{gottlieb_etal_2001}.
 To break this ``barrier'', recently proposed IMEX-RK schemes \cite{chertock_etal_2015,hu_etal_2018} have resorted to first order accuracy in favor of the SSP property in the standard IMEX-RK scheme, and recover second-order accuracy with a correction step.
-We consider the application of this approach to the two-moment model.  
-With the correction step from \cite{chertock_etal_2015} we are unable to prove the realizability-preserving property without invoking a too restrictive time step.  
-With the correction step from \cite{hu_etal_2018} the realizability-preserving property is guaranteed with a time step comparable to that of the forward Euler method, but the resulting scheme performs poorly in the asymptotic diffusion limit.
-Because of these challenges, we resort to first-order accuracy, and propose IMEX-RK schemes that are realizability-preserving with a time step equal to that of forward Euler, perform well in the diffusion limit, and reduce to a second-order SSP-RK scheme in the streaming limit (no collisions with the background material).
+
+We consider the application of the correction approach to the two-moment model.  
+However, with the correction step from \cite{chertock_etal_2015} we are unable to prove the realizability-preserving property without invoking a too restrictive time step.  
+With the correction step from \cite{hu_etal_2018} the realizability-preserving property is guaranteed with a time step comparable to that of the forward Euler method applied to the explicit part of the scheme, but the resulting scheme performs poorly in the asymptotic diffusion limit.
+Because of these challenges, we resort to first-order temporal accuracy, and propose IMEX-RK schemes that are constraint-preserving with a time step equal to that of forward Euler on the explicit part, perform well in the diffusion limit, and reduce to a second-order SSP-RK scheme in the streaming limit (no collisions with the background material).
+
+The realizability-preserving property of the DG-IMEX scheme depends sensitively on the adopted closure procedure.  
+Employing the simple Lax-Friedrichs flux and imposing a suitable CFL condition on the time step, the explicit update of the cell average can be written as a convex combination.  
+Realizability of the updated cell average is then guaranteed from convexity arguments \cite{zhangShu_2010a}, provided all the elements in the convex combination are realizable.  
+Realizability of individual elements in the convex combination is conditional on the closure procedure (components of the Eddington tensor must be computed to evaluate numerical fluxes).  
+We prove that each element in the convex combination is realizable, provided the moments involved in expressing the elements are moments of a distribution function satisfying the bounds implied by Fermi-Dirac statistics (i.e., $0\le f \le 1$).
+For simple algebraic two-moment closures, which we consider, the so-called Eddington factor is given by an algebraic expression depending on the evolved moments and completely determines the components of the Eddington tensor.
+Realizable components of the Eddington tensor demands that the Eddington factor satisfies strict lower and upper bounds (e.g., \cite{levermore_1984,lareckiBanach_2011}).  
+We discuss simple algebraic closures derived from Fermi-Dirac statistics that satisfy these bounds, and demonstrate with numerical experiments that the DG-IMEX scheme preserves realizability of the moments when these closures are used.
+We also demonstrate that further approximations to algebraic two-moment closures for modeling particle systems governed by Fermi-Dirac statistics may give results that are incompatible with a bounded distribution and therefore unphysical.
+The example we consider is the Minerbo closure \cite{minerbo_1978}, which can be obtained as the low occupancy limit of the maximum entropy closure of Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}.
 
@@
 The main results on the realizability-preserving DG-IMEX method for the fermionic two-moment model are worked out in Section~\ref{sec:realizableDGIMEX}.  
-In Section~\ref{sec:limiter} we discuss the realizability-preserving limiter.  
+In Section~\ref{sec:limiter} we discuss the realizability-enforcing limiter.  
 Numerical results are presented in Section~\ref{sec:numerical}, and summary and conclusions are given in Section~\ref{sec:conclusions}.

### 2018-08-22 Documents/M1/realizableFermionicM1/sections/conclusion.tex
Minor edits due to comments from Ran

@@
 We have developed a realizability-preserving DG-IMEX scheme for a two-moment model for fermion transport.  
-The scheme employs simple algebraic two-moment closures rooted in Fermi-Dirac statistics, and combines a CFL condition, a realizability-enforcing limiter, and a constraint-preserving time integrator to maintain point-wise realizability of the moments.
+The scheme employs simple algebraic two-moment closures rooted in Fermi-Dirac statistics, and combines a time step restriction (CFL condition), a realizability-enforcing limiter, and a constraint-preserving time integrator to maintain point-wise realizability of the moments.
 Since the realizable domain is a convex set, the realizability-preserving property is obtained from convexity arguments, building on the framework in \cite{zhangShu_2010a}.
@@
 In this work, we considered a relatively simple model.  
-In particular, we adopted Cartesian coordinates, assumed a linear collision operator and a fixed material background, isotropic elastic scattering, and relativistic effects due to interactions with a moving background or the presence of a strong gravitational field were not included.
+In particular, we adopted Cartesian coordinates, assumed a linear collision operator and a fixed material background.  
+Inelastic scattering and relativistic effects (e.g., due to interactions with a moving background or the presence of a strong gravitational field) were not included.  
 To solve more realistic problems of higher scientific interest, some or all of these physical effects must be included.  

### 2018-08-22 Documents/M1/realizableFermionicM1/sections/realizability.tex
Restricting discussion to 0 < f < 1 to avoid issues on the boundary

@@
 \begin{define}
-  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they can be obtained from a distribution function satisfying $0\le f(\omegaNu) \le 1~\forall~\omegaNu\in\bbS^{2}$.
+  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they can be obtained from a distribution function satisfying $0 < f(\omegaNu) < 1~\forall~\omegaNu\in\bbS^{2}$.
+  \label{def:momentRealizability}
 \end{define}
+\begin{rem}
+  As in \cite{lareckiBanach_2011}, in Definition~\ref{def:momentRealizability}, and in the rest of this paper, we exclude the cases $f=0$ and $f=1$ almost everywhere (a.e.) on $\bbS^{2}$, which would give $\cJ=0$ and $\cJ=1$, respectively.
+\end{rem}
 
-Realizable moments must satisfy algebraic constraints.  
+Realizable moments satisfy algebraic constraints.  
 We proceed by stating the constraints on the moments by restating results from Theorem~7.1 in \cite{banachLarecki_2017a} in the following Lemma.  
@@
 \begin{lemma}
-  Suppose that $0\le f(\omegaNu) \le1~\forall~\omegaNu\in\bbS^{2}$.  
-  Then the moments $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, defined as in Eq.~\eqref{eq:angularMoments}, satisfy $0\le\cJ\le1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}|\ge0$. 
+  Suppose that $0 < f(\omegaNu) < 1~\forall~\omegaNu\in\bbS^{2}$.  
+  Then the moments $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, defined as in Eq.~\eqref{eq:angularMoments}, satisfy $0 < \cJ < 1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}| > 0$. 
   \label{lem:MomentRealizable} 
@@
   \begin{equation}
-    \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in[0,1]~\text{and}~\gamma(\vect{\cM})\equiv(1-\cJ)\cJ-|\vect{\cH}|\ge0\,\big\}.
+    \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in(0,1)~\text{and}~\gamma(\vect{\cM})\equiv(1-\cJ)\cJ-|\vect{\cH}| > 0\,\big\}.
     \label{eq:realizableSet}
@@
   \end{equation*}
-  Since $\cJ_{a},\cJ_{b}\in[0,1]$, it follows that $\cJ_{c} \in [0,1]$.  
-  Since $\cJ_{a},\cJ_{b}\in[0,1]$, it is straightforward to verify that
+  Since $\cJ_{a},\cJ_{b} \in (0,1)$, it follows that $\cJ_{c} \in (0,1)$.  
+  Since $\cJ_{a},\cJ_{b} \in (0,1)$, it is straightforward to verify that
   \begin{equation*}
-  \gamma(\vect{\cM}_{c}) \geq \theta\,\gamma(\vect{\cM}_{a}) + (1-\theta)\,\gamma(\vect{\cM}_{b}) \ge0.
+  \gamma(\vect{\cM}_{c}) \geq \theta\,\gamma(\vect{\cM}_{a}) + (1-\theta)\,\gamma(\vect{\cM}_{b}) > 0.
   \end{equation*}
@@
 \begin{equation}
-  \cR^{+}:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\ge0~\text{and}~\cJ\ge|\vect{\cH}|\,\big\}, 
+  \cR^{+}:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ > 0~\text{and}~\cJ > |\vect{\cH}|\,\big\}, 
   \label{eq:realizableSetPositive}
@@
 \begin{lemma}
-  Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ be defined as in Eq.~\eqref{eq:angularMoments} with distribution function $f_{a}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$.  
-  Similarly, let $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments of a distribution function $f_{b}\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$.  
+  Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ and $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments defined as in Eq.~\eqref{eq:angularMoments} with distribution functions $f_{a}$ and $f_{b}$, respectively, such that $f_{a}(\omega),f_{b}(\omega)\in(0,1)\,\forall\,\omega\in\bbS^{2}$.
   Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector, and $\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})=\big(\widehat{\vect{e}}\cdot\vect{\cH},\widehat{\vect{e}}\cdot\vect{\cK}\big)^{T}$.
@@
   where $f_{ab}(\omegaNu)=\vartheta\,f_{a}(\omegaNu)+(1-\vartheta)\,f_{b}(\omegaNu)$ and $\vartheta(\omegaNu)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omegaNu))/2\in[0,1]$.  
-  Then, since $f_{ab}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
+  Then, since $f_{ab}(\omegaNu)\in(0,1)\,\forall\,\omegaNu\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
 \end{proof}
@@
   where $f_{b}(\omegaNu)=\zeta\,f_{a}(\omegaNu)+(1-\zeta)\,f_{0}$, $\zeta=1/(1+\alpha\,\xi)\in[0,1]$, and $f_{0}$ and $\xi$ are defined in Section~\ref{sec:model}.  
-  Then, since $f_{b}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$, $\cJ_{b}\in[0,1]$.  
+  Then, since $f_{b}(\omegaNu)\in(0,1)\,\forall\,\omegaNu\in\bbS^{2}$, $\cJ_{b}\in(0,1)$.  
   Similarly, we can write
@@
   It follows from Lemma~\ref{lem:MomentRealizable} that $\widetilde{\vect{\bcM}}_{b}=(\cJ_{b},\widetilde{\vect{\cH}}_{b})^{T}\in\cR$.  
-  Then, since $0\le\xi\le1$, we have $|\vect{\cH}_{b}|\le|\widetilde{\vect{\cH}}_{b}|\le(1-\cJ_{b})\,\cJ_{b}$.  
+  Then, since $0\le\xi\le1$, we have $|\vect{\cH}_{b}|\le|\widetilde{\vect{\cH}}_{b}| < (1-\cJ_{b})\,\cJ_{b}$.  
 \end{proof}

### 2018-08-28 Documents/M1/realizableFermionicM1/sections/realizability.tex
reworked section due to comments from Cory

@@
 In this paper, we seek to design a numerical method for solving the system of moment equations given by Eq.~\eqref{eq:momentEquations} that preserves realizability of the moments; i.e., the moments evolve within the set of admissible values as dictated by Pauli's exclusion principle.
-(Since we are only concerned with the angular dependence of $f$ in this section, we simplify the notation by suppressing the $\vect{z}$ and $t$ dependence and write $f(\omegaNu,\vect{z},t)=f(\omegaNu)$.)
+(Since we are only concerned with the angular dependence of $f$ in this section, we simplify the notation by suppressing the $\vect{z}$ and $t$ dependence and write $f(\omega,\vect{z},t)=f(\omega)$.)
 
@@
 \begin{define}
-  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they can be obtained from a distribution function satisfying $0 < f(\omegaNu) < 1~\forall~\omegaNu\in\bbS^{2}$.
+  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they can be obtained from a distribution function satisfying $0 < f(\omega) < 1~\forall~\omega\in\bbS^{2}$.
   \label{def:momentRealizability}
@@
 \begin{lemma}
-  Suppose that $0 < f(\omegaNu) < 1~\forall~\omegaNu\in\bbS^{2}$.  
+  Suppose that $0 < f(\omega) < 1~\forall~\omega\in\bbS^{2}$.  
   Then the moments $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, defined as in Eq.~\eqref{eq:angularMoments}, satisfy $0 < \cJ < 1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}| > 0$. 
@@
 %  \end{equation}  
-%  Since $f(\omegaNu)\in[0,1]$, we have $\mathfrak{f}(\mu)\in[0,1]$, which implies $\cJ\in[0,1]$.  
+%  Since $f(\omega)\in[0,1]$, we have $\mathfrak{f}(\mu)\in[0,1]$, which implies $\cJ\in[0,1]$.  
 %  Next we need to show that $|\vect{\cH}|\le(1-\cJ)\,\cJ$.  
-%  Let $\widehat{\vect{n}}\in\bbR^{3}$ (independent of $\omegaNu$) be an arbitrary unit vector, and write
+%  Let $\widehat{\vect{n}}\in\bbR^{3}$ (independent of $\omega$) be an arbitrary unit vector, and write
 %  \begin{equation}
@@
   \begin{equation*}
-    \cJ_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omegaNu)\,d\omegaNu
+    \cJ_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omega)\,d\omega
     \quad\text{and}\quad
-    \vect{\cH}_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omegaNu)\,\vect{\ell}(\omegaNu)\,d\omegaNu,
+    \vect{\cH}_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omega)\,\vect{\ell}(\omega)\,d\omega,
   \end{equation*}
-  where $f_{ab}(\omegaNu)=\vartheta\,f_{a}(\omegaNu)+(1-\vartheta)\,f_{b}(\omegaNu)$ and $\vartheta(\omegaNu)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omegaNu))/2\in[0,1]$.  
-  Then, since $f_{ab}(\omegaNu)\in(0,1)\,\forall\,\omegaNu\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
+  where $f_{ab}(\omega)=\vartheta\,f_{a}(\omega)+(1-\vartheta)\,f_{b}(\omega)$ and $\vartheta(\omega)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omega))/2\in[0,1]$.  
+  Then, since $f_{ab}(\omega)\in(0,1)\,\forall\,\omega\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
 \end{proof}
@@
   \begin{equation*}
-    \cJ_{b}=\f{1}{4\pi}\int_{\bbS}f_{b}(\omegaNu)\,d\omegaNu,
+    \cJ_{b}=\f{1}{4\pi}\int_{\bbS}f_{b}(\omega)\,d\omega,
   \end{equation*}
-  where $f_{b}(\omegaNu)=\zeta\,f_{a}(\omegaNu)+(1-\zeta)\,f_{0}$, $\zeta=1/(1+\alpha\,\xi)\in[0,1]$, and $f_{0}$ and $\xi$ are defined in Section~\ref{sec:model}.  
-  Then, since $f_{b}(\omegaNu)\in(0,1)\,\forall\,\omegaNu\in\bbS^{2}$, $\cJ_{b}\in(0,1)$.  
+  where $f_{b}(\omega)=\zeta\,f_{a}(\omega)+(1-\zeta)\,f_{0}$, $\zeta=1/(1+\alpha\,\xi)\in[0,1]$, and $f_{0}$ and $\xi$ are defined in Section~\ref{sec:model}.  
+  Then, since $f_{b}(\omega)\in(0,1)\,\forall\,\omega\in\bbS^{2}$, $\cJ_{b}\in(0,1)$.  
   Similarly, we can write
@@
     \quad\text{where}\quad
-    \widetilde{\vect{\cH}}_{b}=\f{1}{4\pi}\int_{\bbS^{2}}f_{b}(\omegaNu)\,\vect{\ell}(\omegaNu)\,d\omegaNu.  
+    \widetilde{\vect{\cH}}_{b}=\f{1}{4\pi}\int_{\bbS^{2}}f_{b}(\omega)\,\vect{\ell}(\omega)\,d\omega.  
   \end{equation*}

### 2018-08-28 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Reworked section due to comments from Cory

@@
 The Lagrange multipliers are implicit functions of $\cJ$ and $\vect{\cH}$.  
-The ME distribution function satisfies $0 \le f_{\mbox{\tiny ME}} \le 1$, but $a$ and $\vect{b}$ are unconstrained.  
+The ME distribution function satisfies $0 < f_{\mbox{\tiny ME}} < 1$, but $a$ and $\vect{b}$ are unconstrained.  
 Specification of $a$ and $\vect{b}$ from $\vect{\cM}=(\cJ,\vect{\cH})^{T}$ gives $f_{\mbox{\tiny ME}}$, and any number of moments can in principle be computed.  
@@
 
-For a bounded distribution $0<f<1$, it is possible to show that the second moment satisfies
+For a bounded distribution $0<f<1$, it is possible to show (e.g., \cite{banachLarecki_2013}) that the second moment satisfies
 \begin{equation}
@@
 \end{equation}
-where $\cK_{\mbox{\tiny L}}=\cJ\,\big(\,\f{1}{3}\,\cJ^{2}+h^{2}\,\big)$, $\cK_{\mbox{\tiny U}}=\cK_{\mbox{\tiny L}} + \cJ\,(1-\cJ)\,(1-x^{2})$, and $x=h/(1-\cJ)$.  
-By convexity, the convex combination
+where $\cK_{\mbox{\tiny L}}=\cJ\,\big(\,\f{1}{3}\,\cJ^{2}+h^{2}\,\big)$, $\cK_{\mbox{\tiny U}}=\cK_{\mbox{\tiny L}} + \cJ\,(1-\cJ)\,(1-x^{2})$, and $x$ is the flux saturation defined in Eq.~\eqref{eq:fluxSaturation}.
+By convexity of the realizable set generated by the moments in Eq.~\eqref{eq:scalarMoments}, the convex combination
 \begin{equation}
@@
 with $\beta\in[0,1]$, is realizable for realizable moments $(\cJ,\cH)^{T}\in\cR$.  
-The Kershaw closure for the two-moment model is then obtained from the ansatz in Eq.~\eqref{eq:kershawAnsatz} with the additional requirement that it be correct in the limit of isotropic distribution functions; i.e., $\cK(\beta,\cJ,0)=\cJ/3$.
+The Kershaw closure for the two-moment model is then obtained from Eq.~\eqref{eq:kershawAnsatz} with the additional requirement that it be correct in the limit of isotropic distribution functions; i.e., $\cK(\beta,\cJ,0)=\cJ/3$.
 One choice for $\beta$, which leads to a strictly hyperbolic and causal two-moment model (and a particularly simple closure function) \cite{banachLarecki_2017a}, is $\beta=(2-\cJ)/3$, so that $\cK_{\mbox{\tiny K}}(\cJ,h)=\chi_{\mbox{\tiny K}}(\cJ,h)\,\cJ$, where
@@
 For multidimensional problems, the Kershaw closure is obtained by using the Eddington factor in Eq.~\eqref{eq:eddingtonFactorKershaw} in Eq.~\eqref{eq:eddingtonTensor}.  
-Finally, we point out that for the two-moment Kershaw closure (see \cite{banachLarecki_2017a} for details), a distribution function $f_{\mbox{\tiny K}}(\vect{\ell},\cJ,\vect{\cH})$, satisfying $0\le f_{\mbox{\tiny K}}\le1$, and reproducing the moments $\cJ$, $\vect{\cH}$, and $\vect{\cK}$, can be written explicitly in terms of Heaviside functions.
+Finally, we point out that for the two-moment Kershaw closure (see \cite{banachLarecki_2017a} for details), a distribution function $f_{\mbox{\tiny K}}(\vect{\ell},\cJ,\vect{\cH})$, satisfying $0 < f_{\mbox{\tiny K}} < 1$, and reproducing the moments $\cJ$, $\vect{\cH}$, and $\vect{\cK}$, can be written explicitly in terms of Heaviside functions.
 
@@
 In particular, the realizability-preserving scheme developed in this paper is based on the result in Lemma~\ref{lem:explicitStep}, which must hold for the adapted closure.  
-The Kershaw closure is consistent with a bounded distribution, $f_{_{\mbox{\tiny K}}}\in[0,1]$, and should be well suited, but the algebraic ME closures are based on approximations to the closure function, and we need to consider if these approximate closures remain consistent with the assumed bounds on the underlying distribution function.
-To this end, we rely on results due to \cite{levermore_1984,lareckiBanach_2011} (see also \cite{kershaw_1976,shohatTamarkin_1943}):  Realizability of the moment triplet $\{\cJ,\vect{\cH},\vect{\cK}\}$ (i.e., they are consistent with a bounded distribution function $0 \le f<1$), with $\vect{\cM}=(\cJ,\vect{\cH})^{T}\in\cR$ and $\vect{\cK}$ given by Eq.~\eqref{eq:eddingtonTensor}, is equivalent to the following requirement for the Eddington factor
+The Kershaw closure is consistent with a bounded distribution, $f_{_{\mbox{\tiny K}}}\in(0,1)$, and should be well suited, but the algebraic ME closures are based on approximations to the closure function, and we need to consider if these approximate closures remain consistent with the assumed bounds on the underlying distribution function.
+To this end, we rely on results in \cite{levermore_1984,lareckiBanach_2011} (see also \cite{kershaw_1976,shohatTamarkin_1943}), which state that realizability of the moment triplet $\{\cJ,\vect{\cH},\vect{\cK}\}$ (with $\vect{\cK}$ given by Eq.~\eqref{eq:eddingtonTensor}), is equivalent to the following requirement for the Eddington factor
 \begin{equation}
@@
 Fortunately, these bounds are satisfied by the algebraic closures based on Fermi-Dirac statistics.  
-(Note that for $\cJ\ll1$ the bounds in Eq.~\eqref{eq:eddingtonFactorBounds} limit to the bounds for positive distributions given by Levermore \cite{levermore_1984}; i.e., $h^{2}\le\chi\le1.$)
+(Note that for $\cJ\ll1$ the bounds in Eq.~\eqref{eq:eddingtonFactorBounds} limit to the bounds for positive distributions given by Levermore \cite{levermore_1984}; i.e., $h^{2}<\chi<1$.)
 
-In Figure~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor $\chi$ versus the flux factor $h\,(\le 1-\cJ)$ for the various algebraic closures discussed above and for different values of $\cJ\in(0,1)$: $0.01$ (upper left panel), $0.4$ (upper right panel), $0.6$ (lower left panel), and $0.99$ (lower right panel).
+In Figure~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor $\chi$ versus the flux factor $h$ for the various algebraic closures discussed above and for different values of $\cJ\in(0,1)$: $0.01$ (upper left panel), $0.4$ (upper right panel), $0.6$ (lower left panel), and $0.99$ (lower right panel).
 The maximum entropy closures of CB and BL are plotted with solid red and dashed orange lines respectively.  
@@
 We note that for all the closures, the Eddington factor $\chi\to1/3$ as $h\to0^{+}$.
+
 For $\cJ=0.01$, the maximum entropy closures (CB, BL, and Minerbo) are practically indistinguishable, while the Eddington factor of the Kershaw closure is clearly larger than that of the other closures over most of the domain.
 For $\cJ=0.4$, the Eddington factor for the closures based on Fermi-Dirac statistics (CB, BL, and Kershaw) remain close together, while the Eddington factor for the Minerbo closure is clearly larger than the other closures for $h\gtrsim0.2$.
-All closures remain between $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ for $\cJ=0.01$ and $\cJ=0.4$.  
+The Eddington factor for all closures remain between $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ for $\cJ=0.01$ and $\cJ=0.4$.
+
 For $\cJ=0.6$, the Eddington factor for the closures based on Fermi-Dirac statistics remain close together and within the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.  
-The dependence of the Eddington factor on $h$ of the Minerbo closure is clearly different from the other closures (i.e., increases vs decreases with increasing $h$), and exceeds $\chi_{\mbox{\tiny max}}$ for $h\gtrsim0.34$.
+The dependence of the Eddington factor on $h$ for the Minerbo closure is clearly different from the other closures (i.e., increases vs decreases with increasing $h$), and exceeds $\chi_{\mbox{\tiny max}}$ for $h\gtrsim0.34$.
 For $\cJ=0.99$, the Eddington factor of the CB and BL closures (indistinguishable) and the Kershaw closure remain within the bounds given in Eq.~\eqref{eq:eddingtonFactorBounds}.  
 The Eddington factor of the Minerbo closure is nearly flat, and exceeds $\chi_{\mbox{\tiny max}}$ for $h\gtrsim0.006$.
+
 \begin{figure}[h]
@@
 \end{figure}
-We have also checked that for all the algebraic closures based on Fermi-Dirac statistics (CB, BL, and Kershaw), the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds} holds for all $\vect{\cM}\in\cR$.
+We have also checked numerically that for all the algebraic closures based on Fermi-Dirac statistics (CB, BL, and Kershaw), the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds} holds for all $\vect{\cM}\in\cR$.
 Thus, we conclude that these closures are suited for development of realizability-preserving numerical methods for the two-moment model of fermion transport.

### 2018-08-28 Documents/M1/realizableFermionicM1/sections/appendix.tex
Reworked section due to comments from Cory

@@
 
-For the analysis of positivity-preserving IMEX schemes, additional coefficients are defined \cite{hu_etal_2018} (cf. Eq.~\eqref{eq:imexStagesRewrite}).  
+For the analysis of constraint-preserving IMEX schemes, additional coefficients are defined \cite{hu_etal_2018} (cf. Eq.~\eqref{eq:imexStagesRewrite}).  
 First, let
@@
 
-A second-order accurate, positivity-preserving IMEX scheme of type $A$ (the matrix $A$ is invertible) was given in \cite{hu_etal_2018}.  
+A second-order accurate, constraint-preserving IMEX scheme of type $A$ (the matrix $A$ is invertible) was given in \cite{hu_etal_2018}.  
 We refer to this scheme as IMEX PA2.  
@@
 
-We have found another second-order accurate, positivity-preserving IMEX scheme of type $A$, which we refer to as IMEX PA2+.  
-This scheme allows for has a larger $c_{\mbox{\tiny Sch}}$ than IMEX PA2 (i.e., a larger time step while maintaining positivity).  
+We have found another second-order accurate, constraint-preserving IMEX scheme of type $A$, which we refer to as IMEX PA2+.  
+This scheme allows for a larger value of $c_{\mbox{\tiny Sch}}$ than IMEX PA2 (i.e., a larger time step while maintaining admissible solutions).  
 The scheme was found by random sampling of the parameter space spanned by the IMEX coefficients, optimizing $c_{\mbox{\tiny Sch}}$.  
@@
 
-We have found diffusion accurate, positivity-preserving IMEX schemes of type ARS that are second-order accurate in the streaming limit, which we refer to as IMEX PD-ARS; see \ref{app:PD-ARS}.  
+We have found diffusion accurate, constraint-preserving IMEX schemes of type ARS that are second-order accurate in the streaming limit, which we refer to as IMEX PD-ARS; see \ref{app:PD-ARS}.  
 For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.
@@
 \end{equation}
-The positivity-preserving property follows from imposing the inequality constraints $a_{22},a_{33}>0$, $c_{20},c_{30},c_{32}\ge0$, and $\tilde{c}_{20},\tilde{c}_{30},\tilde{c}_{32}\ge0$, which imply
+The positivity-preserving property follows from imposing the inequality constraints $a_{22},a_{33}>0$, $c_{20},c_{30},c_{32}\ge0$, and $\tilde{c}_{20},\tilde{c}_{30},\tilde{c}_{32}\ge0$, which imply that
 \begin{equation}
@@
 We chose $x=\f{1}{2}$, so that the explicit part of the IMEX scheme is equivalent to the optimal second-order SSP-RK scheme in \cite{gottlieb_etal_2001} (SSPRK2 in \ref{app:butcherTables}).  
-Then, $y=\f{1}{2} + \epsilon$, where $\epsilon \in [0, \frac{1}{2})$ and $c_{\mbox{\tiny Sch}} = 1 - 2\epsilon$, results in the PD-ARS IMEX scheme.  
+Then, $y=\f{1}{2} + \epsilon$, where $\epsilon \in [0, \frac{1}{2})$, and $c_{\mbox{\tiny Sch}} = 1 - 2\epsilon$ results in the PD-ARS IMEX scheme.  
 Setting $\epsilon = 0$ gives the optimal scheme with $c_{\mbox{\tiny Sch}} = 1$.

### 2018-08-28 Documents/M1/realizableFermionicM1/sections/imex.tex
Reworked section due to comments from Cory

@@
-\section{Positivity-Preserving IMEX Schemes}
+\section{Constraint-Preserving IMEX Schemes}
 \label{sec:imex}
@@
 
-\subsection{Second-Order Accurate, Positivity-Preserving IMEX Schemes}
+Eq.~\eqref{eq:ode} is to be integrated forward in time with an ODE integrator, and we begin with the following definition of a constraint-preserving time integration scheme, as applied to integrate a physical model forward in time.
+\begin{define}
+  Given sufficient conditions, a constraint-preserving time integration scheme preserves the constraints of a model if the set of admissible states satisfying the constraints form a convex set.  
+  \label{def:constraintPreserving}
+\end{define}
+As an example, given a spatial discretization of a model that is constraint-preserving with the forward Euler method for a sufficiently small time step, high-order strong stability-preserving Runge-Kutta (SSP-RK) methods, which can be expressed as convex combinations of forward Euler steps, form a class of constraint-preserving schemes.
+
+\subsection{Second-Order Accurate, Constraint-Preserving IMEX Schemes}
 
@@
 Our goal is to employ IMEX schemes that preserve realizability of the moments, subject only to a time step governed by the explicit transport operator and comparable to the time step required for numerical stability of the explicit scheme.
-(The realizability-preserving and positivity-preserving properties of an IMEX scheme are intimately related, and we use the two phrases interchangeably.)  
-Unfortunately, high-order (second or higher order temporal accuracy) positivity-preserving IMEX methods with time step restrictions solely due to the transport operator do not exist (see for example Proposition~6.2 in \cite{gottlieb_etal_2001}, which rules out the existence of strong stability-preserving implicit Runge-Kutta methods of order higher than one).
-To overcome this barrier, Chertock et al. \cite{chertock_etal_2015} presented IMEX schemes with a correction step, which recovers second-order accuracy.  
-However, the correction step in \cite{chertock_etal_2015} involves both the transport and collision operators, and we have found that realizability is then subject to a time step restriction that depends on $\tau$, which may become too restrictive for stiff problems.
+We seek to achieve this goal with constraint-preserving IMEX schemes.
+
+Unfortunately, high-order (second or higher order temporal accuracy) constraint-preserving IMEX methods with time step restrictions solely due to the transport operator do not exist (see for example Proposition~6.2 in \cite{gottlieb_etal_2001}, which rules out the existence of implicit SSP-RK methods of order higher than one).
+To overcome this barrier, Chertock et al. \cite{chertock_etal_2015} presented IMEX schemes with a correction step.  
+These schemes are SSP but only first-order accurate within the standard IMEX framework.  
+The correction step is introduced to recover second-order accuracy.  
+However, the correction step in \cite{chertock_etal_2015} involves both the transport and collision operators, and we have found that, when applied to the fermionic two-moment model, realizability is subject to a time step restriction that depends on $\tau$, which may become too restrictive for stiff problems.
 More recently, Hu et al.
 \cite{hu_etal_2018}, presented similar IMEX schemes for problems involving BGK-type collision operators, but with a correction step that does not include the transport operator.
-In this case, positivity is only subject to time step restrictions stemming from the transport operator, which is more attractive for our target application.  
+In this case, the scheme is constraint-preserving, subject only to time step restrictions stemming from the transport operator, which is more attractive for our target application.  
 These second-order accurate, $s$-stage IMEX schemes take the following form \cite{hu_etal_2018}
@@
 For globally stiffly accurate (GSA) IMEX schemes, $\tilde{w}_{i}=\tilde{a}_{si}$ and $w_{i}=a_{si}$ for $i=1,\ldots,s$, so that $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$ \cite{ascher_etal_1997}.  
-This property is beneficial for very stiff problems, and also simplifies the proof of the realizability-preserving property of the IMEX scheme since it eliminates the assembly step in Eq.~\eqref{imexIntermediate}.
+This property is beneficial for very stiff problems, and also simplifies the proof of the realizability-preserving property of the DG-IMEX scheme given in Section~\ref{sec:realizableDGIMEX} since it eliminates the assembly step in Eq.~\eqref{imexIntermediate}.
 
-To prove the positivity-preserving property of the IMEX scheme, Hu et al. \cite{hu_etal_2018} rewrite the stage values in Eq.~\eqref{imexStages} in the following form
+Hu et al. \cite{hu_etal_2018} rewrite the stage values in Eq.~\eqref{imexStages} in the following form
 \begin{equation}
@@
 For IMEX schemes of type~ARS, the matrix $A$ can be written as
-\[\left( 
+\begin{equation*}
+  \left( 
     \begin{matrix} 
@@
     \end{matrix}
-\right)\]
+  \right),
+\end{equation*}
 where $\hat{A}$ is invertible.  
 In writing the stages in the IMEX scheme in the general form given by Eq.~\eqref{eq:imexStagesRewrite}, it should be noted that $\tilde{c}_{i0}=0$ for IMEX schemes of Type~A, and $c_{i1}=\tilde{c}_{i1}=0$ for IMEX schemes of Type~ARS \cite{hu_etal_2018}.
-For type A schemes, the positivity-preserving property follows from requiring 
+Type A schemes can be made constraint-preserving by requiring 
 \begin{align}
@@
 \end{align}
-For type ARS schemes, positivity follows from requiring 
+Similarly, type ARS schemes can be made constraint-preserving by requiring 
 \begin{align}
@@
 \end{align}
-Such coefficients were given in \cite{hu_etal_2018} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
-(It was also proven that $s=3$ and $s=4$ are the necessary number of stages needed for GSA second-order positivity-preserving IMEX schemes of type A and type ARS, respectively.)
+Coefficients were given in \cite{hu_etal_2018} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
+(It was also proven that $s=3$ and $s=4$ are the necessary number of stages needed for GSA second-order constraint-preserving IMEX schemes of type A and type ARS, respectively.)
 
-Importantly, the coefficients $c_{ij}$ in Eq.~\eqref{eq:imexStagesRewrite} satisfy $\sum_{j=0}^{i-1}c_{ij}=1$, which implies the so-called Shu-Osher form of the explicit part \cite{shuOsher_1988}.  
-If the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} --- which is in the form of a forward Euler update with time step $\hat{c}_{ij}\,\dt$ --- is positive for all $i=1,\ldots,s$, and $j=0,\ldots,i-1$, then positivity of the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} follows from convexity arguments.
-Thus, if the explicit update with the transport operator is positive for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is positivity-preserving for a time step $\dt\le c_{\mbox{\tiny Sch}}\,\dt_{\mbox{\tiny Ex}}$, where
+For the scheme to be constraint-preserving, the coefficients $c_{ij}$ in Eq.~\eqref{eq:imexStagesRewrite} must also satisfy $\sum_{j=0}^{i-1}c_{ij}=1$, which implies the so-called Shu-Osher form of the explicit part \cite{shuOsher_1988}.
+If the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} --- which is in the form of a forward Euler update with time step $\hat{c}_{ij}\,\dt$ --- is in the (convex) set of admissible states for all $i=1,\ldots,s$, and $j=0,\ldots,i-1$, then it follows from convexity arguments that the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} is also admissible.
+Thus, if the explicit update with the transport operator is admissible for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is constraint-preserving for a time step $\dt\le c_{\mbox{\tiny Sch}}\,\dt_{\mbox{\tiny Ex}}$, where
 \begin{equation}
@@
 \end{equation}
+Here, $c_{\mbox{\tiny Sch}}$ is the CFL condition, relative to $\dt_{\mbox{\tiny Ex}}$, for the IMEX scheme to be constraint-preserving.  
 It is desirable to make $c_{\mbox{\tiny Sch}}$ as large (close to $1$) as possible.  
-Note that positivity of $\vect{u}^{(i)}$ also requires the implicit solve (equivalent to implicit Euler) to preserve positivity.  
-In \cite{hu_etal_2018}, Hu et al. provide examples of GSA, positivity-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
-In \ref{app:butcherTables}, we provide another example of a GSA, positivity-preserving IMEX scheme of type A (scheme PA2+), with a larger $c_{\mbox{\tiny Sch}}$ (a factor of about $1.7$ larger).
+Note that for $\vect{u}^{(i)}$ to be admissible also requires the implicit solve (equivalent to implicit Euler) to be constraint-preserving.  
+In \cite{hu_etal_2018}, Hu et al. provide examples of GSA, constraint-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
+In \ref{app:butcherTables}, we provide another example of a GSA, constraint-preserving IMEX scheme of type A (scheme PA2+), with a larger $c_{\mbox{\tiny Sch}}$ (a factor of about $1.7$ larger).
 
-\subsection{Positivity-Preserving, Diffusion Accurate IMEX (PD-IMEX) Schemes}
+\subsection{Constraint-Preserving, Diffusion Accurate IMEX Schemes}
 
-Unfortunately, the correction step in Eq.~\eqref{eq:imexCorrection} deteriorates the accuracy of the IMEX scheme when applied to the moment equations in the diffusion limit ($\xi=0$, $\tau\ll 1$), where $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$.
-In the diffusion limit, to leading order in $\tau$, we then have $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$, which is due to a balance between the transport term and the collision term in the equation for the particle flux $\vect{\cH}$.
-The absence of the transport operator in the correction step, destroys this balance.  
-We demonstrate the inferior performance of IMEX schemes with the correction step given by Eq.~\eqref{eq:imexCorrection} in the diffusion limit in Section~\ref{sec:smoothProblems}.  
+Unfortunately, the correction step in Eq.~\eqref{eq:imexCorrection} deteriorates the accuracy of the IMEX scheme when applied to the moment equations in the diffusion limit.  
+The diffusion limit is characterized by frequent collisions ($\tau\ll 1$) in a purely scattering medium ($\xi=0$), and exhibits long-time behavior governed by (e.g., \cite{jinLevermore_1996})
+\begin{equation}
+  \pd{\cJ}{t} + \nabla\cdot\vect{\cH} = 0
+  \quad\text{and}\quad
+  \vect{\cH} = - \tau\,\nabla\cdot\vect{\cK}.  
+  \label{eq:diffusionLimit}
+\end{equation}
+Here the time derivative term in the equation for the particle flux has been dropped (formally $\cO(\tau^{2})$) so that, to leading order in $\tau$, the second equation in Eq.~\eqref{eq:diffusionLimit} states a balance between the transport term and the collision term.
+Furthermore, in the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$.  
+The absence of the transport operator in the correction step in Eq.~\eqref{eq:imexCorrection}, destroys the balance between the transport term and the collision term.  
+We demonstrate the inferior performance of IMEX schemes with this correction step in the diffusion limit in Section~\ref{sec:smoothProblems}.  
 We have also implemented and tested one of the IMEX schemes in Chertock et al.
-\cite{chertock_etal_2015}, where the transport operator is included in the correction step, and found it to perform very well in the diffusion limit.
+\cite{chertock_etal_2015} (not included in Section~\ref{sec:smoothProblems}), where the transport operator is part of the correction step, and found it to perform very well in the diffusion limit.
 However, we have not been able to prove the realizability-preserving property with this approach without invoking a too severe time step restriction.  
-We therefore proceed to design positivity-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
+We therefore proceed to design constraint-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
 We limit the scope to IMEX schemes of type~ARS.  
@@
 
-To this end we take a heuristic approach and define the vectors 
+We take a heuristic approach to determine conditions on the coefficients of the IMEX scheme to ensure it performs well in the diffusion limit.  
+Define the vectors 
 \begin{equation}
@@
 \end{equation}
-In the context of IMEX schemes, the diffusion limit balance implies that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold to relate the stage values in Eq.~\eqref{imexStages}.
-Define the inverse of the implicit coefficient matrix for IMEX schemes of type~ARS as
+We can then write the stages of the IMEX scheme in Eq.~\eqref{imexStages} applied to the number density equation as
+\begin{equation}
+  \vec{\cJ}=\cJ^{n}\,\vec{\vect{e}} - \dt\,\tilde{A}\,\nabla\cdot\vec{\vect{\cH}}, 
+  \label{eq:numberDensityIMEX}
+\end{equation}
+where $\vec{\vect{e}}$ is a vector of length $s$ containing all ones, and the divergence operator acts individually on the components of $\vec{\vect{\cH}}$.  
+Similarly, for the number flux equation we have
+\begin{equation}
+  \vec{\vect{\cH}}=\vect{\cH}^{n}\,\vec{\vect{e}}-\dt\,\big(\,\f{1}{3}\tilde{A}\,\nabla\vec{\cJ}+\f{1}{\tau}\,A\,\vec{\vect{\cH}}\,\big).
+  \label{eq:numberFluxIMEX}
+\end{equation}
+In the context of IMEX schemes, the diffusion limit (cf.
+the second equation in \eqref{eq:diffusionLimit}) implies that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold.
+Define the pseudoinverse of the implicit coefficient matrix for IMEX schemes of type~ARS as
 \begin{equation*}
@@
 \end{equation*}
-For the stages $i=1,\ldots,s$ we have
+For the stages $i=1,\ldots,s$ we then have
 \begin{equation}
-  \vect{\cH}^{(i)}=-\f{1}{3}\,\tau\,\vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e}\,\nabla\cJ^{n}+\cO(\dt\,\tau),
+  \vect{\cH}^{(i)}=-\f{1}{3}\,\tau\,\vec{\vect{e}}_{i}^{T}A^{-1}\tilde{A}\,\vec{\vect{e}}\,\nabla\cJ^{n}+\cO(\dt\,\tau^{2}),
 \end{equation}
-where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix and $\vect{e}=(1,\ldots,1)^{T}$.  
+where $\vec{\vect{e}}_{i}$ is the $i$th column of the $s\times s$ identity matrix, and we have introduced the expansion $\vec{\cJ}=\cJ^{n}\vec{\vect{e}}+\cO(\dt\,\tau)$.  
 Thus, for $\vect{\cH}^{(i)}$ to be accurate in the diffusion limit, we require the IMEX coefficients to satisfy
@@
   =-\tilde{\vect{w}}^{T}(\nabla\cdot\vec{\vect{\cH}})
-  \approx\f{1}{3}\tau\,\nabla^{2}\cJ^{n}, 
+  =\f{1}{3}\tau\,\nabla^{2}\cJ^{n}+\cO(\dt\,\tau^{2}), 
 \end{equation}
-which approximates a diffusion equation with the correct diffusion coefficient $\tau/3$.  
-Unfortunately, the ``diffusion limit requirement" in Eq.~\eqref{eq:diffusionCondition}, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints.
-\footnote{It was shown in \cite{hu_etal_2018} --- without the diffusion limit requirement --- that the minimum number of stages for positivity-preserving IMEX schemes of type~ARS is four.)  
+which approximates a diffusion equation for $\cJ$ with the correct diffusion coefficient $\tau/3$.  
+(For a GSA IMEX scheme without the correction step, $\cJ^{n+1}=\cJ^{(s)}$.)
+
+Unfortunately, the ``diffusion limit requirement" in Eq.~\eqref{eq:diffusionCondition}, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints to obtain a constraint-preserving IMEX scheme.
+\footnote{It was shown in \cite{hu_etal_2018} --- without the diffusion limit requirement --- that the minimum number of stages for constraint-preserving IMEX schemes of type~ARS is four.)  
 We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators (e.g., inelastic scattering).}
@@
 \begin{define}
-  Let PD-IMEX be a consistent, positivity-preserving, diffusion accurate, and low-stage GSA IMEX scheme satisfying the following properties
+  Let PD-IMEX be a consistent, constraint-preserving, diffusion accurate, and low-stage GSA IMEX scheme satisfying the following properties
   \begin{enumerate}
@@
     \item Second-order in the streaming limit; i.e., satisfies Eq.~\eqref{eq:orderConditionsEx}.
-    \item Positivity-preserving (conditions given by \cite{hu_etal_2018}; with $c_{\mbox{\tiny Sch}}>0$).
+    \item Constraint-preserving; i.e. satisfies Eq.~\eqref{eq:positivityConditionsTypeARS}, with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\mbox{\tiny Sch}}>0$.
     \item Well-behaved in the diffusion limit; i.e., satisfies Eq.~\eqref{eq:diffusionCondition}.
-    \item Few stages ($s\le3$).
-    \item Globally stiffly accurate (GSA)
-    \begin{equation*}
-      a_{si}=w_{i}\quad\text{and}\quad\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s.
-    \end{equation*}
+    \item Less than four stages ($s\le3$).
+    \item Globally stiffly accurate (GSA) $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$.
   \end{enumerate}
@@
 Fortunately, IMEX schemes of type~ARS satisfying these properties are easy to find, and we provide an example with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PD-ARS; see \ref{app:PD-ARS} for details).
-In the streaming limit, this scheme is identical to the optimal second-order accurate strong-stability preserving Runge-Kutta method \cite{gottlieb_etal_2001}.  
+In the streaming limit, this scheme is identical to the optimal second-order accurate SSP-RK method \cite{gottlieb_etal_2001}.  
 It is also very similar to the scheme given in \cite{mcclarren_etal_2008} (see scheme PC2 in \ref{app:butcherTables}), which is also a GSA IMEX scheme of type ARS with $s=3$.  
-Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclarren_etal_2008,radice_etal_2013}, and satisfies the positivity conditions, but $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).
+Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclarren_etal_2008,radice_etal_2013}, and satisfies the positivity conditions.  
+However, $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).  
 In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PD-ARS is comparable to the accuracy of scheme PC2.
@@
 The stability regions of PA2+ and PD-ARS are plotted in Figure~\ref{fig:AbsoluteStability}.  
-As can be seen from the figures, the absolute stability region of both schemes increases with increasing $|z_{2}|$.  
+As can be seen from the figures, the absolute stability region of both schemes increases with increasing $|z_{2}|$ (increased damping).  
 For a given $|z_{2}|>0$, the stability region of PD-ARS is larger than that of PA2+.  
 In the linear case, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme ($|z_2| = 0$) fulfills the stability requirement for the IMEX scheme as whole ($|z_2| \geq 0$).
-This conclusion is valid for all PD-ARS schemes with $\epsilon\in [0,0.5)$.
+This holds for all PD-ARS schemes with $\epsilon\in [0,0.5)$.
 \begin{figure}[h]

### 2018-08-28 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
Updates to Section 7 after comments from Cory

@@
 \end{equation}
-Then, with $v=1$ in Eq.~\eqref{eq:semidiscreteDG}, and invoking the form in Eq.~\eqref{eq:imexStagesRewrite}, the stage values for the cell average in the IMEX scheme are given by
-\begin{equation}
+Then, with $v=1$ in Eq.~\eqref{eq:semidiscreteDG}, and invoking the form of the IMEX scheme in Eq.~\eqref{eq:imexStagesRewrite}, the stage values for the cell average in the IMEX scheme are given by
+\begin{align}
+  \cM_{\bK}^{(0)}
+  &=\cM_{\bK}^{n}, \nonumber \\
   \vect{\cM}_{\bK}^{(i)}
-  =\sum_{j=0}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}
+  &=\sum_{j=0}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}
   +a_{ii}\,\dt\,\f{1}{\tau}\,\big(\,\vect{\eta}-\vect{\cD}\,\vect{\cM}_{\bK}^{(i)}\,\big), \quad i=1,\ldots,s,
   \label{eq:imexStagesCellAverage}
-\end{equation}
-where $c_{ij}\ge0$, $\sum_{j=0}^{i-1}c_{ij}=1$, and $a_{ii}>0$, and we have defined
+\end{align}
+where $c_{ij}\ge0$, $\sum_{j=0}^{i-1}c_{ij}=1$, $a_{ii}>0$, 
 \begin{equation}
@@
 \end{equation}
-with $\cM_{\bK}^{(0)}=\cM_{\bK}^{n}$, and where $\hat{c}_{ij}\ge0$.  
+and $\hat{c}_{ij}\ge0$.  
 The cell average of the divergence operator is (cf. Section~\ref{sec:dg})
@@
 
-We proceed to establish conditions for which $\vect{\cM}_{\bK}^{(ij)}\in\cR$.  
+We next establish conditions under which $\vect{\cM}_{\bK}^{(ij)}\in\cR$.  
 \begin{lemma}
-  Let $\{\beta_{k}\}_{k=1}^{d}$ be a set of positive constants satisfying $\sum_{k=1}^{d}\beta_{k}=1$.  
+  Let $\{\beta_{k}\}_{k=1}^{d}$ be a set of strictly positive constants satisfying $\sum_{k=1}^{d}\beta_{k}=1$.  
   If for each $k\in\{1,\ldots,d\}$, 
@@
 Next, we establish conditions for which Eq.~\eqref{eq:realizableGamma} holds.  
-We let $\hat{Q}^{k}\colon C^{0}(K^{k})\to\bbR$ denote the $N$-point \emph{Gauss-Lobatto (GL)} quadrature rule on the interval $K^{k}=(x_{\Low}^{k},x_{\Hgh}^{k})$, with points
+To this end, let $\hat{Q}^{k}\colon C^{0}(K^{k})\to\bbR$ denote the $N$-point \emph{Gauss-Lobatto (GL)} quadrature rule on the interval $K^{k}=(x_{\Low}^{k},x_{\Hgh}^{k})$, with points
 \begin{equation}
-  \hat{S}^{k}=\left\{x_{\Low}^{k}=\hat{x}_{1}^{k},\ldots,\hat{x}_{N}^{k}=x_{\Hgh}^{k}\right\}, 
+  \hat{S}^{k}=\left\{\xL^{k}=\hat{x}_{1}^{k},\ldots,\hat{x}_{N}^{k}=\xH^{k}\right\}, 
   \label{eq:quadraturePointsGL}
@@
 
-With the GL quadrature rule in Eq.~\eqref{eq:quadratureRuleGL} (note $\hat{w}_{1}=\hat{w}_{N}$), we can write $\vect{\Gamma}^{k}$ as the convex combination
+We can write $\vect{\Gamma}^{k}$ as the convex combination
 \begin{align}
-  &\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]
-  =\sum_{q=2}^{N-1}\hat{w}_{q}\,\vect{\cM}_{h}^{(j)}(\hat{x}_{q}^{k}) \nonumber \\
-  &\hspace{12pt}
-  +2\,\hat{w}_{N}\,
-  \Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big],
+  \vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]
+  &=\sum_{q=2}^{N-1}\hat{w}_{q}\,\vect{\cM}_{h}^{(j)}(\hat{x}_{q}^{k}) \nonumber \\
+  &\hspace{-12pt}
+  +\hat{w}_{1}\,\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\lambda_{ij}^{k}\,\mathscr{F}^{k}\big(\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big)\,\big] \nonumber \\
+  &\hspace{-12pt}
+  +\hat{w}_{N}\,\big[\,\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})-\lambda_{ij}^{k}\,\mathscr{F}^{k}\big(\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big)\,\big],
   \label{eq:realizableGammaConvex}
 \end{align}
-where
-\begin{align}
-  &\Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big] \nonumber \\
-  &=\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\lambda_{ij}^{k}\,\mathscr{F}\big(\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big)\,\big] \nonumber \\
-  &\hspace{12pt}
-  +\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})-\lambda_{ij}^{k}\,\mathscr{F}\big(\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big)\,\big],
-\end{align}
-with $\lambda_{ij}^{k}=\hat{c}_{ij}\,\dt/(\beta_{k}\,\hat{w}_{N}\,|K^{k}|)$.  
+where $\lambda_{ij}^{k}=\hat{c}_{ij}\,\dt/(\beta_{k}\,\hat{w}_{N}\,|K^{k}|)$.  
+(With the GL quadrature rule in Eq.~\eqref{eq:quadratureRuleGL}, $\hat{w}_{1}=\hat{w}_{N}$).  
 The following Lemma establishes sufficient conditions for realizability of $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]$, and hence $\vect{\cM}_{\bK}^{(ij)}$.  
@@
   Let the time step $\dt$ be chosen so that $\lambda_{ij}^{k}\le1$.  
-  Let the numerical flux be given by the Lax-Friedrichs flux in Eq.~\eqref{eq:fluxFunctionLF} with $\alpha=1$.  
+  Let the numerical flux be given by the Lax-Friedrichs flux in Eq.~\eqref{eq:fluxFunctionLF} with $\alpha^{k}=1$.  
   Then $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]\in\cR$.  
@@
   By assumption, $\vect{\cM}_{h}^{(j)}(\hat{x}_{q}^{k})\in\cR$ ($q=2,\ldots,N-1$).  
-  It remains to show 
-  \begin{equation*}
-    \Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big]\in\cR.  
-  \end{equation*}
-  Using the Lax-Friedrichs flux in Eq.~\eqref{eq:fluxFunctionLF}, with $\alpha^{k}=1$ ($k=\{1,\ldots,d\}$), it is straightforward to show that
-  \begin{align}
-    &\Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big] \nonumber \\
-    &=(1-\lambda_{ij}^{k})\,\big(\,\f{1}{2}\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\f{1}{2}\,\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})\,\big) \nonumber \\
+  Thus it remains to show that
+  \begin{align*}
+    &\Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big] \\
+    &=\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\lambda_{ij}^{k}\,\mathscr{F}\big(\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big)\,\big] \\
     &\hspace{12pt}
-    +\f{1}{2}\,\lambda_{ij}^{k}\,\big(\,\Phi^{+}\big[\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})\big]\,\big) \nonumber \\
-    &\hspace{12pt}
-    +\f{1}{2}\,\lambda_{ij}^{k}\,\big(\,\Phi^{+}\big[\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big]\,\big),
+    +\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})-\lambda_{ij}^{k}\,\mathscr{F}\big(\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big)\,\big]
+  \end{align*}
+  is realizable.  
+  Using the Lax-Friedrichs flux in Eq.~\eqref{eq:fluxFunctionLF}, with $\alpha^{k}=1$ ($k\in\{1,\ldots,d\}$), it is straightforward to show that
+  \begin{equation}
+    \Phi=(1-\lambda_{ij}^{k})\,\Phi_{0} + \f{1}{2}\,\lambda_{ij}^{k}\,\Phi_{1} + \f{1}{2}\,\lambda_{ij}^{k}\,\Phi_{2},
     \label{eq:phiConvex}
-  \end{align}
-  where $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\,\big(\vect{\cM}\pm\vect{e}_{k}\cdot\vect{\cF}^{k}(\vect{\cM})\big)$.  
-  Since $\lambda_{ij}^{k}\le1$, $\Phi$ is expressed as a convex combination of three terms.  
-  By assumption, $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})$, $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})$, $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})$, $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\in\cR$, which immediately implies realizability of the first term on the right-hand side of Eq.~\eqref{eq:phiConvex}.
-  Realizability of the second and third terms follows by invoking Lemma~\ref{lem:explicitStep}.  
+  \end{equation}
+  where
+  \begin{align*}
+    \Phi_{0} &= \f{1}{2}\,\big(\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})\,\big), \\
+    \Phi_{1} &= \Phi^{+}\big[\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})\big], \\
+    \Phi_{2} &= \Phi^{+}\big[\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big],
+  \end{align*}
+  and $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\,\big(\vect{\cM}\pm\vect{e}_{k}\cdot\vect{\cF}^{k}(\vect{\cM})\big)$.  
+  Since $\lambda_{ij}^{k}\le1$, $\Phi$ is expressed as a convex combination of three terms; $\Phi_{0}$, $\Phi_{1}$, and $\Phi_{2}$.  
+  By assumption, $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})$, $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})$, $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})$, $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\in\cR$, which immediately implies realizability of $\Phi_{0}$.
+  Realizability of $\Phi_{1}$ and $\Phi_{2}$ follows by invoking Lemma~\ref{lem:explicitStep}.  
   This completes the proof.  
@@
   Lemma~\eqref{lem:realizableGamma} is proven without specification of $\tilde{\vect{x}}^{k}$.  
-  In the numerical scheme, we need $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]$ to be realizable in the quadrature set $\tilde{\vect{S}}^{k}$ used to approximate the integral over $\tilde{\bK}^{k}$ in Eq.~\eqref{eq:realizableGamma}; typically the Legendre-Gauss quadrature points.
+  In the numerical scheme, we need $\vect{\Gamma}^{k}\big[\bcM_{h}^{(j)};\hat{c}_{ij}\big]$ to be realizable in the quadrature set $\tilde{\vect{S}}^{k}$ used to approximate the integral over $\tilde{\bK}^{k}$ in Eq.~\eqref{eq:realizableGamma}.
+  (Typically, $\tilde{\vect{S}}^{k}$ is a tensor product of Gauss-Legendre quadrature points.)  
   We thus require $\vect{\cM}_{h}^{(j)}$ to be realizable in the quadrature set $\hat{\vect{S}}^{k}=\tilde{\vect{S}}^{k}\otimes\hat{S}^{k}\subset\bK$, where $\tilde{\vect{S}}^{k}\subset\tilde{\bK}^{k}$, and $\hat{S}^{k}\subset K^{k}$ are the GL quadrature points.
@@
   Lemmas~\ref{lem:imexStagesCellAverage}, \ref{lem:realizableMij}, and \ref{lem:realizableGamma} establish sufficient conditions for realizability of the cell average of each IMEX stage $\vect{\cM}_{\bK}^{(i)}$, for $i=1,\ldots,s$.
-  Within (and after) each IMEX stage, the realizability-enforcing limiter discussed in Section~\ref{sec:limiter} is invoked to ensure that the numerical solution $\vect{\cM}_{h}^{(i)}(\vect{x})$ is realizable in the quadrature points $\hat{\vect{S}}^{k}$, for $k=1,\ldots,d$.
+  Within each IMEX stage, the realizability-enforcing limiter discussed in Section~\ref{sec:limiter} is invoked to ensure that the numerical solution $\vect{\cM}_{h}^{(i)}(\vect{x})$ is realizable in the quadrature points $\hat{\vect{S}}^{k}$, for $k=1,\ldots,d$.
 \end{rem}
@@
 \begin{proof}
-  For $i=1$, the cell average $\vect{\cM}_{\bK}^{(1)}$ is obtained by solving (cf. Eq.~\eqref{eq:imexStagesCellAverage})
+  The cell average $\vect{\cM}_{\bK}^{(1)}$ is obtained by solving (cf. Eq.~\eqref{eq:imexStagesCellAverage} with $i=1$)
   \begin{equation*}
@@
   Since $\vect{\cM}_{h}^{n}\in\cR$ on $\hat{\vect{S}}^{k}$, for each $k\in\{1,\ldots,d\}$, it follows from Lemma~\ref{lem:realizableGamma} that $\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{n};\hat{c}_{10}\big]\in\cR$ on $\tilde{\vect{S}}^{k}$.
-  Then, realizability of $\vect{\cM}_{\bK}^{(10)}$ follows from Lemma~\ref{lem:realizableMij}, while $\vect{\cM}_{\bK}^{(1)}\in\cR$ follows by invoking Lemma~\ref{lem:imexStagesCellAverage}.  
+  Then, realizability of $\vect{\cM}_{\bK}^{(10)}$ follows from Lemma~\ref{lem:realizableMij}, after which $\vect{\cM}_{\bK}^{(1)}\in\cR$ follows by invoking Lemma~\ref{lem:imexStagesCellAverage}.  
   By invoking a realizability-enforcing limiter, $\vect{\cM}_{h}^{(1)}(\vect{x})\in\cR$ for all $\vect{x}\in\hat{\vect{S}}^{k}$ and all $k\in\{1,\ldots,d\}$.  

### 2018-09-01 Documents/M1/realizableFermionicM1/manuscript.tex
Work on intro
Work on the introduction
Edits througout after reading the entire paper.

@@
 
-\journal{Journal of Computational Physics }
+\journal{Journal of Computational Physics}
 
@@
 
-\newcommand{\ee}[1]{{\color{red} #1}}
-\newcommand{\rc}[1]{{\color{blue} #1}}
+\newcommand{\ee}[1]{{\color{red} EE:~#1}}
+\newcommand{\rc}[1]{{\color{blue} RC:~#1}}
 
@@
 Appropriate care is taken to ensure the method preserves strict algebraic bounds on the evolved moments (particle density and flux) as dictated by Pauli's exclusion principle, which demands a bounded distribution function (i.e., $f\in[0,1]$).
-This realizability-preserving scheme combines a suitable CFL condition, a realizability-preserving limiter, a closure procedure based on Fermi-Dirac statistics, and an IMEX scheme whose stages can be written as a convex combination of forward Euler steps combined with a backward Euler step.
-The IMEX scheme is formally only first-order accurate, but works well in the diffusion limit and reduces to the optimal second-order strong stability-preserving Runge-Kutta scheme of Shu \& Osher \cite{shuOsher_1988}.
+This realizability-preserving scheme combines a suitable CFL condition, a realizability-enforcing limiter, a closure procedure based on Fermi-Dirac statistics, and an IMEX scheme whose stages can be written as a convex combination of forward Euler steps combined with a backward Euler step.
+The IMEX scheme is formally only first-order accurate, but works well in the diffusion limit, and --- without interactions with the background --- reduces to the optimal second-order explicit strong stability-preserving Runge-Kutta scheme of Shu \& Osher \cite{shuOsher_1988}.
 Numerical results demonstrate the realizability-preserving properties of the scheme.  
@@
 Discontinuous Galerkin, 
+Implicit-Explicit, 
 Moment Realizability

### 2018-09-01 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Edits througout after reading the entire paper.

@@
 For multidimensional problems, the Kershaw closure is obtained by using the Eddington factor in Eq.~\eqref{eq:eddingtonFactorKershaw} in Eq.~\eqref{eq:eddingtonTensor}.  
-Finally, we point out that for the two-moment Kershaw closure (see \cite{banachLarecki_2017a} for details), a distribution function $f_{\mbox{\tiny K}}(\vect{\ell},\cJ,\vect{\cH})$, satisfying $0 < f_{\mbox{\tiny K}} < 1$, and reproducing the moments $\cJ$, $\vect{\cH}$, and $\vect{\cK}$, can be written explicitly in terms of Heaviside functions.
+Finally, we point out that for the two-moment Kershaw closure (see \cite{banachLarecki_2017a} for details), a distribution function $f_{\mbox{\tiny K}}(\omega,\cJ,\vect{\cH})$, satisfying $0 < f_{\mbox{\tiny K}} < 1$, and reproducing the moments $\cJ$, $\vect{\cH}$, and $\vect{\cK}$, can be written explicitly in terms of Heaviside functions.
 
@@
 
-For $\cJ=0.01$, the maximum entropy closures (CB, BL, and Minerbo) are practically indistinguishable, while the Eddington factor of the Kershaw closure is clearly larger than that of the other closures over most of the domain.
-For $\cJ=0.4$, the Eddington factor for the closures based on Fermi-Dirac statistics (CB, BL, and Kershaw) remain close together, while the Eddington factor for the Minerbo closure is clearly larger than the other closures for $h\gtrsim0.2$.
+For $\cJ=0.01$, the maximum entropy closures (CB, BL, and Minerbo) are practically indistinguishable, while the Eddington factor of the Kershaw closure is larger than that of the other closures over most of the domain.
+For $\cJ=0.4$, the Eddington factor for the closures based on Fermi-Dirac statistics (CB, BL, and Kershaw) remain close together, while the Eddington factor for the Minerbo closure is larger than the other closures for $h\gtrsim0.2$.
 The Eddington factor for all closures remain between $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ for $\cJ=0.01$ and $\cJ=0.4$.
@@
 For $\cJ=0.6$, the Eddington factor for the closures based on Fermi-Dirac statistics remain close together and within the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.  
-The dependence of the Eddington factor on $h$ for the Minerbo closure is clearly different from the other closures (i.e., increases vs decreases with increasing $h$), and exceeds $\chi_{\mbox{\tiny max}}$ for $h\gtrsim0.34$.
+The dependence of the Eddington factor on $h$ for the Minerbo closure differs from the other closures (i.e., increases vs decreases with increasing $h$), and exceeds $\chi_{\mbox{\tiny max}}$ for $h\gtrsim0.34$.
 For $\cJ=0.99$, the Eddington factor of the CB and BL closures (indistinguishable) and the Kershaw closure remain within the bounds given in Eq.~\eqref{eq:eddingtonFactorBounds}.  

### 2018-09-01 Documents/M1/realizableFermionicM1/sections/conclusion.tex
Edits througout after reading the entire paper.

@@
 
-In the applications motivating this work, the collision term is stiff in regions of the computational domain, and we have considered IMEX schemes to avoid solving the transport operator implicitly.  
+In the applications motivating this work, the collision term is stiff in regions of the computational domain, and we have considered IMEX schemes to avoid solving the transport operator implicitly in a fully implicit scheme.
 We considered recently proposed second-order accurate, constraint-preserving IMEX schemes (cf.
@@
 The CFL condition is then solely due to the transport operator, and the time step can be as large as that of the forward Euler scheme applied to the explicit part.  
-After each update, the limiter enforces realizability point-wise by damping towards the realizable cell average.  
+After each update, the limiter enforces moment realizability point-wise by damping towards the realizable cell average.  
 Numerical experiments are presented to demonstrate the accuracy and realizability-preserving property of the scheme.  
@@
 The Eddington factors deriving from the maximum entropy closures of Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Larecki \& Banach \cite{lareckiBanach_2011}, and the Kershaw-type closure of Larecki \& Banach \cite{banachLarecki_2017a} satisfy these bounds, and are suitable for the fermionic two-moment model.
-Further approximations of the closure procedure, e.g., employing the low occupancy limit, which results in the Minerbo closure \cite{minerbo_1978} when starting with the maximum entropy closure of \cite{cernohorskyBludman_1994}), is not compatible with realizability of the fermionic two-moment model, and we caution against this approach to modeling particle systems governed by Fermi-Dirac statistics; particularly if the low occupancy approximation is unlikely to hold (e.g., when modeling neutrino transport in core-collapse supernovae).
+Further approximations of the closure procedure, e.g., employing the low occupancy limit, which results in the Minerbo closure \cite{minerbo_1978} when starting with the maximum entropy closure of \cite{cernohorskyBludman_1994}, is not compatible with realizability of the fermionic two-moment model, and we caution against this approach to modeling particle systems governed by Fermi-Dirac statistics; particularly if the low occupancy approximation is unlikely to hold (e.g., when modeling neutrino transport in core-collapse supernovae).
 
@@
 Inelastic scattering and relativistic effects (e.g., due to interactions with a moving background or the presence of a strong gravitational field) were not included.  
-To solve more realistic problems of higher scientific interest, some or all of these physical effects must be included.  
+To solve more realistic problems of higher scientific interest, some or all of these physical effects may have to be included.  
 In the context of constraint-preserving schemes, these extension provide significant challenges suitable for future investigations, and for which the scheme presented here may serve as a foundation.

### 2018-09-01 Documents/M1/realizableFermionicM1/sections/dg.tex
Edits througout after reading the entire paper.

@@
 Here we briefly outline the DG method for the moment equations.  
+(See, e.g., \cite{cockburnShu_2001}, for a comprehensive review on the application of DG methods to solve hyperbolic conservation laws.)  
 Since we do not include any physics that couples the energy dimension, the particle energy $\epsilonNu$ is simply treated as a parameter.  
@@
 \end{equation}
-We also define $\tilde{\vect{x}}^{i}$ as the coordinates orthogonal to the $i$th dimension, so that $\vect{x}=\{\tilde{\vect{x}}^{i},x^{i}\}$.  
+We also define $\tilde{\vect{x}}^{i}$ as the coordinates orthogonal to the $i$th dimension, so that as a set $\vect{x}=\{\tilde{\vect{x}}^{i},x^{i}\}$.  
 The width of an element in the $i$th dimension is $|K^{i}|=\xH^{i}-\xL^{i}$.

### 2018-09-01 Documents/M1/realizableFermionicM1/sections/imex.tex
Edits througout after reading the entire paper.

@@
 \end{define}
-As an example, given a spatial discretization of a model that is constraint-preserving with the forward Euler method for a sufficiently small time step, high-order strong stability-preserving Runge-Kutta (SSP-RK) methods, which can be expressed as convex combinations of forward Euler steps, form a class of constraint-preserving schemes.
+As an example, given a spatial discretization of a model that is constraint-preserving with the forward Euler method for a sufficiently small time step, high-order explicit strong stability-preserving Runge-Kutta (SSP-RK) methods, which can be expressed as convex combinations of forward Euler steps, also preserve the constraints (possibly with a smaller time step), and form a class of constraint-preserving schemes.
+
+Since the realizable set $\cR$ is convex, constraint-preserving schemes can be used to design realizability-preserving schemes for the two-moment model.
 
@@
 
-Unfortunately, the ``diffusion limit requirement" in Eq.~\eqref{eq:diffusionCondition}, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints to obtain a constraint-preserving IMEX scheme.
+Unfortunately, the ``diffusion limit requirement" in Eq.~\eqref{eq:diffusionCondition}, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints to obtain a second-order accurate constraint-preserving IMEX scheme.
 \footnote{It was shown in \cite{hu_etal_2018} --- without the diffusion limit requirement --- that the minimum number of stages for constraint-preserving IMEX schemes of type~ARS is four.)  
@@
 \end{define}
-Fortunately, IMEX schemes of type~ARS satisfying these properties are easy to find, and we provide an example with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PD-ARS; see \ref{app:PD-ARS} for details).
+Fortunately, IMEX schemes of type~ARS satisfying these properties are easy to find, and we provide an example with $s=3$ (two implicit solves) in \ref{app:butcherTables} (scheme PD-ARS; see \ref{app:PD-ARS} for further details).
 In the streaming limit, this scheme is identical to the optimal second-order accurate SSP-RK method \cite{gottlieb_etal_2001}.  
 It is also very similar to the scheme given in \cite{mcclarren_etal_2008} (see scheme PC2 in \ref{app:butcherTables}), which is also a GSA IMEX scheme of type ARS with $s=3$.  
-Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclarren_etal_2008,radice_etal_2013}, and satisfies the positivity conditions.  
+Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclarren_etal_2008,radice_etal_2013}, and satisfies the positivity conditions in Eq.~\eqref{eq:positivityConditionsTypeARS}.
 However, $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).  
@@
 On the right-hand side of Eq.~\eqref{eq:scalarODE}, the first (oscillatory) term is treated explicitly, while the second (damping) term is treated implicitly.  
-The IMEX schemes can then be written as $u^{n+1} =P(z_{1},z_{2})\,u^{n}$, where $P(z_{1},z_{2})$ is the amplification factor of the scheme, $z_{1}=\dt\,\lambda_{1} = x +iy$, and $z_{2} = \dt\,\lambda_{2} < 0$.
+The IMEX schemes can then be written as $u^{n+1} =P(z_{1},z_{2})\,u^{n}$, where $P(z_{1},z_{2})$ is the amplification factor of the scheme, $z_{1}=\dt\,\lambda_{1} = x +iy$, and $z_{2} = \dt\,\lambda_{2} \le 0$.
 Stability of the IMEX scheme requires $|P(z_1,z_2)|\leq 1$.  
@@
 As can be seen from the figures, the absolute stability region of both schemes increases with increasing $|z_{2}|$ (increased damping).  
-For a given $|z_{2}|>0$, the stability region of PD-ARS is larger than that of PA2+.  
+For a given $|z_{2}|\ge0$, the stability region of PD-ARS is larger than that of PA2+.  
 In the linear case, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme ($|z_2| = 0$) fulfills the stability requirement for the IMEX scheme as whole ($|z_2| \geq 0$).

### 2018-09-01 Documents/M1/realizableFermionicM1/sections/intro.tex
Edits througout after reading the entire paper.

@@
 In these situations, a kinetic description may be required, where particle distribution function $f(\vect{p},\vect{x},t)$ is solved for.  
-The distribution function, a phase space density depending on momentum $\vect{p}$ and position $\vect{x}$, gives at time $t$ the number of particles in the phase space volume element $d\vect{p}\,d\vect{x}$ (i.e., $dN=f\,d\vect{p}\,d\vect{x}$).
+The distribution function, a phase space density depending on momentum $\vect{p}\in\bbR^{3}$ and position $\vect{x}\in\bbR^{3}$, gives at time $t\in\bbR^{+}$ the number of particles in the phase space volume element $d\vect{p}\,d\vect{x}$ (i.e., $dN=f\,d\vect{p}\,d\vect{x}$).
 The evolution of the distribution function is governed by the Boltzmann equation, which states a balance between phase space advection and collisions (see, e.g., \cite{braginskii_1965,chapmanCowling_1970,lifshitzPitaevskii_1981}).
@@
 
-In this paper we consider a two-moment model for particles governed by Fermi-Dirac statistics.  
+Here we consider a two-moment model for particles governed by Fermi-Dirac statistics.  
 It is well known from the two-moment model for particles governed by Maxwell-Boltzmann statistics (``classical'' particles with $f\ge0$), that the particle density is nonnegative and the magnitude of the flux vector is bounded by the particle density.
@@
 Furthermore, the set of realizable moments generated by the particle density and flux vector constitutes a convex cone \cite{olbrant_etal_2012}.  
-In the fermionic case, there is also an upper bound on the distribution function because Pauli's exclusion principle prevents particles from occupying the same microscopic state (e.g., $f\le1$).  
+In the fermionic case, there is also an upper bound on the distribution function (e.g., $f\le1$) because Pauli's exclusion principle prevents particles from occupying the same microscopic state.  
 The fermionic two-moment model has recently been studied theoretically in the context of maximum entropy closures \cite{lareckiBanach_2011,banachLarecki_2013,banachLarecki_2017b} and Kershaw-type closures \cite{banachLarecki_2017a}.
@@
 
-The two-moment model is discretized in space using high-order Discontinuous Galerkin (DG) methods (e.g., \cite{cockburnShu_2001,hesthavenWarburton_2008}).  
+In this paper, the two-moment model is discretized in space using high-order Discontinuous Galerkin (DG) methods (e.g., \cite{cockburnShu_2001,hesthavenWarburton_2008}).  
 DG methods combine elements from both spectral and finite volume methods, and are an attractive option for solving hyperbolic partial differential equations (PDEs).  
@@
 (See e.g., \cite{xing_etal_2010,zhangShu_2011,olbrant_etal_2012,cheng_etal_2013,zhang_etal_2013,endeve_etal_2015,wuTang_2015}, for extensions and applications to other systems.)  
-The main ingredients include (1) a realizability-preserving update for the cell averaged moments based on Euler time stepping, which evaluates the polynomial representation of the DG method in a finite number of quadrature points in the local elements and results in a Courant-Friedrichs-Lewy (CFL) condition on the time step; (2) a limiter to modify the polynomial representation to ensure that the algebraic constraints are satisfied point-wise without changing the cell average of the moments; and (3) a time stepping method that can be expressed as a convex combination of Euler steps, and therefore preserves the algebraic constraints as the Euler methods.
+The main ingredients include (1) a realizability-preserving update for the cell averaged moments based on Euler time stepping, which evaluates the polynomial representation of the DG method in a finite number of quadrature points in the local elements and results in a Courant-Friedrichs-Lewy (CFL) condition on the time step; (2) a limiter to modify the polynomial representation to ensure that the algebraic constraints are satisfied point-wise without changing the cell average of the moments; and (3) a time stepping method that can be expressed as a convex combination of Euler steps, and therefore preserves the algebraic constraints as the Euler methods (possibly with a modified CFL condition).
 
@@
 Numerical results are presented in Section~\ref{sec:numerical}, and summary and conclusions are given in Section~\ref{sec:conclusions}.
-
-\clearpage

### 2018-09-01 Documents/M1/realizableFermionicM1/sections/limiter.tex
Completed first pass in updating DGIMEXscheme.tex
Added text for the Fermion Implosion problem
Changed section title
Edits througout after reading the entire paper.

@@
-\section{Realizability-Preserving Limiter}
-\label{eq:limiter}
+\section{Realizability-Enforcing Limiter}
+\label{sec:limiter}
 
-The bound-preserving DG-IMEX method developed in previous sections is designed to preserve realizability of the cell averaged moments, i.e., $\vect{\cM}_{\bK}\in\cR$, provided sufficiently accurate quadratures are used to integrate integrals in the DG method, specific CFL conditions are satisfied, and that the polynomial approximation $\vect{\cM}_{h}$, at time $t^{n}$, is realizable in a set of quadrature points in each element $\bK$.
-We denote this quadrature set by $S\subset\bK$.  
+The bound-preserving DG-IMEX method developed in previous sections is designed to preserve realizability of the cell averaged moments, i.e., $\vect{\cM}_{\bK}\in\cR$, provided sufficiently accurate quadratures are used to integrate integrals in the DG method, a CFL condition is satisfied, and that the polynomial approximation $\vect{\cM}_{h}$, at time $t^{n}$, is realizable in a set of quadrature points in each element $\bK$.
+We denote this quadrature set by $S=\cup_{k=1}^{d}\hat{\vect{S}}^{k}\subset\bK$.  
 In the DG method, we use the limiter proposed by Zhang \& Shu \cite{zhangShu_2010a} for scalar conservation laws to enforce the bounds on the zeroth moment $\cJ$ (see also \cite{liuOsher_1996}).  
-We replace the polynomial $\cJ_{h}^{n}(\vect{z})$ with the limited polynomial
+We replace the polynomial $\cJ_{h}^{n}(\vect{x})$ with the limited polynomial
 \begin{equation}
-  \tilde{\cJ}_{h}^{n}(\vect{z})
-  =\vartheta_{1}\,\cJ_{h}^{n}(\vect{z})+(1-\vartheta_{1})\,\cJ_{\bK}^{n},
+  \tilde{\cJ}_{h}^{n}(\vect{x})
+  =\vartheta_{1}\,\cJ_{h}^{n}(\vect{x})+(1-\vartheta_{1})\,\cJ_{\bK}^{n},
+  \label{eq:limitDensity}
 \end{equation}
@@
 \begin{equation}
-  M_{S}=\max_{\vect{z}\in S}\cJ_{h}^{n}(\vect{z})
+  M_{S}=\max_{\vect{x}\in S}\cJ_{h}^{n}(\vect{x})
   \quad\text{and}\quad
-  m_{S}=\min_{\vect{z}\in S}\cJ_{h}^{n}(\vect{z}).  
+  m_{S}=\min_{\vect{x}\in S}\cJ_{h}^{n}(\vect{x}).  
 \end{equation}
@@
 We let $\widetilde{\vect{\cM}}_{h}^{n}=\big(\tilde{\cJ}_{h}^{n},\vect{\cH}_{h}^{n}\big)^{T}$.  
-Then, if $\widetilde{\bcM}_{h}^{n}$ lies outside $\cR$ for any quadrature point $\vect{z}_{q}\in S$, i.e., $\gamma(\widetilde{\bcM}_{h}^{n})<0$, there exists an intersection point of the straight line, $\vect{s}_{q}(\xi)$, connecting $\vect{\cM}_{\bK}^{n}\in\cR$ and $\widetilde{\vect{\cM}}_{h}^{n}$ evaluated in the troubled quadrature point $\vect{z}_{q}$, denoted $\widetilde{\vect{\cM}}_{q}^{n}$, and the boundary of $\cR$.
+Then, if $\widetilde{\bcM}_{h}^{n}$ lies outside $\cR$ for any quadrature point $\vect{x}_{q}\in S$, i.e., $\gamma(\widetilde{\bcM}_{h}^{n})<0$, there exists an intersection point of the straight line, $\vect{s}_{q}(\xi)$, connecting $\vect{\cM}_{\bK}^{n}\in\cR$ and $\widetilde{\vect{\cM}}_{h}^{n}$ evaluated in the troubled quadrature point $\vect{x}_{q}$, denoted $\widetilde{\vect{\cM}}_{q}^{n}$, and the boundary of $\cR$.
 This line is given by the convex combination 
@@
 \end{equation}
-where $\xi\in[0,1]$, and the intersection point $\xi_{q}$ is obtained by solving $\gamma(\bs_{q}(\xi))=0$ for $\xi$, using the bisection algorithm.  
+where $\xi\in[0,1]$, and the intersection point $\xi_{q}$ is obtained by solving $\gamma(\bs_{q}(\xi))=0$ for $\xi$, using the bisection algorithm\footnote{In practice, $\xi$ needs not be accurate to many significant digits, and the bisection algorithm can be terminated after a few iterations.}.
 We then replace the polynomial representation $\widetilde{\vect{\cM}}_{h}^{n}\to\widehat{\vect{\cM}}_{h}^{n}$, where
 \begin{equation}
-  \widehat{\vect{\cM}}_{h}^{n}(\vect{z})=\vartheta_{2}\,\widetilde{\vect{\cM}}_{h}^{n}(\vect{z})+(1-\vartheta_{2})\,\vect{\cM}_{\bK}^{n},
+  \widehat{\vect{\cM}}_{h}^{n}(\vect{x})=\vartheta_{2}\,\widetilde{\vect{\cM}}_{h}^{n}(\vect{x})+(1-\vartheta_{2})\,\vect{\cM}_{\bK}^{n},
+  \label{eq:limitMoments}
 \end{equation}
@@
 
-We note that the realizability-preserving limiter is conservative; i.e., preserves the cell-average.
+We note that the realizability-enforcing limiter is conservative; i.e., preserves the cell-average $\widehat{\vect{\cM}}_{\bK}=\widetilde{\vect{\cM}}_{\bK}=\vect{\cM}_{\bK}$.

### 2018-09-01 Documents/M1/realizableFermionicM1/sections/numerical.tex
Edits througout after reading the entire paper.

@@
 \label{sec:numerical}
+
+In this section we present numerical results obtained with the DG-IMEX scheme developed in this paper.  
+The first set of tests (Section~\ref{sec:smoothProblems}) are included to compare the time integration schemes in various regimes.  
+We are not concerned with moment realizability here, and we do not apply the realizability-enforcing limiter in these tests.  
+The tests in Sections~\ref{sec:packedBeam} and \ref{sec:fermionImplosion} are designed specifically to demonstrate the robustness of the scheme to dynamics near the boundary of the realizable set $\cR$.
+The test in Section~\ref{sec:homogeneousSphere} (Homogeneous Sphere) is of astrophysical interest.  
+Here we consider moment realizability and compare results obtained with various moment closures.
 
@@
 \cite{mcclarren_etal_2008} (PC2), Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332), and Cavaglieri \& Bewley \cite{cavaglieriBewley2015} (RKCB2).
-In the streaming test, we also include results obtained with second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods \cite{gottlieb_etal_2001} in the comparison (SSPRK2 and SSPRK3, respectively).
+In the streaming test, we also include results obtained with second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods \cite{gottlieb_etal_2001} (SSPRK2 and SSPRK3, respectively).
 See \ref{app:butcherTables} for further details.  
@@
 respectively.  
-The integrals in Eqs.~\eqref{eq:errorNormAbsolute} and \eqref{eq:errorNormRelative} are computed with a $3$-point Gaussian quadrature.
+The integrals in Eqs.~\eqref{eq:errorNormAbsolute} and \eqref{eq:errorNormRelative} are computed with a simple $3$-point equal weight quadrature.
 
@@
 Results for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively (see figure caption for further details).  
-All the second-order accurate schemes (PA2, PA2+, RKCB2, and SSP2332) display second-order accurate convergence rates (cf. bottom, black dash-dot reference line).  
+All the second-order accurate schemes (PA2, PA2+, RKCB2, and SSP2332) display second-order convergence rates (cf. bottom, black dash-dot reference line).  
 For $\sigma_{\Ab}=0.1$, SSP2332 is the most accurate among these schemes, while PA2+ is the most accurate for $\sigma_{\Ab}=10$.  
@@
 
-In Figures~\ref{fig:SineWaveDiffusionJ} and \ref{fig:SineWaveDiffusionJ} we plot the absolute error, obtained using different values of $\sigma_{\Scatt}$, for various IMEX schemes at $t=t_{\mbox{\tiny end}}$.
+In Figures~\ref{fig:SineWaveDiffusionJ} and \ref{fig:SineWaveDiffusionH} we plot the absolute error, obtained using different values of $\sigma_{\Scatt}$, for various IMEX schemes at $t=t_{\mbox{\tiny end}}$.
 Results for $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively (see figure caption for further details).  
@@
 \subsection{Packed Beam}
+\label{sec:packedBeam}
 
@@
 For the results obtained with the CB closure, the limiter was enacted whenever moments ventured outside the realizable set given by Eq.~\eqref{eq:realizableSet}.  
-For the results obtained with the Minerbo closure, which is not based on Fermi-Dirac statistics, we used a modified limiter, which was enacted when the moments ventured outside the realizable domain of positive distributions; i.e., not bounded by $f\le1$, so that $\cJ\ge0$ and $\cJ\ge|\vect{\cH}|$ (e.g., \cite{levermore_1984}; see dashed red line in Figure~\ref{fig:RealizableSetFermionic}).
+For the results obtained with the Minerbo closure, which is not based on Fermi-Dirac statistics, we used a modified limiter, which was enacted when the moments ventured outside the realizable domain of positive distributions; i.e., not bounded by $f < 1$, so that $\cJ > 0$ and $\cJ > \vect{\cH}|$ (e.g., \cite{levermore_1984}; see red line in Figure~\ref{fig:RealizableSetFermionic}).
 
@@
 In the right panel of Figure~\ref{fig:PackedBeam_Realizability} we plot the numerical solutions in the $(\cH,\cJ)$-plane.  
-Initially, the moments are located in two points: $\vect{\cM}_{\mbox{\tiny L}}$ and $\vect{\cM}_{\mbox{\tiny R}}$, for $x\le0$ and $x>0$, respectively.  
+Initially, the moments are located in two points: $\vect{\cM}_{\mbox{\tiny L}}$ and $\vect{\cM}_{\mbox{\tiny R}}$, for $x\le0$ and $x>0$, respectively (marked by circles in Figure~\ref{fig:PackedBeam_Realizability}).
 For $t>0$, the solutions trace out curves in the $(\cH,\cJ)$-plane, connecting $\vect{\cM}_{\mbox{\tiny L}}$ and $\vect{\cM}_{\mbox{\tiny R}}$.  
@@
 black line in Figure~\ref{fig:PackedBeam_Realizability}).
-With the Minerbo closure (magenta points), the solution follows a different curve --- outside the realizable domain for distribution functions bounded by $f\in[0,1]$, but inside the realizable domain of positive distributions (cf.
+With the Minerbo closure (magenta points), the solution follows a different curve --- outside the realizable domain for distribution functions bounded by $f\in(0,1)$, but inside the realizable domain of positive distributions (cf.
 red line in Figure~\ref{fig:PackedBeam_Realizability}).
@@
 Results obtained with the CB and Minerbo closures are plotted in blue and magenta, respectively.
-The solid black and red lines are contours where $(1-\cJ)\,\cJ=\cH$ and $\cJ=\cH$, respectively.}
+The solid black and red lines are contours where $(1-\cJ)\,\cJ=\cH$ and $\cJ=\cH$, respectively.
+The initial states are marked with black circles.}
   \label{fig:PackedBeam_Realizability}
@@
 \subsection{Fermion Implosion}
+\label{sec:fermionImplosion}
 
@@
 
-Here, a modified version of the line source --- dubbed \emph{Fermion Implosion},  designed to test the realizability-preserving properties of the two moment model for fermionic transport --- is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[-1.28,1.28], x^{2}\in[-1.28,1.28]\}$.
+Here, a modified version of the line source --- dubbed \emph{Fermion Implosion},  designed to test the realizability-preserving properties of the two-moment model for fermion transport --- is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[-1.28,1.28], x^{2}\in[-1.28,1.28]\}$.
 Instead of initializing with a delta function, we follow the initialization procedure in \cite{garrettHauck_2013}, and approximate the initial condition using an isotropic Gaussian distribution function.
@@
 The right panel in Figure~\ref{fig:Implosion} illustrates the difference in dynamics resulting from the two closures.  
-(We also plot a reference transport solution obtained using the filtered spherical harmonics scheme described in \cite{garrettHauck_2013}; dashed black lines.)  
+(We also plot a reference transport solution obtained using the filtered spherical harmonics scheme described in \cite{garrettHauck_2013}; dashed black lines.\footnote{Kindly provided by Dr.
+Ming Tse Paul Laiu (private communications).})
 With the CB closure (blue lines), the central density increases towards the maximum value of unity, and an low-density pulse propagates radially.  
@@
 At $t=0.4$, a discontinuity appears to have formed around $R=0.2$, resulting in numerical oscillations.  
-Except for the positivity limiter (which is not triggered for this model), no limiters are used to prevent numerical oscillations.  
+Except for the realizability-enforcing limiter (which is not triggered for this model), no other limiters are used to prevent numerical oscillations.  
 Although the solutions obtained with the two-moment model differ from the reference transport solution, the results obtained with the CB closure are in closer agreement with the transport solution.  
@@
 With the CB closure (blue points), the moments are confined to evolve inside the realizable domain $\cR$ (black), while with the Minerbo closure, the moments are not confined to $\cR$, but to the region above the red lines (the realizable domain for moments of positive distribution functions), and this is the reason for the difference in dynamics in the two models.
-For the model with the CB closure, some moments evolve very close to the boundary of the realizable domain, and the positivity limiter is continuously triggered to damp these moments towards the cell average, which is realizable by the design of our numerical scheme.
+For the model with the CB closure, some moments evolve very close to the boundary of the realizable domain, and the positivity limiter is continuously triggered to damp these moments towards the cell average, which is realizable by the design of the numerical scheme.
 In the lower right panel in Figure~\ref{fig:Implosion} we plot the limiter parameters $\vartheta_{1}$ (solid) and $\vartheta_{2}$ (dashed) (cf.
@@
 \subsection{Homogeneous Sphere}
+\label{sec:homogeneousSphere}
 
-The homogeneous sphere test (e.g., \cite{smit_etal_1997}) considers of a sphere with radius $R$.  
+The homogeneous sphere test (e.g., \cite{smit_etal_1997}) considers a sphere with radius $R$.  
 Inside the sphere (radius $<R$), the absorption opacity $\sigma_{\Ab}$ and the equilibrium distribution function $f_{0}$ are set to constant values.  
@@
 \end{equation}
-where $r=|\vect{x}|$ and
+where $r=|\vect{x}|$, 
 \begin{equation}
@@
 and $g(r,\mu)=[1-(r/R)^{2}(1-\mu^{2})]^{1/2}$.  
-For $f_{0}\in[0,1]$, the analytical solution is bounded $f_{\mbox{\tiny A}}\in[0,1]$.
+For $f_{0}\in(0,1)$, the analytical solution is bounded $f_{\mbox{\tiny A}}\in(0,1)$.
 
@@
 We compute until $t=5$, when the system has reached an approximate steady state.  
-We use the IMEX scheme PD-ARS --- the least compute-intensive of the realizability-preserving IMEX schemes presented here --- in all the tests.  
+In all the tests, we use the IMEX scheme PD-ARS --- the least compute-intensive of the constraint-preserving IMEX schemes presented here.  
 The main purpose of this test is to compare the results obtained using the different algebraic closures discussed in Section~\ref{sec:algebraicClosure}.
@@
 In Figure~\ref{fig:HomogeneousSphere}, we plot results obtained for all tests at $t=5$: Test~A (top panels), Test~B (middle panels), and Test~C (bottom panels).  
-The particle density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$ are plotted versus radius $r=|\vect{x}|$ (left and right panels, respectively).  
+The particle density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$ (left and right panels, respectively) are plotted versus radius $r=|\vect{x}|$ using scatter plots.  
 In each panel, results obtained with the various algebraic closures discussed in Section~\ref{sec:algebraicClosure} are plotted: Minerbo (magenta), CB (blue), BL (green), and Kershaw (cyan).  
@@
 \cite{smit_etal_1997}, when using the CB maximum entropy closure, with $f_{0}=0.8$ and an unsmoothed absorption opacity $\sigma_{\Ab}=4$.
-We also note that our results are at odds with the results recently reported by Murchikova et al.
-\cite{murchikova_etal_2017}, who compared results obtained with with the two-moment model using a large number of algebraic closures for this same problem (albeit using an unsmoothed and slightly different value for the absorption opacity).
+We also note that our results appear to be somewhat at odds with the results recently reported by Murchikova et al.
+\cite{murchikova_etal_2017}, who compared results obtained with the two-moment model using a large number of algebraic closures for this same problem (albeit using an unsmoothed and slightly different value for the absorption opacity).
 Murchikova et al.
@@
 As can be seen in the upper panels in Figure~\ref{fig:HomogeneousSphereRealizability}, the solution to the homogeneous sphere problem covers a large fraction of the right half of the realizable domain $\cR$, whose boundary is indicated by solid black curves in each panel.
+(The moments only appear in the right half of $\cR$ because we only compute in one octant.)  
 When using the CB closure, the realizability-preserving DG-IMEX scheme developed here maintains solutions within $\cR$.  

### 2018-09-01 Documents/M1/realizableFermionicM1/sections/realizability.tex
Edits througout after reading the entire paper.

@@
 \begin{rem}
-  As in \cite{lareckiBanach_2011}, in Definition~\ref{def:momentRealizability}, and in the rest of this paper, we exclude the cases $f=0$ and $f=1$ almost everywhere (a.e.) on $\bbS^{2}$, which would give $\cJ=0$ and $\cJ=1$, respectively.
+  Following \cite{lareckiBanach_2011}, in Definition~\ref{def:momentRealizability}, and in the rest of this paper, we exclude the cases $f=0$ and $f=1$ almost everywhere (a.e.) on $\bbS^{2}$, which would give $\cJ=0$, $\vect{\cH}=0$ and $\cJ=1$, $\vect{\cH}=0$, respectively.
 \end{rem}
@@
 \end{lemma}
-%\begin{proof}
-%  First, let $\mu=\cos\thetaNu$ and $\bbS^{1}:=\{\,\mu\,|\,\mu\in[-1,1]\,\}$, and write
-%  \begin{equation}
-%    \cJ=\f{1}{2}\int_{\bbS^{1}}\mathfrak{f}(\mu)\,d\mu,
-%    \quad\text{where}\quad
-%    \mathfrak{f}(\mu)=\f{1}{2\pi}\int_{0}^{2\pi}f(\mu,\phiNu)\,d\phiNu.  
-%  \end{equation}  
-%  Since $f(\omega)\in[0,1]$, we have $\mathfrak{f}(\mu)\in[0,1]$, which implies $\cJ\in[0,1]$.  
-%  Next we need to show that $|\vect{\cH}|\le(1-\cJ)\,\cJ$.  
-%  Let $\widehat{\vect{n}}\in\bbR^{3}$ (independent of $\omega$) be an arbitrary unit vector, and write
-%  \begin{equation}
-%    \widehat{\vect{n}}\cdot\vect{\cH}
-%    =\f{1}{2} \int_{\bbS^{1}}\mathfrak{f}(\mu)\,\mu\,d\mu,
-%    \label{eq:NdotH}
-%  \end{equation}
-%  where we have aligned the polar axis of the spherical momentum space coordinate system with $\widehat{\vect{n}}$; i.e., $\widehat{\vect{n}}\cdot\vect{\ell}(\omega)=\mu$.  
-%  First, following \cite{banachLarecki_2017a}, we can write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
-%  \begin{equation*}
-%    (1-\cJ)\cJ - \f{1}{2}\int_{-1}^{1-2\cJ}(1-2\cJ-\mu)\,\mathfrak{f}(\mu)\,d\mu
-%    -\f{1}{2}\int_{1-2\cJ}^{1}(2\cJ-1+\mu)\,[1-\mathfrak{f}(\mu)]\,d\mu.  
-%  \end{equation*}
-%  Since $\mathfrak{f}\in[0,1]$, $(1-2\cJ-\mu)$ is nonnegative on the interval $\mu\in[-1,1-2\cJ]$, and $(2\cJ-1+\mu)$ is nonnegative on the interval $\mu\in[1-2\cJ,1]$, we have $\widehat{\vect{n}}\cdot\vect{\cH}\le(1-\cJ)\,\cJ$.
-%  In a similar manner, we can also write the integral on the right-hand side of Eq.~\eqref{eq:NdotH} as
-%  \begin{equation*}
-%    -(1-\cJ)\cJ-\f{1}{2}\int_{-1}^{2\cJ-1}(1-2\cJ+\mu)\,[1-\mathfrak{f}(\mu)]\,d\mu
-%    -\f{1}{2}\int_{2\cJ-1}^{1}(2\cJ-1-\mu)\,\mathfrak{f}(\mu)\,d\mu.  
-%  \end{equation*}
-%  Then, since $\mathfrak{f}\in[0,1]$, $(1-2\cJ+\mu)$ is nonpositive on the interval $\mu\in[-1,2\cJ-1]$, and $(2\cJ-1-\mu)$ is nonpositive on the interval $\mu\in[2\cJ-1,1]$, we have $\widehat{\vect{n}}\cdot\vect{\cH}\ge-(1-\cJ)\,\cJ$.
-%  We therefore have $-(1-\cJ)\,\cJ\le\widehat{\vect{n}}\cdot\vect{\cH}\le(1-\cJ)\,\cJ$.  
-%  Since this holds for any unit vector $\widehat{\vect{n}}\in\bbR^{3}$, we must have $|\vect{\cH}|\le(1-\cJ)\,\cJ$.  
-%\end{proof}
 
@@
   Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ and $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments defined as in Eq.~\eqref{eq:angularMoments} with distribution functions $f_{a}$ and $f_{b}$, respectively, such that $f_{a}(\omega),f_{b}(\omega)\in(0,1)\,\forall\,\omega\in\bbS^{2}$.
-  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector, and $\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})=\big(\widehat{\vect{e}}\cdot\vect{\cH},\widehat{\vect{e}}\cdot\vect{\cK}\big)^{T}$.
+  Let $\Phi^{\pm}(\vect{\cM},\vect{\cK})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector, and $\widehat{\vect{e}}\cdot\vect{\cF}=\big(\widehat{\vect{e}}\cdot\vect{\cH},\widehat{\vect{e}}\cdot\vect{\cK}\big)^{T}$.
   Then
   \begin{equation*}
-    \vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} \equiv \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
+    \vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} \equiv \Phi^{+}(\vect{\cM}_{a},\vect{\cK}_{a})+\Phi^{-}(\vect{\cM}_{b},\vect{\cK}_{b})\in\cR.
   \end{equation*}

### 2018-09-01 Documents/M1/realizableFermionicM1/sections/appendix.tex
More edits

@@
 \end{align*}
-The coefficient in the correction step is $\alpha = 0.2797373792$ and the CFL constant is $c_{sch} = 0.5247457524$.
+The coefficient in the correction step is $\alpha = 0.2797373792$ and the CFL constant is $c_{\mbox{\tiny Sch}} = 0.5247457524$.
 This scheme is globally stiffly accurate (GSA), so that $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.
@@
 \end{align*}
-This scheme is GSA, $\alpha=0$, and requires only two implicit solves per time step.
+This scheme is GSA, $\alpha=0$, and requires two implicit solves per time step (same as IMEX PC2).
 
@@
 
-We compare the performance of the positivity-preserving IMEX schemes with two other, non-positive, schemes.  
+We compare the performance of the constraint-preserving IMEX schemes with two other (not constraint-preserving) IMEX schemes.  
 The first one is the second-order accurate IMEX scheme given in \cite{cavaglieriBewley2015}.  
@@
 \end{equation}
-The positivity-preserving property follows from imposing the inequality constraints $a_{22},a_{33}>0$, $c_{20},c_{30},c_{32}\ge0$, and $\tilde{c}_{20},\tilde{c}_{30},\tilde{c}_{32}\ge0$, which imply that
+The constraint-preserving property requires imposing the inequality constraints $a_{22},a_{33}>0$, $c_{20},c_{30},c_{32}\ge0$, and $\tilde{c}_{20},\tilde{c}_{30},\tilde{c}_{32}\ge0$, which imply that
 \begin{equation}
@@
   \quad\text{and}\quad 
-  -\f{a_{32}\,\tilde{a}_{21}}{a_{22}\,a_{33}} + \f{1}{a_{33}} =1.
+  -\f{a_{32}\,\tilde{a}_{21}}{a_{22}\,a_{33}} + \f{1}{a_{33}} = 1.
 \label{eq:diffusionAccurate}
@@
 \end{align}
-The positivity-preserving property requires $a_{11}, a_{22}, a_{33}>0$ and the inequality constraints
-\begin{align*}
-  & c_{20} = 1 - \frac{a_{21}}{a_{11}} \geq 0, \quad c_{30} = 1-\frac{a_{31}}{a_{11}} + \frac{a_{32}\,a_{21}}{a_{22}\,a_{11}} - \frac{a_{32}}{a_{22}}\geq 0, \\
-  & c_{21} = \frac{a_{21}}{a_{11}} \geq 0, \quad c_{31} = \frac{a_{31}}{a_{11}} - \frac{a_{32}\,a_{21}}{a_{22}\,a_{11}} \geq 0, \quad c_{32} = \frac{a_{32}}{a_{22}} \geq 0,\\
-  & \tilde{c}_{21} = \tilde{a}_{21} \geq 0, \quad \tilde{c}_{31} = \tilde{a}_{31} - \frac{a_{32}\,\tilde{a}_{21}}{a_{22}} \geq 0, \quad \tilde{c}_{32} = \tilde{a}_{32} \geq 0.
-\end{align*}
+The constraint-preserving property requires $a_{11}, a_{22}, a_{33}>0$.  
+The inequality constraints in Eq.~\eqref{eq:positivityConditionsTypeA} also require
+\begin{equation}
+  c_{21} = \frac{a_{21}}{a_{11}} \geq 0, \quad
+  c_{31} = \frac{a_{31}}{a_{11}} - \frac{a_{32}\,a_{21}}{a_{22}\,a_{11}} \geq 0, \quad\text{and}\quad
+  c_{32} = \frac{a_{32}}{a_{22}} \geq 0.
+  \label{eq:constraintsTypeA}
+\end{equation}
 Since $a_{31} = 0$, we have
@@
 \end{equation*}
-Since $a_{21} \geq 0$, $a_{32} \geq 0$, $a_{22} > 0$ and $a_{11} >0$, we have $c_{31} \leq 0$, and the inequality constraints hold only for $c_{31} = 0$.
+Then, since $a_{21} \geq 0$, $a_{32} \geq 0$, $a_{22} > 0$ and $a_{11} >0$, we have $c_{31} \leq 0$, and the inequality constraints in Eq.~\eqref{eq:constraintsTypeA} hold only for $c_{31} = 0$.
 Unfortunately, $c_{31} = 0$ gives $c_{\mbox{\tiny Sch}} = \min \Big\{\,\f{c_{21}}{\tilde{c}_{21}}, \f{c_{31}}{\tilde{c}_{31}}, \f{c_{32}}{\tilde{c}_{32}}\Big\} = 0$.

### 2018-09-06 Documents/M1/realizableFermionicM1/manuscript.tex
More edits
Various edits.  Replaces homogeneous sphere figures

@@
 \usepackage{subcaption}
+\usepackage{float}
 
@@
 %% Group authors per affiliation:
-\author[ornl,utk-phys]{Eirik Endeve\corref{cor}}
+\author[ornl,utk-phys,jics]{Eirik Endeve\corref{cor}}
 \ead{endevee@ornl.gov}
@@
 
-\author[utk-phys]{Anthony Mezzacappa}
+\author[utk-phys,jics]{Anthony Mezzacappa}
 \ead{mezz@utk.edu}
@@
 
+\address[jics]{Joint Institute for Computational Sciences, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354}
+
 \address[utk-math]{Department of Mathematics, University of Tennessee Knoxville, TN 37996-1320}
@@
 \begin{abstract}
-Building on the framework of Zhang \& Shu \cite{zhangShu_2010a,zhangShu_2010b}, we develop a realizability-preserving method to simulate transport of particles (fermions) through a background material using the two-moment model of radiation transport, which evolves angular moments of a phase space distribution function $f$.
-The two-moment model is closed using simple algebraic moment closures, e.g., as proposed by Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Banach \& Larecki \cite{banachLarecki_2017a}.  
+Building on the framework of Zhang \& Shu \cite{zhangShu_2010a,zhangShu_2010b}, we develop a realizability-preserving method to simulate transport of particles (fermions) through a background material using the two-moment model of particle transport, which evolves angular moments of a phase space distribution function $f$.
+The two-moment model is closed using algebraic moment closures; e.g., as proposed by Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Banach \& Larecki \cite{banachLarecki_2017a}.  
 Variations of this model have recently been used to simulate neutrino transport in nuclear astrophysics applications --- including core-collapse supernovae and compact binary mergers.  
@@
 This realizability-preserving scheme combines a suitable CFL condition, a realizability-enforcing limiter, a closure procedure based on Fermi-Dirac statistics, and an IMEX scheme whose stages can be written as a convex combination of forward Euler steps combined with a backward Euler step.
-The IMEX scheme is formally only first-order accurate, but works well in the diffusion limit, and --- without interactions with the background --- reduces to the optimal second-order explicit strong stability-preserving Runge-Kutta scheme of Shu \& Osher \cite{shuOsher_1988}.
+The IMEX scheme is formally only first-order accurate, but works well in the diffusion limit, and --- without interactions with the background --- reduces to the optimal second-order strong stability-preserving explicit Runge-Kutta scheme of Shu \& Osher \cite{shuOsher_1988}.
 Numerical results demonstrate the realizability-preserving properties of the scheme.  
@@
 
-\clearpage
-
 \section*{References}

### 2018-09-06 Documents/M1/realizableFermionicM1/sections/appendix.tex
Various edits.  Replaces homogeneous sphere figures

@@
 
-We have found diffusion accurate, constraint-preserving IMEX schemes of type ARS that are second-order accurate in the streaming limit, which we refer to as IMEX PD-ARS; see \ref{app:PD-ARS}.  
+We have found a family of constraint-preserving, diffusion accurate IMEX schemes of type ARS that are second-order accurate in the streaming limit, which we refer to as IMEX PD-ARS; see \ref{app:PD-ARS}.
 For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.
@@
 We refer to the resulting IMEX scheme as PD-ARS.  
-The double Butcher tableau is
+For a 3-stage scheme, the double Butcher tableau is
 \begin{equation}
@@
 \end{equation}
-Imposing the equality constraints (i.e., Eqs.~\eqref{eq:implicitConsistency}, \eqref{eq:orderConditionsEx}, and \eqref{eq:diffusionCondition}), the double Butcher tableau can be written in terms of two parameters ($x$ and $y$) as
+Imposing the equality constraints (i.e., Eqs.~\eqref{eq:implicitConsistency}, \eqref{eq:orderConditionsEx}, and \eqref{eq:diffusionCondition}), the double Butcher tableau can be written in terms of two independent parameters ($x,y\in\bbR$) as
 \begin{equation}
@@
 
-Here we prove that a PD-IMEX scheme (i.e., conforming to Definition~\ref{def:PD-IMEX}) of type~A does not exist.  
+Here we prove that a PD-IMEX scheme  of type~A (i.e., conforming to Definition~\ref{def:PD-IMEX} with Eq.~\eqref{eq:positivityConditionsTypeA} replacing Eq.~\eqref{eq:positivityConditionsTypeARS} in item 3) does not exist.
 First, for a three-stage, GSA IMEX scheme of type~A the double Butcher tableau is
@@
 \end{align}
-The constraint-preserving property requires $a_{11}, a_{22}, a_{33}>0$.  
-The inequality constraints in Eq.~\eqref{eq:positivityConditionsTypeA} also require
+Next we consider the inequality constraints.  
+The constraint-preserving property in Eq.~\eqref{eq:positivityConditionsTypeA} requires $a_{11}, a_{22}, a_{33}>0$, and 
 \begin{equation}

### 2018-09-06 Documents/M1/realizableFermionicM1/sections/conclusion.tex
Various edits.  Replaces homogeneous sphere figures

@@
 We have developed a realizability-preserving DG-IMEX scheme for a two-moment model for fermion transport.  
-The scheme employs simple algebraic two-moment closures rooted in Fermi-Dirac statistics, and combines a time step restriction (CFL condition), a realizability-enforcing limiter, and a constraint-preserving time integrator to maintain point-wise realizability of the moments.
+The scheme employs algebraic two-moment closures rooted in Fermi-Dirac statistics, and combines a time step restriction (CFL condition), a realizability-enforcing limiter, and a constraint-preserving time integrator to maintain point-wise realizability of the moments.
 Since the realizable domain is a convex set, the realizability-preserving property is obtained from convexity arguments, building on the framework in \cite{zhangShu_2010a}.
@@
 In the applications motivating this work, the collision term is stiff in regions of the computational domain, and we have considered IMEX schemes to avoid solving the transport operator implicitly in a fully implicit scheme.
-We considered recently proposed second-order accurate, constraint-preserving IMEX schemes (cf.
-\cite{chertock_etal_2015,hu_etal_2018}), which restore second-order accuracy with an implicit correction step.
+We considered recently proposed second-order accurate, constraint-preserving IMEX schemes \cite{chertock_etal_2015,hu_etal_2018}, which restore second-order accuracy with an implicit correction step.
 However, we are unable to prove realizability (without invoking a very small time step) with the approach in \cite{chertock_etal_2015}, and we have demonstrated that the approach in \cite{hu_etal_2018} does not perform well in the diffusion limit.
 For these reasons, and the general nonexistence of high-order, implicit SSP-RK schemes \cite{gottlieb_etal_2001}, we have resorted to develop first-order, constraint-preserving IMEX schemes.  
-While the proposed scheme (dubbed PD-ARS) is formally only first-order accurate, it works well in the diffusion limit, is constraint-preserving with a reasonable time step, and reduces to the optimal second-order accurate SSP-RK scheme in the streaming limit.
+While the proposed scheme (dubbed PD-ARS) is formally only first-order accurate, it works well in the diffusion limit, is constraint-preserving with a reasonable time step, and reduces to the optimal second-order accurate explicit SSP-RK scheme in the streaming limit.
 
-For each stage of the IMEX scheme, the cell-averaged moments can be written as a convex combination of forward Euler steps (implying the Shu-Osher form for the explicit part), followed by a backward Euler step.
-Realizability of the explicit part requires the DG solution to be realizable in a finite number of quadrature points in each element and the time step to satisfy a CFL condition.  
-For the backward Euler step, realizability of the cell-averages follows easily from the simple form of the collision operator (which includes emission, absorption, and isotropic elastic scattering), and is independent of the time step.
-The CFL condition is then solely due to the transport operator, and the time step can be as large as that of the forward Euler scheme applied to the explicit part.  
-After each update, the limiter enforces moment realizability point-wise by damping towards the realizable cell average.  
+For each stage of the IMEX scheme, the update of the cell-averaged moments can be written as a convex combination of forward Euler steps (implying the Shu-Osher form for the explicit part), followed by a backward Euler step.
+Realizability of the cell-averaged moments due to the explicit part requires the DG solution to be realizable in a finite number of quadrature points in each element and the time step to satisfy a CFL condition.
+For the backward Euler step, realizability of the cell-averages follows easily from the simple form of the collision operator (which includes emission, absorption, and isotropic scattering without energy exchange), and is independent of the time step.
+The CFL condition is then solely due to the transport operator, and the time step can be as large as that of the forward Euler scheme applied to the explicit part of the cell-average update.  
+After each stage update, the limiter enforces moment realizability point-wise by damping towards the realizable cell average.  
 Numerical experiments are presented to demonstrate the accuracy and realizability-preserving property of the scheme.  
@@
 Realizability of the fermionic two-moment model depends sensitively on the closure procedure.  
-For the simple algebraic closures adapted in this work, realizability of the scheme demands that lower and upper bounds on the Eddington factor are satisfied \cite{levermore_1984,lareckiBanach_2011}.
-The Eddington factors deriving from the maximum entropy closures of Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Larecki \& Banach \cite{lareckiBanach_2011}, and the Kershaw-type closure of Larecki \& Banach \cite{banachLarecki_2017a} satisfy these bounds, and are suitable for the fermionic two-moment model.
-Further approximations of the closure procedure, e.g., employing the low occupancy limit, which results in the Minerbo closure \cite{minerbo_1978} when starting with the maximum entropy closure of \cite{cernohorskyBludman_1994}, is not compatible with realizability of the fermionic two-moment model, and we caution against this approach to modeling particle systems governed by Fermi-Dirac statistics; particularly if the low occupancy approximation is unlikely to hold (e.g., when modeling neutrino transport in core-collapse supernovae).
+For the algebraic closures adapted in this work, realizability of the scheme demands that lower and upper bounds on the Eddington factor are satisfied \cite{levermore_1984,lareckiBanach_2011}.  
+The Eddington factors deriving from the maximum entropy closures of Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Larecki \& Banach \cite{lareckiBanach_2011}, and the Kershaw-type closure of Larecki \& Banach \cite{banachLarecki_2017a}, satisfy these bounds, and are suitable for the fermionic two-moment model.
+Further approximations of the closure procedure (e.g., employing the low occupancy limit, which results in the Minerbo closure \cite{minerbo_1978} when starting with the maximum entropy closure of \cite{cernohorskyBludman_1994}) is not compatible with realizability of the fermionic two-moment model, and we caution against this approach to modeling particle systems governed by Fermi-Dirac statistics; particularly if the low occupancy approximation is unlikely to hold (e.g., when modeling neutrino transport in core-collapse supernovae).
 
 In this work, we considered a relatively simple model.  
-In particular, we adopted Cartesian coordinates, assumed a linear collision operator and a fixed material background.  
-Inelastic scattering and relativistic effects (e.g., due to interactions with a moving background or the presence of a strong gravitational field) were not included.  
-To solve more realistic problems of higher scientific interest, some or all of these physical effects may have to be included.  
-In the context of constraint-preserving schemes, these extension provide significant challenges suitable for future investigations, and for which the scheme presented here may serve as a foundation.
+In particular, we adopted Cartesian coordinates, and assumed a linear collision operator and a fixed material background.  
+Scattering with energy exchange and relativistic effects (e.g., due to a moving material and the presence of a strong gravitational field) were not included.  
+To solve more realistic problems of scientific interest, some or all of these physical effects will have to be included.  
+In the context of developing constraint-preserving schemes, these extensions will provide significant challenges suitable for future investigations, for which the scheme presented here may serve as a foundation.

### 2018-09-06 Documents/M1/realizableFermionicM1/sections/imex.tex
Various edits.  Replaces homogeneous sphere figures

@@
 \begin{define}
-  Given sufficient conditions, a constraint-preserving time integration scheme preserves the constraints of a model if the set of admissible states satisfying the constraints form a convex set.  
+  Given sufficient conditions, a constraint-preserving time integration scheme preserves the constraints of a model if the set of admissible states satisfying the constraints forms a convex set.  
   \label{def:constraintPreserving}
@@
 However, we have not been able to prove the realizability-preserving property with this approach without invoking a too severe time step restriction.  
-We therefore proceed to design constraint-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
+We therefore proceed to design constraint-preserving IMEX schemes, without the correction step, that perform well in the diffusion limit.  
 We limit the scope to IMEX schemes of type~ARS.  
@@
 We take a heuristic approach to determine conditions on the coefficients of the IMEX scheme to ensure it performs well in the diffusion limit.  
+We leave the spatial discretization unspecified.  
 Define the vectors 
@@
 \end{equation}
+(The components of $\vec{\cJ}$ and $\vec{\vect{\cH}}$ can, e.g., be the cell averages evolved with the DG method.)  
 We can then write the stages of the IMEX scheme in Eq.~\eqref{imexStages} applied to the number density equation as
@@
 The stability regions of PA2+ and PD-ARS are plotted in Figure~\ref{fig:AbsoluteStability}.  
+(Contours of constant $z_{2}$ are included, and the stability region for a given $z_{2}$ is enclosed by the corresponding contour.)  
 As can be seen from the figures, the absolute stability region of both schemes increases with increasing $|z_{2}|$ (increased damping).  
-For a given $|z_{2}|\ge0$, the stability region of PD-ARS is larger than that of PA2+.  
+For a given $|z_{2}|>0$, the stability region of PD-ARS is larger than that of PA2+.  
 In the linear case, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme ($|z_2| = 0$) fulfills the stability requirement for the IMEX scheme as whole ($|z_2| \geq 0$).

### 2018-09-06 Documents/M1/realizableFermionicM1/sections/intro.tex
Various edits.  Replaces homogeneous sphere figures

@@
 
-In this paper we design numerical methods to solve the two-moment model governing transport of particles obeying by Fermi-Dirac statistics (e.g., neutrinos), with the ultimate target being nuclear astrophysics applications (e.g., neutrino transport in core-collapse supernovae and compact binary mergers).
-The numerical method is based on the discontinuous Galerkin (DG) method for spatial discretization, implicit-explicit (IMEX) methods for time integration, and is designed to preserve certain physical constraints of the underlying model.
+In this paper we design numerical methods to solve the two-moment model governing transport of particles obeying Fermi-Dirac statistics (e.g., neutrinos), with the ultimate target being nuclear astrophysics applications (e.g., neutrino transport in core-collapse supernovae and compact binary mergers).
+The numerical method is based on the discontinuous Galerkin (DG) method for spatial discretization and implicit-explicit (IMEX) methods for time integration, and is designed to preserve certain physical constraints of the underlying model.
 The latter property is achieved by considering the spatial and temporal discretization together with the closure procedure for the two-moment model.
@@
 In many applications, the particle mean free path is comparable to or exceeds other characteristic length scales in the system under consideration (i.e., the Knudsen number exceeds unity), and non-equilibrium effects may become important.
-In these situations, a kinetic description may be required, where particle distribution function $f(\vect{p},\vect{x},t)$ is solved for.  
+In these situations, a kinetic description may be required, where a particle distribution function $f(\vect{p},\vect{x},t)$ is solved for.  
 The distribution function, a phase space density depending on momentum $\vect{p}\in\bbR^{3}$ and position $\vect{x}\in\bbR^{3}$, gives at time $t\in\bbR^{+}$ the number of particles in the phase space volume element $d\vect{p}\,d\vect{x}$ (i.e., $dN=f\,d\vect{p}\,d\vect{x}$).
@@
 Because of the upper bound on the distribution function, the algebraic constraints on realizable moments differ from the classical case with no upper bound, and can lead to significantly different dynamics when the occupancy is high (i.e., when $f$ is close to its upper bound).
-In the fermionic case, the set of realizable moments generated by the particle density and flux vector is also convex, and resembles a ``pinched'' cone.  
+In the fermionic case, the set of realizable moments generated by the particle density and flux vector is also convex, and resembles a ``pinched'' cone (as will be shown; cf.
+Figure~\ref{fig:RealizableSetFermionic} in Section~\ref{sec:realizability}).
 It coincides with the realizable set for the classical case when the occupancy is low, but is much more restricted for high occupancy.
@@
 Furthermore, they can easily be applied to problems involving curvilinear coordinates (e.g., beneficial in numerical relativity \cite{teukolsky_2016}).  
-Importantly, DG methods, exhibit favorable properties when collisions with a background are included as they recover the correct asymptotic behavior in the diffusion limit, characterized by frequent collisions (e.g., \cite{larsenMorel_1989,adams_2001,guermondKanschat_2010}).
-The DG method was introduced in the 1970s by Reed \& Hill \cite{reedHill_1973} to solve the neutron transport equation, and has undergone remarkable developments since then (see, e.g., \cite{shu_2016}, and references therein).
+Importantly, DG methods exhibit favorable properties when collisions with a background are included, as they recover the correct asymptotic behavior in the diffusion limit, characterized by frequent collisions (e.g., \cite{larsenMorel_1989,adams_2001,guermondKanschat_2010}).
+The DG method was introduced in the 1970s by Reed \& Hill \cite{reedHill_1973} to solve the neutron transport equation, and has undergone remarkable developments since then (see, e.g., \cite{shu_2016} and references therein).
 
@@
 Our approach is based on the constraint-preserving (CP) framework introduced in \cite{zhangShu_2010a}, and later extended to the Euler equations of gas dynamics in \cite{zhangShu_2010b}.  
-(See e.g., \cite{xing_etal_2010,zhangShu_2011,olbrant_etal_2012,cheng_etal_2013,zhang_etal_2013,endeve_etal_2015,wuTang_2015}, for extensions and applications to other systems.)  
-The main ingredients include (1) a realizability-preserving update for the cell averaged moments based on Euler time stepping, which evaluates the polynomial representation of the DG method in a finite number of quadrature points in the local elements and results in a Courant-Friedrichs-Lewy (CFL) condition on the time step; (2) a limiter to modify the polynomial representation to ensure that the algebraic constraints are satisfied point-wise without changing the cell average of the moments; and (3) a time stepping method that can be expressed as a convex combination of Euler steps, and therefore preserves the algebraic constraints as the Euler methods (possibly with a modified CFL condition).
+(See, e.g., \cite{xing_etal_2010,zhangShu_2011,olbrant_etal_2012,cheng_etal_2013,zhang_etal_2013,endeve_etal_2015,wuTang_2015} for extensions and applications to other systems.)  
+The main ingredients include (1) a realizability-preserving update for the cell averaged moments based on Euler time stepping, which evaluates the polynomial representation of the DG method in a finite number of quadrature points in the local elements and results in a Courant-Friedrichs-Lewy (CFL) condition on the time step; (2) a limiter to modify the polynomial representation to ensure that the algebraic constraints are satisfied point-wise without changing the cell average of the moments; and (3) a time stepping method that can be expressed as a convex combination of Euler steps, and therefore preserves the algebraic constraints as do the Euler methods (possibly with a modified CFL condition).
 
@@
 This approach is motivated by the fact that we can resolve time scales associated with particle streaming terms in the moment equations, which will be integrated with explicit methods, while terms associated with collisional interactions with the background induce fast time scales that we do not wish to resolve, and will be integrated with implicit methods.
-This splitting has some advantages when solving kinetic equations since the collisional interactions may couple across momentum space, but are local in position space, and is easier to parallelize than a fully implicit approach.
+This splitting has some advantages when solving kinetic equations since the collisional interactions may couple across momentum space, but are local in position space, and are easier to parallelize than a fully implicit approach.
 
-The CP framework of \cite{zhangShu_2010a} achieve high order (i.e., greater than first order) accuracy in time by employing explicit strong stability-preserving Runge-Kutta (SSP-RK) methods \cite{shuOsher_1988,gottlieb_etal_2001}, which can be written as a convex combination of forward Euler steps.
-Unfortunately, this strategy to achieve high order temporal accuracy does not work as straightforwardly for standard IMEX Runge-Kutta (IMEX-RK) methods because implicit SSP Runge-Kutta methods with greater than first order accuracy do not exist \cite{gottlieb_etal_2001}.
-To break this ``barrier'', recently proposed IMEX-RK schemes \cite{chertock_etal_2015,hu_etal_2018} have resorted to first order accuracy in favor of the SSP property in the standard IMEX-RK scheme, and recover second-order accuracy with a correction step.
+The CP framework of \cite{zhangShu_2010a} achieves high-order (i.e., greater than first order) accuracy in time by employing strong stability-preserving explicit Runge-Kutta (SSP-RK) methods \cite{shuOsher_1988,gottlieb_etal_2001}, which can be written as a convex combination of forward Euler steps.
+Unfortunately, this strategy to achieve high-order temporal accuracy does not work as straightforwardly for standard IMEX Runge-Kutta (IMEX-RK) methods because implicit SSP Runge-Kutta methods with greater than first order accuracy do not exist \cite{gottlieb_etal_2001}.
+To break this ``barrier,'' recently proposed IMEX-RK schemes \cite{chertock_etal_2015,hu_etal_2018} have resorted to first order accuracy in favor of the SSP property in the standard IMEX-RK scheme, and recover second-order accuracy with a correction step.
 
 We consider the application of the correction approach to the two-moment model.  
-However, with the correction step from \cite{chertock_etal_2015} we are unable to prove the realizability-preserving property without invoking a too restrictive time step.  
+However, with the correction step from \cite{chertock_etal_2015} we are unable to prove the realizability-preserving property without invoking a too-restrictive time step.  
 With the correction step from \cite{hu_etal_2018} the realizability-preserving property is guaranteed with a time step comparable to that of the forward Euler method applied to the explicit part of the scheme, but the resulting scheme performs poorly in the asymptotic diffusion limit.
@@
 Realizability of individual elements in the convex combination is conditional on the closure procedure (components of the Eddington tensor must be computed to evaluate numerical fluxes).  
-We prove that each element in the convex combination is realizable, provided the moments involved in expressing the elements are moments of a distribution function satisfying the bounds implied by Fermi-Dirac statistics (i.e., $0\le f \le 1$).
-For simple algebraic two-moment closures, which we consider, the so-called Eddington factor is given by an algebraic expression depending on the evolved moments and completely determines the components of the Eddington tensor.
-Realizable components of the Eddington tensor demands that the Eddington factor satisfies strict lower and upper bounds (e.g., \cite{levermore_1984,lareckiBanach_2011}).  
-We discuss simple algebraic closures derived from Fermi-Dirac statistics that satisfy these bounds, and demonstrate with numerical experiments that the DG-IMEX scheme preserves realizability of the moments when these closures are used.
-We also demonstrate that further approximations to algebraic two-moment closures for modeling particle systems governed by Fermi-Dirac statistics may give results that are incompatible with a bounded distribution and therefore unphysical.
+We prove that each element in the convex combination is realizable provided the moments involved in expressing the elements are moments of a distribution function satisfying the bounds implied by Fermi-Dirac statistics (i.e., $0\le f \le 1$).
+For algebraic two-moment closures, which we consider, the so-called Eddington factor is given by an algebraic expression depending on the evolved moments and completely determines the components of the Eddington tensor.
+Realizable components of the Eddington tensor demand that the Eddington factor satisfies strict lower and upper bounds (e.g., \cite{levermore_1984,lareckiBanach_2011}).  
+We discuss algebraic closures derived from Fermi-Dirac statistics that satisfy these bounds, and demonstrate with numerical experiments that the DG-IMEX scheme preserves realizability of the moments when these closures are used.
+We also demonstrate that further approximations to algebraic two-moment closures for modeling particle systems governed by Fermi-Dirac statistics may give results that are incompatible with a bounded distribution and, therefore, unphysical.
 The example we consider is the Minerbo closure \cite{minerbo_1978}, which can be obtained as the low occupancy limit of the maximum entropy closure of Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}.

### 2018-09-06 Documents/M1/realizableFermionicM1/sections/numerical.tex
More edits
Adjusted figure size
Various edits.  Replaces homogeneous sphere figures

@@
 The first set of tests (Section~\ref{sec:smoothProblems}) are included to compare the time integration schemes in various regimes.  
-We are not concerned with moment realizability here, and we do not apply the realizability-enforcing limiter in these tests.  
+We are not concerned with moment realizability in Section~\ref{sec:smoothProblems}, and we do not apply the realizability-enforcing limiter in these tests.  
 The tests in Sections~\ref{sec:packedBeam} and \ref{sec:fermionImplosion} are designed specifically to demonstrate the robustness of the scheme to dynamics near the boundary of the realizable set $\cR$.
@@
 Errors for the remaining schemes (including SSPRK2) are indistinguishable on the plot.  
-\begin{figure}[h]
+\begin{figure}[H]
   \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
   \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
   \centering
   \begin{tabular}{cc}
-    \includegraphics[width=0.485\textwidth]{figures/PackedBeam_ME_CB} &
-    \includegraphics[width=0.485\textwidth]{figures/PackedBeam_ME_MI}
+    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_ME_CB} &
+    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_ME_MI}
   \end{tabular}
@@
 In Figure~\ref{fig:HomogeneousSphere}, we plot results obtained for all tests at $t=5$: Test~A (top panels), Test~B (middle panels), and Test~C (bottom panels).  
-The particle density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$ (left and right panels, respectively) are plotted versus radius $r=|\vect{x}|$ using scatter plots.  
+The particle density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$ (left and right panels, respectively) are plotted versus radius $r=|\vect{x}|$.  
 In each panel, results obtained with the various algebraic closures discussed in Section~\ref{sec:algebraicClosure} are plotted: Minerbo (magenta), CB (blue), BL (green), and Kershaw (cyan).  
 The analytical solution is also plotted (dashed black lines).  
-\begin{figure}[h]
+\begin{figure}[H]
   \centering
@@
 blue boxes in the upper right panel).
-\begin{figure}[h]
+\begin{figure}[H]
   \centering

### 2018-09-11 Documents/M1/realizableFermionicM1/sections/appendix.tex
minor edits

@@
 \end{equation}
+(Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.)
 
@@
 
-Here we prove that a PD-IMEX scheme  of type~A (i.e., conforming to Definition~\ref{def:PD-IMEX} with Eq.~\eqref{eq:positivityConditionsTypeA} replacing Eq.~\eqref{eq:positivityConditionsTypeARS} in item 3) does not exist.
+Here we prove that a PD-IMEX scheme  of type~A (i.e., conforming to Definition~\ref{def:PD-IMEX}, but with Eq.~\eqref{eq:positivityConditionsTypeA} replacing Eq.~\eqref{eq:positivityConditionsTypeARS} in item 3) does not exist.
 First, for a three-stage, GSA IMEX scheme of type~A the double Butcher tableau is

### 2018-09-11 Documents/M1/realizableFermionicM1/sections/imex.tex
minor edits

@@
 We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators (e.g., inelastic scattering).}
-To reduce the number of constraints, and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
+To reduce the number of constraints and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
 Instead, we only require the scheme to be second-order accurate in the streaming limit ($\vect{\cQ}=0$).  

### 2018-09-11 Documents/M1/realizableFermionicM1/manuscript.tex
Moved Ran to first author.  Minor edits to abstract from Cory

@@
 %% Group authors per affiliation:
+\author[utk-phys]{Ran Chu}
+\ead{rchu@vols.utk.edu}
+
 \author[ornl,utk-phys,jics]{Eirik Endeve\corref{cor}}
 \ead{endevee@ornl.gov}
-
-\author[utk-phys]{Ran Chu}
-\ead{rchu@vols.utk.edu}
 
@@
 \begin{abstract}
-Building on the framework of Zhang \& Shu \cite{zhangShu_2010a,zhangShu_2010b}, we develop a realizability-preserving method to simulate transport of particles (fermions) through a background material using the two-moment model of particle transport, which evolves angular moments of a phase space distribution function $f$.
+Building on the framework of Zhang \& Shu \cite{zhangShu_2010a,zhangShu_2010b}, we develop a realizability-preserving method to simulate the transport of particles (fermions) through a background material using a two-moment model that evolves the angular moments of a phase space distribution function $f$.
 The two-moment model is closed using algebraic moment closures; e.g., as proposed by Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Banach \& Larecki \cite{banachLarecki_2017a}.  
-Variations of this model have recently been used to simulate neutrino transport in nuclear astrophysics applications --- including core-collapse supernovae and compact binary mergers.  
+Variations of this model have recently been used to simulate neutrino transport in nuclear astrophysics applications, including core-collapse supernovae and compact binary mergers.  
 We employ the discontinuous Galerkin (DG) method for spatial discretization (in part to capture the asymptotic diffusion limit of the model) combined with implicit-explicit (IMEX) time integration to stably bypass short timescales induced by frequent interactions between particles and the background.

### 2018-09-11 Documents/M1/realizableFermionicM1/sections/intro.tex
Edits to Sections 1 and 2 after comments form Cory

@@
 
-In this paper we design numerical methods to solve the two-moment model governing transport of particles obeying Fermi-Dirac statistics (e.g., neutrinos), with the ultimate target being nuclear astrophysics applications (e.g., neutrino transport in core-collapse supernovae and compact binary mergers).
-The numerical method is based on the discontinuous Galerkin (DG) method for spatial discretization and implicit-explicit (IMEX) methods for time integration, and is designed to preserve certain physical constraints of the underlying model.
+In this paper we design numerical methods to solve a two-moment model that governs the transport of particles obeying Fermi-Dirac statistics (e.g., neutrinos), with the ultimate target being nuclear astrophysics applications (e.g., neutrino transport in core-collapse supernovae and compact binary mergers).
+The numerical method is based on the discontinuous Galerkin (DG) method for spatial discretization and implicit-explicit (IMEX) methods for time integration, and it is designed to preserve certain physical constraints of the underlying model.
 The latter property is achieved by considering the spatial and temporal discretization together with the closure procedure for the two-moment model.
 
-In many applications, the particle mean free path is comparable to or exceeds other characteristic length scales in the system under consideration (i.e., the Knudsen number exceeds unity), and non-equilibrium effects may become important.
-In these situations, a kinetic description may be required, where a particle distribution function $f(\vect{p},\vect{x},t)$ is solved for.  
-The distribution function, a phase space density depending on momentum $\vect{p}\in\bbR^{3}$ and position $\vect{x}\in\bbR^{3}$, gives at time $t\in\bbR^{+}$ the number of particles in the phase space volume element $d\vect{p}\,d\vect{x}$ (i.e., $dN=f\,d\vect{p}\,d\vect{x}$).
-The evolution of the distribution function is governed by the Boltzmann equation, which states a balance between phase space advection and collisions (see, e.g., \cite{braginskii_1965,chapmanCowling_1970,lifshitzPitaevskii_1981}).
+In many applications, the particle mean free path is comparable to or exceeds other characteristic length scales in the system under consideration, and non-equilibrium effects may become important.  
+In these situations, a kinetic description based on a particle distribution function may be required.  
+The distribution function, a phase space density $f$ depending on momentum $\vect{p}\in\bbR^{3}$ and position $\vect{x}\in\bbR^{3}$, is defined such that $f(\vect{p},\vect{x},t)$ gives at time $t\in\bbR^{+}$ the number of particles in the phase space volume element $d\vect{p}\,d\vect{x}$ (i.e., $d\cN=f\,d\vect{p}\,d\vect{x}$).
+The evolution of the distribution function is governed by the Boltzmann equation, which states a balance between phase space advection and particle collisions (see, e.g., \cite{braginskii_1965,chapmanCowling_1970,lifshitzPitaevskii_1981}).
 
 Solving the Boltzmann equation numerically for $f$ is challenging, in part due to the high dimensionality of phase space.  
-To reduce the dimensionality of the problem and make it more computationally tractable, one may instead solve for a finite number of angular moments $\vect{m}_{N}=(m^{(0)},m^{(1)},\ldots,m^{(N)})^{T}$ of the distribution function, defined as
+To reduce the dimensionality of the problem and make it more computationally tractable, one may instead solve (approximately) for a finite number of angular moments $\vect{m}_{N}=(m^{(0)},m^{(1)},\ldots,m^{(N)})^{T}$ of the distribution function, defined as
 \begin{equation}
@@
 
-In a truncated moment model, the equation governing the evolution of the $N$-th moment $m^{(N)}$ contains higher moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified in order to form a closed system of equations.
+In a truncated moment model, the equation governing the evolution of the \mbox{$N$-th} moment $m^{(N)}$ contains higher moments $\{m^{(k)}\}_{k=N+1}^{M}$ ($M>N$), which must be specified in order to form a closed system of equations.
 For the two-moment model, the symmetric rank-two Eddington tensor (proportional to the pressure tensor) must be specified.  
-Approaches to this \emph{closure problem} include setting $m^{(k)}=0$, for $k>N$ ($P_N$ approximation \cite{brunnerHolloway_2005}), Eddington approximation \cite{mihalasMihalas_1999}, Kershaw-type closure \cite{kershaw_1976}, and maximum entropy closure \cite{minerbo_1978,cernohorskyBludman_1994}.
+Approaches to this \emph{closure problem} include setting $m^{(k)}=0$, for $k>N$ ($P_N$ equations \cite{brunnerHolloway_2005} and filtered versions thereof \cite{mcclarrenHauck_2010,laboure_etal_2016}), Eddington approximation (when $N=0$) \cite{mihalasMihalas_1999}, Kershaw-type closure \cite{kershaw_1976}, and maximum entropy closure \cite{minerbo_1978,cernohorskyBludman_1994,olbrant_etal_2013}.
 The closure procedure often results in a system of nonlinear hyperbolic conservation laws, which can be solved using suitable numerical methods (e.g., \cite{leveque_1992}).
@@
 Because of the upper bound on the distribution function, the algebraic constraints on realizable moments differ from the classical case with no upper bound, and can lead to significantly different dynamics when the occupancy is high (i.e., when $f$ is close to its upper bound).
-In the fermionic case, the set of realizable moments generated by the particle density and flux vector is also convex, and resembles a ``pinched'' cone (as will be shown; cf.
-Figure~\ref{fig:RealizableSetFermionic} in Section~\ref{sec:realizability}).
-It coincides with the realizable set for the classical case when the occupancy is low, but is much more restricted for high occupancy.
+In the fermionic case, the set of realizable moments generated by the particle density and flux vector is also convex. 
+It is ``eye-shaped'' (as will be shown later; cf.
+Figure~\ref{fig:RealizableSetFermionic} in Section~\ref{sec:realizability}) and tangent to the classical realizability cone on the end representing low occupancy, but is much more restricted for high occupancy.
 
 In this paper, the two-moment model is discretized in space using high-order Discontinuous Galerkin (DG) methods (e.g., \cite{cockburnShu_2001,hesthavenWarburton_2008}).  
-DG methods combine elements from both spectral and finite volume methods, and are an attractive option for solving hyperbolic partial differential equations (PDEs).  
+DG methods combine elements from both spectral and finite volume methods and are an attractive option for solving hyperbolic partial differential equations (PDEs).  
 They achieve high-order accuracy on a compact stencil; i.e., data is only communicated with nearest neighbors, regardless of the formal order of accuracy, which can lead to a high computation to communication ratio, and favorable parallel scalability on heterogeneous architectures has been demonstrated \cite{klockner_etal_2009}.
@@
 (See, e.g., \cite{xing_etal_2010,zhangShu_2011,olbrant_etal_2012,cheng_etal_2013,zhang_etal_2013,endeve_etal_2015,wuTang_2015} for extensions and applications to other systems.)  
-The main ingredients include (1) a realizability-preserving update for the cell averaged moments based on Euler time stepping, which evaluates the polynomial representation of the DG method in a finite number of quadrature points in the local elements and results in a Courant-Friedrichs-Lewy (CFL) condition on the time step; (2) a limiter to modify the polynomial representation to ensure that the algebraic constraints are satisfied point-wise without changing the cell average of the moments; and (3) a time stepping method that can be expressed as a convex combination of Euler steps, and therefore preserves the algebraic constraints as do the Euler methods (possibly with a modified CFL condition).
+The main ingredients include (1) a realizability-preserving update for the cell averaged moments based on forward Euler time stepping, which evaluates the polynomial representation of the DG method in a finite number of quadrature points in the local elements and results in a Courant-Friedrichs-Lewy (CFL) condition on the time step; (2) a limiter to modify the polynomial representation to ensure that the algebraic constraints are satisfied point-wise without changing the cell average of the moments; and (3) a time stepping method that can be expressed as a convex combination of Euler steps and therefore preserves the algebraic constraints (possibly with a modified CFL condition).
+As such, our method is an extension of the realizability-preserving scheme developed by Olbrant el al. \cite{olbrant_etal_2012} for the classical two-moment model.
 
@@
 The CP framework of \cite{zhangShu_2010a} achieves high-order (i.e., greater than first order) accuracy in time by employing strong stability-preserving explicit Runge-Kutta (SSP-RK) methods \cite{shuOsher_1988,gottlieb_etal_2001}, which can be written as a convex combination of forward Euler steps.
-Unfortunately, this strategy to achieve high-order temporal accuracy does not work as straightforwardly for standard IMEX Runge-Kutta (IMEX-RK) methods because implicit SSP Runge-Kutta methods with greater than first order accuracy do not exist \cite{gottlieb_etal_2001}.
+Unfortunately, this strategy to achieve high-order temporal accuracy does not work as straightforwardly for standard IMEX Runge-Kutta (IMEX-RK) methods because implicit SSP Runge-Kutta methods with greater than first order accuracy have time step restrictions similar to explicit methods \cite{gottlieb_etal_2001}.
 To break this ``barrier,'' recently proposed IMEX-RK schemes \cite{chertock_etal_2015,hu_etal_2018} have resorted to first order accuracy in favor of the SSP property in the standard IMEX-RK scheme, and recover second-order accuracy with a correction step.
@@
 We consider the application of the correction approach to the two-moment model.  
-However, with the correction step from \cite{chertock_etal_2015} we are unable to prove the realizability-preserving property without invoking a too-restrictive time step.  
+However, with the correction step from \cite{chertock_etal_2015} we are unable to prove the realizability-preserving property without invoking an overly restrictive time step.  
 With the correction step from \cite{hu_etal_2018} the realizability-preserving property is guaranteed with a time step comparable to that of the forward Euler method applied to the explicit part of the scheme, but the resulting scheme performs poorly in the asymptotic diffusion limit.
@@
 The realizability-preserving property of the DG-IMEX scheme depends sensitively on the adopted closure procedure.  
-Employing the simple Lax-Friedrichs flux and imposing a suitable CFL condition on the time step, the explicit update of the cell average can be written as a convex combination.  
+The explicit update of the cell average can, after employing the simple Lax-Friedrichs flux and imposing a suitable CFL condition on the time step, be written as a convex combination.  
 Realizability of the updated cell average is then guaranteed from convexity arguments \cite{zhangShu_2010a}, provided all the elements in the convex combination are realizable.  

### 2018-09-11 Documents/M1/realizableFermionicM1/sections/model.tex
Changes due to comments from Tony and Cory.  Work on IMEX section
Edits to Sections 1 and 2 after comments form Cory

@@
 \section{Mathematical Model}
+\label{sec:model}
 
@@
 
-We consider approximate solutions to the Boltzmann equation for transport of massless particles through a static material in Cartesian geometry, which, after scaling to dimensionless units, can be written as
+We consider approximate solutions to the Boltzmann equation for the transport of massless particles through a static material in Cartesian geometry, which, after scaling to dimensionless units, can be written as
 \begin{equation}
@@
 \end{equation}
-where the distribution function $f\colon(\omega,\varepsilon,\vect{x},t)\in\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in direction $\omega\in\bbS^{2}:=\{\,\omega=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
+where the distribution function $f\colon(\omega,\varepsilon,\vect{x},t)\in\bbS^{2}\times\bbR^{+}\times\bbR^{3}\times\bbR^{+}\to\bbR^{+}$ gives the number of particles propagating in the direction $\omega\in\bbS^{2}:=\{\,\omega=(\thetaNu,\phiNu)~|~\thetaNu\in[0,\pi],\phiNu\in[0,2\pi)\,\}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
 Here we use spherical momentum space coordinates $(\varepsilon,\omega)$, and the unit vector $\vect{\ell}(\omega)\in\bbR^{3}$ (independent of $\varepsilon$ and $\vect{x}$) is parallel to the particle three-momentum $\vect{p}=\varepsilon\,\vect{\ell}$.
@@
 In opaque regions, $\tau\ll1$, while for free streaming particles, $\tau\gg1$.  
-The collision term, due to emission, absorption, and isotropic and elastic scattering, is given by
+The collision operator, which models emission, absorption, and isotropic and elastic scattering, is given by
 \begin{equation}
@@
 \end{equation}
-where evolved moments are $\vect{\cM}=(\cJ,\vect{\cH})^{T}$ and $\vect{\cF}$ are the fluxes.  
+where $\vect{\cM}=(\cJ,\vect{\cH})^{T}$ and $\vect{\cF}=(\vect{\cH},\vect{\cK})^{T}$.  
 Components of the fluxes in each coordinate direction are $\vect{\cF}^{i}=\vect{e}_{i}\cdot\vect{\cF}=(\vect{e}_{i}\cdot\vect{\cH},\vect{e}_{i}\cdot\vect{\cK})^{T}$, where $\vect{e}_{i}$ is the unit vector parallel to the $i$th coordinate direction.
@@
 In order to close the system given by Eq.~\eqref{eq:momentEquations}, the components of the stress tensor $\vect{\cK}$ must be related to the lower moments through a closure procedure.  
-To this end, Levermore \cite{levermore_1984} defined the Eddington tensor $\vect{k}=\vect{\cK}/\cJ$, assumed that the radiation field is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, so that
+To this end, Levermore \cite{levermore_1984} defined the Eddington tensor $\vect{k}=\vect{\cK}/\cJ$ and assumed that the radiation field is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$ so that
 \begin{equation}

### 2018-09-12 Documents/Euler/dgEulerGR.tex
Added bound-preserving time-step constraints derivation to dgEulerGR

@@
 \title{Nodal Discontinuous Galerkin Method for the Euler Equations in GR}
-\author{Sam Dunham\altaffilmark{1}, Eirik Endeve\altaffilmark{2}, et al.}
-\altaffiltext{2}{Vanderbilt}
+\author{Samuel J Dunham\altaffilmark{1}, Eirik Endeve\altaffilmark{2}, et al.}
+\altaffiltext{2}{Department of Astronomy, Vanderbilt University, 6301 Stevenson Science Center, Nashville TN, 37212, USA; samuel.j.dunham@vanderbilt.edu}
 \altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
@@
 
+\section{Bound-Preserving Methods Using First-Order DG Scheme}
+
+\subsection{Cartesian Coordinates}
+This section closely follows \citet{Qin2016}.
+
+\subsubsection{Set of Admissible States}
+We consider a one-dimensional system of conservation laws:
+\begin{equation*}
+    \pd{\vect{U}}{t} + \pd{\vect{F}\left(\vect{U}\right)}{x} = \vect{0},
+\end{equation*}
+where $\vect{U}$ is a vector of conserved variables, defined as:
+\begin{equation}\label{Eq:ConservedVariables}
+    \vect{U}\longrightarrow\begin{pmatrix} D\\ S\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
+\end{equation}
+and $\vect{F}\left(\vect{U}\right)$ are the fluxes of those conserved quantities:
+\begin{equation}\label{Eq:FluxVector}
+    \vect{F}\left(\vect{U}\right)\longrightarrow\begin{pmatrix}\rho\,W\,v\\ \rho\,h\,W^{2}\,v^{2}+p\\\rho\,h\,W^{2}\,v-D\,v\end{pmatrix}.
+\end{equation}
+
+The physics leads us to define a set of admissible states, $\mc{G}_{p}$ (the subscript $p$ stands for primitive), as:
+\begin{equation*}
+    \mc{G}_{p}\equiv\left\{\vect{U}\Big|\rho>0,\,p>0,\,v^{2}<1\right\}.
+\end{equation*}
+
+It is shown in \citet{Mignone2005} that $\mc{G}$ is a convex set\footnote{Convex in the sense that if $\vect{U}_{1}\in\mc{G}$ and $\vect{U}_{2}\in\mc{G}$, then $\alpha_{1}\,\vect{U}_{1}+\alpha_{2}\,\vect{U}_{2}\in\mc{G}$, where $\alpha_{1},\,\alpha_{2}\in\left[0,1\right]$ and $\alpha_{1}+\alpha_{2}=1$.} and can equivalently be written as:
+\begin{equation}\label{Eq:SetOfAdmissibleStates}
+    \mc{G}\equiv\left\{\vect{U}\Big|D>0,\,\tau+D>\sqrt{D^{2}+S^{2}}\right\}.
+\end{equation}
+
+\subsubsection{Time-Step Derivation/CFL Condition}
+For the first-order DG method using forward-Euler time-stepping, we evolve the vector of conserved variables as:
+\begin{equation}\label{Eq:1stOrderDG}
+    \vect{\ol{U}}^{n+1}_{i}=\vect{\ol{U}}^{n}_{i}-\eta\left[\hat{\vect{F}}\left(\vect{\ol{U}}^{n}_{i},\vect{\ol{U}}^{n}_{i+1}\right)-\hat{\vect{F}}\left(\vect{\ol{U}}^{n}_{i-1},\vect{\ol{U}}^{n}_{i}\right)\right],
+\end{equation}
+where
+\begin{equation*}
+    \vect{\ol{U}}\equiv\f{1}{\Delta x}\int_{k}\vect{U}\,dx,
+\end{equation*}
+$\eta\equiv\Delta t/\Delta x$, and $\hat{\vect{F}}$ is the numerical flux. In this document we use the local Lax-Friedrichs flux, defined as:
+\begin{equation}\label{Eq:LLF}
+    \hat{\vect{F}}\left(a,b\right)=\f{1}{2}\left[\vect{F}\left(a\right)+\vect{F}\left(b\right) - \alpha_{ab}\left(b-a\right)\right],
+\end{equation}
+where $a$ and $b$ represent the state of the fluid in two different elements, $\alpha_{ab}$ is an estimate for the wave-speed:
+\begin{equation*}
+    \alpha_{ab}=\text{max}\left[\alpha\left(a\right),\alpha\left(b\right)\right],
+\end{equation*}
+and $\alpha$ is the largest (in absolute value) eigenvalue of the flux-Jacobian:
+\begin{equation*}
+    \alpha=\left|\left|\f{\p\vect{F}}{\p\vect{U}}\right|\right|.
+\end{equation*}
+Using this we define the following variables:
+\begin{equation}\label{Eq:EigVals}
+    \alpha_{i+\f{1}{2}}=\text{max}\left[\alpha\left(\vect{\ol{U}}_{i}\right),\alpha\left(\vect{\ol{U}}_{i+1}\right)\right],\hspace{3em} \alpha_{i-\f{1}{2}}=\text{max}\left[\alpha\left(\vect{\ol{U}}_{i-1}\right),\alpha\left(\vect{\ol{U}}_{i}\right)\right].
+\end{equation}
+
+Substituting \eqref{Eq:LLF} with \eqref{Eq:EigVals} into \eqref{Eq:1stOrderDG}:
+\begin{align}
+    \vect{\ol{U}}^{n+1}_{i}&=\vect{\ol{U}}^{n}_{i}-\f{\eta}{2}\left[\vect{F}\left(\vect{\ol{U}}^{n}_{i}\right)+\vect{F}\left(\vect{\ol{U}}^{n}_{i+1}\right)-\alpha_{i+\f{1}{2}}\left(\vect{\ol{U}}^{n}_{i+1}-\vect{\ol{U}}^{n}_{i}\right)\right.\nonumber\\
+    &\left.\hspace{7em}-\vect{F}\left(\vect{\ol{U}}^{n}_{i}\right)-\vect{F}\left(\vect{\ol{U}}^{n}_{i-1}\right)+\alpha_{i-\f{1}{2}}\left(\vect{\ol{U}}^{n}_{i}-\vect{\ol{U}}^{n}_{i-1}\right)\right]\nonumber\\
+    &=\left[1-\f{\eta}{2}\left(\alpha_{i+\f{1}{2}}+\alpha_{i-\f{1}{2}}\right)\right]\vect{\ol{U}}^{n}_{i}+\f{\eta}{2}\,\alpha_{i+\f{1}{2}}\left[\vect{\ol{U}}^{n}_{i+1}-\f{1}{\alpha_{i+\f{1}{2}}}\vect{F}\left(\vect{\ol{U}}^{n}_{i+1}\right)\right]\nonumber\\
+    &\hspace{15em}+\f{\eta}{2}\,\alpha_{i-\f{1}{2}}\left[\vect{\ol{U}}^{n}_{i-1}+\f{1}{\alpha_{i-\f{1}{2}}}\vect{F}\left(\vect{\ol{U}}^{n}_{i-1}\right)\right]\nonumber\\
+    &=\left[1-\f{\eta}{2}\left(\alpha_{i+\f{1}{2}}+\alpha_{i-\f{1}{2}}\right)\right]\vect{\ol{U}}^{n}_{i}+\f{\eta}{2}\,\alpha_{i+\f{1}{2}}\,\vect{H}^{-}\left(\vect{\ol{U}}^{n}_{i+1},\alpha_{i+\f{1}{2}}\right)+\f{\eta}{2}\,\alpha_{i+\f{1}{2}}\,\vect{H}^{+}\left(\vect{\ol{U}}^{n}_{i-1},\alpha_{i-\f{1}{2}}\right),\label{Eq:ConvComb}
+\end{align}
+where
+\begin{equation}\label{Eq:Hpm}
+    \vect{H}^{\pm}\left(\vect{\ol{U}},\alpha\right)\equiv\vect{\ol{U}}\pm\f{1}{\alpha}\,\vect{F}\left(\vect{\ol{U}}\right).
+\end{equation}
+
+The proof that $\vect{H}^{\pm}\in\mc{G}$ is given in \citet{Qin2016}.
+Therefore, we see that with a restrictions on $\alpha_{i\pm\f{1}{2}}$ that \eqref{Eq:ConvComb} is a convex combination.
+The restriction is (recalling that $\eta=\Delta t/\Delta x$):
+\begin{equation*}
+    1-\f{\eta}{2}\left(\alpha_{i+\f{1}{2}}+\alpha_{i-\f{1}{2}}\right)>0\implies\f{\eta}{2}\left(\alpha_{i+\f{1}{2}}+\alpha_{i-\f{1}{2}}\right)<1\implies \Delta t<\f{2\,\Delta x}{\alpha_{i+\f{1}{2}}+\alpha_{i-\f{1}{2}}}.
+\end{equation*}
+
+We want a time-step that is the same for all elements at a given time, so we tighten the restriction slightly to:
+\begin{equation*}
+    \Delta t<\f{\Delta x}{\text{max}_{i}\left(\alpha_{i-\f{1}{2}}\right)}.
+\end{equation*}
+
+\newpage
+
+\subsection{Curvilinear Coordinates}
+NOTE: We assume a conformally-flat, time-independent spatial three-metric.
+
+\subsubsection{Set of Admissible States}
+We again consider a one-dimensional system of conservation laws, but this time with a curvilinear metric:
+\begin{equation*}
+    \pd{\left(\sqrtgm\,\vect{U}\right)}{t}+\pd{\left(\sqrtgm\,\vect{F}\right)}{1}=\sqrtgm\,\vect{S},
+\end{equation*}
+where $\vect{U}$ is given by:
+\begin{equation*}
+    \vect{U}\longrightarrow\begin{pmatrix} D\\ S_{1}\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v_{1}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{j}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
+\end{equation*}
+$\vect{F}\left(\vect{U}\right)$ are the fluxes of those conserved quantities:
+\begin{equation*}
+    \vect{F}\left(\vect{U}\right)\longrightarrow\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,v^{1}\,v_{1}+p\,\delta^{1}_{~1}\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{1}\,v^{j}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix},
+\end{equation*}
+and $\vect{S}$ is a source term:
+\begin{align*}
+    \vect{S}\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{1k}\,\p_{1}\gamma_{1k}\\0\end{pmatrix}=\begin{pmatrix}0\\\f{1}{2}\,P^{11}\,\p_{1}\gamma_{11}\\0\end{pmatrix}&=\begin{pmatrix}0\\\f{1}{2}\left[S^{1}\,v^{1}+p\,\gamma^{11}\right]\,\p_{1}\gamma_{11}\\0\end{pmatrix}=\begin{pmatrix}0\\\f{1}{2}\gamma^{11}\left[S_{1}\,v^{1}+p\right]\p_{1}\gamma_{11}\\0\end{pmatrix}\\
+    &=\begin{pmatrix}0\\\f{1}{2}\left[S_{1}\,v^{1}+p\right]\p_{1}\ln\gamma_{11}\\0\end{pmatrix},
+\end{align*}
+where the last equality follows because for a conformally-flat spatial three-metric, $\gamma^{11}=1/\gamma_{11}$.
+
+These definitions lead us to define the same set of admissible states as before, namely:
+\begin{equation*}
+    \mc{G}_{p}\equiv\left\{\vect{U}\Big|\rho>0,\,p>0,\,v^{2}<1\right\},
+\end{equation*}
+the difference being that $v^{2}$ now involves the metric:
+\begin{equation*}
+    v^{2}=v^{i}\,v_{i}=v^{1}\,v_{1}=\gamma_{1j}\,v^{1}\,v^{j}.
+\end{equation*}
+
+Before continuing, we show that the introduction of the metric doesn't affect the translation between $\mc{G}_{p}$ and $\mc{G}$...\sd{Need to do this}
+
+\subsubsection{Time-Step Derivation/CFL Condition}
+We start by integrating both sides over the element and dividing by the volume, $V$:
+\begin{equation*}
+    \f{1}{V}\int_{k}\pd{\left(\sqrtgm\,\vect{U}\right)}{t}dx+\f{1}{V}\int_{k}\pd{\left(\sqrtgm\,\vect{F}\left(\vect{U}\right)\right)}{x}dx=\f{1}{V}\int_{k}\sqrtgm\,\vect{S}\,dx,
+\end{equation*}
+where:
+\begin{equation*}
+    V=\int_{k}dV=\int_{k}\sqrtgm\,dx.
+\end{equation*}
+
+By defining the cell-average as:
+\begin{equation*}
+    \vect{\ol{W}}\equiv\f{1}{V}\int_{k}\vect{W}\,dV,
+\end{equation*}
+we have:
+\begin{equation*}
+    \f{d\,\vect{\ol{U}}}{dt}+\f{1}{V}\left.\left(\sqrtgm\,\hat{\vect{F}}\left(\vect{\ol{U}}\right)\right)\right|^{x_{\iph}}_{x_{\imh}}=\vect{\ol{S}},
+\end{equation*}
+or, using the common notation of the time step being represented as a superscript and the spatial element represented by a subscript:
+\begin{equation*}
+    \vect{\ol{U}}^{n+1}_{i}=\vect{\ol{U}}^{n}_{i}-\f{\Delta t}{V}\left[\sqrtgm_{\iph}\,\hat{\vect{F}}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\vect{F}}^{n}_{\imh}\right]+\Delta t\,\vect{\ol{S}}^{n}_{i}.
+\end{equation*}
+
+Now we define a parameter a la \citet{ZS2011b}: $\ve\in\left(0,1\right)$, such that (NOTE: \citet{ZS2011b} set $\ve=1/2$):
+\begin{equation*}
+    \vect{\ol{U}}^{n}_{i}=\ve\,\vect{\ol{U}}^{n}_{i}+\left(1-\ve\right)\vect{\ol{U}}^{n}_{i}.
+\end{equation*}
+We can use the first term to balance out the term in the square brackets and the second term to balance out the source term.
+
+So, we get:
+\begin{align*}
+    \vect{\ol{U}}^{n+1}_{i}&=\ve\left\{\vect{\ol{U}}^{n}_{i}-\f{\Delta t}{\ve\,V}\left[\sqrtgm_{\iph}\,\hat{\vect{F}}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\vect{F}}^{n}_{\imh}\right]\right\}+\left(1-\ve\right)\vect{\ol{U}}^{n}_{i}+\Delta t\,\vect{\ol{S}}^{n}_{i}\\
+    &=\ve\left\{\vect{\ol{U}}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\vect{F}}\left(\vect{\ol{U}}^{n}_{i+1},\vect{\ol{U}}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\vect{F}}\left(\vect{\ol{U}}^{n}_{i},\vect{\ol{U}}^{n}_{i-1}\right)\right]\right\}+\left(1-\ve\right)\vect{\ol{U}}^{n}_{i}+\Delta t\,\vect{\ol{S}}^{n}_{i},\hspace{1em}\eta_{i}\equiv\f{\Delta t}{\ve\,V_{i}}.
+\end{align*}
+
+We proceed by focusing on each term individually.
+
+\subsubsection{Numerical flux term}
+We start with the term in the curly brackets and again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding:
+\begin{align*}
+    \vect{\ol{U}}^{n}_{i}-\f{\eta_{i}}{2}\Big\{&\sqrtgm_{\iph}\left[\vect{F}\left(\vect{\ol{U}}^{n}_{i+1}\right)+\vect{F}\left(\vect{\ol{U}}^{n}_{i}\right)-\alpha_{\iph}\left(\vect{\ol{U}}^{n}_{i+1}-\vect{\ol{U}}^{n}_{i}\right)\right]\\
+    &-\sqrtgm_{\imh}\left[\vect{F}\left(\vect{\ol{U}}^{n}_{i}\right)+\vect{F}\left(\vect{\ol{U}}^{n}_{i-1}\right)-\alpha_{\imh}\left(\vect{\ol{U}}^{n}_{i}-\vect{\ol{U}}^{n}_{i-1}\right)\right]\Big\}\\
+    &\hspace{-10em}=\left(1-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\vect{\ol{U}}^{n}_{i}\\
+    &\hspace{-8em}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\vect{F}\left(\vect{\ol{U}}^{n}_{i}\right)+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\vect{F}\left(\vect{\ol{U}}^{n}_{i}\right)\\
+    &\hspace{-8em}+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\vect{\ol{U}}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\vect{F}\left(\vect{\ol{U}}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\vect{\ol{U}}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\vect{F}\left(\vect{\ol{U}}^{n}_{i+1}\right)\right].
+\end{align*}
+Now we add and subtract $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\,\vect{\ol{U}}^{n}_{i}$ and $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\,\vect{\ol{U}}^{n}_{i}$, yielding:
+\begin{align*}
+    &\left(1-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\vect{\ol{U}}^{n}_{i}\\
+    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\vect{\ol{U}}^{n}_{i}-\f{1}{\alpha_{\iph}}\vect{F}\left(\vect{\ol{U}}^{n}_{i}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\vect{\ol{U}}^{n}_{i}+\f{1}{\alpha_{\imh}}\vect{F}\left(\vect{\ol{U}}^{n}_{i}\right)\right]\\
+    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\vect{\ol{U}}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\vect{F}\left(\vect{\ol{U}}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\vect{\ol{U}}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\vect{F}\left(\vect{\ol{U}}^{n}_{i+1}\right)\right].
+\end{align*}
+All of the terms in square brackets are similar to the $\vect{H}$ quantities in \citet{Qin2016}, and are therefore in $\mc{G}$.
+It can easily be seen that the sum of the coefficients is unity.
+The final condition is that the coefficient of $\vect{\ol{U}}^{n}_{i}>0$, or (recalling that $\eta=\Delta t/\Delta x$):
+\begin{align*}
+    1-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}&-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}>0\implies\eta_{i}\left(\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}\right)<1\\
+    &\implies\Delta t<\f{\Delta x}{\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}}.
+\end{align*}
+Again we want a time-step that is the same for all elements at a given time, so:
+\begin{equation*}
+    \Delta t<\frac{\Delta x}{2\,\text{max}_{i}\left(\sqrtgm_{\iph}\,\alpha_{\iph}\right)}.
+\end{equation*}
+We see that this differs from the case of Cartesian coordinates by a factor of two, as well as a factor of the metric determinant at the boundaries of the element.
+\sd{Why doesn't this reduce to the Cartesian result when $\sqrtgm_{\iph}=1$?}
+
+Next we handle the source term.
+
+\subsubsection{Source term}
+We have to show that $\left(1-\ve\right)\vect{\ol{U}}^{n}_{i}+\Delta t\,\vect{\ol{S}}^{n}_{i}\in\mc{G}$. Following \citet{ZS2011b}, we write out explicitly the cell-averages:
+\begin{equation*}
+    \left(1-\ve\right)\vect{\ol{U}}^{n}_{i}+\Delta t\,\vect{\ol{S}}^{n}_{i}=\f{1-\ve}{V}\int\left[\vect{U}^{n}_{i}+\f{\Delta t}{1-\ve}\vect{S}^{n}_{i}\right]dV.
+\end{equation*}
+Here we note that for a one-dimensional first-order DG scheme we have:
+\begin{equation*}
+    \int\vect{W}^{n}_{i}\left(x\right)\,dV=\Delta x\,w_{1}\,\vect{W}^{n}\left(\eta_{1}\right)\,\sqrtgm\left(\eta_{1}\right),
+\end{equation*}
+and
+\begin{equation*}
+    \int dV=\Delta x\,w_{1}\,\sqrtgm\left(\eta_{1}\right),
+\end{equation*}
+so,
+\begin{equation*}
+    \f{1}{V}\int\vect{W}^{n}_{i}\left(x\right)\,dV=\vect{W}^{n}\left(\eta_{1}\right).
+\end{equation*}
+So, we have:
+\begin{equation*}
+    \f{1-\ve}{V}\int\left[\vect{U}^{n}_{i}+\f{\Delta t}{1-\ve}\vect{S}^{n}_{i}\right]dV=\left(1-\ve\right)\left[\vect{U}^{n}\left(\eta_{1}\right)+\f{\Delta t}{1-\ve}\vect{S}^{n}\left(\eta_{1}\right)\right].
+\end{equation*}
+So we need to show that if $\vect{U}^{n}_{i}\in\mc{G}$, then (omitting the arguments $\eta_{1}$ and superscripts $n$):
+\begin{equation*}
+    \begin{pmatrix}D\\ S_{1}+\f{\Delta t}{2\left(1-\ve\right)}\left[S_{1}\,v^{1}+p\right]\p_{1}\ln\gamma_{11}\\\tau\end{pmatrix}\in\mc{G}.
+\end{equation*}
+The first condition of $\mc{G}$ is immediately obvious, i.e.
+that $D>0$.
+The second condition reduces to the requirement that the argument of the square root in the second condition of $\mc{G}$ be non-negative:
+\begin{equation*}
+    D^{2}+\left\{S_{1}+\f{\Delta t}{2\left(1-\ve\right)}\left[S_{1}\,v^{1}+p\right]\p_{1}\ln\gamma_{11}\right\}^{2}\geq0.
+\end{equation*}
+We define the (scalar) term in the square brackets as $K$, yielding (noting that for the second quantity in curly brackets we convert all the contravariant indices to covariant indices and vice-versa):
+\begin{equation*}
+    D^{2}+\left\{S_{1}+\f{\Delta t}{2\left(1-\ve\right)}K\,\p_{1}\ln\gamma_{11}\right\}\times\left\{S^{1}+\f{\Delta t}{2\left(1-\ve\right)}K\,\p^{1}\ln\gamma^{11}\right\}\geq0.
+\end{equation*}
+Here we note that:
+\begin{equation*}
+    \p^{1}\ln\gamma^{11}=\gamma^{11}\,\p_{1}\ln\gamma^{11}=\gamma^{11}\,\p_{1}\ln\f{1}{\gamma_{11}}=-\gamma^{11}\,\p_{1}\ln\gamma_{11}.
+\end{equation*}
+Using this, we have:
+\begin{equation*}
+    D^{2}+\left\{S_{1}+\f{\Delta t}{2\left(1-\ve\right)}K\,\p_{1}\ln\gamma_{11}\right\}\times\left\{S^{1}-\f{\Delta t}{2\left(1-\ve\right)}K\,\gamma^{11}\,\p_{1}\ln\gamma_{11}\right\}\geq0,
+\end{equation*}
+which gives:
+\begin{equation*}
+    D^{2}+S_{1}\,S^{1}-\left(\f{K\,\p_{1}\ln\gamma_{11}}{2\left(1-\ve\right)}\right)^{2}\gamma^{11}\,\left(\Delta t\right)^{2}-S_{1}\f{\Delta t}{2\left(1-\ve\right)}K\,\gamma^{11}\,\p_{1}\ln\gamma_{11}+S^{1}\f{\Delta t}{2\left(1-\ve\right)}K\,\p_{1}\ln\gamma_{11}\geq0.
+\end{equation*}
+Since $S^{1}=\gamma^{11}\,S_{1}$, the last two terms cancel, yielding (recalling that $\gamma^{11}=1/\gamma_{11}$):
+\begin{align*}
+    D^{2}&+S_{1}\,S^{1}-\left(\f{K\,\p_{1}\ln\gamma_{11}}{2\left(1-\ve\right)}\right)^{2}\gamma^{11}\left(\Delta t\right)^{2}\geq0\\
+    &\implies D^{2}+S_{1}\,S^{1}\geq\left(\f{K\,\p_{1}\gamma_{11}}{2\left(1-\ve\right)}\right)^{2}\f{1}{\gamma_{11}^{3}}\left(\Delta t\right)^{2}\\
+    &\implies\Delta t\leq\f{2\left(1-\ve\right)\sqrt{D^{2}+S_{1}\,S^{1}}}{\left|\left[S_{1}\,v^{1}+p\right]\p_{1}\gamma_{11}\right|}\gamma_{11}^{3/2}.
+\end{align*}
+
+\newpage
+
 \bibliographystyle{apj}

### 2018-09-12 Documents/M1/realizableFermionicM1/sections/DGIMEXscheme.tex
Edits througout after reading the entire paper.
Edits throughout the paper due to extensive comments from Cory.

@@
 The main result of this section is stated in Theorem~\ref{the:realizableDGIMEX}.  
+The realizability-preserving property of the DG-IMEX scheme is stated in Theorem~\ref{the:realizableDGIMEX2} in Section~\ref{sec:limiter}, after the discussion of the limiter.
 
@@
 \end{equation}
-Then, with $v=1$ in Eq.~\eqref{eq:semidiscreteDG}, and invoking the form of the IMEX scheme in Eq.~\eqref{eq:imexStagesRewrite}, the stage values for the cell average in the IMEX scheme are given by
+With $v=1$ in Eq.~\eqref{eq:semidiscreteDG}, the stage values for the cell average in the IMEX scheme (cf. Eq.~\eqref{eq:imexStagesRewrite}) can be written as
 \begin{align}
@@
 and $\hat{c}_{ij}\ge0$.  
-The cell average of the divergence operator is (cf. Section~\ref{sec:dg})
+The cell average of the divergence operator is
 \begin{equation}
@@
   Let $\vect{\cM}_{\bK}^{(i)}$ satisfy Eq.~\eqref{eq:imexStagesCellAverage}.
-  Assume that $\vect{\cM}_{\bK}^{(ij)}\in\cR\,\forall\,i=1,\ldots,s,\,j\le i-1$.  
+  Assume that $\vect{\cM}_{\bK}^{(ij)}\in\cR~\forall\,i=1,\ldots,s,\,j\le i-1$.  
   Then, $\vect{\cM}_{\bK}^{(i)}\in\cR$, for $i=1,\ldots,s$.  
@@
 \begin{proof}
-  For $i=1,\ldots,s$, the first term on the right-hand side of Eq.~\eqref{eq:imexStagesCellAverage} constitutes a convex combination of elements in $\cR$; i.e.,
+  For $i=1,\ldots,s$, 
   \begin{equation*}
-    \sum_{j=0}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}\in\cR.
+    \sum_{j=0}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}\in\cR,
   \end{equation*}
-  Since $a_{ii}\,\dt/\tau>0$, it follows from Lemma~\ref{lem:implicitStep} that $\vect{\cM}_{\bK}^{(i)}\in\cR$, for $i=1,\ldots,s$.  
+  since it is a convex combination of elements in $\bK$.  
+  The Result follows from Lemma~\ref{lem:implicitStep}.  
 \end{proof}
@@
   \begin{align}
-    &\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{(j)};\hat{c}_{ij}\big](\tilde{\vect{x}}^{k}) \label{eq:realizableGamma} \\
+    &\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{(j)};\hat{c}_{ij}\big] \label{eq:realizableGamma} \\
     &:=\f{1}{|K^{k}|}
-    \Big[\,\int_{K^{k}}\vect{\cM}_{h}^{(j)}\,dx^{k}-\f{\hat{c}_{ij}\,\dt}{\beta_{k}}\big(\,\widehat{\bcF}^{k}(\vect{\cM}_{h}^{(j)})\big|_{\xH^{k}}-\widehat{\bcF}^{k}(\vect{\cM}_{h}^{(j)})\big|_{\xL^{k}}\,\big)\,\Big]\in\cR, \nonumber
+    \Big[\,\int_{K^{k}}\vect{\cM}_{h}^{(j)}\,dx^{k}-\f{\hat{c}_{ij}\,\dt}{\beta_{k}}\big(\,\widehat{\bcF}^{k}(\vect{\cM}_{h}^{(j)})\big|_{\xH^{k}}-\widehat{\bcF}^{k}(\vect{\cM}_{h}^{(j)})\big|_{\xL^{k}}\,\big)\,\Big] \nonumber
   \end{align}
-  then $\vect{\cM}_{\bK}^{(ij)}\in\cR$.  
+  is realizable, then $\vect{\cM}_{\bK}^{(ij)}\in\cR$.  
   \label{lem:realizableMij}
@@
 \begin{rem}
-  If a quadrature rule $\tilde{\vect{Q}}^{k}\colon C^{0}(\tilde{\bK}^{k})\to\bbR$, with positive weights, and points defined by the set $\tilde{\vect{S}}^{k}$, is used to approximate the integral over $\tilde{\bK}^{k}$ in Eq.~\eqref{eq:cellAverageInTermsOfGamma}, it is sufficient for Eq.~\eqref{eq:realizableGamma} to hold in the quadrature points $\tilde{\vect{S}}^{k}\subset\tilde{\bK}^{k}$.
+  If a quadrature rule $\tilde{\vect{Q}}^{k}\colon C^{0}(\tilde{\bK}^{k})\to\bbR$, with positive weights, and points defined by the set $\tilde{\vect{S}}^{k}$, is used to approximate the integral over $\tilde{\bK}^{k}$ in Eq.~\eqref{eq:cellAverageInTermsOfGamma}, then it is sufficient for Eq.~\eqref{eq:realizableGamma} to hold in the quadrature points $\tilde{\vect{S}}^{k}\subset\tilde{\bK}^{k}$.
 \end{rem}
@@
 Next, we establish conditions for which Eq.~\eqref{eq:realizableGamma} holds.  
-To this end, let $\hat{Q}^{k}\colon C^{0}(K^{k})\to\bbR$ denote the $N$-point \emph{Gauss-Lobatto (GL)} quadrature rule on the interval $K^{k}=(x_{\Low}^{k},x_{\Hgh}^{k})$, with points
+To this end, let $\hat{Q}^{k}\colon C^{0}(K^{k})\to\bbR$ denote the $N$-point \emph{Gauss-Lobatto (GL)} quadrature rule on the interval $K^{k}=(\xL^{k},\xH^{k})$, with points
 \begin{equation}
@@
 This quadrature integrates polynomials in $x^{k} \in \bbR$ with degree $\le2N-3$ exactly.  
-Then, if $\vect{\cM}_{h}^{(j)}$ is represented by such polynomials we have
+If $\vect{\cM}_{h}^{(j)}$ is represented by such polynomials, then
 \begin{equation}
   \int_{K^{k}} \bcM_{h}^{(j)}(x^{k})\,dx^{k} = \hat{Q}^{k}[\bcM_{h}^{(j)}] \equiv
-  |K^{k}| \sum_{q=1}^{N} \hat{w}_{q}\,\bcM_{h}^{(j)}(\hat{x}_{q}^{k})
+  |K^{k}| \sum_{q=1}^{N} \hat{w}_{q}\,\bcM_{h}^{(j)}(\hat{x}_{q}^{k}),
   \label{eq:quadratureRuleGL}
 \end{equation}
-where, for simplicity of notation, we have suppressed the explicit dependence on $\tilde{\vect{x}}^{k}$ to denote $\bcM_{h}^{(j)}(\hat{x}_q^{k},\tilde{\vect{x}}^{k}) = \bcM_{h}^{(j)}(\hat{x}_{q}^{k})$.
-In each element, we also denote $\vect{\cM}_{h}^{(j)}(\hat{x}_{1}^{k})=\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})$ and $\vect{\cM}_{h}^{(j)}(\hat{x}_{N}^{k})=\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})$.  
-Similarly, the solution on $\tilde{\vect{\bK}}^{k}$ to the immediate left of $x_{\Low}^{k}$ is denoted $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})$, and the solution on $\tilde{\vect{\bK}}^{k}$ to the immediate right of $x_{\Hgh}^{k}$ is denoted $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})$.
+where for simplicity of notation, we have suppressed the explicit dependence on $\tilde{\vect{x}}^{k}$ to denote $\bcM_{h}^{(j)}(\hat{x}_q^{k},\tilde{\vect{x}}^{k}) = \bcM_{h}^{(j)}(\hat{x}_{q}^{k})$.
+In each element, we also denote $\vect{\cM}_{h}^{(j)}(\hat{x}_{1}^{k})=\vect{\cM}_{h}^{(j)}(\xL^{k,+})$ and $\vect{\cM}_{h}^{(j)}(\hat{x}_{N}^{k})=\vect{\cM}_{h}^{(j)}(\xH^{k,-})$.  
+Similarly, the solution on $\tilde{\vect{\bK}}^{k}$ to the immediate left of $\xL^{k}$ is denoted $\vect{\cM}_{h}^{(j)}(\xL^{k,-})$, and the solution on $\tilde{\vect{\bK}}^{k}$ to the immediate right of $\xH^{k}$ is denoted $\vect{\cM}_{h}^{(j)}(\xH^{k,+})$.
 
-We can write $\vect{\Gamma}^{k}$ as the convex combination
+Using Eq.~\eqref{eq:quadratureRuleGL}, $\vect{\Gamma}^{k}$ can be expressed as the convex combination
 \begin{align}
@@
   &\hspace{-12pt}
-  +\hat{w}_{1}\,\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\lambda_{ij}^{k}\,\mathscr{F}^{k}\big(\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big)\,\big] \nonumber \\
+  +\hat{w}_{1}\,\big[\,\vect{\cM}_{h}^{(j)}(\xL^{k,+})+\lambda_{ij}^{k}\,\mathscr{F}^{k}\big(\vect{\cM}_{h}^{(j)}(\xL^{k,-}),\vect{\cM}_{h}^{(j)}(\xL^{k,+})\big)\,\big] \nonumber \\
   &\hspace{-12pt}
-  +\hat{w}_{N}\,\big[\,\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})-\lambda_{ij}^{k}\,\mathscr{F}^{k}\big(\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big)\,\big],
+  +\hat{w}_{N}\,\big[\,\vect{\cM}_{h}^{(j)}(\xH^{k,-})-\lambda_{ij}^{k}\,\mathscr{F}^{k}\big(\vect{\cM}_{h}^{(j)}(\xH^{k,-}),\vect{\cM}_{h}^{(j)}(\xH^{k,+})\big)\,\big],
   \label{eq:realizableGammaConvex}
@@
   \begin{align*}
-    &\Phi\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+});\hat{c}_{ij}\,\big] \\
-    &=\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\lambda_{ij}^{k}\,\mathscr{F}\big(\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big)\,\big] \\
-    &\hspace{12pt}
-    +\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})-\lambda_{ij}^{k}\,\mathscr{F}\big(\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-}),\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big)\,\big]
+    &\Phi\big[\,\vect{\cM}_{h}^{(j)}(\xL^{k,-}),\vect{\cM}_{h}^{(j)}(\xL^{k,+}),\vect{\cM}_{h}^{(j)}(\xH^{k,-}),\vect{\cM}_{h}^{(j)}(\xH^{k,+});\hat{c}_{ij}\,\big] \\
+    &\hspace{6pt}
+    :=\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(\xL^{k,+})+\lambda_{ij}^{k}\,\mathscr{F}^{k}\big(\vect{\cM}_{h}^{(j)}(\xL^{k,-}),\vect{\cM}_{h}^{(j)}(\xL^{k,+})\big)\,\big] \\
+    &\hspace{18pt}
+    +\f{1}{2}\big[\,\vect{\cM}_{h}^{(j)}(\xH^{k,-})-\lambda_{ij}^{k}\,\mathscr{F}^{k}\big(\vect{\cM}_{h}^{(j)}(\xH^{k,-}),\vect{\cM}_{h}^{(j)}(\xH^{k,+})\big)\,\big]
   \end{align*}
@@
   \begin{align*}
-    \Phi_{0} &= \f{1}{2}\,\big(\,\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})+\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})\,\big), \\
-    \Phi_{1} &= \Phi^{+}\big[\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})\big], \\
-    \Phi_{2} &= \Phi^{+}\big[\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\big],
+    \Phi_{0} &= \f{1}{2}\,\big(\,\vect{\cM}_{h}^{(j)}(\xL^{k,+})+\vect{\cM}_{h}^{(j)}(\xH^{k,-})\,\big), \\
+    \Phi_{1} &= \Phi^{+}\big[\vect{\cM}_{h}^{(j)}(\xL^{k,-})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(\xH^{k,-})\big], \\
+    \Phi_{2} &= \Phi^{+}\big[\vect{\cM}_{h}^{(j)}(\xL^{k,+})\big]+\Phi^{-}\big[\vect{\cM}_{h}^{(j)}(\xH^{k,+})\big],
   \end{align*}
-  and $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\,\big(\vect{\cM}\pm\vect{e}_{k}\cdot\vect{\cF}^{k}(\vect{\cM})\big)$.  
-  Since $\lambda_{ij}^{k}\le1$, $\Phi$ is expressed as a convex combination of three terms; $\Phi_{0}$, $\Phi_{1}$, and $\Phi_{2}$.  
-  By assumption, $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,-})$, $\vect{\cM}_{h}^{(j)}(x_{\Low}^{k,+})$, $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,-})$, $\vect{\cM}_{h}^{(j)}(x_{\Hgh}^{k,+})\in\cR$, which immediately implies realizability of $\Phi_{0}$.
+  and $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\,\big(\vect{\cM}\pm\vect{e}_{k}\cdot\vect{\cF}^{k}(\vect{\cM})\big)$; cf. Lemma~\ref{lem:explicitStep}.  
+  Since $\lambda_{ij}^{k}\le1$, $\Phi$ is expressed as a convex combination of $\Phi_{0}$, $\Phi_{1}$, and $\Phi_{2}$.  
+  By assumption, $\vect{\cM}_{h}^{(j)}(\xL^{k,-})$, $\vect{\cM}_{h}^{(j)}(\xL^{k,+})$, $\vect{\cM}_{h}^{(j)}(\xH^{k,-})$, $\vect{\cM}_{h}^{(j)}(\xH^{k,+})\in\cR$, which immediately implies realizability of $\Phi_{0}$.
   Realizability of $\Phi_{1}$ and $\Phi_{2}$ follows by invoking Lemma~\ref{lem:explicitStep}.  
@@
   \begin{equation}
-    \dt = c_{\mbox{\tiny Sch}}\,\min_{k} \Big(\, \beta_{k}\,\hat{w}_{N}\,|K^{k}| \,\Big),
+    \dt \le c_{\Sch}\,\min_{k} \Big(\, \beta_{k}\,\hat{w}_{N}\,|K^{k}| \,\Big),
     \label{eq:imexTimeStep}
   \end{equation}
-  where $c_{\mbox{\tiny Sch}}$ is defined in \eqref{eq:imexCFL}.  
+  where $c_{\Sch}$ is defined in \eqref{eq:imexCFL}.  
 \end{rem}
@@
 \begin{lemma}
-  Suppose that $\tilde{\vect{\cM}}_{\bK}^{n+1}\in\cR$ and $\vect{\cM}_{\bK}^{n+1}$ is obtained by solving Eq.~\eqref{eq:imexCorrectionCellAverage} with $\hat{\alpha}:=\alpha\,\dt^{2}/\tau^{2}\ge0$.  
+  Suppose that $\tilde{\vect{\cM}}_{\bK}^{n+1}\in\cR$ and $\vect{\cM}_{\bK}^{n+1}$ is obtained by solving Eq.~\eqref{eq:imexCorrectionCellAverage}.  
   Then $\vect{\cM}_{\bK}^{n+1}\in\cR$.  
@@
 \begin{proof}
-  With the collision term in Eq.~\eqref{eq:collisionTermMoments}, Eq.~\eqref{eq:imexCorrectionCellAverage} can be rewritten in the form
-  \begin{equation*}
-    \vect{\cM}_{\bK}^{n+1}=\tilde{\vect{\cM}}_{\bK}^{n+1}+\hat{\alpha}\,\vect{\cD}\,\vect{\cC}(\vect{\cM}_{\bK}^{n+1}).  
-  \end{equation*}
-  The proof is completed by invoking Lemma~\ref{lem:correctionStep}.  
+  The result follows immediately from Lemma~\ref{lem:correctionStep}.  
 \end{proof}
@@
 \begin{theorem}
+  Consider the stages of the IMEX scheme in Eq.~\eqref{imexStages} applied to the DG discretization of the two-moment model in Eq.~\eqref{eq:semidiscreteDG}.  
   Suppose that
@@
     \item[1.] For all $k\in\{1,\ldots,d\}$, the Gauss-Lobatto quadrature rule $\hat{Q}^{k}$ is chosen such that Eq.~\eqref{eq:quadratureRuleGL} holds.  
-    \item[2.] For all $k\in\{1,\ldots,d\}$ and all $\vect{x}\in\hat{\vect{S}}^{k}$, $\vect{\cM}_{h}^{n}(\vect{x})\in\cR$.
+    \item[2.] For all $k\in\{1,\ldots,d\}$, $\vect{x}\in\hat{\vect{S}}^{k}$, and $0\le j \le i-1<s$, 
+    \begin{equation*}
+      \vect{\cM}_{h}^{(j)}(\vect{x})\in\cR.
+    \end{equation*}
     \item[3.] The time step $\dt$ is chosen such that Eq.~\eqref{eq:imexTimeStep} holds.  
-    \item[4.] If $\vect{\cM}_{\bK}^{(i)}\in\cR$, a limiter can be invoked to enforce $\vect{\cM}_{h}^{(i)}(\vect{x})\in\cR$ for all $\vect{x}\in\hat{\vect{S}}^{k}$ and all $k\in\{1,\ldots,d\}$.
   \end{itemize}
-  Then $\vect{\cM}_{\bK}^{n+1}\in\cR$.  
+  Then $\vect{\cM}_{\bK}^{(i)}\in\cR$.  
   \label{the:realizableDGIMEX}
@@
 \begin{proof}
-  The cell average $\vect{\cM}_{\bK}^{(1)}$ is obtained by solving (cf. Eq.~\eqref{eq:imexStagesCellAverage} with $i=1$)
+  The cell average $\vect{\cM}_{\bK}^{(i)}$ is obtained by solving (cf. Eq.~\eqref{eq:imexStagesCellAverage})
   \begin{equation*}
-    \vect{\cM}_{\bK}^{(1)}=c_{10}\,\vect{\cM}_{\bK}^{(10)}+a_{11}\,\f{\dt}{\tau}\big(\,\vect{\eta}-\vect{\cD}\,\vect{\cM}_{\bK}^{(1)}\,\big),
+    \vect{\cM}_{\bK}^{(i)}
+    =\sum_{j=0}^{i-1}c_{ij}\,\vect{\cM}_{\bK}^{(ij)}
+    +a_{ii}\,\f{\dt}{\tau}\big(\,\vect{\eta}-\vect{\cD}\,\vect{\cM}_{\bK}^{(i)}\,\big),
   \end{equation*}
@@
   \begin{equation*}
-    \vect{\cM}_{\bK}^{(10)}
-    =\sum_{k=1}^{d}\f{\beta_{k}}{|\tilde{\bK}^{k}|}\tilde{\vect{Q}}^{k}\big(\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{n};\hat{c}_{10}\big]\big).  
+    \vect{\cM}_{\bK}^{(ij)}
+    =\sum_{k=1}^{d}\f{\beta_{k}}{|\tilde{\bK}^{k}|}\tilde{\vect{Q}}^{k}\big(\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{(j)};\hat{c}_{ij}\big]\big).  
   \end{equation*}
-  Since $\vect{\cM}_{h}^{n}\in\cR$ on $\hat{\vect{S}}^{k}$, for each $k\in\{1,\ldots,d\}$, it follows from Lemma~\ref{lem:realizableGamma} that $\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{n};\hat{c}_{10}\big]\in\cR$ on $\tilde{\vect{S}}^{k}$.
-  Then, realizability of $\vect{\cM}_{\bK}^{(10)}$ follows from Lemma~\ref{lem:realizableMij}, after which $\vect{\cM}_{\bK}^{(1)}\in\cR$ follows by invoking Lemma~\ref{lem:imexStagesCellAverage}.  
-  By invoking a realizability-enforcing limiter, $\vect{\cM}_{h}^{(1)}(\vect{x})\in\cR$ for all $\vect{x}\in\hat{\vect{S}}^{k}$ and all $k\in\{1,\ldots,d\}$.  
-  Repeated application of these steps give $\vect{\cM}_{\bK}^{(s)}\in\cR$.  
-  Since the IMEX scheme is GSA, it follows that $\tilde{\vect{\cM}}_{\bK}^{n+1}\in\cR$.  
-  The proof is completed by invoking Lemma~\ref{lem:imexCorrectionCellAverage}.  
+  Since $\vect{\cM}_{h}^{(j)}\in\cR$ on $\hat{\vect{S}}^{k}$, for each $k\in\{1,\ldots,d\}$ and $j\in\{0,\ldots,i-1\}$, it follows from Lemma~\ref{lem:realizableGamma} that $\vect{\Gamma}^{k}\big[\vect{\cM}_{h}^{(j)};\hat{c}_{ij}\big]\in\cR$ on $\tilde{\vect{S}}^{k}$.
+  Then, realizability of $\vect{\cM}_{\bK}^{(ij)}$ follows from Lemma~\ref{lem:realizableMij}, after which $\vect{\cM}_{\bK}^{(i)}\in\cR$ follows by invoking Lemma~\ref{lem:imexStagesCellAverage}.  
 \end{proof}

### 2018-09-12 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
More edits
Edits throughout the paper due to extensive comments from Cory.

@@
 Algebraic moment closures for the two-moment model are computationally efficient as they provide the Eddington factor in Eq.~\eqref{eq:eddingtonTensor} in closed form as a function of the density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$.
-For this reason they are used in applications where transport plays an important role, but where limited computational resources precludes the use of higher fidelity models --- including simulation of neutrino transport in core-collapse supernovae \cite{roberts_etal_2016} and compact binary mergers \cite{foucart_etal_2015}.
+For this reason they are used in applications where transport plays an important role, but where limited computational resources preclude the use of higher fidelity models.  
+Examples include simulation of neutrino transport in core-collapse supernovae \cite{roberts_etal_2016} and compact binary mergers \cite{foucart_etal_2015}.  
 Algebraic moment closures in the context of these aforementioned applications have also been discussed elsewhere (e.g., \cite{janka_etal_1992,pons_etal_2000,smit_etal_2000,just_etal_2015,murchikova_etal_2017}).
 Here we focus on properties of the algebraic closures that are critical to the development of numerical methods for the two-moment model of fermion transport.  
-The family of algebraic closures we consider can be written in the form \cite{cernohorskyBludman_1994}
+For the algebraic closures we consider, the Eddington factor in Eq.~\eqref{eq:eddingtonTensor} can be written in the following form \cite{cernohorskyBludman_1994}
 \begin{equation}
@@
 \end{equation}
-This is also a form of algebraic moment closure suitable for particle systems obeying Maxwell-Boltzmann statistics.
+This for of $\chi$ yields a moment closure that is suitable for particle systems obeying Maxwell-Boltzmann statistics.
 
@@
 
-For the two-moment model, the ME closure attempts to construct the angular distribution based on the limited information available (i.e., $\cJ$ and $\vect{\cH}$) \cite{cernohorskyBludman_1994,lareckiBanach_2011}.
-The ME distribution $f_{\mbox{\tiny ME}}(\omega)$ is found by maximizing the entropy functional, which for particles obeying Fermi-Dirac statistics is given by
+The ME closure constructs an approximation of the angular distribution as a function of $\cJ$ and $\vect{\cH}$ \cite{cernohorskyBludman_1994,lareckiBanach_2011}.  
+The ME distribution $f_{\mbox{\tiny ME}}$ is found by maximizing the entropy functional, which for particles obeying Fermi-Dirac statistics is given by
 \begin{equation}
@@
 \end{equation}
-From the variation of the entropy functional in Eq.~\eqref{eq:entropyFunctional} with respect to $f_{\mbox{\tiny ME}}$ and introducing Lagrange multipliers ($a$ and $\vect{b}$) to enforce the constraints in Eq.~\eqref{eq:closureConstraints}, the ME distribution takes the general form \cite{cernohorskyBludman_1994}
+The solution that maximizes Eq.~\eqref{eq:entropyFunctional} takes the general form \cite{cernohorskyBludman_1994}
 \begin{equation}
-  f_{\mbox{\tiny ME}}(\omega;a,\vect{b})=\f{1}{e^{a + \vect{b}\cdot\vect{\ell}(\omega)}+1}.  
+  f_{\mbox{\tiny ME}}(\omega;a,\vect{b})=\f{1}{e^{a + \vect{b}\cdot\vect{\ell}(\omega)}+1}, 
   \label{eq:fME}
 \end{equation}
-The Lagrange multipliers are implicit functions of $\cJ$ and $\vect{\cH}$.  
+where the Lagrange multipliers $a$ and $\vect{b}$ are implicit functions of $\cJ$ and $\vect{\cH}$.  
 The ME distribution function satisfies $0 < f_{\mbox{\tiny ME}} < 1$, but $a$ and $\vect{b}$ are unconstrained.  
@@
 \end{equation} 
-the closure function $\Theta(x)$ is independent of $\cJ$ and can be written explicitly in terms of the inverse Langevin function.  
-To avoid inverting the Langevin function for $\Theta(x)$, they provide a polynomial fit (accurate to $2\%$) given by
+the closure function $\Theta$ is independent of $\cJ$ and can be written explicitly in terms of the inverse Langevin function.  
+To avoid inverting the Langevin function for $\Theta$, they provide a polynomial fit (accurate to $2\%$) given by
 \begin{equation}
@@
 \end{equation}
-More recently, Larecki \& Banach \cite{lareckiBanach_2011} have shown that the explicit expression given in \cite{cernohorskyBludman_1994} is not exact, and provide another approximate expression
+More recently, Larecki \& Banach \cite{lareckiBanach_2011} have shown that the explicit expression given in \cite{cernohorskyBludman_1994} is not exact and provide another approximate expression
 \begin{equation}
@@
 \end{equation}
-with $\beta\in[0,1]$, is realizable for realizable moments $(\cJ,\cH)^{T}\in\cR$.  
+with $\beta\in[0,1]$, is realizable whenever $(\cJ,\cH)^{T}\in\cR$.  
 The Kershaw closure for the two-moment model is then obtained from Eq.~\eqref{eq:kershawAnsatz} with the additional requirement that it be correct in the limit of isotropic distribution functions; i.e., $\cK(\beta,\cJ,0)=\cJ/3$.
@@
 In Figure~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor $\chi$ versus the flux factor $h$ for the various algebraic closures discussed above and for different values of $\cJ\in(0,1)$: $0.01$ (upper left panel), $0.4$ (upper right panel), $0.6$ (lower left panel), and $0.99$ (lower right panel).
-The maximum entropy closures of CB and BL are plotted with solid red and dashed orange lines respectively.  
-The Kershaw closure is plotted with solid blue lines, while the Minerbo closure is plotted with dash-dot purple lines.  
-The lower and upper bounds on the Eddington factor for realizable closures for fermion particle systems ($\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$, respectively) are plotted with solid black lines.
+The lower and upper bounds on the Eddington factor for realizable closures ($\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$, respectively) are also plotted.  
 We note that for all the closures, the Eddington factor $\chi\to1/3$ as $h\to0^{+}$.
 
-For $\cJ=0.01$, the maximum entropy closures (CB, BL, and Minerbo) are practically indistinguishable, while the Eddington factor of the Kershaw closure is larger than that of the other closures over most of the domain.
-For $\cJ=0.4$, the Eddington factor for the closures based on Fermi-Dirac statistics (CB, BL, and Kershaw) remain close together, while the Eddington factor for the Minerbo closure is larger than the other closures for $h\gtrsim0.2$.
-The Eddington factor for all closures remain between $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ for $\cJ=0.01$ and $\cJ=0.4$.
+When $\cJ=0.01$, the maximum entropy closures (CB, BL, and Minerbo) are practically indistinguishable, while the Eddington factor of the Kershaw closure is larger than that of the other closures over most of the domain.
+When $\cJ=0.4$, the Eddington factor for the closures based on Fermi-Dirac statistics (CB, BL, and Kershaw) remain close together, while the Eddington factor for the Minerbo closure is larger than the other closures for $h\gtrsim0.2$.
+The Eddington factor for all closures remain between $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ when $\cJ=0.01$ and $\cJ=0.4$.
 
-For $\cJ=0.6$, the Eddington factor for the closures based on Fermi-Dirac statistics remain close together and within the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.  
+When $\cJ=0.6$, the Eddington factor for the closures based on Fermi-Dirac statistics remain close together and within the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.  
 The dependence of the Eddington factor on $h$ for the Minerbo closure differs from the other closures (i.e., increases vs decreases with increasing $h$), and exceeds $\chi_{\mbox{\tiny max}}$ for $h\gtrsim0.34$.
-For $\cJ=0.99$, the Eddington factor of the CB and BL closures (indistinguishable) and the Kershaw closure remain within the bounds given in Eq.~\eqref{eq:eddingtonFactorBounds}.  
+When $\cJ=0.99$, the Eddington factor of the CB and BL closures (indistinguishable) and the Kershaw closure remain within the bounds given in Eq.~\eqref{eq:eddingtonFactorBounds}.  
 The Eddington factor of the Minerbo closure is nearly flat, and exceeds $\chi_{\mbox{\tiny max}}$ for $h\gtrsim0.006$.
 
-\begin{figure}[h]
+\begin{figure}[H]
   \centering
@@
 In each panel we plot the Eddington factors of Kershaw (solid blue lines), Cernohorsky \& Bludman (CB, solid red lines), Banach \& Larecki (BL, dashed orange lines), and Minerbo (dash-dot purple lines).
-We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ (lower and upper solid black lines, respectively).}
+We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper solid black lines, respectively).}
   \label{fig:EddingtonFactorsWithDifferentClosure}
@@
 
-In Figure~\ref{fig:MabWithDifferentClosure}, we further illustrate the properties of the algebraic closures by plotting $\vect{\cM}_{ab}$ as defined in Lemma~\ref{lem:explicitStep}.  
-In each of the four panels, representing the algebraic closures discussed above, we plot $\vect{\cM}_{ab}$ constructed from randomly selected pairs $\vect{\cM}_{a},\vect{\cM}_{b}\in\cR$ (each blue dot represents one realization of $\vect{\cM}_{ab}$).
-Results for the maximum entropy closures of BL and CB are plotted in the upper panels (left and right panel, respectively).  
-Results for the Kershaw closure are plotted in the lower left panel, while results for the Minerbo closure are plotted in the lower right panel.  
-As expected for closures consistent with moments of a Fermi-Dirac distribution function, we find $\vect{\cM}_{ab}\in\cR$ for the CB, BL, and Kershaw closures.  
-For the Minerbo closure (right bottom), which is consistent with positive distributions, $\vect{\cM}_{ab}$ is not confined to $\cR$.  
-\begin{figure}[h]
+In Figure~\ref{fig:MabWithDifferentClosure}, we further illustrate properties of the algebraic closures by plotting $\vect{\cM}_{ab}$ as defined in Lemma~\ref{lem:explicitStep} for the maximum entropy closures of CB and Minerbo.
+In both panels, we plot $\vect{\cM}_{ab}$ constructed from randomly selected pairs $\vect{\cM}_{a},\vect{\cM}_{b}\in\cR$ (each blue dot represents one realization of $\vect{\cM}_{ab}$).  
+Results for the maximum entropy closure of CB are plotted in the left panel, while results for the Minerbo closure are plotted in the right panel.  
+As expected for the closure consistent with moments of Fermi-Dirac distributions (CB), we find $\vect{\cM}_{ab}\in\cR$.  
+For the Minerbo closure, which is consistent with positive distributions, $\vect{\cM}_{ab}$ is not confined to $\cR$.  
+\begin{figure}[H]
   \centering
   \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{figures/MabWithBLME}
-    \includegraphics[width=0.5\textwidth]{figures/MabWithCBME} \\
-    \includegraphics[width=0.5\textwidth]{figures/MabWithBLKS}
+%    \includegraphics[width=0.5\textwidth]{figures/MabWithBLME}
+    \includegraphics[width=0.5\textwidth]{figures/MabWithCBME}
+%    \includegraphics[width=0.5\textwidth]{figures/MabWithBLKS}
     \includegraphics[width=0.5\textwidth]{figures/MabWithMI}
   \end{tabular}
-   \caption{Illustration of $\vect{\cM}_{ab}$, as defined in Lemma~\ref{lem:explicitStep}, computed with different algebraic closures: the maximum entropy closures of Banach \& Larecki (top left) and Cernohorsky \& Bludman (top right), the Kershaw closure (bottom left), and the maximum entropy closure of Minerbo (bottom right).
+   \caption{Illustration of $\vect{\cM}_{ab}$, as defined in Lemma~\ref{lem:explicitStep}, computed with algebraic maximum entropy closures of Cernohorsky \& Bludman (left) and Minerbo (right).
 In each panel, $\vect{\cM}_{ab}$ was computed using the respective closure, using $10^{6}$ random pairs ($\vect{\cM}_{a},\vect{\cM}_{b}\in\cR$), and plotted as a light-blue point.

### 2018-09-12 Documents/M1/realizableFermionicM1/sections/appendix.tex
Edits throughout the paper due to extensive comments from Cory.

@@
     \alpha & \vect{w}^{T}
-  \end{array},
+  \end{array}.  
+  \label{eq:butcher}
 \end{equation}
-where the \emph{explicit tableau} (left; components adorned with a tilde) represent the explicit part of the IMEX scheme, and the \emph{implicit tableau} (right; unadorned components) represent the implicit part of the IMEX scheme.
+The \emph{explicit tableau} (left; components adorned with a tilde) represents the explicit part of the IMEX scheme, and the \emph{implicit tableau} (right; unadorned components) represents the implicit part of the IMEX scheme.
 For $s$ stages, $\tilde{A}=(\tilde{a}_{ij})$, $\tilde{a}_{ij}=0$ for $j\ge i$, and $A=(a_{ij})$, $a_{ij}=0$ for $j>i$, are $s\times s$ matrices, and $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$.
@@
 
-For the analysis of constraint-preserving IMEX schemes, additional coefficients are defined \cite{hu_etal_2018} (cf. Eq.~\eqref{eq:imexStagesRewrite}).  
+For the analysis of convex-invariant IMEX schemes, additional coefficients are defined \cite{hu_etal_2018} (cf. Eq.~\eqref{eq:imexStagesRewrite}).  
 First, let
@@
     \tilde{c}_{i0} &= 0, \quad &
-    \tilde{c}_{ij} &= \tilde{a}_{ij} + \sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}.
+    \tilde{c}_{ij} &= \tilde{a}_{ij} + \sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj};
   \end{aligned}
@@
 \end{equation}
-while for IMEX schemes of Type~ARS \cite{ascher_etal_1997}
+for IMEX schemes of Type~ARS \cite{ascher_etal_1997},
 \begin{equation}
@@
 \end{equation}
-(Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.)
+Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.  
+Also note the difference between the matrix coefficients in Eqs.~\eqref{eq:positivityCoefficientsA} and \eqref{eq:positivityCoefficientsARS} and the vector components defined below Eq.~\eqref{eq:butcher}.
 
@@
 
-A second-order accurate, constraint-preserving IMEX scheme of type $A$ (the matrix $A$ is invertible) was given in \cite{hu_etal_2018}.  
+A second-order accurate, convex-invariant IMEX scheme of type $A$ (the matrix $A$ is invertible) with four implicit solves was given in \cite{hu_etal_2018}.  
 We refer to this scheme as IMEX PA2.  
@@
 \end{align*}
-The coefficient in the correction step is $\alpha = 0.2797373792$ and the CFL constant is $c_{\mbox{\tiny Sch}} = 0.5247457524$.
+The coefficient in the correction step is $\alpha = 0.2797373792$ and the CFL constant is $c_{\Sch} = 0.5247457524$.
 This scheme is globally stiffly accurate (GSA), so that $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.
@@
 
-We have found another second-order accurate, constraint-preserving IMEX scheme of type $A$, which we refer to as IMEX PA2+.  
-This scheme allows for a larger value of $c_{\mbox{\tiny Sch}}$ than IMEX PA2 (i.e., a larger time step while maintaining admissible solutions).  
-The scheme was found by random sampling of the parameter space spanned by the IMEX coefficients, optimizing $c_{\mbox{\tiny Sch}}$.  
-For IMEX PA2+, $c_{\mbox{\tiny Sch}} = 0.895041066934$. 
+We have found another second-order accurate, convex-invariant IMEX scheme of type $A$ with four implicit solves, which we refer to as IMEX PA2+.  
+This scheme allows for a larger value of $c_{\Sch}$ than IMEX PA2 (i.e., a larger time step while maintaining admissible solutions).  
+The scheme was found by random sampling of the parameter space spanned by the IMEX coefficients and selecting the scheme with the largest $c_{\Sch}$.  
+For IMEX PA2+, $c_{\Sch} = 0.895041066934$. 
 The non-zero components of $\tilde{A}$ and $A$ are given by
@@
 
-Another IMEX scheme was given in \cite{mcclarren_etal_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclarren_etal_2008}).  
-This scheme can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
+Another IMEX scheme was given in \cite{mcclarren_etal_2008} (referred to there as a semi-implicit predictor-corrector method).  
+This scheme has two implicit solves and can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
 The non-zero components of $\tilde{A}$ and $A$ are given by
@@
 $\alpha=0$, and $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.  
+IMEX PC2 is not convex-invariant, since $c_{\Sch} = 0$ (cf. discussion in Section~\ref{sec:imex}).
 
@@
 
-We have found a family of constraint-preserving, diffusion accurate IMEX schemes of type ARS that are second-order accurate in the streaming limit, which we refer to as IMEX PD-ARS; see \ref{app:PD-ARS}.
-For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.
-Here we give an example by setting $\epsilon=0.1$.
+We have found a family of convex-invariant, diffusion accurate IMEX schemes of type ARS that are second-order accurate in the streaming limit, which we refer to as IMEX PD-ARS; see \ref{app:PD-ARS}.  
+For these schemes, $c_{\Sch}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.
+Here we give an example by setting $\epsilon=0.1$:
 \begin{align*}
@@
 
-We compare the performance of the constraint-preserving IMEX schemes with two other (not constraint-preserving) IMEX schemes.  
-The first one is the second-order accurate IMEX scheme given in \cite{cavaglieriBewley2015}.  
+We compare the performance of the convex-invariant IMEX schemes with two other (not convex-invariant) IMEX schemes.  
+The first one is the second-order accurate IMEX scheme given in \cite{cavaglieriBewley2015} with two implicit solves.  
 We refer to this scheme as IMEX RKCB2.  
@@
 
-Another scheme we use for comparison is the second-order accurate IMEX scheme given in \cite{pareschiRusso_2005}.  
+Another scheme that we use for comparison is the second-order accurate IMEX scheme given in \cite{pareschiRusso_2005} with three implicit solves.  
 We refer to this scheme as IMEX SSP2332.  
@@
 (All elements of the implicit Butcher tableau are zero.)  
-The optimal second-order accurate, strong-stability-preserving Runge-Kutta scheme (SSPRK2) has the following non-zero components
+The optimal second-order accurate, strong-stability-preserving Runge-Kutta scheme (SSPRK2) has the following non-zero components:
 \begin{align}
@@
 \end{align}
-The optimal third-order accurate, strong-stability-preserving Runge-Kutta scheme (SSPRK3) has the following non-zero components
+The optimal third-order accurate, strong-stability-preserving Runge-Kutta scheme (SSPRK3) has the following non-zero components:
 \begin{align}
@@
 \begin{equation}
-  c_{\mbox{\tiny Sch}} = \min \Big\{\, \dfrac{c_{20}}{\tilde{c}_{20}},\, \dfrac{c_{30}}{\tilde{c}_{30}},\, \dfrac{c_{32}}{\tilde{c}_{32}} \,\Big\}.  
+  c_{\Sch} = \min \Big\{\, \dfrac{c_{20}}{\tilde{c}_{20}},\, \dfrac{c_{30}}{\tilde{c}_{30}},\, \dfrac{c_{32}}{\tilde{c}_{32}} \,\Big\}.  
 \end{equation}
-Imposing the equality constraints (i.e., Eqs.~\eqref{eq:implicitConsistency}, \eqref{eq:orderConditionsEx}, and \eqref{eq:diffusionCondition}), the double Butcher tableau can be written in terms of two independent parameters ($x,y\in\bbR$) as
+By imposing the equality constraints (i.e., Eqs.~\eqref{eq:diffusionCondition}, \eqref{eq:orderConditionsEx}, and \eqref{eq:implicitConsistency}), the double Butcher tableau can be written in terms of two independent parameters ($x,y\in\bbR$) as
 \begin{equation}
@@
 \begin{equation}
-  c_{\mbox{\tiny Sch}} = \min \Big\{\, 2x,\, \f{1-2x(1-y)}{y-x},\, 2(1-y) \,\Big\}.  
+  c_{\Sch} = \min \Big\{\, 2x,\, \f{1-2x(1-y)}{y-x},\, 2(1-y) \,\Big\}.  
 \end{equation}
-The constraint-preserving property requires imposing the inequality constraints $a_{22},a_{33}>0$, $c_{20},c_{30},c_{32}\ge0$, and $\tilde{c}_{20},\tilde{c}_{30},\tilde{c}_{32}\ge0$, which imply that
+The convex-invariant property requires imposing the inequality constraints $a_{22},a_{33}>0$, $c_{20},c_{30},c_{32}\ge0$, and $\tilde{c}_{20},\tilde{c}_{30},\tilde{c}_{32}\ge0$, which imply that
 \begin{equation}
@@
 We chose $x=\f{1}{2}$, so that the explicit part of the IMEX scheme is equivalent to the optimal second-order SSP-RK scheme in \cite{gottlieb_etal_2001} (SSPRK2 in \ref{app:butcherTables}).  
-Then, $y=\f{1}{2} + \epsilon$, where $\epsilon \in [0, \frac{1}{2})$, and $c_{\mbox{\tiny Sch}} = 1 - 2\epsilon$ results in the PD-ARS IMEX scheme.  
-Setting $\epsilon = 0$ gives the optimal scheme with $c_{\mbox{\tiny Sch}} = 1$.
+Then, $y=\f{1}{2} + \epsilon$, where $\epsilon \in [0, \frac{1}{2})$, and $c_{\Sch} = 1 - 2\epsilon$ results in the PD-ARS IMEX scheme.  
+Setting $\epsilon = 0$ gives the optimal scheme with $c_{\Sch} = 1$.
 
@@
 \begin{align}
-  \tilde{a}_{21} = a_{22}
+  \f{\tilde{a}_{21}}{a_{22}} = 1
   \quad\text{and}\quad 
-  -\f{a_{32}\,\tilde{a}_{21}}{a_{22}\,a_{33}} + \f{1}{a_{33}} = 1.
+  -\f{a_{32}\,\tilde{a}_{21}}{a_{22}\,a_{33}} + \f{\tilde{a}_{31}+\tilde{a}_{32}}{a_{33}} = 1.
 \label{eq:diffusionAccurate}
 \end{align}
-The first constraint in Eq.~\eqref{eq:1stOrderGeneral} together with the constraints in Eq.~\eqref{eq:diffusionAccurate} gives
+Eq.~\eqref{eq:diffusionAccurate} together with the second constraint in Eq~\eqref{eq:1stOrderGeneral} gives $a_{32}+a_{33}=1$, which together with the first constraint in Eq.~\eqref{eq:1stOrderGeneral} gives
 \begin{align}
@@
 Next we consider the inequality constraints.  
-The constraint-preserving property in Eq.~\eqref{eq:positivityConditionsTypeA} requires $a_{11}, a_{22}, a_{33}>0$, and 
+The convex-invariant property in Eq.~\eqref{eq:positivityConditionsTypeA} requires $a_{11}, a_{22}, a_{33}>0$, and 
 \begin{equation}
@@
 \end{equation}
-Since $a_{31} = 0$, we have
+As a consequence, $a_{21}, a_{32} \geq 0$.  
+However, since $a_{31} = 0$, 
 \begin{equation*}
-  c_{31} = - \frac{a_{32}a_{21}}{a_{22}a_{11}}.  
+  c_{31} = - \frac{a_{32}a_{21}}{a_{22}a_{11}} \le 0.  
 \end{equation*}
-Then, since $a_{21} \geq 0$, $a_{32} \geq 0$, $a_{22} > 0$ and $a_{11} >0$, we have $c_{31} \leq 0$, and the inequality constraints in Eq.~\eqref{eq:constraintsTypeA} hold only for $c_{31} = 0$.
-Unfortunately, $c_{31} = 0$ gives $c_{\mbox{\tiny Sch}} = \min \Big\{\,\f{c_{21}}{\tilde{c}_{21}}, \f{c_{31}}{\tilde{c}_{31}}, \f{c_{32}}{\tilde{c}_{32}}\Big\} = 0$.
+Thus the inequality constraints in Eq.~\eqref{eq:constraintsTypeA} hold only for $c_{31} = 0$, which gives $c_{\Sch} = \min \Big\{\,\f{c_{21}}{\tilde{c}_{21}}, \f{c_{31}}{\tilde{c}_{31}}, \f{c_{32}}{\tilde{c}_{32}}\Big\} = 0$.
 Therefore, a three-stage PD-IMEX scheme (Definition~\ref{def:PD-IMEX}) of type~A does not exist.

### 2018-09-12 Documents/M1/realizableFermionicM1/sections/imex.tex
Edits throughout the paper due to extensive comments from Cory.

--- 2018-09-01 Documents/M1/realizableFermionicM1/sections/imex.tex
@@
-\section{Constraint-Preserving IMEX Schemes}
+\section{Convex-Invariant IMEX Schemes}
 \label{sec:imex}
@@
 In this section we discuss the class of IMEX schemes that are used for the realizability-preserving DG-IMEX method developed in Section~\ref{sec:realizableDGIMEX} (see also \ref{app:butcherTables} for additional details).
-The semi-discretization of the moment equations with the DG method given by Eq.~\eqref{eq:semidiscreteDG} results in a system of ordinary differential equations (ODEs) in each element of the form
+The semi-discretization of the moment equations with the DG method given by Eq.~\eqref{eq:semidiscreteDG} results in a system of ordinary differential equations (ODEs) of the form
 \begin{equation}
@@
 \end{equation}
-where $\vect{u}$ are the degrees of freedom evolved with the DG method; i.e., for a test space spanned by $\{\phi_{i}(\vect{x})\}_{i=1}^{N}\in\bbV^{k}$, we let
+where $\vect{u}=\{\vect{u}_{\bK}\}_{\bK\in\mathscr{T}}$ are the degrees of freedom evolved with the DG method; i.e., for a test space spanned by $\{\phi_{i}(\vect{x})\}_{i=1}^{N}\in\bbV^{k}$, we let
 \begin{equation}
-  \vect{u}=\f{1}{|\bK|}\Big(\,\int_{\bK}\vect{\cM}_{h}\,\phi_{1}\,d\vect{x},\int_{\bK}\vect{\cM}_{h}\,\phi_{2}\,d\vect{x},\ldots,\int_{\bK}\vect{\cM}_{h}\,\phi_{N}\,d\vect{x}\,\Big)^{T}.
+  \vect{u}_{\bK}=\f{1}{|\bK|}\Big(\,\int_{\bK}\vect{\cM}_{h}\,\phi_{1}\,d\vect{x},\int_{\bK}\vect{\cM}_{h}\,\phi_{2}\,d\vect{x},\ldots,\int_{\bK}\vect{\cM}_{h}\,\phi_{N}\,d\vect{x}\,\Big)^{T}.
 \end{equation}
-Thus, for $\phi_{1}=1$, the first components of $\vect{u}$ are the cell averaged moments.  
+Thus, for $\phi_{1}=1$, the first components of $\vect{u}_{\bK}$ are the cell averaged moments.  
 In Eq.~\eqref{eq:ode}, the transport operator $\vect{\cT}$ corresponds to the second and third term on the left-hand side of Eq.~\eqref{eq:semidiscreteDG}, while the collision operator $\vect{\cQ}$ corresponds to the right-hand side of Eq.~\eqref{eq:semidiscreteDG}.
 
-Eq.~\eqref{eq:ode} is to be integrated forward in time with an ODE integrator, and we begin with the following definition of a constraint-preserving time integration scheme, as applied to integrate a physical model forward in time.
+Eq.~\eqref{eq:ode} is to be integrated forward in time with an ODE integrator.  
+Since the realizable set $\cR$ is convex, convex-invariant schemes can be used to design realizability-preserving schemes for the two-moment model.  
 \begin{define}
-  Given sufficient conditions, a constraint-preserving time integration scheme preserves the constraints of a model if the set of admissible states satisfying the constraints form a convex set.  
+  Given sufficient conditions, a convex-invariant time integration scheme preserves the constraints of a model if the set of admissible states satisfying the constraints forms a convex set.  
   \label{def:constraintPreserving}
 \end{define}
-As an example, given a spatial discretization of a model that is constraint-preserving with the forward Euler method for a sufficiently small time step, high-order explicit strong stability-preserving Runge-Kutta (SSP-RK) methods, which can be expressed as convex combinations of forward Euler steps, also preserve the constraints (possibly with a smaller time step), and form a class of constraint-preserving schemes.
+As an example, high-order explicit strong stability-preserving Runge-Kutta (SSP-RK) methods form a class of convex-invariant schemes.
 
-Since the realizable set $\cR$ is convex, constraint-preserving schemes can be used to design realizability-preserving schemes for the two-moment model.
-
-\subsection{Second-Order Accurate, Constraint-Preserving IMEX Schemes}
+\subsection{Second-Order Accurate, Convex-Invariant IMEX Schemes}
 
@@
 Our goal is to employ IMEX schemes that preserve realizability of the moments, subject only to a time step governed by the explicit transport operator and comparable to the time step required for numerical stability of the explicit scheme.
-We seek to achieve this goal with constraint-preserving IMEX schemes.
+We seek to achieve this goal with convex-invariant IMEX schemes.
 
-Unfortunately, high-order (second or higher order temporal accuracy) constraint-preserving IMEX methods with time step restrictions solely due to the transport operator do not exist (see for example Proposition~6.2 in \cite{gottlieb_etal_2001}, which rules out the existence of implicit SSP-RK methods of order higher than one).
+Unfortunately, high-order (second or higher order temporal accuracy) convex-invariant IMEX methods with time step restrictions solely due to the transport operator do not exist (see for example Proposition~6.2 in \cite{gottlieb_etal_2001}, which rules out the existence of implicit SSP-RK methods of order higher than one).
 To overcome this barrier, Chertock et al. \cite{chertock_etal_2015} presented IMEX schemes with a correction step.  
@@
 The correction step is introduced to recover second-order accuracy.  
-However, the correction step in \cite{chertock_etal_2015} involves both the transport and collision operators, and we have found that, when applied to the fermionic two-moment model, realizability is subject to a time step restriction that depends on $\tau$, which may become too restrictive for stiff problems.
+However, the correction step in \cite{chertock_etal_2015} involves both the transport and collision operators, and we have found that, when applied to the fermionic two-moment model, realizability is subject to a time step restriction that depends on $\tau$ in a way that becomes too restrictive for stiff problems.
 More recently, Hu et al.
 \cite{hu_etal_2018}, presented similar IMEX schemes for problems involving BGK-type collision operators, but with a correction step that does not include the transport operator.
-In this case, the scheme is constraint-preserving, subject only to time step restrictions stemming from the transport operator, which is more attractive for our target application.  
+In this case, the scheme is convex-invariant, subject only to time step restrictions stemming from the transport operator, which is more attractive for our target application.  
 These second-order accurate, $s$-stage IMEX schemes take the following form \cite{hu_etal_2018}
@@
 For globally stiffly accurate (GSA) IMEX schemes, $\tilde{w}_{i}=\tilde{a}_{si}$ and $w_{i}=a_{si}$ for $i=1,\ldots,s$, so that $\tilde{\vect{u}}^{n+1}=\vect{u}^{(s)}$ \cite{ascher_etal_1997}.  
-This property is beneficial for very stiff problems, and also simplifies the proof of the realizability-preserving property of the DG-IMEX scheme given in Section~\ref{sec:realizableDGIMEX} since it eliminates the assembly step in Eq.~\eqref{imexIntermediate}.
+This property is beneficial for very stiff problems and also simplifies the proof of the realizability-preserving property of the DG-IMEX scheme given in Section~\ref{sec:realizableDGIMEX}, since it eliminates the assembly step in Eq.~\eqref{imexIntermediate}.
 
@@
 In writing the stages in the IMEX scheme in the general form given by Eq.~\eqref{eq:imexStagesRewrite}, it should be noted that $\tilde{c}_{i0}=0$ for IMEX schemes of Type~A, and $c_{i1}=\tilde{c}_{i1}=0$ for IMEX schemes of Type~ARS \cite{hu_etal_2018}.
-Type A schemes can be made constraint-preserving by requiring 
+Type A schemes can be made convex-invariant by requiring 
 \begin{align}
@@
 \end{align}
-Similarly, type ARS schemes can be made constraint-preserving by requiring 
+Similarly, type ARS schemes can be made convex-invariant by requiring 
 \begin{align}
@@
 Coefficients were given in \cite{hu_etal_2018} for GSA schemes of type A with $s=3$ and type ARS with $s=4$.  
-(It was also proven that $s=3$ and $s=4$ are the necessary number of stages needed for GSA second-order constraint-preserving IMEX schemes of type A and type ARS, respectively.)
+(It was also proven that $s=3$ and $s=4$ are the necessary number of stages needed for GSA second-order convex-invariant IMEX schemes of type A and type ARS, respectively.)
 
-For the scheme to be constraint-preserving, the coefficients $c_{ij}$ in Eq.~\eqref{eq:imexStagesRewrite} must also satisfy $\sum_{j=0}^{i-1}c_{ij}=1$, which implies the so-called Shu-Osher form of the explicit part \cite{shuOsher_1988}.
-If the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} --- which is in the form of a forward Euler update with time step $\hat{c}_{ij}\,\dt$ --- is in the (convex) set of admissible states for all $i=1,\ldots,s$, and $j=0,\ldots,i-1$, then it follows from convexity arguments that the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} is also admissible.
-Thus, if the explicit update with the transport operator is admissible for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is constraint-preserving for a time step $\dt\le c_{\mbox{\tiny Sch}}\,\dt_{\mbox{\tiny Ex}}$, where
+In Eq.~\eqref{eq:imexStagesRewrite}, the explicit part of the IMEX scheme has been written in the so-called Shu-Osher form \cite{shuOsher_1988}.  
+For the scheme to be convex-invariant, the coefficients $c_{ij}$ must also satisfy $\sum_{j=0}^{i-1}c_{ij}=1$.  
+Then, if the expression inside the square brackets in Eq.~\eqref{eq:imexStagesRewrite} --- which is in the form of a forward Euler update with time step $\hat{c}_{ij}\,\dt$ --- is in the (convex) set of admissible states for all $i=1,\ldots,s$, and $j=0,\ldots,i-1$, it follows from convexity arguments that the entire sum on the right-hand side of Eq.~\eqref{eq:imexStagesRewrite} is also admissible.
+Thus, if the explicit update with the transport operator is admissible for a time step $\dt_{\mbox{\tiny Ex}}$, the IMEX scheme is convex-invariant for a time step $\dt\le c_{\Sch}\,\dt_{\mbox{\tiny Ex}}$, where
 \begin{equation}
-  c_{\mbox{\tiny Sch}}=\min_{\substack{i = 2,\ldots,s \\ 
-       j = 1,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}} \quad \text{(Type A)}, \quad  c_{\mbox{\tiny Sch}}=\min_{\substack{i = 2,\ldots,s \\ 
+  c_{\Sch}=\min_{\substack{i = 2,\ldots,s \\ 
+       j = 1,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}} \quad \text{(Type A)}, \quad  c_{\Sch}=\min_{\substack{i = 2,\ldots,s \\ 
               j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}} \quad \text{(Type ARS)}.
@@
 \end{equation}
-Here, $c_{\mbox{\tiny Sch}}$ is the CFL condition, relative to $\dt_{\mbox{\tiny Ex}}$, for the IMEX scheme to be constraint-preserving.  
-It is desirable to make $c_{\mbox{\tiny Sch}}$ as large (close to $1$) as possible.  
-Note that for $\vect{u}^{(i)}$ to be admissible also requires the implicit solve (equivalent to implicit Euler) to be constraint-preserving.  
-In \cite{hu_etal_2018}, Hu et al. provide examples of GSA, constraint-preserving IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
-In \ref{app:butcherTables}, we provide another example of a GSA, constraint-preserving IMEX scheme of type A (scheme PA2+), with a larger $c_{\mbox{\tiny Sch}}$ (a factor of about $1.7$ larger).
+Here, $c_{\Sch}$ is the CFL condition, relative to $\dt_{\mbox{\tiny Ex}}$, for the IMEX scheme to be convex-invariant.  
+It is desirable to make $c_{\Sch}$ as large (close to $1$) as possible.  
+Note that for $\vect{u}^{(i)}$ to be admissible also requires the implicit solve (equivalent to implicit Euler) to be convex-invariant.  
+In \cite{hu_etal_2018}, Hu et al. provide examples of GSA, convex-invariant IMEX schemes of type A (see scheme PA2 in \ref{app:butcherTables}) and type ARS.  
+In \ref{app:butcherTables}, we provide another example of a GSA, convex-invariant IMEX scheme of type A (scheme PA2+), with a larger $c_{\Sch}$ (a factor of about $1.7$ larger).
 
-\subsection{Constraint-Preserving, Diffusion Accurate IMEX Schemes}
+\subsection{Convex-Invariant, Diffusion Accurate IMEX Schemes}
 
@@
 However, we have not been able to prove the realizability-preserving property with this approach without invoking a too severe time step restriction.  
-We therefore proceed to design constraint-preserving IMEX schemes, without the correction step, that perform better in the diffusion limit.  
+We therefore proceed to design convex-invariant IMEX schemes without the correction step that perform well in the diffusion limit.  
 We limit the scope to IMEX schemes of type~ARS.  
@@
 \end{equation}
-We can then write the stages of the IMEX scheme in Eq.~\eqref{imexStages} applied to the number density equation as
+(The components of $\vec{\cJ}$ and $\vec{\vect{\cH}}$ can, e.g., be the cell averages evolved with the DG method.)  
+We can then write the stages of the IMEX scheme in Eq.~\eqref{imexStages} applied to the particle density equation as
 \begin{equation}
@@
 where $\vec{\vect{e}}$ is a vector of length $s$ containing all ones, and the divergence operator acts individually on the components of $\vec{\vect{\cH}}$.  
-Similarly, for the number flux equation we have
+Similarly, for the particle flux equation we have
 \begin{equation}
@@
 \end{equation*}
-For the stages $i=1,\ldots,s$ we then have
+Then, for the stages $i=1,\ldots,s$, 
 \begin{equation}
@@
 \end{equation}
-where $\vec{\vect{e}}_{i}$ is the $i$th column of the $s\times s$ identity matrix, and we have introduced the expansion $\vec{\cJ}=\cJ^{n}\vec{\vect{e}}+\cO(\dt\,\tau)$.  
-Thus, for $\vect{\cH}^{(i)}$ to be accurate in the diffusion limit, we require the IMEX coefficients to satisfy
+where $\vec{\vect{e}}_{i}$ is the $i$th column of the $s\times s$ identity matrix and we have introduced the expansion $\vec{\cJ}=\cJ^{n}\vec{\vect{e}}+\cO(\dt\,\tau)$.  
+For $\vect{\cH}^{(i)}$ to be accurate in the diffusion limit, we require that
 \begin{equation}
@@
 \end{equation}
-(The case $i=1$ is trivial and does not place any constraints on the IMEX coefficients.)  
-Then, for the particle number equation we have
+(The case $i=1$ is trivial and does not place any constraints on the components of $A$ and $\tilde{A}$.)  
+If Eq.~\eqref{eq:diffusionCondition} holds, then
 \begin{equation}
@@
 
-Unfortunately, the ``diffusion limit requirement" in Eq.~\eqref{eq:diffusionCondition}, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints to obtain a second-order accurate constraint-preserving IMEX scheme.
-\footnote{It was shown in \cite{hu_etal_2018} --- without the diffusion limit requirement --- that the minimum number of stages for constraint-preserving IMEX schemes of type~ARS is four.)  
+Unfortunately, the ``diffusion limit requirement" in Eq.~\eqref{eq:diffusionCondition}, together with the order conditions given by Eqs.~\eqref{orderConditions1} and \eqref{orderConditions2} (with $\alpha=0$), and the positivity conditions on $c_{ij}$ and $\tilde{c}_{ij}$, result in too many constraints to obtain a second-order accurate convex-invariant IMEX scheme.%
+\footnote{It was shown in \cite{hu_etal_2018} --- without the diffusion limit requirement --- that the minimum number of stages for convex-invariant IMEX schemes of type~ARS is four.)  
 We are also concerned about increasing the number of stages, and thereby the number of implicit solves, since the implicit solve will dominate the computational cost of the IMEX scheme with more realistic collision operators (e.g., inelastic scattering).}
-To reduce the number of constraints, and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
+To reduce the number of constraints and accommodate accuracy in the diffusion limit, we relax the requirement of overall second-order accuracy of the IMEX scheme.  
 Instead, we only require the scheme to be second-order accurate in the streaming limit ($\vect{\cQ}=0$).  
@@
 \begin{define}
-  Let PD-IMEX be a consistent, constraint-preserving, diffusion accurate, and low-stage GSA IMEX scheme satisfying the following properties
+  Let PD-IMEX be an IMEX scheme satisfying the following properties:
   \begin{enumerate}
@@
     \end{equation}
-    \item Second-order in the streaming limit; i.e., satisfies Eq.~\eqref{eq:orderConditionsEx}.
-    \item Constraint-preserving; i.e. satisfies Eq.~\eqref{eq:positivityConditionsTypeARS}, with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\mbox{\tiny Sch}}>0$.
+    \item Second-order accuracy in the streaming limit; i.e., satisfies Eq.~\eqref{eq:orderConditionsEx}.
+    \item Convex-invariant; i.e. satisfies Eq.~\eqref{eq:positivityConditionsTypeARS}, with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\Sch}>0$.
     \item Well-behaved in the diffusion limit; i.e., satisfies Eq.~\eqref{eq:diffusionCondition}.
     \item Less than four stages ($s\le3$).
-    \item Globally stiffly accurate (GSA) $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$.
+    \item Globally stiffly accurate (GSA): $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$.
   \end{enumerate}
@@
 Scheme PC2 is second-order in the streaming limit, has been demonstrated to work well in the diffusion limit \cite{mcclarren_etal_2008,radice_etal_2013}, and satisfies the positivity conditions in Eq.~\eqref{eq:positivityConditionsTypeARS}.
-However, $c_{\mbox{\tiny Sch}}=0$ (our primary motivation for finding an alternative).  
+However, $c_{\Sch}=0$ (our primary motivation for finding an alternative).  
 In Section~\ref{sec:numerical}, we show numerically that the accuracy of scheme PD-ARS is comparable to the accuracy of scheme PC2.
@@
 \end{equation}
-where $\lambda_{1}\in\mathbb{C}$ and real $\lambda_{2}\le0$.  
+where $\lambda_{1}\in\mathbb{C}$ and $\lambda_{2}\le0$.  
 On the right-hand side of Eq.~\eqref{eq:scalarODE}, the first (oscillatory) term is treated explicitly, while the second (damping) term is treated implicitly.  
@@
 As can be seen from the figures, the absolute stability region of both schemes increases with increasing $|z_{2}|$ (increased damping).  
-For a given $|z_{2}|\ge0$, the stability region of PD-ARS is larger than that of PA2+.  
-In the linear case, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme ($|z_2| = 0$) fulfills the stability requirement for the IMEX scheme as whole ($|z_2| \geq 0$).
+For a given $|z_{2}|>0$, the stability region of PD-ARS is larger than that of PA2+.  
+In the linear model in Eq.~\eqref{eq:scalarODE}, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme ($|z_2| = 0$) fulfills the stability requirement for the IMEX scheme as whole ($|z_2| \geq 0$).
 This holds for all PD-ARS schemes with $\epsilon\in [0,0.5)$.
@@
   \end{tabular}
-   \caption{Boundary of the absolute stability region for different values of $z_2$ for PD-ARS with $\epsilon = 0.1$ (left panel) and PA2+ (right panel).}
+   \caption{Boundary of the absolute stability region in the $xy$-plane ($x=\operatorname{Re}(z_{1})$, $y=\operatorname{Im}(z_{1})$) for different values of $z_2$ for PD-ARS (with $\epsilon = 0.1$; left panel) and PA2+ (right panel).
+Contours of constant $z_{2}$ are included, and the stability region for a given $z_{2}$ is enclosed by the corresponding contour.}
   \label{fig:AbsoluteStability}

### 2018-09-12 Documents/M1/realizableFermionicM1/sections/intro.tex
Edits throughout the paper due to extensive comments from Cory.

@@
 Moments satisfying these constraints are called \emph{realizable moments} (e.g., \cite{levermore_1996}).  
-When evolving a truncated moment model numerically, maintaining realizable moments is challenging, but necessary in order to ensure the well-posedness of the closure procedure, and may also be necessary to guarantee other desirable properties of the model, including hyperbolicity and (mathematical) entropy dissipation (\ee{Need citations here}).
+When evolving a truncated moment model numerically, maintaining realizable moments is challenging, but necessary in order to ensure the well-posedness of the closure procedure \cite{levermore_1996,junk_1998,hauck_2008}.
 In addition to putting the validity of the numerical results into question, failure to maintain moment realizability in a numerical model may, in order to continue a simulation, require ad hoc post-processing steps with undesirable consequences such as loss of conservation.
@@
 
-The CP framework of \cite{zhangShu_2010a} achieves high-order (i.e., greater than first order) accuracy in time by employing strong stability-preserving explicit Runge-Kutta (SSP-RK) methods \cite{shuOsher_1988,gottlieb_etal_2001}, which can be written as a convex combination of forward Euler steps.
-Unfortunately, this strategy to achieve high-order temporal accuracy does not work as straightforwardly for standard IMEX Runge-Kutta (IMEX-RK) methods because implicit SSP Runge-Kutta methods with greater than first order accuracy have time step restrictions similar to explicit methods \cite{gottlieb_etal_2001}.
-To break this ``barrier,'' recently proposed IMEX-RK schemes \cite{chertock_etal_2015,hu_etal_2018} have resorted to first order accuracy in favor of the SSP property in the standard IMEX-RK scheme, and recover second-order accuracy with a correction step.
+The CP framework of \cite{zhangShu_2010a} achieves high-order (i.e., greater than first-order) accuracy in time by employing strong stability-preserving explicit Runge-Kutta (SSP-RK) methods \cite{shuOsher_1988,gottlieb_etal_2001}, which can be written as a convex combination of forward Euler steps.
+Unfortunately, this strategy to achieve high-order temporal accuracy does not work as straightforwardly for standard IMEX Runge-Kutta (IMEX-RK) methods because implicit SSP Runge-Kutta methods with greater than first-order accuracy have time step restrictions similar to explicit methods \cite{gottlieb_etal_2001}.
+To break this ``barrier,'' recently proposed IMEX-RK schemes \cite{chertock_etal_2015,hu_etal_2018} have resorted to first-order accuracy in favor of the SSP property in the standard IMEX-RK scheme, and recover second-order accuracy with a correction step.
 

### 2018-09-12 Documents/M1/realizableFermionicM1/sections/numerical.tex
Edits throughout the paper due to extensive comments from Cory.

@@
 \begin{equation}
-  \cJ_{0}(x)=0.5+0.49\times\sin\big(\pi\,x/3\big)
+  \cJ_{0}(x)=0.5+0.49\times\sin\big(\f{\pi\,x}{3}\big)
   \quad\text{and}\quad
@@
 \begin{equation}
-  \cJ(x,t)=\cJ_{0}(x)\times\exp\big(-\pi^{2}\,t/(27\,\sigma_{\Scatt})\big),
+  \cJ(x,t)=\cJ_{0}(x)\times\exp\big(-\f{\pi^{2}\,t}{27\,\sigma_{\Scatt}}\big),
 \end{equation}
@@
 We set $\sigma_{0}=0.03$, and evolve to a final time of $t=1.0$.  
-We run this test using a grid of $512^{2}$ elements, polynomials of degree $k=1$, and the SSPRK2 time stepping scheme with $\dt=0.1\times\dx^{1}$; a second-order accurate scheme.  
+We run this test using a grid of $512^{2}$ elements, polynomials of degree $k=1$, and the SSPRK2 time stepping scheme with $\dt=0.1\times\dx^{1}$.  
 (There are no collisions included in this test; i.e., $\sigma_{\Ab}=\sigma_{\Scatt}=0$.)  
@@
 Although the solutions obtained with the two-moment model differ from the reference transport solution, the results obtained with the CB closure are in closer agreement with the transport solution.  
+This is likely because the CB closure is consistent with the bound $f<1$ satisfied by the transport solution in this test.  
+(For tests involving lower occupancies, the CB and Minerbo closures are expected to perform similarly.)  
 In the lower left panel in Figure~\ref{fig:Implosion}, the moments are plotted in the $(\cH_{x},\cJ)$-plane for the same times as plotted in the upper left panel.  
 (Each dot represents the moments at a specific spatial point and time.)  
-Initially, $\vect{\cH}=0$, and all the moments lie on on the line connecting $(0,0)$ and $(0,1)$; cyan points.  
+Initially, $\vect{\cH}=0$, and all the moments lie on the line connecting $(0,0)$ and $(0,1)$; cyan points.  
 With the CB closure (blue points), the moments are confined to evolve inside the realizable domain $\cR$ (black), while with the Minerbo closure, the moments are not confined to $\cR$, but to the region above the red lines (the realizable domain for moments of positive distribution functions), and this is the reason for the difference in dynamics in the two models.
@@
 and $g(r,\mu)=[1-(r/R)^{2}(1-\mu^{2})]^{1/2}$.  
-For $f_{0}\in(0,1)$, the analytical solution is bounded $f_{\mbox{\tiny A}}\in(0,1)$.
+Thus, $f_{\mbox{\tiny A}}(r,\mu)\in(0,f_{0})~\forall~r,\mu$.
 
-Here, this test is computed on a three-dimensional Cartesian domain $D=\{\vect{x}\in\bbR^{3}:x^{1}\in[0,2], x^{2}\in[0,2], x^{3}\in[0,2]\}$.  
+Here, this test is computed using a three-dimensional Cartesian domain $D=\{\vect{x}\in\bbR^{3}:x^{1}\in[0,2], x^{2}\in[0,2], x^{3}\in[0,2]\}$.  
 Because of the symmetry of the problem, and to save computational resources, we only compute the solution in one octant.  
@@
 We compute until $t=5$, when the system has reached an approximate steady state.  
-In all the tests, we use the IMEX scheme PD-ARS --- the least compute-intensive of the constraint-preserving IMEX schemes presented here.  
+In all the tests, we use the IMEX scheme PD-ARS with $\dt=0.1\times\dx^{1}$ --- the least compute-intensive of the convex-invariant IMEX schemes presented here.  
 The main purpose of this test is to compare the results obtained using the different algebraic closures discussed in Section~\ref{sec:algebraicClosure}.
@@
   \end{tabular}
-   \caption{Results obtained for the homogeneous sphere problem with the two-moment model for different values of the absorption opacity $\sigma_{\Ab,0}$: $1$ (top panels), $10$, (middle panels), and $1000$ (bottom panels).
+   \caption{Results obtained for the homogeneous sphere problem with the two-moment model for different values of the absorption opacity $\sigma_{\Ab,0}$: $1$ (top panels), $10$ (middle panels), and $1000$ (bottom panels).
 The particle density (left panels) and the flux factor (right panels) are plotted versus radius.
@@
 The results obtained with the maximum entropy closures CB and BL are practically indistinguishable on the plots.  
-This is consistent with the similarity of the Eddington factors for these two closures plotted in Figure~\ref{fig:EddingtonFactorsWithDifferentClosure}.  
+This is consistent with the similarity of the Eddington factors for these two closures, as shown in Figure~\ref{fig:EddingtonFactorsWithDifferentClosure}.  
 We also find that the results obtained with the fermionic Kershaw closure agree well with the maximum entropy closures based on Fermi-Dirac statistics (CB and BL).  
@@
 Similar agreement between the numerical and analytical solutions was reported by Smit et al.
-\cite{smit_etal_1997}, when using the CB maximum entropy closure, with $f_{0}=0.8$ and an unsmoothed absorption opacity $\sigma_{\Ab}=4$.
+\cite{smit_etal_1997}, when using the CB maximum entropy closure with $f_{0}=0.8$ and an unsmoothed absorption opacity $\sigma_{\Ab}=4$.
 We also note that our results appear to be somewhat at odds with the results recently reported by Murchikova et al.
@@
 In Figure~\ref{fig:HomogeneousSphereRealizability}, we further compare the results obtained when using the Minerbo and CB closures by plotting the solutions to the homogeneous sphere problem for Test~C at $t=5$ in the $(\cH_{1},\cJ)$-plane (cf.
-the realizable domain in Figure~\ref{fig:RealizableSetFermionic}):  The numerical solution in each spatial point is represented by a magenta dot in the panels.
+the realizable domain in Figure~\ref{fig:RealizableSetFermionic}).
+The numerical solution at each spatial point is represented by a magenta dot in the panels.  
 Results obtained using the CB closure are plotted in the upper left panel, while results obtained using the Minerbo closure are plotted in the upper right panel.  

### 2018-09-12 Documents/M1/realizableFermionicM1/sections/realizability.tex
More edits
Various edits.  Replaces homogeneous sphere figures
Edits throughout the paper due to extensive comments from Cory.

@@
   The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they can be obtained from a distribution function satisfying $0 < f(\omega) < 1~\forall~\omega\in\bbS^{2}$.  
+  The set of all realizable moments $\cR$ is
+  \begin{equation}
+    \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in(0,1)~\text{and}~\gamma(\vect{\cM}) > 0\,\big\},
+    \label{eq:realizableSet}
+  \end{equation}
+  where we have defined the concave function $\gamma(\vect{\cM})\equiv(1-\cJ)\cJ-|\vect{\cH}|$.  
   \label{def:momentRealizability}
@@
 
-Realizable moments satisfy algebraic constraints.  
-We proceed by stating the constraints on the moments by restating results from Theorem~7.1 in \cite{banachLarecki_2017a} in the following Lemma.  
-The proof is given in \cite{banachLarecki_2017a}.  
-(See also \cite{lareckiBanach_2011,banachLarecki_2013}.)
-\begin{lemma}
-  Suppose that $0 < f(\omega) < 1~\forall~\omega\in\bbS^{2}$.  
-  Then the moments $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, defined as in Eq.~\eqref{eq:angularMoments}, satisfy $0 < \cJ < 1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}| > 0$. 
-  \label{lem:MomentRealizable} 
-\end{lemma}
+The algebraic constraints in Eq.~\eqref{eq:realizableSet} are proven in \cite{banachLarecki_2017a} (see also \cite{lareckiBanach_2011,banachLarecki_2013}).  
+%\begin{lemma}
+%  Suppose that $0 < f(\omega) < 1~\forall~\omega\in\bbS^{2}$.  
+%  Then the moments $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, defined as in Eq.~\eqref{eq:angularMoments}, satisfy $0 < \cJ < 1$ and $\big(1-\cJ\big)\,\cJ-|\vect{\cH}| > 0$. 
+%  \label{lem:MomentRealizable} 
+%\end{lemma}
 
-\begin{define}
-  For the fermion two-moment model, the realizable set is
-  \begin{equation}
-    \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in(0,1)~\text{and}~\gamma(\vect{\cM})\equiv(1-\cJ)\cJ-|\vect{\cH}| > 0\,\big\}.
-    \label{eq:realizableSet}
-  \end{equation}
-\end{define}
+%\begin{define}
+%  For the fermion two-moment model, the realizable set is
+%  \begin{equation}
+%    \cR:=\big\{\,\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}~|~\cJ\in(0,1)~\text{and}~\gamma(\vect{\cM})\equiv(1-\cJ)\cJ-|\vect{\cH}| > 0\,\big\}.
+%    \label{eq:realizableSet}
+%  \end{equation}
+%\end{define}
 
 \begin{lemma}
-  The realizable set $\cR$, defined in Eq.~\eqref{eq:realizableSet}, is convex.  
+  The realizable set $\cR$ is convex.  
 \end{lemma}
 \begin{proof}
-  In order to prove that $\cR$ is convex, it is sufficient to show that any convex combination of elements in $\cR$ also belongs to $\cR$.  
-  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ be two arbitrary elements in $\cR$.  
-  Consider the convex combination $\vect{\cM}_{c} = \theta\,\vect{\cM}_{a} + (1-\theta)\,\vect{\cM}_{b}$, with $0\leq\theta\leq1$.
+%  In order to prove that $\cR$ is convex, it is sufficient to show that any convex combination of elements in $\cR$ also belongs to $\cR$.  
+  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ be two arbitrary elements in $\cR$, and let $\vect{\cM}_{c} = \theta\,\vect{\cM}_{a} + (1-\theta)\,\vect{\cM}_{b}$, with $0\leq\theta\leq1$.
   The first component of $\vect{\cM}_{c}$ is
@@
   Since $\cJ_{a},\cJ_{b} \in (0,1)$, it follows that $\cJ_{c} \in (0,1)$.  
-  Since $\cJ_{a},\cJ_{b} \in (0,1)$, it is straightforward to verify that
+  Concavity of $\gamma$ implies that
+%  Since $\cJ_{a},\cJ_{b} \in (0,1)$, it is straightforward to verify that
   \begin{equation*}
@@
 is partially shown as the light red region above the red lines, which mark the boundary of $\cR^{+}$ (denoted $\partial\cR^{+}$).  
-(A realizability-preserving method, with respect to $\cR^{+}$, for the two-moment model in one spatial dimension was developed in \cite{olbrant_etal_2012}.)  
-The realizable domains $\cR$ and $\cR^{+}$ overlap for low particle densities ($\cJ\ll1$), but for larger values of $\cJ$, the realizable domain of particles governed by Fermi-Dirac statistics is much more restricted than that of particles described by positive distribution functions with no upper bound.
+The realizable set $\cR$ is a bounded subset of $\cR^{+}$.  
+%The realizable domains $\cR$ and $\cR^{+}$ overlap for low particle densities ($\cJ\ll1$), but for larger values of $\cJ$, the realizable domain of particles governed by Fermi-Dirac statistics is much more restricted than that of particles described by positive distribution functions with no upper bound.
 
-\begin{figure}[h]
+\begin{figure}[H]
   \centering
@@
   \begin{equation*}
-    \vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} \equiv \Phi^{+}(\vect{\cM}_{a},\vect{\cK}_{a})+\Phi^{-}(\vect{\cM}_{b},\vect{\cK}_{b})\in\cR.
+    \vect{\cM}_{ab} \equiv \Phi^{+}(\vect{\cM}_{a},\vect{\cK}_{a})+\Phi^{-}(\vect{\cM}_{b},\vect{\cK}_{b})\in\cR.
   \end{equation*}
@@
 \begin{proof}
-  It is straightforward to rewrite the components of $\vect{\cM}_{ab}$ as
+  The components of $\vect{\cM}_{ab}$ are
   \begin{equation*}
@@
   where $f_{ab}(\omega)=\vartheta\,f_{a}(\omega)+(1-\vartheta)\,f_{b}(\omega)$ and $\vartheta(\omega)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omega))/2\in[0,1]$.  
-  Then, since $f_{ab}(\omega)\in(0,1)\,\forall\,\omega\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
+  Then, since $f_{ab}(\omega)\in(0,1)\,\forall\,\omega\in\bbS^{2}$, it follows that $\vect{\cM}_{ab}\in\cR$.  
 \end{proof}
@@
   Let $\vect{\cM}_{b}=(\cJ_{b},\vect{\cH}_{b})^{T}$ satisfy
-  \begin{equation*}
+  \begin{equation}
     \vect{\cM}_{b}=\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b}), 
-  \end{equation*}
+    \label{eq:implicitStep}
+  \end{equation}
   where $\vect{\cC}(\vect{\cM})=\vect{\eta}-\vect{\cD}\,\vect{\cM}$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.  
@@
 \begin{proof}
-  Solving for $\vect{\cM}_{b}$ gives $\vect{\cM}_{b} = \big(\vect{I}+\alpha\,\vect{\cD}\big)^{-1}\big(\vect{\cM}_{a}+\alpha\,\vect{\eta}\big)$.  
+  Solving Eq.~\eqref{eq:implicitStep} for $\vect{\cM}_{b}$ gives $\vect{\cM}_{b} = \big(\vect{I}+\alpha\,\vect{\cD}\big)^{-1}\big(\vect{\cM}_{a}+\alpha\,\vect{\eta}\big)$.  
   The first component of $\vect{\cM}_{b}$ can be written as
@@
   \end{equation*}
-  where $f_{b}(\omega)=\zeta\,f_{a}(\omega)+(1-\zeta)\,f_{0}$, $\zeta=1/(1+\alpha\,\xi)\in[0,1]$, and $f_{0}$ and $\xi$ are defined in Section~\ref{sec:model}.  
+  where $f_{b}(\omega)=\zeta\,f_{a}(\omega)+(1-\zeta)\,f_{0}$, $\zeta=1/(1+\alpha\,\xi)\in[0,1]$, and $f_{0}$ and $\xi$ are defined in Eq.~\eqref{eq:collisionTerm} in Section~\ref{sec:model}.  
   Then, since $f_{b}(\omega)\in(0,1)\,\forall\,\omega\in\bbS^{2}$, $\cJ_{b}\in(0,1)$.  
-  Similarly, we can write
+  Meanwhile, 
   \begin{equation*}
@@
   \end{equation*}
-  It follows from Lemma~\ref{lem:MomentRealizable} that $\widetilde{\vect{\bcM}}_{b}=(\cJ_{b},\widetilde{\vect{\cH}}_{b})^{T}\in\cR$.  
-  Then, since $0\le\xi\le1$, we have $|\vect{\cH}_{b}|\le|\widetilde{\vect{\cH}}_{b}| < (1-\cJ_{b})\,\cJ_{b}$.  
+  It follows that $\widetilde{\vect{\bcM}}_{b}=(\cJ_{b},\widetilde{\vect{\cH}}_{b})^{T}\in\cR$.  
+  Then, since $0\le\xi\le1$, $|\vect{\cH}_{b}|\le|\widetilde{\vect{\cH}}_{b}| < (1-\cJ_{b})\,\cJ_{b}$.  
 \end{proof}
@@
 \begin{lemma}
-  Let $\vect{\cM}_{a}$ and $\alpha$ be given as in Lemma~\ref{lem:implicitStep}, and let $\vect{\cM}_{b}$ satisfy
+  Let $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$.  
+  Let $\vect{\cM}_{b}$ satisfy
   \begin{equation*}
@@
   \end{equation*}
-  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments},  then $\vect{\cM}_{b}\in\cR$.  
+  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments}.  
+  Then $\vect{\cM}_{b}\in\cR$.  
   \label{lem:correctionStep}

### 2018-09-13 Documents/M1/realizableFermionicM1/sections/intro.tex
Minor edits

@@
 With the correction step from \cite{hu_etal_2018} the realizability-preserving property is guaranteed with a time step comparable to that of the forward Euler method applied to the explicit part of the scheme, but the resulting scheme performs poorly in the asymptotic diffusion limit.
-Because of these challenges, we resort to first-order temporal accuracy, and propose IMEX-RK schemes that are constraint-preserving with a time step equal to that of forward Euler on the explicit part, perform well in the diffusion limit, and reduce to a second-order SSP-RK scheme in the streaming limit (no collisions with the background material).
+Because of these challenges, we resort to first-order temporal accuracy, and propose IMEX-RK schemes that are convex-invariant with a time step equal to that of forward Euler on the explicit part, perform well in the diffusion limit, and reduce to a second-order SSP-RK scheme in the streaming limit (no collisions with the background material).
 
@@
 In Section~\ref{sec:realizability} we discuss moment realizability for the fermionic two-moment model, while algebraic moment closures are discussed in Section~\ref{sec:algebraicClosure}.  
-In Section~\ref{sec:dg} we briefly introduce the DG method for the two-moment model, while the IMEX time stepping methods we use are discussed in Section~\ref{sec:imex}.  
-The main results on the realizability-preserving DG-IMEX method for the fermionic two-moment model are worked out in Section~\ref{sec:realizableDGIMEX}.  
-In Section~\ref{sec:limiter} we discuss the realizability-enforcing limiter.  
+In Section~\ref{sec:dg} we briefly introduce the DG method for the two-moment model, while the (convex-invariant) IMEX time stepping methods we use are discussed in Section~\ref{sec:imex}.  
+The main results on the realizability-preserving DG-IMEX method for the fermionic two-moment model are worked out in Sections~\ref{sec:realizableDGIMEX} and \ref{sec:limiter}.  
+In Section~\ref{sec:limiter} we also discuss the realizability-enforcing limiter.  
 Numerical results are presented in Section~\ref{sec:numerical}, and summary and conclusions are given in Section~\ref{sec:conclusions}.  
+Additional details on the IMEX schemes are provided in Appendices.

### 2018-09-13 Documents/M1/realizableFermionicM1/sections/numerical.tex
Minor edits

@@
 The numerical solutions obtained with both of these closures follow the analytic solution well, and remain within the realizable set $\cR$.  
-We point out that simply using the realizability-preserving limiter described in Section~\ref{sec:limiter} with the Minerbo closure does not result in a realizability-preserving scheme for Fermi-Dirac statistics because of the properties of this closure discussed in Section~\ref{sec:algebraicClosure}, and plotted in the lower right panel of Figure~\ref{fig:MabWithDifferentClosure}.
+We point out that simply using the realizability-preserving limiter described in Section~\ref{sec:limiter} with the Minerbo closure does not result in a realizability-preserving scheme for Fermi-Dirac statistics because of the properties of this closure discussed in Section~\ref{sec:algebraicClosure}, and plotted in the right panel of Figure~\ref{fig:MabWithDifferentClosure}.
 
@@
 
-In Figure~\ref{fig:HomogeneousSphereRealizability}, we further compare the results obtained when using the Minerbo and CB closures by plotting the solutions to the homogeneous sphere problem for Test~C at $t=5$ in the $(\cH_{1},\cJ)$-plane (cf.
+In Figure~\ref{fig:HomogeneousSphereRealizability}, we further compare the results obtained when using the Minerbo and CB closures by plotting the solutions to the homogeneous sphere problem for Test~C at $t=5$ in the $(|\vect{\cH}|,\cJ)$-plane (cf.
 the realizable domain in Figure~\ref{fig:RealizableSetFermionic}).
-The numerical solution at each spatial point is represented by a magenta dot in the panels.  
-Results obtained using the CB closure are plotted in the upper left panel, while results obtained using the Minerbo closure are plotted in the upper right panel.  
-In the lower two panel we zoom in on the results obtained with the Minerbo closure around the top and lower right regions of the realizable domain (lower left and lower right panel, respectively; cf.
-blue boxes in the upper right panel).
+The numerical solution at each spatial point is represented by a blue (CB) or magenta (Minerbo) dot in the panels.  
+In the lower two panel we zoom in on the results obtained with the two closures around the top and lower right regions of the realizable domain (lower left and lower right panel, respectively; cf.
+green boxes in the upper right panel).
 \begin{figure}[H]
   \centering
+  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_CBandMinerbo}
   \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_CB}
-    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_Minerbo} \\
-    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_Minerbo_Box1}
-    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_Minerbo_Box2}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_CBandMinerbo_Box1}
+    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Realizability_Chi_1e3_CBandMinerbo_Box2}
   \end{tabular}
-   \caption{Plots of the numerical solution to the homogeneous sphere problem for Test~C in the $(\cH_{1},\cJ)$-plane.
-Results obtained with the CB and Minerbo closures are plotted in the upper left and upper right panels, respectively.
-Zoom-ins on the solutions obtained with the Minerbo closure are plotted in the lower two panels (cf.
-blue boxes in the upper right panel).
+   \caption{Scatter plots of the numerical solution to the homogeneous sphere problem for Test~C in the $(|\vect{\cH}|,\cJ)$-plane.
+Results obtained with the CB and Minerbo closures are plotted in the upper panel, blue and magenta points, respectively.
+Zoom-ins on the solutions obtained with the two closures are plotted in the lower two panels (cf.
+green boxes in the upper panel).
 The boundaries of the realizable domains $\cR$ and $\cR^{+}$ are indicated with solid black and solid red curves, respectively.
@@
 \end{figure}
-As can be seen in the upper panels in Figure~\ref{fig:HomogeneousSphereRealizability}, the solution to the homogeneous sphere problem covers a large fraction of the right half of the realizable domain $\cR$, whose boundary is indicated by solid black curves in each panel.
-(The moments only appear in the right half of $\cR$ because we only compute in one octant.)  
+As can be seen in the upper panel in Figure~\ref{fig:HomogeneousSphereRealizability}, the solutions to the homogeneous sphere problem obtained with the two closures trace out distinct curves relative to the realizable domain $\cR$, whose boundary is indicated by solid black curves in each panel.
 When using the CB closure, the realizability-preserving DG-IMEX scheme developed here maintains solutions within $\cR$.  

### 2018-09-13 Documents/M1/realizableFermionicM1/manuscript.tex
adding ORNL copyright blurb

@@
+%\documentclass[1p]{elsarticle}
 \documentclass[review]{elsarticle}
@@
 
-\title{Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}}
+\title{Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}\tnoteref{copyright}}
 \tnotetext[support]{
@@
 Eirik Endeve was supported in part by NSF under Grant No. 1535130.}
+\tnotetext[copyright]{This manuscript has been authored by UT-Battelle, LLC under Contract No.
+DE-AC05-00OR22725 with the U.S.
+Department of Energy.
+The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, world-wide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
+The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan(http://energy.gov/downloads/doe-public-access-plan).}
 

### 2018-09-13 Documents/M1/realizableFermionicM1/manuscript.tex
Added ASCR credit line

@@
 Department of Energy Office of Science and the National Nuclear Security Administration.
+This material is based, in part, upon work supported by the U.S. Department of Energy, Office of Science, Office of Advanced Scientific Computing Research.  
 Eirik Endeve was supported in part by NSF under Grant No. 1535130.}
-\tnotetext[copyright]{This manuscript has been authored by UT-Battelle, LLC under Contract No.
+\tnotetext[copyright]{
+This manuscript has been authored by UT-Battelle, LLC under Contract No.
 DE-AC05-00OR22725 with the U.S.

### 2018-09-16 Documents/M1/Astronum_2018/manuscript.tex
Created a new directory for Astronum 2018 IMEX contribution.

\documentclass[a4paper]{jpconf}
\usepackage{graphicx}
\usepackage{./definitions}
\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}

\bibliographystyle{iopart-num}

\begin{document}
\title{Constraint-Preserving IMEX Scheme for the Two-Moment Model of Fermion Transport}

\author{Ran Chu}
\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
\ead{rchu@vols.utk.edu}

\author{Eirik Endeve}
\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
\ead{endevee@ornl.gov}

\author{Cory D. Hauck}
\address{Department of Mathematics, University of Tennessee Knoxville, TN 37996-1320}
\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
\ead{hauckc@ornl.gov}

\author{Anthony Mezzacappa}
\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
\ead{mezz@utk.edu}

\begin{abstract}
All articles {\it must} contain an abstract...
\end{abstract}

\input{sections/intro}
\input{sections/TwoMoments}
\input{sections/SpacialDiscretization}
\input{sections/TimeIntegration}
\input{sections/Numerical}

\section*{References}
\bibliography{references/references}

\end{document}

### 2018-09-16 Documents/M1/Astronum_2018/sections/Numerical.tex
Created a new directory for Astronum 2018 IMEX contribution.

\section{Numerical Tests}

\subsection{Accuracy Tests}

\subsection{Constraint-Preserving Tests}

### 2018-09-16 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Created a new directory for Astronum 2018 IMEX contribution.

\section{Spacial Discretization}
Let the spatial domain be $D$ and divide it into $N$ cells, denoted $I_{i}$ with $i = 1,\ldots,N$:
\begin{equation*}
D = \cup_{i = 1}^{N} I_{i}
\end{equation*}
\begin{equation}
\bcM_{i} = \dfrac{1}{\dx} \int_{I_i}\bcM dx
\end{equation}

\begin{equation}
\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{\dx} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) +  \cC(\bcM_{i})
\end{equation}

\begin{equation}
  \widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})
  =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big)
\end{equation}

By treating the flux term explicitly and the collision term implicitly, we have
\begin{align}
\bcM_{i}^{n+1} 
& = \bcM_{i}^{n} - \dfrac{\dt}{\dx} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right) + \dt\,\cC(\bcM^{n+1}_{i}) \nonumber \\
& = (1-\eta)\bcM_{i}^{n} + \f{1}{2}\eta\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\eta\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right) + \dt\,\cC(\bcM^{n+1}_{i})
\end{align}
with $\eta = \dfrac{\dt}{\dx}$. The first three terms can form a convex combination.

### 2018-09-16 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Created a new directory for Astronum 2018 IMEX contribution.

\section{Time Integration}

Let $\vect{\cQ}$ be some linear operators and
\begin{equation}
\vect{u}(t) = \left( \bcM_{1}(t),\ldots,\bcM_{N}(t)\right) ^{T}
\end{equation}
\begin{equation}
  \dfrac{d \vect{u}}{d t} = \vect{\cT}(\vect{u}) + \vect{\cQ}(\vect{u})
\end{equation}
\subsection{Standard Implicit-Explicit Scheme}

\begin{align}
  \vect{u}^{(i)}
  &=\vect{u}^{n}
  +\dt\sum_{j=1}^{i-1}\tilde{a}_{ij}\,\vect{\cT}(\vect{u}^{(j)})
  +\dt\sum_{j=1}^{i}a_{ij}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(j)}),
  \quad i=1,\ldots,s, \label{imexStages} \\
  \tilde{\vect{u}}^{n+1}
  &=\vect{u}^{n}
  +\dt\sum_{i=1}^{s}\tilde{w}_{i}\,\vect{\cT}(\vect{u}^{(i)})
  +\dt\sum_{i=1}^{s}w_{i}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}), \label{imexIntermediate} 
\end{align}

\subsection{Constraint-Preserving Implicit-Explicit Scheme}

\begin{equation}
  \vect{u}^{(i)}
  =\sum_{j=0}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
  \label{eq:imexStagesRewrite}
\end{equation}

\subsubsection{PD-ARS with SSPRK2}

\begin{equation}
  \begin{array}{c | c c c}
  	0 & 0   & 0 & 0 \\
  	1 & 1   & 0 & 0 \\
  	1 & 1/2 & 1/2 & 0 \\ \hline
  	  & 1/2 & 1/2 & 0
  \end{array}
  \qquad
  \begin{array}{c | c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1 & 0 & 1/2-\epsilon & 1/2+\epsilon \\ \hline
  	  & 0 & 1/2-\epsilon & 1/2+\epsilon
  \end{array}
\end{equation}

For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.

\subsubsection{PD-ARS with SSPRK3}
\begin{equation}
  \begin{array}{c | c c c c}
  	    &     &     &     &  \\
  	 1  & 1   &     &     &  \\
  	1/2 & 1/4 & 1/4 &  \\
  	 1  & 1/6 & 1/6 & 2/3 &  \\ \hline
  	    & 1/6 & 1/6 & 2/3 &
  \end{array}
  \qquad
  \begin{array}{c | c c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1/2 & 0 & 1/4 & 1/4 \\ 
  	1 & 0 & 1/6-\epsilon^2 /4 & 1/6-\epsilon/4 & 2/3+\epsilon(1+\epsilon)/4\\\hline
  	  & 0 & 1/6-\epsilon^2 /4 & 1/6-\epsilon/4 & 2/3+\epsilon(1+\epsilon)/4
  \end{array}
\end{equation}
For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 3\epsilon/2$ with $\epsilon \rightarrow 0^{+}$.

### 2018-09-16 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Created a new directory for Astronum 2018 IMEX contribution.

\section{Two-Moment Model}

\subsection{Transport Equations}
Considering some massless fermion pass through a static material and only emission, absorption and elastic scattering exist, the transport equation of the fermion after scaling to dimensionless units can be written as
\begin{equation}
  \pd{f}{t}+\vect{\ell}\cdot\nabla f
  =\f{1}{\tau}\,\cC(f).
  \label{eq:boltzmann}
\end{equation}
whic is known as Boltzmann equation.
The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of particles propagating in the direction $\omega\in\bbS^{2}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.  
$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector which parallel to the fermion three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
On the right-hand side, $\tau$ is interaction strength parameter: $\tau\ll1$ for opaque (strong interaction with the background) region while $\tau\gg1$ for transparent (weak interaction with the background, or free streaming) region.
$\cC(f)$ is the collision term, which models emission, absorption, and isotropic and elastic scattering: 
\begin{equation}
  \cC(f)=\xi\,\big(\,f_{0}-f\,\big)
  +(1-\xi)\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omega-f\,\big),
  \label{eq:collisionTerm}
\end{equation}
where $\xi$ is the emission and absorption contribution parameter: $\xi = 1$ for pure emission and absorption, or no scattering; $\xi = 0$ for pure scattering. 
$f_{0}$ is the fermion equilibrium distribution function which has the following form:
\begin{equation}
  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1},  
  \label{eq:fermiDirac}
\end{equation}
where $T$ is the temperature in energy unit, and $\mu$ is the fermion chemical potential.
Both of them depend on the properties of the background.

\subsection{Two-Moment Model}
An approximate solution of Boltzmann equation Eq.~\eqref{eq:boltzmann} can be found by using two-moment model.
In two-moment model, the angular moments of the distribution function are defined as
\begin{equation}
  \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega.  
  \label{eq:angularMoments}
\end{equation}
with $\vect{z}:=\{\varepsilon,\vect{x}\}$.
The zeroth moment $\cJ$ is referred as the particle density, while the first moment $\bcH$ the particle flux and the second moment $\bcK$ the stress tensor.
Besides, define $\vect{\cM}=(\cJ,\vect{\cH})^{T}$ and $\vect{\cF}=(\vect{\cH},\vect{\cK})^{T}$, then take the zeroth and first moment of Eq.~\eqref{eq:boltzmann}, we have
\begin{equation}
  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}=\f{1}{\tau}\,\vect{\cC}(\vect{\cM}),
  \label{eq:momentEquations}
\end{equation}
with
\begin{equation}
  \vect{\cC}(\vect{\cM})=\vect{\eta}-\vect{\cD}\,\vect{\cM},
  \label{eq:collisionTermMoments}
\end{equation}
where $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$ and $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$.
$\vect{I}$ is the identity matrix.

\subsection{Algebraic Closures }
To close the system given by Eq.~\eqref{eq:momentEquations}, a strategy named algebraic closure is used.
Algebraic closures give approximate $\bcK$ based on the lower moments:
\begin{equation}
\bcK = \vect{k} \cJ,
\end{equation}
where $\vect{k}$ is the Eddington tensor.
Levermore\cite{levermore_1984} assumed that the radiation field is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$ and gave 
\begin{equation}
  \vect{k}=\f{1}{2}\big[\,\big(1-\chi\big)\,\vect{I}+\big(3\,\chi-1\big)\,\widehat{\vect{h}}\otimes\widehat{\vect{h}}\,\big],
  \label{eq:eddingtonTensor}
\end{equation}
where $\chi=\chi(\cJ,|\vect{\cH}|)$ is the Eddington factor.

\subsection{Constraints on Moments}
One fundamental fact one should concern before solving the system is the property he/she should never violate.
For a fermionic system, the property is Pauli exclusion principle, or 
\begin{equation}
f \in (0,1).
\end{equation}
As an result, the angular moments as the integration of $f$ are confined as following
\begin{align}
\cJ \in(0,1), \quad &(1-\cJ)\cJ-|\vect{\cH}|  > 0, \\
  \chi_{\mbox{\tiny min}}
  =\max\big(1-\f{2}{3\cJ},h^{2}\big)
  < & \chi<\min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}}.  
  \label{eq:eddingtonFactorBounds}
\end{align}
As Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the constraints on moments all the time: Kershaw [citation], Wilson [citation], Levermore [citation], Minerbo [citation], Janka 2 [citation] may work fine at low occupancy case, but not at high occupancy situation; Janka 1 [citation] is even worse and not work all the time. Only Cernohorsky \& Bludman[citation] among these plotted closures remains in the realizable region.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_10}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_90}
  \end{tabular}
   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupied) and $\cJ=0.9$ (right panel, high occupied).  In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.  We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dash black lines, respectively).}
  \label{fig:EddingtonFactorsWithDifferentClosure}
\end{figure}

### 2018-09-19 Documents/M1/Astronum_2018/sections/Numerical.tex
Commited for backup.

@@
 \subsection{Accuracy Tests}
+To compare the accuracy of the IMEX scheme, we applied our PDARSs with RKCB2 [citation] and SSP2332[citation] scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
+All the tests in this subsection were applied with third order accurate spatial discretization, the maximum entropy closure in the low occupancy limit and time step $\dt = 0.1 \times \dx $.
+More information and the definition of the absolute error and the relative error can be found in \cite{Chu_2018}.
+
+\subsubsection{Sine Wave Streaming}
+This test involves the streaming part only: the collision term is turned off. 
+A periodic domain $D$ was applied and the initial condition 
+\begin{figure}[h]
+  \centering
+    \includegraphics[width=0.6\textwidth]{figures/SineWaveStreaming}
+   \caption{Sine Wave Streaming}
+\end{figure}
+
+\subsubsection{Sine Wave Damping}
+\begin{figure}[h]
+  \centering
+    \includegraphics[width=0.7\textwidth]{figures/SineWaveDamping}
+   \caption{Sine Wave Damping}
+\end{figure}
+\subsubsection{Sine Wave Diffusion}
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionJ}
+    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionH}
+  \end{tabular}
+   \caption{Sine Wave Diffusion}
+\end{figure}
 
 \subsection{Constraint-Preserving Tests}
+
+\subsubsection{Neutrino Stationary State Test}
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.4\textwidth]{figures/NStatinaryS_EOS}
+    \includegraphics[width=0.55\textwidth]{figures/NSS_Opacities}
+  \end{tabular}
+   \caption{Neutrino Stationary State Test}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=0.45\textwidth]{figures/NSS_0_1}
+    \includegraphics[width=0.45\textwidth]{figures/NSS_0_2} \\
+    \includegraphics[width=0.45\textwidth]{figures/NSS_1_1}
+    \includegraphics[width=0.45\textwidth]{figures/NSS_1_2} \\
+    \includegraphics[width=0.45\textwidth]{figures/NSS_3_1}
+    \includegraphics[width=0.45\textwidth]{figures/NSS_3_2} \\
+    \includegraphics[width=0.45\textwidth]{figures/NSS_5_1}
+    \includegraphics[width=0.45\textwidth]{figures/NSS_5_2} \\
+  \end{tabular}
+   \caption{Neutrino Stationary State Test}
+\end{figure}

### 2018-09-19 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Commited for backup.

@@
 \section{Spacial Discretization}
-Let the spatial domain be $D$ and divide it into $N$ cells, denoted $I_{i}$ with $i = 1,\ldots,N$:
+Divide the spatial domain $D$ into $N$ cells and denote the cell as $I_{i}$ with $i = 1,\ldots,N$, so that
 \begin{equation*}
-D = \cup_{i = 1}^{N} I_{i}
+D = \cup_{i = 1}^{N} I_{i}.
 \end{equation*}
+Each of the cell has a volume/length of $\dx$.
+Then we have cell average moment:
 \begin{equation}
-\bcM_{i} = \dfrac{1}{\dx} \int_{I_i}\bcM dx
+\bcM_{i} = \dfrac{1}{\dx} \int_{I_i}\bcM dx.
 \end{equation}
-
+Integrate Eq.~\eqref{eq:momentEquations} for each cell $I_{i}$ to have
 \begin{equation}
-\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{\dx} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) +  \cC(\bcM_{i})
+\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{\dx} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
 \end{equation}
-
+where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the integrated collision term.
+In this paper we use the simple Lax-Friedrichs flux that given by
 \begin{equation}
-  \widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})
-  =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big)
+  \widehat{\bcF}_{LF}(\vect{\cM}_{a},\vect{\cM}_{b})
+  =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big).
 \end{equation}
-
-By treating the flux term explicitly and the collision term implicitly, we have
+Therefore, by treating the flux term explicitly and the collision term implicitly, we have
 \begin{align}
 \bcM_{i}^{n+1} 
-& = \bcM_{i}^{n} - \dfrac{\dt}{\dx} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right) + \dt\,\cC(\bcM^{n+1}_{i}) \nonumber \\
-& = (1-\eta)\bcM_{i}^{n} + \f{1}{2}\eta\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\eta\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right) + \dt\,\cC(\bcM^{n+1}_{i})
+& = \bcM_{i}^{n} - \dfrac{\dt}{\dx} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right) + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i}) \nonumber \\
+& = (1-\eta)\bcM_{i}^{n} + \f{1}{2}\eta\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\eta\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right) + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i})
 \end{align}
-with $\eta = \dfrac{\dt}{\dx}$. The first three terms can form a convex combination.
+where $\eta := \dfrac{\dt}{\dx}$. The first three terms can form a 3-term convex combination by requiring $\eta \in [0,1]$.
+It can be shown that $\bcM_{i}^{n+1}$ remains realizable given $\bcM_{i}^{n}$ is realizable, $\eta \in [0,1]$ and $\cC(\bcM)$ is positivity-preserving. The proof can be found in \cite{Chu_2018}.

### 2018-09-19 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Commited for backup.

@@
 \section{Time Integration}
-
-Let $\vect{\cQ}$ be some linear operators and
+In this section we show how to use the property we introduced at the end of the previous section to construct a constraint-preserving implicit-explicit (IMEX) scheme.
+We can have a more general form of the partial differential equation, Eq.~\eqref{eq:momentEquations},
+\begin{equation}
+  \dfrac{d \vect{u}}{d t} = \vect{\cT}(\vect{u}) + \f{1}{\tau}\,\vect{\cQ}(\vect{u}),
+\end{equation}
+where
 \begin{equation}
@@
 \end{equation}
-\begin{equation}
-  \dfrac{d \vect{u}}{d t} = \vect{\cT}(\vect{u}) + \vect{\cQ}(\vect{u})
-\end{equation}
+is the collection of all moment cell average, $\vect{\cT}$ is the operator corresponding to the flux term and $\f{1}{\tau}\,\vect{\cQ}$ is a linear operators corresponding to the collision term.
+
 \subsection{Standard Implicit-Explicit Scheme}
-
+Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, the standard $s$-stage IMEX schemes take the following form 
 \begin{align}
@@
   \quad i=1,\ldots,s, \label{imexStages} \\
-  \tilde{\vect{u}}^{n+1}
+  \vect{u}^{n+1}
   &=\vect{u}^{n}
@@
 \end{align}
+where  $(\tilde{a}_{ij})$ and $(a_{ij})$ are coefficients of the $i$th-stage and they are the elements of matrices $\tilde{A}$ and $A$, respectively, and the vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weights vector.
+Some conditions those coefficients and weights have to satisfy to serve an accurate, converge and stable scheme.
+For instance, to have second-order temporal accuracy, the following conditions are required:
+\begin{equation}
+  \sum_{i=1}^{s}\tilde{w}_{i}=\sum_{i=1}^{s}w_{i}=1,
+  \label{orderConditions1}
+\end{equation}
+and
+\begin{equation}
+  \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}
+  =\sum_{i=1}^{s}\tilde{w}_{i}\,c_{i}
+  =\sum_{i=1}^{s}w_{i}\,\tilde{c}_{i}
+  =\sum_{i=1}^{s}w_{i}\,c_{i}=\f{1}{2}, 
+  \label{orderConditions2}
+\end{equation}
+where $\tilde{c}_{i} = \sum_{j}^{s}\tilde{a}_{ij}$ and $c_{i}=\sum_{j}^{s}a_{ij}$.
 
 \subsection{Constraint-Preserving Implicit-Explicit Scheme}
-
+The problem left for constructing a constraint-preserving IMEX is finding the conditions $(\tilde{a}_{ij})$, $(a_{ij})$, $\tilde{w}_{i}$ and $w_{i}$ need to satisfied and giving their possible values.
+As Hu et al. did in their paper \cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten to
 \begin{equation}
@@
 \end{equation}
-
+It can be proved \cite{Chu_2018} that the conditions we need for constraint-preserving IMEX is:
+\begin{enumerate}
+    \item Consistency of the implicit coefficients
+    \begin{equation}
+      \sum_{i=1}^{s}w_{i}=1.
+    \end{equation}
+    \item Second-order accuracy in the streaming limit; i.e., satisfies \begin{equation}
+      \sum_{i=1}^{s}\tilde{w}_{i}=1
+      \quad\text{and}\quad
+      \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2},
+      \label{eq:orderConditionsEx}
+    \end{equation}
+    \item Convex-invariant; i.e. satisfies 
+    \begin{align}
+      &a_{ii}>0, \quad c_{i0},\tilde{c}_{i0}\ge0, \quad \text{for} \quad i=2,\ldots,s, \nonumber \\
+      &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=3,\ldots,s, \quad\text{and}\quad j=2,\ldots,i-1.  
+    \end{align}
+    with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\Sch}=\min_{\substack{i = 2,\ldots,s \\ 
+                  j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
+    \item Well-behaved in the diffusion limit; i.e., satisfies \begin{equation}
+      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s.
+      \label{eq:diffusionCondition}
+    \end{equation}
+    \item Less than four stages ($s\le3$).
+    \item Globally stiffly accurate (GSA): $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$.
+\end{enumerate}  
+We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{Chu_2018})
+We give two optimized PD-ARS scheme here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. They have $2$-nd order and $3$-rd order accuracy in the streaming limit, respectively.
 \subsubsection{PD-ARS with SSPRK2}
-
+The explicit part of this IMEX scheme is SSPRK2.
 \begin{equation}
@@
 \subsubsection{PD-ARS with SSPRK3}
+The explicit part of this IMEX scheme is SSPRK3.
+
 \begin{equation}

### 2018-09-19 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Commited for backup.

@@
 \end{equation}
-As an result, the angular moments as the integration of $f$ are confined as following
+As a result, the angular moments as the integrations of $f$ are confined as following
 \begin{align}
@@
   =\max\big(1-\f{2}{3\cJ},h^{2}\big)
-  < & \chi<\min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}}.  
+  < & \chi<\min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}},
   \label{eq:eddingtonFactorBounds}
 \end{align}
+where $h = |\bcH|/\cJ$ is the flux factor.
 As Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the constraints on moments all the time: Kershaw [citation], Wilson [citation], Levermore [citation], Minerbo [citation], Janka 2 [citation] may work fine at low occupancy case, but not at high occupancy situation; Janka 1 [citation] is even worse and not work all the time.

### 2018-09-20 Documents/M1/Astronum_2018/sections/Numerical.tex
Updated the figures.

@@
 \subsection{Accuracy Tests}
-To compare the accuracy of the IMEX scheme, we applied our PDARSs with RKCB2 [citation] and SSP2332[citation] scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
+To compare the accuracy of the IMEX scheme, we applied our PDARSs with Cavaglieri \& Bewley \cite{cavaglieriBewley2015} (RKCB2) and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
 All the tests in this subsection were applied with third order accurate spatial discretization, the maximum entropy closure in the low occupancy limit and time step $\dt = 0.1 \times \dx $.
@@
   \begin{tabular}{cc}
-    \includegraphics[width=0.4\textwidth]{figures/NStatinaryS_EOS}
-    \includegraphics[width=0.55\textwidth]{figures/NSS_Opacities}
+    \includegraphics[width=0.45\textwidth]{figures/NStatinaryS_EOS}
+    \includegraphics[width=0.45\textwidth]{figures/NSS_Opacities}
   \end{tabular}
@@
   \centering
-  \begin{tabular}{cc}
-    \includegraphics[width=0.45\textwidth]{figures/NSS_0_1}
-    \includegraphics[width=0.45\textwidth]{figures/NSS_0_2} \\
-    \includegraphics[width=0.45\textwidth]{figures/NSS_1_1}
-    \includegraphics[width=0.45\textwidth]{figures/NSS_1_2} \\
-    \includegraphics[width=0.45\textwidth]{figures/NSS_3_1}
-    \includegraphics[width=0.45\textwidth]{figures/NSS_3_2} \\
-    \includegraphics[width=0.45\textwidth]{figures/NSS_5_1}
-    \includegraphics[width=0.45\textwidth]{figures/NSS_5_2} \\
-  \end{tabular}
+    \includegraphics[width=\textwidth]{figures/NSS_1_1}\\
+    \includegraphics[width=\textwidth]{figures/NSS_3_1} \\
+    \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
    \caption{Neutrino Stationary State Test}

### 2018-09-20 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Updated the figures.

@@
 where $h = |\bcH|/\cJ$ is the flux factor.
-As Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the constraints on moments all the time: Kershaw [citation], Wilson [citation], Levermore [citation], Minerbo [citation], Janka 2 [citation] may work fine at low occupancy case, but not at high occupancy situation; Janka 1 [citation] is even worse and not work all the time.
-Only Cernohorsky \& Bludman[citation] among these plotted closures remains in the realizable region.
+As Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the constraints on moments all the time: Kershaw\cite{kershaw_1976}, Wilson [citation], Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2 [citation] may work fine at low occupancy case, but not at high occupancy situation; Janka 1 [citation] is even worse and not work all the time.
+Only Cernohorsky \& Bludman\cite{cernohorskyBludman_1994} among these plotted closures remains in the realizable region.
 \begin{figure}[h]

### 2018-09-21 Documents/M1/Astronum_2018/sections/Numerical.tex
Backup Astronum2018.

@@
 \section{Numerical Tests}
-
+In this section we present the numerical results obtained with the PD-ARS schemes provided in this paper.
+The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in various regimes.
+The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the realizability-preserving of PD-ARSs scheme.
 \subsection{Accuracy Tests}
-To compare the accuracy of the IMEX scheme, we applied our PDARSs with Cavaglieri \& Bewley \cite{cavaglieriBewley2015} (RKCB2) and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
+\label{se: Accuracy Tests}
+To compare the accuracy of the IMEX scheme, we applied our PDARSs and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
 All the tests in this subsection were applied with third order accurate spatial discretization, the maximum entropy closure in the low occupancy limit and time step $\dt = 0.1 \times \dx $.
-More information and the definition of the absolute error and the relative error can be found in \cite{Chu_2018}.
+In the streaming test, the second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} , (SSPRK2 and SSPRK3, respectively) are also applied to serve as an reference.
+More information and the definition of the absolute error and the relative error can be found in \cite{chu_2018}.
 
@@
 This test involves the streaming part only: the collision term is turned off. 
-A periodic domain $D$ was applied and the initial condition 
+A periodic domain $D$ was applied and the initial condition is given by...
+More information can be found in \cite{chu_2018}.
+In Figure ~\ref{fig: SineWaveStreaming}, the absolute error for the number density is plotted versus the number of elements $N$.
+Errors obtained with SSPRK3 and PD-ARS with SSPRK3 decrease as $N^{-3}$ as expected.
+All the other schemes have errors decreases as $N^{-2}$.
+In the streaming limit, PD-ARSs degenerate to their explicit part, SSPRK2 and SSPRK3, respectively.
+Hence, errors of PD-ARS and SSPRKs are indistinguishable on the plot.
+Among the second-order schemes, SSP2332 has the smallest error.
 \begin{figure}[h]
@@
     \includegraphics[width=0.6\textwidth]{figures/SineWaveStreaming}
-   \caption{Sine Wave Streaming}
+   \caption{Absolute error versus number of elements $N$ for the streaming sine wave test.
+Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crossing), PD-ARS with SSPRK2 (light red circles) and PD-ARS with SSPRK2 (light red hexagram).
+Black dash-dot reference lines are proportional to $N^{-1}$ (top), $N^{-2}$ (middle), and $N^{-3}$ (bottom), respectively.}
+   \label{fig: SineWaveStreaming}
 \end{figure}
@@
 \subsubsection{Sine Wave Damping}
+Figure~\ref{fig:SineWaveDamping} shows the numerical result of sine wave damping test.
+See \cite{chu_2018} for more information about the test setting.
+SSP2332 as a second-order scheme display second order convergence rate.
+PD-ARSs convergent in first order, as a price paid for realizability-preserving.
 \begin{figure}[h]
@@
     \includegraphics[width=0.7\textwidth]{figures/SineWaveDamping}
-   \caption{Sine Wave Damping}
+   \caption{Relative error versus number of elements $N$ for the damping sine wave test.
+Results for different values of the absorption opacity $\sigma_{\Ab}$, employing various IMEX time stepping schemes, are compared.
+Errors for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.
+The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).
+Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
+  \label{fig:SineWaveDamping}
 \end{figure}
+
 \subsubsection{Sine Wave Diffusion}
+The last test with known smooth solution is sine wave diffusion test.
+See \cite{chu_2018} for more information about the test setting.
+Figure~\ref{fig:SineWaveDiffusionJ} shows the numerical result.
+SSP2332 and PD-ARSs display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$ and their errors are difficult to distinguish.
+PD-ARS with SSP2332 behaviors as good as SSP2332 in the diffusion region but requires 1/3 less implicit solver.
 \begin{figure}[h]
@@
   \end{tabular}
-   \caption{Sine Wave Diffusion}
+   \caption{Absolute error for the number density $\cJ$ (left) and the number flux $\cH_{x}$ (right) versus number of elements for the sine wave diffusion test.
+Results with different values of the scattering opacity $\sigma_{\Scatt}$, employing different IMEX schemes, are compared.
+Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.
+The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).
+Black dash-dot on the left plot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.
+Black dash-dot on the right plot reference lines are proportional to $N^{-2}$ .}
+   \label{fig:SineWaveDiffusionJ}
 \end{figure}
 
-\subsection{Constraint-Preserving Tests}
+\subsection{Neutrino Stationary State Test}
+Next we consider a two dimension test with
 
-\subsubsection{Neutrino Stationary State Test}
+\label{se: Neutrino Stationary State Test}
 \begin{figure}[h]
@@
   \end{tabular}
-   \caption{Neutrino Stationary State Test}
+   \caption{Equation of state plot (left) and neutrino capture opacity (EC) and neutrino elastic scattering opacity (ES) in space (right) for the neutrino stationary state test.}
+   \label{fig:NeutrinoStationaryTestEOS}
 \end{figure}
@@
     \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
-   \caption{Neutrino Stationary State Test}
+   \caption{Readability plots (left column), the number density $\cJ$ versus radius plots (center column) and the flux factor $|\bcH|/\cJ$ versus radius plots (right column) at $t = 0.01$ms ,$0.35$ms and $5.0$ms for the neutrino stationary state test.}
+      \label{fig:NeutrinoStationaryTestEvolve}
 \end{figure}

### 2018-09-24 Documents/Euler/dgEulerGR.tex
Added section about bounds for finding pressure with bisection/Brents method

--- 2017-12-06 Documents/Euler/dgEulerGR.tex
@@
 \usepackage{graphicx}
-\newtheorem*{remark}{Remark}
+\newtheorem{remark}{Remark}
 \graphicspath{{Figures/}}
@@
   &=\big(D,\,S_{j},\,\tau\big)^{\mbox{\tiny T}}
-  =\big(\rho\,W,\,\rho\,h\,W^{2}\,v_{j},\,\rho\,h\,W^{2}-p-D\big)^{\mbox{\tiny T}}, \\
+  =\big(\rho\,W,\,\rho\,h\,W^{2}\,v_{j},\,\rho\,W\left(h\,W-1\right)-p\big)^{\mbox{\tiny T}}, \\
   \bF^{i}(\bU)
@@
 \end{align}
+
+\section{Bound-Preserving Methods Using First-Order DG Scheme}
+
+\subsection{Cartesian Coordinates}
+This section closely follows \citet{Qin2016}.
+
+\subsubsection{Set of Admissible States}
+We consider a one-dimensional system of conservation laws:
+\begin{equation}
+    \pd{\,\bU}{t} + \pd{\,\bF\left(\bU\right)}{x} = \vect{0},
+\end{equation}
+where $\bU$ is a vector of conserved variables, defined as:
+\begin{equation}\label{Eq:ConservedVariables}
+    \bU\longrightarrow\begin{pmatrix} D\\ S\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
+\end{equation}
+and $\bF\left(\bU\right)$ are the fluxes of those conserved quantities:
+\begin{equation}\label{Eq:FluxVector}
+    \bF\left(\bU\right)\longrightarrow\begin{pmatrix}\rho\,W\,v\\ \rho\,h\,W^{2}\,v^{2}+p\\\rho\,h\,W^{2}\,v-D\,v\end{pmatrix}.
+\end{equation}
+
+The physics leads us to define a set of admissible states, $\cG_{p}$ (the subscript $p$ stands for primitive), as:
+\begin{equation}
+    \cG_{p}\equiv\left\{\bU\Big|\rho>0,\,p>0,\,v^{2}<1\right\}.
+\end{equation}
+
+It is shown in \citet{Mignone2005} that $\cG$ is a convex set\footnote{Convex in the sense that if $\bU_{1}\in\cG$ and $\bU_{2}\in\cG$, then $\alpha_{1}\,\bU_{1}+\alpha_{2}\,\bU_{2}\in\cG$, where $\alpha_{1},\,\alpha_{2}\in\left[0,1\right]$ and $\alpha_{1}+\alpha_{2}=1$.} and can equivalently be written in terms of the conserved variables as:
+\begin{equation}\label{Eq:SetOfAdmissibleStates}
+    \cG\equiv\left\{\bU\Big|D>0,\,\tau+D>\sqrt{D^{2}+S^{2}}\right\}.
+\end{equation}
+
+\subsubsection{Time-Step Derivation/CFL Condition}
+For the first-order DG method using forward-Euler time-stepping, we evolve the vector of conserved variables as:
+\begin{equation}\label{Eq:1stOrderDG}
+    \ol{\bU}^{n+1}_{i}=\ol{\bU}^{n}_{i}-\eta_{i}\left[\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i+1}\right)-\hat{\bF}\left(\ol{\bU}^{n}_{i-1},\ol{\bU}^{n}_{i}\right)\right],
+\end{equation}
+where
+\begin{equation}
+    \ol{\bU}_{i}\equiv\f{1}{\Delta x_{i}}\int_{x_{\imh}}^{x_{\iph}}\bU_{i}\,dx,
+\end{equation}
+$\eta_{i}\equiv\Delta t_{i}/\Delta x_{i}$, and $\hat{\bF}$ is the numerical flux. In this document we use the local Lax-Friedrichs flux, defined as:
+\begin{equation}\label{Eq:LLF}
+    \hat{\bF}\left(a,b\right)=\f{1}{2}\left[\bF\left(a\right)+\bF\left(b\right) - \alpha_{ab}\left(b-a\right)\right],
+\end{equation}
+where $a$ and $b$ represent the state of the fluid in two different elements, $\alpha_{ab}$ is an estimate for the wave-speed:
+\begin{equation}
+    \alpha_{ab}=\text{max}\left[\alpha\left(a\right),\alpha\left(b\right)\right],
+\end{equation}
+and $\alpha$ is the largest (in absolute value) eigenvalue of the flux-Jacobian:
+\begin{equation}
+    \alpha=\left|\left|\f{\p\bF}{\p\bU}\right|\right|.
+\end{equation}
+Using this we define the following variables:
+\begin{equation}\label{Eq:EigVals}
+    \alpha_{\iph}=\text{max}\left[\alpha\left(\ol{\bU}_{i}\right),\alpha\left(\ol{\bU}_{i+1}\right)\right],\hspace{3em} \alpha_{\imh}=\text{max}\left[\alpha\left(\ol{\bU}_{i-1}\right),\alpha\left(\ol{\bU}_{i}\right)\right].
+\end{equation}
+
+Substituting \eqref{Eq:LLF} with \eqref{Eq:EigVals} into \eqref{Eq:1stOrderDG}:
+\begin{align}
+    \ol{\bU}^{n+1}_{i}&=\ol{\bU}^{n}_{i}-\f{\eta_{i}}{2}\left[\bF\left(\ol{\bU}^{n}_{i}\right)+\bF\left(\ol{\bU}^{n}_{i+1}\right)-\alpha_{\iph}\left(\ol{\bU}^{n}_{i+1}-\ol{\bU}^{n}_{i}\right)\right.\nonumber\\
+    &\left.\hspace{7em}-\bF\left(\ol{\bU}^{n}_{i}\right)-\bF\left(\ol{\bU}^{n}_{i-1}\right)+\alpha_{\imh}\left(\ol{\bU}^{n}_{i}-\ol{\bU}^{n}_{i-1}\right)\right]\nonumber\\
+    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right]\nonumber\\
+    &\hspace{15em}+\f{\eta_{i}}{2}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]\nonumber\\
+    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\bH^{-}\left(\ol{\bU}^{n}_{i+1},\alpha_{\iph}\right)+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\bH^{+}\left(\ol{\bU}^{n}_{i-1},\alpha_{\imh}\right),\label{Eq:ConvComb}
+\end{align}
+where
+\begin{equation}\label{Eq:Hpm}
+    \bH^{\pm}\left(\ol{\bU},\alpha\right)\equiv\ol{\bU}\pm\f{1}{\alpha}\,\bF\left(\ol{\bU}\right).
+\end{equation}
+
+The proof that $\bH^{\pm}\in\cG$ is given in \citet{Qin2016}.
+Therefore, we see that with a restriction on $\alpha_{i\pm\f{1}{2}}$ that \eqref{Eq:ConvComb} is a convex combination.
+The restriction is (recalling that $\eta_{i}=\Delta t_{i}/\Delta x_{i}$):
+\begin{equation}
+    1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)>0\implies\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)<1\implies \Delta t_{i}<\f{2\,\Delta x_{i}}{\alpha_{\iph}+\alpha_{\imh}}\leq\f{\Delta x_{i}}{\text{max}\left(\alpha_{i\pm\f{1}{2}}\right)}.
+\end{equation}
+
+We want a time-step that is the same for all elements at a given time, so we tighten the restriction to:
+\begin{equation}
+    \Delta t<\text{min}_{i}\left(\f{\Delta x_{i}}{\text{max}\left(\alpha_{i\pm\f{1}{2}}\right)}\right)=\f{\Delta x}{\text{max}_{i}\left(\alpha_{i\pm\f{1}{2}}\right)},
+\end{equation}
+where the equality follows for a uniform mesh, i.e. $\Delta x_{i}=\Delta x\,\forall i$.
+
+\newpage
+
+\subsection{Curvilinear Coordinates}
+NOTE: We assume a conformally-flat, time-independent spatial three-metric.
+
+\subsubsection{Set of Admissible States}
+We again consider a one-dimensional system of conservation laws, but this time with a curvilinear metric:
+\begin{equation}
+    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF\right)}{1}=\sqrtgm\,\bQ,
+\end{equation}
+where $\bU$ is given by:
+\begin{equation}
+    \bU\longrightarrow\begin{pmatrix} D\\ S_{1}\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v_{1}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{j}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
+\end{equation}
+$\bF\left(\bU\right)$ are the fluxes of those conserved quantities:
+\begin{equation}
+    \bF\left(\bU\right)\longrightarrow\begin{pmatrix}D\,v^{1}\\ S^{1}\,v_{1}+p\,\delta^{1}_{~1}\\ S^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,v^{1}\,v_{1}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{1}\,v^{j}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix},
+\end{equation}
+and $\bQ$ is a source term:
+\begin{align}
+    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{kj}\,\p_{1}\gamma_{kj}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\p_{1}\,\gamma_{11}+P^{22}\,\p_{1}\,\gamma_{22}+P^{33}\,\p_{1}\,\gamma_{33}\right] \\0\end{pmatrix}\\
+    &=\begin{pmatrix}0\\ P^{11}\,h_{1}\,\pd{\,h_{1}}{1}+P^{22}\,h_{2}\,\pd{\,h_{2}}{1}+P^{33}\,h_{3}\,\pd{\,h_{3}}{1} \\0\end{pmatrix},
+\end{align}
+where we have used the fact that $\gamma_{jj}=\left(h_{j}\right)^{2}$. The $P^{kj}$ are components of the pressure tensor:
+\begin{equation}
+    P^{kj}=S^{k}\,v^{j}+p\,\gamma^{kj}=\gamma^{kj}\left[S_{a}\,v^{a}+p\right].
+\end{equation}
+
+These definitions lead us to define the same set of admissible states as before, namely:
+\begin{equation}
+    \cG_{p}\equiv\left\{\bU\Big|\rho>0,\,p>0,\,v^{2}<1\right\},
+\end{equation}
+the only difference being that $v^{2}$ now involves the metric:
+\begin{equation}
+    v^{2}=v^{j}\,v_{j}=\gamma_{kj}\,v^{k}\,v^{j}.
+\end{equation}
+
+Before continuing, we show that the introduction of the metric doesn't affect the translation between $\cG_{p}$ and $\cG$...\sd{Need to do this}
+
+\subsubsection{Time-Step Derivation/CFL Condition}
+We start by integrating both sides over $dx^{1}$ and dividing by the volume, $\Delta V_{i}$:
+\begin{equation}
+    \f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\pd{\left(\sqrtgm\,\bU_{i}\right)}{t}dx^{1}+\f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\pd{\left(\sqrtgm\,\bF\left(\bU_{i}\right)\right)}{1}dx^{1}=\f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\sqrtgm\,\bQ_{i}\,dx^{1},
+\end{equation}
+where:
+\begin{equation}
+    \Delta V_{i}=\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}dV=\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\sqrtgm\,dx^{1}.
+\end{equation}
+
+By defining the cell-average as:
+\begin{equation}
+    \ol{\bW}_{i}\equiv\f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\bW_{i}\,dV,
+\end{equation}
+we have:
+\begin{equation}
+    \f{d\,\ol{\bU}_{i}}{dt}+\f{1}{\Delta V_{i}}\left.\left(\sqrtgm\,\hat{\bF}\left(\ol{\bU}\right)\right)\right|^{x^{1}_{\iph}}_{x^{1}_{\imh}}=\ol{\bQ}_{i},
+\end{equation}
+or, using the common notation of the time step being represented as a superscript and the spatial element represented by a subscript:
+\begin{equation}
+    \ol{\bU}^{n+1}_{i}=\ol{\bU}^{n}_{i}-\f{\Delta t_{i}}{\Delta V_{i}}\left[\sqrtgm_{\iph}\,\hat{\bF}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\bF}^{n}_{\imh}\right]+\Delta t_{i}\,\ol{\bQ}^{n}_{i}.
+\end{equation}
+
+Now we define a parameter a la \citet{ZS2011b}: $\ve\in\left(0,1\right)$, such that (NOTE: \citet{ZS2011b} set $\ve=1/2$):
+\begin{equation}
+    \ol{\bU}^{n}_{i}=\ve\,\ol{\bU}^{n}_{i}+\left(1-\ve\right)\ol{\bU}^{n}_{i}.
+\end{equation}
+We can use the first term to balance out the term in the square brackets and the second term to balance out the source term.
+
+So, we get:
+\begin{align}
+    \ol{\bU}^{n+1}_{i}&=\ve\left\{\ol{\bU}^{n}_{i}-\f{\Delta t_{i}}{\ve\,\Delta V_{i}}\left[\sqrtgm_{\iph}\,\hat{\bF}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\bF}^{n}_{\imh}\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
+    &=\ve\left\{\ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
+    &=\ve\,\bH_{1}+\left(1-\ve\right)\bH_{2},
+\end{align}
+where
+\begin{equation}
+    \bH_{1}\equiv \ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right],
+\end{equation}
+\begin{equation}
+    \bH_{2}\equiv\ol{\bU}^{n}_{i}+\f{\Delta t_{i}}{1-\ve}\,\ol{\bQ}^{n}_{i},
+\end{equation}
+and
+\begin{equation}
+    \eta_{i}\equiv\f{\Delta t_{i}}{\ve\,\Delta V_{i}}.
+\end{equation}
+
+We proceed by focusing on each term individually, starting with the numerical flux term, $\bH_{1}$.
+
+\subsubsection{Numerical flux term}
+We have to show that $\bH_{1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\bH_{1}$:
+\begin{align}
+    \ol{\bU}^{n}_{i}-\f{\eta_{i}}{2}\Big\{&\sqrtgm_{\iph}\left[\bF\left(\ol{\bU}^{n}_{i+1}\right)+\bF\left(\ol{\bU}^{n}_{i}\right)-\alpha_{\iph}\left(\ol{\bU}^{n}_{i+1}-\ol{\bU}^{n}_{i}\right)\right]\\
+    &-\sqrtgm_{\imh}\left[\bF\left(\ol{\bU}^{n}_{i}\right)+\bF\left(\ol{\bU}^{n}_{i-1}\right)-\alpha_{\imh}\left(\ol{\bU}^{n}_{i}-\ol{\bU}^{n}_{i-1}\right)\right]\Big\}\\
+    &\hspace{-10em}=\left(1-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
+    &\hspace{-8em}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\bF\left(\ol{\bU}^{n}_{i}\right)+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\bF\left(\ol{\bU}^{n}_{i}\right)\\
+    &\hspace{-8em}+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
+\end{align}
+Now we add and subtract $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\,\ol{\bU}^{n}_{i}$ and $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\,\ol{\bU}^{n}_{i}$, yielding:
+\begin{align}
+    &\left(1-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
+    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]\\
+    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
+\end{align}
+All of the terms in square brackets are similar to the $\bH$ quantities in \citet{Qin2016}, and are therefore in $\cG$.
+It can easily be seen that the sum of the coefficients is unity.
+The final condition is that the coefficient of $\ol{\bU}^{n}_{i}>0$, or (recalling that $\eta_{i}=\Delta t_{i}/\left(\ve\,\Delta V_{i}\right)$):
+\begin{align}
+    1&-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}>0\implies\eta_{i}\left(\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}\right)<1\\
+    &\implies\Delta t_{i}<\f{\ve\,\Delta V_{i}}{\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}}\leq\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}.
+\end{align}
+Again we want a time-step that is the same for all elements at a given time, so:
+\begin{equation}
+    \Delta t<\text{min}_{i}\left(\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right).
+\end{equation}
+
+We close the numerical flux section by writing the explicit form of the time-step for spherical-polar coordinates.
+
+\subsubsubsection{Time-step for Spherical-Polar Coordinates}
+For spherical-polar coordinates in 1-D we have that $\Delta V_{i}=1/3\left(r_{\iph}^{3}-r_{\imh}^{3}\right)$, and (assuming $\alpha_{i\pm\f{1}{2}}=1\ \forall\ i$) $\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)=r_{\iph}^{2}$, so:
+\begin{align}
+    \Delta t&<\text{min}_{i}\left\{\f{\ve\,1/3\left[r_{\iph}^{3}-r_{\imh}^{3}\right]}{2\,r_{\iph}^{2}}\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[1-\f{r_{\imh}^{3}}{r_{\iph}^{3}}\right]\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[1-\left(1-\f{\Delta r_{i}}{r_{\iph}}\right)^{3}\right]\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[1-\left(1+\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{2}-2\frac{\Delta r_{i}}{r_{\iph}}\right)\left(1-\f{\Delta r_{i}}{r_{\iph}}\right)\right]\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{3}-3\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{2}+3\f{\Delta r_{i}}{r_{\iph}}\right]\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,\Delta r_{i}\left[\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{2}-3\left(\f{\Delta r_{i}}{r_{\iph}}\right)+3\right]\right\}.
+\end{align}
+We know that $\Delta r_{i}/r_{\iph}\in\left[0,1\right]$; the minimum value of the quadratic function in this domain is unity. So, we have that for spherical-polar coordinates:
+\begin{equation}
+\Delta t<\f{\ve}{6}\,\text{min}\left(\Delta r_{i}\right).
+\end{equation}
+
+Next we handle the source term.
+
+\subsubsection{Source term}
+For this section we drop the subscript $i$ and the superscript $n$. We have to show that $\bH_{2}\in\cG$, where
+\begin{equation}
+    \bH_{2}=\begin{pmatrix}\ol{D}\\ \ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}} \\ \ol{\tau}\end{pmatrix},\hspace{1em}\left(H_{2}\right)_{1}>0,\hspace{1em}\left(H_{2}\right)_{3}+\left(H_{2}\right)_{1}>\sqrt{\left(H_{2}\right)_{1}\left(H_{2}\right)_{1}+\left(H_{2}\right)_{2}\left(H_{2}\right)^{2}}.
+\end{equation}
+
+It is clear that the first requirement for $\bH_{2}$ is met, i.e. $\ol{D}>0$. The second requirement is:
+\begin{align}
+\ol{D}+\ol{\tau}&>\sqrt{\ol{D}^{2}+\left[\ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] \left[\ol{S}^{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\p^{1}\,\gamma_{kk}}\right] }\\
+&=\sqrt{\ol{D}^{2}+\left[\ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] \left[\ol{S}^{1}+\gamma^{11}\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}\right] }\\
+&=\sqrt{\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}+\gamma^{11}\left[\f{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}{2\left(1-\ve\right)}\right]^{2}\left(\Delta t\right)^{2}+\f{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}{2\left(1-\ve\right)}\left[\ol{S}_{1}\,\gamma^{11}+\ol{S}^{1}\right]\Delta t}\\
+&=\sqrt{a\left(\Delta t\right)^{2}+b\,\Delta t+c}\geq0,
+\end{align}
+where
+\begin{align}
+    a&=\left[\f{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}{2\,\sqrt{\ol{\gamma_{11}}}\left(1-\ve\right)}\right]^{2}\geq0\\
+    b&=\f{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}{\ol{\gamma_{11}}\left(1-\ve\right)}\ol{S}_{1}=\f{2\,\ol{S}_{1}}{\sqrt{\ol{\gamma_{11}}}}\sqrt{a}\\
+    c&=\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}\geq0.
+\end{align}
+The condition for a quadratic function to be positive-definite is that $a>0$ (concave-up) and $b^{2}-4\,a\,c<0$ (no real roots). The first condition is clearly met. For the second condition:
+\begin{equation}
+    \f{4\left(\ol{S}_{1}\right)^{2}}{\ol{\gamma_{11}}}a-4\,a\left(\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}\right)=4\,\ol{S}_{1}\,\ol{S}^{1}\,a-4\,a\ol{D}^{2}-4\,a\,\ol{S}_{1}\,\ol{S}^{1}=-4\,a\,\ol{D}^{2}<0.
+\end{equation}
+So, the square root is always positive.
+
+With that we have:
+\begin{align}
+    &\ol{D}^{2}+\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}>a\left(\Delta t\right)^{2}+b\,\Delta t+c\\
+    &\implies a\left(\Delta t\right)^{2}+b\,\Delta t+c'<0,
+\end{align}
+where:
+\begin{equation}
+  c'=c-\ol{D}^{2}-\ol{\tau}^{2}-2\,\ol{D}\,\ol{\tau}=\ol{S}_{1}\,\ol{S}^{1}-\ol{\tau}^{2}-2\,\ol{D}\,\ol{\tau}.
+\end{equation}
+
+The solutions of this quadratic equation are:
+\begin{align}
+    \Delta t&=\f{-b}{2\,a}\pm\f{1}{2\,a}\sqrt{b^{2}-4\,a\,c'}=\f{-\ol{S}_{1}}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\pm\f{1}{2\,a}\sqrt{\f{4\ol{S}_{1}^{2}}{\ol{\gamma_{11}}}a-4\,a\,c'}\\
+    &=\f{-\ol{S}_{1}}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\pm\f{1}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\sqrt{\ol{S}_{1}^{2}-c'\,\ol{\gamma_{11}}}=\f{1}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\left[-\ol{S}_{1}\pm\sqrt{\ol{S}_{1}^{2}-c'\,\ol{\gamma_{11}}}\right]\\
+    &=\f{1}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\left(\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}\right)}\right]\\
+    &=\f{2\left(1-\ve\right)}{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\left(\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}\right)}\right].
+\end{align}
+We see that we must have that $\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}>0\implies\ol{\tau}>-2\,\ol{D}$.
+But, since we know that from the second condition of $\bH_{2}$ that $\ol{\tau}>-\ol{D}$, this requirement is met.
+
+\newpage
+\section{Recovery of Primitive Variables}
+In order to recover the primitive from the conserved variables we need to solve the nonlinear equation:
+\begin{equation}
+    f\left(p\right)=p-\ol{p}\left(p\right)=0,
+\end{equation}
+where $\ol{p}\left(p\right)$ is the pressure as obtained via the ideal gas equation of state with an initial guess, $p$:
+\begin{equation}
+    \ol{p}=\left(\Gamma-1\right)\rho\,\epsilon,
+\end{equation}
+where
+\begin{equation}
+    \rho=\rho\left(\bU,p\right),\hspace{1em}\epsilon=\epsilon\left(\bU,p\right).
+\end{equation}
+
+In order to solve this equation we make use of the bisection method, and therefore need bounds on our initial guess for the pressure.
+
+\subsection{Upper and Lower Bounds for Pressure}
+We obtain a lower bound for the pressure with:
+\begin{equation}
+\tau=D\left(h\,W-1\right)-p\implies p=-\left(\tau+D\right)+D\,h\,W\geq-\left(\tau+D\right)+D\,h\,W\,\sqrt{v^{i}\,v_{i}}=-\left(\tau+D\right)+\sqrt{S^{i}\,S_{i}}.
+\end{equation}
+So, since the pressure must be non-negative, we have:
+\begin{equation}
+p\geq\text{MAX}\left[-\left(\tau+D\right)+\sqrt{S^{i}\,S_{i}},\text{SqrtTiny}\right].
+\end{equation}
+
+For an upper bound, we first note that:
+\begin{equation}
+h=1+\f{e+p}{\rho}=1+\f{\Gamma}{\Gamma-1}\f{p}{\rho}=1+\f{\Gamma}{\Gamma-1}\,\f{p\,W}{D},
+\end{equation}
+so,
+\begin{equation}
+\tau=D\left(W+\f{\Gamma}{\Gamma-1}\f{p\,W^{2}}{D}-1\right)-p=D\left(W-1\right)+p\left(\f{\Gamma}{\Gamma-1}W^{2}-1\right).
+\end{equation}
+So,
+\begin{equation}
+p=\f{\tau-D\left(W-1\right)}{\f{\Gamma}{\Gamma-1}W^{2}-1}.
+\end{equation}
+We also have:
+\begin{equation}
+W=\left(1-v^{i}\,v_{i}\right)^{-1/2}=\left(1-\f{S^{i}\,S_{i}}{\left(\tau+D+p\right)^{2}}\right)^{-1/2}.
+\end{equation}
+Treating $p$ as an independent variable \sd{is this valid?}, we have:
+\begin{equation}
+W\Big|_{p\rightarrow\infty}=1,
+\end{equation}
+which gives us an upper limit:
+\begin{equation}
+p\leq\f{\Gamma-1}{\Gamma}\,\tau.
+\end{equation}
+Just to be safe, in the code we multiply this by two, so that:
+\begin{equation}
+p\leq2\,\f{\Gamma-1}{\Gamma}\,\tau.
+\end{equation}
+
+\newpage
 

### 2018-09-24 Documents/Euler/dgEulerGR.tex
Changed style slightly and updated references and definitions files

@@
 \begin{equation}
-    \alpha=\left|\left|\f{\p\bF}{\p\bU}\right|\right|.
+    \alpha=\left|\left|\pderiv{\bF}{\bU}\right|\right|.
 \end{equation}
@@
 \begin{align}
-    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{kj}\,\p_{1}\gamma_{kj}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\p_{1}\,\gamma_{11}+P^{22}\,\p_{1}\,\gamma_{22}+P^{33}\,\p_{1}\,\gamma_{33}\right] \\0\end{pmatrix}\\
+    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{kj}\,\pd{\gamma_{kj}}{1}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\pd{\gamma_{11}}{1}+P^{22}\,\pd{\gamma_{22}}{1}+P^{33}\,\pd{\gamma_{33}}{1}\right] \\0\end{pmatrix}\\
     &=\begin{pmatrix}0\\ P^{11}\,h_{1}\,\pd{\,h_{1}}{1}+P^{22}\,h_{2}\,\pd{\,h_{2}}{1}+P^{33}\,h_{3}\,\pd{\,h_{3}}{1} \\0\end{pmatrix},
@@
 \ol{D}+\ol{\tau}&>\sqrt{\ol{D}^{2}+\left[\ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] \left[\ol{S}^{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\p^{1}\,\gamma_{kk}}\right] }\\
-&=\sqrt{\ol{D}^{2}+\left[\ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] \left[\ol{S}^{1}+\gamma^{11}\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}\right] }\\
-&=\sqrt{\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}+\gamma^{11}\left[\f{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}{2\left(1-\ve\right)}\right]^{2}\left(\Delta t\right)^{2}+\f{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}{2\left(1-\ve\right)}\left[\ol{S}_{1}\,\gamma^{11}+\ol{S}^{1}\right]\Delta t}\\
+&=\sqrt{\ol{D}^{2}+\left[\ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] \left[\ol{S}^{1}+\gamma^{11}\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] }\\
+&=\sqrt{\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}+\gamma^{11}\left[\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{2\left(1-\ve\right)}\right]^{2}\left(\Delta t\right)^{2}+\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{2\left(1-\ve\right)}\left[\ol{S}_{1}\,\gamma^{11}+\ol{S}^{1}\right]\Delta t}\\
 &=\sqrt{a\left(\Delta t\right)^{2}+b\,\Delta t+c}\geq0,
@@
 \begin{align}
-    a&=\left[\f{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}{2\,\sqrt{\ol{\gamma_{11}}}\left(1-\ve\right)}\right]^{2}\geq0\\
-    b&=\f{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}{\ol{\gamma_{11}}\left(1-\ve\right)}\ol{S}_{1}=\f{2\,\ol{S}_{1}}{\sqrt{\ol{\gamma_{11}}}}\sqrt{a}\\
+    a&=\left[\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{2\,\sqrt{\ol{\gamma_{11}}}\left(1-\ve\right)}\right]^{2}\geq0\\
+    b&=\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{\ol{\gamma_{11}}\left(1-\ve\right)}\ol{S}_{1}=\f{2\,\ol{S}_{1}}{\sqrt{\ol{\gamma_{11}}}}\sqrt{a}\\
     c&=\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}\geq0.

### 2018-09-25 Documents/M1/Astronum_2018/manuscript.tex
Updated the figures.
Updated introduction section and backup.

@@
 \begin{document}
-\title{Constraint-Preserving IMEX Scheme for the Two-Moment Model of Fermion Transport}
+\title{\texttt{thornado}-transport: a realizability-preserving IMEX scheme for two-moment neutrino transport}
 
@@
 
+\author{Bronson Messer}
+\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
+\address{Scientific Computing and Theoretical Physics Groups, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
+%\address{Physics Division, Oak Ridge National Laboratory, P.O. Box 2008, Oak Ridge, TN 37831-6354, USA}
+\ead{bronson@ornl.gov}
+
 \begin{abstract}
@@
 \input{sections/Numerical}
+\input{sections/Conclusion}
 

### 2018-09-25 Documents/M1/Astronum_2018/sections/Numerical.tex
Updated introduction section and backup.

@@
-\section{Numerical Tests}
+\section{Numerical Tests}\label{se:NumericalTests}
+
 In this section we present the numerical results obtained with the PD-ARS schemes provided in this paper.
@@
 The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the realizability-preserving of PD-ARSs scheme.
+All the tests in this subsection were applied with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $.
 \subsection{Accuracy Tests}
@@
 To compare the accuracy of the IMEX scheme, we applied our PDARSs and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
-All the tests in this subsection were applied with third order accurate spatial discretization, the maximum entropy closure in the low occupancy limit and time step $\dt = 0.1 \times \dx $.
+All the tests in this subsection were applied with the maximum entropy closure in the low occupancy limit.
 In the streaming test, the second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} , (SSPRK2 and SSPRK3, respectively) are also applied to serve as an reference.
@@
 
-\subsection{Neutrino Stationary State Test}
-Next we consider a two dimension test with
+\subsection{Neutrino Stationary State Test} \label{se: Neutrino Stationary State Test}
+Next we consider a more realistic-like test: two-dimensional neutrino transport with emission, absorption and elastic scattering under a stationary realistic-like background.
+This test is designed to test the realizability-preserving properties of the PD-ARSs schemes.
+Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities we used.
+This test is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements on each direction.
+We take 10 energy groups vary from 0~MeV to 300~MeV and initial the neutrino number density $\cJ$ and flux density $\bcH$ both zero(arbitrary small).
+For realizability-preserving test, CB closure with PD-ARSs schemes, SSP2332, scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015} and scheme proposed by McClarren et al.
+\cite{mcclarren_etal_2008} are all applied.
+Only PD-ARSs schemes produces realizability-preserving result and evolve the model to a stable state.
+The realizability-preserving plot and the evolve process of PD-ARSs are given in Figure~\ref{fig:NeutrinoStationaryTestEvolve}.
 
-\label{se: Neutrino Stationary State Test}
 \begin{figure}[h]
@@
   \end{tabular}
-   \caption{Equation of state plot (left) and neutrino capture opacity (EC) and neutrino elastic scattering opacity (ES) in space (right) for the neutrino stationary state test.}
+   \caption{Thermal state plot (left) and neutrino absorptivity ($\chi$) and neutrino elastic scattering opacity ($\sigma$) in space (right) for the neutrino stationary state test.}
    \label{fig:NeutrinoStationaryTestEOS}
@@
     \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
-   \caption{Readability plots (left column), the number density $\cJ$ versus radius plots (center column) and the flux factor $|\bcH|/\cJ$ versus radius plots (right column) at $t = 0.01$ms ,$0.35$ms and $5.0$ms for the neutrino stationary state test.}
+   \caption{Readability plots (left column), the number density $\cJ$ versus radius plots (center column) and the flux factor $|\bcH|/\cJ$ versus radius plots (right column) at t = 0.01~ms ,0.35~ms and 5.0~ms for the neutrino stationary state test.
+For the realizability plots, the light blue area demonstrate the realizability domain and the black lines define its boundary.
+Each $\bcM=(\cJ,\bcH)^{T}$ state is marked by a red dot.
+The results of PD-ARS with SSPRK2 and PD-ARS with SSPRK3 are indistinguishable in these plot.}
       \label{fig:NeutrinoStationaryTestEvolve}

### 2018-09-25 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Backup Astronum2018.
Updated introduction section and backup.

@@
-\section{Spacial Discretization}
+\section{Spacial Discretization}\label{se:SpacialDiscretization}
+
 Divide the spatial domain $D$ into $N$ cells and denote the cell as $I_{i}$ with $i = 1,\ldots,N$, so that
@@
 where $\eta := \dfrac{\dt}{\dx}$. The first three terms can form a 3-term convex combination by requiring $\eta \in [0,1]$.
-It can be shown that $\bcM_{i}^{n+1}$ remains realizable given $\bcM_{i}^{n}$ is realizable, $\eta \in [0,1]$ and $\cC(\bcM)$ is positivity-preserving. The proof can be found in \cite{Chu_2018}.
+It can be shown that $\bcM_{i}^{n+1}$ remains realizable given $\bcM_{i}^{n}$ is realizable, $\eta \in [0,1]$ and $\cC(\bcM)$ is positivity-preserving. The proof can be found in \cite{c
+chu_2018}.

### 2018-09-25 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Backup Astronum2018.
Updated introduction section and backup.

@@
-\section{Time Integration}
+\section{Time Integration} \label{se:TimeIntegration}
+
 In this section we show how to use the property we introduced at the end of the previous section to construct a constraint-preserving implicit-explicit (IMEX) scheme.
@@
 \end{equation}
-It can be proved \cite{Chu_2018} that the conditions we need for constraint-preserving IMEX is:
+It can be proved \cite{chu_2018} that the conditions we need for constraint-preserving IMEX is:
 \begin{enumerate}

### 2018-09-25 Documents/M1/Astronum_2018/sections/intro.tex
Updated introduction section and backup.

\section{Introduction}

Core-collapse supernovae (CCSNe) are the explosion happens at the end of a massive star's life.
They are the source of heavy elements and play an important role in many astrophysical phenomena, such as neutron star and black hole formation.
Furthermore, these explosions combines extreme energetic and densities with nuclear, particle and relativistic physics. 
A solid theoretical framework for these explosion mechanism will illuminate explanations to many import questions in fundamental physics.

One essential part of the explosion mechanism is neutrino transport which drives the explosion.
Neutrino transport is modeled by Boltzmann transport equation, which is partial differential equation and evolves the distribution function $f$.
Simulating the neutrino transport is finding a solution of Boltzmann transport equation for a given domain and period with an acceptable accuracy.

Solving Boltzmann transport multi-dimensional with high accuracy requirement can be expensive.
One alternation is sacrificing the accuracy: instead of solving Boltzmann transport equations, solve moment equation for an approximate solution.
This kind method is moment method and we focus on two-moment method in this paper.

Applying two-moment method only is not sufficient to have an affordable solution when the simulating period is long.
To be precisely, neutrino interact with the background rapidly and its characteristic time scalar is so small comparing to the length of CCSNe explosion process. 
It makes the time step needed by an explicit time integrator dramatic large and a huge mount of calculation needed. 
To manipulate this challenge, implicit-explicit (IMEX) methods are taken into consideration.
By taking advantage of the fact that collision terms are local, IMEX methods are able to make the time integrator more efficient in diffusion dominate region.

However, price needs to be paid for the lunch.
Two-moment method requires a realizability-preserving algebraic closure for fermion.
IMEX methods should be diffusion limit accurate. 
The discussion of these prices drives this paper.

This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closure and the realizability-preserving property of algebraic closure;
Section~\ref{se:SpacialDiscretization} gives more information of the spacial discretization; Section~\ref{se:TimeIntegration} discusses how to construct a constraint-preserving, diffusion limit accurate IMEX (PD-ARS) scheme and two PD-ARS schemes are presented; Section~\ref{se:NumericalTests} gives the result of the numerical tests of the PD-ARSs; Section~\ref{se:Conclusion} is the conclusion section.

### 2018-09-26 Documents/M1/ornlReport/endeve_etal_2017_ORNL_TM_501.tex
ornl report on transport

--- 2017-07-25 Documents/M1/dgM1Curvilinear.tex
@@
-\documentclass[10pt,preprint]{aastex}
+\documentclass[11pt,letterpaper,twoside,english,final]{article}
 
@@
 \usepackage{mathrsfs}
-\usepackage{cite}
-\usepackage{times}
-\usepackage{url}
-\usepackage{hyperref}
-\usepackage{lineno}
-\usepackage{yhmath}
-\usepackage{natbib}
-\usepackage{../definitions}
-\hypersetup{
-  bookmarksnumbered = true,
-  bookmarksopen=false,
-  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
-  pdffitwindow=true,      % window fit to page when opened
-  pdfnewwindow=true, % links in new window
-  colorlinks=true,           % false: boxed links; true: colored links
-  linkcolor=blue,            % color of internal links
-  citecolor=magenta,    % color of links to bibliography
-  filecolor=magenta,     % color of file links
-  urlcolor=cyan              % color of external links
+\usepackage{definitions}
+
+\newcommand{\NES}{\mbox{\tiny NES}}
+\newcommand{\dx}{\Delta x}
+\newcommand{\sumx}{\sum_{i=1}^{d}}
+\newcommand{\thornado}{\texttt{thornado}}
+
+\input{ornlmacro}
+
+\begin{document}
+
+%\bibliographystyle{plain} 
+\begin{titlepage}
+
+%NOTICE about prelim document
+%delete NOTICE when document become final
+%\vspace{-1.75in}
+%\hspace{-1in}
+%\par
+%\footnotesize
+%\vspace{-.8in} 
+%  \fbox{
+%  \begin{minipage}{0.55\textwidth}
+%   \raggedright
+% \textsf{\textbf{NOTICE: This document contains information of a preliminary nature and is not intended for release.
+It is subject to revision or correction and therefore does not represent a final report.}}
+%  \end{minipage}
+%  }
+
+\URCornerWallPaper{1.0}{Graybar.png}
+\ThisURCornerWallPaper{1.0}{Graybar.png} 
+\ClearWallPaper
+
+\begin{flushright}{\textsf{\bfseries{\large{ORNL/TM-2017/501}}}}\\ 
+\end{flushright}
+
+\vspace{.15in}
+
+\noindent
+\begin{shaded}
+\Huge{\textsf{\bfseries\color{white}{TOWARDS A DISCONTINUOUS GALERKIN METHOD FOR THE MULTI-GROUP TWO-MOMENT MODEL OF NEUTRINO TRANSPORT}}}
+\end{shaded}
+
+\begin{figure}[H]
+\flushright
+\includegraphics[width=4.88in, height=3.47in]{Officiallogo.png} 
+\end{figure}
+
+\def\author#1{\large{\textsf{#1}}\\ }
+
+\def\date#1{{\vspace{.25 in}
+
+\large{\bfseries{\textsf{#1}}}\\ }}
+
+\def\authordate#1{
+
+\noindent
+\vskip 6.8pt
+\vtop to0pt{
+\setlength{\parindent}{112mm}
+
+#1\vss}}
+
+\authordate{
+\author{Eirik Endeve}
+\author{Ran Chu}
+\author{Anthony Mezzacappa}
+\author{Bronson Messer}
+\date{\today}}
+
+% delete NOTICE when document become final
+%\DraftBox                    % command for Draft. Not for public release.
+%\NotPublic                % command for Not for public release.
+\ApprovedBox             % command for Approved for public release.
+%\BusSenBox                 % command for Business Sensitive.
+%\OUOBox                    % command for Official Use Only. To add item, open ORNLmacro.tex, make change, and save
+%\ECIBox                      % command for Export Controlled Information
+%\OUOECIBox               % command for OUO and ECI
+%\OUOATBox                % command for Official Use Only and Applied Technology
+%\OUOECIATBox           % command for Official Use Only, Export Controlled Information, and Applied Technology
+%\UCNIBox                   % command for Unclassified Controlled Nuclear Information
+%\CRADABox                % command for CRADA final.
+
+\setlength{\parindent}{0pt}
+
+\bigskip
+\noindent
+
+\thispagestyle{fancy}
+\fancyfoot{}
+\fancyfoot[L]{\includegraphics[width=3.72in]{textlogo.png}}
+\renewcommand{\headrulewidth}{0pt}
+\addtolength{\footskip}{0.3in}
+
+\end{titlepage}
+
+\newpage
+
+ \newpage
+
+\thispagestyle{empty}                           % Hide when using other pagestyles (Not for public release, OUO, etc.)
+%\thispagestyle{mypagestylepublic}        % Use for "Not for public release." in footer with no page numbers
+%\thispagestyle{mypagestyleempty}    % Use for "OUO" in footer with no page numbers 
+\vspace*{\fill}
+
+  \par
+
+  \par
+  \begin{center}
+    \fbox{
+      \parbox{5.61in}{
+        \small
+        \begin{center}
+
+         {\bf\textsf{ DOCUMENT AVAILABILITY}}
+        \end{center}
+    \textsf{Reports produced after January 1, 1996, are generally available free via US Department of Energy (DOE) SciTech Connect. }
+          \\
+          ~
+
+          \hspace{0.5in}{\textsf{\textbf{\emph{ Website:}}}} \textsf{\url{ http://www.osti.gov/scitech/ }}
+          \\
+          ~
+          \\
+            \textsf{Reports produced before January 1, 1996, may be purchased by members of the public from the following source:}
+          \\  
+          ~
+
+          \hspace{0.5in}   \textsf{National Technical Information Service }
+
+          \hspace{0.5in}   \textsf{5285 Port Royal Road }
+
+          \hspace{0.5in}   \textsf{Springfield, VA 22161 }
+
+          \hspace{0.5in} {\textsf{\textbf{\emph{Telephone:}}}}   \textsf{703-605-6000  (1-800-553-6847) }
+
+          \hspace{0.5in} {\textsf{\textbf{\emph{TDD:}}}}   \textsf{703-487-4639 }
+
+          \hspace{0.5in} {\textsf{\textbf{\emph{Fax:}}}}   \textsf{703-605-6900 }
+
+          \hspace{0.5in} {\textsf{\textbf{\emph{E-mail:}}}}   \textsf{\href{mailto:info@ntis.gov}{info@ntis.gov}}
+
+          \hspace{0.5in} {\textsf{\textbf{\emph{Website:}}}}   \textsf{\url{http://classic.ntis.gov/}} 
+          \\
+          ~
+          \\
+          \textsf{Reports are available to DOE employees, DOE contractors, Energy Technology Data Exchange representatives, and International Nuclear Information System representatives from the following source: }
+          \\
+          ~
+
+          \hspace{0.5in}\textsf{Office of Scientific and Technical Information}
+
+          \hspace{0.5in}\textsf{PO Box 62}
+
+          \hspace{0.5in}\textsf{Oak Ridge, TN  37831}
+
+          \hspace{0.5in}{\textsf{\textbf{\emph{Telephone:}}}}\textsf{ 865-576-8401}
+
+          \hspace{0.5in}{\textsf{\textbf{\emph{Fax:}}}}\textsf{ 865-576-5728}
+
+          \hspace{0.5in}{\textsf{\textbf{\emph{E-mail:}}}} \textsf{\href{mailto:reports@osti.gov}{report@osti.gov}}
+
+          \hspace{0.5in}{\textsf{\textbf{\emph{Website:}}}} \textsf{\url{http://www.osti.gov/contact.html}}
+
          }
-
-\newcommand{\ee}[1]{{\color{red} #1}}
-\newcommand{\dx}{\Delta x}
-\newcommand{\pbK}{\partial\mathbf{K}}
-\newcommand{\UDG}{\bU_{\mbox{\tiny DG}}}
-\newcommand{\sumx}{\sum_{i=1}^{d}}
-\newcommand{\NES}{\mbox{\tiny NES}}
-
-\begin{document}
-
-\title{Nodal Discontinuous Galerkin Method for the Two-Moment Model of Neutrino Transport}
-\author{Eirik Endeve\altaffilmark{1}, et al.}
-\altaffiltext{1}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
-
-\begin{abstract}
-We present a nodal Discontinuous Galerkin (DG) method for solving the non-relativistic two-moment model for neutrino transport.  
-The method --- ultimately targeted for simulations of core-collapse supernovae --- includes the use of curvilinear coordinates and non-ideal microphysics (nuclear equation of state and weak interactions) for neutrino-matter interactions.
-\end{abstract}
-
+      }
+  \end{center}
+  \par
+  \vspace{0.1in}
+  \par
+  \begin{center}
+   \small
+    \fbox{\parbox{4in}{
+
+       \textsf{This report was prepared as an account of work sponsored by an agency of the United States Government.
+Neither the United States Government nor any agency thereof, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights.
+Reference herein to any specific commercial product, process, or service by trade name, trademark, manufacturer, or otherwise, does not necessarily constitute or imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof.
+The views and opinions of authors expressed herein do not necessarily state or reflect those of the United States Government or any agency thereof.
+}}}
+
+  \end{center}
+
+\vspace*{\fill}
+
+\newpage
+
+\begin{titlepage}
+%\thispagestyle{mypagestylepublic}        % Use for "Not for public release." in footer with no page numbers
+%\thispagestyle{mypagestyleempty}    % Use for "OUO" in footer with no page numbers
+
+\begin{flushright}{\textsf{\bfseries{\large{ORNL/TM-2017/501}}}}\\ 
+\end{flushright}
+
+\vspace{0.5in}
+
+\begin{center}
+Computer Science and Mathematics Division
+\end{center}
+
+\vspace{1.25in}
+
+\begin{center}
+{\bf{\large{TOWARDS A DISCONTINUOUS GALERKIN METHOD FOR THE MULTI-GROUP TWO-MOMENT MODEL OF NEUTRINO TRANSPORT}}}\\
+\vspace{0.5in}
+
+Eirik Endeve, Ran Chu, Anthony Mezzacappa, Bronson Messer
+
+\vspace{1.35in}
+
+Date Published: January 2018
+
+\vspace{1.35in}
+
+Prepared by \\
+OAK RIDGE NATIONAL LABORATORY \\
+Oak Ridge, TN 37831-6283 \\
+managed by \\
+UT-Battelle, LLC \\
+for the \\
+US DEPARTMENT OF ENERGY \\
+under contract DE-AC05-00OR22725
+
+\end{center}
+
+\end{titlepage}
+
+\clearemptydoublepage 
+\begin{centering}
 \tableofcontents 
-
-\section{Introduction}
-
-We will use inits in which the speed of light is unity ($c=1$).
-
-\section{Two-Moment Model for Neutrino Transport}
+\end{centering}
+
+%\pagestyle{mypagestylepublicpage}      % Use for "Not for public release." in footer with page numbers
+%\thispagestyle{mypagestyle}                  % Use for "OUO" in footer with page numbers
+
+\pagenumbering{roman}
+
+\setcounter{page}{3}
+
+\newpage
+
+\clearemptydoublepage
+\phantomsection 
+\begin{centering}
+\listoffigures 
+\end{centering}
+
+\addcontentsline{toc}{section}{LIST OF FIGURES}
+
+\newpage
+
+\clearemptydoublepage
+\phantomsection 
+\begin{centering}
+\listoftables 
+\end{centering}
+
+\addcontentsline{toc}{section}{LIST OF TABLES}
+
+\newpage
+
+%\pagestyle{mypagestylepublicpage}      % Use for "Not for public release." in footer with page numbers
+%\thispagestyle{mypagestyle}                  % Use for "OUO" in footer with page numbers
+
+\clearemptydoublepage
+\phantomsection
+\addcontentsline{toc}{section}{ACRONYMS} 
+\begin{center}
+{\bf{ACRONYMS}}
+\end{center}
+
+\begin{table}[h]
+\vspace{-6pt}
+\begin{tabular}{l l} 
+ORNL & Oak Ridge National Laboratory \\
+CCSN & Core-Collapse Supernova \\
+PNS & Proto-Neutron Star \\
+NES & Neutrino-Electron Scattering \\
+SI & Semi-Implicit \\
+IMEX & Implicit-Explicit \\
+SIRK & Semi-Implicit Runge-Kutta \\
+DG & Discontinuous Galerkin \\
+LF & Lax-Friedrichs \\
+HLL & Harten-Lax-van Leer \\
+PDE & Partial Differential Equation \\
+ODE & Ordinary Differential Equation \\
+CFL & Courant-Friedrichs-Lewy \\
+RP & Realizability-Preserving \\
+SSP-RK & Strong Stability-Preserving Runge-Kutta \\
+\end{tabular}
+\end{table}
+
+\newpage
+
+\clearemptydoublepage
+\phantomsection
+\addcontentsline{toc}{section}{ADDITIONAL FRONT MATERIAL}
+\begin{center}
+{\bf{ADDITIONAL FRONT MATERIAL}}
+\end{center}
+
+%Material after the Contents, List of Figures, List of Tables, and the Acronym list may include any or all of the following sections and should begin on an odd-numbered page in the order listed below:
+%
+%\noindent{FOREWORD {\color{blue}{\emph {[Note: Spelling is not ``FORWARD.'']}}}\\
+%\noindent{PREFACE}\\
+
+\noindent{ACKNOWLEDGMENTS}\\
+
+This research used resources of the Oak Ridge Leadership Computing Facility, which is a DOE Office of Science User Facility supported under Contract DE-AC05-00OR22725.  
+This research was supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of the U.S.
+Department of Energy Office of Science and the National Nuclear Security Administration.
+A portion of this research used resources at the Joint Institute for Computational Sciences (JICS), a DOE Office of Science User Facility operated by the Oak Ridge National Laboratory.
+
+thornado{\_}mini uses equation of state and opacity tables and subroutines developed under the WeakLib project.  
+We acknowledge the contributions to WeakLib of W.~Raphael Hix, Ryan Landfield, and Eric J. Lentz.
+
+%\noindent{EXECUTIVE SUMMARY OR SUMMARY}\\
+%\noindent{ABSTRACT}
+%
+%Each section of the front material begins on an odd-numbered page. The abstract, if very brief, may begin on page 1 inserted above the introduction section.
+%
+%\def\thefootnote{\fnsymbol{ctr}} 
+%\long\def\symbolfootnote[#1]#2{\begingroup
+%\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}
+%
+%\bigskip
+%\phantomsection
+%\addcontentsline{toc}{section}{GENERAL INFORMATION}
+%\begin{center}
+%{\bf{GENERAL INFORMATION}}
+%\end{center}
+%
+%Document margins are 1 in. all around.
+%
+%Text footnotes are 9 pt., TNR with no space between notes.\symbolfootnote[1]{Footnotes are 9pt., TNR with no space between notes.
+Footnotes are 9 pt., TNR with no space between notes.} Footnote indicators in text are superscript symbols and should appear in the following order: $\ast$, $\dagger$, $\ddagger$, $\S$, $\ast\ast$, $\dagger\dagger$, $\ddagger\ddagger$.
+Symbols {\underline {are not}} used as table footnote indicators (see page 4).
+%
+%Footnotes may be used in addition to the author-date citation method, in which case, the footnotes provide additional information to the text, not bibliographic citations.
+
+\newpage
+
+\clearemptydoublepage
+
+\pagenumbering{arabic}
+
+\setcounter{page}{1}
+
+\phantomsection
+\addcontentsline{toc}{section}{ABSTRACT}
+\begin{center}
+{\bf{ABSTRACT}}
+\end{center}
+
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
+We present progress on the development of a Discontinuous Galerkin (DG) method for solving the non-relativistic, multi-group two-moment model for neutrino transport.  
+The method --- ultimately targeted at simulation of neutrino transport in core-collapse supernovae --- includes the use of curvilinear coordinates and tabulated microphysics (i.e., nuclear equation of state and weak interaction rates) to model neutrino-matter coupling.
+In this report, we provide algorithm details and present results from an extensive set of benchmark problems in one spatial dimension. 
+The algorithms have been implemented in the Toolkit for High-Order Neutrino-Radiation Hydrodynamics (\thornado), and Fortran code used to generate the results has been made available to the public through GitHub.\footnote{https://github.com/ECP-Astro/thornado{\_}mini}
+
+\begin{center}
+  \section{INTRODUCTION}
+\end{center}
+
+The explosion of a massive star (i.e., with mass $\gtrsim8$ solar masses) in a core-collapse supernova (CCSN) is initiated by the collapse of its iron or oxygen-neon-magnesium core, the product of millions of years of stellar evolution.
+The collapse proceeds to densities exceeding the density of nucleons in the atomic nucleus, at which point the inner core becomes incompressible, ``rebounds," and launches a shock wave into the outer stellar core.
+This shock wave ultimately propagates through the outer layers of the star and disrupts it in a CCSN explosion. 
+However, before this, the shock wave stalls in the outer core, due to energy losses from neutrino emission and dissociation of heavy nuclei, and turns into an accretion shock.  
+Exactly how the shock wave is revived remains a central question in CCSN theory.  
+After core bounce, about $10^{53}$~ergs of energy in the form of neutrinos and antineutrinos of all three flavors (i.e., electron, muon, and tau neutrinos) is emitted from the proto-neutron star (PNS) at the center of the explosion.
+Early simulations \citep[e.g.,][]{betheWilson_1985} have shown that energy from these neutrinos can be deposited behind the shock and revive it, and this neutrino-reheating mechanism is central to current CCSN theory.
+See, e.g., \citet{mezzacappa_2005,janka_2012,burrows_2013,muller_2016}, for comprehensive reviews.
+
+Today, simulations play an indispensable role in disentangling details of the CCSN explosion mechanism, and in connecting observables to physical processes in the explosion.  
+Observables include nucleosynthetic yields, and optical and neutrino signals.  
+Simulations may also play a role in the future detection and interpretation of gravitational wave signals.  
+As such, CCSNe are multi-messengers, and CCSN models are quintessentially multi-physics --- involving all the known fundamental forces of nature.  
+However, the computational cost of CCSNe models is dominated by solving equations describing the transport of neutrinos and their interaction with the stellar fluid. 
+Neutrinos diffuse away from the PNS, become semi-transparent, and eventually free-streaming --- carrying information about the physical conditions in the exploding star.  
+One of the principal goals of a CCSN model is to compute the lepton and four-momentum exchange between the neutrinos and the stellar fluid.
+
+Net energy transfer from neutrinos to the stellar fluid occurs in the layer between the so-called \emph{gain radius} and the shock --- the \emph{heating region}.  
+Importantly, in the heating region, the neutrino mean free path exceeds other characteristic length scales (the Knudsen number exceeds unity), and non-equilibrium effects may become important.  
+To capture non-equilibrium effects, a \emph{kinetic description} is required, where the neutrinos are described by the \emph{distribution function} $f(\omegaNu,\epsilonNu,\vect{x},t)$, a phase space density governed by the Boltzmann equation.
+The distribution function gives, at time $t$, the number of neutrinos at spatial position $\vect{x}\in\mathbb{R}^{3}$, with energy $\epsilonNu\in\mathbb{R}^{+}$, propagating in direction $\omegaNu\in\mathbb{S}^{2}$ --- a seven-dimensional function.
+
+In this work, we seek to develop efficient methods to model neutrino transport in CCSN simulations.  
+On the one hand, the need for high spatial resolution and unconstrained spatial dimensionality to follow important fluid instabilities as the explosion develops makes direct solution of the Boltzmann equation a formidable computational challenge.
+On the other hand, neutrino heating rates are particularly sensitive to the neutrino energy distribution, which requires retention of the energy dimension of momentum space.  
+Therefore, to balance manageable computational cost with required physical fidelity, the number of unknowns can be reduced by a truncated moment expansion of the angular dimensions of momentum space; i.e., by solving for a finite number of angular moments of the distribution function
+\begin{equation}
+  \vect{\mathcal{M}}(\epsilonNu,\vect{x},t)=
+  \int_{\mathbb{S}^{2}}f(\omegaNu,\epsilonNu,\vect{x},t)\,\vect{w}(\omegaNu)\,d\omegaNu,
+\end{equation}
+where $\vect{w}$ are momentum space angular weighting functions.  
+The two-moment model \citep[e.g.,][]{andersonSpiegel_1972} is obtained by truncating the moment expansion at the level of the so-called first order moments (akin to an expansion in spherical harmonics up to degree $\ell=1$), so that the unknown moments are the spectral particle density $\cJ$ and particle flux $\bcH$ --- a two-moment model; $\bcM=(\cJ,\bcH)^{T}$.
+This is the basic system we will consider.  
+Note that the moments depend on the neutrino energy, spatial position, and time, and are governed by a system of nonlinear moment equations.
+
+The solution to a truncated moment model is confronted with the challenge of specifying higher order moments (e.g., radiation stresses), which appear in the governing moment equations.  
+In this work, the solution to this \emph{closure problem} is approximated by relating these higher order moments to the evolved moments through relatively simple analytic expressions \citep[cf.][]{minerbo_1978,levermore_1984,cernohorskyBludman_1994}.
+Obviously, this approach limits the fidelity of the model when the angular distribution of the radiation field is highly anisotropic.  
+However, this shortcoming can (at additional computational cost) be alleviated by extending the moment expansion to include more moments, or by solving the Boltzmann equation directly, in regions where higher fidelity is needed.
+In this approach, the two-moment model becomes a component in a multi-model hierarchy, and the developments described here can be fully leveraged.  
+We note that this multi-model approach introduces additional challenges associated with model coupling.
+
+The neutrino-radiation hydrodynamics system supports three important time scales: (i) the \emph{radiative time scale} $\tau_{\mbox{\tiny r}}$, governed by the speed of light; (ii) the \emph{fluid time scale} $\tau_{\mbox{\tiny f}}$, governed by the fluid flow and sound speeds; and (iii) the \emph{collision time scale} $\tau_{\mbox{\tiny c}}$, governed by the mean time between neutrino-matter interactions.
+In the CCSN environment, the flow \emph{and} sound speeds approach significant fractions of the speed of light, while $\tau_{\mbox{\tiny c}}$ is very short in the dense PNS.  
+Thus, we have the time scale ordering: $\tau_{\mbox{\tiny c}}\ll\tau_{\mbox{\tiny r}}\lesssim\tau_{\mbox{\tiny f}}$.  
+We will not resolve the short timescales imposed by collisions in the PNS, but integrate the stiff collision term with \emph{implicit methods}.  
+Streaming terms will be integrated in time using \emph{explicit methods}.  
+This motivates the use of \emph{Semi-Implicit (SI)}, or \emph{Implicit-Explcit (IMEX)}, time integration methods (e.g., \cite{minion_2003,pareschiRusso_2005,chertock_etal_2015}) for optimal balance between stability and efficiency.
+Specifically, we will use Semi-Implicit Runge-Kutta (SIRK) methods, similar to those discussed by \citet{chertock_etal_2015}.  
+This combination of explicit and implicit methods, as opposed to fully implicit methods, avoids  the need to solve large, distributed systems of algebraic equations for each time step.
+
+To solve the neutrino transport equations we discretize the moment equations in energy-position space using high-order Discontinuous Galerkin (DG) methods (e.g., \cite{cockburnShu_2001,hesthavenWarburton_2008}).
+DG methods combine elements from both spectral and finite volume methods, and are an attractive option for solving hyperbolic partial differential equations (PDEs).  
+They achieve high-order accuracy on a compact stencil; i.e., data is only communicated with nearest neighbors, regardless of the formal order of accuracy.  
+This leads to a high computation to communication ratio, and favorable parallel scalability on heterogeneous architectures has been demonstrated \citep{klockner_etal_2009}.  
+DG methods can be used in combination with $hp$-adaptivity \citep{remacle_etal_2003}, where, in addition to grid refinement with AMR, the local polynomial degree can be chosen differently, and independently, in different cells.
+They can easily be applied to problems involving curvilinear coordinates, which is beneficial in numerical relativity \citep{teukolsky_2016}.  
+Importantly, DG methods, as opposed to, e.g., finite volume methods, exhibit favorable properties when collisions are included.  
+Specifically, without modification, they recover the correct asymptotic behavior in the diffusion limit, characterized by frequent collisions \citep[e.g.,][]{larsenMorel_1989,adams_2001,guermondKanschat_2010}.
+The DG method was introduced in the 1970s by \citet{reedHill_1973} to solve the neutron transport equation, and has undergone remarkable developments since then \citep[see, e.g.,][and references therein]{shu_2016}.
+It has only recently received attention from the computational astrophysics community \citep[e.g.,][]{radiceRezzolla_2011,schaal_etal_2015,wuTang_2017}, mainly to solve the Euler equations for ideal hydrodynamics, but also to solve Einstein's field equations \citep{teukolsky_2016}.
+DG methods have also been considered for the neutrino transport problem in CCSN \citep[e.g.,][]{radice_etal_2013,endeve_etal_2015}.
+
+The ultimate goal of this work is to develop genuinely multi-dimensional, high-order numerical methods within the DG framework for solving the equations of neutrino-radiation hydrodynamics, that include relativity and full nonlinear coupling to the stellar fluid through a complete set of weak interactions, to enable high fidelity simulations of CCSN explosions.
+This is a formidable challenge, and, in our opinion, this goal is best achieved in incremental steps.  
+The work reported here is the initial step toward this goal, where we present developments of a DG method for solving the non-relativistic, multi-group two-moment model in one spatial dimension (but sufficiently general to accommodate Cartesian, spherical, and cylindrical spatial coordinates).
+We have tabulated a basic set of neutrino-matter interactions (electron capture and elastic scattering on nucleons and nuclei, and neutrino-electron scattering, as described by \citet{bruenn_1985}), using a tabulated nuclear equation of state (EoS), and we include lepton and energy exchange with the stellar fluid.
+The algorithms have been implemented in the Toolkit for High-Order Neutrino-Radiation Hydrodynamics (\thornado), and we provide a limited public release of the algorithms on GitHub (\url{https://github.com/ECP-Astro/thornado_mini}).
+
+This report is organized as follows:  
+We describe the non-relativistic, multi-group two-moment model we consider in Section~\ref{sec:twoMomentModel}
+We detail the spatial discretization of the two-moment model using the DG method in Section~\ref{sec:dgMethod}  
+The time integration methods used for problems with and without collisions are described in Section~\ref{sec:timeIntegration}  
+Limiting techniques to control nonphysical oscillations and to prevent nonphysical states are described in Section~\ref{sec:limiters}
+We provide details on the tabulated opacities in Section~\ref{sec:opacities}  
+Results from an extensive set of benchmark problems (in Cartesian, spherical, and cylindrical spatial coordinates), covering streaming and collision dominated limits, but with analytic opacities are presented in Section~\ref{sec:numericalBasic}
+The neutrino-matter coupling method and results from two tests using tabulated opacities are discussed in Section~\ref{sec:numericalTableOpacities} 
+Finally, we summarize and discuss next steps in Section~\ref{sec:summary}
+
+\begin{center}
+  \item\section{TWO-MOMENT MODEL FOR NEUTRINO TRANSPORT}
   \label{sec:twoMomentModel}
-
-\subsection{Basic Mathematical Model}
+\end{center}
+
+Here we give a description of the two-moment model to be solved with the DG method.
+
+\subsection{BASIC MATHEMATICAL MODEL}
 
@@
 \end{equation}
-The angular moments are related to the neutrino energy density, momentum density, and stress ($\cJ$, $\cH^{i}$, and $\cK^{ij}$, respectively).  
+The angular moments in Eq.~\eqref{eq:angularMoments} are related to the neutrino energy density, momentum density, and stress (by $\epsilonNu\,\cJ$, $\epsilonNu\,\cH^{i}$, and $\epsilonNu\,\cK^{ij}$, respectively, see, e.g., \cite{cardall_etal_2013a}).
 They are functions of the neutrino energy $\epsilonNu$, spatial position $\{x^{i}\}$, and time $t$.
 
-To model neutrino matter interactions, we include emission and absorption, (isotropic) elastic scattering on nucleons and nuclei, and neutrino-electron scattering (NES).  
+To model neutrino-matter interactions, we include emission and absorption, (isotropic) elastic scattering on nucleons and nuclei, and neutrino-electron scattering (NES).  
 On the right-hand sides of Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}, $\tilde{\chi}(\epsilonNu,\bU)$ and $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$ are absorption and transport (absorption plus elastic scattering) opacities, respectively.
@@
 \end{equation}
-where $k_{\mbox{\tiny B}}$ is Boltzmann's constant, and $\mu_{\nu}=\mu_{p}-\mu_{n}+\mu_{e}$ is the neutrino chemical potential.  
+where $k_{\mbox{\tiny B}}$ is Boltzmann's constant, and $\mu_{\nu}=\mu_{p}-\mu_{n}+\mu_{e}$ is the neutrino chemical potential in weak equilibrium.  
 (The chemical potentials of protons, neutrons, and electrons are denoted by $\mu_{p}$, $\mu_{n}$, and $\mu_{e}$, respectively.)
@@
 \begin{equation}
-  \psi(h)=\f{1}{3}+\f{2}{3}\,\Big(\,h^{2}\,\big(\,3-h+3h^{2}\,\big)/5\,\Big),
+  \psi(h)=\f{1}{3}+\f{2}{3}\,\Big[\,h^{2}\,\big(\,3-h+3h^{2}\,\big)/5\,\Big],
   \label{eq:eddingtonFactor}
@@
 
-\subsection{Two-Moment Model as a System of Conservation Laws with Sources}
-
-\begin{table}
-  \begin{center}
+\subsection{TWO-MOMENT MODEL AS A SYSTEM OF CONSERVATION LAWS WITH SOURCES}
+
+\begin{table}[h]
   \caption{Relevant metric functions for Cartesian, Cylindrical, and Spherical coordinate systems.\label{tab:metricFunctions}}
+  \small
+  \vspace{-6pt}
+  \begin{center}
   \begin{tabular}{ccccccccccc}
@@
 
-\section{Discontinuous Galerkin Discretization}
+\begin{center}
+  \section{DISCONTINUOUS GALERKIN DISCRETIZATION}
+  \label{sec:dgMethod}
+\end{center}
 
@@
 
-Several books and review articles on the DG method are now available \citep[see, e.g.,][]{cockburnShu_2001,hesthavenWarburton_2008}, and we will not go into too much detail here.  
-However, we review some key concepts to introduce notation, and, since multiple `flavors' of the DG method has emerged, we emphasize specific choices in our implementation.
-
-\subsection{Basic Principles of the DG Method}
+Several books and review articles on the DG method are now available \citep[see, e.g.,][and references therein]{cockburnShu_2001,hesthavenWarburton_2008,shu_2016}, and we will not go into too much detail here.
+However, we review some key concepts to introduce notation, and, since multiple `flavors' of the DG method have emerged, we emphasize specific choices in our implementation.  
+Specifically, we have implemented a nodal DG method where a tensor product of Legendre-Gauss quadrature points define the interpolation nodes within an element (using Lagrange polynomials).  
+Furthermore, we let these Legendre-Gauss quadrature nodes also define the integration points to evaluate integrals in the DG method using the Legendre-Gauss quadrature rule.  
+This approach, called the spectral-type collocation DG method by \citet{bassi_etal_2013}, leads to particularly simple expressions, and offers computational advantages in quadrature evaluations.
+
+\subsection{BASIC PRINCIPLES OF THE DG METHOD}
 
@@
 
-\subsection{Further Details on the DG Discretization of the Moment Equations}
+\subsection{FURTHER DETAILS ON THE DG DISCRETIZATION OF THE MOMENT EQUATIONS}
 
 Here we provide further details on the DG method in order to arrive at the equations that are actually implemented in our code.  
-We start by introducing some notation, defining the polynomial expansion for $\bcM_{\DG}$, and the quadrature rules used to evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}.  
-Then, using these rules, we provide explicit expressions for each of the terms in Equation~\eqref{eq:semidiscreteDG}.
+We start by introducing some notation, defining the polynomial expansion for $\bcM_{\DG}$, and the quadrature rules used to evaluate the integrals in Eq.~\eqref{eq:semidiscreteDG}.  
+Then, using these rules, we provide explicit expressions for each of the terms in Eq.~\eqref{eq:semidiscreteDG}.
 
@@
 Let $\bi=\{i_{1},\ldots,i_{d}\}$ be a multi-index, and define the multidimensional polynomial as $\ell_{\bi}(\bx)=\prod_{k=1}^{d}\ell_{i_{k}}(x^{k})$.  
-From the property $\ell_{i}(x_{j})=\delta_{ij}$ we have the corresponding multidimensional version $\ell_{\bi}(\bx_{\bj})=\delta_{\bi\bj}$, so that $\bcM_{\DG}(\bx_{\bi},t)=\bcM_{\bi}(t)$; i.e., the expansion coefficients in Equation \eqref{eq:conservedNodalExpansion} represent the conserved variables defined in the nodes $\bx_{\bi}$.
+From the property $\ell_{i}(x_{j})=\delta_{ij}$ we have the corresponding multidimensional version $\ell_{\bi}(\bx_{\bj})=\delta_{\bi\bj}$, so that $\bcM_{\DG}(\bx_{\bi},t)=\bcM_{\bi}(t)$; i.e., the expansion coefficients in Eq.
+\eqref{eq:conservedNodalExpansion} represent the conserved variables defined in the nodes $\bx_{\bi}$.
 We then have
@@
 
-To evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}, we introduce numerical quadratures.  
+To evaluate the integrals in Eq.~\eqref{eq:semidiscreteDG}, we introduce numerical quadratures.  
 First we define the one-dimensional $N$-point quadrature $Q_{N}^{i}:C^{0}(I^{i})\to\bbR$ with abscissas $\{\eta_{q}\}_{q=1}^{N}$ and weights $\{w_{q}\}_{q=1}^{N}$, normalized such that $\sum_{q=1}^{N}w_{q}=1$.
@@
 \end{align}
-Equation~\eqref{eq:semidiscreteDiscretized} provides the basis for implementation in our code.
+Eq.~\eqref{eq:semidiscreteDiscretized} provides the basis for implementation in our code.
 
@@
 
-\section{Time Integration}
-
-For time integration we employ the method lines.  
+\begin{center}
+  \section{TIME INTEGRATION}
+  \label{sec:timeIntegration}
+\end{center}
+
+For time integration we employ the method of lines.  
 Having specified the spatial discretization for the advection terms and the representation of the collision terms, we consider the discretized moment equations in Eq.~\eqref{eq:semidiscreteDiscretized} as a system of ordinary differential equations (ODEs) to evolve forward in time, and write
@@
 
-\subsection{Explicit Integration Scheme: SSP-RK Methods}
+\subsection{EXPLICIT INTEGRATION SCHEME: SSP-RK METHODS}
 \label{sec:explicitTime}
@@
 
-\begin{table}
-  \begin{center}
-  \caption{Optimal coefficients for SSP-RK Methods \citep{shuOsher_1988} \label{tab:ssprkCoefficients}}
+\begin{table}[h]
+  \caption{Optimal coefficients for SSP-RK Methods from \citet{shuOsher_1988} \label{tab:ssprkCoefficients}}
+  \small
+  \vspace{-6pt}
+  \begin{center}
   \begin{tabular}{cccccccccccccccccc}
@@
 
-\subsection{Semi-Implicit Runge-Kutta Methods}
+\subsection{SEMI-IMPLICIT RUNGE-KUTTA METHODS}
 \label{sec:semiImplicitTime}
@@
 
-\section{Polynomial Limiting}
+\begin{center}
+  \section{POLYNOMIAL LIMITING}
+  \label{sec:limiters}
+\end{center}
 
@@
 
-\subsection{Slope Limiters}
+\subsection{SLOPE LIMITERS}
 \label{sec:slopeLimiters}
@@
 
-\subsection{Positivity Limiters}
+\subsection{POSITIVITY LIMITERS}
 \label{sec:positivityLimiters}
@@
 
-\section{Neutrino Opacities}
+\begin{center}
+  \section{NEUTRINO OPACITIES}
   \label{sec:opacities}
+\end{center}
 
@@
 We consider a single neutrino specie (electron-type neutrinos), and include the relevant rates due to electron capture on nucleons and nuclei, iso-energetic (elastic) scattering on nucleons and nuclei, and elastic neutrino-electron scattering (NES).
-For completeness, we provide sufficient detail to arrive at the tabulates opacities relevant for the two-moment model.  
+For completeness, we provide sufficient detail to arrive at the tabulated opacities relevant for the two-moment model.  
 For further details on the specific opacities we use, see \citet{bruenn_1985}, \citet{mezzacappaBruenn_1993a}, and \citet{mezzacappaBruenn_1993c}.
@@
 
-\subsection{Emission and Absorption}
+\subsection{EMISSION AND ABSORPTION}
+\label{sec:electronCapture}
 
@@
 
-\subsection{Elastic Scattering}
+\subsection{ELASTIC SCATTERING}
+\label{sec:elasticScattering}
 
@@
 \end{equation}
-These integrals are performed numerically using a ??-point Gauss-Legendre quadrature rule.  (\ee{Ran: Fill in the number of quadrature points}.)
+These integrals are performed numerically using a 20-point Gauss-Legendre quadrature rule.  
 Inserting the Legendre expansion into Eq.~\eqref{eq:homogeneousBoltzmann} and taking the angular moments gives no contribution to the equation for $\cJ$ (energy conservation), while the contribution to the equation for $\bcH$ is
@@
 \end{equation}
-We tabulate the scattering opacities $\sigma_{\IS,0}$ and $\sigma_{\IS,1}$, which have units cm$^{-1}$, but use only $\sigma_{\IS,0}$ in the numerical experiments in Section~\ref{sec:numericalTableOpacities}, where $\sigma=\sigma_{\IS,0}$ in Equation~\eqref{eq:momentEquationMomentum}.
-
-\subsection{Neutrino-Electron Scattering}
+We tabulate the scattering opacities $\sigma_{\IS,0}$ and $\sigma_{\IS,1}$, which have units cm$^{-1}$, but use only $\sigma_{\IS,0}$ in the numerical experiments in Section~\ref{sec:numericalTableOpacities}, where $\sigma=\sigma_{\IS,0}$ in Eq.~\eqref{eq:momentEquationMomentum}.
+
+\subsection{NEUTRINO-ELECTRON SCATTERING}
 
@@
 \end{equation}
-(Again, these integrals are computed numerically using a ??-point Gauss-Legendre quadrature.  (\ee{Ran: Fill in the number of quadrature points}.))
+(These integrals are computed numerically using a 30-point Gauss-Legendre quadrature.  
 The in-scattering kernels $\Phi_{\NES,\ell}^{\In}(\epsilonNu,\epsilonNu')$ are obtained from symmetry properties \citep{cernohorsky_1994}
@@
 We tabulate the scattering kernels $R_{\NES,0}^{\Out}$ and $R_{\NES,1}^{\Out}$, which have units MeV$^{-3}$ cm$^{-1}$, and obtain the in-scattering rates from the symmetry properties in Eq.~\eqref{eq:symmetryNES}.
-We only use $R_{\NES,0}^{\In/\Out}$ in the numerical experiments in Section~\ref{sec:numericalTableOpacities}, so that $R^{\In/\Out}=R_{\NES,0}^{\In/\Out}$ in Eqs~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}.
-
-\section{Basic Benchmark Problems}
+We only use $R_{\NES,0}^{\In/\Out}$ in the numerical experiments in Section~\ref{sec:numericalTableOpacities}, so that $R^{\In/\Out}=R_{\NES,0}^{\In/\Out}$ in Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}.
+
+\begin{center}
+  \section{BASIC BENCHMARK PROBLEMS}
   \label{sec:numericalBasic}
+\end{center}
 
@@
 First we consider test problems in the streaming limit.  
-In this case we use the explicit SSP-RK time integrators in Section~\ref{sec:explicitTime}.  
+In this case we use the explicit SSP-RK time integrators described in Section~\ref{sec:explicitTime}.  
 The 2-stage and 3-stage methods are denoted SSP-RK2 and SSP-RK3, respectively.  
 As an example, an expected third-order accurate method (for problems with smooth solutions), using DG(2) and SSP-RK3, will then be denoted DG(2)+RK3.  
-
-\subsection{Streaming Sine Wave}
+For tests involving collisions we use the two-stage Semi-Implicit Runge-Kutta method described in Section~\ref{sec:semiImplicitTime}.  
+When this time integrator is combined with DG($k$) spatial discretization, the method is denoted DG($k$)+SIRK2.
+
+\subsection{STREAMING SINE WAVE}
 
@@
 
-\begin{figure}
-  \begin{center}
+\begin{figure}[h]
+  \centering
   \includegraphics[scale=0.78]{./Figures/StreamingSineWave1D}
-  \end{center}
-  \caption{Particle density versus position after ten grid crossings ($t=10$) for the streaming sine wave problem computed with the DG(2)+RK3 scheme using 16 elements.  
-  We compare results obtained using various limiter parameters (open circles; see text for details) with the analytic solution (dotted line).  
-  Results obtained using the discontinuity detector (D) is denoted with black open circles.}
+  \vspace{-0.1in}
+  \flushleft\caption[Particle density versus position after ten grid crossings ($t=10$) for the streaming sine wave problem computed with the DG(2)+RK3 scheme using 16 elements.]{Particle density versus position after ten grid crossings ($t=10$) for the streaming sine wave problem computed with the DG(2)+RK3 scheme using 16 elements.
+\textmd{We compare results obtained using various limiter parameters (open circles; see text for details) with the analytic solution (dotted line).
+Results obtained using the discontinuity detector (D) is denoted with black open circles.}}
   \label{fig:streamingSineWave}
@@
 
-\begin{table}
-  \begin{center}
+\begin{table}[h]
   \caption{$L^{\infty}$ error and convergence rates for the streaming sine wave problem.}
+  \small
+  \vspace{-6pt}
+  \begin{center}
   \label{tab:streamingSineWave}
@@
 
-\subsection{Spherical Wave}
+\subsection{SPHERICAL WAVE}
 
@@
 
-\begin{figure}
-  \begin{center}
+\begin{figure}[h]
+  \centering
   \includegraphics[scale=0.78]{./Figures/GaussianSphericalWave1D}
-  \end{center}
-  \caption{Energy density versus radius at various times for the spherical wave problem computed with the DG(2)+RK3 scheme using 32 elements.
-The numerical solution (open circles) is compared to the analytical solution (dotted lines).
-}
+  \vspace{-0.1in}
+  \flushleft\caption[Energy density versus radius at various times for the spherical wave problem computed with the DG(2)+RK3 scheme using 32 elements.]{Energy density versus radius at various times for the spherical wave problem computed with the DG(2)+RK3 scheme using 32 elements.
+\textmd{The numerical solution (open circles) is compared to the analytical solution (dotted lines).}}
   \label{fig:sphericalWave}
@@
 
-\begin{table}
-  \begin{center}
+\begin{table}[h]
   \caption{$L^{\infty}$ error and convergence rates for the spherical wave problem.}
+  \small
+  \vspace{-6pt}
+  \begin{center}
   \label{tab:sphericalWave}
@@
 
-\subsection{Line Source}
+\subsection{LINE SOURCE}
 
@@
 \begin{figure}
-  \begin{center}
+  \centering
   \begin{tabular}{cc}
@@
   \end{tabular}
-  \end{center}
-  \caption{Results from the line source problem with the two-moment model for various times.
-In the left panel we plot the radiation density $\cJ$.
+  \vspace{-0.1in}
+  \flushleft\caption[Results from the line source problem with the two-moment model for various times.]{Results from the line source problem with the two-moment model for various times.
+\textmd{In the left panel we plot the radiation density $\cJ$.
 In the right panel we plot the flux factor $h=|\cH_{1}|/\cJ$.
 Solid lines represent a high resolution (2048 elements) reference solution using the DG(1)+RK2 scheme, while circles are results obtained with the DG(2)+RK3 scheme using 64 elements.
-Both solutions maintain the bounds $\cJ>0$ and $h\in[0,1]$.}
+Both solutions maintain the bounds $\cJ>0$ and $h\in[0,1]$.}}
   \label{fig:lineSource}
@@
 
-\subsection{Riemann Problem}
+\subsection{RIEMANN PROBLEM}
 
@@
 
-\begin{figure}
-  \begin{center}
+\begin{figure}[h]
+  \centering
   \begin{tabular}{cc}
@@
   \end{tabular}
-  \end{center}
-  \caption{Results from the one-dimensional Riemann problem in Eq.~\eqref{eq:riemannProblem}, obtained with the DG(2)+RK3 method using $240$ elements, the HLL Riemann solver, and the Eddington factor in Eq.~\eqref{eq:eddingtonFactorLevermore}.
-  The number density $\cJ$ (black) and the number flux density $\cH_{1}$ (red) are plotted for $t=0.1$.}
+  \vspace{-0.1in}
+  \flushleft\caption[Results from the one-dimensional Riemann problem in Eq.~\eqref{eq:riemannProblem}, obtained with the DG(2)+RK3 scheme using $240$ elements.]{Results from the one-dimensional Riemann problem in Eq.~\eqref{eq:riemannProblem}, obtained with the DG(2)+RK3 method using $240$ elements.
+The HLL Riemann solver and the Eddington factor in Eq.~\eqref{eq:eddingtonFactorLevermore} was used to obtain the results.
+\textmd{The number density $\cJ$ (black) and the number flux density $\cH_{1}$ (red) are plotted for $t=0.1$.}}
   \label{fig:riemannProblem}
@@
 
-\subsection{Spherical Diffusion}
+\subsection{SPHERICAL DIFFUSION}
 
@@
   \end{tabular}
-  \end{center}
-  \caption{Results from the one-dimensional diffusion problem in spherical symmetry, obtained with the DG(2)+SIRK2 method using $32$ elements.  
-  The number density $\cJ$ (left panel) and the number flux density $\cH_{r}$ (right panel) are plotted.  
+  \vspace{-0.1in}
+  \flushleft\caption[Results from the diffusion problem in spherical symmetry, obtained with the DG(2)+SIRK2 method using $32$ elements.]{Results from the diffusion problem in spherical symmetry, obtained with the DG(2)+SIRK2 method using $32$ elements.
+  \textmd{The number density $\cJ$ (left panel) and the number flux density $\cH_{r}$ (right panel) are plotted.
 In the upper panels $\sigma=10^{-5}$~cm$^{-1}$, with results plotted for $t=0,0.3,1.0$~ms (red, blue, and black curves, respectively).
 In the lower panels $\sigma=10^{-1}$~cm$^{-1}$, with results plotted for $t=0,0.4,1.0$~s (red, blue, and black curves, respectively).
-  Solid lines represent the analytical solution while open circles represent the element center value of the numerical solution.}
+Solid lines represent the analytical solution while open circles represent the element center value of the numerical solution.}}
   \label{fig:diffusionProblem}
@@
 
-\subsection{Homogeneous Sphere}
+\subsection{HOMOGENEOUS SPHERE}
+\label{sec:homogeneousSphere}
 
@@
 Outside the sphere, the absorption opacity is zero.  
-The steady state solution, obtained by solving the transport equation in spherical symetry, is given by
+The steady state solution, obtained by solving the transport equation in spherical symmetry, is given by
 \begin{equation}
@@
 
-Similar to \citet{oConnor_2015}, we solve two versions of this test.  
-One where the absorption opacity is set to $\chi_{0}=10^{-4}$~cm$^{-1}$ (thick; similar to the electron capture opacity encountered in the center of a collapsed stellar core), and one where the absorption opacity is set to $\chi_{0}=10^{-6}$~cm$^{-1}$ (thin).
+Similar to \citet{oConnor_2015}, we solve two versions of this test: One where the absorption opacity is set to $\chi_{0}=10^{-4}$~cm$^{-1}$ (thick; similar to the electron capture opacity encountered in the center of a collapsed stellar core), and one where the absorption opacity is set to $\chi_{0}=10^{-6}$~cm$^{-1}$ (thin).
 Both simulations are run with a computational domain with $r\in[0,500]$~km using 100 uniform elements $\Delta r=5$~km.  
@@
 Results are plotted in Figure~\ref{fig:homogeneousSphere1D}.  
-
-\begin{figure}
-  \begin{center}
+In the left panels we plots results obtained for the thick case, while results for the thin case are plotted in the right panels.  
+We plot the radiation density $\cJ$ in the top panels, the flux factor $\cH_{r}/\cJ$ in the middle panels, and the Eddington factor $\psi$ in the bottom panels.  
+The two-moment model captures the analytic solution reasonably well in both the thin and the thick cases, especially for the density $\cJ$.  
+The discrepancy in the flux and Eddington factors between the numerical results and the analytical solution is comparable to that of other implementations of the two-moment model \citep[e.g.,][]{smit_etal_1997}.
+
+\begin{figure}[h]
+  \centering
   \begin{tabular}{cc}
@@
   \end{tabular}
-  \end{center}
-  \caption{Results from solving the Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ elements.  
-  In the left panels, the absorption opacity is set to $\chi_{0}=10^{-4}$~cm$^{-1}$, while in the right panels it is set to $\chi_{0}=10^{-6}$~cm$^{-1}$.  
-  The numerical results (dashed lines) are compared to the analytical solution (solid lines).}
+  \vspace{-0.1in}
+  \flushleft\caption[Results from solving the Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ elements.]{Results from solving the Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ elements.
+\textmd{In the left panels, the absorption opacity is set to $\chi_{0}=10^{-4}$~cm$^{-1}$, while in the right panels it is set to $\chi_{0}=10^{-6}$~cm$^{-1}$.
+The numerical results (dashed lines) are compared to the analytical solution (solid lines).}}
   \label{fig:homogeneousSphere1D}
@@
 
-\subsection{Milne's Problem}
+\subsection{MILNE'S PROBLEM}
 
@@
   \end{tabular}
-  \end{center}
-  \caption{Results of the Milne problem obtained with the two-moment model (solid lines), obtained with the DG(2)+SIRK2 scheme, compared with solutions provided by \citep{hummerRybicki_1971} (boxes).
-See text for details.}
+  \vspace{-0.1in}
+  \flushleft\caption[Results of the Milne problem obtained with the two-moment model (solid lines), using the DG(2)+SIRK2 scheme.]{Results of the Milne problem obtained with the two-moment model (solid lines), using the DG(2)+SIRK2 scheme.
+\textmd{The two-moment results are compared with solutions provided by \citep{hummerRybicki_1971} (boxes).
+See text for details.}}
   \label{fig:milneProblem1D}
@@
 In the lower right panel we plot results for $n=3$, with $R_{\mbox{\tiny max}}=0.1$ (black lines) and $R_{\mbox{\tiny max}}=10$.  
-In the upper right panel we plot flux factors ($\cH_{r}/\cJ$, black lines) and Eddington factors ($\psi$, blue lines) for a model with $n=2$ and $R_{\mbox{\tiny max}}=10$, and compare with results given \citet{hummerRybicki_1971} (their Table~I; boxes).
+In the upper right panel we plot flux factors ($\cH_{r}/\cJ$, black lines) and Eddington factors ($\psi$, blue lines) for a model with $n=2$ and $R_{\mbox{\tiny max}}=10$, and compare with results given by \citet{hummerRybicki_1971} (their Table~I; boxes).
 For this model, we computed results with the Minerbo closure (cf. Eq.~\eqref{eq:eddingtonFactor}; solid lines) and the Levermore closure (cf. Eq.~\eqref{eq:eddingtonFactorLevermore}; dashed lines).  
@@
 
-\section{Transport Problems with Tabulated Neutrino Opacities}
+\begin{center}
+  \section{MULTI-GROUP TRANSPORT PROBLEMS WITH TABULATED NEUTRINO OPACITIES}
   \label{sec:numericalTableOpacities}
-
-For the tests in this section we employ the tabulated opacities described in Section~\ref{sec:opacities}.  
-We present two tests from the previous section (the homogeneous sphere and spherical diffusion problems), where the background is kept fixed.  
-Then we present a relaxation problem involving neutrino-electron scattering (NES) with a homogeneous background.  
-Finally, we present a deleptonization problem where the background density mimics that of a collapsed stellar core.  
-The first deleptonization problem (Em/Ab) involves emission and absorption only, while the second deleptonization problem (Full) involves the full set of opacities described in Section~\ref{sec:opacities}.
+\end{center}
+
+For the tests in this section we employ some of the tabulated opacities described in Section~\ref{sec:opacities}.  
+In Section~\ref{sec:homogeneousSphereTable}, we present a multi-group version of the homogeneous sphere test from Section~\ref{sec:homogeneousSphere}, where the background is kept fixed.  
+In Section~\ref{sec:deleptonizationProblem}, we present a deleptonization problem where the initial background density mimics that of a collapsed stellar core.  
+The deleptonization problem uses the tabulated electron capture and elastic scattering rates on nucleons and nuclei as described in Sections~\ref{sec:electronCapture} and \ref{sec:elasticScattering}.
+For this problem, the temperature and electron fraction of the background are evolved with the radiation field as described in Section~\ref{sec:couplingElectronCapture} below.  
+The deleptonization problem is distributed with the mini-app, available at \url{https://github.com/ECP-Astro/thornado_mini}.
 
@@
 
-\subsection{Fluid-Radiation Coupling}
-
-\subsubsection{Emission and Absorption}
+\subsection{FLUID-RADIATION COUPLING}
+
+\label{sec:couplingElectronCapture}
 
@@
 \end{equation}
-
-\subsubsection{Neutrino-Electron Scattering (NES)}
-
-When NES is included the internal energy of the fluid evolves according to
-\begin{align}
-  \rho\,d_{t}\epsilon
-  &=-\int_{\bbR^{+}}\int_{\bbR^{+}}\big(4\pi-\cJ(\epsilonNu)\big)R^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu} \\
-  &\hspace{12pt}
-  +\int_{\bbR^{+}}\int_{\bbR^{+}}\cJ(\epsilonNu)\,R^{\Out}(\epsilonNu,\epsilonNu')\,\big(4\pi-\cJ(\epsilonNu)\big)\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu}.  
-\end{align}
-With the semi-implicit approximation (evaluating the NES scattering rates using fluid properties at $t^{n}$), the neutrino number density can be solved for without iterative coupling to the thermodynamic state of the fluid.
-We first define the solution vector $\bcJ=(\cJ_{1},\ldots,\cJ_{M^{\epsilonNu}})^{\mbox{\tiny T}}$, and solve the nonlinear system of equations
-\begin{equation}
-  \bF(\bcJ^{n+1})=0
-  \label{eq:NonlinearSystemNES}
-\end{equation}
-using Newton's method.  
-Here, the $j$th component of the nonlinear system of equations is given by
-\begin{equation}
-  F_{j}(\bcJ^{n+1})
-  =\big(\cJ_{j}^{n+1}-\cJ_{j}^{n}\big)
-  -\dt\,\Big\{\,
-    \big(4\pi-\cJ_{j}^{n+1}\big)\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1}
-    -\cJ_{j}^{n+1}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)\,\Big\},
-\end{equation}
-and the Jacobian matrix is
-\begin{align}
-  \pderiv{\bF}{\bcJ}
-  =\pderiv{F_{j}}{\cJ_{k}}
-  &=\delta_{jk}\,\Big(1+\dt\,\Big\{\sum_{l=1}^{M^{\epsilonNu}}W_{l}^{(2)}\,R_{jl}^{\In,n}\,\cJ_{l}
-  +\sum_{l=1}^{M^{\epsilonNu}}W_{l}^{(2)}\,R_{jl}^{\Out,n}\,\big(4\pi-\cJ_{l}\big)\Big\}\Big) \nonumber \\
-  &\hspace{12pt}
-  -\dt\,\Big\{\big(4\pi-\cJ_{j}\big)\,W_{k}^{(2)}\,R_{jk}^{\In,n}+\cJ_{j}\,W_{k}^{(2)}\,R_{jk}^{\Out,n}\Big\}.
-\end{align}
-When Eq.~\eqref{eq:NonlinearSystemNES} is converged to give $\bcJ^{n+1}$, the fluid energy density is updated as
-\begin{align}
-  \epsilon^{n+1}
-  &=\epsilon^{n}-\f{\dt}{\rho}
-  \Big\{\,
-    \sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\big(4\pi-\cJ_{j}^{n+1}\big)
-    \sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1} \nonumber \\
-    &\hspace{56pt}
-    -\sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\,\cJ_{j}^{n+1}
-    \sum_{k=1}^{M^{\epsilonNu}}W^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)
-  \,\Big\}.
-\end{align}
-
-\subsubsection{Full Interaction Set}
-
-\begin{table}
+When elastic scattering is included, the above description remains unchanged, except for $\gamma_{j}^{n}\to\dt\big(\tilde{\chi}_{j}^{n}+\sigma_{j}^{n}\big)$ in Eq.~\eqref{eq:momentEquationMomentumEmAbDiscrete}.
+
+\begin{table}[h]
   \caption{Parameters used for problems with tabulated opacities. \label{tab:tabulatedModels}}
+  \small
+  \vspace{-6pt}
+  \begin{center}
   \begin{tabular}{ccccc}
@@
   \end{tabular}
+  \end{center}
 \end{table}
 
-\begin{figure}
-  \begin{center}
+\begin{figure}[h]
+  \centering
   \includegraphics[scale=0.8]{./Figures/HomogeneousSphere_Opacities}
-  \end{center}
-  \caption{Absorption opacityies versus energy $\epsilonNu$ using values for $\rho$, $T$, and $Y_{e}$ listed in Table~\ref{tab:tabulatedModels}.}
+  \vspace{-0.1in}
+  \caption{Absorption opacities versus energy $\epsilonNu$ using values for $\rho$, $T$, and $Y_{e}$ listed in Table~\ref{tab:tabulatedModels}.}
   \label{fig:absorptionOpacities_weaklib}
@@
 
-\subsection{Homogeneous Sphere}
-
-\begin{figure}
-  \begin{center}
+\subsection{HOMOGENEOUS SPHERE}
+\label{sec:homogeneousSphereTable}
+
+Here we present results from a multi-group version of the homogeneous sphere problem in Section~\ref{sec:homogeneousSphere}, where we use the tabulated electron capture rates from Section~\ref{sec:electronCapture}.
+The radius of the sphere is set to $R=100$~km, and the computational domain covers the region $r\in[0,500]$~km.  
+We present two versions of the test, one for dense conditions, where the $\rho=10^{13}$~g~cm$^{-3}$, $T=16$~MeV, and $Y_{e}=0.14$ inside $r=R$ (Model B in Table~\ref{tab:tabulatedModels}), and one where $\rho=10^{11}$~g~cm$^{-3}$, $T=8$~MeV, and $Y_{e}=0.15$ inside $r=R$ (Model D in Table~\ref{tab:tabulatedModels}).
+The electron capture rates $\tilde{\chi}$ for these conditions are plotted versus energy $\epsilonNu$ in Figure~\ref{fig:absorptionOpacities_weaklib} (blue and magenta lines, respectively).  
+Outside $r=100$~km, we set $\rho=10^{8}$~g~cm$^{-3}$, $T=0.2$~MeV, and $Y_{e}=0.46$ in both models.
+
+Numerical results, obtained with the DG(2)+SIRK2 scheme using 100 equally sized radial elements and 24 geometrically spaced energy groups covering $\epsilonNu\in[0,300]$~MeV (with a minimum energy bin $\Delta\epsilonNu=1$~MeV), are plotted in Figures \ref{fig:homogeneousSphere1D_weaklib_B} (Model B) and \ref{fig:homogeneousSphere1D_weaklib_D} (Model D).
+In the upper left panel we plot the average density $J/V_{\epsilonNu}$, where
+\begin{equation}
+  J=\int_{\bbR^{+}}\cJ\,dV_{\epsilonNu}
+  \quad\text{and}\quad
+  V_{\epsilonNu}=\int_{\bbR^{+}}dV_{\epsilonNu}.  
+  \label{eq:averageDensity}
+\end{equation}
+In the lower left panel we plot the average flux factor, defined as
+\begin{equation}
+  f_{r}=\f{1}{J}\int_{\bbR^{+}}\cH_{r}\,dV_{\epsilonNu}.  
+  \label{eq:averageFluxFactor}
+\end{equation}
+In the upper right panel we plot the average Eddington factor, defined as
+\begin{equation}
+  \langle\psi\rangle=\f{1}{J}\int_{\bbR^{+}}\psi\,\cJ\,dV_{\epsilonNu}.  
+\end{equation}
+In the lower right panel we plot the mean energy
+\begin{equation}
+  \langle\epsilonNu\rangle=\f{1}{J}\int_{\bbR^{+}}\cJ\,\epsilonNu\,dV_{\epsilonNu}.  
+  \label{eq:meanEnergy}
+\end{equation}
+In each panel we compare the numerical and analytical results (dashed and solid lines, respectively).  
+As can be seen, the agreement between the numerical and analytical results is similar to that observed in Section~\ref{sec:homogeneousSphere}.
+
+\begin{figure}[h]
+  \centering
   \begin{tabular}{cc}
@@
   \end{tabular}
-  \end{center}
-  \caption{Results from solving the multi-group Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ spatial elements and $24$ energy groups, and using material properties from Model~D in Table~\ref{tab:tabulatedModels} to compute the neutrino absorption opacities.
+  \vspace{-0.1in}
+  \flushleft\caption[Results from solving the multi-group Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ spatial elements and $24$ energy groups.]{Results from solving the multi-group Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ spatial elements and $24$ energy groups.
+\textmd{The material properties from Model~B in Table~\ref{tab:tabulatedModels} are used to compute the neutrino absorption opacities.
 We plot the energy-averaged neutrino density (upper left), flux factor (lower left), Eddington factor (upper right), and mean neutrino energy (lower right) versus radius.
-    The analytical solution is represented by the solid lines, while the numerical solution is given by the dashed lines.}
+The analytical solution is represented by the solid lines, while the numerical solution is given by the dashed lines.}}
   \label{fig:homogeneousSphere1D_weaklib_B}
@@
   \end{tabular}
-  \end{center}
-  \caption{Same as in Figure~\ref{fig:homogeneousSphere1D_weaklib_B}, but using material properties from Model~D in Table~\ref{tab:tabulatedModels} to compute the neutrino absorption opacities.}
+  \vspace{-0.1in}
+  \caption{Same as Figure~\ref{fig:homogeneousSphere1D_weaklib_B}, but with properties from Model~D in Table~\ref{tab:tabulatedModels} to compute the opacities.}
   \label{fig:homogeneousSphere1D_weaklib_D}
@@
 
-%\begin{figure}
-%  \begin{center}
-%    \begin{tabular}{cc}
-%      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_Opacities} &
-%      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_BaseSpectra} \\
-%      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_B} &
-%      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_D}
-%    \end{tabular}
-%  \end{center}
-%  \caption{Results from solving the multi-group Homogeneous sphere problem with the DG(1)+SIRK2 method using $100$ elements.
-%    In the upper left panel we plot the absorption opacity versus energy $\epsilonNu$ using the values for $\rho$, $T$, and $Y_{e}$ listed in Table~\ref{tab:tabulatedModels}.
-In the upper right panel, we plot the spectral number density versus energy at the end of the computations for a radius of $52.5$~km solid lines.
-The corresponding Fermi-Dirac spectrum is also plotted (dashed lines).
-}
-%  \label{fig:homogeneousSphere1D_weaklib}
-%\end{figure}
-
-\subsection{Diffuse Scattering}
-
-\subsection{Relaxation}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.75\textwidth]{./Figures/RelaxationEmissionAbsorption_Spectra_ModelA}
-  \end{center}
-  \caption{Results from solving an emission/absorption relaxation problem with initial material properties given by Model A in Table~\ref{tab:tabulatedModels}.  
-  The neutrino energy spectrum is plotted for various times as the radiation field approaches equilibrium.}
-  \label{fig:RelaxationEmissionAbsorption}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.85\textwidth]{./Figures/RelaxationNES_Spectra.png}
+\subsection{DELEPTONIZATION PROBLEM}
+\label{sec:deleptonizationProblem}
+
+We conclude with a problem mimicking deleptonization in a collapsed stellar core.  
+To this end, we adopt analytic profiles for the initial mass density, temperature, and electron fraction:
+\begin{align}
+  \rho(r)
+  &=0.5\times
+  \big\{\,
+    \rho_{\mbox{\tiny max}}\times\big[\,1-\tanh\big(\,(r-R_{\rho})/H_{\rho}\,\big)\,\big]
+    +\rho_{\mbox{\tiny min}}\times\big[\,1-\tanh\big(\,(R_{\rho}-r)/H_{\rho}\,\big)\,\big]
+  \,\big\}, \\
+  T(r)
+  &=0.5\times
+  \big\{\,
+    T_{\mbox{\tiny max}}\times\big[\,1-\tanh\big(\,(r-R_{T})/H_{T}\,\big)\,\big]
+    +T_{\mbox{\tiny min}}\times\big[\,1-\tanh\big(\,(R_{T}-r)/H_{T}\,\big)\,\big]
+  \,\big\}, \\
+  Y_{e}(r)
+  &=0.5\times
+  \big\{\,
+    Y_{e,\mbox{\tiny min}}\times\big[\,1-\tanh\big(\,(r-R_{Y_{e}})/H_{Y_{e}}\,\big)\,\big]
+    +Y_{e,\mbox{\tiny max}}\times\big[\,1-\tanh\big(\,(R_{Y_{e}}-r)/H_{Y_{e}}\,\big)\,\big]
+  \,\big\}.  
+\end{align}
+For the density profile we set $\rho_{\mbox{\tiny min}}=10^{8}$~g~cm$^{-3}$, $\rho_{\mbox{\tiny max}}=4\times10^{14}$~g~cm$^{-3}$, $R_{\rho}=20$~km, and $H_{\rho}=10$~km.  
+Thus, the maximum density is consistent with nuclear matter, and neutrinos will be trapped.  
+As the density decreases with radius, the neutrino mean free path increases, and the neutrinos created by electron capture will be able to escape the computational domain (deleptonization).  
+For the temperature profile we set $T_{\mbox{\tiny min}}=5\times10^{9}$~K, $T_{\mbox{\tiny max}}=2.6\times10^{11}$~K, $R_{T}=25$~km, and $H_{T}=20$~km, while for the electron fraction profile we set $Y_{e,\mbox{\tiny min}}=0.3$, $Y_{e,\mbox{\tiny max}}=0.46$, $R_{Y_{e}}=45$~km, and $H_{Y_{e}}=10$~km.
+(The initial temperature and electron fraction profiles are plotted as dotted lines in Figure~\ref{fig:deleptonizationProblemFluid}.)
+The radiation field is initialized by setting the distribution function equal to the local Fermi-Dirac distribution.
+
+In this problem the computational domain covers $r\in[0,100]$~km and $\epsilonNu\in[0,300]$~MeV.  
+We use equally sized spatial elements, while the energy domain is covered by geometrically increasing elements (with the smallest, innermost, energy bin set to $\Delta\epsilonNu=1$~MeV).  
+We evolve until $t=100$~ms.
+
+In Figure~\ref{fig:deleptonizationProblemFluid} we plot fluid quantities versus radius at select times: $t=0$~ms (the initial condition; dotted lines), $t=3$~ms (dash-dot), $t=10$~ms (dashed), and $t=100$~ms (solid).
+The results were obtained with the DG(1)+SIRK2 scheme using 200 radial elements and 30 energy bins.  
+We plot the electron fraction (upper left panel); mass fractions of protons plus neutrons (black), alpha particles (red), and heavy nuclei (blue) (upper right panel); temperature (lower left); and entropy per baryon (lower right).
+
+\begin{figure}[h]
+  \centering
   \begin{tabular}{cc}
-      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_DensitiesVsTime.png} &
-      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_EnergiesVsTime.png}
-    \end{tabular}
-  \end{center}
-  \caption{Results from solving an NES relaxation problem with initial material properties given by Model C in Table~\ref{tab:tabulatedModels}.}
-  \label{fig:RelaxationNES}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{cc}
-      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_DensitiesVsTime_Timestep.png} &
-      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_EnergiesVsTime_Timestep.png}
-    \end{tabular}
-  \end{center}
-  \caption{Results from the NES relaxation problem with initial material properties given by Model C in Table~\ref{tab:tabulatedModels}, where the timestep $\dt$ has been set to $10^{-5}$~ms (solid lines), $10^{-4}$~ms (dashed lines), and $10^{-3}$~ms (dotted lines).
-In the left panel we plot the occupation density versus time for $\epsilonNu=11.2$~MeV (red lines) and $\epsilonNu=97.5$~MeV (blue lines).
-In the right panel we plot the fluid energy versus time.}
-  \label{fig:RelaxationNES_Timestep}
-\end{figure}
-
-\subsection{Deleptonization}
-
-We conclude with a problem mimicking the deleptonization of a collapsed stellar core.  
-To this end, we adopt an analytic density profile
-\begin{equation}
-  \rho(r)=\big[\,1-\Theta(r)\,\big]\,\rho_{1}(r)+\Theta(r)\,\rho_{2}(r)
-  \label{eq:densityProfile}
-\end{equation}
-where the function $\Theta(r)=0.5\times\big[\,1.0+\tanh\big(\,(r-r_{0})/R_{0}\,\big)\,\big]$ transitions smoothly between two density profiles, given by a Gaussian in the central region and a polynomial at larger radii; i.e.,
-\begin{align}
-  \rho_{1}(r)
-  &=\rho_{1,0}\times\exp\big[-(r/R_{1})^{2}\big]
-  \label{eq:densityProfile1} \\
-  \rho_{2}(r)
-  &=\rho_{2,0}\times\big(r/R_{2}\big)^{\alpha},
-  \label{eq:densityProfile2}
-\end{align}
-where $\rho_{1,0}>\rho_{2,0}$ and $\alpha<0$.  
-We set $\rho_{1,0}=4.5\times10^{14}$, $\rho_{1,0}=1.0\times10^{13}$, $\alpha=-4$, and $R_{1}=10$~km.  
-Then, by imposing $\rho_{1}(R_{2})=\rho_{2}(R_{2})$, we find $R_{2}=R_{1}\sqrt{\ln(\rho_{1,0}/\rho_{2,0})}\approx19.5$~km.  
-We also set $r_{0}=R_{2}$ and $R_{0}=1$~km.  
-With these parameters, the density profile given by Eqs~\eqref{eq:densityProfile}, \eqref{eq:densityProfile1}, and \eqref{eq:densityProfile2} provides a reasonable approximation to the density profile in the post-bounce phase of a realistic supernova model (cf.
-Figure~\ref{fig:analyticDensityProfile}).
-
-\begin{figure}
-  \begin{center}
-      \includegraphics[scale=0.78]{./Figures/AnalyticDensityProfile}
-  \end{center}
-  \caption{Density profile used in the deleptonization problem (solid black line; cf. Eq.~\eqref{eq:densityProfile}).  
-  It is composed of a Gaussian profile for radii $\lesssim20$~km (dashed black line), and a power law, with $\rho\propto r^{-4}$, for larger radii (dotted black line).  
-  The density profile from a full physics core-collapse supernova simulation at $100$~ms after core bounce is also plotted (solid red line).  }
-  \label{fig:analyticDensityProfile}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-	\includegraphics[width=.85\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction.png}
-	\begin{tabular}{cc}
+    \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction.png} &
+    \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MassFractions.png} \\
     \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_Temperature.png} &
@@
   \end{tabular}
-  \end{center}
-  \caption{Fluid quantities from the deleptonization problem.  Plotted versus radius for various times are electron fraction (top), temperature (bottom left), and entropy per baryon (bottom right).}
-  \label{fig:}
+  \vspace{-0.1in}
+  \flushleft\caption[Fluid quantities from the deleptonization problem.]{Fluid quantities from the deleptonization problem.
+\textmd{Plotted versus radius for various times are: electron fraction (top left), mass fractions of protons plus neutrons (black), alpha particles (red), and the mean heavy nucleus (blue; top right), temperature (bottom left), and entropy per baryon (bottom right).}}
+  \label{fig:deleptonizationProblemFluid}
 \end{figure}
 
-\begin{equation}
-  J=\int_{\bbR^{+}}\cJ\,dV_{\epsilonNu}
-\end{equation}
-
-\begin{equation}
-  f_{r}=\f{1}{J}\int_{\bbR^{+}}\cH_{r}\,dV_{\epsilonNu}
-\end{equation}
-
-\begin{equation}
-  \bar{\epsilonNu}=\f{1}{J}\int_{\bbR^{+}}\cJ\,\epsilonNu\,dV_{\epsilonNu}
-\end{equation}
-
-\begin{equation}
-  L_{r}=4\pi\,r^{2}\,\int_{\bbR^{+}}\cH_{r}\,\epsilonNu\,dV_{\epsilonNu}
-\end{equation}
-
-\begin{figure}
-  \begin{center}
+In Figure~\ref{fig:deleptonizationProblemRadiation} we plot radiation quantities versus radius at the same times as in Figure~\ref{fig:deleptonizationProblemFluid}.  
+We plot the energy-integrated density $J$ (upper left; cf.
+Eq.~\eqref{eq:averageDensity}), the average flux factor $f_{r}$ (upper right; cf.
+Eq.~\eqref{eq:averageFluxFactor}), and the mean energy $\langle\epsilonNu\rangle$ (lower left; cf.
+Eq.~\eqref{eq:meanEnergy}).
+In the lower right panel we plot the luminosity
+\begin{equation}
+  L_{r}=4\pi\,r^{2}\,\int_{\bbR^{+}}\cH_{r}\,\epsilonNu\,dV_{\epsilonNu}.  
+\end{equation}
+In these plots we have also indicated with vertical lines the radius where the optical depth,
+\begin{equation}
+  \tau(r)=\int_{\infty}^{r}\tilde{\chi}\,dr,
+\end{equation}
+equals $2/3$.  
+(The line styles correspond to those of the various radiation quantities.)
+
+\begin{figure}[h]
+  \centering
   \begin{tabular}{cc}
@@
   \end{tabular}
-  \end{center}
-  \caption{Radiation quantities from the deleptonization problem.
-Plotted versus radius for various times are neutrino number density (top left), flux factor (top right), mean energy (bottom left), and luminosity (bottom right).}
-  \label{fig:}
+  \vspace{-0.1in}
+  \flushleft\caption[Radiation quantities from the deleptonization problem.]{Radiation quantities from the deleptonization problem.
+\textmd{Plotted versus radius for various times are neutrino number density (top left), flux factor (top right), mean energy (bottom left), and luminosity (bottom right).
+The radii where the optical depth $\tau=2/3$ are indicated with vertical lines.}}
+  \label{fig:deleptonizationProblemRadiation}
 \end{figure}
 
+The evolution in this test is driven by electron capture on protons (and the inverse process; i.e., $e^{-}+p\leftrightharpoons n+\nu_{e}$).  
+For $t>0$ the electron fraction begins to decrease in the region between $r=25$~km and $r=80$~km, developing a characteristic ``trough'' in the $Y_{e}$ profile.  
+The minimum is located around $r=50$~km early on, but moves out slightly at later times.  
+The location of the minimum coincides qualitatively with the radius where $\tau=2/3$ (Figure~\ref{fig:deleptonizationProblemRadiation}).  
+The temperature and entropy per baryon responds by increasing with time in the same region (consistent with heating).  
+From the composition (determined by the equation of state), we see that the material consists mostly of neutrons and protons inside $r=25$~km (with $X_{n}\approx0.7$ and $X_{p}\approx0.3$).  
+For $r>80$, the material consists mostly of heavy nuclei.  
+Initially ($t=0$), there is a rather gradual transition from free nucleons to bound nuclei in the region between $r=25$~km and $r=80$~km.  
+At the end of the simulation, the transition from free nucleons to nuclei is rather sharp and has moved out $r\approx70$~km.  
+At this time, as a result of electron capture, the fluid consists mostly of neutrons in the region between $r=35$~km and $r=70$~km ($X_{n}\approx0.85$ and $X_{p}\approx0.15$).  
+Note that we do not include electron anti-neutrinos, so there is no process to produce protons by positron capture on neutrons.
+
+From plots of the radiation field in Figure~\ref{fig:deleptonizationProblemRadiation}, we see that the neutrinos are diffusive in the dense regions, but transition to streaming at larger radii.  
+The flux factor (upper right panel) is very small inside $r=40$~km, but increases monotonically with radius to about $0.9$ at the outer boundary.  
+In fact, the neutrino number density (upper left panel) is essentially unchanged inside $r=25$~km over the $100$~ms the simulation covers.  
+At larger radii, the neutrinos are transported in the radial direction (cf. the luminosity in the lower right panel), and the the neutrino number density profiles decrease with increasing time.  
+The luminosity is nearly constant in radius for $r>70$~km, but decreases with time from about 600~B~s$^{-1}$ at $t=3$~ms to about 40~B~s$^{-1}$ at $t=100$.  
+($1$~B $\equiv10^{51}$~erg.)
+
+To test the sensitivity of the results to resolution, we compare some of the quantities from the reference solution discussed above to results obtained with the DG(2)+SIRK2 scheme using 64 equally spaced spatial elements and 12 geometrically spaced energy bins (but keeping the smallest energy bin at $\Delta\epsilonNu=1$~MeV).
+(This represents a factor of $\sim3.5$ reduction in the total number of degrees of freedom.)  
+Results are plotted in Figure~\ref{fig:deleptonizationProblem_Resolution}, where we plot the electron fraction (left panel) and the mean neutrino energy (right panel) versus radius at $t=100$~ms.  
+The results from the reference solution (DG(1)+SIRK2) are represented by solid black curves, while the DG(2)+SIRK2 results are represented by blue open circles.  
+For the electron fraction, the results are practically indistinguishable.  
+The mean energy is underestimated by the DG(2)+SIRK2 scheme inside $r=15$~km.  
+This is due to poor spectral resolution at high neutrino energies.  
+Outside $r=30$~km, where the mean energy is lower, the agreement is very good.
+
 \begin{figure}
-  \begin{center}
-      \includegraphics[scale=0.78]{./Figures/DeleptonizationProblem1D_Spectra.png}
-  \end{center}
-  \caption{Neutrino energy spectra at various radii for $t=100$~ms (solid lines).  The dashed lines represent equilibrium spectra, computed using local thermodynamic conditions.}
-  \label{fig:}
+  \centering
+  \begin{tabular}{cc}
+    \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction_Resolution.png} &
+    \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MeanEnergy_Resolution.png}
+  \end{tabular}
+  \vspace{-0.1in}
+  \flushleft\caption[Results for the deleptonization problem where the numerical resolution has been varied.]{Results for the deleptonization problem where the numerical resolution has been varied.
+\textmd{The electron fraction (left panel) and mean neutrino energy (right panel) are plotted versus radius for $t=100$~ms.
+The black solid line is obtained with the DG(1)+SIRK2 scheme using $N_{r}\times N_{\epsilonNu}=200\times30$ elements, while blue open circles represent results obtained with the DG(2)+SIRK2 scheme using $64\times12$ elements.}}
+  \label{fig:deleptonizationProblem_Resolution}
 \end{figure}
 
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{cc}
-      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction_SpatialResolution.png} &
-      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MeanEnergy_SpatialResolution.png} \\
-      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction_SpectralResolution.png} &
-      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MeanEnergy_SpectralResolution.png}
-    \end{tabular}
-  \end{center}
-  \caption{Results for the deleptonization problem where the spatial and spectral resolution has been varied: the electron fraction (left panels) and mean energy (right panel) are plotted versus radius for $t=100$~ms.}
-  \label{fig:}
-\end{figure}
-
-\section{Miniapp: Collapse of Stellar Iron Core}
-
-\bibliographystyle{apj}
-\bibliography{../References/references.bib}
-
-\appendix
-
-\clearpage
-
-\section{Eigenvalues and Eigenvectors for the Two-Moment Model}
+\begin{center}
+  \section{SUMMARY}
+  \label{sec:summary}
+\end{center}
+
+We have presented details of a numerical method for solving the multi-group, two-moment model for neutrino transport.  
+The discontinuous Galerkin (DG) method is used for spatial and energy discretization, while a semi-implicit Runge-Kutta method is used for time integration, where the hyperbolic streaming part is treated explicitly and the stiff terms modeling neutrino-matter interactions are treated implicitly.
+The method can solve multi-group transport problems in Cartesian, spherical, and cylindrical coordinates in one spatial dimension.  
+We have demonstrated the accuracy of the method with a series of benchmark problems, including smooth problems with analytical solutions, a Riemann problem, diffusion problems in thin and thick regimes, and tests relevant to astrophysics covering both opaque and streaming regimes.
+We have also detailed the tabulation of an initial set of neutrino-matter interactions (for electron neutrinos) relevant for core-collapse supernova (CCSN) simulations.  
+This initial set includes electron capture and elastic scattering on nucleons and nuclei, and inelastic neutrino-electron scattering (NES).  
+We have also presented results from multi-group simulations that use these tabulated opacities.  
+(Tests involving NES have been deferred to a future publication.)
+
+The algorithms are implemented in the Toolkit for High-Order Neutrino-Radiation Hydrodynamics (\thornado), and a limited version of the code has been made publicly available on GitHub\footnote{\url{https://github.com/ECP-Astro/thornado_mini}}.
+This release includes the deleptonization problem (including some of the data) presented in Section~\ref{sec:deleptonizationProblem}.
+
+The current report details initial steps toward the longer-term goal of deploying high-order DG methods to simulate CCSN explosions.  
+Next steps for the near term include extension to multiple spatial dimensions, inclusion of a larger suite of neutrino-matter interactions, and inclusion of multiple neutrino species (to ultimately include electron, muon, and tau neutrinos, and the corresponding antiparticles).
+For the longer term, extensions will include coupling to self-gravitating hydrodynamics, relativity, and special attention to preservation of integration constants in neutrino-radiation hydrodynamics simulations.
+
+\newpage
+\clearemptydoublepage
+
+\newpage
+\clearemptydoublepage
+
+\begin{center}
+\section{REFERENCES}
+\end{center}
+
+\bibliography{references.bib}
+
+\bibliographystyle{plainnat}
+
+\clearemptydoublepage
+
+\newpage
+
+\renewcommand{\thepage}{A-\arabic{page}} 
+\setcounter{page}{1}
+%\thispagestyle{mypagestylepublic}        % Use for "Not for public release." in footer with no page numbers
+%\thispagestyle{mypagestyleempty}    % Use for "OUO" in footer with no page numbers  
+\thispagestyle{empty}
+
+\vspace*{4in}
+\phantomsection
+\addcontentsline{toc}{section}{APPENDIX A. EIGENVALUES AND EIGENVECTORS FOR THE TWO-MOMENT MODEL}
+\begin{center}
+{\bf\Large{APPENDIX A. EIGENVALUES AND EIGENVECTORS FOR THE TWO-MOMENT MODEL}}
+\end{center}
+
+\clearemptydoublepage
+
+\newpage
+
+\renewcommand{\thepage}{A-\arabic{page}} 
+\setcounter{page}{3}
+
+\begin{center}
+{\bf\large {APPENDIX A.  EIGENVALUES AND EIGENVECTORS FOR THE TWO-MOMENT MODEL}}
+\end{center}
+
 \label{sec:eigenstructure}
@@
 Here we list eigenvalues and eigenvectors for the flux Jacobian associated with the hyperbolic system in Eq.~\eqref{eq:momentEquationsCompact}.  
+These are used to perform limiting in characteristic variables (cf. Section~\ref{sec:slopeLimiters}).  
 To this end, we define the Eddington tensor
@@
 
-Computing the flux Jacobian in the $1$-dimension, using the metric tensor in Eq.~\eqref{eq:threeMetric} and simplifying by setting $h^{2},h^{3}=0$ so that $h^{1}h_{1}=1$, gives
+Computing the flux Jacobian in the $1$-dimension, using the metric tensor in Eq.~\eqref{eq:threeMetric}, and simplifying by setting $h^{2},h^{3}=0$ so that $h^{1}h_{1}=1$, gives
 \begin{equation}
@@
 
-The corresponding right and left eigenvectors are given by the columns and rows, respectively of the matrices
+The corresponding eigenvectors are given by the columns and rows, respectively of the matrices
 \begin{equation}
@@
 
-\clearpage
-
-\section{Moment Equations in Commonly Used Coordinate Systems}
+\newpage
+
+\renewcommand{\thepage}{B-\arabic{page}} 
+\setcounter{page}{1}
+%\thispagestyle{mypagestylepublic}        % Use for "Not for public release." in footer with no page numbers
+%\thispagestyle{mypagestyleempty}    % Use for "OUO" in footer with no page numbers  
+\thispagestyle{empty}
+
+\vspace*{4in}
+\phantomsection
+\addcontentsline{toc}{section}{APPENDIX B. MOMENT EQUATIONS IN COMMONLY USED COORDINATE SYSTEMS}
+\begin{center}
+{\bf\Large{APPENDIX B. MOMENT EQUATIONS IN COMMONLY USED COORDINATE SYSTEMS}}
+\end{center}
+
+\clearemptydoublepage
+
+\newpage
+
+\renewcommand{\thepage}{B-\arabic{page}} 
+\setcounter{page}{3}
+
+\begin{center}
+{\bf\large {APPENDIX B.  MOMENT EQUATIONS IN COMMONLY USED COORDINATE SYSTEMS}}
+\end{center}
 \label{app:CurvilinearEuler}
 
-\subsection{Cylindrical Coordinates}
+Here we provide explicit expressions for the hyperbolic part of the moment equations in cylindrical and spherical polar coordinates.
+
+\subsection{CYLINDRICAL COORDINATES}
 
@@
 
-\subsection{Spherical Coordinates}
+\subsection{SPHERICAL COORDINATES}
 

### 2018-09-26 Documents/M1/ornlReport/ornlmacro.tex
ornl report on transport

\setcounter{secnumdepth}{5}
\usepackage{titlesec} 
\usepackage{parskip}
\usepackage[T1]{fontenc}   
\usepackage{blindtext} 
\usepackage{txfonts} 
\usepackage{graphicx} 
\usepackage{array} 
\usepackage{xcolor} 
\usepackage{wrapfig} 
\usepackage[font=bf]{caption} 
\usepackage{setspace}
\usepackage{tocloft} 
\usepackage{fancyhdr} 
\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} 
\usepackage[hidelinks]{hyperref} 
\usepackage[flushleft]{threeparttable}
\usepackage{fncychap} 
\usepackage{fullpage} 
\usepackage{epsf} 
\usepackage{bm} 
\usepackage{rotating} 
\usepackage{wallpaper} 
\usepackage{sectsty}
\usepackage{framed, color}
\usepackage{float}
\usepackage{calc}
\usepackage{multirow}
\usepackage{natbib}       % Use if using a database of references usually name.bib file.

\definecolor{shadecolor}{RGB}{0,121,52}
\sectionfont{\fontsize{11}{11}\selectfont}

\titleformat{\section}
	{\normalfont\large\bfseries\centering\uppercase}{\thesection}{1em}{}
\titleformat{\subsection}
	{\normalfont\large\bfseries\uppercase}{\thesubsection}{1em}{}
\titleformat{\subsubsection} 
	{\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}
\titleformat{\paragraph} 
	{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}

\renewcommand*{\figurename}{Figure} 
\renewcommand\thefigure{\arabic{figure}}
\renewcommand\thetable{\arabic{table}}
\captionsetup{labelsep=period} 
\newcommand{\clearemptydoublepage}{\newpage{\pagestyle{empty}\cleardoublepage}}
\newcommand{\nd}{\noindent}
\newcommand{\leaderfill}{}

\renewcommand{\cfttoctitlefont}{\large\bfseries\MakeUppercase}
\renewcommand{\cftloftitlefont}{\large\bfseries\MakeUppercase}
\renewcommand{\cftlottitlefont}{\large\bfseries\MakeUppercase}

\renewcommand{\thesection}{\arabic{section}.}
\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}}
\renewcommand{\thesubsubsection}{\arabic{section}.{\arabic{subsection}.\arabic{subsubsection}}}
\renewcommand{\theparagraph}{\arabic{section}.{\arabic{subsection}.{\arabic{subsubsection}.\arabic{paragraph}}}}

\renewcommand{\cftsecfont}{\normalfont}
\renewcommand{\cftsecpagefont}{\normalfont}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

%\newcommand{\eqt}[1]{Eq.~(\ref{#1})}                     % equation
%\newcommand{\eqts}[1]{Eqs.~(\ref{#1})}                     % equation
%\newcommand{\fig}[1]{Fig.~\ref{#1}}                      % figure
%\newcommand{\tbl}[1]{Table~\ref{#1}}                     % table
%\newcommand{\sct}[1]{Section~\ref{#1}}                   % section

\raggedright

\makeatletter
\renewcommand\@tocrmarg{.5in plus .5fil} 
\makeatother

\setlength{\footskip}{65pt}

\setlength{\cftbeforesecskip}{0pt}

\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\\
\vspace{12pt}}

%create a command for fonts on the front cover
   \newcommand{\CoverFont}[4]{
     \fontencoding{OT1}
     \fontfamily{phv}
     \fontseries{#1}
     \fontshape{#2}
     \fontsize{#3}{#4}
     \selectfont
   }

%create a command for Draft. Not for public release.
   \newcommand{\DraftBox}{
     \noindent
    \vskip 24pt
     \begin{minipage}{.45\textwidth}
     \begin{center}
     \begin{framed} 
     \large{\bfseries{\textsf{Draft. Not for public release.}}}\\
     \end{framed}
     \end{center}
     \end{minipage}
     }

%create a command for Not for public release.
   \newcommand{\NotPublic}{
     \noindent
    \vskip 24pt
     \begin{minipage}{.45\textwidth}
     \begin{center}
     \begin{framed} 
     \large{\bfseries{\textsf{Not for public release.}}}\\
     \end{framed}
     \end{center}
     \end{minipage}
     }

\fancypagestyle{mypagestylepublic}{  % without page numbers
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C] {Not for public release.} 
}

\fancypagestyle{mypagestylepublicpage}{   % with page numbers
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C] {Not for public release. \\
 \thepage}  
}

%create a command for Approved for public release.
   \newcommand{\ApprovedBox}{
     \noindent
    \vskip 24pt
     \begin{minipage}{.45\textwidth}
     \begin{center}
     \begin{framed} 
     \large{\bfseries{\textsf{Approved for public release. \\
     Distribution is unlimited.}}}\\
     \end{framed}
     \end{center}
     \end{minipage}
     }

%create a command for Business Sensitive.
   \newcommand{\BusSenBox}{
     \noindent
    \vskip 24pt
     \begin{minipage}{.45\textwidth}
     \begin{center}
     \begin{framed} 
     \large{\bfseries{\textsf{Business Sensitive}}}\\
     \end{framed}
     \end{center}
     \end{minipage}
     }

%create a command for CRADA final.
   \newcommand{\CRADABox}{
     \noindent
    \vskip 24pt
     \begin{minipage}{.45\textwidth}
     \begin{center}
     \begin{framed} 
     \large{\bfseries{\textsf{CRADA final report for \\
     CRADA number NFE-XX-XXXXX}}}\\
     \end{framed}
 \begin{framed} 
     \large{\bfseries{\textsf{Approved for public release. \\
     Distribution is unlimited.}}}\\
     \end{framed}
     \end{center}
     \end{minipage}
     }

%create a command for Official Use Only
   \newcommand{\OUOBox}{
    \noindent
    \vskip 12pt
    \hspace{-.2in}
    \fbox{
    \begin{minipage}[t]{0.525\textwidth}
    \vspace{2pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{10}{11pt}
    \hspace*{\fill} {OFFICIAL USE ONLY \hspace*{\fill} \\
    \CoverFont{mc}{n}{9}{10pt}
    \underline {\smash{May}} be exempt from public release under the Freedom of Information Act \\
(5 U.S.C. 552), exemption number and category: 
    \CoverFont{mc}{n}{9}{10pt} \underline{\smash{Choose an item.}} \\
% Choose an item.
% 3. Statutary Exemption
% 4. Commercial/Proprietary
% 5. Privileged Information
% 6. Personal Privacy
% 7. Law Enforcement
% 9. Wells
    Department of Energy review required before public release \\
    \vspace{0.1in}
    \CoverFont{mc}{n}{9}{10pt}
    Name/Org:  \underline{\smash{Click here to enter text}} Date: \underline{\smash{Click here to enter date}}\\
    \CoverFont{mc}{n}{9}{10pt}
    Guidance (if applicable): \underline{\smash{Click here to enter text}}}} \\
    \end{minipage}
    }}

\fancypagestyle{mypagestyle}{   % With page numbers
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C] {OFFICIAL USE ONLY \\
 \thepage}  
}

\fancypagestyle{mypagestyleempty}{   % Without page numbers
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C] {OFFICIAL USE ONLY} 
}

%create a command for Export Controlled Information
   \newcommand{\ECIBox}{
    \noindent
    \vskip 12pt
    \hspace{-.2in}
    \fbox{
    \begin{minipage}[t]{0.525\textwidth}
    \vspace{2pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{10}{11pt}
    \hspace*{\fill} {EXPORT CONTROLLED INFORMATION \hspace*{\fill} \\
    \CoverFont{mc}{n}{9}{10pt}
    Contains technical information whose export is restricted by 
    \CoverFont{mc}{n}{9}{10pt} \underline{\smash{Enter statute here.}} Violations may result in administrative, civil, and/or criminal penalties. Limit dissemination to U.S. persons.\\
  \CoverFont{mc}{n}{9}{10pt}
    The cognizant program manager must approve other dissemination. This notice shall not be separated from the attached document.\\
    \vspace{0.1in}
    \CoverFont{mc}{n}{9}{10pt}
    Reviewer (Signature) \underline{\smash{Click here to enter signature}} \\
    \CoverFont{mc}{n}{9}{10pt}
    Date \underline{\smash{Click here to enter date}}}} \\
    \end{minipage}
    }}

%create a command for Unclassified Controlled Nuclear Information
   \newcommand{\UCNIBox}{
    \noindent
    \vskip 12pt
    \hspace{-.2in}
    \fbox{
    \begin{minipage}[t]{0.575\textwidth}
    \vspace{2pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{9}{10pt}
    \hspace*{\fill} {UNCLASSIFIED CONTROLLED NUCLEAR INFORMATION\hspace*{\fill} \\
    \CoverFont{mc}{n}{9}{10pt}
    \centering{NOT FOR PUBLIC DISSEMINATION} \\
    \CoverFont{mc}{n}{9}{10pt}
    \flushleft {Unauthorized dissemination subject to civil and criminal sanctions} \\
    \CoverFont{mc}{n}{9}{10pt}
    under section 148 of the Atomic Energy Act of 1954, as amended (42 U.S.C. 2168).\\
    \vspace{0.05in}
    \CoverFont{mc}{n}{9}{10pt}
    \textbf{REVIEWING OFFICIAL:} \underline{\smash{Click here to enter signature}} \\
    \vspace{0.05in}
    \CoverFont{mc}{n}{9}{10pt}
     \textbf{Date:} \underline{\smash{Click here to enter date}} \\
    \vspace{0.05in}
    \CoverFont{mc}{n}{9}{10pt}
     \textbf{Guidance Used:} \underline{\smash{Insert guidance here}} \\
    \vspace{0.05in}
    \CoverFont{mc}{n}{9}{10pt}
    \underline{\smash{Insert more guidance in this area}} \\
    \vspace{0.05in}
    \CoverFont{mc}{n}{9}{10pt}
    \centering{(List all UCNI guidance Used)} }} \\
     \end{minipage}
    }}

%create a command for Official Use Only and Export Controlled Information
   \newcommand{\OUOECIBox}{
    \noindent
    \vskip 12pt
    \hspace{-.2in}
    \fbox{
    \begin{minipage}[t]{0.525\textwidth}
    \vspace{2pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{10}{11pt}
    \hspace*{\fill} {OFFICIAL USE ONLY \hspace*{\fill} \\
    \CoverFont{mc}{n}{9}{10pt}
    \underline {\smash{May}} be exempt from public release under the Freedom of Information Act \\
(5 U.S.C. 552), exemption number and category: 
    \CoverFont{mc}{n}{9}{10pt} \underline{\smash{Choose an item.}} \\
% Choose an item.
% 3. Statutary Exemption
% 4. Commercial/Proprietary
% 5. Privileged Information
% 6. Personal Privacy
% 7. Law Enforcement
% 9. Wells
    Department of Energy review required before public release \\
    \vspace{0.1in}
    \CoverFont{mc}{n}{9}{10pt}
    Name/Org:  \underline{\smash{Click here to enter text}} Date: \underline{\smash{Click here to enter date}}\\
    \CoverFont{mc}{n}{9}{10pt}
    Guidance (if applicable): \underline{\smash{Click here to enter text}}}} \\
\rule{85mm}{.3pt}\\
    \vspace{3pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{10}{11pt}
    \hspace*{\fill} {EXPORT CONTROLLED INFORMATION \hspace*{\fill} \\
    \CoverFont{mc}{n}{9}{10pt}
    Contains technical information whose export is restricted by 
    \CoverFont{mc}{n}{9}{10pt} \underline{\smash{Enter statute here.}} Violations may result in administrative, civil, and/or criminal penalties. Limit dissemination to U.S. persons.\\
  \CoverFont{mc}{n}{9}{10pt}
    The cognizant program manager must approve other dissemination. This notice shall not be separated from the attached document.\\
    \vspace{0.1in}
    \CoverFont{mc}{n}{9}{10pt}
    Reviewer (Signature) \underline{\smash{Click here to enter signature}} \\
    \CoverFont{mc}{n}{9}{10pt}
    Date \underline{\smash{Click here to enter date}}}} \\
    \end{minipage}
    }}

%create a command for Official Use Only and Applied Technology
   \newcommand{\OUOATBox}{
    \noindent
    \vskip 12pt
    \hspace{-.2in}
    \fbox{
    \begin{minipage}[t]{0.525\textwidth}
    \vspace{2pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{10}{11pt}
    \hspace*{\fill} {OFFICIAL USE ONLY \hspace*{\fill} \\
    \CoverFont{mc}{n}{9}{10pt}
    \underline {\smash{May}} be exempt from public release under the Freedom of Information Act \\
(5 U.S.C. 552), exemption number and category: 
    \CoverFont{mc}{n}{9}{10pt} \underline{\smash{Choose an item.}} \\
% Choose an item.
% 3. Statutary Exemption
% 4. Commercial/Proprietary
% 5. Privileged Information
% 6. Personal Privacy
% 7. Law Enforcement
% 9. Wells
    Department of Energy review required before public release \\
    \vspace{0.1in}
    \CoverFont{mc}{n}{9}{10pt}
    Name/Org:  \underline{\smash{Click here to enter text}} Date: \underline{\smash{Click here to enter date}}\\
    \CoverFont{mc}{n}{9}{10pt}
    Guidance (if applicable): \underline{\smash{Click here to enter text}}}} \\
\rule{85mm}{.3pt}\\
    \vspace{3pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{10}{11pt}
    \hspace*{\fill} {APPLIED TECHNOLOGY \hspace*{\fill} \\
    \CoverFont{mc}{n}{9}{10pt}
      Any further distribution by any holder of this document or data therein to third parties representing foreign interests, foreign governments, foreign companies, and foreign subsidiaries or foreign divisions of U.S. companies shall be approved by the [ \emph {insert appropriate NE Program Office Officials} ], U.S. Department of Energy.  Further, foreign party release may require the DOE approval pursuant to Federal Regulation 10 CFR Part 810, and/or may be subject to Section 127 of the Atomic Energy Act.\\ }}
    \end{minipage}
    }}

%create a command for Official Use Only, Export Controlled Information, and Applied Technology
   \newcommand{\OUOECIATBox}{
    \noindent
%    \vskip 6pt
    \hspace{-.2in}
    \fbox{
    \begin{minipage}[t]{0.645\textwidth}
    \vspace{2pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{9}{10pt}
    \hspace*{\fill} {OFFICIAL USE ONLY \hspace*{\fill} \\
    \CoverFont{mc}{n}{8}{9pt}
    \underline {\smash{May}} be exempt from public release under the Freedom of Information Act \\
(5 U.S.C. 552), exemption number and category: 
    \CoverFont{mc}{n}{8}{9pt} \underline{\smash{Choose an item.}} \\
% Choose an item.
% 3. Statutary Exemption
% 4. Commercial/Proprietary
% 5. Privileged Information
% 6. Personal Privacy
% 7. Law Enforcement
% 9. Wells
    Department of Energy review required before public release \\
    \vspace{0.1in}
    \CoverFont{mc}{n}{8}{9pt}
    Name/Org:  \underline{\smash{Click here to enter text}} Date: \underline{\smash{Click here to enter date}}\\
    \CoverFont{mc}{n}{8}{9pt}
    Guidance (if applicable): \underline{\smash{Click here to enter text}}}} \\
\rule{85mm}{.3pt}\\
    \vspace{3pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{9}{10pt}
    \hspace*{\fill} {EXPORT CONTROLLED INFORMATION \hspace*{\fill} \\
    \CoverFont{mc}{n}{8}{9pt}
    Contains technical information whose export is restricted by 
    \CoverFont{mc}{n}{8}{9pt} \underline{\smash{Enter statute here.}} Violations may result in administrative, civil, and/or criminal penalties. Limit dissemination to U.S. persons.\\
  \CoverFont{mc}{n}{8}{9pt}
    The cognizant program manager must approve other dissemination. This notice shall not be separated from the attached document.\\
    \vspace{0.1in}
    \CoverFont{mc}{n}{8}{9pt}
    Reviewer (Signature) \underline{\smash{Click here to enter signature}} \\
    \CoverFont{mc}{n}{8}{9pt}
    Date \underline{\smash{Click here to enter date}}}} \\
\rule{85mm}{.3pt}\\
    \vspace{3pt}
    \raggedright
    \textnormal{
    \CoverFont{b}{n}{9}{10pt}
    \hspace*{\fill} {APPLIED TECHNOLOGY \hspace*{\fill} \\
    \CoverFont{mc}{n}{8}{9pt}
      Any further distribution by any holder of this document or data therein to third parties representing foreign interests, foreign governments, foreign companies, and foreign subsidiaries or foreign divisions of U.S. companies shall be approved by the [ \emph {insert appropriate NE Program Office Officials} ], U.S. Department of Energy.  Further, foreign party release may require the DOE approval pursuant to Federal Regulation 10 CFR Part 810, and/or may be subject to Section 127 of the Atomic Energy Act.\\ }}
    \end{minipage}
    }}

### 2018-09-26 Documents/M1/Astronum_2018/sections/intro.tex
Comments on paper

@@
 Core-collapse supernovae (CCSNe) are the explosion happens at the end of a massive star's life.
-They are the source of heavy elements and play an important role in many astrophysical phenomena, such as neutron star and black hole formation.
-Furthermore, these explosions combines extreme energetic and densities with nuclear, particle and relativistic physics. 
+They are a dominant source of heavy elements and play an important role in many astrophysical phenomena, such as neutron star and black hole formation.  
+Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
 A solid theoretical framework for these explosion mechanism will illuminate explanations to many import questions in fundamental physics.
@@
 Solving Boltzmann transport multi-dimensional with high accuracy requirement can be expensive.
+\ee{Balance physical fidelity and computational expediency?}
 One alternation is sacrificing the accuracy: instead of solving Boltzmann transport equations, solve moment equation for an approximate solution.
+\ee{What are moments?}
 This kind method is moment method and we focus on two-moment method in this paper.
@@
 To be precisely, neutrino interact with the background rapidly and its characteristic time scalar is so small comparing to the length of CCSNe explosion process. 
-It makes the time step needed by an explicit time integrator dramatic large and a huge mount of calculation needed. 
+It makes the time step needed by an explicit time integrator dramatic small and a huge mount of calculation needed. 
+\ee{Discuss fully implicit approach?}
 To manipulate this challenge, implicit-explicit (IMEX) methods are taken into consideration.
@@
 However, price needs to be paid for the lunch.  
+\ee{Nonlinear equations, closure, well-posedness of closure requires realizable moments}
+\ee{What is moment realizability}
 Two-moment method requires a realizability-preserving algebraic closure for fermion.
-IMEX methods should be diffusion limit accurate. 
+IMEX methods should be diffusion limit accurate \ee{why?}. 
 The discussion of these prices drives this paper. 
+\ee{Moment realizabilty and diffusion accurate IMEX scheme motivates this work}
 
-This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closure and the realizability-preserving property of algebraic closure;
-Section~\ref{se:SpacialDiscretization} gives more information of the spacial discretization; Section~\ref{se:TimeIntegration} discusses how to construct a constraint-preserving, diffusion limit accurate IMEX (PD-ARS) scheme and two PD-ARS schemes are presented; Section~\ref{se:NumericalTests} gives the result of the numerical tests of the PD-ARSs; Section~\ref{se:Conclusion} is the conclusion section.
+This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and realizability algebraic closures in the context of Fermi-Dirac statistics;
+Section~\ref{se:SpacialDiscretization} we discuss moment realizability in the context of a first-order finite volume spatial discretization; Section~\ref{se:TimeIntegration} discusses how to construct a constraint-preserving, diffusion limit accurate IMEX (PD-ARS) scheme and two PD-ARS schemes are presented \ee{should we introduce the term PD-ARS here?}; Section~\ref{se:NumericalTests} gives the result of the numerical tests of the PD-ARSs; Section~\ref{se:Conclusion} is the conclusion section.

### 2018-09-28 Documents/M1/Astronum_2018/sections/Numerical.tex
Updated the introduction section.

@@
   \end{tabular}
-   \caption{Thermal state plot (left) and neutrino absorptivity ($\chi$) and neutrino elastic scattering opacity ($\sigma$) in space (right) for the neutrino stationary state test.}
+   \caption{Thermal state plot (left) and neutrino absorptivity ($\sigma_{\Ab}$) and neutrino elastic scattering opacity ($ \sigma_{\Scatt}$) in space (right) for the neutrino stationary state test.}
    \label{fig:NeutrinoStationaryTestEOS}

### 2018-09-28 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Updated introduction section and backup.
Updated the introduction section.

@@
-\section{Two-Moment Model}
+\section{Two-Moment Model}\label{se:Two-MomentModel}
 
 \subsection{Transport Equations}
-Considering some massless fermion pass through a static material and only emission, absorption and elastic scattering exist, the transport equation of the fermion after scaling to dimensionless units can be written as
+Considering the neutrino pass through a static dense matter and only emission, absorption and elastic scattering exist, the transport equation of the fermion after scaling to dimensionless units can be written as
 \begin{equation}
@@
 \end{equation}
-where $\xi$ is the emission and absorption contribution parameter: $\xi = 1$ for pure emission and absorption, or no scattering; $\xi = 0$ for pure scattering. 
+where $\xi = \sigma_{\Ab} / \sigma_{\Scatt} $ is the emission and absorption contribution parameter: $\xi = 1$ for pure emission and absorption, or no scattering; $\xi = 0$ for pure scattering. 
 $f_{0}$ is the fermion equilibrium distribution function which has the following form:

### 2018-09-28 Documents/M1/Astronum_2018/sections/intro.tex
Updated the introduction section.

--- 2018-09-25 Documents/M1/Astronum_2018/sections/intro.tex
@@
 One essential part of the explosion mechanism is neutrino transport which drives the explosion.  
-Neutrino transport is modeled by Boltzmann transport equation, which is partial differential equation and evolves the distribution function $f$.
+Neutrino transport is modeled by Boltzmann transport equation, which is partial differential equation and evolves a phase space distribution function $f$.
 Simulating the neutrino transport is finding a solution of Boltzmann transport equation for a given domain and period with an acceptable accuracy.
 
-Solving Boltzmann transport multi-dimensional with high accuracy requirement can be expensive.
-One alternation is sacrificing the accuracy: instead of solving Boltzmann transport equations, solve moment equation for an approximate solution.
-This kind method is moment method and we focus on two-moment method in this paper.
+Solving multi-dimensional Boltzmann transport equation can be expensive.
+To balance physical fidelity and computational expediency, an approximation method called two-moment method is investigated.
+In two-moment method, the evolve values are the angular moments of the distribution function $f$, the spectral particle density $\cJ$ and flux $\bcH$, which are the zeroth angular moment and the first angular moment, respectively.
 
@@
 To be precisely, neutrino interact with the background rapidly and its characteristic time scalar is so small comparing to the length of CCSNe explosion process. 
-It makes the time step needed by an explicit time integrator dramatic large and a huge mount of calculation needed. 
+It makes the time step needed by an explicit time integrator small and a lot of calculation needed. 
+Moreover, solving the moment equations fully implicitly requires diagonalization of band structure matrices whose sizes depend on the space discretization and makes the simulation expensive.
 To manipulate this challenge, implicit-explicit (IMEX) methods are taken into consideration.
-By taking advantage of the fact that collision terms are local, IMEX methods are able to make the time integrator more efficient in diffusion dominate region.
+By treating the transport term explicitly and the collision term implicitly, IMEX methods subject only to a time step governed by the explicit transport term and the matrix it needs to diagonal is diagonal dominate in most of interested region.
 
-However, price needs to be paid for the lunch.
-Two-moment method requires a realizability-preserving algebraic closure for fermion.
-IMEX methods should be diffusion limit accurate. 
-The discussion of these prices drives this paper.
+To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a constraint-preserving diffusion accurate IMEX schemes for ensure a valid result.
+Here is the explanation.
+First of all, the Boltzmann transport equation is a nonlinear equation.
+Its integral form which gives the two-moment method requires the information of $(i+1)$-th order moment for $i$-th order moment evolution.
+Therefore, two-moment method needs a algebraic closure which gives a approximated value of the second order moment $\bcK$ given $\cJ$ and $\bcH$.
+Second, the angular moments are confined.
+Since a neutrino distribution function is confined ($f\in(0,1)$) by the Pauli exclusion principle, its moments as integrals of a confined function over confined domain ($\omega\in\bbS^{2}$) are also confined.
+We call the moments satisfying a Fermi-Dirac statistics realizable moments.
+Hence, the algebraic closure should give a realizable $\bcK$ and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
+Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a constraint-preserving IMEX.
+Fourth, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.\ee{why?}. 
+Moment realizabilty and diffusion accurate IMEX scheme motivates this work
 
-This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closure and the realizability-preserving property of algebraic closure;
-Section~\ref{se:SpacialDiscretization} gives more information of the spacial discretization; Section~\ref{se:TimeIntegration} discusses how to construct a constraint-preserving, diffusion limit accurate IMEX (PD-ARS) scheme and two PD-ARS schemes are presented; Section~\ref{se:NumericalTests} gives the result of the numerical tests of the PD-ARSs; Section~\ref{se:Conclusion} is the conclusion section.
+This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and realizability algebraic closures in the context of Fermi-Dirac statistics;
+Section~\ref{se:SpacialDiscretization} we discuss moment realizability in the context of a first-order finite volume spatial discretization; Section~\ref{se:TimeIntegration} discusses how to construct a constraint-preserving, diffusion limit accurate IMEX (PD-ARS) scheme and two PD-ARS schemes are presented %\ee{should we introduce the term PD-ARS here?};
+Section~\ref{se:NumericalTests} gives the result of the numerical tests of the PD-ARSs; Section~\ref{se:Conclusion} is the conclusion section.

### 2018-09-28 Documents/M1/Astronum_2018/sections/intro.tex
Modified the introduction section.

@@
 Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a constraint-preserving IMEX.
-Fourth, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.\ee{why?}. 
-Moment realizabilty and diffusion accurate IMEX scheme motivates this work
+Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.
+Fourth, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.
+[citation] showed standard IMEX scheme can't have an order higher than first.
+To have second-order (or higher-order) accuracy, some correction steps are needed.
+However, the correction step can deteriorate the accuracy of the IMEX in the diffusion limit and restrict the time step.
+To keep simple, we focus on the IMEX scheme without correction step and require it high-order (second or higher order) in the streaming limit and diffusion accurate.
+We call these IMEX scheme PD-ARS.
+The study of moment realizabilty and constraint-preserving diffusion accurate IMEX scheme motivates this work.
 
-This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and realizability algebraic closures in the context of Fermi-Dirac statistics;
-Section~\ref{se:SpacialDiscretization} we discuss moment realizability in the context of a first-order finite volume spatial discretization; Section~\ref{se:TimeIntegration} discusses how to construct a constraint-preserving, diffusion limit accurate IMEX (PD-ARS) scheme and two PD-ARS schemes are presented %\ee{should we introduce the term PD-ARS here?};
-Section~\ref{se:NumericalTests} gives the result of the numerical tests of the PD-ARSs; Section~\ref{se:Conclusion} is the conclusion section.
+This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and the constraints on the moments and algebraic closures imposed by Fermi-Dirac statistics;
+Section~\ref{se:SpacialDiscretization} gives a first-order finite volume spatial discretization and shows how the spatial discretization preserve constraints in a IMEX step;
+Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct PD-ARS and two PD-ARSs, one has second-order in the streaming limit and the other has third-order, are provided;
+Section~\ref{se:NumericalTests} presents the results of the numerical tests which demonstrate the portieres of the PD-ARSs; Section~\ref{se:Conclusion} summaries the achievement of this paper.

### 2018-09-28 Documents/M1/Astronum_2018/sections/Conclusion.tex
Modified the two-moment method section.

\section{Conclusion}\label{se:Conclusion}

This is the conclusion section ...

### 2018-09-28 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Modified the two-moment method section.

@@
 \subsection{Transport Equations}
-Considering the neutrino pass through a static dense matter and only emission, absorption and elastic scattering exist, the transport equation of the fermion after scaling to dimensionless units can be written as
+Considering the neutrino pass through a static dense matter and only emission, absorption and elastic scattering exist, the transport equation of the neutrino after scaling to dimensionless units can be written as
 \begin{equation}
   \pd{f}{t}+\vect{\ell}\cdot\nabla f
-  =\f{1}{\tau}\,\cC(f).
+  =\f{1}{\tau}\,\cC(f),
   \label{eq:boltzmann}
 \end{equation}
-whic is known as Boltzmann equation.
-The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of particles propagating in the direction $\omega\in\bbS^{2}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
-$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector which parallel to the fermion three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
-On the right-hand side, $\tau$ is interaction strength parameter: $\tau\ll1$ for opaque (strong interaction with the background) region while $\tau\gg1$ for transparent (weak interaction with the background, or free streaming) region.
+which is known as Boltzmann equation.
+The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrino propagating in the direction $\omega\in\bbS^{2}$, with neutrino energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
+$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector which parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
+On the right-hand side, $\tau$ is interaction strength parameter: $\tau\ll1$ for opaque region where neutrino has strong interaction with the background; $\tau\gg1$ for transparent region where neutrino has weak interaction with the background and streams freely.
 $\cC(f)$ is the collision term, which models emission, absorption, and isotropic and elastic scattering: 
@@
 \end{equation}
-where $\xi = \sigma_{\Ab} / \sigma_{\Scatt} $ is the emission and absorption contribution parameter: $\xi = 1$ for pure emission and absorption, or no scattering; $\xi = 0$ for pure scattering. 
-$f_{0}$ is the fermion equilibrium distribution function which has the following form:
+with $\xi = \sigma_{\Ab} / (\sigma_{\Ab}  + \sigma_{\Scatt} )$ be the emission and absorption contribution parameter: $\xi = 1$ when the scattering opacity $\sigma_{\Scatt} = 0$, pure emission and absorption; $\xi = 0$ when the absorption opacity $\sigma_{\Ab} = 0$, pure scattering.
+$f_{0}$ is the neutrino equilibrium distribution function which has the following form:
 \begin{equation}
-  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1},  
+  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1}.
   \label{eq:fermiDirac}
 \end{equation}
-where $T$ is the temperature in energy unit, and $\mu$ is the fermion chemical potential.
-Both of them depend on the properties of the background.
+$T(\vect{x})$ is the temperature in energy unit and $\mu(\vect{x})$ is the neutrino chemical potential.
+Both of them depend on the properties of the background as a function of $\vect{x}$.
 
 \subsection{Two-Moment Model}
-An approximate solution of Boltzmann equation Eq.~\eqref{eq:boltzmann} can be found by using two-moment model.
-In two-moment model, the angular moments of the distribution function are defined as
+An approximate solution of Boltzmann equation Eq.~\eqref{eq:boltzmann} can be found by employing two-moment model.
+Define the angular moments of the distribution function as following
 \begin{equation}
   \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
-  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega.  
+  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega,
   \label{eq:angularMoments}
 \end{equation}
-with $\vect{z}:=\{\varepsilon,\vect{x}\}$.
-The zeroth moment $\cJ$ is referred as the particle density, while the first moment $\bcH$ the particle flux and the second moment $\bcK$ the stress tensor.
-Besides, define $\vect{\cM}=(\cJ,\vect{\cH})^{T}$ and $\vect{\cF}=(\vect{\cH},\vect{\cK})^{T}$, then take the zeroth and first moment of Eq.~\eqref{eq:boltzmann}, we have
+where $\vect{z}:=\{\varepsilon,\vect{x}\}$, the zeroth moment $\cJ$ is referred as the particle density, the first moment $\bcH$ is the particle flux, and the second moment $\bcK$ is the stress tensor.
+Then integral Eq.~\eqref{eq:boltzmann} as the zeroth and the first moments both side to have
 \begin{equation}
@@
 \end{equation}
-with
+with $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, $\vect{\cF}=(\vect{\cH},\vect{\cK})^{T}$, and
 \begin{equation}
@@
 \end{equation}
-where $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$ and $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$.
+where $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$, $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$, and
 $\vect{I}$ is the identity matrix.
+Therefore, solving Boltzmann equation Eq.~\eqref{eq:boltzmann} for a neutrino distribution function $f(\omega,\vect{z},t)$ is converted to solving two-moment equations for the neutrino number density $\cJ(\vect{z},t)$ and the neutrino flux $\bcH(\vect{z},t)$.
 
 \subsection{Algebraic Closures }
-To close the system given by Eq.~\eqref{eq:momentEquations}, a strategy named algebraic closure is used.
-Algebraic closures give approximate $\bcK$ based on the lower moments:
+As it shown in previous section, the $i$-th order moment equation requires information of the $(i+1)$-th order moment and leads the two-moment system be open. 
+To close the two-moment system, a strategy named algebraic closure is built.
+For a two-moment method, algebraic closures give an approximate $\bcK$ based on the lower moments as following:
 \begin{equation}
@@
 where $\vect{k}$ is the Eddington tensor.
-Levermore\cite{levermore_1984} assumed that the radiation field is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$ and gave 
+Assume the neutrino transport is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore\cite{levermore_1984} proposed
 \begin{equation}
@@
 \subsection{Constraints on Moments}
-One fundamental fact one should concern before solving the system is the property he/she should never violate.
-For a fermionic system, the property is Pauli exclusion principle, or 
-\begin{equation}
-f \in (0,1).
-\end{equation}
-As a result, the angular moments as the integrations of $f$ are confined as following
+One fundamental fact about neutrino is that they are fermion which follow the Pauli exclusion principle, $f \in (0,1)$.
+As a result, the angular moments of $f$ are confined as the following: 
 \begin{align}
-\cJ \in(0,1), \quad &(1-\cJ)\cJ-|\vect{\cH}|  > 0, \\
+\cJ \in(0,1), \quad &(1-\cJ)\cJ-|\vect{\cH}|  > 0, \label{eq:MomentsBounds}\\
   \chi_{\mbox{\tiny min}}
@@
 \end{align}
-where $h = |\bcH|/\cJ$ is the flux factor.
-As Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the constraints on moments all the time: Kershaw\cite{kershaw_1976}, Wilson [citation], Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2 [citation] may work fine at low occupancy case, but not at high occupancy situation; Janka 1 [citation] is even worse and not work all the time.
-Only Cernohorsky \& Bludman\cite{cernohorskyBludman_1994} among these plotted closures remains in the realizable region.
+where $h = |\bcH|/\cJ$ is the flux factor.[citation]
+
+The inequalities in Eq.\ref{eq:MomentsBounds} define the realizable $\bcM$ which defines a convex set in $\cJ -\bcH$ space.
+As we will see later in Section \ref{se:SpacialDiscretization}, this convexity makes a constraint-preserving spacial discretization possible.
+
+The inequalities in Eq.\ref{eq:eddingtonFactorBounds} desire more attention than have be given.
+They have the equal importance as the inequalities in Eq.\ref{eq:MomentsBounds} in preserving the validity of the simulation result.
+However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson [citation], Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2 [citation] may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1 [citation] can be dangerous for both the cases.
+The only algebraic closure that remains in the bounds among those seven plotted closures is Cernohorsky \& Bludman's \cite{cernohorskyBludman_1994}.
 \begin{figure}[h]

### 2018-09-28 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Modified the introduction section.
Modified the spacial discretization section.

@@
 & = \bcM_{i}^{n} - \dfrac{\dt}{\dx} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right) + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i}) \nonumber \\
-& = (1-\eta)\bcM_{i}^{n} + \f{1}{2}\eta\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\eta\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right) + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i})
+& = (1-\eta)\bcM_{i}^{n} + \eta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right]  + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i})
 \end{align}
-where $\eta := \dfrac{\dt}{\dx}$. The first three terms can form a 3-term convex combination by requiring $\eta \in [0,1]$.
-It can be shown that $\bcM_{i}^{n+1}$ remains realizable given $\bcM_{i}^{n}$ is realizable, $\eta \in [0,1]$ and $\cC(\bcM)$ is positivity-preserving. The proof can be found in \cite{c
-chu_2018}.
+where $\eta := \dfrac{\dt}{\dx}$.
+Let's call
+\begin{align*}
+\tilde{\bcM}^{n}_{i} := (1-\eta)\bcM_{i}^{n} + \eta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right],
+\end{align*} 
+and assume $\bcM_{i}^{n}$ is realizable for all $i$. 
+Lemma 3 in \cite{chu_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\tilde{\bcM}^{n}_{i}$ is realizable.
+$\tilde{\bcM}^{n}_{i}$ is a convex combination of $\bcM_{i}^{n}$ and the bracket term if $\eta \in [0,1]$, so it is realizable if $\eta \in [0,1]$ and the bracket term is realizable.
+And the realizability of the bracket term is given by Lemma 2 in \cite{chu_2018}.
+To sum up, $\bcM^{n+1}_{i}$ remains realizable given $\eta \in [0,1]$.
+It's the CFL condition of the Forward-Euler method employing on a transport only Boltzmann equation.

### 2018-09-28 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Backup the latest changes.
Backup once more.

--- 2018-09-25 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
@@
 Therefore, by treating the flux term explicitly and the collision term implicitly, we have
-\begin{align}
-\bcM_{i}^{n+1} 
-& = \bcM_{i}^{n} - \dfrac{\dt}{\dx} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right) + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i}) \nonumber \\
-& = (1-\eta)\bcM_{i}^{n} + \f{1}{2}\eta\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\eta\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right) + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i})
-\end{align}
-where $\eta := \dfrac{\dt}{\dx}$. The first three terms can form a 3-term convex combination by requiring $\eta \in [0,1]$.
-It can be shown that $\bcM_{i}^{n+1}$ remains realizable given $\bcM_{i}^{n}$ is realizable, $\eta \in [0,1]$ and $\cC(\bcM)$ is positivity-preserving. The proof can be found in \cite{c
-chu_2018}.
+\begin{align*}
+\bcM_{i}^{n+1} = \widetilde{\bcM}^{n}_{i} + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i})
+\end{align*}
+with
+\begin{align*}
+\widetilde{\bcM}^{n}_{i} 
+& = \bcM_{i}^{n} - \dfrac{\dt}{\dx} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
+& = (1-\beta)\bcM_{i}^{n} + \beta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right]
+\end{align*}
+where $\beta := \dfrac{\dt}{\dx}$.
+Assume $\bcM_{i}^{n}$ is realizable for all $i$. 
+Lemma 3 in \cite{chu_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.
+$\widetilde{\bcM}^{n}_{i}$ is a convex combination of $\bcM_{i}^{n}$ and the bracket term if $\beta \in [0,1]$, so it is realizable if $\beta \in [0,1]$ and the bracket term is realizable.
+And the realizability of the bracket term is given by Lemma 2 in \cite{chu_2018}.
+To sum up, $\bcM^{n+1}_{i}$ remains realizable given $\beta \in [0,1]$.
+It's the CFL condition of the Forward-Euler method employing on a transport only Boltzmann equation.

### 2018-10-01 Documents/M1/Astronum_2018/manuscript.tex
Comments on paper
Backup once more.
Added abstract.

@@
 \usepackage{mathrsfs}
+\usepackage{color}
+\usepackage{url}
+
+\newcommand{\ee}[1]{{\color{red} EE:~#1}}
+\newcommand{\rc}[1]{{\color{blue} RC:~#1}}
 
@@
 \begin{document}
-\title{\texttt{thornado}-transport: a realizability-preserving IMEX scheme for two-moment neutrino transport}
+\title{\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics}
 
@@
 \author{Eirik Endeve}
+\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
 \address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
-\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
 \ead{endevee@ornl.gov}
@@
 \author{Cory D. Hauck}
+\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
 \address{Department of Mathematics, University of Tennessee Knoxville, TN 37996-1320}
-\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
 \ead{hauckc@ornl.gov}
@@
 \author{Bronson Messer}
+\address{Scientific Computing and Theoretical Physics Groups, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
 \address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
-\address{Scientific Computing and Theoretical Physics Groups, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
-%\address{Physics Division, Oak Ridge National Laboratory, P.O. Box 2008, Oak Ridge, TN 37831-6354, USA}
 \ead{bronson@ornl.gov}
@@
 \begin{abstract}
-All articles {\it must} contain an abstract...
+We develop implicit-explicit (IMEX) schemes for neutrino transport though a background material in \texttt{thornado} code with two-moment method.
+Two-moment method evolves the angular moments of a neutrino phase space distribution function and the moments have upper and lower bounds that introduced by Pauli's exclusion principle.
+To ensure the scheme preserves these bounds, a algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
+Severn algebraic closures are compared with these bounds and Cernohorsky \& Bludman closure which preserves the bounds is chosen for our IMEX schemes.
+For the convex-invariant time integrator, two IMEX scheme named PD-ARSs have been proposed following the work in \cite{chu_2018}.
+PD-ARS denotes convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy, high-order accuracy in the streaming limit, and works well in the diffusion limit.
+The two PD-ARSs have second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore second-order and third-order accurate in the streaming limit.
+The accuracy and convex-variance of PD-ARSs are demonstrated in the numerical tests with a first-order discontinuous Galerkin method for spatial discretization and a simple Lax-Friedrichs flux.
+
 \end{abstract}

### 2018-10-01 Documents/M1/Astronum_2018/sections/Conclusion.tex
Added conclusion section.

@@
 
-This is the conclusion section ...
+We have developed IMEX schemes for the two-moment neutrino transport in \texttt{thornado} code respecting Fermi-Dirac statistics.
+The schemes employ algebraic closure based on Fermi-Dirac statistics, a first-order discontinuous Galerkin method, the simple Lax-Friedrichs flux with the convex-invariant time integrator to maintain point-wise realizability of the moments.
+Since the realizability-preserving property is obtained from convexity of the realizable domain, it's possible to construct a scheme with high order DG method.
+See \cite{chu_2018} for some examples with third-order DG method employed.
+
+In the applications motivating this work, the neutrino distribution function can vary from 0 to 1, and we have considered the algebraic closure respecting Fermi-Dirac statistics for both low and high occupied condition.
+Different values given by different algebraic closures were compared with the boundary values given by the Fermi-Dirac statistics at different occupation.
+Among the algebraic closures we considered, Kershaw\cite{kershaw_1976}, Wilson\cite{wilson1975,leblanc1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka1991} Janka 2\cite{janka1992} and Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}, only Cernohorsky \& Bludman closure respecting Fermi-Dirac statistics for any occupancy.
+And it is Cernohorsky \& Bludman closure that we employed in the numerical tests in Section~\ref{se:NumericalTests}.
+
+Following the work we have done in \cite{chu_2018}, two PD-ARSs have been proposed.
+The one with SSPRK2 is second-order and strong stability-preserving in the streaming limit while other with SSPRK3 is third-order.
+Their properties, accuracy and convex-invariant, are demonstrated with numerical tests.
+
+In this work, we adopted Cartesian coordinates, linear collision term, non-relativistic, and fixed material background.
+More realistic problems of scientific interest, such as with the scattering with energy changes and relativistic effects, are left for future research.

### 2018-10-01 Documents/M1/Astronum_2018/sections/Numerical.tex
Added conclusion section.

@@
 \subsubsection{Sine Wave Damping}
+This test is adapted from \cite{skinnerOstriker_2013}.
 Figure~\ref{fig:SineWaveDamping} shows the numerical result of sine wave damping test.
@@
 The last test with known smooth solution is sine wave diffusion test.
+It is adopted from \cite{radice_etal_2013}.
 See \cite{chu_2018} for more information about the test setting.

### 2018-10-01 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Added conclusion section.

@@
 Lemma 3 in \cite{chu_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.
-$\widetilde{\bcM}^{n}_{i}$ is a convex combination of $\bcM_{i}^{n}$ and the bracket term if $\beta \in [0,1]$, so it is realizable if $\beta \in [0,1]$ and the bracket term is realizable.
-And the realizability of the bracket term is given by Lemma 2 in \cite{chu_2018}.
-To sum up, $\bcM^{n+1}_{i}$ remains realizable given $\beta \in [0,1]$.
-It's the CFL condition of the Forward-Euler method employing on a transport only Boltzmann equation.
+Substitute the Lax-Friedrichs flux formula in and $\widetilde{\bcM}^{n}_{i}$ becomes a convex combination of $\bcM_{i}^{n}$ and the square bracket term if $\beta \in [0,1]$.
+So it is realizable if $\beta \in [0,1]$ and the square bracket term is realizable.
+Given by Lemma 2 in \cite{chu_2018}, the square bracket term is realizable.
+Therefore, $\bcM^{n+1}_{i}$ remains realizable given $\beta \in [0,1]$.
+Note that $\beta \in [0,1]$ is also the CFL condition of the Forward-Euler method employing on a transport only Boltzmann equation.

### 2018-10-01 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Added conclusion section.

@@
 They have the equal importance as the inequalities in Eq.\ref{eq:MomentsBounds} in preserving the validity of the simulation result.
-However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson [citation], Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2 [citation] may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1 [citation] can be dangerous for both the cases.
+However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson1975,leblanc1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka1992} may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1\cite{janka1991} can be dangerous for both the cases.
 The only algebraic closure that remains in the bounds among those seven plotted closures is Cernohorsky \& Bludman's \cite{cernohorskyBludman_1994}.

### 2018-10-01 Documents/M1/Astronum_2018/sections/intro.tex
Modified the two-moment method section.
Added some comments
Backup introduction for updating.

@@
 
-Core-collapse supernovae (CCSNe) are the explosion happens at the end of a massive star's life.
-They are a dominant source of heavy elements and play an important role in many astrophysical phenomena, such as neutron star and black hole formation.  
+Core-collapse supernovae (CCSNe) are the explosion of massive stars which end their life.
+CCSNe are a dominant source of heavy elements and play an important role in many astrophysical phenomena, such as neutron star and black hole formation.  
 Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
@@
 One essential part of the explosion mechanism is neutrino transport which drives the explosion.  
-Neutrino transport is modeled by Boltzmann transport equation, which is partial differential equation and evolves a phase space distribution function $f$.
-Simulating the neutrino transport is finding a solution of Boltzmann transport equation for a given domain and period with an acceptable accuracy.
+Neutrino transport is modeled by Boltzmann transport equation which is partial differential equation evolving a phase space distribution function $f$.
+Simulating the neutrino transport is convert to find a solution of Boltzmann transport equation for a interested domain and period with an acceptable accuracy.
 
-Solving multi-dimensional Boltzmann transport equation can be expensive.
-To balance physical fidelity and computational expediency, an approximation method called two-moment method is investigated.
-In two-moment method, the evolve values are the angular moments of the distribution function $f$, the spectral particle density $\cJ$ and flux $\bcH$, which are the zeroth angular moment and the first angular moment, respectively.
+Nevertheless, solving multi-dimensional Boltzmann transport equation can be expensive.
+To balance physical fidelity and computational expediency, an approximation method called two-moment method is established.
+In two-moment method, the evolve variables are the zeroth and first angular moments of the distribution function $f$, the spectral particle density $\cJ$ and flux $\bcH$ respectively.
 
-Applying two-moment method only is not sufficient to have an affordable solution when the simulating period is long.
-To be precisely, neutrino interact with the background rapidly and its characteristic time scalar is so small comparing to the length of CCSNe explosion process. 
-It makes the time step needed by an explicit time integrator small and a lot of calculation needed. 
-Moreover, solving the moment equations fully implicitly requires diagonalization of band structure matrices whose sizes depend on the space discretization and makes the simulation expensive.
-To manipulate this challenge, implicit-explicit (IMEX) methods are taken into consideration.
-By treating the transport term explicitly and the collision term implicitly, IMEX methods subject only to a time step governed by the explicit transport term and the matrix it needs to diagonal is diagonal dominate in most of interested region.
+Applying two-moment method only is not sufficient to have an affordable solution since the simulating period is long considering the physics it involves.
+To be precisely, neutrino interact with the background rapidly and its characteristic time scalar is very small comparing to the length of CCSNe explosion process. 
+This makes the time step needed by an explicit time integrator small and a lot of calculation needed. 
+On the other hand, solving the moment equations fully implicitly requires inverting many band structure matrices whose sizes depend on the space discretization.
+The band structure of the large matrices makes not only the matrices inverting expensive but also the simulation parallel unfriendly.
+To manipulate these challenges, implicit-explicit (IMEX) methods are taken into consideration.
+By treating the transport term explicitly and the collision term implicitly, IMEX methods subject only to a time step governed by the explicit transport term and the matrix it needs to invert is block diagonal dominated.
+Therefore, IMEX methods need less step and the calculation for each step is parallelable.
+
+\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.}
 
@@
 Here is the explanation.
+
 First of all, the Boltzmann transport equation is a nonlinear equation.
@@
 Therefore, two-moment method needs a algebraic closure which gives a approximated value of the second order moment $\bcK$ given $\cJ$ and $\bcH$.
+
 Second, the angular moments are confined.
@@
 Hence, the algebraic closure should give a realizable $\bcK$ and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
+
 Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a constraint-preserving IMEX.
 Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.
+
 Fourth, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.
-[citation] showed standard IMEX scheme can't have an order higher than first.
+\rc{\cite{gottlieb_etal_2001} showed standard IMEX scheme can't have an order higher than first without a restrict time step requirement.}
 To have second-order (or higher-order) accuracy, some correction steps are needed.
@@
 We call these IMEX scheme PD-ARS.
-The study of moment realizabilty and constraint-preserving diffusion accurate IMEX scheme motivates this work.
+The study of moment realizability and constraint-preserving diffusion accurate IMEX scheme motivates this work.
 

### 2018-10-01 Documents/M1/Astronum_2018/manuscript.tex
Modified the bibliography

@@
 To ensure the scheme preserves these bounds, a algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
-Severn algebraic closures are compared with these bounds and Cernohorsky \& Bludman closure which preserves the bounds is chosen for our IMEX schemes.
-For the convex-invariant time integrator, two IMEX scheme named PD-ARSs have been proposed following the work in \cite{chu_2018}.
+Severn algebraic closures are compared with these bounds and Cernohorsky \& Bludman closure\cite{cernohorskyBludman_1994} which preserves the bounds is chosen for our IMEX schemes.
+For the convex-invariant time integrator, two IMEX scheme named PD-ARSs have been proposed following the work in \cite{chu_etal_2018}.
 PD-ARS denotes convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy, high-order accuracy in the streaming limit, and works well in the diffusion limit.
 The two PD-ARSs have second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore second-order and third-order accurate in the streaming limit.
-The accuracy and convex-variance of PD-ARSs are demonstrated in the numerical tests with a first-order discontinuous Galerkin method for spatial discretization and a simple Lax-Friedrichs flux.
+The accuracy and convex-invariance of PD-ARSs are demonstrated in the numerical tests with a first-order discontinuous Galerkin method for spatial discretization and a simple Lax-Friedrichs flux.
 

### 2018-10-01 Documents/M1/Astronum_2018/sections/Conclusion.tex
Modified the bibliography

@@
 Since the realizability-preserving property is obtained from convexity of the realizable domain, it's possible to construct a scheme with high order DG method.
-See \cite{chu_2018} for some examples with third-order DG method employed.
+See \cite{chu_etal_2018} for some examples with third-order DG method employed.
 
@@
 Different values given by different algebraic closures were compared with the boundary values given by the Fermi-Dirac statistics at different occupation.
-Among the algebraic closures we considered, Kershaw\cite{kershaw_1976}, Wilson\cite{wilson1975,leblanc1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka1991} Janka 2\cite{janka1992} and Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}, only Cernohorsky \& Bludman closure respecting Fermi-Dirac statistics for any occupancy.
+Among the algebraic closures we considered, Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblanc_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka_1991} Janka 2\cite{janka_1992} and Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}, only Cernohorsky \& Bludman closure respecting Fermi-Dirac statistics for any occupancy.
 And it is Cernohorsky \& Bludman closure that we employed in the numerical tests in Section~\ref{se:NumericalTests}.
 
-Following the work we have done in \cite{chu_2018}, two PD-ARSs have been proposed.
+Following the work we have done in \cite{chu_etal_2018}, two PD-ARSs have been proposed.
 The one with SSPRK2 is second-order and strong stability-preserving in the streaming limit while other with SSPRK3 is third-order.

### 2018-10-01 Documents/M1/Astronum_2018/sections/Numerical.tex
Modified the bibliography

@@
 In the streaming test, the second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} , (SSPRK2 and SSPRK3, respectively) are also applied to serve as an reference.
-More information and the definition of the absolute error and the relative error can be found in \cite{chu_2018}.
+More information and the definition of the absolute error and the relative error can be found in \cite{chu_etal_2018}.
 
@@
 A periodic domain $D$ was applied and the initial condition is given by...
-More information can be found in \cite{chu_2018}.
+More information can be found in \cite{chu_etal_2018}.
 In Figure ~\ref{fig: SineWaveStreaming}, the absolute error for the number density is plotted versus the number of elements $N$.
@@
 Figure~\ref{fig:SineWaveDamping} shows the numerical result of sine wave damping test.
-See \cite{chu_2018} for more information about the test setting.
+See \cite{chu_etal_2018} for more information about the test setting.
 SSP2332 as a second-order scheme display second order convergence rate.
@@
 It is adopted from \cite{radice_etal_2013}.
-See \cite{chu_2018} for more information about the test setting.
+See \cite{chu_etal_2018} for more information about the test setting.
 Figure~\ref{fig:SineWaveDiffusionJ} shows the numerical result.

### 2018-10-01 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Modified the bibliography

@@
 Assume $\bcM_{i}^{n}$ is realizable for all $i$. 
-Lemma 3 in \cite{chu_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.
+Lemma 3 in \cite{chu_etal_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.
 Substitute the Lax-Friedrichs flux formula in and $\widetilde{\bcM}^{n}_{i}$ becomes a convex combination of $\bcM_{i}^{n}$ and the square bracket term if $\beta \in [0,1]$.
 So it is realizable if $\beta \in [0,1]$ and the square bracket term is realizable.
-Given by Lemma 2 in \cite{chu_2018}, the square bracket term is realizable.
+Given by Lemma 2 in \cite{chu_etal_2018}, the square bracket term is realizable.
 Therefore, $\bcM^{n+1}_{i}$ remains realizable given $\beta \in [0,1]$.

### 2018-10-01 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Updated the introduction section.
Modified the two-moment method section.
Modified the bibliography

@@
 \end{equation}
-It can be proved \cite{chu_2018} that the conditions we need for constraint-preserving IMEX is:
+It can be proved \cite{chu_etal_2018} that the conditions we need for constraint-preserving IMEX is:
 \begin{enumerate}
@@
 \end{enumerate}  
-We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{Chu_2018})
-We give two optimized PD-ARS scheme here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. They have $2$-nd order and $3$-rd order accuracy in the streaming limit, respectively.
+We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{chu_etal_2018})
+We give two optimized PD-ARS scheme here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. 
+They have $2$-nd order and $3$-rd order accuracy in the streaming limit, respectively.
 \subsubsection{PD-ARS with SSPRK2}
@@
 \end{equation}
-For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 3\epsilon/2$ with $\epsilon \rightarrow 0^{+}$.
+For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 3\epsilon/2$ with $\epsilon \in [0,2/3)$. (\rc{Other forms})

### 2018-10-01 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Modified the bibliography

--- 2018-09-28 Documents/M1/Astronum_2018/sections/TwoMoments.tex
@@
 They have the equal importance as the inequalities in Eq.\ref{eq:MomentsBounds} in preserving the validity of the simulation result.
-However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson [citation], Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2 [citation] may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1 [citation] can be dangerous for both the cases.
+However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblanc_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1\cite{janka_1991} can be dangerous for both the cases.
 The only algebraic closure that remains in the bounds among those seven plotted closures is Cernohorsky \& Bludman's \cite{cernohorskyBludman_1994}.

### 2018-10-01 Documents/M1/Astronum_2018/sections/intro.tex
Modified the bibliography

@@
 
-\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.}
+\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.} \cite{vartanyan_etal_2018,oConnorCouch_2018,pan_etal_2018,cabezon_etal_2018,glas_etal_2018,just_etal_2018,kuroda_etal_2016}
 
-To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a constraint-preserving diffusion accurate IMEX schemes for ensure a valid result.
+To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a convex-invariant diffusion accurate IMEX schemes for ensure a valid result.
 Here is the explanation.
@@
 
-Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a constraint-preserving IMEX.
+Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a convex-invariant IMEX.
 Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.

### 2018-10-01 Documents/Euler/Astronum_2018/manuscript.tex
Initial commit of contribution to Astronum 2018.

\documentclass[letterpaper]{jpconf}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

\newcommand{\deriv}[2]{\frac{d #1}{d #2}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\vect}[1]{\boldsymbol{#1}}
\newcommand{\f}[2]{\frac{#1}{#2}}
\newcommand{\dx}{\Delta x}
\newcommand{\pd}[2]{\partial_{#2}{#1}}
\newcommand{\bx}{\vect{x}}
\newcommand{\bK}{\vect{K}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\xL}{x_{\textnormal{\tiny\textsc{L}}}}
\newcommand{\xH}{x_{\textnormal{\tiny\textsc{H}}}}
\newcommand{\xMin}{x_{\textnormal{\tiny m}}}
\newcommand{\xMax}{x_{\textnormal{\tiny M}}}
\newcommand{\trans}{\textnormal{\tiny\textsc{T}}}
\newcommand{\leftState}{\textnormal{\tiny\textsc{L}}}
\newcommand{\rightState}{\textnormal{\tiny\textsc{R}}}
\newcommand{\TCI}{\textnormal{\tiny\textsc{TCI}}}
\newcommand{\shock}{\textnormal{\tiny\textsc{Sh}}}
\newcommand{\thornado}{\texttt{thornado}}

\newcommand{\ee}[1]{{\color{red} EE:~#1}}

\begin{document}
\title{\thornado-hydro: towards discontinuous galerkin methods for supernova hydrodynamics}

\author{Eirik Endeve}
\address{Computational \& Applied Mathematics, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
\ead{endevee@ornl.gov}

\author{Kristopher Andrew, Brandon Barker, Jesse Buffaloe, Samuel Dunham, David Pochik, Juliana Pulsinelli, Nick Roberts}

\begin{abstract}
The toolkit for high-order neutrino-radiation hydrodynamics (\thornado) is being developed for simulations of core-collapse supernovae (CCSN) and related problems.  
Current capabilities in \thornado\ include solvers for the Euler equations --- in non-relativistic and special relativistic limits --- and the two-moment model of neutrino transport.  
The spatial discretization in \thornado\ is based on the discontinuous Galerkin (DG) method, which is receiving increased attention from the computational astrophysics community.  
In this paper, we provide an overview of the numerical methods for the Euler equations in \thornado, and present some encouraging preliminary numerical results from a set of basic tests in one and two spatial dimensions.  
\end{abstract}

\section{Introduction}

\ee{Introduction coming soon.}

\section{Discontinuous Galerkin Method}

Excellent books and review articles on the DG method are available (see, e.g., \cite{cockburnShu_1998,cockburnShu_2001,hesthavenWarburton_2008,shu_2016} and references therein), and we will not go into too much detail here.  
However, we review some key concepts to introduce notation, and emphasize specific choices in our implementation in \thornado.  
To this end, we consider a system of conservation laws with sources of the form
\begin{equation}
  \pd{}{t}\big(\,\sqrt{\gamma}\,\vect{U}\,\big)
  +\pd{}{i}\Big(\,\sqrt{\gamma}\,\vect{F}^{i}(\vect{U})\,\Big)
  =\sqrt{\gamma}\,\vect{S}(\vect{U}),
  \label{eq:extendedEulerCompact}
\end{equation}
where $\vect{U}$ is the evolved state vector, $\vect{F}^{i}$ the fluxes, and $\vect{S}$ the source vector.  
We use a formulation of the equations sufficiently general to accommodate curvilinear spatial coordinates encoded in the metric $\gamma_{ij}$, giving the squared line element $ds^{2}=\gamma_{ij}dx^{i}dx^{j}$, whose determinant is $\gamma$.  
To solve Eq.~\eqref{eq:extendedEulerCompact}, the computational domain $D$ is divided into a disjoint union $\cT$ of open elements $\bK$, so that $D = \cup_{\bK \in \cT}\bK$.  
We require that each element is a box in the logical coordinates; i.e.,
\begin{equation}
  \bK=\{\vect{x} : x^{i} \in K^{i} := (\xL^{i},\xH^{i})\}, 
\end{equation}
with the surface elements denoted $\partial\bK^{i}=\times_{j\ne i}K^{j}$.  
We let $V_{\bK}$ denote the proper element volume
\begin{equation}
  V_{\bK} = \int_{\bK}dV, \quad\text{where}\quad dV = \sqrt{\gamma}\,\prod_{i=1}^{d}dx^{i}.  
\end{equation}
We also define as a set $\bx=\{\tilde{\bx}^{i},x^{i}\}$, and $\dx^{i}=\xH^{i}-\xL^{i}$.

We let the approximation space for the DG method, $\mathbb{V}^{k}$, be constructed from the tensor product of one-dimensional polynomials of maximal degree $k$.  
(Functions in $\mathbb{V}^{k}$ can be discontinuous across element interfaces.)  
The semi-discrete DG problem is to find $\vect{U}_{h}\in\mathbb{V}^{k}$ (which approximates $\vect{U}$ in Eq.~\eqref{eq:extendedEulerCompact}) such that for all $v\in\mathbb{V}^{k}$ and all $\bK\in\mathcal{T}$
\begin{align}
  &\partial_{t}\int_{\bK}\vect{U}_{h}\,v\,dV
  +\sum_{i=1}^{d}\int_{\partial\bK^{i}}\big(\,\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\vect{U}_{h})\,v\big|_{\xH^{i}}-\sqrt{\gamma}\,\widehat{\vect{F}}^{i}(\vect{U}_{h})\,v\big|_{\xL^{i}}\,\big)\,d\tilde{\bx}^{i} \nonumber \\
  &\hspace{24pt}
  -\sum_{i=1}^{d}\int_{\bK}\vect{F}^{i}(\vect{U}_{h})\,\pd{v}{i}\,dV
  =\int_{\bK}\vect{S}(\vect{U}_{h})\,v\,dV.  
  \label{eq:semidiscreteDG}
\end{align}
In Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\vect{F}}^{i}(\vect{U}_{h})$ is a numerical flux approximating the flux on the $i$th surface of $\bK$.  
The numerical flux function $\vect{f}^{i}$ evaluates the numerical flux given values from both sides of an element interface; i.e.,
\begin{equation}
  \widehat{\vect{F}}^{i}(\vect{U}_{h})=\vect{f}^{i}(\vect{U}_{h}(x^{i,-},\tilde{\bx}^{i}),\vect{U}_{h}(x^{i,+},\tilde{\bx}^{i})),
\end{equation}
where superscripts $-/+$, e.g., in the arguments of $\vect{U}_{h}$, indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
We use the Harten-Lax-van Leer (HLL) flux \cite{harten_etal_1983} or the HLLC flux \cite{toro_etal_1994,mignoneBodo_2005} for all the numerical experiments presented in Section~\ref{sec:numerical}.

We provide further details on the DG method to arrive at the equations that are actually evolved in \thornado.  
We start by introducing some notation, defining the polynomial expansion for $\vect{U}_{h}$, and the quadrature rules used to evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}.  
Then we provide explicit expressions for each of the terms in Equation~\eqref{eq:semidiscreteDG}.  
For simplicity we consider one spatial dimension ($d=1$) and drop indices denoting the spatial dimension.  
In each element $K$, we use a nodal representation of the conserved variables $\vect{U}$; i.e.,
\begin{equation}
  \vect{U}(x,t)\approx
  \vect{U}_{h}(x,t)=\sum_{i=1}^{N}\vect{U}_{i}(t)\,\ell_{i}(x),
  \label{eq:conservedNodalExpansion}
\end{equation}
where $\ell_{i}(x)$ are Lagrange polynomials
\begin{equation}
  \ell_{i}(\eta)=
  \prod_{\substack{j=1\\j\ne i}}^{N}\f{\eta-\eta_{j}}{\eta_{i}-\eta_{j}},
\end{equation}
defined on the reference element $I = \{ \eta : \eta \in (-0.5,0.5) \}$, and constructed to interpolate the node set $S_{N}=\{\eta_{i}\}_{i=1}^{N}\subset I$.  
The spatial coordinate $x$ and the reference coordinate $\eta$ are related by the mapping $x(\eta)=\xL+(0.5+\eta)\,\dx$.  
Then, for any $\eta_{j}\in S_{N}$, $\ell_{i}(\eta_{j})=\delta_{ij}$, so that $\vect{U}_{h}(x(\eta_{j}),t)=\vect{U}_{j}(t)$.  
We introduce numerical quadratures to evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}.  
First we define the $M$-point quadrature $Q_{M}:C^{0}(I)\to\mathbb{R}$ with abscissas $\hat{S}_{M}=\{\eta_{q}\}_{q=1}^{M}$ and weights $\{w_{q}\}_{q=1}^{M}$, normalized such that $\sum_{q=1}^{M}w_{q}=1$.  
The $M$-point Legendre-Gauss quadrature, which we use, integrates polynomials of degree $\le 2M-1$ exactly.  
Then, if $P(x)$ is such a polynomial, we have
\begin{equation}
  \f{1}{\dx}\int_{K}P(x)\,dx=\int_{I}P(\eta)\,d\eta=Q_{N}\big[P\big]\equiv\sum_{q=1}^{M}w_{q}\,P(\eta_{q}).  
\end{equation}

Note that the interpolation points $S_{N}$ and the quadrature points $\hat{S}_{M}$ generally do not coincide.  
However, for sake of computational efficiency we let $M=N$ and $S_{N}=\hat{S}_{N}$, which is a spectral-type nodal collocation DG approximation \cite{bassi_etal_2013}.  
Inserting Eq.~\eqref{eq:conservedNodalExpansion} into Eq.~\eqref{eq:semidiscreteDG}, letting $v(x)=\ell_{k}(x)$, and using the quadratures defined above, we obtain
\begin{align}
  \pd{}{t}\int_{K}\vect{U}_{h}\,v\,dV
  &\approx w_{k}\,\sqrt{\gamma}_{k}\,\pd{}{t}\vect{U}_{k}\,\dx
  \label{eq:timeDerivativeTerm}
\end{align}
for the time derivative term.  
The integration is approximate since we use the Legendre-Gauss quadrature rule with the nodal points given by the expansion in Eq.~\eqref{eq:conservedNodalExpansion}.  
Since $\ell_{i}(\eta_{k})=\delta_{ik}$, this leads to a diagonal mass matrix, and simplifies the implementation.  
Similarly, we obtain
\begin{align}
  \int_{K}\vect{S}(\vect{U}_{h})\,v\,dV
  &\approx w_{k}\,\sqrt{\gamma}_{k}\,\vect{S}(\vect{U}_{k})\,\dx.
  \label{eq:sourceTerm}
\end{align}
for the source term.  
Finally, the volume term (last term on the left-hand side of Eq.~\eqref{eq:semidiscreteDG}) becomes
\begin{equation}
  \int_{K}\vect{F}(\vect{U}_{h})\,\pderiv{v}{x}\,dV
  \approx \sum_{q=1}^{N}w_{q}\,\sqrt{\gamma}_{q}\,\vect{F}(\vect{U}_{q})\,\pderiv{\ell_{k}}{\eta}(\eta_{q}).
  \label{eq:volumeTerm}
\end{equation}
Using Eqs.~\eqref{eq:timeDerivativeTerm}-\eqref{eq:volumeTerm} in Eq.~\eqref{eq:semidiscreteDG} results in the semi-discrete form
\begin{align}
  \deriv{\vect{U}_{k}}{t}
  =-\f{1}{w_{k}\sqrt{\gamma}_{k}\dx}
  \Big\{
  \Big[\,
    \sqrt{\gamma}\widehat{\vect{F}}\ell_{k}\big|_{\xH}
    -\sqrt{\gamma}\widehat{\vect{F}}\ell_{k}\big|_{\xL}
  \,\Big]
  -\sum_{q=1}^{N}w_{q}\,\sqrt{\gamma}_{q}\,\vect{F}(\vect{U}_{q})\,\pderiv{\ell_{k}}{\eta}(\eta_{q})
  \Big\} + \vect{S}(\vect{U}_{k}).
  \label{eq:semidiscreteDiscretized}
\end{align}
Eq.~\eqref{eq:semidiscreteDiscretized} comprises a system of ordinary differential equations (ODEs), which are integrated in time with an ODE solver.  
In section~\ref{sec:numerical} we use the optimal third-order strong stability-preserving Runge-Kutta (SSP-RK3) method from \cite{shuOsher_1988}.

Limiting of the polynomial representation $\vect{U}_{h}$, to reduce oscillations and prevent non-physical states, is a critical step in the DG algorithm.  
We use the TVD-type slope limiter based on limiting characteristic variables discussed in \cite{cockburnShu_1998}.  
To prevent excessive limiting (e.g., at smooth extrema), we use the troubled-cell indicator (TCI) of \cite{fuShu_2017}.  
\begin{equation}
  I_{\bK}(G) = \f{\sum_{j}|G_{\bK}-G_{\bK}^{(j)}|}{\max_{j}|G_{\bK^{(j)}}^{(j)}|},
  \label{eq:indicator}
\end{equation}
where $G\in\vect{G}\subseteq\vect{U}$.  
(Here, $\vect{G}$ consists of the first and last element of $\vect{U}$.)  
In Eq.~\eqref{eq:indicator}, the sum in the numerator and the $\max$ in the denominator extend over the neighboring elements sharing face with the target element $\bK$.  
$G_{\bK}$ is the cell average in $\bK$, $G_{\bK}^{(j)}$ is the cell average computed by extrapolating the polynomial representation from the neighbor element $\bK^{(j)}$ into $\bK$, and $G_{\bK^{(j)}}^{(j)}$ is the cell average native to $\bK^{(j)}$.  
An element is flagged for limiting if $I_{\bK}(G)>C_{\TCI}$ for any $G\in\vect{G}$.  
To prevent negative mass density and pressure (and superluminal velocity for the relativistic Euler equations), we follow the approaches in \cite{zhangShu_2010,wuTang_2015,qin_etal_2016}.

\section{Preliminary Numerical Results}
\label{sec:numerical}

In this section we show preliminary numerical results obtained with the DG method implemented in \thornado\ to solve the non-relativistic and special relativistic Euler equations.  
We use the ideal gas equation of state where the pressure $p$ is related to the internal energy density $e$ by $p=(\Gamma-1)e$, and where $\Gamma$ is the (constant) adiabatic index.  
Let the $d$-dimensional computational domain be $D=\times_{i=1}^{d}[\xMin^{i},\xMax^{i}]$, where $\xMin^{i}$ and $\xMax^{i}$ denote the coordinates of the inner and outer boundary in the $i$-th coordinate direction, respectively.  
We use polynomials of degree $k=2$ combined with SSP-RK3 time stepping, and all the tests were run with a Courant-Friedrichs-Lewy (CFL) factor of $C=0.1$.  
We use the HLL Riemann solver when solving the non-relativistic Euler equations and the HLLC Riemann solver when solving the special relativistic Euler equations.  
The purpose of the tests is gauge the performance of the DG implementation on a set of benchmarks as an initial measure of its suitability for future for CCSN simulations.

\subsection{Non-relativistic (NR) hydrodynamics}

For the NR Euler equations, the state, flux, and source vectors in Eq.~\eqref{eq:extendedEulerCompact} are
\begin{equation}
  \vect{U}=\big(\rho,\rho u_{j},E\big)^{\trans},~
  \vect{F}^{i}=\big(\rho\,u^{i},\Pi^{i}_{~j},(E+p)u^{i}\big)^{\trans},~
  \text{and}~
  \vect{S}=\big(0,\f{1}{2}\Pi^{ik}\pd{\gamma_{ik}}{j}-\rho\pd{\Phi}{j},-\rho u^{i}\pd{\Phi}{i}\big)^{\trans},
\end{equation}
where $\rho$ and $u^{i}$ are the mass density and components of the fluid three-velocity, respectively.  
The stress tensor is $\Pi^{i}_{~j}=\rho u^{i} u_{j}+p\delta^{i}_{~j}$, and $E=e+\f{1}{2}\rho u_{i} u^{i}$ is the fluid (internal plus kinetic) energy density.  
The sources are due to curvilinear coordinates and Newtonian gravity.

\subsubsection{Sod Shock Tube}

The first test is the classical Riemann problem due to Sod \cite{sod_1978}, computed using Cartesian coordinates.  
The one-dimensional computational domain is $D=[0,1]$, and a discontinuity is initially located at $x^{1}=0.5$, separating the left and right states
\begin{equation*}
  \vect{U}_{\leftState}=(1.0,\vect{0.0},2.5)^{\trans}\quad\text{and}\quad
  \vect{U}_{\rightState}=(0.125,\vect{0.0},0.25)^{\trans},
\end{equation*}
where the adiabatic index is $\Gamma=1.4$.  
The test is run with $100$ elements until $t=0.2$, using $C_{\TCI}=0.03$.  
Results are plotted in the left panel of Figure~\ref{fig:SodSedov}.  
The DG method captures the main features of the solution well without introducing noticeable oscillations near the discontinuities.  
\begin{figure}[h]
  \centering
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/Sod_Astronum_2018}
  \end{minipage}\hspace{0.5pc}%
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/Sedov_Astronum_2018}
  \end{minipage}
  \caption{\label{fig:SodSedov}{\it Left panel:} numerical solution of Sod's problem using $100$ elements (plusses) compared with the exact solution (solid lines; from \cite{toro_1999}).  {\it Right panel:} numerical solution of the Sedov-Taylor blast wave using $256$ elements (plusses) against the exact solution (solid lines).}
\end{figure}

\subsubsection{Sedov-Taylor Blast Wave}

This test, detailed in \cite{sedov_1959} (see also {\S}99 in \cite{landauLifshitz_1979}), is computed in spherical polar coordinates with the assumption of spherical symmetry.\footnote{In this paper, all tests in spherical polar coordinates are computed with the assumption of spherical symmetry.}
The computational domain is $D=[0,1.2]$, and the initial condition consists of a fluid at rest with density $\rho=1$.  
The adiabatic index is $\Gamma=1.4$, and an amount of thermal energy equal to $1$ is released in the innermost element.  
We use $256$ elements and run until $t=1$, using $C_{\TCI}=0.03$.  
Again, the DG method captures the characteristic of the exact solution well.  
The maximum density in the shock is somewhat lower for the numerical solution than the exact value (about $5$ versus $6$).

\subsubsection{Shu-Osher Shock Tube}

This test from \cite{shuOsher_1989} is suitable for measuring the amount of dissipation in a numerical scheme.  
The one-dimensional computational domain is $D=[-5,5]$, and a discontinuity is placed at $x^{1}=-4$, separating the states
\begin{equation*}
  \vect{U}_{\leftState}=\big( 3.857143, 10.14185, 0.0, 0.0, 39.16667 \big)^{\trans}\quad\text{and}\quad
  \vect{U}_{\rightState}=\big( 1+0.2\times\sin(5 x^{1}), \vect{0.0}, 2.5 \big)^{\trans},
\end{equation*}
where the adiabatic index is $\Gamma=1.4$.  
The density variations ahead of the Mach=3 shock are compressed through the shock and result in higher-frequency variations downstream, which can be difficult to capture with an excessively dissipative scheme.

We have run this test with $200$ elements to $t=1.8$.  
In the two upper panels of Figure~\ref{fig:ShuOsher} we plot the density for various values of the troubled-cell indicator threshold $C_{\TCI}$; $0.0$ (full limiting, green), $0.03$ (magenta), $0.3$ (red), and $3.0$ (blue).  
(Larger values of $C_{\TCI}$ imply less limiting.)  
The results are compared with a reference solution computed with $2048$ elements.  
With full limiting, the scheme is not able to capture the density variations behind the shock (cf. upper right panel in Figure~\ref{fig:ShuOsher}).  
When $C_{\TCI}=0.03$, the variations are resolved, but the amplitudes are significantly reduced when compared with the reference solution.  
With $C_{\TCI}=3.0$, the variations are well resolved, and the amplitudes are comparable to the reference.  
\begin{figure}[h]
  \centering
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/ShuOsher_Astronum_2018}
  \end{minipage}\hspace{0.5pc}%
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/ShuOsher_Inset_Astronum_2018}
  \end{minipage} \\
  \begin{minipage}{12pc}
    \includegraphics[width=12pc]{./Figures/ShuOsher_TCI_0015_Astronum_2018}
  \end{minipage}\hspace{0.5pc}%
  \begin{minipage}{12pc}
    \includegraphics[width=12pc]{./Figures/ShuOsher_TCI_0150_Astronum_2018}
  \end{minipage}\hspace{0.5pc}
  \begin{minipage}{12pc}
    \includegraphics[width=12pc]{./Figures/ShuOsher_TCI_1500_Astronum_2018}
  \end{minipage}
  \caption{\label{fig:ShuOsher}Results for the Shu-Osher shock tube problem computed with $200$ elements.  The upper panels show the mass density at $t=1.8$ for various values of the troubled-cell indicator threshold $C_{\TCI}$, compared with a high-resolution (2048 elements) reference solution.  In the lower panels we show elements flagged for limiting in the $xt$-plane for various values of $C_{\TCI}$.}
\end{figure}
In the lower panels of Figure~\ref{fig:ShuOsher} we plot locations in the $xt$-plane where elements have been flagged for limiting by the troubled-cell indicator: $C_{\TCI}=0.03$ (left), $C_{\TCI}=0.3$ (middle), and $C_{\TCI}=3.0$ (right).  
With $C_{\TCI}=0.03$, limiting is triggered in a wide region around the shock and also around the peaks of the three leftmost density variations seen in upper left panel in Figure~\ref{fig:ShuOsher}.  
With $C_{\TCI}=3.0$, limiting is only triggered in the shock.

\subsubsection{Kelvin-Helmholtz (KH) Instability}
This hydrodynamic instability is of significant astrophysical relevance --- including in the explosion phase of CCSNe.  
It may occur in the interface separating fluids in relative motion.  
We compute this problem on the unit square $D=[0,1]\times[0,1]$, imposing periodic boundary conditions, and with initial conditions and single-mode perturbation taken from \cite{mcnally_etal_2012}.  
We use $256^{2}$ elements and evolve until $t=3.0$, well into the nonlinear regime.  
Results are displayed in Figure~\ref{fig:KelvinHelmholtz}.  
We have computed two models, one with $C_{\TCI}=0.06$ (left panels) and one without limiting ($C_{\TCI}\to\infty$; right panels).

\begin{figure}[h]
  \centering
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_15_Astronum_2018}
  \end{minipage}\hspace{0.5pc}
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_15_noLim_Astronum_2018}
  \end{minipage} \\
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_24_Astronum_2018}
  \end{minipage}\hspace{0.5pc}
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_24_noLim_Astronum_2018}
  \end{minipage} \\
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_30_Astronum_2018}
  \end{minipage}\hspace{0.5pc}
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_30_noLim_Astronum_2018}
  \end{minipage}
  \caption{\label{fig:KelvinHelmholtz}Mass density from the KH instability at various times, computed with $256^{2}$ elements: $t=1.5$ (top panels), $t=2.4$ (middle panels), and $t=3.0$ (bottom panels).  Results for $C_{\TCI}=0.06$ are shown in left panels, while result with no limiting are shown in right panels.}
\end{figure}

Early on ($t=1.5$), the results from the two runs are practically indistinguishable, show no sign of developing secondary billows, and agree visually with results presented in \cite{mcnally_etal_2012}.  
When $t=2.4$, the run with $C_{\TCI}=0.03$ has started to develop secondary billows within the coiled-up interface separating dense (white) and light (black) fluids, while the model with no limiting has not.  
When $t=3.0$, these secondary instabilities appear to have largely destroyed the coil structure for the model with limiting, while the coils remain intact in the model without limiting (although secondary billows have started to form in this model at this time).  
As discussed in more detail by \cite{mcnally_etal_2012}, the development of the secondary billows may be an artifact of numerical perturbations and diffusion, which is delayed when the resolution is increased.  
Our results are consistent with this in the sense that the less diffusive model develops secondary billows later.

\subsubsection{Liska-Wendroff Implosion}

This test from \cite{liskaWendroff_2003} is computed on a 2D domain $D=[0,0.3]\times[0,0.3]$ with reflecting boundary conditions using $256^{2}$ elements.  
Below the line $x^{2}=0.15-x^{1}$, we initially set $\vect{U}=\big(0.125,\vect{0.0},0.35\big)^{\trans}$, while $\vect{U}=\big(1.0,\vect{0.0},2.5\big)^{\trans}$ elsewhere.

\begin{figure}[h]
  \centering
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/Implosion_01_HighTCI_Astronum_2018}
  \end{minipage}\hspace{0.5pc}%
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/Implosion_02_HighTCI_Astronum_2018}
  \end{minipage}
  \caption{\label{fig:Implosion}Plots for the Liska-Wendroff implosion problem at $t=0.045$ (left) and $t=2.5$ (right), intended to match Figures~4.10 and 4.11 in \cite{liskaWendroff_2003}.  The color map shows the pressure distribution, black contours show the mass density, while arrows indicate the velocity.}
\end{figure}

Results for $t=0.045$ and $t=2.5$, with $C_{\TCI}=0.6$, are displayed in Figure~\ref{fig:Implosion} (left and right panels, respectively), which agree qualitatively with \cite{liskaWendroff_2003}, who compared the results of eight different schemes for this problem.  
When $t=0.045$, a shock wave propagates towards the origin of $D$, while a contact discontinuity is trailing the shock (cf. density contours), and a rarefaction wave is spreading in the opposite directions.  
When $t=2.5$, a complex flow pattern with multiple shocks has emerged due to multiple reflections off the boundaries.  
The initial symmetry about the $x^{1}=x^{2}$ diagonal is maintained, and the results from \thornado\ agree qualitatively with the unsplit schemes in \cite{liskaWendroff_2003}.  
In the right panel of Figure~\ref{fig:Implosion}, the chatacteristic ``jet'' has formed and propagates along the diagonal, similar to that displayed by CLAW and WENO in \cite{liskaWendroff_2003}.

\subsubsection{Standing Accretion Shock (SAS)}

This test is of immediate relevance to simulation of CCSNe.  
The initial condition is described in detail in \cite{blondin_etal_2003}, and has been used by many to study the role of the standing accretion shock instability (SASI) on CCSN explosion dynamics.  
We follow closely the description in \cite{blondin_etal_2003} to initialize this test.  
We use spherical polar coordinates, let $D=[0.2,2.0]$, and $\Gamma=4/3$.  
The gravitational potential is given by the point-mass formula with $GM=0.5$.  
A stationary shock is placed at a radius $R_{\shock}=1$.  
Ahead of the shock, the flow is essentially in free-fall towards the shock with a constant Mach number of $100$.  
The mass accretion rate is held fixed at the outer boundary to $\dot{M}=4\pi$.  
Below the shock, $r\in[0.2,1]$, the settling solution is obtained by solving Bernoulli's equation.  
We let matter flow through the inner boundary, and the density and pressure in the boundary elements are set by extrapolating from $D$ assuming $\rho\propto r^{-3}$ and $E\propto r^{-4}$, while the momentum components are held fixed to their initial values.

\begin{figure}[h]
  \centering
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/SAS_Astronum_2018}
  \end{minipage}\hspace{0.5pc}%
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/SAS_TCI_Astronum_2018}
  \end{minipage} \\
  \begin{minipage}{36pc}
    \includegraphics[width=36pc]{./Figures/SAS_Perturbed_Astronum_2018}
  \end{minipage}
  \caption{\label{fig:SAS}Results from the SAS test using $256$ elements.  In the upper left panel we plot the mass density (blue) and velocity (red) versus radius for the initial condition (dashed lines) and for $t=100$ (solid lines) from an unperturbed run.  In the upper right panel we show elements flagged for limiting in the $rt$-plane.  In the bottom panel we show results from a perturbed model, where we plot the relative deviation of the pressure below the shock from; cf. Eq.~\eqref{eq:pressureDeviation}.}
\end{figure}
We use $256$ elements and run the tests until $t=100$ ($>5$ dynamical times \cite{blondin_etal_2003}).  
Results are shown in Figure~\ref{fig:SAS}.  
In the first test we show results from an unperturbed run to gauge the ability of the DG method to maintain the initial state.  
In the upper left panel we compare the initial state (dashed lines) with the solution at $t=100$.  
Except for a slight shift ($\sim1\%$) in the position of the shock, the initial and final states are indistinguishable on the plot.  
Also, there are no oscillations visible in the numerical results.  
In the upper right panel we show elements flagged for limiting in the $rt$-plane (we set $C_{\TCI}=0.03$ in this run), which illustrates how limiting is confined to the shock.  
In the second test we placed a shell ahead of the shock with thickness $0.2$ and density three times higher than the ambient density to induce a strong radial perturbation (similar to \cite{blondin_etal_2003}; see their Figure~4).  
The initial condition we use should be stable against radial perturbations.  
In the lower panel in Figure~\ref{fig:SAS} we plot the pressure deviation below the shock, defined as
\begin{equation}
  \delta p = (p-\bar{p})/\bar{p},
  \quad\text{where}\quad
  \bar{p}=p_{0}(r_{0}/r)^{4},
  \label{eq:pressureDeviation}
\end{equation}
and $p_{0}$ and $r_{0}$ are the pressure and radius closest to the inner boundary.  
As the shell falls through the shock, the perturbation leads to an interesting pattern of waves propagating inside the shocked cavity and oscillations of the shock position, which eventually die out.  
The configuration eventually settles down to something close to the initial condition.  
However, in the final state, the position of the shock is slightly larger than that of the initial state.

\subsubsection{Yahil-Lattimer Collapse}

The final test of the NR hydrodynamics in \thornado\ involves self-gravity and is due to \cite{yahilLattimer_1982,yahil_1983}.  
It models the self-similar collapse of a polytropic star; i.e., $p=\kappa\rho^{\Gamma}$, where $\kappa$ is the polytropic constant.  
This test is also of immediate relevance to CCSN simulations.  
In \cite{yahilLattimer_1982,yahil_1983}, self-similar solutions to the gravitational collapse problem where constructed for $6/5\le\Gamma<4/3$, which smoothly connect an homologously collapsing subsonic inner core (velocity proportional to radius) to a supersonically collapsing outer core in near free-fall ($u\propto r^{-1/2}$).  
\begin{figure}[h]
  \centering
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/YahilLattimerCollapse_MassDensity_Astronum_2018}
  \end{minipage}\hspace{0.5pc}%
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/YahilLattimerCollapse_Velocity_Astronum_2018}
  \end{minipage}
  \caption{\label{fig:YahilLattimer}Results from the Yahil-Lattimer collapse test using $256$ elements.  Results obtained with \thornado\ (dashed black) are compared with the reference solution from Yahil \cite{yahil_1983} (solid red).  The mass density (left panel) and velocity (right panel) are plotted versus radius.  We compare the solutions at select central densities during collapse, approximately $[10^{10},10^{11},10^{12},10^{13},10^{14}]$~g~cm$^{-3}$, which correspond to $(-t)=[51.0,15.0,5.0,1.5,0.5]$~ms.  }
\end{figure}
With two dimensional parameters in the model (the gravitational constant $G$ and the polytropic constant $\kappa$), the dimensionless similarity variable is
\begin{equation}
  X = \kappa^{-1/2} G^{(\Gamma-1)/2} r (-t)^{\Gamma-2},
\end{equation}
where the origin of time is the moment of infinite central density.  
Then all the hydrodynamic variables can be expressed as a function of $X$, and the time-dependent Euler equations can be recast as a system of ODEs (see \cite{yahil_1983} for details).  
To construct a reference to compare with our numerical results we have solved the ODEs given in \cite{yahil_1983} to obtain these self-similar solutions.

Here we show results for a model with $\Gamma=1.3$.  
We use spherical polar coordinates, and let $D=[0,1\times10^{5}]$~km, which is covered with $256$ elements.  
We use a geometric grid to resolve the mass distribution as the star collapses and the central density increases from about $10^{9}$~g~cm$^{-3}$ to about $10^{14}$~g~cm$^{-3}$.  
The size of the innermost element is set to $1$~km while the last element is about $3\times10^{3}$~km.  
We specify the polytropic constant by setting a reference pressure $p=6\times10^{27}$~erg~cm$^{-3}$ for $\rho=7\times10^{9}$~g~cm$^{-3}$ (reasonable values for a massive star in the pre-collapse stage).  
We also specify the collapse time to $(-t)=150$~ms.  
Results comparing the mass density and velocity of Yahil's reference solution to the solution obtained with \thornado\ using $C_{\TCI}=0.03$ are plotted in Figure~\ref{fig:YahilLattimer}.  
The agreement is good throughout collapse.

\subsection{Special relativistic (SR) hydrodynamics}

Here we show results from solving the SR Euler equations in Cartesian coordinates with \thornado.
In this case the state, flux, and source vectors in Eq.~\eqref{eq:extendedEulerCompact} are
\begin{equation}
  \vect{U}=\big(\rho W, \rho h W^{2} u_{j},\tau\big)^{\trans},~
  \vect{F}^{i}=\big(\rho W u^{i},\Pi^{i}_{~j},\rho(hW-1)W u^{i}\big)^{\trans},~
  \text{and}~\vect{S}=0,
\end{equation}
where $W$ is the Lorentz factor, $h=1+(e+p)/\rho$ is the specific enthalpy, $\tau=\rho W(hW-1)-p$, and $\Pi^{i}_{~j}=\rho h W^{2} u^{i} u_{j}+p\delta^{i}_{~j}$.  
We solve two Riemann problems and compare the numerical results with exact solutions obtained with the solver from \cite{martiMuller_2003}.  
Let the primitive state vector be $\vect{V}=\big(\rho,\vect{u},p\big)^{\trans}$.  
In the first problem (Riemann problem~1), taken from \cite{mignoneBodo_2005}, we use $\Gamma=4/3$ and
\begin{equation*}
  \vect{V}_{\leftState}=\big(1.0,0.9,0.0,0.0,1.0\big)^{\trans}\quad\text{and}\quad
  \vect{V}_{\rightState}=\big(1.0,0.0,0.0,0.0,10.0\big)^{\trans},
\end{equation*}
while in the second problem (Riemann problem~2), also from \cite{mignoneBodo_2005}, we use $\Gamma=5/3$, and let
\begin{equation*}
  \vect{V}_{\leftState}=\big(1.0,\vect{0.0},10^{3}\big)^{\trans}\quad\text{and}\quad
  \vect{V}_{\rightState}=\big(1.0,\vect{0.0},10^{-2}\big)^{\trans}.  
\end{equation*}
In both problems, the computational domain is $D=[0,1]$, and the discontinuity is initially located at $x^{1}=0.5$, and the solutions are integrated to $t=0.4$.  
Results are plotted in Figure~\ref{fig:RelativisticHydro}.

\begin{figure}[h]
  \centering
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/MB2005_01_Astronum_2018}
  \end{minipage}\hspace{0.5pc}%
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/MB2005_04_Astronum_2018}
  \end{minipage}
  \caption{\label{fig:RelativisticHydro}Results from solving the SR Euler equations with \thornado.  Riemann problem~1 (left panel) was solved using $100$ elements, while Riemann problem~2 was solved using $400$ elements.  The numerical and exact solutions are plotted with plusses and solid lines, respectively.}
\end{figure}

The main features of the exact solution are captured quite well with the DG method implemented in \thornado.  
For Riemann problem~1, there we observe some oscillations in the density between the leftmost shock and the contact discontinuity located near $x^{1}=0.6$.  
For Riemann problem~2, the maximum density in the thin density shell between the shock and the contact discontinuity is significantly lower for the numerical solution than the exact solution.  
This is due to a combination of spatial resolution and the action of the slope limiter.  
We used $C_{\TCI}=0.03$ in both tests in this section.  
We have found the agreement with the exact solution to improve for larger values of $C_{\TCI}$, but at the expense of somewhat more oscillatory results.

\section{Summary and Outlook}

\ee{Summary and Outlook coming soon.}

We have presented some implementation details and preliminary results of solvers for the Euler equations of gas dynamics in the toolkit for high-order neutrino-radiation hydrodynamics (\thornado).

The performance of the DG algorithm is sensitive to limiting of the polynomial representation.

The algorithms in \thornado\ are implemented in Fortran and intended for evolution within logically Cartesian grids.

Ongoing and future work includes, extension to nuclear equation of state, general relativity within the conformal flatness approximation, porting to hardware accelerators (e.g., GPUs), and deployment within an adaptive mesh refinement framework such as AMREx.  
We hope to report on progress in these directions in the near future.

\section*{References}
\begin{thebibliography}{24}
  \bibitem{bassi_etal_2013} Bassi, F., Franchina, N. Ghidoni, A., \& Rebay, S. 2013, {\it Int. J. Numer. Meth. Fluids}, {\bf 71}, 1322
  \bibitem{blondin_etal_2003} Blondin, J.M., Mezzacappa, A., \& DeMarino, C. 2003, {\it ApJ}, {\bf 584}, 980
  \bibitem{cockburnShu_1998} Cockburn, B. \& Shu, C.-W. 1998, {\it JCP}, {\bf 141}, 199
  \bibitem{cockburnShu_2001} Cockburn, B. \& Shu, C.-W. 2001, {\it Journal of Scientific Computing}, {\bf 16}, 173
  \bibitem{fuShu_2017} Fu, G. \& Shu, C.-W. 2017, {\it JCP}, {\bf 347}, 305
  \bibitem{harten_etal_1983} Harten, A., Lax, P.D., \& Van Leer, B. 1983, {\it SIAM Review}, {\bf 25}, 35
  \bibitem{hesthavenWarburton_2008} Hesthaven, J.S. \& Warburton T. 2008, {\it Nodal discontinuous Galerkin methods: Algorithms, analysis and applications}, Springer
  \bibitem{landauLifshitz_1979} Landau, L.D. \& Lifshitz, E.M. 1979, {\it Fluid Mechanics}, Pergamon
  \bibitem{liskaWendroff_2003} Liska, R. \& Wendroff, B. 2003, {\it SIAM J. Sci. Comput.}, {\bf 25}, 3
  \bibitem{martiMuller_2003} Mart{\'i}, J.M. \& M{\"u}ller, E. 2003, {\it Living Rev. Relativ.}, {\bf 6}, 7
  \bibitem{mcnally_etal_2012} McNally, C., Lyra, W., \& Passy, J.-C. 2012, {\it ApJS}, {\bf 201}, 18
  \bibitem{mignoneBodo_2005} Mignone, A. \& Bodo, G. 2005, {\it MNRAS}, {\bf 364}, 126
  \bibitem{qin_etal_2016} Qin, T., Shu, C.-W., \& Yang, Y. 2016, {\it JCP}, {\bf 315}, 323
  \bibitem{sedov_1959} Sedov, L.I. 1959, {\it Similarity and Dimensional Methods in Mechanics}, Academic Press
  \bibitem{shuOsher_1988} Shu, C.-W. \& Osher, S. 1988, {\it JCP}, {\bf 77}, 439
  \bibitem{shuOsher_1989} Shu, C.-W. \& Osher, S. 1989, {\it JCP}, {\bf 83}, 32
  \bibitem{shu_2016} Shu, C.-W. 2016, {\it JCP}, {\bf 316}, 598
  \bibitem{sod_1978} Sod, G.A. 1978, {\it JCP}, {\bf 27}, 1
  \bibitem{toro_etal_1994} Toro, E.F., Spruce, M., \& Speares W. 1994, {\it Shock Waves}, {\bf 4}, 25
  \bibitem{toro_1999} Toro, E.F. 1999, NUMERICA: A Library of Source Codes for Teaching, Research and Applications
  \bibitem{wuTang_2015} Wu, K. \& Tang, H. 2015, {\it JCP}, {\bf 298}, 539
  \bibitem{yahilLattimer_1982} Yahil, A. \& Lattimer, J.M. 1982, {\it Supernovae: A Survey of Current Research}, Reidel
  \bibitem{yahil_1983} Yahil, A. 1983, {\it ApJ}, {\bf 265}, 1047
  \bibitem{zhangShu_2010} Zhang, X. \& Shu, C.-W. 2010, {\it JCP}, {\bf 229}, 8918
\end{thebibliography}

\clearpage

\section{Introduction}
These guidelines show how to prepare articles for publication in \jpcs\ using \LaTeX\ so they can be published quickly and accurately. Articles will be refereed by the \corg s but the accepted PDF will be published with no editing, proofreading or changes to layout. It is, therefore, the author's responsibility to ensure that the content and layout are correct.  This document has been prepared using \cls\ so serves as a sample document. The class file and accompanying documentation are available from \verb"http://jpcs.iop.org".

\section{Preparing your paper}
\verb"jpconf" requires \LaTeXe\ and  can be used with other package files such
as those loading the AMS extension fonts 
\verb"msam" and \verb"msbm" (these fonts provide the 
blackboard bold alphabet and various extra maths symbols as well as 
symbols useful in figure captions); an extra style file \verb"iopams.sty" is 
provided to load these packages and provide extra definitions for bold Greek letters. 
\subsection{Headers, footers and page numbers}
Authors should {\it not} add headers, footers or page numbers to the pages of their article---they will
be added by \iopp\ as part of the production process.

\subsection{{\cls\ }package options}
The \cls\ class file has two options `a4paper' and `letterpaper':
\begin{verbatim}
\documentclass[a4paper]{jpconf}
\end{verbatim}

or \begin{verbatim}
\documentclass[letterpaper]{jpconf}
\end{verbatim}

\begin{center}
\begin{table}[h]
\caption{\label{opt}\cls\ class file options.}
%\footnotesize\rm
\centering
\begin{tabular}{@{}*{7}{l}}
\br
Option&Description\\
\mr
\verb"a4paper"&Set the paper size and margins for A4 paper.\\
\verb"letterpaper"&Set the paper size and margins for US letter paper.\\
\br
\end{tabular}
\end{table}
\end{center}

The default paper size is A4 (i.e., the default option is {\tt a4paper}) but this can be changed to Letter by 
using \verb"\documentclass[letterpaper]{jpconf}". It is essential that you do not put macros into the text which alter the page dimensions.

\section{The title, authors, addresses and abstract} 
The code for setting the title page information is slightly different from
the normal default in \LaTeX\ but please follow these instructions as carefully as possible so all articles within a conference have the same style to the title page. 
The title is set in bold unjustified type using the command
\verb"\title{#1}", where \verb"#1" is the title of the article. The
first letter of the title should be capitalized with the rest in lower case. 
The next information required is the list of all authors' names followed by 
the affiliations. For the authors' names type \verb"\author{#1}", 
where \verb"#1" is the 
list of all authors' names. The style for the names is initials then
surname, with a comma after all but the last 
two names, which are separated by `and'. Initials should {\it not} have 
full stops. First names may be used if desired. The command \verb"\maketitle" is not
required.

The addresses of the authors' affiliations follow the list of authors. 
Each address should be set by using
\verb"\address{#1}" with the address as the single parameter in braces. 
If there is more 
than one address then a superscripted number, followed by a space, should come at the start of
each address. In this case each author should also have a superscripted number or numbers following their name to indicate which address is the appropriate one for them.

Please also provide e-mail addresses for any or all of the authors using an \verb"\ead{#1}" command after the last address. \verb"\ead{#1}" provides the text Email: so \verb"#1" is just the e-mail address or a list of emails.

The abstract follows the addresses and
should give readers concise information about the content 
of the article and should not normally exceed 200 
words. {\bf All articles must include an abstract}. To indicate the start 
of the abstract type \verb"\begin{abstract}" followed by the text of the 
abstract.  The abstract should normally be restricted 
to a single paragraph and is terminated by the command
\verb"\end{abstract}"

\subsection{Sample coding for the start of an article}
\label{startsample}
The code for the start of a title page of a typical paper might read:
\begin{verbatim}
\title{The anomalous magnetic moment of the 
neutrino and its relation to the solar neutrino problem}

\author{P J Smith$^1$, T M Collins$^2$, 
R J Jones$^{3,}$\footnote[4]{Present address:
Department of Physics, University of Bristol, Tyndalls Park Road, 
Bristol BS8 1TS, UK.} and Janet Williams$^3$}

\address{$^1$ Mathematics Faculty, Open University, 
Milton Keynes MK7~6AA, UK}
\address{$^2$ Department of Mathematics, 
Imperial College, Prince Consort Road, London SW7~2BZ, UK}
\address{$^3$ Department of Computer Science, 
University College London, Gower Street, London WC1E~6BT, UK}

\ead{williams@ucl.ac.uk}

\begin{abstract}
The abstract appears here.
\end{abstract}
\end{verbatim}

\section{The text}
The text of the article should should be produced using standard \LaTeX\ formatting. Articles may be divided into sections and subsections, but the length limit provided by the \corg\ should be adhered to.

\subsection{Acknowledgments}
Authors wishing to acknowledge assistance or encouragement from 
colleagues, special work by technical staff or financial support from 
organizations should do so in an unnumbered Acknowledgments section 
immediately following the last numbered section of the paper. The 
command \verb"\ack" sets the acknowledgments heading as an unnumbered
section.

\subsection{Appendices}
Technical detail that it is necessary to include, but that interrupts 
the flow of the article, may be consigned to an appendix. 
Any appendices should be included at the end of the main text of the paper, after the acknowledgments section (if any) but before the reference list.
If there are two or more appendices they will be called Appendix A, Appendix B, etc. 
Numbered equations will be in the form (A.1), (A.2), etc,
figures will appear as figure A1, figure B1, etc and tables as table A1,
table B1, etc.

The command \verb"\appendix" is used to signify the start of the
appendixes. Thereafter \verb"\section", \verb"\subsection", etc, will 
give headings appropriate for an appendix. To obtain a simple heading of 
`Appendix' use the code \verb"\section*{Appendix}". If it contains
numbered equations, figures or tables the command \verb"\appendix" should
precede it and \verb"\setcounter{section}{1}" must follow it.

\section{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the online version of \jpcs\ references will be linked to their original source or to the article within a secondary service such as INSPEC or ChemPort wherever possible. To facilitate this linking extra care should be taken when preparing reference lists.

Two different styles of referencing are in common use: the Harvard alphabetical system and the Vancouver numerical system.  For \jpcs, the Vancouver numerical system is preferred but authors should use the Harvard alphabetical system if they wish to do so. In the numerical system references are numbered sequentially throughout the text within square brackets, like this [2], and one number can be used to designate several references.

\subsection{Using \BibTeX}
We highly recommend the {\ttfamily\textbf\selectfont iopart-num} \BibTeX\ package by Mark~A~Caprio \cite{iopartnum}, which is included with this documentation.

\subsection{Reference lists}
A complete reference should provide the reader with enough information to locate the article concerned, whether published in print or electronic form, and should, depending on the type of reference, consist of:

\begin{itemize}
\item name(s) and initials;
\item date published;
\item title of journal, book or other publication; 
\item titles of journal articles may also be included (optional);
\item volume number;
\item editors, if any;
\item town of publication and publisher in parentheses for {\it books};
\item the page numbers.
\end{itemize}

Up to ten authors may be given in a particular reference; where 
there are more than ten only the first should be given followed by 
`{\it et al}'. If an author is unsure of a particular journal's abbreviated title it is best to leave the title in 
full. The terms {\it loc.\ cit.\ }and {\it ibid.\ }should not be used. 
Unpublished conferences and reports should generally not be included 
in the reference list and articles in the course of publication should 
be entered only if the journal of publication is known. 
A thesis submitted for a higher degree may be included 
in the reference list if it has not been superseded by a published 
paper and is available through a library; sufficient information 
should be given for it to be traced readily.

\subsection{Formatting reference lists}
Numeric reference lists should contain the references within an unnumbered section (such as \verb"\section*{References}"). The 
reference list itself is started by the code 
\verb"\begin{thebibliography}{<num>}", where \verb"<num>" is the largest
number in the reference list and is completed by
\verb"\end{thebibliography}". 
Each reference starts with \verb"\bibitem{<label>}", where `label' is the label used for cross-referencing. Each \verb"\bibitem" should only contain a reference to a single article (or a single article and a preprint reference to the same article).  When one number actually covers a group of two or more references to different articles, \verb"\nonum"
should replace \verb"\bibitem{<label>}" at
the start of each reference in the group after the first.

For an alphabetic reference list use \verb"\begin{thereferences}" ... \verb"\end{thereferences}" instead of the
`thebibliography' environment and each reference can be start with just \verb"\item" instead of \verb"\bibitem{label}"
as cross referencing is less useful for alphabetic references.

\subsection {References to printed journal articles}
A normal reference to a journal article contains three changes of font (see table \ref{jfonts}) and is constructed as follows:

\begin{itemize}
\item the authors should be in the form surname (with only the first letter capitalized) followed by the initials with no periods after the initials. Authors should be separated by a comma except for the last two which should be separated by `and' with no comma preceding it;
\item the article title (if given) should be in lower case letters, except for an initial capital, and should follow the date;
\item the journal title is in italic and is abbreviated. If a journal has several parts denoted by different letters the part letter should be inserted after the journal in Roman type, e.g. {\it Phys. Rev.} A;
\item the volume number should be in bold type;
\item both the initial and final page numbers should be given where possible. The final page number should be in the shortest possible form and separated from the initial page number by an en rule `-- ', e.g. 1203--14, i.e. the numbers `12' are not repeated.
\end{itemize}

A typical (numerical) reference list might begin

\medskip
\begin{thebibliography}{9}
\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
{\it J. Appl. Phys}. {\bf 87} 965 
\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
{\it Electron. Lett.} {\bf 32} 1105 
\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
{\it J. Appl. Phys.} {\bf 83} 826 
\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
\end{thebibliography}
\smallskip

\noindent which would be obtained by typing

\begin{verbatim}
\begin{\thebibliography}{9}
\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
{\it J. Appl. Phys}. {\bf 87} 965 
\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
{\it Electron. Lett.} {\bf 32} 1105 
\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
{\it J. Appl. Phys.} {\bf 83} 826 
\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
\end{\thebibliography}
\end{verbatim}

\begin{center}
\begin{table}[h]
\centering
\caption{\label{jfonts}Font styles for a reference to a journal article.} 
\begin{tabular}{@{}l*{15}{l}}
\br
Element&Style\\
\mr
Authors&Roman type\\
Date&Roman type\\
Article title (optional)&Roman type\\
Journal title&Italic type\\
Volume number&Bold type\\
Page numbers&Roman type\\
\br
\end{tabular}
\end{table}
\end{center}

\subsection{References to \jpcs\ articles}
Each conference proceeding published in \jpcs\ will be a separate {\it volume}; 
references should follow the style for conventional printed journals. For example:\vspace{6pt}
\numrefs{1}
\item Douglas G 2004 \textit{J. Phys.: Conf. Series} \textbf{1} 23--36
\endnumrefs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{References to preprints}
For preprints there are two distinct cases:
\renewcommand{\theenumi}{\arabic{enumi}}
\begin{enumerate}
\item Where the article has been published in a journal and the preprint is supplementary reference information. In this case it should be presented as:
\medskip
\numrefs{1}
\item Kunze K 2003 T-duality and Penrose limits of spatially homogeneous and inhomogeneous cosmologies {\it Phys. Rev.} D {\bf 68} 063517 ({\it Preprint} gr-qc/0303038)
\endnumrefs
\item Where the only reference available is the preprint. In this case it should be presented as
\medskip
\numrefs{1}
\item Milson R, Coley A, Pravda V and Pravdova A 2004 Alignment and algebraically special tensors {\it Preprint} gr-qc/0401010
\endnumrefs
\end{enumerate}

\subsection{References to electronic-only journals}
In general article numbers are given, and no page ranges, as most electronic-only journals start each article on page 1.

\begin{itemize} 
\item For {\it New Journal of Physics} (article number may have from one to three digits)
\numrefs{1}
\item Fischer R 2004 Bayesian group analysis of plasma-enhanced chemical vapour deposition data {\it New. J. Phys.} {\bf 6} 25 
\endnumrefs
\item For SISSA journals the volume is divided into monthly issues and these form part of the article number

\numrefs{2}
\item Horowitz G T and Maldacena J 2004 The black hole final state {\it J. High Energy Phys.}  	JHEP02(2004)008
\item Bentivegna E, Bonanno A and Reuter M 2004 Confronting the IR fixed point cosmology 	with 	high-redshift observations {\it J. Cosmol. Astropart. Phys.} JCAP01(2004)001  
\endnumrefs
\end{itemize}

\subsection{References to books, conference proceedings and reports}
References to books, proceedings and reports are similar to journal references, but have 
only two changes of font (see table~\ref{book}).

\begin{table}
\centering
\caption{\label{book}Font styles for references to books, conference proceedings and reports.}
\begin{tabular}{@{}l*{15}{l}}
\br
Element&Style\\
\mr
Authors&Roman type\\
Date&Roman type\\
Book title (optional)&Italic type\\
Editors&Roman type\\
Place (city, town etc) of publication&Roman type\\
Publisher&Roman type\\
Volume&Roman type\\
Page numbers&Roman type\\
\br
\end{tabular}
\end{table}

Points to note are:
\medskip
\begin{itemize}
\item Book titles are in italic and should be spelt out in full with initial capital letters for all except minor words. Words such as Proceedings, Symposium, International, Conference, Second, etc should be abbreviated to {\it Proc.}, {\it Symp.}, {\it Int.}, {\it Conf.}, {\it 2nd}, respectively, but the rest of the title should be given in full, followed by the date of the conference and the town or city where the conference was held. For Laboratory Reports the Laboratory should be spelt out wherever possible, e.g. {\it Argonne National Laboratory Report}.
\item The volume number, for example vol 2, should be followed by the editors, if any, in a form such as `ed A J Smith and P R Jones'. Use {\it et al} if there are more than two editors. Next comes the town of publication and publisher, within brackets and separated by a colon, and finally the page numbers preceded by p if only one number is given or pp if both the initial and final numbers are given.
\end{itemize}

Examples taken from published papers:
\medskip

\numrefs{99}
\item Kurata M 1982 {\it Numerical Analysis for Semiconductor Devices} (Lexington, MA: Heath)
\item Selberherr S 1984 {\it Analysis and Simulation of Semiconductor Devices} (Berlin: Springer)
\item Sze S M 1969 {\it Physics of Semiconductor Devices} (New York: Wiley-Interscience)
\item Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} (Moscow: Moscow State University Press) p 103
\item Caplar R and Kulisic P 1973 {\it Proc. Int. Conf. on Nuclear Physics (Munich)} vol 1 (Amsterdam: 	North-Holland/American Elsevier) p 517
\item Cheng G X 2001 {\it Raman and Brillouin Scattering-Principles and Applications} (Beijing: Scientific) 
\item Szytula A and Leciejewicz J 1989 {\it Handbook on the Physics and Chemistry of Rare Earths} vol 12, ed K A Gschneidner Jr and L Erwin (Amsterdam: Elsevier) p 133
\item Kuhn T 1998 {\it Density matrix theory of coherent ultrafast dynamics Theory of Transport Properties of Semiconductor Nanostructures} (Electronic Materials vol 4) ed E Sch\"oll (London: Chapman and Hall) chapter 6 pp 173--214
\endnumrefs

\section{Tables and table captions}
Tables should be numbered serially and referred to in the text 
by number (table 1, etc, {\bf rather than} tab. 1). Each table should be a float and be positioned within the text at the most convenient place near to where it is first mentioned in the text. It should have an 
explanatory caption which should be as concise as possible.

\subsection{The basic table format}
The standard form for a table is:
\begin{verbatim}
\begin{table}
\caption{\label{label}Table caption.}
\begin{center}
\begin{tabular}{llll}
\br
Head 1&Head 2&Head 3&Head 4\\
\mr
1.1&1.2&1.3&1.4\\
2.1&2.2&2.3&2.4\\
\br
\end{tabular}
\end{center}
\end{table}
\end{verbatim}

The above code produces table~\ref{ex}.

\begin{table}[h]
\caption{\label{ex}Table caption.}
\begin{center}
\begin{tabular}{llll}
\br
Head 1&Head 2&Head 3&Head 4\\
\mr
1.1&1.2&1.3&1.4\\
2.1&2.2&2.3&2.4\\
\br
\end{tabular}
\end{center}
\end{table}

Points to note are:
\medskip
\begin{enumerate}
\item The caption comes before the table.
\item The normal style is for tables to be centred in the same way as
equations. This is accomplished
by using \verb"\begin{center}" \dots\ \verb"\end{center}".

\item The default alignment of columns should be aligned left.

\item Tables should have only horizontal rules and no vertical ones. The rules at
the top and bottom are thicker than internal rules and are set with
\verb"\br" (bold rule). 
The rule separating the headings from the entries is set with
\verb"\mr" (medium rule). These commands do not need a following double backslash.

\item Numbers in columns should be aligned as appropriate, usually on the decimal point;
to help do this a control sequence \verb"\lineup" has been defined 
which sets \verb"\0" equal to a space the size of a digit, \verb"\m"
to be a space the width of a minus sign, and \verb"\-" to be a left
overlapping minus sign. \verb"\-" is for use in text mode while the other
two commands may be used in maths or text.
(\verb"\lineup" should only be used within a table
environment after the caption so that \verb"\-" has its normal meaning
elsewhere.) See table~\ref{tabone} for an example of a table where
\verb"\lineup" has been used.
\end{enumerate}

\begin{table}[h]
\caption{\label{tabone}A simple example produced using the standard table commands 
and $\backslash${\tt lineup} to assist in aligning columns on the 
decimal point. The width of the 
table and rules is set automatically by the 
preamble.}

\begin{center}
\lineup
\begin{tabular}{*{7}{l}}
\br                              
$\0\0A$&$B$&$C$&\m$D$&\m$E$&$F$&$\0G$\cr 
\mr
\0\023.5&60  &0.53&$-20.2$&$-0.22$ &\01.7&\014.5\cr
\0\039.7&\-60&0.74&$-51.9$&$-0.208$&47.2 &146\cr 
\0123.7 &\00 &0.75&$-57.2$&\m---   &---  &---\cr 
3241.56 &60  &0.60&$-48.1$&$-0.29$ &41   &\015\cr 
\br
\end{tabular}
\end{center}
\end{table}

\section{Figures and figure captions}
Figures must be included in the source code of an article at the appropriate place in the text not grouped together at the end.

Each figure should have a brief caption describing it and, if 
necessary, interpreting the various lines and symbols on the figure. 
As much lettering as possible should be removed from the figure itself and 
included in the caption. If a figure has parts, these should be 
labelled ($a$), ($b$), ($c$), etc. 
\Tref{blobs} gives the definitions for describing symbols and lines often
used within figure captions (more symbols are available
when using the optional packages loading the AMS extension fonts).

\begin{table}[h]
\caption{\label{blobs}Control sequences to describe lines and symbols in figure 
captions.}
\begin{center}
\begin{tabular}{lllll}
\br
Control sequence&Output&&Control sequence&Output\\
\mr
\verb"\dotted"&\dotted        &&\verb"\opencircle"&\opencircle\\
\verb"\dashed"&\dashed        &&\verb"\opentriangle"&\opentriangle\\
\verb"\broken"&\broken&&\verb"\opentriangledown"&\opentriangledown\\
\verb"\longbroken"&\longbroken&&\verb"\fullsquare"&\fullsquare\\
\verb"\chain"&\chain          &&\verb"\opensquare"&\opensquare\\
\verb"\dashddot"&\dashddot    &&\verb"\fullcircle"&\fullcircle\\
\verb"\full"&\full            &&\verb"\opendiamond"&\opendiamond\\
\br
\end{tabular}
\end{center}
\end{table}

Authors should try and use the space allocated to them as economically as possible. At times it may be convenient to put two figures side by side or the caption at the side of a figure. To put figures side by side, within a figure environment, put each figure and its caption into a minipage with an appropriate width (e.g. 3in or 18pc if the figures are of equal size) and then separate the figures slightly by adding some horizontal space between the two minipages (e.g. \verb"\hspace{.2in}" or \verb"\hspace{1.5pc}". To get the caption at the side of the figure add the small horizontal space after the \verb"\includegraphics" command and then put the \verb"\caption" within a minipage of the appropriate width aligned bottom, i.e. \verb"\begin{minipage}[b]{3in}" etc (see code in this file used to generate figures 1--3).

Note that it may be necessary to adjust the size of the figures (using optional arguments to \verb"\includegraphics", for instance \verb"[width=3in]") to get you article to fit within your page allowance or to obtain good page breaks.

\begin{figure}[h]
\begin{minipage}{14pc}
\includegraphics[width=14pc]{name.eps}
\caption{\label{label}Figure caption for first of two sided figures.}
\end{minipage}\hspace{2pc}%
\begin{minipage}{14pc}
\includegraphics[width=14pc]{name.eps}
\caption{\label{label}Figure caption for second of two sided figures.}
\end{minipage} 
\end{figure}

\begin{figure}[h]
\includegraphics[width=14pc]{name.eps}\hspace{2pc}%
\begin{minipage}[b]{14pc}\caption{\label{label}Figure caption for a narrow figure where the caption is put at the side of the figure.}
\end{minipage}
\end{figure}

Using the graphicx package figures can be included using code such as:
\begin{verbatim}
\begin{figure}
\begin{center}
\includegraphics{file.eps}
\end{center}
\caption{\label{label}Figure caption}
\end{figure}
\end{verbatim}

\section*{References}
\begin{thebibliography}{9}
\bibitem{iopartnum} IOP Publishing is to grateful Mark A Caprio, Center for Theoretical Physics, Yale University, for permission to include the {\tt iopart-num} \BibTeX package (version 2.0, December 21, 2006) with  this documentation. Updates and new releases of {\tt iopart-num} can be found on \verb"www.ctan.org" (CTAN). 
\end{thebibliography}

\end{document}

### 2018-10-03 Documents/M1/Astronum_2018/manuscript.tex
Update the latest version.

@@
 \usepackage{url}
+\usepackage[numbers]{natbib}
 
@@
 \begin{abstract}
-We develop implicit-explicit (IMEX) schemes for neutrino transport though a background material in \texttt{thornado} code with two-moment method.
-Two-moment method evolves the angular moments of a neutrino phase space distribution function and the moments have upper and lower bounds that introduced by Pauli's exclusion principle.
-To ensure the scheme preserves these bounds, a algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
+We develop implicit-explicit (IMEX) schemes for neutrino transport though a background material in \texttt{thornado} code with two-moment method that evolves the angular moments of a neutrino phase space distribution function.
+Considering the upper and lower bounds that introduced by Pauli's exclusion principle on the moments, a algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
 Severn algebraic closures are compared with these bounds and Cernohorsky \& Bludman closure\cite{cernohorskyBludman_1994} which preserves the bounds is chosen for our IMEX schemes.
@@
 PD-ARS denotes convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy, high-order accuracy in the streaming limit, and works well in the diffusion limit.
-The two PD-ARSs have second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore second-order and third-order accurate in the streaming limit.
-The accuracy and convex-invariance of PD-ARSs are demonstrated in the numerical tests with a first-order discontinuous Galerkin method for spatial discretization and a simple Lax-Friedrichs flux.
+Our two PD-ARSs have second-order and third-order explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore are second-order and third-order accurate in the streaming limit.
+The accuracy and convex-invariance of PD-ARSs are demonstrated in the numerical tests with a first-order discontinuous Galerkin(DG) method for spatial discretization and a simple Lax-Friedrichs flux.
 

### 2018-10-03 Documents/M1/Astronum_2018/sections/Conclusion.tex
Update the latest version.

@@
 
-In the applications motivating this work, the neutrino distribution function can vary from 0 to 1, and we have considered the algebraic closure respecting Fermi-Dirac statistics for both low and high occupied condition.
-Different values given by different algebraic closures were compared with the boundary values given by the Fermi-Dirac statistics at different occupation.
-Among the algebraic closures we considered, Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblanc_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka_1991} Janka 2\cite{janka_1992} and Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}, only Cernohorsky \& Bludman closure respecting Fermi-Dirac statistics for any occupancy.
-And it is Cernohorsky \& Bludman closure that we employed in the numerical tests in Section~\ref{se:NumericalTests}.
+In the applications motivating this work, the neutrino distribution function can vary from 0 to 1.
+Hence, we have considered the algebraic closure respecting Fermi-Dirac statistics for both low and high occupied condition: different values given by different algebraic closures are compared with the boundary values given by the Fermi-Dirac statistics at different occupation.
+Among the seven algebraic closures we considered, Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka_1991} Janka 2\cite{janka_1992} and Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}, only Cernohorsky \& Bludman closure respecting Fermi-Dirac statistics for all the occupancy.
+So we employ Cernohorsky \& Bludman closure in all the numerical tests in Section~\ref{se:NumericalTests}.
 
-Following the work we have done in \cite{chu_etal_2018}, two PD-ARSs have been proposed.
+Two PD-ARSs are proposed for the desired IMEX scheme.
 The one with SSPRK2 is second-order and strong stability-preserving in the streaming limit while other with SSPRK3 is third-order.
-Their properties, accuracy and convex-invariant, are demonstrated with numerical tests.
+Their properties, both accuracy and convex-invariant, are demonstrated with numerical tests.
 

### 2018-10-03 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Update the latest version.

--- 2018-10-01 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
@@
 \section{Spacial Discretization}\label{se:SpacialDiscretization}
-
-Divide the spatial domain $D$ into $N$ cells and denote the cell as $I_{i}$ with $i = 1,\ldots,N$, so that
+Here we briefly outline our spacial discretization with the first order discontinuous Galerkin method.
+Let the spatial dimension be $d$ and employ Cartesian coordinates.
+We divide the spatial domain $D$ evenly into $N$ cells and denote the cell as $\bK_{i}$ with $i = 1,\ldots,N$, so that
 \begin{equation*}
-D = \cup_{i = 1}^{N} I_{i}.
+D = \cup_{i = 1}^{N} \bK_{i} \quad \text{with} \quad
+  \bK_{i}=\{\,\vect{x} : x^{i} \in K^{i} := (\xL^{i},\xH^{i}),~|~i=1,\ldots,d\,\}.
 \end{equation*}
-Each of the cell has a volume/length of $\dx$.
+Each of the cell has a volume of $|\bK|$
+\begin{equation*}
+  |\bK| = \int_{\bK}d\vect{x}, \quad\text{where}\quad d\vect{x} = \prod_{i=1}^{d}dx^{i}.  
+\end{equation*}
 Then we have cell average moment:
 \begin{equation}
-\bcM_{i} = \dfrac{1}{\dx} \int_{I_i}\bcM dx.
+\bcM_{i} = \dfrac{1}{|\bK|} \int_{\bK_i}\bcM dx.
 \end{equation}
-Integrate Eq.~\eqref{eq:momentEquations} for each cell $I_{i}$ to have
+Integrate Eq.~\eqref{eq:momentEquations} for each cell $\bK_{i}$ to have
 \begin{equation}
-\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{\dx} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
+\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{|\bK|} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
 \end{equation}
@@
   =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big).
+  \label{eq:Lax-Friedrichs flux}
 \end{equation}
 Therefore, by treating the flux term explicitly and the collision term implicitly, we have
-\begin{align*}
+\begin{align}
 \bcM_{i}^{n+1} = \widetilde{\bcM}^{n}_{i} + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i})
-\end{align*}
+\label{eq:MomentIMEX}
+\end{align}
 with
-\begin{align*}
+\begin{align}
 \widetilde{\bcM}^{n}_{i} 
-& = \bcM_{i}^{n} - \dfrac{\dt}{\dx} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
+& = \bcM_{i}^{n} - \dfrac{\dt}{|\bK|} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
 & = (1-\beta)\bcM_{i}^{n} + \beta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right]
-\end{align*}
-where $\beta := \dfrac{\dt}{\dx}$.
+\label{eq:widetildeM}
+\end{align}
+where $\beta := \frac{\dt}{|\bK|}$.
+
 Assume $\bcM_{i}^{n}$ is realizable for all $i$. 
-Lemma 3 in \cite{chu_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.
-Substitute the Lax-Friedrichs flux formula in and $\widetilde{\bcM}^{n}_{i}$ becomes a convex combination of $\bcM_{i}^{n}$ and the square bracket term if $\beta \in [0,1]$.
-So it is realizable if $\beta \in [0,1]$ and the square bracket term is realizable.
-Given by Lemma 2 in \cite{chu_2018}, the square bracket term is realizable.
+For Eq.~\eqref{eq:MomentIMEX}, lemma 3 in \cite{chu_etal_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.
+Substitute the Lax-Friedrichs flux Eq.~\eqref{eq:Lax-Friedrichs flux} in and $\widetilde{\bcM}^{n}_{i}$ becomes Eq.~\eqref{eq:widetildeM}, a convex combination of $\bcM_{i}^{n}$ and the square bracket term if $\beta \in [0,1]$, and it is realizable if $\beta \in [0,1]$ and the square bracket term is realizable.
+Given by Lemma 2 in \cite{chu_etal_2018}, the square bracket term is indeed realizable.
 Therefore, $\bcM^{n+1}_{i}$ remains realizable given $\beta \in [0,1]$.

### 2018-10-03 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Update the latest version.

--- 2018-09-28 Documents/M1/Astronum_2018/sections/TwoMoments.tex
@@
 
-The inequalities in Eq.\ref{eq:MomentsBounds} define the realizable $\bcM$ which defines a convex set in $\cJ -\bcH$ space.
+The inequalities in Eq.~\eqref{eq:MomentsBounds} define the realizable $\bcM$ which defines a convex set in $\cJ -\bcH$ space.
 As we will see later in Section \ref{se:SpacialDiscretization}, this convexity makes a constraint-preserving spacial discretization possible.
 
-The inequalities in Eq.\ref{eq:eddingtonFactorBounds} desire more attention than have be given.
-They have the equal importance as the inequalities in Eq.\ref{eq:MomentsBounds} in preserving the validity of the simulation result.
-However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson [citation], Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2 [citation] may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1 [citation] can be dangerous for both the cases.
+The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} desire more attention than have be given.
+They have the equal importance as the inequalities in Eq.~\eqref{eq:MomentsBounds} in preserving the validity of the simulation result.
+However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.~\eqref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1\cite{janka_1991} can be dangerous for both the cases.
 The only algebraic closure that remains in the bounds among those seven plotted closures is Cernohorsky \& Bludman's \cite{cernohorskyBludman_1994}.
+
+Though Levermore closure and Minerbo closure don't conserve the bounds with high occupied distribution, they are widely used: {O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan and et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018} and Just et al\cite{just_etal_2018} use Minerbo closure and Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018} and Kuroda et al\cite{kuroda_etal_2016} use Levermore clsoure.
+
 \begin{figure}[h]

### 2018-10-03 Documents/M1/Astronum_2018/sections/intro.tex
Update the latest version.

@@
 In two-moment method, the evolve variables are the zeroth and first angular moments of the distribution function $f$, the spectral particle density $\cJ$ and flux $\bcH$ respectively.
+However, the Boltzmann transport equation is a nonlinear equation.
+Its integral form which gives the two-moment method requires the information of the second angular moment $\bcK$ to close the system.
+Therefore, a algebraic closure which gives a approximated value of $\bcK$ given $\cJ$ and $\bcH$ is needed.
+The two-moment method has been widely applied with different algebraic closures, such as the Minerbo\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan and et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018} and Just et al\cite{just_etal_2018} ) and the Levermore\cite{levermore_1984} closure(e.g.~Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018} and Kuroda et al\cite{kuroda_etal_2016}).
 
@@
 
-\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.} \cite{vartanyan_etal_2018,oConnorCouch_2018,pan_etal_2018,cabezon_etal_2018,glas_etal_2018,just_etal_2018,kuroda_etal_2016}
-
+%\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.} 
 To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a convex-invariant diffusion accurate IMEX schemes for ensure a valid result.
-Here is the explanation.
-
-First of all, the Boltzmann transport equation is a nonlinear equation.
-Its integral form which gives the two-moment method requires the information of $(i+1)$-th order moment for $i$-th order moment evolution.
-Therefore, two-moment method needs a algebraic closure which gives a approximated value of the second order moment $\bcK$ given $\cJ$ and $\bcH$.
-
-Second, the angular moments are confined.
+Because the angular moments are confined.
 Since a neutrino distribution function is confined ($f\in(0,1)$) by the Pauli exclusion principle, its moments as integrals of a confined function over confined domain ($\omega\in\bbS^{2}$) are also confined.
@@
 Hence, the algebraic closure should give a realizable $\bcK$ and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
+That's why a Fermi-Dirac statistics satisfied algebraic closure is needed.
+Then, the realizability of $\cJ$ and $\bcH$ on each time step requires a convex-invariant IMEX.
+Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.
+What's more, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.
 
-Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a convex-invariant IMEX.
-Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.
-
-Fourth, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.
 \rc{\cite{gottlieb_etal_2001} showed standard IMEX scheme can't have an order higher than first without a restrict time step requirement.}
 To have second-order (or higher-order) accuracy, some correction steps are needed.
-However, the correction step can deteriorate the accuracy of the IMEX in the diffusion limit and restrict the time step.
+Unfortunately, the correction step can deteriorate the accuracy of the IMEX in the diffusion limit and restrict the time step.
 To keep simple, we focus on the IMEX scheme without correction step and require it high-order (second or higher order) in the streaming limit and diffusion accurate.

### 2018-10-03 Documents/M1/Astronum_2018/sections/Numerical.tex
Modified the numerical tests section

--- 2018-09-28 Documents/M1/Astronum_2018/sections/Numerical.tex
@@
 
-In this section we present the numerical results obtained with the PD-ARS schemes provided in this paper.
-The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in various regimes.
-The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the realizability-preserving of PD-ARSs scheme.
+In this section we present the numerical results obtained with the PD-ARS schemes given in Section~\ref{se:TimeIntegration}.
+The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in streaming, absorption, and scattering dominated regimes in one spatial dimension.
+The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the convex-invariance of PD-ARSs scheme.
 All the tests in this subsection were applied with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $.
+
 \subsection{Accuracy Tests}
 \label{se: Accuracy Tests}
-To compare the accuracy of the IMEX scheme, we applied our PDARSs and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
-All the tests in this subsection were applied with the maximum entropy closure in the low occupancy limit.
-In the streaming test, the second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} , (SSPRK2 and SSPRK3, respectively) are also applied to serve as an reference.
-More information and the definition of the absolute error and the relative error can be found in \cite{chu_2018}.
+To compare the accuracy of the IMEX scheme, we applied our PDARSs and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some problems with known smooth solutions in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
+All the tests in this subsection were applied with the maximum entropy closure in the low occupancy limit(i.e., the Minerbo closure).
+In the streaming test, the second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} , (SSPRK2 and SSPRK3, respectively) are also applied to serve as references.
+To compare the numerical results to analytic solutions, the cell averaged absolute error or the cell averaged relative error are computed.
+For convergence test, the number of elements ($N$) vary from 8 to 128.
 
 \subsubsection{Sine Wave Streaming}
-This test involves the streaming part only: the collision term is turned off. 
-A periodic domain $D$ was applied and the initial condition is given by...
-More information can be found in \cite{chu_2018}.
-In Figure ~\ref{fig: SineWaveStreaming}, the absolute error for the number density is plotted versus the number of elements $N$.
-Errors obtained with SSPRK3 and PD-ARS with SSPRK3 decrease as $N^{-3}$ as expected.
+Sine wave streaming test is designed for the steaming dominated regime with $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
+A periodic domain with length=1 is applied and the initial condition is $\cJ = \bcH =$ a spacial sine wave function.
+We evolve until the since wave has completed 10 crossing of the domain.
+Figure~\ref{fig: SineWaveStreaming} plots the absolute error for the number density versus the number of elements $N$.
+We see the errors obtained with SSPRK3 and PD-ARS with SSPRK3 decrease as $N^{-3}$ as expected.
 All the other schemes have errors decreases as $N^{-2}$.
+Among the second-order schemes, SSP2332 has the smallest error.
+
 In the streaming limit, PD-ARSs degenerate to their explicit part, SSPRK2 and SSPRK3, respectively.
-Hence, errors of PD-ARS and SSPRKs are indistinguishable on the plot.
-Among the second-order schemes, SSP2332 has the smallest error.
+That's why errors of PD-ARSs and SSPRKs are indistinguishable on the plot.
+
 \begin{figure}[h]
@@
 Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crossing), PD-ARS with SSPRK2 (light red circles) and PD-ARS with SSPRK2 (light red hexagram).
-Black dash-dot reference lines are proportional to $N^{-1}$ (top), $N^{-2}$ (middle), and $N^{-3}$ (bottom), respectively.}
+Black dash reference lines are proportional to $N^{-2}$ (top), and $N^{-3}$ (bottom), respectively.}
    \label{fig: SineWaveStreaming}
@@
 \subsubsection{Sine Wave Damping}
-Figure~\ref{fig:SineWaveDamping} shows the numerical result of sine wave damping test.
-See \cite{chu_2018} for more information about the test setting.
+This test, adapted from \cite{skinnerOstriker_2013}, is designed for absorption dominated regime with $\sigma_{\Scatt} = 0, f_0 = 0$, which results in exponential damping of the wave amplitude.
+A periodic domain with length=1 and a initial condition with $\cJ = \bcH =$ a spacial sine wave function is applied.
+The amplitude of analytical solution decreasing as $e^{-\sigma_{\Ab} t}$.
+We evolve for $\sigma_{\Ab}$ = 0.1, 1 and 10 until the initial condition has been damped by factor $e^{-10}$. 
+Figure~\ref{fig:SineWaveDamping} shows convergence results of sine wave damping test with a relative error.
 SSP2332 as a second-order scheme display second order convergence rate.
-PD-ARSs convergent in first order, as a price paid for realizability-preserving.
+PD-ARSs convergent in first order as a price paid for convex-invariance.
 \begin{figure}[h]
@@
 The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).
-Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
+Black dash reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
   \label{fig:SineWaveDamping}
@@
 \subsubsection{Sine Wave Diffusion}
-The last test with known smooth solution is sine wave diffusion test.
-See \cite{chu_2018} for more information about the test setting.
-Figure~\ref{fig:SineWaveDiffusionJ} shows the numerical result.
-SSP2332 and PD-ARSs display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$ and their errors are difficult to distinguish.
+The last test with known smooth solution,adopted from \cite{radice_etal_2013}, is sine wave diffusion test with $\sigma_{\Ab} = 0, f_0 = 0$.
+A periodic domain with $D=\{x:x\in[-3,3]\}$ and a initial condition with $\cJ_{0}$ = a spacial sine wave function and $\cH =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ}{x}$ is applied.
+The analytical solution is given by $\cJ = \cJ_{0} \times e^{-\f{\pi^2 t}{27\sigma_{\Scatt}}}$ and $\cH = (3\,\sigma_{\Scatt})^{-1}\pd{\cJ}{x}$.
+We evolve with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$, and adjust the end time so that $t_{\mbox{\tiny end}}/\sigma_{\Scatt}=1$. 
+Then the amplitude of the sine wave has then been reduced by a factor $e^{-\pi^{2}/27}\approx0.694$ for all values of $\sigma_{\Scatt}$. 
+Figure~\ref{fig:SineWaveDiffusionJ} shows the convergence.
+SSP2332 and PD-ARSs display third-order accuracy for the number density $\cJ$ and second-order accuracy for $\cH_{x}$ and their errors are difficult to distinguish.
 PD-ARS with SSP2332 behaviors as good as SSP2332 in the diffusion region but requires 1/3 less implicit solver.
@@
 The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).
-Black dash-dot on the left plot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.
-Black dash-dot on the right plot reference lines are proportional to $N^{-2}$ .}
+Black dash on the left plot reference lines are proportional to $N^{-2}$ (top) and $N^{-3}$ (bottom), respectively.
+Black dash on the right plot reference lines are proportional to $N^{-2}$ .}
    \label{fig:SineWaveDiffusionJ}

### 2018-10-03 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Update the latest version.
Modified the IMEX section.

@@
 In this section we show how to use the property we introduced at the end of the previous section to construct a constraint-preserving implicit-explicit (IMEX) scheme.
-We can have a more general form of the partial differential equation, Eq.~\eqref{eq:momentEquations},
+The semi-discretization of the moment equation, Eq.~\eqref{eq:momentEquations}, results in a system of ordinary differential equations of the form
 \begin{equation}
@@
 \end{equation}
-is the collection of all moment cell average, $\vect{\cT}$ is the operator corresponding to the flux term and $\f{1}{\tau}\,\vect{\cQ}$ is a linear operators corresponding to the collision term.
+is the collection of all moment cell average, $\vect{\cT}$ is the transport operator corresponding to the flux term, the first term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, and $\f{1}{\tau}\,\vect{\cQ}$ is a linear operators corresponding to the collision term, the second term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}.
+
+Sine the realizable $\bcM$ defines a convex set in $\cJ -\bcH$ space, convex-invariant schemes can be used to design realizability-preserving schemes for the two-moment model.
+The following discussion shows how to construct a convex-invariant scheme.
 
 \subsection{Standard Implicit-Explicit Scheme}
-Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, the standard $s$-stage IMEX schemes take the following form 
+Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form 
 \begin{align}
@@
 \subsection{Constraint-Preserving Implicit-Explicit Scheme}
-The problem left for constructing a constraint-preserving IMEX is finding the conditions $(\tilde{a}_{ij})$, $(a_{ij})$, $\tilde{w}_{i}$ and $w_{i}$ need to satisfied and giving their possible values.
-As Hu et al. did in their paper \cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten to
+Beyond the accuracy requirement, a convex-invariant IMEX has extra constraints to satisfy.
+The problem left is finding those constraints on $(\tilde{a}_{ij})$, $(a_{ij})$, $\tilde{w}_{i}$ and $w_{i}$.
+As Hu et al. did in their paper \cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten as
 \begin{equation}
@@
 \end{equation}
-It can be proved \cite{chu_etal_2018} that the conditions we need for constraint-preserving IMEX is:
+with $c_{ij}$ and $\hat{c}_{ij}$ be given by $a_{ij}$ and $\tilde{a}_{ij}$.
+
+It can be proved \cite{chu_etal_2018} that the conditions we need for a simple convex-invariant IMEX is:
 \begin{enumerate}
@@
                   j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
+
+    And $c_{ij}$ and $\hat{c}_{ij}$ be given by
+\begin{equation}
+  \begin{aligned}
+    c_{i0} &= 1-\sum_{j=2}^{i-1}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad &
+    c_{ij} &= \sum_{l=j}^{i-1}a_{il}b_{lj} \\
+    \tilde{c}_{i0} &= \tilde{a}_{i1}+\sum_{j=2}^{i-1}a_{ij}\tilde{b}_{j1}, \quad &
+    \tilde{c}_{ij} &= \tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}.  
+  \end{aligned}
+  \label{eq:positivityCoefficientsARS}
+\end{equation}
+\begin{equation}
+  b_{ii} = \f{1}{a_{ii}}, \quad
+  b_{ij} = -\f{1}{a_{ii}}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad
+  \tilde{b}_{ij} = -\f{1}{a_{ii}}\Big(\tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}\Big).  
+\end{equation}
+Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.
+
     \item Well-behaved in the diffusion limit; i.e., satisfies \begin{equation}
-      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s.
+      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s,
       \label{eq:diffusionCondition}
     \end{equation}
+    where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix.
     \item Less than four stages ($s\le3$).
@@
 We give two optimized PD-ARS scheme here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. 
-They have $2$-nd order and $3$-rd order accuracy in the streaming limit, respectively.
+They have second order and third order accuracy in the streaming limit, respectively.
 \subsubsection{PD-ARS with SSPRK2}

### 2018-10-06 Documents/M1/Astronum_2018/sections/Acknowledge.tex
Added acknowledgment. Cosmetic changes for the sine wave tests plots.

--- 2018-09-11 Documents/M1/realizableFermionicM1/manuscript.tex
@@
-\documentclass[review]{elsarticle}
+\section{Acknowledgment} \label{se:Acknowledgment}
 
-\usepackage{lineno,hyperref}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{mathrsfs}
-\usepackage{subcaption}
-\usepackage{float}
-
-\modulolinenumbers[5]
-\hypersetup{
-  bookmarksnumbered = true,
-  bookmarksopen=false,
-  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
-  pdffitwindow=true,      % window fit to page when opened
-  pdfnewwindow=true, % links in new window
-  colorlinks=true,           % false: boxed links; true: colored links
-  linkcolor=blue,            % color of internal links
-  citecolor=magenta,    % color of links to bibliography
-  filecolor=magenta,     % color of file links
-  urlcolor=cyan              % color of external links
-}
-
-\journal{Journal of Computational Physics}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\newtheorem{define}{Definition}
-\newtheorem{lemma}{Lemma}
-\newtheorem{prop}{Proposition}
-\newtheorem{rem}{Remark}
-\newtheorem{theorem}{Theorem}
-
-\newcommand{\ee}[1]{{\color{red} EE:~#1}}
-\newcommand{\rc}[1]{{\color{blue} RC:~#1}}
-
-\usepackage{./definitions}
-
-\begin{document}
-
-\begin{frontmatter}
-
-\title{Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}}
-\tnotetext[support]{
-This research is sponsored, in part, by the Laboratory Directed Research and Development Program of Oak Ridge National Laboratory (ORNL), managed by UT-Battelle, LLC for the U.
+\rc{This research is sponsored, in part, by the Laboratory Directed Research and Development Program of Oak Ridge National Laboratory (ORNL), managed by UT-Battelle, LLC for the U.
 S.
@@
 Department of Energy Office of Science and the National Nuclear Security Administration.
-Eirik Endeve was supported in part by NSF under Grant No. 1535130.}
-
-%% Group authors per affiliation:
-\author[utk-phys]{Ran Chu}
-\ead{rchu@vols.utk.edu}
-
-\author[ornl,utk-phys,jics]{Eirik Endeve\corref{cor}}
-\ead{endevee@ornl.gov}
-
-\author[ornl,utk-math]{Cory D. Hauck}
-\ead{hauckc@ornl.gov}
-
-\author[utk-phys,jics]{Anthony Mezzacappa}
-\ead{mezz@utk.edu}
-
-\cortext[cor]{Corresponding author. Tel.:+1 865 576 6349; fax:+1 865 241 0381}
-
-\address[ornl]{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA }
-
-\address[utk-phys]{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
-
-\address[jics]{Joint Institute for Computational Sciences, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354}
-
-\address[utk-math]{Department of Mathematics, University of Tennessee Knoxville, TN 37996-1320}
-
-\begin{abstract}
-Building on the framework of Zhang \& Shu \cite{zhangShu_2010a,zhangShu_2010b}, we develop a realizability-preserving method to simulate the transport of particles (fermions) through a background material using a two-moment model that evolves the angular moments of a phase space distribution function $f$.
-The two-moment model is closed using algebraic moment closures; e.g., as proposed by Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Banach \& Larecki \cite{banachLarecki_2017a}.  
-Variations of this model have recently been used to simulate neutrino transport in nuclear astrophysics applications, including core-collapse supernovae and compact binary mergers.  
-We employ the discontinuous Galerkin (DG) method for spatial discretization (in part to capture the asymptotic diffusion limit of the model) combined with implicit-explicit (IMEX) time integration to stably bypass short timescales induced by frequent interactions between particles and the background.
-Appropriate care is taken to ensure the method preserves strict algebraic bounds on the evolved moments (particle density and flux) as dictated by Pauli's exclusion principle, which demands a bounded distribution function (i.e., $f\in[0,1]$).
-This realizability-preserving scheme combines a suitable CFL condition, a realizability-enforcing limiter, a closure procedure based on Fermi-Dirac statistics, and an IMEX scheme whose stages can be written as a convex combination of forward Euler steps combined with a backward Euler step.
-The IMEX scheme is formally only first-order accurate, but works well in the diffusion limit, and --- without interactions with the background --- reduces to the optimal second-order strong stability-preserving explicit Runge-Kutta scheme of Shu \& Osher \cite{shuOsher_1988}.
-Numerical results demonstrate the realizability-preserving properties of the scheme.  
-We also demonstrate that the use of algebraic moment closures not based on Fermi-Dirac statistics can lead to unphysical moments in the context of fermion transport.  
-\end{abstract}
-
-\begin{keyword}
-Boltzmann equation, 
-Radiation transport, 
-Hyperbolic conservation laws, 
-Discontinuous Galerkin, 
-Implicit-Explicit, 
-Moment Realizability
-\end{keyword}
-
-\end{frontmatter}
-
-\tableofcontents
-
-\linenumbers
-
-\input{sections/intro}
-\input{sections/model}
-\input{sections/realizability}
-\input{sections/algebraicClosures}
-\input{sections/dg}
-\input{sections/imex}
-\input{sections/DGIMEXscheme}
-\input{sections/limiter}
-\input{sections/numerical}
-\input{sections/conclusion}
-\input{sections/appendix}
-
-\section*{References}
-
-\bibliography{./references/references.bib}
-\end{document}
+This material is based, in part, upon work supported by the U.S. Department of Energy, Office of Science, Office of Advanced Scientific Computing Research.  
+Ran Chu was supported in part by NSF under Grant No. 1535130.}

### 2018-10-12 Documents/Euler/ContactWaveSpeed_Relativistic/ContactWaveSpeed_Relativistic.tex
Added derivation of middle wave-speed for 3+1 GR HLLC Riemann solver

\documentclass[10pt,preprint]{../aastex}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{yhmath}
\usepackage{natbib}
\usepackage{../../definitions}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

\usepackage{float}
\usepackage{graphicx}
\newtheorem{remark}{Remark}
\graphicspath{{Figures/}}
\newcommand{\figref}[1]{Figure \ref{#1}}

\begin{document}

\section{Derivation of Middle Wave-Speed Estimate for General Relativistic HLLC Numerical Flux}
For a given Riemann problem we assume that the shocked fluid is composed of two distinct regions, separated by a contact discontinuity (see \figref{Fig:HLLC_RiemannFan}).
\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{HLLC_RiemannFan_MB2005}
\caption{HLLC Riemann fan from \citet{Mignone2005}.}\label{Fig:HLLC_RiemannFan}
\end{figure}

Here we derive an estimate for the propagation speed of that contact discontinuity.

The equations we are solving are the general relativistic equations of hydrodynamics in conservative form:
\begin{equation}
    \pderiv{\left(\sqrtgm\,\bU\right)}{t}+\pderiv{\left(\alpha\,\sqrtgm\,\bF^{i}\left(\bU\right)\right)}{x^{i}}=\alpha\,\sqrtgm\,\bS,
\end{equation}
where $\bU$ is the \textit{vector of conserved variables}, $\bF^{i}\left(\bU\right)$ are the fluxes of the conserved variables along the three spatial directions, $\bS$ is a source term (which does \textit{not} contain any derivatives of the fluid variables), $\alpha$ is the lapse function, and $\sqrtgm$ is the determinant of the spatial three-metric. In deriving the above equations we assume that the lapse function is explicitly independent of time. We can re-write this slightly using the product rule:
\begin{equation}
    \sqrtgm\,\pderiv{\bU}{t}+\bU\,\pderiv{\sqrtgm}{t}+\sqrtgm\,\pderiv{\left(\alpha\,\bF^{i}\right)}{x^{i}}+\alpha\,\bF^{i}\,\pderiv{\sqrtgm}{x^{i}}=\alpha\,\sqrtgm\,\bS.
\end{equation}
Now, moving the terms that don't contain derivatives of the fluid variables to the RHS and dividing by $\sqrtgm$, we obtain:
\begin{equation}\label{Eq:EulerConsSources}
    \pderiv{\bU}{t}+\pderiv{\left(\alpha\,\bF^{i}\right)}{x^{i}}=\bQ,
\end{equation}
where:
\begin{equation}
    \bQ\equiv\alpha\,\bS-\f{1}{\sqrtgm}\left(\bU\,\pderiv{\sqrtgm}{t}+\alpha\,\bF^{i}\,\pderiv{\sqrtgm}{x^{i}}\right).
\end{equation}

The vector of conserved variables is given by \citep{Mignone2005}:
\begin{equation}
    \bU\equiv
    \begin{pmatrix}
      D \\
      S_{j} \\
      E
    \end{pmatrix}=
    \begin{pmatrix}
      \rho\,W \\
      \rho\,h\,W^{2}\,v_{j} \\
      \rho\,h\,W^{2}-p,
    \end{pmatrix}
\end{equation}
where $\rho$ is the rest mass-density, $v_{j}$ are the covariant components of the three-velocity, $p$ is the pressure, and $W$ is the Lorentz factor:
\begin{equation}
    W\equiv\left(1-\vv{v}\cdot\vv{v}\right)^{-1/2}.
\end{equation}
The quantity $h$ is the relativistic specific enthalpy, given by:
\begin{equation}
    h\equiv1+\f{e+p}{\rho},
\end{equation}
where $e$ is the internal energy-density. The fluxes are given by \citep{RezzollaRelHyd}:
\begin{equation}
    \bF^{i}\equiv
    \begin{pmatrix}
      D\left(v^{i}-\alpha^{-1}\,\beta^{i}\right) \\
      S_{j}\left(v^{i}-\alpha^{-1}\,\beta^{i}\right) + p\,\delta^{i}_{~j} \\
      S^{i}-\alpha^{-1}\,\beta^{i}\,E
    \end{pmatrix},
\end{equation}
where $\beta^{i}$ are the components of the shift vector. We define the quantity $\eta^{i}$ as:
\begin{equation}
    \eta^{i}\equiv\alpha^{-1}\,\beta^{i},
\end{equation}
which makes the fluxes that we work with:
\begin{equation}
    \bF^{i}\equiv
    \begin{pmatrix}
      D\left(v^{i}-\eta^{i}\right) \\
      S_{j}\left(v^{i}-\eta^{i}\right) + p\,\delta^{i}_{~j} \\
      S^{i}-\eta^{i}\,E
    \end{pmatrix}.
\end{equation}

We will need to know how the fluxes relate to the conserved variables across shocks. These relations are known as the \textit{Rankine-Hugoniot jump conditions}. We derive them next.

\subsection{Derivation of Rankine-Hugoniot Jump Conditions}
This derivation closely follows \citet{RezzollaRelHyd}.

We start the derivation by integrating the one-dimensional version of \eqref{Eq:EulerConsSources} in space from a point $x_{L}$ to a point $x_{R}$, that contains a shock, which we define to be at a time-dependent point $x_{L}<s\left(t\right)<x_{R}$:
\begin{equation}
    \int\limits_{x_{L}}^{x_{R}}\pd{\bU}{t}\,\sqrtgm\,dx+\int\limits_{x_{L}}^{x_{R}}\pd{\left(\alpha\,\bF\right)}{x}\,\sqrtgm\,dx=\int\limits_{x_{L}}^{x_{R}}\bQ\,\sqrtgm\,dx.
\end{equation}
Using the product rule again, we get:
\begin{equation}
    \int\limits_{x_{L}}^{x_{R}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx-\int\limits_{x_{L}}^{x_{R}}\bU\,\pd{\sqrtgm}{t}\,dx+\int\limits_{x_{L}}^{x_{R}}\pd{\left(\alpha\,\sqrtgm\,\bF\right)}{x}\,dx-\int\limits_{x_{L}}^{x_{R}}\alpha\,\bF\,\pd{\sqrtgm}{x}\,dx=\int\limits_{x_{L}}^{x_{R}}\bQ\,\sqrtgm\,dx.
\end{equation}
Again moving the terms that don't contain derivatives of fluid variables to the RHS, we get:
\begin{equation}
    \int\limits_{x_{L}}^{x_{R}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx+\int\limits_{x_{L}}^{x_{R}}\pd{\left(\alpha\,\sqrtgm\,\bF\right)}{x}\,dx=\int\limits_{x_{L}}^{x_{R}}\,\bQ'\,\sqrtgm\,dx,
\end{equation}
where
\begin{equation}
    \bQ'\equiv\bQ+\f{1}{\sqrtgm}\left(\bU\,\pd{\sqrtgm}{t}+\alpha\,\bF\,\pd{\sqrtgm}{x}\right).
\end{equation}

The second term on the LHS becomes a boundary term. Moving that to the RHS and the source term to the LHS we get:
\begin{equation}
    \alpha\left(x_{L},t\right)\,\sqrtgm\left(x_{L},t\right)\,\bF\left(\bU\left(x_{L},t\right)\right)-\alpha\left(x_{R},t\right)\,\sqrtgm\left(x_{R},t\right)\,\bF\left(\bU\left(x_{R},t\right)\right)=\f{d}{dt}\int\limits_{x_{L}}^{x_{R}}\sqrtgm\,\bU\,dx-\int\limits_{x_{L}}^{x_{R}}\bQ'\,\sqrtgm\,dx.
\end{equation}
We now split the first integral into two parts, with the shock being at an endpoint:
\begin{equation}
    \alpha_{L}\,\sqrtgm_{L}\,\bF_{L}-\alpha_{R}\,\sqrtgm_{R}\,\bF_{R}=\f{d}{dt}\int\limits_{x_{L}}^{s_{L}\left(t\right)}\sqrtgm\,\bU\,dx+\f{d}{dt}\int\limits_{s_{R}\left(t\right)}^{x_{R}}\sqrtgm\,\bU\,dx-\int\limits_{x_{L}}^{x_{R}}\sqrtgm\,\bQ'\,dx,
\end{equation}
where $\bF_{L}\equiv\bF\left(\bU\left(x_{L},t\right)\right)$, etc. We also use the notation that $s_{L}$ means ``approaches $s$ from the left state" and $s_{R}$ means ``approaches $s$ from the right state". Using the rule for differentiating an integral with variable bounds:
\begin{equation}
    \f{d}{dt}\int\limits_{x_{1}\left(t\right)}^{x_{2}\left(t\right)}A\left(x,t\right)\,dx=\int\limits_{x_{1}\left(t\right)}^{x_{2}\left(t\right)}\pd{A\left(x,t\right)}{t}\,dx+A\left(x_{2}\left(t\right),t\right)\,\f{dx_{2}\left(t\right)}{dt}-A\left(x_{1}\left(t\right),t\right)\,\f{dx_{1}\left(t\right)}{dt},
\end{equation}
we find:
\begin{equation}
    \alpha_{L}\,\sqrtgm_{L}\,\bF_{L}-\alpha_{R}\,\sqrtgm_{R}\,\bF_{R}=\f{ds}{dt}\left(\sqrtgm_{L}\,\bU_{L}-\sqrtgm_{R}\,\bU_{R}\right)+\int\limits_{x_{L}}^{s_{L}\left(t\right)}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx+\int\limits_{s_{R}\left(t\right)}^{x_{R}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx-\int\limits_{x_{L}}^{x_{R}}\bQ'\,dx.
\end{equation}
Now we take the limit that $x_{L}\longrightarrow s\left(t\right)$ and $x_{R}\longrightarrow s\left(t\right)$. In this limit all the integrals vanish (since no terms in $\bQ'$ depend on derivatives of fluid variables), and since $\alpha$ and $\sqrtgm$ are continuous across shocks, $\alpha_{L}=\alpha_{R}\equiv\alpha$ and $\sqrtgm_{L}=\sqrtgm_{R}\equiv\sqrtgm$. Defining the shock speed as $ds/dt\equiv\lambda$, we see that the metric determinant cancels, leaving us with the jump conditions:
\begin{equation}
    \alpha\left(\bF_{L}-\bF_{R}\right)=\lambda\left(\bU_{L}-\bU_{R}\right).
\end{equation}

\subsection{Derivation of Contact Wave-Speed}
With the jump conditions we are ready to derive an estimate for the propagation speed of the contact discontinuity. If we assume one state is the shocked region and the other state is the unshocked region then the jump conditions become:
\begin{equation}\label{Eq:RHJump_GR}
    \lambda^{i}\left(\bU^{*}-\bU\right)=\alpha\left(\left(\bF^{*}\right)^{i}-\bF^{i}\right).
\end{equation}
We assume that the flux in the shocked region can be written as:
\begin{equation}
    \left(\bF^{*}\right)^{i}\equiv
    \begin{pmatrix}
      D^{*}\left[\left(v^{*}\right)^{i}-\left(\eta^{*}\right)^{i}\right] \\
      S^{*}_{j}\left[\left(v^{*}\right)^{i}-\left(\eta^{*}\right)^{i}\right] + p^{*}\,\delta^{i}_{~j} \\
      \left(S^{*}\right)^{i}-\left(\eta^{*}\right)^{i}\,E^{*}
    \end{pmatrix}.
\end{equation}
Since $\alpha$ and $\boldsymbol{\beta}$ are continuous, we can equate $\alpha^{*}=\alpha$ and $\boldsymbol{\beta}^{*}=\boldsymbol{\beta}$, and therefore $\left(\eta^{*}\right)^{i}=\eta^{i}$. We also define $\left(v^{*}\right)^{i}\equiv\left(\lambda^{*}\right)^{i}$, the propagation speed of the contact discontinuity. We use the shorthand notation:
\begin{equation}
    \left(X^{*}\right)^{i}=X^{*i}.
\end{equation}
With that the fluxes in the shocked region can be written as:
\begin{equation}\label{Eq:StarFlux}
    \bF^{*i}\equiv
    \begin{pmatrix}
      D^{*}\left(\lambda^{*i}-\eta^{i}\right) \\
      S^{*}_{j}\left(\lambda^{*i}-\eta^{i}\right) + p^{*}\,\delta^{i}_{~j} \\
      S^{*i}-\eta^{i}\,E^{*}
    \end{pmatrix}.
\end{equation}

\subsubsection{Applying the Jump Conditions}
Now we apply the jump conditions, \eqref{Eq:RHJump_GR} to the momentum-density:
\begin{align}
    \lambda^{i}\left(S^{*}_{j}-S_{j}\right)&=\alpha\left[S^{*}_{j}\left(\lambda^{*i}-\eta^{i}\right)+p^{*}\,\delta^{i}_{~j}-S_{j}\left(v^{i}-\eta^{i}\right)-p\,\delta^{i}_{~j}\right]\\
    \implies S^{*}_{j}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)&=S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}\label{Eq:RH_Mom}
\end{align}

Before we apply the jump conditions to the energy-density, we note that:
\begin{align}
    S^{i}&=\left(E+p\right)v^{i}\\
    S^{*i}&=\left(E^{*}+p^{*}\right)\lambda^{*i}.\label{Eq:SsEs}
\end{align}
Next we apply the jump conditions to the energy-density:
\begin{align}
    \lambda^{i}\left(E^{*}-E\right)&=\alpha\left(S^{*i}-\eta^{i}\,E^{*}-S^{i}+\eta^{i}\,E\right)\\
    \implies\lambda^{i}\left(E^{*}-E\right)&=\alpha\left(E^{*}\,\lambda^{*i}+p^{*}\,\lambda^{*i}-\eta^{i}\,E^{*}-E\,v^{i}-p\,v^{i}+\eta^{i}\,E\right)\\
    \implies E^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)&=E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}\,\lambda^{*i}-p\,v^{i}\right).\label{Eq:RH_E}
\end{align}
Now we use \eqref{Eq:SsEs} and re-write \eqref{Eq:RH_Mom} (using the metric to raise and lower indices, so $S^{*}_{j}=\gamma_{jk}S^{*k}$):
\begin{equation}
    \left(E^{*}+p^{*}\right)\gamma_{kj}\,\lambda^{*k}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)=S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}.
\end{equation}
Slight manipulation yields:
\begin{equation}
    E^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)=-p^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)+\f{S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}}{\gamma_{kj}\,\lambda^{*k}}.
\end{equation}
Now we equate this with \eqref{Eq:RH_E}, which gives:
\begin{equation}
    E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}\,\lambda^{*i}-p\,v^{i}\right)=-p^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)+\f{S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}}{\gamma_{kj}\,\lambda^{*k}}.
\end{equation}
Or, multiplying through by $\gamma_{kj}\,\lambda^{*k}$:    
\begin{align}
    &\gamma_{kj}\,\lambda^{*k}\left[E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}\,\lambda^{*i}-p\,v^{i}\right)\right]\nonumber\\
    &\hspace{10em}=-\gamma_{kj}\,\lambda^{*k}\,p^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)+S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}.
\end{align}
We see that the term $\gamma_{kj}\,\lambda^{*k}\,\alpha\,p^{*}\,\lambda^{*i}$ cancels. This gives:
\begin{equation}
    \gamma_{kj}\,\lambda^{*k}\left[E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,v^{i}\right]=-\gamma_{kj}\,\lambda^{*k}\,p^{*}\left(\lambda^{i}+\alpha\,\eta^{i}\right)+S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}.
\end{equation}
Or, grouping the terms with $\lambda^{*k}$ to the LHS:
\begin{equation}
    \left[E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,v^{i}+p^{*}\left(\lambda^{i}+\alpha\,\eta^{i}\right)\right]\gamma_{jk}\,\lambda^{*k}=S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,\delta^{i}_{~j}+\alpha\,p^{*}\,\delta^{i}_{~j},
\end{equation}
We can write this as:
\begin{equation}\label{Eq:AB}
    \left[A^{i}+\left(\lambda^{i}+\alpha\,\eta^{i}\right)p^{*}\right]\gamma_{jk}\,\lambda^{*k}=B^{i}_{~j}+\alpha\,p^{*}\,\delta^{i}_{~j},
\end{equation}
where
\begin{equation}
    A^{i}\equiv E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,v^{i}=\lambda^{i}\,E-\alpha\left(E+p\right)v^{i}+\alpha\,\eta^{i}\,E=\lambda^{i}\,E-\alpha\left(S^{i}-\eta^{i}\,E\right)=\lambda^{i}\,E-\alpha\,F^{i}_{E},
\end{equation}
and
\begin{equation}
    B^{i}_{~j}\equiv S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,\delta^{i}_{~j}=\lambda^{i}\,S_{j}-\alpha\left[S_{j}\,v^{i}+p\,\delta^{i}_{~j}-\eta^{i}\,S_{j}\right]=\lambda^{i}\,S_{j}-\alpha\,F^{i}_{S_{j}}.
\end{equation}
We can solve \eqref{Eq:AB} for $p^{*}$:
\begin{equation}\label{Eq:p*}
  \gamma_{jk}\,\lambda^{*k}\,A^{i}+\gamma_{jk}\,\lambda^{*k}\,\left(\lambda^{i}+\alpha\,\eta^{i}\right)p^{*}=B^{i}_{~j}+\alpha\,p^{*}\,\delta^{i}_{~j}\implies p^{*}=\f{\gamma_{jk}\,\lambda^{*k}\,A^{i}-B^{i}_{~j}}{\alpha\,\delta^{i}_{~j}-\gamma_{jk}\,\lambda^{*k}\left(\lambda^{i}+\alpha\,\eta^{i}\right)}
\end{equation}
At this point we note that because of the conformally-flat approximation, the metric contraction term reduces to:
\begin{equation}
    \gamma_{jk}\,\lambda^{*k}=\gamma_{jj}\,\lambda^{*j}\hspace{2em}\text{(No summation over $j$ index)}.
\end{equation}
So if $i=j$, then $\lambda^{*j}=\lambda^{*i}$ is the normal velocity, which must be continuous across a contact discontinuity, i.e. $\lambda^{*j}_{L}=\lambda^{*j}_{R}=\lambda^{*j}$. Otherwise $\lambda^{*j}$, $j\neq i$ is a tangential velocity, which may be discontinuous across a contact discontinuity, i.e. $\lambda^{*j}_{L}\neq\lambda^{*j}_{R}$. We also know that the pressure is continuous across a contact discontinuity, so $p^{*}_{L}=p^{*}_{R}=p^{*}$. Using this, we can obtain an equation for $\lambda^{*i}$ by setting $j=i$ in \eqref{Eq:p*} and applying it to the left and right sides of the contact discontinuity, and then equating them:
\begin{equation}
    \f{\gamma_{ii,L}\,\lambda^{*i}\,A^{i}_{L}-B^{i}_{~i,L}}{\alpha_{L}-\gamma_{ii,L}\,\lambda^{*i}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta_{L}^{i}\right)}=\f{\gamma_{ii,R}\,\lambda^{*i}\,A^{i}_{R}-B^{i}_{~i,R}}{\alpha_{R}-\gamma_{ii,R}\,\lambda^{*i}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta_{R}^{i}\right)}.
\end{equation}
The minus sign in front of $\lambda^{i}_{L}$ comes about because we demand that $\lambda^{i}$ is \textit{always} greater than or equal to zero, so a subsonic left-moving wave requires a minus sign. \sd{What about super-sonic waves? Does it reducing to HLL mean that the sign isn't important?}
Solving the equation for $\lambda^{*i}$:
\begin{align}
    &\left[\alpha_{R}-\gamma_{ii,R}\,\lambda^{*i}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta_{R}^{i}\right)\right]\left(\gamma_{ii,L}\,\lambda^{*i}\,A^{i}_{L}-B^{i}_{~i,L}\right)=\left[\alpha_{L}-\gamma_{ii,L}\,\lambda^{*i}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta_{L}^{i}\right)\right]\left(\gamma_{ii,R}\,\lambda^{*i}\,A^{i}_{R}-B^{i}_{~i,R}\right)\nonumber\\
    &\implies \alpha_{R}\,\gamma_{ii,L}\,A^{i}_{L}\,\lambda^{*i}-\alpha_{R}\,B^{i}_{~i,L}-\gamma_{ii,R}\,\gamma_{ii,L}\,A^{i}_{L}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta^{i}_{R}\right)\left(\lambda^{*i}\right)^{2}+\gamma_{ii,R}\,B^{i}_{~i,L}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta^{i}_{R}\right)\lambda^{*i}\nonumber\\
    &\hspace{3em}=\alpha_{L}\,\gamma_{ii,R}\,A^{i}_{R}\,\lambda^{*i}-\alpha_{L}\,B^{i}_{~i,R}-\gamma_{ii,L}\,\gamma_{ii,R}\,A^{i}_{R}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta^{i}_{L}\right)\left(\lambda^{*i}\right)^{2}+\gamma_{ii,L}\,B^{i}_{~i,R}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta^{i}_{L}\right)\lambda^{*i}\nonumber\\
    &\implies\gamma_{ii,L}\,\gamma_{ii,R}\left[A^{i}_{R}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta^{i}_{L}\right)-A^{i}_{L}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta^{i}_{R}\right)\right]\left(\lambda^{*i}\right)^{2}\nonumber\\
    &\hspace{5em}+\left\{\gamma_{ii,L}\left[\alpha_{R}\,A^{i}_{L}-B^{i}_{~i,R}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta^{i}_{L}\right)\right]+\gamma_{ii,R}\left[B^{i}_{~i,L}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta^{i}_{R}\right)-\alpha_{L}\,A^{i}_{R}\right]\right\}\lambda^{*i}\nonumber\\
    &\hspace{10em}+\alpha_{L}\,B^{i}_{~i,R}-\alpha_{R}\,B^{i}_{~i,L}=0.
\end{align}
So, we have a quadratic equation in $\lambda^{*i}$:
\begin{equation}
    X^{ii}\,\left(\lambda^{*i}\right)^{2}+X^{i}\,\lambda^{*i}+X=0,
\end{equation}
where (recalling that $\alpha\,\eta^{i}=\beta^{i}$):
\begin{align}
    X^{ii}&=\gamma_{ii,L}\,\gamma_{ii,R}\left[A^{i}_{R}\left(-\lambda^{i}_{L}+\beta^{i}_{L}\right)-A^{i}_{L}\left(\lambda^{i}_{R}+\beta^{i}_{R}\right)\right]\\
    X^{i}&=\gamma_{ii,L}\left[\alpha_{R}\,A^{i}_{L}-B^{i}_{~i,R}\left(-\lambda^{i}_{L}+\beta^{i}_{L}\right)\right]-\gamma_{ii,R}\left[\alpha_{L}\,A^{i}_{R}-B^{i}_{~i,L}\left(\lambda^{i}_{R}+\beta^{i}_{R}\right)\right]\\
    X&=\alpha_{L}\,B^{i}_{~i,R}-\alpha_{R}\,B^{i}_{~i,L}.
\end{align}

If we assume that the geometry fields are continuous, then we can simplify further, specifically:
\begin{align}
    X^{ii}&=\left(\gamma_{ii}\right)^{2}\left[A^{i}_{R}\left(-\lambda^{i}_{L}+\beta^{i}\right)-A^{i}_{L}\left(\lambda^{i}_{R}+\beta^{i}\right)\right]\\
    X^{i}&=\gamma_{ii}\left\{\left[\alpha\,A^{i}_{L}-B^{i}_{~i,R}\left(-\lambda^{i}_{L}+\beta^{i}\right)\right]-\left[\alpha\,A^{i}_{R}-B^{i}_{~i,L}\left(\lambda^{i}_{R}+\beta^{i}\right)\right]\right\}\\
    X&=\alpha\left(B^{i}_{~i,R}-B^{i}_{~i,L}\right).
\end{align}

\newpage
\bibliographystyle{../apj}
\bibliography{../../References/references.bib}
\end{document}

### 2018-10-12 Documents/Euler/Astronum_2018/manuscript.tex
First full draft of paper

@@
 \begin{document}
-\title{\thornado-hydro: towards discontinuous galerkin methods for supernova hydrodynamics}
+\title{\thornado-hydro: towards discontinuous galerkin methods for supernova hydrodynamics\footnote{This manuscript has been authored by UT-Battelle, LLC under Contract No.
+DE-AC05-00OR22725 with the U.S.
+Department of Energy.
+The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, world-wide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
+The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan(http://energy.gov/downloads/doe-public-access-plan).}}
 
-\author{Eirik Endeve}
-\address{Computational \& Applied Mathematics, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
-\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
+\author{Eirik Endeve$^{1,2,6}$, Jesse Buffaloe$^{2}$, Samuel Dunham$^{3}$, Nick Roberts$^{2}$, Kristopher Andrew$^{4,1}$, Brandon Barker$^{2}$, David Pochik$^{2}$, Juliana Pulsinelli$^{5,7}$ and Anthony Mezzacappa$^{2,6}$}
+\address{$^{1}$Computer Science and Mathematics Division, Oak Ridge National Laboratory, TN 37831}
+\address{$^{2}$Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996}
+\address{$^{3}$Department of Astronomy, Vanderbilt University, TN 37212}
+\address{$^{4}$Department of Physics and Astronomy, University of Kentucky Lexington, KY 40506}
+\address{$^{5}$Department of Astrophysical Sciences, Princeton University, NJ 08544}
+\address{$^{6}$Joint Institute for Computational Sciences, Oak Ridge National Laboratory, TN 37831}
+\address{$^{7}$Physics Division, Oak Ridge National Laboratory, TN 37831}
 \ead{endevee@ornl.gov}
 
-\author{Kristopher Andrew, Brandon Barker, Jesse Buffaloe, Samuel Dunham, David Pochik, Juliana Pulsinelli, Nick Roberts}
-
 \begin{abstract}
-The toolkit for high-order neutrino-radiation hydrodynamics (\thornado) is being developed for simulations of core-collapse supernovae (CCSN) and related problems.  
+The toolkit for high-order neutrino-radiation hydrodynamics (\thornado) is being developed for simulations of core-collapse supernovae (CCSNe) and related problems.  
 Current capabilities in \thornado\ include solvers for the Euler equations --- in non-relativistic and special relativistic limits --- and the two-moment model of neutrino transport.  
@@
 
-\ee{Introduction coming soon.}
+Along with solvers for neutrino transport and gravity, the hydrodynamics solver constitutes a major component of core-collapse supernova (CCSN) simulations.  
+The dynamics of the bounce shock and associated fluid instabilities, which drive turbulent flows and help shape the explosion, must be faithfully captured (see, e.g., \cite{muller_2016}, for a recent review).
+Essentially, the stellar interior is modeled as a perfect fluid (i.e., thermal conduction and viscosity are not explicitly included) using the Euler equations, but extended to accommodate a nuclear equation of state.
+
+The discontinuous Galerkin (DG) method \cite{cockburnShu_2001,hesthavenWarburton_2008} appears as an appealing choice to model fluid flows in CCSNe.  
+DG methods combine elements of spectral and finite volume methods, and achieve high-order accuracy on a compact stencil.  
+Data is only communicated with nearest neighbors, regardless of the formal order of accuracy, which leads to a high computation to communication ratio, and favorable parallel scalability on heterogeneous architectures has been demonstrated \cite{klockner_etal_2009}.
+They can be used in combination with $hp$-adaptivity \cite{remacle_etal_2003}, where, in addition to grid refinement with AMR, the local polynomial degree can be chosen differently, and independently, in different cells.
+DG methods can easily be applied to problems involving curvilinear coordinates, which is beneficial in numerical relativity \cite{teukolsky_2016}.  
+Currently, most hydrodynamics solvers in CCSN codes are based on finite volume methods.  
+Exploring the utility and performance of DG methods to model CCSNe seems like a worthy exercise by itself.
+
+The toolkit for high-order neutrino-radiation hydrodynamics (\thornado) is being developed to simulate neutrino-radiation hydrodynamics in CCSNe and related applications in nuclear astrophysics.  
+The spatial discretization of solvers for hyperbolic partial differential equations in \thornado\ is based on the DG method, while we foresee using a combination of spectral and continuous finite element methods for solving elliptic equations; e.g., for Newtonian gravity or relativistic gravity employing the conformal flatness approximation \cite{wilson_etal_1996}.
+With these approaches, we employ high-order discretization techniques based on a common mathematical framework in all the major model components.  
+In this paper, we provide an initial description and encouraging demonstration of the DG method implemented in \thornado\ to solve the Euler equations.  
+We note that others (e.g., \cite{radiceRezzolla_2011,schaal_etal_2015}) have also investigated the DG method in the context of astrophysical hydrodynamics and reported encouraging results.  
+Whether the high-order approach will improve accuracy and efficiency of CCSN models remains to be demonstrated.
 
@@
 Excellent books and review articles on the DG method are available (see, e.g., \cite{cockburnShu_1998,cockburnShu_2001,hesthavenWarburton_2008,shu_2016} and references therein), and we will not go into too much detail here.
-However, we review some key concepts to introduce notation, and emphasize specific choices in our implementation in \thornado.  
+However, we review some key concepts to introduce notation, and emphasize specific choices for our implementation in \thornado.  
 To this end, we consider a system of conservation laws with sources of the form
@@
   \pd{}{t}\big(\,\sqrt{\gamma}\,\vect{U}\,\big)
-  +\pd{}{i}\Big(\,\sqrt{\gamma}\,\vect{F}^{i}(\vect{U})\,\Big)
+  +\sum_{i=1}^{d}\pd{}{i}\Big(\,\sqrt{\gamma}\,\vect{F}^{i}(\vect{U})\,\Big)
   =\sqrt{\gamma}\,\vect{S}(\vect{U}),
@@
 We use a formulation of the equations sufficiently general to accommodate curvilinear spatial coordinates encoded in the metric $\gamma_{ij}$, giving the squared line element $ds^{2}=\gamma_{ij}dx^{i}dx^{j}$, whose determinant is $\gamma$.
-To solve Eq.~\eqref{eq:extendedEulerCompact}, the computational domain $D$ is divided into a disjoint union $\cT$ of open elements $\bK$, so that $D = \cup_{\bK \in \cT}\bK$.  
+To solve Eq.~\eqref{eq:extendedEulerCompact}, the computational domain $D\subset\mathbb{R}^{d}$ is divided into a disjoint union $\cT$ of open elements $\bK$, so that $D = \cup_{\bK \in \cT}\bK$.  
 We require that each element is a box in the logical coordinates; i.e.,
 \begin{equation}
-  \bK=\{\vect{x} : x^{i} \in K^{i} := (\xL^{i},\xH^{i})\}, 
+  \bK=\{\,\vect{x} : x^{i} \in K^{i} := (\xL^{i},\xH^{i}),\,i=1,\ldots,d\,\}, 
 \end{equation}
@@
 \end{equation}
-We also define as a set $\bx=\{\tilde{\bx}^{i},x^{i}\}$, and $\dx^{i}=\xH^{i}-\xL^{i}$.
+We also define as a set $\bx=\{\tilde{\bx}^{i},x^{i}\}$ and $\dx^{i}=\xH^{i}-\xL^{i}$.
 
 We let the approximation space for the DG method, $\mathbb{V}^{k}$, be constructed from the tensor product of one-dimensional polynomials of maximal degree $k$.  
-(Functions in $\mathbb{V}^{k}$ can be discontinuous across element interfaces.)  
-The semi-discrete DG problem is to find $\vect{U}_{h}\in\mathbb{V}^{k}$ (which approximates $\vect{U}$ in Eq.~\eqref{eq:extendedEulerCompact}) such that for all $v\in\mathbb{V}^{k}$ and all $\bK\in\mathcal{T}$
+Note that functions in $\mathbb{V}^{k}$ can be discontinuous across element interfaces.  
+The semi-discrete DG problem is to find $\vect{U}_{h}\in\mathbb{V}^{k}$, which approximates $\vect{U}$ in Eq.~\eqref{eq:extendedEulerCompact}, such that for all $v\in\mathbb{V}^{k}$ and all $\bK\in\mathcal{T}$
 \begin{align}
@@
 In Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\vect{F}}^{i}(\vect{U}_{h})$ is a numerical flux approximating the flux on the $i$th surface of $\bK$.  
-The numerical flux function $\vect{f}^{i}$ evaluates the numerical flux given values from both sides of an element interface; i.e.,
+The numerical flux function $\vect{f}^{i}$ is evaluated using values from both sides of an element interface; i.e.,
 \begin{equation}
@@
 We provide further details on the DG method to arrive at the equations that are actually evolved in \thornado.  
-We start by introducing some notation, defining the polynomial expansion for $\vect{U}_{h}$, and the quadrature rules used to evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}.  
+We start by introducing some notation, defining the polynomial expansion for $\vect{U}_{h}$ and the quadrature rules used to evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}.  
 Then we provide explicit expressions for each of the terms in Equation~\eqref{eq:semidiscreteDG}.  
@@
   \vect{U}_{h}(x,t)=\sum_{i=1}^{N}\vect{U}_{i}(t)\,\ell_{i}(x),
+  \quad\text{where}\quad
+  \ell_{i}(\eta)=
+  \prod_{\substack{j=1\\j\ne i}}^{N}\f{\eta-\eta_{j}}{\eta_{i}-\eta_{j}}
   \label{eq:conservedNodalExpansion}
 \end{equation}
-where $\ell_{i}(x)$ are Lagrange polynomials
-\begin{equation}
-  \ell_{i}(\eta)=
-  \prod_{\substack{j=1\\j\ne i}}^{N}\f{\eta-\eta_{j}}{\eta_{i}-\eta_{j}},
-\end{equation}
-defined on the reference element $I = \{ \eta : \eta \in (-0.5,0.5) \}$, and constructed to interpolate the node set $S_{N}=\{\eta_{i}\}_{i=1}^{N}\subset I$.  
+are Lagrange polynomials defined on the reference element $I = \{ \eta : \eta \in (-0.5,0.5) \}$, and constructed to interpolate the node set $S_{N}=\{\eta_{i}\}_{i=1}^{N}\subset I$.  
 The spatial coordinate $x$ and the reference coordinate $\eta$ are related by the mapping $x(\eta)=\xL+(0.5+\eta)\,\dx$.  
@@
 The $M$-point Legendre-Gauss quadrature, which we use, integrates polynomials of degree $\le 2M-1$ exactly.  
-Then, if $P(x)$ is such a polynomial, we have
+Then, if $P_{h}(x)$ is such a polynomial, we have
 \begin{equation}
-  \f{1}{\dx}\int_{K}P(x)\,dx=\int_{I}P(\eta)\,d\eta=Q_{N}\big[P\big]\equiv\sum_{q=1}^{M}w_{q}\,P(\eta_{q}).  
+  \f{1}{\dx}\int_{K}P_{h}(x)\,dx=\int_{I}P_{h}(\eta)\,d\eta=Q_{M}\big[P_{h}\big]\equiv\sum_{q=1}^{M}w_{q}\,P_{h}(\eta_{q}).  
 \end{equation}
@@
 for the time derivative term.  
-The integration is approximate since we use the Legendre-Gauss quadrature rule with the nodal points given by the expansion in Eq.~\eqref{eq:conservedNodalExpansion}.  
-Since $\ell_{i}(\eta_{k})=\delta_{ik}$, this leads to a diagonal mass matrix, and simplifies the implementation.  
+For a general metric, the integral in Eq.~\eqref{eq:timeDerivativeTerm} is approximate since we use the Legendre-Gauss quadrature rule with the nodal points given by the expansion in Eq.~\eqref{eq:conservedNodalExpansion}.
+However, since $\ell_{i}(\eta_{k})=\delta_{ik}$, this leads to a diagonal mass matrix, and simplifies the implementation.  
 Similarly, we obtain
@@
 Eq.~\eqref{eq:semidiscreteDiscretized} comprises a system of ordinary differential equations (ODEs), which are integrated in time with an ODE solver.  
-In section~\ref{sec:numerical} we use the optimal third-order strong stability-preserving Runge-Kutta (SSP-RK3) method from \cite{shuOsher_1988}.
+In Section~\ref{sec:numerical} we use the optimal third-order strong stability-preserving Runge-Kutta (SSP-RK3) method from \cite{shuOsher_1988}.
 
@@
 
-We have run this test with $200$ elements to $t=1.8$.  
+We run this test to $t=1.8$ using $200$ elements.  
 In the two upper panels of Figure~\ref{fig:ShuOsher} we plot the density for various values of the troubled-cell indicator threshold $C_{\TCI}$; $0.0$ (full limiting, green), $0.03$ (magenta), $0.3$ (red), and $3.0$ (blue).
-(Larger values of $C_{\TCI}$ imply less limiting.)  
+Larger $C_{\TCI}$ implies less limiting.  
 The results are compared with a reference solution computed with $2048$ elements.  
-With full limiting, the scheme is not able to capture the density variations behind the shock (cf. upper right panel in Figure~\ref{fig:ShuOsher}).  
-When $C_{\TCI}=0.03$, the variations are resolved, but the amplitudes are significantly reduced when compared with the reference solution.  
-With $C_{\TCI}=3.0$, the variations are well resolved, and the amplitudes are comparable to the reference.  
+With full limiting, the scheme is unable to capture the density variations behind the shock (cf. upper right panel in Figure~\ref{fig:ShuOsher}).  
+When $C_{\TCI}=0.03$, the variations are better resolved, but the amplitudes are much reduced relative to the reference solution.  
+With $C_{\TCI}=3.0$, the variations are well resolved and the amplitudes are comparable to the reference.  
 \begin{figure}[h]
@@
 \end{figure}
-In the lower panels of Figure~\ref{fig:ShuOsher} we plot locations in the $xt$-plane where elements have been flagged for limiting by the troubled-cell indicator: $C_{\TCI}=0.03$ (left), $C_{\TCI}=0.3$ (middle), and $C_{\TCI}=3.0$ (right).
-With $C_{\TCI}=0.03$, limiting is triggered in a wide region around the shock and also around the peaks of the three leftmost density variations seen in upper left panel in Figure~\ref{fig:ShuOsher}.
+In the lower panels of Figure~\ref{fig:ShuOsher} we plot locations in the $xt$-plane of elements flagged for limiting by the troubled-cell indicator: $C_{\TCI}=0.03$ (left), $C_{\TCI}=0.3$ (middle), and $C_{\TCI}=3.0$ (right).
+With $C_{\TCI}=0.03$, limiting is triggered in a wide region around the shock and around the peaks of the three leftmost density variations in the upper left panel in Figure~\ref{fig:ShuOsher}.  
 With $C_{\TCI}=3.0$, limiting is only triggered in the shock.
@@
 \subsubsection{Kelvin-Helmholtz (KH) Instability}
-This hydrodynamic instability is of significant astrophysical relevance --- including in the explosion phase of CCSNe.  
-It may occur in the interface separating fluids in relative motion.  
+This hydrodynamic instability is of significant astrophysical relevance --- including in the explosion phase of CCSNe --- and may occur in the interface separating fluids in relative motion.  
 We compute this problem on the unit square $D=[0,1]\times[0,1]$, imposing periodic boundary conditions, and with initial conditions and single-mode perturbation taken from \cite{mcnally_etal_2012}.  
@@
 This test is of immediate relevance to simulation of CCSNe.  
-The initial condition is described in detail in \cite{blondin_etal_2003}, and has been used by many to study the role of the standing accretion shock instability (SASI) on CCSN explosion dynamics.  
+The initial conditions, described in detail in \cite{blondin_etal_2003}, have been used by many to study the standing accretion shock instability (SASI) and CCSN explosion dynamics.  
 We follow closely the description in \cite{blondin_etal_2003} to initialize this test.  
@@
 Below the shock, $r\in[0.2,1]$, the settling solution is obtained by solving Bernoulli's equation.  
-We let matter flow through the inner boundary, and the density and pressure in the boundary elements are set by extrapolating from $D$ assuming $\rho\propto r^{-3}$ and $E\propto r^{-4}$, while the momentum components are held fixed to their initial values.
+Matter flows through the inner boundary, and the density and pressure in boundary elements are set by extrapolating from $D$ assuming $\rho\propto r^{-3}$ and $E\propto r^{-4}$, while the momentum components are held fixed to their initial values.
 
@@
 In the upper right panel we show elements flagged for limiting in the $rt$-plane.
-In the bottom panel we show results from a perturbed model, where we plot the relative deviation of the pressure below the shock from; cf.
+In the bottom panel we show results from a perturbed model, where we plot the relative deviation of the pressure below the shock; cf.
 Eq.~\eqref{eq:pressureDeviation}.}
 \end{figure}
+
 We use $256$ elements and run the tests until $t=100$ ($>5$ dynamical times \cite{blondin_etal_2003}).  
@@
 In the upper right panel we show elements flagged for limiting in the $rt$-plane (we set $C_{\TCI}=0.03$ in this run), which illustrates how limiting is confined to the shock.  
-In the second test we placed a shell ahead of the shock with thickness $0.2$ and density three times higher than the ambient density to induce a strong radial perturbation (similar to \cite{blondin_etal_2003}; see their Figure~4).
-The initial condition we use should be stable against radial perturbations.  
+In the second test we placed a shell with thickness $0.2$ and density three times higher than the ambient density ahead of the shock to induce a strong radial perturbation (similar to \cite{blondin_etal_2003}; see their Figure~4).
+The initial condition is stable against radial perturbations.  
 In the lower panel in Figure~\ref{fig:SAS} we plot the pressure deviation below the shock, defined as
@@
 \end{equation}
-and $p_{0}$ and $r_{0}$ are the pressure and radius closest to the inner boundary.  
-As the shell falls through the shock, the perturbation leads to an interesting pattern of waves propagating inside the shocked cavity and oscillations of the shock position, which eventually die out.
-The configuration eventually settles down to something close to the initial condition.  
-However, in the final state, the position of the shock is slightly larger than that of the initial state.
+and $p_{0}$ and $r_{0}$ are the pressure and radius at the inner boundary.  
+As the shell falls through the shock, the strong perturbation results in an interesting pattern of waves propagating inside the shocked cavity, and oscillations of the shock position.  
+The configuration eventually settles down to a configuration that is close to the initial condition (although the position of the shock is slightly larger than that of the initial state.)
 
@@
 This test is also of immediate relevance to CCSN simulations.  
-In \cite{yahilLattimer_1982,yahil_1983}, self-similar solutions to the gravitational collapse problem where constructed for $6/5\le\Gamma<4/3$, which smoothly connect an homologously collapsing subsonic inner core (velocity proportional to radius) to a supersonically collapsing outer core in near free-fall ($u\propto r^{-1/2}$).
+In \cite{yahilLattimer_1982,yahil_1983}, self-similar solutions to the gravitational collapse problem where constructed for $6/5\le\Gamma<4/3$.   
+The solutions smoothly connect an homologously collapsing subsonic inner core (velocity proportional to radius) to a supersonically collapsing outer core in near free-fall ($u\propto r^{-1/2}$).  
 \begin{figure}[h]
@@
 \begin{equation}
-  X = \kappa^{-1/2} G^{(\Gamma-1)/2} r (-t)^{\Gamma-2},
+  X = \kappa^{-1/2} \, G^{(\Gamma-1)/2} \, r \, (-t)^{\Gamma-2},
 \end{equation}
 where the origin of time is the moment of infinite central density.  
-Then all the hydrodynamic variables can be expressed as a function of $X$, and the time-dependent Euler equations can be recast as a system of ODEs (see \cite{yahil_1983} for details).  
+All the hydrodynamic variables can be expressed as a function of $X$, and the time-dependent Euler equations can be recast as a system of ODEs (see \cite{yahil_1983} for details).  
 To construct a reference to compare with our numerical results we have solved the ODEs given in \cite{yahil_1983} to obtain these self-similar solutions.
 
-Here we show results for a model with $\Gamma=1.3$.  
+We show results for a model with $\Gamma=1.3$.  
 We use spherical polar coordinates, and let $D=[0,1\times10^{5}]$~km, which is covered with $256$ elements.  
+The Newtonian gravitational potential is obtained by solving Poisson's equation using a third-order accurate continuous finite element method (e.g., \cite{brennerScott_2008}).  
 We use a geometric grid to resolve the mass distribution as the star collapses and the central density increases from about $10^{9}$~g~cm$^{-3}$ to about $10^{14}$~g~cm$^{-3}$.  
@@
 Results comparing the mass density and velocity of Yahil's reference solution to the solution obtained with \thornado\ using $C_{\TCI}=0.03$ are plotted in Figure~\ref{fig:YahilLattimer}.  
-The agreement is good throughout collapse.
+The agreement of the mass density and velocity profiles is good throughout collapse.
 
@@
 \end{equation*}
-In both problems, the computational domain is $D=[0,1]$, and the discontinuity is initially located at $x^{1}=0.5$, and the solutions are integrated to $t=0.4$.  
+In both problems, the computational domain is $D=[0,1]$, the discontinuity is initially located at $x^{1}=0.5$, and the solutions are integrated to $t=0.4$.  
 Results are plotted in Figure~\ref{fig:RelativisticHydro}.
@@
 The main features of the exact solution are captured quite well with the DG method implemented in \thornado.  
-For Riemann problem~1, there we observe some oscillations in the density between the leftmost shock and the contact discontinuity located near $x^{1}=0.6$.  
+For Riemann problem~1, we observe some oscillations in the density between the leftmost shock and the contact discontinuity located near $x^{1}=0.6$.  
 For Riemann problem~2, the maximum density in the thin density shell between the shock and the contact discontinuity is significantly lower for the numerical solution than the exact solution.  
-This is due to a combination of spatial resolution and the action of the slope limiter.  
+This is due to a combination of limited spatial resolution and the action of the slope limiter.  
 We used $C_{\TCI}=0.03$ in both tests in this section.  
@@
 
-\ee{Summary and Outlook coming soon.}
-
-We have presented some implementation details and preliminary results of solvers for the Euler equations of gas dynamics in the toolkit for high-order neutrino-radiation hydrodynamics (\thornado).
+We have presented preliminary algorithm details and numerical results for solvers of the non-relativistic and special relativistic Euler equations of gas dynamics as implemented in the toolkit for high-order neutrino-radiation hydrodynamics (\thornado).
+The spatial discretization is based on the DG method and the ODEs resulting from this discretization are integrated in time using SSP-RK methods.  
+We employ a spectral-type nodal collocation DG approximation based on Legendre-Gauss points for interpolation and numerical quadrature evaluation \cite{bassi_etal_2013}.  
+This choice simplifies expressions for the semi-discretized equations, especially when applied to problems involving curvilinear coordinates encoded in a metric (e.g., in numerical relativity).  
+Results from a suite of tests in one and two spatial dimensions --- including problems with strong shocks --- demonstrate reliable performance of the implementation.  
+Two tests in spherical symmetry (standing accretion shock \cite{blondin_etal_2003} and Yahil-Lattimer collapse \cite{yahilLattimer_1982,yahil_1983}) demonstrate the DG method's ability to handle conditions relevant to simulations of CCSN.
+We will present a more in-depth analysis of the performance of \thornado\ on these (and related) problems in a future study.
 
 The performance of the DG algorithm is sensitive to limiting of the polynomial representation.  
+The combination of a TVD-type limiter (e.g., \cite{cockburnShu_1998}) and the troubled-cell indicator of \cite{fuShu_2017} seems to give satisfactory results for a range of problems.  
+However, in our experience, the optimal value for the indicator threshold $C_{\TCI}$ seems to vary with the specific problem, and further investigation is needed to determine if there exists an optimal value suitable for CCSN simulations.
+Along these lines of investigation, it would also be interesting to explore and compare the use of the {\it a posteriori} subcell limiting approach in \cite{dumbser_etal_2014,fambri_etal_2018} with our current approach.
 
-The algorithms in \thornado\ are implemented in Fortran and intended for evolution within logically Cartesian grids.
-
-Ongoing and future work includes, extension to nuclear equation of state, general relativity within the conformal flatness approximation, porting to hardware accelerators (e.g., GPUs), and deployment within an adaptive mesh refinement framework such as AMREx.
+Ongoing and planned near-future work within \thornado\ include coupling to solvers for two-moment neutrino transport, extensions to accommodate nuclear equations of state, general relativity within the conformal flatness approximation, and deployment within an adaptive mesh refinement framework.
 We hope to report on progress in these directions in the near future.
 
+\ack E.~E. and A.~M. acknowledge support from the NSF Gravitational Physics Program (NSF-GP 1505933 and 1806692).
+
 \section*{References}
-\begin{thebibliography}{24}
+\begin{thebibliography}{34}
   \bibitem{bassi_etal_2013} Bassi, F., Franchina, N. Ghidoni, A., \& Rebay, S. 2013, {\it Int. J. Numer. Meth. Fluids}, {\bf 71}, 1322
   \bibitem{blondin_etal_2003} Blondin, J.M., Mezzacappa, A., \& DeMarino, C. 2003, {\it ApJ}, {\bf 584}, 980
+  \bibitem{brennerScott_2008} Brenner, S.C. \& Scott, L.R. 2008, {\it The Mathematical Theory of Finite Element Methods}, Springer
   \bibitem{cockburnShu_1998} Cockburn, B. \& Shu, C.-W. 1998, {\it JCP}, {\bf 141}, 199
   \bibitem{cockburnShu_2001} Cockburn, B. \& Shu, C.-W. 2001, {\it Journal of Scientific Computing}, {\bf 16}, 173
+  \bibitem{dumbser_etal_2014} Dumbser, M., Zanotti, O., Loub{\`e}re, R., \& Diot, S. 2014, {\it JCP}, {\bf 278}, 47
+  \bibitem{fambri_etal_2018} Fambri, F., Dumbser, M., K{\"o}ppel, S., Rezzolla, L., \& Zanotti, O. 2018, {\it MNRAS}, {\bf 477}, 4543
   \bibitem{fuShu_2017} Fu, G. \& Shu, C.-W. 2017, {\it JCP}, {\bf 347}, 305
-  \bibitem{harten_etal_1983} Harten, A., Lax, P.D., \& Van Leer, B. 1983, {\it SIAM Review}, {\bf 25}, 35
+  \bibitem{harten_etal_1983} Harten, A., Lax, P.D., \& Van Leer, B. 1983, {\it SIAM~Review}, {\bf 25}, 35
   \bibitem{hesthavenWarburton_2008} Hesthaven, J.S. \& Warburton T. 2008, {\it Nodal discontinuous Galerkin methods: Algorithms, analysis and applications}, Springer
+  \bibitem{klockner_etal_2009} Kl{\"o}ckner, A. Warburton, T., Bridge, J. \& Hesthaven, J.S. 2009, {\it JCP}, {\bf 228}, 7863
   \bibitem{landauLifshitz_1979} Landau, L.D. \& Lifshitz, E.M. 1979, {\it Fluid Mechanics}, Pergamon
@@
   \bibitem{mignoneBodo_2005} Mignone, A. \& Bodo, G. 2005, {\it MNRAS}, {\bf 364}, 126
+  \bibitem{muller_2016} M{\"u}ller, B. 2016, {\it PASA}, {\bf 33}, 1
   \bibitem{qin_etal_2016} Qin, T., Shu, C.-W., \& Yang, Y. 2016, {\it JCP}, {\bf 315}, 323
+  \bibitem{radiceRezzolla_2011} Radice, D. \& Rezzolla, L. 2011, {\it Phys. Rev. D}, {\bf 84}, 024010
+  \bibitem{remacle_etal_2003} Remacle, J.-F., Flaherty, J.E., \& Shephard, M.S. 2003, {\it SIAM~Review}, {\bf 45}, 53
+  \bibitem{schaal_etal_2015} Schaal, K., Bauer, A., Chandrashekar, P. R{\"u}diger, P., Klingenberg, C., \& Springel, V. 2015, {\it MNRAS}, {\bf 453}, 4278
   \bibitem{sedov_1959} Sedov, L.I. 1959, {\it Similarity and Dimensional Methods in Mechanics}, Academic Press
@@
   \bibitem{sod_1978} Sod, G.A. 1978, {\it JCP}, {\bf 27}, 1
+  \bibitem{teukolsky_2016} Teukolsky, S.A. 2016, {\it JCP}, {\bf 312}, 333
   \bibitem{toro_etal_1994} Toro, E.F., Spruce, M., \& Speares W. 1994, {\it Shock Waves}, {\bf 4}, 25
   \bibitem{toro_1999} Toro, E.F. 1999, NUMERICA: A Library of Source Codes for Teaching, Research and Applications
+  \bibitem{wilson_etal_1996} Wilson, J.R., Mathews, G.J., \& Marronetti, P. 1996, {\it Phys. Rev. D}, {\bf 54}, 1317
   \bibitem{wuTang_2015} Wu, K. \& Tang, H. 2015, {\it JCP}, {\bf 298}, 539
@@
 
-\clearpage
-
-\section{Introduction}
-These guidelines show how to prepare articles for publication in \jpcs\ using \LaTeX\ so they can be published quickly and accurately.
-Articles will be refereed by the \corg s but the accepted PDF will be published with no editing, proofreading or changes to layout.
-It is, therefore, the author's responsibility to ensure that the content and layout are correct.
-This document has been prepared using \cls\ so serves as a sample document.
-The class file and accompanying documentation are available from \verb"http://jpcs.iop.org".
-
-\section{Preparing your paper}
-\verb"jpconf" requires \LaTeXe\ and  can be used with other package files such
-as those loading the AMS extension fonts 
-\verb"msam" and \verb"msbm" (these fonts provide the 
-blackboard bold alphabet and various extra maths symbols as well as 
-symbols useful in figure captions); an extra style file \verb"iopams.sty" is 
-provided to load these packages and provide extra definitions for bold Greek letters. 
-\subsection{Headers, footers and page numbers}
-Authors should {\it not} add headers, footers or page numbers to the pages of their article---they will
-be added by \iopp\ as part of the production process.
-
-\subsection{{\cls\ }package options}
-The \cls\ class file has two options `a4paper' and `letterpaper':
-\begin{verbatim}
-\documentclass[a4paper]{jpconf}
-\end{verbatim}
-
-or \begin{verbatim}
-\documentclass[letterpaper]{jpconf}
-\end{verbatim}
-
-\begin{center}
-\begin{table}[h]
-\caption{\label{opt}\cls\ class file options.}
-%\footnotesize\rm
-\centering
-\begin{tabular}{@{}*{7}{l}}
-\br
-Option&Description\\
-\mr
-\verb"a4paper"&Set the paper size and margins for A4 paper.\\
-\verb"letterpaper"&Set the paper size and margins for US letter paper.\\
-\br
-\end{tabular}
-\end{table}
-\end{center}
-
-The default paper size is A4 (i.e., the default option is {\tt a4paper}) but this can be changed to Letter by 
-using \verb"\documentclass[letterpaper]{jpconf}". It is essential that you do not put macros into the text which alter the page dimensions.
-
-\section{The title, authors, addresses and abstract} 
-The code for setting the title page information is slightly different from
-the normal default in \LaTeX\ but please follow these instructions as carefully as possible so all articles within a conference have the same style to the title page. 
-The title is set in bold unjustified type using the command
-\verb"\title{#1}", where \verb"#1" is the title of the article. The
-first letter of the title should be capitalized with the rest in lower case. 
-The next information required is the list of all authors' names followed by 
-the affiliations. For the authors' names type \verb"\author{#1}", 
-where \verb"#1" is the 
-list of all authors' names. The style for the names is initials then
-surname, with a comma after all but the last 
-two names, which are separated by `and'. Initials should {\it not} have 
-full stops. First names may be used if desired. The command \verb"\maketitle" is not
-required.
-
-The addresses of the authors' affiliations follow the list of authors. 
-Each address should be set by using
-\verb"\address{#1}" with the address as the single parameter in braces. 
-If there is more 
-than one address then a superscripted number, followed by a space, should come at the start of
-each address. In this case each author should also have a superscripted number or numbers following their name to indicate which address is the appropriate one for them.
-
-Please also provide e-mail addresses for any or all of the authors using an \verb"\ead{#1}" command after the last address.
-\verb"\ead{#1}" provides the text Email: so \verb"#1" is just the e-mail address or a list of emails.
-
-The abstract follows the addresses and
-should give readers concise information about the content 
-of the article and should not normally exceed 200 
-words. {\bf All articles must include an abstract}. To indicate the start 
-of the abstract type \verb"\begin{abstract}" followed by the text of the 
-abstract.  The abstract should normally be restricted 
-to a single paragraph and is terminated by the command
-\verb"\end{abstract}"
-
-\subsection{Sample coding for the start of an article}
-\label{startsample}
-The code for the start of a title page of a typical paper might read:
-\begin{verbatim}
-\title{The anomalous magnetic moment of the 
-neutrino and its relation to the solar neutrino problem}
-
-\author{P J Smith$^1$, T M Collins$^2$, 
-R J Jones$^{3,}$\footnote[4]{Present address:
-Department of Physics, University of Bristol, Tyndalls Park Road, 
-Bristol BS8 1TS, UK.} and Janet Williams$^3$}
-
-\address{$^1$ Mathematics Faculty, Open University, 
-Milton Keynes MK7~6AA, UK}
-\address{$^2$ Department of Mathematics, 
-Imperial College, Prince Consort Road, London SW7~2BZ, UK}
-\address{$^3$ Department of Computer Science, 
-University College London, Gower Street, London WC1E~6BT, UK}
-
-\ead{williams@ucl.ac.uk}
-
-\begin{abstract}
-The abstract appears here.
-\end{abstract}
-\end{verbatim}
-
-\section{The text}
-The text of the article should should be produced using standard \LaTeX\ formatting.
-Articles may be divided into sections and subsections, but the length limit provided by the \corg\ should be adhered to.
-
-\subsection{Acknowledgments}
-Authors wishing to acknowledge assistance or encouragement from 
-colleagues, special work by technical staff or financial support from 
-organizations should do so in an unnumbered Acknowledgments section 
-immediately following the last numbered section of the paper. The 
-command \verb"\ack" sets the acknowledgments heading as an unnumbered
-section.
-
-\subsection{Appendices}
-Technical detail that it is necessary to include, but that interrupts 
-the flow of the article, may be consigned to an appendix. 
-Any appendices should be included at the end of the main text of the paper, after the acknowledgments section (if any) but before the reference list.
-If there are two or more appendices they will be called Appendix A, Appendix B, etc. 
-Numbered equations will be in the form (A.1), (A.2), etc,
-figures will appear as figure A1, figure B1, etc and tables as table A1,
-table B1, etc.
-
-The command \verb"\appendix" is used to signify the start of the
-appendixes. Thereafter \verb"\section", \verb"\subsection", etc, will 
-give headings appropriate for an appendix. To obtain a simple heading of 
-`Appendix' use the code \verb"\section*{Appendix}". If it contains
-numbered equations, figures or tables the command \verb"\appendix" should
-precede it and \verb"\setcounter{section}{1}" must follow it.
-
-\section{References}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the online version of \jpcs\ references will be linked to their original source or to the article within a secondary service such as INSPEC or ChemPort wherever possible.
-To facilitate this linking extra care should be taken when preparing reference lists.
-
-Two different styles of referencing are in common use: the Harvard alphabetical system and the Vancouver numerical system.
-For \jpcs, the Vancouver numerical system is preferred but authors should use the Harvard alphabetical system if they wish to do so.
-In the numerical system references are numbered sequentially throughout the text within square brackets, like this [2], and one number can be used to designate several references.
-
-\subsection{Using \BibTeX}
-We highly recommend the {\ttfamily\textbf\selectfont iopart-num} \BibTeX\ package by Mark~A~Caprio \cite{iopartnum}, which is included with this documentation.
-
-\subsection{Reference lists}
-A complete reference should provide the reader with enough information to locate the article concerned, whether published in print or electronic form, and should, depending on the type of reference, consist of:
-
-\begin{itemize}
-\item name(s) and initials;
-\item date published;
-\item title of journal, book or other publication; 
-\item titles of journal articles may also be included (optional);
-\item volume number;
-\item editors, if any;
-\item town of publication and publisher in parentheses for {\it books};
-\item the page numbers.
-\end{itemize}
-
-Up to ten authors may be given in a particular reference; where 
-there are more than ten only the first should be given followed by 
-`{\it et al}'. If an author is unsure of a particular journal's abbreviated title it is best to leave the title in 
-full. The terms {\it loc.\ cit.\ }and {\it ibid.\ }should not be used. 
-Unpublished conferences and reports should generally not be included 
-in the reference list and articles in the course of publication should 
-be entered only if the journal of publication is known. 
-A thesis submitted for a higher degree may be included 
-in the reference list if it has not been superseded by a published 
-paper and is available through a library; sufficient information 
-should be given for it to be traced readily.
-
-\subsection{Formatting reference lists}
-Numeric reference lists should contain the references within an unnumbered section (such as \verb"\section*{References}"). The 
-reference list itself is started by the code 
-\verb"\begin{thebibliography}{<num>}", where \verb"<num>" is the largest
-number in the reference list and is completed by
-\verb"\end{thebibliography}". 
-Each reference starts with \verb"\bibitem{<label>}", where `label' is the label used for cross-referencing.
-Each \verb"\bibitem" should only contain a reference to a single article (or a single article and a preprint reference to the same article).
-When one number actually covers a group of two or more references to different articles, \verb"\nonum"
-should replace \verb"\bibitem{<label>}" at
-the start of each reference in the group after the first.
-
-For an alphabetic reference list use \verb"\begin{thereferences}" ... \verb"\end{thereferences}" instead of the
-`thebibliography' environment and each reference can be start with just \verb"\item" instead of \verb"\bibitem{label}"
-as cross referencing is less useful for alphabetic references.
-
-\subsection {References to printed journal articles}
-A normal reference to a journal article contains three changes of font (see table \ref{jfonts}) and is constructed as follows:
-
-\begin{itemize}
-\item the authors should be in the form surname (with only the first letter capitalized) followed by the initials with no periods after the initials.
-Authors should be separated by a comma except for the last two which should be separated by `and' with no comma preceding it;
-\item the article title (if given) should be in lower case letters, except for an initial capital, and should follow the date;
-\item the journal title is in italic and is abbreviated.
-If a journal has several parts denoted by different letters the part letter should be inserted after the journal in Roman type, e.g.
-{\it Phys.
-Rev.} A;
-\item the volume number should be in bold type;
-\item both the initial and final page numbers should be given where possible.
-The final page number should be in the shortest possible form and separated from the initial page number by an en rule `-- ', e.g.
-1203--14, i.e.
-the numbers `12' are not repeated.
-\end{itemize}
-
-A typical (numerical) reference list might begin
-
-\medskip
-\begin{thebibliography}{9}
-\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
-\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
-{\it J. Appl. Phys}. {\bf 87} 965 
-\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
-and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
-\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
-{\it Electron. Lett.} {\bf 32} 1105 
-\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
-{\it J. Appl. Phys.} {\bf 83} 826 
-\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
-\end{thebibliography}
-\smallskip
-
-\noindent which would be obtained by typing
-
-\begin{verbatim}
-\begin{\thebibliography}{9}
-\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
-\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
-{\it J. Appl. Phys}. {\bf 87} 965 
-\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
-and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
-\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
-{\it Electron. Lett.} {\bf 32} 1105 
-\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
-{\it J. Appl. Phys.} {\bf 83} 826 
-\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
-\end{\thebibliography}
-\end{verbatim}
-
-\begin{center}
-\begin{table}[h]
-\centering
-\caption{\label{jfonts}Font styles for a reference to a journal article.} 
-\begin{tabular}{@{}l*{15}{l}}
-\br
-Element&Style\\
-\mr
-Authors&Roman type\\
-Date&Roman type\\
-Article title (optional)&Roman type\\
-Journal title&Italic type\\
-Volume number&Bold type\\
-Page numbers&Roman type\\
-\br
-\end{tabular}
-\end{table}
-\end{center}
-
-\subsection{References to \jpcs\ articles}
-Each conference proceeding published in \jpcs\ will be a separate {\it volume}; 
-references should follow the style for conventional printed journals. For example:\vspace{6pt}
-\numrefs{1}
-\item Douglas G 2004 \textit{J. Phys.: Conf. Series} \textbf{1} 23--36
-\endnumrefs
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{References to preprints}
-For preprints there are two distinct cases:
-\renewcommand{\theenumi}{\arabic{enumi}}
-\begin{enumerate}
-\item Where the article has been published in a journal and the preprint is supplementary reference information. In this case it should be presented as:
-\medskip
-\numrefs{1}
-\item Kunze K 2003 T-duality and Penrose limits of spatially homogeneous and inhomogeneous cosmologies {\it Phys. Rev.} D {\bf 68} 063517 ({\it Preprint} gr-qc/0303038)
-\endnumrefs
-\item Where the only reference available is the preprint. In this case it should be presented as
-\medskip
-\numrefs{1}
-\item Milson R, Coley A, Pravda V and Pravdova A 2004 Alignment and algebraically special tensors {\it Preprint} gr-qc/0401010
-\endnumrefs
-\end{enumerate}
-
-\subsection{References to electronic-only journals}
-In general article numbers are given, and no page ranges, as most electronic-only journals start each article on page 1.
-
-\begin{itemize} 
-\item For {\it New Journal of Physics} (article number may have from one to three digits)
-\numrefs{1}
-\item Fischer R 2004 Bayesian group analysis of plasma-enhanced chemical vapour deposition data {\it New. J. Phys.} {\bf 6} 25 
-\endnumrefs
-\item For SISSA journals the volume is divided into monthly issues and these form part of the article number
-
-\numrefs{2}
-\item Horowitz G T and Maldacena J 2004 The black hole final state {\it J. High Energy Phys.}  	JHEP02(2004)008
-\item Bentivegna E, Bonanno A and Reuter M 2004 Confronting the IR fixed point cosmology 	with 	high-redshift observations {\it J. Cosmol. Astropart. Phys.} JCAP01(2004)001  
-\endnumrefs
-\end{itemize}
-
-\subsection{References to books, conference proceedings and reports}
-References to books, proceedings and reports are similar to journal references, but have 
-only two changes of font (see table~\ref{book}).
-
-\begin{table}
-\centering
-\caption{\label{book}Font styles for references to books, conference proceedings and reports.}
-\begin{tabular}{@{}l*{15}{l}}
-\br
-Element&Style\\
-\mr
-Authors&Roman type\\
-Date&Roman type\\
-Book title (optional)&Italic type\\
-Editors&Roman type\\
-Place (city, town etc) of publication&Roman type\\
-Publisher&Roman type\\
-Volume&Roman type\\
-Page numbers&Roman type\\
-\br
-\end{tabular}
-\end{table}
-
-Points to note are:
-\medskip
-\begin{itemize}
-\item Book titles are in italic and should be spelt out in full with initial capital letters for all except minor words.
-Words such as Proceedings, Symposium, International, Conference, Second, etc should be abbreviated to {\it Proc.}, {\it Symp.}, {\it Int.}, {\it Conf.}, {\it 2nd}, respectively, but the rest of the title should be given in full, followed by the date of the conference and the town or city where the conference was held.
-For Laboratory Reports the Laboratory should be spelt out wherever possible, e.g.
-{\it Argonne National Laboratory Report}.
-\item The volume number, for example vol 2, should be followed by the editors, if any, in a form such as `ed A J Smith and P R Jones'.
-Use {\it et al} if there are more than two editors.
-Next comes the town of publication and publisher, within brackets and separated by a colon, and finally the page numbers preceded by p if only one number is given or pp if both the initial and final numbers are given.
-\end{itemize}
-
-Examples taken from published papers:
-\medskip
-
-\numrefs{99}
-\item Kurata M 1982 {\it Numerical Analysis for Semiconductor Devices} (Lexington, MA: Heath)
-\item Selberherr S 1984 {\it Analysis and Simulation of Semiconductor Devices} (Berlin: Springer)
-\item Sze S M 1969 {\it Physics of Semiconductor Devices} (New York: Wiley-Interscience)
-\item Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} (Moscow: Moscow State University Press) p 103
-\item Caplar R and Kulisic P 1973 {\it Proc. Int. Conf. on Nuclear Physics (Munich)} vol 1 (Amsterdam: 	North-Holland/American Elsevier) p 517
-\item Cheng G X 2001 {\it Raman and Brillouin Scattering-Principles and Applications} (Beijing: Scientific) 
-\item Szytula A and Leciejewicz J 1989 {\it Handbook on the Physics and Chemistry of Rare Earths} vol 12, ed K A Gschneidner Jr and L Erwin (Amsterdam: Elsevier) p 133
-\item Kuhn T 1998 {\it Density matrix theory of coherent ultrafast dynamics Theory of Transport Properties of Semiconductor Nanostructures} (Electronic Materials vol 4) ed E Sch\"oll (London: Chapman and Hall) chapter 6 pp 173--214
-\endnumrefs
-
-\section{Tables and table captions}
-Tables should be numbered serially and referred to in the text 
-by number (table 1, etc, {\bf rather than} tab.
-1).
-Each table should be a float and be positioned within the text at the most convenient place near to where it is first mentioned in the text.
-It should have an
-explanatory caption which should be as concise as possible.
-
-\subsection{The basic table format}
-The standard form for a table is:
-\begin{verbatim}
-\begin{table}
-\caption{\label{label}Table caption.}
-\begin{center}
-\begin{tabular}{llll}
-\br
-Head 1&Head 2&Head 3&Head 4\\
-\mr
-1.1&1.2&1.3&1.4\\
-2.1&2.2&2.3&2.4\\
-\br
-\end{tabular}
-\end{center}
-\end{table}
-\end{verbatim}
-
-The above code produces table~\ref{ex}.
-
-\begin{table}[h]
-\caption{\label{ex}Table caption.}
-\begin{center}
-\begin{tabular}{llll}
-\br
-Head 1&Head 2&Head 3&Head 4\\
-\mr
-1.1&1.2&1.3&1.4\\
-2.1&2.2&2.3&2.4\\
-\br
-\end{tabular}
-\end{center}
-\end{table}
-
-Points to note are:
-\medskip
-\begin{enumerate}
-\item The caption comes before the table.
-\item The normal style is for tables to be centred in the same way as
-equations. This is accomplished
-by using \verb"\begin{center}" \dots\ \verb"\end{center}".
-
-\item The default alignment of columns should be aligned left.
-
-\item Tables should have only horizontal rules and no vertical ones. The rules at
-the top and bottom are thicker than internal rules and are set with
-\verb"\br" (bold rule). 
-The rule separating the headings from the entries is set with
-\verb"\mr" (medium rule). These commands do not need a following double backslash.
-
-\item Numbers in columns should be aligned as appropriate, usually on the decimal point;
-to help do this a control sequence \verb"\lineup" has been defined 
-which sets \verb"\0" equal to a space the size of a digit, \verb"\m"
-to be a space the width of a minus sign, and \verb"\-" to be a left
-overlapping minus sign. \verb"\-" is for use in text mode while the other
-two commands may be used in maths or text.
-(\verb"\lineup" should only be used within a table
-environment after the caption so that \verb"\-" has its normal meaning
-elsewhere.) See table~\ref{tabone} for an example of a table where
-\verb"\lineup" has been used.
-\end{enumerate}
-
-\begin{table}[h]
-\caption{\label{tabone}A simple example produced using the standard table commands 
-and $\backslash${\tt lineup} to assist in aligning columns on the 
-decimal point. The width of the 
-table and rules is set automatically by the 
-preamble.}
-
-\begin{center}
-\lineup
-\begin{tabular}{*{7}{l}}
-\br                              
-$\0\0A$&$B$&$C$&\m$D$&\m$E$&$F$&$\0G$\cr 
-\mr
-\0\023.5&60  &0.53&$-20.2$&$-0.22$ &\01.7&\014.5\cr
-\0\039.7&\-60&0.74&$-51.9$&$-0.208$&47.2 &146\cr 
-\0123.7 &\00 &0.75&$-57.2$&\m---   &---  &---\cr 
-3241.56 &60  &0.60&$-48.1$&$-0.29$ &41   &\015\cr 
-\br
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Figures and figure captions}
-Figures must be included in the source code of an article at the appropriate place in the text not grouped together at the end.
-
-Each figure should have a brief caption describing it and, if 
-necessary, interpreting the various lines and symbols on the figure. 
-As much lettering as possible should be removed from the figure itself and 
-included in the caption. If a figure has parts, these should be 
-labelled ($a$), ($b$), ($c$), etc. 
-\Tref{blobs} gives the definitions for describing symbols and lines often
-used within figure captions (more symbols are available
-when using the optional packages loading the AMS extension fonts).
-
-\begin{table}[h]
-\caption{\label{blobs}Control sequences to describe lines and symbols in figure 
-captions.}
-\begin{center}
-\begin{tabular}{lllll}
-\br
-Control sequence&Output&&Control sequence&Output\\
-\mr
-\verb"\dotted"&\dotted        &&\verb"\opencircle"&\opencircle\\
-\verb"\dashed"&\dashed        &&\verb"\opentriangle"&\opentriangle\\
-\verb"\broken"&\broken&&\verb"\opentriangledown"&\opentriangledown\\
-\verb"\longbroken"&\longbroken&&\verb"\fullsquare"&\fullsquare\\
-\verb"\chain"&\chain          &&\verb"\opensquare"&\opensquare\\
-\verb"\dashddot"&\dashddot    &&\verb"\fullcircle"&\fullcircle\\
-\verb"\full"&\full            &&\verb"\opendiamond"&\opendiamond\\
-\br
-\end{tabular}
-\end{center}
-\end{table}
-
-Authors should try and use the space allocated to them as economically as possible.
-At times it may be convenient to put two figures side by side or the caption at the side of a figure.
-To put figures side by side, within a figure environment, put each figure and its caption into a minipage with an appropriate width (e.g.
-3in or 18pc if the figures are of equal size) and then separate the figures slightly by adding some horizontal space between the two minipages (e.g.
-\verb"\hspace{.2in}" or \verb"\hspace{1.5pc}".
-To get the caption at the side of the figure add the small horizontal space after the \verb"\includegraphics" command and then put the \verb"\caption" within a minipage of the appropriate width aligned bottom, i.e.
-\verb"\begin{minipage}[b]{3in}" etc (see code in this file used to generate figures 1--3).
-
-Note that it may be necessary to adjust the size of the figures (using optional arguments to \verb"\includegraphics", for instance \verb"[width=3in]") to get you article to fit within your page allowance or to obtain good page breaks.
-
-\begin{figure}[h]
-\begin{minipage}{14pc}
-\includegraphics[width=14pc]{name.eps}
-\caption{\label{label}Figure caption for first of two sided figures.}
-\end{minipage}\hspace{2pc}%
-\begin{minipage}{14pc}
-\includegraphics[width=14pc]{name.eps}
-\caption{\label{label}Figure caption for second of two sided figures.}
-\end{minipage} 
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=14pc]{name.eps}\hspace{2pc}%
-\begin{minipage}[b]{14pc}\caption{\label{label}Figure caption for a narrow figure where the caption is put at the side of the figure.}
-\end{minipage}
-\end{figure}
-
-Using the graphicx package figures can be included using code such as:
-\begin{verbatim}
-\begin{figure}
-\begin{center}
-\includegraphics{file.eps}
-\end{center}
-\caption{\label{label}Figure caption}
-\end{figure}
-\end{verbatim}
-
-\section*{References}
-\begin{thebibliography}{9}
-\bibitem{iopartnum} IOP Publishing is to grateful Mark A Caprio, Center for Theoretical Physics, Yale University, for permission to include the {\tt iopart-num} \BibTeX package (version 2.0, December 21, 2006) with  this documentation.
-Updates and new releases of {\tt iopart-num} can be found on \verb"www.ctan.org" (CTAN).
-\end{thebibliography}
-
 \end{document}

### 2018-10-16 Documents/Euler/Astronum_2018/ms_endeve.tex
Edits due to comments for Sam.  Also edited the reference list

--- 2018-10-12 Documents/Euler/Astronum_2018/manuscript.tex
@@
 The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, world-wide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
-The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan(http://energy.gov/downloads/doe-public-access-plan).}}
+The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
 
-\author{Eirik Endeve$^{1,2,6}$, Jesse Buffaloe$^{2}$, Samuel Dunham$^{3}$, Nick Roberts$^{2}$, Kristopher Andrew$^{4,1}$, Brandon Barker$^{2}$, David Pochik$^{2}$, Juliana Pulsinelli$^{5,7}$ and Anthony Mezzacappa$^{2,6}$}
+\author{Eirik Endeve$^{1,2,6}$, Jesse Buffaloe$^{2}$, Samuel J Dunham$^{3}$, \\ Nick Roberts$^{2}$, Kristopher Andrew$^{4,1}$, Brandon Barker$^{2}$, \\ David Pochik$^{2}$, Juliana Pulsinelli$^{5,7}$ and Anthony Mezzacappa$^{2,6}$}
 \address{$^{1}$Computer Science and Mathematics Division, Oak Ridge National Laboratory, TN 37831}
@@
 \address{$^{4}$Department of Physics and Astronomy, University of Kentucky Lexington, KY 40506}
-\address{$^{5}$Department of Astrophysical Sciences, Princeton University, NJ 08544}
+\address{$^{5}$Princeton University, NJ 08544}
 \address{$^{6}$Joint Institute for Computational Sciences, Oak Ridge National Laboratory, TN 37831}
@@
 \begin{abstract}
-The toolkit for high-order neutrino-radiation hydrodynamics (\thornado) is being developed for simulations of core-collapse supernovae (CCSNe) and related problems.  
+The {\bf t}oolkit for {\bf h}igh-{\bf or}der {\bf n}eutrino-r{\bf ad}iation hydr{\bf o}dynamics (\thornado) is being developed for simulations of core-collapse supernovae (CCSNe) and related problems.
 Current capabilities in \thornado\ include solvers for the Euler equations --- in non-relativistic and special relativistic limits --- and the two-moment model of neutrino transport.  
@@
 
-The toolkit for high-order neutrino-radiation hydrodynamics (\thornado) is being developed to simulate neutrino-radiation hydrodynamics in CCSNe and related applications in nuclear astrophysics.  
+The {\bf t}oolkit for {\bf h}igh-{\bf or}der {\bf n}eutrino-r{\bf ad}iation hydr{\bf o}dynamics (\thornado) is being developed to simulate neutrino-radiation hydrodynamics in CCSNe and related applications in nuclear astrophysics.
 The spatial discretization of solvers for hyperbolic partial differential equations in \thornado\ is based on the DG method, while we foresee using a combination of spectral and continuous finite element methods for solving elliptic equations; e.g., for Newtonian gravity or relativistic gravity employing the conformal flatness approximation \cite{wilson_etal_1996}.
@@
 
-\section{Discontinuous Galerkin Method}
+\section{Discontinuous Galerkin method}
 
@@
 \end{equation}
-where superscripts $-/+$, e.g., in the arguments of $\vect{U}_{h}$, indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
+where superscripts $-/+$, e.g. in the arguments of $\vect{U}_{h}$, indicate that the function is evaluated to the immediate left/right of $x^{i}$.  
 We use the Harten-Lax-van Leer (HLL) flux \cite{harten_etal_1983} or the HLLC flux \cite{toro_etal_1994,mignoneBodo_2005} for all the numerical experiments presented in Section~\ref{sec:numerical}.
@@
 We provide further details on the DG method to arrive at the equations that are actually evolved in \thornado.  
-We start by introducing some notation, defining the polynomial expansion for $\vect{U}_{h}$ and the quadrature rules used to evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}.  
-Then we provide explicit expressions for each of the terms in Equation~\eqref{eq:semidiscreteDG}.  
+We start by introducing some notation, defining the polynomial expansion for $\vect{U}_{h}$ and the quadrature rules used to evaluate the integrals in Eq.~\eqref{eq:semidiscreteDG}.  
+Then we provide explicit expressions for each of the terms in Eq.~\eqref{eq:semidiscreteDG}.  
 For simplicity we consider one spatial dimension ($d=1$) and drop indices denoting the spatial dimension.  
@@
 Then, for any $\eta_{j}\in S_{N}$, $\ell_{i}(\eta_{j})=\delta_{ij}$, so that $\vect{U}_{h}(x(\eta_{j}),t)=\vect{U}_{j}(t)$.  
-We introduce numerical quadratures to evaluate the integrals in Equation~\eqref{eq:semidiscreteDG}.  
+We introduce numerical quadratures to evaluate the integrals in Eq.~\eqref{eq:semidiscreteDG}.  
 First we define the $M$-point quadrature $Q_{M}:C^{0}(I)\to\mathbb{R}$ with abscissas $\hat{S}_{M}=\{\eta_{q}\}_{q=1}^{M}$ and weights $\{w_{q}\}_{q=1}^{M}$, normalized such that $\sum_{q=1}^{M}w_{q}=1$.
@@
 
-\section{Preliminary Numerical Results}
+\section{Preliminary numerical results}
 \label{sec:numerical}
@@
 We use the HLL Riemann solver when solving the non-relativistic Euler equations and the HLLC Riemann solver when solving the special relativistic Euler equations.  
-The purpose of the tests is gauge the performance of the DG implementation on a set of benchmarks as an initial measure of its suitability for future for CCSN simulations.
+The purpose of the tests is to gauge the performance of the DG implementation on a set of benchmarks as an initial measure of its suitability for future CCSN simulations.
 
@@
   \vect{U}=\big(\rho,\rho u_{j},E\big)^{\trans},~
-  \vect{F}^{i}=\big(\rho\,u^{i},\Pi^{i}_{~j},(E+p)u^{i}\big)^{\trans},~
+  \vect{F}^{i}=\big(\rho u^{i},\Pi^{i}_{~j},(E+p)u^{i}\big)^{\trans},~
   \text{and}~
@@
 
-\subsubsection{Sod Shock Tube}
+\subsubsection{Sod shock tube}
 
@@
 
-\subsubsection{Sedov-Taylor Blast Wave}
+\subsubsection{Sedov-Taylor blast wave}
 
@@
 
-\subsubsection{Shu-Osher Shock Tube}
+\subsubsection{Shu-Osher shock tube}
 
@@
 
-\subsubsection{Kelvin-Helmholtz (KH) Instability}
-This hydrodynamic instability is of significant astrophysical relevance --- including in the explosion phase of CCSNe --- and may occur in the interface separating fluids in relative motion.  
+\subsubsection{Kelvin-Helmholtz (KH) instability}
+This hydrodynamic instability is of significant astrophysical relevance --- including during the explosion phase of CCSNe --- and may occur in the interface separating fluids in relative motion.  
 We compute this problem on the unit square $D=[0,1]\times[0,1]$, imposing periodic boundary conditions, and with initial conditions and single-mode perturbation taken from \cite{mcnally_etal_2012}.  
@@
 Early on ($t=1.5$), the results from the two runs are practically indistinguishable, show no sign of developing secondary billows, and agree visually with results presented in \cite{mcnally_etal_2012}.
-When $t=2.4$, the run with $C_{\TCI}=0.03$ has started to develop secondary billows within the coiled-up interface separating dense (white) and light (black) fluids, while the model with no limiting has not.
+When $t=2.4$, the run with $C_{\TCI}=0.03$ has started to develop secondary billows within the coiled-up interface separating dense (white) and less dense (black) fluids, while the model with no limiting has not.
 When $t=3.0$, these secondary instabilities appear to have largely destroyed the coil structure for the model with limiting, while the coils remain intact in the model without limiting (although secondary billows have started to form in this model at this time).
@@
 
-\subsubsection{Liska-Wendroff Implosion}
+\subsubsection{Liska-Wendroff implosion}
 
@@
 
-\subsubsection{Standing Accretion Shock (SAS)}
+\subsubsection{Standing accretion shock (SAS)}
 
@@
 
-\subsubsection{Yahil-Lattimer Collapse}
+\subsubsection{Yahil-Lattimer collapse}
 
@@
 This test is also of immediate relevance to CCSN simulations.  
-In \cite{yahilLattimer_1982,yahil_1983}, self-similar solutions to the gravitational collapse problem where constructed for $6/5\le\Gamma<4/3$.   
+In \cite{yahilLattimer_1982,yahil_1983}, self-similar solutions to the gravitational collapse problem were constructed for $6/5\le\Gamma<4/3$.   
 The solutions smoothly connect an homologously collapsing subsonic inner core (velocity proportional to radius) to a supersonically collapsing outer core in near free-fall ($u\propto r^{-1/2}$).  
@@
 
-We show results for a model with $\Gamma=1.3$.  
+We show results for a model with $\Gamma=1.30$.  
 We use spherical polar coordinates, and let $D=[0,1\times10^{5}]$~km, which is covered with $256$ elements.  
@@
 
-\section{Summary and Outlook}
+\section{Summary and outlook}
 
@@
 Results from a suite of tests in one and two spatial dimensions --- including problems with strong shocks --- demonstrate reliable performance of the implementation.  
-Two tests in spherical symmetry (standing accretion shock \cite{blondin_etal_2003} and Yahil-Lattimer collapse \cite{yahilLattimer_1982,yahil_1983}) demonstrate the DG method's ability to handle conditions relevant to simulations of CCSN.
+Two tests in spherical symmetry (standing accretion shock \cite{blondin_etal_2003} and Yahil-Lattimer collapse \cite{yahilLattimer_1982,yahil_1983}) demonstrate the DG method's ability to handle conditions relevant to CCSN simulations.
 We will present a more in-depth analysis of the performance of \thornado\ on these (and related) problems in a future study.
@@
 
-\ack E.~E. and A.~M. acknowledge support from the NSF Gravitational Physics Program (NSF-GP 1505933 and 1806692).
+\ack Eirik Endeve and Anthony Mezzacappa acknowledge support from the NSF Gravitational Physics Program (NSF-GP 1505933 and 1806692).
 
@@
 \begin{thebibliography}{34}
-  \bibitem{bassi_etal_2013} Bassi, F., Franchina, N. Ghidoni, A., \& Rebay, S. 2013, {\it Int. J. Numer. Meth. Fluids}, {\bf 71}, 1322
-  \bibitem{blondin_etal_2003} Blondin, J.M., Mezzacappa, A., \& DeMarino, C. 2003, {\it ApJ}, {\bf 584}, 980
-  \bibitem{brennerScott_2008} Brenner, S.C. \& Scott, L.R. 2008, {\it The Mathematical Theory of Finite Element Methods}, Springer
-  \bibitem{cockburnShu_1998} Cockburn, B. \& Shu, C.-W. 1998, {\it JCP}, {\bf 141}, 199
-  \bibitem{cockburnShu_2001} Cockburn, B. \& Shu, C.-W. 2001, {\it Journal of Scientific Computing}, {\bf 16}, 173
-  \bibitem{dumbser_etal_2014} Dumbser, M., Zanotti, O., Loub{\`e}re, R., \& Diot, S. 2014, {\it JCP}, {\bf 278}, 47
-  \bibitem{fambri_etal_2018} Fambri, F., Dumbser, M., K{\"o}ppel, S., Rezzolla, L., \& Zanotti, O. 2018, {\it MNRAS}, {\bf 477}, 4543
-  \bibitem{fuShu_2017} Fu, G. \& Shu, C.-W. 2017, {\it JCP}, {\bf 347}, 305
-  \bibitem{harten_etal_1983} Harten, A., Lax, P.D., \& Van Leer, B. 1983, {\it SIAM~Review}, {\bf 25}, 35
-  \bibitem{hesthavenWarburton_2008} Hesthaven, J.S. \& Warburton T. 2008, {\it Nodal discontinuous Galerkin methods: Algorithms, analysis and applications}, Springer
-  \bibitem{klockner_etal_2009} Kl{\"o}ckner, A. Warburton, T., Bridge, J. \& Hesthaven, J.S. 2009, {\it JCP}, {\bf 228}, 7863
-  \bibitem{landauLifshitz_1979} Landau, L.D. \& Lifshitz, E.M. 1979, {\it Fluid Mechanics}, Pergamon
-  \bibitem{liskaWendroff_2003} Liska, R. \& Wendroff, B. 2003, {\it SIAM J. Sci. Comput.}, {\bf 25}, 3
-  \bibitem{martiMuller_2003} Mart{\'i}, J.M. \& M{\"u}ller, E. 2003, {\it Living Rev. Relativ.}, {\bf 6}, 7
-  \bibitem{mcnally_etal_2012} McNally, C., Lyra, W., \& Passy, J.-C. 2012, {\it ApJS}, {\bf 201}, 18
-  \bibitem{mignoneBodo_2005} Mignone, A. \& Bodo, G. 2005, {\it MNRAS}, {\bf 364}, 126
-  \bibitem{muller_2016} M{\"u}ller, B. 2016, {\it PASA}, {\bf 33}, 1
-  \bibitem{qin_etal_2016} Qin, T., Shu, C.-W., \& Yang, Y. 2016, {\it JCP}, {\bf 315}, 323
-  \bibitem{radiceRezzolla_2011} Radice, D. \& Rezzolla, L. 2011, {\it Phys. Rev. D}, {\bf 84}, 024010
-  \bibitem{remacle_etal_2003} Remacle, J.-F., Flaherty, J.E., \& Shephard, M.S. 2003, {\it SIAM~Review}, {\bf 45}, 53
-  \bibitem{schaal_etal_2015} Schaal, K., Bauer, A., Chandrashekar, P. R{\"u}diger, P., Klingenberg, C., \& Springel, V. 2015, {\it MNRAS}, {\bf 453}, 4278
-  \bibitem{sedov_1959} Sedov, L.I. 1959, {\it Similarity and Dimensional Methods in Mechanics}, Academic Press
-  \bibitem{shuOsher_1988} Shu, C.-W. \& Osher, S. 1988, {\it JCP}, {\bf 77}, 439
-  \bibitem{shuOsher_1989} Shu, C.-W. \& Osher, S. 1989, {\it JCP}, {\bf 83}, 32
-  \bibitem{shu_2016} Shu, C.-W. 2016, {\it JCP}, {\bf 316}, 598
-  \bibitem{sod_1978} Sod, G.A. 1978, {\it JCP}, {\bf 27}, 1
-  \bibitem{teukolsky_2016} Teukolsky, S.A. 2016, {\it JCP}, {\bf 312}, 333
-  \bibitem{toro_etal_1994} Toro, E.F., Spruce, M., \& Speares W. 1994, {\it Shock Waves}, {\bf 4}, 25
-  \bibitem{toro_1999} Toro, E.F. 1999, NUMERICA: A Library of Source Codes for Teaching, Research and Applications
-  \bibitem{wilson_etal_1996} Wilson, J.R., Mathews, G.J., \& Marronetti, P. 1996, {\it Phys. Rev. D}, {\bf 54}, 1317
-  \bibitem{wuTang_2015} Wu, K. \& Tang, H. 2015, {\it JCP}, {\bf 298}, 539
-  \bibitem{yahilLattimer_1982} Yahil, A. \& Lattimer, J.M. 1982, {\it Supernovae: A Survey of Current Research}, Reidel
-  \bibitem{yahil_1983} Yahil, A. 1983, {\it ApJ}, {\bf 265}, 1047
-  \bibitem{zhangShu_2010} Zhang, X. \& Shu, C.-W. 2010, {\it JCP}, {\bf 229}, 8918
+  \bibitem{bassi_etal_2013} Bassi F, Franchina N, Ghidoni A and Rebay S 2013 {\it Int. J. Numer. Meth. Fluids} {\bf 71} 1322
+  \bibitem{blondin_etal_2003} Blondin J M, Mezzacappa A and DeMarino C 2003 {\it ApJ} {\bf 584} 980
+  \bibitem{brennerScott_2008} Brenner S C and Scott L R 2008 {\it The Mathematical Theory of Finite Element Methods} Springer
+  \bibitem{cockburnShu_1998} Cockburn B and Shu C-W 1998 {\it JCP} {\bf 141} 199
+  \bibitem{cockburnShu_2001} Cockburn B and Shu C-W 2001 {\it Journal of Scientific Computing} {\bf 16} 173
+  \bibitem{dumbser_etal_2014} Dumbser M, Zanotti O, Loub{\`e}re R and Diot S 2014 {\it JCP} {\bf 278} 47
+  \bibitem{fambri_etal_2018} Fambri F, Dumbser M, K{\"o}ppel S, Rezzolla L and Zanotti O 2018 {\it MNRAS} {\bf 477} 4543
+  \bibitem{fuShu_2017} Fu G and Shu C-W 2017 {\it JCP} {\bf 347} 305
+  \bibitem{harten_etal_1983} Harten A, Lax P D and Van Leer B 1983 {\it SIAM~Review} {\bf 25} 35
+  \bibitem{hesthavenWarburton_2008} Hesthaven J S and Warburton T 2008 {\it Nodal discontinuous Galerkin methods: Algorithms, analysis and applications} Springer
+  \bibitem{klockner_etal_2009} Kl{\"o}ckner A, Warburton T, Bridge J and Hesthaven J S 2009 {\it JCP} {\bf 228} 7863
+  \bibitem{landauLifshitz_1979} Landau L D and Lifshitz E M 1979 {\it Fluid Mechanics} Pergamon
+  \bibitem{liskaWendroff_2003} Liska R and Wendroff B 2003 {\it SIAM J. Sci. Comput.} {\bf 25} 3
+  \bibitem{martiMuller_2003} Mart{\'i} J M and M{\"u}ller E 2003 {\it Living Rev. Relativ.} {\bf 6} 7
+  \bibitem{mcnally_etal_2012} McNally C, Lyra W and Passy J-C 2012 {\it ApJS} {\bf 201} 18
+  \bibitem{mignoneBodo_2005} Mignone A and Bodo G 2005 {\it MNRAS} {\bf 364} 126
+  \bibitem{muller_2016} M{\"u}ller B 2016 {\it PASA} {\bf 33} 1
+  \bibitem{qin_etal_2016} Qin T, Shu C-W and Yang Y 2016 {\it JCP} {\bf 315} 323
+  \bibitem{radiceRezzolla_2011} Radice D and Rezzolla L 2011 {\it Phys. Rev. D} {\bf 84} 024010
+  \bibitem{remacle_etal_2003} Remacle J-F, Flaherty J E and Shephard M S 2003 {\it SIAM~Review} {\bf 45} 53
+  \bibitem{schaal_etal_2015} Schaal K, Bauer A, Chandrashekar P R{\"u}diger P, Klingenberg C and Springel V 2015 {\it MNRAS} {\bf 453} 4278
+  \bibitem{sedov_1959} Sedov L I 1959 {\it Similarity and Dimensional Methods in Mechanics} Academic Press
+  \bibitem{shuOsher_1988} Shu C-W and Osher S 1988 {\it JCP} {\bf 77} 439
+  \bibitem{shuOsher_1989} Shu C-W and Osher S 1989 {\it JCP} {\bf 83} 32
+  \bibitem{shu_2016} Shu C-W 2016 {\it JCP} {\bf 316} 598
+  \bibitem{sod_1978} Sod G A 1978 {\it JCP} {\bf 27} 1
+  \bibitem{teukolsky_2016} Teukolsky S A 2016 {\it JCP} {\bf 312} 333
+  \bibitem{toro_etal_1994} Toro E F, Spruce M and Speares W 1994 {\it Shock Waves} {\bf 4} 25
+  \bibitem{toro_1999} Toro E F 1999 {\it NUMERICA: A Library of Source Codes for Teaching, Research and Applications}
+  \bibitem{wilson_etal_1996} Wilson J R, Mathews G J and Marronetti P 1996 {\it Phys. Rev. D} {\bf 54} 1317
+  \bibitem{wuTang_2015} Wu K and Tang H 2015 {\it JCP} {\bf 298} 539
+  \bibitem{yahilLattimer_1982} Yahil A and Lattimer J M 1982 {\it Supernovae: A Survey of Current Research} Reidel
+  \bibitem{yahil_1983} Yahil A 1983 {\it ApJ} {\bf 265} 1047
+  \bibitem{zhangShu_2010} Zhang X and Shu C-W 2010 {\it JCP} {\bf 229} 8918
 \end{thebibliography}

### 2018-10-17 Documents/M1/Astronum_2018/manuscript.tex
Added acknowledgment. Cosmetic changes for the sine wave tests plots.
Updated the Astronum_2018 document.

@@
 \begin{abstract}
-We develop implicit-explicit (IMEX) schemes for neutrino transport though a background material in \texttt{thornado} code with two-moment method that evolves the angular moments of a neutrino phase space distribution function.
-Considering the upper and lower bounds that introduced by Pauli's exclusion principle on the moments, a algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
-Severn algebraic closures are compared with these bounds and Cernohorsky \& Bludman closure\cite{cernohorskyBludman_1994} which preserves the bounds is chosen for our IMEX schemes.
-For the convex-invariant time integrator, two IMEX scheme named PD-ARSs have been proposed following the work in \cite{chu_etal_2018}.
-PD-ARS denotes convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy, high-order accuracy in the streaming limit, and works well in the diffusion limit.
-Our two PD-ARSs have second-order and third-order explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore are second-order and third-order accurate in the streaming limit.
-The accuracy and convex-invariance of PD-ARSs are demonstrated in the numerical tests with a first-order discontinuous Galerkin(DG) method for spatial discretization and a simple Lax-Friedrichs flux.
+We develop implicit-explicit (IMEX) schemes for neutrino transport through a background material in the \texttt{thornado} code in the context of a two-moment mode that evolves the angular moments of a neutrino phase-space distribution function.
+Considering the upper and lower bounds that are introduced by Pauli's exclusion principle on the moments, an algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
+Several algebraic closures are compared with these bounds in mind and the Cernohorsky and Bludman closure\cite{cernohorskyBludman_1994}, which preserves the bounds, is chosen for our IMEX schemes.
+For the convex-invariant time integrator, two IMEX scheme named PD-ARS have been proposed following the work in \cite{chu_etal_2018}.
+PD-ARS denotes a convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy in general, high-order accuracy in the streaming limit, and works well in the diffusion limit.
+Our two PD-ARS schemes are second- and third-order, explicit, strong-stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore are second- and third-order accurate in the streaming limit, respectively.
+The accuracy and convex-invariance of our PD-ARS schemes are demonstrated in the numerical tests with a first-order discontinuous Galerkin(DG) method for spatial discretization and a simple Lax-Friedrichs flux.
 
@@
 \input{sections/Conclusion}
+\input{sections/Acknowledge}
 
-\section*{References}
+%\section*{References}
 \bibliography{references/references}

### 2018-10-17 Documents/M1/Astronum_2018/sections/Acknowledge.tex
Updated the Astronum_2018 document.

@@
 
-\rc{This research is sponsored, in part, by the Laboratory Directed Research and Development Program of Oak Ridge National Laboratory (ORNL), managed by UT-Battelle, LLC for the U.
+This research is sponsored, in part, by the Laboratory Directed Research and Development Program of Oak Ridge National Laboratory (ORNL), managed by UT-Battelle, LLC for the U.
 S.
@@
 This material is based, in part, upon work supported by the U.S. Department of Energy, Office of Science, Office of Advanced Scientific Computing Research.
-Ran Chu was supported in part by NSF under Grant No. 1535130.}
+Eirik Endeve and Anthony Mezzacappa acknowledge support from the National Science Foundation under group NSF-GP-... and from the UT-ORNL Joint Institute for Computational Sciences.

### 2018-10-17 Documents/M1/Astronum_2018/sections/Conclusion.tex
Updated the Astronum_2018 document.

@@
 
-We have developed IMEX schemes for the two-moment neutrino transport in \texttt{thornado} code respecting Fermi-Dirac statistics.
-The schemes employ algebraic closure based on Fermi-Dirac statistics, a first-order discontinuous Galerkin method, the simple Lax-Friedrichs flux with the convex-invariant time integrator to maintain point-wise realizability of the moments.
-Since the realizability-preserving property is obtained from convexity of the realizable domain, it's possible to construct a scheme with high order DG method.
-See \cite{chu_etal_2018} for some examples with third-order DG method employed.
+We have developed IMEX schemes for two-moment neutrino transport in \texttt{thornado} that respect Fermi-Dirac statistics.
+The schemes employ algebraic closure based on Fermi-Dirac statistics, a first-order discontinuous Galerkin method, the simple Lax-Friedrichs flux, and convex-invariant time integration to maintain point-wise realizability of the moments.
+Since the realizability-preserving property is obtained from the convexity of the realizable domain, it's possible to construct a scheme with a high-order DG method.
+See \cite{chu_etal_2018} for some examples with third-order DG methods.
 
-In the applications motivating this work, the neutrino distribution function can vary from 0 to 1.
-Hence, we have considered the algebraic closure respecting Fermi-Dirac statistics for both low and high occupied condition: different values given by different algebraic closures are compared with the boundary values given by the Fermi-Dirac statistics at different occupation.
-Among the seven algebraic closures we considered, Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka_1991} Janka 2\cite{janka_1992} and Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}, only Cernohorsky \& Bludman closure respecting Fermi-Dirac statistics for all the occupancy.
-So we employ Cernohorsky \& Bludman closure in all the numerical tests in Section~\ref{se:NumericalTests}.
+In the application motivating this work, the neutrino distribution function can vary from 0 to 1.
+Hence, we have considered algebraic closure respecting Fermi-Dirac statistics for both low and high occupancy.
+Among the seven algebraic closures we considered -- Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka_1991}, Janka 2\cite{janka_1992}, and Cernohorsky \& Bludman\cite{cernohorskyBludman_1994} -- only the Cernohorsky \& Bludman closure respected Fermi-Dirac statistics for all occupancies.
+As a result, we employed the Cernohorsky \& Bludman closure in all of the numerical tests in Section~\ref{se:NumericalTests}.
 
-Two PD-ARSs are proposed for the desired IMEX scheme.
-The one with SSPRK2 is second-order and strong stability-preserving in the streaming limit while other with SSPRK3 is third-order.
-Their properties, both accuracy and convex-invariant, are demonstrated with numerical tests.
+Two PD-ARS schemes are proposed for the desired IMEX scheme.
+The one with SSPRK2 is second-order accurate and strong-stability preserving in the streaming limit while the other with SSPRK3 is third-order accurate.
+Their properties, both accuracy and convex-invariance, were demonstrated with numerical tests.
 
-In this work, we adopted Cartesian coordinates, linear collision term, non-relativistic, and fixed material background.
-More realistic problems of scientific interest, such as with the scattering with energy changes and relativistic effects, are left for future research.
+In this work, we adopted Cartesian coordinates, linear collision term, and a fixed non-relativistic material background.
+More realistic problems of scientific interest, such as with the scattering with energy exchange and relativistic effects, are left for future research.

### 2018-10-17 Documents/M1/Astronum_2018/sections/Numerical.tex
Added acknowledgment. Cosmetic changes for the sine wave tests plots.
Updated the Astronum_2018 document.

--- 2018-10-01 Documents/M1/Astronum_2018/sections/Numerical.tex
@@
 
-In this section we present the numerical results obtained with the PD-ARS schemes provided in this paper.
-The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in various regimes.
-The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the realizability-preserving of PD-ARSs scheme.
-All the tests in this subsection were applied with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $.
+In this section we present the numerical results obtained with the PD-ARS schemes given in Section~\ref{se:TimeIntegration}.
+The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in streaming, absorption, and scattering-dominated regimes in one spatial dimension.
+The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the convex-invariance of PD-ARS schemes schemes.
+All the tests in this subsection were constructed with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $.
+
 \subsection{Accuracy Tests}
 \label{se: Accuracy Tests}
-To compare the accuracy of the IMEX scheme, we applied our PDARSs and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
-All the tests in this subsection were applied with the maximum entropy closure in the low occupancy limit.
-In the streaming test, the second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} , (SSPRK2 and SSPRK3, respectively) are also applied to serve as an reference.
-More information and the definition of the absolute error and the relative error can be found in \cite{chu_2018}.
+To compare the accuracy of the IMEX schemes, we applied our PD-ARS schemes and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some problems with known smooth solutions in streaming, absorption, ans scattering-dominated regimes in one spatial dimension.
+All the tests in this subsection were constructed with the maximum entropy closure in the low-occupancy limit(i.e., the Minerbo closure).
+In the streaming test, the second- and third-order accurate explicit strong-stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} (SSPRK2 and SSPRK3, respectively) are plotted as references.
+To compare the numerical results to analytic solutions, the cell-averaged absolute error or the cell averaged relative error are computed.
+For our convergence test, the number of elements ($N$) vary from 8 to 128.
 
 \subsubsection{Sine Wave Streaming}
-This test involves the streaming part only: the collision term is turned off. 
-A periodic domain $D$ was applied and the initial condition is given by...
-More information can be found in \cite{chu_2018}.
-In Figure ~\ref{fig: SineWaveStreaming}, the absolute error for the number density is plotted versus the number of elements $N$.
-Errors obtained with SSPRK3 and PD-ARS with SSPRK3 decrease as $N^{-3}$ as expected.
-All the other schemes have errors decreases as $N^{-2}$.
-In the streaming limit, PD-ARSs degenerate to their explicit part, SSPRK2 and SSPRK3, respectively.
-Hence, errors of PD-ARS and SSPRKs are indistinguishable on the plot.
+The sine wave streaming test is designed for the steaming dominated regime, with $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
+A periodic domain with length=1 is used and the initial condition is $\cJ = \bcH =$ a spatial sine wave function.
+We evolve the test until the sine wave has completed 10 crossings of the domain.
+Figure~\ref{fig: SineWaveStreaming} plots the absolute error for the number density versus the number of elements $N$.
+We see the errors obtained with SSPRK3 and PD-ARS with SSPRK3 as the explicit part decrease as $N^{-3}$, as expected.
+All the other schemes have errors decreasing as $N^{-2}$.
 Among the second-order schemes, SSP2332 has the smallest error.
+
+In the streaming limit, PD-ARS scheme limit to its explicit part, SSPRK2 and SSPRK3, respectively.
+That's why the absolute errors of PD-ARS and SSPRK are indistinguishable on the plot.
+
 \begin{figure}[h]
   \centering
-    \includegraphics[width=0.6\textwidth]{figures/SineWaveStreaming}
+    \includegraphics[width=0.8\textwidth]{figures/SineWaveStreaming}
    \caption{Absolute error versus number of elements $N$ for the streaming sine wave test.
-Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crossing), PD-ARS with SSPRK2 (light red circles) and PD-ARS with SSPRK2 (light red hexagram).
-Black dash-dot reference lines are proportional to $N^{-1}$ (top), $N^{-2}$ (middle), and $N^{-3}$ (bottom), respectively.}
+Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crosses), PD-ARS with SSPRK2 (light red circles) and PD-ARS with SSPRK2 (light red hexagrams).
+Black dashed reference lines are proportional to $N^{-2}$ (top), and $N^{-3}$ (bottom), respectively.}
    \label{fig: SineWaveStreaming}
@@
 \subsubsection{Sine Wave Damping}
-This test is adapted from \cite{skinnerOstriker_2013}.
-Figure~\ref{fig:SineWaveDamping} shows the numerical result of sine wave damping test.
-See \cite{chu_2018} for more information about the test setting.
-SSP2332 as a second-order scheme display second order convergence rate.
-PD-ARSs convergent in first order, as a price paid for realizability-preserving.
+This test, adapted from \cite{skinnerOstriker_2013}, is designed for absorption-dominated regimes, with $\sigma_{\Scatt} = 0$ and $f_0 = 0$, which results in exponential damping of the wave amplitude.
+A periodic domain with length=1 and an initial condition with $\cJ = \bcH =$ a spacial sine wave function is used.
+The amplitude of the analytical solution decreases as $e^{-\sigma_{\Ab} t}$.
+For $\sigma_{\Ab}$ = 0.1, 1 and 10 we evolve the test until the initial condition has been damped by a factor $e^{-10}$. 
+Figure~\ref{fig:SineWaveDamping} shows convergence results of the sine wave damping test in the relative error.
+SSP2332, a second-order scheme, displays second-order convergence.
+PD-ARS schemes converge with a first-order convergence rate given the price paid for convex-invariance.
 \begin{figure}[h]
   \centering
-    \includegraphics[width=0.7\textwidth]{figures/SineWaveDamping}
-   \caption{Relative error versus number of elements $N$ for the damping sine wave test.
+    \includegraphics[width=0.9\textwidth]{figures/SineWaveDamping}
+   \caption{Relative error versus number of elements, $N$, for the damping sine wave test.
 Results for different values of the absorption opacity $\sigma_{\Ab}$, employing various IMEX time stepping schemes, are compared.
@@
 The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).
-Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
+Black dashed reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
   \label{fig:SineWaveDamping}
@@
 \subsubsection{Sine Wave Diffusion}
-The last test with known smooth solution is sine wave diffusion test.
-It is adopted from \cite{radice_etal_2013}.
-See \cite{chu_2018} for more information about the test setting.
-Figure~\ref{fig:SineWaveDiffusionJ} shows the numerical result.
-SSP2332 and PD-ARSs display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$ and their errors are difficult to distinguish.
-PD-ARS with SSP2332 behaviors as good as SSP2332 in the diffusion region but requires 1/3 less implicit solver.
+The last test with known smooth solution,adopted from \cite{radice_etal_2013}, is the sine wave diffusion test with $\sigma_{\Ab} = 0, f_0 = 0$.
+A periodic domain with $D=\{x:x\in[-3,3]\}$ and an initial condition with $\cJ_{0}$ = a spatial sine wave function and $\cH =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ}{x}$ is used.
+The analytic solution is given by $\cJ = \cJ_{0} \times e^{-\f{\pi^2 t}{27\sigma_{\Scatt}}}$ and $\cH = (3\,\sigma_{\Scatt})^{-1}\pd{\cJ}{x}$.
+We evolve with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$, and adjust the end time so that $t_{\mbox{\tiny end}}/\sigma_{\Scatt}=1$. 
+Then the amplitude of the sine wave has been reduced by a factor $e^{-\pi^{2}/27}\approx0.694$ for all values of $\sigma_{\Scatt}$. 
+Figure~\ref{fig:SineWaveDiffusionJ} shows the convergence.
+SSP2332 and PD-ARS schemes display third-order accuracy for the number density, $\cJ$, and second-order accuracy for $\cH_{x}$, and their errors are difficult to distinguish.
+PD-ARS with SSP2332 behaves as good as SSP2332 in the diffusion region but requires 1/3 less implicit solvers.
 \begin{figure}[h]
   \centering
-  \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionJ}
-    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionH}
-  \end{tabular}
+  \centerline{\includegraphics[width=1.2\textwidth]{figures/SineWaveDiffusion}}
+%  \begin{tabular}{cc}
+%    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionJ}
+%    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionH}
+%  \end{tabular}
    \caption{Absolute error for the number density $\cJ$ (left) and the number flux $\cH_{x}$ (right) versus number of elements for the sine wave diffusion test.
@@
 Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.
-The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).
-Black dash-dot on the left plot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.
-Black dash-dot on the right plot reference lines are proportional to $N^{-2}$ .}
+The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles), and PD-ARS with SSPRK3 (hexagram).
+Black dashed lines on the left plot reference lines proportional to $N^{-2}$ (top) and $N^{-3}$ (bottom), respectively.
+Black dashed line on the right plot reference lines proportional to $N^{-2}$ .}
    \label{fig:SineWaveDiffusionJ}
@@
 \subsection{Neutrino Stationary State Test} \label{se: Neutrino Stationary State Test}
-Next we consider a more realistic-like test: two-dimensional neutrino transport with emission, absorption and elastic scattering under a stationary realistic-like background.
-This test is designed to test the realizability-preserving properties of the PD-ARSs schemes.
+Next we consider a more ``realistic'' test: two-dimensional neutrino transport with emission, absorption, and elastic scattering in a stationary ``realistic'' background.
+This is designed to test the realizability-preserving properties of the PD-ARS schemes.
 Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities we used.
-This test is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements on each direction.
-We take 10 energy groups vary from 0~MeV to 300~MeV and initial the neutrino number density $\cJ$ and flux density $\bcH$ both zero(arbitrary small).
-For realizability-preserving test, CB closure with PD-ARSs schemes, SSP2332, scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015} and scheme proposed by McClarren et al.
-\cite{mcclarren_etal_2008} are all applied.
-Only PD-ARSs schemes produces realizability-preserving result and evolve the model to a stable state.
-The realizability-preserving plot and the evolve process of PD-ARSs are given in Figure~\ref{fig:NeutrinoStationaryTestEvolve}.
+This test is constructed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction.
+We take 10 energy groups from 0~MeV to 300~MeV and initialize the neutrino number density $\cJ$ and flux density $\bcH$ both at zero(arbitrarily small).
+For the realizability-preserving test, CB closure with PD-ARS schemes, SSP2332, a scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and a scheme proposed by McClarren et al \cite{mcclarren_etal_2008} are all applied.
+Only PD-ARS schemes produce realizability-preserving results and evolve the model to a stable state.
+The realizability-preserving plot and the evolve process of PD-ARS schemes are given in Figure~\ref{fig:NeutrinoStationaryTestEvolve}.
 
@@
   \end{tabular}
-   \caption{Thermal state plot (left) and neutrino absorptivity ($\sigma_{\Ab}$) and neutrino elastic scattering opacity ($ \sigma_{\Scatt}$) in space (right) for the neutrino stationary state test.}
+   \caption{Thermal state (left) and neutrino absorptivity ($\sigma_{\Ab}$) and neutrino elastic scattering opacity ($ \sigma_{\Scatt}$) (right) for the neutrino stationary state test.}
    \label{fig:NeutrinoStationaryTestEOS}
@@
     \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
-   \caption{Readability plots (left column), the number density $\cJ$ versus radius plots (center column) and the flux factor $|\bcH|/\cJ$ versus radius plots (right column) at t = 0.01~ms ,0.35~ms and 5.0~ms for the neutrino stationary state test.
-For the realizability plots, the light blue area demonstrate the realizability domain and the black lines define its boundary.
+    \caption{Realizability (left column), the number density $\cJ$ versus radius (center column), and the flux factor $|\bcH|/\cJ$ versus radius (right column) at t = 0.01~ms ,0.35~ms and 5.0~ms for the neutrino stationary state test.
+For the realizability plots, the light blue area highlights the realizability domain, and the black lines define its boundary.
 Each $\bcM=(\cJ,\bcH)^{T}$ state is marked by a red dot.
-The results of PD-ARS with SSPRK2 and PD-ARS with SSPRK3 are indistinguishable in these plot.}
+The results of PD-ARS with SSPRK2 and PD-ARS with SSPRK3 are indistinguishable in these plots.}
     \label{fig:NeutrinoStationaryTestEvolve}
 \end{figure}
+
+\clearpage

### 2018-10-17 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Modified the IMEX section.
Updated the Astronum_2018 document.

@@
-\section{Spacial Discretization}\label{se:SpacialDiscretization}
-Here we briefly outline our spacial discretization with the first order discontinuous Galerkin method.
+\section{Spatial Discretization}\label{se:SpacialDiscretization}
+Here we briefly outline our spatial discretization using the first-order discontinuous Galerkin method.
 Let the spatial dimension be $d$ and employ Cartesian coordinates.
-We divide the spatial domain $D$ evenly into $N$ cells and denote the cell as $\bK_{i}$ with $i = 1,\ldots,N$, so that
+We divide the spatial domain $D$ evenly into $N$ cells and denote the $i$th cell as $\bK_{i}$ with $i = 1,\ldots,N$, so that
 \begin{equation*}
@@
 \end{equation*}
-Each of the cell has a volume of $|\bK|$
+Each of the cells has a volume, $|\bK|$, with
 \begin{equation*}
@@
 \end{equation*}
-Then we have cell average moment:
+Then, we have cell-average moments:
 \begin{equation}
@@
 \end{equation}
-Integrate Eq.~\eqref{eq:momentEquations} for each cell $\bK_{i}$ to have
+Integrating Eq.~\eqref{eq:momentEquations} for each cell $\bK_{i}$ given
 \begin{equation}
 \dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{|\bK|} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
+\label{eq:SemiDiscretizatedMomentEquation}
 \end{equation}
-where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the integrated collision term.
-In this paper we use the simple Lax-Friedrichs flux that given by
+where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is the numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the integrated collision term.
+In this paper we use the simple Lax-Friedrichs flux, given by
 \begin{equation}
@@
 Assume $\bcM_{i}^{n}$ is realizable for all $i$. 
-For Eq.~\eqref{eq:MomentIMEX}, lemma 3 in \cite{chu_etal_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.
-Substitute the Lax-Friedrichs flux Eq.~\eqref{eq:Lax-Friedrichs flux} in and $\widetilde{\bcM}^{n}_{i}$ becomes Eq.~\eqref{eq:widetildeM}, a convex combination of $\bcM_{i}^{n}$ and the square bracket term if $\beta \in [0,1]$, and it is realizable if $\beta \in [0,1]$ and the square bracket term is realizable.
-Given by Lemma 2 in \cite{chu_etal_2018}, the square bracket term is indeed realizable.
+For Eq.~\eqref{eq:MomentIMEX}, lemma 3 in \cite{chu_etal_2018} says that $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and given that $\widetilde{\bcM}^{n}_{i}$ stay realizable.
+Substituting the Lax-Friedrichs flux, Eq.~\eqref{eq:Lax-Friedrichs flux}, in Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, $\widetilde{\bcM}^{n}_{i}$ becomes a convex combination of $\bcM_{i}^{n}$ and the square bracket in Eq.~\eqref{eq:widetildeM} if $\beta \in [0,1]$, and it is realizable if $\beta \in [0,1]$ and the term in square brackets is realizable.
+Given Lemma 2 in \cite{chu_etal_2018}, the term in square brackets is indeed realizable.
 Therefore, $\bcM^{n+1}_{i}$ remains realizable given $\beta \in [0,1]$.
-Note that $\beta \in [0,1]$ is also the CFL condition of the Forward-Euler method employing on a transport only Boltzmann equation.
+Note that $\beta \in [0,1]$ is also the CFL condition of the Forward-Euler method applied to a transport-only Boltzmann equation.

### 2018-10-17 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Modified PD-ARS with SSPRK3 subsection.
Updated the Astronum_2018 document.

@@
 
-In this section we show how to use the property we introduced at the end of the previous section to construct a constraint-preserving implicit-explicit (IMEX) scheme.
-The semi-discretization of the moment equation, Eq.~\eqref{eq:momentEquations}, results in a system of ordinary differential equations of the form
+In this section we show how to use the property we introduced at the end of the previous section to construct a constraint-preserving, implicit-explicit (IMEX) scheme.
+The semi-discretization of the moment equations, Eq.~\eqref{eq:momentEquations}, results in a system of ordinary differential equations of the form
 \begin{equation}
@@
 \end{equation}
-is the collection of all moment cell average, $\vect{\cT}$ is the transport operator corresponding to the flux term, the first term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, and $\f{1}{\tau}\,\vect{\cQ}$ is a linear operators corresponding to the collision term, the second term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}.
+is the collection of all cell-average moments, $\vect{\cT}$ is the transport operator corresponding to the flux term, which is the first term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, and $\f{1}{\tau}\,\vect{\cQ}$ is a linear operator corresponding to the collision term, the second term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}.
 
-Sine the realizable $\bcM$ defines a convex set in $\cJ -\bcH$ space, convex-invariant schemes can be used to design realizability-preserving schemes for the two-moment model.
+Since the realizable $\bcM$ define a convex set in $\cJ -\bcH$ space, convex-invariant schemes, which remain in their initial convex set, can be used to design realizability-preserving schemes for the two-moment model.
 The following discussion shows how to construct a convex-invariant scheme.
@@
 \subsection{Standard Implicit-Explicit Scheme}
-Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form 
+Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form\cite{pareschiRusso_2005}
 \begin{align}
@@
 \end{align}
-where  $(\tilde{a}_{ij})$ and $(a_{ij})$ are coefficients of the $i$th-stage and they are the elements of matrices $\tilde{A}$ and $A$, respectively, and the vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weights vector.
-Some conditions those coefficients and weights have to satisfy to serve an accurate, converge and stable scheme.
+where  $(\tilde{a}_{ij})$ and $(a_{ij})$ are coefficients of the $i$th-stage and they are the elements of matrices $\tilde{A}$ and $A$, respectively, and the vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weight vectors.
+These coefficients and weights have to satisfy certain condition for an accurate, convergent and stable scheme.
 For instance, to have second-order temporal accuracy, the following conditions are required:
@@
 
-\subsection{Constraint-Preserving Implicit-Explicit Scheme}
-Beyond the accuracy requirement, a convex-invariant IMEX has extra constraints to satisfy.
-The problem left is finding those constraints on $(\tilde{a}_{ij})$, $(a_{ij})$, $\tilde{w}_{i}$ and $w_{i}$.
-As Hu et al. did in their paper \cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten as
+\subsection{A Constraint-Preserving Implicit-Explicit Scheme}
+Beyond the accuracy requirement, a convex-invariant IMEX scheme has extra constraints to satisfy.
+The problem left is to find the additional constraints on $(\tilde{a}_{ij})$, $(a_{ij})$, $\tilde{w}_{i}$, and $w_{i}$.
+Following Hu et al\cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten as
 \begin{equation}
@@
 
-It can be proved \cite{chu_etal_2018} that the conditions we need for a simple convex-invariant IMEX is:
+It can be proven that the conditions we need for a simple convex-invariant IMEX scheme are: \cite{chu_etal_2018}
 \begin{enumerate}
-    \item Consistency of the implicit coefficients
+    \item Consistency of the implicit coefficients:
     \begin{equation}
@@
     \end{equation}
-    \item Second-order accuracy in the streaming limit; i.e., satisfies \begin{equation}
+    \item Second-order accuracy in the streaming limit:
+    \begin{equation}
       \sum_{i=1}^{s}\tilde{w}_{i}=1
@@
     \end{equation}
-    \item Convex-invariant; i.e. satisfies 
+    \item Convex-invariant:
     \begin{align}
@@
                   j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
-
     And $c_{ij}$ and $\hat{c}_{ij}$ be given by
@@
     Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.
-
-    \item Well-behaved in the diffusion limit; i.e., satisfies \begin{equation}
+    \item Well-behaved in the diffusion limit:
+    \begin{equation}
       \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s,
@@
     \item Less than four stages ($s\le3$).
-    \item Globally stiffly accurate (GSA): $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$.
+    \item Globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. (GSA)
 \end{enumerate}  
-We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{chu_etal_2018})
-We give two optimized PD-ARS scheme here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. 
-They have second order and third order accuracy in the streaming limit, respectively.
+We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{chu_etal_2018}.)
+We give two optimized PD-ARS schemes here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. 
+They have second- and third-order accuracy in the streaming limit, respectively.
 \subsubsection{PD-ARS with SSPRK2}
-The explicit part of this IMEX scheme is SSPRK2.
+Here we give a family of PD-ARS with SSPRK2 in the standard double Butcher tableau form: explicit tableau on the left ($\tilde{A}$), implicit tableau on the right ($A$):
 \begin{equation}
@@
 \end{equation}
-
-For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$ with $\epsilon \in [0, 1/2)$.
+and $\epsilon \in [0, 1/2)$.
+For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$.
+The optimized scheme ($c_{\mbox{\tiny Sch}}= 1$) is given by $\epsilon = 0$.
+We chose $\epsilon = 0.1$ for the numerical test in Section~\ref{se:NumericalTests}.
 
 \subsubsection{PD-ARS with SSPRK3}
-The explicit part of this IMEX scheme is SSPRK3.
-
+Here we give the optimized PD-ARS with SSPRK3.
+Its standard double Butcher tableau are (explicit tableau on the left, implicit tableau on the right)
 \begin{equation}
@@
   	1/2 & 0 & 1/4 & 1/4 \\ 
-  	1 & 0 & 1/6-\epsilon^2 /4 & 1/6-\epsilon/4 & 2/3+\epsilon(1+\epsilon)/4\\\hline
-  	  & 0 & 1/6-\epsilon^2 /4 & 1/6-\epsilon/4 & 2/3+\epsilon(1+\epsilon)/4
+  	1 & 0 & 1/6 & 1/6 & 2/3\\\hline
+  	  & 0 & 1/6 & 1/6 & 2/3
   \end{array}
 \end{equation}
-For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 3\epsilon/2$ with $\epsilon \in [0,2/3)$. (\rc{Other forms})
+For this schemes, $c_{\mbox{\tiny Sch}}= 1$.

### 2018-10-17 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Updated the Astronum_2018 document.

--- 2018-10-01 Documents/M1/Astronum_2018/sections/TwoMoments.tex
@@
 \subsection{Transport Equations}
-Considering the neutrino pass through a static dense matter and only emission, absorption and elastic scattering exist, the transport equation of the neutrino after scaling to dimensionless units can be written as
+Consider neutrino transport through static dense matter with only emission, absorption and isotropic scattering.
+The Boltzmann equation after scaling to dimensionless units ($k_{B} = \hbar = c = 1$) can be written as
 \begin{equation}
   \pd{f}{t}+\vect{\ell}\cdot\nabla f
-  =\f{1}{\tau}\,\cC(f),
+  =\f{1}{\tau}\,\cC(f).
   \label{eq:boltzmann}
 \end{equation}
-which is known as Boltzmann equation.
-The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrino propagating in the direction $\omega\in\bbS^{2}$, with neutrino energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
-$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector which parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
-On the right-hand side, $\tau$ is interaction strength parameter: $\tau\ll1$ for opaque region where neutrino has strong interaction with the background; $\tau\gg1$ for transparent region where neutrino has weak interaction with the background and streams freely.
+The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with neutrino energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
+$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
+On the right-hand side, $\tau$ is the interaction strength parameter: $\tau\ll1$ for opaque regions where neutrinos have frequent interactions with the background; $\tau\gg1$ for transparent regions where neutrinos rarely interact with the background and stream freely.
 $\cC(f)$ is the collision term, which models emission, absorption, and isotropic and elastic scattering: 
@@
 \end{equation}
-with $\xi = \sigma_{\Ab} / (\sigma_{\Ab}  + \sigma_{\Scatt} )$ be the emission and absorption contribution parameter: $\xi = 1$ when the scattering opacity $\sigma_{\Scatt} = 0$, pure emission and absorption; $\xi = 0$ when the absorption opacity $\sigma_{\Ab} = 0$, pure scattering.
-$f_{0}$ is the neutrino equilibrium distribution function which has the following form:
+with $\xi = \sigma_{\Ab} / (\sigma_{\Ab}  + \sigma_{\Scatt} )$: $\xi = 1$ when the scattering opacity $\sigma_{\Scatt} = 0$ corresponding to pure emission and absorption; $\xi = 0$ when the absorption opacity $\sigma_{\Ab} = 0$ corresponding to pure scattering.
+$f_{0}$ is the neutrino equilibrium distribution function, which has the following form:
 \begin{equation}
@@
 \end{equation}
-$T(\vect{x})$ is the temperature in energy unit and $\mu(\vect{x})$ is the neutrino chemical potential.
+$T(\vect{x})$ is the temperature in energy units and $\mu(\vect{x})$ is the neutrino chemical potential.
 Both of them depend on the properties of the background as a function of $\vect{x}$.
@@
 \subsection{Two-Moment Model}
-An approximate solution of Boltzmann equation Eq.~\eqref{eq:boltzmann} can be found by employing two-moment model.
-Define the angular moments of the distribution function as following
+An approximate solution of the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, can be found by employing a two-moment model.
+Define the angular moments of the distribution function as follows
 \begin{equation}
@@
 \end{equation}
-where $\vect{z}:=\{\varepsilon,\vect{x}\}$, the zeroth moment $\cJ$ is referred as the particle density, the first moment $\bcH$ is the particle flux, and the second moment $\bcK$ is the stress tensor.
-Then integral Eq.~\eqref{eq:boltzmann} as the zeroth and the first moments both side to have
+where $\vect{z}:=\{\varepsilon,\vect{x}\}$.
+The zeroth moment, $\cJ$, is referred to as the particle density.
+The first moment, $\bcH$, is the particle flux.
+And the second moment, $\bcK$, is the stress tensor.
+We can integrate Eq.~\eqref{eq:boltzmann} to their equations of the zeroth and the first moments
 \begin{equation}
@@
 $\vect{I}$ is the identity matrix.
-Therefore, solving Boltzmann equation Eq.~\eqref{eq:boltzmann} for a neutrino distribution function $f(\omega,\vect{z},t)$ is converted to solving two-moment equations for the neutrino number density $\cJ(\vect{z},t)$ and the neutrino flux $\bcH(\vect{z},t)$.
+Therefore, solving the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, for the neutrino distribution function, $f(\omega,\vect{z},t)$, is approximated by solving the two-moment equations for the neutrino number density, $\cJ(\vect{z},t)$, and flux, $\bcH(\vect{z},t)$.
 
 \subsection{Algebraic Closures }
-As it shown in previous section, the $i$-th order moment equation requires information of the $(i+1)$-th order moment and leads the two-moment system be open. 
-To close the two-moment system, a strategy named algebraic closure is built.
-For a two-moment method, algebraic closures give an approximate $\bcK$ based on the lower moments as following:
+As is shown in the previous section, the $i$-th order moment equation requires information of the $(i+1)$-th order moment and the two-moment system is open. 
+To close the two-moment system, an algebraic closure is constructed.
+For a two-moment method, algebraic closures give an approximate $\bcK$ based on the lower moments as follows:
 \begin{equation}
@@
 where $\vect{k}$ is the Eddington tensor.
-Assume the neutrino transport is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore\cite{levermore_1984} proposed
+For example, assuming the neutrino transport is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore\cite{levermore_1984} proposed
 \begin{equation}
@@
 
-\subsection{Constraints on Moments}
-One fundamental fact about neutrino is that they are fermion which follow the Pauli exclusion principle, $f \in (0,1)$.
-As a result, the angular moments of $f$ are confined as the following: 
+\subsection{Constraints on the Moments}
+One fundamental fact about neutrinos is that they are fermions, which obey follow the Pauli exclusion principle, $f \in [0,1]$.
+As a result, the angular moments of $f$ are constrained as follows: 
 \begin{align}
-\cJ \in(0,1), \quad &(1-\cJ)\cJ-|\vect{\cH}|  > 0, \label{eq:MomentsBounds}\\
+\cJ \in[0,1], \quad &(1-\cJ)\cJ-|\vect{\cH}|  \geq 0, \label{eq:MomentsBounds}\\
   \chi_{\mbox{\tiny min}}
   =\max\big(1-\f{2}{3\cJ},h^{2}\big)
-  < & \chi<\min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}},
+  \leq & \chi \leq \min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}},
   \label{eq:eddingtonFactorBounds}
 \end{align}
-where $h = |\bcH|/\cJ$ is the flux factor.[citation]
+where $h = |\bcH|/\cJ$ is the flux factor.\cite{levermore_1984,lareckiBanach_2011,kershaw_1976,shohatTamarkin_1943}
 
-The inequalities in Eq.\ref{eq:MomentsBounds} define the realizable $\bcM$ which defines a convex set in $\cJ -\bcH$ space.
-As we will see later in Section \ref{se:SpacialDiscretization}, this convexity makes a constraint-preserving spacial discretization possible.
+The inequalities in Eq.~\eqref{eq:MomentsBounds} define the realizable $\bcM$, which define a convex set in $\cJ -\bcH$ space.
+As we will see later in Section \ref{se:SpacialDiscretization}, this convexity makes a constraint-preserving spatial discretization possible.
 
-The inequalities in Eq.\ref{eq:eddingtonFactorBounds} desire more attention than have be given.
-They have the equal importance as the inequalities in Eq.\ref{eq:MomentsBounds} in preserving the validity of the simulation result.
-However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson1975,leblanc1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka1992} may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1\cite{janka1991} can be dangerous for both the cases.
-The only algebraic closure that remains in the bounds among those seven plotted closures is Cernohorsky \& Bludman's \cite{cernohorskyBludman_1994}.
+The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} deserve more attention than has been given.
+They have equal importance \rc{relative to} the inequalities in Eq.~\eqref{eq:MomentsBounds} in preserving the validity of the simulation result.
+However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all algebraic closures satisfy the Eddington factor bounds, Eq.~\eqref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine in the neutrino low occupancy limit, but not for high occupancies; Janka 1\cite{janka_1991} can be in error in both cases.
+The only algebraic closure that remains within the Eddington factor bounds among those plotted is Cernohorsky and Bludman's \cite{cernohorskyBludman_1994}.
+
+Though Levermore closure and Minerbo closure don't conserve the bounds in the high occupancy limit, they are widely used: {O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} use Minerbo closure, and Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016} use Levermore clsoure.
+
 \begin{figure}[h]
@@
   \end{tabular}
-   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupied) and $\cJ=0.9$ (right panel, high occupied).
+   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupancy) and $\cJ=0.9$ (right panel, high occupancy).
 In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.
-We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dash black lines, respectively).}
+We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$, defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dashed black lines, respectively).}
   \label{fig:EddingtonFactorsWithDifferentClosure}

### 2018-10-17 Documents/M1/Astronum_2018/sections/intro.tex
Updated the Astronum_2018 document.

@@
 
-Core-collapse supernovae (CCSNe) are the explosion of massive stars which end their life.
+Core-collapse supernovae (CCSNe) are the explosions of massive stars that end their lives.
 CCSNe are a dominant source of heavy elements and play an important role in many astrophysical phenomena, such as neutron star and black hole formation.  
 Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
-A solid theoretical framework for these explosion mechanism will illuminate explanations to many import questions in fundamental physics.
+A solid theoretical framework for the explosion mechanism will illuminate approaches to many import questions in fundamental physics.
 
-One essential part of the explosion mechanism is neutrino transport which drives the explosion.  
-Neutrino transport is modeled by Boltzmann transport equation which is partial differential equation evolving a phase space distribution function $f$.
-Simulating the neutrino transport is convert to find a solution of Boltzmann transport equation for a interested domain and period with an acceptable accuracy.
+One essential part of the explosion mechanism is neutrino transport, which drives the explosion.  
+Ideally neutrino transport would be modeled by the Boltzmann transport equation, which is a partial differential equation evolving a phase-space distribution function $f$.
+Simulating the neutrino transport is equivalent to finding a solution of the Boltzmann equation for a specific domain and period with acceptable accuracy.
 
-Nevertheless, solving multi-dimensional Boltzmann transport equation can be expensive.
-To balance physical fidelity and computational expediency, an approximation method called two-moment method is established.
-In two-moment method, the evolve variables are the zeroth and first angular moments of the distribution function $f$, the spectral particle density $\cJ$ and flux $\bcH$ respectively.
+However, solving the multi-dimensional Boltzmann transport equation is expensive.
+To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted.
+In the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$: the spectral particle density $\cJ$ and flux $\bcH$, respectively.
 However, the Boltzmann transport equation is a nonlinear equation.
-Its integral form which gives the two-moment method requires the information of the second angular moment $\bcK$ to close the system.
-Therefore, a algebraic closure which gives a approximated value of $\bcK$ given $\cJ$ and $\bcH$ is needed.
-The two-moment method has been widely applied with different algebraic closures, such as the Minerbo\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan and et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018} and Just et al\cite{just_etal_2018} ) and the Levermore\cite{levermore_1984} closure(e.g.~Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018} and Kuroda et al\cite{kuroda_etal_2016}).
+Its integral form, which gives the two-moment method system of equations, requires knowledge of the second angular moment $\bcK$ to close this system.
+Therefore, an algebraic closure that gives an approximate value of $\bcK$ given $\cJ$ and $\bcH$ is needed.
+The two-moment method has been widely applied with different algebraic closures, such as the Minerbo\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan and et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} ) and the Levermore\cite{levermore_1984} closure(e.g.~Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016}).
 
-Applying two-moment method only is not sufficient to have an affordable solution since the simulating period is long considering the physics it involves.
-To be precisely, neutrino interact with the background rapidly and its characteristic time scalar is very small comparing to the length of CCSNe explosion process. 
-This makes the time step needed by an explicit time integrator small and a lot of calculation needed. 
-On the other hand, solving the moment equations fully implicitly requires inverting many band structure matrices whose sizes depend on the space discretization.
-The band structure of the large matrices makes not only the matrices inverting expensive but also the simulation parallel unfriendly.
-To manipulate these challenges, implicit-explicit (IMEX) methods are taken into consideration.
-By treating the transport term explicitly and the collision term implicitly, IMEX methods subject only to a time step governed by the explicit transport term and the matrix it needs to invert is block diagonal dominated.
-Therefore, IMEX methods need less step and the calculation for each step is parallelable.
+Applying the two-moment method alone does not guarantee an affordable solution.
+To be precise, neutrinos interact with the background, and the characteristic time scale of these interactions are very small compared to the domination of the CCSN explosion. 
+This makes the time step needed by an explicit time integrator prohibitively small. 
+On the other hand, solving the moment equations fully implicitly requires inverting globally many band-structured matrices whose sizes depend on the spatial discretization.
+Such a global inversion is both expensive and parallelization unfriendly.
+To circumvent these challenges, implicit-explicit (IMEX) methods are taken into consideration.
+By treating the transport terms in the two-moment equations explicitly and the collision terms implicitly, IMEX methods are subject only to a time step governed by the explicit transport terms, and the matrices to be inverted are block diagonal dominated.
+Therefore, IMEX methods require fewer time steps, and the calculation for each step is parallelizable.
 
 %\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.} 
-To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a convex-invariant diffusion accurate IMEX schemes for ensure a valid result.
+To employ IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac-statistics-preserving algebraic closure for closing the two-moment equations and a convex-invariant, diffusion-accurate IMEX scheme to ensure a physical result.
 Because the angular moments are confined.
-Since a neutrino distribution function is confined ($f\in(0,1)$) by the Pauli exclusion principle, its moments as integrals of a confined function over confined domain ($\omega\in\bbS^{2}$) are also confined.
-We call the moments satisfying a Fermi-Dirac statistics realizable moments.
-Hence, the algebraic closure should give a realizable $\bcK$ and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
+Since the neutrino distribution function is constrained ($f\in[0,1]$) by the Pauli exclusion principle, its moments as integrals of a constrained function over constrained domain ($\omega\in\bbS^{2}$) are also constrained.
+We call the moments satisfying Fermi-Dirac statistics \textit{realizable moments}.
+Hence, the algebraic closure should give a realizable $\bcK$, and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
 That's why a Fermi-Dirac statistics satisfied algebraic closure is needed.
-Then, the realizability of $\cJ$ and $\bcH$ on each time step requires a convex-invariant IMEX.
-Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.
-What's more, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.
+Then, the realizability of $\cJ$ and $\bcH$ on each time step requires a convex-invariant IMEX scheme.
+Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX scheme for two-moment neutrino transport.
+What's more, the physics of neutrino transport in CCSN requires the IMEX scheme to be diffusion-accurate.
 
-\rc{\cite{gottlieb_etal_2001} showed standard IMEX scheme can't have an order higher than first without a restrict time step requirement.}
+\cite{gottlieb_etal_2001} showed standard IMEX scheme can't have an order higher than first without a restrict time step requirement.
 To have second-order (or higher-order) accuracy, some correction steps are needed.
-Unfortunately, the correction step can deteriorate the accuracy of the IMEX in the diffusion limit and restrict the time step.
-To keep simple, we focus on the IMEX scheme without correction step and require it high-order (second or higher order) in the streaming limit and diffusion accurate.
-We call these IMEX scheme PD-ARS.
-The study of moment realizability and constraint-preserving diffusion accurate IMEX scheme motivates this work.
+Unfortunately, the correction steps can deteriorate the accuracy of the IMEX scheme in the diffusion limit and restrict the time step.
+To keep things simple, we focus on IMEX schemes without correction steps and require them to be high-order (second or higher order) in the streaming limit and diffusion-accurate.
+We call these IMEX schemes \textit{PD-ARS}.
+The study of moment realizability and constraint-preserving, diffusion-accurate IMEX schemes motivate this work.
 
-This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and the constraints on the moments and algebraic closures imposed by Fermi-Dirac statistics;
-Section~\ref{se:SpacialDiscretization} gives a first-order finite volume spatial discretization and shows how the spatial discretization preserve constraints in a IMEX step;
-Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct PD-ARS and two PD-ARSs, one has second-order in the streaming limit and the other has third-order, are provided;
-Section~\ref{se:NumericalTests} presents the results of the numerical tests which demonstrate the portieres of the PD-ARSs; Section~\ref{se:Conclusion} summaries the achievement of this paper.
+This paper is organized as follows: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and the constraints on the moments and algebraic closures imposed by Fermi-Dirac statistics;
+Section~\ref{se:SpacialDiscretization} gives a first-order finite-volume spatial discretization and shows how the spatial discretization preserves constraints in an IMEX step;
+Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct PD-ARS scheme and two PD-ARS schemes, one with second-order accuracy in the streaming limit and the other with third-order accuracy in the same limit;
+Section~\ref{se:NumericalTests} presents the results of the numerical tests, which demonstrate the properties of the PD-ARS schemes; Section~\ref{se:Conclusion} summarizes the achievements of this paper.

### 2018-10-18 Documents/Euler/Astronum_2018/ms_endeve.tex
Minor corrections due to comments from Tony

@@
 \begin{document}
-\title{\thornado-hydro: towards discontinuous galerkin methods for supernova hydrodynamics\footnote{This manuscript has been authored by UT-Battelle, LLC under Contract No.
+\title{\thornado-hydro: towards discontinuous Galerkin methods for supernova hydrodynamics\footnote{This manuscript has been authored by UT-Battelle, LLC under Contract No.
 DE-AC05-00OR22725 with the U.S.
@@
 \address{$^{3}$Department of Astronomy, Vanderbilt University, TN 37212}
-\address{$^{4}$Department of Physics and Astronomy, University of Kentucky Lexington, KY 40506}
+\address{$^{4}$Department of Physics and Astronomy, University of Kentucky, Lexington, KY 40506}
 \address{$^{5}$Princeton University, NJ 08544}
@@
 The dynamics of the bounce shock and associated fluid instabilities, which drive turbulent flows and help shape the explosion, must be faithfully captured (see, e.g., \cite{muller_2016}, for a recent review).
-Essentially, the stellar interior is modeled as a perfect fluid (i.e., thermal conduction and viscosity are not explicitly included) using the Euler equations, but extended to accommodate a nuclear equation of state.
+Essentially, the stellar interior is modeled as a perfect fluid (thermal conduction and viscosity are not explicitly included) using the Euler equations, but the models are extended to accommodate a nuclear equation of state.
 
@@
 
-\section{Discontinuous Galerkin method}
+\section{The discontinuous Galerkin method}
 
@@
 \end{equation}
-where $\vect{U}$ is the evolved state vector, $\vect{F}^{i}$ the fluxes, and $\vect{S}$ the source vector.  
+where $\vect{U}$ is the evolved state vector, $\vect{F}^{i}$ are the fluxes, and $\vect{S}$ is the source vector.  
 We use a formulation of the equations sufficiently general to accommodate curvilinear spatial coordinates encoded in the metric $\gamma_{ij}$, giving the squared line element $ds^{2}=\gamma_{ij}dx^{i}dx^{j}$, whose determinant is $\gamma$.
@@
 Note that the interpolation points $S_{N}$ and the quadrature points $\hat{S}_{M}$ generally do not coincide.  
-However, for sake of computational efficiency we let $M=N$ and $S_{N}=\hat{S}_{N}$, which is a spectral-type nodal collocation DG approximation \cite{bassi_etal_2013}.  
+However, for the sake of computational efficiency we let $M=N$ and $S_{N}=\hat{S}_{N}$, which is a spectral-type nodal collocation DG approximation \cite{bassi_etal_2013}.  
 Inserting Eq.~\eqref{eq:conservedNodalExpansion} into Eq.~\eqref{eq:semidiscreteDG}, letting $v(x)=\ell_{k}(x)$, and using the quadratures defined above, we obtain
@@
 Limiting of the polynomial representation $\vect{U}_{h}$, to reduce oscillations and prevent non-physical states, is a critical step in the DG algorithm.  
-We use the TVD-type slope limiter based on limiting characteristic variables discussed in \cite{cockburnShu_1998}.  
+We use the TVD-type slope limiter based on limiting characteristic variables, discussed in \cite{cockburnShu_1998}.  
 To prevent excessive limiting (e.g., at smooth extrema), we use the troubled-cell indicator (TCI) of \cite{fuShu_2017}.  
@@
 (Here, $\vect{G}$ consists of the first and last element of $\vect{U}$.)  
-In Eq.~\eqref{eq:indicator}, the sum in the numerator and the $\max$ in the denominator extend over the neighboring elements sharing face with the target element $\bK$.  
+In Eq.~\eqref{eq:indicator}, the sum in the numerator and the $\max$ in the denominator extend over the neighboring elements sharing a face with the target element $\bK$.  
 $G_{\bK}$ is the cell average in $\bK$, $G_{\bK}^{(j)}$ is the cell average computed by extrapolating the polynomial representation from the neighbor element $\bK^{(j)}$ into $\bK$, and $G_{\bK^{(j)}}^{(j)}$ is the cell average native to $\bK^{(j)}$.
@@
 
-The first test is the classical Riemann problem due to Sod \cite{sod_1978}, computed using Cartesian coordinates.  
+The first test is the classic Riemann problem due to Sod \cite{sod_1978}, computed using Cartesian coordinates.  
 The one-dimensional computational domain is $D=[0,1]$, and a discontinuity is initially located at $x^{1}=0.5$, separating the left and right states
@@
 We use $256$ elements and run until $t=1$, using $C_{\TCI}=0.03$.  
-Again, the DG method captures the characteristic of the exact solution well.  
+Again, the DG method captures the characteristic of the exact solution.  
 The maximum density in the shock is somewhat lower for the numerical solution than the exact value (about $5$ versus $6$).
@@
 This hydrodynamic instability is of significant astrophysical relevance --- including during the explosion phase of CCSNe --- and may occur in the interface separating fluids in relative motion.  
-We compute this problem on the unit square $D=[0,1]\times[0,1]$, imposing periodic boundary conditions, and with initial conditions and single-mode perturbation taken from \cite{mcnally_etal_2012}.  
+We compute this problem on the unit square $D=[0,1]\times[0,1]$, imposing periodic boundary conditions, and with initial conditions and single-mode perturbations taken from \cite{mcnally_etal_2012}.  
 We use $256^{2}$ elements and evolve until $t=3.0$, well into the nonlinear regime.  
@@
   \caption{\label{fig:KelvinHelmholtz}Mass density from the KH instability at various times, computed with $256^{2}$ elements: $t=1.5$ (top panels), $t=2.4$ (middle panels), and $t=3.0$ (bottom panels).
-Results for $C_{\TCI}=0.06$ are shown in left panels, while result with no limiting are shown in right panels.}
+Results for $C_{\TCI}=0.06$ and $C_{\TCI}\to\infty$ (no limiting) are shown in the left and right panels, respectively.}
 \end{figure}
@@
 We use a geometric grid to resolve the mass distribution as the star collapses and the central density increases from about $10^{9}$~g~cm$^{-3}$ to about $10^{14}$~g~cm$^{-3}$.  
-The size of the innermost element is set to $1$~km while the last element is about $3\times10^{3}$~km.  
+The size of the innermost element is set to $1$~km while the size of the last element is about $3\times10^{3}$~km.  
 We specify the polytropic constant by setting a reference pressure $p=6\times10^{27}$~erg~cm$^{-3}$ for $\rho=7\times10^{9}$~g~cm$^{-3}$ (reasonable values for a massive star in the pre-collapse stage).
-We also specify the collapse time to $(-t)=150$~ms.  
-Results comparing the mass density and velocity of Yahil's reference solution to the solution obtained with \thornado\ using $C_{\TCI}=0.03$ are plotted in Figure~\ref{fig:YahilLattimer}.  
-The agreement of the mass density and velocity profiles is good throughout collapse.
+We also set the collapse time to $(-t)=150$~ms.  
+Results comparing the mass density and velocity of Yahil's reference solution to those obtained with \thornado\ using $C_{\TCI}=0.03$ are plotted in Figure~\ref{fig:YahilLattimer}.  
+The agreement of the mass density and velocity profiles is excellent throughout collapse.
 
@@
 
-The main features of the exact solution are captured quite well with the DG method implemented in \thornado.  
-For Riemann problem~1, we observe some oscillations in the density between the leftmost shock and the contact discontinuity located near $x^{1}=0.6$.  
+Again, the main features of the exact solution are captured with the DG method implemented in \thornado.  
+For Riemann problem~1, we observe some oscillations in the density profile between the leftmost shock and the contact discontinuity located around $x^{1}=0.6$.  
 For Riemann problem~2, the maximum density in the thin density shell between the shock and the contact discontinuity is significantly lower for the numerical solution than the exact solution.  
@@
 
-We have presented preliminary algorithm details and numerical results for solvers of the non-relativistic and special relativistic Euler equations of gas dynamics as implemented in the toolkit for high-order neutrino-radiation hydrodynamics (\thornado).
+We have presented preliminary algorithm details and numerical results for solvers of the non-relativistic and special relativistic Euler equations of gas dynamics as implemented in the {\bf t}oolkit for {\bf h}igh-{\bf or}der {\bf n}eutrino-r{\bf ad}iation hydr{\bf o}dynamics (\thornado).
 The spatial discretization is based on the DG method and the ODEs resulting from this discretization are integrated in time using SSP-RK methods.  

### 2018-10-18 Documents/Euler/Astronum_2018/ms_endeve.tex
minor edit

@@
 We use the ideal gas equation of state where the pressure $p$ is related to the internal energy density $e$ by $p=(\Gamma-1)e$, and where $\Gamma$ is the (constant) adiabatic index.  
-Let the $d$-dimensional computational domain be $D=\times_{i=1}^{d}[\xMin^{i},\xMax^{i}]$, where $\xMin^{i}$ and $\xMax^{i}$ denote the coordinates of the inner and outer boundary in the $i$-th coordinate direction, respectively.
+Let the $d$-dimensional computational domain be $D=\times_{i=1}^{d}[\xMin^{i},\xMax^{i}]$, where $\xMin^{i}$ and $\xMax^{i}$ denote the coordinates of the inner and outer boundary in the $i$th coordinate direction, respectively.
 We use polynomials of degree $k=2$ combined with SSP-RK3 time stepping, and all the tests were run with a Courant-Friedrichs-Lewy (CFL) factor of $C=0.1$.  

### 2018-10-18 Documents/M1/Astronum_2018/manuscript.tex
Backup the modification made for abstract, introduction and two-moment method section.

@@
 \begin{abstract}
-We develop implicit-explicit (IMEX) schemes for neutrino transport through a background material in the \texttt{thornado} code in the context of a two-moment mode that evolves the angular moments of a neutrino phase-space distribution function.
+We develop implicit-explicit (IMEX) schemes for neutrino transport through a background material in the \texttt{thornado} code in the context of a two-moment model that evolves the angular moments of a neutrino phase-space distribution function.
 Considering the upper and lower bounds that are introduced by Pauli's exclusion principle on the moments, an algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
-Several algebraic closures are compared with these bounds in mind and the Cernohorsky and Bludman closure\cite{cernohorskyBludman_1994}, which preserves the bounds, is chosen for our IMEX schemes.
+A finite-volume/first-order discontinuous Galerkin(DG) method is used to interporate how an algebraic moment closure based on Fermi-Dirac statistics satisfies the bounds.
+Several algebraic closures are compared with these bounds in mind and the Cernohorsky and Bludman closure\cite{cernohorskyBludman_1994}, which satisfies the bounds, is chosen for our IMEX schemes.
 For the convex-invariant time integrator, two IMEX scheme named PD-ARS have been proposed following the work in \cite{chu_etal_2018}.
-PD-ARS denotes a convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy in general, high-order accuracy in the streaming limit, and works well in the diffusion limit.
+PD-ARS denotes a convex-invariant IMEX Runge-Kutta schemes that has first-order accuracy in general, high-order accuracy in the streaming limit, and works well in the diffusion limit.
 Our two PD-ARS schemes are second- and third-order, explicit, strong-stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore are second- and third-order accurate in the streaming limit, respectively.
-The accuracy and convex-invariance of our PD-ARS schemes are demonstrated in the numerical tests with a first-order discontinuous Galerkin(DG) method for spatial discretization and a simple Lax-Friedrichs flux.
+The accuracy and convex-invariance of our PD-ARS schemes are demonstrated in the numerical tests with a third-order DG method for spatial discretization and a simple Lax-Friedrichs flux.
+We show preliminary result employing tabulated neutrino opacities from Bruenn(1985)\citep{Bruenn_1985}
 

### 2018-10-18 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Backup the modification made for abstract, introduction and two-moment method section.

@@
     \begin{align}
+      &a_{i1} = 0, \quad \text{for} \quad i=1,\ldots,s, \nonumber \\
       &a_{ii}>0, \quad c_{i0},\tilde{c}_{i0}\ge0, \quad \text{for} \quad i=2,\ldots,s, \nonumber \\

### 2018-10-18 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Backup the modification made for abstract, introduction and two-moment method section.

@@
 \subsection{Transport Equations}
-Consider neutrino transport through static dense matter with only emission, absorption and isotropic scattering.
-The Boltzmann equation after scaling to dimensionless units ($k_{B} = \hbar = c = 1$) can be written as
+Consider neutrino transport through static dense matter with only emission, absorption and isotropic iso-energetic scattering.
+The Boltzmann equation after scaling to dimensionless units ($k_{B} = c = 1$) can be written as
 \begin{equation}
@@
 \end{equation}
-The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with neutrino energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
+The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
 $\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
-On the right-hand side, $\tau$ is the interaction strength parameter: $\tau\ll1$ for opaque regions where neutrinos have frequent interactions with the background; $\tau\gg1$ for transparent regions where neutrinos rarely interact with the background and stream freely.
+On the right-hand side, $\tau$ is collision time scale: $\tau\ll1$ for opaque regions where neutrinos have frequent interactions with the background; $\tau\gg1$ for transparent regions where neutrinos rarely interact with the background and stream freely.
 $\cC(f)$ is the collision term, which models emission, absorption, and isotropic and elastic scattering: 
@@
 The zeroth moment, $\cJ$, is referred to as the particle density.
-The first moment, $\bcH$, is the particle flux.
-And the second moment, $\bcK$, is the stress tensor.
-We can integrate Eq.~\eqref{eq:boltzmann} to their equations of the zeroth and the first moments
+The first moment, $\bcH$, is the particle flux, and the second moment, $\bcK$, is the stress tensor.
+We can integrate Eq.~\eqref{eq:boltzmann} to obtain equations for the zeroth and the first moments
 \begin{equation}
@@
 \subsection{Algebraic Closures }
-As is shown in the previous section, the $i$-th order moment equation requires information of the $(i+1)$-th order moment and the two-moment system is open. 
+As is shown in the previous section, the moment equation for $\bcH$ involves $\bcK$ and the two-moment system is open. 
 To close the two-moment system, an algebraic closure is constructed.
@@
 where $\vect{k}$ is the Eddington tensor.
-For example, assuming the neutrino transport is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore\cite{levermore_1984} proposed
+For example, assuming the neutrino distribution is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore\cite{levermore_1984} proposed
 \begin{equation}
@@
 \subsection{Constraints on the Moments}
-One fundamental fact about neutrinos is that they are fermions, which obey follow the Pauli exclusion principle, $f \in [0,1]$.
-As a result, the angular moments of $f$ are constrained as follows: 
+Neutrinos are fermions, and obey the Pauli exclusion principle, i.e. $f \in [0,1]$.
+As a result, the angular moments of $f$ and the Eddington factor $\chi$ are constrained as follows\cite{levermore_1984,lareckiBanach_2011,kershaw_1976,shohatTamarkin_1943}: 
 \begin{align}
@@
 \end{align}
-where $h = |\bcH|/\cJ$ is the flux factor.\cite{levermore_1984,lareckiBanach_2011,kershaw_1976,shohatTamarkin_1943}
+where $h = |\bcH|/\cJ$ is the flux factor.
 
-The inequalities in Eq.~\eqref{eq:MomentsBounds} define the realizable $\bcM$, which define a convex set in $\cJ -\bcH$ space.
+The constraints in Eq.~\eqref{eq:MomentsBounds} define realizable $\bcM$, which define a convex set in the $\cJ$-$\bcH$ space.
 As we will see later in Section \ref{se:SpacialDiscretization}, this convexity makes a constraint-preserving spatial discretization possible.
@@
 The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} deserve more attention than has been given.
-They have equal importance \rc{relative to} the inequalities in Eq.~\eqref{eq:MomentsBounds} in preserving the validity of the simulation result.
-However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all algebraic closures satisfy the Eddington factor bounds, Eq.~\eqref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine in the neutrino low occupancy limit, but not for high occupancies; Janka 1\cite{janka_1991} can be in error in both cases.
+They have equal importance relative to the inequalities in Eq.~\eqref{eq:MomentsBounds} in maintain consistency with respect to Fermi-Dirac statistics.
+
+The Eddington factor given by the algebraic closures discussed in \cite{murchikova_etal_2017} are examined in this paper as examples.
+We consider various occupancies and plot at $\cJ = 0.1$ and $\cJ = 0.9$ as examples of low occupancy and high occupancy, respectively, in Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure}.  
+As the figure shows, not all algebraic closures satisfy the Eddington factor bounds, Eq.~\eqref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine in the neutrino low occupancy limit, but not for high occupancies; Janka 1\cite{janka_1991} can be in error in both cases.
 The only algebraic closure that remains within the Eddington factor bounds among those plotted is Cernohorsky and Bludman's \cite{cernohorskyBludman_1994}.

### 2018-10-18 Documents/M1/Astronum_2018/sections/intro.tex
Backup the modification made for abstract, introduction and two-moment method section.

@@
 Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
-A solid theoretical framework for the explosion mechanism will illuminate approaches to many import questions in fundamental physics.
+A solid theoretical framework for the CCSN explosion mechanism may help answer important questions in fundamental physics.
 
-One essential part of the explosion mechanism is neutrino transport, which drives the explosion.  
-Ideally neutrino transport would be modeled by the Boltzmann transport equation, which is a partial differential equation evolving a phase-space distribution function $f$.
-Simulating the neutrino transport is equivalent to finding a solution of the Boltzmann equation for a specific domain and period with acceptable accuracy.
+One essential part of the explosion mechanism is neutrino transport.
+The neutrino energy deposition drives the CCSN explosion.  
+Ideally neutrino transport would be modeled by the Boltzmann transport equation, which is a integro-partial-differential equation evolving a phase-space distribution function $f$.
+Simulating the neutrino transport implies finding a solution of the Boltzmann equation for a specific domain and period with acceptable accuracy.
 
@@
 In the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$: the spectral particle density $\cJ$ and flux $\bcH$, respectively.
-However, the Boltzmann transport equation is a nonlinear equation.
-Its integral form, which gives the two-moment method system of equations, requires knowledge of the second angular moment $\bcK$ to close this system.
+However, the transport term in the Boltzmann transport equation is the dot product of the velocity vector and the gradient of the phase-space distribution function.
+Integrating this term with unit direction vector as the weight introduces the second angular moment $\bcK$ to the moment equations.
+Knowledge of $\bcK$ is needed to close the equation system.
 Therefore, an algebraic closure that gives an approximate value of $\bcK$ given $\cJ$ and $\bcH$ is needed.
@@
 Applying the two-moment method alone does not guarantee an affordable solution.
-To be precise, neutrinos interact with the background, and the characteristic time scale of these interactions are very small compared to the domination of the CCSN explosion. 
+To be precise, neutrinos interact with the background, and the characteristic time scale of these interactions, which can be $\sim\mathcal{O}(10^{-13})$~second, is short compared to the duration of the CCSN explosion, which $\sim\mathcal{O}(1)$~second.
 This makes the time step needed by an explicit time integrator prohibitively small. 
 On the other hand, solving the moment equations fully implicitly requires inverting globally many band-structured matrices whose sizes depend on the spatial discretization.
-Such a global inversion is both expensive and parallelization unfriendly.
+Such a global inversion is both expensive and unfriendly to parallelization.
 To circumvent these challenges, implicit-explicit (IMEX) methods are taken into consideration.
-By treating the transport terms in the two-moment equations explicitly and the collision terms implicitly, IMEX methods are subject only to a time step governed by the explicit transport terms, and the matrices to be inverted are block diagonal dominated.
-Therefore, IMEX methods require fewer time steps, and the calculation for each step is parallelizable.
+By treating the transport terms in the two-moment equations explicitly and the collision terms implicitly, IMEX methods are subject only to a time step governed by the explicit transport terms, and the matrices to be inverted are block diagonal.
+Therefore, IMEX methods require fewer time steps comparing with fully explicit method, and the calculation for each step is easily parallelizable.  
+For a non-relativistic system where the propagating speed of gravity wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.
+But for a relativistic circumstance that we have, where the gravity, fluid, and neutrino have a relativistic propagating speed, IMEX method
+balances the efficiency and cost.
 
-%\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.} 
-To employ IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac-statistics-preserving algebraic closure for closing the two-moment equations and a convex-invariant, diffusion-accurate IMEX scheme to ensure a physical result.
-Because the angular moments are confined.
-Since the neutrino distribution function is constrained ($f\in[0,1]$) by the Pauli exclusion principle, its moments as integrals of a constrained function over constrained domain ($\omega\in\bbS^{2}$) are also constrained.
-We call the moments satisfying Fermi-Dirac statistics \textit{realizable moments}.
-Hence, the algebraic closure should give a realizable $\bcK$, and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
-That's why a Fermi-Dirac statistics satisfied algebraic closure is needed.
-Then, the realizability of $\cJ$ and $\bcH$ on each time step requires a convex-invariant IMEX scheme.
+To model neutrino transport using two-moment method, two things need to be chosen carefully: an algebraic closure based on Fermi-Dirac statistic for closing the two-moment equations and a convex-invariant, diffusion-accurate IMEX scheme to ensure a physical result.
+Since the neutrino distribution function is bounded ($f\in[0,1]$) by the Pauli exclusion principle, its moments as weight integrals of a bounded function over domain $\omega\in\bbS^{2}$ are also bounded.
+We call the moments satisfying the constraints due to Fermi-Dirac statistics \textit{realizable moments}.
+The algebraic closure should give a realizable $\bcK$, and the well-posedness of the closure requires realizable $\cJ$ and $\bcH$.
+It explains why an algebraic closure based on Fermi-Dirac statistics is needed.
+Realizability of $\cJ$ and $\bcH$ after each time step requires a convex-invariant IMEX scheme.
 Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX scheme for two-moment neutrino transport.
@@
 
-\cite{gottlieb_etal_2001} showed standard IMEX scheme can't have an order higher than first without a restrict time step requirement.
+The study of moment realizability and constraint-preserving, diffusion-accurate IMEX schemes motivate this work.
+Gottlieb et al\cite{gottlieb_etal_2001} showed standard IMEX scheme with strong-stability-preserving can't have an order higher than first without a restrict time step requirement.
 To have second-order (or higher-order) accuracy, some correction steps are needed.
-Unfortunately, the correction steps can deteriorate the accuracy of the IMEX scheme in the diffusion limit and restrict the time step.
+Unfortunately, the correction steps can deteriorate the accuracy of the IMEX scheme in the diffusion limit or restrict the time step.
 To keep things simple, we focus on IMEX schemes without correction steps and require them to be high-order (second or higher order) in the streaming limit and diffusion-accurate.
 We call these IMEX schemes \textit{PD-ARS}.
-The study of moment realizability and constraint-preserving, diffusion-accurate IMEX schemes motivate this work.
 
@@
 Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct PD-ARS scheme and two PD-ARS schemes, one with second-order accuracy in the streaming limit and the other with third-order accuracy in the same limit;
-Section~\ref{se:NumericalTests} presents the results of the numerical tests, which demonstrate the properties of the PD-ARS schemes; Section~\ref{se:Conclusion} summarizes the achievements of this paper.
+Section~\ref{se:NumericalTests} presents the results of the numerical tests, which demonstrate the properties of the PD-ARS schemes; Section~\ref{se:Conclusion} summarizes the achievements of this paper and discusses future works.

### 2018-10-18 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Backup the modification made in spatial discretization section.

@@
 
-In this section we show how to use the property we introduced at the end of the previous section to construct a constraint-preserving, implicit-explicit (IMEX) scheme.
+Suppose we have an algebraic closure based on Fermi-Dirac statistic (whose Eddington factor satisfies Eq.~\eqref{eq:eddingtonFactorBounds}).
+We show how to construct a time integration which satisfies the bounds on moment after each time step in this section.
 The semi-discretization of the moment equations, Eq.~\eqref{eq:momentEquations}, results in a system of ordinary differential equations of the form
@@
 \end{equation}
-is the collection of all cell-average moments, $\vect{\cT}$ is the transport operator corresponding to the flux term, which is the first term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, and $\f{1}{\tau}\,\vect{\cQ}$ is a linear operator corresponding to the collision term, the second term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}.
+is the collection of all cell-average moments, $\vect{\cT}$ is the transport operator corresponding to the first term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, and $\f{1}{\tau}\,\vect{\cQ}$ corresponds to the collision operator, the second term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}.
 
-Since the realizable $\bcM$ define a convex set in $\cJ -\bcH$ space, convex-invariant schemes, which remain in their initial convex set, can be used to design realizability-preserving schemes for the two-moment model.
+Since the realizable $\bcM$ define a convex set in $\cJ$-$\bcH$ space, convex-invariant schemes, which remain in their initial convex set, can be used to design realizability-preserving schemes for the two-moment model.
 The following discussion shows how to construct a convex-invariant scheme.
@@
 \subsection{Standard Implicit-Explicit Scheme}
-Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form\cite{pareschiRusso_2005}
+Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form \cite{pareschiRusso_2005}
 \begin{align}
@@
 \end{align}
-where  $(\tilde{a}_{ij})$ and $(a_{ij})$ are coefficients of the $i$th-stage and they are the elements of matrices $\tilde{A}$ and $A$, respectively, and the vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weight vectors.
+where  $(\tilde{a}_{ij})$ and $(a_{ij})$ are coefficients of the $i$-th stage and they are the elements of matrices $\tilde{A}$ and $A$, respectively.
+The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weight vectors.
 These coefficients and weights have to satisfy certain condition for an accurate, convergent and stable scheme.

### 2018-10-18 Documents/M1/Astronum_2018/sections/Conclusion.tex
Backup the modification in time integration section.

@@
 We have developed IMEX schemes for two-moment neutrino transport in \texttt{thornado} that respect Fermi-Dirac statistics.
-The schemes employ algebraic closure based on Fermi-Dirac statistics, a first-order discontinuous Galerkin method, the simple Lax-Friedrichs flux, and convex-invariant time integration to maintain point-wise realizability of the moments.
+The schemes employ algebraic closure based on Fermi-Dirac statistics, a third-order discontinuous Galerkin method, the Lax-Friedrichs flux, and convex-invariant time integration to maintain cell-average realizability of the moments.
 Since the realizability-preserving property is obtained from the convexity of the realizable domain, it's possible to construct a scheme with a high-order DG method.

### 2018-10-18 Documents/M1/Astronum_2018/sections/Numerical.tex
Backup the modification in time integration section.

@@
 The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the convex-invariance of PD-ARS schemes schemes.
-All the tests in this subsection were constructed with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $.
+All the tests in this subsection were constructed with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $, using the DG scheme we present in \cite{chu_etal_2018}.
 
@@
 \subsubsection{Sine Wave Streaming}
-The sine wave streaming test is designed for the steaming dominated regime, with $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
-A periodic domain with length=1 is used and the initial condition is $\cJ = \bcH =$ a spatial sine wave function.
+The sine wave streaming test is designed for the steaming dominated regime, i.e. $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
+A periodic domain of unit length is used and the initial condition is $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$.
 We evolve the test until the sine wave has completed 10 crossings of the domain.
@@
 
-In the streaming limit, PD-ARS scheme limit to its explicit part, SSPRK2 and SSPRK3, respectively.
-That's why the absolute errors of PD-ARS and SSPRK are indistinguishable on the plot.
+In the streaming limit, the PD-ARS schemes limit to their explicit part, SSPRK2 and SSPRK3, respectively.
+Therefore, the absolute errors of PD-ARS and SSPRK are indistinguishable on the plot.
 
@@
 This test, adapted from \cite{skinnerOstriker_2013}, is designed for absorption-dominated regimes, with $\sigma_{\Scatt} = 0$ and $f_0 = 0$, which results in exponential damping of the wave amplitude.
-A periodic domain with length=1 and an initial condition with $\cJ = \bcH =$ a spacial sine wave function is used.
+A periodic domain of unit length and an initial condition with $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$ is used.
 The amplitude of the analytical solution decreases as $e^{-\sigma_{\Ab} t}$.
@@
 SSP2332, a second-order scheme, displays second-order convergence.
-PD-ARS schemes converge with a first-order convergence rate given the price paid for convex-invariance.
+PD-ARS schemes converge with a first-order convergence rate: the price paid for the convex-invariant property.
 \begin{figure}[h]
@@
 \subsubsection{Sine Wave Diffusion}
-The last test with known smooth solution,adopted from \cite{radice_etal_2013}, is the sine wave diffusion test with $\sigma_{\Ab} = 0, f_0 = 0$.
-A periodic domain with $D=\{x:x\in[-3,3]\}$ and an initial condition with $\cJ_{0}$ = a spatial sine wave function and $\cH =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ}{x}$ is used.
+The last test with known smooth solution, adopted from \cite{radice_etal_2013}, is the sine wave diffusion test, i.e. $\sigma_{\Ab} = 0$ and $f_0 = 0$.
+A periodic domain with $D=\{x:x\in[-3,3]\}$ and an initial condition with $\cJ_{0} = 0.5+0.49\times\sin\big(\f{\pi\,x}{3}\big)$ and $\cH_{0} =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}$ is used.
 The analytic solution is given by $\cJ = \cJ_{0} \times e^{-\f{\pi^2 t}{27\sigma_{\Scatt}}}$ and $\cH = (3\,\sigma_{\Scatt})^{-1}\pd{\cJ}{x}$.
@@
 Then the amplitude of the sine wave has been reduced by a factor $e^{-\pi^{2}/27}\approx0.694$ for all values of $\sigma_{\Scatt}$. 
-Figure~\ref{fig:SineWaveDiffusionJ} shows the convergence.
+Figure~\ref{fig:SineWaveDiffusionJ} shows the error versus $N$.
 SSP2332 and PD-ARS schemes display third-order accuracy for the number density, $\cJ$, and second-order accuracy for $\cH_{x}$, and their errors are difficult to distinguish.
-PD-ARS with SSP2332 behaves as good as SSP2332 in the diffusion region but requires 1/3 less implicit solvers.
+PD-ARS with SSPRK2 behaves as good as SSP2332 in the diffusion region but requires 1/3 less implicit solvers.
 \begin{figure}[h]
@@
 \subsection{Neutrino Stationary State Test} \label{se: Neutrino Stationary State Test}
-Next we consider a more ``realistic'' test: two-dimensional neutrino transport with emission, absorption, and elastic scattering in a stationary ``realistic'' background.
+Next we consider a more ``realistic'' test: two-dimensional neutrino transport with emission, absorption, and elastic scattering through a stationary background.
 This is designed to test the realizability-preserving properties of the PD-ARS schemes.
@@
 We take 10 energy groups from 0~MeV to 300~MeV and initialize the neutrino number density $\cJ$ and flux density $\bcH$ both at zero(arbitrarily small).
-For the realizability-preserving test, CB closure with PD-ARS schemes, SSP2332, a scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and a scheme proposed by McClarren et al \cite{mcclarren_etal_2008} are all applied.
-Only PD-ARS schemes produce realizability-preserving results and evolve the model to a stable state.
+For the realizability-preserving test, we employ the CB closure with PD-ARS schemes, SSP2332, a scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and a scheme proposed by McClarren et al \cite{mcclarren_etal_2008} are all applied.
+Only PD-ARS schemes produce realizability-preserving results and evolve the model to a steady state.
+The other schemes crashed immediately after several steps.
 The realizability-preserving plot and the evolve process of PD-ARS schemes are given in Figure~\ref{fig:NeutrinoStationaryTestEvolve}.

### 2018-10-18 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Backup the modification in time integration section.

@@
 The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weight vectors.
-These coefficients and weights have to satisfy certain condition for an accurate, convergent and stable scheme.
+These coefficients and weights have to satisfy certain condition for an accurate and consistent scheme.
 For instance, to have second-order temporal accuracy, the following conditions are required:
@@
     where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix.
-    \item Less than four stages ($s\le3$).
+    \item Less than five stages ($s\le4$).
     \item Globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. (GSA)
@@
 \subsubsection{PD-ARS with SSPRK2}
-Here we give a family of PD-ARS with SSPRK2 in the standard double Butcher tableau form: explicit tableau on the left ($\tilde{A}$), implicit tableau on the right ($A$):
+Here we give the optimized PD-ARS with SSPRK2 in the standard double Butcher tableau form: explicit tableau on the left ($\tilde{A}$), implicit tableau on the right ($A$):
 \begin{equation}
@@
   	1 & 0 & 1            & 0            \\
-  	1 & 0 & 1/2-\epsilon & 1/2+\epsilon \\ \hline
-  	  & 0 & 1/2-\epsilon & 1/2+\epsilon
+  	1 & 0 & 1/2 & 1/2 \\ \hline
+  	  & 0 & 1/2 & 1/2
   \end{array}
 \end{equation}
-and $\epsilon \in [0, 1/2)$.
-For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$.
-The optimized scheme ($c_{\mbox{\tiny Sch}}= 1$) is given by $\epsilon = 0$.
-We chose $\epsilon = 0.1$ for the numerical test in Section~\ref{se:NumericalTests}.
-
+For this scheme, $c_{\mbox{\tiny Sch}}= 1$ and only two implicit solver are needed for each time step.
 \subsubsection{PD-ARS with SSPRK3}
@@
 For this schemes, $c_{\mbox{\tiny Sch}}= 1$.
+Three implicit solver are taken for each time step.
+Since PD-ARS with SSPRK3 is as accurate as PD-ARS with SSPRK2 in collision involved region, see Section~\ref{se:NumericalTests} for the plots, it may not offer any advantage.

### 2018-10-19 Documents/M1/Astronum_2018/sections/Numerical.tex
Buckup the latest changes on M1/Astronum_2018

@@
 PD-ARS with SSPRK2 behaves as good as SSP2332 in the diffusion region but requires 1/3 less implicit solvers.
+
 \begin{figure}[h]
@@
 This test is constructed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction.
-We take 10 energy groups from 0~MeV to 300~MeV and initialize the neutrino number density $\cJ$ and flux density $\bcH$ both at zero(arbitrarily small).
+We take 10 energy groups from 0~MeV to 300~MeV and initialize the neutrino number density $\cJ$ and flux density $\bcH$ \rc{both at zero(arbitrarily small) give the number}.
 For the realizability-preserving test, we employ the CB closure with PD-ARS schemes, SSP2332, a scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and a scheme proposed by McClarren et al \cite{mcclarren_etal_2008} are all applied.
@@
 The realizability-preserving plot and the evolve process of PD-ARS schemes are given in Figure~\ref{fig:NeutrinoStationaryTestEvolve}. 
+\rc{More details of what's plotted.}
 
@@
     \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
-    \caption{Realizability (left column), the number density $\cJ$ versus radius (center column), and the flux factor $|\bcH|/\cJ$ versus radius (right column) at t = 0.01~ms ,0.35~ms and 5.0~ms for the neutrino stationary state test.
-For the realizability plots, the light blue area highlights the realizability domain, and the black lines define its boundary.
+    \caption{Realizability (left column) \rc{Explain the realizability difference(light blue and light red)}, the number density $\cJ$ versus radius (center column), and the flux factor $|\bcH|/\cJ$ versus radius (right column) at t = 0.01~ms ,0.35~ms and 5.0~ms for the neutrino stationary state test.
+For the realizability plots, the light blue area highlights the realizable domain, and the black lines define its boundary.
 Each $\bcM=(\cJ,\bcH)^{T}$ state is marked by a red dot.

### 2018-10-19 Documents/M1/Astronum_2018/sections/SpatialDiscretization.tex
Buckup the latest changes on M1/Astronum_2018

\section{Spatial Discretization}\label{se:SpacialDiscretization}
Here we use the finite-volume/first-order discontinuous Galerkin method to illustrate how the closure affects the realizability-preserving property of the scheme.
To simply the illustration, let's focus on one-dimension uniform mesh on Cartesian coordinates.
We divide the spatial domain $D$ evenly into $N$ cells and denote the $i$th cell as $\bK_{i}$ with $i = 1,\ldots,N$, so that
\begin{equation*}
D = \cup_{i = 1}^{N} \bK_{i} \quad \text{with} \quad
  \bK_{i}=\{\,x : x\in(x_{i-1/2}, x_{i+1/2})\}.
\end{equation*}
Each of the cells has a length, $|\dx|$ and $|\dx| = D/N = \int_{\bK}d\vect{x}$.
The cell-average moments:
\begin{equation}
\bcM_{i} = \dfrac{1}{|\dx|} \int_{\bK_i}\bcM dx.
\end{equation}
Integrating Eq.~\eqref{eq:momentEquations} for each cell $\bK_{i}$ given
\begin{equation}
\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{|\dx|} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
\label{eq:SemiDiscretizatedMomentEquation}
\end{equation}
where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is the numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the integrated collision term.
In this paper we use the simple Lax-Friedrichs flux, given by
\begin{equation}
  \widehat{\bcF}_{LF}(\vect{\cM}_{a},\vect{\cM}_{b})
  =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big).
  \label{eq:Lax-Friedrichs flux}
\end{equation}
Therefore, by treating the flux term explicitly and the collision term implicitly, we have
\begin{align}
\bcM_{i}^{n+1} = \widetilde{\bcM}^{n}_{i} + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i}),
\label{eq:MomentIMEX}
\end{align}
where we define
\begin{align}
\widetilde{\bcM}^{n}_{i} 
& = \bcM_{i}^{n} - \dfrac{\dt}{|\dx|} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
& = (1-\beta)\bcM_{i}^{n} + \beta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right],
\label{eq:widetildeM}
\end{align}
and $\beta := \frac{\dt}{|\dx|}$.

Assume $\bcM_{i}^{n}$ is realizable for all $i$. 
For Eq.~\eqref{eq:MomentIMEX}, Lemma 3 in \cite{chu_etal_2018} says that $\bcM^{n+1}_{i}$ is realizable given $\f{\dt}{\tau} > 0$ and provided that $\widetilde{\bcM}^{n}_{i}$ is realizable.
Substituting the Lax-Friedrichs flux, Eq.~\eqref{eq:Lax-Friedrichs flux}, in Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, $\widetilde{\bcM}^{n}_{i}$ becomes a convex combination of $\bcM_{i}^{n}$ and the square bracket in Eq.~\eqref{eq:widetildeM} if $\beta \in [0,1]$.
$\widetilde{\bcM}^{n}_{i}$ is realizable if $\beta \in [0,1]$ and the term in square brackets is realizable.
Given Lemma 2 in \cite{chu_etal_2018}, the term in square brackets is realizable if $\cJ$, $\bcH$ and $\bcK$ are realizable.
In other words, realizability of the term in square brackets depends on the algebraic closure.
If the closure satisfies Eq.~\eqref{eq:eddingtonFactorBounds},
$\bcM^{n+1}_{i}$ is realizable provided $\beta \in [0,1]$.
Note that $\beta \leq 1$ is also the CFL condition of the Forward-Euler method applied to a transport-only Boltzmann equation.

### 2018-10-19 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Buckup the latest changes on M1/Astronum_2018

@@
 \subsection{Standard Implicit-Explicit Scheme}
-Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form \cite{pareschiRusso_2005}
+Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form \cite{pareschiRusso_2005}: 
 \begin{align}
@@
 where  $(\tilde{a}_{ij})$ and $(a_{ij})$ are coefficients of the $i$-th stage and they are the elements of matrices $\tilde{A}$ and $A$, respectively.
-The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weight vectors.
+The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weights in the assembly step in Eq.~\eqref{imexIntermediate}.
 These coefficients and weights have to satisfy certain condition for an accurate and consistent scheme.
@@
 \subsection{A Constraint-Preserving Implicit-Explicit Scheme}
-Beyond the accuracy requirement, a convex-invariant IMEX scheme has extra constraints to satisfy.
-The problem left is to find the additional constraints on $(\tilde{a}_{ij})$, $(a_{ij})$, $\tilde{w}_{i}$, and $w_{i}$.
+Beyond the accuracy requirement, a convex-invariant IMEX scheme must satisfy additional constraints.
+Our idea is finding the constraints on $a_{ij}$, $\tilde{a}_{ij}$, $\tilde{w}_{i}$, and $w_{i}$ that enable each $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ be convex combination of realizable moments:
+
 Following Hu et al\cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten as
@@
 \end{equation}
-with $c_{ij}$ and $\hat{c}_{ij}$ be given by $a_{ij}$ and $\tilde{a}_{ij}$.
+with $c_{ij}$ and $\hat{c}_{ij}$ be some expression of $a_{ij}$ and $\tilde{a}_{ij}$.
+By requiring the IMEX scheme be globally stiffly accurate (GSA), i.e. $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i}$ for $i=1,\ldots,s$, $\vect{u}^{n+1} = \vect{u}^{(s)}$.
+Using those Lemma proved in \cite{chu_etal_2018}, we can find those constraints that $c_{ij}$ and $\hat{c}_{ij}$ (or $a_{ij}$ and $\tilde{a}_{ij}$) need to satisfy to ensure $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ be realizable.
 
-It can be proven that the conditions we need for a simple convex-invariant IMEX scheme are: \cite{chu_etal_2018}
+\rc{Diffusion accurate detail...}
+
+\rc{Only ARS and define ARS...}
+
+Here is list of our constraints \cite{chu_etal_2018}:
 \begin{enumerate}

### 2018-10-19 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Buckup the latest changes on M1/Astronum_2018

@@
-\section{Two-Moment Model}\label{se:Two-MomentModel}
+\section{Two-Moment Model}
+\label{se:Two-MomentModel}
 
@@
 They have equal importance relative to the inequalities in Eq.~\eqref{eq:MomentsBounds} in maintain consistency with respect to Fermi-Dirac statistics.
-
 The Eddington factor given by the algebraic closures discussed in \cite{murchikova_etal_2017} are examined in this paper as examples.
-We consider various occupancies and plot at $\cJ = 0.1$ and $\cJ = 0.9$ as examples of low occupancy and high occupancy, respectively, in Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure}.  
+We consider various occupancies and plot $\cJ = 0.1$ and $\cJ = 0.9$ as examples for low and high occupancy, respectively, in Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure}.
 As the figure shows, not all algebraic closures satisfy the Eddington factor bounds, Eq.~\eqref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine in the neutrino low occupancy limit, but not for high occupancies; Janka 1\cite{janka_1991} can be in error in both cases.
 The only algebraic closure that remains within the Eddington factor bounds among those plotted is Cernohorsky and Bludman's \cite{cernohorskyBludman_1994}.
-
 Though Levermore closure and Minerbo closure don't conserve the bounds in the high occupancy limit, they are widely used: {O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} use Minerbo closure, and Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016} use Levermore clsoure.
+\rc{Add more discussion.}
 

### 2018-10-19 Documents/M1/Astronum_2018/sections/intro.tex
Buckup the latest changes on M1/Astronum_2018

@@
 Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
-A solid theoretical framework for the CCSN explosion mechanism may help answer important questions in fundamental physics.
+A solid theoretical framework for the CCSN explosion mechanism may help answer important questions in fundamental physics.\rc{[references]}
 
@@
 
-However, solving the multi-dimensional Boltzmann transport equation is expensive.
-To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted.
+However, solving the multi-dimensional Boltzmann transport equation is expensive.\rc{[references]}
+To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted.\rc{[references]}
 In the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$: the spectral particle density $\cJ$ and flux $\bcH$, respectively.
@@
 Therefore, IMEX methods require fewer time steps comparing with fully explicit method, and the calculation for each step is easily parallelizable.  
-For a non-relativistic system where the propagating speed of gravity wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.
+For a non-relativistic system where the propagating speed of gravity wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.\rc{[references]}
 But for a relativistic circumstance that we have, where the gravity, fluid, and neutrino have a relativistic propagating speed, IMEX method

### 2018-10-22 Documents/M1/Astronum_2018/sections/Acknowledge.tex
Updated Astronum_2018.

@@
 This material is based, in part, upon work supported by the U.S. Department of Energy, Office of Science, Office of Advanced Scientific Computing Research.
-Eirik Endeve and Anthony Mezzacappa acknowledge support from the National Science Foundation under group NSF-GP-... and from the UT-ORNL Joint Institute for Computational Sciences.
+Eirik Endeve and Anthony Mezzacappa acknowledge support from the National Science Foundation under group \rc{NSF-GP-... (number?)} and from the UT-ORNL Joint Institute for Computational Sciences.

### 2018-10-22 Documents/M1/Astronum_2018/sections/Conclusion.tex
Buckup the latest changes on M1/Astronum_2018
Updated Astronum_2018.

@@
 The one with SSPRK2 is second-order accurate and strong-stability preserving in the streaming limit while the other with SSPRK3 is third-order accurate.
-Their properties, both accuracy and convex-invariance, were demonstrated with numerical tests.
+Their accuracy were demonstrated with some problems with known smooth solutions in streaming, absorption, ans scattering-dominated regimes.
+Neutrino transport test with neutrino emission, absorption, elastic scattering, and stationary background, was designed to test the convex-invariance of our PD-ARS schemes.
+The neutrino stationary state test shows that it's necessary to combine an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration for a solid CCSN simulation.
 

### 2018-10-22 Documents/M1/Astronum_2018/sections/Numerical.tex
Updated Astronum_2018.

--- 2018-10-18 Documents/M1/Astronum_2018/sections/Numerical.tex
@@
   \centerline{\includegraphics[width=1.2\textwidth]{figures/SineWaveDiffusion}}
-%  \begin{tabular}{cc}
-%    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionJ}
-%    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionH}
-%  \end{tabular}
    \caption{Absolute error for the number density $\cJ$ (left) and the number flux $\cH_{x}$ (right) versus number of elements for the sine wave diffusion test.
@@
 This is designed to test the realizability-preserving properties of the PD-ARS schemes.
-Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities we used.
+Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities, which are adopted from \cite{Bruenn_1985}, we used.
 This test is constructed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction.
-We take 10 energy groups from 0~MeV to 300~MeV and initialize the neutrino number density $\cJ$ and flux density $\bcH$ both at zero(arbitrarily small).
+We take 10 energy groups from 0~MeV to 300~MeV and initialize the neutrino number density $\cJ = 10^{-99}$ and flux density $\bcH=0$.
 For the realizability-preserving test, we employ the CB closure with PD-ARS schemes, SSP2332, a scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and a scheme proposed by McClarren et al \cite{mcclarren_etal_2008} are all applied.
@@
 The other schemes crashed immediately after several steps.
-The realizability-preserving plot and the evolve process of PD-ARS schemes are given in Figure~\ref{fig:NeutrinoStationaryTestEvolve}.
+The realizability-preserving plots are given in the first column of Figure~\ref{fig:NeutrinoStationaryTestEvolve} at $t=0.01$~ms, 0.35~ms and 5.0~ms.
+With each states be marked as a red dot in $\cJ$-$\bcH$ space and the realizable domain be light blue region, they show that all the states achieved in the simulation with PD-ARS schemes are realizable.
+The second and third column of Figure~\ref{fig:NeutrinoStationaryTestEvolve} plot the corresponding the neutrino number density $\cJ$ and flux factor $|\bcH|/\cJ$ in radius.
+These plots show how the neutrinos generate and transport in the simulation.
 
@@
     \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
-    \caption{Realizability (left column), the number density $\cJ$ versus radius (center column), and the flux factor $|\bcH|/\cJ$ versus radius (right column) at t = 0.01~ms ,0.35~ms and 5.0~ms for the neutrino stationary state test.
-For the realizability plots, the light blue area highlights the realizability domain, and the black lines define its boundary.
-Each $\bcM=(\cJ,\bcH)^{T}$ state is marked by a red dot.
+    \caption{Realizability (left column, light blue domain for $f \in [0,1]$ with black-solid-line as boundary, light red for $f\geq 0$ with thin-red-solid-line as boundary) , the number density $\cJ$ versus radius (center column), and the flux factor $|\bcH|/\cJ$ versus radius (right column) at t = 0.01~ms ,0.35~ms and 5.0~ms for the neutrino stationary state test.
+For the realizability plots, each $\bcM=(\cJ,\bcH)^{T}$ state is marked by a red dot, which all sites in the light blue domain.
 The results of PD-ARS with SSPRK2 and PD-ARS with SSPRK3 are indistinguishable in these plots.}

### 2018-10-22 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Updated Astronum_2018.

@@
 
-\subsection{A Constraint-Preserving Implicit-Explicit Scheme}
+\subsection{Constraint-Preserving Implicit-Explicit Schemes}
 Beyond the accuracy requirement, a convex-invariant IMEX scheme must satisfy additional constraints.
@@
 
-\rc{Diffusion accurate detail...}
+\subsection{Diffusion Accurate, Constraint-Preserving Implicit-Explicit Schemes}
+Diffusion accurate is the other property the time integration should have.
+In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$.
+The moment behavior are governed by (e.g., \cite{jinLevermore_1996})
+\begin{equation}
+  \pd{\cJ}{t} + \nabla\cdot\vect{\cH} = 0
+  \quad\text{and}\quad
+  \vect{\cH} = - \tau\,\nabla\cdot\vect{\cK}.  
+  \label{eq:diffusionLimit}
+\end{equation}
+In the context of IMEX schemes, the above relationships imply that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold. 
+We derived the diffusion accurate condition in \cite{chu_etal_2018} and proved that only type~ARS (investigated by Ascher, Ruuth, and Spiteri\cite{ascher_etal_1997}) IMEX schemes can be our candidates.
 
-\rc{Only ARS and define ARS...}
+For type~ARS, $a_{i1} = 0$ for $i=1,\ldots,s$.
+$c_{ij}$ and $\hat{c}_{ij}$ are given by
+    \begin{equation}
+     \begin{aligned}
+      c_{i0} &= 1-\sum_{j=2}^{i-1}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad &
+      c_{ij} &= \sum_{l=j}^{i-1}a_{il}b_{lj}, \\
+      \tilde{c}_{i0} &= \tilde{a}_{i1}+\sum_{j=2}^{i-1}a_{ij}\tilde{b}_{j1}, \quad &
+      \tilde{c}_{ij} &= \tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj},  
+     \end{aligned}
+     \label{eq:positivityCoefficientsARS}
+    \end{equation}
+    \begin{equation}
+      b_{ii} = \f{1}{a_{ii}}, \quad
+      b_{ij} = -\f{1}{a_{ii}}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad
+      \tilde{b}_{ij} = -\f{1}{a_{ii}}\Big(\tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}\Big).  
+    \end{equation}
+    Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.
 
-Here is list of our constraints \cite{chu_etal_2018}:
+Combining the conditions we have, we aim to find type~ARS IMEX scheme with.
 \begin{enumerate}
@@
     \begin{align}
-      &a_{i1} = 0, \quad \text{for} \quad i=1,\ldots,s, \nonumber \\
       &a_{ii}>0, \quad c_{i0},\tilde{c}_{i0}\ge0, \quad \text{for} \quad i=2,\ldots,s, \nonumber \\
@@
                   j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
-    And $c_{ij}$ and $\hat{c}_{ij}$ be given by
-    \begin{equation}
-     \begin{aligned}
-      c_{i0} &= 1-\sum_{j=2}^{i-1}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad &
-      c_{ij} &= \sum_{l=j}^{i-1}a_{il}b_{lj} \\
-      \tilde{c}_{i0} &= \tilde{a}_{i1}+\sum_{j=2}^{i-1}a_{ij}\tilde{b}_{j1}, \quad &
-      \tilde{c}_{ij} &= \tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}.  
-     \end{aligned}
-     \label{eq:positivityCoefficientsARS}
-    \end{equation}
-    \begin{equation}
-      b_{ii} = \f{1}{a_{ii}}, \quad
-      b_{ij} = -\f{1}{a_{ii}}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad
-      \tilde{b}_{ij} = -\f{1}{a_{ii}}\Big(\tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}\Big).  
-    \end{equation}
-    Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.
     \item Well-behaved in the diffusion limit:
@@
     \item Less than five stages ($s\le4$).
-    \item Globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. (GSA)
+    \item Globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. 
 \end{enumerate}  

### 2018-10-22 Documents/M1/Astronum_2018/sections/intro.tex
Updated Astronum_2018.

--- 2018-10-18 Documents/M1/Astronum_2018/sections/intro.tex
@@
 Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
-A solid theoretical framework for the CCSN explosion mechanism may help answer important questions in fundamental physics.
+A solid theoretical framework for the CCSN explosion mechanism may help answer important questions in fundamental physics.\cite{janka_etal_2007}
 
 One essential part of the explosion mechanism is neutrino transport.
-The neutrino energy deposition drives the CCSN explosion.  
-Ideally neutrino transport would be modeled by the Boltzmann transport equation, which is a integro-partial-differential equation evolving a phase-space distribution function $f$.
+The neutrino energy deposition drives the CCSN explosion.\cite{mezzacappaMesser_1999}
+Ideally neutrino transport would be modeled by the Boltzmann transport equation, which is a integro-partial-differential equation evolving a phase-space distribution function $f$.\cite{Bruenn_1985}
 Simulating the neutrino transport implies finding a solution of the Boltzmann equation for a specific domain and period with acceptable accuracy.
@@
 However, solving the multi-dimensional Boltzmann transport equation is expensive.
-To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted.
+To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted.\cite{mezzacappaMesser_1999}
 In the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$: the spectral particle density $\cJ$ and flux $\bcH$, respectively.
@@
 Therefore, IMEX methods require fewer time steps comparing with fully explicit method, and the calculation for each step is easily parallelizable.  
-For a non-relativistic system where the propagating speed of gravity wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.
+For a non-relativistic system where the propagating speed of gravity wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.\cite{cernohorskyVanWeert_1992}(read ?)
 But for a relativistic circumstance that we have, where the gravity, fluid, and neutrino have a relativistic propagating speed, IMEX method
@@
 Section~\ref{se:NumericalTests} presents the results of the numerical tests, which demonstrate the properties of the PD-ARS schemes; Section~\ref{se:Conclusion} summarizes the achievements of this paper and discusses future works.
+
+\rc{Reference check}

### 2018-10-23 Documents/Euler/dgEulerGR.tex
Modified source-term time-step derivation and added proof of validity of using nodal points for higher-order methods

@@
     &\hspace{15em}+\f{\eta_{i}}{2}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]\nonumber\\
-    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\bH^{-}\left(\ol{\bU}^{n}_{i+1},\alpha_{\iph}\right)+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\bH^{+}\left(\ol{\bU}^{n}_{i-1},\alpha_{\imh}\right),\label{Eq:ConvComb}
+    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\ol{\bH}^{-}\left(\ol{\bU}^{n}_{i+1},\alpha_{\iph}\right)+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\ol{\bH}^{+}\left(\ol{\bU}^{n}_{i-1},\alpha_{\imh}\right),\label{Eq:ConvComb}
 \end{align}
@@
 \begin{equation}\label{Eq:Hpm}
-    \bH^{\pm}\left(\ol{\bU},\alpha\right)\equiv\ol{\bU}\pm\f{1}{\alpha}\,\bF\left(\ol{\bU}\right).
+    \ol{\bH}^{\pm}\left(\ol{\bU},\alpha\right)\equiv\ol{\bU}\pm\f{1}{\alpha}\,\bF\left(\ol{\bU}\right).
 \end{equation}
 
-The proof that $\bH^{\pm}\in\cG$ is given in \citet{Qin2016}.
+The proof that $\ol{\bH}^{\pm}\in\cG$ is given in \citet{Qin2016}.
 Therefore, we see that with a restriction on $\alpha_{i\pm\f{1}{2}}$ that \eqref{Eq:ConvComb} is a convex combination.
@@
 \subsection{Curvilinear Coordinates}
-NOTE: We assume a conformally-flat, time-independent spatial three-metric.
+NOTE: We assume a conformally-flat, time-independent spatial three-metric:
+\begin{equation}
+    \gamma_{ij}\left(x^{k},t\right)\longrightarrow\psi^{4}\left(x^{k}\right)\,\ol{\gamma_{ii}}\left(x^{k}\right),
+\end{equation}
+where $\psi\left(x^{k}\right)$ is the conformal factor and $\ol{\gamma}_{ii}$ is the flat-space metric.
 
@@
 \begin{equation}
-    P^{kj}=S^{k}\,v^{j}+p\,\gamma^{kj}=\gamma^{kj}\left[S_{a}\,v^{a}+p\right].
+    P^{kj}=S^{k}\,v^{j}+p\,\gamma^{kj}=\gamma^{k\ell}\,S_{\ell}\,v^{j}+p\,\gamma^{kj}=\gamma^{k\ell}\,S_{\ell}\,v^{j}+p\,\gamma^{k\ell}\,\delta^{j}_{~\ell}=\gamma^{k\ell}\left(S_{\ell}\,v^{j}+p\,\delta^{j}_{~\ell}\right).
+\end{equation}
+Since the spatial three-metric is diagonal we must have that $\ell=k$. We can therefore simplify further:
+\begin{equation}
+    P^{kj}=\gamma^{kk}\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)=\f{1}{\gamma_{kk}}\,\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)=\f{1}{\left(h_{k}\right)^{2}}\,\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)
+\end{equation}
+For the pressure-tensor sum, we then have:
+\begin{equation}\label{Eq:PressureTensorSum}
+    P^{kj}\,\p_{1}\,\gamma_{kj}=P^{kk}\,\p_{1}\,\gamma_{kk}=P^{kk}\,\p_{1}\left(h_{k}\right)^{2}=2\,P^{kk}\,h_{k}\,\p_{1}\,h_{k}=\f{2}{h_{k}}\left(S_{k}\,v^{k}+p\right)\,\p_{1}\,h_{k}.
 \end{equation}
@@
 
-Before continuing, we show that the introduction of the metric doesn't affect the translation between $\cG_{p}$ and $\cG$...\sd{Need to do this}
+Before continuing, we show that the introduction of the metric doesn't affect the translation between $\cG_{p}$ and $\cG$...\sd{I've shown this, just need to TeX it up}
 
@@
     &=\ve\left\{\ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
-    &=\ve\,\bH_{1}+\left(1-\ve\right)\bH_{2},
+    &=\ve\,\ol{\bH}_{1}+\left(1-\ve\right)\ol{\bH}_{2},
 \end{align}
@@
 \begin{equation}
-    \bH_{1}\equiv \ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right],
+    \ol{\bH}_{1}\equiv \ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right],
 \end{equation}
 \begin{equation}
-    \bH_{2}\equiv\ol{\bU}^{n}_{i}+\f{\Delta t_{i}}{1-\ve}\,\ol{\bQ}^{n}_{i},
+    \ol{\bH}_{2}\equiv\ol{\bU}^{n}_{i}+\f{\Delta t_{i}}{1-\ve}\,\ol{\bQ}^{n}_{i},
 \end{equation}
@@
 
-We proceed by focusing on each term individually, starting with the numerical flux term, $\bH_{1}$.
+We proceed by focusing on each term individually, starting with the numerical flux term, $\ol{\bH}_{1}$.
 
 \subsubsection{Numerical flux term}
-We have to show that $\bH_{1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\bH_{1}$:
+We have to show that $\ol{\bH}_{1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\ol{\bH}_{1}$:
 \begin{align}
@@
 \end{align}
-All of the terms in square brackets are similar to the $\bH$ quantities in \citet{Qin2016}, and are therefore in $\cG$.
+All of the terms in square brackets are similar to the $\ol{\bH}$ quantities in \citet{Qin2016}, and are therefore in $\cG$.
 It can easily be seen that the sum of the coefficients is unity.
@@
 \subsubsection{Source term}
-For this section we drop the subscript $i$ and the superscript $n$. We have to show that $\bH_{2}\in\cG$, where
+For this section we drop the subscript $i$ and the superscript $n$. We have to show that $\ol{\bH}_{2}\in\cG$, where
 \begin{equation}
-    \bH_{2}=\begin{pmatrix}\ol{D}\\ \ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}} \\ \ol{\tau}\end{pmatrix},\hspace{1em}\left(H_{2}\right)_{1}>0,\hspace{1em}\left(H_{2}\right)_{3}+\left(H_{2}\right)_{1}>\sqrt{\left(H_{2}\right)_{1}\left(H_{2}\right)_{1}+\left(H_{2}\right)_{2}\left(H_{2}\right)^{2}}.
+    \ol{\bH}_{2}=\begin{pmatrix}\ol{D}\\ \ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}} \\ \ol{\tau}\end{pmatrix},\hspace{1em}\left(\ol{H}_{2}\right)_{1}>0,\hspace{1em}\left(\ol{H}_{2}\right)_{3}+\left(\ol{H}_{2}\right)_{1}>\sqrt{\left(\ol{H}_{2}\right)_{1}\left(\ol{H}_{2}\right)_{1}+\left(\ol{H}_{2}\right)_{2}\left(\ol{H}_{2}\right)^{2}}.
 \end{equation}
 
-It is clear that the first requirement for $\bH_{2}$ is met, i.e. $\ol{D}>0$. The second requirement is:
+It is clear that the first requirement for $\ol{\bH}_{2}$ is met, i.e. $\ol{D}>0$. The second requirement is:
 \begin{align}
@@
 \begin{equation}
-    \f{4\left(\ol{S}_{1}\right)^{2}}{\ol{\gamma_{11}}}a-4\,a\left(\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}\right)=4\,\ol{S}_{1}\,\ol{S}^{1}\,a-4\,a\ol{D}^{2}-4\,a\,\ol{S}_{1}\,\ol{S}^{1}=-4\,a\,\ol{D}^{2}<0.
+    b^{2}-4\,a\,c=\f{4\left(\ol{S}_{1}\right)^{2}}{\ol{\gamma_{11}}}a-4\,a\left(\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}\right)=4\,\ol{S}_{1}\,\ol{S}^{1}\,a-4\,a\ol{D}^{2}-4\,a\,\ol{S}_{1}\,\ol{S}^{1}=-4\,a\,\ol{D}^{2}<0.
 \end{equation}
@@
 
-The solutions of this quadratic equation are:
+This time we want to make sure that our function has at least one real root. We still have that $a>0$, so now we check if $b^{2}-4\,a\,c'>0$:
+\begin{equation}
+    b^{2}-4\,a\,c'=\f{4\left(\ol{S}_{1}\right)^{2}}{\ol{\gamma_{11}}}a-4\,a\left(\ol{S}_{1}\,\ol{S}^{1}-\ol{\tau}^{2}-2\,\ol{D}\,\ol{\tau}\right)=4\,a\,\ol{\tau}\left(\ol{\tau}+2\,\ol{D}\right).
+\end{equation}
+Since $\ol{\tau}\geq0$, we must have that $\ol{\tau}>-2\,\ol{D}$. But, from condition two for $\ol{\bH}_{2}$ we have that $\ol{\tau}>-\ol{D}$, so this condition is automatically satisfied.
+
+The solutions to this quadratic equation are:
 \begin{align}
@@
     &=\f{1}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\left(\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}\right)}\right]\\
-    &=\f{2\left(1-\ve\right)}{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\left(\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}\right)}\right].
+    &=\f{2\left(1-\ve\right)}{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\left(\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}\right)}\right]\\
+    &=\f{2\left(1-\ve\right)}{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\,\ol{\tau}\left(\ol{\tau}+2\,\ol{D}\right)}\right].
 \end{align}
-We see that we must have that $\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}>0\implies\ol{\tau}>-2\,\ol{D}$.
-But, since we know that from the second condition of $\bH_{2}$ that $\ol{\tau}>-\ol{D}$, this requirement is met.
+
+\section{Computing the Time-Step Using Higher-Order DG Schemes}
+
+When making the jump to higher-order DG schemes, we can simply do the same as in the first-order scheme, except we compute the quantities in all of the nodal points instead of using a cell-average.
+This is valid because the cell-average is a convex combination...\sd{Need to expand on this}.
+The proof starts with the discretized equation valid at each quadrature point, $q$:
+\begin{equation}
+    \bU_{q}^{n+1}=\bU_{q}^{n}+\Delta t\,\cL_{q}^{n},
+\end{equation}
+where $\cL_{q}^{n}$ is a general form of the RHS at time $t^{n}$.
+If we define a vector $\ol{\bU}\equiv\left(\bU_{1},\cdots,\bU_{q},\cdots,\bU_{Q}\right)^T$, where $Q$ is the total number of quadrature points, and $\ol{\bW}\equiv\left(\bW_{1},\cdots,\bW_{q},\cdots,\bW_{Q}\right)^T$ as a vector of quadrature weights, then we can write the cell-average of $\bU$ as:
+\begin{equation}
+    \bU_{K}\equiv\ol{\bW}^T\ol{\bU}.
+\end{equation}
+If we then compute the cell-average of the above equation, we get:
+\begin{equation}
+    \bU_{K}^{n+1}=\bU_{K}^{n}+\Delta t\,\ol{\bW}^{T}\,\ol{\cL}_{q}^{n}=\ol{\bW}^{T}\left(\ol{\bU}^{n}+\Delta t\,\ol{\cL}^{n}\right)
+\end{equation}
 

### 2018-10-29 Documents/M1/Astronum_2018/sections/SpatialDiscretization.tex
Edits in Sections 2 and 3

@@
 \section{Spatial Discretization}\label{se:SpacialDiscretization}
-Here we use the finite-volume/first-order discontinuous Galerkin method to illustrate how the closure affects the realizability-preserving property of the scheme.
-To simply the illustration, let's focus on one-dimension uniform mesh on Cartesian coordinates.
-We divide the spatial domain $D$ evenly into $N$ cells and denote the $i$th cell as $\bK_{i}$ with $i = 1,\ldots,N$, so that
+
+In this section we discretize the two-moment model with a simple first-order finite volume method to illustrate how the closure affects the realizability-preserving property of the scheme.  
+By assuming that the moments at time level $t^{n}$ ($\bcM^{n}$) satisfy the bounds in Eq.~\eqref{eq:MomentsBounds}, our goal is to identify sufficient conditions such that the moments at time level $t^{n+1}$ ($\bcM^{n+1}$) also satisfy the bounds.
+To simply the illustration, we limit the discussion to one spatial dimension and employ a uniform Cartesian mesh.  
+(The extension to multiple spatial dimensions and high-order discretization using the discontinuous Galerkin method is given in \cite{chu_etal_2018})
+
+We divide the spatial domain $D$ into $N$ uniform cells and denote the $i$-th cell by $\bK_{i}$, with $i = 1,\ldots,N$; i.e.,
 \begin{equation*}
@@
 \end{equation*}
-Each of the cells has a length, $|\dx|$ and $|\dx| = D/N = \int_{\bK}d\vect{x}$.
-The cell-average moments:
+Denote the cell width by $\dx = D/N$.  
+The cell-average of the moments is defined as
 \begin{equation}
-\bcM_{i} = \dfrac{1}{|\dx|} \int_{\bK_i}\bcM dx.
+  \bcM_{i} = \dfrac{1}{\dx} \int_{\bK_i}\bcM dx.
 \end{equation}
-Integrating Eq.~\eqref{eq:momentEquations} for each cell $\bK_{i}$ given
+Integrating Eq.~\eqref{eq:momentEquations} over $\bK_{i}$ gives
 \begin{equation}
-\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{|\dx|} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
+  \dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{\dx} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
   \label{eq:SemiDiscretizatedMomentEquation}
 \end{equation}
-where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is the numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the integrated collision term.
-In this paper we use the simple Lax-Friedrichs flux, given by
+where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is the numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the collision term evaluated with $\bcM_{i}$.
+In this paper we use the global Lax-Friedrichs flux (setting the largest absolute eigenvalue of the flux Jacobian to one)
 \begin{equation}
-  \widehat{\bcF}_{LF}(\vect{\cM}_{a},\vect{\cM}_{b})
+  \widehat{\bcF}_{\LF}(\vect{\cM}_{a},\vect{\cM}_{b})
   =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big).
@@
 \end{equation}
-Therefore, by treating the flux term explicitly and the collision term implicitly, we have
+By treating the transport term explicitly with forward Euler and the collision term implicitly with backward Euler, we have
 \begin{align}
@@
 \end{align}
-where we define
+where we have defined
 \begin{align}
   \widetilde{\bcM}^{n}_{i} 
-& = \bcM_{i}^{n} - \dfrac{\dt}{|\dx|} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
+  & = \bcM_{i}^{n} - \frac{\dt}{\dx} \left( \widehat{\bcF}_{\LF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}_{\LF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
   & = (1-\beta)\bcM_{i}^{n} + \beta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right],
@@
 \end{align}
-and $\beta := \frac{\dt}{|\dx|}$.
+and $\beta = \frac{\dt}{\dx}$.
 

### 2018-10-29 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Updated Astronum_2018.
Edits in Sections 2 and 3

@@
 \subsection{Transport Equations}
-Consider neutrino transport through static dense matter with only emission, absorption and isotropic iso-energetic scattering.
-The Boltzmann equation after scaling to dimensionless units ($k_{B} = c = 1$) can be written as
+
+We consider neutrino transport through a static background, and include neutrino-matter interactions due to emission, absorption, and isotropic iso-energetic scattering.  
+After scaling to dimensionless units, the Boltzmann equation can be written as
 \begin{equation}
   \pd{f}{t}+\vect{\ell}\cdot\nabla f
-  =\f{1}{\tau}\,\cC(f).
+  =\f{1}{\tau}\,\cC(f),
   \label{eq:boltzmann}
 \end{equation}
-The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
+where the distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
 $\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
-On the right-hand side, $\tau$ is collision time scale: $\tau\ll1$ for opaque regions where neutrinos have frequent interactions with the background; $\tau\gg1$ for transparent regions where neutrinos rarely interact with the background and stream freely.
-$\cC(f)$ is the collision term, which models emission, absorption, and isotropic and elastic scattering: 
+On the right-hand side, $\tau$ is collision time scale.  
+In opaque regions, where neutrinos have frequent interactions with the background, $\tau\ll1$.  
+In transparent regions, where neutrinos rarely interact and stream freely, $\tau\gg1$.
+The collision term, $\cC(f)$, which models emission, absorption, and isotropic and elastic scattering is given by
 \begin{equation}
@@
 \end{equation}
-with $\xi = \sigma_{\Ab} / (\sigma_{\Ab}  + \sigma_{\Scatt} )$: $\xi = 1$ when the scattering opacity $\sigma_{\Scatt} = 0$ corresponding to pure emission and absorption; $\xi = 0$ when the absorption opacity $\sigma_{\Ab} = 0$ corresponding to pure scattering.
-$f_{0}$ is the neutrino equilibrium distribution function, which has the following form:
+where $\xi = \sigma_{\Ab} / (\sigma_{\Ab}  + \sigma_{\Scatt} )$ is the ratio of the absorption opacity $\sigma_{\Ab}$ to the total opacity.  
+The scattering opacity is $\sigma_{\Scatt}$.  
+The limit $\xi = 1$, when $\sigma_{\Scatt} = 0$, corresponds to pure absorption, while $\xi = 0$, when $\sigma_{\Ab} = 0$, corresponds to pure scattering.  
+The equilibrium distribution function for neutrinos is given by the Fermi-Dirac distribution
 \begin{equation}
-  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1}.
+  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1}, 
   \label{eq:fermiDirac}
 \end{equation}
-$T(\vect{x})$ is the temperature in energy units and $\mu(\vect{x})$ is the neutrino chemical potential.
-Both of them depend on the properties of the background as a function of $\vect{x}$.
+where $T$ is the material temperature in energy units and $\mu$ is the neutrino chemical potential.
+Both depend on the spatial position $\vect{x}$.
 
 \subsection{Two-Moment Model}
-An approximate solution of the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, can be found by employing a two-moment model.
-Define the angular moments of the distribution function as follows
+
+Approximate solutions to the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, can be found by solving the two-moment model.
+To this end, define the angular moments of the distribution function as follows
 \begin{equation}
@@
 The zeroth moment, $\cJ$, is referred to as the particle density.  
-The first moment, $\bcH$, is the particle flux, and the second moment, $\bcK$, is the stress tensor.
-We can integrate Eq.~\eqref{eq:boltzmann} to obtain equations for the zeroth and the first moments
+The first moment, $\bcH$, is the particle flux, and the second moment, $\bcK$, is proportional to the stress tensor.  
+By integrating Eq.~\eqref{eq:boltzmann} over the momentum space angular dimension we obtain equations for the zeroth and the first moments
 \begin{equation}
@@
 $\vect{I}$ is the identity matrix.
-Therefore, solving the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, for the neutrino distribution function, $f(\omega,\vect{z},t)$, is approximated by solving the two-moment equations for the neutrino number density, $\cJ(\vect{z},t)$, and flux, $\bcH(\vect{z},t)$.
+Hence, the process of solving the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, for the neutrino distribution function $f(\omega,\vect{z},t)$, is replaced by solving the two-moment equations for the neutrino number density, $\cJ(\vect{z},t)$, and flux, $\bcH(\vect{z},t)$.
 
-\subsection{Algebraic Closures }
-As is shown in the previous section, the moment equation for $\bcH$ involves $\bcK$ and the two-moment system is open. 
-To close the two-moment system, an algebraic closure is constructed.
-For a two-moment method, algebraic closures give an approximate $\bcK$ based on the lower moments as follows:
+\subsection{Algebraic Closures}
+
+As is shown in the previous section, the moment equation for $\bcH$ involves the higher moment $\bcK$ and the two-moment model is open.  
+To close the two-moment model, we consider algebraic closures.  
+For the two-moment model, algebraic closures give an approximation to $\bcK$ using the lower moments.  
+Write
 \begin{equation}
@@
 where $\vect{k}$ is the Eddington tensor.  
-For example, assuming the neutrino distribution is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore\cite{levermore_1984} proposed
+By assuming that the distribution function is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore~\cite{levermore_1984} proposed a simple form for the Eddington tensor
 \begin{equation}
@@
 where $\chi=\chi(\cJ,|\vect{\cH}|)$ is the Eddington factor.  
+Thus, the two-moment model is closed by specifying the scalar $\chi$ in terms of $\cJ$ and $|\vect{\cH}|$.
 
 \subsection{Constraints on the Moments}
-Neutrinos are fermions, and obey the Pauli exclusion principle, i.e. $f \in [0,1]$.
-As a result, the angular moments of $f$ and the Eddington factor $\chi$ are constrained as follows\cite{levermore_1984,lareckiBanach_2011,kershaw_1976,shohatTamarkin_1943}: 
+
+Neutrinos are fermions and obey the Pauli exclusion principle.  
+Because of this, the neutrino distribution function is bounded; i.e. $f \in [0,1]$.
+As a result, the angular moments $\cJ$ and $\vect{\cH}$ and the Eddington factor $\chi$ satisfy the following bounds~\cite{levermore_1984,lareckiBanach_2011,kershaw_1976,shohatTamarkin_1943}: 
 \begin{align}
-\cJ \in[0,1], \quad &(1-\cJ)\cJ-|\vect{\cH}| \geq 0, \label{eq:MomentsBounds}\\
+\cJ \in[0,1], \quad &(1-\cJ)\cJ-|\vect{\cH}| \geq 0, \label{eq:MomentsBounds} \\
   \chi_{\mbox{\tiny min}}
@@
 
-The constraints in Eq.~\eqref{eq:MomentsBounds} define realizable $\bcM$, which define a convex set in the $\cJ$-$\bcH$ space.
-As we will see later in Section \ref{se:SpacialDiscretization}, this convexity makes a constraint-preserving spatial discretization possible.
+The constraints in Eq.~\eqref{eq:MomentsBounds} define realizable moments $\bcM$.  
+For fermions, realizable moments can only be constructed from a distribution satisfying the bounds $f \in [0,1]$.  
+Moreover, the set of realizable moments is convex.  
+As we will see later in Section~\ref{se:SpacialDiscretization}, this convexity makes it possible to design a constraint-preserving discretization for solving the two-moment model numerically.
 
-The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} deserve more attention than has been given.
-They have equal importance relative to the inequalities in Eq.~\eqref{eq:MomentsBounds} in maintain consistency with respect to Fermi-Dirac statistics.
-The Eddington factor given by the algebraic closures discussed in \cite{murchikova_etal_2017} are examined in this paper as examples.
-We consider various occupancies and plot $\cJ = 0.1$ and $\cJ = 0.9$ as examples for low and high occupancy, respectively, in Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure}.
-As the figure shows, not all algebraic closures satisfy the Eddington factor bounds, Eq.~\eqref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine in the neutrino low occupancy limit, but not for high occupancies; Janka 1\cite{janka_1991} can be in error in both cases.
-The only algebraic closure that remains within the Eddington factor bounds among those plotted is Cernohorsky and Bludman's \cite{cernohorskyBludman_1994}.
-Though Levermore closure and Minerbo closure don't conserve the bounds in the high occupancy limit, they are widely used: {O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} use Minerbo closure, and Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016} use Levermore clsoure.
-\rc{Add more discussion.}
+The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} deserve further attention.  
+They are equally important, relative to those in Eq.~\eqref{eq:MomentsBounds}, in maintaining consistency of the two-moment model with respect to Fermi-Dirac statistics.  
+When designing a numerical scheme for the two-moment model that maintains realizable $\bcM$, it is also necessary for the Eddington factor to satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.
+
+However, recently reported CCSN simulations using two-moment neutrino transport with algebraic closures have employed Eddington factors that can violate the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.
+As examples, we consider the Eddington factors discussed in \cite{murchikova_etal_2017}, where the suitability of several algebraic closures for two-moment neutrino transport was evaluated.  
+In Fig.~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor versus the flux factor for two occupancies; $\cJ = 0.1$ (low occupancy) and $\cJ = 0.9$ (high occupancy).  
+Of the algebraic closures plotted, few satisfy the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds}.  
+Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, and Janka~2~\cite{janka_1992} may work fine when the occupancy is low.
+When the occupancy is high, the Eddington factor due to these closures exceeds the upper bound for Fermi-Dirac statistics.  
+The Eddington factor of Janka~1~\cite{janka_1991} may violate both the upper and lower bound on the Eddington factor.  
+Only the closure due to Cernohorsky~\&~Bludman~\cite{cernohorskyBludman_1994} satisfies both the upper and lower bounds.  
+This is not suprising as this is the only closure based on Fermi-Dirac statistics.  
+Althought the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely in simulations of neutrino transport in CCSNe \ee{and neutron star mergers?}; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016} use the Levermore closure.
+When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.
+\ee{so what?  Should we discuss the presence of blocking factors in collision terms?}
+%With those algebraic closures that don't conserve the bounds, the time integrator may give moments that implies $f>1$.
+%Some safety protections may be applied for those method, but the safety protections can break the conservation laws in lepton number or energy and defect the CCSN simulation.
 
@@
    \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupancy) and $\cJ=0.9$ (right panel, high occupancy).
-In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.
+In each panel we plot the Eddington factors of two-moment closures due to Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue), Janka~1 (purple), and Janka~2 (pink) .
 We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$, defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dashed black lines, respectively).}

### 2018-10-31 Documents/Euler/dgEulerGR.tex
Added to dgEulerGR.tex

@@
 
+So, we end up with:
+\begin{equation}
+    \Delta t<\text{min}\left\{\text{min}_{i}\left(\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right),\text{min}^{n}_{i}\left(\f{2\left(1-\ve\right)}{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\,\ol{\tau}\left(\ol{\tau}+2\,\ol{D}\right)}\right]\right)\right\}.
+\end{equation}
+
 \section{Computing the Time-Step Using Higher-Order DG Schemes}

### 2018-11-01 Documents/Euler/dgEulerGR.tex
Added section about limiting when q_K<0

@@
 
+\subsection{Demanding that $q>0$}
+
+Sometimes it happens that $q\left(\ol{\bU}\right)<0$, so our positivity limiter will fail.
+To get around this we modify the conserved energy, $\tau$ to demand that $q=\ve$, where $0<\ve\ll1$.
+The transformation we make is:
+\begin{equation}
+   \ol{ \tau}\longrightarrow\alpha\,\ol{\tau},\hspace{1em}\alpha>1.
+\end{equation}
+This modifies the definition of $q\left(\ol{\bU}\right)\equiv q_{K}$ from:
+\begin{equation}
+   q_{K}=\ol{\tau}+\ol{D}-\sqrt{\ol{D}^{2}+\ol{S}^{2}+\ve}<0,
+\end{equation}
+to:
+\begin{equation}
+   \ve=\alpha\,\ol{\tau}+\ol{D}-\sqrt{\ol{D}^{2}+\ol{S}^{2}+\ve}.
+\end{equation}
+Solving this for $\alpha$, we get:
+\begin{equation}
+   \alpha=\ol{\tau}^{-1}\left[\ve-\ol{D}+\sqrt{\ol{D}^{2}+\ol{S}^{2}+\ve}\right].
+\end{equation}
+
 \section{Computing the Time-Step Using Higher-Order DG Schemes}

### 2018-11-02 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Minor changes

@@
 Only the closure due to Cernohorsky~\&~Bludman~\cite{cernohorskyBludman_1994} satisfies both the upper and lower bounds.  
-This is not suprising as this is the only closure based on Fermi-Dirac statistics.  
-Althought the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely in simulations of neutrino transport in CCSNe \ee{and neutron star mergers?}; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016} use the Levermore closure.
+This is not surprising as this is the only closure based on Fermi-Dirac statistics.  
+Although the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely used in simulations of neutrino transport in CCSNe \ee{and neutron star mergers?}; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016} use the Levermore closure.
 When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.

### 2018-11-02 Documents/M1/Astronum_2018/sections/SpatialDiscretization.tex
Progress on time integration

@@
   & = (1-\beta)\bcM_{i}^{n} + \beta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right],
+  \quad\beta = \frac{\dt}{\dx}.  
 \label{eq:widetildeM}
 \end{align}
-and $\beta = \frac{\dt}{\dx}$.
 
-Assume $\bcM_{i}^{n}$ is realizable for all $i$. 
-For Eq.~\eqref{eq:MomentIMEX}, Lemma 3 in \cite{chu_etal_2018} says that $\bcM^{n+1}_{i}$ is realizable given $\f{\dt}{\tau} > 0$ and provided that $\widetilde{\bcM}^{n}_{i}$ is realizable.
-Substituting the Lax-Friedrichs flux, Eq.~\eqref{eq:Lax-Friedrichs flux}, in Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, $\widetilde{\bcM}^{n}_{i}$ becomes a convex combination of $\bcM_{i}^{n}$ and the square bracket in Eq.~\eqref{eq:widetildeM} if $\beta \in [0,1]$.
-$\widetilde{\bcM}^{n}_{i}$ is realizable if $\beta \in [0,1]$ and the term in square brackets is realizable.
-Given Lemma 2 in \cite{chu_etal_2018}, the term in square brackets is realizable if $\cJ$, $\bcH$ and $\bcK$ are realizable.
-In other words, realizability of the term in square brackets depends on the algebraic closure.
-If the closure satisfies Eq.~\eqref{eq:eddingtonFactorBounds},
-$\bcM^{n+1}_{i}$ is realizable provided $\beta \in [0,1]$.
-Note that $\beta \leq 1$ is also the CFL condition of the Forward-Euler method applied to a transport-only Boltzmann equation.
+Consider Eq.~\eqref{eq:MomentIMEX} and assume that $\bcM_{i}^{n}$ is realizable for all $i$.  
+Lemma~3 in \cite{chu_etal_2018} states that $\bcM^{n+1}_{i}$ is realizable provided $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.  
+In Eq.~\eqref{eq:widetildeM}, if $\beta \in [0,1]$, $\widetilde{\bcM}^{n}_{i}$ is expressed as a convex combination of $\bcM_{i}^{n}$ and the expression in the square brackets on the right-hand side of Eq.~\eqref{eq:widetildeM}.
+It follows that $\widetilde{\bcM}^{n}_{i}$ is realizable if the expression inside the square brackets is realizable.  
+By Lemma~2 in \cite{chu_etal_2018}, the expression in square brackets is realizable for a distribution satisfying $f\in[0,1]$.  
+For the two-moment model considered here, realizability depends in the algebraic closure.  
+Specifically, if $\bcM_{i}^{n}$ is realizable and the Eddington factor satisfies the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, then $\bcM^{n+1}_{i}$ is realizable provided $\beta \in [0,1]$.  
+Thus, realizability of $\bcM^{n+1}_{i}$ requires both a closure based on Fermi-Dirac statistics and a CFL condition $\dt\le\dx$.

### 2018-11-02 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Progress on time integration

@@
+\clearpage
 \section{Time Integration} \label{se:TimeIntegration}
 
-Suppose we have an algebraic closure based on Fermi-Dirac statistic (whose Eddington factor satisfies Eq.~\eqref{eq:eddingtonFactorBounds}).
-We show how to construct a time integration which satisfies the bounds on moment after each time step in this section.
-The semi-discretization of the moment equations, Eq.~\eqref{eq:momentEquations}, results in a system of ordinary differential equations of the form
+Suppose that an algebraic closure based on Fermi-Dirac statistics is used (i.e., the Eddington factor satisfies Eq.~\eqref{eq:eddingtonFactorBounds}).
+Here we consider the construction of an Implicit-Explicit (IMEX) time integration scheme which maintains the bounds in Eq.~\eqref{eq:MomentsBounds}.  
+The semi-discretization of the two-moment model results in a system of ordinary differential equations of the form
 \begin{equation}
@@
 \end{equation}
-where
+where the solution vector
 \begin{equation}
@@
 \end{equation}
-is the collection of all cell-average moments, $\vect{\cT}$ is the transport operator corresponding to the first term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, and $\f{1}{\tau}\,\vect{\cQ}$ corresponds to the collision operator, the second term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}.
+is the collection of all cell-averaged moments, $\vect{\cT}$ is the transport operator, corresponding to the first term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, and $\f{1}{\tau}\,\vect{\cQ}$ is the collision operator, corresponding to the second term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}.
 
-Since the realizable $\bcM$ define a convex set in $\cJ$-$\bcH$ space, convex-invariant schemes, which remain in their initial convex set, can be used to design realizability-preserving schemes for the two-moment model.
-The following discussion shows how to construct a convex-invariant scheme.
+Since the set of realizable moments is convex, convex-invariant schemes, which maintain states in a convex set, can be used to design realizability-preserving schemes for the two-moment model. 
+Ideally, the scheme should also be high-order accurate and work well in the asymptotic diffusion limit (characterized by frequent collisions and long time scales).  
+The following discussion considers the construction of such convex-invariant schemes.
 
-\subsection{Standard Implicit-Explicit Scheme}
-Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form \cite{pareschiRusso_2005}: 
+\subsection{Standard IMEX Schemes}
+
+Treating the transport operator explicitly and the collision operator implicitly, a standard $s$-stage IMEX scheme takes the following form \cite{pareschiRusso_2005}: 
 \begin{align}
@@
 \end{align}
-where  $(\tilde{a}_{ij})$ and $(a_{ij})$ are coefficients of the $i$-th stage and they are the elements of matrices $\tilde{A}$ and $A$, respectively.
+where $(\tilde{a}_{ij})$ and $(a_{ij})$, coefficients of the $i$-th stage, are the elements of matrices $\tilde{A}$ and $A$, respectively.
 The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weights in the assembly step in Eq.~\eqref{imexIntermediate}.
-These coefficients and weights have to satisfy certain condition for an accurate and consistent scheme.
-For instance, to have second-order temporal accuracy, the following conditions are required:
+These coefficients and weights must satisfy certain order conditions for consistency and accuracy.  
+For second-order temporal accuracy, the following conditions are required:
 \begin{equation}
@@
 \end{equation}
-where $\tilde{c}_{i} = \sum_{j}^{s}\tilde{a}_{ij}$ and $c_{i}=\sum_{j}^{s}a_{ij}$.
+where $\tilde{c}_{i} = \sum_{j=1}^{s}\tilde{a}_{ij}$ and $c_{i}=\sum_{j=1}^{s}a_{ij}$.
 
@@
 Since PD-ARS with SSPRK3 is as accurate as PD-ARS with SSPRK2 in collision involved region, see Section~\ref{se:NumericalTests} for the plots, it may not offer any advantage.
+
+\clearpage

### 2018-11-04 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Minor changes.

@@
 This is not surprising as this is the only closure based on Fermi-Dirac statistics.  
-Although the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely used in simulations of neutrino transport in CCSNe \ee{and neutron star mergers?}; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016} use the Levermore closure.
+Although the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely used in simulations of neutrino transport in CCSNe and neutron star mergers; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, Just et al.~\cite{just_etal_2018}, and Foucart et al.~\cite{foucart_etal_2015} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, Kuroda et al.~\cite{kuroda_etal_2016}, and Fujibayashi et al.
+~\cite{fujibayashi_etal_2017} use the Levermore closure.
 When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.

### 2018-11-04 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Minor edits

--- 2018-11-02 Documents/M1/Astronum_2018/sections/TwoMoments.tex
@@
 This is not surprising as this is the only closure based on Fermi-Dirac statistics.  
-Although the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely used in simulations of neutrino transport in CCSNe \ee{and neutron star mergers?}; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016} use the Levermore closure.
+Although the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely used in simulations of neutrino transport in CCSNe and compact binary mergers; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, Just et al.~\cite{just_etal_2018}, and Foucart et al.~\cite{foucart_etal_2015} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, Kuroda et al.~\cite{kuroda_etal_2016}, and Fujibayashi et al.~\cite{fujibayashi_etal_2017} use the Levermore closure.
 When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.

### 2018-11-04 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Some edtis on time integration

@@
 
+\ee{Discuss GSA and Type~ARS here.}
+
 \subsection{Constraint-Preserving Implicit-Explicit Schemes}
+
 Beyond the accuracy requirement, a convex-invariant IMEX scheme must satisfy additional constraints.
@@
 Using those Lemma proved in \cite{chu_etal_2018}, we can find those constraints that $c_{ij}$ and $\hat{c}_{ij}$ (or $a_{ij}$ and $\tilde{a}_{ij}$) need to satisfy to ensure $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ be realizable.
+
+\ee{Move definition of coefficients $c_{ij}$ and $\tilde{c}_{ij}$ here}
 

### 2018-11-04 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Some edtis on time integration

@@
 
-\ee{Move definition of coefficients $c_{ij}$ and $\tilde{c}_{ij}$ here}
+\ee{Move definition of coefficients $c_{ij}$ and $\tilde{c}_{ij}$ here.}
+\ee{Discuss non-existence of high-order convex invariant scheme without explicit time step.}
 
 \subsection{Diffusion Accurate, Constraint-Preserving Implicit-Explicit Schemes}
+
 Diffusion accurate is the other property the time integration should have.
@@
 We derived the diffusion accurate condition in \cite{chu_etal_2018} and proved that only type~ARS (investigated by Ascher, Ruuth, and Spiteri\cite{ascher_etal_1997}) IMEX schemes can be our candidates.
+
+\ee{Discuss conditions on IMEX coefficients for diffusion accuracy here.}
 
@@
     Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.
+
+\ee{Maybe make a separate subsection combining results from previous sections here.}
+\ee{Need to motivate resorting to first-order accuracy.}
 

### 2018-11-06 Documents/Euler/dgEulerGR.tex
Changed representation of cell-average from overline to subscript K

--- 2018-10-31 Documents/Euler/dgEulerGR.tex
@@
 
+\subsection{Demanding that $q>0$}
+
+Sometimes it happens that the cell-average of $q$, $q_{K}\equiv q\left(\bU_{K}\right)<0$, so our positivity limiter will fail.
+To get around this we modify the conserved energy, $\tau$, to demand that $q=\ve$, where $0<\ve\ll1$.
+The transformation we make is:
+\begin{equation}
+   \tau_{K}\longrightarrow\alpha\,\tau_{K},\hspace{1em}\alpha>1.
+\end{equation}
+This modifies the definition of $q_{K}$ from:
+\begin{equation}
+   q_{K}=\tau_{K}+D_{K}-\sqrt{D_{K}^{2}+S_{K}^{2}+\ve}<0,
+\end{equation}
+to:
+\begin{equation}
+   \ve=\alpha\,\tau_{K}+D_{K}-\sqrt{D_{K}^{2}+S_{K}^{2}+\ve}.
+\end{equation}
+Solving this for $\alpha$, we get:
+\begin{equation}
+   \alpha=\tau_{K}^{-1}\left[\ve-D_{K}+\sqrt{D_{K}^{2}+S_{K}^{2}+\ve}\right].
+\end{equation}
+
 \section{Computing the Time-Step Using Higher-Order DG Schemes}

### 2018-11-07 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Modified time integration section.

--- 2018-11-04 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
@@
 \begin{equation}
-  \dfrac{d \vect{u}}{d t} = \vect{\cT}(\vect{u}) + \f{1}{\tau}\,\vect{\cQ}(\vect{u}),
+  \dfrac{d \vect{u}}{d t} = \vect{\cT}(\vect{u}) + \f{ 1}{\tau}\,\vect{\cQ}(\vect{u}),
 \end{equation}
@@
 where $(\tilde{a}_{ij})$ and $(a_{ij})$, coefficients of the $i$-th stage, are the elements of matrices $\tilde{A}$ and $A$, respectively.
+Matrices $\tilde{A}$ and $A$ are both lower triangular matrices.
 The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weights in the assembly step in Eq.~\eqref{imexIntermediate}.
-These coefficients and weights must satisfy certain order conditions for consistency and accuracy.  
-For second-order temporal accuracy, the following conditions are required:
+These coefficients and weights must satisfy certain order conditions for consistency, accuracy and other properties.
+
+For second-order temporal accuracy, the following conditions are required \cite{hairer_1981}:
 \begin{equation}
@@
 
-\ee{Discuss GSA and Type~ARS here.}
+For globally stiffly accuracy (GSA), the coefficients have the following relationship \cite{dimarcoPareschi2013}:
+\begin{equation}
+a_{si}=w_{i}, \quad \tilde{a}_{si}=\tilde{w}_{i}, \quad \text{for} \quad i=1,\ldots,s.
+\end{equation}
+
+The IMEX schemes are usually classified by the structure of matrix $A$, the implicit tableau:
+if $A$ is invertible, the IMEX scheme is type~A \cite{pareschiRusso_2005};
+if $a_{i1} = 0$ for $i=1,\ldots,s$ and $w_{1} = 0$, the IMEX scheme is type~ARS \cite{ascher_etal_1997,pareschiRusso_2005}.
 
@@
 with $c_{ij}$ and $\hat{c}_{ij}$ be some expression of $a_{ij}$ and $\tilde{a}_{ij}$.
-By requiring the IMEX scheme be globally stiffly accurate (GSA), i.e. $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i}$ for $i=1,\ldots,s$, $\vect{u}^{n+1} = \vect{u}^{(s)}$.
-Using those Lemma proved in \cite{chu_etal_2018}, we can find those constraints that $c_{ij}$ and $\hat{c}_{ij}$ (or $a_{ij}$ and $\tilde{a}_{ij}$) need to satisfy to ensure $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ be realizable.
-
-\ee{Move definition of coefficients $c_{ij}$ and $\tilde{c}_{ij}$ here}
-
-\subsection{Diffusion Accurate, Constraint-Preserving Implicit-Explicit Schemes}
-Diffusion accurate is the other property the time integration should have.
-In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$.
-The moment behavior are governed by (e.g., \cite{jinLevermore_1996})
-\begin{equation}
-  \pd{\cJ}{t} + \nabla\cdot\vect{\cH} = 0
-  \quad\text{and}\quad
-  \vect{\cH} = - \tau\,\nabla\cdot\vect{\cK}.  
-  \label{eq:diffusionLimit}
-\end{equation}
-In the context of IMEX schemes, the above relationships imply that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold. 
-We derived the diffusion accurate condition in \cite{chu_etal_2018} and proved that only type~ARS (investigated by Ascher, Ruuth, and Spiteri\cite{ascher_etal_1997}) IMEX schemes can be our candidates.
-
-For type~ARS, $a_{i1} = 0$ for $i=1,\ldots,s$.
-$c_{ij}$ and $\hat{c}_{ij}$ are given by
+For example, type~ARS IMEX schemes have $c_{ij}$ and $\hat{c}_{ij}$ be given by
     \begin{equation}
@@
 
-Combining the conditions we have, we aim to find type~ARS IMEX scheme with.
+By requiring the IMEX scheme be GSA, $\vect{u}^{n+1} = \vect{u}^{(s)}$.
+Then using those Lemma proved in \cite{chu_etal_2018}, we can find those constraints, such as Eq.~\eqref{eq:convexInvariant} for type~ARS, that $c_{ij}$ and $\hat{c}_{ij}$ (or $a_{ij}$ and $\tilde{a}_{ij}$) need to satisfy to ensure $\vect{u}^{(i)}$, Eq.~\eqref{eq:imexStagesRewrite}, be realizable.
+Hence $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ are realizable and the IMEX is constraint-preserving.
+
+When the convex-invariant constraints are satisfied, the first (sum) term on the right-hand side of Eq.\eqref{eq:imexStagesRewrite} is a convex combination of multiple explicit Euler schemes with time step $\hat{c}_{ij}\,\dt$.
+Each of the explicit Euler schemes has a time step condition that ensures its realizability: $\hat{c}_{ij}\,\dt\leq$ the Courant-Friedrichs-Lewy (CFL) condition.
+As a result, the time step of the IMEX scheme is subject to the most restrict time step condition:
+\begin{equation}
+\max(\hat{c}_{ij})\,\dt \leq \text{CFL condition}.
+\end{equation}
+
+Unfortunately, no coefficients can be found for standard IMEX schemes under the constraint-preserving constraints and the accuracy constraints for 2nd-order or higher. 
+To circumvent this problem, some correction steps are introduced after the assembly step, Eq.~\eqref{imexIntermediate}, such as Hu et al.\cite{hu_etal_2018}.
+However, the correction steps impose extra constraints for realizability on time step.
+In the circumstance that we have, correction steps can ruin the efficiency we gain from the IMEX scheme.
+To keep things simple, we aim for 1st-order in general, high-order in streaming limit, diffusion accurate, constraint-preserving IMEX schemes.
+
+\subsection{Diffusion Accurate, Constraint-Preserving Implicit-Explicit Schemes}
+
+Diffusion accurate is an important property the time integration should have.
+In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$.
+The moment behavior are governed by (e.g., \cite{jinLevermore_1996})
+\begin{equation}
+  \pd{\cJ}{t} + \nabla\cdot\vect{\cH} = 0
+  \quad\text{and}\quad
+  \vect{\cH} = - \tau\,\nabla\cdot\vect{\cK}.  
+  \label{eq:diffusionLimit}
+\end{equation}
+In the context of IMEX schemes, the above relationships imply that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold. 
+That's
+\begin{equation}
+   \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s,
+\end{equation}
+where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix.
+\rc{It can be rewrite to $c=\tilde{c}$.}
+We have proved in \cite{chu_etal_2018} that only type~ARS IMEX schemes can be diffusion accurate and constraint-preserving at the same time.
+
+\subsection{PD-ARS schemes}
+
+Combining the conditions we have, the 1st-order in general, high-order in streaming limit, diffusion accurate, constraint-preserving IMEX schemes we need are type~ARS IMEX schemes satisfying the following constraints:
 \begin{enumerate}
@@
     \end{equation}
-    \item Second-order accuracy in the streaming limit:
+    \item High-order accuracy in the streaming limit, 2nd-order for example:
     \begin{equation}
@@
     \end{equation}
+    \item Diffusion accurate: \rc{$c=\tilde{c}$.}
+    \begin{equation}
+      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s.
+      \label{eq:diffusionCondition}
+    \end{equation}
     \item Convex-invariant:
@@
       &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=3,\ldots,s, \quad\text{and}\quad j=2,\ldots,i-1.  
+      \label{eq:convexInvariant}
     \end{align}
@@
                   j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
-    \item Well-behaved in the diffusion limit:
-    \begin{equation}
-      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s,
-      \label{eq:diffusionCondition}
-    \end{equation}
-    where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix.
-    \item Less than five stages ($s\le4$).
+    \item Less than five stages ($s\le4$) \label{cod:statges}.
     \item Globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. 
 \end{enumerate}  
+The \ref{cod:statges} constraint is given by efficiency consideration.
 We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{chu_etal_2018}.)
@@
 Since PD-ARS with SSPRK3 is as accurate as PD-ARS with SSPRK2 in collision involved region, see Section~\ref{se:NumericalTests} for the plots, it may not offer any advantage.
-
-\clearpage

### 2018-11-07 Documents/M1/Astronum_2018/sections/SpatialDiscretization.tex
Changed constraint-preserving to realizability-preserving.

@@
 
-In this section we discretize the two-moment model with a simple first-order finite volume method to illustrate how the closure affects the realizability-preserving property of the scheme.  
+In this section we discretize the two-moment model with a simple first-order finite volume method to illustrate how the closure affects the realizability-preserving property of the method.  
 By assuming that the moments at time level $t^{n}$ ($\bcM^{n}$) satisfy the bounds in Eq.~\eqref{eq:MomentsBounds}, our goal is to identify sufficient conditions such that the moments at time level $t^{n+1}$ ($\bcM^{n+1}$) also satisfy the bounds.

### 2018-11-07 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Changed constraint-preserving to realizability-preserving.

@@
 
-Since the set of realizable moments is convex, convex-invariant schemes, which maintain states in a convex set, can be used to design realizability-preserving schemes for the two-moment model. 
+Since the set of realizable moments is convex, convex-invariant schemes, which maintain states in a convex set, can be used to design realizability-preserving methods for the two-moment model. 
 Ideally, the scheme should also be high-order accurate and work well in the asymptotic diffusion limit (characterized by frequent collisions and long time scales).  
@@
 
-\subsection{Constraint-Preserving Implicit-Explicit Schemes}
+\subsection{Convex-Invariant Implicit-Explicit Schemes}
 
@@
 Then using those Lemma proved in \cite{chu_etal_2018}, we can find those constraints, such as Eq.~\eqref{eq:convexInvariant} for type~ARS, that $c_{ij}$ and $\hat{c}_{ij}$ (or $a_{ij}$ and $\tilde{a}_{ij}$) need to satisfy to ensure $\vect{u}^{(i)}$, Eq.~\eqref{eq:imexStagesRewrite}, be realizable.
-Hence $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ are realizable and the IMEX is constraint-preserving.
+Hence $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ are realizable and the method with this convex-invariant IMEX scheme is realizability-preserving.
 
@@
 
-Unfortunately, no coefficients can be found for standard IMEX schemes under the constraint-preserving constraints and the accuracy constraints for 2nd-order or higher. 
+Unfortunately, no coefficients can be found for standard IMEX schemes under the convex-invariant constraints and the accuracy constraints for 2nd-order or higher. 
 To circumvent this problem, some correction steps are introduced after the assembly step, Eq.~\eqref{imexIntermediate}, such as Hu et al.\cite{hu_etal_2018}.
@@
 In the circumstance that we have, correction steps can ruin the efficiency we gain from the IMEX scheme.
-To keep things simple, we aim for 1st-order in general, high-order in streaming limit, diffusion accurate, constraint-preserving IMEX schemes.
+To keep things simple, we aim for 1st-order in general, high-order in streaming limit, diffusion accurate, convex-invariant IMEX schemes.
 
-\subsection{Diffusion Accurate, Constraint-Preserving Implicit-Explicit Schemes}
+\subsection{Diffusion Accurate, Convex-Invariant Implicit-Explicit Schemes}
 
@@
 where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix.
-\rc{It can be rewrite to $c=\tilde{c}$.}
-We have proved in \cite{chu_etal_2018} that only type~ARS IMEX schemes can be diffusion accurate and constraint-preserving at the same time.
+It can be rewritten as $c=\tilde{c}$.
+We have proved in \cite{chu_etal_2018} that only type~ARS IMEX schemes can be diffusion accurate and convex-invariant at the same time.
 
@@
 
-Combining the conditions we have, the 1st-order in general, high-order in streaming limit, diffusion accurate, constraint-preserving IMEX schemes we need are type~ARS IMEX schemes satisfying the following constraints:
+Combining the conditions we have, the 1st-order in general, high-order in streaming limit, diffusion accurate, convex-invariant IMEX schemes we need are type~ARS IMEX schemes satisfying the following constraints:
 \begin{enumerate}
@@
       \quad\text{and}\quad
-      \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2},
+      \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2}.
       \label{eq:orderConditionsEx}
     \end{equation}
-    \item Diffusion accurate: \rc{$c=\tilde{c}$.}
+    \item Diffusion accurate:
     \begin{equation}
-      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s.
+      c=\tilde{c}.
       \label{eq:diffusionCondition}
@@
     \end{align}
-    with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\Sch}=\min_{\substack{i = 2,\ldots,s \\ 
+    with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\Sch}:=\min_{\substack{i = 2,\ldots,s \\ 
                   j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.

### 2018-11-07 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Changed constraint-preserving to realizability-preserving.

@@
 Moreover, the set of realizable moments is convex.  
-As we will see later in Section~\ref{se:SpacialDiscretization}, this convexity makes it possible to design a constraint-preserving discretization for solving the two-moment model numerically.
+As we will see later in Section~\ref{se:SpacialDiscretization}, this convexity makes it possible to design a realizability-preserving discretization for solving the two-moment model numerically.
 

### 2018-11-07 Documents/M1/Astronum_2018/sections/intro.tex
Changed constraint-preserving to realizability-preserving.

@@
 Therefore, IMEX methods require fewer time steps comparing with fully explicit method, and the calculation for each step is easily parallelizable.  
-For a non-relativistic system where the propagating speed of gravity wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.\cite{cernohorskyVanWeert_1992}(read ?)
-But for a relativistic circumstance that we have, where the gravity, fluid, and neutrino have a relativistic propagating speed, IMEX method
-balances the efficiency and cost.
+%For a non-relativistic system where the propagating speed of gravitional wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.\cite{cernohorskyVanWeert_1992}(read ?)
+For a relativistic circumstance that we have, where the gravity, fluid, and neutrino have a relativistic propagating speed, IMEX method is an efficient method.
 
@@
 Realizability of $\cJ$ and $\bcH$ after each time step requires a convex-invariant IMEX scheme.
-Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX scheme for two-moment neutrino transport.
+Since the realizable moments form a convex set, it is possible to construct a realizability-preserving method with convex-invariant IMEX scheme for two-moment neutrino transport.
 What's more, the physics of neutrino transport in CCSN requires the IMEX scheme to be diffusion-accurate.
 
-The study of moment realizability and constraint-preserving, diffusion-accurate IMEX schemes motivate this work.
+The study of moment realizability and realizability-preserving method with diffusion-accurate IMEX schemes motivate this work.
 Gottlieb et al\cite{gottlieb_etal_2001} showed standard IMEX scheme with strong-stability-preserving can't have an order higher than first without a restrict time step requirement.
@@
 
-\rc{Reference check}
+%\rc{Reference check}

### 2018-11-07 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Rewrote GSA related text in time integration section.

@@
 where $(\tilde{a}_{ij})$ and $(a_{ij})$, coefficients of the $i$-th stage, are the elements of matrices $\tilde{A}$ and $A$, respectively.
-Matrices $\tilde{A}$ and $A$ are both lower triangular matrices.
+Matrices $\tilde{A}$ and $A$ are both lower triangular matrices whose other elements are all zero.
 The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weights in the assembly step in Eq.~\eqref{imexIntermediate}.
@@
 \end{equation}
+It makes the assembly step the same as the $s$th-stage, $\vect{u}^{n+1} = \vect{u}^{(s)}$.
+Therefore, GSA condition, if it is achievable, is also a simplifying condition beyond stiffly accurate condition.
 
@@
 
-Beyond the accuracy requirement, a convex-invariant IMEX scheme must satisfy additional constraints.
+Beyond certain accuracy and GSA requirements, a convex-invariant IMEX scheme must satisfy additional constraints.
 Our idea is finding the constraints on $a_{ij}$, $\tilde{a}_{ij}$, $\tilde{w}_{i}$, and $w_{i}$ that enable each $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ be convex combination of realizable moments:
@@
 
-By requiring the IMEX scheme be GSA, $\vect{u}^{n+1} = \vect{u}^{(s)}$.
+GSA gives $\vect{u}^{n+1} = \vect{u}^{(s)}$.
 Then using those Lemma proved in \cite{chu_etal_2018}, we can find those constraints, such as Eq.~\eqref{eq:convexInvariant} for type~ARS, that $c_{ij}$ and $\hat{c}_{ij}$ (or $a_{ij}$ and $\tilde{a}_{ij}$) need to satisfy to ensure $\vect{u}^{(i)}$, Eq.~\eqref{eq:imexStagesRewrite}, be realizable.
@@
 
-Diffusion accurate is an important property the time integration should have.
+Diffusion accurate is another important property the time integration should have.
 In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$.
@@
 \begin{equation}
-   \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s,
+   \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=1,\ldots,s,
 \end{equation}
 where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix.
-It can be rewritten as $c=\tilde{c}$.
+It can be rewritten as 
+\begin{equation}
+c=\tilde{c}.
+\end{equation}
 We have proved in \cite{chu_etal_2018} that only type~ARS IMEX schemes can be diffusion accurate and convex-invariant at the same time.
+Another short proof is that type~A IMEX schemes have $\tilde{c}_1 = 0$ while $c_i \neq 0$.
 
@@
 
-Combining the conditions we have, the 1st-order in general, high-order in streaming limit, diffusion accurate, convex-invariant IMEX schemes we need are type~ARS IMEX schemes satisfying the following constraints:
+Combining the conditions we have, the 1st-order in general, high-order in streaming limit, diffusion accurate, convex-invariant, GSA IMEX schemes we need are type~ARS IMEX schemes satisfying the following constraints:
 \begin{enumerate}

### 2018-11-13 Documents/Euler/Astronum_2018/ms_endeve.tex
Addition of refs.  Already in submitted version

@@
 \newcommand{\thornado}{\texttt{thornado}}
+\newcommand{\chimera}{{\sc Chimera}}
 
@@
 Results from a suite of tests in one and two spatial dimensions --- including problems with strong shocks --- demonstrate reliable performance of the implementation.  
+The accuracy of \thornado\ on three shock tests (Sod shock tube \cite{sod_1978}, Sedov-Taylor blast wave \cite{sedov_1959}, and Shu-Osher shock tube \cite{shuOsher_1989}) is qualitatively similar to that of the well-established CCSN simulation code \chimera\ \cite{bruenn_etal_2018}, which is based on the PPM finite volume method \cite{colellaWoodward_1984}.
 Two tests in spherical symmetry (standing accretion shock \cite{blondin_etal_2003} and Yahil-Lattimer collapse \cite{yahilLattimer_1982,yahil_1983}) demonstrate the DG method's ability to handle conditions relevant to CCSN simulations.
@@
 \section*{References}
-\begin{thebibliography}{34}
+\begin{thebibliography}{36}
   \bibitem{bassi_etal_2013} Bassi F, Franchina N, Ghidoni A and Rebay S 2013 {\it Int. J. Numer. Meth. Fluids} {\bf 71} 1322
@@
   \bibitem{brennerScott_2008} Brenner S C and Scott L R 2008 {\it The Mathematical Theory of Finite Element Methods} Springer
+  \bibitem{bruenn_etal_2018} Bruenn S W {\it et al} {\it Preprint} arXiv:1809.05608
   \bibitem{cockburnShu_1998} Cockburn B and Shu C-W 1998 {\it JCP} {\bf 141} 199
   \bibitem{cockburnShu_2001} Cockburn B and Shu C-W 2001 {\it Journal of Scientific Computing} {\bf 16} 173
+  \bibitem{colellaWoodward_1984} Colella P and Woodward P 1984 {\it JCP} {\bf 54} 174
   \bibitem{dumbser_etal_2014} Dumbser M, Zanotti O, Loub{\`e}re R and Diot S 2014 {\it JCP} {\bf 278} 47

### 2018-11-13 Documents/M1/dgM1Curvilinear.tex
uncommitted changes

--- 2017-07-25 Documents/M1/dgM1Curvilinear.tex
@@
 \newcommand{\NES}{\mbox{\tiny NES}}
+\newcommand{\thornado}{\texttt{thornado}}
 
@@
 
-\title{Nodal Discontinuous Galerkin Method for the Two-Moment Model of Neutrino Transport}
+\title{A Nodal Discontinuous Galerkin Method for the Multi-Group Two-Moment Model of Neutrino Transport}
 \author{Eirik Endeve\altaffilmark{1}, et al.}
@@
 \begin{abstract}
-We present a nodal Discontinuous Galerkin (DG) method for solving the non-relativistic two-moment model for neutrino transport.  
+We present a nodal Discontinuous Galerkin (DG) method for solving the non-relativistic multi-group two-moment model for neutrino transport.  
 The method --- ultimately targeted for simulations of core-collapse supernovae --- includes the use of curvilinear coordinates and non-ideal microphysics (nuclear equation of state and weak interactions) for neutrino-matter interactions.
+We give implementation details and present results from an extensive set of benchmark problems in one spatial dimension.
 \end{abstract}
@@
 \subsection{Emission and Absorption}
+\label{sec:electronCapture}
 
@@
 \subsection{Elastic Scattering}
+\label{sec:elasticScattering}
 
@@
 As an example, an expected third-order accurate method (for problems with smooth solutions), using DG(2) and SSP-RK3, will then be denoted DG(2)+RK3.  
+For tests involving collisions we use the two-stage Semi-Implicit Runge-Kutta method described in Section~\ref{sec:semiImplicitTime}.  
+When this time integrator is combined with DG($k$) spatial discretization, the method is denoted DG($k$)+SIRK2.
 
@@
 \subsection{Homogeneous Sphere}
+\label{sec:homogeneousSphere}
 
@@
 Results are plotted in Figure~\ref{fig:homogeneousSphere1D}.  
+In the left panels we plots results obtained for the thick case, while results for the thin case are plotted in the right panels.  
+We plot the radiation density $\cJ$ in the top panels, the flux factor $\cH_{r}/\cJ$ in the middle panels, and the Eddington factor $\psi$ in the bottom panels.  
+The two-moment model captures the analytic solution reasonably well in both the thin and the thick cases, especially for the density $\cJ$.  
+The discrepancy in the flux and Eddington factors between the numerical results and the analytical solution is comparable to that of other implementations of the two-moment model \citep[e.g.,][]{smit_etal_1997}.
 
@@
 
-\section{Transport Problems with Tabulated Neutrino Opacities}
+\section{Multi-group Transport Problems with Tabulated Neutrino Opacities}
 \label{sec:numericalTableOpacities}
 
-For the tests in this section we employ the tabulated opacities described in Section~\ref{sec:opacities}.  
-We present two tests from the previous section (the homogeneous sphere and spherical diffusion problems), where the background is kept fixed.  
-Then we present a relaxation problem involving neutrino-electron scattering (NES) with a homogeneous background.  
-Finally, we present a deleptonization problem where the background density mimics that of a collapsed stellar core.  
-The first deleptonization problem (Em/Ab) involves emission and absorption only, while the second deleptonization problem (Full) involves the full set of opacities described in Section~\ref{sec:opacities}.
+For the tests in this section we employ some of the tabulated opacities described in Section~\ref{sec:opacities}.  
+In Section~\ref{sec:homogeneousSphereTable}, we present a multi-group version of the homogeneous sphere test from Section~\ref{sec:homogeneousSphere}, where the background is kept fixed.  
+In Section~\ref{sec:deleptonizationProblem}, we present a deleptonization problem where the initial background density mimics that of a collapsed stellar core.  
+The deleptonization problem uses the tabulated electron capture and elastic scattering rates on nucleons and nuclei as described in Sections~\ref{sec:electronCapture} and \ref{sec:elasticScattering}.
+For this problem, the temperature and electron fraction of the background are evolved with the radiation field as described in Section~\ref{sec:couplingElectronCapture} below.  
+The deleptonization problem is distributed with the mini-app, available at \url{https://github.com/ECP-Astro/thornado_mini}.
 
@@
 
-\subsubsection{Emission and Absorption}
+%\subsubsection{Emission and Absorption}
+\label{sec:couplingElectronCapture}
 
@@
 \end{equation}
-
-\subsubsection{Neutrino-Electron Scattering (NES)}
-
-When NES is included the internal energy of the fluid evolves according to
-\begin{align}
-  \rho\,d_{t}\epsilon
-  &=-\int_{\bbR^{+}}\int_{\bbR^{+}}\big(4\pi-\cJ(\epsilonNu)\big)R^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu} \\
-  &\hspace{12pt}
-  +\int_{\bbR^{+}}\int_{\bbR^{+}}\cJ(\epsilonNu)\,R^{\Out}(\epsilonNu,\epsilonNu')\,\big(4\pi-\cJ(\epsilonNu)\big)\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu}.  
-\end{align}
-With the semi-implicit approximation (evaluating the NES scattering rates using fluid properties at $t^{n}$), the neutrino number density can be solved for without iterative coupling to the thermodynamic state of the fluid.
-We first define the solution vector $\bcJ=(\cJ_{1},\ldots,\cJ_{M^{\epsilonNu}})^{\mbox{\tiny T}}$, and solve the nonlinear system of equations
-\begin{equation}
-  \bF(\bcJ^{n+1})=0
-  \label{eq:NonlinearSystemNES}
-\end{equation}
-using Newton's method.  
-Here, the $j$th component of the nonlinear system of equations is given by
-\begin{equation}
-  F_{j}(\bcJ^{n+1})
-  =\big(\cJ_{j}^{n+1}-\cJ_{j}^{n}\big)
-  -\dt\,\Big\{\,
-    \big(4\pi-\cJ_{j}^{n+1}\big)\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1}
-    -\cJ_{j}^{n+1}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)\,\Big\},
-\end{equation}
-and the Jacobian matrix is
-\begin{align}
-  \pderiv{\bF}{\bcJ}
-  =\pderiv{F_{j}}{\cJ_{k}}
-  &=\delta_{jk}\,\Big(1+\dt\,\Big\{\sum_{l=1}^{M^{\epsilonNu}}W_{l}^{(2)}\,R_{jl}^{\In,n}\,\cJ_{l}
-  +\sum_{l=1}^{M^{\epsilonNu}}W_{l}^{(2)}\,R_{jl}^{\Out,n}\,\big(4\pi-\cJ_{l}\big)\Big\}\Big) \nonumber \\
-  &\hspace{12pt}
-  -\dt\,\Big\{\big(4\pi-\cJ_{j}\big)\,W_{k}^{(2)}\,R_{jk}^{\In,n}+\cJ_{j}\,W_{k}^{(2)}\,R_{jk}^{\Out,n}\Big\}.
-\end{align}
-When Eq.~\eqref{eq:NonlinearSystemNES} is converged to give $\bcJ^{n+1}$, the fluid energy density is updated as
-\begin{align}
-  \epsilon^{n+1}
-  &=\epsilon^{n}-\f{\dt}{\rho}
-  \Big\{\,
-    \sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\big(4\pi-\cJ_{j}^{n+1}\big)
-    \sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1} \nonumber \\
-    &\hspace{56pt}
-    -\sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\,\cJ_{j}^{n+1}
-    \sum_{k=1}^{M^{\epsilonNu}}W^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)
-  \,\Big\}.
-\end{align}
-
-\subsubsection{Full Interaction Set}
+When elastic scattering is included, the above description remains unchanged, except for $\gamma_{j}^{n}\to\dt\big(\tilde{\chi}_{j}^{n}+\sigma_{j}^{n}\big)$ in Eq.~\eqref{eq:momentEquationMomentumEmAbDiscrete}.
+
+%\subsubsection{Neutrino-Electron Scattering (NES)}
+%
+%When NES is included the internal energy of the fluid evolves according to
+%\begin{align}
+%  \rho\,d_{t}\epsilon
+%  &=-\int_{\bbR^{+}}\int_{\bbR^{+}}\big(4\pi-\cJ(\epsilonNu)\big)R^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu} \\
+%  &\hspace{12pt}
+%  +\int_{\bbR^{+}}\int_{\bbR^{+}}\cJ(\epsilonNu)\,R^{\Out}(\epsilonNu,\epsilonNu')\,\big(4\pi-\cJ(\epsilonNu)\big)\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu}.  
+%\end{align}
+%With the semi-implicit approximation (evaluating the NES scattering rates using fluid properties at $t^{n}$), the neutrino number density can be solved for without iterative coupling to the thermodynamic state of the fluid.
+%We first define the solution vector $\bcJ=(\cJ_{1},\ldots,\cJ_{M^{\epsilonNu}})^{\mbox{\tiny T}}$, and solve the nonlinear system of equations
+%\begin{equation}
+%  \bF(\bcJ^{n+1})=0
+%  \label{eq:NonlinearSystemNES}
+%\end{equation}
+%using Newton's method.  
+%Here, the $j$th component of the nonlinear system of equations is given by
+%\begin{equation}
+%  F_{j}(\bcJ^{n+1})
+%  =\big(\cJ_{j}^{n+1}-\cJ_{j}^{n}\big)
+%  -\dt\,\Big\{\,
+%    \big(4\pi-\cJ_{j}^{n+1}\big)\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1}
+%    -\cJ_{j}^{n+1}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)\,\Big\},
+%\end{equation}
+%and the Jacobian matrix is
+%\begin{align}
+%  \pderiv{\bF}{\bcJ}
+%  =\pderiv{F_{j}}{\cJ_{k}}
+%  &=\delta_{jk}\,\Big(1+\dt\,\Big\{\sum_{l=1}^{M^{\epsilonNu}}W_{l}^{(2)}\,R_{jl}^{\In,n}\,\cJ_{l}
+%  +\sum_{l=1}^{M^{\epsilonNu}}W_{l}^{(2)}\,R_{jl}^{\Out,n}\,\big(4\pi-\cJ_{l}\big)\Big\}\Big) \nonumber \\
+%  &\hspace{12pt}
+%  -\dt\,\Big\{\big(4\pi-\cJ_{j}\big)\,W_{k}^{(2)}\,R_{jk}^{\In,n}+\cJ_{j}\,W_{k}^{(2)}\,R_{jk}^{\Out,n}\Big\}.
+%\end{align}
+%When Eq.~\eqref{eq:NonlinearSystemNES} is converged to give $\bcJ^{n+1}$, the fluid energy density is updated as
+%\begin{align}
+%  \epsilon^{n+1}
+%  &=\epsilon^{n}-\f{\dt}{\rho}
+%  \Big\{\,
+%    \sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\big(4\pi-\cJ_{j}^{n+1}\big)
+%    \sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1} \nonumber \\
+%    &\hspace{56pt}
+%    -\sum_{j=1}^{M^{\epsilonNu}}W_{j}^{(3)}\,\cJ_{j}^{n+1}
+%    \sum_{k=1}^{M^{\epsilonNu}}W^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)
+%  \,\Big\}.
+%\end{align}
+
+%\subsubsection{Full Interaction Set}
+%
+%With the complete interaction set considered in this paper (i.e., emission and absorption, elastic scattering, and NES), the electron fraction and fluid internal energy evolve according to
+%\begin{align}
+%  d_{t}Y_{e}
+%  &=-\f{m_{\mbox{\tiny B}}}{\rho}\int_{\bbR^{+}}\tilde{\chi}\,\big(\cJ_{0}-\cJ\big)\,dV_{\epsilonNu}, \\
+%  \rho\,d_{t}\epsilon
+%  &=-\int_{\bbR^{+}}\tilde{\chi}\,\big(\cJ_{0}-\cJ\big)\,\epsilonNu\,dV_{\epsilonNu} \nonumber \\
+%  &\hspace{12pt}
+%  -\int_{\bbR^{+}}\int_{\bbR^{+}}\big(4\pi-\cJ(\epsilonNu)\big)R^{\In}(\epsilonNu,\epsilonNu')\,\cJ(\epsilonNu')\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu} \nonumber \\
+%  &\hspace{12pt}
+%  +\int_{\bbR^{+}}\int_{\bbR^{+}}\cJ(\epsilonNu)\,R^{\Out}(\epsilonNu,\epsilonNu')\,\big(4\pi-\cJ(\epsilonNu)\big)\,dV_{\epsilonNu'}\,\epsilonNu\,dV_{\epsilonNu},
+%\end{align}
+%and the conserved quantities are the total lepton number
+%\begin{equation}
+%  d_{t}\big(\,\f{\rho}{m_{\mbox{\tiny B}}}Y_{e}+\int_{\bbR^{+}}\cJ\,dV_{\epsilonNu}\,\big)=0,
+%  \label{eq:leptonConservationFull}
+%\end{equation}
+%and the total (fluid plus radiation) energy
+%\begin{equation}
+%  d_{t}\big(\,\rho\,\epsilon+\int_{\bbR^{+}}\cJ\,\epsilonNu\,dV_{\epsilonNu}\,\big)=0.  
+%  \label{eq:energyConservationFull}
+%\end{equation}
+%
+%In the solution to the coupled system, we use Eqs.~\eqref{eq:leptonConservationFull} and \eqref{eq:energyConservationFull} together with the equation for the neutrino number density to form a system of nonlinear equations for the solution vector $\bU=(\bcJ,Y_{e},\epsilon)^{\mbox{\tiny T}}$, i.e.,
+%\begin{equation}
+%  \bF(\bU^{n+1})=0,
+%  \label{eq:nonlinearSystemFull}
+%\end{equation}
+%where, for $j=1,\ldots,M^{\epsilonNu}$,
+%\begin{align}
+%  F_{j}(\bU^{n+1})
+%  &=\big(\cJ_{j}^{n+1}-\cJ_{j}^{n}\big)-\dt\,\tilde{\chi}_{j}^{n}\big(\,\cJ_{0,j}^{n+1}-\cJ_{j}^{n+1}\,\big) \nonumber \\
+%  &\hspace{12pt}
+%  -\dt\,\Big\{\,
+%    \big(4\pi-\cJ_{j}^{n+1}\big)\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1}
+%    -\cJ_{j}^{n+1}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\,R_{jk}^{\Out,n}\,\big(4\pi-\cJ_{k}^{n+1}\big)\,\Big\}.
+%\end{align}
+%The electron fraction is constrained by
+%\begin{equation}
+%  F_{M^{\epsilonNu}+1}(\bU^{n+1})
+%  =Y_{e}^{n+1}-Y_{e}^{n}+\f{m_{\mbox{\tiny B}}}{\rho}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\big(\,\cJ_{k}^{n+1}-\cJ_{k}^{n}\,\big),
+%\end{equation}
+%while the internal energy is constrained by
+%\begin{equation}
+%  F_{M^{\epsilonNu}+2}(\bU^{n+1})
+%  =\epsilon^{n+1}-\epsilon^{n}+\f{1}{\rho}\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(3)}\big(\,\cJ_{k}^{n+1}-\cJ_{k}^{n}\,\big).  
+%\end{equation}
+%The system given by Eq.~\eqref{eq:nonlinearSystemFull} is solved using Newton's method, where $\bU^{n}$ is taken as an initial guess.  
+%The dense Jacobian matrix is computed analytically, except for derivatives of the equilibrium density $\cJ_{0}$, which are computed numerically by taking derivatives of table interpolation functions.
+%The radiation flux is subsequently obtained from
+%\begin{equation}
+%  \bcH_{j}^{n+1}-\bcH_{j}^{n}
+%  =-\dt\,\big(\,\tilde{\chi}_{j}^{n}+\sigma_{j}^{n}+\sigma_{\NES,j}^{n}\,\big)\,\bcH_{j}^{n+1},
+%\end{equation}
+%where
+%\begin{equation}
+%  \sigma_{\NES,j}^{n}
+%  =\sum_{k=1}^{M^{\epsilonNu}}W_{k}^{(2)}\big[\,R_{jk}^{\In,n}\,\cJ_{k}^{n+1}+R_{jk}^{\Out,n}\big(4\pi-\cJ_{k}^{n+1}\big)\,\big].
+%\end{equation}
 
@@
 \subsection{Homogeneous Sphere}
+\label{sec:homogeneousSphereTable}
+
+Here we present results from a multi-group version of the homogeneous sphere problem in Section~\ref{sec:homogeneousSphere}, where we use the tabulated electron capture rates from Section~\ref{sec:electronCapture}.
+The radius of the sphere is set to $R=100$~km, and the computational domain covers the region $r\in[0,500]$~km.  
+We present two versions of the test, one for dense conditions, where the $\rho=10^{13}$~g~cm$^{-3}$, $T=16$~MeV, and $Y_{e}=0.14$ inside $r=R$ (Model B in Table~\ref{tab:tabulatedModels}), and one where $\rho=10^{11}$~g~cm$^{-3}$, $T=8$~MeV, and $Y_{e}=0.15$ inside $r=R$ (Model D in Table~\ref{tab:tabulatedModels}).
+The electron capture rates $\tilde{\chi}$ for these conditions are plotted versus energy $\epsilonNu$ in Figure~\ref{fig:absorptionOpacities_weaklib} (blue and magenta lines, respectively).  
+Outside $r=100$~km, we set $\rho=10^{8}$~g~cm$^{-3}$, $T=0.2$~MeV, and $Y_{e}=0.46$ in both models.
+
+Numerical results, obtained with the DG(2)+SIRK2 scheme using 100 equally sized radial elements and 24 geometrically spaced energy groups covering $\epsilonNu\in[0,300]$~MeV (with a minimum energy bin $\Delta\epsilonNu=1$~MeV), are plotted in Figures \ref{fig:homogeneousSphere1D_weaklib_B} (Model B) and \ref{fig:homogeneousSphere1D_weaklib_D} (Model D).
+In the upper left panel we plot the average density $J/V_{\epsilonNu}$, where
+\begin{equation}
+  J=\int_{\bbR^{+}}\cJ\,dV_{\epsilonNu}
+  \quad\text{and}\quad
+  V_{\epsilonNu}=\int_{\bbR^{+}}dV_{\epsilonNu}.  
+  \label{eq:averageDensity}
+\end{equation}
+In the lower left panel we plot the average flux factor, defined as
+\begin{equation}
+  f_{r}=\f{1}{J}\int_{\bbR^{+}}\cH_{r}\,dV_{\epsilonNu}.  
+  \label{eq:averageFluxFactor}
+\end{equation}
+In the upper right panel we plot the average Eddington factor, defined as
+\begin{equation}
+  \langle\psi\rangle=\f{1}{J}\int_{\bbR^{+}}\psi\,\cJ\,dV_{\epsilonNu}.  
+\end{equation}
+In the lower right panel we plot the mean energy
+\begin{equation}
+  \langle\epsilonNu\rangle=\f{1}{J}\int_{\bbR^{+}}\cJ\,\epsilonNu\,dV_{\epsilonNu}.  
+  \label{eq:meanEnergy}
+\end{equation}
+In each panel we compare the numerical and analytical results (dashed and solid lines, respectively).  
+As can be seen, the agreement between the numerical and analytical results is similar to that observed in Section~\ref{sec:homogeneousSphere}.
 
@@
   \end{center}
-  \caption{Results from solving the multi-group Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ spatial elements and $24$ energy groups, and using material properties from Model~D in Table~\ref{tab:tabulatedModels} to compute the neutrino absorption opacities.
+  \caption{Results from solving the multi-group Homogeneous sphere problem with the DG(2)+SIRK2 method using $100$ spatial elements and $24$ energy groups, and using material properties from Model~B in Table~\ref{tab:tabulatedModels} to compute the neutrino absorption opacities.
     We plot the energy-averaged neutrino density (upper left), flux factor (lower left), Eddington factor (upper right), and mean neutrino energy (lower right) versus radius.  
@@
 
-\subsection{Diffuse Scattering}
-
-\subsection{Relaxation}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.75\textwidth]{./Figures/RelaxationEmissionAbsorption_Spectra_ModelA}
-  \end{center}
-  \caption{Results from solving an emission/absorption relaxation problem with initial material properties given by Model A in Table~\ref{tab:tabulatedModels}.  
-  The neutrino energy spectrum is plotted for various times as the radiation field approaches equilibrium.}
-  \label{fig:RelaxationEmissionAbsorption}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.85\textwidth]{./Figures/RelaxationNES_Spectra.png}
-    \begin{tabular}{cc}
-      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_DensitiesVsTime.png} &
-      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_EnergiesVsTime.png}
-    \end{tabular}
-  \end{center}
-  \caption{Results from solving an NES relaxation problem with initial material properties given by Model C in Table~\ref{tab:tabulatedModels}.}
-  \label{fig:RelaxationNES}
-\end{figure}
+%\subsection{Diffuse Scattering}
+
+%\subsection{Relaxation}
+%
+%\begin{figure}
+%  \begin{center}
+%    \includegraphics[width=0.75\textwidth]{./Figures/RelaxationEmissionAbsorption_Spectra_ModelA}
+%  \end{center}
+%  \caption{Results from solving an emission/absorption relaxation problem with initial material properties given by Model A in Table~\ref{tab:tabulatedModels}.  
+%  The neutrino energy spectrum is plotted for various times as the radiation field approaches equilibrium.}
+%  \label{fig:RelaxationEmissionAbsorption}
+%\end{figure}
+%
+%\begin{figure}
+%  \begin{center}
+%    \includegraphics[width=0.85\textwidth]{./Figures/RelaxationNES_Spectra.png}
+%    \begin{tabular}{cc}
+%      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_DensitiesVsTime.png} &
+%      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_EnergiesVsTime.png}
+%    \end{tabular}
+%  \end{center}
+%  \caption{Results from solving an NES relaxation problem with initial material properties given by Model C in Table~\ref{tab:tabulatedModels}.}
+%  \label{fig:RelaxationNES}
+%\end{figure}
+%
+%\begin{figure}
+%  \begin{center}
+%    \begin{tabular}{cc}
+%      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_DensitiesVsTime_Timestep.png} &
+%      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_EnergiesVsTime_Timestep.png}
+%    \end{tabular}
+%  \end{center}
+%  \caption{Results from the NES relaxation problem with initial material properties given by Model C in Table~\ref{tab:tabulatedModels}, where the timestep $\dt$ has been set to $10^{-5}$~ms (solid lines), $10^{-4}$~ms (dashed lines), and $10^{-3}$~ms (dotted lines).
+In the left panel we plot the occupation density versus time for $\epsilonNu=11.2$~MeV (red lines) and $\epsilonNu=97.5$~MeV (blue lines).
+In the right panel we plot the fluid energy versus time.}
+%  \label{fig:RelaxationNES_Timestep}
+%\end{figure}
+
+\subsection{Deleptonization Problem}
+\label{sec:deleptonizationProblem}
+
+We conclude with a problem mimicking deleptonization in a collapsed stellar core.  
+To this end, we adopt analytic profiles for the initial mass density, temperature, and electron fraction:
+\begin{align}
+  \rho(r)
+  &=0.5\times
+  \big\{\,
+    \rho_{\mbox{\tiny max}}\times\big[\,1-\tanh\big(\,(r-R_{\rho})/H_{\rho}\,\big)\,\big]
+    +\rho_{\mbox{\tiny min}}\times\big[\,1-\tanh\big(\,(R_{\rho}-r)/H_{\rho}\,\big)\,\big]
+  \,\big\}, \\
+  T(r)
+  &=0.5\times
+  \big\{\,
+    T_{\mbox{\tiny max}}\times\big[\,1-\tanh\big(\,(r-R_{T})/H_{T}\,\big)\,\big]
+    +T_{\mbox{\tiny min}}\times\big[\,1-\tanh\big(\,(R_{T}-r)/H_{T}\,\big)\,\big]
+  \,\big\}, \\
+  Y_{e}(r)
+  &=0.5\times
+  \big\{\,
+    Y_{e,\mbox{\tiny min}}\times\big[\,1-\tanh\big(\,(r-R_{Y_{e}})/H_{Y_{e}}\,\big)\,\big]
+    +Y_{e,\mbox{\tiny max}}\times\big[\,1-\tanh\big(\,(R_{Y_{e}}-r)/H_{Y_{e}}\,\big)\,\big]
+  \,\big\}.  
+\end{align}
+For the density profile we set $\rho_{\mbox{\tiny min}}=10^{8}$~g~cm$^{-3}$, $\rho_{\mbox{\tiny max}}=4\times10^{14}$~g~cm$^{-3}$, $R_{\rho}=20$~km, and $H_{\rho}=10$~km.  
+For the temperature profile we set $T_{\mbox{\tiny min}}=5\times10^{9}$~K, $T_{\mbox{\tiny max}}=2.6\times10^{11}$~K, $R_{T}=25$~km, and $H_{T}=20$~km.  
+For the electron fraction profile we set $Y_{e,\mbox{\tiny min}}=0.4$, $Y_{e,\mbox{\tiny max}}=0.46$, $R_{Y_{e}}=45$~km, and $H_{Y_{e}}=10$~km.  
+(The initial temperature and electron fraction profiles are plotted as dotted lines in Figure~\ref{fig:deleptonizationProblemFluid}.)
+The radiation field is initialized by setting the distribution function equal to the local Fermi-Dirac distribution.
+
+In this problem the computational domain covers $r\in[0,100]$~km and $\epsilonNu\in[0,300]$~MeV.  
+We use equally sized spatial elements, while the energy domain is covered by geometrically increasing elements (with the smallest, innermost, energy bin set to $\Delta\epsilonNu=1$~MeV).  
+We evolve until $t=100$~ms.
+
+In Figure~\ref{fig:deleptonizationProblemFluid} we plot fluid quantities versus radius at select times: $t=0$~ms (initial condition, dotted lines), $t=3$~ms (dash-dot), $t=10$~ms (dashed), and $t=100$~ms (solid).
+The results were obtained with the DG(1)+SIRK2 scheme using 200 radial elements and 30 energy bins.  
+We plot the electron fraction (upper left panel); mass fractions of protons and neutrons (black), alpha particles (red), and heavy nuclei (blue) (upper right panel); temperature (lower left); and entropy per baryon (lower right).
+
+%\begin{equation}
+%  \rho(r)=\big[\,1-\Theta(r)\,\big]\,\rho_{1}(r)+\Theta(r)\,\rho_{2}(r)
+%  \label{eq:densityProfile}
+%\end{equation}
+%where the function $\Theta(r)=0.5\times\big[\,1.0+\tanh\big(\,(r-r_{0})/R_{0}\,\big)\,\big]$ transitions smoothly between two density profiles, given by a Gaussian in the central region and a polynomial at larger radii; i.e.,
+%\begin{align}
+%  \rho_{1}(r)
+%  &=\rho_{1,0}\times\exp\big[-(r/R_{1})^{2}\big]
+%  \label{eq:densityProfile1} \\
+%  \rho_{2}(r)
+%  &=\rho_{2,0}\times\big(r/R_{2}\big)^{\alpha},
+%  \label{eq:densityProfile2}
+%\end{align}
+%where $\rho_{1,0}>\rho_{2,0}$ and $\alpha<0$.  
+%We set $\rho_{1,0}=4.5\times10^{14}$, $\rho_{1,0}=1.0\times10^{13}$, $\alpha=-4$, and $R_{1}=10$~km.  
+%Then, by imposing $\rho_{1}(R_{2})=\rho_{2}(R_{2})$, we find $R_{2}=R_{1}\sqrt{\ln(\rho_{1,0}/\rho_{2,0})}\approx19.5$~km.  
+%We also set $r_{0}=R_{2}$ and $R_{0}=1$~km.  
+%With these parameters, the density profile given by Eqs~\eqref{eq:densityProfile}, \eqref{eq:densityProfile1}, and \eqref{eq:densityProfile2} provides a reasonable approximation to the density profile in the post-bounce phase of a realistic supernova model (cf.
+Figure~\ref{fig:analyticDensityProfile}).
+%
+%\begin{figure}
+%  \begin{center}
+%      \includegraphics[scale=0.78]{./Figures/AnalyticDensityProfile}
+%  \end{center}
+%  \caption{Density profile used in the deleptonization problem (solid black line; cf. Eq.~\eqref{eq:densityProfile}).  
+%  It is composed of a Gaussian profile for radii $\lesssim20$~km (dashed black line), and a power law, with $\rho\propto r^{-4}$, for larger radii (dotted black line).  
+%  The density profile from a full physics core-collapse supernova simulation at $100$~ms after core bounce is also plotted (solid red line).  }
+%  \label{fig:analyticDensityProfile}
+%\end{figure}
 
@@
 	\begin{tabular}{cc}
-      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_DensitiesVsTime_Timestep.png} &
-      \includegraphics[width=0.475\textwidth]{./Figures/RelaxationNES_EnergiesVsTime_Timestep.png}
-    \end{tabular}
-  \end{center}
-  \caption{Results from the NES relaxation problem with initial material properties given by Model C in Table~\ref{tab:tabulatedModels}, where the timestep $\dt$ has been set to $10^{-5}$~ms (solid lines), $10^{-4}$~ms (dashed lines), and $10^{-3}$~ms (dotted lines).
-In the left panel we plot the occupation density versus time for $\epsilonNu=11.2$~MeV (red lines) and $\epsilonNu=97.5$~MeV (blue lines).
-In the right panel we plot the fluid energy versus time.}
-  \label{fig:RelaxationNES_Timestep}
-\end{figure}
-
-\subsection{Deleptonization}
-
-We conclude with a problem mimicking the deleptonization of a collapsed stellar core.  
-To this end, we adopt an analytic density profile
-\begin{equation}
-  \rho(r)=\big[\,1-\Theta(r)\,\big]\,\rho_{1}(r)+\Theta(r)\,\rho_{2}(r)
-  \label{eq:densityProfile}
-\end{equation}
-where the function $\Theta(r)=0.5\times\big[\,1.0+\tanh\big(\,(r-r_{0})/R_{0}\,\big)\,\big]$ transitions smoothly between two density profiles, given by a Gaussian in the central region and a polynomial at larger radii; i.e.,
-\begin{align}
-  \rho_{1}(r)
-  &=\rho_{1,0}\times\exp\big[-(r/R_{1})^{2}\big]
-  \label{eq:densityProfile1} \\
-  \rho_{2}(r)
-  &=\rho_{2,0}\times\big(r/R_{2}\big)^{\alpha},
-  \label{eq:densityProfile2}
-\end{align}
-where $\rho_{1,0}>\rho_{2,0}$ and $\alpha<0$.  
-We set $\rho_{1,0}=4.5\times10^{14}$, $\rho_{1,0}=1.0\times10^{13}$, $\alpha=-4$, and $R_{1}=10$~km.  
-Then, by imposing $\rho_{1}(R_{2})=\rho_{2}(R_{2})$, we find $R_{2}=R_{1}\sqrt{\ln(\rho_{1,0}/\rho_{2,0})}\approx19.5$~km.  
-We also set $r_{0}=R_{2}$ and $R_{0}=1$~km.  
-With these parameters, the density profile given by Eqs~\eqref{eq:densityProfile}, \eqref{eq:densityProfile1}, and \eqref{eq:densityProfile2} provides a reasonable approximation to the density profile in the post-bounce phase of a realistic supernova model (cf.
-Figure~\ref{fig:analyticDensityProfile}).
-
-\begin{figure}
-  \begin{center}
-      \includegraphics[scale=0.78]{./Figures/AnalyticDensityProfile}
-  \end{center}
-  \caption{Density profile used in the deleptonization problem (solid black line; cf. Eq.~\eqref{eq:densityProfile}).  
-  It is composed of a Gaussian profile for radii $\lesssim20$~km (dashed black line), and a power law, with $\rho\propto r^{-4}$, for larger radii (dotted black line).  
-  The density profile from a full physics core-collapse supernova simulation at $100$~ms after core bounce is also plotted (solid red line).  }
-  \label{fig:analyticDensityProfile}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-	\includegraphics[width=.85\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction.png}
-	\begin{tabular}{cc}
+	  \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction.png} &
+	  \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MassFractions.png} \\
 	  \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_Temperature.png} &
@@
   \end{center}
-  \caption{Fluid quantities from the deleptonization problem.  Plotted versus radius for various times are electron fraction (top), temperature (bottom left), and entropy per baryon (bottom right).}
-  \label{fig:}
+  \caption{Fluid quantities from the deleptonization problem.
+Plotted versus radius for various times are: electron fraction (top left), mass fractions of protons plus neutrons (black), alpha particles (red), and the mean heavy nucleus (blue; top right), temperature (bottom left), and entropy per baryon (bottom right).}
+  \label{fig:deleptonizationProblemFluid}
 \end{figure}
 
-\begin{equation}
-  J=\int_{\bbR^{+}}\cJ\,dV_{\epsilonNu}
-\end{equation}
-
-\begin{equation}
-  f_{r}=\f{1}{J}\int_{\bbR^{+}}\cH_{r}\,dV_{\epsilonNu}
-\end{equation}
-
-\begin{equation}
-  \bar{\epsilonNu}=\f{1}{J}\int_{\bbR^{+}}\cJ\,\epsilonNu\,dV_{\epsilonNu}
-\end{equation}
-
-\begin{equation}
-  L_{r}=4\pi\,r^{2}\,\int_{\bbR^{+}}\cH_{r}\,\epsilonNu\,dV_{\epsilonNu}
-\end{equation}
+In Figure~\ref{fig:deleptonizationProblemRadiation} we plot radiation quantities versus radius at the same times a in Figure~\ref{fig:deleptonizationProblemFluid}.  
+We plot the energy-integrated density $J$ (upper left; cf.
+Eq.~\eqref{eq:averageDensity}), the average flux factor $f_{r}$ (upper right; cf.
+Eq.~\eqref{eq:averageFluxFactor}), and the mean energy $\langle\epsilonNu\rangle$ (lower left; cf.
+Eq.~\eqref{eq:meanEnergy}).
+In the lower right panel we plot the luminosity
+\begin{equation}
+  L_{r}=4\pi\,r^{2}\,\int_{\bbR^{+}}\cH_{r}\,\epsilonNu\,dV_{\epsilonNu}.  
+\end{equation}
+In these plots we have also indicated with vertical lines the radius where the optical depth,
+\begin{equation}
+  \tau(r)=\int_{\infty}^{r}\tilde{\chi}\,dr,
+\end{equation}
+equals $2/3$.
 
@@
   \caption{Radiation quantities from the deleptonization problem.
-Plotted versus radius for various times are neutrino number density (top left), flux factor (top right), mean energy (bottom left), and luminosity (bottom right).}
-  \label{fig:}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-      \includegraphics[scale=0.78]{./Figures/DeleptonizationProblem1D_Spectra.png}
-  \end{center}
-  \caption{Neutrino energy spectra at various radii for $t=100$~ms (solid lines).  The dashed lines represent equilibrium spectra, computed using local thermodynamic conditions.}
-  \label{fig:}
+Plotted versus radius for various times are neutrino number density (top left), flux factor (top right), mean energy (bottom left), and luminosity (bottom right).
+The radii where the optical depth $\tau=2/3$ are indicated with vertical lines.}
+  \label{fig:deleptonizationProblemRadiation}
 \end{figure}
@@
     \begin{tabular}{cc}
-      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction_SpatialResolution.png} &
-      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MeanEnergy_SpatialResolution.png} \\
-      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction_SpectralResolution.png} &
-      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MeanEnergy_SpectralResolution.png}
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_ElectronFraction_Resolution.png} &
+      \includegraphics[width=.475\textwidth]{./Figures/DeleptonizationProblem1D_MeanEnergy_Resolution.png}
     \end{tabular}
   \end{center}
-  \caption{Results for the deleptonization problem where the spatial and spectral resolution has been varied: the electron fraction (left panels) and mean energy (right panel) are plotted versus radius for $t=100$~ms.}
+  \caption{Results for the deleptonization problem where the spatial and spectral resolution has been varied: the electron fraction (left panel) and mean energy (right panel) are plotted versus radius for $t=100$~ms.
+The black solid line is obtained with the DG(1)+SIRK2 scheme using $N_{r}\times N_{\epsilonNu}=200\times30$ elements, while blue circles represent results obtained with the DG(2)+SIRK2 scheme using $64\times12$ elements.
+}
   \label{fig:}
@@
 
-\section{Miniapp: Collapse of Stellar Iron Core}
+\section{Summary}
+
+We have presented details of the DG scheme the two-moment model for neutrino transport in \thornado.
+
+Test problems.
+
+A version of the code has been made publicly available on GitHub\footnote{\url{https://github.com/ECP-Astro/thornado_mini}}.  
+This release includes the deleptonization problem presented in Section~\ref{sec:deleptonizationProblem}.
+
+Next steps.
+
+%\section{Miniapp: Collapse of Stellar Iron Core}
+
+\clearpage
 
@@
 
-\clearpage
-
 \section{Moment Equations in Commonly Used Coordinate Systems}

### 2018-11-16 Documents/Euler/dgEulerGR.tex
Modified upper limit of pressure to 3*tau
Uncommitted change
Added section RE: linear interpolation error

@@
 \graphicspath{{Figures/}}
+
+\usepackage{float}
 
@@
 
-\subsection{Curvilinear Coordinates}
+\subsection{Curvilinear Coordinates in 1-D}
 NOTE: We assume a conformally-flat, time-independent spatial three-metric:
@@
 We again consider a one-dimensional system of conservation laws, but this time with a curvilinear metric:
-\begin{equation}
-    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF\right)}{1}=\sqrtgm\,\bQ,
+\begin{equation}\label{Eq:1DCurvilinearConsLaw}
+    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF^{i}\right)}{i}=\sqrtgm\,\bQ,\hspace{1em}\text{(no sum on $i$)},
 \end{equation}
@@
 \begin{equation}
-    \bU\longrightarrow\begin{pmatrix} D\\ S_{1}\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v_{1}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{j}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
+    \bU\longrightarrow\begin{pmatrix} D\\ S_{j}\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v_{j}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,\gamma_{jk}\,v^{k}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
 \end{equation}
-$\bF\left(\bU\right)$ are the fluxes of those conserved quantities:
+$\bF^{i}\left(\bU\right)$ are the fluxes in the $x^{i}$-direction of those conserved quantities:
 \begin{equation}
-    \bF\left(\bU\right)\longrightarrow\begin{pmatrix}D\,v^{1}\\ S^{1}\,v_{1}+p\,\delta^{1}_{~1}\\ S^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,v^{1}\,v_{1}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{1}\,v^{j}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix},
+    \bF^{i}\left(\bU\right)\longrightarrow\begin{pmatrix}D\,v^{i}\\ S^{i}\,v_{j}+p\,\delta^{i}_{~j}\\ S^{i}-D\,v^{i}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{i}\\ \rho\,h\,W^{2}\,v^{i}\,v_{j}+p\,\delta^{i}_{~j}\\\rho\,h\,W^{2}\,v^{i}-D\,v^{i}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{i}\\ \rho\,h\,W^{2}\,\gamma_{jk}\,v^{i}\,v^{k}+p\,\delta^{i}_{~j}\\\rho\,h\,W^{2}\,v^{i}-D\,v^{i}\end{pmatrix},
 \end{equation}
@@
 \begin{align}
-    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{kj}\,\pd{\gamma_{kj}}{1}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\pd{\gamma_{11}}{1}+P^{22}\,\pd{\gamma_{22}}{1}+P^{33}\,\pd{\gamma_{33}}{1}\right] \\0\end{pmatrix}\\
-    &=\begin{pmatrix}0\\ P^{11}\,h_{1}\,\pd{\,h_{1}}{1}+P^{22}\,h_{2}\,\pd{\,h_{2}}{1}+P^{33}\,h_{3}\,\pd{\,h_{3}}{1} \\0\end{pmatrix},
+    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{ik}\,\pd{\,\gamma_{ik}}{j}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\pd{\,\gamma_{11}}{j}+P^{22}\,\pd{\,\gamma_{22}}{j}+P^{33}\,\pd{\,\gamma_{33}}{j}\right] \\0\end{pmatrix}\\
+    &=\begin{pmatrix}0\\ P^{11}\,h_{1}\,\pd{\,h_{1}}{j}+P^{22}\,h_{2}\,\pd{\,h_{2}}{j}+P^{33}\,h_{3}\,\pd{\,h_{3}}{j} \\0\end{pmatrix},
 \end{align}
-where we have used the fact that $\gamma_{jj}=\left(h_{j}\right)^{2}$. The $P^{kj}$ are components of the pressure tensor:
+where we have used the fact that $\gamma_{kk}=\left(h_{k}\right)^{2}$. The $P^{ik}$ are components of the pressure tensor:
 \begin{equation}
-    P^{kj}=S^{k}\,v^{j}+p\,\gamma^{kj}=\gamma^{k\ell}\,S_{\ell}\,v^{j}+p\,\gamma^{kj}=\gamma^{k\ell}\,S_{\ell}\,v^{j}+p\,\gamma^{k\ell}\,\delta^{j}_{~\ell}=\gamma^{k\ell}\left(S_{\ell}\,v^{j}+p\,\delta^{j}_{~\ell}\right).
+    P^{ik}=S^{i}\,v^{k}+p\,\gamma^{ik}=\gamma^{i\ell}\,S_{\ell}\,v^{k}+p\,\gamma^{ik}=\gamma^{i\ell}\,S_{\ell}\,v^{k}+p\,\gamma^{i\ell}\,\delta^{k}_{~\ell}=\gamma^{i\ell}\left(S_{\ell}\,v^{k}+p\,\delta^{k}_{~\ell}\right).
 \end{equation}
-Since the spatial three-metric is diagonal we must have that $\ell=k$. We can therefore simplify further:
+Since the spatial three-metric is diagonal the only non-zero term is that with $\ell=i$. We can therefore simplify further:
 \begin{equation}
-    P^{kj}=\gamma^{kk}\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)=\f{1}{\gamma_{kk}}\,\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)=\f{1}{\left(h_{k}\right)^{2}}\,\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)
+    P^{ik}=\gamma^{ii}\left(S_{i}\,v^{k}+p\,\delta^{k}_{~i}\right)=\f{1}{\gamma_{ii}}\,\left(S_{i}\,v^{k}+p\,\delta^{k}_{~i}\right),\hspace{1em}\text{(no sum on $i$)}.
 \end{equation}
-For the pressure-tensor sum, we then have:
+For the source-term sum we then have:
 \begin{equation}\label{Eq:PressureTensorSum}
-    P^{kj}\,\p_{1}\,\gamma_{kj}=P^{kk}\,\p_{1}\,\gamma_{kk}=P^{kk}\,\p_{1}\left(h_{k}\right)^{2}=2\,P^{kk}\,h_{k}\,\p_{1}\,h_{k}=\f{2}{h_{k}}\left(S_{k}\,v^{k}+p\right)\,\p_{1}\,h_{k}.
+    Q_{j}=\f{1}{2}\,P^{ik}\,\p_{j}\,\gamma_{ik}=\f{1}{2}\,P^{kk}\,\p_{j}\,\gamma_{kk}=\f{1}{2}\,P^{kk}\,\p_{j}\left(h_{k}\right)^{2}=P^{kk}\,h_{k}\,\p_{j}\,h_{k}.
 \end{equation}
@@
 \subsubsection{Time-Step Derivation/CFL Condition}
-We start by integrating both sides over $dx^{1}$ and dividing by the volume, $\Delta V_{i}$:
+We start by integrating both sides of \eqref{Eq:1DCurvilinearConsLaw} over $dx^{i}$ and dividing by the volume of the $K^{th}$ element, $\Delta V_{K}$ (recalling that there is no sum on $i$):
 \begin{equation}
-    \f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\pd{\left(\sqrtgm\,\bU_{i}\right)}{t}dx^{1}+\f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\pd{\left(\sqrtgm\,\bF\left(\bU_{i}\right)\right)}{1}dx^{1}=\f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\sqrtgm\,\bQ_{i}\,dx^{1},
+    \f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\pd{\left(\sqrtgm\,\bU\right)}{t}dx^{i}+\f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\pd{\left(\sqrtgm\,\bF^{i}\left(\bU\right)\right)}{i}dx^{i}=\f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\sqrtgm\,\bQ\,dx^{i},
 \end{equation}
@@
 \begin{equation}
-    \Delta V_{i}=\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}dV=\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\sqrtgm\,dx^{1}.
+    \Delta V_{K}=\int_{x^{i}_{L}}^{x^{i}_{H}}dV=\int_{x^{i}_{L}}^{x^{i}_{H}}\sqrtgm\,dx^{i}.
 \end{equation}
@@
 \begin{equation}
-    \ol{\bW}_{i}\equiv\f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\bW_{i}\,dV,
+    \bW_{K}\equiv\f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\bW\,dV,
 \end{equation}
@@
 \begin{equation}
-    \f{d\,\ol{\bU}_{i}}{dt}+\f{1}{\Delta V_{i}}\left.\left(\sqrtgm\,\hat{\bF}\left(\ol{\bU}\right)\right)\right|^{x^{1}_{\iph}}_{x^{1}_{\imh}}=\ol{\bQ}_{i},
+    \f{d\,\bU_{K}}{dt}+\f{1}{\Delta V_{K}}\left.\left(\sqrtgm\,\hat{\bF}\left(\bU\right)\right)\right|^{x^{i}_{H}}_{x^{i}_{L}}=\bQ_{K}.
 \end{equation}
-or, using the common notation of the time step being represented as a superscript and the spatial element represented by a subscript:
+Now, using the common notation of the time step being represented as a superscript $n$:
 \begin{equation}
-    \ol{\bU}^{n+1}_{i}=\ol{\bU}^{n}_{i}-\f{\Delta t_{i}}{\Delta V_{i}}\left[\sqrtgm_{\iph}\,\hat{\bF}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\bF}^{n}_{\imh}\right]+\Delta t_{i}\,\ol{\bQ}^{n}_{i}.
+    \bU^{n+1}_{K}=\bU^{n}_{K}-\f{\Delta t^{n}_{K}}{\Delta V_{K}}\left[\sqrtgm_{H}\,\hat{\bF}^{n}_{H}-\sqrtgm_{L}\,\hat{\bF}^{n}_{L}\right]+\Delta t^{n}_{K}\,\bQ^{n}_{K}.
 \end{equation}
@@
 \begin{equation}
-    \ol{\bU}^{n}_{i}=\ve\,\ol{\bU}^{n}_{i}+\left(1-\ve\right)\ol{\bU}^{n}_{i}.
+    \bU^{n}_{K}=\ve\,\bU^{n}_{K}+\left(1-\ve\right)\bU^{n}_{K}.
 \end{equation}
@@
 \begin{align}
-    \ol{\bU}^{n+1}_{i}&=\ve\left\{\ol{\bU}^{n}_{i}-\f{\Delta t_{i}}{\ve\,\Delta V_{i}}\left[\sqrtgm_{\iph}\,\hat{\bF}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\bF}^{n}_{\imh}\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
-    &=\ve\left\{\ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
-    &=\ve\,\ol{\bH}_{1}+\left(1-\ve\right)\ol{\bH}_{2},
+    \bU^{n+1}_{K}&=\ve\left\{\bU^{n}_{K}-\f{\Delta t^{n}_{K}}{\ve\,\Delta V_{K}}\left[\sqrtgm_{H}\,\hat{\bF}^{n}_{H}-\sqrtgm_{L}\,\hat{\bF}^{n}_{L}\right]\right\}+\left(1-\ve\right)\bU^{n}_{K}+\Delta t^{n}_{K}\,\bQ^{n}_{K}\\
+    &=\ve\left\{\bU^{n}_{K}-\eta^{n}_{K}\left[\sqrtgm_{H}\,\hat{\bF}\left(\bU^{n}_{K+1},\bU^{n}_{K}\right)-\sqrtgm_{L}\,\hat{\bF}\left(\bU^{n}_{K},\bU^{n}_{K-1}\right)\right]\right\}+\left(1-\ve\right)\bU^{n}_{K}+\Delta t^{n}_{K}\,\bQ^{n}_{K}\\
+    &=\ve\,\bH_{K,1}+\left(1-\ve\right)\bH_{K,2},
 \end{align}
@@
 \begin{equation}
-    \ol{\bH}_{1}\equiv \ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right],
+    \bH_{K,1}\equiv \bU^{n}_{K}-\eta^{n}_{K}\left[\sqrtgm_{H}\,\hat{\bF}\left(\bU^{n}_{K+1},\bU^{n}_{K}\right)-\sqrtgm_{L}\,\hat{\bF}\left(\bU^{n}_{K},\bU^{n}_{K-1}\right)\right],
 \end{equation}
 \begin{equation}
-    \ol{\bH}_{2}\equiv\ol{\bU}^{n}_{i}+\f{\Delta t_{i}}{1-\ve}\,\ol{\bQ}^{n}_{i},
+    \bH_{K,2}\equiv\bU^{n}_{K}+\f{\Delta t^{n}_{K}}{1-\ve}\,\bQ^{n}_{K},
 \end{equation}
@@
 \begin{equation}
-    \eta_{i}\equiv\f{\Delta t_{i}}{\ve\,\Delta V_{i}}.
+    \eta^{n}_{K}\equiv\f{\Delta t^{n}_{K}}{\ve\,\Delta V_{K}}.
 \end{equation}
 
-We proceed by focusing on each term individually, starting with the numerical flux term, $\ol{\bH}_{1}$.
+We proceed by focusing on each term individually, starting with the numerical flux term, $\bH_{K,1}$.
 
 \subsubsection{Numerical flux term}
-We have to show that $\ol{\bH}_{1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\ol{\bH}_{1}$:
+We have to show that $\bH_{K,1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\bH_{K,1}$:
 \begin{align}
-    \ol{\bU}^{n}_{i}-\f{\eta_{i}}{2}\Big\{&\sqrtgm_{\iph}\left[\bF\left(\ol{\bU}^{n}_{i+1}\right)+\bF\left(\ol{\bU}^{n}_{i}\right)-\alpha_{\iph}\left(\ol{\bU}^{n}_{i+1}-\ol{\bU}^{n}_{i}\right)\right]\\
-    &-\sqrtgm_{\imh}\left[\bF\left(\ol{\bU}^{n}_{i}\right)+\bF\left(\ol{\bU}^{n}_{i-1}\right)-\alpha_{\imh}\left(\ol{\bU}^{n}_{i}-\ol{\bU}^{n}_{i-1}\right)\right]\Big\}\\
-    &\hspace{-10em}=\left(1-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
-    &\hspace{-8em}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\bF\left(\ol{\bU}^{n}_{i}\right)+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\bF\left(\ol{\bU}^{n}_{i}\right)\\
-    &\hspace{-8em}+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
+    \bU^{n}_{K}-\f{\eta^{n}_{K}}{2}\Big\{&\sqrtgm_{H}\left[\bF\left(\bU^{n}_{K+1}\right)+\bF\left(\bU^{n}_{K}\right)-\alpha^{n}_{H}\left(\bU^{n}_{K+1}-\bU^{n}_{K}\right)\right]\\
+    &-\sqrtgm_{L}\left[\bF\left(\bU^{n}_{K}\right)+\bF\left(\bU^{n}_{K-1}\right)-\alpha^{n}_{L}\left(\bU^{n}_{K}-\bU^{n}_{K-1}\right)\right]\Big\}\\
+    &\hspace{-10em}=\left(1-\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}-\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\right)\bU^{n}_{K}\\
+    &\hspace{-8em}-\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\bF\left(\bU^{n}_{K}\right)+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\bF\left(\bU^{n}_{K}\right)\\
+    &\hspace{-8em}+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\left[\bU^{n}_{K-1}+\f{1}{\alpha^{n}_{L}}\bF\left(\bU^{n}_{K-1}\right)\right]+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\left[\bU^{n}_{K+1}-\f{1}{\alpha^{n}_{H}}\bF\left(\bU^{n}_{K+1}\right)\right].
 \end{align}
-Now we add and subtract $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\,\ol{\bU}^{n}_{i}$ and $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\,\ol{\bU}^{n}_{i}$, yielding:
+Now we add and subtract $\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\,\bU^{n}_{K}$ and $\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\,\bU^{n}_{K}$, yielding:
 \begin{align}
-    &\left(1-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
-    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]\\
-    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
+    &\left(1-\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}-\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\right)\bU^{n}_{K}\\
+    &+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\left[\bU^{n}_{K}-\f{1}{\alpha^{n}_{H}}\bF\left(\bU^{n}_{K}\right)\right]+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\left[\bU^{n}_{K}+\f{1}{\alpha^{n}_{L}}\bF\left(\bU^{n}_{K}\right)\right]\\
+    &+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\left[\bU^{n}_{K-1}+\f{1}{\alpha^{n}_{L}}\bF\left(\bU^{n}_{K-1}\right)\right]+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\left[\bU^{n}_{K+1}-\f{1}{\alpha^{n}_{H}}\bF\left(\bU^{n}_{K+1}\right)\right].
 \end{align}
-All of the terms in square brackets are similar to the $\ol{\bH}$ quantities in \citet{Qin2016}, and are therefore in $\cG$.
+All of the terms in square brackets are similar to the $\bH_{K}$ quantities in \citet{Qin2016}, and are therefore in $\cG$.
 It can easily be seen that the sum of the coefficients is unity.
-The final condition is that the coefficient of $\ol{\bU}^{n}_{i}>0$, or (recalling that $\eta_{i}=\Delta t_{i}/\left(\ve\,\Delta V_{i}\right)$):
+The final condition is that the coefficient of $\bU^{n}_{K}>0$, or (recalling that $\eta^{n}_{K}=\Delta t_{K}/\left(\ve\,\Delta V_{K}\right)$):
 \begin{align}
-    1&-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}>0\implies\eta_{i}\left(\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}\right)<1\\
-    &\implies\Delta t_{i}<\f{\ve\,\Delta V_{i}}{\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}}\leq\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}.
+    1&-\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}-\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}>0\implies\eta^{n}_{K}\left(\sqrtgm_{H}\,\alpha^{n}_{H}+\sqrtgm_{L}\,\alpha^{n}_{L}\right)<1\\
+    &\implies\Delta t^{n}_{K}<\f{\ve\,\Delta V_{K}}{\sqrtgm_{H}\,\alpha^{n}_{H}+\sqrtgm_{L}\,\alpha^{n}_{L}}\leq\f{\ve\,\Delta V_{K}}{2\,\text{max}\left(\sqrtgm_{K\pm\f{1}{2}}\,\alpha^{n}_{K\pm\f{1}{2}}\right)}.
 \end{align}
@@
 \begin{equation}
-    \Delta t<\text{min}_{i}\left(\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right).
+    \Delta t^{n}<\text{min}_{K}\left(\f{\ve\,\Delta V_{K}}{2\,\text{max}\left(\sqrtgm_{K\pm\f{1}{2}}\,\alpha^{n}_{K\pm\f{1}{2}}\right)}\right).
 \end{equation}
@@
 \subsubsubsection{Time-step for Spherical-Polar Coordinates}
-For spherical-polar coordinates in 1-D we have that $\Delta V_{i}=1/3\left(r_{\iph}^{3}-r_{\imh}^{3}\right)$, and (assuming $\alpha_{i\pm\f{1}{2}}=1\ \forall\ i$) $\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)=r_{\iph}^{2}$, so:
+For spherical-polar coordinates in 1-D we have that $\Delta V_{K}=1/3\left(r_{H}^{3}-r_{L}^{3}\right)$, and (assuming $\alpha_{K\pm\f{1}{2}}=1\ \forall\ i$) $\text{max}\left(\sqrtgm_{K\pm\f{1}{2}}\,\alpha_{K\pm\f{1}{2}}\right)=r_{H}^{2}$, so:
 \begin{align}
-    \Delta t&<\text{min}_{i}\left\{\f{\ve\,1/3\left[r_{\iph}^{3}-r_{\imh}^{3}\right]}{2\,r_{\iph}^{2}}\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[1-\f{r_{\imh}^{3}}{r_{\iph}^{3}}\right]\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[1-\left(1-\f{\Delta r_{i}}{r_{\iph}}\right)^{3}\right]\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[1-\left(1+\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{2}-2\frac{\Delta r_{i}}{r_{\iph}}\right)\left(1-\f{\Delta r_{i}}{r_{\iph}}\right)\right]\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{3}-3\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{2}+3\f{\Delta r_{i}}{r_{\iph}}\right]\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,\Delta r_{i}\left[\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{2}-3\left(\f{\Delta r_{i}}{r_{\iph}}\right)+3\right]\right\}.
+    \Delta t&<\text{min}_{i}\left\{\f{\ve\,1/3\left[r_{H}^{3}-r_{L}^{3}\right]}{2\,r_{H}^{2}}\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[1-\f{r_{L}^{3}}{r_{H}^{3}}\right]\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[1-\left(1-\f{\Delta r_{i}}{r_{H}}\right)^{3}\right]\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[1-\left(1+\left(\f{\Delta r_{i}}{r_{H}}\right)^{2}-2\frac{\Delta r_{i}}{r_{H}}\right)\left(1-\f{\Delta r_{i}}{r_{H}}\right)\right]\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[\left(\f{\Delta r_{i}}{r_{H}}\right)^{3}-3\left(\f{\Delta r_{i}}{r_{H}}\right)^{2}+3\f{\Delta r_{i}}{r_{H}}\right]\right\}\\
+    &=\text{min}_{i}\left\{\f{\ve}{6}\,\Delta r_{i}\left[\left(\f{\Delta r_{i}}{r_{H}}\right)^{2}-3\left(\f{\Delta r_{i}}{r_{H}}\right)+3\right]\right\}.
 \end{align}
-We know that $\Delta r_{i}/r_{\iph}\in\left[0,1\right]$; the minimum value of the quadratic function in this domain is unity. So, we have that for spherical-polar coordinates:
+We know that $\Delta r_{i}/r_{H}\in\left[0,1\right]$; the minimum value of the quadratic function in this domain is unity. So, we have that for spherical-polar coordinates:
 \begin{equation}
@@
 \subsubsection{Source term}
-For this section we drop the subscript $i$ and the superscript $n$. We have to show that $\ol{\bH}_{2}\in\cG$, where
+For this section we drop the subscript $K$ and the superscript $n$ (but keep in mind that all quantities are still cell-averages). We have to show that $\bH_{2}\in\cG$, where
 \begin{equation}
-    \ol{\bH}_{2}=\begin{pmatrix}\ol{D}\\ \ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}} \\ \ol{\tau}\end{pmatrix},\hspace{1em}\left(\ol{H}_{2}\right)_{1}>0,\hspace{1em}\left(\ol{H}_{2}\right)_{3}+\left(\ol{H}_{2}\right)_{1}>\sqrt{\left(\ol{H}_{2}\right)_{1}\left(\ol{H}_{2}\right)_{1}+\left(\ol{H}_{2}\right)_{2}\left(\ol{H}_{2}\right)^{2}}.
+    \bH_{2}=\begin{pmatrix}D\\ S_{j}+\f{\Delta t}{1-\ve}\,Q_{j} \\ \tau\end{pmatrix},\hspace{1em}\left(H_{2}\right)_{1}>0,\hspace{1em}\left(H_{2}\right)_{5}+\left(H_{2}\right)_{1}>\sqrt{\left(H_{2}\right)_{1}\left(H_{2}\right)_{1}+\left(H_{2}\right)_{j}\left(H_{2}\right)^{j}}.
 \end{equation}
 
-It is clear that the first requirement for $\ol{\bH}_{2}$ is met, i.e. $\ol{D}>0$. The second requirement is:
+It is clear that the first requirement for $\bH_{2}$ is met, i.e. $D>0$. The second requirement is:
 \begin{align}
-    \ol{D}+\ol{\tau}&>\sqrt{\ol{D}^{2}+\left[\ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] \left[\ol{S}^{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\p^{1}\,\gamma_{kk}}\right] }\\
-    &=\sqrt{\ol{D}^{2}+\left[\ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] \left[\ol{S}^{1}+\gamma^{11}\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] }\\
-    &=\sqrt{\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}+\gamma^{11}\left[\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{2\left(1-\ve\right)}\right]^{2}\left(\Delta t\right)^{2}+\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{2\left(1-\ve\right)}\left[\ol{S}_{1}\,\gamma^{11}+\ol{S}^{1}\right]\Delta t}\\
-    &=\sqrt{a\left(\Delta t\right)^{2}+b\,\Delta t+c}\geq0,
+    D+\tau&>\sqrt{D^{2}+\left[S_{j}+\f{\Delta t}{1-\ve}Q_{j}\right] \left[S^{j}+\f{\Delta t}{1-\ve}Q^{j}\right]}\\
+    &=\sqrt{D^{2}+S_{j}\,S^{j}+\f{\Delta t}{1-\ve}\left(S_{j}\,Q^{j}+S^{j}\,Q_{j}\right)+\left(\f{\Delta t}{1-\ve}\right)^{2}\,Q_{j}\,Q^{j}}
 \end{align}
-where
+Now we square both sides:
 \begin{align}
-    a&=\left[\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{2\,\sqrt{\ol{\gamma_{11}}}\left(1-\ve\right)}\right]^{2}\geq0\\
-    b&=\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{\ol{\gamma_{11}}\left(1-\ve\right)}\ol{S}_{1}=\f{2\,\ol{S}_{1}}{\sqrt{\ol{\gamma_{11}}}}\sqrt{a}\\
-    c&=\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}\geq0.
-\end{align}
-The condition for a quadratic function to be positive-definite is that $a>0$ (concave-up) and $b^{2}-4\,a\,c<0$ (no real roots). The first condition is clearly met. For the second condition:
-\begin{equation}
-    b^{2}-4\,a\,c=\f{4\left(\ol{S}_{1}\right)^{2}}{\ol{\gamma_{11}}}a-4\,a\left(\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}\right)=4\,\ol{S}_{1}\,\ol{S}^{1}\,a-4\,a\ol{D}^{2}-4\,a\,\ol{S}_{1}\,\ol{S}^{1}=-4\,a\,\ol{D}^{2}<0.
-\end{equation}
-So, the square root is always positive.
-
-With that we have:
-\begin{align}
-    &\ol{D}^{2}+\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}>a\left(\Delta t\right)^{2}+b\,\Delta t+c\\
-    &\implies a\left(\Delta t\right)^{2}+b\,\Delta t+c'<0,
+    &D^{2}+\tau^{2}+2\,D\,\tau>D^{2}+S_{j}\,S^{j}+\f{\Delta t}{1-\ve}\left(S_{j}\,Q^{j}+S^{j}\,Q_{j}\right)+\left(\f{\Delta t}{1-\ve}\right)^{2}\,Q_{j}\,Q^{j}\\
+    \implies&\tau\left(\tau+2\,D\right)>\gamma^{jk}\,S_{j}\,S_{k}+\f{2\,\Delta t}{1-\ve}\,\gamma^{jk}\,S_{j}\,Q_{k}+\left(\f{\Delta t}{1-\ve}\right)^{2}\,\gamma^{jk}\,Q_{j}\,Q_{k}\\
+    \implies&\tau\left(\tau+2\,D\right)>\f{S_{j}\,S_{k}}{\gamma_{jk}}+\f{2\,\Delta t}{1-\ve}\,\f{S_{j}\,Q_{k}}{\gamma_{jk}}+\left(\f{\Delta t}{1-\ve}\right)^{2}\,\f{Q_{j}\,Q_{k}}{\gamma_{jk}}\\
+    \implies&a\left(\Delta t\right)^{2}+b\,\Delta t+c<0,
 \end{align}
 where:
+\begin{align}
+    a&=\f{1}{\left(1-\ve\right)^{2}}\,\vv{Q}\cdot\vv{Q}=\f{1}{\left(1-\ve\right)^{2}}\,\f{Q_{j}\,Q_{k}}{\gamma_{jk}}=\f{1}{\left(1-\ve\right)^{2}}\sum\limits_{k=1}^{3}\f{\left(Q_{k}\right)^{2}}{\gamma_{kk}}\\
+    b&=\f{2}{1-\ve}\,\vv{S}\cdot\vv{Q}=\f{2}{1-\ve}\,\f{S_{j}\,Q_{k}}{\gamma_{jk}}=\f{2}{1-\ve}\sum\limits_{k=1}^{3}\f{S_{k}\,Q_{k}}{\gamma_{kk}}\\
+    c&=-\tau\left(\tau+2\,D\right)+\vv{S}\cdot\vv{S}=-\tau\left(\tau+2\,D\right)+\sum\limits_{k=1}^{3}\f{\left(S_{k}\right)^{2}}{\gamma_{kk}}.
+\end{align}
+We want to make sure that our function has at least one real root, which means we must have that $b^{2}-4\,a\,c\geq0$:
+\begin{align}
+    b^{2}-4\,a\,c&=\f{4}{\left(1-\ve\right)^{2}}\left(\vv{S}\cdot\vv{Q}\right)^{2}-\f{4}{\left(1-\ve\right)^{2}}\,\vv{Q}\cdot\vv{Q}\left[-\tau\left(\tau+2\,D\right)+\vv{S}\cdot\vv{S}\right]\\
+    &=\f{4}{\left(1-\ve\right)^{2}}\left[\left(\vv{S}\cdot\vv{Q}\right)^{2}-\left(\vv{Q}\cdot\vv{Q}\right)\left(\vv{S}\cdot\vv{S}\right)+\tau\left(\tau+2\,D\right)\vv{Q}\cdot\vv{Q}\right]\\
+    &=\f{4}{\left(1-\ve\right)^{2}}\left[\left|\vv{S}\right|^{2}\left|\vv{Q}\right|^{2}\,\cos^{2}\theta_{SQ}-\left|\vv{Q}\right|^{2}\left|\vv{S}\right|^{2}+\tau\left(\tau+2\,D\right)\left|\vv{Q}\right|^{2}\right]\\
+    &=\f{4}{\left(1-\ve\right)^{2}}\left|\vv{Q}\right|^{2}\left[\tau\left(\tau+2\,D\right)-\left|\vv{S}\right|^{2}\left(1-\cos^{2}\theta_{SQ}\right)\right]\\
+    &=\f{4}{\left(1-\ve\right)^{2}}\left|\vv{Q}\right|^{2}\left[\tau\left(\tau+2\,D\right)-\left|\vv{S}\right|^{2}\sin^{2}\theta_{SQ}\right],
+\end{align}
+where $\theta_{SQ}$ is the angle between the momentum-density vector and the source-term vector. To guarantee at least one real root we must have that
 \begin{equation}
-  c'=c-\ol{D}^{2}-\ol{\tau}^{2}-2\,\ol{D}\,\ol{\tau}=\ol{S}_{1}\,\ol{S}^{1}-\ol{\tau}^{2}-2\,\ol{D}\,\ol{\tau}.
+    \tau\left(\tau+2\,D\right)\geq\left|\vv{S}\right|^{2}\,\sin^{2}\theta_{SQ}.
 \end{equation}
 
-This time we want to make sure that our function has at least one real root. We still have that $a>0$, so now we check if $b^{2}-4\,a\,c'>0$:
+\newpage
 \begin{equation}
-    b^{2}-4\,a\,c'=\f{4\left(\ol{S}_{1}\right)^{2}}{\ol{\gamma_{11}}}a-4\,a\left(\ol{S}_{1}\,\ol{S}^{1}-\ol{\tau}^{2}-2\,\ol{D}\,\ol{\tau}\right)=4\,a\,\ol{\tau}\left(\ol{\tau}+2\,\ol{D}\right).
+    b^{2}-4\,a\,c'=\f{4\left(S_{1}\right)^{2}}{\gamma_{11}}a-4\,a\left(S_{1}\,S^{1}-\tau^{2}-2\,D\,\tau\right)=4\,a\,\tau\left(\tau+2\,D\right).
 \end{equation}
-Since $\ol{\tau}\geq0$, we must have that $\ol{\tau}>-2\,\ol{D}$. But, from condition two for $\ol{\bH}_{2}$ we have that $\ol{\tau}>-\ol{D}$, so this condition is automatically satisfied.
+Since $\tau\geq0$, we must have that $\tau>-2\,D$. But, from condition two for $\bH_{K,2}$ we have that $\tau>-D$, so this condition is automatically satisfied.
 
@@
 \begin{align}
-    \Delta t&=\f{-b}{2\,a}\pm\f{1}{2\,a}\sqrt{b^{2}-4\,a\,c'}=\f{-\ol{S}_{1}}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\pm\f{1}{2\,a}\sqrt{\f{4\ol{S}_{1}^{2}}{\ol{\gamma_{11}}}a-4\,a\,c'}\\
-    &=\f{-\ol{S}_{1}}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\pm\f{1}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\sqrt{\ol{S}_{1}^{2}-c'\,\ol{\gamma_{11}}}=\f{1}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\left[-\ol{S}_{1}\pm\sqrt{\ol{S}_{1}^{2}-c'\,\ol{\gamma_{11}}}\right]\\
-    &=\f{1}{\sqrt{\ol{\gamma_{11}}}\,\sqrt{a}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\left(\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}\right)}\right]\\
-    &=\f{2\left(1-\ve\right)}{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\left(\ol{\tau}^{2}+2\,\ol{D}\,\ol{\tau}\right)}\right]\\
-    &=\f{2\left(1-\ve\right)}{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\,\ol{\tau}\left(\ol{\tau}+2\,\ol{D}\right)}\right].
+    \Delta t&=\f{-b}{2\,a}\pm\f{1}{2\,a}\sqrt{b^{2}-4\,a\,c'}=\f{-S_{1}}{\sqrt{\gamma_{11}}\,\sqrt{a}}\pm\f{1}{2\,a}\sqrt{\f{4S_{1}^{2}}{\gamma_{11}}a-4\,a\,c'}\\
+    &=\f{-S_{1}}{\sqrt{\gamma_{11}}\,\sqrt{a}}\pm\f{1}{\sqrt{\gamma_{11}}\,\sqrt{a}}\sqrt{S_{1}^{2}-c'\,\gamma_{11}}=\f{1}{\sqrt{\gamma_{11}}\,\sqrt{a}}\left[-S_{1}\pm\sqrt{S_{1}^{2}-c'\,\gamma_{11}}\right]\\
+    &=\f{1}{\sqrt{\gamma_{11}}\,\sqrt{a}}\left[-S_{1}\pm\sqrt{\gamma_{11}\left(\tau^{2}+2\,D\,\tau\right)}\right]\\
+    &=\f{2\left(1-\ve\right)}{P^{kk}\,\p_{1}\,\gamma_{kk}}\left[-S_{1}\pm\sqrt{\gamma_{11}\left(\tau^{2}+2\,D\,\tau\right)}\right]\\
+    &=\f{2\left(1-\ve\right)}{P^{kk}\,\p_{1}\,\gamma_{kk}}\left[-S_{1}\pm\sqrt{\gamma_{11}\,\tau\left(\tau+2\,D\right)}\right].
 \end{align}
@@
 \begin{equation}
-    \Delta t<\text{min}\left\{\text{min}_{i}\left(\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right),\text{min}^{n}_{i}\left(\f{2\left(1-\ve\right)}{\ol{P^{kk}\,\p_{1}\,\gamma_{kk}}}\left[-\ol{S}_{1}\pm\sqrt{\ol{\gamma_{11}}\,\ol{\tau}\left(\ol{\tau}+2\,\ol{D}\right)}\right]\right)\right\}.
+    \Delta t<\text{min}\left\{\text{min}_{i}\left(\f{\ve\,\Delta V_{K}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right),\text{min}^{n}_{i}\left(\f{2\left(1-\ve\right)}{P^{kk}\,\p_{1}\,\gamma_{kk}}\left[-S_{1}\pm\sqrt{\gamma_{11}\,\tau\left(\tau+2\,D\right)}\right]\right)\right\}.
 \end{equation}
@@
 so,
+%\begin{equation}
+%    \tau=D\left(W+\f{\Gamma}{\Gamma-1}\f{p\,W^{2}}{D}-1\right)-p=D\left(W-1\right)+p\left(\f{\Gamma}{\Gamma-1}W^{2}-1\right).
+%\end{equation}
+%So,
+%\begin{equation}
+%    p=\f{\tau-D\left(W-1\right)}{\f{\Gamma}{\Gamma-1}W^{2}-1}.
+%\end{equation}
+%We also have:
+%\begin{equation}
+%    W=\left(1-v^{i}\,v_{i}\right)^{-1/2}=\left(1-\f{S^{i}\,S_{i}}{\left(\tau+D+p\right)^{2}}\right)^{-1/2}.
+%\end{equation}
+%Treating $p$ as an independent variable \sd{is this valid?}, we have:
+%\begin{equation}
+%    W\Big|_{p\rightarrow\infty}=1,
+%\end{equation}
+%which gives us an upper limit:
+%\begin{equation}
+%    p\leq\f{\Gamma-1}{\Gamma}\,\tau.
+%\end{equation}
+%Just to be safe, in the code we multiply this by two, so that:
+%\begin{equation}
+%    p\leq2\,\f{\Gamma-1}{\Gamma}\,\tau.
+%\end{equation}
 \begin{equation}
-\tau=D\left(W+\f{\Gamma}{\Gamma-1}\f{p\,W^{2}}{D}-1\right)-p=D\left(W-1\right)+p\left(\f{\Gamma}{\Gamma-1}W^{2}-1\right).
+    \tau=D\left(W+\f{\Gamma}{\Gamma-1}\f{p\,W^{2}}{D}-1\right)-p=D\left(W-1\right)+p\left(\f{\Gamma}{\Gamma-1}W^{2}-1\right)>p\left(\f{\Gamma}{\Gamma-1}-1\right)=\f{p}{\Gamma-1}.
 \end{equation}
@@
 \begin{equation}
-p=\f{\tau-D\left(W-1\right)}{\f{\Gamma}{\Gamma-1}W^{2}-1}.
+    p<\left(\Gamma-1\right)\tau.
 \end{equation}
-We also have:
+Typically, $\Gamma-1<3$. So, we end up with:
 \begin{equation}
-W=\left(1-v^{i}\,v_{i}\right)^{-1/2}=\left(1-\f{S^{i}\,S_{i}}{\left(\tau+D+p\right)^{2}}\right)^{-1/2}.
+    p<3\,\tau.
 \end{equation}
-Treating $p$ as an independent variable \sd{is this valid?}, we have:
+
+\newpage
+
+\section{Error Introduced by Linear Interpolation}
+We obtain the initial conditions for the standing accretion shock problem with an external code.
+We then have to interpolate these data onto the grid for use in \texttt{thornado}.
+We start by proving that linear interpolation is a convex combination of the solution at the boundary points.
+
+\subsection{Proof that Linear Interpolation is a Convex Combination of Boundary-Points}
+Linear interpolation of a function, $f$, of a variable, $r$, bounded by two points $r_{L}$ and $r_{H}$, with $r_{H}>r_{L}$, can be written as:
 \begin{equation}
-W\Big|_{p\rightarrow\infty}=1,
+    f\left(r\right)=f\left(r_{L}\right)+\f{f\left(r_{H}\right)-f\left(r_{L}\right)}{r_{H}-r_{L}}\left(r-r_{L}\right).
 \end{equation}
-which gives us an upper limit:
+By making a change of variables from $r$ to $\eta$, where:
 \begin{equation}
-p\leq\f{\Gamma-1}{\Gamma}\,\tau.
+    r\left(\eta\right)=\eta\,r_{H}+\left(1-\eta\right)r_{L}=r_{L}+\eta\,\Delta r\implies\eta=\f{r-r_{L}}{\Delta r},\hspace{1em}\eta\in\left[0,1\right],
 \end{equation}
-Just to be safe, in the code we multiply this by two, so that:
+such that $r\left(\eta=0\right)=r_{L}$ and $r\left(\eta=1\right)=r_{H}$, we have that:
+\begin{align}
+    f\left(\eta\right)&=f\left(0\right)+\f{f\left(1\right)-f\left(0\right)}{1-0}\left(\eta-0\right)=f\left(0\right)+\left(f\left(1\right)-f\left(0\right)\right)\eta\\
+    \implies f\left(\eta\right)&=\eta\,f\left(1\right)+\left(1-\eta\right)f\left(0\right).
+\end{align}
+
+So when we interpolate a fluid variable, say the mass-density $\rho$, we have:
 \begin{equation}
-p\leq2\,\f{\Gamma-1}{\Gamma}\,\tau.
+    \rho\left(r\right)=\rho_{L}+\f{\Delta\rho}{\Delta r}\left(r-r_{L}\right)\longrightarrow\rho\left(\eta\right)=\eta\,\rho_{H}+\left(1-\eta\right)\rho_{L},
 \end{equation}
+where $\rho_{L}\equiv\rho\left(r_{L}\right)$ and $\rho_{H}=\rho\left(r_{H}\right)$.
+
+\subsection{Example: $f\left(x\right)=x^{2}$}
+We can show this directly for simple functions. We take as an example $f\left(x\right)=x^{2}$:
+\begin{align}
+    f\left(x\right)&=x^{2}=\left[x_{L}+\eta\left(x_{R}-x_{L}\right)\right]^{2}=x_{L}^{2}+\eta^{2}\left(x_{R}-x_{L}\right)^{2}+2\,x_{L}\,\eta\left(x_{R}-x_{L}\right)\\
+    &=x_{L}^{2}+\eta^{2}\,x_{R}^{2}+\eta^{2}\,x_{L}^{2}-2\,\eta^{2}\,x_{L}\,x_{R}+2\,\eta\,x_{L}\,x_{R}-2\,\eta\,x_{L}^{2}.
+\end{align}
+Now we add and subtract the interpolated solution: $\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}$. This yields:
+\begin{align}
+    x^{2}&=x_{L}^{2}+\eta^{2}\,x_{R}^{2}+\eta^{2}\,x_{L}^{2}-2\,\eta^{2}\,x_{L}\,x_{R}+2\,\eta\,x_{L}\,x_{R}-2\,\eta\,x_{L}^{2}+\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}-\eta\,x_{H}^{2}-\left(1-\eta\right)x_{L}^{2}\\
+    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]+\left[-\eta\left(1-\eta\right)x_{L}^{2}-\eta\left(1-\eta\right)x_{H}^{2}+2\,\eta\,x_{L}\,x_{H}\left(1-\eta\right)\right]\\
+    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left[x_{L}^{2}+x_{H}^{2}-2\,x_{L}\,x_{H}\right]\\
+    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left(x_{H}-x_{L}\right)^{2}\\
+    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left(\Delta x\right)^{2}.
+\end{align}
+The term in square brackets is the interpolated solution, and the second term is the remainder, i.e. the error in the interpolated solution. We show the results of this in the following figure:
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.75]{LinearInterpolationError}
+\end{figure}
+
+\subsection{Mass Constant}
+The mass constant, $C_{D}$, from the 3+1 GR hydrodynamics equations is:
+\begin{equation}
+    C_{D}\left(r\right)=\psi\left(r\right)^{6}\,\alpha\left(r\right)\,r^{2}\,\rho\left(r\right)\,W\left[v\left(r\right)\right]\,v\left(r\right).
+\end{equation}
+From the data we have this exact value at the two endpoints:
+\begin{align}
+    C_{D}\left(r_{L}\right)&\equiv C^{L}_{D}=\psi_{L}^{6}\,\alpha_{L}\,r_{L}^{2}\,\rho_{L}\,W_{L}\,v_{L}\\
+    C_{D}\left(r_{H}\right)&\equiv C^{H}_{D}=\psi_{H}^{6}\,\alpha_{H}\,r_{H}^{2}\,\rho_{H}\,W_{H}\,v_{H}.
+\end{align}
 

### 2018-11-19 Documents/Euler/dgEulerGR.tex
Added to dgEulerGR.tex

@@
 \end{align}
-The term in square brackets is the interpolated solution, and the second term is the remainder, i.e. the error in the interpolated solution. We show the results of this in the following figure:
+The term in square brackets is the interpolated solution, and the second term is the remainder, i.e.
+the error in the interpolated solution.
+So we see that when using linear interpolation to interpolate the function $f\left(x\right)=x^{2}$ we introduce an error (of the order $\left(\Delta x\right)^{2}$) that goes to zero as the step-size goes to zero.
+
+As a final step we replace $\eta$ with $x$, yielding:
+\begin{align}
+    f\left(x\right)=x^{2}&=x_{L}^{2}+\f{x_{H}^{2}-x_{L}^{2}}{x_{H}-x_{L}}\left(x-x_{L}\right)-\left(x-x_{L}\right)\left(x_{H}-x\right)\\
+    &=f\left(x_{L}\right)+\f{\Delta f}{\Delta x}\left(x-x_{L}\right)-\left(x-x_{L}\right)\left(x_{H}-x\right).
+\end{align}
+
+We show the results of this in the following figure:
 \begin{figure}[H]
@@
 \end{equation}
+When we map from the radial coordinates from the original data to the mesh in \texttt{thornado} we don't introduce any error, because it is a linear map.
+This means that all the error we introduce must be due to $\rho$, $W$, and $v$.
+So, when deriving the error we consider the different function:
+\begin{equation}
+    C'_{D}\left(r\right)\equiv\f{C_{D}\left(r\right)}{\psi\left(r\right)^{6}\,\alpha\left(r\right)\,r^{2}}=\rho\left(r\right)\,W\left[v\left(r\right)\right]\,v\left(r\right).
+\end{equation}
+
 From the data we have this exact value at the two endpoints:
 \begin{align}
-    C_{D}\left(r_{L}\right)&\equiv C^{L}_{D}=\psi_{L}^{6}\,\alpha_{L}\,r_{L}^{2}\,\rho_{L}\,W_{L}\,v_{L}\\
-    C_{D}\left(r_{H}\right)&\equiv C^{H}_{D}=\psi_{H}^{6}\,\alpha_{H}\,r_{H}^{2}\,\rho_{H}\,W_{H}\,v_{H}.
+    C'_{D}\left(r_{L}\right)&\equiv C'^{L}_{D}=\rho_{L}\,W_{L}\,v_{L}\\
+    C'_{D}\left(r_{H}\right)&\equiv C'^{H}_{D}=\rho_{H}\,W_{H}\,v_{H}.
 \end{align}

### 2018-11-21 Documents/Euler/dgEulerGR.tex

@@
 \author{Samuel J Dunham\altaffilmark{1}, Eirik Endeve\altaffilmark{2}, et al.}
-\altaffiltext{2}{Department of Astronomy, Vanderbilt University, 6301 Stevenson Science Center, Nashville TN, 37212, USA; samuel.j.dunham@vanderbilt.edu}
+\altaffiltext{1}{Department of Astronomy, Vanderbilt University, 6301 Stevenson Science Center, Nashville TN, 37212, USA; samuel.j.dunham@vanderbilt.edu}
 \altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}

### 2018-11-24 Documents/Euler/Astronum_2018/ms_endeve.tex
Inclusion of figures in manuscript

@@
 \usepackage{amsthm}
-\usepackage{graphicx}
+\usepackage{graphicx,wrapfig}
 \usepackage{hyperref}
@@
 
+\subsubsection{Isentropic Vortex}
+
+\begin{wrapfigure}{l}{2.825in}
+  \includegraphics[width=18pc]{./Figures/IsentropicVortex_Astronum_2018}
+  \caption{\label{fig:IsentropicVortex}Convergence results for the Isentropic Vortex test.}
+\end{wrapfigure}
+
 \subsubsection{Kelvin-Helmholtz (KH) instability}
@@
 
+\begin{wrapfigure}{r}{2.825in}
+  \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_TCI_24_Astronum_2018}
+  \caption{\label{fig:KelvinHelmholtz_TCI}Distribution of elements flagged for limiting in the KH test at $t=2.4$.}
+\end{wrapfigure}
+
 \subsubsection{Liska-Wendroff implosion}
@@
 In the right panel of Figure~\ref{fig:Implosion}, the chatacteristic ``jet'' has formed and propagates along the diagonal, similar to that displayed by CLAW and WENO in \cite{liskaWendroff_2003}.
+
+\subsubsection{Liska-Wendroff Explosion}
+
+\begin{figure}[h]
+  \centering
+  \begin{minipage}{18pc}
+    \includegraphics[width=18pc]{./Figures/Explosion_Astronum_2018}
+  \end{minipage}\hspace{0.5pc}%
+  \begin{minipage}{18pc}
+    \includegraphics[width=18pc]{./Figures/Explosion_TCI_Astronum_2018}
+  \end{minipage}
+  \caption{\label{fig:Implosion}Plots for the Liska-Wendroff Explosion problem at $t=3.2$.}
+\end{figure}
 

### 2018-11-28 Documents/Euler/SamsTexFiles/BP_Methods_FirstOrder_DGScheme.tex
Added folder with Sams tex files to simplify document

--- 2018-11-16 Documents/Euler/dgEulerGR.tex
@@
-\documentclass[10pt,preprint]{aastex}
-
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{booktabs}
-\usepackage{mathrsfs}
-\usepackage{cite}
-\usepackage{times}
-\usepackage{url}
-\usepackage{hyperref}
-\usepackage{lineno}
-\usepackage{yhmath}
-\usepackage{natbib}
-\usepackage{../definitions}
-\hypersetup{
-  bookmarksnumbered = true,
-  bookmarksopen=false,
-  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
-  pdffitwindow=true,      % window fit to page when opened
-  pdfnewwindow=true, % links in new window
-  colorlinks=true,           % false: boxed links; true: colored links
-  linkcolor=blue,            % color of internal links
-  citecolor=magenta,    % color of links to bibliography
-  filecolor=magenta,     % color of file links
-  urlcolor=cyan              % color of external links
-}
-
-\usepackage{graphicx}
-\newtheorem{remark}{Remark}
-\graphicspath{{Figures/}}
-
-\usepackage{float}
-
-\begin{document}
-
-\title{Nodal Discontinuous Galerkin Method for the Euler Equations in GR}
-\author{Samuel J Dunham\altaffilmark{1}, Eirik Endeve\altaffilmark{2}, et al.}
-\altaffiltext{2}{Department of Astronomy, Vanderbilt University, 6301 Stevenson Science Center, Nashville TN, 37212, USA; samuel.j.dunham@vanderbilt.edu}
-\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
-
-\tableofcontents
-
-\section{Discontinuous Galerkin Scheme}
-\label{sec:dgMethod}
-
-We assume a spacetime metric
-\begin{equation}
-  ds^{2}=-\alpha^{2}\,dt^{2}+\gamma_{ij}\,dx^{i}\,dx^{j},
-\end{equation}
-and consider the system of conservation laws with sources
-\begin{equation}
-  \pd{}{t}\big(\sqrt{\gamma}\,\bU\big)+\sum_{i=1}^{d}\pd{}{i}\big(\alpha\,\sqrt{\gamma}\,\bF^{i}(\bU)\big)=\alpha\,\sqrt{\gamma}\,\bG(\bU),
-  \label{eq:conservationLaws}
-\end{equation}
-where
-\begin{align}
-  \bU
-  &=\big(D,\,S_{j},\,\tau\big)^{\mbox{\tiny T}}
-  =\big(\rho\,W,\,\rho\,h\,W^{2}\,v_{j},\,\rho\,W\left(h\,W-1\right)-p\big)^{\mbox{\tiny T}}, \\
-  \bF^{i}(\bU)
-  &=\big(D\,v^{i},\,\big)^{\mbox{\tiny T}}
-\end{align}
-
 \section{Bound-Preserving Methods Using First-Order DG Scheme}
@@
 \end{equation}
-
-\section{Computing the Time-Step Using Higher-Order DG Schemes}
-
-When making the jump to higher-order DG schemes, we can simply do the same as in the first-order scheme, except we compute the quantities in all of the nodal points instead of using a cell-average.
-This is valid because the cell-average is a convex combination...\sd{Need to expand on this}.
-The proof starts with the discretized equation valid at each quadrature point, $q$:
-\begin{equation}
-    \bU_{q}^{n+1}=\bU_{q}^{n}+\Delta t\,\cL_{q}^{n},
-\end{equation}
-where $\cL_{q}^{n}$ is a general form of the RHS at time $t^{n}$.
-If we define a vector $\ol{\bU}\equiv\left(\bU_{1},\cdots,\bU_{q},\cdots,\bU_{Q}\right)^T$, where $Q$ is the total number of quadrature points, and $\ol{\bW}\equiv\left(\bW_{1},\cdots,\bW_{q},\cdots,\bW_{Q}\right)^T$ as a vector of quadrature weights, then we can write the cell-average of $\bU$ as:
-\begin{equation}
-    \bU_{K}\equiv\ol{\bW}^T\ol{\bU}.
-\end{equation}
-If we then compute the cell-average of the above equation, we get:
-\begin{equation}
-    \bU_{K}^{n+1}=\bU_{K}^{n}+\Delta t\,\ol{\bW}^{T}\,\ol{\cL}_{q}^{n}=\ol{\bW}^{T}\left(\ol{\bU}^{n}+\Delta t\,\ol{\cL}^{n}\right)
-\end{equation}
-
-\newpage
-\section{Recovery of Primitive Variables}
-In order to recover the primitive from the conserved variables we need to solve the nonlinear equation:
-\begin{equation}
-    f\left(p\right)=p-\ol{p}\left(p\right)=0,
-\end{equation}
-where $\ol{p}\left(p\right)$ is the pressure as obtained via the ideal gas equation of state with an initial guess, $p$:
-\begin{equation}
-    \ol{p}=\left(\Gamma-1\right)\rho\,\epsilon,
-\end{equation}
-where
-\begin{equation}
-    \rho=\rho\left(\bU,p\right),\hspace{1em}\epsilon=\epsilon\left(\bU,p\right).
-\end{equation}
-
-In order to solve this equation we make use of the bisection method, and therefore need bounds on our initial guess for the pressure.
-
-\subsection{Upper and Lower Bounds for Pressure}
-We obtain a lower bound for the pressure with:
-\begin{equation}
-\tau=D\left(h\,W-1\right)-p\implies p=-\left(\tau+D\right)+D\,h\,W\geq-\left(\tau+D\right)+D\,h\,W\,\sqrt{v^{i}\,v_{i}}=-\left(\tau+D\right)+\sqrt{S^{i}\,S_{i}}.
-\end{equation}
-So, since the pressure must be non-negative, we have:
-\begin{equation}
-p\geq\text{MAX}\left[-\left(\tau+D\right)+\sqrt{S^{i}\,S_{i}},\text{SqrtTiny}\right].
-\end{equation}
-
-For an upper bound, we first note that:
-\begin{equation}
-h=1+\f{e+p}{\rho}=1+\f{\Gamma}{\Gamma-1}\f{p}{\rho}=1+\f{\Gamma}{\Gamma-1}\,\f{p\,W}{D},
-\end{equation}
-so,
-%\begin{equation}
-%    \tau=D\left(W+\f{\Gamma}{\Gamma-1}\f{p\,W^{2}}{D}-1\right)-p=D\left(W-1\right)+p\left(\f{\Gamma}{\Gamma-1}W^{2}-1\right).
-%\end{equation}
-%So,
-%\begin{equation}
-%    p=\f{\tau-D\left(W-1\right)}{\f{\Gamma}{\Gamma-1}W^{2}-1}.
-%\end{equation}
-%We also have:
-%\begin{equation}
-%    W=\left(1-v^{i}\,v_{i}\right)^{-1/2}=\left(1-\f{S^{i}\,S_{i}}{\left(\tau+D+p\right)^{2}}\right)^{-1/2}.
-%\end{equation}
-%Treating $p$ as an independent variable \sd{is this valid?}, we have:
-%\begin{equation}
-%    W\Big|_{p\rightarrow\infty}=1,
-%\end{equation}
-%which gives us an upper limit:
-%\begin{equation}
-%    p\leq\f{\Gamma-1}{\Gamma}\,\tau.
-%\end{equation}
-%Just to be safe, in the code we multiply this by two, so that:
-%\begin{equation}
-%    p\leq2\,\f{\Gamma-1}{\Gamma}\,\tau.
-%\end{equation}
-\begin{equation}
-    \tau=D\left(W+\f{\Gamma}{\Gamma-1}\f{p\,W^{2}}{D}-1\right)-p=D\left(W-1\right)+p\left(\f{\Gamma}{\Gamma-1}W^{2}-1\right)>p\left(\f{\Gamma}{\Gamma-1}-1\right)=\f{p}{\Gamma-1}.
-\end{equation}
-So,
-\begin{equation}
-    p<\left(\Gamma-1\right)\tau.
-\end{equation}
-Typically, $\Gamma-1<3$. So, we end up with:
-\begin{equation}
-    p<3\,\tau.
-\end{equation}
-
-\newpage
-
-\section{Error Introduced by Linear Interpolation}
-We obtain the initial conditions for the standing accretion shock problem with an external code.
-We then have to interpolate these data onto the grid for use in \texttt{thornado}.
-We start by proving that linear interpolation is a convex combination of the solution at the boundary points.
-
-\subsection{Proof that Linear Interpolation is a Convex Combination of Boundary-Points}
-Linear interpolation of a function, $f$, of a variable, $r$, bounded by two points $r_{L}$ and $r_{H}$, with $r_{H}>r_{L}$, can be written as:
-\begin{equation}
-    f\left(r\right)=f\left(r_{L}\right)+\f{f\left(r_{H}\right)-f\left(r_{L}\right)}{r_{H}-r_{L}}\left(r-r_{L}\right).
-\end{equation}
-By making a change of variables from $r$ to $\eta$, where:
-\begin{equation}
-    r\left(\eta\right)=\eta\,r_{H}+\left(1-\eta\right)r_{L}=r_{L}+\eta\,\Delta r\implies\eta=\f{r-r_{L}}{\Delta r},\hspace{1em}\eta\in\left[0,1\right],
-\end{equation}
-such that $r\left(\eta=0\right)=r_{L}$ and $r\left(\eta=1\right)=r_{H}$, we have that:
-\begin{align}
-    f\left(\eta\right)&=f\left(0\right)+\f{f\left(1\right)-f\left(0\right)}{1-0}\left(\eta-0\right)=f\left(0\right)+\left(f\left(1\right)-f\left(0\right)\right)\eta\\
-    \implies f\left(\eta\right)&=\eta\,f\left(1\right)+\left(1-\eta\right)f\left(0\right).
-\end{align}
-
-So when we interpolate a fluid variable, say the mass-density $\rho$, we have:
-\begin{equation}
-    \rho\left(r\right)=\rho_{L}+\f{\Delta\rho}{\Delta r}\left(r-r_{L}\right)\longrightarrow\rho\left(\eta\right)=\eta\,\rho_{H}+\left(1-\eta\right)\rho_{L},
-\end{equation}
-where $\rho_{L}\equiv\rho\left(r_{L}\right)$ and $\rho_{H}=\rho\left(r_{H}\right)$.
-
-\subsection{Example: $f\left(x\right)=x^{2}$}
-We can show this directly for simple functions. We take as an example $f\left(x\right)=x^{2}$:
-\begin{align}
-    f\left(x\right)&=x^{2}=\left[x_{L}+\eta\left(x_{R}-x_{L}\right)\right]^{2}=x_{L}^{2}+\eta^{2}\left(x_{R}-x_{L}\right)^{2}+2\,x_{L}\,\eta\left(x_{R}-x_{L}\right)\\
-    &=x_{L}^{2}+\eta^{2}\,x_{R}^{2}+\eta^{2}\,x_{L}^{2}-2\,\eta^{2}\,x_{L}\,x_{R}+2\,\eta\,x_{L}\,x_{R}-2\,\eta\,x_{L}^{2}.
-\end{align}
-Now we add and subtract the interpolated solution: $\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}$. This yields:
-\begin{align}
-    x^{2}&=x_{L}^{2}+\eta^{2}\,x_{R}^{2}+\eta^{2}\,x_{L}^{2}-2\,\eta^{2}\,x_{L}\,x_{R}+2\,\eta\,x_{L}\,x_{R}-2\,\eta\,x_{L}^{2}+\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}-\eta\,x_{H}^{2}-\left(1-\eta\right)x_{L}^{2}\\
-    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]+\left[-\eta\left(1-\eta\right)x_{L}^{2}-\eta\left(1-\eta\right)x_{H}^{2}+2\,\eta\,x_{L}\,x_{H}\left(1-\eta\right)\right]\\
-    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left[x_{L}^{2}+x_{H}^{2}-2\,x_{L}\,x_{H}\right]\\
-    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left(x_{H}-x_{L}\right)^{2}\\
-    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left(\Delta x\right)^{2}.
-\end{align}
-The term in square brackets is the interpolated solution, and the second term is the remainder, i.e. the error in the interpolated solution. We show the results of this in the following figure:
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.75]{LinearInterpolationError}
-\end{figure}
-
-\subsection{Mass Constant}
-The mass constant, $C_{D}$, from the 3+1 GR hydrodynamics equations is:
-\begin{equation}
-    C_{D}\left(r\right)=\psi\left(r\right)^{6}\,\alpha\left(r\right)\,r^{2}\,\rho\left(r\right)\,W\left[v\left(r\right)\right]\,v\left(r\right).
-\end{equation}
-From the data we have this exact value at the two endpoints:
-\begin{align}
-    C_{D}\left(r_{L}\right)&\equiv C^{L}_{D}=\psi_{L}^{6}\,\alpha_{L}\,r_{L}^{2}\,\rho_{L}\,W_{L}\,v_{L}\\
-    C_{D}\left(r_{H}\right)&\equiv C^{H}_{D}=\psi_{H}^{6}\,\alpha_{H}\,r_{H}^{2}\,\rho_{H}\,W_{H}\,v_{H}.
-\end{align}
-
-\newpage
-
-\bibliographystyle{apj}
-\bibliography{../References/references.bib}
-
-\end{document}

### 2018-11-28 Documents/Euler/SamsTexFiles/Time-Step_Restriction_High-Order.tex
Added folder with Sams tex files to simplify document

\section{Computing the Time-Step Using Higher-Order DG Schemes}

When making the jump to higher-order DG schemes, we can simply do the same as in the first-order scheme, except we compute the quantities in all of the nodal points instead of using a cell-average. This is valid because the cell-average is a convex combination...\sd{Need to expand on this}. The proof starts with the discretized equation valid at each quadrature point, $q$:
\begin{equation}
    \bU_{q}^{n+1}=\bU_{q}^{n}+\Delta t\,\cL_{q}^{n},
\end{equation}
where $\cL_{q}^{n}$ is a general form of the RHS at time $t^{n}$. If we define a vector $\ol{\bU}\equiv\left(\bU_{1},\cdots,\bU_{q},\cdots,\bU_{Q}\right)^T$, where $Q$ is the total number of quadrature points, and $\ol{\bW}\equiv\left(\bW_{1},\cdots,\bW_{q},\cdots,\bW_{Q}\right)^T$ as a vector of quadrature weights, then we can write the cell-average of $\bU$ as:
\begin{equation}
    \bU_{K}\equiv\ol{\bW}^T\ol{\bU}.
\end{equation}
If we then compute the cell-average of the above equation, we get:
\begin{equation}
    \bU_{K}^{n+1}=\bU_{K}^{n}+\Delta t\,\ol{\bW}^{T}\,\ol{\cL}_{q}^{n}=\ol{\bW}^{T}\left(\ol{\bU}^{n}+\Delta t\,\ol{\cL}^{n}\right)
\end{equation}

\subsection{High-Order Time-Step Restriction for DG}

\blue{NOTE:} This closely follows Jesse's document CFLCondition.pdf.

Consider the one-dimensional system of hyperbolic balance equations:
\begin{equation}\label{Eq:HypBalEqns}
    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF^{1}\left(\bU\right)\right)}{1}=\sqrtgm\,\bQ,
\end{equation}
where $\bU$ is a vector of conserved variables, $\bF^{1}\left(\bU\right)$ are the fluxes of those conserved variables in the $x^{1}$-direction, $\bQ$ is a source term, and $\sqrtgm$ is the square-root of the determinant of the spatial three-metric.

We define our reference element by:
\begin{equation}
    I_{j}\equiv\left\{x^{1}:x^{1}\in\left(x^{1}_{L},x^{1}_{H}\right)=\left(x^{1}_{\jmh},x^{1}_{\jph}\right)\right\}.
\end{equation}

We proceed by multiplying \eqref{Eq:HypBalEqns} with $v$, where $v=v\left(x^{1}\right)$ is a test function in the DG scheme, and integrate over the $\jth$ element:
\begin{equation}
    \int_{I_{j}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,v\,dx^{1}+\int_{I_{j}}\pd{\left(\sqrtgm\,\bF^{1}\left(\bU\right)\right)}{1}\,v\,dx^{1}=\int_{I_{j}}\sqrtgm\,\bQ\,v\,dx^{1}.
\end{equation}
We now move the flux term to the RHS and perform integration-by-parts on it, yielding:
\begin{equation}\label{Eq:IntByParts}
    \int_{I_{j}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,v\,dx^{1}=-\left[\sqrtgm\,\hat{\bF^{1}}\,v\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\,v\Big|_{x^{1}_{L}}\right]+\int_{I_{j}}\sqrtgm\,\bF^{1}\,\pd{v}{1}\,dx^{1}+\int_{I_{j}}\sqrtgm\,\bQ\,v\,dx^{1},
\end{equation}
where $\hat{\bF^{1}}$ is a numerical flux.

\blue{NOTE:} $v=1$ is in the space of test functions for the DG method, \textit{and} $v=1$ yields the cell-average when substituted into \eqref{Eq:IntByParts}, therefore the DG method evolves the cell-average.

Substituting $v=1$ into \eqref{Eq:IntByParts} yields:
\begin{equation}\label{Eq:CellAverageDG}
    \int_{I_{j}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx^{1}=-\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]+\int_{I_{j}}\sqrtgm\,\bQ\,dx^{1}.
\end{equation}
Note that the volume-term has dropped out because the derivative of a constant is equal to zero.

We define the cell-average of a quantity, $\bX=\bX\left(x^{1},t\right)$, as:
\begin{equation}
    \ol{\bX}\equiv\f{1}{\Delta V_{j}}\int_{I_{j}}\bX\,\sqrtgm\,dx^{1}.
\end{equation}

\red{NEW ASSUMPTION:} We assume that the spatial three-metric is explicitly independent of time. This allows us to pull the metric determinant out of the first integral, yielding for \eqref{Eq:CellAverageDG}:
\begin{equation}
    \f{d\,\ol{\bU}}{dt}=-\f{1}{\Delta V_{j}}\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]+\ol{\bQ}.
\end{equation}

\red{NEW ASSUMPTION:} We now specialize this to using the forward-Euler time-stepping algorithm, yielding:

\begin{equation}
    \ol{\bU}^{n+1}=\ol{\bU}^{n}-\f{\Delta t^{n}_{j}}{\Delta V_{j}}\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]^{n}+\Delta t^{n}_{j}\,\ol{\bQ}^{n}
\end{equation}
\blue{NOTE:} Since the spatial three-metric is explicitly independent of time, we don't need to specify the time-step at which the volume is computed (i.e. we don't have to write $\Delta V^{n}_{j}$).

Now we define a parameter $\ve\in\left(0,1\right)$ a la \citet{ZS2011b} and re-write the above equation as:
\begin{align}
    \ol{\bU}^{n+1}&=\ve\left\{\ol{\bU}^{n}-\f{\Delta t^{n}_{j}}{\ve\,\Delta V_{j}}\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]^{n}\right\}+\left(1-\ve\right)\left\{\ol{\bU}^{n}+\f{\Delta t^{n}_{j}}{1-\ve}\,\ol{\bQ}^{n}\right\}\\
    &=\ve\,\ol{\bH}_{1}+\left(1-\ve\right)\ol{\bH}_{2},
\end{align}
where
\begin{equation}\label{Eq:H1}
    \ol{\bH}_{1}\equiv\ol{\bU}^{n}-\f{\Delta t^{n}_{j}}{\ve\,\Delta V_{j}}\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]^{n},
\end{equation}
and
\begin{equation}
    \ol{\bH}_{2}\equiv\ol{\bU}^{n}+\f{\Delta t^{n}_{j}}{1-\ve}\,\ol{\bQ}^{n}.
\end{equation}
\red{NEW ASSUMPTION:} We assume that $\ol{\bU}^{n}\in\cG$, as defined in \citet{Mignone2005}.

Assuming that $\ol{\bU}^{n}\in\cG$, we now seek to derive the conditions that guarantee $\ol{\bU}^{n+1}\in\cG$.

\subsubsection{The numerical flux term: $\ol{\bH}_{1}$}

We start by numerically computing the cell-average using quadrature with the Gauss-Lobatto quadrature rule. We assume that the DG approximation polynomial for the conserved variables is of order $k$, and that the order of the approximate solution is of order $k+d$, where $d$ is an integer that depends on the metric determinant. For the case of Cartesian coordinates, $d=0$ (because $\sqrtgm\sim x^{0}$), and for spherical-polar coordinates, $d=2$ (because $\sqrtgm\sim r^{2}$). Gauss-Lobatto integration will give an exact result if we choose a sufficiently high number, $M$, of quadrature points:
\begin{equation}
    2\,M-3\geq k+d\implies M\geq\f{k+d+3}{2}.
\end{equation}

\blue{NOTE:} We now drop the superscript $n$ for the rest of this subsection.

Assuming that we choose a sufficient number of points, we can write the cell-average as:
\begin{align}
    \ol{\bU}=\f{1}{\Delta V_{j}}\sum\limits_{q=1}^{M}w_{q}\,\bU_{q}\,\sqrtgm_{q}\,\Delta x_{j}&=\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{1}\,\bU_{1}\,\sqrtgm_{1}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{M}\,\bU_{M}\,\sqrtgm_{M}\\
    &=\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{1}\,\bU^{+}_{L}\,\sqrtgm_{L}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{M}\,\bU^{-}_{H}\,\sqrtgm_{H},\label{Eq:CellAverageGL}
\end{align}
where $w_{q}$ are the Gauss-Lobatto quadrature weights and $\bU_{q}=\bU\left(x_{q}\right)$, and $\sqrtgm_{q}=\sqrt{\gamma\left(x_{q}\right)}$. The quantity $\bU^{+}_{L}$ refers to the vector of conserved variables evaluated at the lower interface, but on the higher side, so that it is evaluated \textit{in} the $\jth$ cell. Similarly for $\bU^{-}_{H}$.

Our approach is to use the end-points to balance the troublesome terms in the numerical fluxes.

\red{NEW ASSUMPTION:} We now specialize to the local Lax-Friedrichs flux:
\begin{align}
    \hat{\bF}^{1}\Big|_{x^{1}_{L}}&=\hat{\bF}^{1}\left(\bU^{+}_{L},\bU^{-}_{L}\right)=\f{1}{2}\left[\bF^{1}\left(\bU^{+}_{L}\right)+\bF^{1}\left(\bU^{-}_{L}\right)-\alpha_{L}\left(\bU_{L}^{+}-\bU_{L}^{-}\right)\right]\\
    &=\f{1}{2}\left\{-\alpha_{L}\left[\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\alpha_{L}\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right\},
\end{align}
and
\begin{align}
    \hat{\bF}^{1}\Big|_{x^{1}_{H}}&=\hat{\bF}^{1}\left(\bU^{+}_{H},\bU^{-}_{H}\right)=\f{1}{2}\left[\bF^{1}\left(\bU^{+}_{H}\right)+\bF^{1}\left(\bU^{-}_{H}\right)-\alpha_{H}\left(\bU_{H}^{+}-\bU_{H}^{-}\right)\right]\\
    &=\f{1}{2}\left\{-\alpha_{H}\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\alpha_{H}\left[\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right\},
\end{align}
where $\alpha_{H}=\text{max}\left(\alpha_{j},\alpha_{j+1}\right)$ and $\alpha_{L}=\text{max}\left(\alpha_{j-1},\alpha_{j}\right)$ are the largest (in magnitude) wavespeeds as given by the flux-Jacobian.
Now we substitute these expressions along with \eqref{Eq:CellAverageGL} into \eqref{Eq:H1}:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{1}\,\bU^{+}_{L}\,\sqrtgm_{L}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{M}\,\bU^{-}_{H}\,\sqrtgm_{H}\\
    &-\f{\Delta t_{j}}{\ve\,\Delta V_{j}}\left[\sqrtgm_{H}\f{1}{2}\left\{-\alpha_{H}\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\alpha_{H}\left[\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right\}\right]\\
    &+\f{\Delta t_{j}}{\ve\,\Delta V_{j}}\left[\sqrtgm_{L}\f{1}{2}\left\{-\alpha_{L}\left[\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\alpha_{L}\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right\}\right].
\end{align}
Now we combine terms with common factors of the metric determinant:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}\\
    &+\f{\sqrtgm_{L}}{\Delta V_{j}}\left\{\Delta x_{j}\,w_{1}\,\bU^{+}_{L}+\f{\Delta t_{j}\,\alpha_{L}}{2\,\ve}\left(-\left[\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right)\right\}\\
    &+\f{\sqrtgm_{H}}{\Delta V_{j}}\left\{\Delta x_{j}\,w_{M}\,\bU^{-}_{H}-\f{\Delta t_{j}\,\alpha_{H}}{2\,\ve}\left(-\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\left[\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right)\right\}.
\end{align}
Next we factor out $\Delta x_{j}$ and the quadrature weights, yielding:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}\\
    &+\f{\sqrtgm_{L}\,\Delta x_{j}\,w_{1}}{\Delta V_{j}}\left\{\bU^{+}_{L}+\f{\Delta t_{j}\,\alpha_{L}}{2\,\ve\,\Delta x_{j}\,w_{1}}\left(-\left[\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right)\right\}\\
    &+\f{\sqrtgm_{H}\,\Delta x_{j}\,w_{M}}{\Delta V_{j}}\left\{\bU^{-}_{H}-\f{\Delta t_{j}\,\alpha_{H}}{2\,\ve\,\Delta x_{j}\,w_{M}}\left(-\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\left[\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right)\right\}.
\end{align}
Next we re-write the $\bU^{+}_{L}$ and $\bU^{-}_{H}$ that appear with the flux terms:
\begin{align}
    \bU^{+}_{L}&=2\,\bU^{+}_{L}-\bU^{+}_{L}\\
    \bU^{-}_{H}&=2\,\bU^{-}_{H}-\bU^{-}_{H}.
\end{align}
This gives:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}\\
    &+\f{\sqrtgm_{L}\,\Delta x_{j}\,w_{1}}{\Delta V_{j}}\left\{\bU^{+}_{L}+\f{\Delta t_{j}\,\alpha_{L}}{2\,\ve\,\Delta x_{j}\,w_{1}}\left(-\left[2\,\bU^{+}_{L}-\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right)\right\}\\
    &+\f{\sqrtgm_{H}\,\Delta x_{j}\,w_{M}}{\Delta V_{j}}\left\{\bU^{-}_{H}-\f{\Delta t_{j}\,\alpha_{H}}{2\,\ve\,\Delta x_{j}\,w_{M}}\left(-\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\left[2\,\bU^{-}_{H}-\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right)\right\}.
\end{align}
This allows us to write the expression with factors similar to those in \citet{Qin2016}. We find:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}\\
    &+\f{\sqrtgm_{L}\,\Delta x_{j}\,w_{1}}{\Delta V_{j}}\left\{\bU^{+}_{L}\left(1-\f{\Delta t_{j}\,\alpha_{L}}{\ve\,\Delta x_{j}\,w_{1}}\right)+\f{\Delta t_{j}\,\alpha_{L}}{2\,\ve\,\Delta x_{j}\,w_{1}}\left(\left[\bU^{+}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right)\right\}\\
    &+\f{\sqrtgm_{H}\,\Delta x_{j}\,w_{M}}{\Delta V_{j}}\left\{\bU^{-}_{H}\left(1-\f{\Delta t_{j}\,\alpha_{H}}{\ve\,\Delta x_{j}\,w_{M}}\right)+\f{\Delta t_{j}\,\alpha_{H}}{2\,\ve\,\Delta x_{j}\,w_{M}}\left(\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\left[\bU^{-}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right)\right\}.
\end{align}
All of the terms in the square brackets are similar the the $\bH$ quantities in \citet{Qin2016}. We see that the expressions in the curly brackets are convex combinations (given a restriction on $\Delta t_{j}$), because the coefficients sum to unity. Since the quadrature weights are symmetric (so $w_{1}=w_{M}\equiv w_{GL}$), we find that the condition for $\ol{\bH}_{1}\in\cG$ is a time-step restriction:
\begin{equation}
\Delta t_{j}<\ve\,\Delta x_{j}\,w_{GL}\,\text{min}\left(\f{1}{\alpha_{L}},\f{1}{\alpha_{H}}\right)
\end{equation}
Since we want a time-step that is constant for all elements, we choose:
\begin{equation}
\Delta t<\ve\,w_{GL}\,\text{min}_{j}\left(\f{\Delta x_{j}}{\text{max}\left(\alpha_{L},\alpha_{H}\right)}\right).
\end{equation}

\red{NEW ASSUMPTION:} In order for this to work, we also demand that all of the $\bU_{q}$ are within physical bounds.

\blue{NOTE:} We see the effect of the high-order approximation in the presence of the quadrature end-point weight $w_{GL}$. As the order increases, $w$ decreases, thus making a tighter restriction on the time-step.

\blue{NOTE:} It is worth noting that this result is independent of the metric determinant.

### 2018-11-28 Documents/Euler/dgEulerGR.tex
Added folder with Sams tex files to simplify document

--- 2018-11-16 Documents/Euler/dgEulerGR.tex
@@
 
-\section{Discontinuous Galerkin Scheme}
-\label{sec:dgMethod}
-
-We assume a spacetime metric
-\begin{equation}
-  ds^{2}=-\alpha^{2}\,dt^{2}+\gamma_{ij}\,dx^{i}\,dx^{j},
-\end{equation}
-and consider the system of conservation laws with sources
-\begin{equation}
-  \pd{}{t}\big(\sqrt{\gamma}\,\bU\big)+\sum_{i=1}^{d}\pd{}{i}\big(\alpha\,\sqrt{\gamma}\,\bF^{i}(\bU)\big)=\alpha\,\sqrt{\gamma}\,\bG(\bU),
-  \label{eq:conservationLaws}
-\end{equation}
-where
-\begin{align}
-  \bU
-  &=\big(D,\,S_{j},\,\tau\big)^{\mbox{\tiny T}}
-  =\big(\rho\,W,\,\rho\,h\,W^{2}\,v_{j},\,\rho\,W\left(h\,W-1\right)-p\big)^{\mbox{\tiny T}}, \\
-  \bF^{i}(\bU)
-  &=\big(D\,v^{i},\,\big)^{\mbox{\tiny T}}
-\end{align}
-
-\section{Bound-Preserving Methods Using First-Order DG Scheme}
-
-\subsection{Cartesian Coordinates}
-This section closely follows \citet{Qin2016}.
-
-\subsubsection{Set of Admissible States}
-We consider a one-dimensional system of conservation laws:
-\begin{equation}
-    \pd{\,\bU}{t} + \pd{\,\bF\left(\bU\right)}{x} = \vect{0},
-\end{equation}
-where $\bU$ is a vector of conserved variables, defined as:
-\begin{equation}\label{Eq:ConservedVariables}
-    \bU\longrightarrow\begin{pmatrix} D\\ S\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
-\end{equation}
-and $\bF\left(\bU\right)$ are the fluxes of those conserved quantities:
-\begin{equation}\label{Eq:FluxVector}
-    \bF\left(\bU\right)\longrightarrow\begin{pmatrix}\rho\,W\,v\\ \rho\,h\,W^{2}\,v^{2}+p\\\rho\,h\,W^{2}\,v-D\,v\end{pmatrix}.
-\end{equation}
-
-The physics leads us to define a set of admissible states, $\cG_{p}$ (the subscript $p$ stands for primitive), as:
-\begin{equation}
-    \cG_{p}\equiv\left\{\bU\Big|\rho>0,\,p>0,\,v^{2}<1\right\}.
-\end{equation}
-
-It is shown in \citet{Mignone2005} that $\cG$ is a convex set\footnote{Convex in the sense that if $\bU_{1}\in\cG$ and $\bU_{2}\in\cG$, then $\alpha_{1}\,\bU_{1}+\alpha_{2}\,\bU_{2}\in\cG$, where $\alpha_{1},\,\alpha_{2}\in\left[0,1\right]$ and $\alpha_{1}+\alpha_{2}=1$.} and can equivalently be written in terms of the conserved variables as:
-\begin{equation}\label{Eq:SetOfAdmissibleStates}
-    \cG\equiv\left\{\bU\Big|D>0,\,\tau+D>\sqrt{D^{2}+S^{2}}\right\}.
-\end{equation}
-
-\subsubsection{Time-Step Derivation/CFL Condition}
-For the first-order DG method using forward-Euler time-stepping, we evolve the vector of conserved variables as:
-\begin{equation}\label{Eq:1stOrderDG}
-    \ol{\bU}^{n+1}_{i}=\ol{\bU}^{n}_{i}-\eta_{i}\left[\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i+1}\right)-\hat{\bF}\left(\ol{\bU}^{n}_{i-1},\ol{\bU}^{n}_{i}\right)\right],
-\end{equation}
-where
-\begin{equation}
-    \ol{\bU}_{i}\equiv\f{1}{\Delta x_{i}}\int_{x_{\imh}}^{x_{\iph}}\bU_{i}\,dx,
-\end{equation}
-$\eta_{i}\equiv\Delta t_{i}/\Delta x_{i}$, and $\hat{\bF}$ is the numerical flux. In this document we use the local Lax-Friedrichs flux, defined as:
-\begin{equation}\label{Eq:LLF}
-    \hat{\bF}\left(a,b\right)=\f{1}{2}\left[\bF\left(a\right)+\bF\left(b\right) - \alpha_{ab}\left(b-a\right)\right],
-\end{equation}
-where $a$ and $b$ represent the state of the fluid in two different elements, $\alpha_{ab}$ is an estimate for the wave-speed:
-\begin{equation}
-    \alpha_{ab}=\text{max}\left[\alpha\left(a\right),\alpha\left(b\right)\right],
-\end{equation}
-and $\alpha$ is the largest (in absolute value) eigenvalue of the flux-Jacobian:
-\begin{equation}
-    \alpha=\left|\left|\pderiv{\bF}{\bU}\right|\right|.
-\end{equation}
-Using this we define the following variables:
-\begin{equation}\label{Eq:EigVals}
-    \alpha_{\iph}=\text{max}\left[\alpha\left(\ol{\bU}_{i}\right),\alpha\left(\ol{\bU}_{i+1}\right)\right],\hspace{3em} \alpha_{\imh}=\text{max}\left[\alpha\left(\ol{\bU}_{i-1}\right),\alpha\left(\ol{\bU}_{i}\right)\right].
-\end{equation}
-
-Substituting \eqref{Eq:LLF} with \eqref{Eq:EigVals} into \eqref{Eq:1stOrderDG}:
-\begin{align}
-    \ol{\bU}^{n+1}_{i}&=\ol{\bU}^{n}_{i}-\f{\eta_{i}}{2}\left[\bF\left(\ol{\bU}^{n}_{i}\right)+\bF\left(\ol{\bU}^{n}_{i+1}\right)-\alpha_{\iph}\left(\ol{\bU}^{n}_{i+1}-\ol{\bU}^{n}_{i}\right)\right.\nonumber\\
-    &\left.\hspace{7em}-\bF\left(\ol{\bU}^{n}_{i}\right)-\bF\left(\ol{\bU}^{n}_{i-1}\right)+\alpha_{\imh}\left(\ol{\bU}^{n}_{i}-\ol{\bU}^{n}_{i-1}\right)\right]\nonumber\\
-    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right]\nonumber\\
-    &\hspace{15em}+\f{\eta_{i}}{2}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]\nonumber\\
-    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\ol{\bH}^{-}\left(\ol{\bU}^{n}_{i+1},\alpha_{\iph}\right)+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\ol{\bH}^{+}\left(\ol{\bU}^{n}_{i-1},\alpha_{\imh}\right),\label{Eq:ConvComb}
-\end{align}
-where
-\begin{equation}\label{Eq:Hpm}
-    \ol{\bH}^{\pm}\left(\ol{\bU},\alpha\right)\equiv\ol{\bU}\pm\f{1}{\alpha}\,\bF\left(\ol{\bU}\right).
-\end{equation}
-
-The proof that $\ol{\bH}^{\pm}\in\cG$ is given in \citet{Qin2016}.
-Therefore, we see that with a restriction on $\alpha_{i\pm\f{1}{2}}$ that \eqref{Eq:ConvComb} is a convex combination.
-The restriction is (recalling that $\eta_{i}=\Delta t_{i}/\Delta x_{i}$):
-\begin{equation}
-    1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)>0\implies\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)<1\implies \Delta t_{i}<\f{2\,\Delta x_{i}}{\alpha_{\iph}+\alpha_{\imh}}\leq\f{\Delta x_{i}}{\text{max}\left(\alpha_{i\pm\f{1}{2}}\right)}.
-\end{equation}
-
-We want a time-step that is the same for all elements at a given time, so we tighten the restriction to:
-\begin{equation}
-    \Delta t<\text{min}_{i}\left(\f{\Delta x_{i}}{\text{max}\left(\alpha_{i\pm\f{1}{2}}\right)}\right)=\f{\Delta x}{\text{max}_{i}\left(\alpha_{i\pm\f{1}{2}}\right)},
-\end{equation}
-where the equality follows for a uniform mesh, i.e. $\Delta x_{i}=\Delta x\,\forall i$.
-
-\newpage
-
-\subsection{Curvilinear Coordinates in 1-D}
-NOTE: We assume a conformally-flat, time-independent spatial three-metric:
-\begin{equation}
-    \gamma_{ij}\left(x^{k},t\right)\longrightarrow\psi^{4}\left(x^{k}\right)\,\ol{\gamma_{ii}}\left(x^{k}\right),
-\end{equation}
-where $\psi\left(x^{k}\right)$ is the conformal factor and $\ol{\gamma}_{ii}$ is the flat-space metric.
-
-\subsubsection{Set of Admissible States}
-We again consider a one-dimensional system of conservation laws, but this time with a curvilinear metric:
-\begin{equation}\label{Eq:1DCurvilinearConsLaw}
-    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF^{i}\right)}{i}=\sqrtgm\,\bQ,\hspace{1em}\text{(no sum on $i$)},
-\end{equation}
-where $\bU$ is given by:
-\begin{equation}
-    \bU\longrightarrow\begin{pmatrix} D\\ S_{j}\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v_{j}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,\gamma_{jk}\,v^{k}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
-\end{equation}
-$\bF^{i}\left(\bU\right)$ are the fluxes in the $x^{i}$-direction of those conserved quantities:
-\begin{equation}
-    \bF^{i}\left(\bU\right)\longrightarrow\begin{pmatrix}D\,v^{i}\\ S^{i}\,v_{j}+p\,\delta^{i}_{~j}\\ S^{i}-D\,v^{i}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{i}\\ \rho\,h\,W^{2}\,v^{i}\,v_{j}+p\,\delta^{i}_{~j}\\\rho\,h\,W^{2}\,v^{i}-D\,v^{i}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{i}\\ \rho\,h\,W^{2}\,\gamma_{jk}\,v^{i}\,v^{k}+p\,\delta^{i}_{~j}\\\rho\,h\,W^{2}\,v^{i}-D\,v^{i}\end{pmatrix},
-\end{equation}
-and $\bQ$ is a source term:
-\begin{align}
-    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{ik}\,\pd{\,\gamma_{ik}}{j}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\pd{\,\gamma_{11}}{j}+P^{22}\,\pd{\,\gamma_{22}}{j}+P^{33}\,\pd{\,\gamma_{33}}{j}\right] \\0\end{pmatrix}\\
-    &=\begin{pmatrix}0\\ P^{11}\,h_{1}\,\pd{\,h_{1}}{j}+P^{22}\,h_{2}\,\pd{\,h_{2}}{j}+P^{33}\,h_{3}\,\pd{\,h_{3}}{j} \\0\end{pmatrix},
-\end{align}
-where we have used the fact that $\gamma_{kk}=\left(h_{k}\right)^{2}$. The $P^{ik}$ are components of the pressure tensor:
-\begin{equation}
-    P^{ik}=S^{i}\,v^{k}+p\,\gamma^{ik}=\gamma^{i\ell}\,S_{\ell}\,v^{k}+p\,\gamma^{ik}=\gamma^{i\ell}\,S_{\ell}\,v^{k}+p\,\gamma^{i\ell}\,\delta^{k}_{~\ell}=\gamma^{i\ell}\left(S_{\ell}\,v^{k}+p\,\delta^{k}_{~\ell}\right).
-\end{equation}
-Since the spatial three-metric is diagonal the only non-zero term is that with $\ell=i$. We can therefore simplify further:
-\begin{equation}
-    P^{ik}=\gamma^{ii}\left(S_{i}\,v^{k}+p\,\delta^{k}_{~i}\right)=\f{1}{\gamma_{ii}}\,\left(S_{i}\,v^{k}+p\,\delta^{k}_{~i}\right),\hspace{1em}\text{(no sum on $i$)}.
-\end{equation}
-For the source-term sum we then have:
-\begin{equation}\label{Eq:PressureTensorSum}
-    Q_{j}=\f{1}{2}\,P^{ik}\,\p_{j}\,\gamma_{ik}=\f{1}{2}\,P^{kk}\,\p_{j}\,\gamma_{kk}=\f{1}{2}\,P^{kk}\,\p_{j}\left(h_{k}\right)^{2}=P^{kk}\,h_{k}\,\p_{j}\,h_{k}.
-\end{equation}
-
-These definitions lead us to define the same set of admissible states as before, namely:
-\begin{equation}
-    \cG_{p}\equiv\left\{\bU\Big|\rho>0,\,p>0,\,v^{2}<1\right\},
-\end{equation}
-the only difference being that $v^{2}$ now involves the metric:
-\begin{equation}
-    v^{2}=v^{j}\,v_{j}=\gamma_{kj}\,v^{k}\,v^{j}.
-\end{equation}
-
-Before continuing, we show that the introduction of the metric doesn't affect the translation between $\cG_{p}$ and $\cG$...\sd{I've shown this, just need to TeX it up}
-
-\subsubsection{Time-Step Derivation/CFL Condition}
-We start by integrating both sides of \eqref{Eq:1DCurvilinearConsLaw} over $dx^{i}$ and dividing by the volume of the $K^{th}$ element, $\Delta V_{K}$ (recalling that there is no sum on $i$):
-\begin{equation}
-    \f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\pd{\left(\sqrtgm\,\bU\right)}{t}dx^{i}+\f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\pd{\left(\sqrtgm\,\bF^{i}\left(\bU\right)\right)}{i}dx^{i}=\f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\sqrtgm\,\bQ\,dx^{i},
-\end{equation}
-where:
-\begin{equation}
-    \Delta V_{K}=\int_{x^{i}_{L}}^{x^{i}_{H}}dV=\int_{x^{i}_{L}}^{x^{i}_{H}}\sqrtgm\,dx^{i}.
-\end{equation}
-
-By defining the cell-average as:
-\begin{equation}
-    \bW_{K}\equiv\f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\bW\,dV,
-\end{equation}
-we have:
-\begin{equation}
-    \f{d\,\bU_{K}}{dt}+\f{1}{\Delta V_{K}}\left.\left(\sqrtgm\,\hat{\bF}\left(\bU\right)\right)\right|^{x^{i}_{H}}_{x^{i}_{L}}=\bQ_{K}.
-\end{equation}
-Now, using the common notation of the time step being represented as a superscript $n$:
-\begin{equation}
-    \bU^{n+1}_{K}=\bU^{n}_{K}-\f{\Delta t^{n}_{K}}{\Delta V_{K}}\left[\sqrtgm_{H}\,\hat{\bF}^{n}_{H}-\sqrtgm_{L}\,\hat{\bF}^{n}_{L}\right]+\Delta t^{n}_{K}\,\bQ^{n}_{K}.
-\end{equation}
-
-Now we define a parameter a la \citet{ZS2011b}: $\ve\in\left(0,1\right)$, such that (NOTE: \citet{ZS2011b} set $\ve=1/2$):
-\begin{equation}
-    \bU^{n}_{K}=\ve\,\bU^{n}_{K}+\left(1-\ve\right)\bU^{n}_{K}.
-\end{equation}
-We can use the first term to balance out the term in the square brackets and the second term to balance out the source term.
-
-So, we get:
-\begin{align}
-    \bU^{n+1}_{K}&=\ve\left\{\bU^{n}_{K}-\f{\Delta t^{n}_{K}}{\ve\,\Delta V_{K}}\left[\sqrtgm_{H}\,\hat{\bF}^{n}_{H}-\sqrtgm_{L}\,\hat{\bF}^{n}_{L}\right]\right\}+\left(1-\ve\right)\bU^{n}_{K}+\Delta t^{n}_{K}\,\bQ^{n}_{K}\\
-    &=\ve\left\{\bU^{n}_{K}-\eta^{n}_{K}\left[\sqrtgm_{H}\,\hat{\bF}\left(\bU^{n}_{K+1},\bU^{n}_{K}\right)-\sqrtgm_{L}\,\hat{\bF}\left(\bU^{n}_{K},\bU^{n}_{K-1}\right)\right]\right\}+\left(1-\ve\right)\bU^{n}_{K}+\Delta t^{n}_{K}\,\bQ^{n}_{K}\\
-    &=\ve\,\bH_{K,1}+\left(1-\ve\right)\bH_{K,2},
-\end{align}
-where
-\begin{equation}
-    \bH_{K,1}\equiv \bU^{n}_{K}-\eta^{n}_{K}\left[\sqrtgm_{H}\,\hat{\bF}\left(\bU^{n}_{K+1},\bU^{n}_{K}\right)-\sqrtgm_{L}\,\hat{\bF}\left(\bU^{n}_{K},\bU^{n}_{K-1}\right)\right],
-\end{equation}
-\begin{equation}
-    \bH_{K,2}\equiv\bU^{n}_{K}+\f{\Delta t^{n}_{K}}{1-\ve}\,\bQ^{n}_{K},
-\end{equation}
-and
-\begin{equation}
-    \eta^{n}_{K}\equiv\f{\Delta t^{n}_{K}}{\ve\,\Delta V_{K}}.
-\end{equation}
-
-We proceed by focusing on each term individually, starting with the numerical flux term, $\bH_{K,1}$.
-
-\subsubsection{Numerical flux term}
-We have to show that $\bH_{K,1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\bH_{K,1}$:
-\begin{align}
-    \bU^{n}_{K}-\f{\eta^{n}_{K}}{2}\Big\{&\sqrtgm_{H}\left[\bF\left(\bU^{n}_{K+1}\right)+\bF\left(\bU^{n}_{K}\right)-\alpha^{n}_{H}\left(\bU^{n}_{K+1}-\bU^{n}_{K}\right)\right]\\
-    &-\sqrtgm_{L}\left[\bF\left(\bU^{n}_{K}\right)+\bF\left(\bU^{n}_{K-1}\right)-\alpha^{n}_{L}\left(\bU^{n}_{K}-\bU^{n}_{K-1}\right)\right]\Big\}\\
-    &\hspace{-10em}=\left(1-\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}-\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\right)\bU^{n}_{K}\\
-    &\hspace{-8em}-\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\bF\left(\bU^{n}_{K}\right)+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\bF\left(\bU^{n}_{K}\right)\\
-    &\hspace{-8em}+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\left[\bU^{n}_{K-1}+\f{1}{\alpha^{n}_{L}}\bF\left(\bU^{n}_{K-1}\right)\right]+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\left[\bU^{n}_{K+1}-\f{1}{\alpha^{n}_{H}}\bF\left(\bU^{n}_{K+1}\right)\right].
-\end{align}
-Now we add and subtract $\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\,\bU^{n}_{K}$ and $\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\,\bU^{n}_{K}$, yielding:
-\begin{align}
-    &\left(1-\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}-\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\right)\bU^{n}_{K}\\
-    &+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\left[\bU^{n}_{K}-\f{1}{\alpha^{n}_{H}}\bF\left(\bU^{n}_{K}\right)\right]+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\left[\bU^{n}_{K}+\f{1}{\alpha^{n}_{L}}\bF\left(\bU^{n}_{K}\right)\right]\\
-    &+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\left[\bU^{n}_{K-1}+\f{1}{\alpha^{n}_{L}}\bF\left(\bU^{n}_{K-1}\right)\right]+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\left[\bU^{n}_{K+1}-\f{1}{\alpha^{n}_{H}}\bF\left(\bU^{n}_{K+1}\right)\right].
-\end{align}
-All of the terms in square brackets are similar to the $\bH_{K}$ quantities in \citet{Qin2016}, and are therefore in $\cG$.
-It can easily be seen that the sum of the coefficients is unity.
-The final condition is that the coefficient of $\bU^{n}_{K}>0$, or (recalling that $\eta^{n}_{K}=\Delta t_{K}/\left(\ve\,\Delta V_{K}\right)$):
-\begin{align}
-    1&-\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}-\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}>0\implies\eta^{n}_{K}\left(\sqrtgm_{H}\,\alpha^{n}_{H}+\sqrtgm_{L}\,\alpha^{n}_{L}\right)<1\\
-    &\implies\Delta t^{n}_{K}<\f{\ve\,\Delta V_{K}}{\sqrtgm_{H}\,\alpha^{n}_{H}+\sqrtgm_{L}\,\alpha^{n}_{L}}\leq\f{\ve\,\Delta V_{K}}{2\,\text{max}\left(\sqrtgm_{K\pm\f{1}{2}}\,\alpha^{n}_{K\pm\f{1}{2}}\right)}.
-\end{align}
-Again we want a time-step that is the same for all elements at a given time, so:
-\begin{equation}
-    \Delta t^{n}<\text{min}_{K}\left(\f{\ve\,\Delta V_{K}}{2\,\text{max}\left(\sqrtgm_{K\pm\f{1}{2}}\,\alpha^{n}_{K\pm\f{1}{2}}\right)}\right).
-\end{equation}
-
-We close the numerical flux section by writing the explicit form of the time-step for spherical-polar coordinates.
-
-\subsubsubsection{Time-step for Spherical-Polar Coordinates}
-For spherical-polar coordinates in 1-D we have that $\Delta V_{K}=1/3\left(r_{H}^{3}-r_{L}^{3}\right)$, and (assuming $\alpha_{K\pm\f{1}{2}}=1\ \forall\ i$) $\text{max}\left(\sqrtgm_{K\pm\f{1}{2}}\,\alpha_{K\pm\f{1}{2}}\right)=r_{H}^{2}$, so:
-\begin{align}
-    \Delta t&<\text{min}_{i}\left\{\f{\ve\,1/3\left[r_{H}^{3}-r_{L}^{3}\right]}{2\,r_{H}^{2}}\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[1-\f{r_{L}^{3}}{r_{H}^{3}}\right]\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[1-\left(1-\f{\Delta r_{i}}{r_{H}}\right)^{3}\right]\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[1-\left(1+\left(\f{\Delta r_{i}}{r_{H}}\right)^{2}-2\frac{\Delta r_{i}}{r_{H}}\right)\left(1-\f{\Delta r_{i}}{r_{H}}\right)\right]\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[\left(\f{\Delta r_{i}}{r_{H}}\right)^{3}-3\left(\f{\Delta r_{i}}{r_{H}}\right)^{2}+3\f{\Delta r_{i}}{r_{H}}\right]\right\}\\
-    &=\text{min}_{i}\left\{\f{\ve}{6}\,\Delta r_{i}\left[\left(\f{\Delta r_{i}}{r_{H}}\right)^{2}-3\left(\f{\Delta r_{i}}{r_{H}}\right)+3\right]\right\}.
-\end{align}
-We know that $\Delta r_{i}/r_{H}\in\left[0,1\right]$; the minimum value of the quadratic function in this domain is unity. So, we have that for spherical-polar coordinates:
-\begin{equation}
-    \Delta t<\f{\ve}{6}\,\text{min}\left(\Delta r_{i}\right).
-\end{equation}
-
-Next we handle the source term.
-
-\subsubsection{Source term}
-For this section we drop the subscript $K$ and the superscript $n$ (but keep in mind that all quantities are still cell-averages). We have to show that $\bH_{2}\in\cG$, where
-\begin{equation}
-    \bH_{2}=\begin{pmatrix}D\\ S_{j}+\f{\Delta t}{1-\ve}\,Q_{j} \\ \tau\end{pmatrix},\hspace{1em}\left(H_{2}\right)_{1}>0,\hspace{1em}\left(H_{2}\right)_{5}+\left(H_{2}\right)_{1}>\sqrt{\left(H_{2}\right)_{1}\left(H_{2}\right)_{1}+\left(H_{2}\right)_{j}\left(H_{2}\right)^{j}}.
-\end{equation}
-
-It is clear that the first requirement for $\bH_{2}$ is met, i.e. $D>0$. The second requirement is:
-\begin{align}
-    D+\tau&>\sqrt{D^{2}+\left[S_{j}+\f{\Delta t}{1-\ve}Q_{j}\right] \left[S^{j}+\f{\Delta t}{1-\ve}Q^{j}\right]}\\
-    &=\sqrt{D^{2}+S_{j}\,S^{j}+\f{\Delta t}{1-\ve}\left(S_{j}\,Q^{j}+S^{j}\,Q_{j}\right)+\left(\f{\Delta t}{1-\ve}\right)^{2}\,Q_{j}\,Q^{j}}
-\end{align}
-Now we square both sides:
-\begin{align}
-    &D^{2}+\tau^{2}+2\,D\,\tau>D^{2}+S_{j}\,S^{j}+\f{\Delta t}{1-\ve}\left(S_{j}\,Q^{j}+S^{j}\,Q_{j}\right)+\left(\f{\Delta t}{1-\ve}\right)^{2}\,Q_{j}\,Q^{j}\\
-    \implies&\tau\left(\tau+2\,D\right)>\gamma^{jk}\,S_{j}\,S_{k}+\f{2\,\Delta t}{1-\ve}\,\gamma^{jk}\,S_{j}\,Q_{k}+\left(\f{\Delta t}{1-\ve}\right)^{2}\,\gamma^{jk}\,Q_{j}\,Q_{k}\\
-    \implies&\tau\left(\tau+2\,D\right)>\f{S_{j}\,S_{k}}{\gamma_{jk}}+\f{2\,\Delta t}{1-\ve}\,\f{S_{j}\,Q_{k}}{\gamma_{jk}}+\left(\f{\Delta t}{1-\ve}\right)^{2}\,\f{Q_{j}\,Q_{k}}{\gamma_{jk}}\\
-    \implies&a\left(\Delta t\right)^{2}+b\,\Delta t+c<0,
-\end{align}
-where:
-\begin{align}
-    a&=\f{1}{\left(1-\ve\right)^{2}}\,\vv{Q}\cdot\vv{Q}=\f{1}{\left(1-\ve\right)^{2}}\,\f{Q_{j}\,Q_{k}}{\gamma_{jk}}=\f{1}{\left(1-\ve\right)^{2}}\sum\limits_{k=1}^{3}\f{\left(Q_{k}\right)^{2}}{\gamma_{kk}}\\
-    b&=\f{2}{1-\ve}\,\vv{S}\cdot\vv{Q}=\f{2}{1-\ve}\,\f{S_{j}\,Q_{k}}{\gamma_{jk}}=\f{2}{1-\ve}\sum\limits_{k=1}^{3}\f{S_{k}\,Q_{k}}{\gamma_{kk}}\\
-    c&=-\tau\left(\tau+2\,D\right)+\vv{S}\cdot\vv{S}=-\tau\left(\tau+2\,D\right)+\sum\limits_{k=1}^{3}\f{\left(S_{k}\right)^{2}}{\gamma_{kk}}.
-\end{align}
-We want to make sure that our function has at least one real root, which means we must have that $b^{2}-4\,a\,c\geq0$:
-\begin{align}
-    b^{2}-4\,a\,c&=\f{4}{\left(1-\ve\right)^{2}}\left(\vv{S}\cdot\vv{Q}\right)^{2}-\f{4}{\left(1-\ve\right)^{2}}\,\vv{Q}\cdot\vv{Q}\left[-\tau\left(\tau+2\,D\right)+\vv{S}\cdot\vv{S}\right]\\
-    &=\f{4}{\left(1-\ve\right)^{2}}\left[\left(\vv{S}\cdot\vv{Q}\right)^{2}-\left(\vv{Q}\cdot\vv{Q}\right)\left(\vv{S}\cdot\vv{S}\right)+\tau\left(\tau+2\,D\right)\vv{Q}\cdot\vv{Q}\right]\\
-    &=\f{4}{\left(1-\ve\right)^{2}}\left[\left|\vv{S}\right|^{2}\left|\vv{Q}\right|^{2}\,\cos^{2}\theta_{SQ}-\left|\vv{Q}\right|^{2}\left|\vv{S}\right|^{2}+\tau\left(\tau+2\,D\right)\left|\vv{Q}\right|^{2}\right]\\
-    &=\f{4}{\left(1-\ve\right)^{2}}\left|\vv{Q}\right|^{2}\left[\tau\left(\tau+2\,D\right)-\left|\vv{S}\right|^{2}\left(1-\cos^{2}\theta_{SQ}\right)\right]\\
-    &=\f{4}{\left(1-\ve\right)^{2}}\left|\vv{Q}\right|^{2}\left[\tau\left(\tau+2\,D\right)-\left|\vv{S}\right|^{2}\sin^{2}\theta_{SQ}\right],
-\end{align}
-where $\theta_{SQ}$ is the angle between the momentum-density vector and the source-term vector. To guarantee at least one real root we must have that
-\begin{equation}
-    \tau\left(\tau+2\,D\right)\geq\left|\vv{S}\right|^{2}\,\sin^{2}\theta_{SQ}.
-\end{equation}
-
-\newpage
-\begin{equation}
-    b^{2}-4\,a\,c'=\f{4\left(S_{1}\right)^{2}}{\gamma_{11}}a-4\,a\left(S_{1}\,S^{1}-\tau^{2}-2\,D\,\tau\right)=4\,a\,\tau\left(\tau+2\,D\right).
-\end{equation}
-Since $\tau\geq0$, we must have that $\tau>-2\,D$. But, from condition two for $\bH_{K,2}$ we have that $\tau>-D$, so this condition is automatically satisfied.
-
-The solutions to this quadratic equation are:
-\begin{align}
-    \Delta t&=\f{-b}{2\,a}\pm\f{1}{2\,a}\sqrt{b^{2}-4\,a\,c'}=\f{-S_{1}}{\sqrt{\gamma_{11}}\,\sqrt{a}}\pm\f{1}{2\,a}\sqrt{\f{4S_{1}^{2}}{\gamma_{11}}a-4\,a\,c'}\\
-    &=\f{-S_{1}}{\sqrt{\gamma_{11}}\,\sqrt{a}}\pm\f{1}{\sqrt{\gamma_{11}}\,\sqrt{a}}\sqrt{S_{1}^{2}-c'\,\gamma_{11}}=\f{1}{\sqrt{\gamma_{11}}\,\sqrt{a}}\left[-S_{1}\pm\sqrt{S_{1}^{2}-c'\,\gamma_{11}}\right]\\
-    &=\f{1}{\sqrt{\gamma_{11}}\,\sqrt{a}}\left[-S_{1}\pm\sqrt{\gamma_{11}\left(\tau^{2}+2\,D\,\tau\right)}\right]\\
-    &=\f{2\left(1-\ve\right)}{P^{kk}\,\p_{1}\,\gamma_{kk}}\left[-S_{1}\pm\sqrt{\gamma_{11}\left(\tau^{2}+2\,D\,\tau\right)}\right]\\
-    &=\f{2\left(1-\ve\right)}{P^{kk}\,\p_{1}\,\gamma_{kk}}\left[-S_{1}\pm\sqrt{\gamma_{11}\,\tau\left(\tau+2\,D\right)}\right].
-\end{align}
-
-So, we end up with:
-\begin{equation}
-    \Delta t<\text{min}\left\{\text{min}_{i}\left(\f{\ve\,\Delta V_{K}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right),\text{min}^{n}_{i}\left(\f{2\left(1-\ve\right)}{P^{kk}\,\p_{1}\,\gamma_{kk}}\left[-S_{1}\pm\sqrt{\gamma_{11}\,\tau\left(\tau+2\,D\right)}\right]\right)\right\}.
-\end{equation}
-
-\subsection{Demanding that $q>0$}
-
-Sometimes it happens that the cell-average of $q$, $q_{K}\equiv q\left(\bU_{K}\right)<0$, so our positivity limiter will fail.
-To get around this we modify the conserved energy, $\tau$, to demand that $q=\ve$, where $0<\ve\ll1$.
-The transformation we make is:
-\begin{equation}
-   \tau_{K}\longrightarrow\alpha\,\tau_{K},\hspace{1em}\alpha>1.
-\end{equation}
-This modifies the definition of $q_{K}$ from:
-\begin{equation}
-   q_{K}=\tau_{K}+D_{K}-\sqrt{D_{K}^{2}+S_{K}^{2}+\ve}<0,
-\end{equation}
-to:
-\begin{equation}
-   \ve=\alpha\,\tau_{K}+D_{K}-\sqrt{D_{K}^{2}+S_{K}^{2}+\ve}.
-\end{equation}
-Solving this for $\alpha$, we get:
-\begin{equation}
-   \alpha=\tau_{K}^{-1}\left[\ve-D_{K}+\sqrt{D_{K}^{2}+S_{K}^{2}+\ve}\right].
-\end{equation}
-
-\section{Computing the Time-Step Using Higher-Order DG Schemes}
-
-When making the jump to higher-order DG schemes, we can simply do the same as in the first-order scheme, except we compute the quantities in all of the nodal points instead of using a cell-average.
-This is valid because the cell-average is a convex combination...\sd{Need to expand on this}.
-The proof starts with the discretized equation valid at each quadrature point, $q$:
-\begin{equation}
-    \bU_{q}^{n+1}=\bU_{q}^{n}+\Delta t\,\cL_{q}^{n},
-\end{equation}
-where $\cL_{q}^{n}$ is a general form of the RHS at time $t^{n}$.
-If we define a vector $\ol{\bU}\equiv\left(\bU_{1},\cdots,\bU_{q},\cdots,\bU_{Q}\right)^T$, where $Q$ is the total number of quadrature points, and $\ol{\bW}\equiv\left(\bW_{1},\cdots,\bW_{q},\cdots,\bW_{Q}\right)^T$ as a vector of quadrature weights, then we can write the cell-average of $\bU$ as:
-\begin{equation}
-    \bU_{K}\equiv\ol{\bW}^T\ol{\bU}.
-\end{equation}
-If we then compute the cell-average of the above equation, we get:
-\begin{equation}
-    \bU_{K}^{n+1}=\bU_{K}^{n}+\Delta t\,\ol{\bW}^{T}\,\ol{\cL}_{q}^{n}=\ol{\bW}^{T}\left(\ol{\bU}^{n}+\Delta t\,\ol{\cL}^{n}\right)
-\end{equation}
-
-\newpage
-\section{Recovery of Primitive Variables}
-In order to recover the primitive from the conserved variables we need to solve the nonlinear equation:
-\begin{equation}
-    f\left(p\right)=p-\ol{p}\left(p\right)=0,
-\end{equation}
-where $\ol{p}\left(p\right)$ is the pressure as obtained via the ideal gas equation of state with an initial guess, $p$:
-\begin{equation}
-    \ol{p}=\left(\Gamma-1\right)\rho\,\epsilon,
-\end{equation}
-where
-\begin{equation}
-    \rho=\rho\left(\bU,p\right),\hspace{1em}\epsilon=\epsilon\left(\bU,p\right).
-\end{equation}
-
-In order to solve this equation we make use of the bisection method, and therefore need bounds on our initial guess for the pressure.
-
-\subsection{Upper and Lower Bounds for Pressure}
-We obtain a lower bound for the pressure with:
-\begin{equation}
-\tau=D\left(h\,W-1\right)-p\implies p=-\left(\tau+D\right)+D\,h\,W\geq-\left(\tau+D\right)+D\,h\,W\,\sqrt{v^{i}\,v_{i}}=-\left(\tau+D\right)+\sqrt{S^{i}\,S_{i}}.
-\end{equation}
-So, since the pressure must be non-negative, we have:
-\begin{equation}
-p\geq\text{MAX}\left[-\left(\tau+D\right)+\sqrt{S^{i}\,S_{i}},\text{SqrtTiny}\right].
-\end{equation}
-
-For an upper bound, we first note that:
-\begin{equation}
-h=1+\f{e+p}{\rho}=1+\f{\Gamma}{\Gamma-1}\f{p}{\rho}=1+\f{\Gamma}{\Gamma-1}\,\f{p\,W}{D},
-\end{equation}
-so,
-%\begin{equation}
-%    \tau=D\left(W+\f{\Gamma}{\Gamma-1}\f{p\,W^{2}}{D}-1\right)-p=D\left(W-1\right)+p\left(\f{\Gamma}{\Gamma-1}W^{2}-1\right).
-%\end{equation}
-%So,
-%\begin{equation}
-%    p=\f{\tau-D\left(W-1\right)}{\f{\Gamma}{\Gamma-1}W^{2}-1}.
-%\end{equation}
-%We also have:
-%\begin{equation}
-%    W=\left(1-v^{i}\,v_{i}\right)^{-1/2}=\left(1-\f{S^{i}\,S_{i}}{\left(\tau+D+p\right)^{2}}\right)^{-1/2}.
-%\end{equation}
-%Treating $p$ as an independent variable \sd{is this valid?}, we have:
-%\begin{equation}
-%    W\Big|_{p\rightarrow\infty}=1,
-%\end{equation}
-%which gives us an upper limit:
-%\begin{equation}
-%    p\leq\f{\Gamma-1}{\Gamma}\,\tau.
-%\end{equation}
-%Just to be safe, in the code we multiply this by two, so that:
-%\begin{equation}
-%    p\leq2\,\f{\Gamma-1}{\Gamma}\,\tau.
-%\end{equation}
-\begin{equation}
-    \tau=D\left(W+\f{\Gamma}{\Gamma-1}\f{p\,W^{2}}{D}-1\right)-p=D\left(W-1\right)+p\left(\f{\Gamma}{\Gamma-1}W^{2}-1\right)>p\left(\f{\Gamma}{\Gamma-1}-1\right)=\f{p}{\Gamma-1}.
-\end{equation}
-So,
-\begin{equation}
-    p<\left(\Gamma-1\right)\tau.
-\end{equation}
-Typically, $\Gamma-1<3$. So, we end up with:
-\begin{equation}
-    p<3\,\tau.
-\end{equation}
-
-\newpage
-
-\section{Error Introduced by Linear Interpolation}
-We obtain the initial conditions for the standing accretion shock problem with an external code.
-We then have to interpolate these data onto the grid for use in \texttt{thornado}.
-We start by proving that linear interpolation is a convex combination of the solution at the boundary points.
-
-\subsection{Proof that Linear Interpolation is a Convex Combination of Boundary-Points}
-Linear interpolation of a function, $f$, of a variable, $r$, bounded by two points $r_{L}$ and $r_{H}$, with $r_{H}>r_{L}$, can be written as:
-\begin{equation}
-    f\left(r\right)=f\left(r_{L}\right)+\f{f\left(r_{H}\right)-f\left(r_{L}\right)}{r_{H}-r_{L}}\left(r-r_{L}\right).
-\end{equation}
-By making a change of variables from $r$ to $\eta$, where:
-\begin{equation}
-    r\left(\eta\right)=\eta\,r_{H}+\left(1-\eta\right)r_{L}=r_{L}+\eta\,\Delta r\implies\eta=\f{r-r_{L}}{\Delta r},\hspace{1em}\eta\in\left[0,1\right],
-\end{equation}
-such that $r\left(\eta=0\right)=r_{L}$ and $r\left(\eta=1\right)=r_{H}$, we have that:
-\begin{align}
-    f\left(\eta\right)&=f\left(0\right)+\f{f\left(1\right)-f\left(0\right)}{1-0}\left(\eta-0\right)=f\left(0\right)+\left(f\left(1\right)-f\left(0\right)\right)\eta\\
-    \implies f\left(\eta\right)&=\eta\,f\left(1\right)+\left(1-\eta\right)f\left(0\right).
-\end{align}
-
-So when we interpolate a fluid variable, say the mass-density $\rho$, we have:
-\begin{equation}
-    \rho\left(r\right)=\rho_{L}+\f{\Delta\rho}{\Delta r}\left(r-r_{L}\right)\longrightarrow\rho\left(\eta\right)=\eta\,\rho_{H}+\left(1-\eta\right)\rho_{L},
-\end{equation}
-where $\rho_{L}\equiv\rho\left(r_{L}\right)$ and $\rho_{H}=\rho\left(r_{H}\right)$.
-
-\subsection{Example: $f\left(x\right)=x^{2}$}
-We can show this directly for simple functions. We take as an example $f\left(x\right)=x^{2}$:
-\begin{align}
-    f\left(x\right)&=x^{2}=\left[x_{L}+\eta\left(x_{R}-x_{L}\right)\right]^{2}=x_{L}^{2}+\eta^{2}\left(x_{R}-x_{L}\right)^{2}+2\,x_{L}\,\eta\left(x_{R}-x_{L}\right)\\
-    &=x_{L}^{2}+\eta^{2}\,x_{R}^{2}+\eta^{2}\,x_{L}^{2}-2\,\eta^{2}\,x_{L}\,x_{R}+2\,\eta\,x_{L}\,x_{R}-2\,\eta\,x_{L}^{2}.
-\end{align}
-Now we add and subtract the interpolated solution: $\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}$. This yields:
-\begin{align}
-    x^{2}&=x_{L}^{2}+\eta^{2}\,x_{R}^{2}+\eta^{2}\,x_{L}^{2}-2\,\eta^{2}\,x_{L}\,x_{R}+2\,\eta\,x_{L}\,x_{R}-2\,\eta\,x_{L}^{2}+\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}-\eta\,x_{H}^{2}-\left(1-\eta\right)x_{L}^{2}\\
-    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]+\left[-\eta\left(1-\eta\right)x_{L}^{2}-\eta\left(1-\eta\right)x_{H}^{2}+2\,\eta\,x_{L}\,x_{H}\left(1-\eta\right)\right]\\
-    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left[x_{L}^{2}+x_{H}^{2}-2\,x_{L}\,x_{H}\right]\\
-    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left(x_{H}-x_{L}\right)^{2}\\
-    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left(\Delta x\right)^{2}.
-\end{align}
-The term in square brackets is the interpolated solution, and the second term is the remainder, i.e. the error in the interpolated solution. We show the results of this in the following figure:
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.75]{LinearInterpolationError}
-\end{figure}
-
-\subsection{Mass Constant}
-The mass constant, $C_{D}$, from the 3+1 GR hydrodynamics equations is:
-\begin{equation}
-    C_{D}\left(r\right)=\psi\left(r\right)^{6}\,\alpha\left(r\right)\,r^{2}\,\rho\left(r\right)\,W\left[v\left(r\right)\right]\,v\left(r\right).
-\end{equation}
-From the data we have this exact value at the two endpoints:
-\begin{align}
-    C_{D}\left(r_{L}\right)&\equiv C^{L}_{D}=\psi_{L}^{6}\,\alpha_{L}\,r_{L}^{2}\,\rho_{L}\,W_{L}\,v_{L}\\
-    C_{D}\left(r_{H}\right)&\equiv C^{H}_{D}=\psi_{H}^{6}\,\alpha_{H}\,r_{H}^{2}\,\rho_{H}\,W_{H}\,v_{H}.
-\end{align}
-
-\newpage
+\include{SamsTexFiles/DGScheme}
+\include{SamsTexFiles/BP_Methods_FirstOrder_DGScheme}
+\include{SamsTexFiles/Time-Step_Restriction_High-Order}
+\include{SamsTexFiles/RecoveryOfPrimitiveVariables}
+\include{SamsTexFiles/LinearInterpolationError}
 

### 2018-11-29 Documents/Euler/SamsTexFiles/Time-Step_Restriction_High-Order.tex
Updated dgEulerGR.tex document

@@
 We assume that the DG approximation polynomial for the conserved variables is of order $k$, and that the order of the approximate solution is of order $k+d$, where $d$ is an integer that depends on the metric determinant.
-For the case of Cartesian coordinates, $d=0$ (because $\sqrtgm\sim x^{0}$), and for spherical-polar coordinates, $d=2$ (because $\sqrtgm\sim r^{2}$).
+For the case of Cartesian coordinates, $d=0$ (because $\sqrtgm\sim x^{0}$), and for spherical-polar coordinates in spherical symmetry, $d=2$ (because $\sqrtgm\sim r^{2}$).
 Gauss-Lobatto integration will give an exact result if we choose a sufficiently high number, $M$, of quadrature points:
@@
 \end{align}
-All of the terms in the square brackets are similar the the $\bH$ quantities in \citet{Qin2016}.
+All of the terms in the square brackets are similar the the $\bH$ quantities in \citet{Qin2016} and therefore belong to the set of admissible states, provided that:
+\begin{equation}
+    \alpha_{L/H}=\alpha^{*}\geq\f{\left|v^{1}\right|\left(h+1-2\,h\,\tau\right)\,W^{2}+\sqrt{\tau^{4}\left(h-1\right)^{2}+\tau^{2}\left(h-1\right)\left(h+1-2\,h\,\tau\right)}}{W^{2}\left(h+1-2\,h\,\tau\right)+\tau^{2}\left(h-1\right)},
+\end{equation}
+where $h$ is the relativistic specific enthalpy and
+\begin{equation}
+    \tau\equiv\f{\Gamma-1}{\Gamma},
+\end{equation}
+where $\Gamma$ is the adiabatic index.
+
 We see that the expressions in the curly brackets are convex combinations (given a restriction on $\Delta t_{j}$), because the coefficients sum to unity.
@@
 \begin{equation}
-\Delta t_{j}<\ve\,\Delta x_{j}\,w_{GL}\,\text{min}\left(\f{1}{\alpha_{L}},\f{1}{\alpha_{H}}\right)
+\Delta t_{j}<\ve\,\Delta x_{j}\,w_{GL}\,\text{min}\left(\f{1}{\alpha_{L}},\f{1}{\alpha_{H}},\f{1}{\alpha^{*}}\right)
 \end{equation}
@@
 \begin{equation}
-\Delta t<\ve\,w_{GL}\,\text{min}_{j}\left(\f{\Delta x_{j}}{\text{max}\left(\alpha_{L},\alpha_{H}\right)}\right).
+\Delta t<\ve\,w_{GL}\,\text{min}_{j}\left(\f{\Delta x_{j}}{\text{max}\left(\alpha_{L},\alpha_{H},\alpha^{*}\right)}\right).
 \end{equation}
@@
 \blue{NOTE:} We see the effect of the high-order approximation in the presence of the quadrature end-point weight $w_{GL}$.
-As the order increases, $w$ decreases, thus making a tighter restriction on the time-step.
+As the order increases, $w_{GL}$ decreases, thus making a tighter restriction on the time-step.
 

### 2018-12-12 Documents/M1/collisionsM1/collisionsM1.tex
initial commit of document on collision terms

\documentclass[12pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{yhmath}
\usepackage{natbib}
\usepackage{../../definitions}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

\newcommand{\IN}{\mbox{\tiny In}}
\newcommand{\OUT}{\mbox{\tiny Out}}
\newcommand{\NNS}{\mbox{\tiny NNS}} % Neutrino-Nucleon/Nuclei Scattering
\newcommand{\NES}{\mbox{\tiny NES}} % Neutrino-Electron Scattering
\newcommand{\PROD}{\mbox{\tiny Pr}}
\newcommand{\ANN}{\mbox{\tiny An}}
\newcommand{\SC}{\mbox{\tiny Sc}}      % Scattering
\newcommand{\TP}{\mbox{\tiny TP}}      % Pair-Processes

\newtheorem{define}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{theorem}{Theorem}

\begin{document}

\title{A Spectral Two-Moment Model \\ for Neutrino-Matter Interactions}
\author{Eirik Endeve et al.}

\maketitle

\begin{abstract}
  We derive moment equations from the space homogeneous Boltzmann equation for neutrino transport and develop algorithms to solve the neutrino-matter coupling problem.  
  Electron-type neutrinos and antineutrinos are coupled to a fluid through emission and absorption, scattering, and pair processes.  
\end{abstract}

\tableofcontents

\section{Mathematical Model}

\subsection{Boltzmann Equation and Neutrino-Matter Interactions}

We denote the neutrino three-momentum with $\vect{p}=\epsilonNu\,\vect{\ell}(\omegaNu)$, the momentum space volume element with $d\vect{p}=dV_{\epsilonNu}\,d\omegaNu$, where $dV_{\epsilonNu}=\epsilonNu^{2}d\epsilonNu$ is the spherical shell energy volume element, and $d\omega$ is the momentum space angular element.  
The distribution function $f_{s}$ gives the number of neutrinos per phase-space volume
\begin{equation}
  dN_{s}=f_{s}(\vect{x},\vect{p},t)\,d\vect{x}\,d\vect{p}
  =f_{s}(\vect{x},\omegaNu,\epsilonNu,t)\,d\vect{x}\,d\omegaNu\,dV_{\epsilonNu},
\end{equation}
and the equation describing the evolution of neutrino flavor $s$ is given by (e.g., \citep{bruenn_1985})
\begin{align}
  \deriv{f_{s}}{t}(\vect{p})
  & = \big(1-f_{s}(\vect{p})\big)\,\eta_{s}(\vect{p}) - \chi_{s}(\vect{p})\,f_{s}(\vect{p}) \nonumber \\
  & \hspace{12pt}
  +\big(1-f_{s}(\vect{p})\big)\int_{\bbR^{3}}R_{s}^{\IN}(\vect{p}',\vect{p})\,f_{s}(\vect{p}')\,d\vect{p}' \nonumber \\
  & \hspace{12pt}
  -f_{s}(\vect{p})\int_{\bbR^{3}}R_{s}^{\OUT}(\vect{p}',\vect{p})\,\big(1-f_{s}(\vect{p}')\big)\,d\vect{p}' \nonumber \\
  & \hspace{12pt}
  +\big(1-f_{s}(\vect{p})\big)\int_{\bbR^{3}}R_{s}^{\PROD}(\vect{p}',\vect{p})\,\big(1-\bar{f}_{s}(\vect{p}')\big)\,d\vect{p}' \nonumber \\
  & \hspace{12pt}
  -f_{s}(\vect{p})\int_{\bbR^{3}}R_{s}^{\ANN}(\vect{p}',\vect{p})\,\bar{f}_{s}(\vect{p}')\,d\vect{p}',
  \label{eq:homogeneousBoltzmann}
\end{align}
where $\eta_{s}$ is the emissivity, $\chi_{s}$ the absorption opacity, $R_{s}^{\IN}$ and $R_{s}^{\OUT}$ scattering rates in and out of the momentum space bin centered on $\vect{p}$, and $R_{s}^{\PROD}$ and $R_{s}^{\ANN}$ are thermal production and annihilation rates due to pair processes.  
(We have adopted units where the speed of light and the Planck constant are unity.)  
In the expressions for pair processes, $\bar{f}_{s}$ is the distribution function for antineutrinos of flavor $s$.

For thermal emission and absorption we define
\begin{equation}
  \tilde{\chi}_{s}=\eta_{s}+\chi_{s},
\end{equation}
and rewrite
\begin{equation}
  \big(1-f_{s}\big)\,\eta_{s}-\chi_{s}\,f_{s}
  =\tilde{\chi}_{s}\,\big(f_{0,s}-f_{s}\big),
\end{equation}
where the equilibrium distribution is
\begin{equation}
  f_{0,s}=\f{\eta_{s}}{\eta_{s}+\chi_{s}}.  
\end{equation}
In beta equilibrium, $f_{0,s}$ is given by the Fermi-Dirac distribution
\begin{equation}
  f_{0,s}=\f{1}{e^{(\varepsilon-\mu_{s})/kT}+1},
\end{equation}
where $\mu_{s}$ is the neutrino chemical potential and $T$ is the matter temperature.  
For electron neutrinos ($s=\nu_{e}$), $\mu_{\nu_{e}}=\mu_{e^{-}}+(\mu_{p}-\mu_{n})$, while for electron antineutrinos ($s=\bar{\nu}_{e}$), $\mu_{\bar{\nu}_{e}}=\mu_{e^{+}}-(\mu_{p}-\mu_{n})$.  
Here, $\mu_{e^{-(+)}}$ is the electron (positron) chemical potential, $\mu_{n}$ the neutron chemical potential, and $\mu_{p}$ the proton chemical potential, which are evaluated with an appropriate equation of state (EoS).

We exploit the fact that the scattering and pair process kernels depend on the energies $\varepsilon$ and $\varepsilon'$ and the cosine of the scattering angle $\cos\alpha=\vect{\ell}\cdot\vect{\ell}'$, and introduce the $L$-term Legendre expansion
\begin{equation}
  R(\vect{p},\vect{p}')
  =R(\varepsilon,\varepsilon',\vect{\ell}\cdot\vect{\ell}')
  \approx\sum_{l=0}^{L}\Phi_{l}(\varepsilon,\varepsilon')\,P_{l}(\vect{\ell}\cdot\vect{\ell}').  
\end{equation}
From orthogonality of the Legendre polynomials, we have
\begin{equation}
  \Phi_{l}(\varepsilon,\varepsilon')
  =\f{1}{C_{l}}\int_{-1}^{1}R(\varepsilon,\varepsilon',x)\,P_{l}(x)\,dx,
\end{equation}
where $C_{l}$ ($l=0,\ldots,L$) are normalization constants.  
In the following, as a first approximation, we will only include the isotropic part of the kernels (i.e., $L=0$).

\subsection{Angular Moment Equations}

In the spectral two-moment model we solve for the zeroth and first moments of the neutrino distribution function, defined respectively as
\begin{equation}
  \big\{\,\cJ_{s},\vect{\cH}_{s}\,\big\}(\varepsilon)=\f{1}{4\pi}\int_{\bbS^{2}}f_{s}(\varepsilon,\omega)\,\big\{\,1,\vect{\ell}(\omega)\,\big\}\,d\omega,
\end{equation}
with moments for antineutrinos ($\bar{\cJ}_{s}$ and $\bar{\vect{\cH}}_{s}$) defined analogously.  
Then, the zeroth moment $\cJ_{s}$ ($\bar{\cJ}_{s}$) is the spectral number density of neutrinos (antineutrinos), and the first moment $\vect{\cH}_{s}$ ($\bar{\vect{\cH}}_{s}$) is the spectral number flux density of neutrinos (antineutrinos).  
Since the distribution function is bounded by $0\le f_{s}\le1$, it can be shown that the moments must satisfy the bounds
\begin{equation}
  0\le\cJ_{s}\le1
  \quad\text{and}\quad
  |\vect{\cH}_{s}|\le\big(1-\cJ_{s}\big)\,\cJ_{s}.  
\end{equation}
(Similar bounds hold for antineutrinos.)

Taking the zeroth moment of Eq.~\eqref{eq:homogeneousBoltzmann} results in the moment equation for the number density
\begin{equation}
  \deriv{\cJ_{s}}{t}
  =\widehat{\eta}_{s} - \widehat{\chi}_{s}\,\cJ_{s},
  \label{eq:momentNumber}
\end{equation}
where we have defined the total emissivity
\begin{equation}
  \widehat{\eta}_{s}(\cJ_{s},\bar{\cJ}_{s})
  =\tilde{\chi}_{s}\,\cJ_{0,s} + \eta_{\SC,s}(\cJ_{s}) + \eta_{\TP,s}(\bar{\cJ}_{s})
\end{equation}
and total opacity
\begin{equation}
  \widehat{\chi}_{s}(\cJ_{s},\bar{\cJ}_{s})
  =\tilde{\chi}_{s} + \chi_{\SC,s}(\cJ_{s}) + \chi_{\TP,s}(\bar{\cJ}_{s}).  
\end{equation}
We have also defined the scattering emissivity
\begin{equation}
  \eta_{\SC,s}(\cJ_{s})
  =\int_{\bbR^{+}}\Phi_{0,s}^{\IN}(\varepsilon,\varepsilon')\,\cJ_{s}(\varepsilon')\,dV_{\varepsilon'},
\end{equation}
the scattering opacity
\begin{equation}
  \chi_{\SC,s}(\cJ_{s})
  =\int_{\bbR^{+}}\big[\,\Phi_{0.s}^{\IN}(\varepsilon,\varepsilon')\,\cJ(\varepsilon')+\Phi_{0,s}^{\Out}(\varepsilon,\varepsilon')\,\big(1-\cJ(\varepsilon')\big)\,\big]\,dV_{\varepsilon'},
\end{equation}
the emissivity due to thermal pair processes
\begin{equation}
  \eta_{\TP,s}(\bar{\cJ}_{s})
  =\int_{\bbR^{+}}\Phi_{0,s}^{\PROD}(\varepsilon,\varepsilon')\,\big(1-\bar{\cJ}_{s}(\varepsilon')\big)\,dV_{\varepsilon'},
\end{equation}
and the opacity due to thermal pair processes
\begin{equation}
  \chi_{\TP,s}(\bar{\cJ}_{s})
  =\int_{\bbR^{+}}\big[\,\Phi_{0,s}^{\PROD}(\varepsilon,\varepsilon')\,\big(1-\bar{\cJ}_{s}(\varepsilon')\big)+\Phi_{0,s}^{\ANN}(\varepsilon,\varepsilon')\,\bar{\cJ}_{s}(\varepsilon')\,\big]\,dV_{\varepsilon'}.  
\end{equation}
Note that the opacities due to scattering and pair processes depend on $\cJ_{s}$ and $\bar{\cJ}_{s}$, respectively, due to the Fermi blocking factors.  
Since $0\le\cJ_{s},\bar{\cJ}_{s}\le1$, we have $\eta_{\SC,s},\chi_{\SC,s},\eta_{\TP,s},\chi_{\TP,s}\ge0$.  
Also note that the emissivities and opacities depend on the neutrino energy $\varepsilon$ and local thermodynamic conditions (e.g., density $\rho$, temperature $T$, and electron fraction $Y_{e}$).

Similarly, taking the first moment of Eq.~\eqref{eq:homogeneousBoltzmann} results in the equation for the number flux density
\begin{equation}
  \deriv{\vect{\cH}_{s}}{t}
  =-\widehat{\chi}_{s}\,\vect{\cH}_{s}.
  \label{eq:momentFlux}
\end{equation}

\subsection{Matter Equations}

Neutrino-matter interactions mediate exchange of lepton number, momentum, and energy between matter and neutrinos.  
As a first approximation, we will assume that the fluid remains static and ignore momentum exchange.  
Only emission and absorption due to electron capture modify $Y_{e}$, while all processes modify the internal energy.  
The electron fraction $Y_{e}$ and internal energy $e=\rho\,\epsilon$ evolve according to
\begin{equation}
  \rho\deriv{Y_{e}}{t}
  =-m_{b}\int_{\bbR^{+}}
  \big[\,
    \tilde{\chi}_{\nu_{e}}\,\big(\cJ_{0,\nu_{e}}-\cJ_{\nu_{e}}\,\big)
    -\tilde{\chi}_{\bar{\nu}_{e}}\,\big(\,\cJ_{0,\bar{\nu}_{e}}-\cJ_{\bar{\nu}_{e}}\,\big)
  \,\big]\,dV_{\varepsilon},
\end{equation}
and
\begin{equation}
  \rho\deriv{\epsilon}{t}
  =-\sum_{s}\int_{\bbR^{+}}\big(\,\widehat{\eta}_{s} - \widehat{\chi}_{s}\,\cJ_{s}\,\big)\,\varepsilon\,dV_{\varepsilon},
\end{equation}
where $\rho$ is the mass density and $m_{b}$ is the average baryon mass.

The matter sources are constructed to ensure conservation of lepton number and energy.  
The neutrino density $J_{s}(\vect{x},t)$ and energy $E_{s}(\vect{x},t)$ are defined as
\begin{equation}
  \big\{\,J_{s},\,E_{s}\,\big\}
  =\int_{\bbR^{+}}\cJ_{s}(\varepsilon)\big\{\,1,\,\varepsilon\,\big\}\,dV_{\varepsilon}.
\end{equation}
Lepton number conservation is due to
\begin{equation}
  \deriv{}{t}\big(\,J_{\nu_{e}}-J_{\bar{\nu}_{e}}\,\big)+\f{\rho}{m_{b}}\deriv{Y_{e}}{t} = 0,
\end{equation}
while energy conservation is due to
\begin{equation}
  \sum_{s}\deriv{E_{s}}{t}+\rho\deriv{\epsilon}{t} = 0.
\end{equation}

\bibliographystyle{plain}
\bibliography{../../References/references.bib}

\end{document}

### 2018-12-13 Documents/Euler/Astronum_2018/ms_endeve.tex
Working on response to reviewer comments

@@
 We use a formulation of the equations sufficiently general to accommodate curvilinear spatial coordinates encoded in the metric $\gamma_{ij}$, giving the squared line element $ds^{2}=\gamma_{ij}dx^{i}dx^{j}$, whose determinant is $\gamma$.
+Henceforth, we will assume that the spatial metric is time-independent.  
 To solve Eq.~\eqref{eq:extendedEulerCompact}, the computational domain $D\subset\mathbb{R}^{d}$ is divided into a disjoint union $\cT$ of open elements $\bK$, so that $D = \cup_{\bK \in \cT}\bK$.  
@@
 In Section~\ref{sec:numerical} we use the optimal third-order strong stability-preserving Runge-Kutta (SSP-RK3) method from \cite{shuOsher_1988}.  
+We assume that the source term $\vect{S}(\vect{U}_{k})$ is non-stiff so that the equations can integrated efficiently with explicit methods.  
+In future applications of the DG method to model CCSNe we plan to use a combination of implicit and explicit methods (e.g., IMEX methods \cite{ascher_etal_1997}) to stably integrate stiff sources due to neutrino-matter interactions.
 
@@
 We use the TVD-type slope limiter based on limiting characteristic variables, discussed in \cite{cockburnShu_1998}.  
-To prevent excessive limiting (e.g., at smooth extrema), we use the troubled-cell indicator (TCI) of \cite{fuShu_2017}.  
+To prevent excessive limiting (e.g., at smooth extrema), we use the troubled-cell indicator (TCI) of \cite{fuShu_2017}:
 \begin{equation}
@@
 The test is run with $100$ elements until $t=0.2$, using $C_{\TCI}=0.03$.  
-Results are plotted in the left panel of Figure~\ref{fig:SodSedov}.  
-The DG method captures the main features of the solution well without introducing noticeable oscillations near the discontinuities.  
+Results are plotted in the left panels of Figure~\ref{fig:SodSedov}.  
+The DG method captures the main features of the solution well without introducing noticeable oscillations near the discontinuities (upper left panel).  
+In the lower left panel we plot locations in the $xt$-plane of elements flagged for limiting.  
+Limiting is mainly triggered by the contact discontinuity and the shock.  
 \begin{figure}[h]
@@
     \includegraphics[width=18pc]{./Figures/Sedov_Astronum_2018}
+  \end{minipage} \\
+  \begin{minipage}{18pc}
+    \includegraphics[width=18pc]{./Figures/Sod_TCI_Astronum_2018}
+  \end{minipage}\hspace{0.5pc}%
+  \begin{minipage}{18pc}
+    \includegraphics[width=18pc]{./Figures/Sedov_TCI_Astronum_2018}
   \end{minipage}
-  \caption{\label{fig:SodSedov}{\it Left panel:} numerical solution of Sod's problem using $100$ elements (plusses) compared with the exact solution (solid lines; from \cite{toro_1999}).
-{\it Right panel:} numerical solution of the Sedov-Taylor blast wave using $256$ elements (plusses) against the exact solution (solid lines).}
+  \caption{\label{fig:SodSedov}{\it Upper left panel:} numerical solution of Sod's problem using $100$ elements (plusses) compared with the exact solution (solid lines; from \cite{toro_1999}).
+{\it Upper right panel:} numerical solution of the Sedov-Taylor blast wave using $256$ elements (plusses) against the exact solution (solid lines).
+In the lower panels we plot locations in the $xt$-plane of elements flagged for limiting ($I_{\bK}>C_{\TCI}$) by the Sod (left) and Sedov (right) problems.}
 \end{figure}
@@
 We use $256$ elements and run until $t=1$, using $C_{\TCI}=0.03$.  
-Again, the DG method captures the characteristic of the exact solution.  
+Again, the DG method captures the characteristic of the exact solution (cf. upper right panel of Figure~\ref{fig:SodSedov}).  
 The maximum density in the shock is somewhat lower for the numerical solution than the exact value (about $5$ versus $6$).  
+In the lower right panel we map locations of elements flagged for limiting in the $xt$-plane.  
+The troubled-cell indicator tracks the shock well (the analytic shock trajectory is given by the dashed cyan line), but also flags elements at smaller radii with low density.
 
@@
 With full limiting, the scheme is unable to capture the density variations behind the shock (cf. upper right panel in Figure~\ref{fig:ShuOsher}).  
+This is expected since the TVD-type limiter clips extrema.  
+The results improve when the troubled-cell indicator is used.  
 When $C_{\TCI}=0.03$, the variations are better resolved, but the amplitudes are much reduced relative to the reference solution.  
@@
 
-\subsubsection{Isentropic Vortex}
+\subsubsection{Isentropic vortex}
+This test from \cite{shu_1997} is included to verify the accuracy of the DG method implemented in \thornado.  
+The periodic computational domain is given by $D=[-5,5]\times[-5,5]$.  
+The initial density and pressure are given by $\rho_{0}=\big(\,1-\f{(\Gamma-1)\,\beta^{2}}{(8\pi\Gamma)}\exp\big(1-r^{2}\big)\,\big)^{1/(\Gamma-1)}$ and $P_{0}=\rho^{\Gamma}$, where $r=\sqrt{(x^{1})^{2}+(x^{2})^{2}}$, while the velocity components are $v_{0}^{1}=1-\f{x^{2}\beta}{2\pi}\,\exp\big((1-r^{2})/2\big)$ and $v_{0}^{2}=1+\f{x^{1}\beta}{2\pi}\,\exp\big((1-r^{2})/2\big)$.
+The strength of the vortex is set to $\beta=5$, and we use $\Gamma=1.4$.  
+We evolve this test until $t=t_{f}=10$, when the vortex has returned to its initial position.
 
@@
   \includegraphics[width=18pc]{./Figures/IsentropicVortex_Astronum_2018}
-  \caption{\label{fig:IsentropicVortex}Convergence results for the Isentropic Vortex test.}
+  \caption{\label{fig:IsentropicVortex}Convergence results for the Isentropic Vortex:  $L^{\infty}$ error norm versus number of elements in the $x^{1}$-dimension.}
 \end{wrapfigure}
+
+In Figure~\ref{fig:IsentropicVortex} we plot the density error measured in the infinity norm $L^{\infty}=\max_{D}|\rho(\vect{x},t_{f})-\rho_{0}(\vect{x})|$ versus number of cells the $x^{1}$-dimension for various configurations.
+We ran with spatial resolutions of $25\times25$, $50\times50$, $100\times100$, and $200\times200$.  
+In the first set of runs, we ran without any limiting and varied the polynomial degree $k$: $k=1$ (solid red), $k=2$ (solid black), and $k=3$ (solid green).  
+We observe the expected order of accuracy for $k=1$ and $k=2$ (second- and third-order accuracy, respectively; cf. dotted reference lines).  
+For $k=3$, the order of accuracy is close to fourth-order for the lower resolutions, but tends to third-order as the resolution increases, presumably due to the use of third-order time stepping.  
+In the second set of runs, we kept $k=2$ and ran with limiting turned on.  
+We ran one set with $C_{\TCI}=0.03$ (dashed magenta) and one set with $C_{\TCI}=0.1$ (dashed cyan).  
+When $C_{\TCI}=0.03$, the limiter is activated for the lowest resolution run and significantly reduces the accuracy of the method.  
+For all the other runs, the limiter is not activated, and the results are identical to the runs with the limiter turned off.
 
@@
 Early on ($t=1.5$), the results from the two runs are practically indistinguishable, show no sign of developing secondary billows, and agree visually with results presented in \cite{mcnally_etal_2012}.
-When $t=2.4$, the run with $C_{\TCI}=0.03$ has started to develop secondary billows within the coiled-up interface separating dense (white) and less dense (black) fluids, while the model with no limiting has not.
+When $t=2.4$, the run with $C_{\TCI}=0.06$ has started to develop secondary billows within the coiled-up interface separating dense (white) and less dense (black) fluids, while the model with no limiting has not.
+See Figure~\ref{fig:KelvinHelmholtz_TCI} for the spatial distribution of elements flagged for limiting at $t=2.4$.  
 When $t=3.0$, these secondary instabilities appear to have largely destroyed the coil structure for the model with limiting, while the coils remain intact in the model without limiting (although secondary billows have started to form in this model at this time).
@@
 
-\begin{wrapfigure}{r}{2.825in}
-  \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_TCI_24_Astronum_2018}
+\begin{wrapfigure}{l}{2.75in}
+  \centering
+  \includegraphics[width=16pc]{./Figures/KelvinHelmholtz_TCI_24_Astronum_2018}
   \caption{\label{fig:KelvinHelmholtz_TCI}Distribution of elements flagged for limiting in the KH test at $t=2.4$.}
@@
 
-\subsubsection{Liska-Wendroff Explosion}
+\subsubsection{Liska-Wendroff explosion}
 
+This test, also from \cite{liskaWendroff_2003}, is computed on the domain $D=[0,1.5]\times[0,1.5]$ with reflecting inner boundaries and outflow outer boundaries using $256^{2}$ elements.  
+Inside the radius $r=\sqrt{(x^{1})^{2}+(x^{2})^{2}}=0.4$, we initially set $\vect{U}=\big(1.0,\vect{0.0},2.5\big)^{\trans}$, while $\vect{U}=\big(0.125,\vect{0.0},0.25\big)^{\trans}$ elsewhere.  
+We did not apply any smoothing to the initial discontinuity.
+
+Results for $t=3.2$, obtained with $C_{\TCI}=0.1$, are displayed in Figure~\ref{fig:Explosion}, which agree qualitatively with results in \cite{liskaWendroff_2003}.  
+Initially, this test is similar to the Sod shock tube in cylindrical geometry: a shock and a contact discontinuity propagate in the positive radial direction, while a rarefaction wave propagates toward the origin.
+Later, the initial shock leaves the computational domain, while an instability (resembling Richtmeyr-Meshkov) develops in the contact discontinuity.  
+A second shock emerges from the origin of the computational domain and runs through the contact discontinuity, which has developed a complex structure (see density contours in Figure~\ref{fig:Explosion}).
+The second shock is located around $r=1.2$ at $t=3.2$.  
+In the right panel we plot the distribution of elements flagged for limiting by the troubled-cell indicator at $t=3.2$.  
+Limiting is mainly focused on elements around the shock and the contact discontinuity.  
 \begin{figure}[h]
@@
   \end{minipage}
-  \caption{\label{fig:Implosion}Plots for the Liska-Wendroff Explosion problem at $t=3.2$.}
+  \caption{\label{fig:Explosion}Plots for the Liska-Wendroff Explosion problem at $t=3.2$.
+In the left panel, intended to match panels in Figure~4.12 in \cite{liskaWendroff_2003}, the color map shows the pressure distribution, black contours show the mass density, while arrows indicate the velocity.
+In the right panel we plot the distribution of elements flagged for limiting $t=3.2$.}
 \end{figure}
@@
 \begin{thebibliography}{36}
+  \bibitem{ascher_etal_1997} Ascher U M, Ruuth S J and Spiteri R J 1997 {\it Applied Numerical Mathematics} {\bf 23} 151
   \bibitem{bassi_etal_2013} Bassi F, Franchina N, Ghidoni A and Rebay S 2013 {\it Int. J. Numer. Meth. Fluids} {\bf 71} 1322
@@
   \bibitem{shuOsher_1989} Shu C-W and Osher S 1989 {\it JCP} {\bf 83} 32
+  \bibitem{shu_1997} Shu C-W 1997 {\it NASA/CR-97-206253 ICASE Report No. 97-65}
   \bibitem{shu_2016} Shu C-W 2016 {\it JCP} {\bf 316} 598

### 2018-12-13 Documents/Euler/Astronum_2018/ms_endeve.tex
Addressing reviewing reviewer comment 11.

@@
 Let the $d$-dimensional computational domain be $D=\times_{i=1}^{d}[\xMin^{i},\xMax^{i}]$, where $\xMin^{i}$ and $\xMax^{i}$ denote the coordinates of the inner and outer boundary in the $i$th coordinate direction, respectively.
-We use polynomials of degree $k=2$ combined with SSP-RK3 time stepping, and all the tests were run with a Courant-Friedrichs-Lewy (CFL) factor of $C=0.1$.  
+To limit the scope of this initial study, we use polynomials of degree $k=2$ (except in Section~\ref{sec:isentropicVortex}, where we also use $k=1$ and $k=3$) combined with SSP-RK3 time stepping, and run all the tests with a Courant-Friedrichs-Lewy (CFL) factor of $C=0.1$.
 We use the HLL Riemann solver when solving the non-relativistic Euler equations and the HLLC Riemann solver when solving the special relativistic Euler equations.  
@@
 \subsubsection{Isentropic vortex}
+\label{sec:isentropicVortex}
+
 This test from \cite{shu_1997} is included to verify the accuracy of the DG method implemented in \thornado.  

### 2018-12-14 Documents/Euler/Astronum_2018/ms_endeve.tex
Progress on reviewer comments

@@
 \newcommand{\shock}{\textnormal{\tiny\textsc{Sh}}}
+\newcommand{\Pos}{\textnormal{\tiny\textsc{Pos}}}
+\newcommand{\TVD}{\textnormal{\tiny\textsc{Tvd}}}
 \newcommand{\thornado}{\texttt{thornado}}
@@
 To prevent negative mass density and pressure (and superluminal velocity for the relativistic Euler equations), we follow the approaches in \cite{zhangShu_2010,wuTang_2015,qin_etal_2016}.
+
+To summarize the RK-DG algorithm we let $\bar{\vect{U}}$ denote the global solution vector containing all the unknowns in $D$ and $\bar{\vect{F}}$ denote the corresponding DG discretization from the right-hand side of Eq.~\eqref{eq:semidiscreteDiscretized}, so that the global ODE system can be written as the $d_{t}\bar{\vect{U}}=\bar{\vect{F}}(\bar{\vect{U}})$.
+We denote the TVD limiter with $\Lambda^{\TVD}\{\}$ and the `positivty' limiter preventing unphysical states with $ \Lambda^{\Pos}\{\}$.  
+(E.g., application of the TVD limiter is $\bar{\vect{U}} := \Lambda^{\TVD}\{\bar{\vect{U}}\}$.)  
+The general $s$-stage Runge-Kutta time stepping algorithm, which includes application of limiters, can then be written as \cite{cockburnShu_2001}:
+\begin{itemize}
+  \item[1.] Set $\bar{\vect{U}}^{(0)} = \bar{\vect{U}}^{n}$,
+  \item[2.] For $i=1,\ldots,s$ compute:
+  \begin{equation}
+    \bar{\vect{U}}^{(i)} 
+    = \Lambda^{\Pos}\Big\{\,\Lambda^{\TVD}\Big\{\,\sum_{j=0}^{i-1}\Big(\,\alpha_{ij}\,\bar{\vect{U}}^{(j)}+\beta_{ij}\,\Delta t\,\bar{\vect{F}}\big(\bar{\vect{U}}^{(j)}\big)\,\Big)\,\Big\}\,\Big\},
+    \label{eq:rkStages}
+  \end{equation}
+  \item[3.] Set $\bar{\vect{U}}^{n+1}=\bar{\vect{U}}^{(s)}$.  
+\end{itemize}
+The coefficients $\alpha_{ij}$ and $\beta_{ij}$ for SSP-RK3 are given in Table~2.1 in \cite{cockburnShu_2001}.  
+In Eq.~\eqref{eq:rkStages}, for each stage, the TVD limiter is applied first (for elements where $I_{\bK}>C_{\TCI}$), followed by the positivity limiter.  
+The positivity limiter
+
+$\Delta t=\min_{D}(\Delta t_{\TVD},\Delta t_{\Pos})$
+\begin{equation}
+  \Delta t_{\TVD} = \f{1}{d}\,\f{1}{(2k+1)}\min_{i}\big(\Delta x^{i}/|\lambda^{i}|\big)\quad\text{and}\quad
+  \Delta t_{\Pos} = \f{\hat{w}_{N}}{d}\min_{i}\big(\Delta x^{i}/|\lambda^{i}|\big)
+\end{equation}
+For $d=k=2$, the effective Courant-Friedrichs-Lewy (CFL) factor is $0.1$ for $\Delta t_{\TVD}$, while it is $1/12$ for $\Delta t_{\Pos}$.
 
@@
 where $W$ is the Lorentz factor, $h=1+(e+p)/\rho$ is the specific enthalpy, $\tau=\rho W(hW-1)-p$, and $\Pi^{i}_{~j}=\rho h W^{2} u^{i} u_{j}+p\delta^{i}_{~j}$.  
+To recover primitive from conserved variables we have implemented the procedure for analytic equations of state detailed in Appendix~D in \cite{rezzollaZanotti_2013}.  
 We solve two Riemann problems and compare the numerical results with exact solutions obtained with the solver from \cite{martiMuller_2003}.  
@@
     \includegraphics[width=18pc]{./Figures/MB2005_04_Astronum_2018}
+  \end{minipage} \\
+  \begin{minipage}{18pc}
+    \includegraphics[width=18pc]{./Figures/MB2005_01_TCI_Astronum_2018}
+  \end{minipage}\hspace{0.5pc}%
+  \begin{minipage}{18pc}
+    \includegraphics[width=18pc]{./Figures/MB2005_04_TCI_Astronum_2018}
   \end{minipage}
   \caption{\label{fig:RelativisticHydro}Results from solving the SR Euler equations with \thornado.
-Riemann problem~1 (left panel) was solved using $100$ elements, while Riemann problem~2 was solved using $400$ elements.
-The numerical and exact solutions are plotted with plusses and solid lines, respectively.}
+Riemann problem~1 (left panels) was solved using $100$ elements, while Riemann problem~2 (right panels) was solved using $400$ elements.
+The numerical and exact solutions are plotted with plusses and solid lines, respectively.
+In the lower panels we plot $xt$-plane locations of elements flagged for limiting}
 \end{figure}
@@
 This is due to a combination of limited spatial resolution and the action of the slope limiter.  
-We used $C_{\TCI}=0.03$ in both tests in this section.  
+We used $C_{\TCI}=0.03$ in both tests in this section, and we plot locations in the $xt$-plane of elements flagged for limiting in Figure~\ref{fig:RelativisticHydro}.  
+The troubled-cell indicator tracks the discontinuities well for both Riemann problems.  
 We have found the agreement with the exact solution to improve for larger values of $C_{\TCI}$, but at the expense of somewhat more oscillatory results.
@@
   \bibitem{remacle_etal_2003} Remacle J-F, Flaherty J E and Shephard M S 2003 {\it SIAM~Review} {\bf 45} 53
+  \bibitem{rezzollaZanotti_2013} Rezzolla L and Zanotti O 2013 {\it Relativistic Hydrodynamics} Oxford
   \bibitem{schaal_etal_2015} Schaal K, Bauer A, Chandrashekar P R{\"u}diger P, Klingenberg C and Springel V 2015 {\it MNRAS} {\bf 453} 4278

### 2018-12-22 Documents/Euler/Astronum_2018/ms_endeve.tex
Work on response

@@
 With these approaches, we employ high-order discretization techniques based on a common mathematical framework in all the major model components.  
-In this paper, we provide an initial description and encouraging demonstration of the DG method implemented in \thornado\ to solve the Euler equations.  
-We note that others (e.g., \cite{radiceRezzolla_2011,schaal_etal_2015}) have also investigated the DG method in the context of astrophysical hydrodynamics and reported encouraging results.  
 Whether the high-order approach will improve accuracy and efficiency of CCSN models remains to be demonstrated.  
+However, in this paper, we provide an initial description and encouraging demonstration of the DG method implemented in \thornado\ to solve the Euler equations.  
+We focus on basic tests in one and two spatial dimensions and focus, to some extent, on the implementation of limiters in \thornado.  
+We note that others (e.g., \cite{radiceRezzolla_2011,schaal_etal_2015,zanotti_etal_2015,dumbser_etal_2018}) have also investigated the DG method in the context of astrophysical applications and reported encouraging results.
+The DG limiting techniques implemented in \thornado\ are similar to those used by \cite{schaal_etal_2015}, but is supplemented with a troubled-cell indicator \cite{fuShu_2017} to prevent excessive limiting (e.g., around smooth extrema), and differs from more recent approaches in the literature (e.g., \cite{huerta_etal_2012,dumbser_etal_2014,zanotti_etal_2015,sonntagMunz_2017}), which combine the sub-cell resolution of the DG method with high-order finite-volume techniques to improve the performance of the DG limiting procedure.
+While the results with current limiters are encouraging, these latter methods appear as attractive options for future implementation in \thornado.
 
@@
 In Section~\ref{sec:numerical} we use the optimal third-order strong stability-preserving Runge-Kutta (SSP-RK3) method from \cite{shuOsher_1988}.  
-We assume that the source term $\vect{S}(\vect{U}_{k})$ is non-stiff so that the equations can integrated efficiently with explicit methods.  
+We assume that the source term $\vect{S}(\vect{U}_{k})$ is non-stiff so that the equations can be integrated efficiently with explicit methods.  
 In future applications of the DG method to model CCSNe we plan to use a combination of implicit and explicit methods (e.g., IMEX methods \cite{ascher_etal_1997}) to stably integrate stiff sources due to neutrino-matter interactions.
 
-Limiting of the polynomial representation $\vect{U}_{h}$, to reduce oscillations and prevent non-physical states, is a critical step in the DG algorithm.  
+Limiting of the polynomial representation $\vect{U}_{h}$, to reduce oscillations and prevent unphysical states, is a critical step in the DG algorithm.  
 We use the TVD-type slope limiter based on limiting characteristic variables, discussed in \cite{cockburnShu_1998}.  
@@
 
-To summarize the RK-DG algorithm we let $\bar{\vect{U}}$ denote the global solution vector containing all the unknowns in $D$ and $\bar{\vect{F}}$ denote the corresponding DG discretization from the right-hand side of Eq.~\eqref{eq:semidiscreteDiscretized}, so that the global ODE system can be written as the $d_{t}\bar{\vect{U}}=\bar{\vect{F}}(\bar{\vect{U}})$.
-We denote the TVD limiter with $\Lambda^{\TVD}\{\}$ and the `positivty' limiter preventing unphysical states with $ \Lambda^{\Pos}\{\}$.  
-(E.g., application of the TVD limiter is $\bar{\vect{U}} := \Lambda^{\TVD}\{\bar{\vect{U}}\}$.)  
+To summarize the full RK-DG algorithm we let $\bar{\vect{U}}$ denote the global solution vector containing all the unknowns in $D$ and $\bar{\vect{F}}$ denote the corresponding DG discretization from the right-hand side of Eq.~\eqref{eq:semidiscreteDiscretized}, so that the global ODE system can be written as the $d_{t}\bar{\vect{U}}=\bar{\vect{F}}(\bar{\vect{U}})$.
+The TVD limiter and the `positivity' limiter preventing unphysical states are denoted by $\Lambda^{\TVD}\{\}$ and $ \Lambda^{\Pos}\{\}$, respectively (e.g., application of the TVD limiter is $\bar{\vect{U}} := \Lambda^{\TVD}\{\bar{\vect{U}}\}$).
 The general $s$-stage Runge-Kutta time stepping algorithm, which includes application of limiters, can then be written as \cite{cockburnShu_2001}:
@@
 In Eq.~\eqref{eq:rkStages}, for each stage, the TVD limiter is applied first (for elements where $I_{\bK}>C_{\TCI}$), followed by the positivity limiter.  
-The positivity limiter
-
-$\Delta t=\min_{D}(\Delta t_{\TVD},\Delta t_{\Pos})$
+The algorithm is subject to two time step restrictions, the stability condition $\Delta t_{\TVD}$ and the positivity condition $\Delta t_{\Pos}$, and we take $\Delta t=\min_{D}(\Delta t_{\TVD},\Delta t_{\Pos})$.
+Let $(h/|\lambda|)=\min_{i\in\{1,\ldots,d\}}(\Delta x^{i}/|\lambda^{i}|)$, where $|\lambda^{i}|$ is the largest absolute eigenvalue of the flux Jacobian.  
+Then, assuming Cartesian coordinates (e.g., \cite{cockburnShu_2001,zhangShu_2010}):
 \begin{equation}
-  \Delta t_{\TVD} = \f{1}{d}\,\f{1}{(2k+1)}\min_{i}\big(\Delta x^{i}/|\lambda^{i}|\big)\quad\text{and}\quad
-  \Delta t_{\Pos} = \f{\hat{w}_{N}}{d}\min_{i}\big(\Delta x^{i}/|\lambda^{i}|\big)
+  \Delta t_{\TVD} \le \f{1}{d}\,\f{(h/|\lambda|)}{(2k+1)} \quad\text{and}\quad
+  \Delta t_{\Pos} \le \f{\hat{w}_{1}(h/|\lambda|)}{d},
+  \label{eq:timestepRestrictions}
 \end{equation}
+where $\hat{w}_{1}$ is the first quadrature weight of the Gauss-Lobatto quadrature that integrates the cell average of $\vect{U}_{h}$ exactly.  
 For $d=k=2$, the effective Courant-Friedrichs-Lewy (CFL) factor is $0.1$ for $\Delta t_{\TVD}$, while it is $1/12$ for $\Delta t_{\Pos}$.  
+The positivity limiter checks for unphysical states in all the quadrature points involved in the DG discretization.  
+If any point in an element is flagged as unphysical, the polynomial representation $\vect{U}_{h}$ is damped towards its cell average $\vect{U}_{\bK}$, which is guaranteed to be physical by the $\Delta t_{\Pos}$ restriction.
+Note that $\Delta t_{\Pos}$ is a sufficient condition.  
+In practice, the time step can often be set larger than $\Delta t_{\Pos}$.
 
@@
 Let the $d$-dimensional computational domain be $D=\times_{i=1}^{d}[\xMin^{i},\xMax^{i}]$, where $\xMin^{i}$ and $\xMax^{i}$ denote the coordinates of the inner and outer boundary in the $i$th coordinate direction, respectively.
-To limit the scope of this initial study, we use polynomials of degree $k=2$ (except in Section~\ref{sec:isentropicVortex}, where we also use $k=1$ and $k=3$) combined with SSP-RK3 time stepping, and run all the tests with a Courant-Friedrichs-Lewy (CFL) factor of $C=0.1$.
+To limit the scope of this initial study, we use polynomials of degree $k=2$ (except in Section~\ref{sec:isentropicVortex}, where we also use $k=1$ and $k=3$) combined with SSP-RK3 time stepping, and, unless stated otherwise, run all the tests with a CFL factor of $C=0.1$.
 We use the HLL Riemann solver when solving the non-relativistic Euler equations and the HLLC Riemann solver when solving the special relativistic Euler equations.  
@@
   \caption{\label{fig:SodSedov}{\it Upper left panel:} numerical solution of Sod's problem using $100$ elements (plusses) compared with the exact solution (solid lines; from \cite{toro_1999}).
-{\it Upper right panel:} numerical solution of the Sedov-Taylor blast wave using $256$ elements (plusses) against the exact solution (solid lines).
+{\it Upper right panel:} numerical solution of the Sedov-Taylor blast wave using $256$ elements (plusses) against the exact solution (solid lines; from \cite{kammTimmes_2007}).
 In the lower panels we plot locations in the $xt$-plane of elements flagged for limiting ($I_{\bK}>C_{\TCI}$) by the Sod (left) and Sedov (right) problems.}
@@
 
-\begin{wrapfigure}{l}{2.825in}
+\begin{wrapfigure}{L}{2.825in}
   \includegraphics[width=18pc]{./Figures/IsentropicVortex_Astronum_2018}
@@
 For $k=3$, the order of accuracy is close to fourth-order for the lower resolutions, but tends to third-order as the resolution increases, presumably due to the use of third-order time stepping.  
+(Note that we ran the $k=3$ case with a CFL factor of $1/14$; cf. Eq.~\eqref{eq:timestepRestrictions}.)
 In the second set of runs, we kept $k=2$ and ran with limiting turned on.  
@@
 
-\begin{wrapfigure}{l}{2.75in}
+\begin{wrapfigure}{R}{2.825in}
   \centering
-  \includegraphics[width=16pc]{./Figures/KelvinHelmholtz_TCI_24_Astronum_2018}
+  \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_TCI_24_Astronum_2018}
   \caption{\label{fig:KelvinHelmholtz_TCI}Distribution of elements flagged for limiting in the KH test at $t=2.4$.}
@@
 
-\begin{figure}[h]
+\begin{figure}[b]
   \centering
@@
   \bibitem{dumbser_etal_2014} Dumbser M, Zanotti O, Loub{\`e}re R and Diot S 2014 {\it JCP} {\bf 278} 47
+  \bibitem{dumbser_etal_2018} Dumbser M, Guercilena F, K{\"o}ppel S, Rezzolla L and Zanotti O 2018 {\it Phys. Rev. D} {\bf 97} 084053
   \bibitem{fambri_etal_2018} Fambri F, Dumbser M, K{\"o}ppel S, Rezzolla L and Zanotti O 2018 {\it MNRAS} {\bf 477} 4543
@@
   \bibitem{hesthavenWarburton_2008} Hesthaven J S and Warburton T 2008 {\it Nodal discontinuous Galerkin methods: Algorithms, analysis and applications} Springer
+  \bibitem{huerta_etal_2012} Huerta A, Casoni E and Peraire J 2012 {\it Int. J. Numer. Meth. Fluids} {\bf 69} 1614
+  \bibitem{kammTimmes_2007} Kamm J R and Timmes F X 2007 {\it LANL Report, No. LA-UR-07-2849}
   \bibitem{klockner_etal_2009} Kl{\"o}ckner A, Warburton T, Bridge J and Hesthaven J S 2009 {\it JCP} {\bf 228} 7863
@@
   \bibitem{sod_1978} Sod G A 1978 {\it JCP} {\bf 27} 1
+  \bibitem{sonntagMunz_2017} Sonntag M and Munz C-D 2017 {\it Journal of Scientific Computing} {\bf 70} 1262
   \bibitem{teukolsky_2016} Teukolsky S A 2016 {\it JCP} {\bf 312} 333
@@
   \bibitem{yahil_1983} Yahil A 1983 {\it ApJ} {\bf 265} 1047
+  \bibitem{zanotti_etal_2015} Zanotti O, Fambri F and Dumser M 2015 {\it MNRAS} {\bf 452} 3010
   \bibitem{zhangShu_2010} Zhang X and Shu C-W 2010 {\it JCP} {\bf 229} 8918

### 2019-01-12 Documents/M1/Astronum_2018/sections/Conclusion.tex
Work on astronum paper

--- 2018-10-18 Documents/M1/Astronum_2018/sections/Conclusion.tex
@@
 
-We have developed IMEX schemes for two-moment neutrino transport in \texttt{thornado} that respect Fermi-Dirac statistics.
-The schemes employ algebraic closure based on Fermi-Dirac statistics, a third-order discontinuous Galerkin method, the Lax-Friedrichs flux, and convex-invariant time integration to maintain cell-average realizability of the moments.
-Since the realizability-preserving property is obtained from the convexity of the realizable domain, it's possible to construct a scheme with a high-order DG method.
+We have developed IMEX schemes suitable for a two-moment model of neutrino transport in \texttt{thornado} that can obey Fermi-Dirac statistics.
+\ee{(What is \texttt{thornado}?
+It is mentioned here and in the abstract, and not anywhere else.
+Need a paragraph in the intro?)}
+The scheme employs algebraic closure based on Fermi-Dirac statistics, high-order discontinuous Galerkin method for spatial discretization, and convex-invariant time integration to maintain realizability of the moments.
+Since the realizability-preserving property is obtained from the convexity of the realizable domain, it is possible to construct a scheme with the high-order DG method \ee{(Not sure what this means.
+Does it have to be DG?)}.
 See \cite{chu_etal_2018} for some examples with third-order DG methods.
@@
 In the application motivating this work, the neutrino distribution function can vary from 0 to 1.  
-Hence, we have considered algebraic closure respecting Fermi-Dirac statistics for both low and high occupancy.
-Among the seven algebraic closures we considered -- Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka_1991}, Janka 2\cite{janka_1992}, and Cernohorsky \& Bludman\cite{cernohorskyBludman_1994} -- only the Cernohorsky \& Bludman closure respected Fermi-Dirac statistics for all occupancies.
-As a result, we employed the Cernohorsky \& Bludman closure in all of the numerical tests in Section~\ref{se:NumericalTests}.
+Hence, we have considered algebraic closures based on Fermi-Dirac statistics for both low and high occupancy.  
+Among the seven algebraic closures we considered -- Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, Janka 1~\cite{janka_1991}, Janka 2~\cite{janka_1992}, and Cernohorsky \& Bludman~\cite{cernohorskyBludman_1994} -- only the Cernohorsky \& Bludman closure obeys Fermi-Dirac statistics for all occupancies.
+As a result, we employed the Cernohorsky \& Bludman closure in all of the numerical tests in Section~\ref{se:NumericalTests}.  \ee{(But you said you used Minerbo for the accuracy tests)}
 
-Two PD-ARS schemes are proposed for the desired IMEX scheme.
-The one with SSPRK2 is second-order accurate and strong-stability preserving in the streaming limit while the other with SSPRK3 is third-order accurate.
-Their properties, both accuracy and convex-invariance, were demonstrated with numerical tests.
+Two PD-ARS schemes are proposed.  
+The one with SSPRK2 is second-order accurate and strong-stability preserving in the streaming limit while the other with SSPRK3 is third-order accurate in the streaming limit.  
+Their accuracy were demonstrated on problems with known smooth solutions in streaming, absorption, and scattering-dominated regimes.
+The neutrino transport test with emission, absorption, and elastic scattering through a stationary background, was designed to test the convex-invariance of our PD-ARS schemes.
+The neutrino stationary state test shows that it's necessary to combine an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration for a solid CCSN simulation.
+\ee{(This statement is too strong.
+Rewrite.)}
 

### 2019-01-12 Documents/M1/Astronum_2018/sections/Numerical.tex
Work on astronum paper

--- 2018-10-18 Documents/M1/Astronum_2018/sections/Numerical.tex
@@
 
-In this section we present the numerical results obtained with the PD-ARS schemes given in Section~\ref{se:TimeIntegration}.
+In this section we present numerical results obtained with the PD-ARS schemes given in Section~\ref{se:TimeIntegration}.
 The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in streaming, absorption, and scattering-dominated regimes in one spatial dimension.
 The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the convex-invariance of PD-ARS schemes schemes.
-All the tests in this subsection were constructed with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $, using the DG scheme we present in \cite{chu_etal_2018}.
+All the tests in this section were computed with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $, using the DG scheme from \cite{chu_etal_2018}.
 
@@
 \label{se: Accuracy Tests}
-To compare the accuracy of the IMEX schemes, we applied our PD-ARS schemes and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some problems with known smooth solutions in streaming, absorption, ans scattering-dominated regimes in one spatial dimension.
-All the tests in this subsection were constructed with the maximum entropy closure in the low-occupancy limit(i.e., the Minerbo closure).
-In the streaming test, the second- and third-order accurate explicit strong-stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} (SSPRK2 and SSPRK3, respectively) are plotted as references.
-To compare the numerical results to analytic solutions, the cell-averaged absolute error or the cell averaged relative error are computed.
+
+To compare the accuracy of the IMEX schemes, we applied our PD-ARS schemes and the SSP2332 scheme from Pareschi \& Russo \cite{pareschiRusso_2005} to problems with known smooth solutions in streaming, absorption, and scattering-dominated regimes in one spatial dimension.
+All the tests in this subsection were computed with the maximum entropy closure in the low-occupancy limit (i.e., the Minerbo closure).  
+In the streaming test, the second- and third-order accurate explicit strong-stability-preserving Runge-Kutta methods from \cite{gottlieb_etal_2001} (SSPRK2 and SSPRK3, respectively) are also included.
+To compare the numerical results to analytic solutions, the cell-averaged absolute error or the cell averaged relative error are computed \ee{(give more specific details here)}.  
 For our convergence test, the number of elements ($N$) vary from 8 to 128.
@@
 \subsubsection{Sine Wave Streaming}
-The sine wave streaming test is designed for the steaming dominated regime, i.e. $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
+
+The sine wave streaming test is designed to test accuracy in the free-steaming regime, i.e. $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
 A periodic domain of unit length is used and the initial condition is $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$.
@@
 Figure~\ref{fig: SineWaveStreaming} plots the absolute error for the number density versus the number of elements $N$.
-We see the errors obtained with SSPRK3 and PD-ARS with SSPRK3 as the explicit part decrease as $N^{-3}$, as expected.
+We see the errors obtained with SSPRK3 and PD-ARS with SSPRK3 decrease as $N^{-3}$, as expected.
 All the other schemes have errors decreasing as $N^{-2}$.
 Among the second-order schemes, SSP2332 has the smallest error.
-
-In the streaming limit, the PD-ARS schemes limit to their explicit part, SSPRK2 and SSPRK3, respectively.
-Therefore, the absolute errors of PD-ARS and SSPRK are indistinguishable on the plot.
+In the streaming limit, the PD-ARS schemes limit to SSPRK2 and SSPRK3, respectively.
+Therefore, the absolute errors of PD-ARS and SSPRK are identical.
 
@@
 \subsubsection{Sine Wave Damping}
+
 This test, adapted from \cite{skinnerOstriker_2013}, is designed for absorption-dominated regimes, with $\sigma_{\Scatt} = 0$ and $f_0 = 0$, which results in exponential damping of the wave amplitude.
-A periodic domain of unit length and an initial condition with $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$ is used.
+A periodic domain of unit length and initial condition $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$ is used.
 The amplitude of the analytical solution decreases as $e^{-\sigma_{\Ab} t}$.
@@
 Figure~\ref{fig:SineWaveDamping} shows convergence results of the sine wave damping test in the relative error.
-SSP2332, a second-order scheme, displays second-order convergence.
-PD-ARS schemes converge with a first-order convergence rate: the price paid for the convex-invariant property.
+SSP2332, a second-order scheme, displays second-order convergence rate.  
+The PD-ARS schemes are only first-order accurate.  
 \begin{figure}[h]
@@
 \subsubsection{Sine Wave Diffusion}
+
 The last test with known smooth solution, adopted from \cite{radice_etal_2013}, is the sine wave diffusion test, i.e. $\sigma_{\Ab} = 0$ and $f_0 = 0$.
-A periodic domain with $D=\{x:x\in[-3,3]\}$ and an initial condition with $\cJ_{0} = 0.5+0.49\times\sin\big(\f{\pi\,x}{3}\big)$ and $\cH_{0} =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}$ is used.
-The analytic solution is given by $\cJ = \cJ_{0} \times e^{-\f{\pi^2 t}{27\sigma_{\Scatt}}}$ and $\cH = (3\,\sigma_{\Scatt})^{-1}\pd{\cJ}{x}$.
+A periodic domain $D=\{x:x\in[-3,3]\}$ with initial conditions $\cJ_{0} = 0.5+0.49\times\sin\big(\f{\pi\,x}{3}\big)$ and $\cH_{0} =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}$ are used.  
+The reference diffusion solution is given by $\cJ = \cJ_{0} \times \exp\big(-\f{\pi^2 t}{27\sigma_{\Scatt}}\big)$ and $\cH = (3\,\sigma_{\Scatt})^{-1}\pd{\cJ}{x}$.  
 We evolve with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$, and adjust the end time so that $t_{\mbox{\tiny end}}/\sigma_{\Scatt}=1$. 
@@
 SSP2332 and PD-ARS schemes display third-order accuracy for the number density, $\cJ$, and second-order accuracy for $\cH_{x}$, and their errors are difficult to distinguish.
-PD-ARS with SSPRK2 behaves as good as SSP2332 in the diffusion region but requires 1/3 less implicit solvers.
+PD-ARS with SSPRK2 behaves as good as SSP2332 in the diffusion region but requires one less implicit solves per time step.
+
 \begin{figure}[h]
@@
 The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles), and PD-ARS with SSPRK3 (hexagram).
-Black dashed lines on the left plot reference lines proportional to $N^{-2}$ (top) and $N^{-3}$ (bottom), respectively.
-Black dashed line on the right plot reference lines proportional to $N^{-2}$ .}
+Black dashed lines in the left plot are reference lines proportional to $N^{-2}$ (top) and $N^{-3}$ (bottom), respectively.
+Black dashed line in the right plot is a reference line proportional to $N^{-2}$ .}
    \label{fig:SineWaveDiffusionJ}
@@
 \subsection{Neutrino Stationary State Test} \label{se: Neutrino Stationary State Test}
-Next we consider a more ``realistic'' test: two-dimensional neutrino transport with emission, absorption, and elastic scattering through a stationary background.
-This is designed to test the realizability-preserving properties of the PD-ARS schemes.
-Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities we used.
-This test is constructed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction.
-We take 10 energy groups from 0~MeV to 300~MeV and initialize the neutrino number density $\cJ$ and flux density $\bcH$ both at zero(arbitrarily small).
-For the realizability-preserving test, we employ the CB closure with PD-ARS schemes, SSP2332, a scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and a scheme proposed by McClarren et al \cite{mcclarren_etal_2008} are all applied.
-Only PD-ARS schemes produce realizability-preserving results and evolve the model to a steady state.
-The other schemes crashed immediately after several steps.
-The realizability-preserving plot and the evolve process of PD-ARS schemes are given in Figure~\ref{fig:NeutrinoStationaryTestEvolve}.
+
+In this section we consider a more ``realistic'' test: two-dimensional multigroup neutrino transport with emission, absorption, and elastic scattering through a stationary background.  
+This test is designed to test the realizability-preserving properties of the PD-ARS schemes.  
+Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities used (adopted from \cite{Bruenn_1985}).  
+This test is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction.  
+\ee{(State boundary conditions.)}
+We use 10 energy groups to cover the range from 0~MeV to 300~MeV and initialize the neutrino number density to $\cJ = 10^{-99}$, flux density $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).
+For this test, we employed the CB closure.  
+We attempted to run this test with our PD-ARS schemes, SSP2332 from \cite{pareschiRusso_2005}, IMEXRKCB2 proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and the scheme proposed by McClarren et al.
+\cite{mcclarren_etal_2008}.
+Only the PD-ARS schemes produce realizable moments and are able to evolve to a steady state.
+The other schemes crashed after a few steps, when moments became non-realizable and the closure procedure failed.
+
+Results obtained with the PD-ARS IMEX schemes are plotted in Figure~\ref{fig:NeutrinoStationaryTestEvolve} for various times: $t=0.01$~ms (top panels), 0.35~ms (middle panels), and 5.0~ms (bottom panels).
+In the left column we plot the solution in the $|\vect{\cH}|\cJ$-plane.  
+In the middle column we show scatter plots of the number density $\cJ$ versus radius for select neutrino energies: 5~MeV (red lines), 16~MeV (magenta lines), and $93$~MeV (blue lines).  
+In the right column we plot the flux factor $|\vect{\cH}|/\cJ$ versus radius for the same neutrino energies as in the middle column.  
+In the left panels, each solution point in the domain is marked as a red dot in the $|\vect{\cH}|\cJ$-plane, and the realizable domain is shown as the light blue region.  
+The figures show that all the states in the simulation with the PD-ARS schemes are realizable.
 
@@
   \end{tabular}
-   \caption{Thermal state (left) and neutrino absorptivity ($\sigma_{\Ab}$) and neutrino elastic scattering opacity ($ \sigma_{\Scatt}$) (right) for the neutrino stationary state test.}
+   \caption{Left panel: thermal state of the background versus radius in the neutrino stationary state test; mass density (solid line), temperature (dashed line), and electron fraction (dotted line).
+Right panel: corresponding opacities for select neutrino energies; absorptivity ($\sigma_{\Ab}$) and scattering opacity ($ \sigma_{\Scatt}$).}
    \label{fig:NeutrinoStationaryTestEOS}
@@
     \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
-    \caption{Realizability (left column), the number density $\cJ$ versus radius (center column), and the flux factor $|\bcH|/\cJ$ versus radius (right column) at t = 0.01~ms ,0.35~ms and 5.0~ms for the neutrino stationary state test.
-For the realizability plots, the light blue area highlights the realizability domain, and the black lines define its boundary.
-Each $\bcM=(\cJ,\bcH)^{T}$ state is marked by a red dot.
+    \caption{Results from the neutrino stationary state test: moments relative to the realizable domain (left column, light blue domain is for $f \in [0,1]$ with black-solid-line as boundary, while light red is for $f\geq 0$ with thin-red-solid-line as boundary), the number density $\cJ$ versus radius (middle column), and the flux factor $|\bcH|/\cJ$ versus radius (right column), at $t = 0.01$~ms, 0.35~ms, and 5.0~ms.
+For the plots in the left column, each $\bcM=(\cJ,\bcH)^{T}$ state is marked by a red dot, which are all inside the light blue region (the realizable domain for fermions).
 The results of PD-ARS with SSPRK2 and PD-ARS with SSPRK3 are indistinguishable in these plots.}
@@
 \end{figure}
-
-\clearpage

### 2019-01-12 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Work on astronum paper

--- 2018-11-07 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
@@
 \begin{equation}
-  \dfrac{d \vect{u}}{d t} = \vect{\cT}(\vect{u}) + \f{ 1}{\tau}\,\vect{\cQ}(\vect{u}),
+  \dot{\vect{u}} = \vect{\cT}(\vect{u}) + \vect{\cQ}(\vect{u}),
 \end{equation}
@@
 \end{equation}
-is the collection of all cell-averaged moments, $\vect{\cT}$ is the transport operator, corresponding to the first term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, and $\f{1}{\tau}\,\vect{\cQ}$ is the collision operator, corresponding to the second term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}.
+is the collection of all cell-averaged moments, $\vect{\cT}$ is the transport operator, corresponding to the first term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}, and $\vect{\cQ}$ is the collision operator, corresponding to the second term on the right-hand side of Eq.~\eqref{eq:SemiDiscretizatedMomentEquation}.
 
@@
   +\dt\sum_{j=1}^{i-1}\tilde{a}_{ij}\,\vect{\cT}(\vect{u}^{(j)})
-  +\dt\sum_{j=1}^{i}a_{ij}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(j)}),
+  +\dt\sum_{j=1}^{i}a_{ij}\,\vect{\cQ}(\vect{u}^{(j)}),
   \quad i=1,\ldots,s, \label{imexStages} \\
@@
   +\dt\sum_{i=1}^{s}\tilde{w}_{i}\,\vect{\cT}(\vect{u}^{(i)})
-  +\dt\sum_{i=1}^{s}w_{i}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}), \label{imexIntermediate} 
+  +\dt\sum_{i=1}^{s}w_{i}\,\vect{\cQ}(\vect{u}^{(i)}), \label{imexIntermediate} 
 \end{align}
-where $(\tilde{a}_{ij})$ and $(a_{ij})$, coefficients of the $i$-th stage, are the elements of matrices $\tilde{A}$ and $A$, respectively.
-Matrices $\tilde{A}$ and $A$ are both lower triangular matrices.
+where $(\tilde{a}_{ij})$ and $(a_{ij})$, coefficients of the $i$-th stage, are elements of matrices $\tilde{A}$ and $A$, respectively.
+The matrices $\tilde{A}$ and $A$ are lower triangular ($\tilde{A}$ is strictly lower triangular so that the transport part is explicit).  
 The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weights in the assembly step in Eq.~\eqref{imexIntermediate}.
-These coefficients and weights must satisfy certain order conditions for consistency, accuracy and other properties.
-
+These coefficients and weights must satisfy certain order conditions for consistency, accuracy, and other properties.  
 For second-order temporal accuracy, the following conditions are required \cite{hairer_1981}:
@@
 
-For globally stiffly accuracy (GSA), the coefficients have the following relationship \cite{dimarcoPareschi2013}:
+The IMEX scheme is called globally stiffly accurate (GSA) if the coefficients satisfy \cite{dimarcoPareschi2013}:
 \begin{equation}
-a_{si}=w_{i}, \quad \tilde{a}_{si}=\tilde{w}_{i}, \quad \text{for} \quad i=1,\ldots,s.
+  a_{si}=w_{i} \quad\text{and}\quad \tilde{a}_{si}=\tilde{w}_{i}, \quad \text{for} \quad i=1,\ldots,s.
 \end{equation}
-
-The IMEX schemes are usually classified by the structure of matrix $A$, the implicit tableau:
-if $A$ is invertible, the IMEX scheme is type~A \cite{pareschiRusso_2005};
-if $a_{i1} = 0$ for $i=1,\ldots,s$ and $w_{1} = 0$, the IMEX scheme is type~ARS \cite{ascher_etal_1997,pareschiRusso_2005}.
+Then, $\vect{u}^{n+1} = \vect{u}^{(s)}$, which is simplifying because the assembly step in Eq.~\eqref{imexIntermediate} is omitted.  
+IMEX schemes are further classified by the structure of implicit matrix $A$.  
+If $A$ is invertible, the IMEX scheme is of type~A \cite{pareschiRusso_2005}.  
+If $a_{i1} = 0$ for $i=1,\ldots,s$, $w_{1} = 0$, and the submatrix consisting of the last $s-1$ rows and columns is invertible, the IMEX scheme is of type~ARS \cite{ascher_etal_1997,pareschiRusso_2005}.
 
@@
 
-Beyond the accuracy requirement, a convex-invariant IMEX scheme must satisfy additional constraints.
-Our idea is finding the constraints on $a_{ij}$, $\tilde{a}_{ij}$, $\tilde{w}_{i}$, and $w_{i}$ that enable each $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ be convex combination of realizable moments:
-
-Following Hu et al\cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten as
+To be convex-invariant, the coefficients and weights defining the IMEX scheme must satisfy additional constraints.
+Our goal is to find constraints on $a_{ij}$, $\tilde{a}_{ij}$, $\tilde{w}_{i}$, and $w_{i}$ that enable each $\vect{u}^{(i)}$ in Eq.~\eqref{imexStages} to be expressed as a convex combination of realizable states.
+Following Hu et al.~\cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten as
 \begin{equation}
   \vect{u}^{(i)}
-  =\sum_{j=0}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
-  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
+  =\sum_{j=0}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big] + a_{ii}\,\dt\,\vect{\cQ}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
   \label{eq:imexStagesRewrite}
 \end{equation}
-with $c_{ij}$ and $\hat{c}_{ij}$ be some expression of $a_{ij}$ and $\tilde{a}_{ij}$.
-For example, type~ARS IMEX schemes have $c_{ij}$ and $\hat{c}_{ij}$ be given by
+where $c_{ij}$ and $\hat{c}_{ij}\equiv\tilde{c}_{ij}/c_{ij}$ are defined in terms of $a_{ij}$ and $\tilde{a}_{ij}$.
+For IMEX schemes of type~ARS, $c_{ij}$ and $\tilde{c}_{ij}$ are given by
     \begin{equation}
@@
     \end{equation}
-Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.
+Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS}, so that $\sum_{j=0}^{i-1}c_{ij}=1$.
 
-By requiring the IMEX scheme be GSA, $\vect{u}^{n+1} = \vect{u}^{(s)}$.
-Then using those Lemma proved in \cite{chu_etal_2018}, we can find those constraints, such as Eq.~\eqref{eq:convexInvariant} for type~ARS, that $c_{ij}$ and $\hat{c}_{ij}$ (or $a_{ij}$ and $\tilde{a}_{ij}$) need to satisfy to ensure $\vect{u}^{(i)}$, Eq.~\eqref{eq:imexStagesRewrite}, be realizable.
-Hence $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ are realizable and the method with this convex-invariant IMEX scheme is realizability-preserving.
-
-When the convex-invariant constraints are satisfied, the first (sum) term on the right-hand side of Eq.\eqref{eq:imexStagesRewrite} is a convex combination of multiple explicit Euler schemes with time step $\hat{c}_{ij}\,\dt$.
-Each of the explicit Euler schemes has a time step condition that ensures its realizability: $\hat{c}_{ij}\,\dt\leq$ the Courant-Friedrichs-Lewy (CFL) condition.
-As a result, the time step of the IMEX scheme is subject to the most restrict time step condition:
+If the IMEX scheme is GSA, $\vect{u}^{n+1} = \vect{u}^{(s)}$.  
+Moreover, if $c_{ij},\tilde{c}_{ij}\ge0$ and $a_{ii}>0$, each stage in Eq.~\eqref{eq:imexStagesRewrite} is a convex combination of explicit Euler steps (with time step $\hat{c}_{ij}\dt$), followed by a implicit Euler step.
+Each of the explicit Euler steps has a time step condition that ensures its realizability given by $\hat{c}_{ij}\,\dt\leq\dx$; the Courant-Friedrichs-Lewy (CFL) condition of the scheme.
+Using results proved in \cite{chu_etal_2018} and discussed in Section~\ref{se:SpacialDiscretization}, the IMEX scheme is convex-invariant and realizability-preserving for the two-moment model in Section~\ref{se:SpacialDiscretization} provided
 \begin{equation}
-\max(\hat{c}_{ij})\,\dt \leq \text{CFL condition}.
+  \max(\hat{c}_{ij})\,\dt \leq \dx.  
 \end{equation}
-
-Unfortunately, no coefficients can be found for standard IMEX schemes under the convex-invariant constraints and the accuracy constraints for 2nd-order or higher. 
-To circumvent this problem, some correction steps are introduced after the assembly step, Eq.~\eqref{imexIntermediate}, such as Hu et al.\cite{hu_etal_2018}.
-However, the correction steps impose extra constraints for realizability on time step.
-In the circumstance that we have, correction steps can ruin the efficiency we gain from the IMEX scheme.
-To keep things simple, we aim for 1st-order in general, high-order in streaming limit, diffusion accurate, convex-invariant IMEX schemes.
+(This CFL condition becomes more restrictive with high-order DG spatial discretization \cite{chu_etal_2018}.)
 
@@
 
-Diffusion accurate is an important property the time integration should have.
-In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$.
-The moment behavior are governed by (e.g., \cite{jinLevermore_1996})
+Accuracy in the diffusion limit is another important property to consider for the IMEX scheme applied to the two-moment model.  
+In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$, and the two-moment model is approximately governed by (e.g., \cite{jinLevermore_1996})
 \begin{equation}
@@
 \end{equation}
-In the context of IMEX schemes, the above relationships imply that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold. 
-That's
+In the context of IMEX schemes, the above relationships imply that the following relations should hold
 \begin{equation}
-   \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s,
+   \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=1,\ldots,s,
+   \label{diffusionAccuracy}
 \end{equation}
-where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix.
-It can be rewritten as $c=\tilde{c}$.
-We have proved in \cite{chu_etal_2018} that only type~ARS IMEX schemes can be diffusion accurate and convex-invariant at the same time.
+where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix and $\vect{e}$ is the vector of ones.
+Eq.~\eqref{diffusionAccuracy} implies
+\begin{equation}
+  c_{i} = \tilde{c}_{i}, \quad i=1,\ldots,s
+\end{equation}
+We have proved in \cite{chu_etal_2018} that only IMEX schemes of type~ARS can be both diffusion accurate and convex-invariant.  
+(Another short proof follows from the fact that IMEX schemes type~A have $\tilde{c}_1 = 0$ while $c_i \neq 0$.)
 
@@
 
-Combining the conditions we have, the 1st-order in general, high-order in streaming limit, diffusion accurate, convex-invariant IMEX schemes we need are type~ARS IMEX schemes satisfying the following constraints:
+Unfortunately, coefficients satisfying the order conditions in Eqs.~\eqref{orderConditions1}-\eqref{orderConditions2} and the conditions for convex-invariance do not exist for the standard IMEX scheme in Eqs.~\eqref{imexStages}-\eqref{imexIntermediate}, unless a small time step is invoked that makes the scheme essentially explicit.
+To circumvent this problem, correction steps can be introduced after the assembly step in Eq.~\eqref{imexIntermediate} (e.g., \cite{chertock_etal_2015,hu_etal_2018}).  
+However, the correction steps can impose time step constraints for realizability or accuracy in the diffusion limit that ruins the efficiency gains expected from the IMEX scheme.  
+Because of this, we sacrifice overall high-order accuracy, and aim for IMEX schemes that are high-order accurate in the streaming limit, diffusion accurate, and convex-invariant.  
+Combining these requirements we seek GSA IMEX schemes of type~ARS with coefficients satisfying the following constraints:
 \begin{enumerate}
@@
     \end{equation}
-    \item High-order accuracy in the streaming limit, 2nd-order for example:
+    \item High-order accuracy in the streaming limit.  For second-order accuracy: \ee{(Do we need to list third-order accuracy also?)}
     \begin{equation}
@@
     \begin{equation}
-      c=\tilde{c}.
+      c_{i}=\tilde{c}_{i}, \quad i=1,\ldots,s.
       \label{eq:diffusionCondition}
@@
 \end{enumerate}
-The \ref{cod:statges} constraint is given by efficiency consideration.
-We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{chu_etal_2018}.)
-We give two optimized PD-ARS schemes here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. 
-They have second- and third-order accuracy in the streaming limit, respectively.
+Fortunately, these IMEX schemes are easy to find.  
+(The constraint in \eqref{cod:statges} is introduced from efficiency considerations to limit the number of implicit solves.)
+We call the IMEX schemes satisfying the above conditions {PD-ARS} (see also Definition~3 in \cite{chu_etal_2018}), and we provide two optimal PD-ARS schemes below: PD-ARS with SSPRK2 and PD-ARS with SSPRK3, which limit to the optimal second-order and third-order SSPRK schemes from \cite{shuOsher_1988}, respectively.
+
 \subsubsection{PD-ARS with SSPRK2}
-Here we give the optimized PD-ARS with SSPRK2 in the standard double Butcher tableau form: explicit tableau on the left ($\tilde{A}$), implicit tableau on the right ($A$):
+
+The optimal PD-ARS with SSPRK2 in the standard double Butcher tableau form, explicit tableau on the left ($\tilde{A}$) and implicit tableau on the right ($A$), is given by:
 \begin{equation}
@@
 \end{equation}
-For this scheme, $c_{\mbox{\tiny Sch}}= 1$ and only two implicit solver are needed for each time step.
+For this scheme, only two implicit solves are needed per time step and $c_{\mbox{\tiny Sch}}= 1$, which implies that the time step restriction for preserving moment realizability is only due to the explicit part.
+
 \subsubsection{PD-ARS with SSPRK3}
-Here we give the optimized PD-ARS with SSPRK3.
-Its standard double Butcher tableau are (explicit tableau on the left, implicit tableau on the right)
+
+The optimial PD-ARS with SSPRK3 is given in its standard double Butcher tableau form (explicit tableau on the left and implicit tableau on the right) by:
 \begin{equation}
@@
 \end{equation}
-For this schemes, $c_{\mbox{\tiny Sch}}= 1$.
-Three implicit solver are taken for each time step.
-Since PD-ARS with SSPRK3 is as accurate as PD-ARS with SSPRK2 in collision involved region, see Section~\ref{se:NumericalTests} for the plots, it may not offer any advantage.
+This scheme requires three implicit solvers per time step, and $c_{\mbox{\tiny Sch}}= 1$.  
+Since PD-ARS with SSPRK3 is not more accurate than PD-ARS with SSPRK2 in collision dominated regions (see results in Section~\ref{se:NumericalTests}), it may not offer any practical advantage over PD-ARS with SSPRK2.

### 2019-01-18 Documents/M1/Astronum_2018/manuscript.tex
Buckup the latest changes on M1/Astronum_2018
Work on astronum paper

@@
 We develop implicit-explicit (IMEX) schemes for neutrino transport through a background material in the \texttt{thornado} code in the context of a two-moment model that evolves the angular moments of a neutrino phase-space distribution function.
-Considering the upper and lower bounds that are introduced by Pauli's exclusion principle on the moments, an algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
-A finite-volume/first-order discontinuous Galerkin(DG) method is used to interporate how an algebraic moment closure based on Fermi-Dirac statistics satisfies the bounds.
+Considering the upper and lower bounds that are introduced by Pauli's exclusion principle on the moments, an algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator both are demanded.
+A finite-volume/first-order discontinuous Galerkin(DG) method is used to interpret how an algebraic moment closure based on Fermi-Dirac statistics satisfies the bounds.
 Several algebraic closures are compared with these bounds in mind and the Cernohorsky and Bludman closure\cite{cernohorskyBludman_1994}, which satisfies the bounds, is chosen for our IMEX schemes.
-For the convex-invariant time integrator, two IMEX scheme named PD-ARS have been proposed following the work in \cite{chu_etal_2018}.
-PD-ARS denotes a convex-invariant IMEX Runge-Kutta schemes that has first-order accuracy in general, high-order accuracy in the streaming limit, and works well in the diffusion limit.
+For the convex-invariant time integrator, two IMEX schemes named PD-ARS have been proposed following the work in \cite{chu_etal_2018}.
+PD-ARS denotes a convex-invariant IMEX Runge-Kutta scheme that has the first-order accuracy in general, high-order accuracy in the streaming limit, and works well in the diffusion limit.
 Our two PD-ARS schemes are second- and third-order, explicit, strong-stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore are second- and third-order accurate in the streaming limit, respectively.
@@
 \input{sections/TwoMoments}
-\input{sections/SpacialDiscretization}
+\input{sections/SpatialDiscretization}
 \input{sections/TimeIntegration}

### 2019-01-18 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Work on astronum paper

@@
 When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.
-\ee{so what?  Should we discuss the presence of blocking factors in collision terms?}
-%With those algebraic closures that don't conserve the bounds, the time integrator may give moments that implies $f>1$.
-%Some safety protections may be applied for those method, but the safety protections can break the conservation laws in lepton number or energy and defect the CCSN simulation.
+If the exceeding happened, the update step may give $f>1$ which changes the sign of the blocking factors in the collision terms.
+If no treatment was taken and the error iterated itself, it would be difficult to predict what the exceeding would result.
+If some treatments are taken to map the outside moments in, the treatments need be manipulated to conserve the lepton number, the momentum, and the energy of the system.
 

### 2019-01-18 Documents/M1/Astronum_2018/sections/intro.tex
Work on astronum paper

@@
 Core-collapse supernovae (CCSNe) are the explosions of massive stars that end their lives.
-CCSNe are a dominant source of heavy elements and play an important role in many astrophysical phenomena, such as neutron star and black hole formation.  
+They are the dominant source of heavy elements and play important roles in many astrophysical phenomena, such as neutron star and black hole formation.  
 Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
@@
 The neutrino energy deposition drives the CCSN explosion.\cite{mezzacappaMesser_1999}
-Ideally neutrino transport would be modeled by the Boltzmann transport equation, which is a integro-partial-differential equation evolving a phase-space distribution function $f$.\cite{Bruenn_1985}
+Ideally, neutrino transport would be modeled by the Boltzmann transport equation, which is an integro-partial-differential equation evolving a phase-space distribution function $f$.\cite{Bruenn_1985}
 Simulating the neutrino transport implies finding a solution of the Boltzmann equation for a specific domain and period with acceptable accuracy.
 
-However, solving the multi-dimensional Boltzmann transport equation is expensive.
+However, solving the Boltzmann transport equation full-dimensionally is expensive.
 To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted.\cite{mezzacappaMesser_1999}
-In the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$: the spectral particle density $\cJ$ and flux $\bcH$, respectively.
-However, the transport term in the Boltzmann transport equation is the dot product of the velocity vector and the gradient of the phase-space distribution function.
-Integrating this term with unit direction vector as the weight introduces the second angular moment $\bcK$ to the moment equations.
-Knowledge of $\bcK$ is needed to close the equation system.
+Using the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$ -- the spectral particle density $\cJ$ and flux $\bcH$, respectively.
+However, the transport term in the Boltzmann transport equation has the dot product of the velocity vector and the gradient of the phase-space distribution function as its form.
+Integrating this term with an unit direction vector as the weight function couples the moment equations: it introduces the second angular moment $\bcK$ to the first moment $\cJ$'s equation.
+Knowledge of $\bcK$ is needed to close the two-moment equation system.
 Therefore, an algebraic closure that gives an approximate value of $\bcK$ given $\cJ$ and $\bcH$ is needed.
@@
 
+\texttt{thornado} is our toolkit for high-order neutrino-radiation hydrodynamics based on high-order Runge-Kutta Discontinuous Galerkin (RKDG) methods.
+It is developed at the University of Tennessee, Knoxville and Oak Ridge National Laboratory.
+It currently solves the Euler equations for fluid dynamics and the two-moment approximation of the radiative transfer equation, both in the non-relativistic limits.\cite{endeve_etal_2018}
+
 This paper is organized as follows: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and the constraints on the moments and algebraic closures imposed by Fermi-Dirac statistics;

### 2019-01-18 Documents/M1/Astronum_2018/sections/intro.tex
Work on astronum paper

@@
 However, the transport term in the Boltzmann transport equation has the dot product of the velocity vector and the gradient of the phase-space distribution function as its form.
-Integrating this term with an unit direction vector as the weight function couples the moment equations: it introduces the second angular moment $\bcK$ to the first moment $\cJ$'s equation.
+Integrating this term with an unit direction vector as the weight function couples the moment equations: it introduces the second angular moment $\bcK$ to the first moment $\bcH$'s equation.
 Knowledge of $\bcK$ is needed to close the two-moment equation system.
-Therefore, an algebraic closure that gives an approximate value of $\bcK$ given $\cJ$ and $\bcH$ is needed.
-The two-moment method has been widely applied with different algebraic closures, such as the Minerbo\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan and et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} ) and the Levermore\cite{levermore_1984} closure(e.g.~Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016}).
+Therefore, an algebraic closure that gives a predicted $\bcK$ given $\cJ$ and $\bcH$ is needed.
+The better the closure predicts $\bcK$, the more accurate the two-moment method. 
+Two-moment method has been widely applied with different algebraic closures, such as the Minerbo\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan and et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} ) and the Levermore\cite{levermore_1984} closure(e.g.~Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016}).
 
-Applying the two-moment method alone does not guarantee an affordable solution.
-To be precise, neutrinos interact with the background, and the characteristic time scale of these interactions, which can be $\sim\mathcal{O}(10^{-13})$~second, is short compared to the duration of the CCSN explosion, which $\sim\mathcal{O}(1)$~second.
-This makes the time step needed by an explicit time integrator prohibitively small. 
+Applying the two-moment method does simplify the problem, but doesn't guarantee an affordable solution.
+To be precise, how to discrete the continuous equation system given by the two-moment method and solve the discretized system efficiently is remain a question.
+In fact, the time scales of neutrino interactions with the background ($\sim\mathcal{O}(10^{-13})$~second) is short compared to the duration of the CCSN explosion ($\sim\mathcal{O}(1)$~second).  
+This means that a lot of time step would be needed for solving the system fully explicitly. 
 On the other hand, solving the moment equations fully implicitly requires inverting globally many band-structured matrices whose sizes depend on the spatial discretization.

### 2019-01-23 Documents/M1/Astronum_2018/sections/Conclusion.tex

@@
 We have developed IMEX schemes suitable for a two-moment model of neutrino transport in \texttt{thornado} that can obey Fermi-Dirac statistics.
-\ee{(What is \texttt{thornado}?
-It is mentioned here and in the abstract, and not anywhere else.
-Need a paragraph in the intro?)}
 The scheme employs algebraic closure based on Fermi-Dirac statistics, high-order discontinuous Galerkin method for spatial discretization, and convex-invariant time integration to maintain realizability of the moments.
-Since the realizability-preserving property is obtained from the convexity of the realizable domain, it is possible to construct a scheme with the high-order DG method \ee{(Not sure what this means.
-Does it have to be DG?)}.
+Since the realizable domain is convex and its convexity can be inherited by a convex combination, some schemes having convex combinations as their stages should be able to preserve the convexity.
+This idea encourages us to construct realizability-preserving time integrators, realizability-preserving IMEX schemes, and eventually a method with realizability-preserving IMEX time integrator and high-order DG method.
 See \cite{chu_etal_2018} for some examples with third-order DG methods.
@@
 Among the seven algebraic closures we considered -- Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, Janka 1~\cite{janka_1991}, Janka 2~\cite{janka_1992}, and Cernohorsky \& Bludman~\cite{cernohorskyBludman_1994} -- only the Cernohorsky \& Bludman closure obeys Fermi-Dirac statistics for all occupancies.
-As a result, we employed the Cernohorsky \& Bludman closure in all of the numerical tests in Section~\ref{se:NumericalTests}.  \ee{(But you said you used Minerbo for the accuracy tests)}
+As a result, we employed the Cernohorsky \& Bludman closure for the neutrino stationary state test in Section~\ref{se: Neutrino Stationary State Test}.
+(We also run the code with other algebraic closures for examination.
+And the program crashed after few steps because of the nonphysical neutrino density/flux.)
 
 Two PD-ARS schemes are proposed.
-The one with SSPRK2 is second-order accurate and strong-stability preserving in the streaming limit while the other with SSPRK3 is third-order accurate in the streaming limit.  
+The one with SSPRK2 has second-order accuracy while the other with SSPRK3 has third-order accuracy, and both have strong-stability preserving property in the streaming limit.  
 Their accuracy were demonstrated on problems with known smooth solutions in streaming, absorption, and scattering-dominated regimes.
 The neutrino transport test with emission, absorption, and elastic scattering through a stationary background, was designed to test the convex-invariance of our PD-ARS schemes. 
-The neutrino stationary state test shows that it's necessary to combine an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration for a solid CCSN simulation.
-\ee{(This statement is too strong.
-Rewrite.)}
+The neutrino stationary state test shows that a method combined an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration can be a candidate for constructing a CCSN simulation code without "nonphysical protection" that may break conservation laws.
 

### 2019-01-23 Documents/M1/Astronum_2018/sections/Numerical.tex

@@
 
-To compare the accuracy of the IMEX schemes, we applied our PD-ARS schemes and the SSP2332 scheme from Pareschi \& Russo \cite{pareschiRusso_2005} to problems with known smooth solutions in streaming, absorption, and scattering-dominated regimes in one spatial dimension.
+To compare the accuracy of the IMEX schemes, we applied our PD-ARS schemes and the SSP2332 scheme from Pareschi \& Russo \cite{pareschiRusso_2005} to problems with known smooth solutions in streaming, absorption(damping), and scattering-dominated(diffusing) regimes in one spatial dimension.
 All the tests in this subsection were computed with the maximum entropy closure in the low-occupancy limit (i.e., the Minerbo closure).  
 In the streaming test, the second- and third-order accurate explicit strong-stability-preserving Runge-Kutta methods from \cite{gottlieb_etal_2001} (SSPRK2 and SSPRK3, respectively) are also included.
-To compare the numerical results to analytic solutions, the cell-averaged absolute error or the cell averaged relative error are computed \ee{(give more specific details here)}.  
-For our convergence test, the number of elements ($N$) vary from 8 to 128.
+To compare the numerical results to analytic solutions, the averaged absolute error or the averaged relative error are computed in the $L^{1}$-error norm: the absolute error for the streaming test and the diffusion test; the relative error for the damping test.
+They are averaged over the cell with a equal weight quadrature for the cell integrals.
+And to examine the convergence, we let the number of elements ($N$) vary from 8 to 128.
 
@@
 Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities used (adopted from \cite{Bruenn_1985}).  
-This test is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction.  
-\ee{(State boundary conditions.)}
+This test is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction, a reflecting inner boundary and a homogeneous out-flowing outer boundary.
 We use 10 energy groups to cover the range from 0~MeV to 300~MeV and initialize the neutrino number density to $\cJ = 10^{-99}$, flux density $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).

### 2019-01-25 Documents/M1/Astronum_2018/manuscript.tex
Work on Astronum paper.

@@
 \author{Ran Chu}
-\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
+\address{Department of Physics and Astronomy, University of Tennessee, Knoxville, TN 37996-1200}
 \ead{rchu@vols.utk.edu}
@@
 \address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
-\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
+\address{Department of Physics and Astronomy, University of Tennessee, Knoxville, TN 37996-1200}
+\address{Joint Institute for Computational Sciences, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
 \ead{endevee@ornl.gov}
@@
 \address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
-\address{Department of Mathematics, University of Tennessee Knoxville, TN 37996-1320}
+\address{Department of Mathematics, University of Tennessee, Knoxville, TN 37996-1320}
 \ead{hauckc@ornl.gov}
@@
 \author{Anthony Mezzacappa}
-\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
+\address{Department of Physics and Astronomy, University of Tennessee, Knoxville, TN 37996-1200}
+\address{Joint Institute for Computational Sciences, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
 \ead{mezz@utk.edu}
@@
 \address{Scientific Computing and Theoretical Physics Groups, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
-\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
+\address{Department of Physics and Astronomy, University of Tennessee, Knoxville, TN 37996-1200}
 \ead{bronson@ornl.gov}
@@
 \begin{abstract}
-We develop implicit-explicit (IMEX) schemes for neutrino transport through a background material in the \texttt{thornado} code in the context of a two-moment model that evolves the angular moments of a neutrino phase-space distribution function.
+We develop implicit-explicit (IMEX) schemes for neutrino transport in a background material using the \texttt{thornado} code in the context of a two-moment model that evolves the angular moments of a neutrino phase-space distribution function.
 Considering the upper and lower bounds that are introduced by Pauli's exclusion principle on the moments, an algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator both are demanded.
@@
 For the convex-invariant time integrator, two IMEX schemes named PD-ARS have been proposed following the work in \cite{chu_etal_2018}.
-PD-ARS denotes a convex-invariant IMEX Runge-Kutta scheme that has the first-order accuracy in general, high-order accuracy in the streaming limit, and works well in the diffusion limit.
-Our two PD-ARS schemes are second- and third-order, explicit, strong-stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore are second- and third-order accurate in the streaming limit, respectively.
+PD-ARS denotes a convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy in general, high-order accuracy in the streaming limit, and works well in the diffusion limit.
+Our two PD-ARS schemes are second- and third-order, explicit, strong-stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} in their explicit part, respectively, and therefore are second- and third-order accurate in the streaming limit, respectively.
 The accuracy and convex-invariance of our PD-ARS schemes are demonstrated in the numerical tests with a third-order DG method for spatial discretization and a simple Lax-Friedrichs flux.
-We show preliminary result employing tabulated neutrino opacities from Bruenn(1985)\citep{Bruenn_1985}
+We show preliminary result employing tabulated neutrino opacities. 
+%from Bruenn(1985)\citep{Bruenn_1985}
 

### 2019-01-25 Documents/M1/Astronum_2018/sections/Acknowledge.tex
Work on astronum paper
Work on Astronum paper.

--- 2018-10-17 Documents/M1/Astronum_2018/sections/Acknowledge.tex
@@
 De-AC05-00OR22725.
-This research was supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of the U.S.
-Department of Energy Office of Science and the National Nuclear Security Administration.
-This material is based, in part, upon work supported by the U.S. Department of Energy, Office of Science, Office of Advanced Scientific Computing Research.
-Eirik Endeve and Anthony Mezzacappa acknowledge support from the National Science Foundation under group NSF-GP-... and from the UT-ORNL Joint Institute for Computational Sciences.
+This material is based, in part, upon work supported by the U.S.
+Department of Energy, Office of Science, Office of Advanced Scientific Computing Research.
+This research was also supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of the U.S.
+Department of Energy Office of Science and the National Nuclear Security Administration, and by the National Science Foundation Gravitational Physics Program (NSF-GP 1505933 and 1806692).

### 2019-01-25 Documents/M1/Astronum_2018/sections/Numerical.tex
Work on Astronum paper.

@@
 The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in streaming, absorption, and scattering-dominated regimes in one spatial dimension.
-The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the convex-invariance of PD-ARS schemes schemes.
-All the tests in this section were computed with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $, using the DG scheme from \cite{chu_etal_2018}.
+The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the convex-invariance of PD-ARS schemes.
+All the tests in this section were computed with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $, using the DG scheme from~\cite{chu_etal_2018}.
 
@@
 
-To compare the accuracy of the IMEX schemes, we applied our PD-ARS schemes and the SSP2332 scheme from Pareschi \& Russo \cite{pareschiRusso_2005} to problems with known smooth solutions in streaming, absorption(damping), and scattering-dominated(diffusing) regimes in one spatial dimension.
+To compare the accuracy of the IMEX schemes, we applied our PD-ARS schemes and the SSP2332 scheme from Pareschi \& Russo~\cite{pareschiRusso_2005} to problems with known smooth solutions in streaming, absorption(damping), and scattering-dominated(diffusing) regimes in one spatial dimension.
 All the tests in this subsection were computed with the maximum entropy closure in the low-occupancy limit (i.e., the Minerbo closure).  
-In the streaming test, the second- and third-order accurate explicit strong-stability-preserving Runge-Kutta methods from \cite{gottlieb_etal_2001} (SSPRK2 and SSPRK3, respectively) are also included.
-To compare the numerical results to analytic solutions, the averaged absolute error or the averaged relative error are computed in the $L^{1}$-error norm: the absolute error for the streaming test and the diffusion test; the relative error for the damping test.
-They are averaged over the cell with a equal weight quadrature for the cell integrals.
+In the streaming test, the second- and third-order accurate explicit strong-stability-preserving Runge-Kutta methods from~\cite{gottlieb_etal_2001} (SSPRK2 and SSPRK3, respectively) are also included.
+To compare the numerical results to analytic solutions, the averaged absolute error or the averaged relative error are computed in the $L^{1}$-error norm.
+We compute the absolute error for the streaming test and the diffusion test and the relative error for the damping test.
+They are averaged over the cell with an equal-weight quadrature for the cell integrals.
 And to examine the convergence, we let the number of elements ($N$) vary from 8 to 128.
@@
 
-The sine wave streaming test is designed to test accuracy in the free-steaming regime, i.e. $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
+The sine wave streaming test is designed to test accuracy in the free-steaming regime; i.e. $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
 A periodic domain of unit length is used and the initial condition is $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$.
@@
 Figure~\ref{fig: SineWaveStreaming} plots the absolute error for the number density versus the number of elements $N$.
-We see the errors obtained with SSPRK3 and PD-ARS with SSPRK3 decrease as $N^{-3}$, as expected.
-All the other schemes have errors decreasing as $N^{-2}$.
+We see the errors obtained with (SSPRK3) and (PD-ARS with SSPRK3) are smallest and decrease as $N^{-3}$, as expected for a scheme combining third-order accurate time stepping with third-order accurate spatial discretization.
+For all the other schemes, using second-order accurate explicit time stepping, the error decreases as $N^{-2}$.
 Among the second-order schemes, SSP2332 has the smallest error.
-In the streaming limit, the PD-ARS schemes limit to SSPRK2 and SSPRK3, respectively.
-Therefore, the absolute errors of PD-ARS and SSPRK are identical.
+In the streaming limit, the PD-ARS schemes reduce to SSPRK schemes, such that (PD-ARS with SSPRK2) to SSPRK2 and (PD-ARS with SSPRK3) to SSPRK3, respectively.
+Therefore, the absolute errors of PD-ARS schemes and SSPRK schemes are indistinguishable.
 
@@
     \includegraphics[width=0.8\textwidth]{figures/SineWaveStreaming}
-   \caption{Absolute error versus number of elements $N$ for the streaming sine wave test.
-Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crosses), PD-ARS with SSPRK2 (light red circles) and PD-ARS with SSPRK2 (light red hexagrams).
+   \caption{Absolute error versus number of elements, $N$, for the streaming sine wave test.
+Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crosses), PD-ARS with SSPRK2 (light red circles) and PD-ARS with SSPRK3 (light red asterisks).
 Black dashed reference lines are proportional to $N^{-2}$ (top), and $N^{-3}$ (bottom), respectively.}
@@
 
-This test, adapted from \cite{skinnerOstriker_2013}, is designed for absorption-dominated regimes, with $\sigma_{\Scatt} = 0$ and $f_0 = 0$, which results in exponential damping of the wave amplitude.
-A periodic domain of unit length and initial condition $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$ is used.
+The next test, adapted from~\cite{skinnerOstriker_2013}, is designed for absorption-dominated regimes, with $\sigma_{\Scatt} = 0$ and $f_0 = 0$, which results in exponential damping of the wave amplitude.
+A periodic domain $D=\{x:x\in[0,1]\}$ and initial condition $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$ is used.
 The amplitude of the analytical solution decreases as $e^{-\sigma_{\Ab} t}$.
 For $\sigma_{\Ab}$ = 0.1, 1 and 10 we evolve the test until the initial condition has been damped by a factor $e^{-10}$. 
-Figure~\ref{fig:SineWaveDamping} shows convergence results of the sine wave damping test in the relative error.
-SSP2332, a second-order scheme, displays second-order convergence rate.  
-The PD-ARS schemes are only first-order accurate.  
+Figure~\ref{fig:SineWaveDamping} shows convergence results of the test in the relative error.
+Results for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.
+SSP2332 is the most accurate among these schemes for $\sigma_{\Ab}= 1$ and 10. 
+For $\sigma_{\Ab}=0.1$, PD-ARS with SSPRK2 is the most accurate schemes for $N=8$ and $N=16$.
+Only SSP2332, a second-order accurate scheme, displays a second-order convergence rate.  
+The PD-ARS schemes are first-order accurate in the damping test as expected.
+
 \begin{figure}[h]
@@
 Errors for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.
-The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).
+The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (triangles pointing up) and PD-ARS with SSPRK3 (triangles pointing down).
 Black dashed reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
@@
 
-The last test with known smooth solution, adopted from \cite{radice_etal_2013}, is the sine wave diffusion test, i.e. $\sigma_{\Ab} = 0$ and $f_0 = 0$.
+The final test with known smooth solution, adopted from~\cite{radice_etal_2013}, is the sine wave diffusion test, i.e. $\sigma_{\Ab} = 0$ and $f_0 = 0$.
 A periodic domain $D=\{x:x\in[-3,3]\}$ with initial conditions $\cJ_{0} = 0.5+0.49\times\sin\big(\f{\pi\,x}{3}\big)$ and $\cH_{0} =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}$ are used.  
 The reference diffusion solution is given by $\cJ = \cJ_{0} \times \exp\big(-\f{\pi^2 t}{27\sigma_{\Scatt}}\big)$ and $\cH = (3\,\sigma_{\Scatt})^{-1}\pd{\cJ}{x}$.  
-We evolve with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$, and adjust the end time so that $t_{\mbox{\tiny end}}/\sigma_{\Scatt}=1$. 
-Then the amplitude of the sine wave has been reduced by a factor $e^{-\pi^{2}/27}\approx0.694$ for all values of $\sigma_{\Scatt}$. 
-Figure~\ref{fig:SineWaveDiffusionJ} shows the error versus $N$.  
+We evolve with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$, and adjust the end time so that $t_{\mbox{\tiny end}}/\sigma_{\Scatt}=1$, 
+at which time the amplitude of the sine wave has been reduced by a factor $e^{-\pi^{2}/27}\approx0.694$ for all values of $\sigma_{\Scatt}$. 
+Figure~\ref{fig:SineWaveDiffusionJ} shows the absolute error, obtained using different values of $\sigma_{\Scatt}$, for various IMEX schemes at $t=t_{\mbox{\tiny end}}$, versus $N$. 
+Results for $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.
 SSP2332 and PD-ARS schemes display third-order accuracy for the number density, $\cJ$, and second-order accuracy for $\cH_{x}$, and their errors are difficult to distinguish.
-PD-ARS with SSPRK2 behaves as good as SSP2332 in the diffusion region but requires one less implicit solves per time step.
+For $\sigma=10^{2}$, the errors on the number density $\cJ$ do not drop below $10^{-6}$ because of differences between the two-moment model and the diffusion equation used to obtain the analytic solution.
+For larger values of the scattering opacity, $\sigma=10^{3}$ or $10^{4}$, the two-moment model agrees better with the diffusion model, and we observe convergence over the entire range of $N$.
+PD-ARS with SSPRK2 behaves as well as SSP2332 in the diffusion region but requires 33\% less implicit solves per time step.
 
@@
    \caption{Absolute error for the number density $\cJ$ (left) and the number flux $\cH_{x}$ (right) versus number of elements for the sine wave diffusion test.
-Results with different values of the scattering opacity $\sigma_{\Scatt}$, employing different IMEX schemes, are compared.
+Results with different values of the scattering opacity, $\sigma_{\Scatt}$, employing different IMEX schemes, are compared.
 Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.
@@
 
-In this section we consider a more ``realistic'' test: two-dimensional multigroup neutrino transport with emission, absorption, and elastic scattering through a stationary background.  
+In this section we consider a more ``realistic'' test: two-dimensional Newtonian multigroup neutrino transport with emission, absorption, and isoenergetic scattering through a stationary background.  
 This test is designed to test the realizability-preserving properties of the PD-ARS schemes.  
-Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities used (adopted from \cite{Bruenn_1985}).  
+Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities used (adopted from~\cite{Bruenn_1985}).  
 This test is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction, a reflecting inner boundary and a homogeneous out-flowing outer boundary.
@@
 For this test, we employed the CB closure.  
-We attempted to run this test with our PD-ARS schemes, SSP2332 from \cite{pareschiRusso_2005}, IMEXRKCB2 proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and the scheme proposed by McClarren et al.
-\cite{mcclarren_etal_2008}.
+We attempted to run this test with our PD-ARS schemes, SSP2332 from~\cite{pareschiRusso_2005}, IMEXRKCB2 proposed by Cavaglieri \& Bewley~\cite{cavaglieriBewley2015}, and the scheme proposed by McClarren et al.~\cite{mcclarren_etal_2008}.
 Only the PD-ARS schemes produce realizable moments and are able to evolve to a steady state.
-The other schemes crashed after a few steps, when moments became non-realizable and the closure procedure failed.
+The other schemes crashed after a few time steps, when moments became non-realizable and the closure procedure failed.
 
@@
 The figures show that all the states in the simulation with the PD-ARS schemes are realizable.
+In the middle column, we can see how the neutrinos are generated near the core, stream out, and reach a equilibrium distribution over the phase space eventually.
+In the right column, we can see how the scattering reshapes the flux direction. 
+The oscillatory behavior which is more obvious on high energy group is caused by the machine accuracy error.
 
@@
     \includegraphics[width=0.45\textwidth]{figures/NStatinaryS_EOS}
+    \hspace{30pt}
     \includegraphics[width=0.45\textwidth]{figures/NSS_Opacities}
@@
     \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
-    \caption{Results from the neutrino stationary state test: moments relative to the realizable domain (left column, light blue domain is for $f \in [0,1]$ with black-solid-line as boundary, while light red is for $f\geq 0$ with thin-red-solid-line as boundary), the number density $\cJ$ versus radius (middle column), and the flux factor $|\bcH|/\cJ$ versus radius (right column), at $t = 0.01$~ms, 0.35~ms, and 5.0~ms.
+    \caption{Results from the neutrino stationary state test: moments relative to the realizable domain (left column, the light blue domain is for $f \in [0,1]$ with the black-solid-line as its boundary, while the light red domain is for $f\geq 0$ with the thin-red-solid-line as its boundary), the number density $\cJ$ versus radius (middle column), and the flux factor $|\bcH|/\cJ$ versus radius (right column), at $t = 0.01$~ms, 0.35~ms, and 5.0~ms.
 For the plots in the left column, each $\bcM=(\cJ,\bcH)^{T}$ state is marked by a red dot, which are all inside the light blue region (the realizable domain for fermions).
-The results of PD-ARS with SSPRK2 and PD-ARS with SSPRK3 are indistinguishable in these plots.}
+The results of (PD-ARS with SSPRK2) and (PD-ARS with SSPRK3) are indistinguishable in these plots.}
     \label{fig:NeutrinoStationaryTestEvolve}

### 2019-01-25 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Work on Astronum paper.

--- 2018-11-07 Documents/M1/Astronum_2018/sections/TwoMoments.tex
@@
-\section{Two-Moment Model}
-\label{se:Two-MomentModel}
+\section{Two-Moment Model}\label{se:Two-MomentModel}
 
 \subsection{Transport Equations}
-
-We consider neutrino transport through a static background, and include neutrino-matter interactions due to emission, absorption, and isotropic iso-energetic scattering.  
+We consider neutrino transport through a static background, and include neutrino-matter interactions due to emission, absorption, and isoenergetic scattering.
 After scaling to dimensionless units, the Boltzmann equation can be written as
@@
 where the distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
-$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
-On the right-hand side, $\tau$ is collision time scale.  
+$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum vector: $\vect{p}=\varepsilon\,\vect{\ell}$.
+On the right-hand side, $\tau$ is a collision time scale.  
 In opaque regions, where neutrinos have frequent interactions with the background, $\tau\ll1$.  
 In transparent regions, where neutrinos rarely interact and stream freely, $\tau\gg1$.
-The collision term, $\cC(f)$, which models emission, absorption, and isotropic and elastic scattering is given by
+The collision term, $\cC(f)$, which models emission, absorption, and isoenergetic scattering is given by
 \begin{equation}
@@
 \end{equation}
-where $T$ is the material temperature in energy units and $\mu$ is the neutrino chemical potential.
-Both depend on the spatial position $\vect{x}$.
+where $\vect{z}:=\{\varepsilon,\vect{x}\}$, $T$ is the material temperature in energy units and $\mu$ is the neutrino chemical potential.
+Both $T$ and $\mu$ depend on the spatial position $\vect{x}$.
 
@@
   \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
-  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega,
+  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega.
   \label{eq:angularMoments}
 \end{equation}  
-where $\vect{z}:=\{\varepsilon,\vect{x}\}$.  
 The zeroth moment, $\cJ$, is referred to as the particle density.  
@@
 For fermions, realizable moments can only be constructed from a distribution satisfying the bounds $f \in [0,1]$.  
-Moreover, the set of realizable moments is convex.  
+Moreover, the set of realizable moments is convex: let $\cR$ contains all the possible $\bcM(f)$ so that for any  $f_1\in [0,1]$ and $f_2\in [0,1]$, $\bcM(f_1) \in \cR$ and $\bcM(f_2) \in \cR$, then $\lambda \bcM(f_1) + (1-\lambda)\bcM(f_2) \in \cR$ for any $\lambda \in [0,1]$~\cite{chu_etal_2018}.
 As we will see later in Section~\ref{se:SpacialDiscretization}, this convexity makes it possible to design a realizability-preserving discretization for solving the two-moment model numerically.
@@
 However, recently reported CCSN simulations using two-moment neutrino transport with algebraic closures have employed Eddington factors that can violate the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.
-As examples, we consider the Eddington factors discussed in \cite{murchikova_etal_2017}, where the suitability of several algebraic closures for two-moment neutrino transport was evaluated.  
+As examples, we consider the Eddington factors discussed in~\cite{murchikova_etal_2017}, where the suitability of several algebraic closures for two-moment neutrino transport was evaluated.  
 In Fig.~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor versus the flux factor for two occupancies; $\cJ = 0.1$ (low occupancy) and $\cJ = 0.9$ (high occupancy).  
 Of the algebraic closures plotted, few satisfy the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds}.  
-Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, and Janka~2~\cite{janka_1992} may work fine when the occupancy is low.
+Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, and Janka~2~\cite{janka_1992} clsoures may work fine when the occupancy is low.
 When the occupancy is high, the Eddington factor due to these closures exceeds the upper bound for Fermi-Dirac statistics.  
@@
 When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.
-\ee{so what?  Should we discuss the presence of blocking factors in collision terms?}
-%With those algebraic closures that don't conserve the bounds, the time integrator may give moments that implies $f>1$.
-%Some safety protections may be applied for those method, but the safety protections can break the conservation laws in lepton number or energy and defect the CCSN simulation.
+If this were to happen, the update step may give $f>1$, which would change the sign of the blocking factors in the collision terms.
+If no corrective actions were taken, it would be difficult to predict the impact of the subsequent induced errors on the simulation outcome (later, we will encounter examples in the 
+test cases we have considered).
+If treatments are developed to map the unrealizable moments into the realizable domain, they must be developed to conserve lepton number, energy, and momentum.
 

### 2019-01-25 Documents/M1/Astronum_2018/sections/intro.tex
Work on Astronum paper.

@@
 Core-collapse supernovae (CCSNe) are the explosions of massive stars that end their lives.
-They are the dominant source of heavy elements and play important roles in many astrophysical phenomena, such as neutron star and black hole formation.  
+They are directly or indirectly responsible for the lion's share of elements heavier than oxygen and play important roles in many astrophysical phenomena, such as neutron star and black hole formation.
 Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
-A solid theoretical framework for the CCSN explosion mechanism may help answer important questions in fundamental physics.\cite{janka_etal_2007}
+A solid theoretical framework for the CCSN explosion mechanism may help answer important questions in fundamental physics~\cite{janka_etal_2007}.
 
 One essential part of the explosion mechanism is neutrino transport.
-The neutrino energy deposition drives the CCSN explosion.\cite{mezzacappaMesser_1999}
-Ideally, neutrino transport would be modeled by the Boltzmann transport equation, which is an integro-partial-differential equation evolving a phase-space distribution function $f$.\cite{Bruenn_1985}
+Neutrino energy deposition is believed to drive CCSN explosions except in cases where rapid rotation is present and magnetohydrodynamic effects may dominate 
+(for a review, see~\cite{mezzacappa_2005,janka_2012,burrows_2013,muller_2016}).
+Ideally, neutrino transport would be modeled by the Boltzmann transport equation, which is an integro-partial-differential equation evolving a phase-space distribution function $f$ (e.g., see~\cite{mezzacappaBruenn_1993a,mezzacappaBruenn_1993b,mezzacappaBruenn_1993c,mezzacappa_etal_2001,liebendoerfer_etal_2001,liebendoerfer_etal_2004,livne_etal_2004,liebendoerfer_etal_2005,ott_etal_2008,sumiyoshiYamada_2012,nagakura_etal_2014,sumiyoshi_etal_2014,nagakura_etal_2018}.
 Simulating the neutrino transport implies finding a solution of the Boltzmann equation for a specific domain and period with acceptable accuracy.
 
-However, solving the Boltzmann transport equation full-dimensionally is expensive.
-To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted.\cite{mezzacappaMesser_1999}
+However, solving the Boltzmann transport equation is at present too expensive.
+To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted 
+(e.g., see~\cite{kuroda_etal_2016,roberts_etal_2016,just_etal_2018,vartanyan_etal_2018}).
 Using the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$ -- the spectral particle density $\cJ$ and flux $\bcH$, respectively.
-However, the transport term in the Boltzmann transport equation has the dot product of the velocity vector and the gradient of the phase-space distribution function as its form.
+However, the transport term in the Boltzmann transport equation includes the dot product of the velocity vector and the gradient of the phase-space distribution function.
 Integrating this term with an unit direction vector as the weight function couples the moment equations: it introduces the second angular moment $\bcK$ to the first moment $\bcH$'s equation.
@@
 The better the closure predicts $\bcK$, the more accurate the two-moment method. 
-Two-moment method has been widely applied with different algebraic closures, such as the Minerbo\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan and et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} ) and the Levermore\cite{levermore_1984} closure(e.g.~Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016}).
+The two-moment method has been widely applied with different algebraic closures, such as the Minerbo~\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}~\cite{oConnorCouch_2018}, Pan and et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} ) and the Levermore~\cite{levermore_1984} closure(e.g.~Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016}).
 
 Applying the two-moment method does simplify the problem, but doesn't guarantee an affordable solution.
-To be precise, how to discrete the continuous equation system given by the two-moment method and solve the discretized system efficiently is remain a question.
+To be precise, how to discretize the continuous equation system given by the two-moment method and solve the discretized system efficiently remains a question.
 In fact, the time scales of neutrino interactions with the background ($\sim\mathcal{O}(10^{-13})$~second) is short compared to the duration of the CCSN explosion ($\sim\mathcal{O}(1)$~second).  
-This means that a lot of time step would be needed for solving the system fully explicitly. 
-On the other hand, solving the moment equations fully implicitly requires inverting globally many band-structured matrices whose sizes depend on the spatial discretization.
+This means that $\sim\mathcal{O}(10^{13})$ time steps would be needed for solving the system fully explicitly. 
+On the other hand, solving the moment equations fully implicitly requires inverting globally many band-structured matrices whose sizes depend on the phase-space discretization.
 Such a global inversion is both expensive and unfriendly to parallelization.
@@
 By treating the transport terms in the two-moment equations explicitly and the collision terms implicitly, IMEX methods are subject only to a time step governed by the explicit transport terms, and the matrices to be inverted are block diagonal.
-Therefore, IMEX methods require fewer time steps comparing with fully explicit method, and the calculation for each step is easily parallelizable.  
-%For a non-relativistic system where the propagating speed of gravitional wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.\cite{cernohorskyVanWeert_1992}(read ?)
-For a relativistic circumstance that we have, where the gravity, fluid, and neutrino have a relativistic propagating speed, IMEX method is an efficient method.
+Therefore, IMEX methods require far fewer time steps compared with a fully explicit method, and the computation for each step is easily parallelizable.  
+%For a non-relativistic system where the propagating speed of gravitional wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.~\cite{cernohorskyVanWeert_1992}(read ?)
+For the relativistic setting that we have, where the fluid and the neutrinos have relativistic propagation speeds, IMEX methods are efficient.
 
-To model neutrino transport using two-moment method, two things need to be chosen carefully: an algebraic closure based on Fermi-Dirac statistic for closing the two-moment equations and a convex-invariant, diffusion-accurate IMEX scheme to ensure a physical result.
-Since the neutrino distribution function is bounded ($f\in[0,1]$) by the Pauli exclusion principle, its moments as weight integrals of a bounded function over domain $\omega\in\bbS^{2}$ are also bounded.
-We call the moments satisfying the constraints due to Fermi-Dirac statistics \textit{realizable moments}.
+To model neutrino transport using a two-moment method, two things need to be chosen carefully: an algebraic closure based on Fermi-Dirac statistics for closing the two-moment equations and a convex-invariant, diffusion-accurate IMEX scheme to ensure a physical result.
+A convex-invariant scheme is a scheme that has the property: if all the possible n-th step has $u^{n}\in W$ and $W$ is convex, then all the possible (n+1)-th step has $u^{n+1}\in W$.
+Since the neutrino distribution function is bounded ($f\in[0,1]$) by the Pauli exclusion principle, its moments as weighted integrals of a bounded function over the domain $\omega\in\bbS^{2}$ are also bounded.
+We call the moments satisfying the constraints due to Fermi-Dirac statistics \textit{realizable moments} and the realizable $\cJ$ and $\bcK$ define a convex set~\cite{chu_etal_2018}.
 The algebraic closure should give a realizable $\bcK$, and the well-posedness of the closure requires realizable $\cJ$ and $\bcH$.
@@
 Realizability of $\cJ$ and $\bcH$ after each time step requires a convex-invariant IMEX scheme.
-Since the realizable moments form a convex set, it is possible to construct a realizability-preserving method with convex-invariant IMEX scheme for two-moment neutrino transport.
-What's more, the physics of neutrino transport in CCSN requires the IMEX scheme to be diffusion-accurate.
+Since the realizable moments form a convex set, it is possible to construct a realizability-preserving method using a convex-invariant IMEX scheme for two-moment neutrino transport.
+What's more, the physics of neutrino transport in CCSNe requires the IMEX scheme to be diffusion-accurate.
 
-The study of moment realizability and realizability-preserving method with diffusion-accurate IMEX schemes motivate this work.
-Gottlieb et al\cite{gottlieb_etal_2001} showed standard IMEX scheme with strong-stability-preserving can't have an order higher than first without a restrict time step requirement.
+The study of moment realizability and realizability-preserving methods with diffusion-accurate IMEX schemes motivates this work.
+Gottlieb et al.~\cite{gottlieb_etal_2001} showed that standard strong-stability-preserving IMEX scheme cannot have an order higher than first without a restricted time step.
 To have second-order (or higher-order) accuracy, some correction steps are needed.
@@
 \texttt{thornado} is our toolkit for high-order neutrino-radiation hydrodynamics based on high-order Runge-Kutta Discontinuous Galerkin (RKDG) methods.
-It is developed at the University of Tennessee, Knoxville and Oak Ridge National Laboratory.
-It currently solves the Euler equations for fluid dynamics and the two-moment approximation of the radiative transfer equation, both in the non-relativistic limits.\cite{endeve_etal_2018}
+It is being developed at the University of Tennessee, Knoxville and Oak Ridge National Laboratory.
+It currently solves the Euler equations for fluid dynamics and the two-moment approximation of the radiative transfer equation, both in the non-relativistic limit~\cite{endeve_etal_2018}.
 
@@
 Section~\ref{se:SpacialDiscretization} gives a first-order finite-volume spatial discretization and shows how the spatial discretization preserves constraints in an IMEX step;
-Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct PD-ARS scheme and two PD-ARS schemes, one with second-order accuracy in the streaming limit and the other with third-order accuracy in the same limit;
-Section~\ref{se:NumericalTests} presents the results of the numerical tests, which demonstrate the properties of the PD-ARS schemes; Section~\ref{se:Conclusion} summarizes the achievements of this paper and discusses future works.
+Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct two PD-ARS schemes, one with second-order accuracy in the streaming limit and the other with third-order accuracy in the same limit;
+Section~\ref{se:NumericalTests} presents the results of the numerical tests, which demonstrate the properties of the PD-ARS schemes; Section~\ref{se:Conclusion} summarizes the achievements of this paper and discusses future work.
 

### 2019-01-26 Documents/M1/Astronum_2018/sections/Conclusion.tex

@@
 
-We have developed IMEX schemes suitable for a two-moment model of neutrino transport in \texttt{thornado} that can obey Fermi-Dirac statistics.
+We have developed IMEX schemes suitable for a two-moment model of neutrino transport in \texttt{thornado} that obeys Fermi-Dirac statistics.
 The scheme employs algebraic closure based on Fermi-Dirac statistics, high-order discontinuous Galerkin method for spatial discretization, and convex-invariant time integration to maintain realizability of the moments.
-Since the realizable domain is convex and its convexity can be inherited by a convex combination, some schemes having convex combinations as their stages should be able to preserve the convexity.
-This idea encourages us to construct realizability-preserving time integrators, realizability-preserving IMEX schemes, and eventually a method with realizability-preserving IMEX time integrator and high-order DG method.
-See \cite{chu_etal_2018} for some examples with third-order DG methods.
+Since the realizable domain is convex and its convexity can be inherited by a convex combination, some schemes having convex combinations as their stages should be able to preserve the realizable domain.
+This idea encourages us to construct realizability-preserving time integrators, realizability-preserving IMEX schemes, and eventually a method with a realizability-preserving IMEX time integrator and high-order DG method.
+See~\cite{chu_etal_2018} for more details and examples of the third-order DG methods.
 
-In the application motivating this work, the neutrino distribution function can vary from 0 to 1.  
+In the applications that motivate this work, the neutrino distribution function can vary from 0 to 1.  
 Hence, we have considered algebraic closures based on Fermi-Dirac statistics for both low and high occupancy.  
@@
 As a result, we employed the Cernohorsky \& Bludman closure for the neutrino stationary state test in Section~\ref{se: Neutrino Stationary State Test}.
-(We also run the code with other algebraic closures for examination.
-And the program crashed after few steps because of the nonphysical neutrino density/flux.)
+(We also ran the code with other algebraic closures for examination.
+And the program crashed after a few time steps because of the nonphysical neutrino density/flux obtained and no correction step was taken for $f>1$.
+We could make the code run by adding correction step, but the quality of the results may be compromised.
+And it's difficult to determine whether the results are in fact compromised by a particular correction step and, if so, in what way and to what degree.)
 
 Two PD-ARS schemes are proposed.
-The one with SSPRK2 has second-order accuracy while the other with SSPRK3 has third-order accuracy, and both have strong-stability preserving property in the streaming limit.  
-Their accuracy were demonstrated on problems with known smooth solutions in streaming, absorption, and scattering-dominated regimes.
-The neutrino transport test with emission, absorption, and elastic scattering through a stationary background, was designed to test the convex-invariance of our PD-ARS schemes. 
-The neutrino stationary state test shows that a method combined an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration can be a candidate for constructing a CCSN simulation code without "nonphysical protection" that may break conservation laws.
+The one with SSPRK2 has second-order accuracy while the other with SSPRK3 has third-order accuracy, and both have the strong-stability preserving property in the streaming limit.  
+Their accuracy was demonstrated on problems with known smooth solutions in streaming, absorption, and scattering-dominated regimes.
+The neutrino transport test with emission, absorption, and isoenergetic scattering through a stationary background, was designed to test the convex-invariance of our PD-ARS schemes. 
+The neutrino stationary state test shows that a method combining an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration can be a candidate for constructing a CCSN simulation code without "unphysical correction steps" that may break conservation laws.
 
-In this work, we adopted Cartesian coordinates, linear collision term, and a fixed non-relativistic material background.
-More realistic problems of scientific interest, such as with the scattering with energy exchange and relativistic effects, are left for future research.
+In this work, we adopted Cartesian coordinates, a linear collision term, and a fixed non-relativistic material background.
+More realistic problems of scientific interest, such as with energy-exchanging scattering and relativistic effects, are left for future research.

### 2019-01-26 Documents/M1/Astronum_2018/sections/SpatialDiscretization.tex

@@
 To simply the illustration, we limit the discussion to one spatial dimension and employ a uniform Cartesian mesh.  
-(The extension to multiple spatial dimensions and high-order discretization using the discontinuous Galerkin method is given in \cite{chu_etal_2018})
+(The extension to multiple spatial dimensions and high-order discretization using the discontinuous Galerkin method is given in~\cite{chu_etal_2018}.)
 
@@
 Consider Eq.~\eqref{eq:MomentIMEX} and assume that $\bcM_{i}^{n}$ is realizable for all $i$.  
-Lemma~3 in \cite{chu_etal_2018} states that $\bcM^{n+1}_{i}$ is realizable provided $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.  
+Lemma~3 in~\cite{chu_etal_2018} states that $\bcM^{n+1}_{i}$ is realizable provided $\f{\dt}{\tau} > 0$. 
+%and $\widetilde{\bcM}^{n}_{i}$ is realizable.  
 In Eq.~\eqref{eq:widetildeM}, if $\beta \in [0,1]$, $\widetilde{\bcM}^{n}_{i}$ is expressed as a convex combination of $\bcM_{i}^{n}$ and the expression in the square brackets on the right-hand side of Eq.~\eqref{eq:widetildeM}.
 It follows that $\widetilde{\bcM}^{n}_{i}$ is realizable if the expression inside the square brackets is realizable.  
-By Lemma~2 in \cite{chu_etal_2018}, the expression in square brackets is realizable for a distribution satisfying $f\in[0,1]$.  
-For the two-moment model considered here, realizability depends in the algebraic closure.  
+By Lemma~2 in~\cite{chu_etal_2018}, the expression in square brackets is realizable for a distribution satisfying $f\in[0,1]$.  
+For the two-moment model considered here, realizability depends on the algebraic closure.  
 Specifically, if $\bcM_{i}^{n}$ is realizable and the Eddington factor satisfies the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, then $\bcM^{n+1}_{i}$ is realizable provided $\beta \in [0,1]$.  

### 2019-01-26 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Work on astronum paper

@@
-\clearpage
 \section{Time Integration} \label{se:TimeIntegration}
@@
 Suppose that an algebraic closure based on Fermi-Dirac statistics is used (i.e., the Eddington factor satisfies Eq.~\eqref{eq:eddingtonFactorBounds}).
-Here we consider the construction of an Implicit-Explicit (IMEX) time integration scheme which maintains the bounds in Eq.~\eqref{eq:MomentsBounds}.  
+Here we consider the construction of an Implicit-Explicit (IMEX) time integration scheme that maintains the bounds in Eq.~\eqref{eq:MomentsBounds}.  
 The semi-discretization of the two-moment model results in a system of ordinary differential equations of the form
@@
 
-Since the set of realizable moments is convex, convex-invariant schemes, which maintain states in a convex set, can be used to design realizability-preserving methods for the two-moment model. 
+Since the set of realizable moments is convex, convex-invariant schemes, which preserve the initial value's convex domain, can be used to design realizability-preserving methods for the two-moment model.
 Ideally, the scheme should also be high-order accurate and work well in the asymptotic diffusion limit (characterized by frequent collisions and long time scales).  
@@
 
-Treating the transport operator explicitly and the collision operator implicitly, a standard $s$-stage IMEX scheme takes the following form \cite{pareschiRusso_2005}: 
+Treating the transport operator explicitly and the collision operator implicitly, a standard $s$-stage IMEX scheme takes the following form~\cite{pareschiRusso_2005}: 
 \begin{align}
@@
 These coefficients and weights must satisfy certain order conditions for consistency, accuracy, and other properties.  
-For second-order temporal accuracy, the following conditions are required \cite{hairer_1981}:
+For second-order temporal accuracy, the following conditions are required~\cite{hairer_1981}:
 \begin{equation}
@@
 
-The IMEX scheme is called globally stiffly accurate (GSA) if the coefficients satisfy \cite{dimarcoPareschi2013}:
+The IMEX scheme is called globally stiffly accurate (GSA) if the coefficients satisfy~\cite{dimarcoPareschi2013}:
 \begin{equation}
@@
 Then, $\vect{u}^{n+1} = \vect{u}^{(s)}$, which is simplifying because the assembly step in Eq.~\eqref{imexIntermediate} is omitted.  
-IMEX schemes are further classified by the structure of implicit matrix $A$.  
-If $A$ is invertible, the IMEX scheme is of type~A \cite{pareschiRusso_2005}.  
-If $a_{i1} = 0$ for $i=1,\ldots,s$, $w_{1} = 0$, and the submatrix consisting of the last $s-1$ rows and columns is invertible, the IMEX scheme is of type~ARS \cite{ascher_etal_1997,pareschiRusso_2005}.
+IMEX schemes are further classified by the structure of the implicit matrix $A$.  
+If $A$ is invertible, the IMEX scheme is of type~A~\cite{pareschiRusso_2005}.  
+If $a_{i1} = 0$ for $i=1,\ldots,s$, $w_{1} = 0$, and the submatrix consisting of the last $s-1$ rows and columns is invertible, the IMEX scheme is of type~ARS~\cite{ascher_etal_1997,pareschiRusso_2005}.
 
@@
 Each of the explicit Euler steps has a time step condition that ensures its realizability given by $\hat{c}_{ij}\,\dt\leq\dx$; the Courant-Friedrichs-Lewy (CFL) condition of the scheme.
-Using results proved in \cite{chu_etal_2018} and discussed in Section~\ref{se:SpacialDiscretization}, the IMEX scheme is convex-invariant and realizability-preserving for the two-moment model in Section~\ref{se:SpacialDiscretization} provided
+Using results proved in~\cite{chu_etal_2018} and discussed in Section~\ref{se:SpacialDiscretization}, the IMEX scheme is convex-invariant and realizability-preserving for the two-moment model in Section~\ref{se:SpacialDiscretization} provided
 \begin{equation}
@@
 \end{equation}
-(This CFL condition becomes more restrictive with high-order DG spatial discretization \cite{chu_etal_2018}.)
+(This CFL condition becomes more restrictive with high-order DG spatial discretization~\cite{chu_etal_2018}.)
 
@@
 \end{equation}
-In the context of IMEX schemes, the above relationships imply that the following relations should hold
+In the context of IMEX schemes, the above relationships imply that the following relations should hold~\cite{chu_etal_2018}
 \begin{equation}
@@
 \end{equation}
-where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix and $\vect{e}$ is the vector of ones.
+where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix, $\vect{e}$ is the vector of ones, and $A$ and $\tilde{A}$ are the matrices of the coefficients $(\tilde{a}_{ij})$ and $(a_{ij})$.
 Eq.~\eqref{diffusionAccuracy} implies
@@
 We have proved in \cite{chu_etal_2018} that only IMEX schemes of type~ARS can be both diffusion accurate and convex-invariant.  
-(Another short proof follows from the fact that IMEX schemes type~A have $\tilde{c}_1 = 0$ while $c_i \neq 0$.)
+(Another short proof follows from the fact that IMEX schemes of type~A have $\tilde{c}_1 = 0$ while $c_i \neq 0$.)
 
@@
 Because of this, we sacrifice overall high-order accuracy, and aim for IMEX schemes that are high-order accurate in the streaming limit, diffusion accurate, and convex-invariant.  
-Combining these requirements we seek GSA IMEX schemes of type~ARS with coefficients satisfying the following constraints:
+Combining these requirements we seek GSA IMEX schemes of type~ARS with coefficients satisfying the following constraints~\cite{hu_etal_2018,chu_etal_2018}:
 \begin{enumerate}
@@
     \end{equation}
-    \item High-order accuracy in the streaming limit.  For second-order accuracy: \ee{(Do we need to list third-order accuracy also?)}
+    \item High-order accuracy in the streaming limit.
+    For second-order accuracy:
     \begin{equation}
@@
       \label{eq:orderConditionsEx}
+    \end{equation}
+    For third-order accuracy: 
+    \begin{equation}
+    \sum_{i=1}^{s}\tilde{w}_{i}=1,
+          \quad
+          \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2},
+          \quad
+          \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c_{i}}^2 = \f{1}{3}
+          \quad\text{and}\quad
+          \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{a_{ij}}\tilde{c}_{j}= \f{1}{6}
     \end{equation}
@@
 (The constraint in \eqref{cod:statges} is introduced from efficiency considerations to limit the number of implicit solves.)
-We call the IMEX schemes satisfying the above conditions {PD-ARS} (see also Definition~3 in \cite{chu_etal_2018}), and we provide two optimal PD-ARS schemes below: PD-ARS with SSPRK2 and PD-ARS with SSPRK3, which limit to the optimal second-order and third-order SSPRK schemes from \cite{shuOsher_1988}, respectively.
+We call the IMEX schemes satisfying the above conditions {PD-ARS} (see also Definition~3 in~\cite{chu_etal_2018}), and we provide two optimal PD-ARS schemes below: (PD-ARS with SSPRK2) and (PD-ARS with SSPRK3), which limit to the optimal second-order and third-order SSPRK schemes from~\cite{shuOsher_1988}, respectively.
 
@@
 The optimal PD-ARS with SSPRK2 in the standard double Butcher tableau form, explicit tableau on the left ($\tilde{A}$) and implicit tableau on the right ($A$), is given by:
-\begin{equation}
-  \begin{array}{c | c c c}
+\begin{align}
+  &\begin{array}{c | c c c}
   	0 & 0   & 0 & 0 \\
@@
   	  & 0 & 1/2 & 1/2
-  \end{array}
-\end{equation}
+  \end{array} \\ 
+  &\hspace{48pt} \tilde{A} \hspace{90pt} A
+\end{align}
 For this scheme, only two implicit solves are needed per time step and $c_{\mbox{\tiny Sch}}= 1$, which implies that the time step restriction for preserving moment realizability is only due to the explicit part.
@@
 
-The optimial PD-ARS with SSPRK3 is given in its standard double Butcher tableau form (explicit tableau on the left and implicit tableau on the right) by:
-\begin{equation}
-  \begin{array}{c | c c c c}
+The optimal PD-ARS with SSPRK3 is given in its standard double Butcher tableau form (explicit tableau on the left and implicit tableau on the right) by:
+\begin{align}
+  &\begin{array}{c | c c c c}
   	    &     &     &     &  \\
@@
   	  & 0 & 1/6 & 1/6 & 2/3
-  \end{array}
-\end{equation}
-This scheme requires three implicit solvers per time step, and $c_{\mbox{\tiny Sch}}= 1$.  
-Since PD-ARS with SSPRK3 is not more accurate than PD-ARS with SSPRK2 in collision dominated regions (see results in Section~\ref{se:NumericalTests}), it may not offer any practical advantage over PD-ARS with SSPRK2.
+  \end{array}\\ 
+    &\hspace{60pt} \tilde{A} \hspace{130pt} A
+\end{align}
+This scheme requires three implicit solves per time step, and $c_{\mbox{\tiny Sch}}= 1$.  
+Since (PD-ARS with SSPRK3) is not more accurate than (PD-ARS with SSPRK2) in collision dominated regions (see results in Section~\ref{se:NumericalTests}), it may not offer any practical advantage over (PD-ARS with SSPRK2).

### 2019-01-30 Documents/M1/Astronum_2018/manuscript.tex
Work on Astronum paper.

@@
 \begin{abstract}
-We develop implicit-explicit (IMEX) schemes for neutrino transport in a background material using the \texttt{thornado} code in the context of a two-moment model that evolves the angular moments of a neutrino phase-space distribution function.
+We develop implicit-explicit (IMEX) schemes for neutrino transport in a background material in the context of a two-moment model that evolves the angular moments of a neutrino phase-space distribution function.
 Considering the upper and lower bounds that are introduced by Pauli's exclusion principle on the moments, an algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator both are demanded.
-A finite-volume/first-order discontinuous Galerkin(DG) method is used to interpret how an algebraic moment closure based on Fermi-Dirac statistics satisfies the bounds.
-Several algebraic closures are compared with these bounds in mind and the Cernohorsky and Bludman closure\cite{cernohorskyBludman_1994}, which satisfies the bounds, is chosen for our IMEX schemes.
-For the convex-invariant time integrator, two IMEX schemes named PD-ARS have been proposed following the work in \cite{chu_etal_2018}.
-PD-ARS denotes a convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy in general, high-order accuracy in the streaming limit, and works well in the diffusion limit.
-Our two PD-ARS schemes are second- and third-order, explicit, strong-stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} in their explicit part, respectively, and therefore are second- and third-order accurate in the streaming limit, respectively.
+A finite-volume/first-order discontinuous Galerkin(DG) method is used to illustrate how an algebraic moment closure based on Fermi-Dirac statistics is needed to satisfy the bounds.
+Several algebraic closures are compared with these bounds in mind and the Cernohorsky and Bludman closure, which satisfies the bounds, is chosen for our IMEX schemes.
+For the convex-invariant time integrator, two IMEX schemes named PD-ARS have been proposed.
+PD-ARS denotes a convex-invariant IMEX Runge-Kutta scheme that is high-order accurate in the streaming limit, and works well in the diffusion limit.
+Our two PD-ARS schemes use second- and third-order, explicit, strong-stability-preserving Runge-Kutta methods as their explicit part, respectively, and therefore are second- and third-order accurate in the streaming limit, respectively.
 The accuracy and convex-invariance of our PD-ARS schemes are demonstrated in the numerical tests with a third-order DG method for spatial discretization and a simple Lax-Friedrichs flux.
-We show preliminary result employing tabulated neutrino opacities. 
-%from Bruenn(1985)\citep{Bruenn_1985}
-
+The method has been implemented in our high-order neutrino-radiation hydrodynamics (\texttt{thornado}) toolkit.
+We show preliminary results employing tabulated neutrino opacities.
 \end{abstract}

### 2019-01-30 Documents/M1/Astronum_2018/sections/Conclusion.tex
Work on Astronum paper.

@@
-\section{Conclusion}\label{se:Conclusion}
+\section{Summary and Outlook}\label{se:Summary}
 
-We have developed IMEX schemes suitable for a two-moment model of neutrino transport in \texttt{thornado} that obeys Fermi-Dirac statistics.
-The scheme employs algebraic closure based on Fermi-Dirac statistics, high-order discontinuous Galerkin method for spatial discretization, and convex-invariant time integration to maintain realizability of the moments.
-Since the realizable domain is convex and its convexity can be inherited by a convex combination, some schemes having convex combinations as their stages should be able to preserve the realizable domain.
-This idea encourages us to construct realizability-preserving time integrators, realizability-preserving IMEX schemes, and eventually a method with a realizability-preserving IMEX time integrator and high-order DG method.
-See~\cite{chu_etal_2018} for more details and examples of the third-order DG methods.
+We have developed IMEX schemes suitable for a two-moment model of neutrino transport that obey Fermi-Dirac statistics.
+The scheme employs algebraic closure based on Fermi-Dirac statistics, high-order discontinuous Galerkin methods for spatial discretization, and convex-invariant time integration to maintain realizability of the moments.
+Since the realizable domain is convex and its convexity can be inherited by a convex combination, a scheme having convex combinations as its stages can preserve the realizable domain.
+This encouraged us to construct realizability-preserving time integrators, realizability-preserving IMEX schemes, and eventually a method with a realizability-preserving IMEX time integrator and high-order DG method.
 
@@
 As a result, we employed the Cernohorsky \& Bludman closure for the neutrino stationary state test in Section~\ref{se: Neutrino Stationary State Test}.
-(We also ran the code with other algebraic closures for examination.
+(We also ran the code with other algebraic closures.
 And the program crashed after a few time steps because of the nonphysical neutrino density/flux obtained and no correction step was taken for $f>1$.
@@
 The neutrino transport test with emission, absorption, and isoenergetic scattering through a stationary background, was designed to test the convex-invariance of our PD-ARS schemes. 
-The neutrino stationary state test shows that a method combining an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration can be a candidate for constructing a CCSN simulation code without "unphysical correction steps" that may break conservation laws.
+The neutrino stationary state test shows that a method combining an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration can be a candidate for constructing a CCSN simulation code without ``unphysical correction steps" that may break conservation laws.
 

### 2019-01-30 Documents/M1/Astronum_2018/sections/Numerical.tex
Work on Astronum paper.

@@
 
-In this section we present numerical results obtained with the PD-ARS schemes given in Section~\ref{se:TimeIntegration}.
+In this section we present numerical results obtained with the PD-ARS schemes in Section~\ref{se:TimeIntegration}.
 The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in streaming, absorption, and scattering-dominated regimes in one spatial dimension.
@@
 
-To compare the accuracy of the IMEX schemes, we applied our PD-ARS schemes and the SSP2332 scheme from Pareschi \& Russo~\cite{pareschiRusso_2005} to problems with known smooth solutions in streaming, absorption(damping), and scattering-dominated(diffusing) regimes in one spatial dimension.
+To compare the accuracy of the IMEX schemes, we applied our PD-ARS schemes and the SSP2332 scheme from Pareschi \& Russo~\cite{pareschiRusso_2005} to problems with known smooth solutions in streaming, absorption (damping), and scattering-dominated (diffusing) regimes in one spatial dimension.
 All the tests in this subsection were computed with the maximum entropy closure in the low-occupancy limit (i.e., the Minerbo closure).  
@@
 To compare the numerical results to analytic solutions, the averaged absolute error or the averaged relative error are computed in the $L^{1}$-error norm.
-We compute the absolute error for the streaming test and the diffusion test and the relative error for the damping test.
+We compute the absolute error for the streaming and diffusion tests and the relative error for the damping test.
 They are averaged over the cell with an equal-weight quadrature for the cell integrals.
-And to examine the convergence, we let the number of elements ($N$) vary from 8 to 128.
+To examine the convergence, we let the number of elements ($N$) vary from 8 to 128.
 
@@
 Figure~\ref{fig: SineWaveStreaming} plots the absolute error for the number density versus the number of elements $N$.
-We see the errors obtained with (SSPRK3) and (PD-ARS with SSPRK3) are smallest and decrease as $N^{-3}$, as expected for a scheme combining third-order accurate time stepping with third-order accurate spatial discretization.
+We see the errors obtained with SSPRK3 and PD-ARS3 are smallest and decrease as $N^{-3}$, as expected for a scheme combining third-order accurate time stepping with third-order accurate spatial discretization.
 For all the other schemes, using second-order accurate explicit time stepping, the error decreases as $N^{-2}$.
 Among the second-order schemes, SSP2332 has the smallest error.
-In the streaming limit, the PD-ARS schemes reduce to SSPRK schemes, such that (PD-ARS with SSPRK2) to SSPRK2 and (PD-ARS with SSPRK3) to SSPRK3, respectively.
+In the streaming limit, the PD-ARS schemes reduce to SSPRK schemes, such that PD-ARS2 to SSPRK2 and PD-ARS3 to SSPRK3, respectively.
 Therefore, the absolute errors of PD-ARS schemes and SSPRK schemes are indistinguishable.
@@
    \caption{Absolute error versus number of elements, $N$, for the streaming sine wave test.
-Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crosses), PD-ARS with SSPRK2 (light red circles) and PD-ARS with SSPRK3 (light red asterisks).
+Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crosses), PD-ARS2 (light red circles) and PD-ARS3 (light red asterisks).
 Black dashed reference lines are proportional to $N^{-2}$ (top), and $N^{-3}$ (bottom), respectively.}
@@
 The next test, adapted from~\cite{skinnerOstriker_2013}, is designed for absorption-dominated regimes, with $\sigma_{\Scatt} = 0$ and $f_0 = 0$, which results in exponential damping of the wave amplitude.
-A periodic domain $D=\{x:x\in[0,1]\}$ and initial condition $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$ is used.
+A periodic domain $D=\{x:x\in[0,1]\}$ and initial condition $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$ are used.
 The amplitude of the analytical solution decreases as $e^{-\sigma_{\Ab} t}$.
@@
 SSP2332 is the most accurate among these schemes for $\sigma_{\Ab}= 1$ and 10. 
-For $\sigma_{\Ab}=0.1$, PD-ARS with SSPRK2 is the most accurate schemes for $N=8$ and $N=16$.
+For $\sigma_{\Ab}=0.1$, PD-ARS2 is the most accurate scheme for $N=8$ and $N=16$. 
+We have seen the same behavior for the scheme proposed by McClarren et al.~\cite{mcclarren_etal_2008} (PC2) in~\cite{chu_etal_2018}.
+Since these are special cases for $N=8$ and $N=16$, we won't recommend PD-ARS2 instead of SSP2332 for the damping problem.
 Only SSP2332, a second-order accurate scheme, displays a second-order convergence rate.  
-The PD-ARS schemes are first-order accurate in the damping test as expected.
+The PD-ARS schemes are first-order accurate.
 
@@
 Errors for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.
-The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (triangles pointing up) and PD-ARS with SSPRK3 (triangles pointing down).
+The IMEX schemes employed are SSP2332 ($+$), PD-ARS2 (triangles pointing up) and PD-ARS3 (triangles pointing down).
 Black dashed reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
@@
 
-The final test with known smooth solution, adopted from~\cite{radice_etal_2013}, is the sine wave diffusion test, i.e. $\sigma_{\Ab} = 0$ and $f_0 = 0$.
+The final test with known smooth solution, adopted from~\cite{radice_etal_2013}, is the sine wave diffusion test; i.e. $\sigma_{\Ab} = 0$ and $f_0 = 0$.
 A periodic domain $D=\{x:x\in[-3,3]\}$ with initial conditions $\cJ_{0} = 0.5+0.49\times\sin\big(\f{\pi\,x}{3}\big)$ and $\cH_{0} =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}$ are used.  
@@
 SSP2332 and PD-ARS schemes display third-order accuracy for the number density, $\cJ$, and second-order accuracy for $\cH_{x}$, and their errors are difficult to distinguish.
-For $\sigma=10^{2}$, the errors on the number density $\cJ$ do not drop below $10^{-6}$ because of differences between the two-moment model and the diffusion equation used to obtain the analytic solution.
+For $\sigma=10^{2}$, the errors in the number density $\cJ$ do not drop below $10^{-6}$ because of differences between the two-moment model and the diffusion equation used to obtain the analytic solution.
 For larger values of the scattering opacity, $\sigma=10^{3}$ or $10^{4}$, the two-moment model agrees better with the diffusion model, and we observe convergence over the entire range of $N$.
-PD-ARS with SSPRK2 behaves as well as SSP2332 in the diffusion region but requires 33\% less implicit solves per time step.
+PD-ARS2 behaves as well as SSP2332 in the diffusion region but requires 33\% less implicit solves per time step.
 
@@
 Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.
-The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles), and PD-ARS with SSPRK3 (hexagram).
+The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS2 (triangles pointing up), and PD-ARS3 (triangles pointing down).
 Black dashed lines in the left plot are reference lines proportional to $N^{-2}$ (top) and $N^{-3}$ (bottom), respectively.
@@
 
-In this section we consider a more ``realistic'' test: two-dimensional Newtonian multigroup neutrino transport with emission, absorption, and isoenergetic scattering through a stationary background.  
+In this section we consider a more ``realistic'' test: two-dimensional multigroup neutrino transport with emission, absorption, and isoenergetic scattering through a stationary background.  
 This test is designed to test the realizability-preserving properties of the PD-ARS schemes.  
@@
 
-Results obtained with the PD-ARS IMEX schemes are plotted in Figure~\ref{fig:NeutrinoStationaryTestEvolve} for various times: $t=0.01$~ms (top panels), 0.35~ms (middle panels), and 5.0~ms (bottom panels).
+Results obtained with the IMEX PD-ARS schemes are plotted in Figure~\ref{fig:NeutrinoStationaryTestEvolve} for various times: $t=0.01$~ms (top panels), 0.35~ms (middle panels), and 5.0~ms (bottom panels).
 In the left column we plot the solution in the $|\vect{\cH}|\cJ$-plane.  
@@
 The figures show that all the states in the simulation with the PD-ARS schemes are realizable.
-In the middle column, we can see how the neutrinos are generated near the core, stream out, and reach a equilibrium distribution over the phase space eventually.
+In the middle column, we can see how the neutrinos are generated near the core, stream out, and reach an equilibrium distribution over the phase space eventually.
 In the right column, we can see how the scattering reshapes the flux direction. 
-The oscillatory behavior which is more obvious on high energy group is caused by the machine accuracy error.
+The oscillatory behavior, which is more obvious for high-energy groups, is caused by machine accuracy error.
 
@@
   \centering
-    \includegraphics[width=\textwidth]{figures/NSS_1_1}\\
-    \includegraphics[width=\textwidth]{figures/NSS_3_1} \\
-    \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
-    \caption{Results from the neutrino stationary state test: moments relative to the realizable domain (left column, the light blue domain is for $f \in [0,1]$ with the black-solid-line as its boundary, while the light red domain is for $f\geq 0$ with the thin-red-solid-line as its boundary), the number density $\cJ$ versus radius (middle column), and the flux factor $|\bcH|/\cJ$ versus radius (right column), at $t = 0.01$~ms, 0.35~ms, and 5.0~ms.
+    \includegraphics[width=.9\textwidth]{figures/NSS_1_1}\\
+    \includegraphics[width=.9\textwidth]{figures/NSS_3_1} \\
+    \includegraphics[width=.9\textwidth]{figures/NSS_5_1} \\
+    \caption{Results from the neutrino stationary state test: moments relative to the realizable domain (left column, the light blue domain is for $f \in [0,1]$, with the black-solid-line as its boundary, while the light red domain is for $f\geq 0$, with the thin-red-solid-line as its boundary), the number density $\cJ$ versus radius (middle column), and the flux factor $|\bcH|/\cJ$ versus radius (right column), at $t = 0.01$~ms, 0.35~ms, and 5.0~ms.
 For the plots in the left column, each $\bcM=(\cJ,\bcH)^{T}$ state is marked by a red dot, which are all inside the light blue region (the realizable domain for fermions).
-The results of (PD-ARS with SSPRK2) and (PD-ARS with SSPRK3) are indistinguishable in these plots.}
+The results of PD-ARS2 and PD-ARS3 are indistinguishable in these plots.}
     \label{fig:NeutrinoStationaryTestEvolve}

### 2019-01-30 Documents/M1/Astronum_2018/sections/SpatialDiscretization.tex
Work on Astronum paper.

@@
-\section{Spatial Discretization}\label{se:SpacialDiscretization}
+\section{Spatial Discretization}\label{se:SpatialDiscretization}
 
@@
 where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is the numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the collision term evaluated with $\bcM_{i}$.
-In this paper we use the global Lax-Friedrichs flux (setting the largest absolute eigenvalue of the flux Jacobian to one)
+In this paper we use the global Lax-Friedrichs flux (setting the largest absolute eigenvalue of the flux Jacobian to one):
 \begin{equation}
@@
 Consider Eq.~\eqref{eq:MomentIMEX} and assume that $\bcM_{i}^{n}$ is realizable for all $i$.  
-Lemma~3 in~\cite{chu_etal_2018} states that $\bcM^{n+1}_{i}$ is realizable provided $\f{\dt}{\tau} > 0$. 
+It can be shown (Lemma~3 in~\cite{chu_etal_2018}) that $\bcM^{n+1}_{i}$ is realizable provided $\f{\dt}{\tau} > 0$. 
 %and $\widetilde{\bcM}^{n}_{i}$ is realizable.  
@@
 It follows that $\widetilde{\bcM}^{n}_{i}$ is realizable if the expression inside the square brackets is realizable.  
-By Lemma~2 in~\cite{chu_etal_2018}, the expression in square brackets is realizable for a distribution satisfying $f\in[0,1]$.  
+It can be shown (Lemma~2 in~\cite{chu_etal_2018}) that the expression in square brackets is realizable for a distribution satisfying $f\in[0,1]$.  
 For the two-moment model considered here, realizability depends on the algebraic closure.  
 Specifically, if $\bcM_{i}^{n}$ is realizable and the Eddington factor satisfies the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, then $\bcM^{n+1}_{i}$ is realizable provided $\beta \in [0,1]$.  
-Thus, realizability of $\bcM^{n+1}_{i}$ requires both a closure based on Fermi-Dirac statistics and a CFL condition $\dt\le\dx$.
+Thus, realizability of $\bcM^{n+1}_{i}$ requires both a closure based on Fermi-Dirac statistics and a Courant-Friedrichs-Lewy (CFL) condition $\dt\le\dx$.

### 2019-01-31 Documents/M1/Astronum_2018/sections/TimeIntegration.tex

@@
 
-Since the set of realizable moments is convex, convex-invariant schemes, which preserve the initial value's convex domain, can be used to design realizability-preserving methods for the two-moment model.
+Since the set of realizable moments is convex, convex-invariant schemes, which maps the initial value remains in its domain, can be used to design realizability-preserving methods for the two-moment model.
 Ideally, the scheme should also be high-order accurate and work well in the asymptotic diffusion limit (characterized by frequent collisions and long time scales).  
@@
 
-\subsection{Convex-Invariant Implicit-Explicit Schemes}
+\subsection{Convex-Invariant IMEX Schemes}
 
@@
 where $c_{ij}$ and $\hat{c}_{ij}\equiv\tilde{c}_{ij}/c_{ij}$ are defined in terms of $a_{ij}$ and $\tilde{a}_{ij}$.
-For IMEX schemes of type~ARS, $c_{ij}$ and $\tilde{c}_{ij}$ are given by
+For IMEX schemes of type~ARS, $c_{ij}$ and $\tilde{c}_{ij}$ are given by~\cite{hu_etal_2018}
     \begin{equation}
@@
 Moreover, if $c_{ij},\tilde{c}_{ij}\ge0$ and $a_{ii}>0$, each stage in Eq.~\eqref{eq:imexStagesRewrite} is a convex combination of explicit Euler steps (with time step $\hat{c}_{ij}\dt$), followed by a implicit Euler step.
-Each of the explicit Euler steps has a time step condition that ensures its realizability given by $\hat{c}_{ij}\,\dt\leq\dx$; the Courant-Friedrichs-Lewy (CFL) condition of the scheme.
-Using results proved in~\cite{chu_etal_2018} and discussed in Section~\ref{se:SpacialDiscretization}, the IMEX scheme is convex-invariant and realizability-preserving for the two-moment model in Section~\ref{se:SpacialDiscretization} provided
+Each of the explicit Euler steps has a time step condition that ensures its realizability given by $\hat{c}_{ij}\,\dt\leq\dx$; the CFL condition of the scheme.
+Using results proved in~\cite{chu_etal_2018} and discussed in Section~\ref{se:SpatialDiscretization}, the IMEX scheme is convex-invariant and realizability-preserving for the two-moment model in Section~\ref{se:SpatialDiscretization} provided
 \begin{equation}
@@
 
-\subsection{Diffusion Accurate, Convex-Invariant Implicit-Explicit Schemes}
+\subsection{Diffusion Accurate, Convex-Invariant IMEX Schemes}
 
-Accuracy in the diffusion limit is another important property to consider for the IMEX scheme applied to the two-moment model.  
+Accuracy in the diffusion limit is another important property to consider when an IMEX scheme is applied to the two-moment model.  
 In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$, and the two-moment model is approximately governed by (e.g., \cite{jinLevermore_1996})
@@
 \end{equation}
-In the context of IMEX schemes, the above relationships imply that the following relations should hold~\cite{chu_etal_2018}
+In the context of IMEX schemes, the above relationships imply that the following relations should hold~\cite{chu_etal_2018}:
 \begin{equation}
@@
 where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix, $\vect{e}$ is the vector of ones, and $A$ and $\tilde{A}$ are the matrices of the coefficients $(\tilde{a}_{ij})$ and $(a_{ij})$.
-Eq.~\eqref{diffusionAccuracy} implies
+Eq.~\eqref{diffusionAccuracy} implies:
 \begin{equation}
-  c_{i} = \tilde{c}_{i}, \quad i=1,\ldots,s
+  c_{i} = \tilde{c}_{i}, \quad i=1,\ldots,s.
 \end{equation}
@@
 
-\subsection{PD-ARS schemes}
+\subsection{PD-ARS IMEX schemes}
 
@@
 To circumvent this problem, correction steps can be introduced after the assembly step in Eq.~\eqref{imexIntermediate} (e.g., \cite{chertock_etal_2015,hu_etal_2018}).  
-However, the correction steps can impose time step constraints for realizability or accuracy in the diffusion limit that ruins the efficiency gains expected from the IMEX scheme.  
+However, the correction steps can impose time step constraints for realizability or accuracy in the diffusion limit that ruin the efficiency gains expected from the IMEX scheme.  
 Because of this, we sacrifice overall high-order accuracy, and aim for IMEX schemes that are high-order accurate in the streaming limit, diffusion accurate, and convex-invariant.  
@@
           \quad\text{and}\quad
-          \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{a_{ij}}\tilde{c}_{j}= \f{1}{6}
+          \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{a_{ij}}\tilde{c}_{j}= \f{1}{6}.
     \end{equation}
-    \item Diffusion accurate:
+    \item Diffusion accuracy:
     \begin{equation}
@@
     \end{equation}
-    \item Convex-invariant:
+    \item Convex-invariance:
     \begin{align}
       &a_{ii}>0, \quad c_{i0},\tilde{c}_{i0}\ge0, \quad \text{for} \quad i=2,\ldots,s, \nonumber \\
-      &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=3,\ldots,s, \quad\text{and}\quad j=2,\ldots,i-1.  
+      &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=3,\ldots,s, \quad\text{and}\quad j=2,\ldots,i-1,
       \label{eq:convexInvariant}
@@
                   j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
-    \item Less than five stages ($s\le4$) \label{cod:statges}.
-    \item Globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. 
+
+    (Note that the greater the $c_{\Sch}$, the larger the time step can be.
+    And $c_{\Sch} \leq 1$.)
+    \item Have less than five stages ($s\le4$)\label{cod:statges}.
+    \item Are globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. 
 \end{enumerate}
@@
 (The constraint in \eqref{cod:statges} is introduced from efficiency considerations to limit the number of implicit solves.)
-We call the IMEX schemes satisfying the above conditions {PD-ARS} (see also Definition~3 in~\cite{chu_etal_2018}), and we provide two optimal PD-ARS schemes below: (PD-ARS with SSPRK2) and (PD-ARS with SSPRK3), which limit to the optimal second-order and third-order SSPRK schemes from~\cite{shuOsher_1988}, respectively.
+We call the IMEX schemes satisfying the above conditions {PD-ARS} (see also Definition~3 in~\cite{chu_etal_2018}), and we provide two optimal PD-ARS schemes below: PD-ARS2 and PD-ARS3, each limits to the optimal second-order and third-order SSPRK schemes from~\cite{shuOsher_1988}, respectively.
+\subsubsection{PD-ARS2}
 
-\subsubsection{PD-ARS with SSPRK2}
-
-The optimal PD-ARS with SSPRK2 in the standard double Butcher tableau form, explicit tableau on the left ($\tilde{A}$) and implicit tableau on the right ($A$), is given by:
+The optimal 3-statge PD-ARS, PD-ARS2, in the standard double Butcher tableau form, with explicit tableau ($\tilde{A}$) on the left and implicit tableau ($A$) on the right, is given by
 \begin{align}
@@
   	  & 0 & 1/2 & 1/2
-  \end{array} \\ 
-  &\hspace{48pt} \tilde{A} \hspace{90pt} A
+  \end{array}
 \end{align}
-For this scheme, only two implicit solves are needed per time step and $c_{\mbox{\tiny Sch}}= 1$, which implies that the time step restriction for preserving moment realizability is only due to the explicit part.
+Note its explicit tableau is SSPRK2. 
+For this scheme, only two implicit solves are needed per time step and $c_{\Sch}= 1$, which implies that the time step restriction for preserving moment realizability is only due to the explicit part.
 
-\subsubsection{PD-ARS with SSPRK3}
+\subsubsection{PD-ARS3}
 
-The optimal PD-ARS with SSPRK3 is given in its standard double Butcher tableau form (explicit tableau on the left and implicit tableau on the right) by:
+The optimal 4-stage PD-ARS, PD-ARS3, is given in its standard double Butcher tableau form (explicit tableau on the left and implicit tableau on the right) by
 \begin{align}
@@
   	  & 0 & 1/6 & 1/6 & 2/3
-  \end{array}\\ 
-    &\hspace{60pt} \tilde{A} \hspace{130pt} A
+  \end{array}
 \end{align}
-This scheme requires three implicit solves per time step, and $c_{\mbox{\tiny Sch}}= 1$.  
-Since (PD-ARS with SSPRK3) is not more accurate than (PD-ARS with SSPRK2) in collision dominated regions (see results in Section~\ref{se:NumericalTests}), it may not offer any practical advantage over (PD-ARS with SSPRK2).
+Its explicit tableau is SSPRK3. 
+This scheme requires three implicit solves per time step, and $c_{\Sch}= 1$.  
+Since PD-ARS3 is not more accurate than PD-ARS2 in collision dominated regions (see our results in Section~\ref{se:NumericalTests}), it may not offer any practical advantage over PD-ARS2.

### 2019-01-31 Documents/M1/Astronum_2018/sections/TwoMoments.tex

@@
 where the distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.
-$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum vector: $\vect{p}=\varepsilon\,\vect{\ell}$.
+$\vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum: $\vect{p}=\varepsilon\,\vect{\ell}$.
 On the right-hand side, $\tau$ is a collision time scale.  
@@
 The limit $\xi = 1$, when $\sigma_{\Scatt} = 0$, corresponds to pure absorption, while $\xi = 0$, when $\sigma_{\Ab} = 0$, corresponds to pure scattering.  
-The equilibrium distribution function for neutrinos is given by the Fermi-Dirac distribution
+The equilibrium distribution function for neutrinos is given by the Fermi-Dirac distribution:
 \begin{equation}
@@
 Approximate solutions to the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, can be found by solving the two-moment model.
-To this end, define the angular moments of the distribution function as follows
+To this end, define the angular moments of the distribution function as follows:
 \begin{equation}
@@
 The first moment, $\bcH$, is the particle flux, and the second moment, $\bcK$, is proportional to the stress tensor.  
-By integrating Eq.~\eqref{eq:boltzmann} over the momentum space angular dimension we obtain equations for the zeroth and the first moments
+By integrating Eq.~\eqref{eq:boltzmann} over the momentum-space angular dimension we obtain equations for the zeroth and the first moments:
 \begin{equation}
@@
 
-As is shown in the previous section, the moment equation for $\bcH$ involves the higher moment $\bcK$ and the two-moment model is open.  
+The moment equation for $\bcH$ involves the higher moment $\bcK$ and the two-moment model is open.  
 To close the two-moment model, we consider algebraic closures.  
@@
 where $\vect{k}$ is the Eddington tensor.  
-By assuming that the distribution function is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore~\cite{levermore_1984} proposed a simple form for the Eddington tensor
+By assuming that the distribution function is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore~\cite{levermore_1984} proposed a simple form for the Eddington tensor:
 \begin{equation}
@@
 Neutrinos are fermions and obey the Pauli exclusion principle.  
-Because of this, the neutrino distribution function is bounded; i.e. $f \in [0,1]$.
+Because of this, the neutrino distribution function is bounded; i.e.~$f \in [0,1]$.
 As a result, the angular moments $\cJ$ and $\vect{\cH}$ and the Eddington factor $\chi$ satisfy the following bounds~\cite{levermore_1984,lareckiBanach_2011,kershaw_1976,shohatTamarkin_1943}: 
@@
 For fermions, realizable moments can only be constructed from a distribution satisfying the bounds $f \in [0,1]$.  
-Moreover, the set of realizable moments is convex: let $\cR$ contains all the possible $\bcM(f)$ so that for any  $f_1\in [0,1]$ and $f_2\in [0,1]$, $\bcM(f_1) \in \cR$ and $\bcM(f_2) \in \cR$, then $\lambda \bcM(f_1) + (1-\lambda)\bcM(f_2) \in \cR$ for any $\lambda \in [0,1]$~\cite{chu_etal_2018}.
-As we will see later in Section~\ref{se:SpacialDiscretization}, this convexity makes it possible to design a realizability-preserving discretization for solving the two-moment model numerically.
+Moreover, the set of realizable moments is convex: let $\cR$ be the realizability set and $\bcM_{1}, \bcM_{2} \in \cR$, then $\lambda \bcM_{1} + (1-\lambda)\bcM_{2} \in \cR$ for any $\lambda \in [0,1]$~\cite{chu_etal_2018}.
+As we will see later in Section~\ref{se:SpatialDiscretization}, this convexity makes it possible to design a realizability-preserving discretization for solving the two-moment model numerically.
 
 The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} deserve further attention.  
-They are equally important, relative to those in Eq.~\eqref{eq:MomentsBounds}, in maintaining consistency of the two-moment model with respect to Fermi-Dirac statistics.  
+They are important as those in Eq.~\eqref{eq:MomentsBounds}, in maintaining consistency of the two-moment model with respect to Fermi-Dirac statistics.  
 When designing a numerical scheme for the two-moment model that maintains realizable $\bcM$, it is also necessary for the Eddington factor to satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.
@@
 Of the algebraic closures plotted, few satisfy the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds}.  
-Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, and Janka~2~\cite{janka_1992} clsoures may work fine when the occupancy is low.
+Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, and Janka~2~\cite{janka_1992} closures may work fine when the occupancy is low.
 When the occupancy is high, the Eddington factor due to these closures exceeds the upper bound for Fermi-Dirac statistics.  
@@
 When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.
-If this were to happen, the update step may give $f>1$, which would change the sign of the blocking factors in the collision terms.
-If no corrective actions were taken, it would be difficult to predict the impact of the subsequent induced errors on the simulation outcome (later, we will encounter examples in the 
-test cases we have considered).
-If treatments are developed to map the unrealizable moments into the realizable domain, they must be developed to conserve lepton number, energy, and momentum.
+If this were to happen, the update step may give $\cJ>1$.
+Considering the fact that the completed collision term contains blocking factors, i.e.~$(1-\cJ)\times$ something positive, $\cJ > 1$ would change blocking factors' sign and it would be difficult to predict the impact of the subsequent induced errors on the simulation outcome.
+\rc{Besides, even with the simplified collision term, Eq~\ref{eq:collisionTermMoments}, $\cJ>1$ could result... the reason of crash}
+If treatments are developed to map the unrealizable moments into the realizable domain, they should be developed to conserve lepton number, energy, and momentum.
 

### 2019-01-31 Documents/M1/Astronum_2018/sections/intro.tex

@@
 One essential part of the explosion mechanism is neutrino transport.
-Neutrino energy deposition is believed to drive CCSN explosions except in cases where rapid rotation is present and magnetohydrodynamic effects may dominate 
-(for a review, see~\cite{mezzacappa_2005,janka_2012,burrows_2013,muller_2016}).
-Ideally, neutrino transport would be modeled by the Boltzmann transport equation, which is an integro-partial-differential equation evolving a phase-space distribution function $f$ (e.g., see~\cite{mezzacappaBruenn_1993a,mezzacappaBruenn_1993b,mezzacappaBruenn_1993c,mezzacappa_etal_2001,liebendoerfer_etal_2001,liebendoerfer_etal_2004,livne_etal_2004,liebendoerfer_etal_2005,ott_etal_2008,sumiyoshiYamada_2012,nagakura_etal_2014,sumiyoshi_etal_2014,nagakura_etal_2018}.
-Simulating the neutrino transport implies finding a solution of the Boltzmann equation for a specific domain and period with acceptable accuracy.
+Neutrino energy deposition is believed to be the major driver of CCSN explosions, -- except in cases where rapid rotation is present and magnetohydrodynamic effects may dominate (for reviews, see~\cite{mezzacappa_2005,janka_2012,burrows_2013,muller_2016}).
+Ideally, neutrino transport would be modeled by the Boltzmann transport equation, which is an integro-partial-differential equation evolving a phase-space distribution function $f$.~(e.g., see~\cite{mezzacappaBruenn_1993a,mezzacappaBruenn_1993b,mezzacappaBruenn_1993c,mezzacappa_etal_2001,liebendoerfer_etal_2001,liebendoerfer_etal_2004,livne_etal_2004,liebendoerfer_etal_2005,ott_etal_2008,sumiyoshiYamada_2012,nagakura_etal_2014,sumiyoshi_etal_2014,nagakura_etal_2018} for studies of CCSN with Boltzmann transport in various approximate settings.)
+Simulating the neutrino transport implies finding a solution of the Boltzmann equation for a specific domain and period, with acceptable accuracy.
 
-However, solving the Boltzmann transport equation is at present too expensive.
-To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted 
-(e.g., see~\cite{kuroda_etal_2016,roberts_etal_2016,just_etal_2018,vartanyan_etal_2018}).
+However, solving the Boltzmann transport equation with sufficient phase-space resolution and full weak interaction physics is at present too expensive.
+To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted (e.g., see~\cite{kuroda_etal_2016,roberts_etal_2016,just_etal_2018,vartanyan_etal_2018}).
 Using the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$ -- the spectral particle density $\cJ$ and flux $\bcH$, respectively.
 However, the transport term in the Boltzmann transport equation includes the dot product of the velocity vector and the gradient of the phase-space distribution function.
-Integrating this term with an unit direction vector as the weight function couples the moment equations: it introduces the second angular moment $\bcK$ to the first moment $\bcH$'s equation.
-Knowledge of $\bcK$ is needed to close the two-moment equation system.
-Therefore, an algebraic closure that gives a predicted $\bcK$ given $\cJ$ and $\bcH$ is needed.
+Integrating this term with a unit direction vector as the weight function couples the moment equations: it introduces the second angular moment $\bcK$ to the first moment $\bcH$'s equation.
+Knowledge of $\bcK$ is needed to close the two-moment system.
+Therefore, a closure that gives $\bcK$ consistent with $\cJ$ and $\bcH$ is needed.
 The better the closure predicts $\bcK$, the more accurate the two-moment method. 
-The two-moment method has been widely applied with different algebraic closures, such as the Minerbo~\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}~\cite{oConnorCouch_2018}, Pan and et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} ) and the Levermore~\cite{levermore_1984} closure(e.g.~Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016}).
+The two-moment method has been widely applied in the CCSN modeling community with different algebraic closures, such as the Minerbo~\cite{minerbo_1978} closure (e.g.~{O'Connor} and {Couch}~\cite{oConnorCouch_2018}, Pan and et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018}) and the Levermore~\cite{levermore_1984} closure (e.g.~Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016}).
 
 Applying the two-moment method does simplify the problem, but doesn't guarantee an affordable solution.
-To be precise, how to discretize the continuous equation system given by the two-moment method and solve the discretized system efficiently remains a question.
-In fact, the time scales of neutrino interactions with the background ($\sim\mathcal{O}(10^{-13})$~second) is short compared to the duration of the CCSN explosion ($\sim\mathcal{O}(1)$~second).  
+To be precise, how to discretize the continuous equation of system given by the two-moment method and solve the discretized system efficiently remains a question.
+In fact, the time scales of neutrino interactions with the background (can be $\sim\mathcal{O}(10^{-13})$~second) is short compared to the duration of the CCSN explosion ($\sim\mathcal{O}(1)$~second).
 This means that $\sim\mathcal{O}(10^{13})$ time steps would be needed for solving the system fully explicitly. 
-On the other hand, solving the moment equations fully implicitly requires inverting globally many band-structured matrices whose sizes depend on the phase-space discretization.
+On the other hand, solving the moment equations fully implicitly requires inverting global band-structured matrices whose sizes depend on the phase-space discretization.
 Such a global inversion is both expensive and unfriendly to parallelization.
@@
 Therefore, IMEX methods require far fewer time steps compared with a fully explicit method, and the computation for each step is easily parallelizable.
-%For a non-relativistic system where the propagating speed of gravitional wave and fluid is much slower than the light speed, fully implicit method is a better choice for neutrino transport in CCSN simulation.~\cite{cernohorskyVanWeert_1992}(read ?)
-For the relativistic setting that we have, where the fluid and the neutrinos have relativistic propagation speeds, IMEX methods are efficient.
+For the relativistic setting that we have, where the fluid and the neutrinos have comparable propagation speeds, and IMEX methods can be efficient.
 
-To model neutrino transport using a two-moment method, two things need to be chosen carefully: an algebraic closure based on Fermi-Dirac statistics for closing the two-moment equations and a convex-invariant, diffusion-accurate IMEX scheme to ensure a physical result.
-A convex-invariant scheme is a scheme that has the property: if all the possible n-th step has $u^{n}\in W$ and $W$ is convex, then all the possible (n+1)-th step has $u^{n+1}\in W$.
+To model neutrino transport using a two-moment method, two (or at least two) things need to be chosen carefully: an algebraic closure based on Fermi-Dirac statistics for closing the two-moment equations and a convex-invariant, diffusion-accurate IMEX scheme to ensure a physical result.
+A convex-invariant scheme has the following property: if the solution $u^{n}\in W$ and $W$ is convex, then $u^{n+1}\in W$.
 Since the neutrino distribution function is bounded ($f\in[0,1]$) by the Pauli exclusion principle, its moments as weighted integrals of a bounded function over the domain $\omega\in\bbS^{2}$ are also bounded.
-We call the moments satisfying the constraints due to Fermi-Dirac statistics \textit{realizable moments} and the realizable $\cJ$ and $\bcK$ define a convex set~\cite{chu_etal_2018}.
+We call the moments satisfying the constraints due to Fermi-Dirac statistics \textit{realizable moments} and the realizable $\cJ$ and $\bcH$ define a convex set~\cite{chu_etal_2018}.
 The algebraic closure should give a realizable $\bcK$, and the well-posedness of the closure requires realizable $\cJ$ and $\bcH$.
@@
 Since the realizable moments form a convex set, it is possible to construct a realizability-preserving method using a convex-invariant IMEX scheme for two-moment neutrino transport.
-What's more, the physics of neutrino transport in CCSNe requires the IMEX scheme to be diffusion-accurate.
+In addition, the physics of neutrino transport in CCSNe requires the IMEX scheme to be diffusion-accurate.
 
 The study of moment realizability and realizability-preserving methods with diffusion-accurate IMEX schemes motivates this work.
-Gottlieb et al.~\cite{gottlieb_etal_2001} showed that standard strong-stability-preserving IMEX scheme cannot have an order higher than first without a restricted time step.
+Gottlieb et al.~\cite{gottlieb_etal_2001} showed that standard strong-stability-preserving IMEX schemes cannot have an order higher than first without a restricted time step.
 To have second-order (or higher-order) accuracy, some correction steps are needed.
@@
 It is being developed at the University of Tennessee, Knoxville and Oak Ridge National Laboratory.
-It currently solves the Euler equations for fluid dynamics and the two-moment approximation of the radiative transfer equation, both in the non-relativistic limit~\cite{endeve_etal_2018}.
+It currently includes solvers for the Euler equations for fluid dynamics and the two-moment approximation of the radiative transfer equation~\cite{endeve_etal_2018}.
+In this paper, we focus on the transport methods in \texttt{thornado} with emphasis on IMEX.
 
 This paper is organized as follows: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and the constraints on the moments and algebraic closures imposed by Fermi-Dirac statistics;
-Section~\ref{se:SpacialDiscretization} gives a first-order finite-volume spatial discretization and shows how the spatial discretization preserves constraints in an IMEX step;
+Section~\ref{se:SpatialDiscretization} gives a first-order finite-volume spatial discretization and shows how the spatial discretization preserves constraints in an IMEX step;
 Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct two PD-ARS schemes, one with second-order accuracy in the streaming limit and the other with third-order accuracy in the same limit;
-Section~\ref{se:NumericalTests} presents the results of the numerical tests, which demonstrate the properties of the PD-ARS schemes; Section~\ref{se:Conclusion} summarizes the achievements of this paper and discusses future work.
-
-%\rc{Reference check}
+Section~\ref{se:NumericalTests} presents the results of the numerical tests, which demonstrate the properties of the PD-ARS schemes; Section~\ref{se:Summary} summarizes the achievements of this paper and discusses future work.

### 2019-02-01 Documents/M1/Astronum_2018/sections/Conclusion.tex
Work on Astronum paper.

@@
 Since the realizable domain is convex and its convexity can be inherited by a convex combination, a scheme having convex combinations as its stages can preserve the realizable domain.
-This encouraged us to construct realizability-preserving time integrators, realizability-preserving IMEX schemes, and eventually a method with a realizability-preserving IMEX time integrator and high-order DG method.
+This encouraged us to construct realizability-preserving time integrators, realizability-preserving IMEX schemes, and a method with a realizability-preserving IMEX time integrator and high-order DG method.
 
@@
 As a result, we employed the Cernohorsky \& Bludman closure for the neutrino stationary state test in Section~\ref{se: Neutrino Stationary State Test}.
-(We also ran the code with other algebraic closures.
-And the program crashed after a few time steps because of the nonphysical neutrino density/flux obtained and no correction step was taken for $f>1$.
-We could make the code run by adding correction step, but the quality of the results may be compromised.
-And it's difficult to determine whether the results are in fact compromised by a particular correction step and, if so, in what way and to what degree.)
+We also ran our code with Minerbo closure, IMEX PC2, IMEX SSP2332 and IMEXRKCB2 schemes.
+And the results show that only PD-ARS schemes have stability.
+In addition, closures have impact on the simulation result.
+Even though RKCB2 with Minerbo closure luckily survived in our test, the result it gives is compromised.
+In what way and what degree the results are in fact compromised either by the closure or by a particular correction step for unrealizable moments are difficult to determine and left for further study.
 
@@
 The neutrino transport test with emission, absorption, and isoenergetic scattering through a stationary background, was designed to test the convex-invariance of our PD-ARS schemes. 
-The neutrino stationary state test shows that a method combining an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration can be a candidate for constructing a CCSN simulation code without ``unphysical correction steps" that may break conservation laws.
+The neutrino stationary state test shows that a method combining an algebraic closure based on Fermi-Dirac statistics and convex-invariant time integration is promising for robust CCSN simulation.
 
-In this work, we adopted Cartesian coordinates, a linear collision term, and a fixed non-relativistic material background.
+In this work, we adopted Cartesian coordinates, a linear collision term, and a fixed material background.
 More realistic problems of scientific interest, such as with energy-exchanging scattering and relativistic effects, are left for future research.

### 2019-02-01 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Work on Astronum paper.

@@
 Considering the fact that the completed collision term contains blocking factors, i.e.~$(1-\cJ)\times$ something positive, $\cJ > 1$ would change blocking factors' sign and it would be difficult to predict the impact of the subsequent induced errors on the simulation outcome.
-\rc{Besides, even with the simplified collision term, Eq~\ref{eq:collisionTermMoments}, $\cJ>1$ could result... the reason of crash}
+Besides, even with the simplified collision term Eq~\ref{eq:collisionTermMoments}, $\cJ>1$ could result information lose (such as, lose the neutrino distribution for high-energy groups), closure failure, and other unpredictable consequences.
 If treatments are developed to map the unrealizable moments into the realizable domain, they should be developed to conserve lepton number, energy, and momentum.

### 2019-02-01 Documents/M1/Astronum_2018/sections/intro.tex

@@
 One essential part of the explosion mechanism is neutrino transport.
-Neutrino energy deposition is believed to be the major driver of CCSN explosions, -- except in cases where rapid rotation is present and magnetohydrodynamic effects may dominate (for reviews, see~\cite{mezzacappa_2005,janka_2012,burrows_2013,muller_2016}).
+Neutrino energy deposition is believed to be the major driver of CCSN explosions, -- except in peculiar cases where rapid rotation is present and magnetohydrodynamic effects may dominate (for reviews, see~\cite{mezzacappa_2005,janka_2012,burrows_2013,muller_2016}).
 Ideally, neutrino transport would be modeled by the Boltzmann transport equation, which is an integro-partial-differential equation evolving a phase-space distribution function $f$.~(e.g., see~\cite{mezzacappaBruenn_1993a,mezzacappaBruenn_1993b,mezzacappaBruenn_1993c,mezzacappa_etal_2001,liebendoerfer_etal_2001,liebendoerfer_etal_2004,livne_etal_2004,liebendoerfer_etal_2005,ott_etal_2008,sumiyoshiYamada_2012,nagakura_etal_2014,sumiyoshi_etal_2014,nagakura_etal_2018} for studies of CCSN with Boltzmann transport in various approximate settings.)
@@
 Using the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$ -- the spectral particle density $\cJ$ and flux $\bcH$, respectively.
-However, the transport term in the Boltzmann transport equation includes the dot product of the velocity vector and the gradient of the phase-space distribution function.
-Integrating this term with a unit direction vector as the weight function couples the moment equations: it introduces the second angular moment $\bcK$ to the first moment $\bcH$'s equation.
+However, the equation of $\bcH$ includes the second angular moment $\bcK$.
 Knowledge of $\bcK$ is needed to close the two-moment system.
@@
 Gottlieb et al.~\cite{gottlieb_etal_2001} showed that standard strong-stability-preserving IMEX schemes cannot have an order higher than first without a restricted time step.
-To have second-order (or higher-order) accuracy, some correction steps are needed.
+One way to obtain the second-order (or higher-order) accuracy is to add some correction steps after the standard step~\cite{huangShu_2017,hu_etal_2018}.
 Unfortunately, the correction steps can deteriorate the accuracy of the IMEX scheme in the diffusion limit or restrict the time step.

### 2019-02-04 Documents/M1/Astronum_2018/sections/Numerical.tex

@@
 We use 10 energy groups to cover the range from 0~MeV to 300~MeV and initialize the neutrino number density to $\cJ = 10^{-99}$, flux density $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).
-For this test, we employed the CB closure.  
-We attempted to run this test with our PD-ARS schemes, SSP2332 from~\cite{pareschiRusso_2005}, IMEXRKCB2 proposed by Cavaglieri \& Bewley~\cite{cavaglieriBewley2015}, and the scheme proposed by McClarren et al.~\cite{mcclarren_etal_2008}.
-Only the PD-ARS schemes produce realizable moments and are able to evolve to a steady state.
-The other schemes crashed after a few time steps, when moments became non-realizable and the closure procedure failed.
+For this test, we employed both CB and Minerbo closures.  
+We attempted to run this test with our PD-ARS schemes, SSP2332 from~\cite{pareschiRusso_2005}, IMEXRKCB2 proposed by Cavaglieri \& Bewley~\cite{cavaglieriBewley2015}, and the IMEX PC2 scheme proposed by McClarren et al.~\cite{mcclarren_etal_2008}.
+Only the PD-ARS schemes produce realizable moments and are able to evolve to a steady state with either CB or Minerbo closure.
+SSP2332 and IMEX PC2 failed after a few time step with neither CB or Minerbo closure because of unrealizable moment.
+Even though IMEXRKCB2 with Minerbo closure can run and reach a steady state in this test, its results are different from that of PD-ARS schemes with CB closure and there is no guarantee for its stability.
+%It's difficult to determine whether the results are in fact compromised by a particular correction step and, if so, in what way and to what degree.
 
@@
 The figures show that all the states in the simulation with the PD-ARS schemes are realizable.
-In the middle column, we can see how the neutrinos are generated near the core, stream out, and reach an equilibrium distribution over the phase space eventually.
-In the right column, we can see how the scattering reshapes the flux direction. 
-The oscillatory behavior, which is more obvious for high-energy groups, is caused by machine accuracy error.
+In the middle and right column, we can see how the neutrinos are generated near the core, stream out, and reach an equilibrium distribution over the phase space eventually.
+The oscillation in the right column is caused by numerical error.
+%can see how the scattering reshapes the flux direction. 
+%The oscillatory behavior, which is more obvious for high-energy groups, is due to numerical error.
+%by the oscillatory in $|\bcH|$ as a result of scattering: scattering changes neutrino's direction and brings randomness to $|\bcH|$.  
+%High-energy groups can gain more randomness due to machine accuracy error.
 

### 2019-02-12 Documents/M1/Astronum_2018/manuscript.tex
Work on Astronum 2018

@@
 A finite-volume/first-order discontinuous Galerkin(DG) method is used to illustrate how an algebraic moment closure based on Fermi-Dirac statistics is needed to satisfy the bounds.
-Several algebraic closures are compared with these bounds in mind and the Cernohorsky and Bludman closure, which satisfies the bounds, is chosen for our IMEX schemes.
+Several algebraic closures are compared with these bounds in mind, and the Cernohorsky and Bludman closure, which satisfies the bounds, is chosen for our IMEX schemes.
 For the convex-invariant time integrator, two IMEX schemes named PD-ARS have been proposed.

### 2019-02-14 Documents/M1/Astronum_2018/sections/TimeIntegration.tex

@@
 
-Since the set of realizable moments is convex, convex-invariant schemes, which maps the initial value remains in its domain, can be used to design realizability-preserving methods for the two-moment model.
+Since the set of realizable moments is convex, convex-invariant schemes, which map the initial values into this set, can be used to design realizability-preserving methods for the two-moment model.
 Ideally, the scheme should also be high-order accurate and work well in the asymptotic diffusion limit (characterized by frequent collisions and long time scales).  
@@
 If the IMEX scheme is GSA, $\vect{u}^{n+1} = \vect{u}^{(s)}$.  
-Moreover, if $c_{ij},\tilde{c}_{ij}\ge0$ and $a_{ii}>0$, each stage in Eq.~\eqref{eq:imexStagesRewrite} is a convex combination of explicit Euler steps (with time step $\hat{c}_{ij}\dt$), followed by a implicit Euler step.
+Moreover, if $c_{ij},\tilde{c}_{ij}\ge0$ and $a_{ii}>0$, each stage in Eq.~\eqref{eq:imexStagesRewrite} is a convex combination of explicit Euler steps (with time step $\hat{c}_{ij}\dt$), followed by an implicit Euler step.
 Each of the explicit Euler steps has a time step condition that ensures its realizability given by $\hat{c}_{ij}\,\dt\leq\dx$; the CFL condition of the scheme.
@@
 Accuracy in the diffusion limit is another important property to consider when an IMEX scheme is applied to the two-moment model.  
-In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$, and the two-moment model is approximately governed by (e.g., \cite{jinLevermore_1996})
+In the diffusion limit, the distribution function is nearly isotropic, so $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$, and the two-moment model is approximately governed by (e.g., \cite{jinLevermore_1996})
 \begin{equation}
@@
     And $c_{\Sch} \leq 1$.)
-    \item Have less than five stages ($s\le4$)\label{cod:statges}.
+    \item Having less than five stages ($s\le4$)\label{cod:statges}.
     \item Are globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. 
@@
 (The constraint in \eqref{cod:statges} is introduced from efficiency considerations to limit the number of implicit solves.)
-We call the IMEX schemes satisfying the above conditions {PD-ARS} (see also Definition~3 in~\cite{chu_etal_2018}), and we provide two optimal PD-ARS schemes below: PD-ARS2 and PD-ARS3, each limits to the optimal second-order and third-order SSPRK schemes from~\cite{shuOsher_1988}, respectively.
+We call the IMEX schemes satisfying the above conditions {PD-ARS} (see also Definition~3 in~\cite{chu_etal_2018}), and we provide two optimal PD-ARS schemes below: PD-ARS2 and PD-ARS3, each limiting to the optimal second-order and third-order SSPRK schemes from~\cite{shuOsher_1988}, respectively.
 \subsubsection{PD-ARS2}
 
-The optimal 3-statge PD-ARS, PD-ARS2, in the standard double Butcher tableau form, with explicit tableau ($\tilde{A}$) on the left and implicit tableau ($A$) on the right, is given by
+The optimal 3-stage PD-ARS, PD-ARS2, in the standard double Butcher tableau form, with explicit tableau ($\tilde{A}$) on the left and implicit tableau ($A$) on the right, is given by
 \begin{align}
@@
 This scheme requires three implicit solves per time step, and $c_{\Sch}= 1$.  
-Since PD-ARS3 is not more accurate than PD-ARS2 in collision dominated regions (see our results in Section~\ref{se:NumericalTests}), it may not offer any practical advantage over PD-ARS2.
+Since PD-ARS3 is not more accurate than PD-ARS2 in collision-dominated regions (see our results in Section~\ref{se:NumericalTests}), it may not offer any practical advantage over PD-ARS2.

### 2019-02-15 Documents/M1/Astronum_2018/sections/TwoMoments.tex

@@
 The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} deserve further attention.  
-They are important as those in Eq.~\eqref{eq:MomentsBounds}, in maintaining consistency of the two-moment model with respect to Fermi-Dirac statistics.  
+They are as important as those in Eq.~\eqref{eq:MomentsBounds}, in maintaining consistency of the two-moment model with respect to Fermi-Dirac statistics.  
 When designing a numerical scheme for the two-moment model that maintains realizable $\bcM$, it is also necessary for the Eddington factor to satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.
@@
 As examples, we consider the Eddington factors discussed in~\cite{murchikova_etal_2017}, where the suitability of several algebraic closures for two-moment neutrino transport was evaluated.  
-In Fig.~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor versus the flux factor for two occupancies; $\cJ = 0.1$ (low occupancy) and $\cJ = 0.9$ (high occupancy).  
+In Fig.~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor versus the flux factor for two occupancies: $\cJ = 0.1$ (low occupancy) and $\cJ = 0.9$ (high occupancy).  
 Of the algebraic closures plotted, few satisfy the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds}.  
@@
 If this were to happen, the update step may give $\cJ>1$.
-Considering the fact that the completed collision term contains blocking factors, i.e.~$(1-\cJ)\times$ something positive, $\cJ > 1$ would change blocking factors' sign and it would be difficult to predict the impact of the subsequent induced errors on the simulation outcome.
-Besides, even with the simplified collision term Eq~\ref{eq:collisionTermMoments}, $\cJ>1$ could result information lose (such as, lose the neutrino distribution for high-energy groups), closure failure, and other unpredictable consequences.
+Considering the fact that the collision term contains blocking factors --- i.e.~$(1-\cJ)\times$ something positive --- $\cJ > 1$ would change the blocking factors' sign, and it would be difficult to predict the impact of the subsequent induced errors on the simulation outcome.
+Besides, even with the simplified collision term Eq~\ref{eq:collisionTermMoments}, $\cJ>1$ could result in information loss (such as loss to the neutrino distribution for the group that exceed the bounds), closure failure, and other unpredictable consequences.
 If treatments are developed to map the unrealizable moments into the realizable domain, they should be developed to conserve lepton number, energy, and momentum.

### 2019-02-15 Documents/M1/Astronum_2018/sections/Acknowledge.tex

@@
 
-This research is sponsored, in part, by the Laboratory Directed Research and Development Program of Oak Ridge National Laboratory (ORNL), managed by UT-Battelle, LLC for the U.
-S.
+This research is sponsored, in part, by the Laboratory Directed Research and Development Program of Oak Ridge National Laboratory (ORNL), managed by UT-Battelle, LLC for the U.S.
 Department of Energy under Contract No.
 De-AC05-00OR22725.
-This material is based, in part, upon work supported by the U.S.
+This material is based, in part, on work supported by the U.S.
 Department of Energy, Office of Science, Office of Advanced Scientific Computing Research.
 This research was also supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of the U.S.
-Department of Energy Office of Science and the National Nuclear Security Administration, and by the National Science Foundation Gravitational Physics Program (NSF-GP 1505933 and 1806692).
+Department of Energy Office of Science and the National Nuclear Security Administration, and by the National Science Foundation Gravitational Physics Program (NSF-GP 1806692).

### 2019-02-15 Documents/M1/Astronum_2018/sections/Conclusion.tex

@@
 As a result, we employed the Cernohorsky \& Bludman closure for the neutrino stationary state test in Section~\ref{se: Neutrino Stationary State Test}.
-We also ran our code with Minerbo closure, IMEX PC2, IMEX SSP2332 and IMEXRKCB2 schemes.
-And the results show that only PD-ARS schemes have stability.
+We also ran our code with Minerbo closure, IMEX PC2, IMEX SSP2332 and IMEXRKCB2 schemes, and the results show that only PD-ARS schemes have stability.
 In addition, closures have impact on the simulation result.
-Even though RKCB2 with Minerbo closure luckily survived in our test, the result it gives is compromised.
-In what way and what degree the results are in fact compromised either by the closure or by a particular correction step for unrealizable moments are difficult to determine and left for further study.
+As we observed, both using PD-ARS scheme, there are $\sim30\%$ difference in the neutrino number densities (and relaxation time) between the results obtained with Minerbo closure and that with CB closure.
+Even though RKCB2 with Minerbo closure luckily survived our test, the results it gave were compromised: closer to PD-ARS scheme with Minerbo closure other than PD-ARS scheme with CB closure.
+In what way and to what degree the results are in fact compromised either by the closure or by a particular correction step for unrealizable moments are difficult to determine fully and is left for further study.
 

### 2019-02-15 Documents/M1/Astronum_2018/sections/Numerical.tex

@@
 Among the second-order schemes, SSP2332 has the smallest error.
-In the streaming limit, the PD-ARS schemes reduce to SSPRK schemes, such that PD-ARS2 to SSPRK2 and PD-ARS3 to SSPRK3, respectively.
+In the streaming limit, the PD-ARS schemes reduce to SSPRK schemes --- PD-ARS2 to SSPRK2 and PD-ARS3 to SSPRK3, respectively.
 Therefore, the absolute errors of PD-ARS schemes and SSPRK schemes are indistinguishable.
@@
 For $\sigma_{\Ab}=0.1$, PD-ARS2 is the most accurate scheme for $N=8$ and $N=16$. 
-We have seen the same behavior for the scheme proposed by McClarren et al.~\cite{mcclarren_etal_2008} (PC2) in~\cite{chu_etal_2018}.
-Since these are special cases for $N=8$ and $N=16$, we won't recommend PD-ARS2 instead of SSP2332 for the damping problem.
+We have seen the same behavior for the scheme proposed by McClarren et al.~\cite{mcclarren_etal_2008} (PC2 in~\cite{chu_etal_2018}).
+Since these are special cases for $N=8$ and $N=16$, we do not recommend PD-ARS2 instead of SSP2332 for the damping problem.
 Only SSP2332, a second-order accurate scheme, displays a second-order convergence rate.  
@@
 
-The final test with known smooth solution, adopted from~\cite{radice_etal_2013}, is the sine wave diffusion test; i.e. $\sigma_{\Ab} = 0$ and $f_0 = 0$.
+The final test with known smooth solutions, adopted from~\cite{radice_etal_2013}, is the sine wave diffusion test; i.e. $\sigma_{\Ab} = 0$ and $f_0 = 0$.
 A periodic domain $D=\{x:x\in[-3,3]\}$ with initial conditions $\cJ_{0} = 0.5+0.49\times\sin\big(\f{\pi\,x}{3}\big)$ and $\cH_{0} =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}$ are used.  
@@
 This test is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction, a reflecting inner boundary and a homogeneous out-flowing outer boundary.
-We use 10 energy groups to cover the range from 0~MeV to 300~MeV and initialize the neutrino number density to $\cJ = 10^{-99}$, flux density $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).
+We use 10 energy groups to cover the range from 0~MeV to 300~MeV and initialize the neutrino number density to $\cJ = 10^{-99}$, flux density to $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).
 For this test, we employed both CB and Minerbo closures.  
@@
 Only the PD-ARS schemes produce realizable moments and are able to evolve to a steady state with either CB or Minerbo closure.
-SSP2332 and IMEX PC2 failed after a few time step with neither CB or Minerbo closure because of unrealizable moment.
-Even though IMEXRKCB2 with Minerbo closure can run and reach a steady state in this test, its results are different from that of PD-ARS schemes with CB closure and there is no guarantee for its stability.
+SSP2332 and IMEX PC2 failed after a few time steps with either CB or Minerbo closure because of the development of unrealizable moments.
+Even though IMEXRKCB2 with Minerbo closure can run and reach a steady state in this test, its results are different from that of PD-ARS schemes with CB closure, and there is no guarantee of stability.
 %It's difficult to determine whether the results are in fact compromised by a particular correction step and, if so, in what way and to what degree.
@@
 The figures show that all the states in the simulation with the PD-ARS schemes are realizable.
-In the middle and right column, we can see how the neutrinos are generated near the core, stream out, and reach an equilibrium distribution over the phase space eventually.
+In the middle and right column, we can see how the neutrinos are generated near the core, stream out, and eventually reach an equilibrium distribution over the phase space.
 The oscillation in the right column is caused by numerical error.

### 2019-02-15 Documents/M1/Astronum_2018/sections/intro.tex

@@
 One essential part of the explosion mechanism is neutrino transport.
-Neutrino energy deposition is believed to be the major driver of CCSN explosions, -- except in peculiar cases where rapid rotation is present and magnetohydrodynamic effects may dominate (for reviews, see~\cite{mezzacappa_2005,janka_2012,burrows_2013,muller_2016}).
-Ideally, neutrino transport would be modeled by the Boltzmann transport equation, which is an integro-partial-differential equation evolving a phase-space distribution function $f$.~(e.g., see~\cite{mezzacappaBruenn_1993a,mezzacappaBruenn_1993b,mezzacappaBruenn_1993c,mezzacappa_etal_2001,liebendoerfer_etal_2001,liebendoerfer_etal_2004,livne_etal_2004,liebendoerfer_etal_2005,ott_etal_2008,sumiyoshiYamada_2012,nagakura_etal_2014,sumiyoshi_etal_2014,nagakura_etal_2018} for studies of CCSN with Boltzmann transport in various approximate settings.)
+Neutrino energy deposition is believed to be the major driver of CCSN explosions, except in peculiar cases where rapid rotation is present and magnetohydrodynamic effects may dominate (for reviews, see~\cite{mezzacappa_2005,janka_2012,burrows_2013,muller_2016}).
+Ideally, neutrino transport would be modeled by the Boltzmann transport equation, which is an integro-partial-differential equation evolving a phase-space distribution function $f$~(e.g., see~\cite{mezzacappaBruenn_1993a,mezzacappaBruenn_1993b,mezzacappaBruenn_1993c,mezzacappa_etal_2001,liebendoerfer_etal_2001,liebendoerfer_etal_2004,livne_etal_2004,liebendoerfer_etal_2005,ott_etal_2008,sumiyoshiYamada_2012,nagakura_etal_2014,sumiyoshi_etal_2014,nagakura_etal_2018} for studies of CCSN with Boltzmann transport in various approximate settings).
 Simulating the neutrino transport implies finding a solution of the Boltzmann equation for a specific domain and period, with acceptable accuracy.
@@
 Therefore, a closure that gives $\bcK$ consistent with $\cJ$ and $\bcH$ is needed.
-The better the closure predicts $\bcK$, the more accurate the two-moment method. 
+The better the closure predicts $\bcK$, the more accurate the two-moment method will be. 
 The two-moment method has been widely applied in the CCSN modeling community with different algebraic closures, such as the Minerbo~\cite{minerbo_1978} closure (e.g.~{O'Connor} and {Couch}~\cite{oConnorCouch_2018}, Pan and et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018}) and the Levermore~\cite{levermore_1984} closure (e.g.~Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016}).
@@
 Applying the two-moment method does simplify the problem, but doesn't guarantee an affordable solution.
-To be precise, how to discretize the continuous equation of system given by the two-moment method and solve the discretized system efficiently remains a question.
-In fact, the time scales of neutrino interactions with the background (can be $\sim\mathcal{O}(10^{-13})$~second) is short compared to the duration of the CCSN explosion ($\sim\mathcal{O}(1)$~second).
-This means that $\sim\mathcal{O}(10^{13})$ time steps would be needed for solving the system fully explicitly. 
+To be precise, how to discretize the continuous system of equation given by the two-moment method and solve the discretized system efficiently remains a question.
+In fact, the time scales of neutrino interactions with the background (they can be $\sim\mathcal{O}(10^{-13})$~second) is short compared to the duration of the CCSN explosion ($\sim\mathcal{O}(1)$~second).
+This means that $\sim\mathcal{O}(10^{13})$ time steps could be needed for solving the system fully explicitly. 
 On the other hand, solving the moment equations fully implicitly requires inverting global band-structured matrices whose sizes depend on the phase-space discretization.
@@
 Therefore, IMEX methods require far fewer time steps compared with a fully explicit method, and the computation for each step is easily parallelizable.
-For the relativistic setting that we have, where the fluid and the neutrinos have comparable propagation speeds, and IMEX methods can be efficient.
+For the relativistic setting that we have, where the fluid and the neutrinos have comparable propagation speeds, IMEX methods can be efficient.
 
 To model neutrino transport using a two-moment method, two (or at least two) things need to be chosen carefully: an algebraic closure based on Fermi-Dirac statistics for closing the two-moment equations and a convex-invariant, diffusion-accurate IMEX scheme to ensure a physical result.
-A convex-invariant scheme has the following property: if the solution $u^{n}\in W$ and $W$ is convex, then $u^{n+1}\in W$.
+A convex-invariant scheme has the following property: if the solution $u^{n}\in W$ and $W$ is a convex set, then $u^{n+1}\in W$.
 Since the neutrino distribution function is bounded ($f\in[0,1]$) by the Pauli exclusion principle, its moments as weighted integrals of a bounded function over the domain $\omega\in\bbS^{2}$ are also bounded.
@@
 The algebraic closure should give a realizable $\bcK$, and the well-posedness of the closure requires realizable $\cJ$ and $\bcH$.
-It explains why an algebraic closure based on Fermi-Dirac statistics is needed.
+This explains why an algebraic closure based on Fermi-Dirac statistics is needed.
 Realizability of $\cJ$ and $\bcH$ after each time step requires a convex-invariant IMEX scheme.

### 2019-03-05 Documents/M1/Astronum_2018/sections/Conclusion.tex

@@
 As we observed, both using PD-ARS scheme, there are $\sim30\%$ difference in the neutrino number densities (and relaxation time) between the results obtained with Minerbo closure and that with CB closure.
-Even though RKCB2 with Minerbo closure luckily survived our test, the results it gave were compromised: closer to PD-ARS scheme with Minerbo closure other than PD-ARS scheme with CB closure.
+Even though RKCB2 with Minerbo closure luckily survived our test, the results it gave were compromised: they were closer to the results of the PD-ARS scheme with Minerbo closure than to the results of the PD-ARS scheme with CB closure.
 In what way and to what degree the results are in fact compromised either by the closure or by a particular correction step for unrealizable moments are difficult to determine fully and is left for further study.

### 2019-03-05 Documents/M1/Astronum_2018/sections/TwoMoments.tex

@@
 To close the two-moment model, we consider algebraic closures.  
-For the two-moment model, algebraic closures give an approximation to $\bcK$ using the lower moments.  
-Write
+For the two-moment model, algebraic closures give an approximation to $\bcK$ using the lower moments:
 \begin{equation}
@@
 Considering the fact that the collision term contains blocking factors --- i.e.~$(1-\cJ)\times$ something positive --- $\cJ > 1$ would change the blocking factors' sign, and it would be difficult to predict the impact of the subsequent induced errors on the simulation outcome.
-Besides, even with the simplified collision term Eq~\ref{eq:collisionTermMoments}, $\cJ>1$ could result in information loss (such as loss to the neutrino distribution for the group that exceed the bounds), closure failure, and other unpredictable consequences.
+Besides, even with the simplified collision term Eq~\ref{eq:collisionTermMoments}, $\cJ>1$ could result in information loss (such as loss to the neutrino distribution for the groups that exceed the bounds), closure failure, and other unpredictable consequences.
 If treatments are developed to map the unrealizable moments into the realizable domain, they should be developed to conserve lepton number, energy, and momentum.

### 2019-03-14 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex

@@
 \end{equation}
-For multidimensional problems, the Kershaw closure is obtained by using the Eddington factor in Eq.~\eqref{eq:eddingtonFactorKershaw} in Eq.~\eqref{eq:eddingtonTensor}.  
+\modified{For multidimensional problems, the Kershaw closure is obtained by inserting the Eddington factor $\chi_{\mbox{\tiny K}}$ in Eq.~\eqref{eq:eddingtonFactorKershaw} into the Eddington tensor in Eq.~\eqref{eq:eddingtonTensor}.}
 Finally, we point out that for the two-moment Kershaw closure (see \cite{banachLarecki_2017a} for details), a distribution function $f_{\mbox{\tiny K}}(\omega,\cJ,\vect{\cH})$, satisfying $0 < f_{\mbox{\tiny K}} < 1$, and reproducing the moments $\cJ$, $\vect{\cH}$, and $\vect{\cK}$, can be written explicitly in terms of Heaviside functions.

### 2019-03-19 Documents/M1/Astronum_2018/sections/Numerical.tex

@@
 This test is designed to test the realizability-preserving properties of the PD-ARS schemes.  
-Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities used (adopted from~\cite{Bruenn_1985}).  
-This test is computed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction, a reflecting inner boundary and a homogeneous out-flowing outer boundary.
-We use 10 energy groups to cover the range from 0~MeV to 300~MeV and initialize the neutrino number density to $\cJ = 10^{-99}$, flux density to $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).
+Figure~\ref{fig:NeutrinoStationaryTestEOS} left plots the initial thermal state: 
+\begin{subequations}
+\begin{align}
+\text{Density: }~\rho & = 4 \times 10^{14} \times \dfrac{7.5}{( 7.5 + ( r / 5 )^4 )} ~\text{g $\cdot$ cm$^{-3}$}\\
+\text{Temperature: }~T & = 1.5 \times 10^{11} \times \dfrac{1}{1 + ( r / 50 )^2 } ~\text{K}\\
+\text{Electron Fraction: }~Y_e & = 0.25 \times \left(  1 + \dfrac{1}{1+ ( r / 50 )^{-12}}  \right) 
+\end{align}
+\label{eq:NuStatinaryStateEOS}
+\end{subequations}
+with radius $r$ in kilometer unit. 
+Eq.~\eqref{eq:NuStatinaryStateEOS} is designed to simulate a CCSN progenitor.
+Figure~\ref{fig:NeutrinoStationaryTestEOS} right plots the used opacities which are provided by interpolations of a pre-calculated opacity table based on~\cite{Bruenn_1985}.
+This test is computed on Cartesian coordinate with a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ in kilometer unit, a grid of 128 elements in each direction, 10 energy groups covering $(0,300)$~MeV, a reflecting inner boundary and a homogeneous out-flowing outer boundary.
+Because of the Cartesian coordinate, we ignored some geometric terms, which leads the initial condition to be non-axisymmetric.
+We initialize the neutrino number density to $\cJ = 10^{-99}$, flux density to $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).
+No hydrodynamics is used for the stationary background.
 For this test, we employed both CB and Minerbo closures.  

### 2019-03-19 Documents/M1/Astronum_2018/sections/TimeIntegration.tex

@@
 where $(\tilde{a}_{ij})$ and $(a_{ij})$, coefficients of the $i$-th stage, are elements of matrices $\tilde{A}$ and $A$, respectively.
-The matrices $\tilde{A}$ and $A$ are lower triangular ($\tilde{A}$ is strictly lower triangular so that the transport part is explicit).  
+The matrices $\tilde{A}$ and $A$ are lower triangular.
+($\tilde{A}$ is strictly lower triangular so that the transport part is explicit.)  
 The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weights in the assembly step in Eq.~\eqref{imexIntermediate}.

### 2019-03-19 Documents/M1/Astronum_2018/sections/TwoMoments.tex

@@
 \subsection{Transport Equations}
-We consider neutrino transport through a static background, and include neutrino-matter interactions due to emission, absorption, and isoenergetic scattering.
+We consider neutrino transport through a static background under the Newtonian framework.
+We include neutrino-matter interactions due to emission, absorption, and isoenergetic scattering, which dominate the opacity under the physical conditions that we're interested in.
+It's possible to include other interactions, such as neutrino-electron scattering and neutrino pair production, in the two-moment model.
+But involving those interactions complicates the collision term and requires more efforts in proving the realizability of a scheme.
+We leave it for future work.
 After scaling to dimensionless units, the Boltzmann equation can be written as
@@
 where $h = |\bcH|/\cJ$ is the flux factor.
+These relationships hold for moment in the comoving frame.
+Similar relationships can be derived in the laboratory frame, which we leave for future work.
 

### 2019-03-19 Documents/M1/Astronum_2018/sections/intro.tex

@@
 Applying the two-moment method does simplify the problem, but doesn't guarantee an affordable solution.
-To be precise, how to discretize the continuous system of equation given by the two-moment method and solve the discretized system efficiently remains a question.
+To be precise, how to discretize the continuous system of equatio
+ns given by the two-moment method and solve the discretized system efficiently remains a question.
 In fact, the time scales of neutrino interactions with the background (they can be $\sim\mathcal{O}(10^{-13})$~second) is short compared to the duration of the CCSN explosion ($\sim\mathcal{O}(1)$~second).

### 2019-03-26 Documents/M1/Astronum_2018/sections/Numerical.tex

@@
 In the middle and right column, we can see how the neutrinos are generated near the core, stream out, and eventually reach an equilibrium distribution over the phase space.
-The oscillation in the right column is caused by numerical error.
-%can see how the scattering reshapes the flux direction. 
-%The oscillatory behavior, which is more obvious for high-energy groups, is due to numerical error.
-%by the oscillatory in $|\bcH|$ as a result of scattering: scattering changes neutrino's direction and brings randomness to $|\bcH|$.  
-%High-energy groups can gain more randomness due to machine accuracy error.
+The oscillation in the right column is caused by the oscillation in the numerical flux $|\vect{\cH}|$.
+Parts of the causes can be the numerical error and the non-axisymmetric boundary condition.
+We should also note that no flux limiter is used in this test.
+The oscillation can be the spurious oscillations that occur due to discontinuities in the solution domain.
+We leave these for our future study.
 

### 2019-03-29 Documents/M1/Astronum_2018/sections/Numerical.tex
Workin on revisions for Astronum

@@
 In this section we consider a more ``realistic'' test: two-dimensional multigroup neutrino transport with emission, absorption, and isoenergetic scattering through a stationary background.  
-This test is designed to test the realizability-preserving properties of the PD-ARS schemes.  
+\modified{This test is designed to test the realizability-preserving properties of the PD-ARS schemes.  
 Figure~\ref{fig:NeutrinoStationaryTestEOS} left plots the initial thermal state: 
@@
 This test is computed on Cartesian coordinate with a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ in kilometer unit, a grid of 128 elements in each direction, 10 energy groups covering $(0,300)$~MeV, a reflecting inner boundary and a homogeneous out-flowing outer boundary.
-Because of the Cartesian coordinate, we ignored some geometric terms, which leads the initial condition to be non-axisymmetric.
+Because of the Cartesian coordinate, we ignored some geometric terms, which leads the initial condition to be non-axisymmetric.}
 We initialize the neutrino number density to $\cJ = 10^{-99}$, flux density to $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).
@@
 In the middle and right column, we can see how the neutrinos are generated near the core, stream out, and eventually reach an equilibrium distribution over the phase space.
-The oscillation in the right column is caused by the oscillation in the numerical flux $|\vect{\cH}|$.
+\modified{The oscillation in the right column is caused by the oscillation in the numerical flux $|\vect{\cH}|$.
 Parts of the causes can be the numerical error and the non-axisymmetric boundary condition.
@@
 The oscillation can be the spurious oscillations that occur due to discontinuities in the solution domain.
-We leave these for our future study.
+We leave these for our future study.}
 

### 2019-03-29 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Workin on revisions for Astronum

--- 2019-03-05 Documents/M1/Astronum_2018/sections/TwoMoments.tex
@@
 \subsection{Transport Equations}
-We consider neutrino transport through a static background, and include neutrino-matter interactions due to emission, absorption, and isoenergetic scattering.
+\modified{We consider neutrino transport through a static background in a non-relativistic framework.  
+For simplicity, we only include neutrino-matter interactions due to emission, absorption, and isoenergetic scattering.  
+It is possible to include other interactions, such as neutrino-electron scattering and pair processes, in the two-moment model.  
+However, these interactions result in dense coupling across neutrino energies and across neutrino species, and we have not yet considered the realizability-preserving property of our scheme in this case.
+We leave this for future work.}
+
 After scaling to dimensionless units, the Boltzmann equation can be written as
@@
 where $h = |\bcH|/\cJ$ is the flux factor.
+\modified{The inequalities in Eqs.~\eqref{eq:MomentsBounds} and \eqref{eq:eddingtonFactorBounds} hold for moments as defined in Eq.~\eqref{eq:angularMoments} with $f\in[0,1]$.  
+In a relativistic model (e.g., \cite{shibata_etal_2011,cardall_etal_2013}), the evolved quantities --- functions of the moments in Eq.~\eqref{eq:angularMoments} --- satisfy different bounds.  
+We are currently exploring extensions of the realizability-preserving scheme presented here to the relativistic case.}
 

### 2019-03-29 Documents/M1/Astronum_2018/sections/Numerical.tex
More work on revision

@@
 \modified{This test is designed to test the realizability-preserving properties of the PD-ARS schemes.  
-Figure~\ref{fig:NeutrinoStationaryTestEOS} left plots the initial thermal state: 
+In the left panel in Figure~\ref{fig:NeutrinoStationaryTestEOS} we plot the thermal state of the background, which mimic a collapsed stellar core: 
 \begin{subequations}
   \begin{align}
-\text{Density: }~\rho & = 4 \times 10^{14} \times \dfrac{7.5}{( 7.5 + ( r / 5 )^4 )} ~\text{g $\cdot$ cm$^{-3}$}\\
-\text{Temperature: }~T & = 1.5 \times 10^{11} \times \dfrac{1}{1 + ( r / 50 )^2 } ~\text{K}\\
-\text{Electron Fraction: }~Y_e & = 0.25 \times \left(  1 + \dfrac{1}{1+ ( r / 50 )^{-12}}  \right) 
+    \text{Mass Density: }~\rho & = 4 \times 10^{14} \times \dfrac{7.5}{( 7.5 + ( r / 5~\mbox{km} )^4 )} ~\text{g~cm$^{-3}$}, \\
+    \text{Temperature: }~T & = 1.5 \times 10^{11} \times \dfrac{1}{1 + ( r / 50~\mbox{km} )^2 } ~\text{K}, \\
+    \text{Electron Fraction: }~Y_e & = 0.25 \times \left(  1 + \dfrac{1}{1+ ( r / 50~\mbox{km} )^{-12}}  \right), 
   \end{align}
@@
 \end{subequations}
-with radius $r$ in kilometer unit. 
-Eq.~\eqref{eq:NuStatinaryStateEOS} is designed to simulate a CCSN progenitor.
-Figure~\ref{fig:NeutrinoStationaryTestEOS} right plots the used opacities which are provided by interpolations of a pre-calculated opacity table based on~\cite{Bruenn_1985}.
-This test is computed on Cartesian coordinate with a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ in kilometer unit, a grid of 128 elements in each direction, 10 energy groups covering $(0,300)$~MeV, a reflecting inner boundary and a homogeneous out-flowing outer boundary.
-Because of the Cartesian coordinate, we ignored some geometric terms, which leads the initial condition to be non-axisymmetric.}
-We initialize the neutrino number density to $\cJ = 10^{-99}$, flux density to $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).
-No hydrodynamics is used for the stationary background.
+where the radius $r=\sqrt{(x^{1})^{2}+(x^{2})^{2}}$ is in kilometers.  
+In the right panel in Figure~\ref{fig:NeutrinoStationaryTestEOS} we plot the neutrino opacities, computed by interpolation of a pre-calculated opacity table based on~\cite{Bruenn_1985}.
+This test is computed using Cartesian coordinates on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200]~\mbox{km}, x^{2}\in[0,200]~\mbox{km}\}$, using a grid of 128 elements in each direction, 10 energy groups covering $0$-$300$~MeV, reflecting inner boundaries and outflow outer boundaries.
+Because we use Cartesian coordinates in two spatial dimensions, this problem has cylindrical geometry, and results in an artificial stratification of the radiation quantities.}
+We initialize the neutrino number density to $\cJ = 10^{-99}$, the number flux density to $\bcH=0$, and evolve until an approximate steady state is reached ($t=5$~ms).
+The background is kept fixed during the entire run.  
 For this test, we employed both CB and Minerbo closures.  
@@
 In the middle and right column, we can see how the neutrinos are generated near the core, stream out, and eventually reach an equilibrium distribution over the phase space.
-\modified{The oscillation in the right column is caused by the oscillation in the numerical flux $|\vect{\cH}|$.
-Parts of the causes can be the numerical error and the non-axisymmetric boundary condition.
-We should also note that no flux limiter is used in this test.
-The oscillation can be the spurious oscillations that occur due to discontinuities in the solution domain.
-We leave these for our future study.}
+\modified{The oscillations in the flux factor seen in the right columns are associated with steep gradients in the radiation field as the initial transient propagates through the computational domain.
+Note that we do not apply any limiters to prevent oscillations in the numerical solution, and these will likely go away when we implement slope limiters, e.g., as described in \cite{cockburnShu_1998}.
+The fact that we can still evolve the solution to a steady state speaks to the robustness of the scheme.}
 

### 2019-03-30 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Work on Astronum paper.

@@
 \modified{We consider neutrino transport through a static background in a non-relativistic framework.  
-For simplicity, we only include neutrino-matter interactions due to emission, absorption, and isoenergetic scattering.  
-It is possible to include other interactions, such as neutrino-electron scattering and pair processes, in the two-moment model.  
+For simplicity, we only include neutrino--matter interactions due to emission, absorption, and isoenergetic scattering.  
+It is possible to include other interactions, such as neutrino--electron scattering and pair processes, in the two-moment model.  
 However, these interactions result in dense coupling across neutrino energies and across neutrino species, and we have not yet considered the realizability-preserving property of our scheme in this case.

### 2019-04-02 Documents/M1/realizableFermionicM1/sections/realizability.tex

@@
 
-We begin with the following definition of moment realizability.  
+\modified{
+We let
+\begin{equation}
+  \mathfrak{R} := \left\{\,f~|~0\le f \le 1 ~\text{and}~0<\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omega<1\,\right\},
+\end{equation}
+and begin with the following definition of moment realizability.}  
 \begin{define}
-  The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they can be obtained from a distribution function satisfying $0 < f(\omega) < 1~\forall~\omega\in\bbS^{2}$.  
+  \modified{The moments $\vect{\cM}=\big(\cJ,\vect{\cH}\big)^{T}$ are realizable if they can be obtained from a distribution function $f(\omega)\in\mathfrak{R}$.}  
+  %satisfying $0 < f(\omega) < 1~\forall~\omega\in\bbS^{2}$.  
   The set of all realizable moments $\cR$ is
@@
 \end{rem}
+\modified{
+\begin{rem}
+  The conditions in Eq.~\eqref{eq:realizableSet} are necessary and sufficient for the moments to be realizable \cite[Theorem 7.1]{banachLarecki_2017a}.
+(See also \cite{lareckiBanach_2011,banachLarecki_2013}.)
+\end{rem}
+}
 
-The algebraic constraints in Eq.~\eqref{eq:realizableSet} are proven in \cite{banachLarecki_2017a} (see also \cite{lareckiBanach_2011,banachLarecki_2013}).  
+%The algebraic constraints in Eq.~\eqref{eq:realizableSet} are proven in \cite{banachLarecki_2017a}.  
 %\begin{lemma}

### 2019-04-29 Documents/M1/Astronum_2018/sections/Numerical.tex

@@
 \modified{This test is designed to test the realizability-preserving properties of the PD-ARS schemes.  
-In the left panel in Figure~\ref{fig:NeutrinoStationaryTestEOS} we plot the thermal state of the background, which mimic a collapsed stellar core: 
+In the left panel in Figure~\ref{fig:NeutrinoStationaryTestEOS} we plot the thermal state of the background, which mimics a collapsed stellar core: 
 \begin{subequations}
@@
 \end{subequations}
-where the radius $r=\sqrt{(x^{1})^{2}+(x^{2})^{2}}$ is in kilometers.  
-In the right panel in Figure~\ref{fig:NeutrinoStationaryTestEOS} we plot the neutrino opacities, computed by interpolation of a pre-calculated opacity table based on~\cite{Bruenn_1985}.
-This test is computed using Cartesian coordinates on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200]~\mbox{km}, x^{2}\in[0,200]~\mbox{km}\}$, using a grid of 128 elements in each direction, 10 energy groups covering $0$-$300$~MeV, reflecting inner boundaries and outflow outer boundaries.
+\hspace{-6pt}where the radius $r=\sqrt{(x^{1})^{2}+(x^{2})^{2}}$ is in kilometers.  
+In the right panel in Figure~\ref{fig:NeutrinoStationaryTestEOS} we plot the neutrino opacities, computed by interpolation in a pre-calculated opacity table based on~\cite{Bruenn_1985}.
+This test is computed using Cartesian coordinates on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200]~\mbox{km}, x^{2}\in[0,200]~\mbox{km}\}$, using a grid of 128 elements in each direction, 10 energy groups covering $0$-$300$~MeV, reflecting inner boundaries, and outflow outer boundaries.
 Because we use Cartesian coordinates in two spatial dimensions, this problem has cylindrical geometry, and results in an artificial stratification of the radiation quantities.}
@@
 \modified{The oscillations in the flux factor seen in the right columns are associated with steep gradients in the radiation field as the initial transient propagates through the computational domain.
-Note that we do not apply any limiters to prevent oscillations in the numerical solution, and these will likely go away when we implement slope limiters, e.g., as described in \cite{cockburnShu_1998}.
+Note that we do not apply any limiters to prevent oscillations in the numerical solution, and these will likely go away when we implement slope limiters; e.g., as described in \cite{cockburnShu_1998}.
 The fact that we can still evolve the solution to a steady state speaks to the robustness of the scheme.}

### 2019-06-11 Documents/Euler/ContactWaveSpeed_Relativistic/ContactWaveSpeed_Relativistic.tex

@@
 \begin{document}
+Throughout this document, lowercase latin indices ($i,j,$ etc.) run from 1 to 3, lowercase Greek indices ($\mu,\nu,$ etc.) run from 0 to 3, and uppercase latin indices ($J$) run from 1 to 5.
+
+\section{Equations}
+We are solving the general relativistic hydrodynamics (GRH) equations \citep{RezzollaRelHyd}:
+\begin{equation}\label{Eq:GRH}
+\pd{\left(\sqrt{\gamma}\,\bU\right)}{t}+\pd{\left(\alpha\,\sqrt{\gamma}\,\bF^{i}\right)}{i}=\sqrt{\gamma}\,\bS,
+\end{equation}
+where $\bU$ is the vector of conserved variables, defined as
+\begin{equation}
+\bU\longrightarrow U^{J}=\begin{pmatrix}D\\ S_{j}\\ E\end{pmatrix}=\begin{pmatrix}\rho\,W\\ \rho\,h\,W^{2}\,v_{j}\\\rho\,h\,W^{2}-p\end{pmatrix},
+\end{equation}
+$\bF^{i}$ is the vector of fluxes of the conserved variables in the $x^{i}$-direction, defined as
+\begin{equation}
+\bF^{i}\longrightarrow \left(F^{i}\right)^{J}=\begin{pmatrix}D\left(v^{i}-\eta^{i}\right)\\ S_{j}\left(v^{i}-\eta^{i}\right)+p\,\delta^{i}_{~j}\\S^{i}-\eta^{i}\,E\end{pmatrix},
+\end{equation}
+$\bS$ is the vector of sources, defined as
+\begin{equation}
+\bS\longrightarrow S^{J}=\begin{pmatrix}0\\\frac{1}{2}\,\alpha\,P^{ik}\,\pd{\gamma_{ik}}{j}+S_{i}\,\pd{\beta^{i}}{j}-E\,\pd{\alpha}{j}\\\alpha\,P^{ij}\,K_{ij}-S^{j}\,\pd{\alpha}{j}\end{pmatrix},
+\end{equation}
+where $\rho$ is the mass-density of the fluid, $v^{i}$ are the contravariant components of the fluid three-velocity, and $p$ is the pressure of the fluid.
+The quantity $h$ is the specific enthalpy of the fluid, defined as
+\begin{equation}
+h\equiv1+\frac{e+p}{\rho},
+\end{equation}
+where $e$ is the internal energy-density of the fluid. The quantity $W$ is the Lorentz factor of the fluid, defined as
+\begin{equation}
+W\equiv\left(1-\vv{v}\cdot\vv{v}\right)^{-1/2}.
+\end{equation}
+The quantity $\alpha$ is the lapse function, $\eta^{i}$ are the ratio of the components shift-vector, $\beta^{i}$, to the lapse function:
+\begin{equation}
+\vv{\eta}\longrightarrow\eta^{i}\equiv\alpha^{-1}\,\beta^{i},
+\end{equation}
+and $\gamma_{ij}$ are the covariant components of the spatial three-metric tensor, i.e.
+$\gamma^{ij}\,\gamma_{jk}=\delta^{i}_{~k}$, where $\delta^{i}_{~k}$ are the usual components of the Kronecker delta tensor.
+The $P^{ij}$ are the components of the stress-tensor, defined as
+\begin{equation}
+\bP\longrightarrow P^{ij}\equiv\rho\,h\,W^{2}\,v^{i}\,v^{j}+p\,\gamma^{ij},
+\end{equation}
+and the $K_{ij}$ are the components of the extrinsic curvature, defined as
+\begin{equation}
+\text{FILL IN HERE}.
+\end{equation}
 
 \section{Derivation of Middle Wave-Speed Estimate for General Relativistic HLLC Numerical Flux}
-For a given Riemann problem we assume that the shocked fluid is composed of two distinct regions, separated by a contact discontinuity (see \figref{Fig:HLLC_RiemannFan}).
+For a given Riemann problem we assume that a discontinuity breaks up into four distinct regions (see \figref{Fig:HLLC_RiemannFan}).
 \begin{figure}[H]
@@
 
-Here we derive an estimate for the propagation speed of that contact discontinuity.
-
-The equations we are solving are the general relativistic equations of hydrodynamics in conservative form:
-\begin{equation}
-    \pderiv{\left(\sqrtgm\,\bU\right)}{t}+\pderiv{\left(\alpha\,\sqrtgm\,\bF^{i}\left(\bU\right)\right)}{x^{i}}=\alpha\,\sqrtgm\,\bS,
-\end{equation}
-where $\bU$ is the \textit{vector of conserved variables}, $\bF^{i}\left(\bU\right)$ are the fluxes of the conserved variables along the three spatial directions, $\bS$ is a source term (which does \textit{not} contain any derivatives of the fluid variables), $\alpha$ is the lapse function, and $\sqrtgm$ is the determinant of the spatial three-metric.
-In deriving the above equations we assume that the lapse function is explicitly independent of time.
-We can re-write this slightly using the product rule:
-\begin{equation}
-    \sqrtgm\,\pderiv{\bU}{t}+\bU\,\pderiv{\sqrtgm}{t}+\sqrtgm\,\pderiv{\left(\alpha\,\bF^{i}\right)}{x^{i}}+\alpha\,\bF^{i}\,\pderiv{\sqrtgm}{x^{i}}=\alpha\,\sqrtgm\,\bS.
-\end{equation}
-Now, moving the terms that don't contain derivatives of the fluid variables to the RHS and dividing by $\sqrtgm$, we obtain:
-\begin{equation}\label{Eq:EulerConsSources}
-    \pderiv{\bU}{t}+\pderiv{\left(\alpha\,\bF^{i}\right)}{x^{i}}=\bQ,
-\end{equation}
-where:
-\begin{equation}
-    \bQ\equiv\alpha\,\bS-\f{1}{\sqrtgm}\left(\bU\,\pderiv{\sqrtgm}{t}+\alpha\,\bF^{i}\,\pderiv{\sqrtgm}{x^{i}}\right).
-\end{equation}
-
-The vector of conserved variables is given by \citep{Mignone2005}:
-\begin{equation}
-    \bU\equiv
-    \begin{pmatrix}
-      D \\
-      S_{j} \\
-      E
-    \end{pmatrix}=
-    \begin{pmatrix}
-      \rho\,W \\
-      \rho\,h\,W^{2}\,v_{j} \\
-      \rho\,h\,W^{2}-p,
-    \end{pmatrix}
-\end{equation}
-where $\rho$ is the rest mass-density, $v_{j}$ are the covariant components of the three-velocity, $p$ is the pressure, and $W$ is the Lorentz factor:
-\begin{equation}
-    W\equiv\left(1-\vv{v}\cdot\vv{v}\right)^{-1/2}.
-\end{equation}
-The quantity $h$ is the relativistic specific enthalpy, given by:
-\begin{equation}
-    h\equiv1+\f{e+p}{\rho},
-\end{equation}
-where $e$ is the internal energy-density. The fluxes are given by \citep{RezzollaRelHyd}:
-\begin{equation}
-    \bF^{i}\equiv
-    \begin{pmatrix}
-      D\left(v^{i}-\alpha^{-1}\,\beta^{i}\right) \\
-      S_{j}\left(v^{i}-\alpha^{-1}\,\beta^{i}\right) + p\,\delta^{i}_{~j} \\
-      S^{i}-\alpha^{-1}\,\beta^{i}\,E
-    \end{pmatrix},
-\end{equation}
-where $\beta^{i}$ are the components of the shift vector. We define the quantity $\eta^{i}$ as:
-\begin{equation}
-    \eta^{i}\equiv\alpha^{-1}\,\beta^{i},
-\end{equation}
-which makes the fluxes that we work with:
-\begin{equation}
-    \bF^{i}\equiv
-    \begin{pmatrix}
-      D\left(v^{i}-\eta^{i}\right) \\
-      S_{j}\left(v^{i}-\eta^{i}\right) + p\,\delta^{i}_{~j} \\
-      S^{i}-\eta^{i}\,E
-    \end{pmatrix}.
-\end{equation}
-
-We will need to know how the fluxes relate to the conserved variables across shocks. These relations are known as the \textit{Rankine-Hugoniot jump conditions}. We derive them next.
-
 \subsection{Derivation of Rankine-Hugoniot Jump Conditions}
@@
 
-We start the derivation by integrating the one-dimensional version of \eqref{Eq:EulerConsSources} in space from a point $x_{L}$ to a point $x_{R}$, that contains a shock, which we define to be at a time-dependent point $x_{L}<s\left(t\right)<x_{R}$:
+We start the derivation by integrating the one-dimensional version of \eqref{Eq:GRH} in space from a point $x_{L}$ to a point $x_{R}$, that contains a shock, which we define to be at a time-dependent point $x_{L}<\lambda\left(t\right)<x_{R}$:
 \begin{equation}
-    \int\limits_{x_{L}}^{x_{R}}\pd{\bU}{t}\,\sqrtgm\,dx+\int\limits_{x_{L}}^{x_{R}}\pd{\left(\alpha\,\bF\right)}{x}\,\sqrtgm\,dx=\int\limits_{x_{L}}^{x_{R}}\bQ\,\sqrtgm\,dx.
+\int\limits_{x_{L}}^{x_{R}}\pd{\left(\sqrt{\gamma}\,\bU\right)}{t}\,dx+\int\limits_{x_{L}}^{x_{R}}\pd{\left(\alpha\,\sqrt{\gamma}\,\bF^{x}\right)}{x}\,dx=\int\limits_{x_{L}}^{x_{R}}\sqrt{\gamma}\,\bS\,dx.
 \end{equation}
-Using the product rule again, we get:
+First, we note that in the first integral on the LHS we can pull out the partial derivative with respect to time, which converts it into a total derivative.
+We also perform an integration-by-parts on the second integral on the LHS, yielding
+\begin{align}
+\frac{d}{dt}\int\limits_{x_{L}}^{x_{R}}&\sqrt{\gamma}\,\bU\,dx+\left[\alpha\,\sqrt{\gamma}\,\bF^{x}\right]^{x_{R}}_{x_{L}}=\int\limits_{x_{L}}^{x_{R}}\sqrt{\gamma}\,\bS\,dx\\
+&\implies\frac{d}{dt}\int\limits_{x_{L}}^{x_{R}}\sqrt{\gamma}\,\bU\,dx+\alpha_{R}\,\sqrt{\gamma_{R}}\,\bF_{R}^{x}-\alpha_{L}\,\sqrt{\gamma_{L}}\,\bF_{L}^{x}=\int\limits_{x_{L}}^{x_{R}}\sqrt{\gamma}\,\bS\,dx,
+\end{align}
+where $\alpha_{L}=\alpha\left(x_{L}\right)$, etc.
+The integral over the vector of conserved variables contains the discontinuity, and therefore it's derivative is not well-defined.
+To overcome this we split the integral into one integral from $x_{L}$ to the location of the shock as approached from below, $s^{-}\left(t\right)$, and another integral from the location of the shock as approached from above, $s^{+}\left(t\right)$, to $x_{R}$:
 \begin{equation}
-    \int\limits_{x_{L}}^{x_{R}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx-\int\limits_{x_{L}}^{x_{R}}\bU\,\pd{\sqrtgm}{t}\,dx+\int\limits_{x_{L}}^{x_{R}}\pd{\left(\alpha\,\sqrtgm\,\bF\right)}{x}\,dx-\int\limits_{x_{L}}^{x_{R}}\alpha\,\bF\,\pd{\sqrtgm}{x}\,dx=\int\limits_{x_{L}}^{x_{R}}\bQ\,\sqrtgm\,dx.
+\int\limits_{x_{L}}^{x_{R}}\sqrt{\gamma}\,\bU\,dx=\int\limits_{x_{L}}^{s^{-}\left(t\right)}\sqrt{\gamma}\,\bU\,dx+\int\limits_{s^{+}\left(t\right)}^{x_{R}}\sqrt{\gamma}\,\bU\,dx.
 \end{equation}
-Again moving the terms that don't contain derivatives of fluid variables to the RHS, we get:
+Both of these integrals are smooth. Next we use the rule for differentiation of an integral depending on a parameter \citep{RezzollaRelHyd}:
 \begin{equation}
-    \int\limits_{x_{L}}^{x_{R}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx+\int\limits_{x_{L}}^{x_{R}}\pd{\left(\alpha\,\sqrtgm\,\bF\right)}{x}\,dx=\int\limits_{x_{L}}^{x_{R}}\,\bQ'\,\sqrtgm\,dx,
+\f{d}{dt}\int\limits_{x_{1}\left(t\right)}^{x_{2}\left(t\right)}Q\left(x,t\right)\,dx=\int\limits_{x_{1}\left(t\right)}^{x_{2}\left(t\right)}\pd{Q\left(x,t\right)}{t}\,dx+Q\left(x_{2}\left(t\right),t\right)\,\frac{dx_{2}\left(t\right)}{dt}-Q\left(x_{1}\left(t\right),t\right)\,\frac{dx_{1}\left(t\right)}{dt}.
 \end{equation}
-where
+This yields, since $x_{L}$ and $x_{R}$ are constant,
+\begin{align}
+\int\limits_{x_{L}}^{s^{-}\left(t\right)}&\pd{\left(\sqrt{\gamma}\,\bU\right)}{t}\,dx+\sqrt{\gamma\left(s^{-}\left(t\right),t\right)}\,\bU\left(s^{-}\left(t\right),t\right)\,\frac{ds^{-}}{dt}\\
+&+\int\limits_{s^{+}\left(t\right)}^{x_{R}}\pd{\left(\sqrt{\gamma}\,\bU\right)}{t}\,dx-\sqrt{\gamma\left(s^{+}\left(t\right),t\right)}\,\bU\left(s^{+}\left(t\right),t\right)\,\frac{ds^{+}}{dt}\\
+&+\alpha_{R}\,\sqrt{\gamma_{R}}\,\bF_{R}-\alpha_{L}\,\sqrt{\gamma_{L}}\,\bF_{L}=\int\limits_{x_{L}}^{x_{R}}\sqrt{\gamma}\,\bS\,dx.
+\end{align}
+We will now take the limit that $x_{L}\longrightarrow s^{-}$ and $x_{R}\longrightarrow s^{+}$.
+When we do this, we see that the integrals vanish, because the integrands are all smooth in the regions considered.
+This yields (defining $\bU_{L}\equiv\bU\left(s^{-}\left(t\right),t\right)$, etc.)
 \begin{equation}
-    \bQ'\equiv\bQ+\f{1}{\sqrtgm}\left(\bU\,\pd{\sqrtgm}{t}+\alpha\,\bF\,\pd{\sqrtgm}{x}\right).
+\sqrt{\gamma_{L}}\,\bU_{L}\,\frac{ds_{L}}{dt}-\sqrt{\gamma_{R}}\,\bU_{R}\,\frac{ds_{R}}{dt}=\alpha_{L}\,\sqrt{\gamma_{L}}\,\bF_{L}-\alpha_{R}\,\sqrt{\gamma_{R}}\,\bF_{R}.
 \end{equation}
+Now, we note that $s_{L}=s_{R}$, and that geometry fields are continuous across discontinuities, which means that the metric determinant cancels.
+This yields, defining the middle wave-speed $\lambda$ as
+\begin{equation}
+\lambda\equiv\frac{ds}{dt},
+\end{equation}
+\begin{equation}
+\lambda\left(\bU_{L}-\bU_{R}\right)=\alpha\left(\bF_{L}-\bF_{R}\right).
+\end{equation}
+These are the \textit{Rankine-Hugoniot jump conditions} and they describe how the fluid variables change across a discontinuity.
+Next we derive an expression for an estimate of the value of the middle wave-speed, $\lambda$.
 
-The second term on the LHS becomes a boundary term. Moving that to the RHS and the source term to the LHS we get:
+\subsection{Derivation of Estimate of Middle Wave-Speed $\lambda$}
+Now we apply the jump conditions to the shocked and un-shocked fluid (either the left or the right state):
 \begin{equation}
-    \alpha\left(x_{L},t\right)\,\sqrtgm\left(x_{L},t\right)\,\bF\left(\bU\left(x_{L},t\right)\right)-\alpha\left(x_{R},t\right)\,\sqrtgm\left(x_{R},t\right)\,\bF\left(\bU\left(x_{R},t\right)\right)=\f{d}{dt}\int\limits_{x_{L}}^{x_{R}}\sqrtgm\,\bU\,dx-\int\limits_{x_{L}}^{x_{R}}\bQ'\,\sqrtgm\,dx.
-\end{equation}
-We now split the first integral into two parts, with the shock being at an endpoint:
-\begin{equation}
-    \alpha_{L}\,\sqrtgm_{L}\,\bF_{L}-\alpha_{R}\,\sqrtgm_{R}\,\bF_{R}=\f{d}{dt}\int\limits_{x_{L}}^{s_{L}\left(t\right)}\sqrtgm\,\bU\,dx+\f{d}{dt}\int\limits_{s_{R}\left(t\right)}^{x_{R}}\sqrtgm\,\bU\,dx-\int\limits_{x_{L}}^{x_{R}}\sqrtgm\,\bQ'\,dx,
-\end{equation}
-where $\bF_{L}\equiv\bF\left(\bU\left(x_{L},t\right)\right)$, etc.
-We also use the notation that $s_{L}$ means ``approaches $s$ from the left state" and $s_{R}$ means ``approaches $s$ from the right state".
-Using the rule for differentiating an integral with variable bounds:
-\begin{equation}
-    \f{d}{dt}\int\limits_{x_{1}\left(t\right)}^{x_{2}\left(t\right)}A\left(x,t\right)\,dx=\int\limits_{x_{1}\left(t\right)}^{x_{2}\left(t\right)}\pd{A\left(x,t\right)}{t}\,dx+A\left(x_{2}\left(t\right),t\right)\,\f{dx_{2}\left(t\right)}{dt}-A\left(x_{1}\left(t\right),t\right)\,\f{dx_{1}\left(t\right)}{dt},
-\end{equation}
-we find:
-\begin{equation}
-    \alpha_{L}\,\sqrtgm_{L}\,\bF_{L}-\alpha_{R}\,\sqrtgm_{R}\,\bF_{R}=\f{ds}{dt}\left(\sqrtgm_{L}\,\bU_{L}-\sqrtgm_{R}\,\bU_{R}\right)+\int\limits_{x_{L}}^{s_{L}\left(t\right)}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx+\int\limits_{s_{R}\left(t\right)}^{x_{R}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx-\int\limits_{x_{L}}^{x_{R}}\bQ'\,dx.
-\end{equation}
-Now we take the limit that $x_{L}\longrightarrow s\left(t\right)$ and $x_{R}\longrightarrow s\left(t\right)$.
-In this limit all the integrals vanish (since no terms in $\bQ'$ depend on derivatives of fluid variables), and since $\alpha$ and $\sqrtgm$ are continuous across shocks, $\alpha_{L}=\alpha_{R}\equiv\alpha$ and $\sqrtgm_{L}=\sqrtgm_{R}\equiv\sqrtgm$.
-Defining the shock speed as $ds/dt\equiv\lambda$, we see that the metric determinant cancels, leaving us with the jump conditions:
-\begin{equation}
-    \alpha\left(\bF_{L}-\bF_{R}\right)=\lambda\left(\bU_{L}-\bU_{R}\right).
-\end{equation}
-
-\subsection{Derivation of Contact Wave-Speed}
-With the jump conditions we are ready to derive an estimate for the propagation speed of the contact discontinuity.
-If we assume one state is the shocked region and the other state is the unshocked region then the jump conditions become:
-\begin{equation}\label{Eq:RHJump_GR}
 \lambda^{i}\left(\bU^{*}-\bU\right)=\alpha\left(\left(\bF^{*}\right)^{i}-\bF^{i}\right).
 \end{equation}
-We assume that the flux in the shocked region can be written as:
+We will use the shorthand notation:
 \begin{equation}
-    \left(\bF^{*}\right)^{i}\equiv
-    \begin{pmatrix}
-      D^{*}\left[\left(v^{*}\right)^{i}-\left(\eta^{*}\right)^{i}\right] \\
-      S^{*}_{j}\left[\left(v^{*}\right)^{i}-\left(\eta^{*}\right)^{i}\right] + p^{*}\,\delta^{i}_{~j} \\
-      \left(S^{*}\right)^{i}-\left(\eta^{*}\right)^{i}\,E^{*}
-    \end{pmatrix}.
+\bF^{*i}=\left(\bF^{*}\right)^{i}.
 \end{equation}
-Since $\alpha$ and $\boldsymbol{\beta}$ are continuous, we can equate $\alpha^{*}=\alpha$ and $\boldsymbol{\beta}^{*}=\boldsymbol{\beta}$, and therefore $\left(\eta^{*}\right)^{i}=\eta^{i}$.
-We also define $\left(v^{*}\right)^{i}\equiv\left(\lambda^{*}\right)^{i}$, the propagation speed of the contact discontinuity.
-We use the shorthand notation:
+Recalling that the geometry fields are continuous, we assume that the flux in the shocked region can be written as
 \begin{equation}
-    \left(X^{*}\right)^{i}=X^{*i}.
+\bF^{*i}\longrightarrow\left(F^{*i}\right)^{J}=\begin{pmatrix}D^{*}\left(\lambda^{*i}-\eta^{i}\right)\\ S^{*}_{j}\left(\lambda^{*i}-\eta^{i}\right)+p^{*}\,\delta^{i}_{~j}\\S^{*i}-\eta^{i}\,E^{*}\end{pmatrix}.
 \end{equation}
-With that the fluxes in the shocked region can be written as:
-\begin{equation}\label{Eq:StarFlux}
-    \bF^{*i}\equiv
-    \begin{pmatrix}
-      D^{*}\left(\lambda^{*i}-\eta^{i}\right) \\
-      S^{*}_{j}\left(\lambda^{*i}-\eta^{i}\right) + p^{*}\,\delta^{i}_{~j} \\
-      S^{*i}-\eta^{i}\,E^{*}
-    \end{pmatrix}.
+Applying the jump conditions to the momentum-density equation we get
+\begin{align}
+\lambda^{i}\left(S_{j}^{*}-S_{j}\right)&=\alpha\left[S^{*}_{j}\left(\lambda^{*i}-\eta^{i}\right)+p^{*}\,\delta^{i}_{~j}-S_{j}\left(v^{i}-\eta^{i}\right)-p\,\delta^{i}_{~j}\right]\\
+\implies S^{*}_{j}\left[\lambda^{i}-\alpha\left(\lambda^{*i}-\eta^{i}\right)\right]&=S_{j}\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}.
+\end{align}
+Now we apply the jump conditions to the energy-density equation, which gives
+\begin{equation}
+\lambda^{i}\left(E^{*}-E\right)=\alpha\left[S^{*i}-\eta^{i}\,E^{*}-S^{i}+\eta^{i}\,E\right].
 \end{equation}
-
-\subsubsection{Applying the Jump Conditions}
-Now we apply the jump conditions, \eqref{Eq:RHJump_GR} to the momentum-density:
+Now, we note that
 \begin{align}
-    \lambda^{i}\left(S^{*}_{j}-S_{j}\right)&=\alpha\left[S^{*}_{j}\left(\lambda^{*i}-\eta^{i}\right)+p^{*}\,\delta^{i}_{~j}-S_{j}\left(v^{i}-\eta^{i}\right)-p\,\delta^{i}_{~j}\right]\\
-    \implies S^{*}_{j}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)&=S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}\label{Eq:RH_Mom}
+S^{i}&=\left(E+p\right)v^{i}\label{Eq:Mom-En}\\
+S^{*i}&=\left(E^{*}+p^{*}\right)\lambda^{*i}.
 \end{align}
-
-Before we apply the jump conditions to the energy-density, we note that:
+Substituting this into the energy-density equation gives
 \begin{align}
-    S^{i}&=\left(E+p\right)v^{i}\\
-    S^{*i}&=\left(E^{*}+p^{*}\right)\lambda^{*i}.\label{Eq:SsEs}
+\lambda^{i}\left(E^{*}-E\right)&=\alpha\left[\left(E^{*}+p^{*}\right)\lambda^{*i}-\eta^{i}\,E^{*}-\left(E+p\right)v^{i}+\eta^{i}\,E\right]\\
+\implies E^{*}\left[\lambda^{i}-\alpha\left(\lambda^{*i}-\eta^{i}\right)\right]&=E\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]+\alpha\left(p^{*}\,\lambda^{*i}-p\,v^{i}\right).\label{Eq:En1}
 \end{align}
-Next we apply the jump conditions to the energy-density:
+Now we substitute \eqref{Eq:Mom-En} into the momentum-density equation which yields
 \begin{align}
-    \lambda^{i}\left(E^{*}-E\right)&=\alpha\left(S^{*i}-\eta^{i}\,E^{*}-S^{i}+\eta^{i}\,E\right)\\
-    \implies\lambda^{i}\left(E^{*}-E\right)&=\alpha\left(E^{*}\,\lambda^{*i}+p^{*}\,\lambda^{*i}-\eta^{i}\,E^{*}-E\,v^{i}-p\,v^{i}+\eta^{i}\,E\right)\\
-    \implies E^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)&=E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}\,\lambda^{*i}-p\,v^{i}\right).\label{Eq:RH_E}
+\left(E^{*}+p^{*}\right)\lambda^{*}_{j}\left[\lambda^{i}-\alpha\left(\lambda^{*i}-\eta^{i}\right)\right]&=S_{j}\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}\\
+\implies E^{*}\left[\lambda^{i}-\alpha\left(\lambda^{*i}-\eta^{i}\right)\right]\lambda^{*}_{j}&=-p^{*}\left[\lambda^{i}-\alpha\left(\lambda^{*i}-\eta^{i}\right)\right]\lambda^{*}_{j}+S_{j}\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}.
 \end{align}
-Now we use \eqref{Eq:SsEs} and re-write \eqref{Eq:RH_Mom} (using the metric to raise and lower indices, so $S^{*}_{j}=\gamma_{jk}S^{*k}$):
+Equating this with \eqref{Eq:En1} gives
+\begin{align}
+&\left\{E\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]+\alpha\left(p^{*}\,\lambda^{*i}-p\,v^{i}\right)\right\}\lambda^{*}_{j}\\
+&\hspace{5em}=-p^{*}\left[\lambda^{i}-\alpha\left(\lambda^{*i}-\eta^{i}\right)\right]\lambda^{*}_{j}+S_{j}\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}.
+\end{align}
+We see that the term $\alpha\,p^{*}\,\lambda^{*i}\,\lambda^{*}_{j}$ cancels from both sides. We now isolate $p^{*}$ to get
+\begin{align}
+p^{*}&=\frac{E\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]\lambda^{*}_{j}-\alpha\,p\,v^{i}\,\lambda^{*}_{j}-S_{j}\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]+\alpha\,p\,\delta^{i}_{~j}}{\alpha\,\delta^{i}_{~j}-\left(\lambda^{i}+\alpha\,\eta^{i}\right)\lambda^{*}_{j}}\\
+&=\frac{\left\{E\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]-\alpha\,p\,v^{i}\right\}\lambda^{*}_{j}-\left\{S_{j}\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]-\alpha\,p\,\delta^{i}_{~j}\right\}}{\alpha\,\delta^{i}_{~j}-\left(\lambda^{i}+\alpha\,\eta^{i}\right)\lambda^{*}_{j}}.
+\end{align}
+Now we note that
 \begin{equation}
-    \left(E^{*}+p^{*}\right)\gamma_{kj}\,\lambda^{*k}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)=S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}.
-\end{equation}
-Slight manipulation yields:
-\begin{equation}
-    E^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)=-p^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)+\f{S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}}{\gamma_{kj}\,\lambda^{*k}}.
-\end{equation}
-Now we equate this with \eqref{Eq:RH_E}, which gives:
-\begin{equation}
-    E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}\,\lambda^{*i}-p\,v^{i}\right)=-p^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)+\f{S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}}{\gamma_{kj}\,\lambda^{*k}}.
-\end{equation}
-Or, multiplying through by $\gamma_{kj}\,\lambda^{*k}$:    
-\begin{align}
-    &\gamma_{kj}\,\lambda^{*k}\left[E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}\,\lambda^{*i}-p\,v^{i}\right)\right]\nonumber\\
-    &\hspace{10em}=-\gamma_{kj}\,\lambda^{*k}\,p^{*}\left(\lambda^{i}-\alpha\,\lambda^{*i}+\alpha\,\eta^{i}\right)+S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}.
-\end{align}
-We see that the term $\gamma_{kj}\,\lambda^{*k}\,\alpha\,p^{*}\,\lambda^{*i}$ cancels. This gives:
-\begin{equation}
-    \gamma_{kj}\,\lambda^{*k}\left[E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,v^{i}\right]=-\gamma_{kj}\,\lambda^{*k}\,p^{*}\left(\lambda^{i}+\alpha\,\eta^{i}\right)+S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)+\alpha\left(p^{*}-p\right)\delta^{i}_{~j}.
-\end{equation}
-Or, grouping the terms with $\lambda^{*k}$ to the LHS:
-\begin{equation}
-    \left[E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,v^{i}+p^{*}\left(\lambda^{i}+\alpha\,\eta^{i}\right)\right]\gamma_{jk}\,\lambda^{*k}=S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,\delta^{i}_{~j}+\alpha\,p^{*}\,\delta^{i}_{~j},
-\end{equation}
-We can write this as:
-\begin{equation}\label{Eq:AB}
-    \left[A^{i}+\left(\lambda^{i}+\alpha\,\eta^{i}\right)p^{*}\right]\gamma_{jk}\,\lambda^{*k}=B^{i}_{~j}+\alpha\,p^{*}\,\delta^{i}_{~j},
-\end{equation}
-where
-\begin{equation}
-    A^{i}\equiv E\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,v^{i}=\lambda^{i}\,E-\alpha\left(E+p\right)v^{i}+\alpha\,\eta^{i}\,E=\lambda^{i}\,E-\alpha\left(S^{i}-\eta^{i}\,E\right)=\lambda^{i}\,E-\alpha\,F^{i}_{E},
+E\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]-\alpha\,p\,v^{i}=\lambda^{i}\,E-\alpha\left[\left(E+p\right)v^{i}-\eta^{i}\,E\right]=\lambda^{i}\,E-\alpha\left(S^{i}-\eta^{i}\,E\right)=\lambda^{i}\,E-\alpha\,F^{i}_{E},
 \end{equation}
@@
 \begin{equation}
-    B^{i}_{~j}\equiv S_{j}\left(\lambda^{i}-\alpha\,v^{i}+\alpha\,\eta^{i}\right)-\alpha\,p\,\delta^{i}_{~j}=\lambda^{i}\,S_{j}-\alpha\left[S_{j}\,v^{i}+p\,\delta^{i}_{~j}-\eta^{i}\,S_{j}\right]=\lambda^{i}\,S_{j}-\alpha\,F^{i}_{S_{j}}.
+S_{j}\left[\lambda^{i}-\alpha\left(v^{i}-\eta^{i}\right)\right]-\alpha\,p\,\delta^{i}_{~j}=\lambda^{i}\,S_{j}-\alpha\left[S_{j}\left(v^{i}-\eta^{i}\right)+p\,\delta^{i}_{~j}\right]=\lambda^{i}\,S_{j}-\alpha\,F^{i}_{S_{j}}.
 \end{equation}
-We can solve \eqref{Eq:AB} for $p^{*}$:
-\begin{equation}\label{Eq:p*}
-  \gamma_{jk}\,\lambda^{*k}\,A^{i}+\gamma_{jk}\,\lambda^{*k}\,\left(\lambda^{i}+\alpha\,\eta^{i}\right)p^{*}=B^{i}_{~j}+\alpha\,p^{*}\,\delta^{i}_{~j}\implies p^{*}=\f{\gamma_{jk}\,\lambda^{*k}\,A^{i}-B^{i}_{~j}}{\alpha\,\delta^{i}_{~j}-\gamma_{jk}\,\lambda^{*k}\left(\lambda^{i}+\alpha\,\eta^{i}\right)}
+With this, we have
+\begin{equation}
+p^{*}=\frac{\left(\lambda^{i}\,E-\alpha\,F^{i}_{E}\right)\lambda^{*}_{j}-\left(\lambda^{i}\,S_{j}-\alpha\,F^{i}_{S_{j}}\right)}{\alpha\,\delta^{i}_{~j}-\left(\lambda^{i}+\alpha\,\eta^{i}\right)\lambda^{*}_{j}}.
 \end{equation}
-At this point we note that because of the conformally-flat approximation, the metric contraction term reduces to:
+Now, since the pressure is continuous across contact discontinuities we can equate the left and right states, giving
 \begin{equation}
-    \gamma_{jk}\,\lambda^{*k}=\gamma_{jj}\,\lambda^{*j}\hspace{2em}\text{(No summation over $j$ index)}.
+\frac{\left(-\lambda^{i}_{L}\,E_{L}-\alpha\,F^{i}_{E,L}\right)\lambda^{*}_{j}-\left(-\lambda^{i}_{L}\,S_{j,L}-\alpha\,F^{i}_{S_{j},L}\right)}{\alpha\,\delta^{i}_{~j}-\left(-\lambda^{i}_{L}+\alpha\,\eta^{i}\right)\lambda^{*}_{j}}=\frac{\left(\lambda^{i}_{R}\,E_{R}-\alpha\,F^{i}_{E,R}\right)\lambda^{*}_{j}-\left(\lambda^{i}_{R}\,S_{j,R}-\alpha\,F^{i}_{S_{j},R}\right)}{\alpha\,\delta^{i}_{~j}-\left(\lambda^{i}_{R}+\alpha\,\eta^{i}\right)\lambda^{*}_{j}}.
 \end{equation}
-So if $i=j$, then $\lambda^{*j}=\lambda^{*i}$ is the normal velocity, which must be continuous across a contact discontinuity, i.e.
-$\lambda^{*j}_{L}=\lambda^{*j}_{R}=\lambda^{*j}$.
-Otherwise $\lambda^{*j}$, $j\neq i$ is a tangential velocity, which may be discontinuous across a contact discontinuity, i.e.
-$\lambda^{*j}_{L}\neq\lambda^{*j}_{R}$.
-We also know that the pressure is continuous across a contact discontinuity, so $p^{*}_{L}=p^{*}_{R}=p^{*}$.
-Using this, we can obtain an equation for $\lambda^{*i}$ by setting $j=i$ in \eqref{Eq:p*} and applying it to the left and right sides of the contact discontinuity, and then equating them:
+Now, cross-multiplying and focusing on the LHS:
+\begin{align}
+&\left[\alpha\,\delta^{i}_{~j}-\left(\lambda^{i}_{R}+\alpha\,\eta^{i}\right)\lambda^{*}_{j}\right]\left[\left(-\lambda^{i}_{L}\,E_{L}-\alpha\,F^{i}_{E,L}\right)\lambda^{*}_{j}-\left(-\lambda^{i}_{L}\,S_{j,L}-\alpha\,F^{i}_{S_{j},L}\right)\right]\\
+&=\left[\alpha\,\delta^{i}_{~j}-\left(\lambda^{i}_{R}+\beta^{i}\right)\lambda^{*}_{j}\right]\left[\left(-\lambda^{i}_{L}\,E_{L}-\alpha\,F^{i}_{E,L}\right)\lambda^{*}_{j}-\left(-\lambda^{i}_{L}\,S_{j,L}-\alpha\,F^{i}_{S_{j},L}\right)\right]\\
+&=\alpha\,\delta^{i}_{~j}\left(-\lambda^{i}_{L}\,E_{L}-\alpha\,F^{i}_{E,L}\right)\lambda^{*}_{j}-\alpha\,\delta^{i}_{~j}\left(-\lambda^{i}_{L}\,S_{j,L}-\alpha\,F^{i}_{S_{j},L}\right)\\
+&\hspace{3em}-\left(\lambda^{i}_{R}+\beta^{i}\right)\left(-\lambda^{i}_{L}\,E_{L}-\alpha\,F^{i}_{E,L}\right)\left(\lambda^{*}_{j}\right)^{2}+\left(\lambda^{i}_{R}+\beta^{i}\right)\left(-\lambda^{i}_{L}\,S_{j,L}-\alpha\,F^{i}_{S_{j},L}\right)\lambda^{*}_{j}\\
+&=-\left(\lambda^{i}_{R}+\beta^{i}\right)\left(-\lambda^{i}_{L}\,E_{L}-\alpha\,F^{i}_{E,L}\right)\left(\lambda^{*}_{j}\right)^{2}\\
+&\hspace{3em}+\left[\alpha\,\delta^{i}_{~j}\left(-\lambda^{i}_{L}\,E_{L}-\alpha\,F^{i}_{E,L}\right)+\left(\lambda^{i}_{R}+\beta^{i}\right)\left(-\lambda^{i}_{L}\,S_{j,L}-\alpha\,F^{i}_{S_{j},L}\right)\right]\lambda^{*}_{j}\\
+&\hspace{3em}-\alpha\,\delta^{i}_{~j}\left(-\lambda^{i}_{L}\,S_{j,L}-\alpha\,F^{i}_{S_{j,L}}\right).
+\end{align}
+Expanding out the terms gives
+\begin{align}
+&\left[\lambda^{i}_{R}\,\lambda^{i}_{L}\,E_{L}+\lambda^{i}_{R}\,\alpha\,F^{i}_{E,L}-\beta^{i}\left(-\lambda^{i}_{L}\,E_{L}-\alpha\,F^{i}_{E,L}\right)\right]\left(\lambda^{*}_{j}\right)^{2}\\
+&+\left[\alpha\,\delta^{i}_{~j}\left(-\lambda^{i}_{L}\,E_{L}-\alpha\,F^{i}_{E,L}\right)-\lambda^{i}_{R}\,\lambda^{i}_{L}\,S_{j,L}-\lambda^{i}_{R}\,\alpha\,F^{i}_{S_{j},L}+\beta^{i}\left(-\lambda^{i}_{L}\,S_{j,L}-\alpha\,F^{i}_{S_{j},L}\right)\right]\lambda^{*}_{j}\\
+&-\alpha\,\delta^{i}_{~j}\left(-\lambda^{i}_{L}\,S_{j,L}-\alpha\,F^{i}_{S_{j},L}\right).
+\end{align}
+From symmetry, by letting $L\leftrightarrow R$ and $\lambda^{i}_{L}\leftrightarrow-\lambda^{i}_{R}$, we can immediately write down the RHS as
+\begin{align}
+&\left[\lambda^{i}_{R}\,\lambda^{i}_{L}\,E_{R}-\lambda^{i}_{L}\,\alpha\,F^{i}_{E,R}-\beta^{i}\left(\lambda^{i}_{R}\,E_{R}-\alpha\,F^{i}_{E,R}\right)\right]\left(\lambda^{*}_{j}\right)^{2}\\
+&+\left[\alpha\,\delta^{i}_{~j}\left(\lambda^{i}_{R}\,E_{R}-\alpha\,F^{i}_{E,R}\right)-\lambda^{i}_{R}\,\lambda^{i}_{L}\,S_{j,R}+\lambda^{i}_{L}\,\alpha\,F^{i}_{S_{j},R}+\beta^{i}\left(\lambda^{i}_{R}\,S_{j,R}-\alpha\,F^{i}_{S_{j},R}\right)\right]\lambda^{*}_{j}\\
+&-\alpha\,\delta^{i}_{~j}\left(\lambda^{i}_{R}\,S_{j,R}-\alpha\,F^{i}_{S_{j},R}\right).
+\end{align}
+Now we subtract the LHS from the RHS, giving
+\begin{align}
+&\left[\lambda^{i}_{R}\,\lambda^{i}_{L}\left(E_{R}-E_{L}\right)-\left(\lambda^{i}_{R}\,\alpha\,F^{i}_{E,L}+\lambda^{i}_{L}\,\alpha\,F^{i}_{E,R}\right)-\beta^{i}\left(\lambda^{i}_{R}\,E_{R}+\lambda^{i}_{L}\,E_{L}+\alpha\,F^{i}_{E,L}-\alpha\,F^{i}_{E,R}\right)\right]\left(\lambda^{*}_{j}\right)^{2}\\
+&+\left[\alpha\,\delta^{i}_{~j}\left(\lambda^{i}_{R}\,E_{R}+\lambda^{i}_{L}\,E_{L}+\alpha\,F^{i}_{E,L}-\alpha\,F^{i}_{E,R}\right)-\lambda^{i}_{R}\,\lambda^{i}_{L}\left(S_{j,R}-S_{j,L}\right)+\lambda^{i}_{R}\,\alpha\,F^{i}_{S_{j},L}+\lambda^{i}_{L}\,\alpha\,F^{i}_{S_{j},R}\right.\\
+&\hspace{3em}\left.+\beta^{i}\left(\lambda^{i}_{R}\,S_{j,R}+\lambda^{i}_{L}\,S_{j,L}+\alpha\,F^{i}_{S_{j},L}-\alpha\,F^{i}_{S_{j},R}\right)\right]\\
+&-\alpha\,\delta^{i}_{~j}\left(\lambda^{i}_{R}\,S_{j,R}+\lambda^{i}_{L}\,S_{j,L}+\alpha\,F^{i}_{S_{j},L}-\alpha\,F^{i}_{S_{j},R}\right).
+\end{align}
+By making use of the HLL conserved variables and fluxes,
+\begin{align}
+\left(\lambda^{i}_{R}+\lambda^{i}_{L}\right)\bU_{HLL}&=\lambda^{i}_{R}\,\bU_{R}+\lambda^{i}_{L}\,\bU_{L}+\alpha\,\bF^{i}_{L}-\alpha\,\bF^{i}_{R}\\
+\left(\lambda^{i}_{R}+\lambda^{i}_{L}\right)\bF^{i}_{HLL}&=\lambda^{i}_{R}\,\alpha\,\bF^{i}_{L}+\lambda^{i}_{L}\,\alpha\,\bF_{R}-\lambda^{i}_{R}\,\lambda^{i}_{L}\left(\bU_{R}-\bU_{L}\right),
+\end{align}
+we can simplify the quadratic equation to (assuming that $\lambda^{i}_{L}\neq0$ \textbf{and} $\lambda^{i}_{R}\neq0$)
 \begin{equation}
-    \f{\gamma_{ii,L}\,\lambda^{*i}\,A^{i}_{L}-B^{i}_{~i,L}}{\alpha_{L}-\gamma_{ii,L}\,\lambda^{*i}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta_{L}^{i}\right)}=\f{\gamma_{ii,R}\,\lambda^{*i}\,A^{i}_{R}-B^{i}_{~i,R}}{\alpha_{R}-\gamma_{ii,R}\,\lambda^{*i}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta_{R}^{i}\right)}.
+\left(-F^{i}_{E,HLL}-\beta^{i}\,E_{HLL}\right)\left(\lambda^{*}_{j}\right)^{2}+\left[\alpha\,\delta^{i}_{~j}\,E_{HLL}+F^{i}_{S_{j},HLL}+\beta^{i}\,S_{j,HLL}\right]\lambda^{*}_{j}-\alpha\,\delta^{i}_{~j}\,S_{j,HLL}=0.
 \end{equation}
-The minus sign in front of $\lambda^{i}_{L}$ comes about because we demand that $\lambda^{i}$ is \textit{always} greater than or equal to zero, so a subsonic left-moving wave requires a minus sign.
-\sd{What about super-sonic waves?
-Does it reducing to HLL mean that the sign isn't important?}
-Solving the equation for $\lambda^{*i}$:
-\begin{align}
-    &\left[\alpha_{R}-\gamma_{ii,R}\,\lambda^{*i}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta_{R}^{i}\right)\right]\left(\gamma_{ii,L}\,\lambda^{*i}\,A^{i}_{L}-B^{i}_{~i,L}\right)=\left[\alpha_{L}-\gamma_{ii,L}\,\lambda^{*i}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta_{L}^{i}\right)\right]\left(\gamma_{ii,R}\,\lambda^{*i}\,A^{i}_{R}-B^{i}_{~i,R}\right)\nonumber\\
-    &\implies \alpha_{R}\,\gamma_{ii,L}\,A^{i}_{L}\,\lambda^{*i}-\alpha_{R}\,B^{i}_{~i,L}-\gamma_{ii,R}\,\gamma_{ii,L}\,A^{i}_{L}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta^{i}_{R}\right)\left(\lambda^{*i}\right)^{2}+\gamma_{ii,R}\,B^{i}_{~i,L}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta^{i}_{R}\right)\lambda^{*i}\nonumber\\
-    &\hspace{3em}=\alpha_{L}\,\gamma_{ii,R}\,A^{i}_{R}\,\lambda^{*i}-\alpha_{L}\,B^{i}_{~i,R}-\gamma_{ii,L}\,\gamma_{ii,R}\,A^{i}_{R}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta^{i}_{L}\right)\left(\lambda^{*i}\right)^{2}+\gamma_{ii,L}\,B^{i}_{~i,R}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta^{i}_{L}\right)\lambda^{*i}\nonumber\\
-    &\implies\gamma_{ii,L}\,\gamma_{ii,R}\left[A^{i}_{R}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta^{i}_{L}\right)-A^{i}_{L}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta^{i}_{R}\right)\right]\left(\lambda^{*i}\right)^{2}\nonumber\\
-    &\hspace{5em}+\left\{\gamma_{ii,L}\left[\alpha_{R}\,A^{i}_{L}-B^{i}_{~i,R}\left(-\lambda^{i}_{L}+\alpha_{L}\,\eta^{i}_{L}\right)\right]+\gamma_{ii,R}\left[B^{i}_{~i,L}\left(\lambda^{i}_{R}+\alpha_{R}\,\eta^{i}_{R}\right)-\alpha_{L}\,A^{i}_{R}\right]\right\}\lambda^{*i}\nonumber\\
-    &\hspace{10em}+\alpha_{L}\,B^{i}_{~i,R}-\alpha_{R}\,B^{i}_{~i,L}=0.
-\end{align}
-So, we have a quadratic equation in $\lambda^{*i}$:
+Now we just multiply the equation by $-1$, which gives
 \begin{equation}
-    X^{ii}\,\left(\lambda^{*i}\right)^{2}+X^{i}\,\lambda^{*i}+X=0,
+\left(F^{i}_{E,HLL}+\beta^{i}\,E_{HLL}\right)\left(\lambda^{*}_{j}\right)^{2}-\left[\alpha\,\delta^{i}_{~j}\,E_{HLL}+F^{i}_{S_{j},HLL}+\beta^{i}\,S_{j,HLL}\right]\lambda^{*}_{j}+\alpha\,\delta^{i}_{~j}\,S_{j,HLL}=0.
 \end{equation}
-where (recalling that $\alpha\,\eta^{i}=\beta^{i}$):
-\begin{align}
-    X^{ii}&=\gamma_{ii,L}\,\gamma_{ii,R}\left[A^{i}_{R}\left(-\lambda^{i}_{L}+\beta^{i}_{L}\right)-A^{i}_{L}\left(\lambda^{i}_{R}+\beta^{i}_{R}\right)\right]\\
-    X^{i}&=\gamma_{ii,L}\left[\alpha_{R}\,A^{i}_{L}-B^{i}_{~i,R}\left(-\lambda^{i}_{L}+\beta^{i}_{L}\right)\right]-\gamma_{ii,R}\left[\alpha_{L}\,A^{i}_{R}-B^{i}_{~i,L}\left(\lambda^{i}_{R}+\beta^{i}_{R}\right)\right]\\
-    X&=\alpha_{L}\,B^{i}_{~i,R}-\alpha_{R}\,B^{i}_{~i,L}.
-\end{align}
+Finally, we use the metric to raise the index on the contact wave-speed, which gives
+\begin{equation}
+\left(\gamma_{jk}\right)^{2}\left(F^{i}_{E,HLL}+\beta^{i}\,E_{HLL}\right)\left(\lambda^{*k}\right)^{2}-\gamma_{jk}\left[\alpha\,\delta^{i}_{~j}\,E_{HLL}+F^{i}_{S_{j},HLL}+\beta^{i}\,S_{j,HLL}\right]\lambda^{*k}+\alpha\,\delta^{i}_{~j}\,S_{j,HLL}=0.
+\end{equation}
 
-If we assume that the geometry fields are continuous, then we can simplify further, specifically:
-\begin{align}
-    X^{ii}&=\left(\gamma_{ii}\right)^{2}\left[A^{i}_{R}\left(-\lambda^{i}_{L}+\beta^{i}\right)-A^{i}_{L}\left(\lambda^{i}_{R}+\beta^{i}\right)\right]\\
-    X^{i}&=\gamma_{ii}\left\{\left[\alpha\,A^{i}_{L}-B^{i}_{~i,R}\left(-\lambda^{i}_{L}+\beta^{i}\right)\right]-\left[\alpha\,A^{i}_{R}-B^{i}_{~i,L}\left(\lambda^{i}_{R}+\beta^{i}\right)\right]\right\}\\
-    X&=\alpha\left(B^{i}_{~i,R}-B^{i}_{~i,L}\right).
-\end{align}
+We see that in the special relativistic, Cartesian coordinate limit of $\alpha\rightarrow1$, $\beta^{i}\rightarrow0^{i}$, and $\gamma_{ij}=\delta_{ij}$, we recover the result of \citet{Mignone2005}.
 

### 2019-06-14 Documents/M1/collisionsM1/collisionsM1.tex

@@
 
-\newcommand{\IN}{\mbox{\tiny In}}
-\newcommand{\OUT}{\mbox{\tiny Out}}
+\newcommand{\EC}{\mbox{\tiny{\sc Ec}}}
+\newcommand{\IN}{\mbox{\tiny{\sc In}}}
+\newcommand{\OUT}{\mbox{\tiny{\sc Out}}}
 \newcommand{\NNS}{\mbox{\tiny NNS}} % Neutrino-Nucleon/Nuclei Scattering
-\newcommand{\NES}{\mbox{\tiny NES}} % Neutrino-Electron Scattering
-\newcommand{\PROD}{\mbox{\tiny Pr}}
-\newcommand{\ANN}{\mbox{\tiny An}}
-\newcommand{\SC}{\mbox{\tiny Sc}}      % Scattering
-\newcommand{\TP}{\mbox{\tiny TP}}      % Pair-Processes
+\newcommand{\NES}{\mbox{\tiny{\sc Nes}}} % Neutrino-Electron Scattering
+\newcommand{\PROD}{\mbox{\tiny{\sc Pr}}}
+\newcommand{\ANN}{\mbox{\tiny{\sc An}}}
+\newcommand{\SC}{\mbox{\tiny{\sc Sc}}}      % Scattering
+\newcommand{\TP}{\mbox{\tiny{\sc Tp}}}      % Pair-Processes
 
@@
 
+\section{Implicit Solvers}
+
+We discuss the implicit solver in the context of a system of electron neutrinos and antineutrinos.  
+We let $\mathcal{J}_{\nu_{e}}\to\mathcal{J}$ and $\mathcal{J}_{\bar{\nu}_{e}}\to\bar{\mathcal{J}}$.  
+The electron fraction is updated from
+\begin{equation}
+  \f{\rho}{m_{b}}\big(Y_{e}^{n+1}-Y_{e}^{n}\big) + \big[\,\big(J^{n+1}-\bar{J}^{n+1}\big)-\big(J^{n}-\bar{J}^{n}\big)\,\big] = 0,
+  \label{eq:electronFractionContinuous}
+\end{equation}
+where
+\begin{equation}
+  \big\{\,J,\bar{J}\,\big\}
+  =\sum_{q=1}^{N_{\varepsilon}}\hat{w}_{q}^{(2)}\,\big\{\,\mathcal{J}_{q},\bar{\mathcal{J}}_{q}\,\big\}
+  \quad\text{with}\quad
+  \hat{w}_{q}^{(2)}=\f{4\pi}{h^{3}}\,w_{q}^{(2)},
+\end{equation}
+where $w_{q}^{(2)}$ are quadrature weights for energy integrals with respect to $dV_{\varepsilon}=\varepsilon^{2}\,d\varepsilon$.  
+Defining $S_{Y_{e}}\equiv \rho\,Y_{e}^{n}/m_{b}$ and $U_{Y_{e}} \equiv Y_{e}/Y_{e}^{n}$, we can write Eq.~\eqref{eq:electronFractionContinuous} in discrete form as
+\begin{equation}
+  F_{Y_{e}}(\vect{U}^{n+1})\equiv
+  U_{Y_{e}}^{n+1} + \sum_{q}\hat{w}_{q}^{(2)}\big(\,\mathcal{J}_{q}^{n+1}-\bar{\mathcal{J}}_{q}^{n+1}\,\big)/S_{Y_{e}} 
+  - \big\{\,1+\sum_{q}\hat{w}_{q}^{(2)}\big(\,\mathcal{J}_{q}^{n}-\bar{\mathcal{J}}_{q}^{n}\,\big)/S_{Y_{e}}\,\big\} = 0.
+  \label{eq:electronFractionDiscrete}
+\end{equation}
+Here we have defined the solution vector $\vect{U}=\big(Y_{e},\epsilon,\vect{\mathcal{J}},\vect{\bar{\mathcal{J}}}\big)^{T}$, where $\vect{\mathcal{J}}=\big(\mathcal{J}_{1},\ldots,\mathcal{J}_{N_{\varepsilon}}\big)^{T}$ and $\vect{\bar{\mathcal{J}}}=\big(\bar{\mathcal{J}}_{1},\ldots,\bar{\mathcal{J}}_{N_{\varepsilon}}\big)^{T}$.
+We also define the vectors $\vect{u}=\big(Y_{e},\epsilon\big)^{T}$ and $\vect{\mathcal{U}}=\big(\vect{\mathcal{J}},\vect{\bar{\mathcal{J}}}\big)^{T}$.
+
+The specific internal energy is updated from
+\begin{equation}
+  \rho\,\big(\epsilon^{n+1}-\epsilon^{n}\big)
+  +\big[\,\big(E^{n+1}+\bar{E}^{n+1}\big)-\big(E^{n}+\bar{E}^{n}\big)\,\big] = 0,
+  \label{eq:internalEnergyContinuous}
+\end{equation}
+where
+\begin{equation}
+  \big\{\,E,\bar{E}\,\big\}
+  =\sum_{q=1}^{N_{\varepsilon}}\hat{w}_{q}^{(3)}\,\big\{\,\mathcal{J}_{q},\bar{\mathcal{J}}_{q}\,\big\}
+  \quad\text{with}\quad
+  \hat{w}_{q}^{(3)}=\f{4\pi}{h^{3}}\,w_{q}^{(3)},
+\end{equation}
+where $w_{q}^{(3)}$ are quadrature weights for energy integrals with respect to $\varepsilon\,dV_{\varepsilon}=\varepsilon^{3}\,d\varepsilon$.  
+Defining $S_{\epsilon}\equiv\rho\epsilon^{n}$ and $U_{\epsilon}\equiv\epsilon/\epsilon^{n}$, we can write Eq.~\eqref{eq:internalEnergyContinuous} as
+\begin{equation}
+  F_{\epsilon}(\vect{U}^{n+1})\equiv
+  U_{\epsilon}^{n+1} + \sum_{q}\hat{w}_{q}^{(3)}\big(\,\mathcal{J}_{q}^{n+1}+\bar{\mathcal{J}}_{q}^{n+1}\,\big)/S_{\epsilon}
+  -\big\{\,1+\sum_{q}\hat{w}_{q}^{(3)}\big(\,\mathcal{J}_{q}^{n}+\bar{\mathcal{J}}_{q}^{n}\,\big)/S_{\epsilon}\,\big\} = 0.  
+  \label{eq:internalEnergyDiscrete}
+\end{equation}
+
+The neutrino density is updated from
+\begin{align}
+  \f{\big(\mathcal{J}_{i}^{n+1}-\mathcal{J}_{i}^{n}\big)}{\dt}
+  &=\big[\chi_{\EC}\big]_{i}^{n}\,\big(\mathcal{J}_{0,i}^{n+1}-\mathcal{J}_{i}^{n+1}\big) \nonumber \\
+  &\hspace{12pt}
+  +\sum_{q}w_{q}^{(2)}\,\big[\Phi_{\NES,0}^{\In}\big]_{qi}^{n+1}\,\mathcal{J}_{q}^{n+1} \nonumber \\
+  &\hspace{12pt}
+  -\mathcal{J}_{i}^{n+1}\sum_{q}w_{q}^{(2)}\,\big\{\,\big[\Phi_{\NES,0}^{\In}\big]_{qi}^{n+1}\,\mathcal{J}_{q}^{n+1}+\big[\Phi_{\NES,0}^{\Out}\big]_{qi}^{n+1}\,\big(1-\mathcal{J}_{q}^{n+1}\big)\,\big\} \nonumber \\
+  &\hspace{12pt}
+  + \sum_{q}w_{q}^{(2)}\,\big[\Phi_{\TP,0}^{\PROD}\big]_{qi}^{n+1}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big) \nonumber \\
+  &\hspace{12pt}
+  -\mathcal{J}_{i}^{n+1}\sum_{q}w_{q}^{(2)}\big\{\,\big[\Phi_{\TP,0}^{\PROD}\big]_{qi}^{n+1}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big)+\big[\Phi_{\TP,0}^{\ANN}\big]_{qi}^{n+1}\,\bar{\mathcal{J}}_{q}^{n+1}\,\big\} \nonumber \\
+  &=\big(\big[\eta_{\EC}\big]_{i}^{n+1}+\big[\eta_{\NES}\big]_{i}^{n+1}+\big[\eta_{\TP}\big]_{i}^{n+1}\big) \nonumber \\
+  &\hspace{12pt}
+  -\big(\big[\chi_{\EC}\big]_{i}^{n}+\big[\chi_{\NES}\big]_{i}^{n+1}+\big[\chi_{\TP}\big]_{i}^{n+1}\big)\,\mathcal{J}_{i}^{n+1} \nonumber \\
+  &=\big[\eta\big]_{i}^{n+1} - \big[\chi\big]_{i}^{n+1}\,\mathcal{J}_{i}^{n+1},
+  \label{eq:neutrinoDiscrete}
+\end{align}
+where we have defined
+\begin{align}
+  \big[\eta_{\EC}\big]_{i}^{n+1}
+  &=\big[\chi_{\EC}\big]_{i}^{n}\,\mathcal{J}_{0,i}^{n+1}, \label{eq:ECemissivityNeutrino} \\
+  \big[\eta_{\NES}\big]_{i}^{n+1}
+  &=\sum_{q}w_{q}^{(2)}\,\big[\Phi_{\NES,0}^{\In}\big]_{qi}^{n+1}\,\mathcal{J}_{q}^{n+1}, \label{eq:NESemissivityNeutrino} \\
+  \big[\eta_{\TP}\big]_{i}^{n+1}
+  &=\sum_{q}w_{q}^{(2)}\,\big[\Phi_{\TP,0}^{\PROD}\big]_{qi}^{n+1}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big), \label{eq:PAIRemissivityNeutrino} \\
+  \big[\chi_{\NES}\big]_{i}^{n+1}
+  &=\sum_{q}w_{q}^{(2)}\,\big\{\,\big[\Phi_{\NES,0}^{\In}\big]_{qi}^{n+1}\,\mathcal{J}_{q}^{n+1}+\big[\Phi_{\NES,0}^{\Out}\big]_{qi}^{n+1}\,\big(1-\mathcal{J}_{q}^{n+1}\big)\,\big\} \\
+  &=\big[\eta_{\NES}\big]_{i}^{n+1}+\sum_{q}w_{q}^{(2)}\,\big[\Phi_{\NES,0}^{\Out}\big]_{qi}^{n+1}\,\big(1-\mathcal{J}_{q}^{n+1}\big), \label{eq:NESopacityNeutrino} \\
+  \big[\chi_{\TP}\big]_{i}^{n+1}
+  &=\sum_{q}w_{q}^{(2)}\big\{\,\big[\Phi_{\TP,0}^{\PROD}\big]_{qi}^{n+1}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big)+\big[\Phi_{\TP,0}^{\ANN}\big]_{qi}^{n+1}\,\bar{\mathcal{J}}_{q}^{n+1}\,\big\} \\
+  &=\big[\eta_{\TP}\big]_{i}^{n+1}+\sum_{q}w_{q}^{(2)}\,\big[\Phi_{\TP,0}^{\ANN}\big]_{qi}^{n+1}\,\bar{\mathcal{J}}_{q}^{n+1}, \label{eq:PAIRopacityNeutrino} \\
+  \big[\eta\big]_{i}^{n+1}
+  &=\big[\eta_{\EC}\big]_{i}^{n+1}+\big[\eta_{\NES}\big]_{i}^{n+1}+\big[\eta_{\TP}\big]_{i}^{n+1}, \label{eq:TOTALemissivityNeutrino} \\
+  \big[\chi\big]_{i}^{n+1}
+  &=\big[\chi_{\EC}\big]_{i}^{n}+\big[\chi_{\NES}\big]_{i}^{n+1}+\big[\chi_{\TP}\big]_{i}^{n+1}.  \label{eq:TOTALopacityNeutrino}
+\end{align}
+We rewrite Eq.~\eqref{eq:neutrinoDiscrete} and define
+\begin{equation}
+  \mathcal{F}_{i}(\vect{U}^{n+1})
+  \equiv\big(\,1+\dt\,\big[\chi\big]_{i}^{n+1}\,\big)\,\mathcal{J}_{i}^{n+1}-\big(\,\mathcal{J}_{i}^{n}+\dt\,\big[\eta\big]_{i}^{n+1}\,\big)=0.
+  \label{eq:neutrinoDiscreteResidualForm}
+\end{equation}
+Similarly, the antineutrino density is updated from
+\begin{align}
+  \f{\big(\bar{\mathcal{J}}_{i}^{n+1}-\bar{\mathcal{J}}_{i}^{n}\big)}{\dt}
+  &=\big[\bar{\chi}_{\EC}\big]_{i}^{n}\,\big(\bar{\mathcal{J}}_{0,i}^{n+1}-\bar{\mathcal{J}}_{i}^{n+1}\big) \nonumber \\
+  &\hspace{12pt}
+  +\sum_{q}w_{q}^{(2)}\,\big[\bar{\Phi}_{\NES,0}^{\In}\big]_{qi}^{n+1}\,\bar{\mathcal{J}}_{q}^{n+1} \nonumber \\
+  &\hspace{12pt}
+  -\bar{\mathcal{J}}_{i}^{n+1}\sum_{q}w_{q}^{(2)}\,\big\{\,\big[\bar{\Phi}_{\NES,0}^{\In}\big]_{qi}^{n+1}\,\bar{\mathcal{J}}_{q}^{n+1}+\big[\bar{\Phi}_{\NES,0}^{\Out}\big]_{qi}^{n+1}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big)\,\big\} \nonumber \\
+  &\hspace{12pt}
+  + \sum_{q}w_{q}^{(2)}\,\big[\bar{\Phi}_{\TP,0}^{\PROD}\big]_{qi}^{n+1}\,\big(1-\mathcal{J}_{q}^{n+1}\big) \nonumber \\
+  &\hspace{12pt}
+  -\bar{\mathcal{J}}_{i}^{n+1}\sum_{q}w_{q}^{(2)}\big\{\,\big[\bar{\Phi}_{\TP,0}^{\PROD}\big]_{qi}^{n+1}\,\big(1-\mathcal{J}_{q}^{n+1}\big)+\big[\bar{\Phi}_{\TP,0}^{\ANN}\big]_{qi}^{n+1}\,\mathcal{J}_{q}^{n+1}\,\big\} \nonumber \\
+  &=\big(\,\big[\bar{\eta}_{\EC}\big]_{i}^{n+1}+\big[\bar{\eta}_{\NES}\big]_{i}^{n+1}+\big[\bar{\eta}_{\TP}\big]_{i}^{n+1}\,\big) \nonumber \\
+  &\hspace{12pt}
+  -\big(\,\big[\bar{\chi}_{\EC}\big]_{i}^{n}+\big[\bar{\chi}_{\NES}\big]_{i}^{n+1}+\big[\bar{\chi}_{\TP}\big]_{i}^{n+1}\,\big)\,\bar{\mathcal{J}}_{i}^{n+1} \nonumber \\
+  &=\big[\bar{\eta}\big]_{i}^{n+1} - \big[\bar{\chi}\big]_{i}^{n+1}\,\bar{\mathcal{J}}_{i}^{n+1},
+  \label{eq:antineutrinoDiscrete}
+\end{align}
+where we have defined
+\begin{align}
+  \big[\bar{\eta}_{\EC}\big]_{i}^{n+1}
+  &=\big[\bar{\chi}_{\EC}\big]_{i}^{n}\,\bar{\mathcal{J}}_{0,i}^{n+1}, \label{eq:ECemissivityAntineutrino} \\
+  \big[\bar{\eta}_{\NES}\big]_{i}^{n+1}
+  &=\sum_{q}w_{q}^{(2)}\,\big[\bar{\Phi}_{\NES,0}^{\In}\big]_{qi}^{n+1}\,\bar{\mathcal{J}}_{q}^{n+1}, \label{eq:NESemissivityAntineutrino} \\
+  \big[\bar{\eta}_{\TP}\big]_{i}^{n+1}
+  &=\sum_{q}w_{q}^{(2)}\,\big[\bar{\Phi}_{\TP,0}^{\PROD}\big]_{qi}^{n+1}\,\big(1-\mathcal{J}_{q}^{n+1}\big), \label{eq:PAIRemissivityAntineutrino} \\
+  \big[\bar{\chi}_{\NES}\big]_{i}^{n+1}
+  &=\sum_{q}w_{q}^{(2)}\,\big\{\,\big[\bar{\Phi}_{\NES,0}^{\In}\big]_{qi}^{n+1}\,\bar{\mathcal{J}}_{q}^{n+1}+\big[\bar{\Phi}_{\NES,0}^{\Out}\big]_{qi}^{n+1}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big)\,\big\} \\
+  &=\big[\bar{\eta}_{\NES}\big]_{i}^{n+1}+\sum_{q}w_{q}^{(2)}\,\big[\bar{\Phi}_{\NES,0}^{\Out}\big]_{qi}^{n+1}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big), \label{eq:NESopacityAntineutrino} \\
+  \big[\bar{\chi}_{\TP}\big]_{i}^{n+1}
+  &=\sum_{q}w_{q}^{(2)}\big\{\,\big[\bar{\Phi}_{\TP,0}^{\PROD}\big]_{qi}^{n+1}\,\big(1-\mathcal{J}_{q}^{n+1}\big)+\big[\bar{\Phi}_{\TP,0}^{\ANN}\big]_{qi}^{n+1}\,\mathcal{J}_{q}^{n+1}\,\big\} \\
+  &=\big[\bar{\eta}_{\TP}\big]_{i}^{n+1}+\sum_{q}w_{q}^{(2)}\,\big[\bar{\Phi}_{\TP,0}^{\ANN}\big]_{qi}^{n+1}\,\mathcal{J}_{q}^{n+1}, \label{eq:PAIRopacityAntineutrino} \\
+  \big[\bar{\eta}\big]_{i}^{n+1}
+  &=\big[\bar{\eta}_{\EC}\big]_{i}^{n+1}+\big[\bar{\eta}_{\NES}\big]_{i}^{n+1}+\big[\bar{\eta}_{\TP}\big]_{i}^{n+1}, \label{eq:TOTALemissivityAntineutrino} \\
+  \big[\bar{\chi}\big]_{i}^{n+1}
+  &=\big[\bar{\chi}_{\EC}\big]_{i}^{n}+\big[\bar{\chi}_{\NES}\big]_{i}^{n+1}+\big[\bar{\chi}_{\TP}\big]_{i}^{n+1}. \label{eq:TOTALopacityAntineutrino}
+\end{align}
+We rewrite Eq.~\eqref{eq:antineutrinoDiscrete} and define
+\begin{equation}
+  \bar{\mathcal{F}}_{i}(\vect{U}^{n+1})\equiv
+  \big(\,1+\dt\,\big[\bar{\chi}\big]_{i}^{n+1}\,\big)\,\bar{\mathcal{J}}_{i}^{n+1}-\big(\,\bar{\mathcal{J}}_{i}^{n}+\dt\,\big[\bar{\eta}\big]_{i}^{n+1}\,\big)=0.
+  \label{eq:antineutrinoDiscreteResidualForm}
+\end{equation}
+
+Next, we define
+\begin{align}
+  \vect{\mathcal{F}}(\vect{U})=\big(\,\mathcal{F}_{1}(\vect{U}),\ldots,\mathcal{F}_{N_{\varepsilon}}(\vect{U})\,\big)^{T}, \\
+  \vect{\bar{\mathcal{F}}}(\vect{U})=\big(\,\bar{\mathcal{F}}_{1}(\vect{U}),\ldots,\bar{\mathcal{F}}_{N_{\varepsilon}}(\vect{U})\,\big)^{T}
+\end{align}
+and
+\begin{equation}
+  \vect{F}(\vect{U})=\big(F_{Y_{e}}(\vect{U}),F_{\epsilon}(\vect{U}),\vect{\mathcal{F}}(\vect{U}),\vect{\bar{\mathcal{F}}}(\vect{U})\big)^{T},
+\end{equation}
+so that we can write the coupled nonlinear system consisting of Eqs.~\eqref{eq:electronFractionDiscrete}, \eqref{eq:internalEnergyDiscrete}, \eqref{eq:neutrinoDiscreteResidualForm}, and \eqref{eq:antineutrinoDiscreteResidualForm} in the compact form
+\begin{equation}
+  \vect{F}(\vect{U}) = 0.
+  \label{eq:nonlinearSystemResidualForm}
+\end{equation}
+
+\subsection{Newton's Method}
+
+Newton's method if given by
+\begin{itemize}
+  \item[1.] Set $\vect{U}^{[0]} = \vect{U}^{n}$
+  \item[2.] For $k=1,\ldots,M$ compute
+  \begin{equation}
+    \vect{U}^{[k]}=\vect{U}^{[k-1]} + \delta\vect{U}^{[k-1]}
+  \end{equation}
+  \item[3.] Set $\vect{U}^{n+1}=\vect{U}^{[M]}$,
+\end{itemize}
+where
+\begin{equation}
+  \delta\vect{U}^{[k]} = - \vect{J}(\vect{U}^{[k]})^{-1}\,\vect{F}(\vect{U}^{[k]}), \quad\text{with}\quad \vect{J}(\vect{U}^{[k]})=\vect{F}'(\vect{U}^{[k]}),
+\end{equation}
+and where the number of iterations $M$ is given by suitable convergence criteria.
+
+From Eq.~\eqref{eq:electronFractionDiscrete}, the elements of the Jacobian matrix are
+\begin{align}
+  \pderiv{F_{Y_{e}}}{Y_{e}}
+  &=\f{1}{Y_{e}^{n}}, \\
+  \pderiv{F_{Y_{e}}}{\epsilon}
+  &=0, \\
+  \pderiv{F_{Y_{e}}}{\mathcal{J}_{j}}
+  &=\f{\hat{w}_{j}^{(2)}}{S_{Y_{e}}}, \\
+  \pderiv{F_{Y_{e}}}{\bar{\mathcal{J}}_{j}}
+  &=-\f{\hat{w}_{j}^{(2)}}{S_{Y_{e}}}.  
+\end{align}
+From Eq.~\eqref{eq:internalEnergyDiscrete}, the elements of the Jacobian matrix are
+\begin{align}
+  \pderiv{F_{\epsilon}}{Y_{e}}
+  &=0, \\
+  \pderiv{F_{\epsilon}}{\epsilon}
+  &=\f{1}{\epsilon^{n}}, \\
+  \pderiv{F_{\epsilon}}{\mathcal{J}_{j}}
+  &=\f{\hat{w}_{j}^{(3)}}{S_{\epsilon}}, \\
+  \pderiv{F_{\epsilon}}{\bar{\mathcal{J}}_{j}}
+  &=\f{\hat{w}_{j}^{(3)}}{S_{\epsilon}}
+\end{align}
+From Eq.~\eqref{eq:neutrinoDiscreteResidualForm}, the elements of the Jacobian are
+\begin{align}
+  \pderiv{\mathcal{F}_{i}}{Y_{e}}
+  &=\dt\,\Big(\,\pderiv{\big[\chi\big]_{i}}{Y_{e}}\,\mathcal{J}_{i}-\pderiv{\big[\eta\big]_{i}}{Y_{e}}\,\Big), \\
+  \pderiv{\mathcal{F}_{i}}{\epsilon}
+  &=\dt\,\Big(\,\pderiv{\big[\chi\big]_{i}}{\epsilon}\,\mathcal{J}_{i}-\pderiv{\big[\eta\big]_{i}}{\epsilon}\,\Big), \\
+  \pderiv{\mathcal{F}_{i}}{\mathcal{J}_{j}}
+  &=\big(\,1+\dt\,\big[\chi\big]_{i}\,\big)\,\delta_{ij}
+  +\dt\,\Big(\,\pderiv{\big[\chi\big]_{i}}{\mathcal{J}_{j}}\,\mathcal{J}_{i}-\pderiv{\big[\eta\big]_{i}}{\mathcal{J}_{j}}\,\Big), \\
+  \pderiv{\mathcal{F}_{i}}{\bar{\mathcal{J}}_{j}}
+  &=\dt\,\Big(\,\pderiv{\big[\chi\big]_{i}}{\bar{\mathcal{J}}_{j}}\,\mathcal{J}_{i}-\pderiv{\big[\eta\big]_{i}}{\bar{\mathcal{J}}_{j}}\,\Big).  
+\end{align}
+The derivatives of neutrino emissivities and opacities with respect to $Y_{e}$ are
+\begin{align}
+  \pderiv{\big[\eta\big]_{i}}{Y_{e}}
+  &=\big[\chi_{\EC}\big]_{i}^{n}\,\pderiv{\mathcal{J}_{0,i}}{Y_{e}} \nonumber \\
+  &\hspace{12pt}
+  +\sum_{q}w_{q}^{(2)}\,\pderiv{\big[\Phi_{\NES,0}^{\In}\big]_{qi}}{Y_{e}}\,\mathcal{J}_{q}^{n+1}
+  +\sum_{q}w_{q}^{(2)}\,\pderiv{\big[\Phi_{\TP,0}^{\PROD}\big]_{qi}}{Y_{e}}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big) , \\
+  \pderiv{\big[\chi\big]_{i}}{Y_{e}}
+  &=\sum_{q}w_{q}^{(2)}\,\Big\{\,\pderiv{\big[\Phi_{\NES,0}^{\In}\big]_{qi}}{Y_{e}}\,\mathcal{J}_{q}^{n+1}+\pderiv{\big[\Phi_{\NES,0}^{\Out}\big]_{qi}}{Y_{e}}\,\big(1-\mathcal{J}_{q}^{n+1}\big)\,\Big\} \nonumber \\
+  &\hspace{12pt}
+  +\sum_{q}w_{q}^{(2)}\Big\{\,\pderiv{\big[\Phi_{\TP,0}^{\PROD}\big]_{qi}}{Y_{e}}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big)+\pderiv{\big[\Phi_{\TP,0}^{\ANN}\big]_{qi}}{Y_{e}}\,\bar{\mathcal{J}}_{q}^{n+1}\,\Big\}.
+\end{align}
+The derivatives of neutrino emissivities and opacities with respect to $\epsilon$ are
+\begin{align}
+  \pderiv{\big[\eta\big]_{i}}{\epsilon}
+  &=\big[\chi_{\EC}\big]_{i}^{n}\,\pderiv{\mathcal{J}_{0,i}}{\epsilon} \nonumber \\
+  &\hspace{12pt}
+  +\sum_{q}w_{q}^{(2)}\,\pderiv{\big[\Phi_{\NES,0}^{\In}\big]_{qi}}{\epsilon}\,\mathcal{J}_{q}^{n+1}
+  +\sum_{q}w_{q}^{(2)}\,\pderiv{\big[\Phi_{\TP,0}^{\PROD}\big]_{qi}}{\epsilon}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big) , \\
+  \pderiv{\big[\chi\big]_{i}}{\epsilon}
+  &=\sum_{q}w_{q}^{(2)}\,\Big\{\,\pderiv{\big[\Phi_{\NES,0}^{\In}\big]_{qi}}{\epsilon}\,\mathcal{J}_{q}^{n+1}+\pderiv{\big[\Phi_{\NES,0}^{\Out}\big]_{qi}}{\epsilon}\,\big(1-\mathcal{J}_{q}^{n+1}\big)\,\Big\} \nonumber \\
+  &\hspace{12pt}
+  +\sum_{q}w_{q}^{(2)}\Big\{\,\pderiv{\big[\Phi_{\TP,0}^{\PROD}\big]_{qi}}{\epsilon}\,\big(1-\bar{\mathcal{J}}_{q}^{n+1}\big)+\pderiv{\big[\Phi_{\TP,0}^{\ANN}\big]_{qi}}{\epsilon}\,\bar{\mathcal{J}}_{q}^{n+1}\,\Big\}.
+\end{align}
+The derivatives of neutrino emissivities and opacities with respect to $\mathcal{J}_{j}$ are
+\begin{align}
+  \pderiv{\big[\eta\big]_{i}}{\mathcal{J}_{j}}
+  &=w^{(2)}_{j}\,\big[\Phi_{\NES,0}^{\In}\big]_{ji}, \\
+  \pderiv{\big[\chi\big]_{i}}{\mathcal{J}_{j}}
+  &=w^{(2)}_{j}\,\Big(\,\big[\Phi_{\NES,0}^{\In}\big]_{ji}-\big[\Phi_{\NES,0}^{\Out}\big]_{ji}\,\Big).  
+\end{align}
+The derivatives of neutrino emissivities and opacities with respect to $\bar{\mathcal{J}}_{j}$ are
+\begin{align}
+  \pderiv{\big[\eta\big]_{i}}{\bar{\mathcal{J}}_{j}}
+  &=-w_{j}^{(2)}\,\big[\Phi_{\TP,0}^{\PROD}\big]_{ji} , \\
+  \pderiv{\big[\chi\big]_{i}}{\bar{\mathcal{J}}_{j}}
+  &=w_{j}^{(2)}\,\big(\,\big[\Phi_{\TP,0}^{\ANN}\big]_{ji}-\big[\Phi_{\TP,0}^{\PROD}\big]_{ji}\,\big) .
+\end{align}
+
 \bibliographystyle{plain}
@@
 
+\appendix
+
+\section{Kernel Derivatives}
+
+NES and pair kernels are tabulated in terms of temperature $T$ and degeneracy parameter $\eta=\mu_{e}/kT$
+\begin{equation}
+  \Phi=\Phi(T,\eta).  
+\end{equation}
+For solvers based on Newton's method, we need derivatives with respect to internal energy $\epsilon$ and electron fraction $Y_{e}$.  
+\begin{align}
+  d\Phi 
+  &= \Big(\pderiv{\Phi}{T}\Big)_{\eta}\,dT+\Big(\pderiv{\Phi}{\eta}\Big)_{T}\,d\eta \nonumber \\
+  &=\f{1}{kT}\Big(\pderiv{\Phi}{\eta}\Big)_{T}\,\Big(\pderiv{\mu_{e}}{\rho}\Big)_{T,Y_{e}}\,d\rho
+  +\Big\{\,\Big(\pderiv{\Phi}{T}\Big)_{\eta} + \Big(\pderiv{\Phi}{\eta}\Big)_{T}\,\Big[\,\f{1}{kT}\Big(\pderiv{\mu_{e}}{T}\Big)_{\rho,Y_{e}}-\f{\eta}{T}\,\Big]\,\Big\}\,dT \nonumber \\
+  &\hspace{12pt}
+  +\f{1}{kT}\Big(\pderiv{\Phi}{\eta}\Big)_{T}\,\Big(\pderiv{\mu_{e}}{Y_{e}}\Big)_{\rho,T}\,dY_{e},
+  \label{eq:variation_T_Eta}
+\end{align}
+where we used
+\begin{align}
+  d\eta &= \Big(\pderiv{\eta}{\rho}\Big)_{T,Y_{e}}\,d\rho+\Big(\pderiv{\eta}{T}\Big)_{\rho,Y_{e}}\,dT+\Big(\pderiv{\eta}{Y_{e}}\Big)_{\rho,T}\,dY_{e} \nonumber \\
+  &=\f{1}{kT}\Big(\pderiv{\mu_{e}}{\rho}\Big)_{T,Y_{e}}\,d\rho 
+  + \Big[\,\f{1}{kT}\Big(\pderiv{\mu_{e}}{T}\Big)_{\rho,Y_{e}}-\f{\eta}{T}\,\Big]\,dT + \f{1}{kT}\Big(\pderiv{\mu_{e}}{Y_{e}}\Big)_{\rho,T}\,dY_{e}.  
+\end{align}
+
+\begin{align}
+  d\Phi
+  &=\Big(\pderiv{\Phi}{\epsilon}\Big)_{Y_{e}}\,d\epsilon+\Big(\pderiv{\Phi}{Y_{e}}\Big)_{\epsilon}\,dY_{e} \nonumber \\
+  &=\Big(\pderiv{\Phi}{\epsilon}\Big)_{Y_{e}}\,\Big(\pderiv{\epsilon}{\rho}\Big)_{T,Y_{e}}\,d\rho
+  +\Big(\pderiv{\Phi}{\epsilon}\Big)_{Y_{e}}\,\Big(\pderiv{\epsilon}{T}\Big)_{\rho,Y_{e}}\,dT \nonumber \\
+  &\hspace{12pt}
+  +\Big[\,\Big(\pderiv{\Phi}{\epsilon}\Big)_{Y_{e}}\,\Big(\pderiv{\epsilon}{Y_{e}}\Big)_{\rho,T}+\Big(\pderiv{\Phi}{Y_{e}}\Big)_{\epsilon}\,\Big]\,dY_{e},
+  \label{eq:variation_Epsilon_Ye}
+\end{align}
+where we used
+\begin{equation}
+  d\epsilon
+  =\Big(\pderiv{\epsilon}{\rho}\Big)_{T,Y_{e}}\,d\rho+\Big(\pderiv{\epsilon}{T}\Big)_{\rho,Y_{e}}\,dT+\Big(\pderiv{\epsilon}{Y_{e}}\Big)_{\rho,T}\,dY_{e}
+\end{equation}
+Comparing Eq.~\eqref{eq:variation_T_Eta} and Eq.~\eqref{eq:variation_Epsilon_Ye}, we have
+\begin{align}
+  \Big(\pderiv{\Phi}{T}\Big)_{\eta} + \Big[\,\f{1}{kT}\Big(\pderiv{\mu_{e}}{T}\Big)_{\rho,Y_{e}}-\f{\eta}{T}\,\Big]\,\Big(\pderiv{\Phi}{\eta}\Big)_{T}
+  &=\Big(\pderiv{\epsilon}{T}\Big)_{\rho,Y_{e}}\,\Big(\pderiv{\Phi}{\epsilon}\Big)_{Y_{e}}, \\
+  \f{1}{kT}\Big(\pderiv{\mu_{e}}{Y_{e}}\Big)_{\rho,T}\,\Big(\pderiv{\Phi}{\eta}\Big)_{T}
+  &=\Big(\pderiv{\epsilon}{Y_{e}}\Big)_{\rho,T}\,\Big(\pderiv{\Phi}{\epsilon}\Big)_{Y_{e}}+\Big(\pderiv{\Phi}{Y_{e}}\Big)_{\epsilon}
+\end{align}
+Solving for $(\partial\Phi/\partial\epsilon)_{Y_{e}}$ and $(\partial\Phi/\partial Y_{e})_{\epsilon}$ we obtain
+\begin{align}
+  \Big(\pderiv{\Phi}{\epsilon}\Big)_{Y_{e}}
+  &=\Big[\,\f{1}{kT}\Big(\pderiv{\mu_{e}}{T}\Big)_{\rho,Y_{e}}-\f{\eta}{T}\,\Big]/\Big(\pderiv{\epsilon}{T}\Big)_{\rho,Y_{e}}\,\Big(\pderiv{\Phi}{\eta}\Big)_{T} + \Big(\pderiv{\epsilon}{T}\Big)_{\rho,Y_{e}}^{-1}\,\Big(\pderiv{\Phi}{T}\Big)_{\eta}, \\
+  \Big(\pderiv{\Phi}{Y_{e}}\Big)_{\epsilon}
+  &=\Big\{\,\f{1}{kT}\Big(\pderiv{\mu_{e}}{Y_{e}}\Big)_{\rho,T} - \Big(\pderiv{\epsilon}{Y_{e}}\Big)_{\rho,T}\,\Big[\,\f{1}{kT}\Big(\pderiv{\mu_{e}}{T}\Big)_{\rho,Y_{e}}-\f{\eta}{T}\,\Big]/\Big(\pderiv{\epsilon}{T}\Big)_{\rho,Y_{e}}\,\Big\}\,\Big(\pderiv{\Phi}{\eta}\Big)_{T} \nonumber \\
+  &\hspace{12pt}
+  - \Big\{\,\Big(\pderiv{\epsilon}{Y_{e}}\Big)_{\rho,T}/\Big(\pderiv{\epsilon}{T}\Big)_{\rho,Y_{e}}\,\Big\}\,\Big(\pderiv{\Phi}{T}\Big)_{\eta}.
+\end{align}
+
 \end{document}

### 2020-11-09 Documents/M1/MeshRefinement/MeshRefinement.tex

\documentclass[10pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{yhmath}
\usepackage{natbib}
\usepackage{../../definitions}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

\newcommand{\ee}[1]{{\color{blue} EE:~#1}}
\newcommand{\Lo}{\textsc{L}}
\newcommand{\Hi}{\textsc{H}}
\newcommand{\trans}{\textsc{T}}
\newcommand{\dx}{\Delta x}

\newtheorem{define}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{theorem}{Theorem}

\begin{document}

\title{Mesh Refinement and Derefinement of Two-Moment Radiation Fields}
\author{Eirik Endeve et al.}

\maketitle

\begin{abstract}
  We consider refinement and coarsening of polynomial representations.  
  We basically follow Schaal et al.~\cite{schaal_etal_2015}.  
\end{abstract}

\tableofcontents

\section{Preliminaries}

\subsection{Coarse and Fine Elements}

Consider the $d$-dimensional (coarse) element $\bK$
\begin{equation}
  \vect{K} = \big\{\,\vect{x} : x^{i} \in K^{i} := (x_{\Lo}^{i},x_{\Hi}^{i}), i = 1,\ldots,d \,\big\}.  
\end{equation}
We also define the unit reference element $\vect{I}$
\begin{equation}
  \vect{I} = \big\{\,\vect{\eta} : \eta^{i} \in (-1/2,+1/2), i = 1,\ldots,d \,\big\},
\end{equation}
and the standard mapping $x^{i}(\eta^{i})=x_{\Lo}^{i}+\eta^{i}\,\dx^{i}$, where $\dx^{i}=x_{\Hi}^{i}-x_{\Lo}^{i}$.  
We also define $|\vect{K}|=\prod_{i=1}^{d}\dx^{i}$.

The element $\vect{K}$ is to be refined into $N$ (finer) elemets $\vect{k}_{(j)}$
\begin{equation}
  \vect{k}_{(j)} = \big\{\,\vect{x} : x^{i} \in k_{(j)}^{i} := (x_{\Lo,(j)}^{i},x_{\Hi,(j)}^{i}), i = 1,\ldots,d\,\big\},
\end{equation}
where
\begin{equation}
  \vect{K} = \cup_{j=1}^{N}\vect{k}_{(j)}.  
\end{equation}
We will also consider derefinement (coarsening).  
The reference element associated with $\vect{k}_{(j)}$ is denoted $\vect{i}_{(j)}$
\begin{equation}
  \vect{i}_{(j)} = \big\{\,\vect{\xi} : \xi^{i} \in (-1/2,+1/2), i = 1,\ldots,d \,\big\},
\end{equation}
with mapping $x^{i}(\xi^{i})=x_{\Lo,(j)}^{i}+\xi^{i}\,\dx_{(j)}^{i}$, where $\dx_{(j)}^{i}=x_{\Hi,(j)}^{i}-x_{\Lo,(j)}^{i}$.  
We also let $|\vect{k}_{(j)}|=\prod_{i=1}^{d}\dx_{(j)}^{i}$.

\subsection{Approximation Spaces}

On $\vect{K}$, we denote the approximation space by
\begin{equation}
  \mathbb{V}^{k} = \big\{\,v_{h} : v_{h}\big|_{\vect{K}}\in\mathbb{Q}^{k}(\vect{K})\,\big\}
\end{equation}
where $\mathbb{Q}^{k}$ is constructed from the tensor product of one-dimensional polynomials of degree at most $k$.  
Similarly, the approximation space on $\vect{k}_{(j)}$ is
\begin{equation}
  \mathbb{V}_{(j)}^{k} = \big\{\,v_{h} : v_{h}\big|_{\vect{k}_{(j)}}\in\mathbb{Q}^{k}(\vect{k}_{(j)})\,\big\}.  
\end{equation}

\subsection{Polynomial Representations}

On the coarse element $\vect{K}$, the physical (conserved) variable $U$ is approximated by $U_{h}$
\begin{equation}
  U_{h}(\vect{x}) = \sum_{i=1}^{M}U_{i}\,\ell_{i}(\vect{x}),
\end{equation}
where $\ell_{i}\in\mathbb{V}^{k}$.  
The vector of expansion coefficients in the coarse element $\vect{K}$ is denoted $\vect{U}=(U_{1},\ldots,U_{M})^{\trans}$.  
Similarly, in each fine element $\vect{k}_{(j)}$, the same variable is approximated by $u_{h}^{(j)}$
\begin{equation}
  u_{h}^{(j)}(\vect{x})=\sum_{i=1}^{M}u_{i}^{(j)}\ell_{i}^{(j)}(\vect{x}),
\end{equation}
where $\ell_{i}^{(j)}\in\mathbb{V}_{(j)}^{k}$.  
We denote the vector of expansion coefficients in the fine elements by $\vect{u}^{(j)}=(u_{1}^{(j)},\ldots,u_{M}^{(j)})^{\trans}$ and the basis by $\vect{\ell}^{(j)}(\vect{x})=(\ell_{1}^{(j)}(\vect{x}),\ldots,\ell_{N}^{(j)}(\vect{x}))^{\trans}$.

\section{Refinement}

Upon mesh refinement, the representation of the variable $U$ on the fine element $\vect{k}_{(j)}$ is obtained from solving the minimization problem
\begin{equation}
  \min_{\vect{u}^{(j)}}\int_{\vect{k}_{(j)}}\big(\,U_{h}(\vect{x})-u_{h}^{(j)}(\vect{x})\,\big)^{2}\,d\vect{x}.  
\end{equation}
This gives
\begin{equation}
  \int_{\vect{k}_{(j)}}u_{h}^{(j)}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,d\vect{x}
  =\int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,d\vect{x},\quad i=1,\ldots,M.  
  \label{eq:refinementProjection}
\end{equation}
Evaluating the left-hand side of Eq.~\eqref{eq:refinementProjection} gives
\begin{equation}
  \int_{\vect{k}_{(j)}}u_{h}^{(j)}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,d\vect{x}
  =|\vect{k}_{(j)}|\,w_{i}\,u_{i}^{(j)}.  
\end{equation}
\ee{Need to elaborate on this result.}
Evaluating the right-hand side of Eq.~\eqref{eq:refinementProjection} gives
\begin{equation}
  \int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,d\vect{x}
  =|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\eta})\,\ell_{k}(\vect{\xi}(\vect{\eta}))\,d\vect{\eta}\,U_{k}.
\end{equation}
Defining the projection matrix $\mathcal{P}^{(j)}$, with components
\begin{equation}
  \mathcal{P}_{ik}^{(j)} = \int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\eta})\,\ell_{k}(\vect{\xi}(\vect{\eta}))\,d\vect{\eta},
  \label{eq:refinementProjectionMatrix}
\end{equation}
and the diagonal matrix $\mathcal{D}=\mbox{diag}(w_{1},\ldots,w_{M})$, the components of the expansion in the refined element $\vect{k}_{(j)}$ are obtained from the matrix-vector product
\begin{equation}
  \mathcal{D}\,\vect{u}^{(j)} = \mathcal{P}^{(j)}\,\vect{U}.  
\end{equation}
The projection matrix can be computed once and stored at program startup.

\section{Coarsening}

In $\vect{K}$, using the fine representations, we have
\begin{equation}
  u_{h}(\vect{x}) = \sum_{j=1}^{N}\chi(\vect{k}_{(j)})\,u_{h}^{(j)}(\vect{x}),
\end{equation}
where $\chi$ is the indicator function.  
Thus, upon coarsening, the representation of the variable $U$ in the coarse element is obtained by solving the minimization problem
\begin{equation}
  \min_{\vect{U}}\int_{\vect{K}}\big(\,U_{h}(\vect{x})-u_{h}(\vect{x})\,\big)^{2}\,d\vect{x}.
\end{equation}
This gives
\begin{equation}
  \int_{\vect{K}}U_{h}(\vect{x})\,\ell_{i}(\vect{x})\,d\vect{x}
  =\int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,d\vect{x}.  
  \label{eq:coarseningProjection}
\end{equation}
Evaluating the left-hand side of Eq.~\eqref{eq:coarseningProjection} gives
\begin{equation}
  \int_{\vect{K}}U_{h}(\vect{x})\,\ell_{i}(\vect{x})\,d\vect{x}
  =|\vect{K}|\,w_{i}\,U_{i}.  
\end{equation}
Evaluating the right-hand side of Eq.~\eqref{eq:coarseningProjection} gives
\begin{equation}
  \int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,d\vect{x}
  =\sum_{j=1}^{N}|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}(\vect{\xi}(\vect{\eta}))\,\ell_{k}(\vect{\eta})\,d\vect{\eta}\,u_{k}^{(j)}.
\end{equation}
Thus, 
\begin{equation}
  \mathcal{D}\,\vect{U}=\sum_{j=1}^{N}\f{|\vect{k}_{(j)}|}{|\vect{K}|}
  \big(\mathcal{P}^{(j)}\big)^{\trans}\,\vect{u}^{(j)}.  
\end{equation}
For a refinement factor of $2$, $|\vect{k}_{(j)}|/|\vect{K}|=2^{-d}$.

\bibliographystyle{plain}
\bibliography{../../References/references.bib}

\end{document}

### 2020-11-09 Documents/M1/SubcellReconstruction/SubcellReconstruction.tex

\documentclass[10pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{yhmath}
\usepackage{natbib}
\usepackage{../../definitions}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

\newcommand{\ee}[1]{{\color{blue} EE:~#1}}
\newcommand{\Lo}{\textsc{L}}
\newcommand{\Hi}{\textsc{H}}
\newcommand{\trans}{\textsc{T}}
\newcommand{\dx}{\Delta x}

\newtheorem{define}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{theorem}{Theorem}

\begin{document}

\title{Subcell Projection and Reconstruction}
\author{Eirik Endeve et al.}

\maketitle

\begin{abstract}
  We consider subcell projection and reconstruction to move between discontinuous Galerkin (DG) and finite volume (FV) representations.  
  When the FV variables are represented on a subgrid with the same number of degrees of freedom as the DG representation, we can move between representations without loss of information.  
  We basically follow Dumbser et al. (2014, {\it JCP}, {\bf 278}, 47).  
\end{abstract}

\tableofcontents

\section{Preliminaries}

Consider an element $\vect{K}\subset\bbR^{d}$ where the DG representation is denoted $u_{h}(\vect{x},t)\in\bbV^{k}$, where $\bbV^{k}$ is constructed from the tensor product of one-dimensional polynomials of maximal degree $k$
\begin{equation}
  u_{h}(\vect{x},t)=\sum_{j=1}^{(k+1)^{d}}u_{j}(t)\,\Phi_{j}(\vect{x}).
  \label{eq:dgRepresentation}
\end{equation}
Next, consider dividing the element $\vect{K}$ into a subgrid $S$ of $(k+1)^{d}$ nonoverlapping FV cells $S_{j}$, $S=\cup_{j=1}^{(k+1)^{d}} S_{j}$, so that $K\setminus S=\emptyset$; see Figure~\ref{fig:ElementSubgrid} for an example in two spatial dimensions ($d=2$) and $k=1$.  
On the subgrid, the representation is given by piecewise constants (cell averages)
\begin{equation}
  v_{h}(\vect{x},t)=\sum_{j=1}^{(k+1)^{d}}\chi(S_{j})\,v_{j}(t),
  \label{eq:piecewiseConstants}
\end{equation}
where $v_{j}(t)$ is the cell average in subgrid cell $S_{j}$ and the $\chi(S_{j})$ is the indicator function on $S_{j}$.

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{./ElementSubgrid}
   \caption{Division of an element $\vect{K}$ into a subgrid of finite volume cells in two spatial dimensions ($d=2$) using DG polynomials of maximal degree $k=1$.}
  \label{fig:ElementSubgrid}
\end{figure}

\section{FV to DG Representation (Reconstruction)}

Knowing the cell averages $v_{j}$ (we suppress time dependence from here on), we reconstruct the DG representation $u_{h}$ by requiring that
\begin{equation}
  \f{1}{|S_{i}|}\int_{S_{i}}u_{h}(\vect{x})\,d\vect{x}
  =\f{1}{|S_{i}|}\int_{S_{i}}v_{h}(\vect{x})\,d\vect{x}=v_{i}, \forall~S_{i}\in S.
\end{equation}
With the definition in Eq.~\eqref{eq:dgRepresentation}, this gives
\begin{equation}
  R^{-1}\,\vect{u} = \vect{v},
\end{equation}
where $\vect{u}=(u_{1},\ldots,u_{(k+1)^{d}})^{T}$, $\vect{v}=(v_{1},\ldots,v_{(k+1)^{d}})^{T}$, and the components of the $(k+1)^{d}\times(k+1)^{d}$ inverse reconstruction matrix are
\begin{equation}
  R_{ij}^{-1}=\f{1}{|S_{i}|}\int_{S_{i}}\Phi_{j}(\vect{x})\,d\vect{x}.  
\end{equation}
The reconstruction step amounts inverting to find
\begin{equation}
  \vect{u} = R\,\vect{v}.
\end{equation}

\section{DG to FV Representation (Projection)}

Knowing the DG representation $u_{h}(\vect{x})$, we can easily compute the cell averages for the finite volume representation
\begin{equation}
  v_{i} = \f{1}{|S_{i}|}\int_{S_{i}}\,u_{h}(\vect{x})\,d\vect{x} = \f{1}{|S_{i}|}\sum_{j=1}^{(k+1)^{d}}\int_{S_{i}}\Phi_{j}(\vect{x})\,d\vect{x}\,u_{j},
\end{equation}
which can be written as
\begin{equation}
  \vect{v} = P\,\vect{u},
\end{equation}
where the components of the $(k+1)^{d}\times(k+1)^{d}$ projection matrix $P$ are
\begin{equation}
  P_{ij} = \f{1}{|S_{i}|}\int_{S_{i}}\Phi_{j}(\vect{x})\,d\vect{x}.  
\end{equation}
From the definitions above, it is obvious that $R\,P = I$; i.e., we do not lose any accuracy when switching between DG and FV representations.  
The reconstruction and projection matrices are plotted in Figure~\ref{fig:matrices} for $d=2$, $k=1$.  
\begin{figure}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{./ReconstructionMatrix} &
    \includegraphics[width=0.5\textwidth]{./ProjectionMatrix}
  \end{tabular}
   \caption{Reconstruction matrix $R$ (left) and projection matrix $P$ for two spatial dimensions ($d=2$) using DG polynomials of maximal degree $k=1$.}
  \label{fig:matrices}
\end{figure}

\end{document}

### 2020-11-10 Documents/M1/MeshRefinement/MeshRefinement.tex
Added curvilinear coordinates to MeshRefinement documentation

@@
 
+\section{Curvilinear Coordinates}
+
+\subsection{Preliminaries}
+
+The introduction of curvilinear coordinates doesn't change any of the preliminaries.
+
+\subsection{Refinement}
+
+The refinement
+section does change, in that when demanding equality of the cell averages, the metric determinant
+must be taken into account, i.e., Eq.~\eqref{eq:refinementProjection} becomes
+\begin{equation}
+  \int_{\vect{k}_{(j)}}u_{h}^{(j)}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
+  =\int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x},\quad i=1,\ldots,M.
+  \label{eq:refinementProjection_CC}
+\end{equation}
+Evaluating the left-hand side of Eq.~\eqref{eq:refinementProjection_CC} gives
+\begin{equation}
+  \int_{\vect{k}_{(j)}}u_{h}^{(j)}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
+  =|\vect{k}_{(j)}|\,w_{i}\,u_{i}^{(j)}\,\sqrt{\gamma_{i}}.
+  \end{equation}
+  Evaluating the right-hand side of Eq.~\eqref{eq:refinementProjection_CC} gives
+  \sd{Why isn't this integrated over $\vect{\xi}$?}
+  \footnote{I found  $\int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
+  =|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\xi})\,\ell_{k}(\vect{\eta}(\vect{\xi}))\,\sqrt{\gamma}\,d\vect{\xi}\,U_{k}$}
+  \begin{equation}
+  \int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
+  =|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\eta})\,\ell_{k}(\vect{\xi}(\vect{\eta}))\,\sqrt{\gamma}\,d\vect{\eta}\,U_{k}.
+\end{equation}
+Defining the projection matrix, $P^{\left(j\right)}_{\gamma}$, with components
+\begin{equation}
+P^{\left(j\right)}_{ik,\gamma}
+=\int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\eta})\,\ell_{k}(\vect{\xi}(\vect{\eta}))\,\sqrt{\gamma}\,d\vect{\eta},
+\end{equation}
+and the diagonal matrix $\mathcal{D}_{\gamma}
+=\mbox{diag}(\sqrt{\gamma_{1}}\,w_{1},\ldots,\sqrt{\gamma_{M}}\,w_{M})$, the components of the expansion in the refined element $\vect{k}_{(j)}$ are obtained from the matrix-vector product
+\begin{equation}
+  \mathcal{D}_{\gamma}\,\vect{u}^{(j)} = \mathcal{P}^{(j)}_{\gamma}\,\vect{U}.
+\end{equation}
+Since $\gamma=\gamma\left(t\right)$, $\mathcal{P}^{\left(j\right)}_{\gamma}$ and $\cD_{\gamma}$
+must be computed at each time step.
+
+\subsection{Coarsening}
+
+As with refinement, Eq.~\eqref{eq:coarseningProjection} becomes
+\begin{equation}
+  \int_{\vect{K}}U_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
+  =\int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}.
+  \label{eq:coarseningProjection_CC}
+\end{equation}
+Evaluating the left-hand side of Eq.~\eqref{eq:coarseningProjection_CC} gives
+\begin{equation}
+  \int_{\vect{K}}U_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
+  =|\vect{K}|\,w_{i}\,U_{i}\,\sqrt{\gamma_{i}}.
+\end{equation}
+Evaluating the right-hand side of Eq.~\eqref{eq:coarseningProjection_CC} gives
+  \sd{Why isn't this integrated over $\vect{\xi}$?}
+\footnote{I found $\int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
+  =\sum_{j=1}^{N}|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}(\vect{\eta}(\vect{\xi}))\,\ell_{k}^{\left(j\right)}(\vect{\xi})\,\sqrt{\gamma}\,d\vect{\xi}\,u_{k}^{(j)}$}
+\begin{equation}
+  \int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
+  =\sum_{j=1}^{N}|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}(\vect{\xi}(\vect{\eta}))\,\ell_{k}(\vect{\eta})\,\sqrt{\gamma}\,d\vect{\eta}\,u_{k}^{(j)}.
+\end{equation}
+Thus,
+\begin{equation}
+  \mathcal{D}_{\gamma}\,\vect{U}=\sum_{j=1}^{N}\f{|\vect{k}_{(j)}|}{|\vect{K}|}
+  \big(\mathcal{P}_{\gamma}^{(j)}\big)^{\trans}\,\vect{u}^{(j)}.
+\end{equation}
+For a refinement factor of $2$, $|\vect{k}_{(j)}|/|\vect{K}|=2^{-d}$.
+
+\subsection{Mapping $\eta\rightarrow\xi$}
+For a 1D problem with two subcells, the mapping from the coarse reference element, coordinatized
+by $\eta$, to the fine reference element, coordinatized by $\xi$, is
+\begin{equation}
+\xi\left(\eta\right)=\frac{1}{2}\left(\eta+\frac{1}{2}\left(-1\right)^{k}\right),\hspace{1em}k=1,2.
+\end{equation}
+
 \bibliographystyle{plain}

### 2024-11-25 Documents/Euler/Astronum_2018/JPCSLaTeXGuidelines.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

\documentclass[a4paper]{jpconf}
\usepackage{graphicx}
\begin{document}
\title{Preparing a paper using \LaTeXe\ for publication in \jpcs}

\author{Jacky Mucklow}

\address{Production Editor, \jpcs, \iopp, Dirac House, Temple Back, Bristol BS1~6BE, UK}

\ead{jacky.mucklow@iop.org}

\begin{abstract}
All articles {\it must} contain an abstract. This document describes the  preparation of a conference paper to be published in \jpcs\ using \LaTeXe\ and the \cls\ class file. The abstract text should be formatted using 10 point font and indented 25 mm from the left margin. Leave 10 mm space after the abstract before you begin the main text of your article. The text of your article should start on the same page as the abstract. The abstract follows the addresses and should give readers concise information about the content of the article and indicate the main results obtained and conclusions drawn. As the abstract is not part of the text it should be complete in itself; no table numbers, figure numbers, references or displayed mathematical expressions should be included. It should be suitable for direct inclusion in abstracting services and should not normally exceed 200 words. The abstract should generally be restricted to a single paragraph. Since contemporary information-retrieval systems rely heavily on the content of titles and abstracts to identify relevant articles in literature searches, great care should be taken in constructing both.
\end{abstract}

\section{Introduction}
These guidelines show how to prepare articles for publication in \jpcs\ using \LaTeX\ so they can be published quickly and accurately. Articles will be refereed by the \corg s but the accepted PDF will be published with no editing, proofreading or changes to layout. It is, therefore, the author's responsibility to ensure that the content and layout are correct.  This document has been prepared using \cls\ so serves as a sample document. The class file and accompanying documentation are available from \verb"http://jpcs.iop.org".

\section{Preparing your paper}
\verb"jpconf" requires \LaTeXe\ and  can be used with other package files such
as those loading the AMS extension fonts 
\verb"msam" and \verb"msbm" (these fonts provide the 
blackboard bold alphabet and various extra maths symbols as well as 
symbols useful in figure captions); an extra style file \verb"iopams.sty" is 
provided to load these packages and provide extra definitions for bold Greek letters. 
\subsection{Headers, footers and page numbers}
Authors should {\it not} add headers, footers or page numbers to the pages of their article---they will
be added by \iopp\ as part of the production process.

\subsection{{\cls\ }package options}
The \cls\ class file has two options `a4paper' and `letterpaper':
\begin{verbatim}
\documentclass[a4paper]{jpconf}
\end{verbatim}

or \begin{verbatim}
\documentclass[letterpaper]{jpconf}
\end{verbatim}

\begin{center}
\begin{table}[h]
\caption{\label{opt}\cls\ class file options.}
%\footnotesize\rm
\centering
\begin{tabular}{@{}*{7}{l}}
\br
Option&Description\\
\mr
\verb"a4paper"&Set the paper size and margins for A4 paper.\\
\verb"letterpaper"&Set the paper size and margins for US letter paper.\\
\br
\end{tabular}
\end{table}
\end{center}

The default paper size is A4 (i.e., the default option is {\tt a4paper}) but this can be changed to Letter by 
using \verb"\documentclass[letterpaper]{jpconf}". It is essential that you do not put macros into the text which alter the page dimensions.

\section{The title, authors, addresses and abstract} 
The code for setting the title page information is slightly different from
the normal default in \LaTeX\ but please follow these instructions as carefully as possible so all articles within a conference have the same style to the title page. 
The title is set in bold unjustified type using the command
\verb"\title{#1}", where \verb"#1" is the title of the article. The
first letter of the title should be capitalized with the rest in lower case. 
The next information required is the list of all authors' names followed by 
the affiliations. For the authors' names type \verb"\author{#1}", 
where \verb"#1" is the 
list of all authors' names. The style for the names is initials then
surname, with a comma after all but the last 
two names, which are separated by `and'. Initials should {\it not} have 
full stops. First names may be used if desired. The command \verb"\maketitle" is not
required.

The addresses of the authors' affiliations follow the list of authors. 
Each address should be set by using
\verb"\address{#1}" with the address as the single parameter in braces. 
If there is more 
than one address then a superscripted number, followed by a space, should come at the start of
each address. In this case each author should also have a superscripted number or numbers following their name to indicate which address is the appropriate one for them.

Please also provide e-mail addresses for any or all of the authors using an \verb"\ead{#1}" command after the last address. \verb"\ead{#1}" provides the text Email: so \verb"#1" is just the e-mail address or a list of emails.

The abstract follows the addresses and
should give readers concise information about the content 
of the article and should not normally exceed 200 
words. {\bf All articles must include an abstract}. To indicate the start 
of the abstract type \verb"\begin{abstract}" followed by the text of the 
abstract.  The abstract should normally be restricted 
to a single paragraph and is terminated by the command
\verb"\end{abstract}"

\subsection{Sample coding for the start of an article}
\label{startsample}
The code for the start of a title page of a typical paper might read:
\begin{verbatim}
\title{The anomalous magnetic moment of the 
neutrino and its relation to the solar neutrino problem}

\author{P J Smith$^1$, T M Collins$^2$, 
R J Jones$^{3,}$\footnote[4]{Present address:
Department of Physics, University of Bristol, Tyndalls Park Road, 
Bristol BS8 1TS, UK.} and Janet Williams$^3$}

\address{$^1$ Mathematics Faculty, Open University, 
Milton Keynes MK7~6AA, UK}
\address{$^2$ Department of Mathematics, 
Imperial College, Prince Consort Road, London SW7~2BZ, UK}
\address{$^3$ Department of Computer Science, 
University College London, Gower Street, London WC1E~6BT, UK}

\ead{williams@ucl.ac.uk}

\begin{abstract}
The abstract appears here.
\end{abstract}
\end{verbatim}

\section{The text}
The text of the article should should be produced using standard \LaTeX\ formatting. Articles may be divided into sections and subsections, but the length limit provided by the \corg\ should be adhered to.

\subsection{Acknowledgments}
Authors wishing to acknowledge assistance or encouragement from 
colleagues, special work by technical staff or financial support from 
organizations should do so in an unnumbered Acknowledgments section 
immediately following the last numbered section of the paper. The 
command \verb"\ack" sets the acknowledgments heading as an unnumbered
section.

\subsection{Appendices}
Technical detail that it is necessary to include, but that interrupts 
the flow of the article, may be consigned to an appendix. 
Any appendices should be included at the end of the main text of the paper, after the acknowledgments section (if any) but before the reference list.
If there are two or more appendices they will be called Appendix A, Appendix B, etc. 
Numbered equations will be in the form (A.1), (A.2), etc,
figures will appear as figure A1, figure B1, etc and tables as table A1,
table B1, etc.

The command \verb"\appendix" is used to signify the start of the
appendixes. Thereafter \verb"\section", \verb"\subsection", etc, will 
give headings appropriate for an appendix. To obtain a simple heading of 
`Appendix' use the code \verb"\section*{Appendix}". If it contains
numbered equations, figures or tables the command \verb"\appendix" should
precede it and \verb"\setcounter{section}{1}" must follow it.

\section{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the online version of \jpcs\ references will be linked to their original source or to the article within a secondary service such as INSPEC or ChemPort wherever possible. To facilitate this linking extra care should be taken when preparing reference lists.

Two different styles of referencing are in common use: the Harvard alphabetical system and the Vancouver numerical system.  For \jpcs, the Vancouver numerical system is preferred but authors should use the Harvard alphabetical system if they wish to do so. In the numerical system references are numbered sequentially throughout the text within square brackets, like this [2], and one number can be used to designate several references.

\subsection{Using \BibTeX}
We highly recommend the {\ttfamily\textbf\selectfont iopart-num} \BibTeX\ package by Mark~A~Caprio \cite{iopartnum}, which is included with this documentation.

\subsection{Reference lists}
A complete reference should provide the reader with enough information to locate the article concerned, whether published in print or electronic form, and should, depending on the type of reference, consist of:

\begin{itemize}
\item name(s) and initials;
\item date published;
\item title of journal, book or other publication; 
\item titles of journal articles may also be included (optional);
\item volume number;
\item editors, if any;
\item town of publication and publisher in parentheses for {\it books};
\item the page numbers.
\end{itemize}

Up to ten authors may be given in a particular reference; where 
there are more than ten only the first should be given followed by 
`{\it et al}'. If an author is unsure of a particular journal's abbreviated title it is best to leave the title in 
full. The terms {\it loc.\ cit.\ }and {\it ibid.\ }should not be used. 
Unpublished conferences and reports should generally not be included 
in the reference list and articles in the course of publication should 
be entered only if the journal of publication is known. 
A thesis submitted for a higher degree may be included 
in the reference list if it has not been superseded by a published 
paper and is available through a library; sufficient information 
should be given for it to be traced readily.

\subsection{Formatting reference lists}
Numeric reference lists should contain the references within an unnumbered section (such as \verb"\section*{References}"). The 
reference list itself is started by the code 
\verb"\begin{thebibliography}{<num>}", where \verb"<num>" is the largest
number in the reference list and is completed by
\verb"\end{thebibliography}". 
Each reference starts with \verb"\bibitem{<label>}", where `label' is the label used for cross-referencing. Each \verb"\bibitem" should only contain a reference to a single article (or a single article and a preprint reference to the same article).  When one number actually covers a group of two or more references to different articles, \verb"\nonum"
should replace \verb"\bibitem{<label>}" at
the start of each reference in the group after the first.

For an alphabetic reference list use \verb"\begin{thereferences}" ... \verb"\end{thereferences}" instead of the
`thebibliography' environment and each reference can be start with just \verb"\item" instead of \verb"\bibitem{label}"
as cross referencing is less useful for alphabetic references.

\subsection {References to printed journal articles}
A normal reference to a journal article contains three changes of font (see table \ref{jfonts}) and is constructed as follows:

\begin{itemize}
\item the authors should be in the form surname (with only the first letter capitalized) followed by the initials with no periods after the initials. Authors should be separated by a comma except for the last two which should be separated by `and' with no comma preceding it;
\item the article title (if given) should be in lower case letters, except for an initial capital, and should follow the date;
\item the journal title is in italic and is abbreviated. If a journal has several parts denoted by different letters the part letter should be inserted after the journal in Roman type, e.g. {\it Phys. Rev.} A;
\item the volume number should be in bold type;
\item both the initial and final page numbers should be given where possible. The final page number should be in the shortest possible form and separated from the initial page number by an en rule `-- ', e.g. 1203--14, i.e. the numbers `12' are not repeated.
\end{itemize}

A typical (numerical) reference list might begin

\medskip
\begin{thebibliography}{9}
\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
{\it J. Appl. Phys}. {\bf 87} 965 
\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
{\it Electron. Lett.} {\bf 32} 1105 
\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
{\it J. Appl. Phys.} {\bf 83} 826 
\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
\end{thebibliography}
\smallskip

\noindent which would be obtained by typing

\begin{verbatim}
\begin{\thebibliography}{9}
\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
{\it J. Appl. Phys}. {\bf 87} 965 
\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
{\it Electron. Lett.} {\bf 32} 1105 
\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
{\it J. Appl. Phys.} {\bf 83} 826 
\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
\end{\thebibliography}
\end{verbatim}

\begin{center}
\begin{table}[h]
\centering
\caption{\label{jfonts}Font styles for a reference to a journal article.} 
\begin{tabular}{@{}l*{15}{l}}
\br
Element&Style\\
\mr
Authors&Roman type\\
Date&Roman type\\
Article title (optional)&Roman type\\
Journal title&Italic type\\
Volume number&Bold type\\
Page numbers&Roman type\\
\br
\end{tabular}
\end{table}
\end{center}

\subsection{References to \jpcs\ articles}
Each conference proceeding published in \jpcs\ will be a separate {\it volume}; 
references should follow the style for conventional printed journals. For example:\vspace{6pt}
\numrefs{1}
\item Douglas G 2004 \textit{J. Phys.: Conf. Series} \textbf{1} 23--36
\endnumrefs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{References to preprints}
For preprints there are two distinct cases:
\renewcommand{\theenumi}{\arabic{enumi}}
\begin{enumerate}
\item Where the article has been published in a journal and the preprint is supplementary reference information. In this case it should be presented as:
\medskip
\numrefs{1}
\item Kunze K 2003 T-duality and Penrose limits of spatially homogeneous and inhomogeneous cosmologies {\it Phys. Rev.} D {\bf 68} 063517 ({\it Preprint} gr-qc/0303038)
\endnumrefs
\item Where the only reference available is the preprint. In this case it should be presented as
\medskip
\numrefs{1}
\item Milson R, Coley A, Pravda V and Pravdova A 2004 Alignment and algebraically special tensors {\it Preprint} gr-qc/0401010
\endnumrefs
\end{enumerate}

\subsection{References to electronic-only journals}
In general article numbers are given, and no page ranges, as most electronic-only journals start each article on page 1.

\begin{itemize} 
\item For {\it New Journal of Physics} (article number may have from one to three digits)
\numrefs{1}
\item Fischer R 2004 Bayesian group analysis of plasma-enhanced chemical vapour deposition data {\it New. J. Phys.} {\bf 6} 25 
\endnumrefs
\item For SISSA journals the volume is divided into monthly issues and these form part of the article number

\numrefs{2}
\item Horowitz G T and Maldacena J 2004 The black hole final state {\it J. High Energy Phys.}  	JHEP02(2004)008
\item Bentivegna E, Bonanno A and Reuter M 2004 Confronting the IR fixed point cosmology 	with 	high-redshift observations {\it J. Cosmol. Astropart. Phys.} JCAP01(2004)001  
\endnumrefs
\end{itemize}

\subsection{References to books, conference proceedings and reports}
References to books, proceedings and reports are similar to journal references, but have 
only two changes of font (see table~\ref{book}).

\begin{table}
\centering
\caption{\label{book}Font styles for references to books, conference proceedings and reports.}
\begin{tabular}{@{}l*{15}{l}}
\br
Element&Style\\
\mr
Authors&Roman type\\
Date&Roman type\\
Book title (optional)&Italic type\\
Editors&Roman type\\
Place (city, town etc) of publication&Roman type\\
Publisher&Roman type\\
Volume&Roman type\\
Page numbers&Roman type\\
\br
\end{tabular}
\end{table}

Points to note are:
\medskip
\begin{itemize}
\item Book titles are in italic and should be spelt out in full with initial capital letters for all except minor words. Words such as Proceedings, Symposium, International, Conference, Second, etc should be abbreviated to {\it Proc.}, {\it Symp.}, {\it Int.}, {\it Conf.}, {\it 2nd}, respectively, but the rest of the title should be given in full, followed by the date of the conference and the town or city where the conference was held. For Laboratory Reports the Laboratory should be spelt out wherever possible, e.g. {\it Argonne National Laboratory Report}.
\item The volume number, for example vol 2, should be followed by the editors, if any, in a form such as `ed A J Smith and P R Jones'. Use {\it et al} if there are more than two editors. Next comes the town of publication and publisher, within brackets and separated by a colon, and finally the page numbers preceded by p if only one number is given or pp if both the initial and final numbers are given.
\end{itemize}

Examples taken from published papers:
\medskip

\numrefs{99}
\item Kurata M 1982 {\it Numerical Analysis for Semiconductor Devices} (Lexington, MA: Heath)
\item Selberherr S 1984 {\it Analysis and Simulation of Semiconductor Devices} (Berlin: Springer)
\item Sze S M 1969 {\it Physics of Semiconductor Devices} (New York: Wiley-Interscience)
\item Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} (Moscow: Moscow State University Press) p 103
\item Caplar R and Kulisic P 1973 {\it Proc. Int. Conf. on Nuclear Physics (Munich)} vol 1 (Amsterdam: 	North-Holland/American Elsevier) p 517
\item Cheng G X 2001 {\it Raman and Brillouin Scattering-Principles and Applications} (Beijing: Scientific) 
\item Szytula A and Leciejewicz J 1989 {\it Handbook on the Physics and Chemistry of Rare Earths} vol 12, ed K A Gschneidner Jr and L Erwin (Amsterdam: Elsevier) p 133
\item Kuhn T 1998 {\it Density matrix theory of coherent ultrafast dynamics Theory of Transport Properties of Semiconductor Nanostructures} (Electronic Materials vol 4) ed E Sch\"oll (London: Chapman and Hall) chapter 6 pp 173--214
\endnumrefs

\section{Tables and table captions}
Tables should be numbered serially and referred to in the text 
by number (table 1, etc, {\bf rather than} tab. 1). Each table should be a float and be positioned within the text at the most convenient place near to where it is first mentioned in the text. It should have an 
explanatory caption which should be as concise as possible.

\subsection{The basic table format}
The standard form for a table is:
\begin{verbatim}
\begin{table}
\caption{\label{label}Table caption.}
\begin{center}
\begin{tabular}{llll}
\br
Head 1&Head 2&Head 3&Head 4\\
\mr
1.1&1.2&1.3&1.4\\
2.1&2.2&2.3&2.4\\
\br
\end{tabular}
\end{center}
\end{table}
\end{verbatim}

The above code produces table~\ref{ex}.

\begin{table}[h]
\caption{\label{ex}Table caption.}
\begin{center}
\begin{tabular}{llll}
\br
Head 1&Head 2&Head 3&Head 4\\
\mr
1.1&1.2&1.3&1.4\\
2.1&2.2&2.3&2.4\\
\br
\end{tabular}
\end{center}
\end{table}

Points to note are:
\medskip
\begin{enumerate}
\item The caption comes before the table.
\item The normal style is for tables to be centred in the same way as
equations. This is accomplished
by using \verb"\begin{center}" \dots\ \verb"\end{center}".

\item The default alignment of columns should be aligned left.

\item Tables should have only horizontal rules and no vertical ones. The rules at
the top and bottom are thicker than internal rules and are set with
\verb"\br" (bold rule). 
The rule separating the headings from the entries is set with
\verb"\mr" (medium rule). These commands do not need a following double backslash.

\item Numbers in columns should be aligned as appropriate, usually on the decimal point;
to help do this a control sequence \verb"\lineup" has been defined 
which sets \verb"\0" equal to a space the size of a digit, \verb"\m"
to be a space the width of a minus sign, and \verb"\-" to be a left
overlapping minus sign. \verb"\-" is for use in text mode while the other
two commands may be used in maths or text.
(\verb"\lineup" should only be used within a table
environment after the caption so that \verb"\-" has its normal meaning
elsewhere.) See table~\ref{tabone} for an example of a table where
\verb"\lineup" has been used.
\end{enumerate}

\begin{table}[h]
\caption{\label{tabone}A simple example produced using the standard table commands 
and $\backslash${\tt lineup} to assist in aligning columns on the 
decimal point. The width of the 
table and rules is set automatically by the 
preamble.}

\begin{center}
\lineup
\begin{tabular}{*{7}{l}}
\br                              
$\0\0A$&$B$&$C$&\m$D$&\m$E$&$F$&$\0G$\cr 
\mr
\0\023.5&60  &0.53&$-20.2$&$-0.22$ &\01.7&\014.5\cr
\0\039.7&\-60&0.74&$-51.9$&$-0.208$&47.2 &146\cr 
\0123.7 &\00 &0.75&$-57.2$&\m---   &---  &---\cr 
3241.56 &60  &0.60&$-48.1$&$-0.29$ &41   &\015\cr 
\br
\end{tabular}
\end{center}
\end{table}

\section{Figures and figure captions}
Figures must be included in the source code of an article at the appropriate place in the text not grouped together at the end.

Each figure should have a brief caption describing it and, if 
necessary, interpreting the various lines and symbols on the figure. 
As much lettering as possible should be removed from the figure itself and 
included in the caption. If a figure has parts, these should be 
labelled ($a$), ($b$), ($c$), etc. 
\Tref{blobs} gives the definitions for describing symbols and lines often
used within figure captions (more symbols are available
when using the optional packages loading the AMS extension fonts).

\begin{table}[h]
\caption{\label{blobs}Control sequences to describe lines and symbols in figure 
captions.}
\begin{center}
\begin{tabular}{lllll}
\br
Control sequence&Output&&Control sequence&Output\\
\mr
\verb"\dotted"&\dotted        &&\verb"\opencircle"&\opencircle\\
\verb"\dashed"&\dashed        &&\verb"\opentriangle"&\opentriangle\\
\verb"\broken"&\broken&&\verb"\opentriangledown"&\opentriangledown\\
\verb"\longbroken"&\longbroken&&\verb"\fullsquare"&\fullsquare\\
\verb"\chain"&\chain          &&\verb"\opensquare"&\opensquare\\
\verb"\dashddot"&\dashddot    &&\verb"\fullcircle"&\fullcircle\\
\verb"\full"&\full            &&\verb"\opendiamond"&\opendiamond\\
\br
\end{tabular}
\end{center}
\end{table}

Authors should try and use the space allocated to them as economically as possible. At times it may be convenient to put two figures side by side or the caption at the side of a figure. To put figures side by side, within a figure environment, put each figure and its caption into a minipage with an appropriate width (e.g. 3in or 18pc if the figures are of equal size) and then separate the figures slightly by adding some horizontal space between the two minipages (e.g. \verb"\hspace{.2in}" or \verb"\hspace{1.5pc}". To get the caption at the side of the figure add the small horizontal space after the \verb"\includegraphics" command and then put the \verb"\caption" within a minipage of the appropriate width aligned bottom, i.e. \verb"\begin{minipage}[b]{3in}" etc (see code in this file used to generate figures 1--3).

Note that it may be necessary to adjust the size of the figures (using optional arguments to \verb"\includegraphics", for instance \verb"[width=3in]") to get you article to fit within your page allowance or to obtain good page breaks.

\begin{figure}[h]
\begin{minipage}{14pc}
\includegraphics[width=14pc]{name.eps}
\caption{\label{label}Figure caption for first of two sided figures.}
\end{minipage}\hspace{2pc}%
\begin{minipage}{14pc}
\includegraphics[width=14pc]{name.eps}
\caption{\label{label}Figure caption for second of two sided figures.}
\end{minipage} 
\end{figure}

\begin{figure}[h]
\includegraphics[width=14pc]{name.eps}\hspace{2pc}%
\begin{minipage}[b]{14pc}\caption{\label{label}Figure caption for a narrow figure where the caption is put at the side of the figure.}
\end{minipage}
\end{figure}

Using the graphicx package figures can be included using code such as:
\begin{verbatim}
\begin{figure}
\begin{center}
\includegraphics{file.eps}
\end{center}
\caption{\label{label}Figure caption}
\end{figure}
\end{verbatim}

\section*{References}
\begin{thebibliography}{9}
\bibitem{iopartnum} IOP Publishing is to grateful Mark A Caprio, Center for Theoretical Physics, Yale University, for permission to include the {\tt iopart-num} \BibTeX package (version 2.0, December 21, 2006) with  this documentation. Updates and new releases of {\tt iopart-num} can be found on \verb"www.ctan.org" (CTAN). 
\end{thebibliography}

\end{document}

### 2024-11-25 Documents/Euler/SamsTexFiles/LinearInterpolationError.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

\section{Error Introduced by Linear Interpolation}
We obtain the initial conditions for the standing accretion shock problem with an external code. We then have to interpolate these data onto the grid for use in \texttt{thornado}. We start by proving that linear interpolation is a convex combination of the solution at the boundary points.

\subsection{Proof that Linear Interpolation is a Convex Combination of Boundary-Points}
Linear interpolation of a function, $f$, of a variable, $r$, bounded by two points $r_{L}$ and $r_{H}$, with $r_{H}>r_{L}$, can be written as:
\begin{equation}
    f\left(r\right)=f\left(r_{L}\right)+\f{f\left(r_{H}\right)-f\left(r_{L}\right)}{r_{H}-r_{L}}\left(r-r_{L}\right).
\end{equation}
By making a change of variables from $r$ to $\eta$, where:
\begin{equation}
    r\left(\eta\right)=\eta\,r_{H}+\left(1-\eta\right)r_{L}=r_{L}+\eta\,\Delta r\implies\eta=\f{r-r_{L}}{\Delta r},\hspace{1em}\eta\in\left[0,1\right],
\end{equation}
such that $r\left(\eta=0\right)=r_{L}$ and $r\left(\eta=1\right)=r_{H}$, we have that:
\begin{align}
    f\left(\eta\right)&=f\left(0\right)+\f{f\left(1\right)-f\left(0\right)}{1-0}\left(\eta-0\right)=f\left(0\right)+\left(f\left(1\right)-f\left(0\right)\right)\eta\\
    \implies f\left(\eta\right)&=\eta\,f\left(1\right)+\left(1-\eta\right)f\left(0\right).
\end{align}

So when we interpolate a fluid variable, say the mass-density $\rho$, we have:
\begin{equation}
    \rho\left(r\right)=\rho_{L}+\f{\Delta\rho}{\Delta r}\left(r-r_{L}\right)\longrightarrow\rho\left(\eta\right)=\eta\,\rho_{H}+\left(1-\eta\right)\rho_{L},
\end{equation}
where $\rho_{L}\equiv\rho\left(r_{L}\right)$ and $\rho_{H}=\rho\left(r_{H}\right)$.

\subsection{Example: $f\left(x\right)=x^{2}$}
We can show this directly for simple functions. We take as an example $f\left(x\right)=x^{2}$:
\begin{align}
    f\left(x\right)&=x^{2}=\left[x_{L}+\eta\left(x_{R}-x_{L}\right)\right]^{2}=x_{L}^{2}+\eta^{2}\left(x_{R}-x_{L}\right)^{2}+2\,x_{L}\,\eta\left(x_{R}-x_{L}\right)\\
    &=x_{L}^{2}+\eta^{2}\,x_{R}^{2}+\eta^{2}\,x_{L}^{2}-2\,\eta^{2}\,x_{L}\,x_{R}+2\,\eta\,x_{L}\,x_{R}-2\,\eta\,x_{L}^{2}.
\end{align}
Now we add and subtract the interpolated solution: $\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}$. This yields:
\begin{align}
    x^{2}&=x_{L}^{2}+\eta^{2}\,x_{R}^{2}+\eta^{2}\,x_{L}^{2}-2\,\eta^{2}\,x_{L}\,x_{R}+2\,\eta\,x_{L}\,x_{R}-2\,\eta\,x_{L}^{2}+\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}-\eta\,x_{H}^{2}-\left(1-\eta\right)x_{L}^{2}\\
    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]+\left[-\eta\left(1-\eta\right)x_{L}^{2}-\eta\left(1-\eta\right)x_{H}^{2}+2\,\eta\,x_{L}\,x_{H}\left(1-\eta\right)\right]\\
    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left[x_{L}^{2}+x_{H}^{2}-2\,x_{L}\,x_{H}\right]\\
    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left(x_{H}-x_{L}\right)^{2}\\
    &=\left[\eta\,x_{H}^{2}+\left(1-\eta\right)x_{L}^{2}\right]-\eta\left(1-\eta\right)\left(\Delta x\right)^{2}.
\end{align}
The term in square brackets is the interpolated solution, and the second term is the remainder, i.e. the error in the interpolated solution. So we see that when using linear interpolation to interpolate the function $f\left(x\right)=x^{2}$ we introduce an error (of the order $\left(\Delta x\right)^{2}$) that goes to zero as the step-size goes to zero.

As a final step we replace $\eta$ with $x$, yielding:
\begin{align}
    f\left(x\right)=x^{2}&=x_{L}^{2}+\f{x_{H}^{2}-x_{L}^{2}}{x_{H}-x_{L}}\left(x-x_{L}\right)-\left(x-x_{L}\right)\left(x_{H}-x\right)\\
    &=f\left(x_{L}\right)+\f{\Delta f}{\Delta x}\left(x-x_{L}\right)-\left(x-x_{L}\right)\left(x_{H}-x\right).
\end{align}

We show the results of this in the following figure:
\begin{figure}[H]
\centering
\includegraphics[scale=0.75]{LinearInterpolationError}
\end{figure}

\subsection{Mass Constant}
The mass constant, $C_{D}$, from the 3+1 GR hydrodynamics equations is:
\begin{equation}
    C_{D}\left(r\right)=\psi\left(r\right)^{6}\,\alpha\left(r\right)\,r^{2}\,\rho\left(r\right)\,W\left[v\left(r\right)\right]\,v\left(r\right).
\end{equation}
When we map from the radial coordinates from the original data to the mesh in \texttt{thornado} we don't introduce any error, because it is a linear map. This means that all the error we introduce must be due to $\rho$, $W$, and $v$. So, when deriving the error we consider the different function:
\begin{equation}
    C'_{D}\left(r\right)\equiv\f{C_{D}\left(r\right)}{\psi\left(r\right)^{6}\,\alpha\left(r\right)\,r^{2}}=\rho\left(r\right)\,W\left[v\left(r\right)\right]\,v\left(r\right).
\end{equation}

From the data we have this exact value at the two endpoints:
\begin{align}
    C'_{D}\left(r_{L}\right)&\equiv C'^{L}_{D}=\rho_{L}\,W_{L}\,v_{L}\\
    C'_{D}\left(r_{H}\right)&\equiv C'^{H}_{D}=\rho_{H}\,W_{H}\,v_{H}.
\end{align}

### 2024-11-25 Documents/Euler/SamsTexFiles/Time-Step_Restriction_High-Order.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

@@
 
+\blue{NOTE:} We do not use this restriction in the code.
+We simply take $M$ equal to the number of quadrature points (which is the same as the number of interpolation points).
+The difference will be accounted for by the presence of the CFL number.
+
 \blue{NOTE:} We now drop the superscript $n$ for the rest of this subsection.
@@
 
-\blue{NOTE:} It is worth noting that this result is independent of the metric determinant.
+\blue{NOTE:} It is worth noting that this result is \textit{not} independent of the metric, because it is incorporated through the wave-speed in the numerical flux.

### 2024-11-25 Documents/Euler/dgEulerCurvilinear.tex
finished entropy wave error chart
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

--- 2017-07-11 Documents/Euler/dgEulerCurvilinear.tex
@@
 where $\alpha^{i}=||\mbox{eig}\big(\partial\bF^{i}/\partial\bU\big)||_{\infty}$ is the largest eigenvalue of the flux jacobian.  
+We have implemented the Local Lax-Friedrichs flux, the Harten-Lax-van Leer (HLL) flux, and the HLLC flux, but use the HLLC flux for all the numerical experiments presented in Sections~\ref{sec:NumericalExperiments} and \ref{sec:MiniApp}.
 
@@
 \section{Time Integration}
+\label{sec:TimeIntegration}
+
+For time integration, we employ the strong stability-preserving Runge-Kutta (SSP-RK) methods \citep[e.g.,][]{gottlieb_etal_2001}, which, for evolving the Euler equations from $t^{n}$ to $t^{n+1}=t^{n}+\dt$ ($\bU^{n}\to\bU^{n+1}$) using $m$ stages, take the general form
+\begin{align}
+  \bU^{(0)}
+  &=\bU^{n}, \\
+  \bU^{(i)}
+  &=\sum_{k=0}^{i-1}\alpha_{ik}\,\big[\,\bU^{(k)}+\beta_{ik}\,\dt\,\bcL(\bU^{(k)})\,\big], \quad i=1,\ldots,m 
+  \label{eq:ssprkStages} \\
+  \bU^{n+1}
+  &=\bU^{(m)}.  
+\end{align}
+For second- and third-order temporal accuracy (denoted SSP-RK2 and SSP-RK3, respectively), the coefficient matrices $\alpha_{ik}$ and $\beta_{ik}$ are given by \citep{shuOsher_1988}.  
+Note that $\alpha_{ik},\beta_{ik}\ge0$ and $\sum_{k}\alpha_{ik}=1~\forall i$, so that the RK stages in Eq.~\eqref{eq:ssprkStages} are simply convex combinations of forward Euler steps with time step $\beta_{ik}\,\dt$.
 
@@
 \section{Gravity Solver: Finite Element Method}
+\label{sec:FiniteElementMethod}
 
@@
 \section{Benchmark Problems}
+\label{sec:NumericalExperiments}
+
+We benchmark the DG implementation against a series of test problems.  
+We will vary the degree $k$ of the polynomial representation from 0 to 3, which we then denote DG($k$).  
+IWe use the explicit SSP-RK time integrators in Section~\ref{sec:explicitTime}.  
+The 2-stage and 3-stage methods are denoted SSP-RK2 and SSP-RK3, respectively.  
+As an example, an expected third-order accurate method (for problems with smooth solutions), using DG(2) and SSP-RK3, will then be denoted DG(2)+RK3.  
+We use the finite element method in Section~\ref{sec:FiniteElementMethod} with the same polynomial degree as the DG method for problems involving self-gravity.
 
@@
 
+\subsubsection{Entropy Waves (Accuracy Test)}
+
+\begin{table}
+  \begin{center}
+  \caption{$L^{\infty}$ error and convergence rates for the entropy wave problem.}
+  \label{tab:streamingSineWave}
+  \begin{tabular}{ccccccccc}
+    & \multicolumn{4}{c}{SSP-RK2} & \multicolumn{4}{c}{SSP-RK3} \\
+    \cmidrule(r){2-5} \cmidrule(r){6-9}
+    $N$ & DG(1) & Rate & DG(2) & Rate & DG(2) & Rate & DG(3) & Rate \\
+    \midrule \midrule
+    8     & $1.766\times10^{-1}$ & ---  & $2.371\times10^{-3}$ & ---  & $1.700\times10^{-3}$ & ---  & $4.958\times10^{-5}$  & --- \\
+    16   & $2.893\times10^{-2}$ &2.61& $3.236\times10^{-4}$ &2.87& $1.300\times10^{-4}$ &3.71& $3.044\times10^{-6}$ &4.03 \\
+    32   & $4.203\times10^{-3}$ &2.78& $6.800\times10^{-5}$ &2.25& $1.580\times10^{-5}$ &3.04& $1.983\times10^{-7}$ &3.94 \\
+    64   & $6.455\times10^{-4}$ &2.70& $1.542\times10^{-5}$ &2.14& $1.971\times10^{-6}$ &3.00& $1.343\times10^{-8}$ &3.88 \\
+    128 & $1.101\times10^{-4}$ &2.55& $3.659\times10^{-6}$ &2.08& $2.464\times10^{-7}$ &3.00& $9.737\times10^{-10}$ &3.79 \\
+    256 & $2.109\times10^{-5}$ &2.38& $8.904\times10^{-7}$ &2.04& $3.081\times10^{-8}$ &3.00& $9.012\times10^{-11}$ &3.43 \\
+    \midrule \midrule
+  \end{tabular}
+  \end{center}
+\end{table}
+
+\subsubsection{Sound Waves}
+
 \subsection{Riemann Problems}
+
+\subsubsection{Shock Tube}
 
@@
 
+\subsubsection{Homologous Collapse}
+
 \subsubsection{Evrard's Collapse Test}
@@
 \section{Miniapp: Adiabatic Collapse of Stellar Iron Core}
+\label{sec:MiniApp}
+
+\section{Summary and Conclusions}
 

### 2024-11-25 Documents/M1/Astronum_2018/sections/SpatialDiscretization.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

@@
 
-In this section we discretize the two-moment model with a simple first-order finite volume method to illustrate how the closure affects the realizability-preserving property of the method.  
+We discretize the two-moment model with a simple first-order finite volume method to illustrate how the closure affects the realizability-preserving property of the method.  
 By assuming that the moments at time level $t^{n}$ ($\bcM^{n}$) satisfy the bounds in Eq.~\eqref{eq:MomentsBounds}, our goal is to identify sufficient conditions such that the moments at time level $t^{n+1}$ ($\bcM^{n+1}$) also satisfy the bounds.
-To simply the illustration, we limit the discussion to one spatial dimension and employ a uniform Cartesian mesh.  
+To simplify, we limit the discussion to one spatial dimension and employ a uniform Cartesian mesh.  
 (The extension to multiple spatial dimensions and high-order discretization using the discontinuous Galerkin method is given in~\cite{chu_etal_2018}.)
@@
   D = \cup_{i = 1}^{N} \bK_{i} \quad \text{with} \quad
-  \bK_{i}=\{\,x : x\in(x_{i-1/2}, x_{i+1/2})\}.
+  \bK_{i}=\{\,x : x\in(x_{i-1/2}, x_{i+1/2})\},
 \end{equation*}
-Denote the cell width by $\dx = D/N$.  
+and cell width $\dx = D/N$.  
 The cell-average of the moments is defined as
@@
 \end{equation}
-Integrating Eq.~\eqref{eq:momentEquations} over $\bK_{i}$ gives
+Integrating Eq.~\eqref{eq:momentEquations} over each cell $\bK_{i}$ gives
 \begin{equation}
@@
 
-Consider Eq.~\eqref{eq:MomentIMEX} and assume that $\bcM_{i}^{n}$ is realizable for all $i$.  
-It can be shown (Lemma~3 in~\cite{chu_etal_2018}) that $\bcM^{n+1}_{i}$ is realizable provided $\f{\dt}{\tau} > 0$. 
+Considering Eqs.~\eqref{eq:MomentIMEX} and \eqref{eq:widetildeM} and assuming that $\bcM_{i}^{n}$ is realizable for all $i$, it can be shown (Lemma~3 in~\cite{chu_etal_2018}) that $\bcM^{n+1}_{i}$ is realizable provided $\f{\dt}{\tau} > 0$.
 %and $\widetilde{\bcM}^{n}_{i}$ is realizable.  

### 2024-11-25 Documents/M1/Astronum_2018/sections/intro.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

@@
 ns given by the two-moment method and solve the discretized system efficiently remains a question.
-In fact, the time scales of neutrino interactions with the background (they can be $\sim\mathcal{O}(10^{-13})$~second) is short compared to the duration of the CCSN explosion ($\sim\mathcal{O}(1)$~second).
-This means that $\sim\mathcal{O}(10^{13})$ time steps could be needed for solving the system fully explicitly. 
+In fact, the time scales of neutrino interactions with the background (they can be $\sim\mathcal{O}(10^{-10})$~second) is short compared to the duration of the CCSN explosion ($\sim\mathcal{O}(1)$~second).
+This means that $\sim\mathcal{O}(10^{10})$ time steps could be needed for solving the system fully explicitly. 
 On the other hand, solving the moment equations fully implicitly requires inverting global band-structured matrices whose sizes depend on the phase-space discretization.

### 2024-11-25 Documents/M1/MeshRefinement/MeshRefinement.tex
Minor changes to Documents/M1/MeshRefinement/MeshRefinement.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

--- 2020-11-09 Documents/M1/MeshRefinement/MeshRefinement.tex
@@
 
+\section{Curvilinear Coordinates}
+
+\subsection{Preliminaries}
+
+The introduction of curvilinear coordinates doesn't change any of the preliminaries.
+
+\subsection{Refinement}
+
+As with Cartesian coordinates, the representation of the variable $U$ on the fine element
+$\vect{k}_{\left(j\right)}$ is obtained from solving the minimization problem,
+\begin{equation}
+  \min_{\vect{u}^{(j)}}\int_{\vect{k}_{(j)}}\big(\,U_{h}(\vect{x})-u_{h}^{(j)}(\vect{x})\,\big)^{2}\,
+  \sqrt{\gamma_{h}}\,d\vect{x},
+\end{equation}
+where $\sqrt{\gamma_{h}}$ is the numerical approximation to the metric determinant $\sqrt{\gamma}$.
+
+When demanding equality of the cell averages, the metric determinant
+must be taken into account, i.e., Eq.~\eqref{eq:refinementProjection} becomes
+\begin{equation}
+  \int_{\vect{k}_{(j)}}u_{h}^{(j)}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma_{h}}\,d\vect{x}
+  =\int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma_{h}}\,d\vect{x},\quad i=1,\ldots,M.
+  \label{eq:refinementProjection_CC}
+\end{equation}
+Evaluating the left-hand side of Eq.~\eqref{eq:refinementProjection_CC} gives
+\begin{equation}
+  \int_{\vect{k}_{(j)}}u_{h}^{(j)}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma_{h}}\,d\vect{x}
+  =|\vect{k}_{(j)}|\,w_{i}\,u_{i}^{(j)}\,\sqrt{\gamma_{i}}.
+  \end{equation}
+  Evaluating the right-hand side of Eq.~\eqref{eq:refinementProjection_CC} gives
+  \begin{equation}
+  \int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma_{h}}\,d\vect{x}
+  =|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\eta})\,\ell_{k}(\vect{\xi}(\vect{\eta}))\,\sqrt{\gamma_{h}}\,d\vect{\eta}\,U_{k}.
+\end{equation}
+Defining the projection matrix, $P^{\left(j\right)}_{\gamma_{h}}$, with components
+\begin{equation}
+P^{\left(j\right)}_{ik,\gamma_{h}}
+=\int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\eta})\,\ell_{k}(\vect{\xi}(\vect{\eta}))\,\sqrt{\gamma_{h}}\,d\vect{\eta},
+\end{equation}
+and the diagonal matrix $\mathcal{D}_{\gamma_{h}}
+=\mbox{diag}(\sqrt{\gamma_{1}}\,w_{1},\ldots,\sqrt{\gamma_{M}}\,w_{M})$, the components of the expansion in the refined element $\vect{k}_{(j)}$ are obtained from the matrix-vector product
+\begin{equation}
+  \mathcal{D}_{\gamma_{h}}\,\vect{u}^{(j)} = \mathcal{P}^{(j)}_{\gamma_{h}}\,\vect{U}.
+\end{equation}
+Since $\gamma_{h}=\gamma_{h}\left(t\right)$, $\mathcal{P}^{\left(j\right)}_{\gamma_{h}}$
+and $\cD_{\gamma_{h}}$
+must be computed at each time step.
+
+\subsection{Coarsening}
+
+The minimization problem in this case is
+\begin{equation}
+  \min_{\vect{U}}\int_{\vect{K}}\big(\,U_{h}(\vect{x})-u_{h}(\vect{x})\,\big)^{2}\,\sqrt{\gamma_{h}}\,d\vect{x}.
+\end{equation}
+As with refinement, Eq.~\eqref{eq:coarseningProjection} becomes
+\begin{equation}
+  \int_{\vect{K}}U_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma_{h}}\,d\vect{x}
+  =\int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma_{h}}\,d\vect{x}.
+  \label{eq:coarseningProjection_CC}
+\end{equation}
+Evaluating the left-hand side of Eq.~\eqref{eq:coarseningProjection_CC} gives
+\begin{equation}
+  \int_{\vect{K}}U_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma_{h}}\,d\vect{x}
+  =|\vect{K}|\,w_{i}\,U_{i}\,\sqrt{\gamma_{i}}.
+\end{equation}
+Evaluating the right-hand side of Eq.~\eqref{eq:coarseningProjection_CC} gives
+\begin{equation}
+  \int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma_{h}}\,d\vect{x}
+  =\sum_{j=1}^{N}|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}(\vect{\xi}(\vect{\eta}))\,\ell_{k}^{\left(j\right)}(\vect{\eta})\,\sqrt{\gamma_{h}}\,d\vect{\eta}\,u_{k}^{(j)}.
+\end{equation}
+Thus,
+\begin{equation}
+  \mathcal{D}_{\gamma_{h}}\,\vect{U}=\sum_{j=1}^{N}\f{|\vect{k}_{(j)}|}{|\vect{K}|}
+  \big(\mathcal{P}_{\gamma_{h}}^{(j)}\big)^{\trans}\,\vect{u}^{(j)}.
+\end{equation}
+For a refinement factor of $2$, $|\vect{k}_{(j)}|/|\vect{K}|=2^{-d}$.
+
+\subsection{Mapping $\eta\rightarrow\xi$}
+For a 1D problem with two subcells, the mapping from the coarse reference element, coordinatized
+by $\eta$, to the fine reference element, coordinatized by $\xi$, is
+\begin{equation}
+\xi\left(\eta\right)=\frac{1}{2}\left(\eta+\frac{1}{2}\left(-1\right)^{k}\right),\hspace{1em}k=1,2.
+\end{equation}
+
 \bibliographystyle{plain}

### 2024-11-25 Documents/M1/averagedMoments.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

\documentclass[10pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{yhmath}
\usepackage{natbib}
\usepackage{../definitions}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

\newcommand{\ee}[1]{{\color{blue} EE:~#1}}
\newcommand{\Lo}{\textsc{L}}
\newcommand{\Hi}{\textsc{H}}
\newcommand{\trans}{\textsc{T}}
\newcommand{\dx}{\Delta x}

\newtheorem{define}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{theorem}{Theorem}

\begin{document}

\title{Cell Averaged and Energy Integrated Moments}
\author{Eirik Endeve}

\maketitle

Moments are defined as weighted integrals of the distribution function; i.e.,
\begin{equation}
  \vect{\mathcal{M}}(\varepsilon,\vect{x},t) = \f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\varepsilon,\vect{x},t)\,\vect{w}(\omega)\,d\omega.  
\end{equation}

We let the computational domain be subdivided into elements
\begin{equation}
  \bK^{(p\bq)} = K_{\varepsilon}^{(p)} \times \bK_{\vect{x}}^{(\bq)},
\end{equation}
where the $p$th energy space element (energy bin) is
\begin{equation}
  K_{\varepsilon}^{(p)} = (\varepsilon_{p-\f{1}{2}},\varepsilon_{p+\f{1}{2}}),
\end{equation}
and the $d$-dimensional position space element (equivalent to a finite volume cell) is
\begin{equation}
  \bK_{\vect{x}}^{(\bq)} = \big\{\,\vect{x}~:~x^{i}\in(x_{q^{i}-\f{1}{2}}^{i},x_{q^{i}+\f{1}{2}}^{i}),~i=1,\ldots,d\,\big\}.  
\end{equation}
We use multi index notation (bold indices) to refer to spatial elements in a multidimensional spatial domain; e.g., $\bq=\{q^{1},\ldots,q^{d}\}$.  
We define the volume of the element as
\begin{equation}
  \Delta V^{(p\bq)} 
  = \int_{\bK^{(p\bq)}}\varepsilon^{2}\,d\varepsilon\,d\vect{x}
  = \int_{K_{\varepsilon}^{(p)}}\varepsilon^{2}\,d\varepsilon\,\int_{\bK_{\vect{x}}^{(\bq)}}d\vect{x}
  = \Delta V_{\varepsilon}^{(p)}\,\Delta V_{\vect{x}}^{(\bq)}.
\end{equation}
The factor $\varepsilon^{2}$ comes from using spherical momentum space coordinates.  
Cartesian position space coordinates are assumed.  
We also define $\Delta\varepsilon_{p} = \varepsilon_{p+\f{1}{2}}-\varepsilon_{p-\f{1}{2}}$ and $\Delta \vect{x}_{\bq}=\prod_{i=1}^{d}(x_{q^{i}+\f{1}{2}}^{i}-x_{q^{i}-\f{1}{2}}^{i})$.

The moments are approximated by
\begin{equation}
  \vect{\mathcal{M}}_{h}(\varepsilon,\vect{x})=\sum_{p\vect{q}}\chi(\bK^{(p\bq)})\,\vect{\mathcal{M}}_{h}^{(p\bq)}(\varepsilon,\vect{x}),
\end{equation}
where $\chi$ is the indicator function, and the approximation in each element $\bK^{(p\bq)}$ is given by
\begin{equation}
  \vect{\mathcal{M}}_{h}^{(p\bq)}(\varepsilon,\vect{x}) = \sum_{i\bj}\vect{\mathcal{M}}_{i\bj}^{(p\bq)}\,\ell_{i}(\varepsilon)\,\ell_{\vect{j}}(\vect{x}).  
  \label{eq:nodalExpansion}
\end{equation}
(Here we have suppressed dependence on time $t$ for brevity.)
In Eq.~\eqref{eq:nodalExpansion}, $\ell_{i}(\varepsilon)$ and $\ell_{\bj}(\vect{x})$ are local basis polynomials, which we take to be Lagrange polynomials constructed from Gaussian quadrature points in each element.

The element average (average over energy and position nodes in each element) is computed as
\begin{align}
  \langle\vect{\mathcal{M}}\rangle^{(p\bq)}
  &=\f{1}{\Delta V^{(p\bq)}}\int_{\bK^{(p\bq)}}\vect{\mathcal{M}}_{h}^{(p\bq)}(\varepsilon,\vect{x})\,\varepsilon^{2}\,d\varepsilon\,d\vect{x} \nonumber \\
  &=\f{\Delta\varepsilon_{p}\,\Delta\vect{x}_{\bq}}{\Delta V^{(p\bq)}}\sum_{i\bj}w_{i}\,w_{\bj}\,\varepsilon_{i}^{2}\,\vect{\mathcal{M}}_{i\bj}^{(p\bq)}.  
\end{align}
Energy integrated (grey) moments are computed as
\begin{equation}
  \vect{M}^{(\bq)}
  =\f{4\pi}{\Delta V_{\vect{x}}^{(\bq)}}\int_{\bbR^{+}}\int_{\bK_{\vect{x}}^{(\bq)}}\vect{\mathcal{M}}_{h}(\varepsilon,\vect{x})\,\varepsilon^{2}\,d\varepsilon\,d\vect{x}
  =4\pi\sum_{p}\langle\vect{\mathcal{M}}\rangle^{(p\bq)}\,\Delta V_{\varepsilon}^{(p)}.  
\end{equation}

\end{document}

### 2024-11-25 Documents/M1/realizableFermionicM1/sections/conclusion.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

@@
 
-We have developed a realizability-preserving DG-IMEX scheme for a two-moment model for fermion transport.  
-The scheme employs algebraic two-moment closures rooted in Fermi-Dirac statistics, and combines a time step restriction (CFL condition), a realizability-enforcing limiter, and a constraint-preserving time integrator to maintain point-wise realizability of the moments.
+We have developed a realizability-preserving DG-IMEX scheme for a two-moment model of fermion transport.  
+The scheme employs algebraic closures based on Fermi-Dirac statistics and combines a time step restriction (CFL condition), a realizability-enforcing limiter, and a convex-invariant time integrator to maintain point-wise realizability of the moments.
 Since the realizable domain is a convex set, the realizability-preserving property is obtained from convexity arguments, building on the framework in \cite{zhangShu_2010a}.
 
-In the applications motivating this work, the collision term is stiff in regions of the computational domain, and we have considered IMEX schemes to avoid solving the transport operator implicitly in a fully implicit scheme.
-We considered recently proposed second-order accurate, constraint-preserving IMEX schemes \cite{chertock_etal_2015,hu_etal_2018}, which restore second-order accuracy with an implicit correction step.
+In the applications motivating this work, the collision term is stiff in regions of the computational domain, and we have considered IMEX schemes to avoid treating the transport operator implicitly.  
+We have considered two recently proposed second-order accurate, convex-invariant IMEX schemes \cite{chertock_etal_2015,hu_etal_2018}, that restore second-order accuracy with an implicit correction step.
 However, we are unable to prove realizability (without invoking a very small time step) with the approach in \cite{chertock_etal_2015}, and we have demonstrated that the approach in \cite{hu_etal_2018} does not perform well in the diffusion limit.
-For these reasons, and the general nonexistence of high-order, implicit SSP-RK schemes \cite{gottlieb_etal_2001}, we have resorted to develop first-order, constraint-preserving IMEX schemes.  
-While the proposed scheme (dubbed PD-ARS) is formally only first-order accurate, it works well in the diffusion limit, is constraint-preserving with a reasonable time step, and reduces to the optimal second-order accurate explicit SSP-RK scheme in the streaming limit.
+For these reasons, we have resorted to first-order, convex-invariant IMEX schemes.  
+While the proposed scheme (dubbed PD-ARS) is formally only first-order accurate, it works well in the diffusion limit, is convex-invariant with a reasonable time step, and reduces to the optimal second-order accurate explicit SSP-RK scheme in the streaming limit.
 
@@
 After each stage update, the limiter enforces moment realizability point-wise by damping towards the realizable cell average.  
-Numerical experiments are presented to demonstrate the accuracy and realizability-preserving property of the scheme.  
+Numerical experiments are presented to demonstrate the accuracy and realizability-preserving property of the DG-IMEX scheme.  
 The applicability of the PD-ARS scheme is not restricted to the fermionic two-moment model.  
@@
 For the algebraic closures adapted in this work, realizability of the scheme demands that lower and upper bounds on the Eddington factor are satisfied \cite{levermore_1984,lareckiBanach_2011}.  
-The Eddington factors deriving from the maximum entropy closures of Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Larecki \& Banach \cite{lareckiBanach_2011}, and the Kershaw-type closure of Larecki \& Banach \cite{banachLarecki_2017a}, satisfy these bounds, and are suitable for the fermionic two-moment model.
+The Eddington factors deriving from the maximum entropy closures of Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Larecki \& Banach \cite{lareckiBanach_2011}, and the Kershaw-type closure of Larecki \& Banach \cite{banachLarecki_2017a} all satisfy these bounds and are suitable for the fermionic two-moment model.
 Further approximations of the closure procedure (e.g., employing the low occupancy limit, which results in the Minerbo closure \cite{minerbo_1978} when starting with the maximum entropy closure of \cite{cernohorskyBludman_1994}) is not compatible with realizability of the fermionic two-moment model, and we caution against this approach to modeling particle systems governed by Fermi-Dirac statistics; particularly if the low occupancy approximation is unlikely to hold (e.g., when modeling neutrino transport in core-collapse supernovae).
 
-In this work, we considered a relatively simple model.  
+In this work, we started with a relatively simple kinetic model.  
 In particular, we adopted Cartesian coordinates, and assumed a linear collision operator and a fixed material background.  
@@
 To solve more realistic problems of scientific interest, some or all of these physical effects will have to be included.  
-In the context of developing constraint-preserving schemes, these extensions will provide significant challenges suitable for future investigations, for which the scheme presented here may serve as a foundation.
+In the context of developing realizability-preserving schemes, these extensions will provide significant challenges suitable for future investigations, for which the scheme presented here may serve as a foundation.

### 2024-11-25 Documents/M1/realizableFermionicM1/sections/dg.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

@@
 \end{equation}
-with surface elements denoted $\tilde{\bK}^{i}=\otimes_{j\ne i}K^{j}$.  
+with surface elements denoted $\tilde{\bK}^{i}=\times_{j\ne i}K^{j}$.  
 We let $|\bK|$ denote the volume of an element
@@
 
-In Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\bcF}^{i}(\vect{\cM}_{h})$ is a numerical flux, approximating the flux on the surface of $\bK$ with unit normal along the $i$th coordinate direction, and is evaluated with a flux function $\vect{\mathscr{F}}^{i}$ using the DG approximation from both sides of the element interface; i.e.,
+In Eq.~\eqref{eq:semidiscreteDG}, $\widehat{\bcF}^{i}(\vect{\cM}_{h})$ is a numerical flux, approximating the flux on the surface of $\bK$ with unit normal along the $i$th coordinate direction.  
+It is evaluated with a flux function $\vect{\mathscr{F}}^{i}$ using the DG approximation from both sides of the element interface; i.e.,
 \begin{equation}

### 2024-11-25 Documents/M1/realizableFermionicM1/sections/imex.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

@@
 \cite{chertock_etal_2015} (not included in Section~\ref{sec:smoothProblems}), where the transport operator is part of the correction step, and found it to perform very well in the diffusion limit.
-However, we have not been able to prove the realizability-preserving property with this approach without invoking a too severe time step restriction.  
+However, we have not been able to prove the realizability-preserving property with this approach without invoking a too severe time step restriction.%
+\footnote{\modified{For example in the pure absorption case, we find that there is a sufficient time step, proportional to $\sqrt{\tau|K|}$ (as opposed to $|K|$ without the correction step), which guarantees moment realizability.
+In numerical experiments, we have observed for the homogeneous sphere problem in Section~\ref{sec:homogeneousSphere} that this approach breaks for stiff problems ($\tau\ll1$) when this restriction is violated.}}
 We therefore proceed to design convex-invariant IMEX schemes without the correction step that perform well in the diffusion limit.  

### 2024-11-25 Documents/M1/realizableFermionicM1/sections/limiter.tex
Deploying to gh-pages from @ endeve/thornado@19001b5f50db3df8a7773519599ef6fc4c2d1d53 🚀

--- 2018-02-25 Documents/M1/realizableFermionicM1/sections/limiter.tex
@@
-\section{Realizability-Preserving Limiter}
-\label{eq:limiter}
+\section{Realizability-Enforcing Limiter}
+\label{sec:limiter}
 
-The bound-preserving DG-IMEX method developed in previous sections is designed to preserve realizability of the cell averaged moments, i.e., $\vect{\cM}_{\bK}\in\cR$, provided sufficiently accurate quadratures are used to integrate integrals in the DG method, specific CFL conditions are satisfied, and that the polynomial approximation $\vect{\cM}_{h}$, at time $t^{n}$, is realizable in a set of quadrature points in each element $\bK$.
-We denote this quadrature set by $S\subset\bK$.  
-In the DG method, we use the limiter proposed by Zhang \& Shu \cite{zhangShu_2010a} for scalar conservation laws to enforce the bounds on the zeroth moment $\cJ$ (see also \cite{liuOsher_1996}).  
-We replace the polynomial $\cJ_{h}^{n}(\vect{z})$ with the limited polynomial
+Condition~2 of Theorem~\ref{the:realizableDGIMEX} requires that the polynomial approximation $\vect{\cM}_{h}=\vect{\cM}_{h}^{(j)}$ ($j\in\{0,\ldots,i-1\}$) is realizable in every point in the quadrature set $S=\cup_{k=1}^{d}\hat{\vect{S}}^{k}$.
+Following Zhang \& Shu \cite{zhangShu_2010a} we use the limiter in \cite{liuOsher_1996} to enforce the bounds on the zeroth moment $\cJ$.  
+%The bound-preserving DG-IMEX method developed in previous sections is designed to preserve realizability of the cell averaged moments, i.e., $\vect{\cM}_{\bK}\in\cR$, provided sufficiently accurate quadratures are used to integrate integrals in the DG method, a CFL condition is satisfied, and that the polynomial approximation $\vect{\cM}_{h}$, at time $t^{n}$, is realizable in a set of quadrature points in each element $\bK$.
+%We denote this quadrature set by $S=\cup_{k=1}^{d}\hat{\vect{S}}^{k}\subset\bK$.  
+%In the DG method, we use the limiter proposed by Zhang \& Shu \cite{zhangShu_2010a} for scalar conservation laws to enforce the bounds on the zeroth moment $\cJ$ (see also \cite{liuOsher_1996}).  
+We replace the polynomial $\cJ_{h}(\vect{x})$ with the limited polynomial
 \begin{equation}
-  \tilde{\cJ}_{h}^{n}(\vect{z})
-  =\vartheta_{1}\,\cJ_{h}^{n}(\vect{z})+(1-\vartheta_{1})\,\cJ_{\bK}^{n},
+  \tilde{\cJ}_{h}(\vect{x})
+  =\vartheta_{1}\,\cJ_{h}(\vect{x})+(1-\vartheta_{1})\,\cJ_{\bK},
+  \label{eq:limitDensity}
 \end{equation}
@@
   \vartheta_{1}
-  =\min\Big\{\,\Big|\f{M-\cJ_{\bK}^{n}}{M_{S}-\cJ_{\bK}^{n}}\Big|,\Big|\f{m-\cJ_{\bK}^{n}}{m_{S}-\cJ_{\bK}^{n}}\Big|,1\,\Big\},
+  =\min\Big\{\,\Big|\f{M-\cJ_{\bK}}{M_{S}-\cJ_{\bK}}\Big|,\Big|\f{m-\cJ_{\bK}}{m_{S}-\cJ_{\bK}}\Big|,1\,\Big\},
 \end{equation}
@@
 \begin{equation}
-  M_{S}=\max_{\vect{z}\in S}\cJ_{h}^{n}(\vect{z})
+  M_{S}=\max_{\vect{x}\in S}\cJ_{h}(\vect{x})
   \quad\text{and}\quad
-  m_{S}=\min_{\vect{z}\in S}\cJ_{h}^{n}(\vect{z}).  
+  m_{S}=\min_{\vect{x}\in S}\cJ_{h}(\vect{x}).  
 \end{equation}
@@
 In the next step, we ensure realizability of the moments by following the framework of \cite{zhangShu_2010b}, developed to ensure positivity of the pressure when solving the Euler equations of gas dynamics.
-We let $\widetilde{\vect{\cM}}_{h}^{n}=\big(\tilde{\cJ}_{h}^{n},\vect{\cH}_{h}^{n}\big)^{T}$.  
-Then, if $\widetilde{\bcM}_{h}^{n}$ lies outside $\cR$ for any quadrature point $\vect{z}_{q}\in S$, i.e., $\gamma(\widetilde{\bcM}_{h}^{n})<0$, there exists an intersection point of the straight line, $\vect{s}_{q}(\xi)$, connecting $\vect{\cM}_{\bK}^{n}\in\cR$ and $\widetilde{\vect{\cM}}_{h}^{n}$ evaluated in the troubled quadrature point $\vect{z}_{q}$, denoted $\widetilde{\vect{\cM}}_{q}^{n}$, and the boundary of $\cR$.
+We let $\widetilde{\vect{\cM}}_{h}=\big(\tilde{\cJ}_{h},\vect{\cH}_{h}\big)^{T}$.  
+Then, if $\widetilde{\bcM}_{h}$ lies outside $\cR$ for any quadrature point $\vect{x}_{q}\in S$, i.e., $\gamma(\widetilde{\bcM}_{h})<0$, there exists an intersection point of the straight line, $\vect{s}_{q}(\psi)$, connecting $\vect{\cM}_{\bK}\in\cR$ and $\widetilde{\vect{\cM}}_{h}$ evaluated in the troubled quadrature point $\vect{x}_{q}$, denoted $\widetilde{\vect{\cM}}_{q}$, and the boundary of $\cR$.
 This line is given by the convex combination 
 \begin{equation}
-  \vect{s}_{q}(\xi)=\xi\,\widetilde{\vect{\cM}}_{q}^{n}+(1-\xi)\,\bcM_{\bK}^{n},
+  \vect{s}_{q}(\psi)=\psi\,\widetilde{\vect{\cM}}_{q}+(1-\psi)\,\bcM_{\bK},
 \end{equation}
-where $\xi\in[0,1]$, and the intersection point $\xi_{q}$ is obtained by solving $\gamma(\bs_{q}(\xi))=0$ for $\xi$, using the bisection algorithm.  
-We then replace the polynomial representation $\widetilde{\vect{\cM}}_{h}^{n}\to\widehat{\vect{\cM}}_{h}^{n}$, where
+where $\psi\in[0,1]$, and the intersection point $\psi_{q}$ is obtained by solving $\gamma(\bs_{q}(\psi))=0$ for $\psi$, using the bisection algorithm\footnote{In practice, $\psi$ needs not be accurate to many significant digits, and the bisection algorithm can be terminated after a few iterations.}.
+We then replace the polynomial representation $\widetilde{\vect{\cM}}_{h}\to\widehat{\vect{\cM}}_{h}$, where
 \begin{equation}
-  \widehat{\vect{\cM}}_{h}^{n}(\vect{z})=\vartheta_{2}\,\widetilde{\vect{\cM}}_{h}^{n}(\vect{z})+(1-\vartheta_{2})\,\vect{\cM}_{\bK}^{n},
+  \widehat{\vect{\cM}}_{h}(\vect{x})=\vartheta_{2}\,\widetilde{\vect{\cM}}_{h}(\vect{x})+(1-\vartheta_{2})\,\vect{\cM}_{\bK},
+  \label{eq:limitMoments}
 \end{equation}
-and $\vartheta_{2}=\min_{q}\xi_{q}$ is the smallest $\xi$ obtained in the element by considering all the troubled quadrature points.
+and $\vartheta_{2}=\min_{q}\psi_{q}$ is the smallest $\psi$ obtained in the element by considering all the troubled quadrature points.  
+This limiter is conservative in the sense that it preserves the cell-average $\widehat{\vect{\cM}}_{\bK}=\widetilde{\vect{\cM}}_{\bK}=\vect{\cM}_{\bK}$.
 
-We note that the realizability-preserving limiter is conservative; i.e., preserves the cell-average.
+The realizability-preserving property of the DG-IMEX scheme results from the following theorem.
+\begin{theorem}
+  Consider the IMEX scheme in Eqs.~\eqref{imexStages}-\eqref{eq:imexCorrection} applied to the DG discretization of the two-moment model in Eq.~\eqref{eq:semidiscreteDG}.  
+  Suppose that
+  \begin{itemize}
+    \item[1.] The conditions of Theorem~\ref{the:realizableDGIMEX} hold.  
+    \item[2.] With $\vect{\cM}_{\bK}^{(i)}\in\cR$, the limiter described above is invoked to enforce 
+    \begin{equation*}
+      \vect{\cM}_{h}^{(i)}(\vect{x})\in\cR ~ \text{for all} ~ \vect{x} \in S.  
+    \end{equation*}
+    \item[3.] The IMEX scheme is GSA.  
+  \end{itemize}
+  Then $\vect{\bcM}_{\bK}^{n+1}\in\cR$.  
+  \label{the:realizableDGIMEX2}
+\end{theorem}
+\begin{proof}
+  By Theorem~\ref{the:realizableDGIMEX} (with $i=1$), we have $\vect{\cM}_{\bK}^{(1)}\in\cR$.  
+  Application of the realizability-enforcing limiter gives $\vect{\cM}_{h}^{(1)}(\vect{x})\in\cR$ for all $\vect{x} \in S$.  
+  Repeated application of these steps give $\vect{\cM}_{h}^{(i)}(\vect{x})\in\cR$ for all $\vect{x} \in S$ and $i\in\{1,\ldots,s\}$.  
+  Since the IMEX scheme is GSA, $\tilde{\vect{\cM}}_{\bK}^{n+1}\in\cR$.  
+  Finally, $\vect{\bcM}_{\bK}^{n+1}\in\cR$ follows from Lemma~\ref{lem:imexCorrectionCellAverage}.  
+\end{proof}

### 2024-11-25 Documents/M1/collisionsM1/Matlab/ComputeNESKernelOnEGrid_TABLE.m

@@ -1,0 +1,11 @@
+function  [Chi] = ComputeNESKernelOnEGrid_TABLE(E_N, D, T, Y) 
+    
+    global g_D1D g_T1D g_Y1D g_E1D g_Chi_N g_Ab_OS;
+    
+    [ Me, ~, ~, ~ ] = interpolateDifferentiateEos...
+        ( D, T, Y, g_D1D, g_T1D, g_Y1D, g_Me.v3D, g_EOS_OS(g_Me.i) );
+    
+    [ Chi ] = interpolate4D(E_N, D, T, Y, g_E1D, g_D1D, ...
+        g_T1D, g_Y1D, [1 1 1 0], g_Chi_N, g_Ab_OS(1));
+
+end

### 2024-11-25 Documents/M1/collisionsM1/Matlab/ComputeNesScatteringOpacityOnEGrid_TABLE.m

@@ -1,0 +1,44 @@
+function  [R_in_NES_Ne, R_out_NES_Ne, R_in_NES_ANe, R_out_NES_ANe] = ComputeNesScatteringOpacityOnEGrid_TABLE(E_N, D, T, Y) 
+
+    global g_D1D g_T1D g_Y1D g_E1D g_Me g_EOS_OS g_Eta g_H_I0 g_H_II0 g_NES_OS;
+%     global g_H_I1 g_H_II1;
+    global BoltzmannConstant;
+    
+    kT = BoltzmannConstant * T;
+    
+    [ Me, ~, ~, ~ ] = interpolateDifferentiateEos...
+        ( D, T, Y, g_D1D, g_T1D, g_Y1D, g_Me.v3D, g_EOS_OS(g_Me.i) );
+    
+    Eta = Me / kT;
+    
+    % zero-th order for now
+    [ H_I0 ] = interpolate2D2D( E_N, E_N, T, Eta, g_E1D, g_E1D, g_T1D, g_Eta, [1 1 1 1], g_H_I0, g_NES_OS(1));
+    [ H_II0 ] = interpolate2D2D( E_N, E_N, T, Eta, g_E1D, g_E1D, g_T1D, g_Eta, [1 1 1 1], g_H_II0, g_NES_OS(2));
+%     [ H_I1 ] = interpolate2D2D( E_N, E_N, T, Eta, g_E1D, g_E1D, g_T1D, g_Eta, [1 1 1 1], g_H_I1, g_NES_OS(3));
+%     [ H_II1 ] = interpolate2D2D( E_N, E_N, T, Eta, g_E1D, g_E1D, g_T1D, g_Eta, [1 1 1 1], g_H_II1, g_NES_OS(4));
+
+
+    % Constants from (C50) in Bruenn 1985.
+    % see also wlOpacityInterpolationModule.f90
+    Cv = 0.96; Ca = 0.5;
+    
+    % this is (77) in the Tech Report, check the scaling
+    R_out_NES_Ne = (Cv + Ca)^2 * H_I0 + (Cv - Ca)^2 * H_II0;
+    R_out_NES_ANe = (Cv - Ca)^2 * H_I0 + (Cv + Ca)^2 * H_II0;
+    
+%%%
+% Potential saving: interpolating only upper half, and assigning the lower
+% half as below
+%%%
+    for iE  = 1:length(E_N)
+        for iEp = iE+1:length(E_N)
[…]

### 2024-11-25 Documents/M1/collisionsM1/Matlab/CreateEnergyGrid.m

@@ -1,0 +1,73 @@
+function [ eGrid ] = CreateEnergyGrid( E_lo, E_hi, nE, nGhostE, dE_0, nUni )
+
+  if ~exist( 'dE_0', 'var' )
+    dE_0 = (E_hi-E_lo)/nE;
+  end
+  
+  if ~exist( 'nUni', 'var' )
+    nUni = 1;
+  end
+  
+  eGrid.nE     = nE;
+  eGrid.E_lo   = E_lo;
+  eGrid.E_hi   = E_hi;
+  eGrid.nGhost = nGhostE;
+  
+  eGrid.Center  = zeros( nE+2*nGhostE, 1 );
+  eGrid.Width   = zeros( nE+2*nGhostE, 1 );
+  eGrid.Edge_lo = zeros( nE+2*nGhostE, 1 );
+  eGrid.Edge_hi = zeros( nE+2*nGhostE, 1 );
+  eGrid.V       = zeros( nE+2*nGhostE, 1 );
+  
+  if( dE_0 >= (E_hi-E_lo)/nE )
+    
+    % --- Return Unigrid ---
+    
+    eGrid.Width(:) = ( E_hi - E_lo ) / nE;
+  
+    for i = 1 : nE + 2 * nGhostE
+
+      j = i - nGhostE;
+    
+      eGrid.Edge_lo(i) = (j-1) * eGrid.Width(i);
+      eGrid.Edge_hi(i) = (j-0) * eGrid.Width(i);
+    
+      eGrid.Center(i) = 0.5 * ( eGrid.Edge_lo(i) + eGrid.Edge_hi(i) );
+      
+    end
+    
+  else
+      
+    % --- Return Geometric Grid ---
+    
+    nUni = max( 1, nUni );
+    
+    FUN = @( x ) (x.^(nE-(nUni-1))-1.0).*dE_0-(x-1.0).*(E_hi-(E_lo+(nUni-1)*dE_0));
+    
+    delta = 1.0d-8;
+    alpha = fzero( FUN, [(1.0+delta) 2.0] ); % --- Zoom Factor
+    
+    iOS = nGhostE;
+    
+    eGrid.Width  (iOS+1:iOS+nUni) = dE_0;
+    eGrid.Edge_lo(iOS+1:iOS+nUni) = E_lo + ((1:nUni)-1) .* dE_0;
[…]

### 2024-11-25 Documents/M1/collisionsM1/Matlab/SolveMatterEquations_EmAb_FP.m

@@ -1,0 +1,136 @@
+function [J0, D, T, Y, E, iter, Inneriter] = SolveMatterEquations_EmAb_FP( Jin, Chi, D, T, Y, E )
+
+% g_E_N       : nE_G x 1 (energy grid)
+% J, J_0    : nE_G x 1 (size of energy grid)
+% Chi       : nE_G x 1 (size of energy grid)
+% W2_N, W3_N: nE_G x 1 (size of energy grid)
+
+% constants
+global AtomicMassUnit BoltzmannConstant Erg2MeV SpeedOfLight PlanckConstant;
+
+% energy grid
+global g_E_N g_W2_N g_W3_N;
+
+% iteration data
+
+global g_Iterations_Min g_Iterations_Max g_Iterations_Ave;
+
+hc = PlanckConstant * SpeedOfLight;
+c = SpeedOfLight;
+
+Rtol = 1e-8; Utol = 1e-10; maxIter = 100;
+
+iY = 1;
+iE = 2;
+U = zeros(2,1);
+C = zeros(2,1);
+Unew = zeros(2,1);
+
+
+% \rho / m_B
+N_B = D / AtomicMassUnit;
+
+Chi = Chi * c;
+
+% scales
+s_Y = N_B;
+s_E = D;
+
+
+% (scaled) weights
+Theta2_N = 4 * pi * g_W2_N;
+Theta3_N = 4 * pi * g_W3_N;
+
+Theta2_N = Theta2_N / (hc)^3;
+Theta3_N = Theta3_N / (hc)^3;
+
+% store initial values
+Y0 = Y;
+E0 = E * Erg2MeV; % change unit
+
+% update scales
+s_Y = s_Y * Y0;
+s_E = s_E * E0;
+
+% initial guess (both 1 for now)
+U(iY) = Y / Y0;
+U(iE) = E * Erg2MeV / E0; % change unit
+
+U0 = U;
+
+% calculate known values
+C(iY) = Theta2_N' * Jin / s_Y;
+C(iE) = Theta3_N' * Jin / s_E;
+
+
+k = 0;
+Inneriter = 0;
+CONVERGED = false;
+
+while((~CONVERGED)&&(k<=maxIter))
+    
+    k = k + 1;
+    
+    % compute chemical potential and derivatives
+    [Mnu, ~, ~] = ComputeNeutrinoChemicalPotentials(D, T, Y);
+    
+    % equilibrium distribution
+    J0 = FermiDirac( g_E_N, Mnu, BoltzmannConstant * T );
+    
[…]

### 2024-11-25 Documents/M1/collisionsM1/Matlab/SolveMatterEquations_EmAb_NES_FP_coupled.m

@@ -1,0 +1,155 @@
+function [J0, D, T, Y, E, iter] = SolveMatterEquations_EmAb_NES_FP_coupled( Jin, dt, Chi, D, T, Y, E)
+
+% g_E_N       : nE_G x 1 (energy grid)
+% J, J_0    : nE_G x 1 (size of energy grid)
+% Chi       : nE_G x 1 (size of energy grid)
+% W2_N, W3_N: nE_G x 1 (size of energy grid)
+
+% constants
+global AtomicMassUnit BoltzmannConstant Erg2MeV SpeedOfLight PlanckConstant;
+
+% energy grid
+global g_E_N g_W2_N g_W3_N;
+
+
+hc = PlanckConstant * SpeedOfLight;
+c = SpeedOfLight;
+
+Rtol = 1e-8; Utol = 1e-10; maxIter = 100;
+
+iY = 1;
+iE = 2;
+U = zeros(2,1);
+C = zeros(2,1);
+Unew = zeros(2,1);
+
+
+% \rho / m_B
+N_B = D / AtomicMassUnit;
+
+Chi = Chi * c * dt;
+% R_in_NES = R_in_NES * c * dt;
+% R_out_NES = R_out_NES * c * dt;
+
+% scales
+s_Y = N_B;
+s_E = D;
+
+% weights (for NES)
+W2_N = g_W2_N;
+
+
+% (scaled) weights
+Theta2_N = 4 * pi * g_W2_N;
+Theta3_N = 4 * pi * g_W3_N;
+
+Theta2_N = Theta2_N / (hc)^3;
+Theta3_N = Theta3_N / (hc)^3;
+
+% store initial values
+Y0 = Y;
+E0 = E * Erg2MeV; % change unit
+
+% update scales
+s_Y = s_Y * Y0;
+s_E = s_E * E0;
+
+% initial guess (both 1 for now)
+U(iY) = Y / Y0;
+U(iE) = E * Erg2MeV / E0; % change unit
+
+U0 = U;
+
+J = Jin;
+
+% calculate known values
+C(iY) = Theta2_N' * Jin / s_Y;
+C(iE) = Theta3_N' * Jin / s_E;
+
+
+k = 0;
+CONVERGED = false;
+
+
+% compute chemical potential and derivatives
+[Mnu, ~, ~] = ComputeNeutrinoChemicalPotentials(D, T, Y);
+
+% equilibrium distribution
+J0 = FermiDirac( g_E_N, Mnu, BoltzmannConstant * T );
[…]

### 2024-11-25 Documents/M1/collisionsM1/Matlab/SolveMatterEquations_Pair.m

@@ -1,0 +1,238 @@
+function [J, J0, D, T, Y, E, iter] = SolveMatterEquations_Pair( Jin, dt, Chi, D, T, Y, E)
+
+% g_E_N       : nE_G x 1 (energy grid)
+% J, J_0    : nE_G x 1 (size of energy grid)
+% Chi       : nE_G x 1 (size of energy grid)
+% W2_N, W3_N: nE_G x 1 (size of energy grid)
+
+% constants
+global AtomicMassUnit BoltzmannConstant Erg2MeV SpeedOfLight PlanckConstant;
+
+% energy grid
+global g_E_N g_W2_N g_W3_N;
+
+
+hc = PlanckConstant * SpeedOfLight;
+c = SpeedOfLight;
+
+Rtol = 1e-8; Utol = 1e-10; maxIter = 100;
+
+iY = 1;
+iE = 2;
+iJNe = iE + (1:length(Jin.Ne));
+iJANe = iJNe(end) + (1:length(Jin.ANe));
+
+U = zeros(2,1);
+C = zeros(2,1);
+
+
+% \rho / m_B
+N_B = D / AtomicMassUnit;
+
+Chi.Ne = Chi.Ne * c * dt;
+Chi.ANe = Chi.ANe * c * dt;
+
+% scales
+s_Y = N_B;
+s_E = D;
+
+% weights (for NES)
+W2_N = g_W2_N;
+
+
+% (scaled) weights
+Theta2_N = 4 * pi * g_W2_N;
+Theta3_N = 4 * pi * g_W3_N;
+
+Theta2_N = Theta2_N / (hc)^3;
+Theta3_N = Theta3_N / (hc)^3;
+
+% store initial values
+Y0 = Y;
+E0 = E * Erg2MeV; % change unit
+
+% update scales
+s_Y = s_Y * Y0;
+s_E = s_E * E0;
+
+% initial guess (both 1 for now)
+U(iY) = Y / Y0;
+U(iE) = E * Erg2MeV / E0; % change unit
+
+U0 = U;
+
+J = Jin;
+
+
+% calculate known values
+C(iY) = Theta2_N' * (Jin.Ne - Jin.ANe)/ s_Y;
+C(iE) = Theta3_N' * (Jin.Ne + Jin.ANe) / s_E;
+
+
+k = 0;
+CONVERGED = false;
+
[…]

### 2024-11-25 Documents/M1/collisionsM1/Matlab/UpdateNeutrinoDistribution_exact.m

@@ -1,0 +1,8 @@
+function [Jout, iter] = UpdateNeutrinoDistribution_exact(Jin, J0, Chi)
+
+Jout = (Jin + Chi.*J0)./(1 + Chi);
+
+iter = 1;
+
+end
+

### 2024-11-25 Documents/M1/collisionsM1/Matlab/interpolate2D2D.m

@@ -1,0 +1,102 @@
+function [ Interpolant ] = interpolate2D2D( x1, x2, x3, x4, x11D, x21D, x31D, x41D, Logflag, V4D,OS )
+% function [ Interpolant ] =
+%          interpolate2D2D( x1, x2, x3, x4, x11D, x21D, x31D, x41D, Logflag, V4D,OS )
+% x1, x2 are (N,1) array
+% x3, x4 are (M,1) array
+% function value Interpolant is a (N,N,M) array
+
+Interpolant = zeros( size( x1, 1 ), size( x2, 1 ), size( x3, 1 ) );
+
+for k = 1 : size( x3, 1)
+    
+    ix3 = find( x31D < x3(k), 1, 'last' );
+    ix4 = find( x41D < x4(k), 1, 'last' );
+    
+    if ( Logflag(3) == 1 ) dx3 = log10( x3(k) / x31D(ix3) ) / log10( x31D(ix3+1) / x31D(ix3) );
+    elseif ( Logflag(3) == 0 ) dx3 = ( x3(k) - x31D(ix3) ) / ( x31D(ix3+1) - x31D(ix3) );
+    end
+    
+    if ( Logflag(4) == 1 ) dx4 = log10( x4(k) / x41D(ix4) ) / log10( x41D(ix4+1) / x41D(ix4) );
+    elseif ( Logflag(4) == 0 ) dx4 = ( x4(k) - x41D(ix4) ) / ( x41D(ix4+1) - x41D(ix4) );
+    end
+    
+    for i = 1 : size( x2, 1 )
+        
+        ix2 = find( x21D < x2(i), 1, 'last' );
+        
+        if ( Logflag(2) == 1 ) dx2 = log10( x2(i) / x21D(ix2) ) / log10( x21D(ix2+1) / x21D(ix2) );
+        elseif ( Logflag(2) == 0 ) dx2 = ( x2(i) - x21D(ix2) ) / ( x21D(ix2+1) - x21D(ix2) );
+        end
+        
+        for j = 1 : size( x1, 1)
+            
+            ix1 = find( x11D < x1(j), 1, 'last' );
+            
+            
+            
+            if ( Logflag(1) == 1 ) dx1 = log10( x1(j) / x11D(ix1) ) / log10( x11D(ix1+1) / x11D(ix1) );
[…]

### 2024-11-25 Documents/M1/collisionsM1/Matlab/readTables.m

@@ -1,0 +1,49 @@
+function readTables()
+% read tables
+    
+    % grids
+    global g_D1D g_T1D g_Y1D;
+    
+    % chemical potential
+    global g_Me g_Mp g_Mn;
+    
+    % internal energy density
+    global g_E;
+    
+    % EOS offset
+    global g_EOS_OS;
+    
+    % Emission and Absorption (neutrino and antineutrino)
+    global g_Chi_Ne g_Chi_ANe g_Ab_OS;
+    
+    % energy grid
+    global g_E1D;
+    
+    % Eta grid
+    global g_Eta;
+    
+    % NES kernels
+    global g_H_I0 g_H_II0 g_H_I1 g_H_II1; 
+    
+    % NES offset
+    global g_NES_OS;
+    
+    % NES kernels
+    global g_J_I0 g_J_II0 g_J_I1 g_J_II1; 
+    
+    % NES offset
+    global g_Pair_OS;
+
+    [ g_D1D, g_T1D, g_Y1D, nD, nT, nY, P, S, g_E, g_Me, g_Mp, g_Mn, Xp, Xn, Xa, Xh,...
+    Zh, Ah, Eh, Eth, Gm, g_EOS_OS ] = readEosTable('wl-EOS-SFHo-15-25-50.h5');
+
+    [ g_E1D, ~, ~, ~, g_Chi_Ne, g_Chi_ANe, g_Ab_OS ] = readAbsorptionOpacityTable('wl-Op-SFHo-15-25-50-E40-B85-AbEm.h5');
+    
+     
+% [ E, D, T, Y, R_0_N, R_1_N, R_0_AN, R_1_AN, OS ] = readIsoScatteringOpacityTable('wl-Op-SFHo-15-25-50-E40-B85-Iso.h5');
+
+    [ ~, ~, g_Eta, g_H_I0, g_H_II0, g_H_I1, g_H_II1, g_NES_OS] = readNesScatteringOpacityTable('wl-Op-SFHo-15-25-50-E40-B85-NES.h5');
+
+    [ ~, ~, ~, g_J_I0, g_J_II0, g_J_I1, g_J_II1, g_Pair_OS] = readPairOpacityTable('wl-Op-SFHo-15-25-50-E40-B85-Pair.h5');
+
+end

### 2024-11-25 Examples/TwoMoment/InitializationModule.F90

@@ -1,0 +1,380 @@
+MODULE InitializationModule
+
+  USE KindModule, ONLY: &
+    DP, Zero, One, Two, TwoPi
+  USE UnitsModule, ONLY: &
+    Centimeter, &
+    Kilometer, &
+    Gram, &
+    MeV, &
+    BoltzmannConstant, &
+    SpeedOfLight
+  USE ProgramHeaderModule, ONLY: &
+    ProgramName, &
+    iX_B0, iX_E0, &
+    iE_B0, iE_E0, &
+    nDOF, nDOFE, nDOFX
+  USE ReferenceElementModule, ONLY: &
+    NodeNumberTable
+  USE MeshModule, ONLY: &
+    MeshE, &
+    MeshX, &
+    NodeCoordinate
+  USE FluidFieldsModule, ONLY: &
+    uPF, iPF_D, iPF_V1, iPF_V2, iPF_V3, iPF_E, iPF_Ne, &
+    uCF, iCF_D, iCF_S1, iCF_S2, iCF_S3, iCF_E, iCF_Ne, &
+    uAF, iAF_P, iAF_T, iAF_Ye, iAF_S, iAF_E, iAF_Me, iAF_Mp, iAF_Mn, &
+    iAF_Xp, iAF_Xn, iAF_Xa, iAF_Xh, iAF_Gm
+  USE RadiationFieldsModule, ONLY: &
+    nSpecies, &
+    uPR, iPR_D, iPR_I1, iPR_I2, iPR_I3, &
+    uCR, iCR_N, iCR_G1, iCR_G2, iCR_G3
+  USE Euler_UtilitiesModule_NonRelativistic, ONLY: &
+    ComputeConserved_Euler_NonRelativistic
+  USE TwoMoment_UtilitiesModule, ONLY: &
+    ComputeConserved_TwoMoment
+  USE EquationOfStateModule_TABLE, ONLY: &
+    ApplyEquationOfState_TABLE, &
+    ComputeThermodynamicStates_Primitive_TABLE
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeFields
+  PUBLIC :: ComputeError
+
+CONTAINS
+
+
+  SUBROUTINE InitializeFields
+
+    WRITE(*,*)
+    WRITE(*,'(A2,A6,A)') '', 'INFO: ', TRIM( ProgramName )
+
+    SELECT CASE( TRIM( ProgramName ) )
+
[…]

### 2024-11-25 Modules/Euler/Euler_CharacteristicDecompositionModule_Relativistic_IDEAL.F90

@@ -1,0 +1,1020 @@
+MODULE Euler_CharacteristicDecompositionModule_Relativistic_IDEAL
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One, &
+    Two
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    iCF_D, &
+    iCF_S1, &
+    iCF_S2, &
+    iCF_S3, &
+    iCF_E, &
+    iCF_Ne
+  USE Euler_UtilitiesModule_Relativistic, ONLY: &
+    ComputePrimitive_Euler_Relativistic, &
+    Eigenvalues_Euler_Relativistic
+  USE EquationOfStateModule_IDEAL, ONLY: &
+    Gamma_IDEAL
+  USE EquationOfStateModule, ONLY: &
+    ComputeSoundSpeedFromPrimitive, &
+    ComputePressureFromPrimitive
+
+  USE MPI
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: ComputeCharacteristicDecomposition_Euler_Relativistic_IDEAL
+
+
+CONTAINS
+
+
+  SUBROUTINE ComputeCharacteristicDecomposition_Euler_Relativistic_IDEAL &
+    ( iDim, G, U, R, invR )
+
+#if defined(THORNADO_OMP_OL) && !defined(THORNADO_EULER_NOGPU)
+    !$OMP DECLARE TARGET
+#elif defined(THORNADO_OACC) && !defined(THORNADO_EULER_NOGPU)
+    !$ACC ROUTINE SEQ
+#endif
+
+    INTEGER,  INTENT(in)    :: iDim
+    REAL(DP), INTENT(in)    :: G(8)
+    REAL(DP), INTENT(inout) :: U(nCF)
+    REAL(DP), INTENT(out)   :: R(nCF,nCF), invR(nCF,nCF)
+
+    ! --- Expressions for right and left eigenvector matrices from
+    !     Rezzolla & Zanotti, Relativistic Hydrodynamics, Eq. 7.240-7.248 ---
+
+    REAL(DP) :: D, V1, V2, V3, E, Ne
+    REAL(DP) :: P, Cs
+    REAL(DP) :: Vu1, Vu2, Vu3, Vd1, Vd2, Vd3, VSq
[…]

### 2024-11-25 Modules/Euler/Euler_DiscontinuityDetectionModule.F90

@@ -1,0 +1,1732 @@
+MODULE Euler_DiscontinuityDetectionModule
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One, &
+    Two, &
+    Third, &
+    SqrtTiny
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDimsX, &
+    nNodes
+  USE ReferenceElementModuleX, ONLY: &
+    NodeNumberTableX, &
+    WeightsX_q, &
+    NodesX1, &
+    NodesX2, &
+    NodesX3
+  USE LinearAlgebraModule, ONLY: &
+    MatrixVectorMultiply
+  USE PolynomialBasisModuleX_Lagrange, ONLY: &
+    L_X1, &
+    L_X2, &
+    L_X3
+  USE GeometryFieldsModule, ONLY: &
+    nGF, &
+    iGF_Gm_dd_11, &
+    iGF_Gm_dd_22, &
+    iGF_Gm_dd_33, &
+    iGF_Alpha, &
+    iGF_Beta_1, &
+    iGF_Beta_2, &
+    iGF_Beta_3, &
+    iGF_SqrtGm
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    iCF_D, &
+    iCF_S1, &
+    iCF_S2, &
+    iCF_S3, &
+    iCF_E, &
+    iCF_Ne, &
+    nPF, &
+    iPF_D, &
+    iPF_V1, &
+    iPF_V2, &
+    iPF_V3, &
+    iPF_E, &
+    iPF_Ne, &
+    nDF, &
+    iDF_TCI, &
+    iDF_Sh_X1, &
+    iDF_Sh_X2, &
+    iDF_Sh_X3
+  USE Euler_UtilitiesModule, ONLY: &
+    ComputePrimitive_Euler
+  USE EquationOfStateModule, ONLY: &
+    ComputePressureFromPrimitive
+  USE UtilitiesModule, ONLY: &
+    IsCornerCell
+  USE TimersModule_Euler, ONLY: &
+    TimersStart_Euler, &
+    TimersStop_Euler, &
+    Timer_Euler_DD_TCI, &
+    Timer_Euler_DD_TCI_DetectTroubledCells, &
+    Timer_Euler_DD_TCI_CopyIn, &
+    Timer_Euler_DD_TCI_CopyOut, &
[…]

### 2024-11-25 Modules/Euler/Euler_MeshRefinementModule.F90

@@ -1,0 +1,790 @@
+MODULE Euler_MeshRefinementModule
+
+  USE ISO_C_BINDING
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One, &
+    Half, &
+    Two
+  USE ProgramHeaderModule, ONLY: &
+    nDimsX, &
+    nNodesX, &
+    nDOFX
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+     LX_X1_Dn, &
+     LX_X1_Up, &
+     LX_X2_Dn, &
+     LX_X2_Up, &
+     LX_X3_Dn, &
+     LX_X3_Up
+  USE ReferenceElementModuleX, ONLY: &
+    NodesX1, &
+    NodesX2, &
+    NodesX3, &
+    NodesLX1, &
+    NodesLX2, &
+    NodesLX3, &
+    WeightsX1, &
+    WeightsX2, &
+    WeightsX3, &
+    WeightsX_X1, &
+    WeightsX_X2, &
+    WeightsX_X3, &
+    WeightsX_q, &
+    nDOFX_X1, &
+    nDOFX_X2, &
+    nDOFX_X3, &
+    NodeNumberTableX, &
+    NodeNumberTableX_X1, &
+    NodeNumberTableX_X2, &
+    NodeNumberTableX_X3, &
+    NodeNumberTableX3D
+  USE PolynomialBasisModuleX_Lagrange, ONLY: &
+    IndLX_Q, &
+    L_X1, &
+    L_X2, &
+    L_X3
+  USE GeometryFieldsModule, ONLY: &
+    iGF_SqrtGm
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeMeshRefinement_Euler
+  PUBLIC :: FinalizeMeshRefinement_Euler
+  PUBLIC :: Refine_Euler
+  PUBLIC :: Coarsen_Euler
+
+  REAL(DP)         :: VolumeRatio
+  REAL(DP), PUBLIC :: FaceRatio
+  INTEGER , PUBLIC :: nFine, nFineX_X1, nFineX_X2, nFineX_X3
+  INTEGER          :: nFineX(3)
+
+  ! --- For reflux ---
+
+  TYPE(c_ptr), PUBLIC                 ::  pNodeNumberTableX_X1_c
[…]

### 2024-11-25 Modules/Euler/Euler_PositivityLimiterModule.F90

@@ -1,0 +1,252 @@
+MODULE Euler_PositivityLimiterModule
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One
+
+#if   defined( MICROPHYSICS_WEAKLIB ) && defined( HYDRO_RELATIVISTIC    )
+
+  USE Euler_PositivityLimiterModule_Relativistic_TABLE
+
+#elif defined( MICROPHYSICS_WEAKLIB ) && defined( HYDRO_NONRELATIVISTIC )
+
+  USE Euler_PositivityLimiterModule_NonRelativistic_TABLE
+
+#elif defined( HYDRO_RELATIVISTIC )
+
+  USE Euler_PositivityLimiterModule_Relativistic_IDEAL
+
+#else
+
+  USE Euler_PositivityLimiterModule_NonRelativistic_IDEAL
+
+#endif
+
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializePositivityLimiter_Euler
+  PUBLIC :: FinalizePositivityLimiter_Euler
+  PUBLIC :: ApplyPositivityLimiter_Euler
+
+
+CONTAINS
+
+
+  SUBROUTINE InitializePositivityLimiter_Euler &
+    ( UsePositivityLimiter_Option, Verbose_Option, &
+      Min_1_Option, Min_2_Option, Min_3_Option, &
+      Max_1_Option, Max_2_Option, Max_3_Option, &
+      D_Min_Euler_PL_Option, IntE_Min_Euler_PL_Option )
+
+    LOGICAL , INTENT(in), OPTIONAL :: UsePositivityLimiter_Option
+    LOGICAL , INTENT(in), OPTIONAL :: Verbose_Option
+    REAL(DP), INTENT(in), OPTIONAL :: Min_1_Option, Max_1_Option
+    REAL(DP), INTENT(in), OPTIONAL :: Min_2_Option, Max_2_Option
+    REAL(DP), INTENT(in), OPTIONAL :: Min_3_Option, Max_3_Option
+    REAL(DP), INTENT(in), OPTIONAL :: D_Min_Euler_PL_Option
+    REAL(DP), INTENT(in), OPTIONAL :: IntE_Min_Euler_PL_Option
+
+    LOGICAL  :: UsePositivityLimiter
+    LOGICAL  :: Verbose
+    REAL(DP) :: Min_1, Max_1
[…]

### 2024-11-25 Modules/Euler/Euler_PositivityLimiterModule_NonRelativistic_IDEAL.f90

@@ -1,0 +1,534 @@
+MODULE Euler_PositivityLimiterModule_NonRelativistic_IDEAL
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    Half, &
+    One
+  USE UtilitiesModule, ONLY: &
+    IsCornerCell
+  USE ProgramHeaderModule, ONLY: &
+    nNodesX, &
+    nDOFX
+  USE ReferenceElementModuleX, ONLY: &
+    WeightsX_q, &
+    nDOFX_X1, &
+    nDOFX_X2, &
+    nDOFX_X3
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+    LX_X1_Dn, &
+    LX_X1_Up, &
+    LX_X2_Dn, &
+    LX_X2_Up, &
+    LX_X3_Dn, &
+    LX_X3_Up
+  USE GeometryComputationModule, ONLY: &
+    ComputeGeometryX_FromScaleFactors
+  USE GeometryFieldsModule, ONLY: &
+    nGF, &
+    iGF_h_1, &
+    iGF_h_2, &
+    iGF_h_3, &
+    iGF_Gm_dd_11, &
+    iGF_Gm_dd_22, &
+    iGF_Gm_dd_33, &
+    iGF_SqrtGm
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    iCF_D, &
+    iCF_S1, &
+    iCF_S2, &
+    iCF_S3, &
+    iCF_E
+  USE TimersModule_Euler, ONLY: &
+    TimersStart_Euler, &
+    TimersStop_Euler, &
+    Timer_Euler_PositivityLimiter
+  USE UnitsModule, ONLY: &
+    UnitsDisplay
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializePositivityLimiter_Euler_NonRelativistic_IDEAL
+  PUBLIC :: FinalizePositivityLimiter_Euler_NonRelativistic_IDEAL
+  PUBLIC :: ApplyPositivityLimiter_Euler_NonRelativistic_IDEAL
+
+
+  LOGICAL               :: UsePositivityLimiter
+  LOGICAL               :: Verbose
+  INTEGER, PARAMETER    :: nPS = 7
+  INTEGER               :: nPP(nPS)
+  INTEGER               :: nPT
[…]

### 2024-11-25 Modules/Euler/Euler_PositivityLimiterModule_NonRelativistic_TABLE.F90

@@ -1,0 +1,1251 @@
+MODULE Euler_PositivityLimiterModule_NonRelativistic_TABLE
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    Half, &
+    One, &
+    SqrtTiny
+  USE UnitsModule, ONLY: &
+    Gram, &
+    Centimeter, &
+    Kelvin, &
+    AtomicMassUnit
+  USE ProgramHeaderModule, ONLY: &
+    nNodesX, &
+    nDOFX
+  USE LinearAlgebraModule, ONLY: &
+    MatrixMatrixMultiply
+  USE ReferenceElementModuleX, ONLY: &
+    WeightsX_q, &
+    nDOFX_X1, &
+    nDOFX_X2, &
+    nDOFX_X3
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+    LX_X1_Dn, &
+    LX_X1_Up, &
+    LX_X2_Dn, &
+    LX_X2_Up, &
+    LX_X3_Dn, &
+    LX_X3_Up
+  USE GeometryFieldsModule, ONLY: &
+    nGF, &
+    iGF_h_1, &
+    iGF_h_2, &
+    iGF_h_3, &
+    iGF_SqrtGm
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    iCF_D, &
+    iCF_S1, &
+    iCF_S2, &
+    iCF_S3, &
+    iCF_E, &
+    iCF_Ne, &
+    nDF, &
+    iDF_T1, &
+    iDF_T2, &
+    iDF_T3, &
+    iDF_MinE, &
+    iDF_MaxE
+  USE EquationOfStateModule_TABLE, ONLY: &
+    ComputeSpecificInternalEnergy_TABLE
+  USE TimersModule_Euler, ONLY: &
+    TimersStart_Euler, &
+    TimersStop_Euler, &
+    Timer_Euler_PositivityLimiter, &
+    Timer_Euler_PL_LimitCells, &
+    Timer_Euler_PL_CopyIn, &
+    Timer_Euler_PL_CopyOut, &
+    Timer_Euler_PL_Permute, &
+    Timer_Euler_PL_Integrate
+
+  IMPLICIT NONE
+  PRIVATE
+
[…]

### 2024-11-25 Modules/Euler/Euler_PositivityLimiterModule_Relativistic_IDEAL.F90

@@ -1,0 +1,921 @@
+!> Initialize, finalize, and apply positivity limiter from
+!> Qin et al., (2016), JCP, 315, 323
+MODULE Euler_PositivityLimiterModule_Relativistic_IDEAL
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    Half, &
+    One, &
+    SqrtTiny
+  USE UtilitiesModule, ONLY: &
+    IsCornerCell
+  USE UnitsModule, ONLY: &
+    UnitsDisplay
+  USE ProgramHeaderModule, ONLY: &
+    nNodesX, &
+    nDOFX
+  USE LinearAlgebraModule, ONLY: &
+    MatrixMatrixMultiply
+  USE ReferenceElementModuleX, ONLY: &
+    nDOFX_X1, &
+    nDOFX_X2, &
+    nDOFX_X3, &
+    WeightsX_q
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+    LX_X1_Dn, &
+    LX_X1_Up, &
+    LX_X2_Dn, &
+    LX_X2_Up, &
+    LX_X3_Dn, &
+    LX_X3_Up
+  USE GeometryFieldsModule, ONLY: &
+    iGF_h_1, &
+    iGF_h_2, &
+    iGF_h_3, &
+    iGF_SqrtGm
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    iCF_D, &
+    iCF_S1, &
+    iCF_S2, &
+    iCF_S3, &
+    iCF_E
+  USE TimersModule_Euler, ONLY: &
+    TimersStart_Euler, &
+    TimersStop_Euler, &
+    Timer_Euler_PositivityLimiter, &
+    Timer_Euler_PL_LimitCells, &
+    Timer_Euler_PL_CopyIn, &
+    Timer_Euler_PL_CopyOut, &
+    Timer_Euler_PL_Permute, &
+    Timer_Euler_PL_Integrate, &
+    Timer_Euler_PL_ErrorCheck
+  USE Euler_ErrorModule, ONLY: &
+    DescribeError_Euler
+
+  USE MPI
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializePositivityLimiter_Euler_Relativistic_IDEAL
+  PUBLIC :: FinalizePositivityLimiter_Euler_Relativistic_IDEAL
+  PUBLIC :: ApplyPositivityLimiter_Euler_Relativistic_IDEAL
+
[…]

### 2024-11-25 Modules/Euler/Euler_SlopeLimiterModule_NonRelativistic_IDEAL.f90

@@ -1,0 +1,600 @@
+MODULE Euler_SlopeLimiterModule_NonRelativistic_IDEAL
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDimsX, &
+    nNodes, &
+    nNodesX, &
+    bcX
+  USE ReferenceElementModuleX, ONLY: &
+    WeightsX_q
+  USE UtilitiesModule, ONLY: &
+    MinModB, &
+    NodeNumberX
+  USE PolynomialBasisModule_Legendre, ONLY: &
+    P_X1, &
+    P_X2, &
+    P_X3, &
+    IndPX_Q
+  USE PolynomialBasisMappingModule, ONLY: &
+    MapNodalToModal_Fluid, &
+    MapModalToNodal_Fluid
+  USE MeshModule, ONLY: &
+    MeshX
+  USE GeometryFieldsModule, ONLY: &
+    nGF, &
+    iGF_Gm_dd_11, &
+    iGF_Gm_dd_22, &
+    iGF_Gm_dd_33, &
+    iGF_SqrtGm
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    iDF_TCI
+  USE Euler_BoundaryConditionsModule, ONLY: &
+    ApplyInnerBC_Euler, &
+    ApplyOuterBC_Euler, &
+    iApplyBC_Euler_Both, &
+    ApplyBoundaryConditions_Euler
+  USE Euler_CharacteristicDecompositionModule_NonRelativistic_IDEAL, ONLY: &
+    ComputeCharacteristicDecomposition_Euler_NonRelativistic_IDEAL
+  USE Euler_DiscontinuityDetectionModule, ONLY: &
+    InitializeTroubledCellIndicator_Euler, &
+    FinalizeTroubledCellIndicator_Euler, &
+    LimiterThreshold, &
+    DetectTroubledCells_Euler
+  USE TimersModule_Euler, ONLY: &
+    TimersStart_Euler, &
+    TimersStop_Euler, &
+    Timer_Euler_SlopeLimiter
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeSlopeLimiter_Euler_NonRelativistic_IDEAL
[…]

### 2024-11-25 Modules/Euler/Euler_SlopeLimiterModule_Relativistic_IDEAL_WENO.F90

@@ -1,0 +1,1415 @@
+MODULE Euler_SlopeLimiterModule_Relativistic_IDEAL_WENO
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One, &
+    Two
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDimsX, &
+    nNodes, &
+    nNodesX, &
+    bcX
+  USE LinearAlgebraModule, ONLY: &
+    MatrixVectorMultiply, &
+    MatrixMatrixMultiply
+  USE ReferenceElementModuleX, ONLY: &
+    WeightsX_q, &
+    NodeNumberTableX
+  USE UtilitiesModule, ONLY: &
+    MinModB, &
+    NodeNumberX
+  USE PolynomialBasisModule_Legendre, ONLY: &
+    P_X1, &
+    P_X2, &
+    P_X3, &
+    IndPX_Q, &
+    MassPX
+  USE PolynomialBasisMappingModule, ONLY: &
+    MapNodalToModal_Fluid, &
+    MapModalToNodal_Fluid, &
+    Kij_X, &
+    Pij_X
+  USE MeshModule, ONLY: &
+    MeshX
+  USE GeometryFieldsModule, ONLY: &
+    nGF, &
+    iGF_Gm_dd_11, &
+    iGF_Gm_dd_22, &
+    iGF_Gm_dd_33, &
+    iGF_Alpha, &
+    iGF_Beta_1, &
+    iGF_Beta_2, &
+    iGF_Beta_3, &
+    iGF_SqrtGm
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    iCF_D, &
+    iCF_S1, &
+    iCF_S2, &
+    iCF_S3, &
+    iCF_E, &
+    iCF_Ne, &
+    iDF_TCI
+  USE Euler_BoundaryConditionsModule, ONLY: &
+    ApplyInnerBC_Euler, &
+    ApplyOuterBC_Euler, &
+    iApplyBC_Euler_Both, &
+    ApplyBoundaryConditions_Euler
+  USE Euler_CharacteristicDecompositionModule_Relativistic_IDEAL, ONLY: &
+    ComputeCharacteristicDecomposition_Euler_Relativistic_IDEAL
+  USE Euler_DiscontinuityDetectionModule, ONLY: &
+    InitializeTroubledCellIndicator_Euler, &
+    FinalizeTroubledCellIndicator_Euler, &
+    LimiterThreshold, &
[…]

### 2024-11-25 Modules/Euler/Euler_UtilitiesModule_NonRelativistic.F90

@@ -1,0 +1,815 @@
+MODULE Euler_UtilitiesModule_NonRelativistic
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    SqrtTiny, &
+    Half, &
+    One
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDimsX
+  USE MeshModule, ONLY: &
+    MeshX
+  USE GeometryFieldsModule, ONLY: &
+    iGF_Gm_dd_11, &
+    iGF_Gm_dd_22, &
+    iGF_Gm_dd_33
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    iCF_D, &
+    iCF_S1, &
+    iCF_S2, &
+    iCF_S3, &
+    iCF_E, &
+    iCF_Ne, &
+    nPF, &
+    iPF_D, &
+    iPF_V1, &
+    iPF_V2, &
+    iPF_V3, &
+    iPF_E, &
+    iPF_Ne, &
+    iAF_P, &
+    iAF_T, &
+    iAF_Ye, &
+    iAF_S, &
+    iAF_E, &
+    iAF_Gm, &
+    iAF_Cs, &
+    iAF_Me, &
+    iAF_Mp, &
+    iAF_Mn, &
+    iAF_Xp, &
+    iAF_Xn, &
+    iAF_Xa, &
+    iAF_Xh
+  USE EquationOfStateModule, ONLY: &
+    ComputeSoundSpeedFromPrimitive, &
+    ComputeAuxiliary_Fluid, &
+    ApplyEquationOfState
+  USE TimersModule_Euler, ONLY: &
+    TimersStart_Euler, &
+    TimersStop_Euler, &
+    Timer_Euler_ComputeTimeStep, &
+    Timer_Euler_CTS_ComputeTimeStep, &
+    Timer_Euler_CTS_CopyIn, &
+    Timer_Euler_CTS_CopyOut
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: ComputePrimitive_Euler_NonRelativistic
+  PUBLIC :: ComputeConserved_Euler_NonRelativistic
+  PUBLIC :: ComputeFromConserved_Euler_NonRelativistic
+  PUBLIC :: ComputeTimeStep_Euler_NonRelativistic
+  PUBLIC :: Eigenvalues_Euler_NonRelativistic
[…]

### 2024-11-25 Modules/Geometry/GravitySolutionModule_XCFC_Poseidon.F90

@@ -1,0 +1,224 @@
+MODULE GravitySolutionModule_XCFC_Poseidon
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    Half
+  USE ProgramHeaderModule, ONLY: &
+    nX, &
+    nNodesX, &
+    nNodes, &
+    xL, &
+    xR
+  USE MeshModule, ONLY: &
+    MeshX
+  USE GeometryComputationModule, ONLY: &
+    LapseFunction, &
+    ConformalFactor
+  USE XCFC_UtilitiesModule, ONLY: &
+    iGS_E, &
+    iGS_S1, &
+    iGS_S2, &
+    iGS_S3, &
+    iGS_S, &
+    iMF_Psi, &
+    iMF_Alpha, &
+    iMF_Beta_1, &
+    iMF_Beta_2, &
+    iMF_Beta_3, &
+    iMF_K_dd_11, &
+    iMF_K_dd_12, &
+    iMF_K_dd_13, &
+    iMF_K_dd_22, &
+    iMF_K_dd_23, &
+    iMF_K_dd_33, &
+    swX_GS, &
+    ComputeGravitationalMass
+
+#ifdef GRAVITY_SOLVER_POSEIDON_XCFC
+
+  ! --- Poseidon Modules ---
+
+  USE Poseidon_Interface_Initialization, ONLY: &
+    Initialize_Poseidon
+  USE Poseidon_Interface_Boundary_Conditions, ONLY : &
+    Poseidon_Set_Uniform_Boundary_Conditions
+  USE Poseidon_Interface_Source_Input, ONLY: &
+    Poseidon_Input_Sources_Part1, &
+    Poseidon_Input_Sources_Part2
+  USE Poseidon_Interface_Run, ONLY: &
+    Poseidon_XCFC_Run_Part1, &
+    Poseidon_XCFC_Run_Part2
+  USE Poseidon_Interface_Return_Routines, ONLY: &
+    Poseidon_Return_Conformal_Factor, &
+    Poseidon_Return_Lapse_Function, &
+    Poseidon_Return_Shift_Vector, &
+    Poseidon_Return_Extrinsic_Curvature
+  USE Poseidon_Interface_Close, ONLY: &
+    Poseidon_Close
+
+#endif
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeGravitySolver_XCFC_Poseidon
[…]

### 2024-11-25 Modules/Geometry/XCFC_UtilitiesModule.f90

@@ -1,0 +1,426 @@
+MODULE XCFC_UtilitiesModule
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    Two, &
+    Pi
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDOFE, &
+    nDOF, &
+    nDimsX, &
+    swE
+  USE ReferenceElementModuleX, ONLY: &
+    WeightsX_q, &
+    NodeNumberTableX
+  USE MeshModule, ONLY: &
+    MeshX, &
+    NodeCoordinate
+  USE GeometryFieldsModule, ONLY: &
+    iGF_h_1, &
+    iGF_h_2, &
+    iGF_h_3, &
+    iGF_SqrtGm, &
+    iGF_Alpha, &
+    iGF_Beta_1, &
+    iGF_Beta_2, &
+    iGF_Beta_3, &
+    iGF_Psi, &
+    iGF_K_dd_11, &
+    iGF_K_dd_12, &
+    iGF_K_dd_13, &
+    iGF_K_dd_22, &
+    iGF_K_dd_23, &
+    iGF_K_dd_33
+  USE GeometryBoundaryConditionsModule, ONLY: &
+    ApplyBoundaryConditions_Geometry_X1_Inner_Reflecting, &
+    ApplyBoundaryConditions_Geometry_X1_Outer_ExtrapolateToFace
+  USE GeometryComputationModule, ONLY: &
+    ComputeGeometryX_FromScaleFactors
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: MultiplyWithPsi6
+  PUBLIC :: ApplyBoundaryConditions_Geometry_XCFC
+  PUBLIC :: ComputeGravitationalMass
+  PUBLIC :: UpdateConformalFactorAndMetric_XCFC
+  PUBLIC :: UpdateLapseShiftCurvature_XCFC
+
+  INTEGER, PUBLIC :: swX_GS(3)
+
+  ! --- MF: Metric Fields ---
+
+  INTEGER, PARAMETER, PUBLIC :: iMF_Psi     = 1
+  INTEGER, PARAMETER, PUBLIC :: iMF_Alpha   = 2
+  INTEGER, PARAMETER, PUBLIC :: iMF_Beta_1  = 3
[…]

### 2024-11-25 Modules/Library/ReferenceElementModule.F90

@@ -1,0 +1,341 @@
+MODULE ReferenceElementModule
+
+  USE KindModule, ONLY: &
+    DP
+  USE QuadratureModule, ONLY: &
+    GetQuadrature
+  USE ProgramHeaderModule, ONLY: &
+    nNodesX, &
+    nNodesE, &
+    nNodesZ, &
+    nDOFX, &
+    nDOFE, &
+    nDOF
+
+  IMPLICIT NONE
+  PRIVATE
+
+  INTEGER,               PUBLIC :: nDOF_E
+  INTEGER,               PUBLIC :: nDOF_X1
+  INTEGER,               PUBLIC :: nDOF_X2
+  INTEGER,               PUBLIC :: nDOF_X3
+  INTEGER,  ALLOCATABLE, PUBLIC :: NodeNumbersX(:)
+  INTEGER,  ALLOCATABLE, PUBLIC :: NodeNumbersE(:,:)
+  INTEGER,  ALLOCATABLE, PUBLIC :: NodeNumberTable(:,:)
+  INTEGER,  ALLOCATABLE, PUBLIC :: NodeNumberTable_E (:,:)
+  INTEGER,  ALLOCATABLE, PUBLIC :: NodeNumberTable_X1(:,:)
+  INTEGER,  ALLOCATABLE, PUBLIC :: NodeNumberTable_X2(:,:)
+  INTEGER,  ALLOCATABLE, PUBLIC :: NodeNumberTable_X3(:,:)
+  INTEGER,  ALLOCATABLE, PUBLIC :: NodeNumberTable4D(:,:,:,:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: NodesE (:), WeightsE (:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: NodesX1(:), WeightsX1(:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: NodesX2(:), WeightsX2(:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: NodesX3(:), WeightsX3(:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: Weights_q(:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: Weights_E (:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: Weights_X1(:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: Weights_X2(:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: Weights_X3(:)
[…]

### 2024-11-25 Modules/Library/SubcellReconstructionModule.F90

@@ -1,0 +1,248 @@
+MODULE SubcellReconstructionModule
+
+  USE KindModule, ONLY: &
+    DP, Zero, Half, One
+  USE ProgramHeaderModule, ONLY: &
+    nNodesX, nDOFX, iX_B0, iX_E0, iX_B1, iX_E1
+  USE ReferenceElementModuleX, ONLY: &
+    NodesX1, WeightsX1, &
+    NodesX2, WeightsX2, &
+    NodesX3, WeightsX3
+  USE PolynomialBasisModuleX_Lagrange, ONLY: &
+    IndLX_Q, L_X1, L_X2, L_X3
+  USE GeometryFieldsModule, ONLY: &
+    CoordinateSystem, &
+    uGF, iGF_SqrtGm
+  USE MeshModule, ONLY: &
+    MeshX
+  USE LinearAlgebraModule, ONLY: &
+    MatrixVectorMultiply
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeSubcellReconstruction
+  PUBLIC :: FinalizeSubcellReconstruction
+  PUBLIC :: CreateSubcellReconstruction
+  PUBLIC :: DestroySubcellReconstruction
+
+  REAL(DP), ALLOCATABLE, PUBLIC :: ProjectionMatrix0(:,:,:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: ProjectionMatrix(:,:,:,:,:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: ReconstructionMatrix(:,:,:,:,:)
+
+CONTAINS
+
+
+  SUBROUTINE InitializeSubcellReconstruction
+
+    INTEGER  :: iS1, iS2, iS3, iS
+    INTEGER  :: jS1, jS2, jS3, jS
+    INTEGER  :: kS1, kS2, kS3, kS
+    INTEGER  :: iN1, iN2, iN3
+    INTEGER  :: INFO
+    INTEGER  :: IPIV(nDOFX)
+    REAL(DP) :: WORK(nDOFX)
+    REAL(DP) :: EtaLo(3), dEta(3)
+    REAL(DP) :: Eta_X1(nNodesX(1))
+    REAL(DP) :: Eta_X2(nNodesX(2))
+    REAL(DP) :: Eta_X3(nNodesX(3))
+
+    ALLOCATE( ProjectionMatrix0(nDOFX,nDOFX,nDOFX) )
+
+    ProjectionMatrix0 = Zero
+
[…]

### 2024-11-25 Modules/Library/TimersModule_Euler.f90

@@ -1,0 +1,873 @@
+MODULE TimersModule_Euler
+
+  USE, INTRINSIC :: ISO_FORTRAN_ENV, ONLY: &
+    I8=>INT64
+  USE KindModule, Only: &
+    DP, SqrtTiny
+
+  IMPLICIT NONE
+  PRIVATE
+
+  LOGICAL,  PUBLIC :: TimeIt_Euler = .FALSE.
+
+  REAL(DP), PUBLIC :: Timer_Euler_Program
+
+  ! --- ApplicationDriver ---
+
+  REAL(DP), PUBLIC :: Timer_Euler_Initialize
+  REAL(DP), PUBLIC :: Timer_Euler_UpdateFluid
+  REAL(DP), PUBLIC :: Timer_Euler_InputOutput
+  REAL(DP), PUBLIC :: Timer_Euler_Finalize
+
+  REAL(DP), PUBLIC :: Timer_Euler_ComputeTimeStep
+  REAL(DP), PUBLIC :: Timer_Euler_CTS_ComputeTimeStep
+  REAL(DP), PUBLIC :: Timer_Euler_CTS_CopyIn
+  REAL(DP), PUBLIC :: Timer_Euler_CTS_CopyOut
+
+  ! --- DG discretization ---
+
+  REAL(DP), PUBLIC :: Timer_Euler_DG
+  REAL(DP), PUBLIC :: Timer_Euler_Increment
+  REAL(DP), PUBLIC :: Timer_Euler_Divergence
+  REAL(DP), PUBLIC :: Timer_Euler_SurfaceTerm
+  REAL(DP), PUBLIC :: Timer_Euler_VolumeTerm
+  REAL(DP), PUBLIC :: Timer_Euler_Geometry
+  REAL(DP), PUBLIC :: Timer_Euler_Gravity
+  REAL(DP), PUBLIC :: Timer_Euler_DG_CopyIn
+  REAL(DP), PUBLIC :: Timer_Euler_DG_CopyOut
+  REAL(DP), PUBLIC :: Timer_Euler_DG_ComputePrimitive
+  REAL(DP), PUBLIC :: Timer_Euler_DG_Permute
+  REAL(DP), PUBLIC :: Timer_Euler_DG_Interpolate
+  REAL(DP), PUBLIC :: Timer_Euler_DG_ErrorCheck
+
+  ! --- Compute Primitive --
+
[…]

### 2024-11-25 Modules/Library/UtilitiesModule.F90

@@ -1,0 +1,642 @@
+MODULE UtilitiesModule
+
+  USE KindModule, ONLY: &
+    DP
+  USE ProgramHeaderModule, ONLY: &
+    nNodesX, nNodesE, nDimsX
+
+#ifdef THORNADO_USE_AMREX
+
+    USE amrex_error_module, ONLY: &
+      amrex_abort
+
+#endif
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: Locate
+  PUBLIC :: NodeNumber
+  PUBLIC :: NodeNumber_X1
+  PUBLIC :: NodeNumberX
+  PUBLIC :: NodeNumberX_X1
+  PUBLIC :: InitializeWeights
+  PUBLIC :: Interpolate1D_Linear
+  PUBLIC :: Interpolate2D_BiLinear
+  PUBLIC :: Interpolate1D_Log
+  PUBLIC :: MapTo1D
+  PUBLIC :: MapFrom1D
+  PUBLIC :: GetRoots_Quadratic
+  PUBLIC :: MinModB
+  PUBLIC :: WriteVector
+  PUBLIC :: WriteMatrix
+  PUBLIC :: WriteRank3Tensor
+  PUBLIC :: IsCornerCell
+  PUBLIC :: thornado_abort
+
+  INTERFACE InitializeWeights
+    MODULE PROCEDURE InitializeWeights3D
+    MODULE PROCEDURE InitializeWeights4D
+  END INTERFACE InitializeWeights
+
+  INTERFACE MapTo1D
+    MODULE PROCEDURE Map4DTo1D
+  END INTERFACE MapTo1D
+
+  INTERFACE MapFrom1D
+    MODULE PROCEDURE Map1DTo4D
+  END INTERFACE MapFrom1D
+
+  INTERFACE MinMod2
+    MODULE PROCEDURE MinMod2_Scalar
+    MODULE PROCEDURE MinMod2_Vector
+  END INTERFACE MinMod2
+
+  INTERFACE MinMod
+    MODULE PROCEDURE MinMod_Scalar
+    MODULE PROCEDURE MinMod_Vector
+  END INTERFACE MinMod
+
+  INTERFACE MinModB
+    MODULE PROCEDURE MinModB_Scalar
+    MODULE PROCEDURE MinModB_Vector
+  END INTERFACE MinModB
+
+CONTAINS
+
+
[…]

### 2024-11-25 Modules/Numbers/KindModule.f90

@@ -1,0 +1,27 @@
+MODULE KindModule
+
+  IMPLICIT NONE
+  PRIVATE
+
+  INTEGER, PUBLIC, PARAMETER :: &
+    DP = KIND( 1.d0 )
+  REAL(DP), PUBLIC, PARAMETER :: &
+    Zero  = 0.0_DP, &
+    One   = 1.0_DP, &
+    Two   = 2.0_DP, &
+    Three = 3.0_DP, &
+    Four  = 4.0_DP, &
+    Five  = 5.0_DP
+  REAL(DP), PUBLIC, PARAMETER :: &
+    Fifth  = 1.0_DP / 5.0_DP, &
+    Fourth = 0.25_DP, &
+    Third  = 1.0_DP / 3.0_DP, &
+    Half   = 0.5_DP
+  REAL(DP), PUBLIC, PARAMETER :: &
+    Pi     = ACOS( - 1.0_DP ), &
+    TwoPi  = 2.0_DP * Pi, &
+    FourPi = 4.0_DP * Pi
+  REAL(DP), PUBLIC, PARAMETER :: &
+    SqrtTiny = SQRT( TINY( 1.0_DP ) )
+
+END MODULE KindModule

### 2024-11-25 Modules/Opacities/OpacityModule.f90

@@ -1,0 +1,141 @@
+MODULE OpacityModule
+
+  USE KindModule, ONLY: &
+    DP
+  USE OpacityModule_IDEAL, ONLY: &
+    InitializeOpacities_IDEAL, &
+    FinalizeOpacities_IDEAL, &
+    ComputeEmissivity_IDEAL, &
+    ComputeAbsorptionOpacity_IDEAL, &
+    ComputeScatteringOpacity_ES_IDEAL
+  USE OpacityModule_TABLE, ONLY: &
+    InitializeOpacities_TABLE, &
+    FinalizeOpacities_TABLE, &
+    ComputeAbsorptionOpacity_TABLE, &
+    ComputeScatteringOpacity_ES_TABLE, &
+    ComputeScatteringOpacity_NES_TABLE
+
+  IMPLICIT NONE
+  PRIVATE
+
+  CHARACTER(5) :: &
+    Opacity
+
+  ! ---
+  ! --- Interfaces for Various Opacity Functions and Subroutines ---
+  ! ---
+
+  INTERFACE
+    SUBROUTINE ComputeOpacity_A( E, D, T, Y, X1, X2, X3, Opacity )
+      USE KindModule, ONLY: DP
+      REAL(DP), DIMENSION(:),   INTENT(in)  :: E, D, T, Y, X1, X2, X3
+      REAL(DP), DIMENSION(:,:), INTENT(out) :: Opacity
+    END SUBROUTINE ComputeOpacity_A
+  END INTERFACE
+
+  INTERFACE
+    SUBROUTINE ComputeOpacity_B( E, T, Eta, R0_In, R0_Out )
+      USE KindModule, ONLY: DP
+      REAL(DP), DIMENSION(:),     INTENT(in)  :: E, T, Eta
+      REAL(DP), DIMENSION(:,:,:), INTENT(out) :: R0_In, R0_Out
+    END SUBROUTINE ComputeOpacity_B
+  END INTERFACE
+
+  ! ---
+  ! --- Declaration of Opacity Functions and Subroutines ---
+  ! ---
+
+  PROCEDURE (ComputeOpacity_A), POINTER, PUBLIC :: &
+    ComputeEmissivity            => NULL(), &
+    ComputeAbsorptionOpacity     => NULL(), &
+    ComputeScatteringOpacity_ES  => NULL() ! --- Elastic Scattering
+  PROCEDURE (ComputeOpacity_B), POINTER, PUBLIC :: &
[…]

### 2024-11-25 Modules/RadHydro/EulerEquationsUtilitiesModule_GR.f90

@@ -1,0 +1,331 @@
+MODULE EulerEquationsUtilitiesModule_GR
+
+  USE, INTRINSIC :: ieee_arithmetic, ONLY: &
+    IEEE_IS_NAN
+
+  USE KindModule, ONLY: &
+    DP, SqrtTiny
+  USE GeometryFieldsModule, ONLY: &
+    iGF_Gm_dd_11, iGF_Gm_dd_22, iGF_Gm_dd_33
+  USE FluidFieldsModule, ONLY: &
+    iCF_D, iCF_S1, iCF_S2, iCF_S3, iCF_E, iCF_Ne, nCF, &
+    iPF_D, iPF_V1, iPF_V2, iPF_V3, iPF_E, iPF_Ne, &
+    iAF_P
+  USE EquationOfStateModule, ONLY: &
+    ComputePressureFromSpecificInternalEnergy    
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: ComputeConserved
+  PUBLIC :: ComputePrimitive
+  PUBLIC :: Eigenvalues
+  PUBLIC :: ComputeSoundSpeed
+  PUBLIC :: Flux_X1
+  PUBLIC :: AlphaC
+
+CONTAINS
+
+
+  SUBROUTINE ComputeConserved( uPF, uAF, uGF, uCF )
+
+    REAL(DP), DIMENSION(:,:), INTENT(in)  :: uPF
+    REAL(DP), DIMENSION(:,:), INTENT(in)  :: uAF
+    REAL(DP), DIMENSION(:,:), INTENT(in)  :: uGF
+    REAL(DP), DIMENSION(:,:), INTENT(out) :: uCF
+
+    INTEGER  :: i
+    REAL(DP) :: Gm11, Gm22, Gm33, vSq, W, h
+
+    DO i = 1, SIZE( uCF, DIM = 1 )
+
+      Gm11 = uGF(i,iGF_Gm_dd_11)
+      Gm22 = uGF(i,iGF_Gm_dd_22)
+      Gm33 = uGF(i,iGF_Gm_dd_33)
+
+      vSq = Gm11 * uPF(i,iPF_V1)**2 &
+            + Gm22 * uPF(i,iPF_V2)**2 &
+            + Gm33 * uPF(i,iPF_V3)**2
+
+      W = 1.0_DP / SQRT( 1.0_DP - vSq )
[…]

### 2024-11-25 Modules/RadHydro/FluidRadiationCouplingModule.f90

@@ -1,0 +1,146 @@
+MODULE FluidRadiationCouplingModule
+
+  USE KindModule, ONLY: &
+    DP
+  USE FluidRadiationCouplingSolutionModule_ConstantOpacities, ONLY: &
+    CoupleFluidRadiation_ConstantOpacities
+  USE FluidRadiationCouplingSolutionModule_ThermalReservoir, ONLY: &
+    CoupleFluidRadiation_ThermalReservoir
+  USE FluidRadiationCouplingSolutionModule_EmissionAbsorption, ONLY: &
+    CoupleFluidRadiation_EmissionAbsorption
+  USE FluidRadiationCouplingSolutionModule_ElasticScattering, ONLY: &
+    CoupleFluidRadiation_ElasticScattering
+  USE FluidRadiationCouplingSolutionModule_NES, ONLY: &
+    CoupleFluidRadiation_NES
+  USE FluidRadiationCouplingSolutionModule_B85, ONLY: &
+    CoupleFluidRadiation_B85
+
+  IMPLICIT NONE
+  PRIVATE
+
+  CHARACTER(32) :: FluidRadiationCoupling = 'Dummy'
+
+  PROCEDURE (CouplingProcedure), POINTER, PUBLIC :: &
+    CoupleFluidRadiation => NULL(), &
+    ComputeImplicitIncrement_FluidRadiation => NULL()
+
+  INTERFACE
+    SUBROUTINE CouplingProcedure &
+                 ( dt, iX_B0, iX_E0, iX_B1, iX_E1, U_F, dU_F, U_R, dU_R, &
+                   EvolveFluid_Option )
+      USE KindModule, ONLY: DP
+      REAL(DP), INTENT(in)  :: &
+        dt
+      INTEGER,  INTENT(in)  :: &
+        iX_B0(3), iX_B1(3), iX_E0(3), iX_E1(3)
+      REAL(DP), INTENT(in)  :: &
+        U_F (1:,iX_B1(1):,iX_B1(2):,iX_B1(3):,1:)
+      REAL(DP), INTENT(out) :: &
+        dU_F(1:,iX_B0(1):,iX_B0(2):,iX_B0(3):,1:)
+      REAL(DP), INTENT(in)  :: &
+        U_R (1:,1:,iX_B1(1):,iX_B1(2):,iX_B1(3):,1:,1:)
+      REAL(DP), INTENT(out) :: &
[…]

### 2024-11-25 Modules/RadHydro/FluidRadiationCouplingSolutionModule_B85.f90

@@ -1,0 +1,716 @@
+MODULE FluidRadiationCouplingSolutionModule_B85
+
+  USE KindModule, ONLY: &
+    DP, FourPi
+  USE UnitsModule, ONLY: &
+    BoltzmannConstant, &
+    PlanckConstant, &
+    SpeedOfLight
+  USE ProgramHeaderModule, ONLY: &
+    nX, nNodesX, nDOFX, &
+    nE, nNodesE, nDOFE
+  USE UtilitiesModule, ONLY: &
+    WriteVector, &
+    WriteMatrix
+  USE FluidFieldsModule, ONLY: &
+    uCF, nCF, &
+    uPF, nPF, iPF_D, iPF_E, iPF_Ne, &
+    uAF, nAF, iAF_P, iAF_T, iAF_E, iAF_Ye, iAF_S, &
+    iAF_Me, iAF_Mp, iAF_Mn, iAF_Gm, iAF_Cs
+  USE EulerEquationsUtilitiesModule, ONLY: &
+    ComputeConserved, &
+    ComputePrimitive
+  USE RadiationFieldsModule, ONLY: &
+    nPR, iPR_D, iPR_I1, iPR_I2, iPR_I3
+  USE MomentEquationsUtilitiesModule, ONLY: &
+    ComputeConservedMoments, &
+    ComputePrimitiveMoments
+  USE FluidRadiationCouplingUtilitiesModule, ONLY: &
+    InitializeNodes, &
+    InitializeNodesX, &
+    InitializeWeights, &
+    InitializeFluidFields, &
+    InitializeRadiationFields, &
+    FinalizeFluidFields, &
+    FinalizeRadiationFields, &
+    FermiDirac, &
+    dFermiDiracdT, &
+    dFermiDiracdY, &
+    ENORM
+  USE EquationOfStateModule, ONLY: &
+    BaryonMass, &
+    ComputeAuxiliary_Fluid, &
+    ComputeSpecificInternalEnergy, &
+    ComputeTemperatureFromSpecificInternalEnergy, &
+    ComputeThermodynamicStates_Primitive, &
+    ComputeElectronChemicalPotential, &
+    ComputeProtonChemicalPotential, &
[…]

### 2024-11-25 Modules/RadHydro/FluidRadiationCouplingUtilitiesModule.f90

@@ -1,0 +1,512 @@
+MODULE FluidRadiationCouplingUtilitiesModule
+
+  USE KindModule, ONLY: &
+    DP
+  USE ProgramHeaderModule, ONLY: &
+    nX, nNodesX, &
+    nE, nNodesE
+  USE ReferenceElementModuleE, ONLY: &
+    WeightsE
+  USE UtilitiesModule, ONLY: &
+    NodeNumberX, &
+    NodeNumber
+  USE MeshModule, ONLY: &
+    MeshX, MeshE, &
+    NodeCoordinate
+  USE FluidFieldsModule, ONLY: &
+    uPF, nPF, uAF, nAF
+  USE RadiationFieldsModule, ONLY: &
+    uPR, nPR
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeNodes
+  PUBLIC :: InitializeNodesX
+  PUBLIC :: InitializeWeights
+  PUBLIC :: InitializeFluidFields
+  PUBLIC :: FinalizeFluidFields
+  PUBLIC :: InitializeRadiationFields
+  PUBLIC :: FinalizeRadiationFields
+  PUBLIC :: MapForward_FluidField
+  PUBLIC :: MapBackward_FluidField
+  PUBLIC :: MapForward_RadiationField
+  PUBLIC :: MapBackward_RadiationField
+  PUBLIC :: FermiDirac
+  PUBLIC :: dFermiDiracdT
+  PUBLIC :: dFermiDiracdY
+  PUBLIC :: ENORM
+
+CONTAINS
+
+
+  SUBROUTINE InitializeNodes( E_N )
+
+    REAL(DP), DIMENSION(:), INTENT(out) :: E_N
+
+    INTEGER :: iE, iNodeE, iNode
+
+    iNode = 0
+    DO iE = 1, nE
+      DO iNodeE = 1, nNodesE
+
+        iNode = iNode + 1
+
+        E_N(iNode) = NodeCoordinate( MeshE, iE, iNodeE )
+
+      END DO
+    END DO
+
+  END SUBROUTINE InitializeNodes
+
+
+  SUBROUTINE InitializeNodesX( X_N )
+
+    REAL(DP), DIMENSION(:,:), INTENT(out) :: X_N
+
+    INTEGER :: iX1, iX2, iX3
[…]

### 2024-11-25 Modules/RadHydro/GravitySolutionModule_Newtonian_Poseidon.F90

@@ -1,0 +1,171 @@
+MODULE GravitySolutionModule_Newtonian_Poseidon
+
+  USE KindModule, ONLY: &
+    DP, Pi
+  USE ProgramHeaderModule, ONLY: &
+    nX, nNodesX, &
+    nNodes, xL, xR
+  USE UtilitiesModule, ONLY: &
+    NodeNumberX
+  USE MeshModule, ONLY: &
+    MeshX, &
+    NodeCoordinate
+  USE GeometryFieldsModule, ONLY: &
+    uGF, iGF_Phi_N
+  USE FluidFieldsModule, ONLY: &
+    uCF, iCF_D
+  USE GravitySolutionUtilitiesModule, ONLY: &
+    ComputeTotalBaryonMass
+
+#ifdef GRAVITY_SOLVER_POSEIDON_NEWTON
+
+  ! --- Poseidon Modules --------------------
+
+  USE Poseidon_Main_Module, ONLY: &
+    Poseidon_Initialize, &
+    Poseidon_Newtonian_Source_Input, &
+    Poseidon_Set_Uniform_Boundary_Condition, &
+    Poseidon_Run,  &
+    Poseidon_Newtonian_Potential_Output, &
+    Poseidon_Close
+
+  ! -----------------------------------------
+
+#endif
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeGravitySolver_Newtonian_Poseidon
+  PUBLIC :: FinalizeGravitySolver_Newtonian_Poseidon
+  PUBLIC :: SolveGravity_Newtonian_Poseidon
+
+CONTAINS
+
+
+  SUBROUTINE InitializeGravitySolver_Newtonian_Poseidon
+
+#ifdef GRAVITY_SOLVER_POSEIDON_NEWTON
+
+    CALL Poseidon_Initialize &
+         ( FEM_Degree_Input          &
+             = MAX( 1, nNodes - 1 ), &
+           L_Limit_Input = 0,        &
+           Inner_Radius = xL(1),     &
+           Outer_Radius = xR(1),     &
+           R_Elements_Input = nX(1), &
+           T_Elements_Input = nX(2), &
+           P_Elements_Input = nX(3), &
+           Input_Delta_R_Vector      &
+             = MeshX(1) % Width(1:nX(1)) )
+
+#endif
+
+  END SUBROUTINE InitializeGravitySolver_Newtonian_Poseidon
+
+
[…]

### 2024-11-25 Modules/RadHydro/MomentEquationsLimiterUtilitiesModule_DG.f90

@@ -1,0 +1,349 @@
+MODULE MomentEquationsLimiterUtilitiesModule_DG
+
+  USE KindModule, ONLY: &
+    DP
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, nDOF, &
+    nX, nNodesX, &
+    nE, nNodesE
+  USE ReferenceElementModule, ONLY: &
+    Weights_q
+  USE UtilitiesModule, ONLY: &
+    NodeNumberX, &
+    NodeNumber
+  USE PolynomialBasisModule_Lagrange, ONLY: &
+    L_E, L_X1, L_X2, L_X3
+  USE PolynomialBasisMappingModule, ONLY: &
+    MapNodalToModal_Radiation, &
+    MapModalToNodal_Radiation
+  USE MeshModule, ONLY: &
+    MeshE, &
+    MeshX
+  USE RadiationFieldsModule, ONLY: &
+    nSpecies, &
+    uCR, iCR_N, nCR, &
+    Discontinuity
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeDiscontinuityDetector
+  PUBLIC :: DetectDiscontinuities
+  PUBLIC :: PackSpatialNodes
+  PUBLIC :: UnpackSpatialNodes
+  PUBLIC :: SolveTheta_Bisection
+
+  LOGICAL, PARAMETER :: UseDiscontinuityDetector = .TRUE.
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE :: Lagrange_X1_P
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE :: Lagrange_X1_M
+
+CONTAINS
+
+
+  SUBROUTINE InitializeDiscontinuityDetector
+
+    INTEGER  :: iNodeE, iNodeX1, iNodeX2, iNodeX3, iNode
+    INTEGER  :: jNodeE, jNodeX1, jNodeX2, jNodeX3, jNode
+    REAL(DP) :: eta_E, eta_X1, eta_X2, eta_X3
+
+    ALLOCATE( Lagrange_X1_P(nDOF,nDOF) )
+    ALLOCATE( Lagrange_X1_M(nDOF,nDOF) )
+
+    DO jNodeX3 = 1, nNodesX(3)
+      DO jNodeX2 = 1, nNodesX(2)
+        DO jNodeX1 = 1, nNodesX(1)
+          DO jNodeE = 1, nNodesE
+
[…]

### 2024-11-25 Modules/RadHydro/RiemannSolverModule.f90

@@ -1,0 +1,373 @@
+MODULE RiemannSolverModule
+
+  USE KindModule, ONLY: &
+    DP
+  USE FluidFieldsModule, ONLY: &
+    iCF_D, iCF_S1, iCF_S2, iCF_S3, iCF_E, iCF_Ne, &
+    iPF_V1, iAF_P
+
+  IMPLICIT NONE
+  PRIVATE
+
+  CHARACTER(32) :: FluidRiemannSolver     = 'LLF'
+  CHARACTER(32) :: RadiationRiemannSolver = 'LLF'
+
+  PROCEDURE (RiemannSolver),    POINTER, PUBLIC :: &
+    NumericalFlux_Fluid     => NULL(), &
+    NumericalFlux_Radiation => NULL()
+
+  PROCEDURE (FluidRiemannSolver_GR), POINTER, PUBLIC :: &
+    NumericalFlux_Fluid_GR  => NULL()
+
+  PUBLIC :: NumericalFlux_Fluid_GR_HLL
+  
+  INTERFACE
+    PURE FUNCTION RiemannSolver &
+      ( u_L, u_R, Flux_L, Flux_R, a, aP, aM, aC, nF )
+      USE KindModule, ONLY: DP
+      INTEGER,                   INTENT(in) :: nF
+      REAL(DP), DIMENSION(1:nF), INTENT(in) :: u_L, u_R, flux_L, flux_R
+      REAL(DP),                  INTENT(in) :: a, aP, aM, aC
+      REAL(DP), DIMENSION(1:nF)             :: RiemannSolver
+    END FUNCTION RiemannSolver
+  END INTERFACE
+
+  INTERFACE
+    PURE FUNCTION FluidRiemannSolver_GR &
+      ( u_L, u_R, Flux_L, Flux_R, a, aP, aM, aC, nF, &
+        V1_L, V1_R, p_L, p_R, Beta_u_1, Gm_dd_11 )
+
+    USE KindModule, ONLY: DP
+    INTEGER,  INTENT(in)                  :: nF
+    REAL(DP), DIMENSION(1:nF), INTENT(in) :: u_L, u_R, Flux_L, Flux_R
+    REAL(DP), INTENT(in)                  :: a, aP, aM, aC, V1_L, V1_R,    &
+                                             p_L, p_R, Beta_u_1, Gm_dd_11
+    REAL(DP)                              :: p, D, S1, S2, S3, E, Ne
[…]

### 2024-11-25 Modules/TwoMoment/TwoMoment_ClosureModule.F90

@@ -1,0 +1,883 @@
+MODULE TwoMoment_ClosureModule
+
+  USE KindModule, ONLY: &
+    DP, SqrtTiny, &
+    Zero, One, Two, Three, Four, &
+    Fifth, Third
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeClosure_TwoMoment
+  PUBLIC :: FluxFactor
+  PUBLIC :: FluxFactor_Relativistic
+  PUBLIC :: EddingtonFactor
+  PUBLIC :: HeatFluxFactor
+  PUBLIC :: ComputeEddingtonFactorDerivatives
+
+  INTERFACE FluxFactor
+    MODULE PROCEDURE FluxFactor_Scalar
+    MODULE PROCEDURE FluxFactor_Vector
+  END INTERFACE FluxFactor
+
+  INTERFACE FluxFactor_Relativistic
+    MODULE PROCEDURE FluxFactor_Relativistic_Scalar
+    MODULE PROCEDURE FluxFactor_Relativistic_Vector
+  END INTERFACE FluxFactor_Relativistic
+
+  INTERFACE EddingtonFactor
+    MODULE PROCEDURE EddingtonFactor_Scalar
+    MODULE PROCEDURE EddingtonFactor_Vector
+  END INTERFACE EddingtonFactor
+
+  INTERFACE HeatFluxFactor
+    MODULE PROCEDURE HeatFluxFactor_Scalar
+    MODULE PROCEDURE HeatFluxFactor_Vector
+  END INTERFACE HeatFluxFactor
+
+  INTERFACE ClosurePolynomial_ME_CB
+    MODULE PROCEDURE ClosurePolynomial_ME_CB_Scalar
+    MODULE PROCEDURE ClosurePolynomial_ME_CB_Vector
+  END INTERFACE ClosurePolynomial_ME_CB
+
+  INTERFACE ClosurePolynomial_ME_BL
+    MODULE PROCEDURE ClosurePolynomial_ME_BL_Scalar
+    MODULE PROCEDURE ClosurePolynomial_ME_BL_Vector
+  END INTERFACE ClosurePolynomial_ME_BL
+
+  INTERFACE ClosurePolynomial_KE_BL
+    MODULE PROCEDURE ClosurePolynomial_KE_BL_Scalar
[…]

### 2024-11-25 SandBox/AMReX/Applications/CoreCollapseSupernova_XCFC/InitializationModule.f90

@@ -1,0 +1,771 @@
+MODULE InitializationModule
+
+  USE ISO_C_BINDING
+
+  ! --- AMReX Modules ---
+
+  USE amrex_init_module, ONLY: &
+    amrex_init
+  USE amrex_parmparse_module, ONLY: &
+    amrex_parmparse, &
+    amrex_parmparse_build, &
+    amrex_parmparse_destroy
+  USE amrex_amrcore_module, ONLY: &
+    amrex_amrcore_init, &
+    amrex_init_virtual_functions, &
+    amrex_init_from_scratch, &
+    amrex_ref_ratio, &
+    amrex_get_numlevels, &
+    amrex_geom
+  USE amrex_boxarray_module, ONLY: &
+    amrex_boxarray
+  USE amrex_distromap_module, ONLY: &
+    amrex_distromap
+  USE amrex_multifab_module, ONLY: &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy, &
+    amrex_multifab, &
+    amrex_multifab_build, &
+    amrex_multifab_destroy
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor
+  USE thornado_amrex_fluxregister_module, ONLY: &
+    amrex_fluxregister_build, &
+    amrex_fluxregister_destroy
+  USE amrex_tagbox_module, ONLY: &
+    amrex_tagboxarray
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDOFZ, &
+    iE_B0, &
+    iE_E0, &
+    iE_B1, &
+    iE_E1, &
+    nNodesE, &
+    swX, &
+    swE, &
+    zoomE, &
+    eL, &
+    eR, &
+    nE, &
+    DescribeProgramHeaderX
+  USE TwoMoment_NeutrinoMatterSolverModule, ONLY: &
+    InitializeNeutrinoMatterSolverParameters
+  USE PolynomialBasisModule_Lagrange, ONLY: &
+    InitializePolynomialBasis_Lagrange
+  USE PolynomialBasisModule_Legendre, ONLY: &
+    InitializePolynomialBasis_Legendre
+  USE PolynomialBasisModuleX_Lagrange, ONLY: &
+    InitializePolynomialBasisX_Lagrange
[…]

### 2024-11-25 SandBox/AMReX/Applications/DynamicTOV_XCFC/InitializationModule.f90

@@ -1,0 +1,576 @@
+MODULE InitializationModule
+
+  USE ISO_C_BINDING
+
+  ! --- AMReX Modules ---
+
+  USE amrex_init_module, ONLY: &
+    amrex_init
+  USE amrex_parmparse_module, ONLY: &
+    amrex_parmparse, &
+    amrex_parmparse_build, &
+    amrex_parmparse_destroy
+  USE amrex_amrcore_module, ONLY: &
+    amrex_amrcore_init, &
+    amrex_init_virtual_functions, &
+    amrex_init_from_scratch, &
+    amrex_ref_ratio, &
+    amrex_get_numlevels
+  USE amrex_boxarray_module, ONLY: &
+    amrex_boxarray
+  USE amrex_distromap_module, ONLY: &
+    amrex_distromap
+  USE amrex_multifab_module, ONLY: &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy, &
+    amrex_multifab, &
+    amrex_multifab_build, &
+    amrex_multifab_destroy
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor
+  USE thornado_amrex_fluxregister_module, ONLY: &
+    amrex_fluxregister_build, &
+    amrex_fluxregister_destroy
+  USE amrex_tagbox_module, ONLY: &
+    amrex_tagboxarray
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    swX, &
+    DescribeProgramHeaderX
+  USE PolynomialBasisModule_Lagrange, ONLY: &
+    InitializePolynomialBasis_Lagrange
+  USE PolynomialBasisModule_Legendre, ONLY: &
+    InitializePolynomialBasis_Legendre
+  USE PolynomialBasisModuleX_Lagrange, ONLY: &
+    InitializePolynomialBasisX_Lagrange
+  USE PolynomialBasisModuleX_Legendre, ONLY: &
+    InitializePolynomialBasisX_Legendre
+  USE PolynomialBasisMappingModule, ONLY: &
+    InitializePolynomialBasisMapping
[…]

### 2024-11-25 SandBox/AMReX/Applications/SedovTaylorBlastWave_XCFC/ApplicationDriver.f90

@@ -1,0 +1,310 @@
+PROGRAM main
+
+  ! --- AMReX Modules ---
+
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor, &
+    amrex_parallel_communicator
+
+  ! --- thornado Modules ---
+
+  USE UnitsModule, ONLY: &
+    UnitsDisplay
+
+  ! --- Local Modules ---
+
+  USE MF_KindModule, ONLY: &
+    DP
+  USE MF_FieldsModule_Geometry, ONLY: &
+    MF_uGF
+  USE MF_FieldsModule_Euler, ONLY: &
+    MF_uCF, &
+    MF_uPF, &
+    MF_uAF, &
+    MF_uDF
+  USE InitializationModule, ONLY: &
+    InitializeProgram
+  USE FinalizationModule, ONLY: &
+    FinalizeProgram
+  USE MF_Euler_UtilitiesModule, ONLY: &
+    ComputeTimeStep_Euler_MF, &
+    ComputeFromConserved_Euler_MF
+  USE InputOutputModuleAMReX, ONLY: &
+    WriteFieldsAMReX_PlotFile, &
+    WriteFieldsAMReX_Checkpoint
+  USE MF_Euler_TallyModule, ONLY: &
+    ComputeTally_Euler_MF, &
+    BaryonicMass_Initial, &
+    BaryonicMass_OffGrid, &
+    EulerMomentumX1_Initial, &
+    EulerMomentumX1_OffGrid, &
+    EulerMomentumX2_Initial, &
+    EulerMomentumX2_OffGrid, &
+    EulerMomentumX3_Initial, &
+    EulerMomentumX3_OffGrid, &
+    EulerEnergy_Initial, &
+    EulerEnergy_OffGrid, &
+    ElectronNumber_Initial, &
+    ElectronNumber_OffGrid, &
+    ADMMass_Initial, &
+    ADMMass_OffGrid, &
+    ADMMass_Interior
+  USE MF_TimeSteppingModule_SSPRK, ONLY: &
+    UpdateFluid_SSPRK_MF, &
+    CFL
+  USE InputParsingModule, ONLY: &
+    nLevels, &
+    StepNo, &
+    t_end, &
+    t_new, &
+    t_old, &
+    dt, &
+    iCycleD, &
+    iCycleW, &
+    iCycleChk, &
+    t_wrt, &
+    t_chk, &
+    dt_wrt, &
+    dt_chk, &
[…]

### 2024-11-25 SandBox/AMReX/Applications/YahilCollapse_Newtonian/FinalizationModule.f90

@@ -1,0 +1,154 @@
+MODULE FinalizationModule
+
+  ! --- AMReX Modules ---
+
+  USE amrex_init_module, ONLY: &
+    amrex_finalize
+  USE amrex_amrcore_module, ONLY: &
+    amrex_amrcore_finalize
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor
+
+  ! --- thornado Modules ---
+
+  USE ReferenceElementModuleX, ONLY: &
+    FinalizeReferenceElementX
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+    FinalizeReferenceElementX_Lagrange
+  USE Euler_MeshRefinementModule, ONLY: &
+    FinalizeMeshRefinement_Euler
+
+  ! --- Local Modules ---
+
+  USE MF_EquationOfStateModule, ONLY: &
+    FinalizeEquationOfState_MF
+  USE MF_FieldsModule_Geometry, ONLY: &
+    MF_uGF, &
+    DestroyFields_Geometry_MF
+  USE MF_FieldsModule_Euler, ONLY: &
+    MF_uCF, &
+    MF_uPF, &
+    MF_uAF, &
+    MF_uDF, &
+    DestroyFields_Euler_MF
+  USE MF_Euler_SlopeLimiterModule, ONLY: &
+    FinalizeSlopeLimiter_Euler_MF
+  USE MF_Euler_PositivityLimiterModule, ONLY: &
+    FinalizePositivityLimiter_Euler_MF
+  USE MF_TimeSteppingModule_SSPRK_Newtonian, ONLY: &
+    FinalizeFluid_SSPRK_Newtonian_MF
+  USE MF_Euler_UtilitiesModule, ONLY: &
+    ComputeFromConserved_Euler_MF
+  USE InputOutputModuleAMReX, ONLY: &
+    WriteFieldsAMReX_PlotFile, &
+    WriteFieldsAMReX_Checkpoint
+  USE MF_Euler_TallyModule, ONLY: &
+    ComputeTally_Euler_MF, &
+    FinalizeTally_Euler_MF, &
+    BaryonicMass_Initial, &
+    BaryonicMass_OffGrid, &
+    EulerMomentumX1_Initial, &
+    EulerMomentumX1_OffGrid, &
+    EulerMomentumX2_Initial, &
+    EulerMomentumX2_OffGrid, &
+    EulerMomentumX3_Initial, &
+    EulerMomentumX3_OffGrid, &
[…]

### 2024-11-25 SandBox/AMReX/Applications/YahilCollapse_Newtonian/InitializationModule.f90

@@ -1,0 +1,571 @@
+MODULE InitializationModule
+
+  USE ISO_C_BINDING
+
+  ! --- AMReX Modules ---
+
+  USE amrex_init_module, ONLY: &
+    amrex_init
+  USE amrex_parmparse_module, ONLY: &
+    amrex_parmparse, &
+    amrex_parmparse_build, &
+    amrex_parmparse_destroy
+  USE amrex_amrcore_module, ONLY: &
+    amrex_amrcore_init, &
+    amrex_init_virtual_functions, &
+    amrex_init_from_scratch, &
+    amrex_ref_ratio, &
+    amrex_get_numlevels
+  USE amrex_boxarray_module, ONLY: &
+    amrex_boxarray
+  USE amrex_distromap_module, ONLY: &
+    amrex_distromap
+  USE amrex_multifab_module, ONLY: &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy, &
+    amrex_multifab, &
+    amrex_multifab_build, &
+    amrex_multifab_destroy
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor
+  USE thornado_amrex_fluxregister_module, ONLY: &
+    amrex_fluxregister_build, &
+    amrex_fluxregister_destroy
+  USE amrex_tagbox_module, ONLY: &
+    amrex_tagboxarray
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    swX, &
+    DescribeProgramHeaderX
+  USE PolynomialBasisModule_Lagrange, ONLY: &
+    InitializePolynomialBasis_Lagrange
+  USE PolynomialBasisModule_Legendre, ONLY: &
+    InitializePolynomialBasis_Legendre
+  USE PolynomialBasisModuleX_Lagrange, ONLY: &
+    InitializePolynomialBasisX_Lagrange
+  USE PolynomialBasisModuleX_Legendre, ONLY: &
+    InitializePolynomialBasisX_Legendre
+  USE PolynomialBasisMappingModule, ONLY: &
+    InitializePolynomialBasisMapping
[…]

### 2024-11-25 SandBox/AMReX/Applications/YahilCollapse_XCFC/InitializationModule.f90

@@ -1,0 +1,567 @@
+MODULE InitializationModule
+
+  USE ISO_C_BINDING
+
+  ! --- AMReX Modules ---
+
+  USE amrex_init_module, ONLY: &
+    amrex_init
+  USE amrex_parmparse_module, ONLY: &
+    amrex_parmparse, &
+    amrex_parmparse_build, &
+    amrex_parmparse_destroy
+  USE amrex_amrcore_module, ONLY: &
+    amrex_amrcore_init, &
+    amrex_init_virtual_functions, &
+    amrex_init_from_scratch, &
+    amrex_ref_ratio, &
+    amrex_get_numlevels
+  USE amrex_boxarray_module, ONLY: &
+    amrex_boxarray
+  USE amrex_distromap_module, ONLY: &
+    amrex_distromap
+  USE amrex_multifab_module, ONLY: &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy, &
+    amrex_multifab, &
+    amrex_multifab_build, &
+    amrex_multifab_destroy
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor
+  USE thornado_amrex_fluxregister_module, ONLY: &
+    amrex_fluxregister_build, &
+    amrex_fluxregister_destroy
+  USE amrex_tagbox_module, ONLY: &
+    amrex_tagboxarray
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    swX, &
+    DescribeProgramHeaderX
+  USE PolynomialBasisModule_Lagrange, ONLY: &
+    InitializePolynomialBasis_Lagrange
+  USE PolynomialBasisModule_Legendre, ONLY: &
+    InitializePolynomialBasis_Legendre
+  USE PolynomialBasisModuleX_Lagrange, ONLY: &
+    InitializePolynomialBasisX_Lagrange
+  USE PolynomialBasisModuleX_Legendre, ONLY: &
+    InitializePolynomialBasisX_Legendre
+  USE PolynomialBasisMappingModule, ONLY: &
+    InitializePolynomialBasisMapping
[…]

### 2024-11-25 SandBox/AMReX/Modules/Euler/MF_Euler_SlopeLimiterModule.F90

@@ -1,0 +1,316 @@
+!> Module to apply slope-limiter to AMReX MultiFabs.
+!> @todo Fix issue of multiple grids giving different results.
+MODULE MF_Euler_SlopeLimiterModule
+
+  ! --- AMReX Modules ---
+
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_communicator, &
+    amrex_parallel_ioprocessor
+  USE amrex_parmparse_module, ONLY: &
+    amrex_parmparse, &
+    amrex_parmparse_build, &
+    amrex_parmparse_destroy
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    swX
+  USE MeshModule, ONLY: &
+    MeshX
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    nDF
+  USE GeometryFieldsModule, ONLY: &
+    nGF
+  USE Euler_SlopeLimiterModule, ONLY: &
+    InitializeSlopeLimiter_Euler, &
+    FinalizeSlopeLimiter_Euler, &
+    ApplySlopeLimiter_Euler
+
+  ! --- Local Modules ---
+
+  USE MF_KindModule, ONLY: &
+    DP
+  USE MF_UtilitiesModule, ONLY: &
+    amrex2thornado_X, &
+    thornado2amrex_X, &
+    AllocateArray_X, &
+    DeallocateArray_X
+  USE InputParsingModule, ONLY: &
+    nLevels, &
+    UseTiling, &
+    DEBUG
+  USE MF_MeshModule, ONLY: &
+    CreateMesh_MF, &
+    DestroyMesh_MF
+  USE MF_EdgeMapModule, ONLY: &
+    EdgeMap, &
+    ConstructEdgeMap
+  USE AverageDownModule, ONLY: &
+    AverageDown
+  USE FillPatchModule, ONLY: &
+    FillPatch
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeSlopeLimiter_Euler_MF
+  PUBLIC :: FinalizeSlopeLimiter_Euler_MF
+  PUBLIC :: ApplySlopeLimiter_Euler_MF
+
[…]

### 2024-11-25 SandBox/AMReX/Modules/Euler_Deprecated/TimersModule_AMReX_Euler_Deprecated.f90

@@ -1,0 +1,535 @@
+MODULE TimersModule_AMReX_Euler
+
+  ! --- AMReX Modules ---
+
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor,  &
+    amrex_parallel_reduce_min,   &
+    amrex_parallel_reduce_max,   &
+    amrex_parallel_reduce_sum,   &
+    amrex_parallel_nprocs
+
+  ! --- Thornado Modules ---
+
+  USE TimersModule_Euler,    ONLY: &
+    InitializeTimers_Euler,             &
+    FinalizeTimers_Euler,               &
+    Timer_Euler_DG,                     &
+    Timer_Euler_Increment,              &
+    Timer_Euler_Divergence,             &
+    Timer_Euler_SurfaceTerm,            &
+    Timer_Euler_VolumeTerm,             &
+    Timer_Euler_Geometry,               &
+    Timer_Euler_DD_TCI,                 &
+    Timer_Euler_DD_SD,                  &
+    Timer_Euler_SlopeLimiter,           &
+    Timer_Euler_PositivityLimiter,      &
+    Timer_Euler_BoundaryConditions,     &
+    Timer_Euler_SL_CharDecomp
+
+  ! --- Local Modules ---
+
+  USE MF_KindModule,         ONLY: &
+    DP, &
+    Zero
+  USE InputParsingModule,    ONLY: &
+    nLevels
+
+  IMPLICIT NONE
+  PRIVATE
+
+  INCLUDE 'mpif.h'
+
+  PUBLIC :: InitializeTimers_AMReX_Euler
+  PUBLIC :: FinalizeTimers_AMReX_Euler
+  PUBLIC :: TimersStart_AMReX_Euler
+  PUBLIC :: TimersStop_AMReX_Euler
+  PUBLIC :: TimersWtime_AMReX
+
+  LOGICAL,  PUBLIC :: TimeIt_AMReX_Euler = .FALSE.
+
+  REAL(DP), PUBLIC :: Timer_AMReX_Euler_Program;          INTEGER :: iT_P   = 1
+
+  ! --- fmain ---
+  REAL(DP), PUBLIC :: Timer_AMReX_Euler_Initialize;       INTEGER :: iT_I   = 2
[…]

### 2024-11-25 SandBox/AMReX/Modules/Gravity/MF_MetricInitializationModule_XCFC_Poseidon.F90

@@ -1,0 +1,639 @@
+MODULE MF_MetricInitializationModule_XCFC_Poseidon
+
+  ! --- AMReX Modules ---
+
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_multifab_build, &
+    amrex_multifab_destroy, &
+    amrex_imultifab, &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor, &
+    amrex_parallel_reduce_max
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDOFZ, &
+    iE_E0, &
+    iE_B0, &
+    iE_E1, &
+    iE_B1, &
+    nE, &
+    xR, &
+    swX
+  USE GeometryFieldsModule, ONLY: &
+    iGF_Alpha, &
+    iGF_Beta_1, &
+    iGF_Beta_2, &
+    iGF_Beta_3, &
+    iGF_K_dd_11, &
+    iGF_K_dd_12, &
+    iGF_K_dd_13, &
+    iGF_K_dd_22, &
+    iGF_K_dd_23, &
+    iGF_K_dd_33, &
+    iGF_Psi
+  USE GeometryComputationModule, ONLY: &
+    LapseFunction, &
+    ConformalFactor
+  USE FluidFieldsModule, ONLY: &
+    nCF
+  USE RadiationFieldsModule, ONLY: &
+    nCR, &
+    nSpecies
+  USE XCFC_UtilitiesModule, ONLY: &
+    nGS, &
+    iMF_Psi, &
+    iMF_Alpha, &
+    iMF_Beta_1, &
+    iMF_Beta_2, &
+    iMF_Beta_3, &
+    iMF_K_dd_11, &
+    iMF_K_dd_12, &
+    iMF_K_dd_13, &
+    iMF_K_dd_22, &
+    iMF_K_dd_23, &
+    iMF_K_dd_33, &
+    nMF, &
+    swX_GS
+
+  ! --- Local Modules ---
+
+  USE MF_KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One
+  USE MF_Euler_UtilitiesModule, ONLY: &
+    ComputeConserved_Euler_MF
[…]

### 2024-11-25 SandBox/AMReX/Modules/InputOutput/InputOutputModuleAMReX.f90

@@ -1,0 +1,1242 @@
+MODULE InputOutputModuleAMReX
+
+  USE ISO_C_BINDING
+
+  ! --- AMReX Modules ---
+
+  USE amrex_plotfile_module, ONLY: &
+    amrex_write_plotfile
+  USE amrex_string_module, ONLY: &
+    amrex_string, &
+    amrex_string_build
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_boxarray_module, ONLY: &
+    amrex_boxarray, &
+    amrex_boxarray_build
+  USE amrex_distromap_module,  ONLY: &
+    amrex_distromap,       &
+    amrex_distromap_build
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_multifab_build, &
+    amrex_multifab_destroy, &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy
+  USE amrex_geometry_module, ONLY: &
+    amrex_geometry, &
+    amrex_geometry_build
+  USE amrex_amrcore_module, ONLY: &
+    amrex_get_amrcore, &
+    amrex_get_numlevels, &
+    amrex_ref_ratio, &
+    amrex_set_boxarray, &
+    amrex_set_distromap, &
+    amrex_set_geometry, &
+    amrex_set_finest_level
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor, &
+    amrex_parallel_myproc
+  USE thornado_amrex_fluxregister_module, ONLY: &
+    amrex_fluxregister_build
+  USE amrex_amr_module, ONLY: &
+    amrex_geom
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDOFZ, &
+    nDOFE, &
+    iZ_B0, &
+    iZ_E0, &
+    swX, &
+    nX, &
+    nE, &
+    nDimsX
+  USE ReferenceElementModuleX, ONLY: &
+    WeightsX_q, &
+    nDOFX_X1
+  USE ReferenceElementModuleZ, ONLY: &
+    nDOFZ_Z2
+  USE ReferenceElementModule, ONLY: &
+    Weights_q
+  USE MeshModule, ONLY: &
+    MeshType, &
+    MeshE, &
+    NodeCoordinate
[…]

### 2024-11-25 SandBox/AMReX/Modules/Library/MF_EdgeMapModule.f90

@@ -1,0 +1,101 @@
+MODULE MF_EdgeMapModule
+
+  ! --- AMReX Modules ---
+
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_amrcore_module, ONLY: &
+    amrex_geom
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nDimsX
+  USE Euler_BoundaryConditionsModule, ONLY: &
+    iApplyBC_Euler_Both,  &
+    iApplyBC_Euler_Inner, &
+    iApplyBC_Euler_Outer, &
+    iApplyBC_Euler_None
+
+  ! --- Local Modules ---
+
+  USE MF_KindModule, ONLY: &
+    DP
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: ConstructEdgeMap
+
+  TYPE, PUBLIC :: EdgeMap
+    LOGICAL :: IsLowerBoundary(3)
+    LOGICAL :: IsUpperBoundary(3)
+  CONTAINS
+    PROCEDURE :: GetBC => EdgeMap_GetBC
+  END TYPE EdgeMap
+
+CONTAINS
+
+
+  SUBROUTINE ConstructEdgeMap( iLevel, BX, Edge_Map )
+
+    INTEGER        , INTENT(in)    :: iLevel
+    TYPE(amrex_box), INTENT(in)    :: BX
+    TYPE(EdgeMap)  , INTENT(inout) :: Edge_Map
+
+    INTEGER :: iDimX
+
+    Edge_Map % IsLowerBoundary = .FALSE.
+    Edge_Map % IsUpperBoundary = .FALSE.
+
+    DO iDimX = 1, 3
+
+      IF( iDimX .LE. nDimsX )THEN
+
+        IF( BX % lo( iDimX ) .LE. amrex_geom(iLevel) % DOMAIN % lo( iDimX ) ) &
+          Edge_Map % IsLowerBoundary( iDimX ) = .TRUE.
+
+        IF( BX % hi( iDimX ) .GE. amrex_geom(iLevel) % DOMAIN % hi( iDimX ) ) &
+          Edge_Map % IsUpperBoundary( iDimX ) = .TRUE.
+
+      END IF
+
+    END DO
+
+  END SUBROUTINE ConstructEdgeMap
+
+
+  SUBROUTINE EdgeMap_GetBC( this, iApplyBC )
+
[…]

### 2024-11-25 SandBox/AMReX/Modules/Library/MF_UtilitiesModule_fi.cpp

@@ -1,0 +1,18 @@
+#include <iostream>
+
+#include <AMReX_BoxArray.H>
+
+using namespace amrex;
+
+extern "C"
+{
+    void print_boxarray
+      ( const BoxArray& ba )
+    {
+        std::cout << ba << "\n";
+        std::cout << "Total number of boxes    = " << ba.size() << "\n";
+        std::cout << "Total number of elements = " << ba.numPts() << "\n";
+
+    }
+
+}

### 2024-11-25 SandBox/AMReX/Modules/Mesh/MF_MeshModule.f90

@@ -1,0 +1,70 @@
+MODULE MF_MeshModule
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nNodesX, &
+    nX, &
+    swX, &
+    xL, &
+    xR, &
+    nDimsX
+  USE MeshModule, ONLY: &
+    MeshType, &
+    CreateMesh, &
+    DestroyMesh
+
+  ! --- Local Modules ---
+
+  USE InputParsingModule, ONLY: &
+    iOS_CPP
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: CreateMesh_MF
+  PUBLIC :: DestroyMesh_MF
+
+CONTAINS
+
+
+  SUBROUTINE CreateMesh_MF( iLevel, MeshX )
+
+    INTEGER,        INTENT(in)  :: iLevel
+    TYPE(MeshType), INTENT(out) :: MeshX(3)
+
+    INTEGER :: iDimX, nXX(3)
+
+    nXX = nX
+
+    nXX(1) = 2**( iLevel ) * nX(1)
+    IF( nDimsX .GT. 1 ) nXX(2) = 2**( iLevel ) * nX(2)
+    IF( nDimsX .GT. 2 ) nXX(3) = 2**( iLevel ) * nX(3)
+
+    DO iDimX = 1, 3
+
+      CALL CreateMesh &
+             ( MeshX(iDimX), nXX(iDimX), nNodesX(iDimX), swX(iDimX), &
+               xL(iDimX), xR(iDimX), iOS_Option = iOS_CPP(iDimX) )
+
+    END DO
+
+  END SUBROUTINE CreateMesh_MF
+
+
+  SUBROUTINE DestroyMesh_MF( MeshX )
+
+    TYPE(MeshType), INTENT(inout) :: MeshX(3)
+
+    INTEGER :: iDimX
+
+    DO iDimX = 1, 3
+
+      CALL DestroyMesh( MeshX(iDimX) )
+
+    END DO
+
+  END SUBROUTINE DestroyMesh_MF
+
+
+END MODULE MF_MeshModule

### 2024-11-25 SandBox/AMReX/Modules/MeshRefinement/FillPatchModule.F90

@@ -1,0 +1,930 @@
+MODULE FillPatchModule
+
+  USE ISO_C_BINDING
+
+  ! --- AMReX Modules ---
+
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_multifab_build, &
+    amrex_multifab_destroy, &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_amr_module, ONLY: &
+    amrex_geom, &
+    amrex_ref_ratio
+  USE thornado_amrex_fillpatch_module, ONLY: &
+    thornado_amrex_fillpatch, &
+    thornado_amrex_fillcoarsepatch
+  USE amrex_geometry_module, ONLY: &
+    amrex_geometry, &
+    amrex_is_all_periodic
+  USE amrex_filcc_module, ONLY: &
+    amrex_filcc
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_communicator, &
+    amrex_parallel_ioprocessor
+  USE amrex_bc_types_module, ONLY: &
+    amrex_bc_bogus
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    swX, &
+    nDimsX
+  USE ReferenceElementModuleX, ONLY: &
+    NodeNumberTableX
+  USE MeshModule, ONLY: &
+    MeshType, &
+    NodeCoordinate
+  USE GeometryFieldsModule, ONLY: &
+    iGF_SqrtGm, &
+    CoordinateSystem
+  USE Euler_MeshRefinementModule, ONLY: &
+    nFine, &
+    vpCoarseToFineProjectionMatrix
+
+  ! --- Local Modules ---
+
+  USE thornado_amrex_interpolater_module, ONLY: &
+    amrex_interp_dg
+  USE MF_KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One
+  USE InputParsingModule, ONLY: &
+    UseTiling, &
+    DEBUG
+  USE MF_MeshModule, ONLY: &
+    CreateMesh_MF, &
+    DestroyMesh_MF
+  USE MF_GeometryModule, ONLY: &
+    ApplyBoundaryConditions_Geometry_MF, &
+    UpdateSpatialMetric_MF
+  USE MF_Euler_BoundaryConditionsModule, ONLY: &
[…]

### 2024-11-25 SandBox/AMReX/Modules/ProgramHeader/InputParsingModule.F90

@@ -1,0 +1,552 @@
+MODULE InputParsingModule
+
+  ! --- AMReX modules ---
+
+  USE amrex_fort_module, ONLY: &
+    amrex_spacedim
+  USE amrex_parmparse_module, ONLY: &
+    amrex_parmparse, &
+    amrex_parmparse_build, &
+    amrex_parmparse_destroy
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    InitializeProgramHeader, &
+    bcZ, &
+    nDimsX
+  USE UnitsModule, ONLY: &
+    ActivateUnitsDisplay, &
+    UnitsDisplay
+  USE GeometryFieldsModule, ONLY: &
+    CoordinateSystem
+  USE RadiationFieldsModule, ONLY: &
+    SetNumberOfSpecies
+
+  ! --- Local modules ---
+
+  USE MF_KindModule, ONLY: &
+    DP, &
+    Zero
+  USE MF_ErrorModule, ONLY: &
+    DescribeError_MF
+
+  IMPLICIT NONE
+
+  ! -- thornado ---
+
+  CHARACTER(:), ALLOCATABLE :: ProgramName
+  INTEGER     , ALLOCATABLE :: swX(:)
+  INTEGER     , ALLOCATABLE :: bcX(:)
+  INTEGER                   :: nNodes
+  REAL(DP)                  :: t_end, t_wrt, t_chk, dt_wrt, dt_chk, dt_rel
+  INTEGER                   :: iCycleW, iCycleChk, iCycleD, iRestart, iReGrid
+  LOGICAL                   :: UsePhysicalUnits
+  LOGICAL                   :: DEBUG
+  LOGICAL                   :: SolveGravity_NR
+
+  ! --- Transport ---
+
+  INTEGER, ALLOCATABLE :: bcZ_TwoMoment(:)
+  INTEGER              :: nE, nSpecies, swE, bcE
+  REAL(DP)             :: eL, eR, zoomE
+
+  ! --- Opacity Tables ---
+
+  CHARACTER(:), ALLOCATABLE :: OpacityTableName_AbEm
+  CHARACTER(:), ALLOCATABLE :: OpacityTableName_Iso
+  CHARACTER(:), ALLOCATABLE :: OpacityTableName_NES
[…]

### 2024-11-25 SandBox/AMReX/Modules/TwoMoment/FinalizationModule_old.f90

@@ -1,0 +1,70 @@
+MODULE FinalizationModule
+
+  ! --- AMReX Modules ---
+  USE amrex_amr_module,     ONLY: &
+    amrex_geometry, &
+    amrex_geometry_destroy, &
+    amrex_finalize
+  USE amrex_amrcore_module, ONLY: &
+    amrex_amrcore_finalize
+
+  ! --- thornado Modules ---
+  USE RadiationFieldsModule,                ONLY: &
+    DestroyRadiationFields
+  USE TwoMoment_TimersModule, ONLY: &
+    FinalizeTimers
+
+  ! --- Local Modules ---
+  USE InputParsingModule,                 ONLY: &
+    nLevels, MyAmrFinalize
+  USE MF_TwoMoment_SlopeLimiterModule, ONLY: &
+    FinalizeSlopeLimiter_TwoMoment_MF
+  USE MF_TwoMoment_PositivityLimiterModule, ONLY: &
+    FinalizePositivityLimiter_TwoMoment_MF
+  USE MF_TwoMoment_TimeSteppingModule_Relativistic,    ONLY: &
+    Finalize_IMEX_RK_MF
+
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: FinalizeProgram
+
+
+
+ CONTAINS
+
+
+
+  SUBROUTINE FinalizeProgram(GEOM)
+
+
+    TYPE(amrex_geometry),  INTENT(inout) :: GEOM(0:nLevels-1)
+
+    INTEGER :: iLevel
+
+    CALL DestroyRadiationFields
+
+    CALL Finalize_IMEX_RK_MF
+
+    DO iLevel = 0, nLevels-1
+      CALL amrex_geometry_destroy( GEOM(iLevel) )
+    END DO
+
+    CALL FinalizeSlopeLimiter_TwoMoment_MF
+
+    CALL FinalizePositivityLimiter_TwoMoment_MF
+
+    CALL MyAmrFinalize
+
+    CALL FinalizeTimers
+
+    CALL amrex_amrcore_finalize
+
+    CALL amrex_finalize
+
+
+  END SUBROUTINE FinalizeProgram
+
+
+END MODULE FinalizationModule

### 2024-11-25 SandBox/AMReX/Modules/TwoMoment/InputOutputEuler.f90

@@ -1,0 +1,680 @@
+MODULE InputOutputEuler
+
+  ! --- AMReX Modules ---
+
+  USE ISO_C_BINDING
+  USE amrex_fort_module,       ONLY: &
+    AR => amrex_real, &
+    amrex_spacedim
+  USE amrex_plotfile_module,   ONLY: &
+    amrex_write_plotfile
+  USE amrex_string_module,     ONLY: &
+    amrex_string, &
+    amrex_string_build
+  USE amrex_box_module,        ONLY: &
+    amrex_box
+  USE amrex_boxarray_module,   ONLY: &
+    amrex_boxarray,       &
+    amrex_boxarray_build, &
+    amrex_boxarray_destroy
+  USE amrex_distromap_module,  ONLY: &
+    amrex_distromap,       &
+    amrex_distromap_build, &
+    amrex_distromap_destroy
+  USE amrex_multifab_module,   ONLY: &
+    amrex_multifab,         &
+    amrex_multifab_build,   &
+    amrex_multifab_destroy, &
+    amrex_mfiter,           &
+    amrex_mfiter_build,     &
+    amrex_mfiter_destroy
+  USE amrex_geometry_module,   ONLY: &
+    amrex_geometry,       &
+    amrex_geometry_build, &
+    amrex_geometry_destroy
+  USE amrex_amrcore_module,    ONLY: &
+    amrex_get_amrcore, &
+    amrex_ref_ratio
+  USE amrex_parallel_module,   ONLY: &
+    amrex_parallel_ioprocessor
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule,     ONLY: &
+    nDOFX
+  USE ReferenceElementModuleX, ONLY: &
+    WeightsX_q
+  USE GeometryFieldsModule,    ONLY: &
+    ShortNamesGF, &
+    unitsGF,      &
+    nGF,          &
+    iGF_SqrtGm
+  USE FluidFieldsModule,       ONLY: &
+    ShortNamesCF, &
+    unitsCF,      &
+    nCF,          &
+    ShortNamesPF, &
+    unitsPF,      &
+    nPF,          &
+    ShortNamesAF, &
+    unitsAF,      &
[…]

### 2024-11-25 SandBox/AMReX/Modules/TwoMoment/MF_FieldsModule.f90

@@ -1,0 +1,74 @@
+
+MODULE MF_FieldsModule
+
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_multifab_destroy
+
+  IMPLICIT NONE
+  PRIVATE
+
+  TYPE(amrex_multifab), ALLOCATABLE, PUBLIC :: MF_uCF(:)
+  TYPE(amrex_multifab), ALLOCATABLE, PUBLIC :: MF_uPF(:)
+  TYPE(amrex_multifab), ALLOCATABLE, PUBLIC :: MF_uGF(:)
+  TYPE(amrex_multifab), ALLOCATABLE, PUBLIC :: MF_uAF(:)
+  TYPE(amrex_multifab), ALLOCATABLE, PUBLIC :: MF_uDF(:)
+  TYPE(amrex_multifab), ALLOCATABLE, PUBLIC :: MF_uPR(:)
+  TYPE(amrex_multifab), ALLOCATABLE, PUBLIC :: MF_uCR(:)
+  REAL(DP), ALLOCATABLE, PUBLIC :: MF_OffGridFlux_Twomoment(:,:)
+
+  PUBLIC :: InitializeDataAMReX
+  PUBLIC :: FinalizeDataAMReX
+
+CONTAINS
+
+
+  SUBROUTINE InitializeDataAMReX( nLevels )
+
+    INTEGER, INTENT(in) :: nLevels
+
+    ALLOCATE( MF_uCF(0:nLevels-1) )
+    ALLOCATE( MF_uPF(0:nLevels-1) )
+    ALLOCATE( MF_uGF(0:nLevels-1) )
+    ALLOCATE( MF_uAF(0:nLevels-1) )
+    ALLOCATE( MF_uDF(0:nLevels-1) )
+    ALLOCATE( MF_uPR(0:nLevels-1) )
+    ALLOCATE( MF_uCR(0:nLevels-1) )
+    ALLOCATE( MF_OffGridFlux_TwoMoment(0:nLevels-1,2*nCR) )
+
+  END SUBROUTINE InitializeDataAMReX
+
+
+  SUBROUTINE FinalizeDataAMReX( nLevels )
+
+    INTEGER, INTENT(in) :: nLevels
+
+    INTEGER :: iLevel
+      
+
+    DEALLOCATE( MF_OffGridFlux_TwoMoment )
+    DO iLevel = 0, nLevels-1
+
+      CALL amrex_multifab_destroy( MF_uCF(iLevel) )
[…]

### 2024-11-25 SandBox/AMReX/Modules/TwoMoment/MF_TwoMoment_DiscretizationModule_Collisions_Neutrinos_GR.f90

@@ -1,0 +1,300 @@
+MODULE MF_TwoMoment_DiscretizationModule_Collisions_Neutrinos_GR
+
+  ! --- AMReX Modules ---
+
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_geometry_module, ONLY: &
+    amrex_geometry
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    swX, &
+    swE, &
+    nDOFX, &
+    nDOFE, &
+    nDOFZ, &
+    iE_B0, &
+    iE_E0, &
+    iE_B1, &
+    iE_E1
+  USE MeshModule, ONLY: &
+    MeshX
+  USE GeometryFieldsModule, ONLY: &
+    nGF
+  USE GeometryFieldsModuleE, ONLY: &
+    nGE, &
+    uGE
+  USE RadiationFieldsModule, ONLY: &
+    nCR
+  USE FluidFieldsModule, ONLY: &
+    nCF
+  USE TwoMoment_DiscretizationModule_Collisions_Neutrinos, ONLY: &
+    ComputeIncrement_TwoMoment_Implicit
+
+
+  ! --- Local Modules ---
+
+  USE MF_KindModule, ONLY: &
+    DP, &
+    Zero
+  USE MF_UtilitiesModule, ONLY: &
+    amrex2thornado_X, &
+    amrex2thornado_Z, &
+    thornado2amrex_Z, &
+    thornado2amrex_X, &
+    AllocateArray_X, &
+    DeallocateArray_X, &
+    AllocateArray_Z, &
+    DeallocateArray_Z
+  USE InputParsingModule,ONLY: &
+    nLevels, &
+    nSpecies, &
+    UseTiling, &
+    nE
+  USE MF_MeshModule, ONLY: &
+    CreateMesh_MF, &
+    DestroyMesh_MF
+  USE MF_TwoMoment_BoundaryConditionsModule, ONLY: &
+    ApplyBoundaryConditions_TwoMoment_MF
+  USE MF_Euler_BoundaryConditionsModule, ONLY: &
+    ApplyBoundaryConditions_Euler_MF
+  USE MF_EdgeMapModule, ONLY: &
[…]

### 2024-11-25 SandBox/AMReX/Modules/TwoMoment/MF_TwoMoment_DiscretizationModule_Collisions_Relativistic.f90

@@ -1,0 +1,282 @@
+MODULE  MF_TwoMoment_DiscretizationModule_Collisions_Relativistic
+
+  ! --- AMReX Modules ---
+  USE amrex_fort_module,     ONLY: &
+    amrex_real
+  USE amrex_box_module,      ONLY: &
+    amrex_box
+  USE amrex_geometry_module, ONLY: &
+    amrex_geometry
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_mfiter,   &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy
+
+  ! --- thornado Modules ---
+  USE ProgramHeaderModule,      ONLY: &
+    swX, nDOFX, nDOFZ, swE, nDOFE, iE_B0, iE_E0, iE_B1, iE_E1
+  USE GeometryFieldsModule,     ONLY: &
+    nGF
+  USE GeometryFieldsModuleE,     ONLY: &
+    nGE, uGE
+  USE RadiationFieldsModule,            ONLY: &
+    nCR
+  USE FluidFieldsModule,            ONLY: &
+    nCF
+  USE TwoMoment_DiscretizationModule_Collisions, ONLY: &
+    ComputeIncrement_TwoMoment_Implicit
+  USE MeshModule, ONLY: &
+    MeshX
+
+  ! --- Local Modules ---
+  USE MF_UtilitiesModule,                ONLY: &
+    amrex2thornado_X, &
+    amrex2thornado_Z, &
+    thornado2amrex_Z, &
+    AllocateArray_X, &
+    DeallocateArray_X, &
+    AllocateArray_Z, &
+    DeallocateArray_Z
+  USE InputParsingModule,                       ONLY: &
+    nLevels, &
+    nSpecies, &
+    UseTiling, &
+    nE
+  USE MF_MeshModule, ONLY: &
+    CreateMesh_MF, &
+    DestroyMesh_MF
+  USE MF_TwoMoment_BoundaryConditionsModule, ONLY: &
+    ApplyBoundaryConditions_TwoMoment_MF
+  USE MF_Euler_BoundaryConditionsModule, ONLY: &
+    ApplyBoundaryConditions_Euler_MF
+  USE MF_EdgeMapModule, ONLY: &
+    ConstructEdgeMap, &
+    EdgeMap
+
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: ComputeIncrement_TwoMoment_Implicit_MF
+
+
+CONTAINS
+
+
[…]

### 2024-11-25 SandBox/AMReX/Modules/TwoMoment/MF_TwoMoment_PositivityLimiterModule.f90

@@ -1,0 +1,255 @@
+MODULE MF_TwoMoment_PositivityLimiterModule
+
+  ! --- AMReX Modules ---
+
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_geometry_module, ONLY: &
+    amrex_geometry
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor
+  USE amrex_parmparse_module, ONLY: &
+    amrex_parmparse, &
+    amrex_parmparse_build, &
+    amrex_parmparse_destroy
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    swX, &
+    nDOFX, &
+    nDOFZ, &
+    iE_B0, &
+    iE_E0, &
+    iE_B1, &
+    iE_E1
+  USE GeometryFieldsModule, ONLY: &
+    nGF
+  USE GeometryFieldsModuleE, ONLY: &
+    uGE
+  USE RadiationFieldsModule, ONLY: &
+    nCR, &
+    nSpecies
+  USE FluidFieldsModule, ONLY: &
+    nCF
+  USE TwoMoment_PositivityLimiterModule, ONLY: &
+    InitializePositivityLimiter_TwoMoment, &
+    FinalizePositivityLimiter_TwoMoment, &
+    ApplyPositivityLimiter_TwoMoment
+
+  ! --- Local Modules ---
+
+  USE MF_KindModule, ONLY: &
+    DP
+  USE MF_UtilitiesModule, ONLY: &
+    amrex2thornado_X, &
+    amrex2thornado_Z, &
+    thornado2amrex_Z, &
+    AllocateArray_X, &
+    DeallocateArray_X, &
+    AllocateArray_Z, &
+    DeallocateArray_Z
+  USE InputParsingModule, ONLY: &
+    nLevels, &
+    UseTiling, &
+    nE
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializePositivityLimiter_TwoMoment_MF
+  PUBLIC :: FinalizePositivityLimiter_TwoMoment_MF
+  PUBLIC :: ApplyPositivityLimiter_TwoMoment_MF
+
+  LOGICAL :: UsePositivityLimiter
+
+CONTAINS
+
+
[…]

### 2024-11-25 SandBox/AMReX/Modules/TwoMoment/MF_TwoMoment_TallyModule.f90

@@ -1,0 +1,859 @@
+MODULE MF_TwoMoment_TallyModule
+
+  ! --- AMReX Modules ---
+
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_geometry_module, ONLY: &
+    amrex_geometry
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor, &
+    amrex_parallel_reduce_sum
+
+  ! --- thornado Modules ---
+
+  USE UnitsModule, ONLY: &
+    UnitsActive, &
+    SpeedOfLight, &
+    PlanckConstant, &
+    MeV,            &
+    UnitsDisplay
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nNodesX, &
+    nDimsX
+  USE ReferenceElementModuleX, ONLY: &
+    WeightsX_q
+  USE ReferenceElementModule, ONLY: &
+    Weights_q
+  USE UnitsModule, ONLY: &
+    UnitsDisplay
+  USE MeshModule, ONLY: &
+    MeshType, &
+    CreateMesh, &
+    DestroyMesh
+  USE GeometryFieldsModule, ONLY: &
+    nGF, &
+    iGF_SqrtGm, &
+    iGF_Gm_dd_11, &
+    iGF_Gm_dd_22, &
+    iGF_Gm_dd_33, &
+    CoordinateSystem
+  USE FluidFieldsModule, ONLY: &
+    nCF, &
+    iCF_D, &
+    iCF_E
+  USE GeometryFieldsModuleE,     ONLY: &
+    nGE, uGE, iGE_Ep2, iGE_Ep3
+  USE RadiationFieldsModule, ONLY: &
+    nSpecies, LeptonNumber, &
+    nCR, iCR_N, iCR_G1, iCR_G2, iCR_G3
+  USE Euler_UtilitiesModule_Relativistic, ONLY: &
+    ComputePrimitive_Euler_Relativistic
+  USE FluidFieldsModule, ONLY: &
+    nCF, iCF_D, iCF_S1, iCF_S2, iCF_S3, iCF_E, iCF_Ne, &
+    nPF, iPF_D, iPF_V1, iPF_V2, iPF_V3, iPF_E, iPF_Ne
+  USE ProgramHeaderModule,      ONLY: &
[…]

### 2024-11-25 SandBox/AMReX/Modules/TwoMoment/Restart_old.cpp

@@ -1,0 +1,277 @@
+/*
+Restart.cpp
+
+Originally created by nataraj for one MultiFab
+
+Modified by sjdunham for multiple MultiFabs (not working yet)
+
+*/
+
+#include <sstream>
+#include <iomanip>
+
+#include <AMReX_ParmParse.H>
+#include <AMReX_PlotFileUtil.H>
+#include <AMReX_VisMF.H>
+
+#ifdef BL_MEM_PROFILING
+#include <AMReX_MemProfiler.H>
+#endif
+
+#include "Restart.H"
+
+using namespace amrex;
+
+extern "C"
+{
+  void writefieldsamrex_checkpoint
+         ( int StepNo[], int nLevels,
+           Real dt[], Real time[], Real t_wrt[],BoxArray** BA,
+           MultiFab** MF_uCR, MultiFab** MF_uPR )
+  {
+
+    // chk00010            Write a checkpoint file with this root directory
+    // chk00010/Header     This contains information you need to save
+    //                       (e.g., FinestLevel, time, etc.), and also
+    //                       the BoxArrays at each level
+    // chk00010/Level_0/
+    // chk00010/Level_1/
+    // etc.                These subdirectories will hold the MultiFab
+    //                     data at each level of refinement
+
+    // Checkpoint file name, e.g., chk00010
+
+
+    const std::string& checkpointname
+                         = amrex::Concatenate( chk_file, StepNo[0], 8 );
+
+    if ( ParallelDescriptor::IOProcessor() )
+      amrex::Print() << "\n    Writing checkpoint " << checkpointname << "\n";
+
+    const int FinestLevel = nLevels-1;
+
+    // ---- Prebuild a hierarchy of directories
+    // ---- dirName is built first. If dirName exists, it is renamed. Then build
+    // ----   dirName/subDirPrefix_0 .. dirName/subDirPrefix_nLevels-1
+    // ---- If callBarrier is true, call ParallelDescriptor::Barrier()
+    // ----   after all directories are built
+    // ---- ParallelDescriptor::IOProcessor() creates the directories
+    amrex::PreBuildDirectorHierarchy( checkpointname, "Level_", nLevels, true );
+
+    // Write Header file
+    if ( ParallelDescriptor::IOProcessor() )
+    {
+
+      std::string HeaderFileName( checkpointname + "/Header" );
[…]

### 2024-11-25 SandBox/AMReX/TwoMoment_Test/ApplicationDriver.f90

@@ -1,0 +1,206 @@
+PROGRAM main
+
+  ! --- AMReX Modules ---
+  USE amrex_fort_module,                ONLY: &
+    amrex_real
+  USE amrex_parallel_module,            ONLY: &
+    amrex_parallel_ioprocessor, &
+    amrex_parallel_communicator
+  USE amrex_amrcore_module, ONLY: &
+    amrex_geom
+
+  ! --- Local Modules ---
+  USE MF_TwoMoment_UtilitiesModule,     ONLY: &
+    ComputeTimeStep_TwoMoment_MF,                &
+    ComputeTimeStep_TwoMoment_Fancy_MF,          &
+    ComputeFromConserved_TwoMoment_MF, &
+    ComputeGray_TwoMoment_MF
+  USE MF_Euler_UtilitiesModule, ONLY: &
+    ComputeFromConserved_Euler_MF
+  USE MF_UtilitiesModule,     ONLY: &
+    ShowVariableFromMultiFab
+  USE MF_FieldsModule_Geometry,                  ONLY: &
+    MF_uGF
+  USE MF_FieldsModule_Euler,                  ONLY: &
+    MF_uCF, &
+    MF_uPF, &
+    MF_uAF, &
+    MF_uDF
+  USE MF_FieldsModule_TwoMoment,                  ONLY: &
+    MF_uPR, &
+    MF_uCR, &
+    MF_uGR
+  USE MF_TwoMoment_TallyModule,         ONLY: &
+    ComputeTally_TwoMoment_MF
+  USE MF_Euler_TallyModule,         ONLY: &
+    ComputeTally_Euler_MF, &
+    BaryonicMass_Initial, &
+    BaryonicMass_OffGrid, &
+    EulerMomentumX1_Initial, &
+    EulerMomentumX1_OffGrid, &
+    EulerMomentumX2_Initial, &
+    EulerMomentumX2_OffGrid, &
+    EulerMomentumX3_Initial, &
+    EulerMomentumX3_OffGrid, &
+    EulerEnergy_Initial, &
+    EulerEnergy_OffGrid, &
+    ElectronNumber_Initial, &
+    ElectronNumber_OffGrid, &
+    ADMMass_Initial, &
+    ADMMass_OffGrid
+  USE InitializationModule,             ONLY: &
+    InitializeProgram
+  USE FinalizationModule,               ONLY: &
[…]

### 2024-11-25 SandBox/AMReX/TwoMoment_Test/PlotAMReX_yt.py

@@ -1,0 +1,471 @@
+#!/usr/local/bin/python3
+
+import yt
+import numpy as np
+import subprocess
+from os import listdir
+from os.path import isfile
+from sys import argv, exit
+import matplotlib.pyplot as plt
+
+"""
+Default use (python3 PlotAMReX_yt.py), plots last plot-file in ProblemDirectory
+
+Can also specify certain plot-file:  python3 PlotAMReX_yt.py thornado_00000010
+"""
+
+yt.funcs.mylog.setLevel(0) # Suppress initial yt output to screen
+
+# --- Get user's HOME directory ---
+HOME = subprocess.check_output( ["echo $HOME"], shell = True)
+HOME = HOME[:-1].decode( "utf-8" ) + '/'
+
+# --- Get user's THORNADO_DIR directory ---
+THORNADO_DIR = subprocess.check_output( ["echo $THORNADO_DIR"], shell = True)
+THORNADO_DIR = THORNADO_DIR[:-1].decode( "utf-8" ) + '/'
+
+#### ========== User Input ==========
+
+# Specify directory containing plotfiles
+ProblemDirectory = THORNADO_DIR + 'SandBox/AMReX/TwoMoment_Test/'
+
+# Specify name of problem (only used for name of output file(s))
+ProblemName = 'KHI'
+
+# Specify plot file base name
+PlotFileBaseName = 'thornado'
+
+# Specify field to plot
+VariableToPlot = 'CR_N'
+
+# Specify to plot in log-scale
+UseLogScale = False
+
+# Specify whether or not to use physical units
+UsePhysicalUnits = False
+
+# Specify coordinate system (currently supports 'cartesian' and 'spherical' )
+CoordinateSystem = 'cartesian'
+
+# Specify aspect ratio (relativistic KHI needs aspect = 0.5)
+aspect = 1.0
+
+# Specify colormap
+cmap = 'jet'
+
+# Specify to write out data to a file
+WriteOut = 1
+# Specify to read in data from a file
+ReadIn = 1
+
+#init or final
+time = 1
+#number of cells
+cells = "8"
+
+# Specify whether or not to make a movie
+MakeMovie, DataFileName, TimeFileName = False, 'MovieData.dat', 'MovieTime.dat'
+
+#### ================================
+
+if( len( argv ) > 1 ):
+    File = argv[1]
+else:
+    # Get last plotfile in directory
+    FileArray \
[…]

### 2024-11-25 SandBox/AMReX/UnitTests/CheckInterpolation/ApplicationDriver.f90

@@ -1,0 +1,16 @@
+PROGRAM main
+
+  USE InitializationModule, ONLY: &
+    InitializeProgram
+  USE FinalizationModule, ONLY: &
+    FinalizeProgram
+
+  IMPLICIT NONE
+
+  INCLUDE 'mpif.h'
+
+  CALL InitializeProgram
+
+  CALL FinalizeProgram
+
+END PROGRAM main

### 2024-11-25 SandBox/AMReX/dgExperiments_Euler_Relativistic_IDEAL/MF_InitializationModule.f90

@@ -1,0 +1,1500 @@
+MODULE MF_InitializationModule
+
+  ! --- AMReX Modules ---
+
+  USE amrex_box_module, ONLY: &
+    amrex_box
+  USE amrex_multifab_module, ONLY: &
+    amrex_multifab, &
+    amrex_mfiter, &
+    amrex_mfiter_build, &
+    amrex_mfiter_destroy
+  USE amrex_parmparse_module, ONLY: &
+    amrex_parmparse, &
+    amrex_parmparse_build, &
+    amrex_parmparse_destroy
+  USE amrex_parallel_module, ONLY: &
+    amrex_parallel_ioprocessor, &
+    amrex_parallel_reduce_min
+
+  ! --- thornado Modules ---
+
+  USE ProgramHeaderModule, ONLY: &
+    ProgramName, &
+    swX, &
+    nDOFX
+  USE ReferenceElementModuleX, ONLY: &
+    NodeNumberTableX
+  USE MeshModule, ONLY: &
+    MeshX, &
+    NodeCoordinate
+  USE EquationOfStateModule_IDEAL, ONLY: &
+    ComputePressureFromPrimitive_IDEAL, &
+    Gamma_IDEAL
+  USE GeometryFieldsModule, ONLY: &
+    iGF_Gm_dd_11, &
+    iGF_Gm_dd_22, &
+    iGF_Gm_dd_33, &
+    nGF
+  USE FluidFieldsModule, ONLY: &
+    iCF_D, &
+    iCF_S1, &
+    iCF_S2, &
+    iCF_S3, &
+    iCF_E, &
+    iCF_Ne, &
+    nCF, &
+    iPF_D, &
+    iPF_V1, &
+    iPF_V2, &
+    iPF_V3, &
+    iPF_E, &
+    iPF_Ne, &
+    nPF
+  USE Euler_UtilitiesModule, ONLY: &
+    ComputeConserved_Euler
+  USE Euler_UtilitiesModule_Relativistic, ONLY: &
+    rhoMin_Euler_GR, &
+    epsMin_Euler_GR
+
+  ! --- Local Modules ---
+
+  USE MF_KindModule, ONLY: &
+    DP, &
+    Zero, &
+    Half, &
+    One, &
+    Two, &
+    TwoPi
+  USE MF_UtilitiesModule, ONLY: &
+    thornado2amrex_X, &
+    amrex2thornado_X, &
[…]

### 2024-11-25 SandBox/AdiabaticCollapse_XCFC/TestPressure.f90

@@ -1,0 +1,80 @@
+PROGRAM TestPressure
+
+  USE KindModule, ONLY: &
+    DP
+  USE EquationOfStateModule, ONLY: &
+    InitializeEquationOfState, &
+    FinalizeEquationOfState,   &
+    ComputePressureFromSpecificInternalEnergy
+  USE UnitsModule, ONLY: &
+    Gram, Centimeter, Erg
+
+  IMPLICIT NONE
+
+  INTEGER  :: i
+  INTEGER, PARAMETER :: N = 1000
+
+  REAL(DP) :: rhoMin, rhoMax, drho, rho(N)
+  REAL(DP) :: epsMin, epsMax, deps, eps(N)
+  REAL(DP) :: YeMin , YeMax , dYe , Ye(N)
+  REAL(DP) :: p(N)
+
+  CALL InitializeEquationOfState &
+         ( EquationOfState_Option &
+             = 'TABLE', &
+           EquationOfStateTableName_Option &
+             = 'wl-EOS-SFHo-25-50-100.h5' )
+
+rho(1) = 9.314925e13_DP * ( Gram / Centimeter**3 )
+eps(1) = 5.465183e19_DP * ( Erg / Gram )
+Ye (1) = 0.442_DP
+
+rho(2) = 9.266702e13_DP * ( Gram / Centimeter**3 )
+eps(2) = 5.299234e19_DP * ( Erg / Gram )
+Ye (2) = 0.442_DP
+
+    CALL ComputePressureFromSpecificInternalEnergy &
+           ( rho(1), eps(1), Ye(1), p(1) )
+    PRINT '(A,ES14.6E3)', 'p(1) = ', p(1) / ( Erg / Centimeter**3 )
+
+    CALL ComputePressureFromSpecificInternalEnergy &
+           ( rho(2), eps(2), Ye(2), p(2) )
+    PRINT '(A,ES14.6E3)', 'p(2) = ', p(2) / ( Erg / Centimeter**3 )
+stop
+
+  rhoMin = 9.0e13_DP * ( Gram / Centimeter**3 )
+  rhoMax = 1.0e14_DP * ( Gram / Centimeter**3 )
+  drho   = ( rhoMax - rhoMin ) / DBLE( N )
+
+  epsMin = 5.0e19_DP * ( Erg / Gram )
+  epsMax = 6.0e19_DP * ( Erg / Gram )
[…]

### 2024-11-25 SandBox/CoreCollapseSupernova_Relativistic/ApplicationDriver.f90

@@ -1,0 +1,647 @@
+PROGRAM ApplicationDriver_CCSN
+
+  USE KindModule, ONLY: &
+    DP, Zero, One, Two, Pi, TwoPi, SqrtTiny
+  USE UnitsModule, ONLY: &
+    Kilometer, &
+    Millisecond, &
+    MeV
+  USE ProgramHeaderModule, ONLY: &
+    iX_B0, iX_E0, iX_B1, iX_E1, &
+    iE_B0, iE_E0, iE_B1, iE_E1, &
+    iZ_B0, iZ_E0, iZ_B1, iZ_E1
+  USE GeometryFieldsModule, ONLY: &
+    uGF
+  USE GeometryFieldsModuleE, ONLY: &
+    uGE
+  USE FluidFieldsModule, ONLY: &
+    uCF, iCF_D, &
+    uPF, uAF, uDF
+  USE Euler_UtilitiesModule_NonRelativistic, ONLY: &
+    ComputeFromConserved_Euler_NonRelativistic, &
+    ComputeTimeStep_Euler_NonRelativistic
+  USE Euler_SlopeLimiterModule_NonRelativistic_TABLE, ONLY: &
+    ApplySlopeLimiter_Euler_NonRelativistic_TABLE
+  USE Euler_PositivityLimiterModule_NonRelativistic_TABLE, ONLY: &
+    ApplyPositivityLimiter_Euler_NonRelativistic_TABLE
+  USE RadiationFieldsModule, ONLY: &
+    uCR, uPR
+  USE TwoMoment_UtilitiesModule_OrderV, ONLY: &
+    ComputeFromConserved_TwoMoment, &
+    ComputeTimeStep_TwoMoment
+  USE TwoMoment_SlopeLimiterModule_OrderV, ONLY: &
+    ApplySlopeLimiter_TwoMoment
+  USE TwoMoment_PositivityLimiterModule_OrderV, ONLY: &
+    ApplyPositivityLimiter_TwoMoment
+  USE TwoMoment_DiscretizationModule_Collisions_Neutrinos_OrderV, ONLY: &
+    ComputeIncrement_TwoMoment_Implicit
+  USE GravitySolutionModule_Newtonian_Poseidon, ONLY: &
+    SolveGravity_Newtonian_Poseidon
+  USE TwoMoment_TimeSteppingModule_OrderV, ONLY: &
+    Update_IMEX_RK
[…]

### 2024-11-25 SandBox/DeleptonizationWave/DeleptonizationWave.F90

@@ -1,0 +1,402 @@
+PROGRAM DeleptonizationWave
+
+  USE KindModule, ONLY: &
+    DP, SqrtTiny, Third, Zero
+  USE ProgramHeaderModule, ONLY: &
+    nZ, nNodesZ, &
+    iX_B0, iX_E0, iX_B1, iX_E1, &
+    iE_B0, iE_E0, iE_B1, iE_E1, &
+    iZ_B0, iZ_E0, iZ_B1, iZ_E1
+  USE UnitsModule, ONLY: &
+    Kilometer, &
+    Millisecond, &
+    MeV
+  USE ProgramInitializationModule, ONLY: &
+    InitializeProgram, &
+    FinalizeProgram
+  USE TimersModule, ONLY: &
+    InitializeTimers, &
+    FinalizeTimers, &
+    TimersStart, &
+    TimersStop, &
+    Timer_Initialize, &
+    Timer_InputOutput, &
+    Timer_Evolve, &
+    Timer_PositivityLimiter, &
+    Timer_PL_In, &
+    Timer_PL_Points, &
+    Timer_PL_CellAverage, &
+    Timer_PL_Theta_1, &
+    Timer_PL_Theta_2, &
+    Timer_PL_Out
+  USE ReferenceElementModuleX, ONLY: &
+    InitializeReferenceElementX, &
+    FinalizeReferenceElementX
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+    InitializeReferenceElementX_Lagrange, &
+    FinalizeReferenceElementX_Lagrange
+  USE ReferenceElementModuleE, ONLY: &
+    InitializeReferenceElementE, &
+    FinalizeReferenceElementE
+  USE ReferenceElementModuleE_Lagrange, ONLY: &
+    InitializeReferenceElementE_Lagrange, &
+    FinalizeReferenceElementE_Lagrange
+  USE ReferenceElementModule, ONLY: &
+    InitializeReferenceElement, &
+    FinalizeReferenceElement
+  USE ReferenceElementModule_Lagrange, ONLY: &
+    InitializeReferenceElement_Lagrange, &
+    FinalizeReferenceElement_Lagrange
+  USE GeometryFieldsModule, ONLY: &
+    uGF
+  USE GeometryComputationModule, ONLY: &
+    ComputeGeometryX
+  USE GeometryFieldsModuleE, ONLY: &
+    uGE
[…]

### 2024-11-25 SandBox/DeleptonizationWave/DeleptonizationWave1D.F90

@@ -1,0 +1,484 @@
+PROGRAM DeleptonizationWave1D
+
+  USE KindModule, ONLY: &
+    DP, SqrtTiny, Half, Zero, &
+    Pi, TwoPi
+  USE ProgramHeaderModule, ONLY: &
+    nZ, nNodesZ, &
+    iX_B0, iX_E0, iX_B1, iX_E1, &
+    iE_B0, iE_E0, iE_B1, iE_E1, &
+    iZ_B0, iZ_E0, iZ_B1, iZ_E1
+  USE UnitsModule, ONLY: &
+    Kilometer, &
+    Millisecond, &
+    MeV
+  USE ProgramInitializationModule, ONLY: &
+    InitializeProgram, &
+    FinalizeProgram
+  USE TimersModule, ONLY: &
+    InitializeTimers, &
+    FinalizeTimers, &
+    TimersStart, &
+    TimersStop, &
+    Timer_Initialize, &
+    Timer_InputOutput, &
+    Timer_Evolve, &
+    Timer_PositivityLimiter, &
+    Timer_PL_In, &
+    Timer_PL_Points, &
+    Timer_PL_CellAverage, &
+    Timer_PL_Theta_1, &
+    Timer_PL_Theta_2, &
+    Timer_PL_Out
+  USE ReferenceElementModuleX, ONLY: &
+    InitializeReferenceElementX, &
+    FinalizeReferenceElementX
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+    InitializeReferenceElementX_Lagrange, &
+    FinalizeReferenceElementX_Lagrange
+  USE ReferenceElementModuleE, ONLY: &
+    InitializeReferenceElementE, &
+    FinalizeReferenceElementE
+  USE ReferenceElementModuleE_Lagrange, ONLY: &
+    InitializeReferenceElementE_Lagrange, &
+    FinalizeReferenceElementE_Lagrange
+  USE ReferenceElementModule, ONLY: &
+    InitializeReferenceElement, &
+    FinalizeReferenceElement
+  USE ReferenceElementModule_Lagrange, ONLY: &
+    InitializeReferenceElement_Lagrange, &
+    FinalizeReferenceElement_Lagrange
+  USE MeshModule, ONLY: &
+    MeshX
+  USE GeometryFieldsModule, ONLY: &
+    uGF, &
+    iGF_Gm_dd_11, &
+    iGF_Gm_dd_22, &
[…]

### 2024-11-25 SandBox/Interface_CASTRO/Driver.f90

@@ -1,0 +1,88 @@
+PROGRAM Driver
+
+  USE KindModule, ONLY: &
+    DP
+  USE UnitsModule, ONLY: &
+    Gram, &
+    Centimeter, &
+    Kilometer, &
+    Millisecond, &
+    MeV, &
+    Erg
+  USE GeometryFieldsModuleE, ONLY: &
+    uGE
+  USE GeometryFieldsModule, ONLY: &
+    uGF
+  USE FluidFieldsModule, ONLY: &
+    uCF, iCF_D, iCF_S1, iCF_S2, iCF_S3, iCF_E, iCF_Ne
+  USE RadiationFieldsModule, ONLY: &
+    uCR, iCR_N, iCR_G1, iCR_G2, iCR_G3
+  USE ThornadoInitializationModule, ONLY: &
+    InitThornado, &       ! --- To be called once
+    InitThornado_Patch, & ! --- To be called once per patch
+    FreeThornado_Patch    ! --- To be called once per parch
+  USE TimeSteppingModule_Castro, ONLY: &
+    Update_IMEX_PDARS
+
+  IMPLICIT NONE
+
+  INCLUDE 'mpif.h'
+
+  INTEGER  :: i
+  INTEGER  :: mpierr
+  REAL(DP) :: wTime
+  REAL(DP) :: dt
+
+  CALL MPI_INIT( mpierr )
+
+  wTime = MPI_WTIME( )
+
+  CALL InitThornado &
+         ( nDimsX = 3, nE = 10, swE = 0, eL_in = 0.0d0, eR_in = 1.0d2, &
+           zoomE = 1.0_DP, nSpecies_in = 1 )
+
+  wTime = MPI_WTIME( ) - wTime
+
+  WRITE(*,*)
+  WRITE(*,'(A,A32,ES8.2E2)') '', 'InitThornado: ', wTime
+  WRITE(*,*)
+
+  wTime = MPI_WTIME( )
+
+  DO i = 1, 2
+
+    CALL InitThornado_Patch &
+           ( nX    = [ 12, 12, 12 ], &
+             swX   = [ 2, 2, 2 ], &
+             xL    = [ 00.0_DP, 00.0_DP, 00.0_DP ] * Kilometer, &
[…]

### 2024-11-25 SandBox/Opacities/Executables/PlotNeutrinoOpacities.m

@@ -1,0 +1,32 @@
+close all
+clear all
+
+E = ReadVector( 'E.dat' );
+
+Chi_NuE      = ReadVector(      'Chi_NuE.dat' );
+Sig_NuE      = ReadVector(    'Sigma_NuE.dat' );
+Chi_NES_NuE  = ReadVector(  'Chi_NES_NuE.dat' );
+Chi_Pair_NuE = ReadVector( 'Chi_Pair_NuE.dat' );
+
+Chi_NuE_Bar      = ReadVector(      'Chi_NuE_Bar.dat' );
+Sig_NuE_Bar      = ReadVector(    'Sigma_NuE_Bar.dat' );
+Chi_NES_NuE_Bar  = ReadVector(  'Chi_NES_NuE_Bar.dat' );
+Chi_Pair_NuE_Bar = ReadVector( 'Chi_Pair_NuE_Bar.dat' );
+
+loglog( E, Chi_NuE,              '-k', 'linewidth', 2 ); hold on
+loglog( E, Sig_NuE,              '-b', 'linewidth', 2 )
+loglog( E, Chi_NES_NuE,          '-c', 'linewidth', 2 )
+loglog( E, 1.d3 .* Chi_Pair_NuE, '-r', 'linewidth', 2 )
+
+loglog( E, Chi_NuE_Bar,              '--k', 'linewidth', 3 )
+loglog( E, Sig_NuE_Bar,              '--b', 'linewidth', 3 )
+loglog( E, Chi_NES_NuE_Bar,          '--c', 'linewidth', 3 )
+loglog( E, 1.d3 .* Chi_Pair_NuE_Bar, '--r', 'linewidth', 3 )
+
+set( gca, 'fontsize', 13 )
+set( gca, 'fontweight', 'bold' )
+set( gca, 'linewidth', 02 )
+axis( [ 0.95 300 1e-6 1e-0 ] )
+title( 'Neutrino Opacities' )
+xlabel( '[ MeV ]',     'fontsize', 18 )
+ylabel( '[ cm^{-1} ]', 'fontsize', 18 )

### 2024-11-25 SandBox/PolynomialBasis/PolynomialBasisMappingTest.f90

@@ -1,0 +1,148 @@
+PROGRAM PolynomialBasisMappingTest
+
+  USE KindModule, ONLY: &
+    DP, TwoPi
+  USE UtilitiesModule, ONLY: &
+    NodeNumber, &
+    WriteVector, &
+    WriteMatrix
+  USE ProgramHeaderModule, ONLY: &
+    nNodes, nNodesE, nNodesX, nDOF, nDOFX, &
+    nDims, nDimsX
+  USE QuadratureModule, ONLY: &
+    InitializeQuadratures, &
+    GetQuadrature
+  USE PolynomialBasisModule_Lagrange, ONLY: &
+    InitializePolynomialBasis_Lagrange, &
+    EvalL
+  USE PolynomialBasisModule_Legendre, ONLY: &
+    InitializePolynomialBasis_Legendre, &
+    EvalP
+  USE PolynomialBasisMappingModule, ONLY: &
+    InitializePolynomialBasisMapping, &
+    MapNodalToModal_Radiation, &
+    MapModalToNodal_Radiation
+
+  IMPLICIT NONE
+
+  INTEGER :: iNodeE, iNodeX1, iNodeX2, iNodeX3, iNode
+  INTEGER :: iPointE, iPointX1
+  INTEGER, PARAMETER :: nPointsE = 64, nPointsX1 = 64
+  REAL(DP), PARAMETER :: eL = - 0.5_DP, eR = + 0.5_DP
+  REAL(DP), PARAMETER :: xL = - 0.5_DP, xR = + 0.5_DP
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: U, U_2, C, C_2
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: NodesE,  WeightsE
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: NodesX1, WeightsX1
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: NodesX2, WeightsX2
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: NodesX3, WeightsX3
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: PointsE
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: PointsX1
[…]

### 2024-11-25 SandBox/ProgenitorReader/PlotVX_G15.m

@@ -1,0 +1,93 @@
+close all
+clear all
+
+R_003 = ReadVector( './Executables/R_003ms.dat' );
+R_010 = ReadVector( './Executables/R_010ms.dat' );
+R_050 = ReadVector( './Executables/R_050ms.dat' );
+R_100 = ReadVector( './Executables/R_100ms.dat' );
+R_150 = ReadVector( './Executables/R_150ms.dat' );
+R_250 = ReadVector( './Executables/R_250ms.dat' );
+
+D_003 = ReadVector( './Executables/D_003ms.dat' );
+D_010 = ReadVector( './Executables/D_010ms.dat' );
+D_050 = ReadVector( './Executables/D_050ms.dat' );
+D_100 = ReadVector( './Executables/D_100ms.dat' );
+D_150 = ReadVector( './Executables/D_150ms.dat' );
+D_250 = ReadVector( './Executables/D_250ms.dat' );
+
+fig_1 = figure( 1 );
+
+semilogy( R_003/1.d5, D_003, '-k', 'linewidth', 3 ); hold on
+semilogy( R_010/1.d5, D_010, '-b', 'linewidth', 3 )
+semilogy( R_050/1.d5, D_050, '-r', 'linewidth', 3 )
+semilogy( R_100/1.d5, D_100, '-m', 'linewidth', 3 )
+semilogy( R_150/1.d5, D_150, '-c', 'linewidth', 3 )
+semilogy( R_250/1.d5, D_250, '-g', 'linewidth', 3 )
+set( gca, 'fontsize',   20 )
+set( gca, 'linewidth',  02 )
+xlabel( 'Radius [ km ]', 'fontsize', 20 )
+ylabel( 'Mass Density [ g cm^{-3} ]', 'fontsize', 20 )
+axis( [ 0 200 1.d7 1.d15 ] )
+legend_h...
+  = legend...
+      ( '003 ms', '010 ms', '050 ms', '100 ms', '150 ms', '250 ms',...
+        'location', 'northeast' );
+set( legend_h, 'fontsize', 20 );
+
+print( fig_1, '-dpng', 'MassDensity_VX_G15.png' )
+
+T_003 = ReadVector( './Executables/T_003ms.dat' );
+T_010 = ReadVector( './Executables/T_010ms.dat' );
+T_050 = ReadVector( './Executables/T_050ms.dat' );
[…]

### 2024-11-25 SandBox/StandingAccretionShock_CFA/ApplicationDriver.F90

@@ -1,0 +1,519 @@
+PROGRAM ApplicationDriver
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One, &
+    Two, &
+    Pi, &
+    TwoPi
+  USE ProgramInitializationModule, ONLY: &
+    InitializeProgram, &
+    FinalizeProgram
+  USE ReferenceElementModuleX, ONLY: &
+    InitializeReferenceElementX, &
+    FinalizeReferenceElementX
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+    InitializeReferenceElementX_Lagrange, &
+    FinalizeReferenceElementX_Lagrange
+  USE EquationOfStateModule, ONLY: &
+    InitializeEquationOfState, &
+    FinalizeEquationOfState
+  USE ProgramHeaderModule, ONLY: &
+    iX_B0, &
+    iX_B1, &
+    iX_E0, &
+    iX_E1, &
+    nDimsX
+  USE GeometryComputationModule, ONLY: &
+    ComputeGeometryX
+  USE InitializationModule_Relativistic, ONLY: &
+    InitializeFields_Relativistic
+  USE Euler_SlopeLimiterModule_Relativistic_IDEAL, ONLY: &
+    InitializeSlopeLimiter_Euler_Relativistic_IDEAL, &
+    FinalizeSlopeLimiter_Euler_Relativistic_IDEAL, &
+    ApplySlopeLimiter_Euler_Relativistic_IDEAL
+  USE Euler_PositivityLimiterModule_Relativistic_IDEAL, ONLY: &
+    InitializePositivityLimiter_Euler_Relativistic_IDEAL, &
+    FinalizePositivityLimiter_Euler_Relativistic_IDEAL, &
+    ApplyPositivityLimiter_Euler_Relativistic_IDEAL
+  USE Euler_UtilitiesModule_Relativistic, ONLY: &
+    ComputeFromConserved_Euler_Relativistic, &
+    ComputeTimeStep_Euler_Relativistic
+  USE InputOutputModuleHDF, ONLY: &
+    WriteFieldsHDF, &
+    ReadFieldsHDF, &
+    WriteAccretionShockDiagnosticsHDF
+  USE FluidFieldsModule, ONLY: &
+    uCF, &
+    uPF, &
+    uAF, &
+    uDF
+  USE GeometryFieldsModule, ONLY: &
+    uGF
+  USE Euler_dgDiscretizationModule, ONLY: &
[…]

### 2024-11-25 SandBox/TOV_Star/Poseidon_UtilitiesModule.F90

@@ -1,0 +1,1 @@
+../dgExperiments_Euler_Relativistic_IDEAL/Poseidon_UtilitiesModule.F90

### 2024-11-25 SandBox/TOV_Star/TimeSteppingModule_SSPRK.f90

@@ -1,0 +1,1 @@
+../YahilLattimerCollapse_CFA/TimeSteppingModule_SSPRK.f90

### 2024-11-25 SandBox/TwoMoment_FMC/ApplicationDriver.F90

@@ -1,0 +1,721 @@
+PROGRAM ApplicationDriver
+
+  USE KindModule, ONLY: &
+    DP, SqrtTiny, One, Zero, TwoPi
+  USE ProgramHeaderModule, ONLY: &
+    iX_B0, iX_E0, iX_B1, iX_E1, &
+    iE_B0, iE_E0, iE_B1, iE_E1, &
+    iZ_B0, iZ_E0, iZ_B1, iZ_E1
+  Use FluidFieldsModule, ONLY: &
+    uPF
+  USE GeometryFieldsModule, ONLY: &
+    uGF
+  USE GeometryFieldsModuleE, ONLY: &
+    uGE
+  USE TwoMoment_DiscretizationModule_Collisions_FMC, ONLY: &
+    ComputeIncrement_TwoMoment_Implicit
+  USE TwoMoment_FieldsModule_FMC, ONLY: &
+    uCM, uPM, uAM, uGM
+  USE TwoMoment_InputOutputModule_FMC, ONLY: &
+    ReadTwoMomentFieldsHDF, &
+    WriteTwoMomentFieldsHDF, &
+    WriteFluidFieldsHDF
+  USE TwoMoment_UtilitiesModule_FMC, ONLY: &
+    ComputeFromConserved_TwoMoment_FMC, &
+    HeatFluxTensorComponents_uuu, &
+    ComputeHeatFluxTensorComponents_ddd_Lagrangian, &
+    ComputeHeatFluxTensorComponents_uud_Lagrangian, &
+    Flux_X1, Flux_X2, Flux_X3, ComputeTimeStep_TwoMoment, &
+    ComputeTimeStep_TwoMoment_Realizable
+  USE TwoMoment_OpacityModule_FMC, ONLY: &
+    SetOpacities
+  USE TwoMoment_TimeSteppingModule_FMC, ONLY: &
+    Update_IMEX_RK
+  USE InitializationModule, ONLY: &
+    InitializeFields
+
+  IMPLICIT NONE
+
+  CHARACTER(2)  :: Direction
+  CHARACTER(32) :: Spectrum
+  CHARACTER(32) :: ProgramName
+  CHARACTER(32) :: CoordinateSystem = 'CARTESIAN'
+  CHARACTER(32) :: TimeSteppingScheme
+  LOGICAL       :: UsePositivityLimiter
+  LOGICAL       :: UseEnergyLimiter
[…]

### 2024-11-25 SandBox/TwoMoment_FMC/TwoMoment_DiscretizationModule_Collisions_FMC.F90

@@ -1,0 +1,392 @@
+MODULE TwoMoment_DiscretizationModule_Collisions_FMC
+
+  USE KindModule, ONLY: &
+    DP, Zero, One, Half, Three
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDOFE, &
+    nDOFZ
+  USE FluidFieldsModule, ONLY: &
+    nPF, iPF_V1, iPF_V2, iPF_V3
+  USE GeometryFieldsModuleE, ONLY: &
+    nGE
+  USE GeometryFieldsModule, ONLY: &
+    nGF, iGF_Gm_dd_11, iGF_Gm_dd_22, iGF_Gm_dd_33
+  USE TwoMoment_FieldsModule_FMC, ONLY: &
+    nSpecies, &
+    nCM, iCM_E, iCM_F1, iCM_F2, iCM_F3
+  USE TwoMoment_UtilitiesModule_FMC, ONLY: &
+    EddingtonTensorComponents_dd, ComputeHatMomentsFromConserved
+  USE TwoMoment_OpacityModule_FMC, ONLY: &
+    uOP, iOP_J0, iOP_Chi, iOP_Sigma, nOP
+  USE TwoMoment_ClosureModule, ONLY: &
+    FluxFactor, &
+    EddingtonFactor, &
+    HeatFluxFactor
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: ComputeIncrement_TwoMoment_Implicit
+
+  INTEGER :: iE_B0,    iE_E0
+  INTEGER :: iX_B0(3), iX_E0(3)
+  INTEGER :: nZ(4), nE, nX(3), nE_G, nX_G
+
+  INTEGER , ALLOCATABLE :: nIterations(:,:,:)
+  REAL(DP), ALLOCATABLE :: GX_N(:,:)
+  REAL(DP), ALLOCATABLE :: PF_N(:,:)
+  REAL(DP), ALLOCATABLE :: CM_N(:,:,:,:)
+  REAL(DP), ALLOCATABLE :: dCM_N(:,:,:,:)
+  REAL(DP), ALLOCATABLE :: OP_N(:,:,:,:)
+
+  CONTAINS
+
+  SUBROUTINE ComputeIncrement_TwoMoment_Implicit &
+    ( iZ_B0, iZ_E0, iZ_B1, iZ_E1, dt, GE, GX, U_F, U_M, dU_M)
+
[…]

### 2024-11-25 SandBox/TwoMoment_FMC/TwoMoment_DiscretizationModule_Streaming_FMC.F90

@@ -1,0 +1,2929 @@
+MODULE TwoMoment_DiscretizationModule_Streaming_FMC
+
+  USE KindModule, ONLY: &
+    DP, Zero, Half, One, Two, &
+    SqrtTiny, Pi
+  USE ProgramHeaderModule, ONLY: &
+    nDOFX, &
+    nDOFE, &
+    nDOFZ
+  USE LinearAlgebraModule, ONLY: &
+    MatrixMatrixMultiply, &
+    EigenvaluesSymmetric3
+  USE ReferenceElementModuleX, ONLY: &
+    nDOFX_X1, nDOFX_X2, nDOFX_X3
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+    dLXdX1_q, LX_X1_Dn, LX_X1_Up, &
+    dLXdX2_q, LX_X2_Dn, LX_X2_Up, &
+    dLXdX3_q, LX_X3_Dn, LX_X3_Up
+  USE ReferenceElementModule, ONLY: &
+    nDOF_E, &
+    nDOF_X1, nDOF_X2, nDOF_X3, &
+    Weights_q, &
+    Weights_E, &
+    Weights_X1, Weights_X2, Weights_X3
+  USE ReferenceElementModule_Lagrange, ONLY: &
+    L_E_Dn,  L_E_Up, &
+    dLdE_q, &
+    L_X1_Dn, L_X1_Up, &
+    L_X2_Dn, L_X2_Up, &
+    L_X3_Dn, L_X3_Up, &
+    dLdX1_q, dLdX2_q, dLdX3_q
+  USE MeshModule, ONLY: &
+    MeshE, &
+    MeshX
+  USE GeometryFieldsModuleE, ONLY: &
+    nGE, iGE_Ep1, iGE_Ep2, iGE_Ep3
+  USE GeometryFieldsModule, ONLY: &
+    nGF, iGF_h_1, iGF_h_2, iGF_h_3, &
+    iGF_Gm_dd_11, iGF_Gm_dd_22, iGF_Gm_dd_33, iGF_SqrtGm
+  USE FluidFieldsModule, ONLY: &
+    nPF, iPF_V1, iPF_V2, iPF_V3
+  USE Euler_BoundaryConditionsModule, ONLY: &
+    ApplyBoundaryConditions_Euler
+  USE TwoMoment_FieldsModule_FMC, ONLY: &
+    nSpecies, &
[…]

### 2024-11-25 SandBox/TwoMoment_OrderV/ApplicationDriver_Neutrinos.F90

@@ -1,0 +1,728 @@
+PROGRAM ApplicationDriver_Neutrinos
+
+  USE KindModule, ONLY: &
+    DP, Zero, One, Two, &
+    Pi, TwoPi, SqrtTiny
+  USE UnitsModule, ONLY: &
+    Kilometer, &
+    Millisecond, &
+    MeV
+  USE ProgramHeaderModule, ONLY: &
+    iX_B0, iX_E0, iX_B1, iX_E1, &
+    iE_B0, iE_E0, iE_B1, iE_E1, &
+    iZ_B0, iZ_E0, iZ_B1, iZ_E1
+  USE GeometryFieldsModule, ONLY: &
+    uGF
+  USE GeometryFieldsModuleE, ONLY: &
+    uGE
+  USE FluidFieldsModule, ONLY: &
+    uCF, uPF, uAF, uDF
+  USE Euler_UtilitiesModule_NonRelativistic, ONLY: &
+    ComputeFromConserved_Euler_NonRelativistic
+  USE Euler_SlopeLimiterModule_NonRelativistic_TABLE, ONLY: &
+    ApplySlopeLimiter_Euler_NonRelativistic_TABLE
+  USE Euler_PositivityLimiterModule_NonRelativistic_TABLE, ONLY: &
+    ApplyPositivityLimiter_Euler_NonRelativistic_TABLE
+  USE RadiationFieldsModule, ONLY: &
+    uCR, uPR, uAR, uGR
+  USE InputOutputModuleHDF, ONLY: &
+    WriteFieldsHDF, &
+    ReadFieldsHDF
+  USE TwoMoment_UtilitiesModule, ONLY: &
+    ComputeFromConserved_TwoMoment, &
+    ComputeTimeStep_TwoMoment
+  USE TwoMoment_SlopeLimiterModule, ONLY: &
+    ApplySlopeLimiter_TwoMoment
+  USE TwoMoment_PositivityLimiterModule, ONLY: &
+    ApplyPositivityLimiter_TwoMoment
+  USE TwoMoment_DiscretizationModule_Collisions_Neutrinos, ONLY: &
+    ComputeIncrement_TwoMoment_Implicit
+  USE TwoMoment_NeutrinoMatterSolverModule, ONLY: &
+    InitializeNeutrinoMatterSolverParameters
+  USE TwoMoment_TimeSteppingModule, ONLY: &
+    Update_IMEX_RK
+  USE InitializationModule_Neutrinos, ONLY: &
+    InitializeFields, &
[…]

### 2024-11-25 SandBox/TwoMoment_OrderV/InitializationModule_CCSN.F90

@@ -1,0 +1,249 @@
+MODULE InitializationModule_CCSN
+
+  USE KindModule, ONLY: &
+    DP, Zero
+  USE ProgramHeaderModule, ONLY: &
+    iX_B0, iX_E0, iX_B1, iX_E1, &
+    iE_B0, iE_E0, iE_B1, iE_E1, &
+    nDOFX, nDOFE
+  USE ReferenceElementModuleX, ONLY: &
+    NodeNumberTableX
+  USE MeshModule, ONLY: &
+    MeshX, &
+    NodeCoordinate
+  USE GeometryFieldsModule, ONLY: &
+    uGF, iGF_Phi_N, iGF_Gm_dd_11, iGF_Gm_dd_22, iGF_Gm_dd_33
+  USE FluidFieldsModule, ONLY: &
+    uPF, iPF_D, iPF_V1, iPF_V2, iPF_V3, iPF_E, iPF_Ne, &
+    uCF, iCF_D, iCF_S1, iCF_S2, iCF_S3, iCF_E, iCF_Ne, &
+    uAF, iAF_P, iAF_Ye, iAF_T, iAF_E, iAF_S, iAF_Me, &
+    iAF_Mp, iAF_Mn, iAF_Xp, iAF_Xn, iAF_Xa, iAF_Xh, iAF_Gm
+  USE RadiationFieldsModule, ONLY: &
+    nSpecies, &
+    uPR, nPR, iPR_D, iPR_I1, iPR_I2, iPR_I3, &
+    uCR, nCR, iCR_N, iCR_G1, iCR_G2, iCR_G3
+  USE Euler_UtilitiesModule_NonRelativistic, ONLY: &
+    ComputeConserved_Euler_NonRelativistic
+  USE TwoMoment_UtilitiesModule, ONLY: &
+    ComputeConserved_TwoMoment
+  USE EquationOfStateModule_TABLE, ONLY: &
+    ComputeThermodynamicStates_Primitive_TABLE, &
+    ApplyEquationOfState_TABLE
+  USE UtilitiesModule, ONLY: &
+    Locate, &
+    Interpolate1D_Linear
+  USE ProgenitorModule, ONLY: &
+    ProgenitorType1D, &
+    ReadProgenitor1D
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeFields
+
+CONTAINS
+
+
+  SUBROUTINE InitializeFields( ProgenitorFileName )
+
[…]

### 2024-11-25 SandBox/TwoMoment_Relativistic/InitializationModule.F90

@@ -1,0 +1,347 @@
+MODULE InitializationModule
+
+  USE KindModule, ONLY: &
+    DP, Zero, Half, One, Three, Pi, TwoPi
+  USE ProgramHeaderModule, ONLY: &
+    ProgramName, &
+    nDOFZ, nDOFX, nDOFE, &
+    iX_B0, iX_E0, iX_B1, iX_E1, &
+    iZ_B0, iZ_E0, iZ_B1, iZ_E1
+  USE ReferenceElementModuleX, ONLY: &
+    NodeNumberTableX
+  USE MeshModule, ONLY: &
+    MeshX, &
+    MeshE, &
+    NodeCoordinate
+  USE GeometryFieldsModule, ONLY: &
+    uGF, iGF_Gm_dd_11, iGF_Gm_dd_22, iGF_Gm_dd_33, &
+    iGF_Alpha, iGF_Beta_1, iGF_Beta_2, iGF_Beta_3
+  USE FluidFieldsModule, ONLY: &
+    uPF, iPF_D, iPF_V1, iPF_V2, iPF_V3, iPF_E, iPF_Ne, &
+    uCF, iCF_D, iCF_S1, iCF_S2, iCF_S3, iCF_E, iCF_Ne
+  USE EquationOfStateModule_IDEAL, ONLY: &
+    ComputePressureFromPrimitive_IDEAL
+  USE Euler_UtilitiesModule_Relativistic, ONLY: &
+    ComputeConserved_Euler_Relativistic
+  USE RadiationFieldsModule, ONLY: &
+    nSpecies, &
+    uPR, iPR_D, iPR_I1, iPR_I2, iPR_I3, &
+    uCR, iCR_N, iCR_G1, iCR_G2, iCR_G3
+  USE TwoMoment_UtilitiesModule, ONLY: &
+    ComputeConserved_TwoMoment
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeFields
+
+
+CONTAINS
+
+
+  SUBROUTINE InitializeFields( V_0, LengthScale )
+
+    REAL(DP), INTENT(in) :: V_0(3)
+    REAL(DP), INTENT(in) :: LengthScale
+
+    WRITE(*,*)
+    WRITE(*,'(A2,A6,A)') '', 'INFO: ', TRIM( ProgramName )
+
+    SELECT CASE( TRIM( ProgramName ) )
+
[…]

### 2024-11-25 SandBox/YahilLattimerCollapse/TimeSteppingModule_SSPRK.f90

@@ -1,0 +1,1 @@
+../dgExperiments_Euler_NonRelativistic_IDEAL/TimeSteppingModule_SSPRK.f90

### 2024-11-25 SandBox/dgExperiments_Euler_NonRelativistic_IDEAL/TimeSteppingModule_SSPRK.f90

@@ -1,0 +1,339 @@
+MODULE TimeSteppingModule_SSPRK
+
+  USE KindModule, ONLY: &
+    DP, Zero, One
+  USE ProgramHeaderModule, ONLY: &
+    iX_B0, iX_B1, iX_E0, iX_E1, &
+    nDOFX
+  USE FluidFieldsModule, ONLY: &
+    nCF, iCF_D
+  USE Euler_SlopeLimiterModule_NonRelativistic_IDEAL, ONLY: &
+    ApplySlopeLimiter_Euler_NonRelativistic_IDEAL
+  USE Euler_PositivityLimiterModule_NonRelativistic_IDEAL, ONLY: &
+    ApplyPositivityLimiter_Euler_NonRelativistic_IDEAL
+  USE TimersModule_Euler, ONLY: &
+    TimersStart_Euler, TimersStop_Euler, &
+    Timer_Euler_UpdateFluid
+  USE Euler_dgDiscretizationModule, ONLY: &
+    OffGridFlux_Euler_X1_Inner, &
+    OffGridFlux_Euler_X1_Outer, &
+    OffGridFlux_Euler_X2_Inner, &
+    OffGridFlux_Euler_X2_Outer, &
+    OffGridFlux_Euler_X3_Inner, &
+    OffGridFlux_Euler_X3_Outer
+  USE Euler_TallyModule_NonRelativistic, ONLY: &
+    IncrementOffGridTally_Euler_NonRelativistic
+
+  IMPLICIT NONE
+  PRIVATE
+
+  INTEGER :: nStages_SSPRK
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: c_SSPRK
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: w_SSPRK
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE :: a_SSPRK
+
+  REAL(DP), DIMENSION(:,:,:,:,:),   ALLOCATABLE :: U_SSPRK
+  REAL(DP), DIMENSION(:,:,:,:,:,:), ALLOCATABLE :: D_SSPRK
+
+  LOGICAL :: Verbose
+
+  PUBLIC :: InitializeFluid_SSPRK
+  PUBLIC :: UpdateFluid_SSPRK
+  PUBLIC :: FinalizeFluid_SSPRK
+
+  INTERFACE
+    SUBROUTINE FluidIncrement &
[…]

### 2024-11-25 SandBox/dgExperiments_Euler_Relativistic_IDEAL/SlopeLimiterDiagnostics.f90

@@ -1,0 +1,172 @@
+PROGRAM SlopeLimiterDiagnostics
+
+  USE KindModule, ONLY: &
+    DP, Zero, One, Two, Pi, TwoPi
+  USE ProgramInitializationModule, ONLY: &
+    InitializeProgram, &
+    FinalizeProgram
+  USE ReferenceElementModuleX, ONLY: &
+    InitializeReferenceElementX, &
+    FinalizeReferenceElementX
+  USE ReferenceElementModuleX_Lagrange, ONLY: &
+    InitializeReferenceElementX_Lagrange, &
+    FinalizeReferenceElementX_Lagrange
+  USE EquationOfStateModule, ONLY: &
+    InitializeEquationOfState, &
+    FinalizeEquationOfState
+  USE ProgramHeaderModule, ONLY: &
+    iX_B0, iX_B1, iX_E0, iX_E1, &
+    nDimsX, nDOFX
+  USE GeometryComputationModule, ONLY: &
+    ComputeGeometryX
+  USE InitializationModule_Relativistic, ONLY: &
+    InitializeFields_Relativistic
+  USE Euler_SlopeLimiterModule_Relativistic_IDEAL, ONLY: &
+    InitializeSlopeLimiter_Euler_Relativistic_IDEAL, &
+    FinalizeSlopeLimiter_Euler_Relativistic_IDEAL, &
+    ApplySlopeLimiter_Euler_Relativistic_IDEAL
+  USE Euler_UtilitiesModule_Relativistic, ONLY: &
+    ComputeFromConserved_Euler_Relativistic
+  USE InputOutputModuleHDF, ONLY: &
+    WriteFieldsHDF, &
+    ReadFieldsHDF
+  USE FluidFieldsModule, ONLY: &
+    nCF, nPF, nAF, &
+    uCF, uPF, uAF, &
+    uDF
+  USE GeometryFieldsModule, ONLY: &
+    nGF, uGF
+
+  IMPLICIT NONE
+
+  INCLUDE 'mpif.h'
+
+  CHARACTER(32) :: ProgramName
+  LOGICAL       :: UseSlopeLimiter
+  LOGICAL       :: UseCharacteristicLimiting
+  LOGICAL       :: UseTroubledCellIndicator
+  INTEGER       :: nX(3), bcX(3), nNodes
+  REAL(DP)      :: xL(3), xR(3), Gamma
+
[…]

### 2024-11-25 SandBox/dgExperiments_Euler_Relativistic_IDEAL/TimeSteppingModule_SSPRK.F90

@@ -1,0 +1,370 @@
+MODULE TimeSteppingModule_SSPRK
+
+  USE KindModule, ONLY: &
+    DP, &
+    Zero, &
+    One
+  USE ProgramHeaderModule, ONLY: &
+    iX_B0, &
+    iX_B1, &
+    iX_E0, &
+    iX_E1, &
+    nDOFX
+  USE FluidFieldsModule, ONLY: &
+    nCF
+  USE Euler_SlopeLimiterModule_Relativistic_IDEAL, ONLY: &
+    ApplySlopeLimiter_Euler_Relativistic_IDEAL
+  USE Euler_PositivityLimiterModule_Relativistic_IDEAL, ONLY: &
+    ApplyPositivityLimiter_Euler_Relativistic_IDEAL
+  USE TimersModule_Euler, ONLY: &
+    TimersStart_Euler, &
+    TimersStop_Euler, &
+    Timer_Euler_UpdateFluid
+  USE Euler_dgDiscretizationModule, ONLY: &
+    OffGridFlux_Euler_X1_Inner, &
+    OffGridFlux_Euler_X1_Outer, &
+    OffGridFlux_Euler_X2_Inner, &
+    OffGridFlux_Euler_X2_Outer, &
+    OffGridFlux_Euler_X3_Inner, &
+    OffGridFlux_Euler_X3_Outer
+  USE Euler_TallyModule_Relativistic, ONLY: &
+    IncrementOffGridTally_Euler_Relativistic
+
+  IMPLICIT NONE
+  PRIVATE
+
+  INTEGER :: nStages_SSPRK
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: c_SSPRK
+  REAL(DP), DIMENSION(:),   ALLOCATABLE :: w_SSPRK
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE :: a_SSPRK
+
+  REAL(DP), DIMENSION(:,:,:,:,:),   ALLOCATABLE :: U_SSPRK
+  REAL(DP), DIMENSION(:,:,:,:,:,:), ALLOCATABLE :: D_SSPRK
+
+  PUBLIC :: InitializeFluid_SSPRK
+  PUBLIC :: UpdateFluid_SSPRK
+  PUBLIC :: FinalizeFluid_SSPRK
+
+  INTERFACE
+    SUBROUTINE FluidIncrement &
[…]

### 2024-11-25 SandBox/dgExperiments_M1/GeometryComputationModule_Beta.f90

@@ -1,0 +1,1 @@
+../dgExperiments_Euler/GeometryComputationModule_Beta.f90

### 2024-11-25 SandBox/dgExperiments_M1/TwoMoment_TallyModule.f90

@@ -1,0 +1,173 @@
+MODULE TwoMoment_TallyModule
+
+  USE KindModule, ONLY: &
+    DP, Zero
+  USE ReferenceElementModule, ONLY: &
+    Weights_q
+  USE RadiationFieldsModule, ONLY: &
+    nCR, iCR_N, iCR_G1, iCR_G2, iCR_G3, &
+    nSpecies
+
+  IMPLICIT NONE
+  PRIVATE
+
+  PUBLIC :: InitializeTally_TwoMoment
+  PUBLIC :: FinalizeTally_TwoMoment
+  PUBLIC :: ComputeTally_TwoMoment
+
+  CHARACTER(256)        :: TallyFileName
+  REAL(DP), ALLOCATABLE :: TwoMomentTally(:,:,:)
+
+CONTAINS
+
+
+  SUBROUTINE InitializeTally_TwoMoment &
+    ( iZ_B0, iZ_E0, iZ_B1, iZ_E1, GE, GX, U )
+
+    ! --- {Z1,Z2,Z3,Z4} = {E,X1,X2,X3} ---
+
+    INTEGER,  INTENT(in)           :: &
+      iZ_B0(4), iZ_E0(4), iZ_B1(4), iZ_E1(4)
+    REAL(DP), INTENT(in)           :: &
+      GE(1:,iZ_B1(1):,1:)
+    REAL(DP), INTENT(in)           :: &
+      GX(1:,iZ_B1(2):,iZ_B1(3):,iZ_B1(4):,1:)
+    REAL(DP), INTENT(in)           :: &
+      U (1:,iZ_B1(1):,iZ_B1(2):,iZ_B1(3):,iZ_B1(4):,1:,1:)
+
+    INTEGER :: FileUnit
+
+    ALLOCATE( TwoMomentTally(1:nCR,1:nSpecies,0:1) )
+
+    TallyFileName = '../Output/TwoMomentTally.dat'
+
+    OPEN( NEWUNIT = FileUnit, FILE = TRIM( TallyFileName ) )
+
+    WRITE( FileUnit, '(5(A14,x))' ) 'Time', 'N', 'G1', 'G2', 'G3'
+
+    CLOSE( FileUnit )
+
+    CALL ComputeTally_TwoMoment &
+           ( iZ_B0, iZ_E0, iZ_B1, iZ_E1, GE, GX, U, Time = Zero, &
+             iState_Option = 0, DisplayTally_Option = .FALSE. )
+
+    CALL ComputeTally_TwoMoment &
[…]

### 2024-11-25 SandBox/dgExperiments_M1_GPU/ReferenceElementModule_Lagrange.f90

@@ -1,0 +1,270 @@
+MODULE ReferenceElementModule_Lagrange
+
+  USE KindModule, ONLY: &
+    DP, Half
+  USE ProgramHeaderModule, ONLY: &
+    nNodesE, &
+    nNodesX, &
+    nDOF
+  USE UtilitiesModule, ONLY: &
+    WriteMatrix
+  USE PolynomialBasisModule_Lagrange, ONLY: &
+    L_E,  L_X1,  L_X2,  L_X3, &
+         dL_X1, dL_X2, dL_X3
+  USE ReferenceElementModule_Beta, ONLY: &
+    nDOF_X1, &
+    nDOF_X2, &
+    nDOF_X3, &
+    NodeNumberTable, &
+    NodeNumberTable_X1, &
+    NodeNumberTable_X2, &
+    NodeNumberTable_X3, &
+    NodesE, &
+    NodesX1, &
+    NodesX2, &
+    NodesX3
+
+  IMPLICIT NONE
+  PRIVATE
+
+  INCLUDE 'mpif.h'
+
+  REAL(DP) :: wTime
+  INTEGER,  DIMENSION(:),   ALLOCATABLE, PUBLIC :: i_L_X1
+  INTEGER,  DIMENSION(:),   ALLOCATABLE, PUBLIC :: j_L_X1
+  REAL(DP), DIMENSION(:),   ALLOCATABLE, PUBLIC :: L_X1_Dn_CRS
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE, PUBLIC :: L_X1_Dn
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE, PUBLIC :: L_X1_Up
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE, PUBLIC :: L_X2_Dn
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE, PUBLIC :: L_X2_Up
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE, PUBLIC :: L_X3_Dn
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE, PUBLIC :: L_X3_Up
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE, PUBLIC :: dLdX1_q
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE, PUBLIC :: dLdX2_q
+  REAL(DP), DIMENSION(:,:), ALLOCATABLE, PUBLIC :: dLdX3_q
+
[…]

### 2024-11-25 Workflow/AMReX/GlobalVariables/Settings.py

@@ -1,0 +1,123 @@
+#!/usr/bin/env python3
+
+global tb
+tb = -1.0
+global xLabel
+xLabel = ''
+global yLabel
+yLabel = ''
+global yScale
+yScale = 1.0
+
+global ProblemName
+global FigTitle
+global MovieName
+
+global PlotDirectory
+global PlotBaseName
+
+global Field
+
+global nDirs
+
+global UseLogScale_X
+global UseLogScale_Y
+global UseLogScale_2D
+
+global UsePhysicalUnits
+
+global CoordinateSystem
+
+global PlotEvery
+
+global SSi
+global SSf
+global nSS
+
+
+global MaxLevel
+
+global ShowIC
+global PlotMesh
+
+global Verbose
+
+global UseCustomLimits
+global vmin
+global vmax
+
+global MovieRunTime
+
+global ReferenceBounce
+global StopTime
+
+global ShowRefinement
+global RefinementLevels
+
+global MarkDensityCliff
+
+global DataDirectory
+global DataType
+
+global cellAverageFlag
+
+global nSources
+
+global amr
+
+global SaveFig
+
+# Default Settings
+
+ProblemName = ''
+FigTitle    = ''
+
+PlotDirectory = ''
+PlotBaseName  = ''
+
+Field = ''
+
+nDirs = 1
+
+UseLogScale_X = True
+UseLogScale_Y = True
+UseLogScale_2D = True
+
+UsePhysicalUnits = True
+
+CoordinateSystem = 'cartesian'
+
+PlotEvery = 1
+
+SSi = -1
+SSf = -1
+nSS = -1
+
+MaxLevel = -1
+
+ShowIC   = False
+PlotMesh = False
+
+Verbose  = False
+
+UseCustomLimits = False
+vmin = 2.0
+vmax = 1.0
+
+MovieRunTime = 10
+
+ShowRefinement       = False
+RefinementLocations  = []
+
+ReferenceBounce = False
+
+MarkDensityCliff = False
+
+DataDirectory = ''
+
+nSources = 1
+
+amr = False
+
+
+SaveFig = True

### 2024-11-25 Workflow/AMReX/Utilities/GetPlotData.py

@@ -1,0 +1,50 @@
+#!/usr/bin/env python3
+
+from Utilities.GetFrameData import GetFrameData
+from Utilities.Mesh         import CreateLocations
+from Utilities.Files        import GetFileNumberArray, ChoosePlotFile
+
+#=============================================#
+#   Included Routines
+#
+#   GetPlotData
+#
+#=============================================#
+
+
+ #=============================================#
+#                                               #
+#   GetPlotData                                 #
+#                                               #
+ #=============================================#
+def GetPlotData( PlotDirectory,     \
+                 PlotBaseName,      \
+                 Field,             \
+                 DataType,          \
+                 FrameNumber = -1,  \
+                 argv = ['a'],      \
+                 Verbose = "False"  ):
+
+    FileNumberArray \
+      = GetFileNumberArray( PlotDirectory, PlotBaseName   )
+
+    if FrameNumber == -1:
+        argv = argv
+    else:
+        argv = ['a',str(FrameNumber)]
+
+
+    FileName \
+      = ChoosePlotFile \
+          ( FileNumberArray,    \
+            PlotBaseName   ,    \
+            argv = argv    ,    \
+            DataType = DataType,\
+            Verbose = Verbose )
+
+    File = PlotDirectory + FileName
+
+    Data, DataUnit, X1_C, X2_C, X3_C, dX1, dX2, dX3, Time \
+      = GetFrameData( File, DataType, Field )
+
+    return Data, DataUnit, Time, X1_C, X2_C, X3_C, dX1, dX2, dX3

### 2024-11-25 Workflow/AMReX/Utilities/MovieMaker_Dual.py

@@ -1,0 +1,536 @@
+#!/usr/bin/env python3
+
+import numpy as np
+from sys import argv
+from matplotlib import animation
+from functools import partial
+import matplotlib.pyplot as plt
+plt.style.use( 'publication.sty' )
+
+import GlobalVariables.Settings as gvS
+import GlobalVariables.Units    as gvU
+import Utilities.BounceFinder   as BF
+from Utilities.RefinementBoundaryFinder import FindRefinementBoundaries
+from Utilities.Synchronizer import SynchronizeFrameLists
+from Utilities.FetchData import fetchData_AMReX, fetchData_Native, ReadHeader
+
+
+#=============================================#
+#   Included Routines
+#
+#   MakeMovie
+#   CreateMovie
+#   CreateFrame         - Contains Line Settings -
+#   InitializeFrame
+#   UpdateFrame
+#   fetchData_AMReX
+#   ReadHeader
+#   ApplyAction
+#
+#=============================================#
+
+ #=============================================#
+#                                               #
+#   MakeMovie                                   #
+#                                               #
+ #=============================================#
+def MakeMovie(  FileNumberArray,    \
+                Field,              \
+                DataDirectories,    \
+                Action = 'None'     ):
+
+    global nDirs
+    global nFiles
+
+    # Check if FileNumberArray and DataDirectories are lists
+    if type(FileNumberArray) is list:
+        nFiles = len(FileNumberArray)
+    else:
+        nFiles = 1
+        
+        
+    if type(DataDirectories) is list:
+        nDirs = len(DataDirectories)
+    else:
+        nDirs = 1
+    
+            
+    if type(Field) is list:
+        nFields = len(Field)
+        if nFields == 1:
+            Field = Field[0]
+    else:
+        nFields = 1
+    
+    
+    if  nFiles == nDirs:
+
+        CreateMovie(FileNumberArray,    \
+                    Field,              \
+                    DataDirectories,    \
+                    Action = Action     )
+                                
+    else:
+    
+        msg =  "\n MakeMovie Error \n"
+        msg += "MakeMovie requires the same number of FileNumberArrays \n"
+        msg += "as DataDirectories. One FileNumberArray per DataDirectory \n"
+        msg += "must be passed into the routine."
+        
+        assert(nFiles == nDirs),msg
+
+    return
+
+ #=============================================#
+#                                               #
+#   CreateMovie                                 #
+#                                               #
+ #=============================================#
[…]

### 2024-11-25 Workflow/AMReX/Utilities/RefinementBoundaryFinder.py

@@ -1,0 +1,22 @@
+#!/usr/bin/env python3
+
+
+
+ #=============================================#
+#                                               #
+#   FindRefinementBoundaries                    #
+#                                               #
+ #=============================================#
+def FindRefinementBoundaries( dX ):
+
+    RefinementLocations = []
+    nX = dX.shape[0]
+    cur_width = dX[0]
+    
+    for i in range(nX):
+        if ( dX[i] - cur_width != 0.0 ):
+            cur_width = dX[i]
+            RefinementLocations += [sum(dX[0:i])]
+
+
+    return RefinementLocations

### 2024-11-25 Workflow/AMReX/makeMovie1D_Multi_Sync.py

@@ -1,0 +1,181 @@
+#!/usr/bin/env python3
+
+import numpy as np
+from sys import argv
+import matplotlib.pyplot as plt
+plt.style.use( 'publication.sty' )
+
+
+import GlobalVariables.Settings     as gvS
+import Utilities.BounceFinder       as BF
+from GlobalVariables.Units          import SetSpaceTimeUnits
+
+from Utilities.Files                import GetFileNumberArray
+from Utilities.MakeDataDirectory    import MakeProblemDataDirectory
+from Utilities.MovieMaker_Dual      import MakeMovie
+#from Utilities.BounceFinder     import FindBounce, BounceDensityList, BounceFrameList, BounceTimeList
+
+
+if __name__ == "__main__":
+
+    #### ========== User Input ==========
+
+    # Specify name of problem
+    ProblemName = 'AdiabaticCollapse_XCFC'
+
+    # Specify title of figure
+    gvS.FigTitle = ProblemName
+
+    # Specify directory containing amrex Plotfiles
+    gvS.nDirs = 2
+    
+    PlotDirectories = ['None']*gvS.nDirs
+
+    THORNADO_DIR = '/Users/nickroberts/thornado/'
+    
+    PlotDirectory[0] \
+          = THORNADO_DIR    \
+          + 'SandBox/AdiabaticCollapse_XCFC/Output'
+          
+    PlotDirectory[1] \
+          = THORNADO_DIR    \
+          + 'SandBox/AMReX/Applications/AdiabaticCollapse_XCFC/AdiabaticCollapse_XCFC_AMR_dr0.25km'
+
+
+    gvS.DataType = ['None']*gvS.nDirs
+    gvS.DataType[0] = 'Native'
+    gvS.DataType[1] = 'AMReX'
+
+
+
+    # Specify plot file base name
+    PlotBaseName = ProblemName + '.plt'
+
+    # Specify field to plot
+    Field = 'PF_D'
+
+    # Specify to plot in log-scale
+    gvS.UseLogScale_X  = True
+    gvS.UseLogScale_Y  = True
+    gvS.UseLogScale_2D = False
+
+    # Specify whether or not to use physical units
+    UsePhysicalUnits = True
+
+    # Specify coordinate system (currently supports 'cartesian' and 'spherical')
+    CoordinateSystem = 'spherical'
+
+    # Only use every <plotEvery> plotfile
+    PlotEvery = 1
+
[…]

### 2024-11-25 Workflow/AMReX/makeMovie1D_RelDiff.py

@@ -1,0 +1,170 @@
+#!/usr/bin/env python3
+
+import numpy as np
+from sys import argv
+import matplotlib.pyplot as plt
+plt.style.use( 'publication.sty' )
+
+
+import GlobalVariables.Settings     as gvS
+import Utilities.BounceFinder       as BF
+from GlobalVariables.Units          import SetSpaceTimeUnits
+
+from Utilities.Files                import GetFileNumberArray
+from Utilities.MakeDataDirectory    import MakeProblemDataDirectory
+from Utilities.MovieMaker_Dual      import MakeMovie
+
+
+if __name__ == "__main__":
+
+    #### ========== User Input ==========
+
+    # Specify name of problem
+    ProblemName = 'AdiabaticCollapse_XCFC'
+
+    # Specify title of figure
+    gvS.FigTitle = ProblemName
+
+    # Specify directory containing amrex Plotfiles
+    gvS.nDirs = 2
+    
+    PlotDirectories = ['None']*gvS.nDirs
+
+#    PlotDirectories[0] = '/Users/nickroberts/Downloads/native'
+#    PlotDirectories[1] = '/Users/nickroberts/Downloads/amrex'
+
+#    PlotDirectories[0] = '/Users/nickroberts/thornado/SandBox/AMReX/Applications/AdiabaticCollapse_XCFC'
+#    PlotDirectories[0] = '/Users/nickroberts/thornado/SandBox/AdiabaticCollapse_XCFC/Output'
+    PlotDirectories[0] = '/Users/nickroberts/thornado_clean/thornado/SandBox/AdiabaticCollapse_XCFC/Output'
+    PlotDirectories[1] = '/Users/nickroberts/thornado_clean/thornado/SandBox/AMReX/Applications/AdiabaticCollapse_XCFC'
+    
+    gvS.DataType = ['None']*gvS.nDirs
+    gvS.DataType[0] = 'Native'
+    gvS.DataType[1] = 'AMReX'
+
+    # Specify plot file base name
+    PlotBaseName = ProblemName + '.plt'
+
+    # Specify field to plot
+    Field = 'PF_D'
+
+    # Specify to plot in log-scale
+    gvS.UseLogScale_X  = True
+    gvS.UseLogScale_Y  = True
+    gvS.UseLogScale_2D = False
+
+    # Specify whether or not to use physical units
+    UsePhysicalUnits = True
+
[…]

### 2024-11-25 Workflow/ComputeEffectiveTandChemicalPotentials.m

@@ -1,0 +1,73 @@
+function [MnuEff, TEff] = ComputeEffectiveTandChemicalPotentials(J, E_N, iSpecies, M_matter, T_matter )
+
+BoltzmannConstant =   8.6173e-11;
+
+Tol = 1e-6;
+if (iSpecies == 1)
+    alpha = 1;
+elseif (iSpecies == 2)
+    alpha = -1;
+else
+    error('invalid species');
+end
+
+% y = kT
+y0 = T_matter*BoltzmannConstant;
+
+x0 = M_matter/y0;
+
+
+Converge = 0;
+
+% x = Mnu/kT;
+x = x0;
+
+% N = sum(g_W2_N .* J);
+% E = sum(g_W3_N .* J);
+N = trapz(E_N, J.*E_N.^2);
+E = trapz(E_N, J.*E_N.^3);
+c = N^(4/3)/E;
+
+k = 0;
+MaxIter = 10000;
+while(~Converge && k < MaxIter)
+    k = k + 1;
+    if (iSpecies == 1)
+        exponent = min( max( E_N - x, -100 ), 100 );
+    elseif (iSpecies == 2)
+        exponent = min( max( E_N + x, -100 ), 100 );
+    else
+        error('invalid species');
+    end
+    F = 1.0 ./ ( exp( exponent ) + 1 );
+%     F2 = sum(g_W2_N .* F);
+%     F3 = sum(g_W3_N .* F);
+    F2 = trapz(E_N, F.*E_N.^2);
+    F3 = trapz(E_N, F.*E_N.^3);
+    G = F2^(4/3)/F3;
+    x_new = x - alpha*(G - c);
+    
+    if (abs(x_new - x) < Tol)
+        Converge = 1;
+    end
+    x = x_new;
+end
+if(k >= MaxIter)
+    warning('max iteration');
+end
+if (iSpecies == 1)
+    exponent = min( max( E_N - x, -100 ), 100 );
+elseif (iSpecies == 2)
+    exponent = min( max( E_N + x, -100 ), 100 );
+else
+    error('invalid species');
+end
+F = 1.0 ./ ( exp( exponent ) + 1 );
+% F2 = sum(g_W2_N .* F);
+F2 = trapz(E_N, F.*E_N.^2);
+
+y = (N/F2)^(1/3);
+MnuEff = x*y;
+TEff = y/BoltzmannConstant;
+
+end

### 2024-11-25 Workflow/ComputeRadius.m

@@ -1,0 +1,20 @@
+function [ R ] = ComputeRadius( X1, X2, X3 )
+
+  nR = prod( [ size(X1,1), size(X2,1), size(X3,1) ] );
+  R  = zeros( nR, 1 );
+  
+  iR = 0;
+  for iX3 = 1 : size( X3, 1 )
+  for iX2 = 1 : size( X2, 1 )
+  for iX1 = 1 : size( X1, 1 )
+    
+    iR = iR + 1;
+    
+    R(iR) = sqrt( X1(iX1)^2 + X2(iX2)^2 + X3(iX3)^2 );
+    
+  end
+  end
+  end
+
+end
+

### 2024-11-25 Workflow/ReadGeometryFields.m

@@ -1,0 +1,37 @@
+function...
+  [ Time, X1, X2, X3, uGF_H1, uGF_H2, uGF_H3, uGF_Gm11, uGF_Gm22, uGF_Gm33, uGF_SqrtGm,...
+    uGF_Phi_N, uGF_Alpha, uGF_Psi, uGF_Beta1, uGF_Beta2, uGF_Beta3 ]...
+    = ReadGeometryFields( AppName, FileNumber, Directory )
+
+  if( exist( 'Directory', 'var' ) )
+    DirName = Directory;
+  else
+    DirName = './Output';
+  end
+
+  FileName = [ DirName '/' AppName '_GeometryFields_' sprintf( '%06d', FileNumber ) '.h5' ];
+
+  Time = h5read( FileName, '/Time' );
+  
+  X1   = h5read( FileName, '/Spatial Grid/X1' );
+  X2   = h5read( FileName, '/Spatial Grid/X2' );
+  X3   = h5read( FileName, '/Spatial Grid/X3' );
+  
+  uGF_H1     = h5read( FileName, '/Geometry Fields/Spatial Scale Factor (1)' );
+  uGF_H2     = h5read( FileName, '/Geometry Fields/Spatial Scale Factor (2)' );
+  uGF_H3     = h5read( FileName, '/Geometry Fields/Spatial Scale Factor (3)' );
+
+  uGF_Gm11   = h5read( FileName, '/Geometry Fields/Spatial Metric Component (11)' );
+  uGF_Gm22   = h5read( FileName, '/Geometry Fields/Spatial Metric Component (22)' );
+  uGF_Gm33   = h5read( FileName, '/Geometry Fields/Spatial Metric Component (33)' );
+  uGF_SqrtGm = h5read( FileName, '/Geometry Fields/Sqrt Spatial Metric Determinant' );
+
+  uGF_Phi_N  = h5read( FileName, '/Geometry Fields/Newtonian Potential' );
+  
+  uGF_Alpha  = h5read( FileName, '/Geometry Fields/Lapse Function' );
+  uGF_Psi    = h5read( FileName, '/Geometry Fields/Conformal Factor' );
+  uGF_Beta1  = h5read( FileName, '/Geometry Fields/Shift Vector (1)' );
+  uGF_Beta2  = h5read( FileName, '/Geometry Fields/Shift Vector (2)' );
+  uGF_Beta3  = h5read( FileName, '/Geometry Fields/Shift Vector (3)' );
+  
+end

### 2024-11-25 Workflow/ReadOpacitiesEC.m

@@ -1,0 +1,30 @@
+function...
+  [ Time, E, X1, X2, X3, opEC ]...
+    = ReadOpacitiesEC( AppName, FileNumber, Species, Directory )
+
+  if( exist( 'Species', 'var' ) )
+    SpeciesIndex = Species;
+  else
+    SpeciesIndex = 1;
+  end
+
+  if( exist( 'Directory', 'var' ) )
+    DirName = Directory;
+  else
+    DirName = './Output';
+  end
+
+  FileName = [ DirName '/' AppName '_Opacities_' sprintf( '%06d', FileNumber ) '.h5' ];
+
+  Time = h5read( FileName, '/Time' );
+  E    = h5read( FileName, '/Energy Grid/E' );
+  X1   = h5read( FileName, '/Spatial Grid/X1' );
+  X2   = h5read( FileName, '/Spatial Grid/X2' );
+  X3   = h5read( FileName, '/Spatial Grid/X3' );
+  
+  SpeciesString = [ 'Species_' sprintf( '%02d', SpeciesIndex ) ];
+  
+  opEC = h5read( FileName, [ '/Opacities/' SpeciesString '/Electron Capture Opacities' ] );
+
+end
+
